---
title: "extract_Dem_climate_veg_data_for_map"
author: "Elizabeth Kleynhans"
date: '2022-09-09'
output: html_document
---

## Description

This script generates a data.table that has for each pixel of the province the elevation, slope, aspect, distance to infrastructure, wind in summer and wind in winter. These variables do not change in time (or at least for the purpose of my model I am not changing them). thus with these variables i estimate the constant part of my logisitic equation and create four rasters one lighting ignition, human initions, fire escape and fire spread.  Each raster holds the value of the coefficients that are constant through out time. for example for lightining ignitions a raster is created at the bottom of this file that has the intercept + b1 * elevation or what ever the equation is for each fire regime type. For human caused fires the raster contains the value of 
intercept + b1*elevation + b1*distance to infrastructure or what ever the equation is for that fire regime type. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(mapview)
library(tmap)
library(rpostgis)
library(keyring)


```

#import FRT and change it to a raster for faster extraction

```{r}

 
#Create a provincial raster
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216,
                              xmn = 159587.5, xmx = 1881187.5,
                              ymn = 173787.5, ymx = 1748187.5,
                              crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
                              resolution = c(100, 100),
                              vals = 0)

   
    pts <- data.table(terra::xyFromCell(prov.rast,1:ncell(prov.rast))) #Seems to be faster than rasterTopoints
    pts <- pts[, pixelid:= seq_len(.N)] # add in the pixelid which streams data in according to the cell number = pixelid
    
    pixels <- data.table(V1 = as.integer(prov.rast[]))
    pixels[, pixelid := seq_len(.N)]
    
    pixels<-left_join(pixels, pts)
    setorder(pixels, "pixelid")#sort the pixels table so that pixelid is in order.
  

  #   prov.rast[]<-pixels$pixelid
  #   #sim$rasVelo<-velox::velox(sim$ras)
  #   
  #   #Add the raster_info
  #   ras.extent<-terra::ext(prov.rast)
  #   #TODO: Hard coded for epsg 3005 need to convert to terra?
  #   dbExecute(castordb, glue::glue("INSERT INTO raster_info (name, xmin, xmax, ymin, ymax, ncell, nrow, crs) values ('prov.rast', {ras.extent[1]}, {ras.extent[2]}, {ras.extent[3]}, {ras.extent[4]}, {ncell(prov.rast)}, {nrow(prov.rast)}, '3005');"))
  #   
  # 
   aoi<-terra::ext(prov.rast) #need to check that each of the extents are the same
  # 
  # dbGetQuery(castordb, "Select * from raster_info")
  
```

  

```{r}
#---------------------#
  #Get the FRT----
  #---------------------#

 frt<-getSpatialQuery("SELECT * FROM frt_canada")
 ras.frt <- fasterize::fasterize (frt, prov.rast, field = "Cluster")
 
    if(aoi == terra::ext(ras.frt)){ # need to check that each of the extents are the same
      pixels<-cbind(pixels, data.table(frt= as.numeric(ras.frt[])))
      rm(ras.frt)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }

  #---------------------#
  #Get the elevation----
  #---------------------#
DEM <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\dem\\all_bc\\dem.tif")

 
if(aoi == terra::ext(DEM)){#need to check that each of the extents are the same
      pixels <- cbind(pixels, data.table(dem = as.integer(DEM[]))) # add the ownership to the pixels table
      rm(DEM)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }

# slope
DEM_slope <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\dem\\all_bc\\slope_ha_bc_3005.tif")
if(aoi == terra::ext(DEM_slope)){#need to check that each of the extents are the same
      pixels <- cbind(pixels, data.table(slope = as.integer(DEM_slope[]))) # add the ownership to the pixels table
      rm(DEM_slope)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }

#Aspect
DEM_aspect <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\dem\\all_bc\\aspect_ha_bc_3005.tif")

if(aoi == terra::ext(DEM_aspect)){#need to check that each of the extents are the same
      pixels <- cbind(pixels, data.table(aspect = as.integer(DEM_aspect[]))) # add the ownership to the pixels table
      rm(DEM_aspect)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }


# dist infrastructure
# first calculate the minimum distance to infrastructure. Then save that raster and upload it to the database. Then use that.

dist_rail<- raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_rail.tif")
dist_power<- raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_power.tif")
dist_oil<- raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_oil.tif")
dist_mines<- raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_mines.tif")
dist_urban<- raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_urban.tif")

 inf.rast<- function(rast1, rast2) {
  ifelse(rast1 < rast2, rast1, rast2)
 }

 dist.inf <- overlay(dist_rail, dist_power, fun=inf.rast)
 dist.inf <- overlay(dist.inf, dist_oil, fun=inf.rast)
 dist.inf <- overlay(dist.inf, dist_mines, fun=inf.rast)
 dist.inf <- overlay(dist.inf, dist_urban, fun=inf.rast)

plot(dist.inf)

if(aoi == terra::ext(dist.inf)){#need to check that each of the extents are the same
      pixels <- cbind(pixels, data.table(distinfrastructure = as.integer(dist.inf[]))) # add the ownership to the pixels table
      rm(dist.inf)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }

rm(dist_rail, dist_power, dist_oil, dist_mines, dist_urban)
gc()

# distance to roads
roads_dist <- raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_roads.tif")
if(aoi == terra::ext(roads_dist)){#need to check that each of the extents are the same
      pixels <- cbind(pixels, data.table(distroads = as.integer(roads_dist[]))) # add the ownership to the pixels table
      rm(roads_dist)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }


# summer wind
wind_summer<-raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\rast_summer_wind.tif")


if(aoi == terra::ext(wind_summer)){#need to check that each of the extents are the same
      pixels <- cbind(pixels, data.table(summerwind = as.integer(wind_summer[]))) # add the ownership to the pixels table
      rm(wind_summer)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }

# spring wind

wind_spring<- raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\rast_spring_wind.tif")

if(aoi == terra::ext(wind_spring)){#need to check that each of the extents are the same
      pixels <- cbind(pixels, data.table(springwind = as.integer(wind_spring[]))) # add the ownership to the pixels table
      rm(wind_spring)
      gc()
    }else{
      stop(paste0("ERROR: extents are not the same check -"))
    }

head(pixels)

dat<-pixels

dat<-dat %>% drop_na(dem)
```


```{r}
#Change Aspect to N,S,E,W

library(tidyverse)

dat<- dat %>% 
  mutate(aspect_cardinal = if_else(aspect > 315 & aspect <= 45, "N",
                 if_else(aspect > 45 & aspect <= 135, "E",
                         if_else(aspect > 135 & aspect <= 225, "S",
                                 if_else(aspect > 225 & aspect <= 315, "W", "NA")))))

names(dat)
# create dummy variables for aspect
dat$aspect_N <- ifelse(dat$aspect_cardinal == 'N', 1, 0)
dat$aspect_E <- ifelse(dat$aspect_cardinal == 'E', 1, 0)
dat$aspect_S <- ifelse(dat$aspect_cardinal == 'S', 1, 0)
dat$aspect_W <- ifelse(dat$aspect_cardinal == 'W', 1, 0)
```

### FRT 5
```{r}
frt5<- dat %>% filter(frt==5)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt5_lightning.csv")

model_coef_table_lightning

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_lightning_coef<- model_coef_table_lightning$intercept + 
  model_coef_table_lightning$coef_elevatn * frt5$dem

frt5$logit_P_lightning_coef<-logit_P_lightning_coef

####################################
# PErson ignitions

model_coef_table_person<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT5_person.csv")
model_coef_table_person

logit_P_person_coef<- model_coef_table_person$intercept + 
  model_coef_table_person$coef_log_infr_dist*(log(frt5$distinfrastructure+1))

frt5$logit_P_person_coef<-logit_P_person_coef

##########################
# probability of escape

model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt5_escape.csv")

model_coef_table_escape

logit_P_escape_coef<- model_coef_table_escape$intercept + 
  model_coef_table_escape$coef_elevation*frt5$dem + 
  model_coef_table_escape$coef_dist_infra*frt5$distinfrastructure
  
frt5$logit_P_escape_coef<-logit_P_escape_coef

##################################
# spread probabilities

model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt5_spread.csv")

model_coef_table_spread

# there are some Na values for wind so Ill fill in those values with the average.
table(is.na(frt5$springwind))
frt5$springwind[is.na(frt5$springwind)] <- mean(frt5$springwind, na.rm = TRUE)
# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread_coef<- model_coef_table_spread$intercept + 
  model_coef_table_spread$coef_elevation*frt5$dem +
  model_coef_table_spread$coef_aspect_N*frt5$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt5$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt5$aspect_W +
  model_coef_table_spread$coef_dist_infr*(log(frt5$distinfrastructure+1)) +
  model_coef_table_spread$coef_win_spg*frt5$springwind
  
frt5$logit_P_spread_coef<-logit_P_spread_coef

rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread)
gc()

```

## FRT 7
```{r}
frt7<- dat %>% filter(frt==7)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt7_lightning.csv")

model_coef_table_lightning

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_lightning_coef<- model_coef_table_lightning$intercept

frt7$logit_P_lightning_coef<-logit_P_lightning_coef

#####################
# Ignition Person
model_coef_table_person<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT7_person.csv")

model_coef_table_person

logit_P_person_coef<- model_coef_table_person$intercept + 
  model_coef_table_person$coef_infr_dist*frt7$distinfrastructure

frt7$logit_P_person_coef<-logit_P_person_coef

###################
# escape
model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT7_escape.csv")

model_coef_table_escape

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_escape_coef<- model_coef_table_escape$intercept 

frt7$logit_P_escape_coef<-logit_P_escape_coef

######################
## spread
model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt7_spread.csv")

model_coef_table_spread

logit_P_spread_coef<- model_coef_table_spread$intercept + 
  model_coef_table_spread$coef_slope*frt7$slope +
  model_coef_table_spread$coef_aspect_N*frt7$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt7$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt7$aspect_W +
  model_coef_table_spread$coef_dist_infr*frt7$distinfrastructure

frt7$logit_P_spread_coef<-logit_P_spread_coef

rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread)
gc()


```

## FRT9

```{r}
frt9<- dat %>% filter(frt==9)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt9_lightning.csv")
model_coef_table_lightning
# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_lightning_coef<- model_coef_table_lightning$intercept + 
  model_coef_table_lightning$coef_elevatn*frt9$dem

frt9$logit_P_lightning_coef<-logit_P_lightning_coef
######################################3
# person caused ignitions

model_coef_table_person<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt9_person.csv")
model_coef_table_person

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_person_coef<- model_coef_table_person$intercept + 
  model_coef_table_person$coef_elevatn*frt9$dem  +
  model_coef_table_person$coef_infr_dist*frt9$distinfrastructure


frt9$logit_P_person_coef<-logit_P_person_coef

##################################
# escape
model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_escape.csv")

model_coef_table_escape

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_escape_coef<- model_coef_table_escape$intercept +
  model_coef_table_escape$coef_dist_infra_m*frt9$distinfrastructure

frt9$logit_P_escape_coef<-logit_P_escape_coef

################################
# spread
model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt9_spread.csv")

model_coef_table_spread

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table_spread$intercept +
  model_coef_table_spread$coef_elev*frt9$dem +
  model_coef_table_spread$coef_aspect_N*frt9$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt9$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt9$aspect_W +
  model_coef_table_spread$coef_dist_infr_m*frt9$distinfrastructure

logit_P_spread

frt9$logit_P_spread_coef<-logit_P_spread

rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread)
gc()

```

## FRT10
```{r}
frt10<- dat %>% filter(frt==10)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT10_lightning.csv")

model_coef_table_lightning

logit_P_lightning_coef<- model_coef_table_lightning$intercept + 
  model_coef_table_lightning$coef_elevatn*frt10$dem

frt10$logit_P_lightning_coef<-logit_P_lightning_coef

########################################
# Person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT10_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept
frt10$logit_P_person_coef<-logit_P_person_coef

#################################
# escape
model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt10_escape.csv")

model_coef_table_escape

logit_P_escape<- model_coef_table_escape$intercept + 
  model_coef_table_escape$coef_elevation*frt10$dem +
  model_coef_table_escape$coef_log_infr_dist*log(frt10$distinfrastructure +1)

frt10$logit_P_escape_coef<-logit_P_escape

###########################
# Spread

model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt10_spread.csv")

model_coef_table_spread

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table_spread$intercept +
  model_coef_table_spread$coef_elevation*frt10$dem +
  model_coef_table_spread$coef_slope*frt10$slope +
  model_coef_table_spread$coef_aspect_N*frt10$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt10$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt10$aspect_W +
  model_coef_table_spread$coef_dist_infr*frt10$distinfrastructure

frt10$logit_P_spread_coef<-logit_P_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread, prob_ignition_escape, prob_ignition_lightning, prob_ignition_person, prob_ignition_spread, logit_P_escape, logit_P_lightning, logit_P_person, logit_P_spread)
gc()

```


## FRT 11 

```{r}
frt11<- dat %>% filter(frt==11)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT11_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept

frt11$logit_P_lightning_coef<-logit_P_lightning_coef

##########################
#Person
model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept +
  model_coef_table$coef_log_infr_dist_m*log(frt11$distinfrastructure+1) 

frt11$logit_P_person_coef<-logit_P_person_coef


################################
# Escape

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_escape.csv")

model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_dist_infra_m*frt11$distinfrastructure

frt11$logit_P_escape_coef<-logit_P_escape_coef

##########################
# Spread

table(is.na(frt11$summerwind))
frt11$summerwind[is.na(frt11$summerwind)] <- mean(frt11$summerwind, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt11$slope +
  model_coef_table$coef_aspect_N*frt11$aspect_N +
  model_coef_table$coef_aspect_S*frt11$aspect_S +
  model_coef_table$coef_aspect_W*frt11$aspect_W +
  model_coef_table$coef_dist_infr*frt11$distinfrastructure +
  model_coef_table$coef_wind_summer*frt11$summerwind

frt11$logit_P_spread_coef<-logit_P_spread

```

## FRT 12

```{r}
frt12<- dat %>% filter(frt==12)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT12_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt12$dem

frt12$logit_P_lightning_coef<-logit_P_lightning_coef

##########################
# Person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT12_person.csv")
model_coef_table

#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt12$dem +
  model_coef_table$coef_log_inf_dist*log(frt12$distinfrastructure+1)
  
frt12$logit_P_person_coef<-logit_P_person_coef

##################################
#escape
model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt12_escape.csv")

model_coef_table

logit_P_escape_coef<- model_coef_table$intercept +
  model_coef_table$coef_win_sum*frt12$summerwind + 
  model_coef_table$coef_dist_infr_m*frt12$distinfrastructure

frt12$logit_P_escape_coef<-logit_P_escape_coef

########################
# Spread

table(is.na(frt12$summerwind))
frt12$summerwind[is.na(frt12$summerwind)] <- mean(frt12$summerwind, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt12_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept +
  model_coef_table$coef_elevation*frt12$dem +
  model_coef_table$coef_slope*frt12$slope +
  model_coef_table$coef_log_dist_infra*log(frt12$distinfrastructure+1) +
  model_coef_table$coef_wind_summer*frt12$summerwind

logit_P_spread
frt12$logit_P_spread_coef<-logit_P_spread

gc()



```

## FRT13
```{r}
frt13<- dat %>% filter(frt==13)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT13_lightning.csv")
model_coef_table

#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk

logit_P_lightning_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt13$dem

frt13$logit_P_lightning_coef<-logit_P_lightning_coef

#############################
# person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT13_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt13$dem + 
  model_coef_table$coef_log_inf_dist*log(frt13$distinfrastructure+1)

frt13$logit_P_person_coef<-logit_P_person_coef

################################
#escape

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt13_escape.csv")
model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt13$slope +
  model_coef_table$coef_win_sum*frt13$summerwind +
  model_coef_table$coef_infr_m*frt13$distinfrastructure

frt13$logit_P_escape_coef<-logit_P_escape_coef

##########################
#spread

frt13$summerwind[is.na(frt13$summerwind)] <- mean(frt13$summerwind, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt13_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_elevation*frt13$dem +
  model_coef_table$coef_aspect_N*frt13$aspect_N +
  model_coef_table$coef_aspect_S*frt13$aspect_S +
  model_coef_table$coef_aspect_W*frt13$aspect_W +
  model_coef_table$coef_log_dist_infra*log(frt13$distinfrastructure+1) +
  model_coef_table$coef_wind_summer*frt13$summerwind

logit_P_spread
frt13$logit_P_spread_coef<-logit_P_spread

```

#FRT 14
```{r}
frt14<- dat %>% filter(frt==14)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT14_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept
frt14$logit_P_lightning_coef<-logit_P_lightning_coef

############################
# person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT14_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_log_inf_dist*log(frt14$distinfrastructure+1)

frt14$logit_P_person_coef<-logit_P_person_coef

##############################
#escape  

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt14_escape.csv")
model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elev*frt14$dem +
  model_coef_table$coef_slope*frt14$slope +
  model_coef_table$coef_win_sum*frt14$summerwind +
  model_coef_table$coef_dist_infr_m*frt14$distinfrastructure
  
frt14$logit_P_escape_coef<-logit_P_escape_coef

################################
#spread

frt14$summerwind[is.na(frt14$summerwind)] <- mean(frt14$summerwind, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt14_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_elevation*frt14$dem +
  model_coef_table$coef_slope*frt14$slope +
  model_coef_table$coef_aspect_N*frt14$aspect_N +
  model_coef_table$coef_aspect_S*frt14$aspect_S +
  model_coef_table$coef_aspect_W*frt14$aspect_W +
  model_coef_table$coef_log_dist_infra*log(frt14$distinfrastructure+1) +
  model_coef_table$coef_wind_summer*frt14$summerwind

logit_P_spread
frt14$logit_P_spread_coef<-logit_P_spread

```

## FRT15
```{r}
frt15<- dat %>% filter(frt==15)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT15_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt15$dem

frt15$logit_P_lightning_coef<-logit_P_lightning_coef

################################
# Person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT15_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_infr_dist*frt15$distinfrastructure 

frt15$logit_P_person_coef<-logit_P_person_coef

################################
# escape

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt15_escape.csv")
model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt15$slope +
  model_coef_table$coef_log_infr_ds*log(frt15$distinfrastructure+1)

frt15$logit_P_escape_coef<-logit_P_escape_coef

#################################
# spread
frt15$summerwind[is.na(frt15$summerwind)] <- mean(frt15$summerwind, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt15_spread.csv")
model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt15$slope +
  model_coef_table$coef_aspect_N*frt15$aspect_N +
  model_coef_table$coef_aspect_S*frt15$aspect_S +
  model_coef_table$coef_aspect_W*frt15$aspect_W +
  model_coef_table$coef_log_dist_infra*log(frt15$distinfrastructure+1) +
  model_coef_table$coef_wind_summer*frt15$summerwind

logit_P_spread
frt15$logit_P_spread_coef<-logit_P_spread


rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread, prob_ignition_escape, prob_ignition_lightning, prob_ignition_person, prob_ignition_spread, logit_P_escape, logit_P_lightning, logit_P_person, logit_P_spread)
gc()

table(is.na(frt15$prob_ignition_spread))

```

# now join all the frt's back together. 
```{r}
#frt_all<-rbind(rbind(rbind(rbind(rbind(rbind(rbind(rbind(frt5, frt7), frt9), frt10), frt11), frt12), frt13), frt14), frt15)

frt_all <- do.call("rbind", list(frt5, frt7, frt9, frt10, frt11, frt12, frt13, frt14, frt15))

dim(frt_all)
table(frt_all$frt)
table(pixels$frt)

table(is.na(frt_all$logit_P_lightning_coef ))
table(is.na(frt_all$logit_P_person_coef))
table(is.na(frt_all$logit_P_escape_coef ))
table(is.na(frt_all$logit_P_spread_coef))

frt_const<-frt_all %>% dplyr::select(pixelid, x, y,  frt: springwind, logit_P_lightning_coef:logit_P_spread_coef) %>%
            rename(logit_P_lightning_coef_const =logit_P_lightning_coef,
                   logit_P_person_coef_const=logit_P_person_coef, 
                   logit_P_escape_coef_const=logit_P_escape_coef,
                   logit_P_spread_coef_const=logit_P_spread_coef)


table(frt_all$frt)

names(frt_const)
names(pixels)

rm(frt5, frt7, frt9, frt10, frt11, frt12, frt13, frt14, frt15)

const_coef_data<- left_join(pixels2, frt_const)
table(const_coef_data$frt)

```


```{r}
#Create a provincial raster as a frame for constnat coefficient lightning ignition values
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216,
                              xmn = 159587.5, xmx = 1881187.5,
                              ymn = 173787.5, ymx = 1748187.5,
                              crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
                              resolution = c(100, 100),
                              vals = 0)

   
    pts <- data.table(terra::xyFromCell(prov.rast,1:ncell(prov.rast))) #Seems to be faster than rasterTopoints
    pts <- pts[, pixelid:= seq_len(.N)] # add in the pixelid which streams data in according to the cell number = pixelid
    
    pixels <- data.table(V1 = as.integer(prov.rast[]))
    pixels[, pixelid := seq_len(.N)]
    
    pixels<-left_join(pixels, pts)
    setorder(pixels, "pixelid")#sort the pixels table so that pixelid is in order.
    
    prov.rast[]<-pixels$pixelid
    
    setorder(const_coef_data, "pixelid")
    prov.rast[]<-const_coef_data$logit_P_lightning_coef_const
    
# upload const_coef_lighting_raster to postgres
    
 writeRaster(prov.rast, file=" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\rast_const_coef_lighting.tif", format="GTiff", overwrite=TRUE)
# 
# # run this in R:
 paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', 'C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/rast_const_coef_lighting.tif -t 100x100 rast.const_coef_lightning_ignit | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/castor')
# then copy the output thats between the " " from the above and paste it into the cmd and run that... should show Insert 0  1 lots of times.

 rm(prov.rast, pixels)    
 gc()
 
#############################
 #constant coeffieitn values for human caused ignitions
 
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216,
                              xmn = 159587.5, xmx = 1881187.5,
                              ymn = 173787.5, ymx = 1748187.5,
                              crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
                              resolution = c(100, 100),
                              vals = 0)

  
pixels <- data.table(V1 = as.integer(prov.rast[]))
pixels[, pixelid := seq_len(.N)]
setorder(pixels, "pixelid")#sort the pixels table so that pixelid is in order.
    
prov.rast[]<-pixels$pixelid
    
setorder(const_coef_data, "pixelid")
prov.rast[]<-const_coef_data$logit_P_person_coef_const
    
# upload const_coef_lighting_raster to postgres
    
 writeRaster(prov.rast, file=" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\rast_const_coef_person.tif", format="GTiff", overwrite=TRUE)
# # run this in R:
 paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', 'C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/rast_const_coef_person.tif -t 100x100 rast.const_coef_person_ignit | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/castor')
# then copy the output thats between the " " from the above and paste it into the cmd and run that... should show Insert 0  1 lots of times.

 
#############################
 #constant coeffieitn values for escaped fires
 
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216,
                              xmn = 159587.5, xmx = 1881187.5,
                              ymn = 173787.5, ymx = 1748187.5,
                              crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
                              resolution = c(100, 100),
                              vals = 0)

  
pixels <- data.table(V1 = as.integer(prov.rast[]))
pixels[, pixelid := seq_len(.N)]
setorder(pixels, "pixelid")#sort the pixels table so that pixelid is in order.
    
prov.rast[]<-pixels$pixelid
    
setorder(const_coef_data, "pixelid")
prov.rast[]<-const_coef_data$logit_P_escape_coef_const
    
# upload const_coef_lighting_raster to postgres
    
 writeRaster(prov.rast, file=" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\rast_const_coef_escaped.tif", format="GTiff", overwrite=TRUE)
# # run this in R:
 paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', 'C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/rast_const_coef_escaped.tif -t 100x100 rast.const_coef_escaped_fires | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/castor')
# then copy the output thats between the " " from the above and paste it into the cmd and run that... should show Insert 0  1 lots of times.

 
#############################
 #constant coeffieitn values for spreading fires
 
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216,
                              xmn = 159587.5, xmx = 1881187.5,
                              ymn = 173787.5, ymx = 1748187.5,
                              crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
                              resolution = c(100, 100),
                              vals = 0)

  
pixels <- data.table(V1 = as.integer(prov.rast[]))
pixels[, pixelid := seq_len(.N)]
setorder(pixels, "pixelid")#sort the pixels table so that pixelid is in order.
    
prov.rast[]<-pixels$pixelid
    
setorder(const_coef_data, "pixelid")
prov.rast[]<-const_coef_data$logit_P_spread_coef_const
    
# upload const_coef_lighting_raster to postgres
    
 writeRaster(prov.rast, file=" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\rast_const_coef_spread.tif", format="GTiff", overwrite=TRUE)
# # run this in R:
 paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', 'C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/rast_const_coef_spread.tif -t 100x100 rast.const_coef_spread_fires | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/castor')
# then copy the output thats between the " " from the above and paste it into the cmd and run that... should show Insert 0  1 lots of times.

 
    
```

