---
title: "Probability of ignition from lightning and human caused fires in the Quesnel,
  Williams Lake, and 100-mile House TSA's"
author: "Elizabeth Kleynhans"
date: "2023-02-10"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
require (kableExtra)


```
##

## Goal

The aim of this document is to describe the methods used to created a map of the probability of ignition as a result of lightning and humans, the map of escape and the map of spread. 

# 1.) Obtain data fire data

## Fire ignition and escape data

To create the probability of ignition and probability of spread maps obtained fire ignition point data from the BCGW (https://catalogue.data.gov.bc.ca/dataset/fire-incident-locations-historical). This data contains information on the cause of the fire and the area that the fire burned. Because we only have vegetation data for the years 2002 to 2021, I filtered the ignition point data to those years. For the ignition analysis I separated the ignitions points by cause (human or lighting). For the probability of escape analysis I filtered the data to fires greated than 10ha (fires classified as escaping) and the fires that were 10ha or less were considered as fires that did not manage to escape. 

## Fire spread data

To obtain information on fires that spread I collected fire polygon data from the BCGW (https://catalogue.data.gov.bc.ca/dataset/fire-perimeters-historical). This data has polygons of the areas that burned within BC for each year. For each fire I sampled locations within each fire polygon very 500 x 500km. These I used as my presence points. For my fire absence / available points i created a 2km buffer around each fire polygon and sampled within that area every 500 x 500m. 

# 2.) Split BC up into fire regime types (FRT) 

Erni et al. 2020 (https://cdnsciencepub.com/doi/10.1139/cjfr-2019-0191) statistically classified  Canada into different fire regime types. These fire regime types (FRT) are based on cause of ignition, timing of ignition (seasonality), and fire activity (e.g. fire size). BC is too large and too diverse to run a single statistical model to determine which variables best predict fire ignitions for both lighting and human caused fires. Thus I used the FRT's determined by Erni et al.2020 to run separate statistical models for each FRT. Within BC there are 10 FRT's  (figure 1). 

```{r FRT, echo=FALSE, fig.cap = "Figure 1. Fire regime types overlaping the Quesnel, Williams Lake and 100 Mile House TSA's"}
frt <- getSpatialQuery("SELECT * FROM frt_canada")
frt<-st_transform(frt, 3005) 
frt$Cluster<- as.factor(frt$Cluster)


prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T)
prov.bnd <- st_transform (prov.bnd, 3005)
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ]  
study_area2<-st_transform(prov.bnd, 3005) 

frt.bc = st_intersection(frt, study_area2)

plot(frt.bc["Cluster"])

```

# 3.) Analysis by FRT 

## Fire ignitions

Within each FRT and for each year I determined how many lightning caused and human caused fires had occurred and then I sampled double the number of points in locations where fires had not been observed to start for each ignition cause.

## Fire escape and spread

Fire escape and spread was analysed separately within each FRT. 

# 4.) Determine the climate variables that best predict ignition and non-ignition locations

I extracted maximum temperature, average temperature, total precipitation, and relative humidity for each location from climateBC (http://climatebc.ca/). These variables were extracted for each month between April and September for each point in its relevant year. Because fire ignitions might be more likely after several months of drought or heat or both I also calculated the average of each of these variables over two, three, four, five and six consecutive months. Using the precipitation and temperature data I also calculated monthly drought code following the methods of Bergeron et al. (2010) as this variable has previously been found to be a good predictor of fire (Marchal et al. 2020). 

Separate statistical models including each single climate variable, the averages across several months as well as combinations of temperature and precipitation were fitted for each FRT and ignition cause (lightning or human) (Table 1). Then the models with delta AIC less than 2 were selected and the model within that set that had the highest AUC was selected. The same method was used to determine which climate variables best described fire escape (Table 2) and fire spread (Table 3)

# 5.) Obtain vegetation data and create fuel types

For each year from 2002 vegetation data was extracted from the corresponding VRI for all ignition and non-ignition points, all escape points and all spread points. This VRI data was then used to create the British Columbia provincial Fuel Type Layer used by the BC Wildfire Service. Classification rules used to create this layer can be found in Perrakis et al. (2018) (https://cfs.nrcan.gc.ca/publications?id=39432). This fuel type layer is created using a combination of vegetation data obtained from the VRI and BEC zone information and is a composite measure of vegetation type and structure. Variables such as leading species and percent, crown closure, projected height, years since harvest, years since fire, bec zone and bec subzone are used in classifying the vegetation.  There are ~ 15 fuel types within BC and these fuel types have been shown to accurately predict fire behaviour in wildfire events (Perrakis et al. 2014) and are used to create the Candian Forest Fire Danger Rating System and in the fire behaviour prediction system.

# 6.) Extract elevation, slope and aspect data 

For each point elevation, aspect and slope data was extracted from the Digital Elevation Model of BC (https://www2.gov.bc.ca/gov/content/data/geographic-data-services/topographic-data/elevation/digital-elevation-model).

# 7.) Extract distance to infrastructure and distance to roads

For each point the distance to the nearest road and the nearest infrastructure was calculated. I used the digital roads atlas [Digital Road Atlas (DRA) available from the B.C. Data Catalogue]((https://catalogue.data.gov.bc.ca/dataset/bb060417-b6e6-4548-b837-f9060d94743e)) to determine distance to road. Roads classified as boat, overgrown, decomissioned, ferry routes, non-motorized trails, proposed roads, and pedestrian mall roads were excluded.
Infrastructure such as mines, railways, oil and gas infrastructure, power lines, and urban were extracted and the distance from each point to the nearest infrastructure regardless of type was estimated 

# 8.) Extract wind speed data

Wind speed averaged over 43 years to get an idea of the spring and summer wind speeds experienced in an area was extracted from the Canadian Wind Atlas. These files were acquired from the Wind Atlas from the government of Canada:http://www.windatlas.ca/index-en.php. Spring is represented by MAM (March, April, May). Summer is represented by JJA (representing June, July and August). 

# 8.) Fit lightning ignition models

The final lightning caused ignition models were fitted with the top selected climate variable/s (described above), a variable describing fuel type, and elevation (table 1). 


```{r, model table lightning, echo = F}
stats_model <- data.table (
FRT = c ("5", "7", "9", "10", "11", "12", "13", "14", "15"),

No_Ignits = c(1065, 188, 83, 595, 170, 2544, 10476, 4013, 856), 

Model_Terms = c (
  "ignit ~ mean_PPT05_PPT06_PPT07_PPT08 + fuel type + elev", 
  "ignit ~ mean_RH05_RH06_RH07 + fuel type",
  "ignit ~ Tmax05 + fuel type + elev",
  "ignit ~ mean_Tave07_Tave08_Tave09 + mean_PPT07_PPT08_PPT09 + fuel type + elev",
  "ignit ~ mean_Tmax07_Tmax08_Tmax09 + mean_PPT07_PPT08_PPT09 + fuel type",
  "ignit ~ mean_Tmax07_Tmax08 + fuel type + elev",
  "ignit ~ Tave07 + PPT07 + fuel type + elev",
  "ignit ~ mean_Tave07_Tave08 + fuel type",
  "ignit ~ mean_PPT06_PPT07_PPT08 + fuel type + elev"),
 
AUC = c (0.60, 0.56, 0.62, 0.78, 0.57, 0.63, 0.63, 0.56, 0.69)                            
                             )

kable (stats_model, 
       caption = "Table 1. Model terms and the estimated AUC value for each fire regime type (FRT) as a result of lightning caused ignitions") %>%
  kable_styling (position = "left")
```

# 9.) Fit human caused ignition models

The final human caused ignition models were fitted with the top selected climate variable/s (described above), a variable describing fuel type, elevation, distance to the nearest road and/or distance to the nearest infrastructure (table 2). 


```{r, model table person, echo = F}
stats_model <- data.table (
FRT = c ("5", "7", "9", "10", "11", "12", "13", "14", "15"),

No_Ignits = c(143, 919, 33, 51, 57, 2236, 1949, 4991, 2183), 

Model_Terms = c (
  "ignit ~ mean_PPT06_PPT07 + log(dist_road) + log(dist_infra)",
  "ignit ~ mean_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10 + fuel type + log(dist_road) + dist_infra",
  "ignit ~ Tmax05 + elev + dist_infra",
  "ignit ~ mean_PPT06_PPT07_PPT08_PPT09 + fuel type + log(dist road)",
  "ignit ~ mean_Tave08_Tave09_Tave10 + log(dist_road) + log(dist_infra)",
  "ignit ~ mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10 + fuel type + elev + log(dist road)",
  "ignit ~ mean_Tave07_Tave08_Tave09 + mean_PPT07_PPT08_PPT09 + fuel type + elev + log(dist road) + log(dist infra)",
  "ignit ~ mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10 + fuel type + log(dist road) + log(dist infra)",
  "ignit ~ mean_Tave07_Tave08_Tave09 + mean_PPT07_PPT08_PPT09 + fuel type + log(dist road) + dist infra"),
 
AUC = c (0.79, 0.77, 0.77, 0.84, 0.84, 0.82, 0.85, 0.81, 0.87)                            
                             )

kable (stats_model, 
       caption = "Table 2. Model terms and the estimated AUC value for each fire regime type (FRT) as a result of human caused ignitions") %>%
  kable_styling (position = "left")
```


Using the models outlined in table 1 a probability of ignition by lightning map was created (figure 2). Data for this map was extracted at a scale of 400 x 400m. Weather, elevation, vegetation, distance to road and distance to infrastructure data was extracted at the center of each pixel. After the models were fitted to each point the data was rasterized. 


```{r echo=FALSE, fig.cap = "Figure 2. Probability of lightning ignition for BC"}

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

lightning.ignit_2021 <- pgGetRast(conn, c("rast", "prob_lightning_ignit_bc_2021"))

dbDisconnect(conn)
#lightning.ignit<-getSpatialQuery("SELECT * FROM #rast.prob_lightning_ignit_quesnel_williamsl_100mile")


plot(lightning.ignit_2021)
```

```{r echo=FALSE, fig.cap = "Figure 3. Probability of human ignition for BC"}

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

human.ignit_2021 <- pgGetRast(conn, c("rast", "prob_human_ignit_bc_2021"))

dbDisconnect(conn)
#lightning.ignit<-getSpatialQuery("SELECT * FROM #rast.prob_lightning_ignit_quesnel_williamsl_100mile")


plot(human.ignit_2021)
```

Following Barros et al. 2021 the lightnin and human caused fire rasters are joined together to create a single ignition layer. The following equation is used to combine the two rasters P(Igit) = P(lightning) x (1-P(human)) + P(human) x (  1-P(lightning)). 

```{r}
prob_ignit<-(lightning.ignit_2021 * (1-human.ignit_2021)) + (human.ignit_2021 * (1-lightning.ignit_2021))

plot(prob_ignit)
```


# 10.) Fit fire escape models


```{r, model table escape, echo = F}
stats_model <- data.table (
FRT = c ("5", "7", "9", "10", "11", "12", "13", "14", "15"),

No_Escape = c(266, 204, 64, 114, 86, 461, 1097, 558, 150), 

Model_Terms = c (
  "escape ~ PPT05 + fuel type + elev + log(dist_infra)", 
  "escape ~ PPT03 + log(dist_infra)",
  "escape ~ Tave05 + log(dist_road)",
  "escape ~ mean_Tave05_Tave06_Tave07_Tave08 + mean_PPT05_PPT06_PPT07_PPT08 + log(dist_road) + dist_infra",
  "escape ~ Tave09 + log(dist_road) + log(dist_infra)",
  "escape ~ mean_PPT04_PPT05_PPT06 + fuel type + slope + wind_summer + log(dist_road) + log(dist_infra)",
  "escape ~ Tave09 + fuel type + slope + elev + wind_summer+ log(dist_road) + log(dist_infra)",
  "escape ~ mean_PPT05_PPT06 + fuel type + wind_summer + log(dist_road) + log(dist_infra)",
  "escape ~ PPT04 + fuel type + slope + dist_infra"),
 
AUC = c (0.65, 0.60, 0.73, 0.67, 0.76, 0.72, 0.72, 0.62, 0.75)                            
                             )

kable (stats_model, 
       caption = "Table 3. Model terms and the estimated AUC value for each fire regime type (FRT) as a result of fires that escaped (grew > 10ha) between the years 2002 and 2021") %>%
  kable_styling (position = "left")
```

```{r echo=FALSE, fig.cap = "Figure 5. Probability of escape for BC"}

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

escape_2021 <- pgGetRast(conn, c("rast", "prob_escape_bc_2021"))

dbDisconnect(conn)
#lightning.ignit<-getSpatialQuery("SELECT * FROM #rast.prob_lightning_ignit_quesnel_williamsl_100mile")


plot(escape_2021)
```


# 10.) Fit fire spread models


```{r, model table spread, echo = F}
stats_model <- data.table (
FRT = c ("5", "7", "9", "10", "11", "12", "13", "14", "15"),

No_Spread = c(15671, 2631, 5753, 12403, 24861, 67758, 46824, 41645, 1029), 

Model_Terms = c (
  "spread ~ lat + long + PPT07 + fuel type + elev + aspect + wind_spring + dist_road + dist_infra", 
  "spread ~ lat + long + mean_Tave04_Tave05_Tave06 + mean_PPT04_PPT05_PPT06 + fuel type + elev + aspect + wind_spring + log(dist_road) + dist_infra",
  "spread ~ lat + long + mean_Tave04_Tave05_Tave06 + mean_PPT04_PPT05_PPT06 + fuel type + aspect + log(dist_road)",
  "spread ~ lat + long + mean_Tmax05_Tmax06_Tmax07_Tmax08 + mean_PPT05_PPT06_PPT07_PPT08 + fuel type + aspect + wind_spring + dist_road + dist_infra",
  "spread ~ long + RH08 + PPT08 + fuel type + elev + aspect + wind_spring + dist_road",
  "spread ~ lat + long + mean_Tmax05_Tmax06_Tmax07_Tmax08 + mean_PPT05_PPT06_PPT07_PPT08 + fuel type + elev + aspect + wind_summer + log(dist_road) + log(dist_infra)",
  "spread ~ lat + long + mean_PPT05_PPT06_PPT07_PPT08 + fuel type + elev + aspect + wind_summer + log(dist_road) + log(dist_infra)",
  "spread ~ lat + long + mean_PPT05_PPT06_PPT07_PPT08 + fuel type + elev + aspect + wind_summer + log(dist_road) + log(dist_infra)",
  "spread ~ lat + long + PPT05 + fuel type + elev + aspect + wind_summer + log(dist_infra)"),
 
AUC = c (0.68, 0.82, 0.67
         , 0.84, 0.69, 0.77, 0.74, 0.84, 0.77)                            
                             )

kable (stats_model, 
       caption = "Table 4. Model terms and the estimated AUC value for each fire regime type (FRT). This model compares the attributes of the landscape in which spread occured to areas adjacent where spread did not occur.") %>%
  kable_styling (position = "left")
```

```{r echo=FALSE, fig.cap = "Figure 5. Probability of escape for BC"}

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

escape_2021 <- pgGetRast(conn, c("rast", "prob_escape_bc_2021"))

dbDisconnect(conn)
#lightning.ignit<-getSpatialQuery("SELECT * FROM #rast.prob_lightning_ignit_quesnel_williamsl_100mile")


plot(escape_2021)
```