---
title: "Fire statistics per area"
author: "Elizabeth Kleynhans"
date: "2023-02-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
require (sf)
require (raster)
require (dplyr)
library(bcdata)
library(ggplot2)

```

The point of this script is to summarize the fire statistics in each FRT. In Erni et al. 2020 there is a summary table (Table A2) that descirbes fire attributes and metrics of each Fire Regime Type. For example it has the size of the area, the population in that area, the average fire size (ha) The Frequency of fires, Burn Rate, proportion of fires that occur in spring and summer and proportion of fires that area cuased by humans versus lightning. this script attemps to get similar metrics for the FRT's in BC and summaries for those area in BC.

```{r ignitions}

ignit<-try(
  bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_INCIDENTS_SP") %>%
    filter(FIRE_YEAR > 2001) %>%
    filter(FIRE_TYPE == "Fire") %>%
    collect()
)

# first join the ignition points to frt so that I can see whether different frt react differently i.e. whether some are better than others.
frt <- st_read ( dsn = "D:\\Fire\\fire_data\\Fire_Regime_Types\\FRT\\FRT_Canada.shp", stringsAsFactors = T) # Read simple features from file or person_22aabase, or retrieve layer names and their geometry type(s)
st_crs(frt) #Retrieve coordinate reference system from sf or sfc object
frt<-st_transform(frt, 3005) #transform coordinate system to 3005 - that for BC, Canada

#get provincial boundary for clipping the layers to the area of interest
prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
crs(prov.bnd)# this one needs to be transformed to 3005
bc.bnd <- st_transform (prov.bnd, 3005) #Transform coordinate system
st_crs(bc.bnd)

#Clip FRT here
frt_clipped<-st_intersection(bc.bnd, frt)
#plot(st_geometry(frt_clipped), col=sf.colors(10,categorical=TRUE))
length(unique(frt_clipped$Cluster))
frt_sf<-st_as_sf(frt_clipped)

fire.ignt.frt <- st_join(ignit, frt_clipped)
table(fire.ignt.frt$Cluster)
table(is.na(fire.ignt.frt$Cluster))

# change any ignition points in FRT =3 to frt=5
fire.ignt.frt$Cluster[fire.ignt.frt$Cluster ==3] <- 5
fire.ignt.frt$ig_mnth<-stringi::stri_sub(fire.ignt.frt$IGNITION_DATE,6,7)
```

```{r}
# proportion of cause in each FRT

dat_for_erni<-fire.ignt.frt %>% filter(CURRENT_SIZE>=9)
table(dat_for_erni$FIRE_CAUSE, dat_for_erni$Cluster)

#
table(dat_for_erni$ig_mnth, dat_for_erni$Cluster)
dat_for_erni$ig_mnth<- as.numeric(as.character(dat_for_erni$ig_mnth))

dat_for_erni$Cluster<-as.character(dat_for_erni$Cluster)

fire_cause_by_area<-dat_for_erni %>% filter(FIRE_CAUSE !="Unknown") %>% 
  group_by(Cluster, FIRE_CAUSE) %>%
  summarize(sum_area=sum(CURRENT_SIZE))
print(fire_cause_by_area,n=30)

ggplot(fire_cause_by_area, aes(x=Cluster, y=sum_area, fill=FIRE_CAUSE))+
  geom_col(position = "dodge")

fire_cause_by_mnth<-dat_for_erni %>%
  group_by(Cluster, ig_mnth) %>%
  summarize(sum_area=sum(CURRENT_SIZE))

ggplot(fire_cause_by_mnth, aes(x=ig_mnth, y=sum_area)) +
  geom_col() + 
  xlim(4, 10) +
  facet_grid(~Cluster)

fire_cause_by_mnth_spring<-dat_for_erni %>% 
  filter(ig_mnth %in% c(4, 5, 6)) %>%
  group_by(Cluster) %>%
  summarize(sum_area=sum(CURRENT_SIZE))
print(fire_cause_by_mnth_spring)

fire_cause_by_mnth_summer<-dat_for_erni %>% 
  filter(ig_mnth %in% c(7, 8, 9)) %>%
  group_by(Cluster) %>%
  summarize(sum_area=sum(CURRENT_SIZE))
print(fire_cause_by_mnth_summer)



total_spring<-dat_for_erni %>% dplyr::filter(ig_month %in% c(4, 5, 5))
```

