---
title: "Probability_of_spread_varification"
author: "Elizabeth Kleynhans"
date: "2023-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source(here::here("R/functions/R_Postgres.R"))
library (kableExtra)
library(tidyverse)
require (sf)
require (RPostgreSQL)
require (rpostgis)
require (fasterize)
require (raster)
require (dplyr)
library(bcdata)
library(SpaDES.tools)
library(terra)
library(quickPlot)
library(data.table)
library(ggplot2)
library(SpaDES.addins)
library(SpaDES)
library(SpaDES.core)

```

## Validating fire spread map

Following methods outlined in Johnson et. al. (2006) Resource selection functions based on use-availability data: Theoretical motivation and evaluation methods.Journal of wildlife management 70: 347-357. I will test whether my ignition points are reasonably estimated by my logistic regression equation. Basically, the idea is to take my probability of ignition map and bin the predicted probabilities into bins. Then weight these bins by the amount of area they cover on the maps. by multiplying the mid point of the probability bin by its area we can estimate the proportion of ignition points we expect to fall in that bin. Then using an independent data set (such as 2022 ignition points) we can check whether our expected number of ignition points actually lines up with our actual data. if the two match then by ploting predicted proportion of igntions in each bin by actual proportion of igntions in each bin I should see a line that has a slope of 1 and intercept of 0. If I get this it indicates that my model is proportional to the probability of use. 

This is what the paper says: 

"First,  assess  the  slope  of  the  regression  line  for  a  significant difference   from   a   slope   of   zero   where   use   would   equal availability   and   therefore   indicate   that   the   model   is   not different  from  that  of  a  random  or  neutral  model.  Second, assess whether the slope is different from 1.0, which is the slope expected for a model that is proportional to the probability of use.  Third,  assess  the  constant  for  an  intercept  of  zero,  the intercept  expected  for  a  model  that  is  approximately  proportional to probability of use. And finally, use both the R2 of the model and Chi2 goodness-of-fit test to assess fit. A model that was  proportional  to  probability  of  use  would  have  a  slope different from 0, but not different from 1, an intercept of 0, and a high R2 value with a nonsignificant Chi2 goodness-of-fit value.Finally, chi2 tests for each observed and expected proportion can be used to determine in which RSF bins the observed frequency differs from expected. If these conditions are not satisfied, the user  might  consider  revisiting  the  process  starting  at  step  3 (reclassify the RSF using a different model), rebinning the RSF values,  or  estimating  a  model  with  different  environmental factors".

#########
Import spread raster and bin the probabilities of spread. Then calculate the area on the map within each bin

```{r}
spread.ras<-raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\rast_spread_2001.tif")

crs(spread.ras)
raster::crs(spread.ras) <- "EPSG:3005"

# this next step may not be neccessary but here I change all NA values into zero. Then I cut out the boarder of BC to remove the zero's in the ocean. I did this because I think some areas on land are classified as NA when they should be zero e.g. because they are water. 
# replacing NA's by zero
spread.ras[is.na(spread.ras[])] <- 0 

#get provincial boundary for clipping the layers to the area of interest
prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
crs(prov.bnd)# this one needs to be transformed to 3005
bc.bnd <- st_transform (prov.bnd, 3005) #Transform coordinate system
st_crs(bc.bnd)

bc.bnd<-sf::st_as_sf(bc.bnd) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(bc.bnd))
r3 <- mask(r2, bc.bnd)
spread.ras<-r3
plot(spread.ras)


rm(r2, r3)

```

# Predict RSF values and reclassify pixels into ordinal classes or rank bins of a specified number
```{r}
x<- as.data.frame(spread.ras)
hist(x$rast_spread_2001)
y_alt<-x %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt$x_bin)

y <- y_alt %>% drop_na()
plot(y$x_bin)
y2<-as.data.frame(table(y$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2$midpoint <- sapply(y2$Var1, get_midpoint)
y2$wi_Ai<- y2$midpoint * y2$Freq
y2$Ui<- y2$wi_Ai/sum(y2$wi_Ai)
y2<- y2 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2$bins, y2$Area)
plot(y2$bins, y2$Ui)
```


## Getting data from an independent data set
# 6.) Count the number of used observations from an independent data set that fall in each RSF bin. 

For this I will extract the probability of ignition points from my fire map at each of the points

# import spread polygons for 2022
```{r}
fire_bounds_hist<-try(
  bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_FIRE_POLYS_SP") %>%
    filter(FIRE_YEAR == 2001) %>%
    collect()
)

table(fire_bounds_hist$FIRE_YEAR)

names(fire_bounds_hist)
hist(fire_bounds_hist$FIRE_SIZE_HECTARES)
fire_bounds_hist2<-fire_bounds_hist %>% filter(FIRE_SIZE_HECTARES>10)
dim(fire_bounds_hist)
dim(fire_bounds_hist2)
```


```{r}
foo_sp<-as(fire_bounds_hist2,"Spatial")
samp_points <- spsample (foo_sp, cellsize = c (1000, 1000), type = "regular")
samp_points_new <- data.frame (matrix (ncol = 2, nrow = nrow (samp_points@coords))) # add 'data' to the points
colnames (samp_points_new) <- c ("pttype","year")
samp_points_new$pttype <- 1
samp_points_new$year<-2001
      
sampled_points <- SpatialPointsDataFrame (samp_points, data = samp_points_new)
sampled_points_sf<-st_as_sf(sampled_points)
      
##########################

test<-cbind(sampled_points_sf, st_coordinates(sampled_points_sf))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)
#crs(pointCoordinates) #No CRS when a dataframe

##Extract spread values from stacked layer
rasValue2=raster::extract(spread.ras, pointCoordinates)
head(rasValue2)
str(rasValue2) #200298 values
str(sampled_points_sf)#200298 values

#Append new information
sampled_points_sf1<-cbind(sampled_points_sf, rasValue2)
head(sampled_points_sf1)

table(is.na(sampled_points_sf1$rasValue2))

breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2$bins)), ","))))
sampled_points_sf1<-sampled_points_sf1 %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3<-as.data.frame(table(sampled_points_sf1$points_bin))
y2$used_obs<-y3$Freq

y2$expected_no_obs<-sum(y2$used_obs)*y2$Ui

ggplot(data=y2) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2$prop_used<-y2$used_obs/(sum(y2$used_obs))
y2$prop_expected<-y2$expected_no_obs/(sum(y2$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0

p_bc <- ggplot(data=y2, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_bc

Xsq<-chisq.test(y2$used_obs, p=y2$prop_expected, simulate.p.value = TRUE)  
Xsq

my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

```

# Get FRT data

```{r}
# first join the spread points to frt so that I can see whether different frt react differently i.e. whether some are better than others.
frt <- st_read ( dsn = "D:\\Fire\\fire_data\\Fire_Regime_Types\\FRT\\FRT_Canada.shp", stringsAsFactors = T) # Read simple features from file or person_22aabase, or retrieve layer names and their geometry type(s)
st_crs(frt) #Retrieve coordinate reference system from sf or sfc object
frt<-st_transform(frt, 3005) #transform coordinate system to 3005 - that for BC, Canada

#get provincial boundary for clipping the layers to the area of interest
prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
crs(prov.bnd)# this one needs to be transformed to 3005
bc.bnd <- st_transform (prov.bnd, 3005) #Transform coordinate system
st_crs(bc.bnd)

#Clip FRT here
frt_clipped<-st_intersection(bc.bnd, frt)
#plot(st_geometry(frt_clipped), col=sf.colors(10,categorical=TRUE))
length(unique(frt_clipped$Cluster))
frt_sf<-st_as_sf(frt_clipped)

fire.spread.frt <- st_join(sampled_points_sf1, frt_clipped)
table(fire.spread.frt$Cluster)
table(is.na(fire.spread.frt$Cluster))

# change any ignition points in FRT =3 to frt=5
fire.spread.frt$Cluster[fire.spread.frt$Cluster ==3] <- 5

# plotting points on raster to check they are still correct
spread_pts <- rasterToPoints(spread.ras, spatial = TRUE)
# Then to a 'conventional' dataframe
spread_pts_df  <- data.frame(spread_pts)

ggplot() +
 geom_raster(data = spread_pts_df , aes(x = x, y = y, fill = rast_spread_2001)) +
  geom_sf(data=fire.spread.frt)

```


# FRT 5
```{r}

# first work out proportion of habitat types across the landscape
frt5<-frt_clipped %>% filter(Cluster %in% c(3,5))
frt5<-sf::st_as_sf(frt5) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt5))
r3 <- mask(r2, frt5)
plot(r3)

x_frt5<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt5<-x_frt5 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt5$x_bin)

y5 <- y_alt5 %>% drop_na()
plot(y5$x_bin)
y2_frt5<-as.data.frame(table(y5$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt5$midpoint <- sapply(y2_frt5$Var1, get_midpoint)
y2_frt5$wi_Ai<- y2_frt5$midpoint * y2_frt5$Freq
y2_frt5$Ui<- y2_frt5$wi_Ai/sum(y2_frt5$wi_Ai)
y2_frt5<- y2_frt5 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt5$bins, y2_frt5$Area)

# now extract probabilty of ignition from fires points in FRT5
## Start here!

frt5_spread<-fire.spread.frt %>% filter(Cluster==5)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt5$bins)), ","))))
frt5_spread<-frt5_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt5<-as.data.frame(table(frt5_spread$points_bin))
y2_frt5$used_obs<-y3_frt5$Freq
y2_frt5$expected_no_obs<-sum(y2_frt5$used_obs)*y2_frt5$Ui


ggplot(data=y2_frt5) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt5$prop_used<-y2_frt5$used_obs/(sum(y2_frt5$used_obs))
y2_frt5$prop_expected<-y2_frt5$expected_no_obs/(sum(y2_frt5$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt5)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt5 <- ggplot(data=y2_frt5, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt5

Xsq<-chisq.test(y2_frt5$used_obs, p=y2_frt5$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```

# FRT 7
```{r}

# first work out proportion of habitat types across the landscape
frt7<-frt_clipped %>% filter(Cluster == 7)
frt7<-sf::st_as_sf(frt7) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt7))
r3 <- mask(r2, frt7)
plot(r3)

x_frt7<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt7<-x_frt7 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt7<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt7$midpoint <- sapply(y2_frt7$Var1, get_midpoint)
y2_frt7$wi_Ai<- y2_frt7$midpoint * y2_frt7$Freq
y2_frt7$Ui<- y2_frt7$wi_Ai/sum(y2_frt7$wi_Ai)
y2_frt7<- y2_frt7 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt7$bins, y2_frt7$Area)

# now extract probabilty of ignition from fires points in frt7
## Start here!

frt7_spread<-fire.spread.frt %>% filter(Cluster==7)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt7$bins)), ","))))
frt7_spread<-frt7_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt7<-as.data.frame(table(frt7_spread$points_bin))
y2_frt7$used_obs<-y3_frt7$Freq
y2_frt7$expected_no_obs<-sum(y2_frt7$used_obs)*y2_frt7$Ui


ggplot(data=y2_frt7) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt7$prop_used<-y2_frt7$used_obs/(sum(y2_frt7$used_obs))
y2_frt7$prop_expected<-y2_frt7$expected_no_obs/(sum(y2_frt7$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt7)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt7 <- ggplot(data=y2_frt7, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt7

Xsq<-chisq.test(y2_frt7$used_obs, p=y2_frt7$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```

# FRT 9
```{r}

# first work out proportion of habitat types across the landscape
frt9<-frt_clipped %>% filter(Cluster == 9)
frt9<-sf::st_as_sf(frt9) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt9))
r3 <- mask(r2, frt9)
plot(r3)

x_frt9<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt7<-x_frt9 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt9<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt9$midpoint <- sapply(y2_frt9$Var1, get_midpoint)
y2_frt9$wi_Ai<- y2_frt9$midpoint * y2_frt9$Freq
y2_frt9$Ui<- y2_frt9$wi_Ai/sum(y2_frt9$wi_Ai)
y2_frt9<- y2_frt9 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt9$bins, y2_frt9$Area)

# now extract probabilty of ignition from fires points in frt9
## Start here!

frt9_spread<-fire.spread.frt %>% filter(Cluster==9)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt9$bins)), ","))))
frt9_spread<-frt9_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt9<-as.data.frame(table(frt9_spread$points_bin))
y2_frt9$used_obs<-y3_frt9$Freq
y2_frt9$expected_no_obs<-sum(y2_frt9$used_obs)*y2_frt9$Ui


ggplot(data=y2_frt9) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt9$prop_used<-y2_frt9$used_obs/(sum(y2_frt9$used_obs))
y2_frt9$prop_expected<-y2_frt9$expected_no_obs/(sum(y2_frt9$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt9)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt9 <- ggplot(data=y2_frt9, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt9

Xsq<-chisq.test(y2_frt9$used_obs, p=y2_frt9$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```

# FRT 10
```{r}

# first work out proportion of habitat types across the landscape
frt10<-frt_clipped %>% filter(Cluster == 10)
frt10<-sf::st_as_sf(frt10) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt10))
r3 <- mask(r2, frt10)
plot(r3)

x_frt10<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt7<-x_frt10 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt10<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt10$midpoint <- sapply(y2_frt10$Var1, get_midpoint)
y2_frt10$wi_Ai<- y2_frt10$midpoint * y2_frt10$Freq
y2_frt10$Ui<- y2_frt10$wi_Ai/sum(y2_frt10$wi_Ai)
y2_frt10<- y2_frt10 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt10$bins, y2_frt10$Area)

# now extract probabilty of ignition from fires points in frt10
## Start here!

frt10_spread<-fire.spread.frt %>% filter(Cluster==10)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt10$bins)), ","))))
frt10_spread<-frt10_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt10<-as.data.frame(table(frt10_spread$points_bin))
y2_frt10$used_obs<-y3_frt10$Freq
y2_frt10$expected_no_obs<-sum(y2_frt10$used_obs)*y2_frt10$Ui


ggplot(data=y2_frt10) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt10$prop_used<-y2_frt10$used_obs/(sum(y2_frt10$used_obs))
y2_frt10$prop_expected<-y2_frt10$expected_no_obs/(sum(y2_frt10$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt10)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt10 <- ggplot(data=y2_frt10, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt10

Xsq<-chisq.test(y2_frt10$used_obs, p=y2_frt10$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```

# FRT 11
```{r}

# first work out proportion of habitat types across the landscape
frt11<-frt_clipped %>% filter(Cluster == 11)
frt11<-sf::st_as_sf(frt11) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt11))
r3 <- mask(r2, frt11)
plot(r3)

x_frt11<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt7<-x_frt11 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt11<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt11$midpoint <- sapply(y2_frt11$Var1, get_midpoint)
y2_frt11$wi_Ai<- y2_frt11$midpoint * y2_frt11$Freq
y2_frt11$Ui<- y2_frt11$wi_Ai/sum(y2_frt11$wi_Ai)
y2_frt11<- y2_frt11 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt11$bins, y2_frt11$Area)

# now extract probabilty of ignition from fires points in frt11
## Start here!

frt11_spread<-fire.spread.frt %>% filter(Cluster==11)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt11$bins)), ","))))
frt11_spread<-frt11_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt11<-as.data.frame(table(frt11_spread$points_bin))
y2_frt11$used_obs<-y3_frt11$Freq
y2_frt11$expected_no_obs<-sum(y2_frt11$used_obs)*y2_frt11$Ui


ggplot(data=y2_frt11) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt11$prop_used<-y2_frt11$used_obs/(sum(y2_frt11$used_obs))
y2_frt11$prop_expected<-y2_frt11$expected_no_obs/(sum(y2_frt11$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt11)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt11 <- ggplot(data=y2_frt11, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt11

Xsq<-chisq.test(y2_frt11$used_obs, p=y2_frt11$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```

# FRT 12
```{r}

# first work out proportion of habitat types across the landscape
frt12<-frt_clipped %>% filter(Cluster == 12)
frt12<-sf::st_as_sf(frt12) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt12))
r3 <- mask(r2, frt12)
plot(r3)

x_frt12<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
#rm(r2, r3, y_alt7, y7)

y_alt7<-x_frt12 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt12<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt12$midpoint <- sapply(y2_frt12$Var1, get_midpoint)
y2_frt12$wi_Ai<- y2_frt12$midpoint * y2_frt12$Freq
y2_frt12$Ui<- y2_frt12$wi_Ai/sum(y2_frt12$wi_Ai)
y2_frt12<- y2_frt12 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt12$midpoint, y2_frt12$Ui)

# now extract probabilty of ignition from fires points in frt12
## Start here!

frt12_spread<-fire.spread.frt %>% filter(Cluster==12)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt12$bins)), ","))))
frt12_spread<-frt12_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt12<-as.data.frame(table(frt12_spread$points_bin))
y2_frt12$used_obs<-y3_frt12$Freq
y2_frt12$expected_no_obs<-(sum(y2_frt12$used_obs))*y2_frt12$Ui


ggplot(data=y2_frt12) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt12$prop_used<-y2_frt12$used_obs/(sum(y2_frt12$used_obs))
y2_frt12$prop_expected<-y2_frt12$expected_no_obs/(sum(y2_frt12$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt12)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt12 <- ggplot(data=y2_frt12, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt12

Xsq<-chisq.test(y2_frt12$used_obs, p=y2_frt12$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# plotting points on raster to check they are still correct
spread_pts <- rasterToPoints(r3, spatial = TRUE)
# Then to a 'conventional' dataframe
spread_pts_df  <- data.frame(spread_pts)

ggplot() +
 geom_raster(data = spread_pts_df , aes(x = x, y = y, fill = rast_spread_2001)) +
  geom_sf(data=frt12_spread, col="red")


```

# FRT 13
```{r}

# first work out proportion of habitat types across the landscape
frt13<-frt_clipped %>% filter(Cluster == 13)
frt13<-sf::st_as_sf(frt13) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt13))
r3 <- mask(r2, frt13)
plot(r3)

x_frt13<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt7<-x_frt13 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt13<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt13$midpoint <- sapply(y2_frt13$Var1, get_midpoint)
y2_frt13$wi_Ai<- y2_frt13$midpoint * y2_frt13$Freq
y2_frt13$Ui<- y2_frt13$wi_Ai/sum(y2_frt13$wi_Ai)
y2_frt13<- y2_frt13 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt13$bins, y2_frt13$Area)

# now extract probabilty of ignition from fires points in frt13
## Start here!

frt13_spread<-fire.spread.frt %>% filter(Cluster==13)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt13$bins)), ","))))
frt13_spread<-frt13_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt13<-as.data.frame(table(frt13_spread$points_bin))
y2_frt13$used_obs<-y3_frt13$Freq
y2_frt13$expected_no_obs<-sum(y2_frt13$used_obs)*y2_frt13$Ui

ggplot(data=y2_frt13) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt13$prop_used<-y2_frt13$used_obs/(sum(y2_frt13$used_obs))
y2_frt13$prop_expected<-y2_frt13$expected_no_obs/(sum(y2_frt13$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt13)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt13 <- ggplot(data=y2_frt13, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt13

Xsq<-chisq.test(y2_frt13$used_obs, p=y2_frt13$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```

# FRT 14
```{r}

# first work out proportion of habitat types across the landscape
frt14<-frt_clipped %>% filter(Cluster == 14)
frt14<-sf::st_as_sf(frt14) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt14))
r3 <- mask(r2, frt14)
plot(r3)

x_frt14<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt7<-x_frt14 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt14<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt14$midpoint <- sapply(y2_frt14$Var1, get_midpoint)
y2_frt14$wi_Ai<- y2_frt14$midpoint * y2_frt14$Freq
y2_frt14$Ui<- y2_frt14$wi_Ai/sum(y2_frt14$wi_Ai)
y2_frt14<- y2_frt14 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt14$bins, y2_frt14$Area)

# now extract probabilty of ignition from fires points in frt14
## Start here!

frt14_spread<-fire.spread.frt %>% filter(Cluster==14)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt14$bins)), ","))))
frt14_spread<-frt14_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt14<-as.data.frame(table(frt14_spread$points_bin))
y2_frt14$used_obs<-y3_frt14$Freq
y2_frt14$expected_no_obs<-sum(y2_frt14$used_obs)*y2_frt14$Ui


ggplot(data=y2_frt14) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt14$prop_used<-y2_frt14$used_obs/(sum(y2_frt14$used_obs))
y2_frt14$prop_expected<-y2_frt14$expected_no_obs/(sum(y2_frt14$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt14)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt14 <- ggplot(data=y2_frt14, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt14

Xsq<-chisq.test(y2_frt14$used_obs, p=y2_frt14$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```

# FRT 15
```{r}

# first work out proportion of habitat types across the landscape
frt15<-frt_clipped %>% filter(Cluster == 15)
frt15<-sf::st_as_sf(frt15) %>% st_combine() %>% st_sf() #flatten layer

r2 <- crop(spread.ras, extent(frt15))
r3 <- mask(r2, frt15)
plot(r3)

x_frt15<- as.data.frame(r3)
#hist(x$layer, breaks=c(0, 0.125, 0.2, 0.24, 0.28, 0.31, 0.34, 0.38, 0.43,0.5, 1.0))
rm(r2, r3)

y_alt7<-x_frt15 %>% mutate(x_bin = cut(rast_spread_2001, breaks=10))

table(y_alt7$x_bin)

y7 <- y_alt7 %>% drop_na()
plot(y7$x_bin)
y2_frt15<-as.data.frame(table(y7$x_bin))

# determine midpoints of each bin
get_midpoint <- function(cut_label) {
  mean(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(cut_label)), ","))))
}

y2_frt15$midpoint <- sapply(y2_frt15$Var1, get_midpoint)
y2_frt15$wi_Ai<- y2_frt15$midpoint * y2_frt15$Freq
y2_frt15$Ui<- y2_frt15$wi_Ai/sum(y2_frt15$wi_Ai)
y2_frt15<- y2_frt15 %>% rename(bins=Var1,
                   Area = Freq)
plot(y2_frt15$bins, y2_frt15$Area)

# now extract probabilty of ignition from fires points in frt15
## Start here!

frt15_spread<-fire.spread.frt %>% filter(Cluster==15)
breakno<-unique(as.numeric(unlist(strsplit(gsub("\\(|\\)|\\[|\\]", "", as.character(y2_frt15$bins)), ","))))
frt15_spread<-frt15_spread %>% mutate(points_bin = cut(rasValue2, breaks=breakno))

y3_frt15<-as.data.frame(table(frt15_spread$points_bin))
y2_frt15$used_obs<-y3_frt15$Freq
y2_frt15$expected_no_obs<-sum(y2_frt15$used_obs)*y2_frt15$Ui


ggplot(data=y2_frt15) +
  geom_line(aes(midpoint, used_obs), col="red") +
  geom_line(aes(midpoint, expected_no_obs), col="blue")

y2_frt15$prop_used<-y2_frt15$used_obs/(sum(y2_frt15$used_obs))
y2_frt15$prop_expected<-y2_frt15$expected_no_obs/(sum(y2_frt15$expected_no_obs))

relationship.fit<-lm(prop_used ~ prop_expected, data=y2_frt15)
anova(relationship.fit)
summary(relationship.fit) # slope looks close to 1 and intercept is at 0


p_frt15 <- ggplot(data=y2_frt15, aes(x=prop_expected, y=prop_used)) +
  geom_point() +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) + 
  geom_abline(slope =1, intercept=0, linetype=2)
p_frt15

Xsq<-chisq.test(y2_frt15$used_obs, p=y2_frt15$prop_expected, simulate.p.value = TRUE)  
Xsq


my.slope <- summary(relationship.fit)$coef["prop_expected", c("Estimate", "Std. Error")]
my.df <- summary(relationship.fit)$df[2]
t_value_zero <- my.slope["Estimate"] / my.slope["Std. Error"] # tests if the slope is different to zero
2*pt(t_value_zero, df=my.df, lower.tail=(t_value_zero<0)) # two sided test
summary(relationship.fit)
t_value_one <- (my.slope["Estimate"] - 1) / my.slope["Std. Error"] # tests if slope different to 1
2*pt(t_value_one, df=my.df, lower.tail=(t_value_one<0)) # two sided test

# conclusion for this FRT. intercept is not different to zero and slope is not different than 1. GOOD
```



# Plot all frt data together in one panel
```{r}
library(ggpubr)

p_bc

ggarrange(#p_bc, 
          # p_frt5,
          # p_frt7,
          # p_frt9,
          # p_frt10,
          # p_frt11,
          # p_frt12,
          p_frt13,
          p_frt14 + rremove("x.text"), 
          labels = c("FRT 13", "FRT 14"),
          ncol = 1, nrow = 2)
```