---
title: "Fire_size_test"
author: "Elizabeth Kleynhans"
date: "2023-01-11"
output: html_document
editor_options: 
  chunk_output_type: inline
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source(here::here("R/functions/R_Postgres.R"))
library(tidyverse)
require (sf)
require (RPostgreSQL)
require (rpostgis)
require (fasterize)
require (raster)
require (dplyr)
library(bcdata)
library(SpaDES.tools)
library(terra)
library(quickPlot)
library(data.table)
library(ggplot2)
library(SpaDES.addins)
library(SpaDES)
library(SpaDES.core)

```

## Introduction

Here I want to test the simulation to check that its performing as expected i.e. that its somewhat mimicking real fires on the landscape.

#Ideas on how to test this:

1) If I input all actual ignition points observed for an area into the simulation does a similar proportion of fires escape. For the purpose of my escape layer I included only fires taht got bigger than 10ha. THus, here I check whether I get similar numbers of fires that are larger than 10ha's with my simulation as I do in real life.

2.) If I allow fires to spread out from those ignition points do I get a similar distribution of fire sizes as I observe in the data?

- I should do 1 and 2 for 2022 fires as an independent check of the data. 

3.) Something else to check is whether the probability of escape is similar to the probability of spread. Also are these similar for fires that dont escape as they are for fires that do escape? 
To do this if I regress the probability of escape on the probability of spread at the same locations i.e. locations where ignition occured. 

4.) I dont thinkg this will influence anything but I could also play with the number of neightbours that can ignite. Spread2 allows either 4 or 8 neighbours for spreading each simulation. Does this make any difference?

# import my ignition locations
```{r, echo=TRUE}
# get latest data off BCGW
# ignit<-try(
#   bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_INCIDENTS_SP") %>%
#     filter(FIRE_YEAR > 2020) %>%
#     filter(FIRE_TYPE == "Fire") %>%
#     collect()
# )

ignit<-try(
  bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_CURRENT_FIRE_PNTS_SP") %>%    
    filter(FIRE_TYPE == "Fire") %>%
    collect()
)


head(ignit)
table(ignit$FIRE_YEAR)
length(ignit$CURRENT_SIZE)

ignit_escape<- ignit %>% filter(CURRENT_SIZE >10)
length(ignit_escape$CURRENT_SIZE) # out of a total of 1647 fires only 263 of them escaped.
hist(ignit_escape$CURRENT_SIZE, breaks=50)
```

# select a study area
```{r}
# get study area
study_area<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM study_area_compart where tsa_name in ('Quesnel TSA', 'Williams Lake TSA',  '100 Mile House TSA')")

study_area2<-study_area %>% group_by ( tsa_name) %>% summarise()
st_crs(study_area2)

ignit_subset <- ignit[study_area2, ]
ignit_subset_10<- ignit_subset %>% filter(CURRENT_SIZE >10)

length(ignit_subset$CURRENT_SIZE) # 249 locations caught fire
length(ignit_subset_10$CURRENT_SIZE) # 42 locations had fires > 10ha
```


```{r, study area with ignition points, eval = F, echo = T}
# look at where the ignition points are on the map
ggplot() +
  geom_sf(data=study_area2) + 
  geom_sf(data=ignit_subset)  +
  geom_sf(dat=ignit_subset_10, col="red")

```

```{r}
lightning_ignition<-raster(" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\rast_lightning_ignit_2022.tif")
human_ignition<-raster(" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\rast_human_ignit_2022.tif")
escape.ras<-raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\rast_escape_2022.tif")
spread.ras<-raster("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\rast_spread_2022.tif")

crs(spread.ras)
crs(escape.ras)

# assign negative values (no data values) NA
lightning_ignition <- reclassify(lightning_ignition, cbind(-Inf, 0, NA), right=FALSE)
human_ignition <- reclassify(human_ignition, cbind(-Inf, 0, NA), right=FALSE)
escape.ras <- reclassify(escape.ras, cbind(-Inf, 0, NA), right=FALSE)
spread.ras <- reclassify(spread.ras, cbind(-Inf, 0, NA), right=FALSE)

dim(escape.ras)
dim(spread.ras)

# combine lightning and person caused fires to create general ignition map.

#P(Ignition) = P(lightning) x  (1-P(human)) + P(human) x (  1-P(lightning)) # Formula was used in this paper: https://iopscience.iop.org/article/10.1088/1748-9326/ac03da (Barros et.al. (2021) Contrasting the role of human- and lightning-caused wildfires on future fire regimes on a Central Oregon landscape. )

total.ignit <- (lightning_ignition * (1-human_ignition)) + (human_ignition * (1-lightning_ignition))

plot(total.ignit, col=rev(heat.colors(255)))
plot(spread.ras, col=rev(heat.colors(255)))
plot(escape.ras, col=rev(heat.colors(255)))

# crop the raster using the vector extent
ignit_crop <- crop(total.ignit, study_area2)
escape_crop <- crop(escape.ras, study_area2)
spread_crop <- crop(spread.ras, study_area2)

# replacing NA's by zero
escape_crop[is.na(escape_crop[])] <- 0 
ignit_crop[is.na(ignit_crop[])] <- 0 
spread_crop[is.na(spread_crop[])] <- 0 

# replacing NA's by zero
escape.ras[is.na(escape.ras[])] <- 0 
total.ignit[is.na(total.ignit[])] <- 0 
spread.ras[is.na(spread.ras[])] <- 0 

```

```{r}
#create landscape  raster with each pixel having a different idno
a <- raster(extent(spread_crop), 
  crs = st_crs(spread_crop)$proj4string, resolution = c(400, 400), vals = 1:ncell(ignit_crop))

# make the starting locations the same as the actual ignition locations. Expect to see similar distribution of fire sizes as seen in the original data.
test<-cbind(ignit_subset, st_coordinates(ignit_subset))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)

start_points=raster::extract(a, pointCoordinates)

test2<-cbind(test,start_points )

start_points<- unique(start_points) # there appear to be two starting cells that get ignited twice so Im removing the duplicates

#####
# plotting points on raster to check they are still correct
ignit_pts <- rasterToPoints(escape_crop, spatial = TRUE)
# Then to a 'conventional' dataframe
ignit_pts_df  <- data.frame(ignit_pts)

ignit_subset<-ignit_subset %>%
  mutate(escaped = case_when(CURRENT_SIZE > 10 ~ 1,
                           CURRENT_SIZE <= 10 ~ 0))

ggplot() +
 geom_raster(data = ignit_pts_df , aes(x = x, y = y, fill = rast_escape_2022)) +
  geom_sf(data=ignit_subset, aes(color = as.factor(escaped)))  #+
  #geom_point(data = pointCoordinates, aes(x = test.X, y = test.Y))
#####
```

#### TRY 2

After playing with this for a while, I realize that at each iteration it test whether it can spread into all 8 adjacent cells. Thus for the escape step the fire starts at its ignition point and then spreads / or not into some of the adjacent cells. I want to test whether if i rather make escape more like ignition. Testing whether a single point can escape i.e. test its value agains some random number. if the random number is smaller than the escape probability then the fire is allowed to spread using spread2. Rather than letting spread2 act on both the escape an spread probability rasters
```{r}
#create landscape  raster with each pixel having a different idno
a <- raster(extent(ignit_crop), 
  crs = st_crs(ignit_crop)$proj4string, resolution = c(400, 400), vals = 1:ncell(ignit_crop))

#no_ignitions=length(ignit_subset$CURRENT_SIZE) # number of ignitions (FIX this so its drawn from a distribution or pulled off a map or something)
n<-100 # number of reps
out<-list()
set.seed(123)

#####
ignition.pts<-start_points
tot.area.burned<-integer(n)
tot.escapes<-integer(n)

for (i in 1:n) {
  
# initiate ignitions at randomly chosen points
#startCells <- as.integer(sample(1:ncell(ignit_crop), no_ignitions))
#startCells<-start_points

#extract probability numbers from the igniton map
#probs.ignit<-ignit_crop[startCells]
#draw random number from uniform distribution
#random.num<-runif(no_ignitions)
#combine values into a datagram
#df<-as.data.frame(cbind(startCells, probs.ignit, random.num))
#select points that have an ignition probability greater than the randomly drawn number.
#ignition.pts<- df$startCells[df$probs.ignit > df$random.num ]

# Now test if the fire can escape from the ignition point
  #extract probability numbers from the escape map
probs.escape<-escape_crop[ignition.pts]
#draw random number from uniform distribution
random.num<-runif(length(ignition.pts))
#combine values into a datagram
df<-as.data.frame(cbind(ignition.pts, probs.escape, random.num))
#select points that have an ignition probability greater than the randomly drawn number.
escape.pts<- df$ignition.pts[df$probs.escape > df$random.num ]

tot.escapes[i]<-length(escape.pts)


#dim(ignit_subset[(ignit_subset$CURRENT_SIZE>10),])

out[[i]]  <- spread2(a, start = escape.pts, spreadProb = spread_crop, asRaster = FALSE, allowOverlap = FALSE)
tot.area.burned[i]<-out[[i]][,.N]

}

out2<-data.table::rbindlist(out)
b<-table(a[out2$pixels])
b1<-b/n

b.tab<-data.table(b1)
b.tab$V1<-as.numeric(b.tab$V1)
a[]<-0
a[b.tab$V1]<-b.tab$N

plot(a)

```


```{r}
#question is it burning this many pixels because it runs out of pixels? Test this by increasing the area that is availabel to burn

# some other stats 
number_ignits<-list()

fire_size_end <- data.frame (matrix (ncol = 3, nrow = 0)) # add 'data' to the points
colnames (fire_size_end) <- c ("Var1", "Freq", "rep")

for (i in 1:n) {
  
  number_ignits[[i]]<-out[[i]][, .N, by = "initialPixels"]$N
  #number_ignits[[i]]<-length(unique(out[[i]]$initialPixels))
  
  fire_size_intermediate<-as.data.frame(table(out[[i]]$initialPixels))
  fire_size_intermediate$rep<-i
  
  fire_size_end<-rbind(fire_size_end, fire_size_intermediate)
  
}

fire_size_end$Freq<-as.numeric(fire_size_end$Freq)
x<-aggregate(fire_size_end$Freq, by=list(Category=fire_size_end$Var1), FUN=mean)

x<-x %>% rename(start_points=Category,
                size = x)

x$start_points<-as.numeric(as.character(x$start_points))
x2<-left_join(test2, x)
x2 <- x2 %>% mutate(size = ifelse(is.na(size), 1, size))

ggplot(data=x2) +    
   geom_histogram(aes(x=size), fill = "blue") 
ggplot(data=x2) +    
   geom_histogram(aes(x=CURRENT_SIZE), fill = "green") 

hist(x2$CURRENT_SIZE, breaks=50, xlim=c(0,80000))

library(reshape2)
# reshape data from wide to long format
long <- melt(x2, id= "start_points", measure.vars = c("size", "CURRENT_SIZE"))
g <- long%>%
  ggplot(aes(x=value, fill=variable)) +
  geom_histogram(alpha=0.3) #+
  #scale_x_log10()

g
```


```{r}
###########################
# how many fires escaped i.e. grew bigger than 10 ha?

rep<-1:n
number_escaped<-as.data.frame(cbind(rep, tot.escapes, tot.area.burned))
number_escaped$tot.escapes
length(ignit_subset_10$CURRENT_SIZE)


# Basic density
p <- ggplot(number_escaped, aes(x=tot.escapes)) + 
  geom_density() + 
   xlim(0, 30)
# Add mean line
p + geom_vline(aes(xintercept=length(ignit_subset_10$CURRENT_SIZE)), color="blue", linetype="dashed", size=1)

# Basic density
# p2 <- ggplot(number_escaped, aes(x=tot.area.burned)) + 
#   geom_density() + 
#    xlim(0, 400000)
# # Add mean line
# p2 + geom_vline(aes(xintercept=sum(ignit_subset_10$CURRENT_SIZE)), color="blue", linetype="dashed", size=1)
#          

```



##### Try the same for the whole of BC

```{r}
#create landscape  raster with each pixel having a different idno
a <- raster(extent(spread.ras), 
  crs = st_crs(spread.ras)$proj4string, resolution = c(400, 400), vals = 1:ncell(spread.ras))

# make the starting locations the same as the actual ignition locations. Expect to see similar distribution of fire sizes as seen in the original data.
test<-cbind(ignit_subset, st_coordinates(ignit_subset))
head(test)


pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)

start_points=raster::extract(a, pointCoordinates)
test2<-cbind(test,start_points )

start_points<- unique(start_points) # there appear to be two starting cells that get ignited twice so Im removing the duplicates

#####
# plotting points on raster to check they are still correct
escape_pts <- rasterToPoints(spread.ras, spatial = TRUE)
# Then to a 'conventional' dataframe
escape_pts_df  <- data.frame(spread.ras)

ggplot() +
 geom_raster(data = escape_pts_df , aes(x = x, y = y, fill = rast_spread_2022 )) +
  geom_point(data = pointCoordinates, aes(x = test.X, y = test.Y))
#####
```


```{r}
#create landscape  raster with each pixel having a different idno
a <- raster(extent(escape.ras), 
  crs = st_crs(escape.ras)$proj4string, resolution = c(400, 400), vals = 1:ncell(escape.ras))

#no_ignitions=length(ignit_subset$CURRENT_SIZE) # number of ignitions (FIX this so its drawn from a distribution or pulled off a map or something)
n<-100 # number of reps
out<-list()
set.seed(123)

#####
ignition.pts<-start_points
tot.area.burned<-integer(n)
tot.escapes<-integer(n)


for (i in 1:n) {
  
# initiate ignitions at randomly chosen points
#startCells <- as.integer(sample(1:ncell(ignit_crop), no_ignitions))
#startCells<-start_points

#extract probability numbers from the igniton map
#probs.ignit<-ignit_crop[startCells]
#draw random number from uniform distribution
#random.num<-runif(no_ignitions)
#combine values into a datagram
#df<-as.data.frame(cbind(startCells, probs.ignit, random.num))
#select points that have an ignition probability greater than the randomly drawn number.
#ignition.pts<- df$startCells[df$probs.ignit > df$random.num ]

# Now test if the fire can escape from the ignition point
  #extract probability numbers from the escape map
probs.escape<-escape.ras[ignition.pts]
#draw random number from uniform distribution
random.num<-runif(length(ignition.pts))
#combine values into a datagram
df<-as.data.frame(cbind(ignition.pts, probs.escape, random.num))
#select points that have an ignition probability greater than the randomly drawn number.
escape.pts<- df$ignition.pts[df$probs.escape > df$random.num ]

tot.escapes[i]<-length(escape.pts)


#dim(ignit_subset[(ignit_subset$CURRENT_SIZE>10),])

out[[i]]  <- spread2(a, start = escape.pts, spreadProb = spread.ras, asRaster = FALSE, allowOverlap = FALSE)

tot.area.burned[i]<-out[[i]][,.N]

}

out2<-data.table::rbindlist(out)
b<-table(a[out2$pixels])
b1<-b/n

b.tab<-data.table(b1)
b.tab$V1<-as.numeric(b.tab$V1)
a[]<-0
a[b.tab$V1]<-b.tab$N
#clearPlot()
plot(a)
```


```{r}
#question is it burning this many pixels because it runs out of pixels? Test this by increasing the area that is availabel to burn

# some other stats 
number_ignits<-list()

fire_size_end <- data.frame (matrix (ncol = 3, nrow = 0)) # add 'data' to the points
colnames (fire_size_end) <- c ("Var1", "Freq", "rep")

for (i in 1:n) {
  
  number_ignits[[i]]<-out[[i]][, .N, by = "initialPixels"]$N
  #number_ignits[[i]]<-length(unique(out[[i]]$initialPixels))
  
  fire_size_intermediate<-as.data.frame(table(out[[i]]$initialPixels))
  fire_size_intermediate$rep<-i
  
  fire_size_end<-rbind(fire_size_end, fire_size_intermediate)
  
}

fire_size_end$Freq<-as.numeric(fire_size_end$Freq)
x<-fire_size_end %>% filter(rep==1)
p <- ggplot(fire_size_end, aes(x=Freq, color = rep)) + 
  geom_density() 
# Add mean line
p + geom_vline(aes(xintercept=length(ignit_subset_10$CURRENT_SIZE)), color="blue", linetype="dashed", size=1)




x<-aggregate(fire_size_end$Freq, by=list(Category=fire_size_end$Var1), FUN=mean)

x<-x %>% rename(start_points=Category,
                size = x)
x$size<-as.numeric(x$size)

x$start_points<-as.numeric(as.character(x$start_points))
x2<-left_join(test2, x)
x2 <- x2 %>% mutate(size = ifelse(is.na(size), 0.001, size))

ggplot(data=x2) +    
   geom_histogram(aes(x=size), fill = "blue") 
ggplot(data=x2) +    
   geom_histogram(aes(x=CURRENT_SIZE), fill = "green") 

hist(x2$CURRENT_SIZE, breaks=50, xlim=c(0,80000))

library(reshape2)
# reshape data from wide to long format
long <- melt(x2, id= "start_points", measure.vars = c("size", "CURRENT_SIZE"))
g <- long%>%
  ggplot(aes(x=value, fill=variable)) +
  geom_histogram(alpha=0.3) #+
  #scale_x_log10()

g
```


```{r}
###########################
# how many fires escaped i.e. grew bigger than 10 ha?

rep<-1:n
number_escaped<-as.data.frame(cbind(rep, tot.escapes, tot.area.burned))

# Basic density
p <- ggplot(number_escaped, aes(x=tot.escapes)) + 
  geom_density() + 
   xlim(0, 100)
# Add mean line
p + geom_vline(aes(xintercept=length(ignit_subset_10$CURRENT_SIZE)), color="blue", linetype="dashed", size=1)

# Basic density
# p2 <- ggplot(number_escaped, aes(x=tot.area.burned)) + 
#   geom_density() + 
#    xlim(0, 400000)
# # Add mean line
# p2 + geom_vline(aes(xintercept=sum(ignit_subset_10$CURRENT_SIZE)), color="blue", linetype="dashed", size=1)
#          

```


```{r}
# some other stats 
number_ignits<-list()

fire_size_end <- data.frame (matrix (ncol = 3, nrow = 0)) # add 'data' to the points
colnames (fire_size_end) <- c ("Var1", "Freq", "rep")

for (i in 1:n) {
  
  number_ignits[[i]]<-out[[i]][, .N, by = "initialPixels"]$N
  #number_ignits[[i]]<-length(unique(out[[i]]$initialPixels))
  
  fire_size_intermediate<-as.data.frame(table(out[[i]]$initialPixels))
  fire_size_intermediate$rep<-i
  
  fire_size_end<-rbind(fire_size_end, fire_size_intermediate)
  
}

hist(fire_size_end$Freq, breaks=50) # gives distribution of fire sizes
```


```{r}
###########################
# how many fires escaped i.e. grew bigger than 10 ha?
number_escaped <- data.frame (matrix (ncol = 2, nrow = 0)) # add 'data' to the points
colnames (number_escaped) <- c ("rep", "tot_escaped")

for (i in 1:n) {
  no_fires_escaped<-fire_size_end %>% filter(rep==i & Freq>1) 
  number_escaped[i,1]<-i
  number_escaped[i,2]<-length(no_fires_escaped$Freq)
}


library(ggplot2)
# Basic density
p <- ggplot(number_escaped, aes(x=tot_escaped)) + 
  geom_density(fill="purple") + 
   xlim(200, 900)

ignit_10ha<-ignit %>% filter(CURRENT_SIZE>1)
# Add mean line
p + geom_vline(aes(xintercept=length(ignit_10ha$CURRENT_SIZE)), color="blue", linetype="dashed", size=1)
         
```

# Here Im going to test whether escape or spread generally has a higher probability of occuring at each of the ignition points
```{r}
test<-cbind(ignit, st_coordinates(ignit))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)

rasStack<-stack(escape.ras, spread.ras)

pts=raster::extract(rasStack, pointCoordinates)

ignit_pts_info<-ignit %>% dplyr::select(FIRE_CAUSE, CURRENT_SIZE )

ignit_pts_info<- cbind(ignit_pts_info, pts)
ignit_pts_info<-ignit_pts_info %>%
  mutate(escape = case_when(CURRENT_SIZE > 10 ~ 1,
                           CURRENT_SIZE <= 10 ~ 0))

ignit_pts_info$escape<-as.character(ignit_pts_info$escape)

ggplot(ignit_pts_info, aes(x=rast_spread_400m_2, y=rast_escape_400m, color=escape, shape=escape)) +
  geom_point() + 
  geom_smooth(method=lm, aes(fill=escape))


start_points<- unique(start_points) # there appear to be two starting cells that get ignited twice so Im removing the duplicates

```

## I dont think the below is correct
#### TRY 1

Running this with only escape and spread. The ignition points are the same as the data that I got for 2021.

It looks like Im getting around double the number of escaped fires as I should in comparison to what the data has. 

I should check this for other areas as well.

After playing with this for a while, I realize that at each iteration it test whether it can spread into all 8 adjacent cells. Thus for the escape step the fire starts at its ignition point and then spreads / or not into some of the adjacent cells. I want to test whether if i rather make escape more like ignition. Testing whether a single point can escape i.e. test its value agains some random number. if the random number is smaller than the escape probability then the fire is allowed to spread using spread2. Rather than letting spread2 act on both the escape an spread probability rasters



# FIRE SIM

```{r}
####################
# Spread with Escape FUNCTION
# Iterative calling -- create a function with escape and spread probability
####################

spreadWithEscape <- function(ras, start, escapeProb, spreadProb) {
  out <- spread2(ras, start = start, spreadProb = escapeProb, asRaster = FALSE, allowOverlap = FALSE, iterations=1, directions=4)
  while (any(out$state == "activeSource")) {
    # pass in previous output as start
    out <- spread2(ras, start = out, spreadProb = spreadProb,
                   asRaster = FALSE, allowOverlap = FALSE, skipChecks = FALSE) # skipChecks for speed
  }
  out
}
```


```{r}
#create landscape  raster with each pixel having a different idno
a <- raster(extent(ignit_crop), 
  crs = st_crs(ignit_crop)$proj4string, resolution = c(400, 400), vals = 1:ncell(ignit_crop))

#no_ignitions=length(ignit_subset$CURRENT_SIZE) # number of ignitions (FIX this so its drawn from a distribution or pulled off a map or something)
n<-20 # number of reps
out<-list()
set.seed(123)

#####
ignition.pts<-start_points
tot.area.burned<-integer(n)

for (i in 1:n) {
  
  # initiate ignitions at randomly chosen points
#startCells <- as.integer(sample(1:ncell(ignit_crop), no_ignitions))
#startCells<-start_points

#extract probability numbers from the igniton map
#probs.ignit<-ignit_crop[startCells]
#draw random number from uniform distribution
#random.num<-runif(no_ignitions)
#combine values into a datagram
#df<-as.data.frame(cbind(startCells, probs.ignit, random.num))
#select points that have an ignition probability greater than the randomly drawn number.
#ignition.pts<- df$startCells[df$probs.ignit > df$random.num ]


#dim(ignit_subset[(ignit_subset$CURRENT_SIZE>10),])

out[[i]]  <- spreadWithEscape(a, start = ignition.pts, escapeProb = escape_crop , spreadProb = spread_crop)
tot.area.burned[i]<-out[[i]][,.N]

}

out2<-data.table::rbindlist(out)
b<-table(a[out2$pixels])
b1<-b/n

b.tab<-data.table(b1)
b.tab$V1<-as.numeric(b.tab$V1)
a[]<-0
a[b.tab$V1]<-b.tab$N
clearPlot()
Plot(a)

# some other stats 
number_ignits<-list()

fire_size_end <- data.frame (matrix (ncol = 3, nrow = 0)) # add 'data' to the points
colnames (fire_size_end) <- c ("Var1", "Freq", "rep")

for (i in 1:n) {
  
  number_ignits[[i]]<-out[[i]][, .N, by = "initialPixels"]$N
  #number_ignits[[i]]<-length(unique(out[[i]]$initialPixels))
  
  fire_size_intermediate<-as.data.frame(table(out[[i]]$initialPixels))
  fire_size_intermediate$rep<-i
  
  fire_size_end<-rbind(fire_size_end, fire_size_intermediate)
  
}

  #hist(fire_size_end$Freq) # gives distribution of fire sizes
  
###########################
# how many fires escaped i.e. grew bigger than 10 ha?
number_escaped <- data.frame (matrix (ncol = 2, nrow = 0)) # add 'data' to the points
colnames (number_escaped) <- c ("rep", "tot_escaped")

for (i in 1:n) {
  no_fires_escaped<-fire_size_end %>% filter(rep==i & Freq>1) 
  number_escaped[i,1]<-i
  number_escaped[i,2]<-length(no_fires_escaped$Freq)
}


# Basic density
p <- ggplot(number_escaped, aes(x=tot_escaped)) + 
  geom_density() + 
   xlim(0, 300)
# Add mean line
p + geom_vline(aes(xintercept=length(ignit_subset_10$CURRENT_SIZE)), color="blue", linetype="dashed", size=1)
         

```


1.) test that the distribution of escaped fires matches the actual data:

This is wrong! I did not think about this properly. I need to count how many fires during the simulation get bigger than 10ha. 
For this Ill 
```{r}
#####

dist_ignitions <- data.frame (matrix (ncol = 2, nrow = 0)) # add 'data' to the points
colnames (dist_ignitions) <- c ("rep", "number_ignitions")

for (i in 1:10000) {

probs.ignit<-ignit_crop[startCells]
#draw random number from uniform distribution
random.num<-runif(no_ignitions)
#combine values into a datagram
df<-as.data.frame(cbind(startCells, probs.ignit, random.num))
#select points that have an ignition probability greater than the randomly drawn number.
ignition.pts<- df$startCells[df$probs.ignit > df$random.num ]

dist_ignitions[i,1]<-i
dist_ignitions[i,2]<-length(ignition.pts)

}

hist(dist_ignitions$number_ignitions)
```
