<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

---
title: "BlockingCastor inputs"
author: "Elizabeth Kleynhans"
date: "2026-06-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(fasterize)
library(bcdata)
library(terra)
library(data.table)
library(dplyr)
library(keyring)

```

# Consolidated cutblocks

The consolidated cutblocks layer can be downloaded from the BC Geographic warehouse. It combines forest harvesting data from various datasets (i.e . Reporting Silviculture Updates and Land Status Tracking System (RESULTS), Forest Cover Inventory (VRI) and satellite imagery change detection). These consolidated datasets show historical cutblocks on the landscape and their associated harvest dates. This dataset is required by blockingCastor

```{r, cutblocks}
cns_cutblock <- bcdc_query_geodata("WHSE_FOREST_VEGETATION.VEG_CONSOLIDATED_CUT_BLOCKS_SP") %>%
    collect()

#Harvest locations year
cns_cutblock2 <- cns_cutblock %>%
  dplyr::filter(AREA_HA >= 0.5) %>%
  dplyr::select(HARVEST_MID_YEAR_CALENDAR,OBJECTID, geometry) %>%
  dplyr::arrange(HARVEST_MID_YEAR_CALENDAR, OBJECTID) %>%
  mutate(objectid = row_number())
  
layer.ras <-fasterize::fasterize(sf= cns_cutblock2, raster = prov.rast , field = "objectid")
layer.ras[is.na(layer.ras[])]<-0
terra::writeRaster (layer.ras, file = paste0(data.dir, "\\cns_cutblk_2026.tif"), overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\cns_cutblk_2026.tif -t 100x100 ', database.schema,'.cns_cutblk_2026 | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/',keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```


