<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

---
title: "Scripts for creating spatial inputs for Castor"
author: "Elizabeth Kleynhans"
date: "20/04/2026"
output: html_document
---

# About this document

This document provides example scripts for constructing the core spatial layers required to initialize and run a Castor model. Scripts are intended as illustrative templates and may be adapted to local study areas, datasets, or resolutions.


```{r setup, include=FALSE}
# Global setup for Castor preprocessing scripts
# - Loads common spatial and data wrangling libraries
# - Defines the standard provincial grid used throughout the model
# - Ensures all rasters are aligned (CRS, extent, resolution)
# - Specifies the location of the files and which schema the data should be loaded into in the postgreSQL database

knitr::opts_chunk$set(echo = TRUE)

#Get some important castor specific functions
source(here::here("functions/R_Postgres.R"))

library(data.table)
library(sf)
library(tidyverse)
library(raster)
library(fasterize)
library(bcdata)
library(bcmaps)
library(terra)

# Create the standard Castor provincial raster grid
# All spatial layers used by Castor must align with this grid
prov.rast <- raster(
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = c(100, 100),
  vals = 0
)

data.dir <- "<path\\to\\files>" # path where the files you want to include in your postgres database are temporarily stored e.g. this could be your downloads folder or another folder within the project. 
database.schema<-'test' # name of the schema in you database that you want to load the relevant files
```


# Vegetation Resource Inventory (VRI)

The [VRI](https://catalogue.data.gov.bc.ca/dataset/vri-2024-forest-vegetation-composite-rank-1-layer-r1-) provides the initial forest state for Castor, including species composition, age, height, and basal area. For most castor applications, the **Forest Vegetation Composite Rank 1 layer** is sufficient, as it provides a single
best‑available representation of stand attributes per polygon.

Users may substitute alternative forest inventory data if:
 - the data has the following attributes: age, height, crown closure, quadratic mean diameter 125, BC Land-cover Classification System Level 1, 2 and 4, and site index
- polygons can be rasterized to the Castor grid.

```{r, inventory data}
# download and open the VRI data
vri_all <- st_read(paste0(data.dir,"\\VEG_COMP_LYR_R1_POLY_2024.gdb"))

# The VRI is huge so unless you are planning on running your analysis in multiple area I would recommend clipping the full VRI layer to your area of interest and then only upload that to postgres.

# first clip the vri to the bounding box of the tsa. 
vri_tsa_bbox <- st_crop(vri_all, st_bbox(tsa)) # in this case tsa is your area of interest that you created i.e. in the study_area_boundaries.Rmd (https://github.com/bcgov/castor/blob/main/functions/study_area_boundaries.Rmd)

# create some space on your hard drive if its small
rm(vri_all) 
gc()

# Next select only the features we are interested in.
vri_tsa<- vri_tsa_bbox %>% 
  dplyr::select(FEATURE_ID, OPENING_ID, OPENING_NUMBER, FEATURE_CLASS_SKEY, BCLCS_LEVEL_1, BCLCS_LEVEL_4, BCLCS_LEVEL_5, BEC_ZONE_CODE, BASAL_AREA, SPECIES_CD_1, SPECIES_PCT_1, SPECIES_CD_2, SPECIES_PCT_2, SPECIES_CD_3, SPECIES_PCT_3, SPECIES_CD_4, SPECIES_PCT_4, SPECIES_CD_5, SPECIES_PCT_5, SPECIES_CD_6, SPECIES_PCT_6, PROJ_AGE_1, PROJ_HEIGHT_1) %>%
  dplyr::rename_with(tolower)

con <- dbConnect(RPostgres::Postgres(),host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), port='5432' ,user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), password = keyring::key_get ('dbpass', keyring = 'postgreSQL')) 

st_write(st_as_sf(vri_tsa, crs=3005), con, Id(schema = database.schema, table = "vri_2024_test"))
dbDisconnect(con)

# Rasterize 
ras.vri <- fasterize::fasterize (st_cast (vri_tsa, "MULTIPOLYGON"), prov.rast, field = "feature_id")
writeRaster (ras.vri, paste0(data.dir,("\\raster_vri_fid.tif")), overwrite = T)

# write data
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir,'\\raster_vri_fid.tif -t 100x100 ', database.schema,'.rast_vri_id_test | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```
The resulting VRI raster contains a feature ID per pixel, which allows Castor to join pixel‑level state back to polygon‑level forest attributes when initializing the database.


# Timber Harvesting Land Base (THLB)

The THLB layer defines which pixels are eligible for harvest activities in Castor. Pixels outside the THLB are excluded from harvest scheduling.

Any spatial representation of the THLB may be used, provided it:
- is binary (inside / outside THLB),
- aligns to the Castor grid,
- and is consistent with the planning context of the analysis.

A version of the provincial timber harvesting land base can be obtained from https://catalogue.data.gov.bc.ca/dataset/provincial-timber-harvesting-land-base-thlb-by-timber-supply-area-tsa-

```{r thlb}

thlb<-st_read(paste0(data.dir,"\\tsa02_thlb.gdb"))

# Rasterize THLB to match Castor grid

ras.thlb <- fasterize::fasterize (st_cast (thlb, "MULTIPOLYGON"), prov.rast, field = "thlb_fact")

terra::writeRaster (ras.thlb, file = paste0(data.dir, "\\raster_thlb.tif"), overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_thlb.tif -t 100x100 ',database.schema,'.rast_thlb | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/',keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```

