<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->


---
title: "Script for creating fireCastor inputs"
author: "Elizabeth Kleynhans"
date: "2026-05-11"
output: html_document
---

# About this document

This document describes methods to create scripts for constructing the core spatial layers required to run fireCastor within Castor. Scripts are intended as illustrative templates and may be adapted to local study areas and datasets.

### What about bec zone, distance to infrastructure and wind? Do i still need these layers?


```{r setup, include=FALSE}
# - Loads common spatial and data wrangling libraries
# - Defines the standard provincial grid used throughout the model
# - Specifies the location of the files and which schema the data should be loaded into in the postgreSQL database

knitr::opts_chunk$set(echo = TRUE)

#Get some important castor specific functions
source(here::here("functions/R_Postgres.R"))

library(terra)
library(sf)
library(fasterize)
library(data.table)
library(bcmaps)
library(bcdata)
library(DBI)
library(RPostgres)
library(keyring)
library(here)


# Create the standard Castor provincial raster grid
# All spatial layers used by Castor must align with this grid

prov.rast <- rast(
  nrows = 15744,
  ncols = 17216,
  xmin  = 159587.5,
  xmax  = 1881187.5,
  ymin  = 173787.5,
  ymax  = 1748187.5,
  crs   = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  vals  = 0
)


data.dir <- "<path\\to\\files>" # path where the files you want to include in your postgres database are temporarily stored e.g. this could be your downloads folder or another folder within the project. 
database.schema<-'test' # name of the schema in you database that you want to load the relevant files
```

# Elevation, slope and aspect

Elevation, slope and aspect are used directly in fireCastor to predict ignition location and fire spread.
Here we use the Canadian digital elevation model (CDED) (https://publications.gc.ca/site/eng/9.952083/publication.html) and resample it to the Castor 100‑m grid It can also be obtained from https://catalogue.data.gov.bc.ca/dataset/digital-elevation-model-for-british-columbia-cded-1-250-000.

Alternative DEM sources can be used but they must be:
- projected to BC Albers,
- resampled to the Castor grid

In the example below I demonstrate uploading DEM for the Boundary TSA. However, if you plan on doing various analyses for different regions of the province it may be more efficient to upload a single dem raster in to postgres that castor will then query on the fly. 

```{r elevation}

#Get Canadian digital elevation model for area of interest (https://publications.gc.ca/site/eng/9.952083/publication.html)
cded_vrt <- cded(
  aoi = tsa, #tsa referes to the the study area created in study_area_boundaries.Rmd
  ask = FALSE   # important for scripts / pipelines
)

dem <- rast(cded_vrt)

#--------------------------------------------
## Alternatively you can download dem for the entire province like this:
# Get the provincial boundary as your AOI
#bc_boundary <- bc_bound() 

# Fetch the CDED data 
# Note: At a provincial scale, this may take a moment to download/process the first time
# prov_dem <- cded(
#   aoi = bc_boundary,
#   ask = FALSE
# )

#dem <- terra::rast(prov_dem)
#---------------------------------------------


dem_bc <- project(dem, prov.rast)
# resample dem to the resolution used by castor
dem_bc_100m <- resample(
  dem_bc,
  prov.rast,
  method = "bilinear"
)

#Calculate slope and aspect from dem
slope  <- terrain(dem_bc_100m, v = "slope",  unit = "degrees")
aspect <- terrain(dem_bc_100m, v = "aspect", unit = "degrees")

plot(dem)
plot(slope)
plot(aspect)

## Upload data to db
writeRaster (dem_bc_100m, file = paste0(data.dir,"\\raster_elev.tif"), format = "GTiff", overwrite = TRUE)
writeRaster (slope, file = paste0(data.dir,"\\raster_slope.tif"), format = "GTiff", overwrite = TRUE)
writeRaster (aspect, file = paste0(data.dir,"\\raster_aspect.tif"), format = "GTiff", overwrite = TRUE)

#write dem to postgres
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_elev.tif -t 100x100 ',database.schema,'.rast_elev | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

#write slope to postgres
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_slope.tif -t 100x100 ',database.schema,'.rast_slope | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

#write aspect to postgres
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_aspect.tif -t 100x100 ',database.schema,'.rast_aspect | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)
```

## Fire regime type

FireCastor uses fire regime type (Erni et al. 2020) (https://cdnsciencepub.com/doi/10.1139/cjfr-2019-0191?mobileUi=0) (https://natural-resources.canada.ca/forests-forestry/wildland-fires/fire-regime) as a fixed effect factor to represent broad, long‑standing regional differences in how fire typically occurs across the province. Fire regime types capture characteristic patterns of fire frequency, size, and behaviour that arise from persistent climate, vegetation, and landscape conditions, allowing the model to distinguish areas where fire is inherently more or less frequent or extensive (for example, dry interior landscapes with frequent large fires versus wetter coastal or montane systems with infrequent fire). This allows the model to better capture large‑scale spatial variation in fire processes while keeping the fire model computationally efficient. Note, fire regime type is kept constant through time. 

I would suggest contacting Erni et al. and asking for a shape file of there fire regime types. Once you have this file you need to change it into a raster. Then fireCastor will query the raster to get the fire regime type in your area of interest and include that as a structural modifier in the statistical model as it runs over time. 


```{r}
FRT<-st_read(paste0(data.dir,"\\frt_clipped.shp")) # this is probably a shape file covering all of Canada

prov_bbox <- st_as_sfc(st_bbox(prov.rast), crs = st_crs(FRT)) #create a bounding box to clip FRT to
FRT_crop <- st_intersection(FRT, prov_bbox) # clip FRT. This speeds up the rasterization (below)

frt.ras <- fasterize::fasterize (st_cast (FRT_crop, "MULTIPOLYGON"), prov.rast, field = "Cluster")
plot(frt.ras)

## Upload data to db
writeRaster (frt.ras, file = paste0(data.dir,"\\raster_frt.tif"), format = "GTiff", overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_elev.tif -t 100x100 ',database.schema,'.rast_elev | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```

## Spatially varying intercept

To predict the number of ignitions the model includes a spatially varying intercept represented as a latent Gaussian random field constructed using the INLA–SPDE framework. This term allows the baseline log‑intensity of the inhomogeneous Poisson process to vary smoothly over space, capturing broad‑scale spatial structure and unobserved drivers of event occurrence that are not explained by the explicit covariates.

Although the spatially varying intercept is estimated statistically as a random field, it is treated as fixed during simulation, providing a stable representation of long‑term spatial structure against which stochastic event dynamics are simulated.


The provincial spatially varying intercept table and associated raster with identifying pixelid is available on github. This data is provided as a static GeoTIFF and a look up table and is not generated at runtime.

Download it from the GitHub Releases page:
https://github.com/bcgov/castor/releases/tag/data-v1.0


After downloading the csv and raster files you need to upload these files into postgres. Below are the steps

```{r}
# read the look-up table into R
vat<-read.csv(paste0(data.dir,"\\spatially_varying_10km_vat.csv"))

# write look-up table into postgres
#connect with postgres
con <- dbConnect(RPostgres::Postgres(),
                 host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), 
                 dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), 
                 port='5432',
                 user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), 
                 password = keyring::key_get ('dbpass', keyring = 'postgreSQL')) 


dbWriteTable(
  con,
  Id(schema = database.schema, table = "spatially_varying_10km_vat"),
  vat,
  overwrite = TRUE,
  row.names = FALSE
)

#upload spatially varying intercept raster into postgres. make sure to change your file path
#data.dir <- "<path\\to\\files>"
#(data.dir, '\\pixelId10km.tif) to match the location of where the raster is saved on your computer
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\pixelId10km.tif -t 100x100 ',database.schema,'.rast_elev | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```


