<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->


---
title: "Script for creating fireCastor inputs"
author: "Elizabeth Kleynhans"
date: "2026-05-11"
output: html_document
---

# About this document

This document describes methods to create scripts for constructing the core spatial layers required to run fireCastor within Castor. Scripts are intended as illustrative templates and may be adapted to local study areas, datasets, or resolutions.


```{r setup, include=FALSE}
# - Loads common spatial and data wrangling libraries
# - Defines the standard provincial grid used throughout the model
# - Specifies the location of the files and which schema the data should be loaded into in the postgreSQL database

knitr::opts_chunk$set(echo = TRUE)

#Get some important castor specific functions
source(here::here("functions/R_Postgres.R"))

library(data.table)
library(sf)
library(tidyverse)
library(raster)
library(fasterize)
library(bcdata)
library(bcmaps)
library(terra)
library(dplyr)
library(climr)
library(DBI)


# Create the standard Castor provincial raster grid
# All spatial layers used by Castor must align with this grid

prov.rast <- rast(
  nrows = 15744,
  ncols = 17216,
  xmin  = 159587.5,
  xmax  = 1881187.5,
  ymin  = 173787.5,
  ymax  = 1748187.5,
  crs   = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  vals  = 0
)


data.dir <- "<path\\to\\files>" # path where the files you want to include in your postgres database are temporarily stored e.g. this could be your downloads folder or another folder within the project. 
database.schema<-'test' # name of the schema in you database that you want to load the relevant files
```

# Elevation, slope and aspect

Elevation, slope and aspect are used directly in fireCastor to predict ignition location and fire spread.
Here we use the Canadian digital elevation model (CDED) (https://publications.gc.ca/site/eng/9.952083/publication.html) and resample it to the Castor 100‑m grid It can also be obtained from https://catalogue.data.gov.bc.ca/dataset/digital-elevation-model-for-british-columbia-cded-1-250-000.

Alternative DEM sources can be used but they must be:
- projected to BC Albers,
- resampled to the Castor grid

```{r elevation}

#Get Canadian digital elevation model (https://publications.gc.ca/site/eng/9.952083/publication.html)
cded_vrt <- cded(
  aoi = tsa,
  ask = FALSE   # important for scripts / pipelines
)

dem <- rast(cded_vrt)
dem_bc <- project(dem, prov.rast)
# resample dem to the resolution used by castor
dem_bc_100m <- resample(
  dem_bc,
  prov.rast,
  method = "bilinear"
)

#Calculate slope and aspect from dem
slope  <- terrain(dem_bc_100m, v = "slope",  unit = "degrees")
aspect <- terrain(dem_bc_100m, v = "aspect", unit = "degrees")

plot(dem)
plot(slope)
plot(aspect)

## Upload data to db
writeRaster (dem_bc_100m, file = paste0(data.dir,"\\raster_elev.tif"), format = "GTiff", overwrite = TRUE)
writeRaster (slope, file = paste0(data.dir,"\\raster_slope.tif"), format = "GTiff", overwrite = TRUE)
writeRaster (aspect, file = paste0(data.dir,"\\raster_aspect.tif"), format = "GTiff", overwrite = TRUE)

#write dem to postgres
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_elev.tif -t 100x100 ',database.schema,'.rast_elev | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

#write slope to postgres
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_slope.tif -t 100x100 ',database.schema,'.rast_slope | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

#write aspect to postgres
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_aspect.tif -t 100x100 ',database.schema,'.rast_aspect | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)
```

## Fire regime type

FireCastor uses fire regime type (Erni et al. 2020) (https://cdnsciencepub.com/doi/10.1139/cjfr-2019-0191?mobileUi=0) (https://natural-resources.canada.ca/forests-forestry/wildland-fires/fire-regime) as a fixed effect factor to represent broad, long‑standing regional differences in how fire typically occurs across the province. Fire regime types capture characteristic patterns of fire frequency, size, and behaviour that arise from persistent climate, vegetation, and landscape conditions, allowing the model to distinguish areas where fire is inherently more or less frequent or extensive (for example, dry interior landscapes with frequent large fires versus wetter coastal or montane systems with infrequent fire). This allows the model to better capture large‑scale spatial variation in fire processes while keeping the fire model computationally efficient. Note, fire regime type is kept constant through time. 

I would suggest contacting Erni et al. and asking for a shape file of there fire regime types. Once you have this file you need to change it into a raster. Then fireCastor will query the raster to get the fire regime type in your area of interest and include that as a structural modifier in the statistical model as it runs over time. 


```{r}
FRT<-st_read(paste0(data.dir,"\\frt_clipped.shp")) # this is probably a shape file covering all of Canada

prov_bbox <- st_as_sfc(st_bbox(prov.rast), crs = st_crs(FRT)) #create a bounding box to clip FRT to
FRT_crop <- st_intersection(FRT, prov_bbox) # clip FRT. This speeds up the rasterization (below)

frt.ras <- fasterize::fasterize (st_cast (FRT_crop, "MULTIPOLYGON"), prov.rast, field = "Cluster")
plot(frt.ras)

## Upload data to db
writeRaster (frt.ras, file = paste0(data.dir,"\\raster_frt.tif"), format = "GTiff", overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\raster_elev.tif -t 100x100 ',database.schema,'.rast_elev | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```

## Spatially varying intercept

To predict the number of ignitions the model includes a spatially varying intercept represented as a latent Gaussian random field constructed using the INLA–SPDE framework. This term allows the baseline log‑intensity of the inhomogeneous Poisson process to vary smoothly over space, capturing broad‑scale spatial structure and unobserved drivers of event occurrence that are not explained by the explicit covariates.

Although the spatially varying intercept is estimated statistically as a random field, it is treated as fixed during simulation, providing a stable representation of long‑term spatial structure against which stochastic event dynamics are simulated.


### Required spatial inputs

The provincial spatially varying intercept table and associated raster with identifying pixelid is available on github. This data is provided as a static GeoTIFF and a look up table and is not generated at runtime.

Download it from the GitHub Releases page:
https://github.com/bcgov/castor/releases

Raster details:
- Projection: EPSG:3005 (BC Albers)
- Resolution: 100 m
- Extent: British Columbia

After download the csv and raster files you need to upload these files into postgres. Below are the steps

```{r}
# read the look-up table into R
vat<-read.csv(paste0(data.dir,"\\spatially_varying_10km_vat.csv"))

# write look-up table into postgres
#connect with postgres
con <- dbConnect(RPostgres::Postgres(),
                 host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), 
                 dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), 
                 port='5432',
                 user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), 
                 password = keyring::key_get ('dbpass', keyring = 'postgreSQL')) 


dbWriteTable(
  con,
  Id(schema = database.schema, table = "spatially_varying_10km_vat"),
  vat,
  overwrite = TRUE,
  row.names = FALSE
)

#upload spatially varying intercept raster into postgres. make sure to change your file path
#data.dir <- "<path\\to\\files>"
#(data.dir, '\\pixelId10km.tif) to match the location of where the raster is saved on your computer
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\pixelId10km.tif -t 100x100 ',database.schema,'.rast_elev | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```

## Provincial CMI value raster

The lavaf3r (Lochhead in prep.) equations used in fireCastor to predict the number of ignitions and fire size require a single climate moisture index (CMI) value that represents how dry the entire province is that summer. Below is a script to create this value for historical and future years of your choice for your choice of global circulation models (GCM's). 

```{r}
## --- Configuration Section ---
# User: Edit these variables to change the GCMs, scenarios, or resolution
target_gcms   <- c("MPI-ESM1-2-HR") 
target_ssps   <- c("ssp245", "ssp370")
target_years  <- 2015:2100
target_runs   <- 8
grid_res      <- 5000  # Meters (5km). We increase the grid size from 100m to 5km because it takes for ever if you do it at 100m. 
output_table  <- "prov_cmi_ave" # Postgres table name

# Define Summer CMI variables
vars_cmi      <- c("CMI_05", "CMI_06", "CMI_07", "CMI_08")
## -----------------------------

### 1. Generate Provincial Grid
message("Generating provincial grid at ", grid_res, "m resolution...")


prov_rast_large <- rast(
  xmin = 159587.5, xmax = 1881187.5,
  ymin = 173787.5, ymax = 1748187.5,
  crs   = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = c(grid_res, grid_res)
)

# Extract coordinates from the provincial raster and project to WGS84 for climr

prov.rast_wgs84 <- terra::project(prov_rast_large, "EPSG:4326")

# 2. Get coordinates directly from the projected raster
latlong <- as.data.table(terra::crds(prov.rast_wgs84, df = TRUE))
setnames(latlong, c("lon", "lat"))
latlong[, id := seq_len(.N)]

### 2. Extract Elevation for every point. climR needs this to adjust the values to account for elevation

# if you have an elevation map for the entire province skip this.
#---------------------------

message("Fetching provincial DEM data...")

# 1. Get the provincial boundary as your AOI
# This ensures you have the extent of all of BC
bc_boundary <- bc_bound() 

# 2. Fetch the CDED data 
# Note: At a provincial scale, this may take a moment to download/process the first time
prov_dem <- cded(
  aoi = bc_boundary,
  ask = FALSE
)

dem_raster <- terra::rast(prov_dem)

#----------------------------

# 2. Extract the CRS from the raster object
dem_crs <- terra::crs(dem_raster)

# 3. Transform your points to match the DEM's projection
# We use st_transform on our points sf object
pts_sf <- st_transform(pts_sf, dem_crs)

# 4. Extract values using terra (passing the SpatRaster and the transformed points)
# We convert pts_sf to a SpatVector for maximum speed with terra
elev_values <- terra::extract(dem_raster, terra::vect(pts_sf))

# 5. Assign back to your data.table
# Column 1 is the ID, Column 2 is the elevation (usually named after the file)
latlong[, elev := elev_values[[2]]]
latlong <- latlong[!is.na(elev)]    # Drop points outside the terrestrial boundary

### 3. Downscale Climate Data (Batch Processing)
# Function to process in chunks to prevent memory crashes
process_cmi <- function(input_dt, gcms, ssps, years, runs) {
  
  # Split data into chunks of 5000 points
  chunk_size <- 5000
  n_chunks <- ceiling(nrow(input_dt) / chunk_size)
  full_out <- list()
  
  for(i in 1:n_chunks) {
    message("Processing chunk ", i, " of ", n_chunks)
    idx <- ((i-1) * chunk_size + 1):min(i * chunk_size, nrow(input_dt))
    
    ds <- downscale(
      xyz = input_dt[idx],
      which_refmap = "refmap_climr",
      gcm_ssp_years = years,
      gcms = gcms,
      ssps = ssps,
      max_run = runs,
      vars = vars_cmi,
      ensemble_mean = FALSE,
      db_option = "local" #there are various options for db_option but I find local to work best.
    )
    
    # Calculate Mean Summer CMI
    ds[, rowmeanCMI := rowMeans(.SD), .SDcols = vars_cmi]
    ds <- ds[RUN != "ensembleMean", .(GCM, SSP, RUN, PERIOD, rowmeanCMI)]
    
    full_out[[i]] <- ds
  }
  
  # Combine chunks and aggregate to provincial average
  final_dt <- rbindlist(full_out)
  summary_dt <- final_dt[, .(ave_cmi = mean(rowmeanCMI, na.rm = TRUE)), 
                        by = .(GCM, SSP, RUN, PERIOD)]
  
  # Standardize names for Postgres
  setnames(summary_dt, tolower(names(summary_dt)))
  summary_dt[, gcm := gsub("-", "_", gcm)]
  
  return(summary_dt)
}

# Run the process
results <- process_cmi(latlong, target_gcms, target_ssps, target_years, target_runs)

### 4. Load into Postgres
message("Connecting to database and uploading results...")

conn <- DBI::dbConnect(
  dbDriver("PostgreSQL"), 
  host = keyring::key_get('dbhost'), 
  dbname = keyring::key_get('dbname'), 
  port = '5432', 
  user = keyring::key_get('dbuser'), 
  password = keyring::key_get('dbpass')
)

# Check if table exists to decide on append vs overwrite

if(dbExistsTable(conn, output_table)) {
  # Option A: Append new data
  dbWriteTable(conn, output_table, results, append = TRUE, row.names = FALSE)
  message("Data appended to ", output_table)
} else {
  # Option B: Create new table
  dbWriteTable(conn, output_table, results, row.names = FALSE)
  message("New table created: ", output_table)
}

dbDisconnect(conn)

# you can also 
```



## BEC
This rmd produces a raster that specifies the BEC zones in British Columbia, as defined by [Biogeoclimatic Ecosystem Classification Program](https://www.for.gov.bc.ca/hre/becweb/). 

It was developed to be used in fireCastor.

BEC data is available from  [DataBC](https://catalogue.data.gov.bc.ca/dataset/f358a53b-ffde-4830-a325-a5a03ff672c3). 

```{r, get BEC data from BCGW}

# grab most recent version of BEC from the data warehouse.
bec<-try(
  bcdc_query_geodata("WHSE_FOREST_VEGETATION.BEC_BIOGEOCLIMATIC_POLY") %>%
    collect()
)

#create a look up table with bec zone and a unique number (id) for each
bec_df<-st_drop_geometry(bec) # drop the geometry column
bec.unique<-unique(bec_df[c('ZONE')])
bec.unique$idkey<-1:length(bec.unique$ZONE)

# join the unique id back to the shape file
bec2<-left_join(bec, bec.unique)

bec.unique<-bec.unique %>% rename(zone=ZONE)

bec2<- bec2 %>% rename(zone=ZONE)

## Rasterize the Data
#Here we convert the polygon to a raster, following the provincial hectares BC raster convention that we are using in the CLUS model to ensure all rasters overlap.

ras.bec <- fasterize::fasterize (st_collection_extract(bec2, "POLYGON"), prov.rast, field = "idkey") 
# turn the polygon into a raster

plot (ras.bec) # make sure the raster looks good

```

## Commit the Data to the PostgreSQL database
Now we need to save the data. We save the raster to the raster schema and look-up table to the public schema in our postgreSQL database. 

```{r, commit data to the dbase}
con <- dbConnect(RPostgres::Postgres(),host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), port='5432' ,user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), password = keyring::key_get ('dbpass', keyring = 'postgreSQL')) 

# write the look up table to postgres
dbWriteTable (con, Id(schema=database.schema, table="bec_zone_vat"), value = bec.unique, 
                   row.names = FALSE, overwrite = TRUE)

# save the raster locally and then upload it on postgres
writeRaster (ras.bec, file = "bec.tif", format = "GTiff", overwrite = TRUE)

#Upload to PostgreSQL
#paste this in the cmd to upload the raster to my local postgreSQL database
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir,'\\bec.tif -t 100x100 ', database.schema,'.bec_current | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```


