<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->


---
title: "Script for creating roads layers for roadsCastor"
author: "Elizabeth Kleynhans"
date: "2026-05-11"
output: html_document
---

# About this document

This document describes methods to create scripts for constructing the core spatial layers required to run roadsCastor within Castor. Scripts are intended as illustrative templates and may be adapted to local study areas, datasets, or resolutions.


```{r setup, include=FALSE}
# - Loads common spatial and data wrangling libraries
# - Defines the standard provincial grid used throughout the model
# - Specifies the location of the files and which schema the data should be loaded into in the postgreSQL database

knitr::opts_chunk$set(echo = TRUE)

#Get some important castor specific functions
source(here::here("functions/R_Postgres.R"))

library(data.table)
library(sf)
library(tidyverse)
library(raster)
library(fasterize)
library(bcdata)
library(bcmaps)
library(terra)

# Create the standard Castor provincial raster grid
# All spatial layers used by Castor must align with this grid
prov.rast <- raster(
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = c(100, 100),
  vals = 0
)

data.dir <- "<path\\to\\files>" # path where the files you want to include in your postgres database are temporarily stored e.g. this could be your downloads folder or another folder within the project. 
database.schema<-'test' # name of the schema in you database that you want to load the relevant files
```


# Roads

Road layers influence access, disturbance patterns, and spatial cost effects in Castor.
Two road representations are supported:
- a simple binary access layer, and
- a distance‑weighted access layer that penalizes remoteness from mills.
Users should choose the option appropriate to their research question.

## Overview of road options

**Option 1 — Simple (binary) roads**
This option treats all roads as providing equal, unconstrained access. Roads indicate where access exists, but do not impose any access cost or remoteness penalty.

 - Equivalent to the logic used in the [Roads](https://landscitech.github.io/roads/) R package
 - Equivalent to the simple version of RoadsCastor
 - No mill locations required
 - Roads act as a binary access mask only

**Option 2 — Distance‑weighted roads (advanced)**
This option applies a penalty to non‑permanent roads that increases with distance from processing facilities (mills).

 - Supported by RoadsCastor and is a more complex workflow
 - Captures remoteness and access gradients
 - Requires mill location data
 - More computationally expensive, but potentially more realistic
 
We provide example code for both options but first provide an example for getting roads data and getting it into the correct format.

### Get roads data

Get roads data. In this example Ill use the BC Cumulative Effects Framework - Integrated Roads - 2026 (https://catalogue.data.gov.bc.ca/dataset/bc-cumulative-effects-framework-integrated-roads-current/resource/4b2aa2a5-8cfd-4410-a0af-d7f257b4131c) but any data can be used. 

Roads are first classified into permanent and non‑permanent types and then buffered by 51 m prior to rasterization.
This buffering step ensures that linear road features adequately intersect the 100 m raster grid. Without buffering, narrow road lines may fall between raster cell centers and be omitted during rasterization, leading to incomplete road representation.

```{r roads}
library(sf)
library(raster)
library(fasterize)
library(data.table)
library(RANN)
library(dplyr)

# get roads data
roads <- st_read(paste0(data.dir,"\\BC_CE_Integrated_Roads_2026.gdb")) %>%
  st_transform(3005)

roads$road_class <- NA_integer_

# Permanent roads
roads$road_class[
  roads$DRA_ROAD_SURFACE == "paved" |
  (!is.na(roads$DRA_ROAD_NAME_FULL) & roads$DRA_ROAD_CLASS != "Trail")
] <- -2

# Non-permanent roads
roads$road_class[is.na(roads$road_class)] <- -1

# buffer roads
roads_buf <- st_buffer(roads, dist = 51)

road_class_rast <- fasterize(
  st_cast(roads_buf, "MULTIPOLYGON"),
  prov.rast,
  field = "road_class"
)

road_class_rast[is.na(road_class_rast[])] <- 0
```

#### Option 1 — Simple (binary) roads
Description
This option assumes all roads provide equal access with zero penalty, regardless of road type or distance from mills. Roads are treated purely as an access mask.
This is the approach taken by the R package [Roads](https://landscitech.github.io/roads/)
```{r roads}
# Binary road access raster
# 0  = road present (accessible)
# NA = no road (inaccessible)


road_binary <- road_class_rast
road_binary[] <- NA                # start with everything NA
road_binary[road_class_rast < 0] <- 0


plot(road_binary, main = "Binary Roads (Simple Option)")

writeRaster (road_binary, paste0(data.dir, "\\road_binary.tif", overwrite = T))

system ("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', data.dir, '\\road_binary.tif -t 100x100 ',database.schema,'.rast_roads_binary | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)
```

#### Option 2 — Distance‑weighted roads (advanced)

Description
This option applies a remoteness penalty to non‑permanent roads based on distance to the nearest processing facility (mill).

Permanent roads have zero penalty
Non‑permanent roads incur a penalty proportional to distance

```{r}

# Get mill locations
mills <- bcdc_query_geodata("WHSE_IMAGERY_AND_BASE_MAPS.GSR_TMBR_PRCSSING_FAC_SV") %>%
  collect()

# remove duplicates
mills_unique <- mills %>% 
  dplyr::distinct(geometry, .keep_all = TRUE)

# Identify road cells
road_cells <- which(road_class_rast[] < 0)

# Cell coordinates
road_pts <- xyFromCell(road_class_rast, road_cells)

# Mill coordinates
mill_xy <- st_coordinates(mills_unique)

# Nearest‑neighbour distance (meters)
dist <- RANN::nn2(
  data  = mill_xy,
  query = road_pts,
  k = 1
)

road_dist <- road_class_rast
road_dist[road_cells] <- dist$nn.dists[, 1]
road_dist[road_dist == 0] <- NA

# apply road penalties
road_weight <- road_class_rast

# Reclassify to penalty weights
road_weight[road_weight == -2] <- 0   # permanent roads
road_weight[road_weight == -1] <- 1   # non‑permanent roads
road_weight[road_weight ==  0] <- NA  # no road

#
road_weighted <- road_weight * road_dist

plot(road_weighted, main = "Distance‑Weighted Roads (Advanced Option)")

writeRaster (road_weighted, paste0(data.dir, "\\road_weighted.tif", overwrite = T))

system ("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', data.dir, '\\road_weighted.tif -t 100x100 ',database.schema,'.rast_roads_weighted | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)
```

## Roads Cost surface

In addition to knowing the location of pre-existing roads, roadCastor also needs to know the cost for building a road across a landscape so that the best path and be chosen. Thus, the following section describes some options for doing this. However, because there are many ways to do this we do not provide an example script rather users are responsible for supplying a road‑building cost surface appropriate to their analysis. If you require further help with creating a cost surface contact Kyle.Lochhead@gov.bc.ca. He is very knowledgable about various options for doing this and can help you to work out what the most appropriate cost surface is for your analysis. 

A road‑building cost surface is a raster layer that represents the relative cost of constructing a road through each cell of the landscape. This surface is used by graph‑based and least‑cost path algorithms (e.g., Castor, [Roads R package](https://landscitech.github.io/roads/))) to simulate where new roads would most likely be built. Importantly, a road‑building cost surface represents construction difficulty, not road access, remoteness, or travel cost after roads exist.

### User responsibility
The creation of a road‑building cost surface is intentionally left to the user. Neither Castor, SELES‑STSM, nor the roads R package prescribe a single method for defining construction cost. Instead, users are expected to supply a cost surface that is appropriate for their modeling objectives, spatial scale, and available data.

**Users may:**
 - construct their own cost surface from input layers,
 - reuse an existing cost surface developed for a similar application,
 - or apply a simplified formulation suitable for exploratory or sensitivity analyses.

**Conceptual model**
In general form, a road‑building cost surface encodes a function such as:
road_build_cost = f(terrain, region, land cover, crossings, barriers)

Each raster cell is assigned a numeric value proportional to the marginal cost of road construction through that location. Cells that cannot support road construction (e.g., large lakes or coastal waterbodies) are treated as absolute barriers and excluded from the graph.

**Typical input data layers**
While specific implementations vary, road‑building cost surfaces commonly incorporate some subset of the following inputs.

1. Topography

Slope derived from a digital elevation model (DEM). Steeper slopes represent higher construction cost and can be included as a linear or nonlinear term.

2. Regional context

Regional boundaries such as Timber Supply Areas (TSAs)
Used to apply region‑specific intercepts or coefficients
Reflects variation in geology, climate, and engineering standards

3. Land cover or ecological modifiers

Biogeoclimatic zones (e.g., ESSF)
Used to represent systematic cost differences associated with soil conditions, precipitation, or ecosystem type

4. Linear feature crossings

Pipeline crossings
Watercourse crossings
Typically represented as per‑cell counts multiplied by unit crossing costs

5. Absolute barriers

Large lakes or coastal waterbodies
Treated as non‑buildable areas (NA values)


6. Appraisal‑based cost estimates (optional)

In some applications (e.g., Castor), road‑building cost surfaces have been informed by road development cost models documented in the BC Interior and Coast Appraisal Manuals: [Interior Appraisal Manual](https://www2.gov.bc.ca/gov/content/industry/forestry/competitive-forest-industry/timber-pricing/interior-timber-pricing/interior-appraisal-manual), [Coast Appraisal Manual](https://www2.gov.bc.ca/gov/content/industry/forestry/competitive-forest-industry/timber-pricing/coast-timber-pricing/coast-appraisal-manual).

