---
title: "Model_coefficient_table"
author: "Elizabeth Kleynhans"
date: "2023-06-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Varying coefficients for fire castor 

Here Im creating a look up table with the value of the model coefficients i.e. slopes (b1, b2, b3 etc) for each variable and each fire cause. I initally thought of hard coding it into fireCastor. But if I ever update or add values it will be annoying to change the values. so instead Ill make a script so that I can more easily update it. 


## Coefficient table for lightning 

# get coefficient data
```{r cars}

###############################
#Import climate data per ignition and sample location
###############################

#Depending on where you saved your output, you may need to update the directory below
file.list1<-list.files("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables", pattern="top_mod_table", all.files=FALSE, full.names=FALSE)
y1<-gsub(".csv","",file.list1)
the_dir <- "C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables"

for (i in 1:length(file.list1)){
  assign(paste0(y1[i]),read.csv (file=paste0(the_dir, "\\", file.list1[i])))
}


```
# Check all files have frt in them!!


# create and empty table and populate
```{r}
coef_table <- data.frame (matrix (ncol = 17, nrow = 0))
colnames (coef_table ) <- c ("cause", "frt","coef_climate_1", "coef_climate_2", "coef_log_climate_2",   "coef_c1", "coef_c2", "coef_c3", "coef_c4","coef_c5", "coef_c7", "coef_d12","coef_m12", "coef_o1ab", "coef_s1", "coef_road_dist", "coef_log_road_dist")

for (i in 1: length(y1)){
  print(i)
  
  x<-eval(as.name(y1[i]))


coef_table[i,"cause"]<-str_split(y1[i], "_", simplify=T)[,5]
coef_table[i,"frt"]<-x$FRT

if("coef_climate_1" %in% names(x)){
  coef_table[i, "coef_climate_1"]<-x$coef_climate_1
} else if ("coef_climate1" %in% names(x)){
  coef_table[i, "coef_climate_1"]<-x$coef_climate1
  } else {
    coef_table[i, "coef_climate_1"]<-NA}

if("coef_climate_2" %in% names(x)){
  coef_table[i, "coef_climate_2"]<-x$coef_climate_2
} else {
    coef_table[i, "coef_climate_2"]<-NA}

if("coef_log_climate2" %in% names(x)){
  coef_table[i, "coef_log_climate_2"]<-x$coef_log_climate2
} else {
    coef_table[i, "coef_log_climate_2"]<-NA}

if("coef_fwveg_C.1" %in% names(x)){
  coef_table[i, "coef_c1"]<-x$coef_fwveg_C.1
} else {
    coef_table[i, "coef_c1"]<-NA}

if("coef_fwvegC.2" %in% names(x)){
  coef_table[i, "coef_c2"]<-x$coef_fwvegC.2
} else if ("coef_fwveg_C.2" %in% names(x)){
  coef_table[i, "coef_c2"]<-x$coef_fwveg_C.2
  } else {
    coef_table[i, "coef_c2"]<-NA}

if("coef_fwveg_C-3" %in% names(x)){
  coef_table[i, "coef_c3"]<-x$coef_FWI_veg_C.3
} else if ("coef_fwvegC.3" %in% names(x)){
  coef_table[i, "coef_c3"]<-x$coef_fwvegC.3
  } else if ("coef_fwveg_C.3" %in% names(x)){
  coef_table[i, "coef_c3"]<-x$coef_fwveg_C.3
  } else {
    coef_table[i, "coef_c3"]<-NA}

if("coef_fwveg_C-4" %in% names(x)){
  coef_table[i, "coef_c4"]<-x$coef_FWI_veg_C.4
} else {
    coef_table[i, "coef_c4"]<-NA}

if("coef_fwvegC.5" %in% names(x)){
  coef_table[i, "coef_c5"]<-x$coef_fwvegC.5
} else if ("coef_fwveg_C.5" %in% names(x)){
  coef_table[i, "coef_c5"]<-x$coef_fwveg_C.5
  } else {
    coef_table[i, "coef_c5"]<-NA}

if("coef_fwvegC.7" %in% names(x)){
  coef_table[i, "coef_c7"]<-x$coef_fwvegC.7
} else if ("coef_fwveg_C.7" %in% names(x)){
  coef_table[i, "coef_c7"]<-x$coef_fwveg_C.7
  } else {
    coef_table[i, "coef_c7"]<-NA}

if("coef_fwvegD.1.2" %in% names(x)){
  coef_table[i, "coef_d12"]<-x$coef_fwvegD.1.2
} else if ("coef_fwveg_D.1.2" %in% names(x)){
  coef_table[i, "coef_d12"]<-x$coef_fwveg_D.1.2
  } else {
    coef_table[i, "coef_d12"]<-NA}

if("coef_fwvegM.1.2" %in% names(x)){
  coef_table[i, "coef_m12"]<-x$coef_fwvegM.1.2
} else if ("coef_fwveg_M.1.2" %in% names(x)){
  coef_table[i, "coef_m12"]<-x$coef_fwveg_M.1.2
  } else {
    coef_table[i, "coef_m12"]<-NA}

if("coef_fwvegO.1a.b" %in% names(x)){
  coef_table[i, "coef_o1ab"]<-x$coef_fwvegO.1a.b
} else if ("coef_fwveg_O.1a.b" %in% names(x)){
  coef_table[i, "coef_o1ab"]<-x$coef_fwveg_O.1a.b
  } else {
    coef_table[i, "coef_o1ab"]<-NA}

if("coef_fwveg_S.1" %in% names(x)){
  coef_table[i, "coef_s1"]<-x$coef_fwveg_S.1
} else if ("coef_fwvegS.1" %in% names(x)){
  coef_table[i, "coef_s1"]<-x$coef_fwvegS.1
  } else {
    coef_table[i, "coef_s1"]<-NA}

if("coef_road_dist" %in% names(x)){
  coef_table[i, "coef_road_dist"]<-x$coef_road_dist
  } else if ("coef_dist_roads" %in% names(x)){
  coef_table[i, "coef_road_dist"]<-x$coef_dist_roads
  } else if ("coef_dist_road_m" %in% names(x)){
  coef_table[i, "coef_road_dist"]<-x$coef_dist_road_m
  } else if ("coef_road_dist_m " %in% names(x)){
  coef_table[i, "coef_road_dist"]<-x$coef_road_dist_m 
  } else if ("coef_roads_m " %in% names(x)){
  coef_table[i, "coef_road_dist"]<-x$coef_roads_m 
  } else {
    coef_table[i, "coef_road_dist"]<-NA
    }

if("coef_log_road_dist" %in% names(x)){
  (coef_table[i, "coef_log_road_dist"]<-x$coef_log_road_dist) 
  } else if ("coef_log_road_dist_m" %in% names(x)){
  coef_table[i, "coef_log_road_dist"]<-x$coef_log_road_dist_m
  } else if ("coef_log_rd_dst" %in% names(x)){
  coef_table[i, "coef_log_road_dist"]<-x$coef_log_rd_dst
  } else {
    coef_table[i, "coef_log_road_dist"]<-NA
  }

# if("coef_dist_infrastructure_m" %in% names(x)){
#   (coef_table[i, "coef_dist_infr"]<-x$coef_dist_infrastructure_m) 
#   } else if ("coef_log_road_dist_m" %in% names(x)){
#   coef_table[i, "coef_dist_infr"]<-x$coef_log_road_dist_m
#   } else if ("coef_log_rd_dst" %in% names(x)){
#   coef_table[i, "coef_dist_infr"]<-x$coef_log_rd_dst
#   } else {
#     coef_table[i, "coef_dist_infr"]<-NA
#   }
# 
# if("coef_log_infr" %in% names(x)){
#   (coef_table[i, "coef_log_dist_infr"]<-x$coef_log_infr) 
#   } else if ("coef_log_dist_infra" %in% names(x)){
#   coef_table[i, "coef_log_dist_infr"]<-x$coef_log_dist_infra
#   } else if ("coef_log_dist_infr" %in% names(x)){
#   coef_table[i, "coef_log_dist_infr"]<-x$coef_log_dist_infr
#   } else {
#     coef_table[i, "coef_log_dist_infr"]<-NA
#   }
# 
# if("coef_slope" %in% names(x)){
#   coef_table[i, "coef_slope"]<-x$coef_slope
# } else if ("coef_fwvegS.1" %in% names(x)){
#   coef_table[i, "coef_s1"]<-x$coef_fwvegS.1
#   } else {
#     coef_table[i, "coef_slope"]<-NA}
# 
# }
# 
# if("coef_dm_h_bc" %in% names(x)){
#   coef_table[i, "coef_dem"]<-x$coef_dm_h_bc
# } else if ("coef_fwvegS.1" %in% names(x)){
#   coef_table[i, "coef_s1"]<-x$coef_fwvegS.1
#   } else {
#     coef_table[i, "coef_dem"]<-NA}
# 
# if("coef_dm_h_bc" %in% names(x)){
#   coef_table[i, "coef_dem"]<-x$coef_dm_h_bc
# } else if ("coef_fwvegS.1" %in% names(x)){
#   coef_table[i, "coef_s1"]<-x$coef_fwvegS.1
#   } else {
#     coef_table[i, "coef_dem"]<-NA}

}


```

### Upload table to postgres database

```{r}
library(data.table)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "fire_model_coef_tbl"), value= coef_table, row.names = FALSE, overwrite = TRUE)
dbDisconnect(conn)
```

