---
title: "Provincial CMI values"
author: "Elizabeth Kleynhans"
date: "2024-05-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(climr)

source (paste0(here::here(), "/R/functions/R_Postgres.R"))
```

## Description of script

This script creates a table of average CMI values for the entire province for various GCM's, ssp's, run's and time periods. For the number of ignitions and area burned models in fireCastor the average provincial CMI value is required but it takes a long time to generate this value so instead I have decided to pre-calculate this value for a whole sweet of models, runs, and gcm's. Then these values will be stored in a table in the postgres database so taht we can just query the table and get the value quickly. 

The script below keeps running out of memmory so Ill split the data collection into two separate chuncks 2015 - 2034 and 2035 - 2050

```{r get provincial grid}
message("extract climate_id values from raster")

location_table<-getSpatialQuery(paste0("SELECT * FROM ", "vat.climate_prism_lat_lon_lookup",";"))
setnames(location_table, c("lon", "lat", "id", "elev"))
location_table<-location_table[,c("id", "lon", "lat", "elev")]

#get climate data for locations on land i.e. that have an elevation
location_table<-data.table(location_table)
location_table<-location_table[elev!="NA",]

# when i try to get climr data it crashes because there are to many locations so Ill split the file up into multiple sections


x<-round(length(location_table$id)/20,0)

x1<-location_table[1:x,]
x2<-location_table[(x+1):(x*2),]
x3<-location_table[(x*2+1):(x*3),]
x4<-location_table[(x*3+1):(x*4),]
x5<-location_table[(x*4+1):(x*5),]
x6<-location_table[(x*5+1):(x*6),]
x7<-location_table[(x*6+1):(x*7),]
x8<-location_table[(x*7+1):(x*8),]
x9<-location_table[(x*8+1):(x*9),]
x10<-location_table[(x*9+1):(x*10),]
x11<-location_table[(x*10+1):(x*11),]
x12<-location_table[(x*11+1):(x*12),]
x13<-location_table[(x*12+1):(x*13),]
x14<-location_table[(x*13+1):(x*14),]
x15<-location_table[(x*14+1):(x*15),]
x16<-location_table[(x*15+1):(x*16),]
x17<-location_table[(x*16+1):(x*17),]
x18<-location_table[(x*17+1):(x*18),]
x19<-location_table[(x*18+1):(x*19),]
x20<-location_table[(x*19+1):(length(location_table$id)),]

rm(location_table)
gc()

message("Downloading provincial CMI from climateBC")  

inputs <- list(x1, x2, x3, x4, x5, x6,x7,x8, x9, x10, x11, x12, x13, x14, x15, x16, x17, x18, x19, x20)
ds_out<-list()
filenames<-list()

gcm_models<-c("ACCESS-ESM1-5","CanESM5","MPI-ESM1-2-HR")
gcm_model_names<-c("access_esm", "canesm", "mpi_esm")
gcm_ssps<-c("ssp126","ssp245","ssp370")
vars_prov = c("CMI_05", "CMI_06", "CMI_07", "CMI_08")
maxRun = 4
```

#Loop for future gcm models
```{r get provincial grid}
for (h in 1:length(gcm_models)){
  print(gcm_models[h])
  for(j in 1:length(gcm_ssps)){
    print(gcm_ssps[j])
    ds_out<-list()
    for (i in 1:length(inputs)){
    print(i)
  
    ds_out_prov <- downscale(
        xyz = inputs[[i]],
        which_refmap = "auto",
        gcm_ssp_years = 2015:2050,
        gcms = gcm_models[h],
        ssps = gcm_ssps[j],
        max_run = maxRun,
        return_refperiod = FALSE,
        vars = vars_prov) # also need annual CMI (I think) for ignitions
  
    setnames(ds_out_prov, old = "id", new="pixelid_climate")
    ds_out_prov[,rowmeanCMI:=(CMI_05+CMI_06+CMI_07+CMI_08)/4]
    ds_out_prov[, c("CMI_05", "CMI_06", "CMI_07", "CMI_08"):=NULL]
    ds_out_prov<-ds_out_prov[RUN != "ensembleMean", ]
    ds_out<-rbind(ds_out, ds_out_prov)
  
    rm(ds_out_prov)
    gc()
    }

  ds_out<-ds_out[!is.na(rowmeanCMI)]
  ds_out[, AveCMI:=mean(rowmeanCMI), by=c("GCM", "SSP", "RUN", "PERIOD")]
  ds_out_summary<-unique(ds_out, by = c("AveCMI", "GCM", "SSP", "RUN", "PERIOD"))
  ds_out_summary[, c("pixelid_climate", "rowmeanCMI"):=NULL]

  nam<-paste0(gcm_model_names[h], gcm_ssps[j])
  assign(nam,ds_out_summary)
  filenames<-append(filenames,nam)
  rm(ds_out)
  
  }
}

# combined all the DC.ignition files together
mkFrameList <- function(nfiles) {
  d <- lapply(seq_len(nfiles),function(i) {
    eval(parse(text=filenames[i]))
  })
  do.call(rbind,d)
}

n<-length(filenames)
Prov_CMI<-mkFrameList(n) 

write.csv(Prov_CMI, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\Future_climate\\prov_cmi_gmc_2009_2023.csv")


#qry<-paste0("INSERT INTO climate_provincial_", tolower(P(sim, "gcmname", "climateCastor")),"_",P(sim, "ssp", "climateCastor"), " (run, period, meanCMI) VALUES (:RUN, :PERIOD, :AveCMI)")

```


#Loop for historic gcm models
```{r}
for (h in 2:length(gcm_models)){
  print(gcm_models[h])
  #for(j in 1:length(gcm_ssps)){
    #print(gcm_ssps[j])
    ds_out<-list()
    for (i in 1:length(inputs)){
    print(i)
  
    ds_out_prov <- downscale(
        xyz = inputs[[i]],
        which_refmap = "auto",
        gcm_hist_years = 2009:2015,
        gcms = gcm_models[h],
        ssps = gcm_ssps[j],
        max_run = maxRun,
        return_refperiod = FALSE,
        vars = vars_prov) # also need annual CMI (I think) for ignitions
  
    setnames(ds_out_prov, old = "id", new="pixelid_climate")
    ds_out_prov[,rowmeanCMI:=(CMI_05+CMI_06+CMI_07+CMI_08)/4]
    ds_out_prov[, c("CMI_05", "CMI_06", "CMI_07", "CMI_08"):=NULL]
    ds_out_prov<-ds_out_prov[RUN != "ensembleMean", ]
    ds_out<-rbind(ds_out, ds_out_prov)
  
    rm(ds_out_prov)
    gc()
    }

  ds_out<-ds_out[!is.na(rowmeanCMI)]
  ds_out[, AveCMI:=mean(rowmeanCMI), by=c("GCM", "RUN", "PERIOD")]
  ds_out_summary<-unique(ds_out, by = c("AveCMI", "GCM", "RUN", "PERIOD"))
  ds_out_summary[, c("pixelid_climate", "rowmeanCMI"):=NULL]

  nam<-paste0(gcm_model_names[h])
  assign(nam,ds_out_summary)
  filenames<-append(filenames,nam)
  rm(ds_out)
  
}

# combined all the DC.ignition files together
mkFrameList <- function(nfiles) {
  d <- lapply(seq_len(nfiles),function(i) {
    eval(parse(text=filenames[i]))
  })
  do.call(rbind,d)
}

n<-length(filenames)
Prov_CMI<-mkFrameList(n) 

write.csv(Prov_CMI, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\Future_climate\\prov_cmi_gmc_2009_2015.csv")
```

#Loop for actual climate data
```{r}

ds_out<-list()    
for (i in 1:length(inputs)){
    print(i)
  
    ds_out_prov <- downscale(
        xyz = inputs[[i]],
        which_refmap = "auto",
        obs_years = 2009:2023,
        obs_ts_dataset = "climatena",
        vars = vars_prov) # also need annual CMI (I think) for ignitions
  
    setnames(ds_out_prov, old = "id", new="pixelid_climate")
    ds_out_prov[,rowmeanCMI:=(CMI_05+CMI_06+CMI_07+CMI_08)/4]
    ds_out_prov[, c("CMI_05", "CMI_06", "CMI_07", "CMI_08"):=NULL]
    #ds_out_prov<-ds_out_prov[RUN != "ensembleMean", ]
    ds_out<-rbind(ds_out, ds_out_prov)
  
    rm(ds_out_prov)
    gc()
    }

  ds_out<-ds_out[!is.na(rowmeanCMI)]
  ds_out[, AveCMI:=mean(rowmeanCMI), by=c("PERIOD", "DATASET")]
  ds_out_summary<-unique(ds_out, by = c("AveCMI", "PERIOD"))
  ds_out_summary[, c("pixelid_climate", "rowmeanCMI"):=NULL]
  
write.csv(ds_out_summary, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\Future_climate\\prov_cmi_actual_2009_2023.csv")
```


```{r}

CMI_15_34<-read.csv("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\Future_climate\\prov_cmi_2015_2034.csv")

CMI_35_50<-read.csv("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\Future_climate\\prov_cmi_2035_2050.csv")

CMI_actual_09_23<-read.csv("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\Future_climate\\prov_cmi_actual_2009_2023.csv")

CMI_09_15<-read.csv("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\Future_climate\\prov_cmi_gmc_2009_2015.csv")

names(CMI_09_15)
CMI_09_15$SSP<-"none"
names(CMI_15_34)
names(CMI_actual_09_23)
CMI_actual_09_23<- CMI_actual_09_23 %>% dplyr::rename(GCM = DATASET)
CMI_actual_09_23$RUN<-"none"
CMI_actual_09_23$SSP<-"none"

prov_CMI<-rbind(rbind(rbind(CMI_09_15, CMI_15_34), CMI_35_50), CMI_actual_09_23)

prov_CMI<-data.table(prov_CMI)
setnames(prov_CMI, c("gcm", "run", "period", "ave_cmi", "ssp"))
prov_CMI<-prov_CMI[gcm == "ACCESS-ESM1-5", gcm:="ACCESS_ESM1_5"]
prov_CMI<-prov_CMI[gcm == "MPI-ESM1-2-HR", gcm:="MPI_ESM1_2_HR"]
prov_CMI$period<-as.integer(prov_CMI$period)
#prov_CMI<-prov_CMI[gcm == "CanESM5", GCM:="CanESM5"]

conn <- DBI::dbConnect (dbDriver ("PostgreSQL"), host = keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432', user = keyring::key_get('dbuser', keyring = 'postgreSQL'), password = keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable (conn, c("public", "prov_cmi_ave"), value = prov_CMI, 
                   row.names = FALSE, overwrite = TRUE)


prov_CMI<-prov_CMI[gcm == "ACCESS_ESM1_5", gcm:="ACCESS"]
prov_CMI<-prov_CMI[gcm == "MPI_ESM1_2_HR", gcm:="MPI"]
prov_CMI<-prov_CMI[gcm == "CanESM5", gcm:="CanESM"]
prov_CMI$period<-as.numeric(prov_CMI$period)
```

## Plot CMI



```{r pressure, echo=FALSE}
prov.CMI<-prov_CMI
prov.CMI<-prov.CMI[!is.na(gcm),]
prov.CMI$GCM_SSP_RUN<-paste0(prov.CMI$gcm, prov.CMI$ssp, prov.CMI$run)

prov_CMI_ssp126<-prov_CMI[ssp %in% c("none","ssp126") & gcm!="climatena",]
prov_CMI_ssp126<-prov_CMI_ssp126[!is.na(gcm),]
prov_CMI_ssp126$prov_CMI_GCM_run<-paste0(prov_CMI_ssp126$gcm, prov_CMI_ssp126$run)
prov_CMI_actual<-prov.CMI[gcm=="climatena",]
#prov_CMI_access<-prov_CMI_ssp126[gcm=="ACCESS",]

ggplot(prov_CMI_ssp126, aes(period, ave_cmi, color=gcm)) +
  geom_line(aes(group = prov_CMI_GCM_run), alpha = .4) + 
  geom_smooth(aes(color=gcm), se = TRUE) +
  geom_line(data=prov_CMI_actual, size=1, colour = "black")
 

prov_CMI_ssp245<-prov_CMI[ssp %in% c("none", "ssp245") & gcm!="climatena",]
prov_CMI_ssp245<-prov_CMI_ssp245[!is.na(gcm),]
prov_CMI_ssp245$prov_CMI_GCM_run<-paste0(prov_CMI_ssp245$gcm, prov_CMI_ssp245$run)

ggplot(prov_CMI_ssp245, aes(period, ave_cmi, color=gcm)) +
  geom_line(aes(group = prov_CMI_GCM_run), alpha = .4) + 
  geom_smooth(aes(color=gcm), se = TRUE) +
  geom_line(data=prov_CMI_actual, size=1, colour = "black")

prov_CMI_ssp370<-prov_CMI[ssp %in% c("none", "ssp370") & gcm!="climatena",]
prov_CMI_ssp370<-prov_CMI_ssp370[!is.na(gcm),]
prov_CMI_ssp370$prov_CMI_GCM_run<-paste0(prov_CMI_ssp370$gcm, prov_CMI_ssp370$run)


ggplot(prov_CMI_ssp370, aes(period, ave_cmi, color=gcm)) +
  geom_line(aes(group = prov_CMI_GCM_run), alpha = .4) + 
  geom_smooth(aes(color=gcm), se = TRUE) +
  geom_line(data=prov_CMI_actual, size=1, colour = "black")

prov_CMI_ssp370<-prov_CMI[SSP %in% c("none", ""),]
prov_CMI_ssp370<-prov_CMI_ssp370[!is.na(GCM),]
prov_CMI_ssp370$PERIOD<-as.numeric(prov_CMI_ssp370$PERIOD)


ggplot(prov_CMI_ssp370, aes(PERIOD, AveCMI, colour = GCM)) +
  geom_point() +
  geom_smooth(se = TRUE)

ggplot(prov_CMI, aes(PERIOD, AveCMI, colour = GCM)) +
  geom_point() +
  geom_smooth(se = TRUE) +
  facet_wrap(~SSP)




ggplot(prov.CMI, aes(x=PERIOD, y=AveCMI, color = GCM_SSP_RUN)) +
  geom_line(show.legend=FALSE)+
  scale_color_manual(values=c("#00CCFF", "#7AC5CD","#0000FF","#00008B", "#006633", "#66CC33","#669933", "#99FF00","#000000", "#FF66FF", "#FF33FF", "#990099", "#660099")) +
  scale_size_manual(values = c(0.7, 0.7, 0.7, 0.7, 0.7, 0.7, 0.7, 0.7, 20, 0.7, 0.7, 0.7, 0.7))

prov.CMI<-prov.CMI[,c("PERIOD", "AveCMI","GCM_SSP_RUN")]


prov_wide<-reshape(prov.CMI, idvar = "PERIOD", timevar = "GCM_SSP_RUN", direction="wide")

ggplot(prov_wide, aes(x=PERIOD))+
  geom_line(aes(y=AveCMI.ACCESSnoner10i1p1f1, color = "#00CCFF", size=0.1))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
