---
title: "Contribution of Caribou Herd Range to the Allowable Annual Cut in British Columbia: An Analysis to Support the Caribou Program Decision Support Tool"
author: "Tyler Muhly"
date: "December 18, 2017"
output:
  pdf_document: default
  word_document: default
  html_document: default
params:
  data.dir: G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data
---

```{r setup, include = FALSE}
knitr::opts_chunk$set (echo = TRUE)
```

## Overview
Here I estimate the potential maximum contribution of caribou herd ranges to the allowable annual cut (AAC) of timber in British Columbia. This analysis supports the structured decision making (SDM) program provincial decision support tool (DST). The provincial DST was built to help the caribou program provincial leadership team (PLT) prioritize where to implement recovery actions on caribou herds across the province. The DST will help the PLT priortize based on biological characteristics of caribou herds, the estimated economic costs of implementing various recovery actions and the estimated economic value of natural resources in caribou herd ranges. 

## Methods
The analyses can be broadly described using the following steps:
1. Calculate the area of timber harvest land base (THLB), by timber supply area (TSA) and tree farm license (TFL) area, in each caribou herd range.
2. Determine the most recent AAC for each TSA and TFL that overlaps each caribou herd range.
3. Sum the proportion of AAC of each TSA's and TFL's THLB in each caribou herd range to calculate the contribution of the caribou range to the AAC. 

### Step 1: Area of timber harvest land base (THLB) in caribou herd ranges
The spatial analyses were completed in ArcGIS 10.3. I obtained the spatial provincial caribou herd range data (downloadable from: <https://catalogue.data.gov.bc.ca/dataset/caribou-herd-locations-for-bc>). I only estimated AAC within the boundaries of the extant herds. 

I  obtained the THLB dataset, which is not currently publically available online, from the Forest Analysis and Inventory Branch (FAIB) in the Ministry of Forests, Lands, Natural Resource Operations and Rural Development (FLNR). The THLB are areas of the province where it is legally and operationally feasible to harvest timber. It is the spatial area defined to model timber harvest flow for timber supply reviews, which are fundamental to establishing the legal AAC in each TSA and TFL unit in British Columbia. The specific definition of THLB varies by TSA and TFL unit, depending on what was considered important during the most recent timber supply review. Thus, there will be inconsistency in the THLB definition across caribou range. However, legal restrictions on cutting are typically consistent across units. For example, ungulate winter ranges and wildlife habitat areas that restrict cutting are part of the THLB definition across all units. Nevertheless, the THLB is best considered as a 'best estimate' of where timber harvest could occur rather than an actual map of where timber harvest will occur.

Within the THLB dataset is a THLB 'factor', which defines the proportion of a spatially defined area (i.e., a polygon) that is considered THLB. In ArcGIS 10.3 I did a 'Clip' of the THLB data to within the extant caribou herd boundaries. Next I removed all data with a THLB factor of 0 (i.e., locations that will not be harvested). I then did a 'Union' of these two datasets to associate THLB to each caribou herd range. 

We do not know the THLB for TFLs, as the timber supply analyses for TFLs are completed by consultants, outside of  government, and the THLB data is not provided. Therefore, for TFLs I did not use THLB to define the harvestable area. Rather, I considered all parts of a TFL as harvestable. 

I obtained the spatial TSA data (downloadable from: <https://catalogue.data.gov.bc.ca/dataset/fadm-timber-supply-area-tsa>) and spatial TFL data (downloadable from: <https://catalogue.data.gov.bc.ca/dataset/fadm-tree-farm-license-tfl>). These are the areas with unique AAC values. I added TFL additions 
(downloadable from: <https://catalogue.data.gov.bc.ca/dataset/fadm-tree-farm-license-tfl-addition>)  and removed TFL deletions 
(downloadable from: <https://catalogue.data.gov.bc.ca/dataset/fadm-tree-farm-license-tfl-deletion>) to the TFL data. 

I  did a 'Union' of the THLB/caribou herd dataset with the TSA data to obtain the area of THLB by TSA and caribou herd range. I did a 'Clip' of the TFLs within extant caribou herd boundaries and then did a 'Union' of these two datasets to associate TFL to each caribou herd range. The resulting data was exported from ArcGIS and imported into Program R for analysis. 

```{r overlap data, include = F, results = 'hide', message = F, warning = F}
library (dplyr)
library (tidyr)
library (kableExtra)
library (maptools)
library (classInt)
library (RColorBrewer)
library (maptools)
library (rgeos)
library (grid)
options (scipen = 999)
overlap.data <- read.table ('G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\caribou_areas_tsa_tfl_thlb_20171204.csv', header = T, sep = ",") # THLB/TSA/caribou herd overlap data from ArcGIS
overlap.table <- overlap.data %>%
                   filter (TSA.NUMB.1 != '' | FOREST.FIL != '') %>% # remove THLB outside of caribou                                                                        range
                   mutate (bou.tsa.thlb.ha = area.ha.12*THLB.FACT) %>% # multiply THLB factor by                                                                               polygon area
                   mutate (bou.tfl.area.ha = area.ha.12) %>% # make TFL area by caribou herd range
                   unite (tsa.tfl, TSA.NUMB.1, FOREST.FIL)
overlap.table$tsa.tfl <- gsub ("_NA", "", overlap.table$tsa.tfl) # some data cleaning
overlap.table$tsa.tfl <- gsub ("NA_", "", overlap.table$tsa.tfl)
overlap.table$tsa.tfl <- gsub ("_", "", overlap.table$tsa.tfl)
tsa.overlap.table <- overlap.table %>% # pulling apart the TSA and TFL area because harvestable area                                          is defined differently
                       group_by (HERD.NAME, tsa.tfl) %>%
                       summarise (sum (bou.tsa.thlb.ha)) %>% # summarize the area of THLB by TSA and                                                                 caribou herd
                       filter (grepl ('.TSA', tsa.tfl))
tfl.overlap.table <- overlap.table %>%
                       group_by (HERD.NAME, tsa.tfl) %>%
                       summarise (sum (bou.tfl.area.ha)) %>% # summarize the area of TFL by                                                                          caribou herd
                       filter (grepl ('TFL.', tsa.tfl))
overlap.table <- dplyr::bind_rows (tsa.overlap.table, tfl.overlap.table) # put them back together
names (overlap.table) [3] <- "bou.tsa.thlb.ha"
names (overlap.table) [4] <- "bou.tfl.area.ha"
overlap.table$tsa.tfl <- gsub (" TSA", "", overlap.table$tsa.tfl)
tfl.area.data <- read.table  ('G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\tfl_area_20171206.csv', header = T, sep = ",") # TFL area data from ArcGIS
tfl.area.data <- tfl.area.data %>%
                  group_by (FOREST_FIL) %>%
                  summarise (sum (tfl_area_h)) # sum total TFL area
names (tfl.area.data) [1] <- "tsa.tfl"
names (tfl.area.data) [2] <- "tfl.tot.area.ha"
```

### Step 2: Determine the most recent allowable annual cut by timber supply area and tree farm license
Here I  get the most recent AAC data by TSA and TFL from FAIBs websites (<https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/timber-supply-review-and-allowable-annual-cut/allowable-annual-cut-timber-supply-areas> and <https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/timber-supply-review-and-allowable-annual-cut/allowable-annual-cut-tree-farm-licences>, respectively). 

One important consideration here is that I did not consider AAC 'partitions' within a TSA. When making AAC decisions the chief forester may propose to partition the amount of AAC to specific tree species or areas of a TSA. Here I did not account for those partitions, and therefore the spatial distribution of AAC is not as precise as defined in some TSAs. 

```{r aac data, echo = F}
tfl.aac.data <- read.table ('G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\tfl_aac_20171130.csv', header = T, sep = ",") # data summarized from website
tsa.aac.data <- read.table ('G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\tsa_aac_20171130.csv', header = T, sep = ",") # data summarized from website
names (tfl.aac.data) [1] <- "tsa.tfl" # some data 'cleaning'
names (tsa.aac.data) [2] <- "tsa.tfl"
tfl.aac.data$tsa.tfl <- gsub (" ", "", tfl.aac.data$tsa.tfl)
tsa.aac.data$tsa.tfl <- gsub ("Mackenzie", "MacKenzie", tsa.aac.data$tsa.tfl)
tsa.aac.data$tsa.tfl <- gsub ("Pacific ", "Pacific", tsa.aac.data$tsa.tfl)
tsa.aac.data$tsa.tfl <- gsub ("Great Bear Rainforest \\(\\GBR)", "GBR", tsa.aac.data$tsa.tfl) # note here that the open brackets need to be 'bracketed' with \\, i.e.,  \\(\\, for this to work
tsa.aac.data$tsa.tfl <- gsub ("(non-Great Bear Rainforest)", "", tsa.aac.data$tsa.tfl)
tsa.aac.data$tsa.tfl <- gsub ("\\(\\)", "", tsa.aac.data$tsa.tfl)
# tfl.aac.data
# tsa.aac.data
```

### Step 3: Calculate the contribution of each caribou herd range to the AAC
I calculated the proportion of THLB in each caribou herd range, by TSA or TFL unit, and multiplied that by the AAC value for each unit. I then summed these values by caribou herd range to obtain the estimated potential maximum contribution of the range to the AAC. 

```{r AAC caribou, echo = F, message = FALSE, results = 'hide', include = F, warning = F}
tsa.thlb.data <- read.table ('G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\tsa_thlb_20171206.csv', header = T, sep = ",") # TSA total THLB area calculated from spatial THLB data by FAIB 
tsa.thlb.data <- tsa.thlb.data %>%
                    filter (tsa != "Cascadia TSA") # there is no THLB or AAC for Cascadia
tsa.thlb.data$tsa <- gsub ("Timber Supply Area", "", tsa.thlb.data$tsa) # some data cleaning
tsa.thlb.data$tsa <- gsub ("TSA", "", tsa.thlb.data$tsa)
tsa.thlb.data$tsa <- gsub ("Robson_Valley", "Robson Valley", tsa.thlb.data$tsa)
tsa.thlb.data$tsa <- gsub ("Fort Saint John", "Fort St. John", tsa.thlb.data$tsa)
tsa.thlb.data$tsa <- gsub ("Mackenzie", "MacKenzie", tsa.thlb.data$tsa)
tsa.thlb.data$tsa <- gsub ("Golden ", "Golden", tsa.thlb.data$tsa) # annoying space at the end
tsa.thlb.data$tsa <- gsub ("Kalum ", "Kalum", tsa.thlb.data$tsa) 
tsa.thlb.data$tsa <- gsub ("Kootenay Lake ", "Kootenay Lake", tsa.thlb.data$tsa) 
tsa.thlb.data$tsa <- gsub ("Pacific ", "Pacific", tsa.thlb.data$tsa)  
tsa.thlb.data$tsa <- gsub ("Prince George ", "Prince George", tsa.thlb.data$tsa)  
tsa.thlb.data$tsa <- gsub ("Williams Lake ", "Williams Lake", tsa.thlb.data$tsa) 
names (tsa.thlb.data) [1] <- "tsa.tfl"
names (tsa.thlb.data) [2] <- "tsa.tot.thlb.ha"

final.table <- full_join (overlap.table, tsa.thlb.data, by = "tsa.tfl") # combining the 'overlap' data                                                                           with the total THLB area by                                                                           TSA 
final.table <- full_join (final.table, tfl.area.data, by = "tsa.tfl") # combining the 'overlap' data                                                                          with the total TFL area
final.table <- left_join (final.table, tfl.aac.data, by = "tsa.tfl") # combine with AAC data
final.table <- left_join (final.table, tsa.aac.data, by = "tsa.tfl")
final.table <- final.table %>% # some data cleaning
                    filter (HERD.NAME != "") %>%
                    filter (tsa.tfl != "Cascadia") %>%
                    filter (tsa.tfl != "Kingcome") %>%
                    filter (tsa.tfl != "Mid Coast") %>%
                    select (HERD.NAME, tsa.tfl, bou.tsa.thlb.ha, bou.tfl.area.ha, tsa.tot.thlb.ha,                                tfl.tot.area.ha, aac.m3, aac)
names (final.table) [7] <- "tfl.aac"
names (final.table) [8] <- "tsa.aac"     
final.table [is.na (final.table)] <- 0
final.table <- final.table %>%  # calculate proportion of TSA THLB or TFL area by caribou herd range 
                    mutate (prop.tsa.thlb = bou.tsa.thlb.ha / tsa.tot.thlb.ha) %>%
                    mutate (prop.tfl.area = bou.tfl.area.ha / tfl.tot.area.ha)
final.table <- replace (final.table, is.na (final.table), 0) # change NaN to 0
final.aac.table <- final.table %>% # calculate proportion of AAC by caribou herd range
                    mutate (prop.thlb.area = prop.tsa.thlb + prop.tfl.area) %>%
                    mutate (aac = tfl.aac + tsa.aac) %>%
                    mutate (prop.aac = aac * prop.thlb.area) %>%
                    group_by (HERD.NAME) %>%
                    summarise (sum (prop.aac))
names (final.aac.table) [2] <- "aac"
# write.csv (final.aac.table, "G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\output_aac_caribou_range_tsa_tfl.csv")
```
## Results 
The greatest contribution to the AAC was from the Wolverine (1,135,411 m^3^), Chase (979,333 m^3^), Hart Ranges (877,104 m^3^) and Itcha-Ilgachuz (806,149 m^3^) caribou herds, which are in central British Columbia (Table 1; Figure 1). There was relatively little (<250,000 m^3^) or no contribution to the AAC from caribou ranges in northwestern and southern British Columbia. Note that these results indicate the maximum potential contribution to the AAC from a caribou range. Thus, the results likely overestimate the proportion of the AAC that could be cut in a caribou range (i.e., the results are biased high). The total AAC for the province is 65,271,756 m^3^. Caribou range might contribute a maximum of 11,838,972 m^3^ (18%) of the AAC. 

```{r AAC table and map by caribou herd range, echo = FALSE, message = F, warning = F}
print.aac.table <- final.aac.table
names (print.aac.table) [1] <- "Caribou Herd Name" # some stuff here to make the table pretty and 'print' it
names (print.aac.table) [2] <- "Allowable Annual Cut Contribution (m3)"
print.aac.table <- print.aac.table [order (-print.aac.table$`Allowable Annual Cut Contribution (m3)`),]
print.aac.table$`Allowable Annual Cut Contribution (m3)` <- formatC (print.aac.table$`Allowable Annual Cut Contribution (m3)`, format = "d", big.mark = ",", digits = 0)
knitr::kable (print.aac.table, caption = "Contribution to the Allowable Annual Cut (m^3^) by Caribou Herd Range", align = 'c') %>%
  column_spec (1, width = "15cm", border_right = T) %>%
  column_spec (2, width = "15cm") 

herds <- readShapePoly ("G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\caribou_range_shape\\caribou_extant_rge.shp")
prov.bc <- readShapePoly ("G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\province\\provinces.shp")
# prov.bc.diss <- gUnaryUnion (prov.bc, id = prov.bc@data$POLITICAL1) # Dissolve by factor
prov.bc.sub <- subset (prov.bc, POLITICAL1 == "British Columbia")
prov.layer <- list ("sp.polygons", prov.bc.sub, col = "black")
herds <- merge (herds, final.aac.table, by.x = "CARIBOU_TA", by.y = "HERD.NAME")
brks <-  classIntervals (herds$aac,  n = 6, style = "fixed", fixedBreaks = c (0, 250000, 500000, 750000, 1000000, 1250000))$brks
brks [length (brks)] <- brks [length (brks)] + 1
pal  <- brewer.pal (6, "Greens")
# Extent parameters
scale.parameter <- 1  # scaling parameter. less than 1 is zooming in, more than 1 zooming out. 
xshift <- 0  # Shift to right in map units. 
yshift <- 0  # Shift to left in map units. 
original.bbox <- prov.bc.sub@bbox  # Pass bbox of your Spatial* Object. 
edges = original.bbox
edges[1, ] <- (edges[1, ] - mean(edges[1, ])) * scale.parameter + mean(edges[1, 
    ]) + xshift
edges[2, ] <- (edges[2, ] - mean(edges[2, ])) * scale.parameter + mean(edges[2, 
    ]) + yshift

scale <- list ("SpatialPolygonsRescale", layout.scale.bar(), scale = 250000, fill = c("transparent", 
    "black"), offset = c(500000, 545000))
# The scale argument sets length of bar in map units
text1 <- list ("sp.text", c(510000, 500000 ), "0")
text2 <- list ("sp.text", c(791000, 500000), "250 km")
# text3 <- list ("sp.text", c(1750000, 1500000), "AAC " ~ m^3 ~ "")
arrow <- list ("SpatialPolygonsRescale", layout.north.arrow (type = 1), offset = c(1500000, 
              1400000), scale = 200000)

spplot (herds, z = "aac", at = brks, col.regions = pal, sp.layout = list (scale, text1, text2, arrow, prov.layer), xlim = edges[1, ], ylim = edges[2, ], main = list ( label = "Estimated Maximum Contribution to the Allowable Annual Cut ("~m^3~")", cex = 1.1)) # in spplot () use scales = list (draw = T) to find the grid locations of the figure
 
```
Figure 1. Estimated maximum contribution of caribou herd ranges (green coloured polygons, where darker greens have higher values) to the allowable annual cut (m^3^) in British Columbia.


The results of this analysis can be used to provide a relative index of timber supply value by caribou range. The absolute value estimates of the contribution of each caribou herd to the AAC lack precision, thus they should be used and interpreted with caution. In addition, there are likely different biases in estimates between different caribou ranges, as each TSA and TFL is unique. For example, THLB in caribou ranges that are closer to mills or existing forestry road infrastructure may be more likely to be cut than THLB in more remote ranges. Thus, comparsion of absolute values between caribou ranges should be done with caution. Another bias with this analysis is that it assumes that timber volume is equally distributed across a TSA or TFL, which is unlikely to be true. It is more likely that forest in caribou range is less productive (lower volume) than other areas of a TSA or TFL. Therefore, the AAC contribution estimates are very likely greater than what would be cut in reality. However, this bias is likely consistent across ranges (i.e., most caribou range is in lower productivity forest) and thus the estimates may be reasonable for comparing between caribou ranges. Given these biases, more detailed analyses are needed to evaluate impacts of specific caribou recovery actions on the AAC. 
