---
title: "Distance_from_ignition"
author: "Elizabeth Kleynhans"
date: '2022-11-04'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
require (sf)
require (RPostgreSQL)
require (rpostgis)
require (fasterize)
require (raster)
require (dplyr)
library(bcdata)
```

Purpose: to create a distance raster for each year of distance away from closest ignition point. I was thinking of including this variables (distance from ignition) in my spread model... or having a look to see whether it makes a difference. 

# import my ignition locations
```{r}
perim_current<-st_read("D:\\Fire\\fire_data\\raw_data\\Historical_Fire_Perimiter_polygons\\PROT_CURRENT_FIRE_POLYS_SP\\C_FIRE_PLY_polygon.shp")

perim_hist<-st_read("D:\\Fire\\fire_data\\raw_data\\Historical_Fire_Perimiter_polygons\\PROT_HISTORICAL_FIRE_POLYS_SP\\H_FIRE_PLY_polygon.shp")

perim_current<-perim_current %>% dplyr::select(FIRE_NO: LOAD_DATE, FCODE: geometry)

perim_current$FIRE_CAUSE<-NA
perim_current$FIRELABEL<-NA
perim_current$FIRELABEL<-NA
perim_current$FIRE_DATE<-NA
perim_current$METHOD<-NA
perim<-rbind(perim_current, perim_hist)

table(perim$FIRE_YEAR)

perim<-perim %>% filter(FIRE_YEAR>2001, SIZE_HA>=10)
perim


# get latest data off BCGW
perim<-try(
  bcdc_query_geodata("WSHE_LAND_NATURAL_RESOURCE.PROT_HISTORICAL_FIRE_POLYS_SP") %>% 
    collect()
)

try(
  bcdc_get_data("WSHE_LAND_NATURAL_RESOURCE.PROT_CURRENT_FIRE_POLYS_SP")
)

head(ignit)
table(ignit$FIRE_YEAR)

# ha BC standard raster
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216, 
                              xmn = 159587.5, xmx = 1881187.5, 
                              ymn = 173787.5, ymx = 1748187.5, 
                              crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", 
                              resolution = c(100, 100),                               
                              vals = 0)
```


# Save each fire year separately as a raster

```{r}


years<-c("2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016","2017","2018", "2019", "2020", "2021")

for (i in 1:length(years)) {
ignit_all<- ignit %>% filter(FIRE_YEAR==years[i])
ignit_all<-st_buffer(ignit_all,500)
ras.ignit <- fasterize (ignit_all, ProvRast, 
                                 field = NULL,# raster cells that were cut get in 2017 get a value of 1
                                 background = 0) # unharvested raster cells get value = 0

raster::writeRaster (ras.ignit, 
                     filename = paste0( "C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\tmp\\spread\\","rast_ignit_", years[i], ".tiff", sep=""), 
                     format = "GTiff", 
                     datatype = 'INT1U')
}
```


After making the ignition rasters. I must used the Raster -> Analysis -> Proximity (Raster distance) tool to calculate the distance from any pixel to the nearest ignition point. After doing this the goal will be to sample the distance to the closest ignition point for burned and not burned areas. My thought is that locations further from ignition points will have a lower probability of burning and I want to test this. I was thinking that maybe I could include this variable in my models instead of the function that Kyle was suggestign i.e. that as fire size increases so the probability of selecting a point declines. 

