---
title: "Fire_veg"
author: "Elizabeth Kleynhans"
date: '2022-08-19'
output: html_document
---


# FIX it appears some fires are found to be started in the FWI_veg type =N. I think part of the problem is that if earliest disturbance year is the same as the fire year it is making years since disturbance =0 and then as a result it is classifying vegetation type as N because that area was just burned. But I think this is actually the fire i want to get info for. So I think therea re two solutions. 1.) either I reclassify the vegetation in the VRI using the VRI from the year before so that the burn date does not appear or I include an if statement saying that if the year burnt = the same year as my fire year then I should ignore it. ill try the latter for starters but I might swithch. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sf)
library(tidyverse)
```


```{r}
#fire_veg_sf<-st_read("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\spread\\Spread_dem_clim_rds_infr_wind_veg.gpkg")

fire_veg_sf<-fire_spread_02_21

fire_veg_sf<- fire_veg_sf%>% rename(fire_yr=year)

head(fire_veg_sf)
```

Now take fire_veg_sf and run it through 09_veg_classification_as_FWI.Rmd to make sure its classified the same way as the vegetation was for escape and for ignition.

```{r}


st_write(veg2, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\spread\\Fire_spread_data_all_veg_Dec23.gpkg", delete_layer=TRUE, driver="GPKG")

veg2<-st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\spread\\Fire_spread_data_all_veg_Dec23.gpkg")

# upload to Kyle clus. Just update the relevant credentials 
key_get('dbpass', keyring = 'postgreSQL')
key_get('dbhost', keyring = 'postgreSQL')

#ogr2ogr -f PostgreSQL PG:"host= user= dbname=clus password= port=5432" C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Fire_data_all_veg.gpkg -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI

```
