---
title: "ROracle Connection"
author: "Kyle Lochhead"
date: "April 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Install Oracle Client

FROM SSC install the following

* install Oracle 11g from SSC (https://selfservecentre.gov.bc.ca/?)

* install OracleConnections FLNR from SSC

#Set ENV

* SET ENV # (https://www.google.ca/search?q=set+environment+windows&oq=set+environment+windows&aqs=chrome..69i57j0l5.3583j0j4&sourceid=chrome&ie=UTF-8)

* set OCI_LIB64=C:\ORACLE\ORAHOME_11g\bin

* New = OCI_LIB64

* Variable Value = C:\ORACLE\ORAHOME_11g\bin

* set OCI_INC=C:\ORACLE\ORAHOME_11g\oci\include  #doesn't seem to be requried

# Get ROracle

From: http://www.oracle.com/technetwork/database/database-technologies/r/roracle/downloads/index.html

* copy ROracle_1.2-1.zip #(or copy from G:\!Project\U3\Win7Apps\Oracle)

* Copy this to C:/data/temp_install

* From this folder, copy oci_dlls to C:\Oracle\ORAHOME_11g\bin AND to where you ROracle package was installed

# In an R session
```{r, eval =FALSE }
setwd ('C:/Data/temp_install')
install.packages('ROracle.zip', repos = NULL)

require (rgdal)
library(ROracle, lib.loc="C:/Program Files/R/R-3.5.1/library")
drv <- dbDriver("Oracle")
connect.string <-"(DESCRIPTION=(ADDRESS=(PROTOCOL=TCP) (HOST=BCGW.BCGOV)(PORT=1521)) (CONNECT_DATA=(SERVICE_NAME=IDWPROD1.BCGOV)))"

con <- dbConnect(drv, username = "", password = "", dbname = connect.string)
t <- dbGetQuery (con, "select count(*)  from whse_forest_vegetation.veg_comp_lyr_r1_poly")
t

dbDisconnect(con)
```


get instant client from :
http://www.oracle.com/technetwork/topics/winx64soft-089540.html
get the 64 bit version

need to set: ENV OCI_LIB64 to point to the ocit.dll

try C:\Oracle\orahome_11g\bin

