---
title: "keyring init"
author: "Kyle Lochhead"
date: "June 26, 2019"
output: html_document
---

# Keyrings and keys
In the Windows "Credentials Manager" you can create 'keyrings' that contain multiple 'keys' that allow you to access, for example, websites, databases or network computers. A keyring is secured with a single password, which then grants access to all of its keys. In the case of accessing a database, this means we first create a keyring that holds all of the credentials to login to the database (i.e., each credential is a key). Second we unlock the keyring only once at the start of an R session. Lastly, in the code we then use `key_get()` to return the needed credentials, like the host, dbname, user, password, etc. Note this can be started for any project. Below outlines the steps to do this.

```{r, install_keyring}
#install.packages("keyring")
library(keyring)
```

### 1. Create the keyring
First, you will create a keyring. This information gets put into the Windows "Credentials Manager". Name the keyring "postgreSQL", so that it is consistent with other CASTOR users, and because we "hard code" this name into the CASTOR code.

When you run the *keyring_create()* function you will be prompted to add a password that will be used to open the keyring. This will be the password you use at the start of an R session. You can keep this simple as you will be the primary, and likely only user on your computer.

```{r, create}
keyring_create("postgreSQL") 
```

### 2. Unlock the keyring before your session
Next, you will need to 'unlock' the keyring that you just created. You will be prompted for the password you created in step 1.

```{r, unlock}
keyring_unlock("postgreSQL")
```

### 3. Set the Credentials
Here we set the "keys" in the postgreSQL "keyring". These keys contain the credentials for accessing the postgreSQL databases (i.e., database name, host, user name and password). You will need to get the credentials to access two databases from Kyle Lochhead (Kyle.Lochhead@gov.bc.ca). Our 'main' database is hosted on a government network computer. We also have a 'virtual machine' that stores our model outputs on a cloud-based computer. 

Again, it is important to use the same naming convention that we use here, as these "key" names are "hard coded" into CASTOR code. Use "dbhost" to identify the name of the  government network computer postgreSQL database host, "dbname' to identify the database name on dbhost, "dbuser" to identify your user name for accessing the database on dbhost, and "dbpass" to identify your password for accessing the database on dbhost. Similarly, use "vmdbhost" to identify the name of the 'virtual machine' postgreSQL database host, 'vmdbname' to identify the database name on vmdbhost, "vmdbuser" to identify your user name for accessing the database on vmdbhost, and "vmdbpass" to identify your password for accessing the database on vmdbhost. 

When you run the *key_set()* function, it will open a new window with a text box prompting you for a 'password'. You *do not* enter a password into the text box, but rather, you enter the value you want to set for that parameter, e.g., for key_set("vmdbhost", keyring ="postgreSQL"), enter the host into the text box.

```{r, set}
key_set("dbhost", keyring ="postgreSQL") 
key_set("dbname", keyring ="postgreSQL") 
key_set("dbuser", keyring ="postgreSQL")
key_set("dbpass", keyring ="postgreSQL")

#to view the keys in the keyring use:
key_list(keyring ="postgreSQL") # they will be labeled under 'service'

#Virtual machine -  digital ocean
key_set("vmdbhost", keyring = "postgreSQL") 
key_set("vmdbname", keyring = "postgreSQL") 
key_set("vmdbuser", keyring = "postgreSQL")
key_set("vmdbpass", keyring = "postgreSQL")

# virtual machine - westgrid
key_set("vmdbwghost", keyring = "postgreSQL") 
key_set("vmdbwgname", keyring = "postgreSQL") 
key_set("vmdbwguser", keyring = "postgreSQL")
key_set("vmdbwgpass", keyring = "postgreSQL")
```
## Use the keyring in code
Now, when you need to access data in the PostgreSQL database, you can connect using the keyring function calls below to get credentials in place of writing them in the code. You can also now test whether the functions are calling the correct credentials using the code below. 

```{r, use, echo =FALSE}
key_get("dbhost", keyring="postgreSQL")
key_get("dbuser", keyring="postgreSQL")
key_get("dbpass", keyring="postgreSQL")

key_get("vmdbhost", keyring="postgreSQL")
key_get("vmdbuser", keyring="postgreSQL")
key_get("vmdbpass", keyring="postgreSQL")

key_get("vmdbwghost", keyring="postgreSQL")
key_get("vmdbwguser", keyring="postgreSQL")
key_get("vmdbwgpass", keyring="postgreSQL")
```