---
title: "Buffaloberry_Data_analysis"
author: "Cora Skaien"
date: "17/03/2022"
output: html_document
---
<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)
library(rgeos)
library(car)
library(rje)
library(caret)
library(pROC)
library(visreg)
library(arm)
library(mgcv)
library(mgcViz)
library(plyr)

#source(here::here("R/functions/R_Postgres.R"))
```

##Data set
cutblock_plots_openings_Buff_ALL_df_March2022

#Overview
This file continues from Buffaloberry&buffaloberry_data_processing_Jan2022. Here, we explore how silviculture practices influence the abundance of buffaloberry berries.

#Load Data In
```{r}
cutblock_plots_openings_Buff_ALL_df_b2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_Buff_ALL_df_March30_2022.csv")
head(cutblock_plots_openings_Buff_ALL_df_b2)

cutblock_plots_openings_Buff_ALL_df<-cutblock_plots_openings_Buff_ALL_df_b2
                             
```

#Begin Exploration of variables
```{r}
head(cutblock_plots_openings_Buff_ALL_df)
names(cutblock_plots_openings_Buff_ALL_df)

cutblock_plots_openings_Buff_ALL_df$Species.Pr

#Check have from both datasets
table(cutblock_plots_openings_Buff_ALL_df$DATASET) #84 from Clayton, 47 from Mackenzie

```

## Looking at DN1_DIS_CD (DENUDATION_1_DISTURBANCE_CODE) between openings and openings + activity files
```{r}
#See if worth losing the data points - i.e., do we have consistent good data within this.
head(cutblock_plots_openings_Buff_ALL_df)
table(cutblock_plots_openings_Buff_ALL_df$G_BGC_ZONE) #BEC Zone: ESSF, ICH, IDF, MS, SBPS (1), SBS
cutblock_plots_openings_Buff_ALL_df$OPEN_GRSAR<-as.numeric(cutblock_plots_openings_Buff_ALL_df$OPEN_GRSAR)
hist(cutblock_plots_openings_Buff_ALL_df$OPEN_GRSAR) #total area the opening encompasses
table(cutblock_plots_openings_Buff_ALL_df$DN1_DIS_CD) # 3 B (burned wildfire); 135 logged (L); 1 P (pest); 3 S (Salvage); 3 W; 
table(cutblock_plots_openings_Buff_ALL_df$DN2_DIS_CD) #Additional elements; 115 total

```

May wish to remove P, S and W, and B
#Given small sample size, and insufficient information, we have not removed data as of March 2022

```{r}
#cutblock_plots_openings_Buff_ALL_df<-subset(cutblock_plots_openings_Buff_ALL_df, cutblock_plots_openings_Buff_ALL_df$DN1_DIS_CD!="P")
#cutblock_plots_openings_Buff_ALL_df<-subset(cutblock_plots_openings_Buff_ALL_df, cutblock_plots_openings_Buff_ALL_df$DN1_DIS_CD!="S")
#cutblock_plots_openings_Buff_ALL_df<-subset(cutblock_plots_openings_Buff_ALL_df, cutblock_plots_openings_Buff_ALL_df$DN1_DIS_CD!="B")
#cutblock_plots_openings_Buff_ALL_df<-subset(cutblock_plots_openings_Buff_ALL_df, cutblock_plots_openings_Buff_ALL_df$DN1_DIS_CD!="W")

table(cutblock_plots_openings_Buff_ALL_df$DN1_DIS_CD) #144 logged
```

#Inspect DN1_SILSYS (DENUDATION_1_SILV_SYSTEM_CODE)
```{r}
table(cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS) #53 CCRES (Clearcut with reserves); 54 Clearcut; spattering of others; 
table(cutblock_plots_openings_Buff_ALL_df$DN2_SILSYS)

#May wish to group the smaller groups into an "other" category
#cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP<-cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS
#cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP <- recode_factor(cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP, CCRES = "CCRES", CLEAR = "CLEAR", IMCUT  = "Other",  SEEDT = "Other", SELEC = "Other", SHELT = "Other")
#table(cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP) 

#cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP #NAs exist... turn them into Other? Or maybe Unknown.
#cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP<-as.factor(cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP)

library(forcats) 
#cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP<-fct_explicit_na(cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP, na_level = "Unknown")

#table(cutblock_plots_openings_Buff_ALL_df$DN1_SILSYS_GP) #Could consider combining Unknown and Other. They are slightly different, however, but Other is such a small category. Consider this if partial residuals are wonky.

```

#Investigate other categories
```{r}
table(cutblock_plots_openings_Buff_ALL_df$DN1_SILVAR) # Not many records; not useful
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH) # 16 BU (burn), 30 ME (mechanical), 2 MA (Manual)
table(cutblock_plots_openings_Buff_ALL_df$PREP2_TECH)
# Mostly same categories as above at different values
cutblock_plots_openings_Buff_ALL_df$PREP1_TECH<-as.factor(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)
cutblock_plots_openings_Buff_ALL_df$PREP2_TECH<-as.factor(cutblock_plots_openings_Buff_ALL_df$PREP2_TECH)
#cutblock_plots_openings_Buff_ALL_df$PREP1_2_TECH<- ifelse (is.na(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH), cutblock_plots_openings_Buff_ALL_df$PREP2_TECH, cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)
#table(cutblock_plots_openings_Buff_ALL_df$PREP1_2_TECH)# 516; get two additional one, but names messed up (become numbers)
```


```{r}
cutblock_plots_openings_Buff_ALL_df$PREP1_2<-paste(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH,cutblock_plots_openings_Buff_ALL_df$PREP2_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP1_2) #336 records of NA, lots of combinations otherwise. Maybe make a column that is yes/no for each technique that is considered important? We see that the 2 in above that we gain are the "NA GS" here. We also see that some were burned first and then had mechanical treatment (50), and some had mechanical treatment and then were burned (57)

cutblock_plots_openings_Buff_ALL_df$PREP1_2<-as.factor(cutblock_plots_openings_Buff_ALL_df$PREP1_2)
cutblock_plots_openings_Buff_ALL_df$PREP1_TECH<-as.factor(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)

table(cutblock_plots_openings_Buff_ALL_df$PREP1_2)

##All 3 of the ifelse statements below get the same result
cutblock_plots_openings_Buff_ALL_df$PREP_TECH <- ifelse (cutblock_plots_openings_Buff_ALL_df$PREP1_2 == "BU ME", cutblock_plots_openings_Buff_ALL_df$PREP1_2, ifelse (cutblock_plots_openings_Buff_ALL_df$PREP1_2 == "ME BU", cutblock_plots_openings_Buff_ALL_df$PREP1_2, cutblock_plots_openings_Buff_ALL_df$PREP1_TECH))

cutblock_plots_openings_Buff_ALL_df$PREP_TECH <- ifelse ((cutblock_plots_openings_Buff_ALL_df$PREP1_2 == "BU ME" | cutblock_plots_openings_Buff_ALL_df$PREP1_2 == "ME BU"), cutblock_plots_openings_Buff_ALL_df$PREP1_2, cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)
cutblock_plots_openings_Buff_ALL_df$PREP_TECH <- ifelse ((cutblock_plots_openings_Buff_ALL_df$PREP1_2 == "ME BU" | cutblock_plots_openings_Buff_ALL_df$PREP1_2 == "BU ME"), cutblock_plots_openings_Buff_ALL_df$PREP1_2, cutblock_plots_openings_Buff_ALL_df$PREP1_TECH) #get same result if change order of names
table(cutblock_plots_openings_Buff_ALL_df$PREP_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP2_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP1_2)
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH, cutblock_plots_openings_Buff_ALL_df$PREP_TECH) #1 = BU; 2=CA; 3=CG; 4=GS; 5=MA; 6=ME; 7=BI; 24=?? NA? 
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH, cutblock_plots_openings_Buff_ALL_df$PREP1_2)

cutblock_plots_openings_Buff_ALL_df$PREP_TECH_2<-paste(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH, cutblock_plots_openings_Buff_ALL_df$PREP_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP_TECH_2) #This helps fix the weird error above; n = 641 

```

Create additional columns that indicate whether burning happened and whether mechanical application happened.

```{r}

cutblock_plots_openings_Buff_ALL_df$PREP_BU <- ifelse ((cutblock_plots_openings_Buff_ALL_df$PREP1_TECH == "BU" | cutblock_plots_openings_Buff_ALL_df$PREP2_TECH == "BU"), 1, 0)

#Attempt 2
cutblock_plots_openings_Buff_ALL_df$PREP_BU <- ifelse ((cutblock_plots_openings_Buff_ALL_df$PREP1_TECH != "BU" & cutblock_plots_openings_Buff_ALL_df$PREP2_TECH != "BU"), 0, 1)                                                     
table(cutblock_plots_openings_Buff_ALL_df$PREP_BU)    #8 not burned, 22 burned; MANY NAs

cutblock_plots_openings_Buff_ALL_df$PREP_BU
#Lots of NAs - there should be no NAs. It is an ifelse statement where all should be 1s or 0s...
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH) #16 burned
table(cutblock_plots_openings_Buff_ALL_df$PREP2_TECH) #7 burned
table(cutblock_plots_openings_Buff_ALL_df$PREP_TECH_2) #122 9 (so burned both times); so 200 burned seemed realistic

table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH, cutblock_plots_openings_Buff_ALL_df$PREP2_TECH) #Won't see all because many NAs in PREP2_TECH; here 23 are BU BU


table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH, cutblock_plots_openings_Buff_ALL_df$PREP_BU)
table(cutblock_plots_openings_Buff_ALL_df$PREP_BU, cutblock_plots_openings_Buff_ALL_df$Burned)
table(cutblock_plots_openings_Buff_ALL_df$Burned)

cutblock_plots_openings_Buff_ALL_df$PREP_BU[is.na(cutblock_plots_openings_Buff_ALL_df$PREP_BU)]<-0
table(cutblock_plots_openings_Buff_ALL_df$PREP_BU) #This looks better, but keep in mind that some that had no info may have had treatments not listed; 306 not burned, 186 burned


```

Repeat for mechanical.

```{r}
cutblock_plots_openings_Buff_ALL_df$PREP_ME <- ifelse ((cutblock_plots_openings_Buff_ALL_df$PREP1_TECH == "ME" | cutblock_plots_openings_Buff_ALL_df$PREP2_TECH == "ME"), 1, 0)
table(cutblock_plots_openings_Buff_ALL_df$PREP_ME) #There should be a LOT more data here
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH, cutblock_plots_openings_Buff_ALL_df$PREP_ME)
cutblock_plots_openings_Buff_ALL_df$PREP_ME # A lot of NAs: turn to 0s
cutblock_plots_openings_Buff_ALL_df$PREP_ME[is.na(cutblock_plots_openings_Buff_ALL_df$PREP_ME)]<-0
table(cutblock_plots_openings_Buff_ALL_df$PREP_ME) #This looks better, but keep in mind that some that had no info may have had treatments not listed; 291 no mechanical treatment, 201 mechanical treatment

#Compare PREP_ME to Mechanical from atu data
table(cutblock_plots_openings_Buff_ALL_df$PREP_ME, cutblock_plots_openings_Buff_ALL_df$Mechanical) #A few more yeses in each
table(cutblock_plots_openings_Buff_ALL_df$PREP_ME) #37 yes
table(cutblock_plots_openings_Buff_ALL_df$Mechanical) #34 yes

cutblock_plots_openings_Buff_ALL_df$Mechanical2<-ifelse(cutblock_plots_openings_Buff_ALL_df$Mechanical==1,1, 
                                                                ifelse(cutblock_plots_openings_Buff_ALL_df$PREP_ME==1,1,0))
table(cutblock_plots_openings_Buff_ALL_df$Mechanical2) #40 yeses, combining infor from both

```
Repeat for MA (manual?)

```{r}
cutblock_plots_openings_Buff_ALL_df$PREP_MA <- ifelse ((cutblock_plots_openings_Buff_ALL_df$PREP1_TECH == "MA" | cutblock_plots_openings_Buff_ALL_df$PREP2_TECH == "MA"), 1, 0)
table(cutblock_plots_openings_Buff_ALL_df$PREP_MA) #There should be a LOT more data here
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH, cutblock_plots_openings_Buff_ALL_df$PREP_MA)
cutblock_plots_openings_Buff_ALL_df$PREP_MA # A lot of NAs: turn to 0s
cutblock_plots_openings_Buff_ALL_df$PREP_MA[is.na(cutblock_plots_openings_Buff_ALL_df$PREP_MA)]<-0
table(cutblock_plots_openings_Buff_ALL_df$PREP_MA) #This looks better, but keep in mind that some that had no info may have had treatmeants not listed; 20 manual treatment, 472 no manual treatment' not useful, do not use.

#Compare PREP_MA to Manual from atu data
table(cutblock_plots_openings_Buff_ALL_df$PREP_MA, cutblock_plots_openings_Buff_ALL_df$Manual) #Dramatic differences
table(cutblock_plots_openings_Buff_ALL_df$PREP_MA) #19 yeses
table(cutblock_plots_openings_Buff_ALL_df$Manual) # 44 yeses

cutblock_plots_openings_Buff_ALL_df$Manual2<-ifelse(cutblock_plots_openings_Buff_ALL_df$Manual==1,1, 
                                                                ifelse(cutblock_plots_openings_Buff_ALL_df$PREP_MA==1,1,0))
table(cutblock_plots_openings_Buff_ALL_df$Manual2) #40 yeses, combining info from both
#Perhaps this firm manual refers to something different and not brushing?

```


```{r}
table(cutblock_plots_openings_Buff_ALL_df$BRSH1_TECH)#Brushing technique; 121 MA (manual); 16 CG (Chemical Ground); 4 CA (Chemical Air); and others

cutblock_plots_openings_Buff_ALL_df$BRUSH_MA <- ifelse ((cutblock_plots_openings_Buff_ALL_df$BRSH1_TECH == "MA"), 1, 0)
table(cutblock_plots_openings_Buff_ALL_df$BRUSH_MA) #There should be a LOT more data here

cutblock_plots_openings_Buff_ALL_df$BRUSH_MA # A lot of NAs: turn to 0s
cutblock_plots_openings_Buff_ALL_df$BRUSH_MA[is.na(cutblock_plots_openings_Buff_ALL_df$BRUSH_MA)]<-0
table(cutblock_plots_openings_Buff_ALL_df$BRUSH_MA) #This looks better, but keep in mind that some that had no info may have had treatmeants not listed; 112 manual brushing, 311 not

table(cutblock_plots_openings_Buff_ALL_df$Brushing_ALL, cutblock_plots_openings_Buff_ALL_df$BRUSH_MA)

cutblock_plots_openings_Buff_ALL_df$Brush2<-ifelse(cutblock_plots_openings_Buff_ALL_df$Brushing_ALL==1,1, 
                                                                ifelse(cutblock_plots_openings_Buff_ALL_df$BRUSH_MA==1,1,0))
table(cutblock_plots_openings_Buff_ALL_df$Brush2) #44 yeses, combining info from both
```


```{r}
#Repeat for chemical
cutblock_plots_openings_Buff_ALL_df$BRUSH_CM <- ifelse ((cutblock_plots_openings_Buff_ALL_df$BRSH1_TECH == "CA" | cutblock_plots_openings_Buff_ALL_df$BRSH1_TECH== "CG"), 1, 0)
table(cutblock_plots_openings_Buff_ALL_df$BRUSH_CM) #There should be a LOT more data here

cutblock_plots_openings_Buff_ALL_df$BRUSH_CM # A lot of NAs: turn to 0s
cutblock_plots_openings_Buff_ALL_df$BRUSH_CM[is.na(cutblock_plots_openings_Buff_ALL_df$BRUSH_CM)]<-0
table(cutblock_plots_openings_Buff_ALL_df$BRUSH_CM) #This is whether brushing with chemicals was applied; 20 chemical brushing, 472 not

table(cutblock_plots_openings_Buff_ALL_df$BRUSH_CM, cutblock_plots_openings_Buff_ALL_df$Chemical) #Some differences

cutblock_plots_openings_Buff_ALL_df$Chem2<-ifelse(cutblock_plots_openings_Buff_ALL_df$Chemical==1,1, 
                                                                ifelse(cutblock_plots_openings_Buff_ALL_df$BRUSH_CM==1,1,0))
table(cutblock_plots_openings_Buff_ALL_df$Chem2) #28 yeses, combining info from both

```


```{r}
table(cutblock_plots_openings_Buff_ALL_df$PLNT1_TECH) #Mostly PL (planting). RP (replanting). FP (Fill planting). Do NAs mean no planting? Or unknown?
cutblock_plots_openings_Buff_ALL_df$PLNT1_TECH
table(cutblock_plots_openings_Buff_ALL_df$PLNT2_TECH)

cutblock_plots_openings_Buff_ALL_df$PLNT1_2_TECH<-paste(cutblock_plots_openings_Buff_ALL_df$PLNT1_TECH, cutblock_plots_openings_Buff_ALL_df$PLNT2_TECH)
table(cutblock_plots_openings_Buff_ALL_df$PLNT1_2_TECH)
cutblock_plots_openings_Buff_ALL_df$PLNT1_2_TECH<-as.factor(cutblock_plots_openings_Buff_ALL_df$PLNT1_2_TECH)

cutblock_plots_openings_Buff_ALL_df$PLANTED<- ifelse (cutblock_plots_openings_Buff_ALL_df$PLNT1_2_TECH=="NA NA", 0, 1)
table(cutblock_plots_openings_Buff_ALL_df$PLANTED) #Very uneven sample size.
#With current data, 386 planted, 37 not.

table(cutblock_plots_openings_Buff_ALL_df$PLANTED, cutblock_plots_openings_Buff_ALL_df$Planted_ALL) #A few differences

cutblock_plots_openings_Buff_ALL_df$Planted2<-ifelse(cutblock_plots_openings_Buff_ALL_df$Planted_ALL==1,1, 
                                                                ifelse(cutblock_plots_openings_Buff_ALL_df$PLANTED==1,1,0))
table(cutblock_plots_openings_Buff_ALL_df$Planted2) #124 yeses, combining info from both; 11 nos
```


```{r}
cutblock_plots_openings_Buff_ALL_df$FEAT_AREA<-as.numeric(cutblock_plots_openings_Buff_ALL_df$FEAT_AREA)
hist(cutblock_plots_openings_Buff_ALL_df$FEAT_AREA)
cutblock_plots_openings_Buff_ALL_df$PLNT1_AREA<-as.numeric(cutblock_plots_openings_Buff_ALL_df$PLNT1_AREA)
hist(cutblock_plots_openings_Buff_ALL_df$PLNT1_AREA) #Also has a Plant2, so could add together for total planting area?
cutblock_plots_openings_Buff_ALL_df$PLNT2_AREA<-as.numeric(cutblock_plots_openings_Buff_ALL_df$PLNT2_AREA)
hist(cutblock_plots_openings_Buff_ALL_df$PLNT2_AREA)
cutblock_plots_openings_Buff_ALL_df$TOTAL_plant_area<-cutblock_plots_openings_Buff_ALL_df$PLNT1_AREA+cutblock_plots_openings_Buff_ALL_df$PLNT2_AREA
cutblock_plots_openings_Buff_ALL_df$TOTAL_plant_area
#cutblock_plots_openings_Buff_ALL_df$TOTAL_plant_area[is.na(cutblock_plots_openings_Buff_ALL_df$TOTAL_plant_area)]<-0
cutblock_plots_openings_Buff_ALL_df$TOTAL_plant_area # We will assume an absence is indicative of no planting
hist(cutblock_plots_openings_Buff_ALL_df$TOTAL_plant_area)

cutblock_plots_openings_Buff_ALL_df$PLANTING<-ifelse (cutblock_plots_openings_Buff_ALL_df$TOTAL_plant_area==0, 0, 1)
table(cutblock_plots_openings_Buff_ALL_df$PLANTING) # We see that this is far different than the data for whether planted or not, suggesting that not all planted sites have planting density. These are NOT true 0s and this data can only be used for locations where we know planting occurred.
#Compare to:
table(cutblock_plots_openings_Buff_ALL_df$PLANTED)
#New metric obviously incomplete as have 290 0s instead of 56.

```


```{r}
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH) #May wish to combine smaller groups into "other"
cutblock_plots_openings_Buff_ALL_df$PREP1_TECH_GP<-cutblock_plots_openings_Buff_ALL_df$PREP1_TECH
cutblock_plots_openings_Buff_ALL_df$PREP1_TECH_GP <- recode_factor(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH_GP, BU="BU", CA="Other",CG="Other",GS="Other",MA="Other",ME="ME", "BI"="Other")
table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH_GP)
#Not as useful as individual assessments that account for both Phase 1 and Phase 2

library(forcats) 
cutblock_plots_openings_Buff_ALL_df$PREP1_TECH_GP<-fct_explicit_na(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH_GP, na_level = "Unknown")

table(cutblock_plots_openings_Buff_ALL_df$PREP1_TECH_GP)

```


```{r}
table(cutblock_plots_openings_Buff_ALL_df$PREP_BU) #122 no, 22 yes
table(cutblock_plots_openings_Buff_ALL_df$PREP_ME) #105 no, 39 yes
table(cutblock_plots_openings_Buff_ALL_df$PREP_MA) #142 no, 2 yes

#With refined data
table(cutblock_plots_openings_Buff_ALL_df$Burned) #122 no, 22 yes
table(cutblock_plots_openings_Buff_ALL_df$Mechanical2) #104 no, 40 yes
table(cutblock_plots_openings_Buff_ALL_df$Manual2) #100 no, 44 yes 
#March 30, Manual and Mechanical same above - suspicious. Needs investigating.
table(cutblock_plots_openings_Buff_ALL_df$Brushing_ALL) 
table(cutblock_plots_openings_Buff_ALL_df$Brush2) 
```

Investigate date when operations began and ended

```{r}
head(cutblock_plots_openings_Buff_ALL_df)
table(cutblock_plots_openings_Buff_ALL_df$DST_STR_DT)
table(cutblock_plots_openings_Buff_ALL_df$DST_END_DT)

#Select month that data was collected
library(stringi)
cutblock_plots_openings_Buff_ALL_df$Date_month_START<-stri_sub(cutblock_plots_openings_Buff_ALL_df$DST_STR_DT,5,6)
table(cutblock_plots_openings_Buff_ALL_df$Date_month_START) #

cutblock_plots_openings_Buff_ALL_df$Date_month_END<-stri_sub(cutblock_plots_openings_Buff_ALL_df$DST_END_DT,5,6)
table(cutblock_plots_openings_Buff_ALL_df$Date_month_END) #

table(cutblock_plots_openings_Buff_ALL_df$Date_month_START, cutblock_plots_openings_Buff_ALL_df$Date_month_END) 

#Get Years
cutblock_plots_openings_Buff_ALL_df$Date_year_START<-stri_sub(cutblock_plots_openings_Buff_ALL_df$DST_STR_DT,1,4)
table(cutblock_plots_openings_Buff_ALL_df$Date_year_START) #

cutblock_plots_openings_Buff_ALL_df$Date_year_END<-stri_sub(cutblock_plots_openings_Buff_ALL_df$DST_END_DT,1,4)
table(cutblock_plots_openings_Buff_ALL_df$Date_year_END) #

#How many went between years
str(cutblock_plots_openings_Buff_ALL_df$Date_year_END)
cutblock_plots_openings_Buff_ALL_df$Date_year_END<-as.numeric(cutblock_plots_openings_Buff_ALL_df$Date_year_END)
cutblock_plots_openings_Buff_ALL_df$Date_year_START<-as.numeric(cutblock_plots_openings_Buff_ALL_df$Date_year_START)

cutblock_plots_openings_Buff_ALL_df$NumYearsTreat<-cutblock_plots_openings_Buff_ALL_df$Date_year_END - cutblock_plots_openings_Buff_ALL_df$Date_year_START

table(cutblock_plots_openings_Buff_ALL_df$NumYearsTreat) #Some ended 59 years after starting.


#Even though not entirely accurate, let's use the start month as a proxy. Will group September-November as fall, December-February as winter, March-May as Spring and June-August as summer
cutblock_plots_openings_Buff_ALL_df$START_SEASON<-cutblock_plots_openings_Buff_ALL_df$Date_month_START
str(cutblock_plots_openings_Buff_ALL_df$START_SEASON)

cutblock_plots_openings_Buff_ALL_df$START_SEASON<-recode_factor(cutblock_plots_openings_Buff_ALL_df$START_SEASON, "01"="Winter", "02"="Winter","03"="Spring","04"="Spring","05"="Spring","06"="Summer", "07"="Summer", "08"="Summer", "09"="Fall", "10" ="Fall", "11"="Fall", "12" ="Winter")

table(cutblock_plots_openings_Buff_ALL_df$START_SEASON)

```

```{r}
cutblock_plots_openings_Buff_ALL_df$START_SEASON2<-recode_factor(cutblock_plots_openings_Buff_ALL_df$START_SEASON, "Winter"="Winter", "Spring" = "Not Winter","Summer" = "Not Winter", "Fall" ="Not Winter")
table(cutblock_plots_openings_Buff_ALL_df$START_SEASON2)
```


Investigate the newer variables from Dave Waddell.

```{r}
names(cutblock_plots_openings_Buff_ALL_df)
head(cutblock_plots_openings_Buff_ALL_df)

#Look at Planting density - no records in remaining 470 plots
hist(cutblock_plots_openings_Buff_ALL_df$planted_density_TOT)
table(cutblock_plots_openings_Buff_ALL_df$planted_species1) #Dominate species planted when reported; only 238 reported the species of the 406 records
table(cutblock_plots_openings_Buff_ALL_df$planted_species2) #172 records, so suggests Qa was reported most, as not all plotshad a second species

```



############ Prepare Climate Variables for P/A and % Cover #########

Check lat-long.

```{r}
cutblock_plots_openings_Buff_ALL_df$Lat
cutblock_plots_openings_Buff_ALL_df$Long

```


#Determine density of plants by cutblock size.
Keep in mind that cutblocks that are adjacent to each other are still currently not combined together to represent total cutblock size.

```{r}
cutblock_plots_openings_Buff_ALL_df$planted_density_TOT #This indicates planting density of the up to 5 species planted. Probably more accurate than creating a proxy. But note, not all have this info, so will lose more data again. Lots of NAs - remove? Make 0? Investigate if these ones are the few without planting.
table(cutblock_plots_openings_Buff_ALL_df$Planted_ALL) 
#There are more than 13 records With NAs :( But only 13 without planting.

#Make ifelse statement for Planted to be 0 density planted if not planted.

```


```{r}
#Make spring growing degree day variables
cutblock_plots_openings_Buff_ALL_df$GDD2_sp_0<-(cutblock_plots_openings_Buff_ALL_df$DD5_04_0 + cutblock_plots_openings_Buff_ALL_df$DD5_05_0 + cutblock_plots_openings_Buff_ALL_df$DD5_06_0)

cutblock_plots_openings_Buff_ALL_df$GDD2_sp_1<-(cutblock_plots_openings_Buff_ALL_df$DD5_04_1 + cutblock_plots_openings_Buff_ALL_df$DD5_05_1 + cutblock_plots_openings_Buff_ALL_df$DD5_06_1)

cutblock_plots_openings_Buff_ALL_df$GDD2_sp_2<-(cutblock_plots_openings_Buff_ALL_df$DD5_04_2 + cutblock_plots_openings_Buff_ALL_df$DD5_05_2 + cutblock_plots_openings_Buff_ALL_df$DD5_06_2)

#Number of Frost Free Days
cutblock_plots_openings_Buff_ALL_df$NFFD2_sp_0<-(cutblock_plots_openings_Buff_ALL_df$NFFD04_0 + cutblock_plots_openings_Buff_ALL_df$NFFD05_0 + cutblock_plots_openings_Buff_ALL_df$NFFD06_0)

cutblock_plots_openings_Buff_ALL_df$NFFD2_sp_1<-(cutblock_plots_openings_Buff_ALL_df$NFFD04_1 + cutblock_plots_openings_Buff_ALL_df$NFFD05_1 + cutblock_plots_openings_Buff_ALL_df$NFFD06_1)

cutblock_plots_openings_Buff_ALL_df$NFFD2_sp_2<-(cutblock_plots_openings_Buff_ALL_df$NFFD04_2 + cutblock_plots_openings_Buff_ALL_df$NFFD05_2 + cutblock_plots_openings_Buff_ALL_df$NFFD06_2)
```

Save file.

```{r}
write.csv(cutblock_plots_openings_Buff_ALL_df, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_Buff_ALL_df_March30_2022.csv")

```



##################### BEGIN VISUALIZATIONS ###############

Visualize differences by categories.

1. Berry abundance by canopy closure, by BEC

```{r}
cutblock_plots_openings_Buff_ALL_df$Fruit.AbunTEST
cutblock_plots_openings_Buff_ALL_df$Canopy.Cov
table(cutblock_plots_openings_Buff_ALL_df$G_BGC_ZONE) #Might need to combine SBPS (n=1) with something else, or just exclude. Also may need to do something with IDF (7).
cutblock_plots_openings_Buff_ALL_df$G_BGC_ZONE 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Canopy Cover",
        x = "Canopy Cover (%)",
        y = "Berry Abundance")  #+


#Remove BEC
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Canopy Cover",
        x = "Canopy Cover (%)",
        y = "Berry Abundance") 
```

Compare to origin age.
```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Time Since Cutblock",
        x = "Time Since Logging",
        y = "Berry Abundance") 

#By BEC
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST,colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Time Since Cutblock",
        x = "Time Since Logging",
        y = "Berry Abundance") 
```

Comapre to VRI age.

```{r}
cutblock_plots_openings_Buff_ALL_df$vri_age #some NAs

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = vri_age, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by VRI Age",
        x = "VRI age",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = vri_age, y = Fruit.AbunTEST, colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by VRI Age",
        x = "VRI age",
        y = "Berry Abundance") 
```


Compare age of cutblock to canopy cover.

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov, colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov)) +
  geom_point () +
  geom_smooth (se=F) +
    theme(panel.background = element_rect(fill = "transparent"),
        panel.border = element_rect(linetype = "solid", fill = NA)) +
  labs (
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

cor(cutblock_plots_openings_Buff_ALL_df$TimeSinceCutblock, cutblock_plots_openings_Buff_ALL_df$Canopy.Cov) #0.70
```


#Look at Growing Degree Days
```{r}
cutblock_plots_openings_Buff_ALL_df$DD5_at_0

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = DD5_at_0, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Growing Degree Days",
        x = "Growing Degree Days > 5",
        y = "Berry Abundance") 
```

```{r}
cutblock_plots_openings_Buff_ALL_df$heatload

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = heatload, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Heatload",
        x = "Heatload",
        y = "Berry Abundance") 

```

Plot berry abundance by plant cover; but note, not complete.

```{r}
cutblock_plots_openings_Buff_ALL_df$Species.Co #About half have NAs
cutblock_plots_openings_Buff_ALL_df$Species.Co<-as.numeric(cutblock_plots_openings_Buff_ALL_df$Species.Co)
cor(cutblock_plots_openings_Buff_ALL_df$Species.Co, cutblock_plots_openings_Buff_ALL_df$Fruit.AbunTEST, use = "complete.obs") #0.05

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Species.Co, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Species Cover",
        x = "Species Cover (%)",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Species.Co, y = Fruit.AbunTEST, colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Species Cover",
        x = "Species Cover (%)",
        y = "Berry Abundance") 
```

By Species Height.
```{r}
cutblock_plots_openings_Buff_ALL_df$Species.He #Only a handful of NAs, actually not too bad
cutblock_plots_openings_Buff_ALL_df$Species.He<-as.numeric(cutblock_plots_openings_Buff_ALL_df$Species.He)

cor(cutblock_plots_openings_Buff_ALL_df$Species.He, cutblock_plots_openings_Buff_ALL_df$Fruit.AbunTEST, use = "complete.obs") #0.27 - this correlation is stronger

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Species.He, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Species Height",
        x = "Species Height (cm)",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Species.He, y = Fruit.AbunTEST, colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Species Height",
        x = "Species Height (cm)",
        y = "Berry Abundance") 
```


planted_density_TOT
# We see not much influence of planting density on berry production here
```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = planted_density_TOT, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Planting Density",
        x = "Planting Density (trees/ha)",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = planted_density_TOT, y = Fruit.AbunTEST, colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Buffaloberry Berry Abundance by Planting Density",
        x = "Planting Density (trees/ha)",
        y = "Berry Abundance") 
```


```{r}
cutblock_plots_openings_Buff_ALL_df$Fruit.Cove<-as.numeric(cutblock_plots_openings_Buff_ALL_df$Fruit.Cove)
cutblock_plots_openings_Buff_ALL_df$Fruit.Cove #Lots of missing values
cutblock_plots_openings_Buff_ALL_df$Burned<-as.factor(cutblock_plots_openings_Buff_ALL_df$Burned)
cutblock_plots_openings_Buff_ALL_df$Burned # We somehow have NA values. Assume not burned.
cutblock_plots_openings_Buff_ALL_df$Burned[is.na(cutblock_plots_openings_Buff_ALL_df$Burned)]<-0

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Burned, y = Fruit.AbunTEST)) +
  geom_boxplot () +
  labs (x = "Not Burned (0), Burned(1)",
        y = "Buffaloberry Fruit Cover")

#No difference
```

Assess for differences in stand age by category.

```{r}
cutblock_plots_openings_Buff_ALL_df$Burned<-as.factor(cutblock_plots_openings_Buff_ALL_df$Burned)

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Burned, y = TimeSinceCutblock)) +
  geom_boxplot () +
  labs (x = "Not Burned (0), Burned(1)",
        y = "Stand Age")

#Stand age is greater in burned areas.
```

Determine canopy cover and stand age by breaking it into burned and not burned.

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov, colour = factor(Burned))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(Burned))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Berry Abundance") 


ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(Burned))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover",
        x = "Canopy Cover",
        y = "Berry Abundance") 
```

#Repeat for Mechanical treatment
#using Mechanical2 

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov, colour = factor(Mechanical2))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(Mechanical2))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(Mechanical2))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover",
        x = "Canopy Cover",
        y = "Berry Abundance") 
```

#Repeat for if planted or not

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov, colour = factor(PLANTED))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(PLANTED))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(PLANTED))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover",
        x = "Canopy Cover",
        y = "Berry Abundance") 
```

Does clearcut technique matter?

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov, colour = factor(DN1_SILSYS_GP))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(DN1_SILSYS_GP))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(DN1_SILSYS_GP))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover",
        x = "Canopy Cover",
        y = "Berry Abundance") 
```

Differences by main species planted?

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Canopy.Cov, colour = factor(Qa))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(Qa))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(Qa))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover",
        x = "Canopy Cover",
        y = "Berry Abundance") 
```


Start season of operations.
```{r}
cutblock_plots_openings_Buff_ALL_df2<-subset(cutblock_plots_openings_Buff_ALL_df, cutblock_plots_openings_Buff_ALL_df$START_SEASON!="NA")

ggplot (cutblock_plots_openings_Buff_ALL_df2, aes (x = TimeSinceCutblock, y = Canopy.Cov, colour = factor(START_SEASON))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Canopy Cover by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Canopy Cover (%)") 

ggplot (cutblock_plots_openings_Buff_ALL_df2, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(START_SEASON))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time Since Cutblock/Logging",
        x = "Time Since Logging",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df2, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(START_SEASON))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover",
        x = "Canopy Cover",
        y = "Berry Abundance") 
```


Cutblock Area.
AREA_SQM
```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = AREA_SQM, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Area of Cutblock",
        x = "Area of Cutblock",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = AREA_SQM, y = Fruit.AbunTEST, colour = factor(G_BGC_ZONE))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Area of Cutblock",
        x = "Area of Cutblock",
        y = "Berry Abundance") 


```

#Chemicals
Chem2
```{r}
cutblock_plots_openings_Buff_ALL_df$Chem2 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(Chem2))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover and Chemical Application",
        x = "Canopy Cover",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(Chem2))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time and Chemical Application",
        x = "Time Since Cutblock",
        y = "Berry Abundance") 
```

#Brushing
Brush2
```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Canopy.Cov, y = Fruit.AbunTEST, colour = factor(Brush2))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Canopy Cover and Brushing",
        x = "Canopy Cover",
        y = "Berry Abundance") 

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TimeSinceCutblock, y = Fruit.AbunTEST, colour = factor(Brush2))) +
  geom_point () +
  geom_smooth (se=F) +
  labs (title = "Berry Abundance by Time and Brushing",
        x = "Time Since Cutblock",
        y = "Berry Abundance") 
```

Look at raw data relationhship shapes to each climate variable

```{r}
str(cutblock_plots_openings_Buff_ALL_df$TSAND)
cutblock_plots_openings_Buff_ALL_df$TSAND<-as.numeric(cutblock_plots_openings_Buff_ALL_df$TSAND)
cutblock_plots_openings_Buff_ALL_df$TSAND

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = TSAND, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Berry Abundance in Cutblocks by % Sand",
        x = "% Sand",
        y = "Berry Abundance")
```


```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Tave_wt_0, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Average Winter Temperature Season Prior",
        x = "Average Winter Temp",
        y = "Berry Abundance")

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Tave_wt_1, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Average Winter Temperature Season Prior",
        x = "Average Winter Temp",
        y = "Berry Abundance")
#Relationship may be more hump shaped centred around -7 degrees as opposed to linear
```

Spring Temperature.
```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Tave_sp_0, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Average Spring Temperature Season Prior",
        x = "Average Spring Temp",
        y = "Berry Abundance")

```

Summer Temperature.
```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = Tave_sm_0, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Average Summer Temperature Season Prior",
        x = "Average Summer Temp",
        y = "Berry Abundance")

```


```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = PAS_total, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Precipitation as Snow",
        x = "Precipitation as snow (mm)",
        y = "Berry Abundance")
```


```{r}
cutblock_plots_openings_Buff_ALL_df$PH2
cutblock_plots_openings_Buff_ALL_df$PH2<-as.numeric(cutblock_plots_openings_Buff_ALL_df$PH2)

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = PH2, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by pH",
        x = "Soil PH",
        y = "Berry Abundance")
#Extrapolated to those <2 pH likely false
```


```{r}
plot(cutblock_plots_openings_Buff_ALL_df$slope_30m_, cutblock_plots_openings_Buff_ALL_df$slope_ha_bc) #Not the same... but positively correlated

cutblock_plots_openings_Buff_ALL_df$slope_30m_<-as.numeric(cutblock_plots_openings_Buff_ALL_df$slope_30m_)
cutblock_plots_openings_Buff_ALL_df$slope_ha_bc<-as.numeric(cutblock_plots_openings_Buff_ALL_df$slope_ha_bc)

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = slope_30m_, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Slope",
        x = "Slope",
        y = "Fruit Abundance")
#Weak relationship (positive)
```

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = slope_ha_bc, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Slope",
        x = "Slope",
        y = "Fruit Abundance")
```

```{r}
cutblock_plots_openings_Buff_ALL_df$aspect_30m<-as.numeric(cutblock_plots_openings_Buff_ALL_df$aspect_30m)

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = aspect_30m, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Coverby Apsect",
        x = "Aspect",
        y = "Fruit Abundance")
```

```{r}
cutblock_plots_openings_Buff_ALL_df$aspect_ha_bc<-as.numeric(cutblock_plots_openings_Buff_ALL_df$aspect_ha_bc)

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = aspect_ha_bc, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Aspect",
        x = "Aspect",
        y = "Fruit Abundance")
```

```{r}
cutblock_plots_openings_Buff_ALL_df$cos_aspect<-cos(cutblock_plots_openings_Buff_ALL_df$aspect_ha_bc)

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = cos_aspect, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Aspect",
        x = "cos(Aspect)",
        y = "Fruit Abundance")
```


```{r}
cutblock_plots_openings_Buff_ALL_df$dem_ha_bc<-as.numeric(cutblock_plots_openings_Buff_ALL_df$dem_ha_bc)

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = dem_ha_bc, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by Elevation",
        x = "Elevation (m)",
        y = "Fruit Abundance")
```


#Because max slope ~40 degrees, can create an SAI (slope-aspect index) value: example = sin(aspect +225) x (slope/45).

```{r}
names(cutblock_plots_openings_Buff_ALL_df)
hist(cutblock_plots_openings_Buff_ALL_df$slope_ha_bc)
cutblock_plots_openings_Buff_ALL_df$SLOPE<-as.numeric(cutblock_plots_openings_Buff_ALL_df$slope_ha_bc)
max(cutblock_plots_openings_Buff_ALL_df$SLOPE) 
hist(cutblock_plots_openings_Buff_ALL_df$aspect_ha_bc)

cor(cutblock_plots_openings_Buff_ALL_df$SLOPE, cutblock_plots_openings_Buff_ALL_df$slope_30m_) #0.70
plot(cutblock_plots_openings_Buff_ALL_df$SLOPE ~ cutblock_plots_openings_Buff_ALL_df$slope_30m_) #Quite different. Perhaps use point values and use DEM to get slope and aspect? Or use the cutblock data because it likely takes the average for the cutblock which is probably more representative.
plot(cutblock_plots_openings_Buff_ALL_df$aspect_ha_bc ~ cutblock_plots_openings_Buff_ALL_df$aspect_30m)


cutblock_plots_openings_Buff_ALL_df$SAI_cb<-(sin(cutblock_plots_openings_Buff_ALL_df$aspect_ha_bc + 225) *(cutblock_plots_openings_Buff_ALL_df$SLOPE/58.9)) #SAI (Slope to aspect Index) of cutblock data slope and aspect
cutblock_plots_openings_Buff_ALL_df$SAI_rec<-(sin(cutblock_plots_openings_Buff_ALL_df$aspect_30m + 225) *(cutblock_plots_openings_Buff_ALL_df$slope_30m_/45)) #SAI of slope and aspect from Clayton's data

hist(cutblock_plots_openings_Buff_ALL_df$SAI_cb)
hist(cutblock_plots_openings_Buff_ALL_df$SAI_rec)
plot(cutblock_plots_openings_Buff_ALL_df$SAI_cb ~ cutblock_plots_openings_Buff_ALL_df$SAI_rec) # The result is COMPLETELY different, depending on which values are used. No correlation what so ever.

```

Compare probabilities between values.

```{r}

ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = SAI_cb, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by SAI",
        x = "SAI_cb",
        y = "Species Cover")
```

```{r}
ggplot (cutblock_plots_openings_Buff_ALL_df, aes (x = SAI_rec, y = Fruit.AbunTEST)) +
  geom_point () +
  geom_smooth () +
  labs (title = "Buffaloberry Percent Cover by SAI",
        x = "SAI_rec",
        y = "Species Cover")
```



#####################  Begin Exploratory Analyses ###########################

#Explore these Harvesting Variables:
Mechanical2 --> although see concerns of how it is the same as mech
Burned
Brush2
Chem2
OPEN_GRSAR OR AREA_SQM (on in ha and one km square)
Canopy_Cov
TimeSinceCutblock/TimeSinceCutblock
START_SEASON2

#Potential Seasonal variables And:
heatload

PAS_total
Tave_wt_1
Tave_sp_0
Tave_sm_0
DD5_0


```{r}

cutblock_plots_openings_Buff_ALL_df$PLANTED<-as.factor(cutblock_plots_openings_Buff_ALL_df$PLANTED)

cutblock_plots_openings_Buff_ALL_df$Mechanical2[is.na(cutblock_plots_openings_Buff_ALL_df$Mechanical2)]<-0
cutblock_plots_openings_Buff_ALL_df$Mechanical2<-as.factor(cutblock_plots_openings_Buff_ALL_df$Mechanical2)

cutblock_plots_openings_Buff_ALL_df$Burned[is.na(cutblock_plots_openings_Buff_ALL_df$Burned)]<-0
cutblock_plots_openings_Buff_ALL_df$Burned<-as.factor(cutblock_plots_openings_Buff_ALL_df$Burned)

cutblock_plots_openings_Buff_ALL_df$Manual2[is.na(cutblock_plots_openings_Buff_ALL_df$Manual2)]<-0
cutblock_plots_openings_Buff_ALL_df$Manual2<-as.factor(cutblock_plots_openings_Buff_ALL_df$Manual2)

cutblock_plots_openings_Buff_ALL_df$Brush2<-as.factor(cutblock_plots_openings_Buff_ALL_df$Brush2)

cutblock_plots_openings_Buff_ALL_df$Chem2[is.na(cutblock_plots_openings_Buff_ALL_df$Chem2)]<-0
cutblock_plots_openings_Buff_ALL_df$Chem2<-as.factor(cutblock_plots_openings_Buff_ALL_df$Chem2)

```

First, let's run a quick GAM on berry abundance in relation to only time since logging, with no covariates. The idea here is just to get an idea of the pattern across time to relate to literature.

```{r}
library(mgcv)

buff.Time.1<-gam(Fruit_Abun_100~ s(TimeSinceCutblock), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Time.1) #not as good of a fit as the huckleberry model
summary(buff.Time.1)
visreg(buff.Time.1, "TimeSinceCutblock")

buff.Time.2<-gam(Fruit_Abun_100~ s(TimeSinceCutblock), family = poisson(), data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Time.2) #WAY WORSE - DO NOT USE!
summary(buff.Time.1)
visreg(buff.Time.1, "TimeSinceCutblock")

##try with canopy cover and no other variables
buff.Time.1b<-gam(Fruit_Abun_100~ s(Canopy_Cov2), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Time.1b) #
summary(buff.Time.1b)
visreg(buff.Time.1b, "Canopy_Cov2") # 0.000958% deviance explained

buff.Time.1b<-gam(Fruit_Abun_100~ s(Canopy_Cov2, k=30), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Time.1b) #
summary(buff.Time.1b)
visreg(buff.Time.1b, "Canopy_Cov2") 

buff.Time.1c<-lm(Fruit_Abun_100 ~ Canopy_Cov2, data=cutblock_plots_openings_Buff_ALL_df)
anova(buff.Time.1c)
visreg(buff.Time.1c, "Canopy_Cov2") 


```

Now, let's assess with Canopy Cover.

```{r}
#Too large below; will need to consider different combinations.
buff.Cov.1<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(Canopy_Cov2, by = Mechanical2) + s(Canopy_Cov2, by = Manual2) + s(Canopy_Cov2, by = Chem2) + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS1), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.1) #Most p-values < 0.05, so may have problems
summary(buff.Cov.1)

#
buff.Cov.1<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(Canopy_Cov2, by = Mechanical2) + s(Canopy_Cov2, by = Manual2) + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS_1), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.1) #Most p-values < 0.05, so may have problems
summary(buff.Cov.1)

#
buff.Cov.2<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(Canopy_Cov2, by = Mechanical2) + s(Canopy_Cov2, by = Chem2) + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS_1), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.2) #Most p-values < 0.05, so may have problems
summary(buff.Cov.2)

AIC(buff.Cov.2, buff.Cov.1) #equiavalent models

#
buff.Cov.3<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(Canopy_Cov2, by = Mechanical2) + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS_1), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.3) #Most p-values < 0.05, so may have problems
summary(buff.Cov.3)

AIC(buff.Cov.2, buff.Cov.3) #equiavalent models

#Remove climate variables not influencing here
buff.Cov.4<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(Canopy_Cov2, by = Mechanical2) + s(Tmax05_0) + s(PPT07_0), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.4) #Most p-values < 0.05, so may have problems
summary(buff.Cov.4)

AIC(buff.Cov.2, buff.Cov.4) #equiavalent models

#
buff.Cov.5<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(Canopy_Cov2, by = Mechanical2) + s(PPT07_0), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.5) #Most p-values < 0.05, so may have problems
summary(buff.Cov.5)

AIC(buff.Cov.5, buff.Cov.4) #Model 5 better

#
buff.Cov.6<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.6) #Most p-values < 0.05, so may have problems
summary(buff.Cov.6)

AIC(buff.Cov.5, buff.Cov.6) #Model 5 is marginally better

#
buff.Cov.7<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.7) #Most p-values < 0.05, so may have problems
summary(buff.Cov.7)

AIC(buff.Cov.7, buff.Cov.6) #Model 7 is better
AIC(buff.Cov.7, buff.Cov.5) #Model 7 is better

draw(buff.Cov.7, scales= 'fixed')

visreg(buff.Cov.7, "Canopy_Cov2", by = "Burned")
visreg(buff.Cov.7, "Canopy_Cov2", by="START_SEASON2")

visreg(buff.Cov.7, "Canopy_Cov2")
visreg(buff.Cov.7, "PPT07_0")

visreg(buff.Cov.7, "START_SEASON2")
visreg(buff.Cov.7, "Mechanical2")
visreg(buff.Cov.7, "Burned")

#Compare to different link function
buff.Cov.8<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0), family = nb(link="sqrt"), data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.8) #Most p-values < 0.05, so may have problems
summary(buff.Cov.8)
#Does not work above

#heatload
buff.Cov.8<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0) + s(heatload), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.8) #Most p-values < 0.05, so may have problems
summary(buff.Cov.8)

AIC(buff.Cov.7, buff.Cov.8) #Models equivalent, but heatload did not add anything.

draw(buff.Cov.7, scales= 'fixed')

visreg(buff.Cov.7, "Canopy_Cov2", by = "Burned")
visreg(buff.Cov.7, "Canopy_Cov2", by="START_SEASON2")

visreg(buff.Cov.7, "Canopy_Cov2")
visreg(buff.Cov.7, "PPT07_0")
visreg(buff.Cov.7, "heatload")

visreg(buff.Cov.7, "START_SEASON2")
visreg(buff.Cov.7, "Mechanical2")
visreg(buff.Cov.7, "Burned")

#slope
buff.Cov.8<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0) + s(heatload) + s(slope_ha_bc_3005), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.8) #Most p-values < 0.05, so may have problems
summary(buff.Cov.8)

buff.Cov.8<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0) + s(slope_ha_bc_3005), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.8) #Most p-values < 0.05, so may have problems
summary(buff.Cov.8)

visreg(buff.Cov.8, "Canopy_Cov2", by = "Burned")
visreg(buff.Cov.8, "Canopy_Cov2", by="START_SEASON2")

visreg(buff.Cov.8, "Canopy_Cov2")
visreg(buff.Cov.8, "PPT07_0")

visreg(buff.Cov.8, "slope_ha_bc_3005")
visreg(buff.Cov.8, "Mechanical2")
visreg(buff.Cov.8, "Burned")


buff.Cov.8b<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0) + s(PPT07_1) + s(slope_ha_bc_3005), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.8b) #Most p-values < 0.05, so may have problems
summary(buff.Cov.8b)

buff.Cov.8b<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + s(Canopy_Cov2, by = START_SEASON2) + s(Canopy_Cov2, by = Burned) + s(PPT07_0) + s(dem_ha_bc) + s(slope_ha_bc_3005), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.8b) #Most p-values < 0.05, so may have problems
summary(buff.Cov.8b)

visreg(buff.Cov.8, "Canopy_Cov2", by = "Burned")
visreg(buff.Cov.8, "Canopy_Cov2", by="START_SEASON2")

visreg(buff.Cov.8, "Canopy_Cov2")
visreg(buff.Cov.8, "PPT07_0")

visreg(buff.Cov.8, "slope_ha_bc_3005")
visreg(buff.Cov.8, "Mechanical2")
visreg(buff.Cov.8, "Burned")



```

Now make a model where each variable is smoothed according to time since that intervention occurred.
```{r}
cutblock_plots_openings_Buff_ALL_df$PREP1_YEAR
cutblock_plots_openings_Buff_ALL_df$PREP2_YEAR

table(cutblock_plots_openings_Buff_ALL_df$PREP1_YEAR, cutblock_plots_openings_Buff_ALL_df$Mechanical2)

```


```{r}
#Below will be too large, so will need to divide and inspect
buff.Cov.9<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(TimeSinceCutblock, by = START_SEASON2) + s(TimeSinceCutblock, by = Burned) + s(CTimeSinceCutblock, by = Mechanical2) + s(TimeSinceCutblock, by = Manual2) + s(TimeSinceCutblock, by = Chem2) + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS1) + s(heatload) + s(Canopy_Cov2), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.9) #Most p-values < 0.05, so may have problems
summary(buff.Cov.9)

#Remove  s(TimeSinceCutblock, by = Manual2) + s(TimeSinceCutblock, by = Chem2)  first
buff.Cov.9<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(TimeSinceCutblock, by = START_SEASON2) + s(TimeSinceCutblock, by = Burned) + s(TimeSinceCutblock, by = Mechanical2) + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS_1) + s(heatload) + s(Canopy_Cov2), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.9) #Most p-values < 0.05, so may have problems
summary(buff.Cov.9)

buff.Cov.10<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2  + s(TimeSinceCutblock, by = Manual2) + s(TimeSinceCutblock, by = Chem2) + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS_1) + s(heatload) + s(Canopy_Cov2), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.10) #P-values good!
summary(buff.Cov.10)

AIC(buff.Cov.10, buff.Cov.9) #Equivalent models

#
buff.Cov.11<-gam(Fruit_Abun_100 ~ START_SEASON2 + Burned + Mechanical2 + Manual2 + Chem2 + s(Tmax05_0) + s(PPT07_0) + s(Tave_wt_0) + s(PAS_1) + s(heatload) + s(Canopy_Cov2), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.11) #P-values mostly < 0.05
summary(buff.Cov.11)

AIC(buff.Cov.10, buff.Cov.11) #Equivalent models
AIC(buff.Cov.11, buff.Cov.9) #Equivalent models

#
buff.Cov.12<-gam(Fruit_Abun_100 ~ START_SEASON2 + Mechanical2 + s(PPT07_0) + s(heatload) + s(Canopy_Cov2), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.12) #P-values mostly < 0.05
summary(buff.Cov.12)

AIC(buff.Cov.12, buff.Cov.11) #Model 12 is better, despite limited predictive capabilities

AIC(buff.Cov.12, buff.Cov.7) #Model 7 a bit better

buff.Cov.13<-gam(Fruit_Abun_100 ~ START_SEASON2 + Mechanical2 + s(PPT07_0) + s(heatload) + s(Canopy_Cov2) + s(slope_ha_bc_3005), family = nb, data=cutblock_plots_openings_Buff_ALL_df, method = "REML", select=TRUE)
gam.check(buff.Cov.13) #P-values mostly < 0.05
summary(buff.Cov.13)

```


