---
title: "Huckleberry_Data_Analysis_Berries_PA"
author: "Cora Skaien"
date: "26/01/2022"
output: html_document
---

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)
library(rgeos)
library(car)
library(rje)
library(caret)
library(pROC)
library(visreg)
library(arm)

source(here::here("R/functions/R_Postgres.R"))
```

#Overview
This file continues from Hucklberry_Data_analysis_Plant_PA, and works with locations where huckleberry did exist to assess patterns for P/A of berries.

#Load in data and prep
```{r}
cutblock_plots_openings_HuckBuff_ALL_df<-read.csv(file="D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_HuckBuff_ALL_df_Jan.csv")

cutblock_plots_openings_Huck_ALL_df_PA<-subset(cutblock_plots_openings_Huck_ALL_df, cutblock_plots_openings_Huck_ALL_df$Species.Pr=="1")

```

Check distribution of plants with berries and those without.

```{r}
table(cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Pres) #122 without, 310 with.

cutblock_plots_openings_Huck_ALL_df_PA$Species.He #Note, lots of NAs... this will be lost data for when this metric is included in the analysis.

cutblock_plots_openings_Huck_ALL_df_PA$Species.Co #Note: lots of NAs here too, so more lost data
```

#####################  Begin Exploratory Analyses ###########################

#Explore these Harvesting Variables:
DN1_DIS_CD
DN1_SILSYS_GP
PREP_MA
PREP_ME
PREP_BU
BRUSH_MA
BRUSH_CM
G_BGC_ZONE
OPEN_GRSAR OR AREA_SQM
PLANTED
Origin
Origin.age
TimeSinceF
TimeSinceC
START_SEASON

#And:
PAS_total
Tave_wt
Tave_sp
Tave_sm
PPT_sp
PPT_sm
Tave_wt_1
Tave_sp_1
Tave_sm_1
PPT_sp_1
PPT_sm_1
Tave_wt_2
Tave_sp_2
Tave_sm_2
PPT_sp_2
PPT_sm_2
DD5_at
DD5_sp
DD5_sm
DD5_wt
NFFD_sp

TSAND
PH2
MODIS_LC (land cover type)
SAI_rec
dem_ha_bc
LandsatCC_

Species.Co
Species.He

```{r}
cutblock_plots_openings_Huck_ALL_df_PA$PAS_total_ann<-cutblock_plots_openings_Huck_ALL_df_PA$PAS_at+ cutblock_plots_openings_Huck_ALL_df_PA$PAS_sm + cutblock_plots_openings_Huck_ALL_df_PA$PAS_sp + cutblock_plots_openings_Huck_ALL_df_PA$PAS_wt
```


```{r}
cutblock_plots_openings_Huck_ALL_df_PA$MODIS_LC<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$MODIS_LC)
table(cutblock_plots_openings_Huck_ALL_df_PA$MODIS_LC)

cutblock_plots_openings_Huck_ALL_df_PA$PLANTED<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PLANTED)

cutblock_plots_openings_Huck_ALL_df_PA$DN1_DIS_CD<-as.factor(as.character(cutblock_plots_openings_Huck_ALL_df_PA$DN1_DIS_CD))

cutblock_plots_openings_Huck_ALL_df_PA$PREP_MA<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PREP_MA)
cutblock_plots_openings_Huck_ALL_df_PA$PREP_ME<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PREP_ME)
cutblock_plots_openings_Huck_ALL_df_PA$PREP_BU<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PREP_BU)

cutblock_plots_openings_Huck_ALL_df_PA$BRUSH_MA<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$BRUSH_MA)

```


#Begin Analyses
Note, these are a lot of variables to be assessing at this time with such a small dataset...
```{r}
#Note: origin + origin.age + TimeSinceF + TimeSinceC are all related and should not all be included in final model

#Species Present or Absent Huckleberry
model.new.1 <- glm (Fruit.Pres ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_wt + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 * Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sp_1*PPT_sp_2 + PPT_sm_1*PPT_sm_2 + DD5_at + DD5_sp + DD5_wt + NFFD_sp + TSAND + PH2 + MODIS_LC + SAI_cb + dem_ha_bc + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #267.4

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_wt + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 * Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sp_1 + PPT_sp_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + DD5_sp + DD5_wt + NFFD_sp + TSAND + PH2 + MODIS_LC + SAI_cb + dem_ha_bc + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #263.7

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_wt + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 * Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sp_1 + PPT_sp_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + DD5_sp + DD5_wt + NFFD_sp + TSAND + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #259.9

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_wt + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 * Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sp_1 + PPT_sp_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + DD5_wt + NFFD_sp + TSAND + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #255.98

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 * Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sp_1 + PPT_sp_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + NFFD_sp + TSAND + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #252.1

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 * Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sp_1 + PPT_sp_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + NFFD_sp + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #250.7

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sp_1 + PPT_sp_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + NFFD_sp + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #249.5

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total_ann + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + NFFD_sp + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #245.9

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + NFFD_sp + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #242.4

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_ME * PREP_BU + BRUSH_MA + PLANTED + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sp + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + NFFD_sp + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #234.98

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_ME * PREP_BU + BRUSH_MA + PLANTED + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + NFFD_sp + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #233.7

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_ME * PREP_BU + BRUSH_MA + PLANTED + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_1 + PPT_sm_2 + DD5_at + PH2 + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #233.6

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_ME * PREP_BU + BRUSH_MA + PLANTED + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #230.5

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ DN1_SILSYS_GP + PREP_ME * PREP_BU + BRUSH_MA + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #228.6

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at + MODIS_LC + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #226.4

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + origin + origin.age + TimeSinceC + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #220.2

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + origin + origin.age + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #220.0

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + origin  + AREA_SQM + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #218.5

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + origin + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #217.6

#Remove least significant
model.new.1 <- glm (Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #216.9

```

Partial residuals

```{r}
model.new.1 <- glm (Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He,
               data=cutblock_plots_openings_Huck_ALL_df_PA,
               family = binomial (link = "logit"))

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #216.9

# model diagnostic plots
binnedplot (fitted(model.new.1), 
            residuals(model.new.1), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
#Despite model performing well (see AUC in next section), this resid plot does not look great?

#Partial residuals plot
visreg(model.new.1, "PREP_ME", by="PREP_BU")
visreg(model.new.1, "PREP_BU", by="PREP_ME")

visreg(model.new.1, "BRUSH_MA")
visreg(model.new.1, "START_SEASON")

visreg(model.new.1, "Tave_sm")
visreg(model.new.1, "PPT_sp")
visreg(model.new.1, "PPT_sm")
visreg(model.new.1, "Tave_wt_1")
visreg(model.new.1, "Tave_wt_2")
visreg(model.new.1, "Tave_sp_1", by="Tave_sp_2")
visreg(model.new.1, "Tave_sp_2", by="Tave_sp_1")
visreg(model.new.1, "Tave_sm_1", by="Tave_sm_2")
visreg(model.new.1, "Tave_sm_2", by="Tave_sm_1")
visreg(model.new.1, "PPT_sm_2")
visreg(model.new.1, "DD5_at")

visreg(model.new.1, "LandsatCC_")
visreg(model.new.1, "Species.Co")
visreg(model.new.1, "Species.He")
```


Determine AUC by splitting into training and validation set (85% and 15% given small sample size).

```{r}
summary(model.new.1)

#Create a new blank table and get AUC too
top_mod_table_PA_Plant <- data.frame (matrix (ncol = 27, nrow = 0))
colnames (top_mod_table_PA_Plant ) <- c ("Model", "Model_terms", "intercept", "coef_PREP_ME1", "coef_PREP_BU1", "coef_BRUSH_MA1", "coef_START_SEASONSpring", "coef_START_SEASONSummer",  "coef_START_SEASONFall", "coef_Tave_sm", "coef_PPT_sp", "coef_PPT_sm","coef_Tave_wt_1", "coef_Tave_wt_2", "coef_Tave_sp_1", "coef_Tave_sp_2", "coef_Tave_sm_1", "coef_Tave_sm_2", "coef_PPT_sm_2", "coef_DD5_at", "coef_LandsatCC_", "coef_Species.Co", "coef_Species_He", "coef_PREP_ME1:PREP_BU1", "coef_Tave_sp_1:Tave_sp_2", "coef_Tave_sm_1:Tave_sm_2", "AUC")
```

Let's run it 500 times to get good mean values.

Remove NAs in response.

```{r}
cutblock_plots_openings_Huck_ALL_df_PA2<-subset(cutblock_plots_openings_Huck_ALL_df_PA, cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Pres!="NA")
```


```{r}

for (g in 1:500){

prop<-0.85
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(cutblock_plots_openings_Huck_ALL_df_PA2$Fruit.Pres, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- cutblock_plots_openings_Huck_ALL_df_PA2[ trainIndex,]
   Valid <- cutblock_plots_openings_Huck_ALL_df_PA2[-trainIndex,]
   
#Model   
model.new.1<-glm(Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.new.1, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"Fruit.Pres"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_PlantPA <- data.frame (matrix (ncol = 27, nrow = 0))
colnames (top_mod_table_PlantPA ) <- c ("Model", "Model_terms", "intercept", "coef_PREP_ME1", "coef_PREP_BU1", "coef_BRUSH_MA1", "coef_START_SEASONSpring", "coef_START_SEASONSummer",  "coef_START_SEASONFall", "coef_Tave_sm", "coef_PPT_sp", "coef_PPT_sm","coef_Tave_wt_1", "coef_Tave_wt_2", "coef_Tave_sp_1", "coef_Tave_sp_2", "coef_Tave_sm_1", "coef_Tave_sm_2", "coef_PPT_sm_2", "coef_DD5_at", "coef_LandsatCC_", "coef_Species.Co", "coef_Species_He", "coef_PREP_ME1:PREP_BU1", "coef_Tave_sp_1:Tave_sp_2", "coef_Tave_sm_1:Tave_sm_2", "AUC")

##Add data for NDT1
top_mod_table_PlantPA[1,1]<-"Berries PA"
top_mod_table_PlantPA[1,2]<-"Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He"
top_mod_table_PlantPA[1,3]<- coef(model.new.1)[1] #Intercept
top_mod_table_PlantPA[1,4]<- coef(model.new.1)[2] #Intercept
top_mod_table_PlantPA[1,5]<- coef(model.new.1)[3] #Intercept
top_mod_table_PlantPA[1,6]<- coef(model.new.1)[4] #
top_mod_table_PlantPA[1,7]<- coef(model.new.1)[5] #
top_mod_table_PlantPA[1,8]<- coef(model.new.1)[6] #coefficient 
top_mod_table_PlantPA[1,9]<- coef(model.new.1)[7] #coefficient 
top_mod_table_PlantPA[1,10]<- coef(model.new.1)[8] #coefficient
top_mod_table_PlantPA[1,11]<- coef(model.new.1)[9] #
top_mod_table_PlantPA[1,12]<- coef(model.new.1)[10] #coefficient 
top_mod_table_PlantPA[1,13]<- coef(model.new.1)[11] #coefficient 
top_mod_table_PlantPA[1,14]<- coef(model.new.1)[12] #coefficient
top_mod_table_PlantPA[1,15]<- coef(model.new.1)[13] #coefficient
top_mod_table_PlantPA[1,16]<- coef(model.new.1)[14] #coefficient
top_mod_table_PlantPA[1,17]<- coef(model.new.1)[15] #coefficien
top_mod_table_PlantPA[1,18]<- coef(model.new.1)[16] #coefficient 
top_mod_table_PlantPA[1,19]<- coef(model.new.1)[17] #
top_mod_table_PlantPA[1,20]<- coef(model.new.1)[18] #  
top_mod_table_PlantPA[1,21]<- coef(model.new.1)[19] # 
top_mod_table_PlantPA[1,22]<- coef(model.new.1)[20] # 
top_mod_table_PlantPA[1,23]<- coef(model.new.1)[21] # 
top_mod_table_PlantPA[1,24]<- coef(model.new.1)[22] # 
top_mod_table_PlantPA[1,25]<- coef(model.new.1)[23] # 
top_mod_table_PlantPA[1,26]<- coef(model.new.1)[24] # 
top_mod_table_PlantPA[1,27]<- mod.auc

top_mod_table_PA_Plant<-rbind(top_mod_table_PA_Plant, top_mod_table_PlantPA)

}

```

Check.
```{r}
head(top_mod_table_PA_Plant)

```

#Save coefficient table

```{r}
write.csv(top_mod_table_PA_Plant, file="D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Top_Mod_PlantPA.csv")
```

Get mean values.

```{r}
top_mod_table_PA_Plant_mean<-top_mod_table_PA_Plant %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table_PA_Plant_mean

top_mod_table_PA_Plant_mean[1,1]<-"Berries PA"
top_mod_table_PA_Plant_mean[1,2]<-"Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He"
top_mod_table_PA_Plant_mean
```
Save mean coefficient table.

```{r}
write.csv(top_mod_table_PA_Plant_mean, file="D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Top_Mod_PlantPA_mean.csv")
```

Get SD.

```{r}
top_mod_table_PA_Plant_SD<-top_mod_table_PA_Plant %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_PA_Plant_SD

top_mod_table_PA_Plant_SD[1,1]<-"Berries PA"
top_mod_table_PA_Plant_SD[1,2]<-"Fruit.Pres ~ PREP_ME * PREP_BU + BRUSH_MA + START_SEASON + Tave_sm + PPT_sp + PPT_sm + Tave_wt_1 + Tave_wt_2 + Tave_sp_1*Tave_sp_2 + Tave_sm_1*Tave_sm_2 + PPT_sm_2 + DD5_at  + LandsatCC_ + Species.Co + Species.He"
top_mod_table_PA_Plant_SD
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_PA_Plant_SD, file="D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Top_Mod_PlantPA_SD.csv")
```

