---
title: "Buffaloberry_Data_analysis"
author: "Cora Skaien"
date: "14/01/2022"
output: html_document
---
<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)
library(rgeos)
library(car)
library(rje)
library(caret)
library(pROC)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

##Data sets for what purpose
1. Percent cover huckleberry: cutblock_plots_openings_Huck_ALL_df
2. Other elements huckleberry: cutblock_plots_openings_Huck_ALL_df_Huck (although if use above, NA remove will likely get same result- *should* at least)

3. Percent cover buffaloberry (plant and berries separate), Presence buffaloberry (plant and berries separate): cutblock_plots_openings_Buff_ALL_df

#Overview
This file continues from huckleberry_data_processing_Dec2021, and shows some initial exploration of the buffaloberry data. The buffaloberry data is comprised of two datasets, both from Mowat but from different colleagues of his. The second dataset is missing some of the crucial information in the first dataset (pH, % sand, ClimateBC data, etc). These additional elements must be appended to the data before performing analyses.

The weather the year before dictate flowering and berries for buffaloberry. Get the year before data as well! Maybe spring weather year before. Garth to send some papers and link to website.

More data coming from Laura apparently!



########## Repeat for Buffalo berry


```{r}
buffalo_data<-subset(berry_data, berry_data$Species=="Shepherdia_canadensis")
str(buffalo_data)#208
hist(buffalo_data$CutBlock_Year)
table(buffalo_data$CutBlock_Occurrence) #Suggests that 17 of these were not actually in cutblocks.
table(buffalo_data$CutBlock_Occurrence, buffalo_data$CutBlock_Year) #All 16 not in cutblocks were indicated last harvested in 1900 in Clayton's data
table(buffalo_data$CutBlock_Occurrence, buffalo_data$HARVESTYR) #appears that 13/16 of the plots not harvested were harvested after Clayton's data. Use Clayton's harvest year data as a result. Some data was even collected in 2014 or 2015, so the patches were likely harvested after. Remove all with cutblock_occurence = 0
buffalo_data<-subset(buffalo_data,buffalo_data$CutBlock_Occurrence=="1")
str(buffalo_data) #191 observations

#Inspect presence/absence of huckleberries in data
table(buffalo_data$Species.Present) #88 absences and 103 presences

#I am curious about cutblock size, but I acknowledge that it is not fully representative of the greater area given that adjacent cutblocks could occur before or after this cutblock, making the greater connected area far larger than what this value suggests.

hist(buffalo_data$AREAHA)
hist(buffalo_data$AREA_SQM)


hist(buffalo_data$OPEN_GRSAR)
table(buffalo_data$DN1_DIS_CD) # Mostly L (logged). May want to subset so only have logged
table(buffalo_data$DN2_DIS_CD) #Additional elements
table(buffalo_data$DN1_SILSYS) #79 CCRES (Clearcut with reserves); 82 Clearcut; spattering of others.
table(buffalo_data$PREP1_TECH) # 29 BU (burn), 63 ME (mechanical); spattering of others.

buffalo_data$PREP1_2<-paste(buffalo_data$PREP1_TECH,buffalo_data$PREP2_TECH)
table(buffalo_data$PREP1_2) #210 records of NA, lots of combinations otherwise. Maybe make a column that is yes/no for each technique that is considered important?
table(buffalo_data$BRSH1_TECH) #Brushing technique;37 MA (manual); 8 CG (Chemical Ground); 12 CA (Chemical Air); and others
table(buffalo_data$PLNT1_TECH) #Mostly PL (planting); some FP (Fill Planting); likely not as useful.
hist(buffalo_data$FEAT_AREA)
hist(buffalo_data$PLNT1_AREA) #Also has a Plant2, so could add together for total planting area?

```



If select only logged sites:

```{r}
buffalo_data_logged<-subset(berry_data_logged, berry_data_logged$Species=="Shepherdia_canadensis")

table(buffalo_data_logged$DN1_SILSYS) #May wish to group the smaller groups into an "other" category; or remove
table(buffalo_data_logged$PREP1_TECH) #May wish to remove the 4 MA.

#Compare above with data
table(buffalo_data_logged$Species.Present) #93 absent, 103 present
table(buffalo_data_logged$Species.Present, buffalo_data_logged$PREP1_TECH) #I would remove all small categories
table(buffalo_data_logged$Species.Present, buffalo_data_logged$DN1_SILSYS) #I would remove all small categories

```

Now that we know that we have data that we can play around with, we can add additional information to these. We want to find out information on elements of forestry practices, such as planting density, burning, site prep, etc.

