---
title: "Huckleberry_data_processing"
author: "Cora Skaien"
date: "29/07/2021"
output: html_document
---
<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)
library(rgeos)
library(car)
library(rje)
library(caret)
library(pROC)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

#Overview
We have a dataset provided by Clayton Lamb and Garth Mowat that contains information on numerous shrub species occurrence, cover, fruit phenology, sugar content, etc. Using the consolidated cutblock layer available online (https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-), I was able to use the intersect tool in QGIS to determine which of the plots in the provided data occurred in cutblocks. Here, we will bring in both layers, append the data together between the two files, and then subset the huckleberry (Vaccinium membranaceum) and buffalo berry (Shepherdia canadensis) to see how large our dataset is.

Bring in the shape file with the coordinates within cutblocks. This data was processed in QGIS, using the consolidated cutblock layer. This data also has the Relevant "Openings data" and "Activity Treatment" appended to it. Note, that when selecting points by polygons within Openings and Activity Treatment data sets, often points were duplicated. To fix this issue, we used the "Delete Duplicate Geometries" function in QGIS. Because of limitations with the data, each time we intersect with more RESULTS layers, we lose data. As a result, it is important to consider which factors (and specificity) are most important for the analysis as 30-50% of the data is lost when we use the ACTIVITY TREATMENT data as opposed to just the OPENINGS data. 

This link will be very useful for determining what the codes mean:
https://www.for.gov.bc.ca/hfp/publications/00026/fs708-14-appendix_d.htm#ad_16

This may also prove useful:
https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/silviculture/silviculture-reporting-results/technical-documentation

We have multiple datasets to work with.

#Dataset #1: Clayton Lamb and Garth Mowat data on huckleberry and Buffaloberry
This data has P/A of plants and of berries, and P/A of fruits and of berries. There is also a measure of sugar content (energetics) and other potentially useful and interesting response variables.
```{r}
#This first file has ALL of the locations within cutblocks 
cutblock_plots<- st_read ( dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Plots_in_cutblocks_FINAL.shp", stringsAsFactors = T)

#This second file has openings data from RESULTS already appended in QGIS, but we lose data
cutblock_plots_openings<- st_read ( dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Huck_Buff_Openings_duplicates_removed.shp", stringsAsFactors = T)
str(cutblock_plots_openings)

st_crs(cutblock_plots_openings)
plot(cutblock_plots_openings)
table(cutblock_plots_openings$Site_ID) 

#This third file has Openings and Activity Treatment data appended, but we lose even more data
cutblock_plots_openings_activity<- st_read ( dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Huck_Buff_Openings_Activity_duplicates_removed.shp", stringsAsFactors = T)
str(cutblock_plots_openings_activity)

st_crs(cutblock_plots_openings_activity)
plot(cutblock_plots_openings_activity)
table(cutblock_plots_openings_activity$Site_ID) 
```

```{r}
## Elevation is missing from data! Need to get from DEM
#Elevation
DEM <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\dem_ha_bc.tif")
plot(DEM)
crs(DEM)
crs(cutblock_plots_openings) #Same!

pointCoordinates<-data.frame(cutblock_plots_openings$coords_x1, cutblock_plots_openings$coords_x2)
head(pointCoordinates)

ELEVATION=raster::extract(DEM, pointCoordinates)
head(ELEVATION)

#Append
cutblock_plots_openings<-cbind(cutblock_plots_openings, ELEVATION)
head(cutblock_plots_openings)
```
Need to decide whether want DEM Slope and Aspect as well, in case other values differ.


#Datasets #2: Garth Mowat and new student's data on huckleberry and buffalo berry separately.
This dataset should have the same features as the above overall, but column names differ and will need to be re-named for binding datasets together.

```{r}
cutblock_plots_openings_mowatBuff<- st_read ( dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Mowat_Buff_Openings_duplicates_removed.shp", stringsAsFactors = T)

cutblock_plots_openings_activity_mowatBuff<- st_read ( dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Mowat_Buff_Openings_Activity_duplicates_removed.shp", stringsAsFactors = T)
```

#DEM Info inaccurate in cutblock_plots_openings_mowatBuff, so append DEM info

```{r}
##Slope
DEM_slope <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc.tif")

DEM_aspect <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc.tif")

#Elevation
DEM <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\dem_ha_bc.tif")

#Stack rasters
rasStack = stack(DEM_slope, DEM_aspect, DEM)
crs(rasStack)
head(rasStack)
str(rasStack)
crs(cutblock_plots_openings_mowatBuff)
plot(DEM)
plot(cutblock_plots_openings_mowatBuff[1])
plot(DEM ,cutblock_plots_openings_mowatBuff[1]) #Hard to gauge if in right spot

#Set crs
cutblock_plots_openings_mowatBuff2 <- st_transform (cutblock_plots_openings_mowatBuff, 3005)
crs(cutblock_plots_openings_mowatBuff2)

#Extract GPS locations
names(cutblock_plots_openings_mowatBuff)

##Try this first
test<-cbind(cutblock_plots_openings_mowatBuff2, st_coordinates(cutblock_plots_openings_mowatBuff2))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)
#crs(pointCoordinates) #No CRS when a dataframe

##Extract DEM values from stacked layer
rasValue2=raster::extract(rasStack, pointCoordinates)
head(rasValue2) #ALL NAs so did not work right
str(rasValue2) #59 values
str(cutblock_plots_openings_mowatBuff)#59 values

#Append new information
cutblock_plots_openings_mowatBuff<-cbind(cutblock_plots_openings_mowatBuff2, rasValue2)
head(cutblock_plots_openings_mowatBuff)
crs(cutblock_plots_openings_mowatBuff)
```
Save new file.
```{r}
st_write(cutblock_plots_openings_mowatBuff, dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Mowat_Buff_Openings_duplicates_removed_DEM.shp")
```


#Datasets #3: BEC Plots
This dataset has presence only values for each huckleberry and buffalo berry, and only presents the percent cover of the plant itself (not berries). This can be used best for percent cover models, but because does not have absence values, may be best only to use for percent cover.

```{r}

cutblock_plots_openings_BECHuck<- st_read ( dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\BEC_huck_Openings_duplicates_removed.shp", stringsAsFactors = T)

cutblock_plots_openings_activity_BECHuck<- st_read ( dsn = "D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\BEC_huck_Openings_Activity_duplicates_removed.shp", stringsAsFactors = T)

```

##Remove Geometry for Processing Moving Forwards
For processing below, we do not need these files to be spatial files. Turn them into dataframes and this will help speed up processing.

```{r}
cutblock_plots_df<-st_drop_geometry(cutblock_plots)
str(cutblock_plots_df)
cutblock_plots_openings_Huck_ALL_df<-st_drop_geometry(cutblock_plots_openings)
cutblock_plots_openings_activity_df<-st_drop_geometry(cutblock_plots_openings_activity)

cutblock_plots_openings_mowatBuff_df<-st_drop_geometry(cutblock_plots_openings_mowatBuff)
cutblock_plots_openings_activity_mowatBuff_df<-st_drop_geometry(cutblock_plots_openings_activity_mowatBuff)

cutblock_plots_openings_BECHuck_df<-st_drop_geometry(cutblock_plots_openings_BECHuck)
cutblock_plots_openings_activity_BECHuck_df<-st_drop_geometry(cutblock_plots_openings_activity_BECHuck)

```

#Productivity data missing in cutblock_plots_openings_Huck_ALL_df and cutblock_plots_openings_activity_df. Must bring in and append

```{r}
prod.data<-read.csv(file="D://Hucklberry//Grizzly Bear stuff//berries//data//Productivity_Data.csv")
head(prod.data)
prod.data$Site_ID<-prod.data$Site.ID
head(cutblock_plots_df)

cutblock_plots_df<-left_join(cutblock_plots_df, prod.data, by="Site_ID")
head(cutblock_plots_df)

cutblock_plots_openings_Huck_ALL_df<-left_join(cutblock_plots_openings_Huck_ALL_df, prod.data, by="Site_ID")
head(cutblock_plots_openings_Huck_ALL_df)

cutblock_plots_openings_activity_df<-left_join(cutblock_plots_openings_activity_df, prod.data, by="Site_ID")
head(cutblock_plots_openings_activity_df)

```

#Combine appropriate files

```{r}
head(cutblock_plots_openings_Huck_ALL_df)
table(cutblock_plots_openings_Huck_ALL_df$Species.y) #202 buffaloberry; 628 huckleberry
head(cutblock_plots_openings_mowatBuff_df) #Only Buffaloberry
head(cutblock_plots_openings_BECHuck_df) #only huckleberry

#Separate by species
cutblock_plots_openings_Huck_ALL_df_Buff<-subset(cutblock_plots_openings_Huck_ALL_df, cutblock_plots_openings_Huck_ALL_df$Species.y=="Shepherdia_canadensis")
cutblock_plots_openings_Huck_ALL_df_Huck<-subset(cutblock_plots_openings_Huck_ALL_df, cutblock_plots_openings_Huck_ALL_df$Species.y=="Vaccinium_membranaceum")

#Because sample size increased, see if in cutblocks
table(cutblock_plots_openings_Huck_ALL_df_Buff$CutBlock_Occurrence)#Suggests 16 not
table(cutblock_plots_openings_Huck_ALL_df_Huck$CutBlock_Occurrence) #Suggests 27 not

cutblock_plots_openings_Huck_ALL_df_Buff<-subset(cutblock_plots_openings_Huck_ALL_df_Buff, cutblock_plots_openings_Huck_ALL_df_Buff$CutBlock_Occurrence=="1")

cutblock_plots_openings_Huck_ALL_df_Huck<-subset(cutblock_plots_openings_Huck_ALL_df_Huck, cutblock_plots_openings_Huck_ALL_df_Huck$CutBlock_Occurrence=="1")
```

```{r}
#Ensure names consistent between files to be combined
## 1. cutblock_plots_openings_Huck_ALL_df_Huck, cutblock_plots_openings_BECHuck_df
names(cutblock_plots_openings_Huck_ALL_df_Huck) # Key names: Species.Cover, HARVEST_YE == CutBlock_Year
names(cutblock_plots_openings_BECHuck_df) #key names: TotalB, HARVESTYR 
#Many other variables may qish to acquire for BEC data, like fire year, 
##Note, all climate variables NAs... need to run through climateBC and get


#Update names in cutblock_plots_openings_BECHuck_df
cutblock_plots_openings_BECHuck_df<-rename(cutblock_plots_openings_BECHuck_df,
                   c("Species.Cover"="TotalB",
                     "HARVEST_YE"="HARVESTYR"))

cutblock_plots_openings_BECHuck_df$Species.Present<-1
table(cutblock_plots_openings_BECHuck_df$Species.Present)

#Combine
# fill in non-overlapping columns with NAs
cutblock_plots_openings_Huck_ALL_df_Huck[setdiff(names(cutblock_plots_openings_BECHuck_df), names(cutblock_plots_openings_Huck_ALL_df_Huck))] <- NA
cutblock_plots_openings_BECHuck_df[setdiff(names(cutblock_plots_openings_Huck_ALL_df_Huck), names(cutblock_plots_openings_BECHuck_df))] <- NA

cutblock_plots_openings_Huck_ALL_df<-rbind(cutblock_plots_openings_Huck_ALL_df_Huck, cutblock_plots_openings_BECHuck_df)

head(cutblock_plots_openings_Huck_ALL_df) #May need to alter additional columns to be synonymous - will find out during data processing

table(cutblock_plots_openings_Huck_ALL_df$Species.y)
table(cutblock_plots_openings_Huck_ALL_df_Huck$Species.y)
table(cutblock_plots_openings_BECHuck_df$Species) #1686
table(cutblock_plots_openings_Huck_ALL_df$Species)
head(cutblock_plots_openings_BECHuck_df)
```

Repeat for Buffaloberry

```{r}
## 2. cutblock_plots_openings_Huck_ALL_df_Buff, cutblock_plots_openings_mowatBuff_df
names(cutblock_plots_openings_Huck_ALL_df_Buff)
names(cutblock_plots_openings_mowatBuff_df)

cutblock_plots_openings_mowatBuff_df$Clear_Cut
cutblock_plots_openings_mowatBuff_df$Canopy_C_1
cutblock_plots_openings_mowatBuff_df$Canopy_Cov

plot(cutblock_plots_openings_mowatBuff_df$Canopy_C_1, cutblock_plots_openings_mowatBuff_df$Canopy_Cov)

cutblock_plots_openings_mowatBuff_df$Buff_Spe_1 #Buff Species Percent cover

#"Buff_Fruit" "Buff_Fru_1" "Buff_Fru_2" "count_of_B" "count_of_1" "Buff_Fru_3" "USED"
cutblock_plots_openings_mowatBuff_df$Buff_Fruit #Buff_Fruit_Present
cutblock_plots_openings_mowatBuff_df$Buff_Fru_1 # Buff_Fruit_Stage
cutblock_plots_openings_mowatBuff_df$Buff_Fru_2 # Buff_Fruiting_Plant_Cover_percent
cutblock_plots_openings_Huck_ALL_df_Buff$Fruit.Cover

cutblock_plots_openings_mowatBuff_df$count_of_B #--> count_of_Buff_Estimate_per_m2
cutblock_plots_openings_mowatBuff_df$count_of_1 #--> count_of_Buffaloberrries_per_plot
cutblock_plots_openings_mowatBuff_df$Buff_Fru_3 # --> Buff_Fruiting_Plant_Height_cm


#mowat
cutblock_plots_openings_mowatBuff_df2<-rename(cutblock_plots_openings_mowatBuff_df,
                   c("Species.Present"="shep_occur",
                     "Species.Cover"="Buff_Spe_1",
                     "HARVEST_YE"="Harvest_Ye",
                     "CutBlock_Occurrence"="Clear_Cut",
                     "LandsatCC_2010_Fixed" = "Canopy_C_1",
                      "Fruit.Present"="Buff_Fruit",
                     "Fruit.Cover"="Buff_Fru_2",
                     "Species.Height"="Buff_Fru_3",
                     "Fruit.Abund"="count_of_B", ##Need to check this is indeed equivalent
                     "Fruit.Phenology"="Buff_Fru_1"))

#Need to figure out how to relate Fruit.Brix and shep_KCAL between files.
#DEM_SLOPE is suspicious as all values are 89 except one that is 0.... redo DEM data?
# No PH data for this second file

#If we assume all data was collected in 2021, we can calculate time since fire and harvest
head(cutblock_plots_openings_mowatBuff_df2)
table(cutblock_plots_openings_mowatBuff_df2$WILDFIRE_Y) #I am unsure how to assess these values... there are 58 values of 0 and one value of 109??
table(cutblock_plots_openings_mowatBuff_df2$HARVEST_YE) #Are these number of years since? Cross check with RESULTS data
table(cutblock_plots_openings_mowatBuff_df2$HARVEST_YE, cutblock_plots_openings_mowatBuff_df2$HARVESTYR) #Do not make sense...


cutblock_plots_openings_mowatBuff_df2$TimeSinceCut<-(2021-cutblock_plots_openings_mowatBuff_df2$HARVESTYR)

table(cutblock_plots_openings_mowatBuff_df2$TimeSinceCut)

```
Now combine

```{r}
# fill in non-overlapping columns with NAs
cutblock_plots_openings_Huck_ALL_df_Buff[setdiff(names(cutblock_plots_openings_mowatBuff_df2), names(cutblock_plots_openings_Huck_ALL_df_Buff))] <- NA
cutblock_plots_openings_mowatBuff_df2[setdiff(names(cutblock_plots_openings_Huck_ALL_df_Buff), names(cutblock_plots_openings_mowatBuff_df2))] <- NA

#Combine
cutblock_plots_openings_Buff_ALL_df<-rbind(cutblock_plots_openings_Huck_ALL_df_Buff, cutblock_plots_openings_mowatBuff_df2)

head(cutblock_plots_openings_Buff_ALL_df)
table(cutblock_plots_openings_Buff_ALL_df$CutBlock_Occurrence) #25 without, 236 with
```
Save Buffaloberry files.

```{r}
names(cutblock_plots_openings_Buff_ALL_df)
cutblock_plots_openings_Buff_ALL_df[68]
cutblock_plots_openings_Buff_ALL_df[184]

cutblock_plots_openings_Buff_ALL_df<-cutblock_plots_openings_Buff_ALL_df[-184]

st_write(cutblock_plots_openings_Buff_ALL_df, dsn="D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Mowat_Buff_Openings_duplicates_removed_DEM_df2b.csv")
```
############################ PREP COMPLETE ####################

##Data sets for what purpose
1. Percent cover huckleberry: cutblock_plots_openings_Huck_ALL_df
2. Other elements huckleberry: cutblock_plots_openings_Huck_ALL_df_Huck (although if use above, NA remove will likely get same result- *should* at least)

3. Percent cover buffaloberry (plant and berries separate), Presence buffaloberry (plant and berries separate): cutblock_plots_openings_Buff_ALL_df

##############

