---
title: "Huckleberry_Soils"
author: "Cora Skaien"
date: "16/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sf)
library(dplyr)
```

#Overview
This document is meant to bring in the files for soils and to take away the spatial component so that I can send them to Deepa Filatow to see if we can make soil layers for my points of interest.

Bring in the data for soils. Used files with duplicates removed.
```{r}
cutblock_plots_openings_soils<- st_read ( dsn = "D:\\Hucklberry\\Clayton_openings_soils_reduced.shp", stringsAsFactors = T) #986 observations
str(cutblock_plots_openings)

Huck_Laura_Berries_soils<-st_read ( dsn = "D:\\Hucklberry\\Laura_openings_soils_reduced.shp", stringsAsFactors = T)
head(Huck_Laura_Berries) #42 datapoints

cutblock_plots_openings_mowatBuff_soils<- st_read ( dsn = "D:\\Hucklberry\\Mackenzie_openings_soils_reduced.shp", stringsAsFactors = T)

```

Bring in the data for openings without soils.
```{r}
cutblock_plots_openings<- st_read ( dsn = "D:\\Hucklberry\\Clayton_OPENINIGS_Plots2.shp", stringsAsFactors = T) #986 observations
str(cutblock_plots_openings)

Huck_Laura_Berries<-st_read ( dsn = "D:\\Hucklberry\\Laura_OPENINGS_All.shp", stringsAsFactors = T)
head(Huck_Laura_Berries) #42 datapoints

cutblock_plots_openings_mowatBuff<- st_read ( dsn = "D:\\Hucklberry\\Mackenzie_Points_Buff_OPENINGS.shp", stringsAsFactors = T)
```

Make into dataframes.
```{r}
cutblock_plots_openings_soils_df<- st_drop_geometry(cutblock_plots_openings_soils)
Huck_Laura_Berries_soils_df<- st_drop_geometry(Huck_Laura_Berries_soils)
cutblock_plots_openings_mowatBuff_soils_df<-st_drop_geometry(cutblock_plots_openings_mowatBuff_soils) 

cutblock_plots_openings_df<- st_drop_geometry(cutblock_plots_openings)
Huck_Laura_Berries_df<- st_drop_geometry(Huck_Laura_Berries)
cutblock_plots_openings_mowatBuff_df<- st_drop_geometry(cutblock_plots_openings_mowatBuff)
```

From above: 
  1. Clayton data: 986 observations, 1181 soils
  2. Laura's data: 42 observations, somehow 84 in soils data (repeats)
  3. Mackenzie's data: 68 observations, 79 from soils

Combine files together so that rows from openings data have information from sols data regardless.

```{r}
Clayton_cutblock_plots_openings_df_soils<-full_join(cutblock_plots_openings_df, cutblock_plots_openings_soils_df) #If join this way, end up with 1240 observations

Laura_cutblock_plots_openings_df_soils<-full_join(Huck_Laura_Berries_df, Huck_Laura_Berries_soils_df) # end up with 42 observations - excellent!

Mackenzie_cutblock_plots_openings_df_soils<-full_join(cutblock_plots_openings_mowatBuff_df, cutblock_plots_openings_mowatBuff_soils_df) #End up with 68 observations - excellent!

```

Note, there are many repeat rows, likely from overlap? Send to Deepa and discuss.

Save files.
```{r}
write.csv(Clayton_cutblock_plots_openings_df_soils, file="D:\\Hucklberry\\Clayton_cutblock_plots_openings_df_soils.csv")

write.csv(Laura_cutblock_plots_openings_df_soils, file="D:\\Hucklberry\\Laura_cutblock_plots_openings_df_soils.csv")

write.csv(Mackenzie_cutblock_plots_openings_df_soils, file="D:\\Hucklberry\\Mackenzie_cutblock_plots_openings_df_soils.csv")
```

Investigate each for duplicates and nature of duplicates.
```{r}
head(Clayton_cutblock_plots_openings_df_soils) #Top 2 rows are identical
table(Clayton_cutblock_plots_openings_df_soils$Site.ID) # many IDs repeated
table(cutblock_plots_openings_df$Site.ID) #Some repeats in SiteID as well towards end

cutblock_plots_openings_df$Site.ID2<-paste(cutblock_plots_openings_df$Site.ID, cutblock_plots_openings_df$coords.x2)
table(cutblock_plots_openings_df$Site.ID2) #Repeats exist. Perhaps because huckleberry and buffaloberry. But fewer repeats than above.
```

```{r}
head(Laura_cutblock_plots_openings_df_soils) #Every set of 2 at top are duplicated with each other
Laura_cutblock_plots_openings_df_soils$Site_ID2<-paste(Laura_cutblock_plots_openings_df_soils$Site_ID, Laura_cutblock_plots_openings_df_soils$Distance, Laura_cutblock_plots_openings_df_soils$Year)
table(Laura_cutblock_plots_openings_df_soils$Site_ID2) #Everything has 2 reports

#also note, because so close together along transect, all get given same soil information from that polygon.

head(Huck_Laura_Berries_df)
table(Huck_Laura_Berries_df$Site_ID)
Huck_Laura_Berries_df$Site_ID2<-paste(Huck_Laura_Berries_df$Site_ID, Huck_Laura_Berries_df$Distance, Huck_Laura_Berries_df$Year)
table(Huck_Laura_Berries_df$Site_ID2) #Every ID represented once
```

```{r}
head(Mackenzie_cutblock_plots_openings_df_soils)
Mackenzie_cutblock_plots_openings_df_soils$Site_ID<-paste(Mackenzie_cutblock_plots_openings_df_soils$Study_Area, Mackenzie_cutblock_plots_openings_df_soils$Drainage, Mackenzie_cutblock_plots_openings_df_soils$LONGITUDE)
table(Mackenzie_cutblock_plots_openings_df_soils$Site_ID) #Some duplicated for SIte_ID, but most not

head(cutblock_plots_openings_mowatBuff_df)
cutblock_plots_openings_mowatBuff_df$Site_ID<-paste(cutblock_plots_openings_mowatBuff_df$Study_Area, cutblock_plots_openings_mowatBuff_df$Drainage, cutblock_plots_openings_mowatBuff_df$LONGITUDE)
table(cutblock_plots_openings_mowatBuff_df$Site_ID) #Occasional duplicates, but mostly not

```

