---
title: "Scripts for creating spatial inputs for Castor"
author: "Elizabeth Kleynhans"
date: "20/04/2026"
output: html_document
---

# About this document

This document provides example scripts for constructing the core spatial layers required to initialize and run a Castor model. Scripts are intended as illustrative templates and may be adapted to local study areas, datasets, or resolutions.


```{r setup, include=FALSE}
# Global setup for Castor preprocessing scripts
# - Loads common spatial and data wrangling libraries
# - Defines the standard provincial grid used throughout the model
# - Ensures all rasters are aligned (CRS, extent, resolution)

knitr::opts_chunk$set(echo = TRUE)

#Get some important castor specific functions
source(here::here("functions/R_Postgres.R"))

library(data.table)
library(sf)
library(tidyverse)
library(raster)
library(fasterize)
library(bcdata)
library(bcmaps)
library(terra)

# Create the standard Castor provincial raster grid
# All spatial layers used by Castor must align with this grid
prov.rast <- raster(
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = c(100, 100),
  vals = 0
)
```


# Vegetation Resource Inventory (VRI)

The [VRI](https://catalogue.data.gov.bc.ca/dataset/vri-2024-forest-vegetation-composite-rank-1-layer-r1-) provides the initial forest state for Castor, including species composition, age, height, and basal area. For most castor applications, the **Forest Vegetation Composite Rank 1 layer** is sufficient, as it provides a single
best‑available representation of stand attributes per polygon.

Users may substitute alternative forest inventory data if:
 - the data has the following attributes: age, height, crown closure, quadratic mean diameter 125, BC Land-cover Classification System Level 1, 2 and 4, and site index
- polygons can be rasterized to the Castor grid.

```{r, inventory data}
# download and open the VRI data
vri_all <- st_read("C:\\Users\\ekleynha\\Downloads\\VEG_COMP_LYR_R1_POLY_2024\\VEG_COMP_LYR_R1_POLY_2024.gdb")

# The VRI is huge so unless you are planning on running your analysis in multiple area I would recommend clipping the full VRI layer to your area of interest and then only upload that to postgres.

# first clip the vri to the bounding box of the tsa. 
vri_tsa_bbox <- st_crop(vri_all, st_bbox(tsa))
rm(vri_all)

# Next select only the features we are interested in.
vri_tsa<- vri_tsa_bbox %>% 
  dplyr::select(FEATURE_ID, OPENING_ID, OPENING_NUMBER, FEATURE_CLASS_SKEY, BCLCS_LEVEL_1, BCLCS_LEVEL_4, BCLCS_LEVEL_5, BEC_ZONE_CODE, BASAL_AREA, SPECIES_CD_1, SPECIES_PCT_1, SPECIES_CD_2, SPECIES_PCT_2, SPECIES_CD_3, SPECIES_PCT_3, SPECIES_CD_4, SPECIES_PCT_4, SPECIES_CD_5, SPECIES_PCT_5, SPECIES_CD_6, SPECIES_PCT_6, PROJ_AGE_1, PROJ_HEIGHT_1) %>%
  dplyr::rename_with(tolower)

con <- dbConnect(RPostgres::Postgres(),host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), port='5432' ,user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), password = keyring::key_get ('dbpass', keyring = 'postgreSQL')) 

st_write(st_as_sf(vri_tsa, crs=3005), con, Id(schema = "test", table = "vri_2024_test"))
dbDisconnect(con)

# Rasterize 
ras.vri <- fasterize::fasterize (st_cast (vri_tsa, "MULTIPOLYGON"), prov.rast, field = "feature_id")
writeRaster (ras.vri, ("C:\\Users\\ekleynha\\Downloads\\raster_vri_fid.tif"), overwrite = T)

# write data
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  C:\\Users\\ekleynha\\Downloads\\raster_vri_fid.tif -t 100x100 test.rast_vri_id_test | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

```
The resulting VRI raster contains a feature ID per pixel, which allows Castor to join pixel‑level state back
to polygon‑level forest attributes when initializing the database.


# Timber Harvesting Land Base (THLB)

The THLB layer defines which pixels are eligible for harvest activities in Castor. Pixels outside the THLB are excluded from harvest scheduling.

Any spatial representation of the THLB may be used, provided it:
- is binary (inside / outside THLB),
- aligns to the Castor grid,
- and is consistent with the planning context of the analysis.

A version of the provincial timber harvesting land base can be obtained from https://catalogue.data.gov.bc.ca/dataset/provincial-timber-harvesting-land-base-thlb-by-timber-supply-area-tsa-

```{r thlb}

thlb<-st_read("C:\\Users\\ekleynha\\Downloads\\tsa02\\tsa02_thlb.gdb")

# Rasterize THLB to match Castor grid

ras.thlb <- fasterize::fasterize (st_cast (thlb, "MULTIPOLYGON"), prov.rast, field = "thlb_fact")

terra::writeRaster (ras.thlb, file = "C:\\Users\\ekleynha\\Downloads\\raster_thlb.tif", overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 C:\\Users\\ekleynha\\Downloads\\raster_thlb.tif -t 100x100 test.rast_thlb | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

```

# Elevation

Elevation is used directly in Castor and indirectly to derive secondary variables such as slope.
Here we use the BC provincial CDED DEM and resample it to the Castor 100‑m grid.

Alternative DEM sources may be used if they are:
- projected to BC Albers,
- resampled to the Castor grid,
- and internally consistent with other spatial layers.

```{r elevation}

cded_vrt <- cded(
  aoi = tsa,
  ask = FALSE   # important for scripts / pipelines
)

dem <- rast(cded_vrt)
dem_bc <- project(dem, prov.rast)

dem_bc_r <- raster::raster(dem_bc)
dem_bc_100m <- raster::resample(
  dem_bc_r,
  prov.rast,
  method = "bilinear"
)

# check dem_bc_100m matches ras.thlb
dem_bc_100m
ras.thlb

## Upload data to db
writeRaster (dem_bc_100m, file = "C:\\Users\\ekleynha\\Downloads\\raster_elev.tif", format = "GTiff", overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 C:\\Users\\ekleynha\\Downloads\\raster_elev.tif -t 100x100 test.rast_elev | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

```

# Roads

Road layers influence access, disturbance patterns, and spatial cost effects in Castor.
Two road representations are supported:
- a simple binary access layer, and
- a distance‑weighted access layer that penalizes remoteness from mills.
Users should choose the option appropriate to their research question.

## Overview of road options

**Option 1 — Simple (binary) roads**
This option treats all roads as providing equal, unconstrained access. Roads indicate where access exists, but do not impose any access cost or remoteness penalty.

 - Equivalent to the logic used in the roads R package
 - Equivalent to the simple version of RoadsCastor
 - No mill locations required
 - Roads act as a binary access mask only

**Option 2 — Distance‑weighted roads (advanced)**
This option applies a penalty to non‑permanent roads that increases with distance from processing facilities (mills).

 - Aligns with historical Castor / RoadsCastor workflows
 - Captures remoteness and access gradients
 - Requires mill location data
 - More computationally expensive, but more realistic

### Get data
Get roads data. In this example Ill use the BC Cumulative Effects Framework - Integrated Roads - 2026 (https://catalogue.data.gov.bc.ca/dataset/bc-cumulative-effects-framework-integrated-roads-current/resource/4b2aa2a5-8cfd-4410-a0af-d7f257b4131c) but any data can be used. 

Roads are first classified into permanent and non‑permanent types and then buffered by 51 m prior to rasterization.
This buffering step ensures that linear road features adequately intersect the 100 m raster grid. Without buffering, narrow road lines may fall between raster cell centers and be omitted during rasterization, leading to incomplete road representation.

```{r roads}
library(sf)
library(raster)
library(fasterize)
library(data.table)
library(RANN)
library(dplyr)

# get roads data
roads <- st_read("C:\\Users\\ekleynha\\Downloads\\BC_CEF_Integrated_Roads_2026\\BC_CE_Integrated_Roads_2026.gdb") |> 
  st_transform(3005)

roads$road_class <- NA_integer_

# Permanent roads
roads$road_class[
  roads$DRA_ROAD_SURFACE == "paved" |
  (!is.na(roads$DRA_ROAD_NAME_FULL) & roads$DRA_ROAD_CLASS != "Trail")
] <- -2

# Non-permanent roads
roads$road_class[is.na(roads$road_class)] <- -1

# buffer roads
roads_buf <- st_buffer(roads, dist = 51)

prov.rast <- raster(
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = CRS("EPSG:3005"),
  resolution = 100
)

road_class_rast <- fasterize(
  st_cast(roads_buf, "MULTIPOLYGON"),
  prov.rast,
  field = "road_class"
)

road_class_rast[is.na(road_class_rast[])] <- 0
```

#### Option 1 — Simple (binary) roads
Description
This option assumes all roads provide equal access with zero penalty, regardless of road type or distance from mills. Roads are treated purely as an access mask.
This is the approach taken by the R package [Roads](https://landscitech.github.io/roads/)
```{r roads}
# Binary road access raster
# 0  = road present (accessible)
# NA = no road (inaccessible)


road_binary <- road_class_rast
road_binary[] <- NA                # start with everything NA
road_binary[road_class_rast < 0] <- 0


plot(road_binary, main = "Binary Roads (Simple Option)")

writeRaster (road_binary, "C:\\Users\\ekleynha\\Downloads\\road_binary.tif", overwrite = T)

system ("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', 'C:\\Users\\ekleynha\\Downloads\\road_binary.tif -t 100x100 test.rast_roads_binary | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)
```

#### Option 2 — Distance‑weighted roads (advanced)
Description
This option applies a remoteness penalty to non‑permanent roads based on distance to the nearest processing facility (mill).

Permanent roads have zero penalty
Non‑permanent roads incur a penalty proportional to distance

```{r}

# Get mill locations
mills <- bcdc_query_geodata("WHSE_IMAGERY_AND_BASE_MAPS.GSR_TMBR_PRCSSING_FAC_SV") %>%
  collect()

# remove duplicates
mills_unique <- mills %>% 
  dplyr::distinct(geometry, .keep_all = TRUE)

# Identify road cells
road_cells <- which(road_class_rast[] < 0)

# Cell coordinates
road_pts <- xyFromCell(road_class_rast, road_cells)

# Mill coordinates
mill_xy <- st_coordinates(mills_unique)

# Nearest‑neighbour distance (meters)
dist <- RANN::nn2(
  data  = mill_xy,
  query = road_pts,
  k = 1
)

road_dist <- road_class_rast
road_dist[road_cells] <- dist$nn.dists[, 1]
road_dist[road_dist == 0] <- NA

# apply road penalties
road_weight <- road_class_rast

# Reclassify to penalty weights
road_weight[road_weight == -2] <- 0   # permanent roads
road_weight[road_weight == -1] <- 1   # non‑permanent roads
road_weight[road_weight ==  0] <- NA  # no road

#
road_weighted <- road_weight * road_dist

plot(road_weighted, main = "Distance‑Weighted Roads (Advanced Option)")

writeRaster (road_weighted,"C:\\Users\\ekleynha\\Downloads\\road_weighted.tif", overwrite = T)

system ("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', 'C:\\Users\\ekleynha\\Downloads\\road_weighted.tif -t 100x100 test.rast_roads_weighted | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)
```

## Roads Cost surface


This section is descriptive rather than prescriptive. Users are responsible for supplying a road‑building cost surface appropriate to their analysis.

A road‑building cost surface is a raster layer that represents the relative cost of constructing a road through each cell of the landscape. This surface is used by graph‑based and least‑cost path algorithms (e.g., Castor, roads::projectRoads()) to simulate where new roads would most likely be built. Importantly, a road‑building cost surface represents construction difficulty, not road access, remoteness, or travel cost after roads exist.

### User responsibility
The creation of a road‑building cost surface is intentionally left to the user. Neither Castor, SELES‑STSM, nor the roads R package prescribe a single method for defining construction cost. Instead, users are expected to supply a cost surface that is appropriate for their modeling objectives, spatial scale, and available data.

**Users may:**
 - construct their own cost surface from input layers,
 - reuse an existing cost surface developed for a similar application,
 - or apply a simplified formulation suitable for exploratory or sensitivity analyses.

**Conceptual model**
In general form, a road‑building cost surface encodes a function such as:
road_build_cost = f(terrain, region, land cover, crossings, barriers)

Each raster cell is assigned a numeric value proportional to the marginal cost of road construction through that location. Cells that cannot support road construction (e.g., large lakes or coastal waterbodies) are treated as absolute barriers and excluded from the graph.

**Typical input data layers**
While specific implementations vary, road‑building cost surfaces commonly incorporate some subset of the following inputs.

1. Topography

Slope derived from a digital elevation model (DEM)
Often included as a linear or nonlinear term
Steeper slopes represent higher construction cost

2. Regional context

Regional boundaries such as Timber Supply Areas (TSAs)
Used to apply region‑specific intercepts or coefficients
Reflects variation in geology, climate, and engineering standards

3. Land cover or ecological modifiers

Biogeoclimatic zones (e.g., ESSF)
Used to represent systematic cost differences associated with soil conditions, precipitation, or ecosystem type

4. Linear feature crossings

Pipeline crossings
Watercourse crossings
Typically represented as per‑cell counts multiplied by unit crossing costs

5. Absolute barriers

Large lakes or coastal waterbodies
Treated as non‑buildable areas (NA values)


6. Appraisal‑based cost estimates (optional)

In some applications (e.g., Castor), road‑building cost surfaces have been informed by road development cost models documented in the BC Interior and Coast Appraisal Manuals: [Interior Appraisal Manual](https://www2.gov.bc.ca/gov/content/industry/forestry/competitive-forest-industry/timber-pricing/interior-timber-pricing/interior-appraisal-manual), [Coast Appraisal Manual](https://www2.gov.bc.ca/gov/content/industry/forestry/competitive-forest-industry/timber-pricing/coast-timber-pricing/coast-appraisal-manual).


# Growth and Yield

## Overview

In Castor, tree growth is not simulated directly. Instead, forest growth is modelled by supplying pre‑computed growth and yield curves that describe how stand attributes (e.g. volume, height, basal area, crown closure) change with stand age. During a simulation, Castor advances stand age through time and uses these input curves to update forest conditions.
Because Castor relies entirely on input growth and yield curves, growth and yield modelling has two required components:

Growth and yield modelling in Castor has two required components:
 - A description of forest growth based on the current landscape condition, and
 - A description of how growth changes after disturbance (i.e. harvesting).

At any point in time, the landscape is composed of two stand types:

**Natural stands:** stands that have not been harvested since inventory establishment. Growth for these stands is represented using [VDYP](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/variable-density-yield-projection-vdyp) curves.

**Managed stands:** stands that have been harvested and regenerated. Growth for these stands is represented using [TASS](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/tree-and-stand-simulator-tass) / [TIPSY](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/table-interpolation-program-for-stand-yields-tipsy) output.

Both natural and managed stands are represented in Castor as age‑based yield curves that include volume, height, basal area, crown closure, and related stand attributes.

When a natural stand is harvested, Castor resets stand age to zero and switches the stand from a VDYP yield curve to a TASS/TIPSY yield curve. This transition is implemented as a discrete change in yield curve ID at the time of harvest; VDYP and TIPSY curves are not blended or linked directly. Note, Castor does not implement an explicit regeneration delay. Following harvest, stand age begins increasing immediately, and growth is applied directly from the TIPSY/TASS yield curve as soon as the next simulation time step is evaluated. Any delay in post‑harvest growth must therefore either be implicit in the shape of the TASS/TIPSY yield curves themselves or the code in growingStockCastor needs be modified to include regeneration delay.

Overall, Castor therefore requires:
 - [VDYP](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/variable-density-yield-projection-vdyp) curves for natural (unharvested) stands
 - [TASS](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/tree-and-stand-simulator-tass) / [TIPSY](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/table-interpolation-program-for-stand-yields-tipsy) curves for managed (harvested) stands
 - A consistent mapping that allows stands to switch from VDYP to TIPSY/TASS at harvest

This script ingests raw [VDYP and TASS/TIPSY](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling) outputs obtained from modellers within FAIB and reformats it into the structures required by Castor, including both current and future yield curves, along with spatial rasters that identify which yield curve applies to each analysis unit at different points in time.


## Get_curves

**Purpose:**
   
Read growth and yield model outputs (managed and natural) and supporting reference tables needed to construct Castor yield curves


```{r}
# get the current tipsy table

data.dir <- "<path\\to\\files>"

tipsy <- read_csv(paste0(data.dir, "\\MSYT\\MSYT_current_output.csv"))

reference_tab <- read_csv(paste0(data.dir,"\\MSYT\\MSYT_reference.csv"))
input_tab<-read_csv(paste0(data.dir,"\\MSYT\\MSYT_current_input.csv"))

#get the natural stand yield table in wide format
vdyp_wide<-read_csv(paste0(data.dir,"\\NSYT\\tsa02_nsyt.csv")) 
```


Before proceeding, the analysis‑ready (AR) attribute table for the TSA may need to be loaded into Postgres.
This table is used to identify forest composition (e.g. deciduous vs conifer). These forest attributes may not have been fully encoded in the growth and yield model inputs. If they are missing from the growth and yield data then do this next step
```{r}
library(DBI)
library(RPostgres)

schema_name <- "test"
sql_file    <- "path/to/ar_table.sql"

con <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get ('dbhost', keyring = 'postgreSQL'),
  port     = 5432,
  dbname   = keyring::key_get ('dbname', keyring = 'postgreSQL'),
  user     = keyring::key_get ('dbuser', keyring = 'postgreSQL'),
  password = keyring::key_get("dbpass", keyring = "postgreSQL")
)

# 1. Set the search path for this connection
dbExecute(con, paste0(
  "SET search_path TO ",
  DBI::dbQuoteIdentifier(con, schema_name)
))

# 2. Read and execute the SQL file
sql_text <- readChar(sql_file, file.info(sql_file)$size)
dbExecute(con, sql_text)

dbDisconnect(con)

```


```{r}
## Identify feature_ids where TIPSY inputs indicate:
##  - no planted species (i.e., natural origin prior to harvest)
##  - a deciduous-leading natural species (here, Aspen = 'At')
##
## These are candidates where managed stand yields may include
## both conifer and deciduous volume components.
input_fids <- input_tab %>%
  filter(is.na(planted_species1) & natural_species1 == 'At')

nrow(input_fids)  # diagnostic: number of candidate deciduous-leading features

## Query the analysis-ready (AR) attribute table to independently
## identify deciduous-leading stands based on inventory species codes.
##
## Species codes beginning with 'A' or 'E' are treated as deciduous.
query <- "select feature_id, spec_cd_1 from test.tsa02_ar_table where spec_cd_1 like 'A%' or spec_cd_1 like 'E%';"

## Connect to Postgres database containing AR attributes
con <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get('dbhost', keyring = 'postgreSQL'),
  dbname   = keyring::key_get('dbname', keyring = 'postgreSQL'),
  port     = '5432',
  user     = keyring::key_get('dbuser', keyring = 'postgreSQL'),
  password = keyring::key_get('dbpass', keyring = 'postgreSQL')
)

## Retrieve distinct deciduous feature_ids from AR table
dec <- dbGetQuery(con, query) %>%
  distinct(feature_id)
## Reconcile the two sources of deciduous identification:
##  - input_fids: derived from TIPSY input tables
##  - dec: derived from AR inventory attributes
##
## This ensures consistent feature_id coverage for later joins.
input_fids_2  <- anti_join(input_fids, dec, join_by("feature_id"))
input_fids_dec <- left_join(dec, input_fids, join_by("feature_id"))

## Combine both sets into a single deciduous feature_id table
dec <- bind_rows(input_fids_dec, input_fids_2)

nrow(dec)  # diagnostic check
```

Conceptual note:
The above step step exists solely to decide whether managed stand volume should be calculated as MVcon or MVcon + MVdec.
It is not required by Castor itself, but supports species-aware volume accounting.

## Current Managed stand yield curves (current condition: TIPSY / TASS)

This section constructs current‑condition managed stand yield curves from TIPSY output for all stands that have been previously harvested and regenerated.
Managed stands are identified using the reference table, which links each feature to an opening_id. Only features with a valid opening_id are treated as managed; all other features are handled later as natural (VDYP) stands.
Because TIPSY outputs contain separate yield components for conifer and deciduous species, managed stands are split into two groups before curve construction:

Deciduous or mixedwood managed stands, where total stand volume is calculated as the sum of conifer (MVcon) and deciduous (MVdec) components.
Conifer‑only managed stands, where total stand volume is derived from the conifer component alone.

The classification of stands as deciduous/mixedwood versus conifer‑only is based on previously identified feature_ids (derived from inventory attributes and/or TIPSY inputs).
For each managed stand, age‑based yield curves are constructed for the following attributes:

Merchantable volume
Dominant height
Basal area
Crown closure

TIPSY outputs are available in 10‑year increments up to age 120. Because Castor requires yield values to cover the full simulation horizon, curves are extended to age 250 by holding the age‑120 values constant. This extension is a modelling convenience to prevent curve truncation; it does not imply continued biological growth beyond the TIPSY projection range.
Finally, the conifer‑only and deciduous/mixedwood managed curves are combined into a single table of managed stand yield curves and labelled as "managed". These curves represent the current yield trajectory for all managed stands prior to any additional disturbance and will later be merged with natural (VDYP) curves to describe the full landscape.


```{r}
# Select feature id with an opening id
openings <- reference_tab %>%
  filter(!is.na(opening_id)) %>%
  dplyr::select(feature_id, opening_id)

nrow(openings) 

tab.count <- tipsy %>%
              group_by (feature_id) %>%
               tally ()

check <- tab.count %>%
          dplyr::filter (n > 1)

# get stands that have both deciduous and coniferous species

op_id1 <- inner_join(openings, tipsy, join_by("feature_id")) # An inner_join() only keeps observations from x that have a matching key in y.
op_id_dec<- inner_join(op_id1, dec,join_by("feature_id"))

#managed stand curves go out to 120 years...need to fill out to 250
op_yield1 <- op_id_dec%>%
  mutate(vol0 = 0,
    vol10 = MVcon_10 + MVdec_10,
    vol20 = MVcon_20 + MVdec_20,
    vol30 = MVcon_30 + MVdec_30,
    vol40 = MVcon_40 + MVdec_40,
    vol50 = MVcon_50 + MVdec_50,
    vol60 = MVcon_60 + MVdec_60,
    vol70 = MVcon_70 + MVdec_70,
    vol80 = MVcon_80 + MVdec_80,
    vol90 = MVcon_90 + MVdec_90,
    vol100 = MVcon_100 + MVdec_100,
    vol110 = MVcon_110 + MVdec_110,
    vol120 = MVcon_120 + MVdec_120,
    vol130 = MVcon_120 + MVdec_120,# fill out to 250
    vol140 = MVcon_120 + MVdec_120,
    vol150 = MVcon_120 + MVdec_120,
    vol160 = MVcon_120 + MVdec_120,
    vol170 = MVcon_120 + MVdec_120,
    vol180 = MVcon_120 + MVdec_120,
    vol190 = MVcon_120 + MVdec_120,
    vol200 = MVcon_120 + MVdec_120,
    vol210 = MVcon_120 + MVdec_120,
    vol220 = MVcon_120 + MVdec_120,
    vol230 = MVcon_120 + MVdec_120,
    vol240 = MVcon_120 + MVdec_120,
    vol250 = MVcon_120 + MVdec_120,
    ht0 = 0,
    ht10 = HTdec_10,
    ht20 = HTdec_20,
    ht30 = HTdec_30,
    ht40 = HTdec_40,
    ht50 = HTdec_50,
    ht60 = HTdec_60,
    ht70 = HTdec_70,
    ht80 = HTdec_80,
    ht90 = HTdec_90,
    ht100 = HTdec_100,
    ht110 = HTdec_110,
    ht120 = HTdec_120,
    ht130 = HTdec_120,# fill out to 250
    ht140 = HTdec_120,
    ht150 = HTdec_120,
    ht160 = HTdec_120,
    ht170 = HTdec_120,
    ht180 = HTdec_120,
    ht190 = HTdec_120,
    ht200 = HTdec_120,
    ht210 = HTdec_120,
    ht220 = HTdec_120,
    ht230 = HTdec_120,
    ht240 = HTdec_120,
    ht250 = HTdec_120,
    ba0 = 0,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
  dplyr::select(feature_id,vol0:cc250)

View(op_yield1)

# Get only coniferous stands (not deciduous)
openings2_not_decid<-anti_join(op_id1, dec, join_by("feature_id"))

op_yield2 <- openings2_not_decid %>%
  mutate(
    vol0 = 0,
    vol10 = MVcon_10,
    vol20 = MVcon_20,
    vol30 = MVcon_30,
    vol40 = MVcon_40,
    vol50 = MVcon_50,
    vol60 = MVcon_60,
    vol70 = MVcon_70,
    vol80 = MVcon_80,
    vol90 = MVcon_90,
    vol100 = MVcon_100,
    vol110 = MVcon_110,
    vol120 = MVcon_120,
    vol130 = MVcon_120,# fill out to 250
    vol140 = MVcon_120,
    vol150 = MVcon_120,
    vol160 = MVcon_120,
    vol170 = MVcon_120,
    vol180 = MVcon_120,
    vol190 = MVcon_120,
    vol200 = MVcon_120,
    vol210 = MVcon_120,
    vol220 = MVcon_120,
    vol230 = MVcon_120,
    vol240 = MVcon_120,
    vol250 = MVcon_120,
    ht0 = 0,
    ht10 = HTcon_10,
    ht20 = HTcon_20,
    ht30 = HTcon_30,
    ht40 = HTcon_40,
    ht50 = HTcon_50,
    ht60 = HTcon_60,
    ht70 = HTcon_70,
    ht80 = HTcon_80,
    ht90 = HTcon_90,
    ht100 = HTcon_100,
    ht110 = HTcon_110,
    ht120 = HTcon_120,
    ht130 = HTcon_120,# fill out to 250
    ht140 = HTcon_120,
    ht150 = HTcon_120,
    ht160 = HTcon_120,
    ht170 = HTcon_120,
    ht180 = HTcon_120,
    ht190 = HTcon_120,
    ht200 = HTcon_120,
    ht210 = HTcon_120,
    ht220 = HTcon_120,
    ht230 = HTcon_120,
    ht240 = HTcon_120,
    ht250 = HTcon_120,
    ba0 = 0,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
  dplyr::select(feature_id,vol0:cc250
  )

View(op_yield2)
dim(op_yield2)

op_yield<-bind_rows(op_yield2,op_yield1)%>%
  arrange(feature_id)
op_yield$current_curve<-"managed"

```

Current yield curves: reshape and merge managed (TIPSY) curves

This section prepares managed stand yield curves for use in Castor by reshaping them from a wide, age‑in‑columns format into a long, age‑explicit format, and then assembling all yield attributes into a single table.
Castor expects yield information in long form, where each row represents a single stand (feature_id) at a single age, with associated yield attributes (volume, height, basal area, crown closure).

```{r}
# Select only volume columns (vol0–vol250) and reshape to long format
op_yield_long_vol<- op_yield %>% dplyr::select(feature_id: vol250)
op_yield_long_vol<-op_yield_long_vol %>% 
  pivot_longer(cols = starts_with("vol"), names_to = "age_temp", values_to = "vol") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"vol", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

#Repeat the wide → long conversion for other yield attributes

# Height
op_yield_long_ht<- op_yield %>% dplyr::select(feature_id,ht0: ht250)
op_yield_long_ht<-op_yield_long_ht %>% 
  pivot_longer(cols = starts_with("ht"), names_to = "age_temp", values_to = "ht") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ht", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# basal area
op_yield_long_ba<- op_yield %>% dplyr::select(feature_id,ba0: ba250)
op_yield_long_ba<-op_yield_long_ba %>% 
  pivot_longer(cols = starts_with("ba"), names_to = "age_temp", values_to = "ba") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ba", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# crown closure
op_yield_long_cc<- op_yield %>% dplyr::select(feature_id, cc0: cc250)
op_yield_long_cc<-op_yield_long_cc %>% 
  pivot_longer(cols = starts_with("cc"), names_to = "age_temp", values_to = "cc") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"cc", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

#Combine all managed stand yield attributes into a single long table
op_yield_long<-left_join(op_yield_long_vol, op_yield_long_ht, by=c("feature_id", "age"))
op_yield_long<-left_join(op_yield_long, op_yield_long_ba, by=c("feature_id", "age"))
op_yield_long<-left_join(op_yield_long, op_yield_long_cc, by=c("feature_id", "age"))
```

The resulting table has the structure:
feature_id | age | vol | ht | ba | cc

This is the canonical Castor yield table structure.

## Current Natural (VDYP) stands and merge with managed stands

This section completes the construction of current-condition yield curves for the entire landscape by adding natural stand (VDYP) curves and merging them with the managed stand (TIPSY) curves created earlier.
At the end of this section, there will be one unified table describing, for each feature_id and age: merchantable volume, dominant height, basal area, crown closure, and whether the curve represents a natural or planted stand.

```{r}
# Rename VDYP fields to match Castor naming conventions
vdyp_wide1<-vdyp_wide %>% 
  rename(feature_id=FEATURE_ID,
        age=PRJ_TOTAL_AGE)

vdyp_mat <- vdyp_wide1 %>%
  anti_join(
    op_yield_long %>% distinct(feature_id),
    by = "feature_id"
  )
 # remove VDYP curves in openings
vdyp_mat$current_curve<-"natural"

vdyp_mat<-vdyp_mat %>% dplyr::select(feature_id, age, PRJ_VOL_DWB, PRJ_DOM_HT, PRJ_BA, current_curve) %>%
  rename(vol=PRJ_VOL_DWB, 
         ht = PRJ_DOM_HT,
         ba = PRJ_BA)

#Add missing attributes for natural stands. If VDYP does not provide crown closure information add cc = 0 as a placeholder
vdyp_mat$cc<-0

op_yield_long$current_curve<-"planted"

vdyp_mat<-vdyp_mat %>% select(feature_id, age, vol, ht, ba, cc, current_curve)

#Combine natural and managed curves into a single current dataset
current <- bind_rows(vdyp_mat, op_yield_long) %>%# bring the two dataframs together
  arrange(feature_id) %>% #sort by feature_id in prep for au designation
  group_by(feature_id) %>% #group by feature_id
  arrange(feature_id, age) #%>% #sort by feature_id and age

# check you have both natural and planted curves
table(current$current_curve)

```

Writes the current-condition growth and yield curves to the Postgres database so they can be accessed by downstream Castor modules.
```{r}
if (dbExistsTable(con, SQL("test.tsa02_current_thin_all"))) {
  dbRemoveTable(con, SQL("test.tsa02_current_thin_all"))
}

dbWriteTable(con, SQL("test.tsa02_current_thin_all"), current, row.names = FALSE)


```

## Future Managed Stand yield curves (post‑harvest condition: TIPSY / TASS)

This section constructs future managed‑stand yield curves that represent post‑harvest growth trajectories in Castor. These curves are used when a stand transitions from a natural (VDYP) curve to a new managed state following harvest.
Unlike the current‑condition curves, which describe the landscape at the start of the simulation, the future curves describe how stands will grow after a harvest event. Note if the current state of the stand is on a managed stand yield curve the future state after harvest will not shift to a new curve rather it will just stay on the same managed stand yield curve but start again from age zero.

**Input data**
Future yield curves are derived from:

Future TIPSY output tables, generated using MSYT inputs that represent post‑harvest regeneration assumptions (species, site index, density, etc.). A future TIPSY input table, used to identify species composition (e.g., deciduous vs conifer).

```{r}
input_tab<-read_csv(paste0(data.dir, "BaseCase_nog\\tsa02\\R\\data\\MSYT\\MSYT_future_input.csv"))
tipsy_fut <- read_csv(paste0(data.dir, "BaseCase_nog\\tsa02\\R\\data\\MSYT\\MSYT_future_output.csv"))

dec<-input_tab%>%filter(planted_species1 == 'At'|
  (is.na(planted_species1) & natural_species1 == 'At'))
nrow(dec)

#get deciduous future curves
tipsy_fut1<-inner_join(tipsy_fut, dec,join_by("feature_id"))
fut_yield1 <- tipsy_fut1 %>%
  mutate(
    vol0 = 0,
    vol10 = MVcon_10 + MVdec_10,
    vol20 = MVcon_20 + MVdec_20,
    vol30 = MVcon_30 + MVdec_30,
    vol40 = MVcon_40 + MVdec_40,
    vol50 = MVcon_50 + MVdec_50,
    vol60 = MVcon_60 + MVdec_60,
    vol70 = MVcon_70 + MVdec_70,
    vol80 = MVcon_80 + MVdec_80,
    vol90 = MVcon_90 + MVdec_90,
    vol100 = MVcon_100 + MVdec_100,
    vol110 = MVcon_110 + MVdec_110,
    vol120 = MVcon_120 + MVdec_120,
    vol130 = MVcon_120 + MVdec_120,
    vol140 = MVcon_120 + MVdec_120,
    vol150 = MVcon_120 + MVdec_120,
    vol160 = MVcon_120 + MVdec_120,
    vol170 = MVcon_120 + MVdec_120,
    vol180 = MVcon_120 + MVdec_120,
    vol190 = MVcon_120 + MVdec_120,
    vol200 = MVcon_120 + MVdec_120,
    vol210 = MVcon_120 + MVdec_120,
    vol220 = MVcon_120 + MVdec_120,
    vol230 = MVcon_120 + MVdec_120,
    vol240 = MVcon_120 + MVdec_120,
    vol250 = MVcon_120 + MVdec_120,
    ht0 = 0,
    ht10 = HTdec_10,
    ht20 = HTdec_20,
    ht30 = HTdec_30,
    ht40 = HTdec_40,
    ht50 = HTdec_50,
    ht60 = HTdec_60,
    ht70 = HTdec_70,
    ht80 = HTdec_80,
    ht90 = HTdec_90,
    ht100 = HTdec_100,
    ht110 = HTdec_110,
    ht120 = HTdec_120,
    ht130 = HTdec_120,# fill out to 250
    ht140 = HTdec_120,
    ht150 = HTdec_120,
    ht160 = HTdec_120,
    ht170 = HTdec_120,
    ht180 = HTdec_120,
    ht190 = HTdec_120,
    ht200 = HTdec_120,
    ht210 = HTdec_120,
    ht220 = HTdec_120,
    ht230 = HTdec_120,
    ht240 = HTdec_120,
    ht250 = HTdec_120,
    ba0 = `Basal Area_0`,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
   dplyr::select(feature_id,vol0:cc250
  )
nrow(fut_yield1)# 932

tipsy_fut2<-anti_join(tipsy_fut, dec, join_by("feature_id"))
view(tipsy_fut2)

fut_yield2<- tipsy_fut2 %>%
  mutate(
    vol0 = 0,
    vol10 = MVcon_10,
    vol20 = MVcon_20,
    vol30 = MVcon_30,
    vol40 = MVcon_40,
    vol50 = MVcon_50,
    vol60 = MVcon_60,
    vol70 = MVcon_70,
    vol80 = MVcon_80,
    vol90 = MVcon_90,
    vol100 = MVcon_100,
    vol110 = MVcon_110,
    vol120 = MVcon_120,
    vol130 = MVcon_120,# fill out to 250
    vol140 = MVcon_120,
    vol150 = MVcon_120,
    vol160 = MVcon_120,
    vol170 = MVcon_120,
    vol180 = MVcon_120,
    vol190 = MVcon_120,
    vol200 = MVcon_120,
    vol210 = MVcon_120,
    vol220 = MVcon_120,
    vol230 = MVcon_120,
    vol240 = MVcon_120,
    vol250 = MVcon_120,
    ht0 = 0,
    ht10 = HTcon_10,
    ht20 = HTcon_20,
    ht30 = HTcon_30,
    ht40 = HTcon_40,
    ht50 = HTcon_50,
    ht60 = HTcon_60,
    ht70 = HTcon_70,
    ht80 = HTcon_80,
    ht90 = HTcon_90,
    ht100 = HTcon_100,
    ht110 = HTcon_110,
    ht120 = HTcon_120,
    ht130 = HTcon_120,# fill out to 250
    ht140 = HTcon_120,
    ht150 = HTcon_120,
    ht160 = HTcon_120,
    ht170 = HTcon_120,
    ht180 = HTcon_120,
    ht190 = HTcon_120,
    ht200 = HTcon_120,
    ht210 = HTcon_120,
    ht220 = HTcon_120,
    ht230 = HTcon_120,
    ht240 = HTcon_120,
    ht250 = HTcon_120,
    ba0 = 0,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
  dplyr::select(feature_id,vol0:cc250
  )

names(fut_yield2)
fut_yield<-bind_rows(fut_yield2,fut_yield1)%>%
  arrange(feature_id)



##################################################################################
#identify future MSYT feature_id for auinfo
future_fid<-fut_yield %>% dplyr::select(feature_id)%>%
  mutate(fut_fid = feature_id)
names(future_fid)
#################################################################################
```

Change future yield curves from wide to long format

```{r}
# change op_yield from wide to long
#Volume
fut_yield_long_vol<- fut_yield %>% dplyr::select(feature_id: vol250)
fut_yield_long_vol<-fut_yield_long_vol %>% 
  pivot_longer(cols = starts_with("vol"), names_to = "age_temp", values_to = "vol") %>% # pivot to a long format
    mutate(age_temp = str_replace(age_temp,"vol", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# height
fut_yield_long_ht<- fut_yield %>% dplyr::select(feature_id,ht0: ht250)
fut_yield_long_ht<-fut_yield_long_ht %>% 
  pivot_longer(cols = starts_with("ht"), names_to = "age_temp", values_to = "ht") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ht", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# basal area
fut_yield_long_ba<- fut_yield %>% dplyr::select(feature_id,ba0: ba250)
fut_yield_long_ba<-fut_yield_long_ba %>% 
  pivot_longer(cols = starts_with("ba"), names_to = "age_temp", values_to = "ba") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ba", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# crown closure
fut_yield_long_cc<- fut_yield %>% dplyr::select(feature_id, cc0: cc250)
fut_yield_long_cc<-fut_yield_long_cc %>% 
  pivot_longer(cols = starts_with("cc"), names_to = "age_temp", values_to = "cc") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"cc", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

fut_yield_long1<-left_join(fut_yield_long_vol, fut_yield_long_ht, by=c("feature_id", "age"))
fut_yield_long<-left_join(fut_yield_long1, fut_yield_long_ba, by=c("feature_id", "age"))
fut_yield_long<-left_join(fut_yield_long, fut_yield_long_cc, by=c("feature_id", "age"))
```

Get Natural stand yield curves (VDYP curves curves) for locations where there is no managed stand curve i.e. the feature_id has no managed stand yield curve associated with it.
```{r}
vdyp_mat <- anti_join(vdyp_wide1, fut_yield_long) # remove VDYP curves in openings
vdyp_mat$future_curve<-"natural" # label the future curves that will stay on the natural stand yield curve

vdyp_mat<-vdyp_mat %>% dplyr::select(feature_id, age, PRJ_VOL_DWB, PRJ_DOM_HT, PRJ_BA, future_curve) %>%
  rename(vol=PRJ_VOL_DWB, 
         ht = PRJ_DOM_HT,
         ba = PRJ_BA)
vdyp_mat$cc<-0

fut_yield_long$future_curve<-"planted" # label the curves that are planted

# join managed and natural stand yield curves together
future2 <- bind_rows(vdyp_mat, fut_yield_long) %>%# bring the two dataframs together
  arrange(feature_id) %>% #sort by feature_id in prep for au designation
  group_by(feature_id) %>% #group by feature_id
  arrange(feature_id, age) #sort by feature_id and age
```

Upload data to postgres
```{r}
tab.count <- future2 %>%
              group_by (feature_id) %>%
               tally () # all feature id's should have a tally of 26 for every year a growth and yield exists

if(dbExistsTable(con, SQL("test.tsa02_future_thin_all")))
{dbRemoveTable(con, SQL("test.tsa02_future_thin_all"))}
dbWriteTable(con, SQL("test.tsa02_future_thin_all"),future2,row.names=FALSE)

```

## Link yield curves to Analysis Units and prepare Castor inputs

This section takes the current and future growth‑and‑yield curves prepared earlier and performs the final integration steps required for use in Castor simulations. Specifically, it:

Links yield curves to Analysis Units (AUs), assigns yield curve IDs (YCIDs) for current and future conditions, creates spatial rasters that tell Castor which yield curve applies to each location, and writes all tabular and spatial inputs to Postgres in the formats expected by Castor.

At the end of this section, all growth and yield inputs are fully aligned with Castor’s data model.


```{r, G&Y data}
#Load and format Analysis Unit (AU) information
#This table defines the relationship between spatial Analysis Units and yield curves, and includes attributes such as:
#stand type classifications, current and future yield curve IDs, and metadata linking AUs to managed and natural yield trajectories. Note this table may have regeneration delay but Castor currently does not have the functionality to use this parameter. 

tab.au.info <- data.table(read.csv(paste0(data.dir,"\\csv\\auinfo_tsa02_stsm2024.txt"), header = T, sep = '\t'))

# feature_id serves as the common key, and column names are replaced to match Castor’s expected schema.
#This AU table provides the bridge between spatial units and yield curves.

tab.au.info <- tab.au.info [, c ("auid", "AUid", "RegenDelay", "MHA", "MHV", "StandType", "LeadSpp", "pPlantedAU1", "PlantedAU1", "UnmanagedAU")]
colnames (tab.au.info) <- c ("auid", "feature_id", "regen_delay", "mha", "mhv", "standtype", "leadspp", "perc_planted", "managed_ycid", "natural_ycid")
```


Merge yield curves with AU information
Current and future yield curves are merged with the AU table to create a single working dataset that contains, for each feature and age:
 -growth attributes (volume, height, basal area, crown closure),
 - deciduous percentage,
 -stand type, and
 - assigned current and future yield curve IDs.

A consistency check confirms that each feature_id has both a current and a future yield curve (52 rows total: 26 ages × 2 curve states).

Note: the tab.au.info table is organized so that the first half of the table represents the current yield information and the second half of the table represents the future yield information.

```{r, G&Y data}
tab.au.info<-data.table(tab.au.info)
tab.au.info<-tab.au.info[order(feature_id, auid)]
tab.au.info.cur<-tab.au.info[auid<(length(tab.au.info$auid)/2 +1), ]
tab.au.info.fut<-tab.au.info[auid>length(tab.au.info$auid)/2, ]

tab.dat<-data.table(current)
tab.dat.fut<-data.table(future2)
current_curves<-merge(tab.dat, tab.au.info.cur, by="feature_id")
future_curves<-merge(tab.dat.fut, tab.au.info.fut, by="feature_id")

current_curves<-current_curves %>% rename(curve = current_curve)
future_curves<-future_curves %>% rename(curve = future_curve)

curves<-rbind(current_curves, future_curves)
```

### Calculate deciduous percentage from the VRI

Castor can store a deciduous percentage (dec_pcnt) for each stand, which is used to support reporting and volume attribution, but does not influence growth dynamics or yield trajectories. If this information is not already included in the growth and yield tables, it can be derived from Vegetation Resources Inventory (VRI) species composition.
The approach shown below demonstrates one way to estimate deciduous percentage using standard VRI attributes:

Individual species components in the VRI are classified as conifer or deciduous based on species codes.
For each stand, the percentage cover of all conifer species (up to six species entries) is summed to compute total conifer cover.
Deciduous percentage is then calculated as:

dec_pcnt = 100 − conifer_pct_cover_total

The resulting dec_pcnt value is merged into the yield curve tables and carried through the Castor workflow. In growingStockCastor, this value is used only at the reporting stage to estimate deciduous volume as a proportion of total simulated stand volume (e.g., for compartment‑level summaries). Castor does not simulate conifer and deciduous growth separately, and dec_pcnt does not affect yield curve selection, stand transitions, or growth projections.
For attributes that are not actively modeled in this workflow (e.g., quadratic mean diameter (QMD) or equivalent clearcut area (ECA)), placeholder values are assigned to satisfy Castor’s schema requirements without affecting simulation behavior.

Important:
Deciduous percentage in Castor is a static attribution parameter, not a dynamic growth variable. It is used for accounting and reporting purposes only.

```{r, G&Y data}
library(DBI)
library(RPostgres)
library(sf)

con <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get("dbhost", keyring = "postgreSQL"),
  dbname   = keyring::key_get("dbname", keyring = "postgreSQL"),
  port     = 5432,
  user     = keyring::key_get("dbuser", keyring = "postgreSQL"),
  password = keyring::key_get("dbpass", keyring = "postgreSQL")
)

vri <- st_read(
  con,
  layer = Id(schema = "test", table = "vri_2024_test")
)

vri<- vri %>% select (feature_id, species_cd_1: species_pct_6)

conifer<-c("C","CW","Y","YC","F","FD","FDC","FDI","B","BB","BA","BG","BL","H","HM","HW","HXM","J","JR","JS","P","PJ","PF","PL","PR","PLI","PXJ","PY","PLC","PW","PA","S","SB","SE","SS","SW","SX","SXW","SXL","SXS","T","TW","X", "XC","XH", "ZC")

deciduous<-c("L", "LA", "LT", "LW", "D", "DR", "U", "UP", "A", "AC", "ACB", "ACT", "AX", "AT", "R", "RA", "E", "EA", "EXP", "EP", "EW", "K", "KC", "V", "VB", "VV", "VP", "G", "M", "MB", "MV", "Q", "QG", "W", "WB", "WP", "WA", "WD", "WS", "WT", "XH", "ZH")

vri<- vri %>%
  mutate(pct1 = ifelse(species_cd_1 %in% conifer, species_pct_1, NA),
         pct2 = ifelse(species_cd_2 %in% conifer, species_pct_2, NA),
         pct3 = ifelse(species_cd_3 %in% conifer, species_pct_3, NA),
         pct4 = ifelse(species_cd_4 %in% conifer, species_pct_4, NA),
         pct5 = ifelse(species_cd_5 %in% conifer, species_pct_5, NA),
         pct6 = ifelse(specoes_cd_6 %in% conifer, species_pct_6, NA),
         dominant_conifer = ifelse(species_cd_1 %in% conifer, species_cd_1, 
                                   ifelse(species_cd_2 %in% conifer, species_cd_2,
                                          ifelse(species_cd_3 %in% conifer, species_cd_3,
                                                 ifelse(species_cd_4 %in% conifer, species_cd_4,
                                                        ifelse(species_cd_5 %in% conifer, species_cd_5,
                                                               ifelse(species_cd_6 %in% conifer, species_cd_6, NA)))))))

table(vri$dominant_conifer)

vri<-vri %>% mutate(conifer_pct_cover_total=rowSums(across(c(pct1:pct6)), na.rm=TRUE))

vri_con<-vri[,c("feature_id", "conifer_pct_cover_total")]

curves<-merge(curves, vri_con, by="feature_id")

curves [, dec_pcnt := 100 - conifer_pct_cover_total]
#remove the column conifer_pct_cover_total
curves[, conifer_pct_cover_total:=NULL]
curves [, qmd := 0] # if you have no quad mean diameter values include it as 0 for a place holder
curves [, eca := 0] # similarly if you have no expected clearcut area values include it as a zero
```

### Assign current and future yield curve IDs (YCIDs)

Yield curve IDs are assigned based on stand type:
Natural stands reference the natural (VDYP‑based) YCID,
Managed stands reference the managed (TIPSY‑based) YCID,
All stands are assigned a future managed YCID, which will be used after harvest.

Negative YCIDs are used to distinguish natural yield curves from managed ones, following Castor convention.
This step defines the rule‑based transition from current to future yield curves that Castor applies during simulation.
```{r}

library(data.table)
library(dplyr)
library(terra)
library(DBI)
library(RPostgres)

## ---------------------------------------------------------------------
## 1. Define YCID boundary (natural vs managed)
## ---------------------------------------------------------------------
## Convention: lower half = natural, upper half = managed
ycid_split <- max(tab.au.info$auid) / 2


## ---------------------------------------------------------------------
## 2. Assign current and future YCIDs by stand type
## ---------------------------------------------------------------------
## Current condition:
##   - oldCurve / thriftyCurve → natural (VDYP)
##   - managedCurve           → managed (TIPSY)

curves[
  standtype %in% c("oldCurve", "thriftyCurve"),
  ycid_current := natural_ycid
]

curves[
  standtype == "managedCurve",
  ycid_current := managed_ycid
]

## Future condition:
##   - After harvest, all stands use managed (TIPSY) curves
curves[, ycid_future := managed_ycid]


## ---------------------------------------------------------------------
## 3. Build AU-level transition table (one row per AU)
## ---------------------------------------------------------------------
tab.transition <- unique(
  curves[
    auid <= ycid_split,
    .(feature_id, auid, ycid_current, ycid_future)
  ]
)

## Negative YCIDs indicate natural yield curves (Castor convention)
tab.transition[
  ycid_current <= ycid_split,
  ycid_current := -ycid_current
]


## ---------------------------------------------------------------------
## 4. Create spatial YCID rasters (current and future)
## ---------------------------------------------------------------------
## Load AU raster once
rast.auid <- terra::rast(paste0(data.dir,
  "/tiff/tsa02_au.tif"))

## Current YCID raster
rast.current.ycid <- terra::subst(
  rast.auid,
  tab.transition$auid,
  tab.transition$ycid_current
)

## Future YCID raster
rast.future.ycid <- terra::subst(
  rast.auid,
  tab.transition$auid,
  tab.transition$ycid_future
)


## ---------------------------------------------------------------------
## 5. Write YCID rasters to disk and Postgres
## ---------------------------------------------------------------------
writeRaster(
  extend(rast.current.ycid, ras.aoi),
  paste0(data.dir, "rast_ycid_current.tif"),
  overwrite = TRUE
)

system(
  paste0(
    'raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ',
    data.dir, 'rast_ycid_current.tif -t 100x100 test.rast_ycid_current | ',
    'psql postgres://',
    keyring::key_get("dbuser",  keyring = "postgreSQL"), ':',
    keyring::key_get("dbpass",  keyring = "postgreSQL"), '@',
    keyring::key_get("dbhost",  keyring = "postgreSQL"), ':5432/clus'
  )
)

writeRaster(
  extend(rast.future.ycid, ras.aoi),
  paste0(data.dir, "rast_ycid_future.tif"),
  overwrite = TRUE
)

system(
  paste0(
    'raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ',
    data.dir, 'rast_ycid_future.tif -t 100x100 test.rast_ycid_future | ',
    'psql postgres://',
    keyring::key_get("dbuser",  keyring = "postgreSQL"), ':',
    keyring::key_get("dbpass",  keyring = "postgreSQL"), '@',
    keyring::key_get("dbhost",  keyring = "postgreSQL"), ':5432/clus'
  )
)


## ---------------------------------------------------------------------
## 6. Build Castor-ready CURRENT yield table
## ---------------------------------------------------------------------
tab.current <- curves[
  ycid_current <= ycid_split,
  .(ycid_current, feature_id, age, vol, dec_pcnt, ht, qmd, ba, cc, eca)
]

setnames(
  tab.current,
  old = c("ycid_current", "vol", "ht", "ba", "cc"),
  new = c("ycid",         "tvol", "height", "basalarea", "crownclosure")
)

tab.current[, ycid := as.integer(ycid)]
tab.current <- unique(tab.current)


## ---------------------------------------------------------------------
## 7. Build Castor-ready FUTURE yield table
## ---------------------------------------------------------------------
tab.future <- curves[
  ycid_future > ycid_split,
  .(ycid_future, feature_id, age, vol, dec_pcnt, ht, qmd, ba, cc, eca)
]

setnames(
  tab.future,
  old = c("ycid_future", "vol", "ht", "ba", "cc"),
  new = c("ycid",        "tvol", "height", "basalarea", "crownclosure")
)

tab.future[, ycid := as.integer(ycid)]
tab.future <- unique(tab.future)


## ---------------------------------------------------------------------
## 8. Write yield tables to Postgres
## ---------------------------------------------------------------------
conn <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get("dbhost", keyring = "postgreSQL"),
  dbname   = keyring::key_get("dbname", keyring = "postgreSQL"),
  port     = 5432,
  user     = keyring::key_get("dbuser", keyring = "postgreSQL"),
  password = keyring::key_get("dbpass", keyring = "postgreSQL")
)

dbWriteTable(
  conn,
  Id(schema = "test", table = "yields_current"),
  tab.current,
  overwrite = TRUE
)

dbWriteTable(
  conn,
  Id(schema = "test", table = "yields_future"),
  tab.future,
  overwrite = TRUE
)

dbDisconnect(conn)
```

