<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->


---
title: "Example growth and yield data import"
author: "Elizabeth Kleynhans"
date: "2026-05-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Growth and Yield

## Overview

In Castor, tree growth is not simulated directly. Instead, forest growth is modelled by supplying pre‑computed growth and yield curves that describe how stand attributes (e.g. volume, height, basal area, crown closure) change with stand age. During a simulation, Castor advances stand age through time and uses these input curves to update forest conditions.
Growth and yield modelling has two required components:

 - A description of forest growth based on the current landscape condition, and
 - A description of how growth changes after disturbance (i.e. harvesting).

At any point in time, the landscape is composed of two stand types:

**Natural stands:** stands that have not been harvested since inventory establishment. Growth for these stands is represented using [VDYP](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/variable-density-yield-projection-vdyp) curves.

**Managed stands:** stands that have been harvested and regenerated. Growth for these stands is represented using [TASS](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/tree-and-stand-simulator-tass) / [TIPSY](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/table-interpolation-program-for-stand-yields-tipsy) output.

Both natural and managed stands are represented in Castor as age‑based yield curves that include volume, height, basal area, crown closure, and related stand attributes.

At the start of a simulation, each analysis unit (pixel) is assigned a current yield curve which could either be natural (VDYP) or managed (TASS/TIPSY) depending on its harvest history.  
When a stand is harvested in Castor:
- all pixels within that stand have their ages resets to zero, and
- the yield curve switches to the future yield curve. For natural stands this means that its yield curve updates from a natural stand yield curve to a managed stand yield curve i.e. VDYP curve -> TASS/TIPSY curve. This transition is implemented as a discrete change in yield curve ID at the time of harvest. However, if the pixel was already on a managed stand yield curve because it had previously been harvested and replanted then its future yield curve will be the same as before i.e. it stays on the same yield curve (TASS/TIPSY curve -> same TASS/TIPSY curve). Yield curves therefore encode all growth and regeneration assumptions used by the model.

Note, Castor does not implement an explicit regeneration delay. Following harvest, stand age begins increasing immediately, and growth is applied directly from the TIPSY/TASS yield curve as soon as the next simulation time step is evaluated. Any delay in post‑harvest growth must therefore either be implicit in the shape of the TASS/TIPSY yield curves themselves or the code in growingStockCastor needs be modified to include regeneration delay.

In summary, Castor requires:
 - [VDYP](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/variable-density-yield-projection-vdyp) curves for natural (unharvested) stands
 - [TASS](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/tree-and-stand-simulator-tass) / [TIPSY](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling/table-interpolation-program-for-stand-yields-tipsy) curves for managed (harvested) stands
 - A consistent mapping that allows stands to switch from VDYP to TIPSY/TASS at harvest

This script ingests raw VDYP and TASS/TIPSY outputs obtained from modellers within FAIB (https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory/growth-and-yield-modelling) and reformats it into the structures required by Castor, including both current and future yield curves, along with spatial rasters that identify which yield curve applies to each pixel at different points in time.


## Get_curves

**Purpose:**
   
Read growth and yield model outputs (managed and natural) and supporting reference tables needed to construct Castor yield curves


```{r}
# load path to where files are stored
data.dir <- "<path\\to\\files>"

# get the current tipsy table
tipsy <- read_csv(paste0(data.dir, "\\MSYT\\MSYT_current_output.csv"))

reference_tab <- read_csv(paste0(data.dir,"\\MSYT\\MSYT_reference.csv"))
input_tab<-read_csv(paste0(data.dir,"\\MSYT\\MSYT_current_input.csv"))

#get the natural stand yield table in wide format
vdyp_wide<-read_csv(paste0(data.dir,"\\NSYT\\tsa02_nsyt.csv")) #in this case we use the growth and yield data obtained for the boundary TSA (TSA 02) as an example
```


Before proceeding, the analysis‑ready (AR) attribute table for the TSA may need to be loaded into Postgres.
This table is used to identify forest composition (e.g. deciduous vs conifer). These forest attributes may not have been fully encoded in the growth and yield model inputs. If they are missing from the growth and yield data then do this next step
```{r}
library(DBI)
library(RPostgres)

sql_file    <- "path/to/ar_table.sql"

con <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get ('dbhost', keyring = 'postgreSQL'),
  port     = 5432,
  dbname   = keyring::key_get ('dbname', keyring = 'postgreSQL'),
  user     = keyring::key_get ('dbuser', keyring = 'postgreSQL'),
  password = keyring::key_get("dbpass", keyring = "postgreSQL")
)

# 1. Set the search path for this connection
dbExecute(con, paste0(
  "SET search_path TO ",
  DBI::dbQuoteIdentifier(con, database.schema)
))

# 2. Read and execute the SQL file
sql_text <- readChar(sql_file, file.info(sql_file)$size)
dbExecute(con, sql_text)

dbDisconnect(con)

```


```{r}
## Identify feature_ids where TIPSY inputs indicate:
##  - no planted species (i.e., natural origin prior to harvest)
##  - a deciduous-leading natural species (here, Aspen = 'At')
##
## These are candidates where managed stand yields may include
## both conifer and deciduous volume components.
input_fids <- input_tab %>%
  filter(is.na(planted_species1) & natural_species1 == 'At')

nrow(input_fids)  # diagnostic: number of candidate deciduous-leading features

## Query the analysis-ready (AR) attribute table to independently
## identify deciduous-leading stands based on inventory species codes.
##
## Species codes beginning with 'A' or 'E' are treated as deciduous.
query <- "select feature_id, spec_cd_1 from test.tsa02_ar_table where spec_cd_1 like 'A%' or spec_cd_1 like 'E%';"

## Connect to Postgres database containing AR attributes
con <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get('dbhost', keyring = 'postgreSQL'),
  dbname   = keyring::key_get('dbname', keyring = 'postgreSQL'),
  port     = '5432',
  user     = keyring::key_get('dbuser', keyring = 'postgreSQL'),
  password = keyring::key_get('dbpass', keyring = 'postgreSQL')
)

## Retrieve distinct deciduous feature_ids from AR table
dec <- dbGetQuery(con, query) %>%
  distinct(feature_id)
## Reconcile the two sources of deciduous identification:
##  - input_fids: derived from TIPSY input tables
##  - dec: derived from AR inventory attributes
##
## This ensures consistent feature_id coverage for later joins.
input_fids_2  <- anti_join(input_fids, dec, join_by("feature_id"))
input_fids_dec <- left_join(dec, input_fids, join_by("feature_id"))

## Combine both sets into a single deciduous feature_id table
dec <- bind_rows(input_fids_dec, input_fids_2)

nrow(dec)  # diagnostic check
```

Conceptual note:
The above step  exists solely to decide whether managed stand volume should be calculated as MVcon or MVcon + MVdec.

## Current Managed stand yield curves (current condition: TIPSY / TASS)

This section constructs current‑condition managed stand yield curves from TIPSY output for all stands that have been previously harvested and regenerated.
Managed stands are identified using the reference table, which links each feature to an opening_id. Only features with a valid opening_id are treated as managed; all other features are handled later as natural (VDYP) stands.
Because TIPSY outputs contain separate yield components for conifer and deciduous species, managed stands are split into two groups before curve construction:

For deciduous or mixedwood managed stands, total stand volume is calculated as the sum of conifer (MVcon) and deciduous (MVdec) components.
For conifer‑only managed stands, total stand volume is derived from the conifer component alone (MVcon).

The classification of stands as deciduous/mixedwood versus conifer‑only is based on previously identified feature_ids (derived from inventory attributes and/or TIPSY inputs).
For each managed stand, age‑based yield curves are constructed for the following attributes:

Merchantable volume
Dominant height
Basal area
Crown closure

TIPSY outputs are available in 10‑year increments up to age 120. Because Castor requires yield values to cover the full simulation horizon and TSR simulations often run for 250 years, curves are extended to age 250 by holding the age‑120 values constant. This extension is a modelling convenience to prevent curve truncation; it does not imply continued biological growth beyond the TIPSY projection range.

Finally, the conifer‑only and deciduous/mixedwood managed curves are combined into a single table of managed stand yield curves and labelled as "managed". These curves represent the current yield trajectory for all managed stands prior to any additional disturbance and will later be merged with natural (VDYP) curves to describe the full landscape.


```{r}
# Select feature id with an opening id
openings <- reference_tab %>%
  filter(!is.na(opening_id)) %>%
  dplyr::select(feature_id, opening_id)

nrow(openings) 

tab.count <- tipsy %>%
              group_by (feature_id) %>%
               tally ()

check <- tab.count %>%
          dplyr::filter (n > 1)

# get stands that have both deciduous and coniferous species

op_id1 <- inner_join(openings, tipsy, join_by("feature_id")) # An inner_join() only keeps observations from x that have a matching key in y.
op_id_dec<- inner_join(op_id1, dec,join_by("feature_id"))

#managed stand curves go out to 120 years...need to fill out to 250
op_yield1 <- op_id_dec%>%
  mutate(vol0 = 0,
    vol10 = MVcon_10 + MVdec_10,
    vol20 = MVcon_20 + MVdec_20,
    vol30 = MVcon_30 + MVdec_30,
    vol40 = MVcon_40 + MVdec_40,
    vol50 = MVcon_50 + MVdec_50,
    vol60 = MVcon_60 + MVdec_60,
    vol70 = MVcon_70 + MVdec_70,
    vol80 = MVcon_80 + MVdec_80,
    vol90 = MVcon_90 + MVdec_90,
    vol100 = MVcon_100 + MVdec_100,
    vol110 = MVcon_110 + MVdec_110,
    vol120 = MVcon_120 + MVdec_120,
    vol130 = MVcon_120 + MVdec_120,# fill out to 250
    vol140 = MVcon_120 + MVdec_120,
    vol150 = MVcon_120 + MVdec_120,
    vol160 = MVcon_120 + MVdec_120,
    vol170 = MVcon_120 + MVdec_120,
    vol180 = MVcon_120 + MVdec_120,
    vol190 = MVcon_120 + MVdec_120,
    vol200 = MVcon_120 + MVdec_120,
    vol210 = MVcon_120 + MVdec_120,
    vol220 = MVcon_120 + MVdec_120,
    vol230 = MVcon_120 + MVdec_120,
    vol240 = MVcon_120 + MVdec_120,
    vol250 = MVcon_120 + MVdec_120,
    ht0 = 0,
    ht10 = HTdec_10,
    ht20 = HTdec_20,
    ht30 = HTdec_30,
    ht40 = HTdec_40,
    ht50 = HTdec_50,
    ht60 = HTdec_60,
    ht70 = HTdec_70,
    ht80 = HTdec_80,
    ht90 = HTdec_90,
    ht100 = HTdec_100,
    ht110 = HTdec_110,
    ht120 = HTdec_120,
    ht130 = HTdec_120,# fill out to 250
    ht140 = HTdec_120,
    ht150 = HTdec_120,
    ht160 = HTdec_120,
    ht170 = HTdec_120,
    ht180 = HTdec_120,
    ht190 = HTdec_120,
    ht200 = HTdec_120,
    ht210 = HTdec_120,
    ht220 = HTdec_120,
    ht230 = HTdec_120,
    ht240 = HTdec_120,
    ht250 = HTdec_120,
    ba0 = 0,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
  dplyr::select(feature_id,vol0:cc250)

View(op_yield1)

# Get only coniferous stands (not deciduous)
openings2_not_decid<-anti_join(op_id1, dec, join_by("feature_id")) # anti_join keeps rows from one table (op_id1) that do not have a matching key in another (dec) i.e. removes deciduous stands and keeps only coniferous ones 

op_yield2 <- openings2_not_decid %>%
  mutate(
    vol0 = 0,
    vol10 = MVcon_10,
    vol20 = MVcon_20,
    vol30 = MVcon_30,
    vol40 = MVcon_40,
    vol50 = MVcon_50,
    vol60 = MVcon_60,
    vol70 = MVcon_70,
    vol80 = MVcon_80,
    vol90 = MVcon_90,
    vol100 = MVcon_100,
    vol110 = MVcon_110,
    vol120 = MVcon_120,
    vol130 = MVcon_120,# fill out to 250
    vol140 = MVcon_120,
    vol150 = MVcon_120,
    vol160 = MVcon_120,
    vol170 = MVcon_120,
    vol180 = MVcon_120,
    vol190 = MVcon_120,
    vol200 = MVcon_120,
    vol210 = MVcon_120,
    vol220 = MVcon_120,
    vol230 = MVcon_120,
    vol240 = MVcon_120,
    vol250 = MVcon_120,
    ht0 = 0,
    ht10 = HTcon_10,
    ht20 = HTcon_20,
    ht30 = HTcon_30,
    ht40 = HTcon_40,
    ht50 = HTcon_50,
    ht60 = HTcon_60,
    ht70 = HTcon_70,
    ht80 = HTcon_80,
    ht90 = HTcon_90,
    ht100 = HTcon_100,
    ht110 = HTcon_110,
    ht120 = HTcon_120,
    ht130 = HTcon_120,# fill out to 250
    ht140 = HTcon_120,
    ht150 = HTcon_120,
    ht160 = HTcon_120,
    ht170 = HTcon_120,
    ht180 = HTcon_120,
    ht190 = HTcon_120,
    ht200 = HTcon_120,
    ht210 = HTcon_120,
    ht220 = HTcon_120,
    ht230 = HTcon_120,
    ht240 = HTcon_120,
    ht250 = HTcon_120,
    ba0 = 0,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
  dplyr::select(feature_id,vol0:cc250
  )

View(op_yield2)
dim(op_yield2)

op_yield<-bind_rows(op_yield2,op_yield1)%>%
  arrange(feature_id)
op_yield$current_curve<-"managed"

```

Current yield curves: reshape and merge managed (TIPSY) curves

This section prepares managed stand yield curves for use in Castor by reshaping them from a wide, age‑in‑columns format into a long, age‑explicit format, and then assembling all yield attributes into a single table.
Castor expects yield information in long form, where each row represents a single stand (feature_id) at a single age, with associated yield attributes (volume, height, basal area, crown closure).

```{r}
# Select only volume columns (vol0–vol250) and reshape to long format
op_yield_long_vol<- op_yield %>% dplyr::select(feature_id: vol250)
op_yield_long_vol<-op_yield_long_vol %>% 
  pivot_longer(cols = starts_with("vol"), names_to = "age_temp", values_to = "vol") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"vol", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

#Repeat the wide → long conversion for other yield attributes

# Height
op_yield_long_ht<- op_yield %>% dplyr::select(feature_id,ht0: ht250)
op_yield_long_ht<-op_yield_long_ht %>% 
  pivot_longer(cols = starts_with("ht"), names_to = "age_temp", values_to = "ht") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ht", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# basal area
op_yield_long_ba<- op_yield %>% dplyr::select(feature_id,ba0: ba250)
op_yield_long_ba<-op_yield_long_ba %>% 
  pivot_longer(cols = starts_with("ba"), names_to = "age_temp", values_to = "ba") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ba", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# crown closure
op_yield_long_cc<- op_yield %>% dplyr::select(feature_id, cc0: cc250)
op_yield_long_cc<-op_yield_long_cc %>% 
  pivot_longer(cols = starts_with("cc"), names_to = "age_temp", values_to = "cc") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"cc", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

#Combine all managed stand yield attributes into a single long table
op_yield_long<-left_join(op_yield_long_vol, op_yield_long_ht, by=c("feature_id", "age"))
op_yield_long<-left_join(op_yield_long, op_yield_long_ba, by=c("feature_id", "age"))
op_yield_long<-left_join(op_yield_long, op_yield_long_cc, by=c("feature_id", "age"))
```

The resulting table has the structure:
feature_id | age | vol | ht | ba | cc

This is the canonical Castor yield table structure.

## Current Natural (VDYP) stands and merge with current managed stands (done above)

This section completes the construction of current-condition yield curves for the entire landscape by adding natural stand (VDYP) curves and merging them with the managed stand (TIPSY) curves created earlier.
At the end of this section, there will be one unified table describing, for each feature_id and age: merchantable volume, dominant height, basal area, crown closure, and whether the curve represents a natural or planted stand.

```{r}
# Rename VDYP fields to match Castor naming conventions
vdyp_wide1<-vdyp_wide %>% 
  rename(feature_id=FEATURE_ID,
        age=PRJ_TOTAL_AGE)

vdyp_mat <- vdyp_wide1 %>%
  anti_join(
    op_yield_long %>% distinct(feature_id),
    by = "feature_id"
  )
 # remove VDYP curves in openings
vdyp_mat$current_curve<-"natural"

vdyp_mat<-vdyp_mat %>% dplyr::select(feature_id, age, PRJ_VOL_DWB, PRJ_DOM_HT, PRJ_BA, current_curve) %>%
  rename(vol=PRJ_VOL_DWB, 
         ht = PRJ_DOM_HT,
         ba = PRJ_BA)

#Add missing attributes for natural stands. If VDYP does not provide crown closure information add cc = 0 as a placeholder
vdyp_mat$cc<-0

op_yield_long$current_curve<-"planted"

vdyp_mat<-vdyp_mat %>% select(feature_id, age, vol, ht, ba, cc, current_curve)

#Combine natural and managed curves into a single current dataset
current <- bind_rows(vdyp_mat, op_yield_long) %>%# bring the two dataframs together
  arrange(feature_id) %>% #sort by feature_id in prep for au designation
  group_by(feature_id) %>% #group by feature_id
  arrange(feature_id, age) #%>% #sort by feature_id and age

# check you have both natural and planted curves
table(current$current_curve)

```

Writes the current-condition growth and yield curves to the Postgres database so they can be accessed by downstream Castor modules.
```{r}
if (dbExistsTable(con, SQL("test.tsa02_current_thin_all"))) {
  dbRemoveTable(con, SQL("test.tsa02_current_thin_all"))
}

dbWriteTable(con, SQL("test.tsa02_current_thin_all"), current, row.names = FALSE)


```

## Future Managed Stand yield curves (post‑harvest condition: TIPSY / TASS)

This section constructs future managed‑stand yield curves that represent post‑harvest growth trajectories in Castor. These curves are used when a stand transitions from a natural (VDYP) curve to a new managed state following harvest.
Unlike the current‑condition curves, which describe the landscape at the start of the simulation, the future curves describe how stands will grow after a harvest event. Note if the current state of the stand is on a managed stand yield curve the future state after harvest will not shift to a new curve rather it will just stay on the same managed stand yield curve but start again from age zero.

**Input data**
Future yield curves are derived from:

Future TIPSY output tables, generated using MSYT inputs that represent post‑harvest regeneration assumptions (species, site index, density, etc.). A future TIPSY input table, used to identify species composition (e.g., deciduous vs conifer).

```{r}
input_tab<-read_csv(paste0(data.dir, "BaseCase_nog\\tsa02\\R\\data\\MSYT\\MSYT_future_input.csv"))
tipsy_fut <- read_csv(paste0(data.dir, "BaseCase_nog\\tsa02\\R\\data\\MSYT\\MSYT_future_output.csv"))

dec<-input_tab%>%filter(planted_species1 == 'At'|
  (is.na(planted_species1) & natural_species1 == 'At'))
nrow(dec)

#get deciduous future curves
tipsy_fut1<-inner_join(tipsy_fut, dec,join_by("feature_id"))
fut_yield1 <- tipsy_fut1 %>%
  mutate(
    vol0 = 0,
    vol10 = MVcon_10 + MVdec_10,
    vol20 = MVcon_20 + MVdec_20,
    vol30 = MVcon_30 + MVdec_30,
    vol40 = MVcon_40 + MVdec_40,
    vol50 = MVcon_50 + MVdec_50,
    vol60 = MVcon_60 + MVdec_60,
    vol70 = MVcon_70 + MVdec_70,
    vol80 = MVcon_80 + MVdec_80,
    vol90 = MVcon_90 + MVdec_90,
    vol100 = MVcon_100 + MVdec_100,
    vol110 = MVcon_110 + MVdec_110,
    vol120 = MVcon_120 + MVdec_120,
    vol130 = MVcon_120 + MVdec_120,
    vol140 = MVcon_120 + MVdec_120,
    vol150 = MVcon_120 + MVdec_120,
    vol160 = MVcon_120 + MVdec_120,
    vol170 = MVcon_120 + MVdec_120,
    vol180 = MVcon_120 + MVdec_120,
    vol190 = MVcon_120 + MVdec_120,
    vol200 = MVcon_120 + MVdec_120,
    vol210 = MVcon_120 + MVdec_120,
    vol220 = MVcon_120 + MVdec_120,
    vol230 = MVcon_120 + MVdec_120,
    vol240 = MVcon_120 + MVdec_120,
    vol250 = MVcon_120 + MVdec_120,
    ht0 = 0,
    ht10 = HTdec_10,
    ht20 = HTdec_20,
    ht30 = HTdec_30,
    ht40 = HTdec_40,
    ht50 = HTdec_50,
    ht60 = HTdec_60,
    ht70 = HTdec_70,
    ht80 = HTdec_80,
    ht90 = HTdec_90,
    ht100 = HTdec_100,
    ht110 = HTdec_110,
    ht120 = HTdec_120,
    ht130 = HTdec_120,# fill out to 250
    ht140 = HTdec_120,
    ht150 = HTdec_120,
    ht160 = HTdec_120,
    ht170 = HTdec_120,
    ht180 = HTdec_120,
    ht190 = HTdec_120,
    ht200 = HTdec_120,
    ht210 = HTdec_120,
    ht220 = HTdec_120,
    ht230 = HTdec_120,
    ht240 = HTdec_120,
    ht250 = HTdec_120,
    ba0 = `Basal Area_0`,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
   dplyr::select(feature_id,vol0:cc250
  )
nrow(fut_yield1)# 932

tipsy_fut2<-anti_join(tipsy_fut, dec, join_by("feature_id"))
view(tipsy_fut2)

fut_yield2<- tipsy_fut2 %>%
  mutate(
    vol0 = 0,
    vol10 = MVcon_10,
    vol20 = MVcon_20,
    vol30 = MVcon_30,
    vol40 = MVcon_40,
    vol50 = MVcon_50,
    vol60 = MVcon_60,
    vol70 = MVcon_70,
    vol80 = MVcon_80,
    vol90 = MVcon_90,
    vol100 = MVcon_100,
    vol110 = MVcon_110,
    vol120 = MVcon_120,
    vol130 = MVcon_120,# fill out to 250
    vol140 = MVcon_120,
    vol150 = MVcon_120,
    vol160 = MVcon_120,
    vol170 = MVcon_120,
    vol180 = MVcon_120,
    vol190 = MVcon_120,
    vol200 = MVcon_120,
    vol210 = MVcon_120,
    vol220 = MVcon_120,
    vol230 = MVcon_120,
    vol240 = MVcon_120,
    vol250 = MVcon_120,
    ht0 = 0,
    ht10 = HTcon_10,
    ht20 = HTcon_20,
    ht30 = HTcon_30,
    ht40 = HTcon_40,
    ht50 = HTcon_50,
    ht60 = HTcon_60,
    ht70 = HTcon_70,
    ht80 = HTcon_80,
    ht90 = HTcon_90,
    ht100 = HTcon_100,
    ht110 = HTcon_110,
    ht120 = HTcon_120,
    ht130 = HTcon_120,# fill out to 250
    ht140 = HTcon_120,
    ht150 = HTcon_120,
    ht160 = HTcon_120,
    ht170 = HTcon_120,
    ht180 = HTcon_120,
    ht190 = HTcon_120,
    ht200 = HTcon_120,
    ht210 = HTcon_120,
    ht220 = HTcon_120,
    ht230 = HTcon_120,
    ht240 = HTcon_120,
    ht250 = HTcon_120,
    ba0 = 0,
    ba10 = `Basal Area_10`,
    ba20 = `Basal Area_20`,
    ba30 = `Basal Area_30`,
    ba40 = `Basal Area_40`,
    ba50 = `Basal Area_50`,
    ba60 = `Basal Area_60`,
    ba70 = `Basal Area_70`,
    ba80 = `Basal Area_80`,
    ba90 = `Basal Area_90`,
    ba100 = `Basal Area_100`,
    ba110 = `Basal Area_110`,
    ba120 = `Basal Area_120`,
    ba130 = `Basal Area_120`,# fill out to 250
    ba140 = `Basal Area_120`,
    ba150 = `Basal Area_120`,
    ba160 = `Basal Area_120`,
    ba170 = `Basal Area_120`,
    ba180 = `Basal Area_120`,
    ba190 = `Basal Area_120`,
    ba200 = `Basal Area_120`,
    ba210 = `Basal Area_120`,
    ba220 = `Basal Area_120`,
    ba230 = `Basal Area_120`,
    ba240 = `Basal Area_120`,
    ba250 = `Basal Area_120`,
    cc0 = CC_0,
    cc10 = CC_10,
    cc20 = CC_20,
    cc30 = CC_30,
    cc40 = CC_40,
    cc50 = CC_50,
    cc60 = CC_60,
    cc70 = CC_70,
    cc80 = CC_80,
    cc90 = CC_90,
    cc100 = CC_100,
    cc110 = CC_110,
    cc120 = CC_120,
    cc130 = CC_120,
    cc140 = CC_120,
    cc150 = CC_120,
    cc160 = CC_120,
    cc170 = CC_120,
    cc180 = CC_120,
    cc190 = CC_120,
    cc200 = CC_120,
    cc210 = CC_120,
    cc220 = CC_120,
    cc230 = CC_120,
    cc240 = CC_120,
    cc250 = CC_120
  ) %>%
  dplyr::select(feature_id,vol0:cc250
  )

names(fut_yield2)
fut_yield<-bind_rows(fut_yield2,fut_yield1)%>%
  arrange(feature_id)



##################################################################################
#identify future MSYT feature_id for auinfo
future_fid<-fut_yield %>% dplyr::select(feature_id)%>%
  mutate(fut_fid = feature_id)
names(future_fid)
#################################################################################
```

Change future yield curves from wide to long format

```{r}
# change op_yield from wide to long
#Volume
fut_yield_long_vol<- fut_yield %>% dplyr::select(feature_id: vol250)
fut_yield_long_vol<-fut_yield_long_vol %>% 
  pivot_longer(cols = starts_with("vol"), names_to = "age_temp", values_to = "vol") %>% # pivot to a long format
    mutate(age_temp = str_replace(age_temp,"vol", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# height
fut_yield_long_ht<- fut_yield %>% dplyr::select(feature_id,ht0: ht250)
fut_yield_long_ht<-fut_yield_long_ht %>% 
  pivot_longer(cols = starts_with("ht"), names_to = "age_temp", values_to = "ht") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ht", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# basal area
fut_yield_long_ba<- fut_yield %>% dplyr::select(feature_id,ba0: ba250)
fut_yield_long_ba<-fut_yield_long_ba %>% 
  pivot_longer(cols = starts_with("ba"), names_to = "age_temp", values_to = "ba") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"ba", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

# crown closure
fut_yield_long_cc<- fut_yield %>% dplyr::select(feature_id, cc0: cc250)
fut_yield_long_cc<-fut_yield_long_cc %>% 
  pivot_longer(cols = starts_with("cc"), names_to = "age_temp", values_to = "cc") %>% # pivot to a long format
  mutate(age_temp = str_replace(age_temp,"cc", ""),
         age = as.numeric(age_temp)) %>% 
  dplyr::select(-age_temp)

fut_yield_long1<-left_join(fut_yield_long_vol, fut_yield_long_ht, by=c("feature_id", "age"))
fut_yield_long<-left_join(fut_yield_long1, fut_yield_long_ba, by=c("feature_id", "age"))
fut_yield_long<-left_join(fut_yield_long, fut_yield_long_cc, by=c("feature_id", "age"))
```

Get Natural stand yield curves (VDYP curves curves) for locations where there is no managed stand curve i.e. the feature_id has no managed stand yield curve associated with it.
```{r}
vdyp_mat <- anti_join(vdyp_wide1, fut_yield_long) # remove VDYP curves in openings
vdyp_mat$future_curve<-"natural" # label the future curves that will stay on the natural stand yield curve

vdyp_mat<-vdyp_mat %>% dplyr::select(feature_id, age, PRJ_VOL_DWB, PRJ_DOM_HT, PRJ_BA, future_curve) %>%
  rename(vol=PRJ_VOL_DWB, 
         ht = PRJ_DOM_HT,
         ba = PRJ_BA)
vdyp_mat$cc<-0

fut_yield_long$future_curve<-"planted" # label the curves that are planted

# join managed and natural stand yield curves together
future2 <- bind_rows(vdyp_mat, fut_yield_long) %>%# bring the two dataframs together
  arrange(feature_id) %>% #sort by feature_id in prep for au designation
  group_by(feature_id) %>% #group by feature_id
  arrange(feature_id, age) #sort by feature_id and age
```

Upload data to postgres
```{r}
tab.count <- future2 %>%
              group_by (feature_id) %>%
               tally () # all feature id's should have a tally of 26 for every year a growth and yield exists

if(dbExistsTable(con, SQL("test.tsa02_future_thin_all")))
{dbRemoveTable(con, SQL("test.tsa02_future_thin_all"))}
dbWriteTable(con, SQL("test.tsa02_future_thin_all"),future2,row.names=FALSE)

```

## Link yield curves to Analysis Units and prepare Castor inputs

This section takes the current and future growth‑and‑yield curves prepared earlier and performs the final integration steps required for use in Castor simulations. Specifically, it:

Links yield curves to Analysis Units (AUs), assigns yield curve IDs (YCIDs) for current and future conditions, creates spatial rasters that tell Castor which yield curve applies to each location, and writes all tabular and spatial inputs to Postgres in the formats expected by Castor.

At the end of this section, all growth and yield inputs are fully aligned with Castor’s data model.


```{r, G&Y data}
#Load and format Analysis Unit (AU) information
#This table defines the relationship between spatial Analysis Units and yield curves, and includes attributes such as:
#stand type classifications, current and future yield curve IDs, and metadata linking AUs to managed and natural yield trajectories. Note this table may have regeneration delay but Castor currently does not have the functionality to use this parameter. 

tab.au.info <- data.table(read.csv(paste0(data.dir,"\\csv\\auinfo_tsa02_stsm2024.txt"), header = T, sep = '\t'))

# feature_id serves as the common key, and column names are replaced to match Castor’s expected schema.
#This AU table provides the bridge between spatial units and yield curves.

tab.au.info <- tab.au.info [, c ("auid", "AUid", "RegenDelay", "MHA", "MHV", "StandType", "LeadSpp", "pPlantedAU1", "PlantedAU1", "UnmanagedAU")]
colnames (tab.au.info) <- c ("auid", "feature_id", "regen_delay", "mha", "mhv", "standtype", "leadspp", "perc_planted", "managed_ycid", "natural_ycid")
```


Merge yield curves with AU information
Current and future yield curves are merged with the AU table to create a single working dataset that contains, for each feature and age:
 -growth attributes (volume, height, basal area, crown closure),
 - deciduous percentage,
 -stand type, and
 - assigned current and future yield curve IDs.

A consistency check confirms that each feature_id has both a current and a future yield curve (52 rows total: 26 ages × 2 curve states).

Note: the tab.au.info table is organized so that the first half of the table represents the current yield information and the second half of the table represents the future yield information.

```{r, G&Y data}
tab.au.info<-data.table(tab.au.info)
tab.au.info<-tab.au.info[order(feature_id, auid)]
tab.au.info.cur<-tab.au.info[auid<(length(tab.au.info$auid)/2 +1), ]
tab.au.info.fut<-tab.au.info[auid>length(tab.au.info$auid)/2, ]

tab.dat<-data.table(current)
tab.dat.fut<-data.table(future2)
current_curves<-merge(tab.dat, tab.au.info.cur, by="feature_id")
future_curves<-merge(tab.dat.fut, tab.au.info.fut, by="feature_id")

current_curves<-current_curves %>% rename(curve = current_curve)
future_curves<-future_curves %>% rename(curve = future_curve)

curves<-rbind(current_curves, future_curves)
```

### Calculate deciduous percentage from the VRI

Castor can store a deciduous percentage (dec_pcnt) for each stand, which is used to support reporting and volume attribution, but does not influence growth dynamics or yield trajectories. If this information is not already included in the growth and yield tables, it can be derived from Vegetation Resources Inventory (VRI) species composition.
The approach shown below demonstrates one way to estimate deciduous percentage using standard VRI attributes:

Individual species components in the VRI are classified as conifer or deciduous based on species codes.
For each stand, the percentage cover of all conifer species (up to six species entries) is summed to compute total conifer cover.
Deciduous percentage is then calculated as:

dec_pcnt = 100 − conifer_pct_cover_total

The resulting dec_pcnt value is merged into the yield curve tables and carried through the Castor workflow. In growingStockCastor, this value is used only at the reporting stage to estimate deciduous volume as a proportion of total simulated stand volume (e.g., for compartment‑level summaries). Castor does not simulate conifer and deciduous growth separately, and dec_pcnt does not affect yield curve selection, stand transitions, or growth projections.
For attributes that are not actively modeled in this workflow (e.g., quadratic mean diameter (QMD) or equivalent clearcut area (ECA)), placeholder values are assigned to satisfy Castor’s schema requirements without affecting simulation behavior.

Important:
Deciduous percentage in Castor is a static attribution parameter, not a dynamic growth variable. It is used for accounting and reporting purposes only.

```{r, G&Y data}
library(DBI)
library(RPostgres)
library(sf)

con <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get("dbhost", keyring = "postgreSQL"),
  dbname   = keyring::key_get("dbname", keyring = "postgreSQL"),
  port     = 5432,
  user     = keyring::key_get("dbuser", keyring = "postgreSQL"),
  password = keyring::key_get("dbpass", keyring = "postgreSQL")
)

vri <- st_read(
  con,
  layer = Id(schema = database.schema, table = "vri_2024_test")
)

vri<- vri %>% select (feature_id, species_cd_1: species_pct_6)

conifer<-c("C","CW","Y","YC","F","FD","FDC","FDI","B","BB","BA","BG","BL","H","HM","HW","HXM","J","JR","JS","P","PJ","PF","PL","PR","PLI","PXJ","PY","PLC","PW","PA","S","SB","SE","SS","SW","SX","SXW","SXL","SXS","T","TW","X", "XC","XH", "ZC")

deciduous<-c("L", "LA", "LT", "LW", "D", "DR", "U", "UP", "A", "AC", "ACB", "ACT", "AX", "AT", "R", "RA", "E", "EA", "EXP", "EP", "EW", "K", "KC", "V", "VB", "VV", "VP", "G", "M", "MB", "MV", "Q", "QG", "W", "WB", "WP", "WA", "WD", "WS", "WT", "XH", "ZH")

vri<- vri %>%
  mutate(pct1 = ifelse(species_cd_1 %in% conifer, species_pct_1, NA),
         pct2 = ifelse(species_cd_2 %in% conifer, species_pct_2, NA),
         pct3 = ifelse(species_cd_3 %in% conifer, species_pct_3, NA),
         pct4 = ifelse(species_cd_4 %in% conifer, species_pct_4, NA),
         pct5 = ifelse(species_cd_5 %in% conifer, species_pct_5, NA),
         pct6 = ifelse(specoes_cd_6 %in% conifer, species_pct_6, NA),
         dominant_conifer = ifelse(species_cd_1 %in% conifer, species_cd_1, 
                                   ifelse(species_cd_2 %in% conifer, species_cd_2,
                                          ifelse(species_cd_3 %in% conifer, species_cd_3,
                                                 ifelse(species_cd_4 %in% conifer, species_cd_4,
                                                        ifelse(species_cd_5 %in% conifer, species_cd_5,
                                                               ifelse(species_cd_6 %in% conifer, species_cd_6, NA)))))))

table(vri$dominant_conifer)

vri<-vri %>% mutate(conifer_pct_cover_total=rowSums(across(c(pct1:pct6)), na.rm=TRUE))

vri_con<-vri[,c("feature_id", "conifer_pct_cover_total")]

curves<-merge(curves, vri_con, by="feature_id")

curves [, dec_pcnt := 100 - conifer_pct_cover_total]
#remove the column conifer_pct_cover_total
curves[, conifer_pct_cover_total:=NULL]
curves [, qmd := 0] # if you have no quad mean diameter values include it as 0 for a place holder
curves [, eca := 0] # similarly if you have no expected clearcut area values include it as a zero
```

### Assign current and future yield curve IDs (YCIDs)

Yield curve IDs are assigned based on stand type:
Natural stands reference the natural (VDYP‑based) YCID,
Managed stands reference the managed (TIPSY‑based) YCID,
All stands are assigned a future managed YCID, which will be used after harvest.

Negative YCIDs are used to distinguish natural yield curves from managed ones, following Castor convention.
This step defines the rule‑based transition from current to future yield curves that Castor applies during simulation.
```{r}

library(data.table)
library(dplyr)
library(terra)
library(DBI)
library(RPostgres)

## ---------------------------------------------------------------------
## 1. Define YCID boundary (natural vs managed)
## ---------------------------------------------------------------------
## Convention: lower half = natural, upper half = managed
ycid_split <- max(tab.au.info$auid) / 2


## ---------------------------------------------------------------------
## 2. Assign current and future YCIDs by stand type
## ---------------------------------------------------------------------
## Current condition:
##   - oldCurve / thriftyCurve → natural (VDYP)
##   - managedCurve           → managed (TIPSY)

curves[
  standtype %in% c("oldCurve", "thriftyCurve"),
  ycid_current := natural_ycid
]

curves[
  standtype == "managedCurve",
  ycid_current := managed_ycid
]

## Future condition:
##   - After harvest, all stands use managed (TIPSY) curves
curves[, ycid_future := managed_ycid]


## ---------------------------------------------------------------------
## 3. Build AU-level transition table (one row per AU)
## ---------------------------------------------------------------------
tab.transition <- unique(
  curves[
    auid <= ycid_split,
    .(feature_id, auid, ycid_current, ycid_future)
  ]
)

## Negative YCIDs indicate natural yield curves (Castor convention)
tab.transition[
  ycid_current <= ycid_split,
  ycid_current := -ycid_current
]


## ---------------------------------------------------------------------
## 4. Create spatial YCID rasters (current and future)
## ---------------------------------------------------------------------
## Load AU raster once
rast.auid <- terra::rast(paste0(data.dir,
  "/tiff/tsa02_au.tif"))

## Current YCID raster
rast.current.ycid <- terra::subst(
  rast.auid,
  tab.transition$auid,
  tab.transition$ycid_current
)

## Future YCID raster
rast.future.ycid <- terra::subst(
  rast.auid,
  tab.transition$auid,
  tab.transition$ycid_future
)


## ---------------------------------------------------------------------
## 5. Write YCID rasters to disk and Postgres
## ---------------------------------------------------------------------
writeRaster(
  extend(rast.current.ycid, ras.aoi),
  paste0(data.dir, "rast_ycid_current.tif"),
  overwrite = TRUE
)

system(
  paste0(
    'raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ',
    data.dir, 'rast_ycid_current.tif -t 100x100 ',database.schema,'.rast_ycid_current | ',
    'psql postgres://',
    keyring::key_get("dbuser",  keyring = "postgreSQL"), ':',
    keyring::key_get("dbpass",  keyring = "postgreSQL"), '@',
    keyring::key_get("dbhost",  keyring = "postgreSQL"), ':5432/',
    keyring::key_get("dbname",  keyring = "postgreSQL")
  )
)

writeRaster(
  extend(rast.future.ycid, ras.aoi),
  paste0(data.dir, "rast_ycid_future.tif"),
  overwrite = TRUE
)

system(
  paste0(
    'raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ',
    data.dir, 'rast_ycid_future.tif -t 100x100 ',database.schema,'.rast_ycid_future | ',
    'psql postgres://',
    keyring::key_get("dbuser",  keyring = "postgreSQL"), ':',
    keyring::key_get("dbpass",  keyring = "postgreSQL"), '@',
    keyring::key_get("dbhost",  keyring = "postgreSQL"), ':5432/',
    keyring::key_get("dbname",  keyring = "postgreSQL")
  )
)


## ---------------------------------------------------------------------
## 6. Build Castor-ready CURRENT yield table
## ---------------------------------------------------------------------
tab.current <- curves[
  ycid_current <= ycid_split,
  .(ycid_current, feature_id, age, vol, dec_pcnt, ht, qmd, ba, cc, eca)
]

setnames(
  tab.current,
  old = c("ycid_current", "vol", "ht", "ba", "cc"),
  new = c("ycid",         "tvol", "height", "basalarea", "crownclosure")
)

tab.current[, ycid := as.integer(ycid)]
tab.current <- unique(tab.current)


## ---------------------------------------------------------------------
## 7. Build Castor-ready FUTURE yield table
## ---------------------------------------------------------------------
tab.future <- curves[
  ycid_future > ycid_split,
  .(ycid_future, feature_id, age, vol, dec_pcnt, ht, qmd, ba, cc, eca)
]

setnames(
  tab.future,
  old = c("ycid_future", "vol", "ht", "ba", "cc"),
  new = c("ycid",        "tvol", "height", "basalarea", "crownclosure")
)

tab.future[, ycid := as.integer(ycid)]
tab.future <- unique(tab.future)


## ---------------------------------------------------------------------
## 8. Write yield tables to Postgres
## ---------------------------------------------------------------------
conn <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get("dbhost", keyring = "postgreSQL"),
  dbname   = keyring::key_get("dbname", keyring = "postgreSQL"),
  port     = 5432,
  user     = keyring::key_get("dbuser", keyring = "postgreSQL"),
  password = keyring::key_get("dbpass", keyring = "postgreSQL")
)

dbWriteTable(
  conn,
  Id(schema = database.schema, table = "yields_current"),
  tab.current,
  overwrite = TRUE
)

dbWriteTable(
  conn,
  Id(schema = database.schema, table = "yields_future"),
  tab.future,
  overwrite = TRUE
)

dbDisconnect(conn)
```

