<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

---
title: "Provincial Forest Management Objectives"
author: "Kyle Lochhead"
original creation date: "March 15, 2019"
updated: "March 13, 2026"
update by: "Elizabeth Kleynhans"
output: 
  html_document: 
    keep_md: yes
    toc: true
---

## Purpose

Create a provincial scale forest management objective raster(s) based on two categories: i) zonal constraints; ii) no-harvesting constraints and iii) conditional harvesting constraints. For iii) condition harvesting constraints refer to: [uwr_cond_harvest](https://github.com/bcgov/castor/tree/main/functions/uwr_cond_harvest.Rmd) and [wha_cond_harvest](https://github.com/bcgov/castor/tree/main/functions/wha_cond_harvest.Rmd). The various management objectives being considered and sources include:

```{r table_objs, echo=FALSE}
library(data.table)
library(here)
knitr::kable(data.table(objective = c(
                        "Aspatial Old Growth Retention",
                        "Fisheries Sensitive Watersheds",
                        "Visual Quality Objectives"), 
             source = c("https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf",
                       "http://www.env.gov.bc.ca/wld/frpa/fsw/approved.html" ,
                       "https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/visual-resource-management"
                        )),
             caption = "Zonal Constraints")

knitr::kable(data.table(objective = c(
                        "Wildlife Habitat Areas",
                        "Ungulate Winter Range",
                        "Wildlife Management Areas",
                        "Visual Quality Objectives",
                        "Spatial Old Growth Management Areas"),
             source = c(
               "http://www.env.gov.bc.ca/cgi-bin/apps/faw/wharesult.cgi?search=show_approved",
               "http://www.env.gov.bc.ca/wld/frpa/uwr/approved_uwr.html",
               "https://catalogue.data.gov.bc.ca/dataset/tantalis-wildlife-management-areas",
               "https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/visual-resource-mgmt/vrm_a_guide_to_visual_quality_objectives.pdf",
               "https://catalogue.data.gov.bc.ca/dataset/old-growth-management-areas-legal-current"
             )),
             caption = "Harvesting Constraint")
```

>Note: these management objectives are not inclusive of all objectives - but rather they are a set of common constraints considered in timber supply review. Remaining detailed layers indicating either zonal or harvesting constraints will be incorporated at a later time

# Create a provincial raster
```{r}
#Create a provincial raster
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", resolution = c(100, 100), vals = 0)
```


## Forest harvesting restrictions

 download forest harvest restrictions layer from: https://catalogue.data.gov.bc.ca/dataset/forest-harvesting-restrictions-generalized-
Then extract the layer
```{r}
harvest_restrictions<-st_read("C:\\Users\\ekleynha\\Downloads\\forest_harvesting_restrictions.gdb")
harvest_restrictions

harvest_restrictions
```


## Watershed units
```{r}
unique(harvest_restrictions$land_designation_type_name)


wau<-harvest_restrictions %>% dplyr::filter(land_designation_type_name %in% c("Greater Vancouver Water District", "CRD Water Supply Area"))

ggplot(data=wau)+
  geom_sf()

wau$ogc_fid<-1
wau.ras<-fasterize::fasterize(wau, raster = prov.rast, field="ogc_fid")
writeRaster(wau.ras, "D:/Fire/fire_data/raw_data/wau.tif", overwrite=TRUE)

zone.wau<-data.table(zoneid =  unique(wau.ras[]), reference_zone = 'rast.zone_cond_wau', ndt =0, variable= 'eca', threshold = 100, type = 'le', percentage = 100, multi_condition =NA, denom =NA, start = 0, stop = 250, label = 'watershed_analysis')
zone.wau<-zone.wau[!is.na(zone.wau$zoneid),]

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
DBI::dbWriteTable(conn, c("zone", "zone_wau"), value= zone.wau, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

```


## Biodiversity Emphasis Options - Zonal Constraints

Biodiversity Emphasis Options (BEO) are defined during landscape level planning, typically an a landscape unit or on BEC zones (natural disturbance types) within a landscape unit. If no landscape unit has been designated for an area, or an emphasis option has not been assigned for a particular landscape unit, the default is that the area is managed using the lower biodiversity emphasis option. see [Biodiversity Guidebook](https://www.for.gov.bc.ca/ftp/hfp/external/!publish/FPC%20archive/old%20web%20site%20contents/fpc/fpcguide/BIODIV/chap1.htm#bid)

#### Get data  

Download the data from here: https://catalogue.data.gov.bc.ca/dataset/landscape-units-of-british-columbia-current
```{r zoneStep1, echo=FALSE}

lu<-st_read("C:\\Users\\ekleynha\\Downloads\\BCGW_02001F02_1773432047803_13220\\RMP_LANDSCAPE_UNIT_SVW\\RMP_LU_SVW_polygon.shp")

lu<-lu %>% rename(lu_id=LU_ID,
                  lu_name=LU_NAME,
                  beo=BEO,
                  #rt_dt=RT_DT,
                  gis_ch_dt=GIS_CH_DT,
                  wkb_geometry=geometry) %>%
  dplyr::select(lu_id, lu_name, beo, gis_ch_dt, wkb_geometry)

lu.dt<-data.table(lu)
lu.dt<-lu.dt[beo=="High", beo:=1][beo=="Intermediate", beo:=2][beo=="Low", beo:=3]
lu.dt[is.na(beo), beo:=3]
lu<-rbind(lu.dt1, lu.mult)
lu$beo<-as.numeric(lu$beo)
lu[is.na(beo), beo:=3]

lu<-st_as_sf(lu)
#Rasterize the bidodiversity emphasis options
beo.ras<-fasterize::fasterize(sf= lu, raster = prov.rast , field = "beo")
luid.ras<-fasterize::fasterize(sf= lu, raster = prov.rast , field = "lu_id")

#Get the natural disturbance types
ndt <- bcdc_query_geodata("WHSE_FOREST_VEGETATION.BEC_BIOGEOCLIMATIC_POLY") %>%
  collect()
  
ndt<-data.table(ndt)

ndt[NATURAL_DISTURBANCE=="NDT1",ndt:=1]
ndt[NATURAL_DISTURBANCE=="NDT2",ndt:=2]
ndt[NATURAL_DISTURBANCE=="NDT3",ndt:=3]
ndt[NATURAL_DISTURBANCE=="NDT4",ndt:=4]
ndt[NATURAL_DISTURBANCE=="NDT5",ndt:=5]

ndt[ZONE == 'BWBS', zone:=1]
ndt[ZONE == 'CDF', zone:=2]
ndt[ZONE == 'CWH', zone:=3]
ndt[ZONE == 'ESSF', zone:=4]
ndt[ZONE == 'ICH', zone:=5]
ndt[ZONE == 'IDF', zone:=6]
ndt[ZONE == 'MH', zone:=7]
ndt[ZONE == 'MS', zone:=8]
ndt[ZONE == 'PP', zone:=9]
ndt[ZONE == 'SBPS', zone:=10]
ndt[ZONE == 'SBS', zone:=11]
ndt[ZONE == 'SWB', zone:=12]

ndt<-st_as_sf(ndt)

#Rasterize the NDT
ndt.ras<-fasterize::fasterize(sf= ndt, raster = prov.rast , field = "ndt")

#Rasterize the BEC zone (key for BEC zones)
bec.ras<-fasterize::fasterize(sf= ndt, raster = prov.rast , field = "zone")

rm(lu,ndt) # free some memory
gc()# Clean up

#Make a stack raster with all the information needed for BEO contraints
ogm<-stack(bec.ras, ndt.ras, luid.ras, beo.ras)
names(ogm)<-c("BEC", "NDT", "LU_ID", "BEO")
raster::plot(ogm) #plot the stack
```

#### Make unique zones within Landscape Units

```{r zoneStep2, echo=FALSE}
library(data.table)
library(here)

#------------------------------------
#Biodiversity Emphasis Options on Age
#------------------------------------
ogm.table<-data.table(as.data.frame(ogm)) #ogn is the stacked raster of the BEO
ogm.table[, id := seq_len(.N)]#assign a unique id for each pixel

rm(ogm, bec.ras, beo.ras, ndt.ras, luid.ras) #clear up some memory
gc() # clean up

#concactenate and join in old growth percentage
print(head(ogm.table))
ogm.table[, ogm := paste0(BEC, '_', NDT, '_', BEO)]
#print(ogm.table[!is.na(BEC)])#CHECK

#Create oldgrowth look up table. Note for ndt 3 in the BWBS there is a further difference between conifer and deciduous. I omitted this level of precision and used the most conservative one -- the conifer percentage . This adds an extra 2-3 percent!!! see Table 3 in https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf

NDT1<-data.table(BEC = c("CWH", "CWH", "CWH", 
                         "ICH", "ICH", "ICH",
                         "ESSF","ESSF","ESSF",
                         "MH",  "MH",  "MH"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          28, 19, 19,
                          28, 19, 19), AGE = 250, NDT = 1, BEO = 1:3)

NDT2<-data.table(BEC = c("CWH", "CWH", "CWH",
                         "CDF", "CDF", "CDF", 
                         "ICH", "ICH", "ICH",
                         "SBS", "SBS", "SBS",
                         "ESSF","ESSF","ESSF",
                         "SWB", "SWB", "SWB"),
                 p_OGR= c(13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9), AGE = 250, NDT = 2, BEO = 1:3)

NDT3<-data.table(BEC = c("BWBS","BWBS","BWBS", 
                         "SBPS","SBPS","SBPS",
                         "SBS", "SBS", "SBS",
                         "MS",  "MS",  "MS",
                         "ESSF","ESSF","ESSF",
                         "ICH", "ICH", "ICH",
                         "CWH", "CWH", "CWH"),
                 p_OGR= c(19, 13, 13,
                          10, 7, 7,
                          16, 11, 11,
                          21, 14, 14,
                          21, 14, 14,
                          21, 14, 14,
                          16, 11, 11), 
                 AGE = c(100, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140), NDT = 3, BEO = 1:3)

NDT4<-data.table(BEC = c("ICH", "ICH", "ICH",
                         "IDF", "IDF", "IDF",
                         "PP",  "PP",  "PP"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          19, 13, 13), AGE = 250, NDT = 4, BEO = 1:3)

p_OGR<-rbind(NDT1, NDT2, NDT3, NDT4) #this is the lookup for geting the percentage of old growth required for retention by bec and ndt

#Create a value attribute table which assigns an integer key called BEC2 to each BEC zone
vat<-data.table(BEC  = 
                c('BWBS', 'CDF', 'CWH', 'ESSF', 'ICH', 'IDF', 'MH', 'MS', 'PP','SBPS', 'SBS', 'SWB'),
                BEC2 = 1:12)

p_OGR<-merge(x=p_OGR, y=vat, by.x= "BEC", by.y= "BEC") # join vat and p_OGR to get BEC2 key
p_OGR[, ogm := paste0(BEC2, '_', NDT, '_', BEO)] # concatenate to get a unique constraint

p_OGR<-p_OGR[, c(2:3,7)] #Keep only the unique constraint, the p_OGR and age threshold

setkey(ogm.table, ogm) # assign a data.table key thats the unique constraint for joining
setkey(p_OGR, ogm)# assign a data.table key thats the unique constraint for joining

ogm.final<-merge(x=p_OGR, y=ogm.table, by="ogm", all.y=TRUE) # merge the constraint with each spatial landscape unit

#rm(ogm.table) # clear memory
gc() # clean up
#----Checking----
#print(ogm.final[!is.na(p_OGR)])
#out<-data.frame(ogm.final[order(id)])
#print(head(out[]))
#ogm.ras<-prov.rast
#ogm.ras[]<-out[,2]
#writeRaster(ogm.ras, file="ogm_ret_thres.tif", format="GTiff", overwrite=TRUE)
#rm(ogm.ras, out, NDT1, NDT2, NDT3, NDT4, vat, p_OGR)
gc()

ogm.final[, zone := .GRP, by=.(LU_ID,BEC,NDT)] #Creates a unique id for each zone grouped by Lu_ID, BEC and NDT
#remove zones that are ndt5 or other wise do not have a ogr, age
print(head(ogm.final[is.na(AGE),]))
ogm.final[is.na(AGE), zone:=NA]
out<-data.frame(ogm.final[order(id)])
gc()
zone.ras<-prov.rast
zone.ras[]<-out[,9] #assign the zone to each pixel


writeRaster(zone.ras, file=paste0(here(),"/zone_beo.tif"), format="GTiff", overwrite=TRUE)#print the raster
rm(zone.ras, out)

# Upload to postgres database
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_beo.tif -t 100x100 rast.zone_cond_beo |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = FALSE)

library(RPostgreSQL)
ogm.final[zone == 2435,]
zone_beo_table<-setDT(ogm.final)[, .SD[which.max(AGE)], by=zone]

zone_beo_table<-zone_beo_table[,c(1,3:4, 6)]
zone_beo_table[, reference_zone := 'rast.zone_cond_beo']
zone_beo_table[, variable := 'age']
zone_beo_table[, type := 'ge']

setnames(zone_beo_table, c("zoneid", "percentage", 
                  "threshold","ndt", "reference_zone", 
                  "variable", "type"))
zone_beo_table[, ndt := as.integer(ndt)]
df<-as.data.frame(zone_beo_table)
df$label<-'beo' #TODO: label this is as high/I/L ?
df$multi_condition<-NA 
df$denom<-NA 
df$start <- 0
df$stop <- 250

#Upload the constraint table to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("zone", "zone_beo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(zone_beo_table, df, ogm.final)
gc()

```


# Fisheries Sensitive Areas and Equivalent Clearcut Area
```{r, fsw}
#Fisheries Sensitive Areas
#source (paste0(here(),"/R/functions/R_Postgres.R"))
library(bcdata)
fsw<-try(
  bcdc_query_geodata("WHSE_WILDLIFE_MANAGEMENT.WCP_FISH_SENSITIVE_WS_POLY") %>%
    collect()
)

st_geometry(fsw) <- "wkb_geometry"
fsw_orig<- st_cast(fsw, "MULTIPOLYGON")

#fsw<-getSpatialQuery("SELECT fsw_id, wkb_geometry FROM public.wcp_f_s_ws_polygon")

st_geometry(fsw) <- "wkb_geometry"
fsw_orig<- st_cast(fsw, "MULTIPOLYGON")

#Rasterize the fisher sensitive areas
fsw.ras<-fasterize::fasterize(sf= fsw_orig, raster = prov.rast , field = "FISH_SENSITIVE_WS_POLY_ID")
writeRaster(fsw.ras, file=paste0(here(),"/zone_fsw_gbr.tif"), format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_fsw_gbr.tif -t 100x100 rast.zone_cond_fsw |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

plot(fsw.ras)
rm(fsw.ras)
gc()
library(dplyr)

df<-as.data.frame(fsw)
df$type<-'le' # less than (le), greater than (ge)
df$variable<-'eca' # equivalent clear cut area (eca)
df$threshold<-20
df$reference_zone<-'rast.zone_cond_fsw'
df$percentage<-100
df$ndt<-as.integer(0)
df<-df[,c("FISH_SENSITIVE_WS_POLY_ID","type","variable", "threshold", "reference_zone", "percentage", "ndt" )]
colnames(df) <- c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")

df$zoneid<-as.integer(df$zoneid)#assign integer
df$label<-'fsw'
df$multi_condition <-NA
df$denom<-NA
df$start <- 0 
df$stop <- 250
#upload the constraint table for FSW to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("zone", "zone_fsw"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(df_final, df_gbr1, df_gbr2, df_other, fsw, gbr_fsw, gbr_fsw1, gbr_fsw2)
gc()
```

# Visual Quality Constraints
```{r, vqo}
vqo<-try(
  bcdc_query_geodata("WHSE_FOREST_VEGETATION.REC_VIMS_EVQO_SVW") %>%
    collect()
)
#Visual Quality Constraints on height
#see https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/visual-resource-mgmt/vrm_a_guide_to_visual_quality_objectives.pdf

vqo<-data.table(vqo)
vqo[REC_EVQO_CODE=="P", vli_id:=0][REC_EVQO_CODE=="R", vli_id:=2][REC_EVQO_CODE=="PR", vli_id:=7][REC_EVQO_CODE=="M", vli_id:=18][REC_EVQO_CODE=="MM", vli_id:=30]
vqo2<-vqo[REC_EVQO_CODE!="SCO",c("vli_id", "geometry")]

vqo2<-st_as_sf(vqo2)

vqo.ras<-fasterize::fasterize(sf= vqo2, raster = prov.rast , field = "vli_id")
writeRaster(vqo.ras, file=paste0(here(),"/zone_vqo.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_vqo.tif -t 100x100 rast.zone_cond_vqo |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

df<-as.data.frame(vqo2)
df<-df[,1:2]
df$type<-'le'
df$variable<-'height'
df$threshold<-5
df$reference_zone<-'rast.zone_cond_vqo'
df$ndt<-as.integer(0)
colnames(df) <- c("percentage", "zoneid", "type", "variable", "threshold", "reference_zone", "ndt") # the vqo column gets labeled as percentage
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'vqo'

df<-data.table(unique(df))# get rid of the multiple zoneid = 0 )
df[zoneid == 0, type := 'nh']
df$multi_condition <-NA
df$denom<-NA
df$start <- 0 
df$stop <- 250


conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "zone_vqo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(df, vqo.ras, vqo)
gc()
```

# Spatial No Harvesting Constraints 

These are areas that can contribute to zonal constraints but cannot harvest within these boundaries. For instance a spatial OGMA constraint refers to a mapped out spatial location for no harvesting. This area may be within a larger BEO that would include these pixels as part of the landscape level age constraint.

The steps involved in the harvesting constraints:
1. Get spatial old growth management areas (OGMA) - legal - no harvesting
2. Get Parks and Protected Areas (parks)
3. Get Biodiversity, Mining and Tourism areas 

```{r hc_step1, echo=FALSE}

#ogma
ogma<-try(
  bcdc_query_geodata("WHSE_LAND_USE_PLANNING.RMP_OGMA_LEGAL_ALL_SVW") %>%
    collect()
)
# or download it and read the file in.
#ogma<-st_read("C:\\Users\\ekleynha\\Downloads\\BCGW_02001F02_1738909358527_8012\\RMP_OGMA_LEGAL_ALL_SVW\\OGMA_LEGAL_polygon.shp")
names(ogma)

ogma<-ogma %>%filter(!is.na(RT_DT)) %>% select(OGMA_TYPE, geometry)

ogma$harvest<-1
ogma.ras<-fasterize::fasterize(sf= ogma, raster = prov.rast , field = "harvest")
ogma.ras[is.na(ogma.ras)]<-0

#parks and conservancies and biodiversity, tourisms and mining
unique(harvest_restrictions$rr_restriction)
parks<-harvest_restrictions %>% filter(rr_restriction %in% c("01_National Park", "02_Ecological Reserve", "03_Provincial Park","04_Conservancy", "05_Protected Area","06_Heritage Site","07_Recreation Area", "08_Regional Park","11_Biodiversity Mining and Tourism Area","12_Sea to Sky Wildland Zone", "15_South Chilcotin Mountains Mining and Tourism Areas","32_Private Conservation Land: Reserve Land", "38_National Wildlife Areas")) %>% select(Shape)
parks$harvest<-1
parks.ras<-fasterize::fasterize(sf= parks, raster = prov.rast , field = "harvest")
parks.ras[is.na(parks.ras)]<-0

# #conservancies
# conserv<-getSpatialQuery("SELECT wkb_geometry FROM public.ta_ca_svw_polygon")
# conserv$harvest<-1
# conserv.ras<-fasterize::fasterize(sf= conserv, raster = prov.rast , field = "harvest")
# conserv.ras[is.na(conserv.ras)]<-0

#Biodiversity, mining and tourism areas
# Data was taken from https://catalogue.data.gov.bc.ca/dataset/legal-planning-objectives-all-polygon

# RMP_poly<-sf::st_read("//spatialfiles2.bcgov/work/FOR/VIC/HTS/ANA/Workarea/ekleynhans/BCGW_7113060B_1596086267627_5328/RMP_PLAN_LEGAL_POLY_SVW/RMP_LG_PL_polygon.shp")
# 
# bmta<-RMP_poly %>% filter(FEAT_OBJ=="Biodiversity, Mining and Tourism Areas (BMTA)") %>%
#   dplyr::select(geometry)
# bmta$harvest<-1
# 
# names(bmta)<-c("wkb_geometry", "harvest")
# st_geometry(bmta) <- "wkb_geometry"
# bmta.ras<-fasterize::fasterize(sf= bmta, raster = prov.rast , field = "harvest")

nharv.ras<- ogma.ras + parks.ras 
plot(nharv.ras)
nharv.ras[nharv.ras[] == 0 ] <- NA
nharv.ras[nharv.ras[] > 0 ] <- 0
writeRaster(nharv.ras, file=paste0(here(),"/nharv.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M  ', here::here(), '/nharv.tif -t 100x100 rast.zone_cond_nharv | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

df<-data.frame(type='nh', variable= '', threshold=0, reference_zone='rast.zone_cond_nharv_gbr',
ndt=0,percentage = 0, zoneid =0)
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'parks or OGMA'
df$ndt<-as.integer(0)
df$multi_condition <-NA
df$denom<-NA
df$start <- 0 
df$stop <- 250

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("zone", "zone_nharv"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(ogma.ras , parks.ras, parks, ogma, pres, wha, uwr)
gc()
```

### Community Watersheds
Water in community watersheds is a value identified under the Forest and Range Practices Act. From the Kamloops TSR:  The approach was to ensure that no more than an equivalent clear-cut area (ECA) of 20% of the gross land base that applies to the upper 60% of all community watersheds and that standard management practices applies to the lower 40% of the watershed. The upper 60% (snow pack area) is considered hydrologically recovered upon
reaching 9 metres in height and the lower 40% being a 3 metre green up height. Therefore, averaging the above, in each community watershed the modelled practice was that no more than 25.2% of the gross area in a community watershed could be less than 6.6 metres in height.
```{r, com_water}
#com_wat<-getSpatialQuery("SELECT * FROM com_ws_pub_polygon;")
com_wat<-harvest_restrictions %>% filter(land_designation_type_name %in% c("Community Watershed")) %>% select(geom)
com_wat$ogc_fid<-2



#Rasterize the community watersheds
com_wat.ras<-fasterize::fasterize(sf= com_wat, raster = prov.rast , field = "ogc_fid")
com_wat.ras[is.na(com_wat.ras)]<-0
writeRaster(com_wat.ras, file=paste0(here::here(),"/zone_cw.tif"), format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here::here(), '/zone_cw.tif -t 100x100 rast.zone_cond_cw |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(com_wat.ras)
gc()
df<-as.data.frame(com_wat)
df$zoneid<-df$ogc_fid
df$type<-'le'
df$variable<-'eca'
df$threshold<-20
df$reference_zone<-'rast.zone_cond_cw'
df$percentage<-100
df$ndt<-as.integer(0)
df<-df[,c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")]
colnames(df) <- c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")
df$zoneid<-as.integer(df$zoneid)#assign integer
df$label<-'cw'
df$multi_condition <-NA
df$denom<-NA
df$start <- 0 
df$stop <- 250


#upload the constraint table for CW to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("zone", "zone_cw"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)
```

# Setting PostgreSQL Inheritance
PostgreSQL implements table inheritance. See [here]("https://www.postgresql.org/docs/9.5/ddl-inherit.html")

```{r zoneCleanUp, echo=FALSE, eval=FALSE}
#----------------------------
#Inheritability in PostgreSQL
#----------------------------
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

dbExecute(conn, "CREATE TABLE IF NOT EXISTS zone_constraints (zoneid integer, reference_zone text, ndt integer, variable text, threshold double precision, type text, percentage double precision, multi_condition text, denom character varying, start integer, stop integer, label text )")


dbExecute(conn, "ALTER TABLE zone.zone_nharv INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone.constraints")
#dbExecute(conn, "ALTER TABLE zone.zone_wha INHERIT zone.constraints") # defined in wha_cond_harvest_GBR.RMD
dbExecute(conn, "ALTER TABLE zone.zone_beo INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone.zone_fsw INHERIT zone.constraints")
#dbExecute(conn, "ALTER TABLE zone_uwr_gbr INHERIT zone_constraints_gbr") # defined in uwr_cond_harvest_GBR.RMD
dbExecute(conn, "ALTER TABLE zone.zone_cw INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone.zone_wau INHERIT zone.constraints")
#dbExecute(conn, "ALTER TABLE zone_mofrl_gbr INHERIT zone_constraints_gbr")

#if you need to change the column types do as below
dbExecute(conn, "ALTER TABLE zone.zone_beo ALTER COLUMN multi_condition SET DATA TYPE text;")
dbExecute(conn, "ALTER TABLE zone.zone_beo ALTER COLUMN denom SET DATA TYPE character varying;")
dbExecute(conn, "ALTER TABLE zone.zone_beo ALTER COLUMN start SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE zone.zone_beo ALTER COLUMN stop SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE zone.zone_beo ALTER COLUMN label SET DATA TYPE text;")

dbDisconnect(conn)
```
