<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

---
title: "Study Area Boundaries"
author: "Tyler Muhly and Elizabeth Kleynhans"
updated: "12/03/2026"
output: html_document
---

This script creates the neccessary study area boundary information needed for Castor to run a simulation on your area of interest. Other required parameters are detailed in other scripts.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(sf)
library(tidyverse)
library(bcdata)
library(fasterize)

#Create a provincial raster
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", resolution = c(100, 100), vals = 0)
```


## Get area of interest e.g. Okanagan TSA, 100 Mile House TSA, and Kamloops TSA. However, the area can be any area of your choosing.
```{r, data}
# ─────────────────────────────────────────────
# Load TSA / TFL Boundaries or any area that you are interested in using
# ─────────────────────────────────────────────
tsa_vals <- c("Okanagan TSA", "100 Mile House TSA", "Kamloops TSA")

tsa_raw <- bcdc_query_geodata("8daa29da-d7f4-401c-83ae-d962e3a28980") %>%
  filter(TSA_NUMBER_DESCRIPTION %in% tsa_vals) %>%  # match any of these
  collect()

tsa <- tsa_raw %>%
  group_by(TSA_NUMBER, TSA_NUMBER_DESCRIPTION) %>%
  summarise(do_union = TRUE) %>%
  st_make_valid()

plot(tsa["TSA_NUMBER"])

# ─────────────────────────────────────────────
# Create Clean TSA Identifier Table
# ─────────────────────────────────────────────
tsa_ids <- tsa %>%
  st_drop_geometry() %>%
  select(TSA_NUMBER, TSA_NUMBER_DESCRIPTION) %>%
  distinct() %>%
  mutate(
    tsa_name = gsub(" ", "_", TSA_NUMBER_DESCRIPTION),
    tsa_id   = as.numeric(TSA_NUMBER)
  )

# Join back to geometry
tsa_clean <- tsa %>%
  left_join(tsa_ids, by = c("TSA_NUMBER", "TSA_NUMBER_DESCRIPTION")) %>%
  select(tsa_id, tsa_name, shape = geometry)

# ─────────────────────────────────────────────
# Save Clean Shapefile and write it to your local postgres database
# ─────────────────────────────────────────────

con <- dbConnect(RPostgres::Postgres(),host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), port='5432' ,user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), password = keyring::key_get ('dbpass', keyring = 'postgreSQL')) 
st_write(st_as_sf(tsa_clean, crs=3005), con, Id(schema = "public", table = "test_tsa"))
dbDisconnect(con)

# ─────────────────────────────────────────────
# Create the look up table
# ─────────────────────────────────────────────
tsa_clean_vat <- as.data.table (st_drop_geometry (tsa_clean))
tsa_clean_vat<-tsa_clean_vat %>% 
  rename(value=tsa_id)

# ─────────────────────────────────────────────
# Rasterize 
# ─────────────────────────────────────────────
tsa_rast <- fasterize(
  st_cast(tsa_clean, "MULTIPOLYGON"),
  prov.rast,
  field = "tsa_id"
)

plot(tsa_rast)
writeRaster(tsa_rast, "tsa_boundary.tif", overwrite = TRUE)

# ─────────────────────────────────────────────
# write data to postgres
# ─────────────────────────────────────────────

conn<-DBI::dbConnect (dbDriver("PostgreSQL"), host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), port='5432' ,user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), password = keyring::key_get ('dbpass', keyring = 'postgreSQL'))
setnames (tsa_clean_vat, c ("value", "tsa_name")) # Note use convention; always name these value and attribute
DBI::dbWriteTable(conn, c("public", "vat_test_tsa"), value = tsa_clean_vat, row.names = FALSE, overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ',  here::here("functions//tsa_boundary.tif"),' -t 100x100 public.rast_test_tsa | psql postgres://', keyring::key_get ('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get ('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get ('dbhost', keyring = 'postgreSQL'), ':5432/',keyring::key_get ('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

dbDisconnect(conn)

```