<!--
Copyright 2025 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

---
title: "Example_castor_simulation"
author: "Elizabeth Kleynhans"
date: "2026-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(terra)
library(sf)
library(data.table)
library(DBI)
library(RPostgres)
library(keyring)
library(fasterize)
library(raster)
library(bcdata)
```

## 1. Provincial raster template
This template is needed so that the extent of every raster used in the analyses in Castor line up
```{r}
prov.rast <- raster::raster(
  nrows = 15744,
  ncols = 17216,
  xmn = 159587.5,
  xmx = 1881187.5,
  ymn = 173787.5,
  ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = c(100, 100),
  vals = 0
)
```

## 2. Create my boundary files
The bounday files determine where the analysis takes place. Three files are required; a shapefile of your area of interest, a raster of your area of interest, and a lookup table for your area of interest. These need to be loaded into your postgres database.
```{r}
# ─────────────────────────────────────────────
# 1. Create your area of interest
# ─────────────────────────────────────────────

xmin <- 999987.5
xmax <- 1063088
ymin <- 1167088
ymax <- 1223388

study_area_sf <- st_sf(
  area_id = 1,
  tsa_name = "study_area_test",
  geometry = st_as_sfc(
    st_bbox(c(
      xmin = xmin,
      xmax = xmax,
      ymin = ymin,
      ymax = ymax
    ), crs = st_crs(3005))
  )
)

# ─────────────────────────────────────────────
# 2. Lookup table (VAT)
# ─────────────────────────────────────────────

vat <- data.table(
  value = 1,
  tsa_name = "study_area"
)

setnames(vat, c("value", "tsa_name"))

# ─────────────────────────────────────────────
# 3. Fasterize ONTO prov.rast ✅
# ─────────────────────────────────────────────

study_area_rast <- fasterize(
  st_cast(study_area_sf, "MULTIPOLYGON"),
  prov.rast,
  field = "area_id"
)

plot(study_area_rast)

# Save raster
writeRaster(study_area_rast, "study_area.tif", overwrite = TRUE)

# ─────────────────────────────────────────────
# 4. Write shapefile locally
# ─────────────────────────────────────────────

st_write(study_area_sf, "study_area.shp", delete_dsn = TRUE)

# ─────────────────────────────────────────────
# 5. Connect to Postgres
# ─────────────────────────────────────────────

conn <- dbConnect(
  RPostgres::Postgres(),
  host     = keyring::key_get("dbhost", keyring = "postgreSQL"),
  dbname   = keyring::key_get("dbname", keyring = "postgreSQL"),
  port     = 5432,
  user     = keyring::key_get("dbuser", keyring = "postgreSQL"),
  password = keyring::key_get("dbpass", keyring = "postgreSQL")
)

# ─────────────────────────────────────────────
# 6. Write vector to Postgres
# ─────────────────────────────────────────────
# I created a schema called test, so that is where I will write the data. If you want your data in a different postgres schema change the name from test to your schema name. 
st_write(
  study_area_sf,
  conn,
  Id(schema = "test", table = "study_area")
)

# ─────────────────────────────────────────────
# 7. Write lookup table (VAT)
# ─────────────────────────────────────────────

dbWriteTable(
  conn,
  Id(schema = "test", table = "vat_study_area"),
  vat,
  overwrite = TRUE,
  row.names = FALSE
)

# ─────────────────────────────────────────────
# 8. Upload raster (prov-aligned) to PostGIS
# ─────────────────────────────────────────────

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 study_area.tif -t 100x100 test.rast_study_area | psql postgres://', keyring::key_get ('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get ('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get ('dbhost', keyring = 'postgreSQL'), ':5432/',keyring::key_get ('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

# ─────────────────────────────────────────────
# 9. Disconnect
# ─────────────────────────────────────────────

dbDisconnect(conn)
```

## 3. get THLB for area of interest

I our example the area of interest crosses both the MacKenzie TSA and the Prince George TSA so we need to download both of those. 
A version of the provincial timber harvesting land base can be obtained from https://catalogue.data.gov.bc.ca/dataset/provincial-timber-harvesting-land-base-thlb-by-timber-supply-area-tsa-
Head to this site and download the THLB data for TSA24 and TSA 16

```{r}
data.dir <- "<path\\to\\files>"
thlb_24<-st_read(paste0(data.dir,"\\tsa24\\tsa24_thlb.gdb"))
thlb_16<-st_read(paste0(data.dir,"\\tsa16\\tsa16_thlb.gdb"))

# check CRS match
st_crs(thlb_24)
st_crs(thlb_16)
st_crs(study_area_sf)

# combine THLB for both TSA's
thlb <- bind_rows(thlb_24, thlb_16)


# clip thlb to my area of interest
thlb_crop <- st_crop(thlb, st_bbox(study_area_sf))
thlb_crop <- st_make_valid(thlb_crop)


# Rasterize THLB to match Castor grid
ras.thlb <- fasterize::fasterize (st_cast (thlb_crop, "MULTIPOLYGON"), prov.rast, field = "thlb_fact")
plot(ras.thlb)

terra::writeRaster (ras.thlb, file = "raster_thlb.tif", overwrite = TRUE)
# upload raster to postgres
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 raster_thlb.tif -t 100x100 test.rast_thlb | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/',keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```
## 4. Get the VRI for your area of interest. Note uploading the whole VRI file takes ages so I clip it to the area of interest before working with it.
```{r}
# download and open the VRI data

# ─────────────────────────────────────────────
# 1. Define bbox from study area
# ─────────────────────────────────────────────

bbox <- st_bbox(study_area_sf)

# Convert bbox to WKT polygon
bbox_wkt <- st_as_text(st_as_sfc(bbox))

# ─────────────────────────────────────────────
# 2. Read VRI clipped to bbox (FAST)
# ─────────────────────────────────────────────

vri_tsa <- st_read(
  dsn = paste0(data.dir, "\\VEG_COMP_LYR_R1_POLY_2025.gdb"),
  wkt_filter = bbox_wkt
)

# ─────────────────────────────────────────────
# 3. Ensure CRS is correct (important)
# ─────────────────────────────────────────────

vri_tsa <- st_transform(vri_tsa, 3005)

# ─────────────────────────────────────────────
# 4. Select only needed columns + rename
# ─────────────────────────────────────────────

vri_tsa <- vri_tsa %>%
  dplyr::select(
    FEATURE_ID, OPENING_ID, OPENING_NUMBER,
    BCLCS_LEVEL_1, BCLCS_LEVEL_2, BCLCS_LEVEL_4, BCLCS_LEVEL_5,
    BEC_ZONE_CODE, BASAL_AREA, CROWN_CLOSURE,
    SPECIES_CD_1, SPECIES_PCT_1,
    SPECIES_CD_2, SPECIES_PCT_2,
    SPECIES_CD_3, SPECIES_PCT_3,
    SPECIES_CD_4, SPECIES_PCT_4,
    SPECIES_CD_5, SPECIES_PCT_5,
    SPECIES_CD_6, SPECIES_PCT_6,
    PROJ_AGE_1, PROJ_HEIGHT_1,
    SITE_INDEX, QUAD_DIAM_125,
    Shape
  ) %>%
  dplyr::rename_with(tolower)

# ─────────────────────────────────────────────
# 5. Optional: clean geometry (only after clipping!)
# ─────────────────────────────────────────────

vri_tsa <- st_make_valid(vri_tsa)

# ─────────────────────────────────────────────
# 6. Upload to postgres
# ─────────────────────────────────────────────

con <- dbConnect(RPostgres::Postgres(),host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get ('dbname', keyring = 'postgreSQL'), port='5432' ,user = keyring::key_get ('dbuser', keyring = 'postgreSQL'), password = keyring::key_get ('dbpass', keyring = 'postgreSQL')) 

st_write(st_as_sf(vri_tsa, crs=3005), con, Id(schema = "test", table = "vri_2025"))
dbDisconnect(con)

# ─────────────────────────────────────────────
# 8. Rasterize feature_id and upload to postgres
# ─────────────────────────────────────────────
ras.vri <- fasterize::fasterize (st_cast (vri_tsa, "MULTIPOLYGON"), prov.rast, field = "feature_id")
writeRaster (ras.vri, "raster_vri_fid.tif", overwrite = T)

# write data
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 raster_vri_fid.tif -t 100x100 test.rast_vri_id_test | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)
```

## 5. Get land constraints i.e. harvesting constraints

Our test area has some harvest constraints such as no harvesting in provincial parks, protected areas, ogmas, and some ungulate winter ranges and wildlife habitat areas. It also has some conditional harvesting associated with ungulate winter range, and some wildlife habitat area. In the section below we will include a few of these constraint as a demonstration for how to do this. For a full script creating constraints for the whole province see the files uwr_cond_harvest.Rmd, wha_cond_harvest.Rmd, and prov_manage_objs.Rmd in the 'castor//params//' folder. 

Download the forest harvest restrictions layer from: https://catalogue.data.gov.bc.ca/dataset/forest-harvesting-restrictions-generalized-
Then extract the layer and read it into R
```{r}
harvest_restrictions<-st_read(paste0(data.dir,"\\forest_harvesting_restrictions.gdb"))

harvest_restrictions_crop <- st_crop(harvest_restrictions, st_bbox(study_area_sf))

unique(harvest_restrictions_crop$land_designation_type_name)
unique(harvest_restrictions_crop$harvest_restriction_class_name)

# ─────────────────────────────────────────────
# 1. Create no harvest constraints
# ─────────────────────────────────────────────

harvest_restrictions_crop_nh<-harvest_restrictions_crop %>% dplyr::filter(land_designation_type_name %in% c("Ungulate Winter Range: No harvest", "Wildlife Habitat Area: No harvest", "Provincial Park", "Protected Area", "Old Growth Management Area (OGMA): Legal"))

harvest_restrictions_crop_nh$harvest<-1
nh.ras<-fasterize::fasterize(sf= harvest_restrictions_crop_nh, raster = prov.rast , field = "harvest")
nh.ras[is.na(nh.ras)]<-0

plot(nh.ras)
nh.ras[nh.ras[] == 0 ] <- NA
nh.ras[nh.ras[] > 0 ] <- 0
writeRaster(nh.ras, "nharv.tif", overwrite = TRUE)


system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M  C:\\Castor\\castor\\nharv.tif -t 100x100 test.zone_nharv_rast | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

df<-data.frame(type='nh', variable= '', threshold=0, reference_zone='test.zone_cond_nharv',
ndt=0, percentage = 0, zoneid =0)
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'parks or OGMA'
df$ndt<-as.integer(0)
df$multi_condition <-NA
df$denom<-NA
df$start <- 0 
df$stop <- 250

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("test", "zone_nharv"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

# ─────────────────────────────────────────────
# 1. Create conditional harvest constraints
# ─────────────────────────────────────────────

# first remove the no harvest areas that we delt with above.
harvest_restrictions_crop<-data.table(harvest_restrictions_crop)
harvest_restrictions_crop_nh<-data.table(harvest_restrictions_crop_nh)

cond_harv<-anti_join(harvest_restrictions_crop,harvest_restrictions_crop_nh)

cond_harv_uwr<-cond_harv %>% filter(land_designation_type_code == "uwr_conditional_harvest")
cond_harv_uwr$ogc_fid <- seq_len(nrow(cond_harv_uwr))

# first we will lookt at ungulate winter range u-7-015 for northern Caribou
#Under GVM 1: harvesting is not to occur in the winter. GVM 2: manage using a two pass 140 year rotation such that 50% +/- 20% is harvested. This will be interpreted as 50% of the area has to be greater than 140 years. see http://www.env.gov.bc.ca/wld/documents/uwr/uwr_u7_015.pdf

u7015<-cond_harv_uwr %>% 
  dplyr::select(ogc_fid, land_designation_name, geom) %>%
  filter(land_designation_name=='u-7-015')

u7015_table<-data.table(u7015)[,c("ogc_fid")]

#SPC-009 - Primary forestry activites will all for 33% of area less than 3 meters
u7015_table[, `:=`(reference_zone = 'test.zone_uwr', variable = 'age', type = 'ge', percentage = 50, threshold = 140, ndt =0, label = 'u-7-015', multi_condition=NA, denom=NA, start=0, stop=250)]

setnames(u7015_table, "ogc_fid", "zoneid")

df<-rbind(df, u7015_table)


# Not lets do it for u-7-007
u7007<-cond_harv_uwr2 %>%
  dplyr::select(ogc_fid, land_designation_name, geom) %>%
  filter(land_designation_name=='u-7-007')

#This UWR has three main General Wildlife Measures: Prevent displacement of caribou, reduce predator effectiveness and maintain forage biomass. see http://www.env.gov.bc.ca/wld/documents/uwr/uwr_u7_007.pdf

#Terrestrial lichen habitat are generally found in pine dominated forests with site index less than 14.5. We equate this to having at least 50 percent of this landbase greater than 70 years for the entire area

# change the uwr to one unit (the min of the ogc_fid)
zoneid_new2<-min(u7007$ogc_fid) #177829
cond_harv_uwr[cond_harv_uwr$land_designation_name == 'u-7-007',]$ogc_fid<-zoneid_new2

u7007_table<-data.table(zoneid =zoneid_new2, reference_zone ='test.zone_uwr', variable ='age', type = 'ge', percentage =50 , threshold = 70, ndt = 0, label = 'u-7-007',multi_condition=NA, denom=NA, start=0, stop=250)

df<-rbind(df, u7007_table)

# even thought there are more land constraints we will stop at this for our example
cond_harv_uwr<-st_as_sf(cond_harv_uwr) %>% filter(ogc_fid %in% (df$zoneid))

uwr.ras<-fasterize::fasterize(sf= cond_harv_uwr, raster = prov.rast , field = "ogc_fid")
uwr.ras[nh.ras[] == 0 ] <- 0
writeRaster(uwr.ras, file="C:\\Castor\\castor\\uwr.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 C:\\Castor\\castor\\uwr.tif -t 100x100 test.zone_uwr_rast | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

df$ndt<-as.integer(0)
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$multi_condition <- as.character ('')


conn <- dbConnect(
  Postgres(),
  host     = keyring::key_get('dbhost',  keyring = 'postgreSQL'),
  dbname   = keyring::key_get('dbname',  keyring = 'postgreSQL'),
  port     = 5432,
  user     = keyring::key_get('dbuser',  keyring = 'postgreSQL'),
  password = keyring::key_get('dbpass',  keyring = 'postgreSQL')
)


DBI::dbWriteTable(conn, DBI::Id(schema = "test", table = "cond_harv_uwr"), value = df, row.names = FALSE, overwrite = TRUE)

dbExecute(conn,"UPDATE test.cond_harv_uwr SET denom = NULL WHERE denom IS NOT NULL;")

#----------------------------
#Inheritability in PostgreSQL
#----------------------------


dbExecute(conn, "CREATE TABLE IF NOT EXISTS test.zone_constraints (zoneid integer, reference_zone text, ndt integer, variable text, threshold double precision, type text, percentage double precision, multi_condition text, denom character varying, start integer, stop integer, label text )")

dbExecute(conn, "ALTER TABLE test.cond_harv_uwr ALTER COLUMN denom SET DATA TYPE character varying;")
dbExecute(conn, "ALTER TABLE test.zone_nharv ALTER COLUMN denom SET DATA TYPE character varying;")
dbExecute(conn, "ALTER TABLE test.zone_nharv ALTER COLUMN multi_condition SET DATA TYPE text;")
dbExecute(conn, "ALTER TABLE test.zone_nharv ALTER COLUMN start SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE test.zone_nharv ALTER COLUMN stop SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE test.cond_harv_uwr ALTER COLUMN start SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE test.cond_harv_uwr ALTER COLUMN stop SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE test.zone_nharv INHERIT test.zone_constraints")
dbExecute(conn, "ALTER TABLE test.cond_harv_uwr INHERIT test.zone_constraints")

```

## Biodiversity Emphasis Options - Zonal Constraints

Biodiversity Emphasis Options (BEO) are defined during landscape level planning, typically an a landscape unit or on BEC zones (natural disturbance types) within a landscape unit. If no landscape unit has been designated for an area, or an emphasis option has not been assigned for a particular landscape unit, the default is that the area is managed using the lower biodiversity emphasis option. see [Biodiversity Guidebook](https://www.for.gov.bc.ca/ftp/hfp/external/!publish/FPC%20archive/old%20web%20site%20contents/fpc/fpcguide/BIODIV/chap1.htm#bid)

#### Get data  

Download the data from here: https://catalogue.data.gov.bc.ca/dataset/landscape-units-of-british-columbia-current
```{r zoneStep1, echo=FALSE}
bbox <- st_bbox(study_area_sf)
# Convert bbox to WKT polygon
bbox_wkt <- st_as_text(st_as_sfc(bbox))

# ─────────────────────────────────────────────
# 2. Read VRI clipped to bbox (FAST)
# ─────────────────────────────────────────────

lu<-st_read(
  dsn = paste0(data.dir,"\\RMP_LANDSCAPE_UNIT_SVW\\RMP_LU_SVW_polygon.shp"),
  wkt_filter = bbox_wkt
)

lu<-lu %>% dplyr::rename(lu_id=LU_ID,
                  lu_name=LU_NAME,
                  beo=BEO,
                  #rt_dt=RT_DT,
                  gis_ch_dt=GIS_CH_DT,
                  wkb_geometry=geometry) %>%
  dplyr::select(lu_id, lu_name, beo, gis_ch_dt, wkb_geometry)

lu.dt<-data.table(lu)
lu.dt<-lu.dt[beo=="High", beo:=1][beo=="Intermediate", beo:=2][beo=="Low", beo:=3]
lu.dt$beo<-as.numeric(lu.dt$beo)
lu.dt[is.na(beo), beo:=3]
lu.dt<-st_as_sf(lu.dt)


#Rasterize the bidodiversity emphasis options
beo.ras<-fasterize::fasterize(sf= lu.dt, raster = prov.rast , field = "beo")
luid.ras<-fasterize::fasterize(sf= lu.dt, raster = prov.rast , field = "lu_id")

library(terra)
plot(beo.ras)
plot(luid.ras)

#Get the natural disturbance types
library(bcdata)
ndt <- bcdc_query_geodata("WHSE_FOREST_VEGETATION.BEC_BIOGEOCLIMATIC_POLY") %>%
  collect()

ndt_crop <- st_crop(ndt, st_bbox(study_area_sf))
  
ndt_crop<-data.table(ndt_crop)
ndt_crop[NATURAL_DISTURBANCE=="NDT2",ndt:=2]
ndt_crop[NATURAL_DISTURBANCE=="NDT3",ndt:=3]
ndt_crop[NATURAL_DISTURBANCE=="NDT5",ndt:=5]

ndt_crop[ZONE == 'BWBS', zone:=1]
ndt_crop[ZONE == 'ESSF', zone:=4]
ndt_crop[ZONE == 'SBS', zone:=11]

ndt_crop<-st_as_sf(ndt_crop)

#Rasterize the NDT
ndt.ras<-fasterize::fasterize(sf= ndt_crop, raster = prov.rast , field = "ndt")
#Rasterize the BEC zone (key for BEC zones)
bec.ras<-fasterize::fasterize(sf= ndt_crop, raster = prov.rast , field = "zone")

rm(lu,ndt_crop, ndt) # free some memory
gc()# Clean up

#Make a stack raster with all the information needed for BEO contraints
ogm<-stack(bec.ras, ndt.ras, luid.ras, beo.ras)
names(ogm)<-c("BEC", "NDT", "LU_ID", "BEO")
raster::plot(ogm) #plot the stack
```

#### Make unique zones within Landscape Units

```{r zoneStep2, echo=FALSE}

#------------------------------------
#Biodiversity Emphasis Options on Age
#------------------------------------
ogm.table<-data.table(as.data.frame(ogm)) #ogn is the stacked raster of the BEO
ogm.table[, id := seq_len(.N)]#assign a unique id for each pixel

rm(ogm, bec.ras, beo.ras, ndt.ras, luid.ras) #clear up some memory
gc() # clean up

#concactenate and join in old growth percentage
print(head(ogm.table))
ogm.table[, ogm := paste0(BEC, '_', NDT, '_', BEO)]
#print(ogm.table[!is.na(BEC)])#CHECK

#Create oldgrowth look up table. Note for ndt 3 in the BWBS there is a further difference between conifer and deciduous. I omitted this level of precision and used the most conservative one -- the conifer percentage . This adds an extra 2-3 percent!!! see Table 3 in https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf

NDT1<-data.table(BEC = c("CWH", "CWH", "CWH", 
                         "ICH", "ICH", "ICH",
                         "ESSF","ESSF","ESSF",
                         "MH",  "MH",  "MH"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          28, 19, 19,
                          28, 19, 19), AGE = 250, NDT = 1, BEO = 1:3)

NDT2<-data.table(BEC = c("CWH", "CWH", "CWH",
                         "CDF", "CDF", "CDF", 
                         "ICH", "ICH", "ICH",
                         "SBS", "SBS", "SBS",
                         "ESSF","ESSF","ESSF",
                         "SWB", "SWB", "SWB"),
                 p_OGR= c(13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9), AGE = 250, NDT = 2, BEO = 1:3)

NDT3<-data.table(BEC = c("BWBS","BWBS","BWBS", 
                         "SBPS","SBPS","SBPS",
                         "SBS", "SBS", "SBS",
                         "MS",  "MS",  "MS",
                         "ESSF","ESSF","ESSF",
                         "ICH", "ICH", "ICH",
                         "CWH", "CWH", "CWH"),
                 p_OGR= c(19, 13, 13,
                          10, 7, 7,
                          16, 11, 11,
                          21, 14, 14,
                          21, 14, 14,
                          21, 14, 14,
                          16, 11, 11), 
                 AGE = c(100, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140), NDT = 3, BEO = 1:3)

NDT4<-data.table(BEC = c("ICH", "ICH", "ICH",
                         "IDF", "IDF", "IDF",
                         "PP",  "PP",  "PP"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          19, 13, 13), AGE = 250, NDT = 4, BEO = 1:3)

p_OGR<-rbind(NDT1, NDT2, NDT3, NDT4) #this is the lookup for geting the percentage of old growth required for retention by bec and ndt

#Create a value attribute table which assigns an integer key called BEC2 to each BEC zone
vat<-data.table(BEC  = 
                c('BWBS', 'CDF', 'CWH', 'ESSF', 'ICH', 'IDF', 'MH', 'MS', 'PP','SBPS', 'SBS', 'SWB'),
                BEC2 = 1:12)

p_OGR<-merge(x=p_OGR, y=vat, by.x= "BEC", by.y= "BEC") # join vat and p_OGR to get BEC2 key
p_OGR[, ogm := paste0(BEC2, '_', NDT, '_', BEO)] # concatenate to get a unique constraint

p_OGR<-p_OGR[, c(2:3,7)] #Keep only the unique constraint, the p_OGR and age threshold

setkey(ogm.table, ogm) # assign a data.table key thats the unique constraint for joining
setkey(p_OGR, ogm)# assign a data.table key thats the unique constraint for joining

ogm.final<-merge(x=p_OGR, y=ogm.table, by="ogm", all.y=TRUE) # merge the constraint with each spatial landscape unit

gc() # clean up

ogm.final[, zone := .GRP, by=.(LU_ID,BEC,NDT)] #Creates a unique id for each zone grouped by Lu_ID, BEC and NDT
#remove zones that are ndt5 or other wise do not have a ogr, age
print(head(ogm.final[is.na(AGE),]))
ogm.final[is.na(AGE), zone:=NA]
out<-data.frame(ogm.final[order(id)])
gc()
zone.ras<-prov.rast
zone.ras[]<-out[,9] #assign the zone to each pixel


writeRaster(zone.ras, file=paste0(data.dir,"\\zone_beo.tif"), format="GTiff", overwrite=TRUE)#print the raster
rm(zone.ras, out)

# Upload to postgres database
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', data.dir, '\\zone_beo.tif -t 100x100 test.zone_cond_beo |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = FALSE)

library(RPostgreSQL)
ogm.final[zone == 2435,]
zone_beo_table<-setDT(ogm.final)[, .SD[which.max(AGE)], by=zone]

zone_beo_table<-zone_beo_table[,c(1,3:4, 6)]
zone_beo_table[, reference_zone := 'rast.zone_cond_beo']
zone_beo_table[, variable := 'age']
zone_beo_table[, type := 'ge']

setnames(zone_beo_table, c("zoneid", "percentage", 
                  "threshold","ndt", "reference_zone", 
                  "variable", "type"))
zone_beo_table[, ndt := as.integer(ndt)]
df<-as.data.frame(zone_beo_table)
df$label<-'beo' #TODO: label this is as high/I/L ?
df$multi_condition<-NA 
df$denom<-NA 
df$start <- 0
df$stop <- 250

#Upload the constraint table to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("test", "zone_beo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(zone_beo_table, df, ogm.final)
gc()

conn <- dbConnect(
  Postgres(),
  host     = keyring::key_get('dbhost',  keyring = 'postgreSQL'),
  dbname   = keyring::key_get('dbname',  keyring = 'postgreSQL'),
  port     = 5432,
  user     = keyring::key_get('dbuser',  keyring = 'postgreSQL'),
  password = keyring::key_get('dbpass',  keyring = 'postgreSQL')
)
dbExecute(conn, "ALTER TABLE test.zone_beo ALTER COLUMN multi_condition SET DATA TYPE text;")
dbExecute(conn, "ALTER TABLE test.zone_beo ALTER COLUMN denom SET DATA TYPE character varying;")
dbExecute(conn, "ALTER TABLE test.zone_beo ALTER COLUMN start SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE test.zone_beo ALTER COLUMN stop SET DATA TYPE integer;")
dbExecute(conn, "ALTER TABLE test.zone_beo ALTER COLUMN label SET DATA TYPE text;")
dbExecute(conn, "ALTER TABLE test.zone_beo INHERIT test.zone_constraints")

```


## 6. Get growth and yield information

At its simplest castor models forest growth through the use of two rasters. For each pixel the rasters provide  to indicate the current and future state of the forest and through look up tables that indicate 

Read in the growth and yield data and upload it to postgreSQL
```{r}
yields_current<-read.csv(here::here("data/yields.current.csv"))
yields_future<-read.csv(here::here("data/yields.future.csv"))
rast_ycid_future<-rast(here::here("data/rast_ycid_future.tif"))
rast_ycid_current<-rast(here::here("data/rast_ycid_current.tif"))

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("test", "yields_current"), value= yields_current, row.names = FALSE, overwrite = TRUE) 
DBI::dbWriteTable(conn, c("test", "yields_future"), value= yields_future, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

prov <- rast(prov.rast)
rast_ycid_current_full <- extend(rast_ycid_current, prov)
rast_ycid_future_full <- extend(rast_ycid_future, prov)

writeRaster(rast_ycid_current_full, file=here::here("data\\rast_ycid_current_full.tif"), overwrite=TRUE)#print the raster
writeRaster(rast_ycid_future_full, file=here::here("data\\rast_ycid_future_full.tif"), overwrite=TRUE)#print the raster


system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M  C:\\Castor\\castor\\data\\rast_ycid_current_full.tif -t 100x100 test.rast_ycid_current | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M  C:\\Castor\\castor\\data\\rast_ycid_future_full.tif -t 100x100 test.rast_ycid_future | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```

##  7. Get historical cutblock information

Here we will download the consolidated cutblocks layer from the BC Geographic warehouse. It combines forest harvesting data from various datasets (i.e . Reporting Silviculture Updates and Land Status Tracking System (RESULTS), Forest Cover Inventory (VRI) and satellite imagery change detection). These consolidated datasets show historical cutblocks on the landscape and their associated harvest dates. This dataset is required by blockingCastor

```{r, cutblocks}
cns_cutblock <- bcdc_query_geodata("WHSE_FOREST_VEGETATION.VEG_CONSOLIDATED_CUT_BLOCKS_SP") %>%
    collect()

cns_cutblock <- st_intersection(cns_cutblock, study_area_sf)


#Harvest locations year
cns_cutblock2 <- cns_cutblock %>%
  dplyr::filter(AREA_HA >= 0.5) %>%
  dplyr::select(HARVEST_MID_YEAR_CALENDAR,OBJECTID, geometry) %>%
  dplyr::arrange(HARVEST_MID_YEAR_CALENDAR, OBJECTID) %>%
  mutate(objectid = row_number())
  
layer.ras <-fasterize::fasterize(sf= cns_cutblock2, raster = prov.rast , field = "objectid")
layer.ras[is.na(layer.ras[])]<-0
terra::writeRaster (layer.ras, file = paste0(data.dir, "\\cns_cutblk_2026.tif"), overwrite = TRUE)

system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648 ', data.dir, '\\cns_cutblk_2026.tif -t 100x100 test.cns_cutblk_2026 | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/',keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```

## 8. Get roads data

Get roads data. In this example Ill use the BC Cumulative Effects Framework - Integrated Roads - 2026 (https://catalogue.data.gov.bc.ca/dataset/bc-cumulative-effects-framework-integrated-roads-current/resource/4b2aa2a5-8cfd-4410-a0af-d7f257b4131c) but any data can be used. 

Roads are first classified into permanent and non‑permanent types and then buffered by 51 m prior to rasterization.
This buffering step ensures that linear road features adequately intersect the 100 m raster grid. Without buffering, narrow road lines may fall between raster cell centers and be omitted during rasterization, leading to incomplete road representation.

```{r roads}

# get roads data
roads <- st_read(paste0(data.dir,"\\BC_CE_Integrated_Roads_2026.gdb")) %>%
  st_transform(3005)

roads$road_class <- NA_integer_

roads_small <- st_intersection(roads, study_area_sf)

# Permanent roads
roads_small$road_class[
  roads_small$DRA_ROAD_SURFACE == "paved" |
  (!is.na(roads_small$DRA_ROAD_NAME_FULL) & roads_small$DRA_ROAD_CLASS != "Trail")
] <- -2

# Non-permanent roads
roads_small$road_class[is.na(roads_small$road_class)] <- -1

# buffer roads
roads_buf <- st_buffer(roads_small, dist = 51)

road_class_rast <- fasterize(
  st_cast(roads_buf, "MULTIPOLYGON"),
  prov.rast,
  field = "road_class"
)

road_binary <- road_class_rast
road_binary[] <- NA                # start with everything NA
road_binary[road_class_rast < 0] <- 0
road_binary[road_class_rast < 0] <- 1

plot(road_binary, main = "Binary Roads (Simple Option)")

writeRaster (road_binary, paste0(data.dir, "\\road_binary.tif", overwrite = T))

system ("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', data.dir, '\\road_binary.tif -t 100x100 test.rast_roads_binary | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/', keyring::key_get('dbname', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)

```




