---
title: "FLEX2"
author: ""
date: "26 October 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'
```

## Overview
This is an agent based model (ABM) to simulate fisher life history on a landscape. This version is written to input habitat data that was written as a raster output from the fisherHabitatLoader module. The fisherHabitatLoader saves rasters of the occurrence of fisher habitat types (denning, rust, cavity, resting and movement) at each interval of a forestry simulation using forestryCastor. The forestryCastor module is a simulation model that returns a single solution for a set of parameters (i.e., it's a deterministic model). Thus fisherHabitatLoader updates fisher habitat conditions over a simulation period. This approach  allows for faster simulation of multiple iterations of a fisher population on a landscape. as it can read the habitat conditions as predetermined by the simulation model. I is more efficient to run the fisher ABM as a *post-hoc* analysis, rather than concurrently with forestryCastor.


### Usage
Run the model below
```{r module_usage}
library (data.table)
library (terra)
library (keyring)
library (tidyverse)
library (here)
library (stringr)
library (truncnorm)
library (RANN)
library(sampling)
library(BalancedSampling)
library(ggplot2)
library(DBI)
moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
paths <- list(
  modulePath = paste0(here::here(),"/R/SpaDES-modules"),
  outputPath = paste0(here::here(),"/R/scenarios/test_flex2/outputs")
)

times <- list (start = 0, end = 3)

parameters <- list(FLEX = list (female_max_age = 9,
                                 reproductive_age = 2, 
                                 sex_ratio = 0.5,
                                 female_dispersal = 785000,  # ha; radius = 500 pixels = 50km = 7850km2 area
                                 timeInterval = 5, # should be consistent with the time interval used to model habitat
                                                    # e.g., growingstockLCUS periodLength
                                # rasterHabitat = paste0 (here::here(), "/R/SpaDES-modules/FLEX/williston.tif")
                                rasterHabitat = paste0 (here::here(), "/R/SpaDES-modules/FLEX/lakes.tif")

                )
)

modules <- list ("FLEX")
#female_hr_table <- data.table (fisher_pop = c (1:4),  hr_mean = c (1500, 1500, 2100, 1500),hr_sd = c (500, 500, 500, 500))
survival_rate_table<-rbindlist(list(
      data.table (fisher_pop = c (1,1,1,1,2,2,2,2,30,30,30,30,3,3,3,3),
                  type = "Established",
                  cohort = c ("Adult", "Juvenile", "Senior", "Old", "Adult", "Juvenile", "Senior", "Old", "Adult", "Juvenile", "Senior", "Old", "Adult", "Juvenile", "Senior", "Old"),
                  Mean = c (0.9, 0.6, 0.9, 0.2,  0.9, 0.6, 0.9, 0.2, 0.9, 0.6, 0.9, 0.2, 0.9, 0.6, 0.9,0.2),
                  SD = c (0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1, 0.2,0.1,0.1,0.1,0.1,0.1,0.1)), 
      data.table (fisher_pop = c (1,1,1,1,2,2,2,2,30,30,30,30,3,3,3,3),
                  type = "Disperser",
                  cohort = c ("Adult", "Juvenile", "Senior", "Old", "Adult", "Juvenile", "Senior", "Old", "Adult", "Juvenile", "Senior", "Old", "Adult", "Juvenile", "Senior", "Old"),
                  Mean = c (0.8, 0.6, 0.8, 0.2,  0.8, 0.6, 0.8, 0.2, 0.8, 0.6, 0.8, 0.2, 0.8, 0.6, 0.8, 0.2),
                  SD = c (0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1, 0.1,0.1,0.1,0.1,0.1,0.1,0.1))
                                ))
mySim <- SpaDES.core::simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = list(scenario = data.table(name = "test"),survival_rate_table=survival_rate_table),
                 paths = paths)

SpaDES.core::outputs(mySim) <- data.frame (objectName = c("fisherABMReport"))
mySimOut <- SpaDES.core::spades(mySim)
#experiment(mySim, replicates = 2)
```

#Plot
```{r}
rast.stk<- rast(paste0 (here::here(), "/R/SpaDES-modules/fisherHabitatCastor/scen1c_static_high.tif"))
plot(rast.stk["ras_fisher_movement_init"])
plot(rast.stk["ras_fisher_movement_5"])
plot(rast.stk["ras_fisher_movement_10"])
plot(rast.stk["ras_fisher_movement_15"])
plot(rast.stk["ras_fisher_movement_20"])
plot(rast.stk["ras_fisher_denning_init"])
plot(rast.stk["ras_fisher_denning_5"])
plot(rast.stk["ras_fisher_denning_10"])
plot(rast.stk["ras_fisher_denning_15"])
plot(rast.stk["ras_fisher_denning_20"])

dir_reps<-data.table(dir(paste0(here::here(),"/R/scenarios/test_flex2/outputs/static_high/columbia/")))[V1 %like% "rep",]
abmReport<-rbindlist(lapply(dir_reps$V1, function(x) {
  readRDS(paste0(here::here(),"/R/scenarios/test_flex2/outputs/static_high/columbia/",x,"/fisherABMReport_year4.rds"))}))

ggplot(data = abmReport, aes(x=timeperiod,y=n_f_adult)) +
   stat_binhex() +
  geom_smooth()
#writeRaster(terr.ras, "test_terr2.tif", overwrite = T)

ggplot(data = abmReport, aes(x=timeperiod,y=n_f_adult, group = timeperiod)) +
  geom_boxplot()
```