---
title: "Delivered Wood Costs"
author: "Tyler Muhly"
date: '2023-05-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (DBI)
library (data.table)
library (terra)
library (dplyr)
library (rpostgis)
library (gstat)
library (here)
library (keyring)
library (stars)
library (automap)
source (here::here("R/functions/R_Postgres.R"))

prov.rast.stars <- st_as_stars (raster::raster (nrows = 15744, ncols = 17216, 
                                                xmn = 159587.5, xmx = 1881187.5, 
                                                ymn = 173787.5, ymx = 1748187.5, 
                                                crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", 
                                                resolution = c (100, 100), vals = 0)) # needs to be a 'stars' object for gstat
### GET DATA
conn <- DBI::dbConnect (RPostgreSQL::PostgreSQL(), 
                        host=keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                        dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                        port='5432',
                        user = keyring::key_get('dbuser', keyring = 'postgreSQL'),
                        password = keyring::key_get('dbpass', keyring = 'postgreSQL'))
# ecas points
  ## single points in terra spatvector format
point.ecas <- terra::vect (st_cast (getSpatialQuery ("SELECT * from public.ecas_cycle_time_harvest_system_points;"), "POINT"))
  
# distance to permanent road raster
  ## created in QGIS because of processing speed
  ## source data is cumulative effects 2021
dist.rd <- terra::rast ("D:\\clus_data\\roads\\dist_perm_road_2021.tif")

# elevation
rast.dem <- terra::rast ("D:\\clus_data\\dem\\dem_db.tif")


### Extract data at ECAS points
# distance to permanent road 
point.ecas.d.road <- terra::extract (dist.rd, point.ecas)
point.ecas$dist_road <- point.ecas.d.road [, -1]
# elevation
point.ecas.dem <- terra::extract (rast.dem, point.ecas)
point.ecas$elev <- point.ecas.dem [, -1]

### Convert to sf obkect for use in gstat pacakge
point.ecas.sf <- sf::st_as_sf (point.ecas)
rm (dist.rd, point.ecas.d.road, point.ecas.dem, point.ecas, rast.dem)
gc ()
```

## Introduction

- forest harvest pattern in interior B.C. is largely driven by costs of cutting and hauling timber

- understanding these costs will help us better spatially model near-term timber harvest patterns 

- useful for assessing short-term implications of proposed reserve areas to timber supply, i.e., reserves in low costs areas may have larger impacts on short-term timber supply than reserves in high cost areas 

- here I develop approach to creating a delivered wood costs model

- costs are largely driven by the time it takes to haul timber from a harvest block to a milling facility (i.e., cycle time) and the harvesting system (e.g., whether timber can be moved to a landing by cable or skidder), which is largely driven by terrain (i.e., steep slopes)

- there is not necessarily a need to produce an actual delivered wood cost; many factors will change over time (e.g., costs of fuel) 

- instead the approach here is to develop a model of the fundamental aspects that go into determinign costs, and these are haul distance and terrain



## Methods

- relative delivered cost (dc) is a function of cycle time (ct) and harvest system (hs)
  dc = B0 + B1ct + B2hs

- ct is spaitla interpolation
  - multiple mill destiantions, o hard to fit a model of cost, will vary depedngin on mill that wood is going to, which depends on forest type, mill size, etc. that we don't necessarily have info on
  - oso intead we assuem future cyle team is reflective of hisotric cycle time, whcih may not be true, but a mroe complex moel requires udnersatding of where timber will lfow 

- hs is a fucntion fo slope
  hs = B0 + B1slope
  
- in sum, costs is ultimately a function of slope and cycle time

### Haul Distance
- cycle tiem model
- compare:
  - inverse distance weighted
  - ordinary kriging (no covariates)
  - universal kriging (distance to road covaraiate)
  
- compared predictive accuracy with leave-some-out 
  - remove 20% of data five times and fit model with 80% off data
  - see how well model predicts actual cycle time at withehdl points


```{r cycle time interpolation, echo = F, message = F, eval = T, include = F}

# memory issues...
# needs to be sub-divided areas for prediction (the province is too big)
tsa.williams.lake <- getSpatialQuery (paste0 ("SELECT * FROM tsa_aac_bounds where tsa_name in ('Williams_Lake_TSA')"))
tsa.gold <- getSpatialQuery (paste0 ("SELECT * FROM tsa_aac_bounds where tsa_name in ('Golden_TSA')"))
tsa.morice <- getSpatialQuery (paste0 ("SELECT * FROM tsa_aac_bounds where tsa_name in ('Morice_TSA')"))
tsa.cran <- getSpatialQuery (paste0 ("SELECT * FROM tsa_aac_bounds where tsa_name in ('Cranbrook_TSA')"))

prov.rast.rast <- as (prov.rast.stars, "Raster")
tsa.wl.rast <- crop (prov.rast.rast, tsa.williams.lake)
tsa.gold.rast <- crop (prov.rast.rast, tsa.gold)
tsa.morice.rast <- crop (prov.rast.rast, tsa.morice)
tsa.cran.rast <- crop (prov.rast.rast, tsa.cran)

rm (prov.rast.rast, tsa.williams.lake, tsa.gold, tsa.morice, tsa.cran)
gc ()

#### Inverse-distance weighted
mod.idw <- gstat (formula = p_cyc_time ~ 1, data = point.ecas.sf) # run model

# predictive surface
pred.idw.tsa.wl <- predict (mod.idw, st_as_stars (tsa.wl.rast))
pred.idw.tsa.gold <- predict (mod.idw, st_as_stars (tsa.gold.rast))
pred.idw.tsa.morice <- predict (mod.idw, st_as_stars (tsa.morice.rast))
pred.idw.tsa.cran <- predict (mod.idw, st_as_stars (tsa.cran.rast))

## to plot...
# preds.idw <- pred.idw.tsa.wl ["var1.pred",,]
# names (preds.idw) <- "idw_pred"
# 
# b <- seq (0, 12, 1)
# plot (preds.idw, breaks = b, col = hcl.colors(length(b)-1, "Spectral"), reset = FALSE)
# plot (st_geometry (point.ecas.sf), pch = 3, add = TRUE)
# contour (preds.idw, breaks = b, add = TRUE)

# save predictions as raster
write_stars (pred.idw.tsa.wl, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\idw_williams_lake.tif", layer = 1)
write_stars (pred.idw.tsa.gold, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\idw_golden.tif", layer = 1)
write_stars (pred.idw.tsa.morice, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\idw_morice.tif", layer = 1)
write_stars (pred.idw.tsa.cran, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\idw_cranbrook.tif", layer = 1)
rm (pred.idw.tsa.wl, pred.idw.tsa.gold, pred.idw.tsa.morice, pred.idw.tsa.cran)
gc () 



#### Ordinary Kriging
var.ord.krig <- variogram (p_cyc_time ~ 1, point.ecas.sf)
plot (var.ord.krig)

# fir variogram model; convert sf to sp object for use in this function
mod.var.ord.krig <- automap::autofitVariogram (p_cyc_time ~ 1, as (point.ecas.sf, "Spatial"))
plot (mod.var.ord.krig)

mod.ok <- gstat (formula = p_cyc_time ~ 1, model = mod.var.ord.krig$var_model, data = point.ecas.sf)

# predictive surface
pred.ok.tsa.wl <- predict (mod.ok, st_as_stars (tsa.wl.rast))









pred.ok.tsa.gold <- predict (mod.ok, st_as_stars (tsa.gold.rast))
pred.ok.tsa.morice <- predict (mod.ok, st_as_stars (tsa.morice.rast))
pred.ok.tsa.cran <- predict (mod.ok, st_as_stars (tsa.cran.rast))



write_stars (pred.ok.tsa.wl, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_williams_lake.tif", layer = 1)
write_stars (pred.ok.tsa.gold, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_golden.tif", layer = 1)
write_stars (pred.ok.tsa.morice, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_morice.tif", layer = 1)
write_stars (pred.ok.tsa.cran, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_cranbrook.tif", layer = 1)
rm (pred.ok.tsa.wl, pred.ok.tsa.gold, pred.ok.tsa.morice, pred.ok.tsa.cran)
gc () 








#### Universal Kriging
var.ord.krig <- variogram (p_cyc_time ~ dist , point.ecas.sf)
plot (var.ord.krig)

# fir variogram model; convert sf to sp object for use in this function
mod.var.ord.krig <- automap::autofitVariogram (p_cyc_time ~ 1, as (point.ecas.sf, "Spatial"))
plot (mod.var.ord.krig)

mod.ok <- gstat (formula = p_cyc_time ~ 1, model = mod.var.ord.krig$var_model, data = point.ecas.sf)

# predictive surface
pred.ok.tsa.wl <- predict (mod.ok, st_as_stars (tsa.wl.rast))


pred.ok.tsa.gold <- predict (mod.ok, st_as_stars (tsa.gold.rast))
pred.ok.tsa.morice <- predict (mod.ok, st_as_stars (tsa.morice.rast))
pred.ok.tsa.cran <- predict (mod.ok, st_as_stars (tsa.cran.rast))



write_stars (pred.ok.tsa.wl, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_williams_lake.tif", layer = 1)
write_stars (pred.ok.tsa.gold, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_golden.tif", layer = 1)
write_stars (pred.ok.tsa.morice, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_morice.tif", layer = 1)
write_stars (pred.ok.tsa.cran, dsn = "D:\\clus_data\\dlvd_wood_cost\\output\\ok_cranbrook.tif", layer = 1)
rm (pred.ok.tsa.wl, pred.ok.tsa.gold, pred.ok.tsa.morice, pred.ok.tsa.cran)
gc ()


```


### Harvest Type
- terrain model

