---
title: "Business-as-usual Simulation for Central Group Caribou Recovery Planning"
author: ""
date: "21 July 2022"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

## Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

## Central Group Scenarios
Here we use forestryCLUS to assess the potential impact of a hypothetical land use orders and deferral areas on timber supply within the area-of-interest for central group cariobu (east-central B.C.).

Here we simulate the 'business-as-usual' (BAU) scenario, where we only apply existing legal constraints, caribou or otherwise, including the partnership agreement zones. This scenario is used to establish the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat.

We identify the non-declining maximum annual harvest volume that can be achieved as the baseline level of forestry that could occur in the region, given existing legal constraints. 

## Model Paramters
### BAU Zones 
zone_cond_beo = biodiversity emphasis options 
zone_cond_vqo = visual quality objectives
zone_wha_2021 = wildlife habitat areas
zone_uwr_2021 =  ungulate winter ranges
zone_cond_fsw = fisheries sensitive watersheds
zone_cond_nharv = parks and protected areas
zone_cond_cw = community watersheds
central_grp_partner_areas_072022 = Partnership Agreement areas, where no harvest is permitted in A2, B2, B3 and B4 zones; A1, B1, B5 max 10% <40 years old
central_group_chra_032023 = No harvest

```{r, update chra zone constraints}
require (DBI)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))
castordb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/central_group/inputs/central_group_tsu_march2023_castordb_chra_modified.sqlite"))

check <- dbGetQuery (castordb, "SELECT * from zoneconstraints WHERE reference_zone = 'rast.central_group_chra_032023'") # rast.central_group_chra_032023
dbExecute (castordb, "UPDATE zoneconstraints SET type = 'nh' WHERE reference_zone = 'rast.central_group_chra_032023'") 
dbExecute (castordb, "UPDATE zoneconstraints SET stop = 80 WHERE reference_zone = 'rast.central_group_chra_032023'") 

dbExecute(castordb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(1872,5,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,240,81,250),
(1873,6,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,459,81,250),
(1874,7,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3716,81,250),
(1875,8,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,814,81,250),
(1876,9,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3399,81,250),
(1877,10,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2116,81,250),
(1878,13,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1118,81,250),
(1879,14,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1066,81,250),
(1880,15,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2289,81,250),
(1881,16,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,913,81,250),
(1882,17,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1007,81,250),
(1883,19,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,10,81,250),
(1884,20,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,479,81,250),
(1885,21,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1586,81,250),
(1886,22,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,518,81,250),
(1887,23,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,636,81,250),
(1888,24,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,143,81,250),
(1889,25,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3498,81,250),
(1890,26,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,342,81,250),
(1891,27,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,190,81,250),
(1892,28,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,812,81,250),
(1893,29,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,580,81,250),
(1894,30,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1601,81,250),
(1895,31,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5879,81,250),
(1896,32,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,373,81,250),
(1897,33,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,17701,81,250),
(1898,34,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,880,81,250),
(1899,35,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,812,81,250),
(1900,36,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2700,81,250),
(1901,37,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,15571,81,250),
(1902,38,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4373,81,250),
(1903,39,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,770,81,250),
(1904,40,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2182,81,250),
(1905,41,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2546,81,250),
(1906,42,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1481,81,250),
(1907,43,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5222,81,250),
(1908,44,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,158,81,250),
(1909,45,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,644,81,250),
(1910,46,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4542,81,250),
(1911,47,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1600,81,250),
(1912,48,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,477,81,250),
(1913,49,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1224,81,250),
(1914,50,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4776,81,250),
(1915,51,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3893,81,250),
(1916,52,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,17114,81,250),
(1917,53,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4937,81,250),
(1918,54,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,819,81,250),
(1919,55,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2073,81,250),
(1920,56,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,271,81,250),
(1921,57,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1996,81,250),
(1922,58,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,893,81,250),
(1923,59,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,73,81,250),
(1924,60,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,353,81,250),
(1925,61,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,522,81,250),
(1926,62,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1496,81,250),
(1927,63,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1638,81,250),
(1928,64,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,639,81,250),
(1929,65,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,156,81,250),
(1930,66,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,539,81,250),
(1931,67,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,482,81,250),
(1932,68,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4474,81,250),
(1933,69,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,6118,81,250),
(1934,70,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2,81,250),
(1935,71,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,109,81,250),
(1936,72,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,480,81,250),
(1937,73,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,8577,81,250),
(1938,74,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,218,81,250),
(1939,75,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,42,81,250),
(1940,76,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,9233,81,250),
(1941,77,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,9183,81,250),
(1942,78,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1378,81,250),
(1943,79,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,911,81,250),
(1944,80,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1233,81,250),
(1945,81,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,75,81,250),
(1946,82,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,790,81,250),
(1947,83,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,21530,81,250),
(1948,84,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4463,81,250),
(1949,85,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,21809,81,250),
(1950,86,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,93,81,250),
(1951,87,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,6308,81,250),
(1952,88,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2779,81,250),
(1953,89,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1012,81,250),
(1954,90,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,313,81,250),
(1955,91,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,684,81,250),
(1956,92,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,73,81,250),
(1957,93,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2291,81,250),
(1958,94,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,323,81,250),
(1959,95,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,793,81,250),
(1960,96,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,395,81,250),
(1961,97,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,713,81,250),
(1962,98,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1196,81,250),
(1963,99,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,67,81,250),
(1964,100,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,510,81,250),
(1965,101,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,16812,81,250),
(1966,102,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2936,81,250),
(1967,103,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1074,81,250),
(1968,104,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3516,81,250),
(1969,105,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,6906,81,250),
(1970,106,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,194,81,250),
(1971,107,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,974,81,250),
(1972,108,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,7526,81,250),
(1973,109,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3208,81,250),
(1974,110,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,9,81,250),
(1975,111,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4355,81,250),
(1976,112,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,550,81,250),
(1977,113,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,91,81,250),
(1978,114,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,343,81,250),
(1979,115,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3093,81,250),
(1980,116,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2157,81,250),
(1981,117,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3676,81,250),
(1982,118,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,8378,81,250),
(1983,119,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,779,81,250),
(1984,120,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,38,81,250),
(1985,121,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4,81,250),
(1986,122,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,12756,81,250),
(1987,123,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,6788,81,250),
(1988,124,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2975,81,250),
(1989,125,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1181,81,250),
(1990,126,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,140,81,250),
(1991,127,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,629,81,250),
(1992,128,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1947,81,250),
(1993,129,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,973,81,250),
(1994,130,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5598,81,250),
(1995,131,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,19205,81,250),
(1996,132,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4677,81,250),
(1997,133,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,670,81,250),
(1998,134,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,338,81,250),
(1999,135,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,197,81,250),
(2000,136,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,837,81,250),
(2001,137,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4488,81,250),
(2002,138,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1128,81,250),
(2003,139,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1222,81,250),
(2004,140,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3094,81,250),
(2005,141,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,586,81,250),
(2006,142,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1932,81,250),
(2007,143,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,478,81,250),
(2008,144,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,713,81,250),
(2009,145,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5545,81,250),
(2010,146,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,287,81,250),
(2011,147,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,58,81,250),
(2012,148,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,282,81,250),
(2013,149,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1349,81,250),
(2014,150,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4292,81,250),
(2015,151,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1263,81,250),
(2016,152,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,249,81,250),
(2017,153,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,349,81,250),
(2018,154,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,877,81,250),
(2019,155,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1474,81,250),
(2020,156,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2611,81,250),
(2021,157,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,495,81,250),
(2022,158,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1337,81,250),
(2023,159,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,8744,81,250),
(2024,160,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,23,81,250),
(2025,161,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,794,81,250),
(2026,162,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,825,81,250),
(2027,163,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,465,81,250),
(2028,164,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,11596,81,250),
(2029,165,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,7236,81,250),
(2030,166,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1657,81,250),
(2031,167,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,97,81,250),
(2032,168,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,6802,81,250),
(2033,169,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2678,81,250),
(2034,170,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1459,81,250),
(2035,171,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,7005,81,250),
(2036,172,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1168,81,250),
(2037,173,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,308,81,250),
(2038,174,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,13282,81,250),
(2039,175,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1147,81,250),
(2040,176,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,935,81,250),
(2041,177,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3635,81,250),
(2042,178,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3427,81,250),
(2043,179,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3610,81,250),
(2044,180,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4507,81,250),
(2045,181,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,7420,81,250),
(2046,182,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,713,81,250),
(2047,183,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,396,81,250),
(2048,184,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,379,81,250),
(2049,185,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,72,81,250),
(2050,186,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,806,81,250),
(2051,187,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,364,81,250),
(2052,188,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3116,81,250),
(2053,189,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1221,81,250),
(2054,190,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1256,81,250),
(2055,191,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,979,81,250),
(2056,192,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2778,81,250),
(2057,193,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2878,81,250),
(2058,194,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1888,81,250),
(2059,195,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2660,81,250),
(2060,196,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,29282,81,250),
(2061,197,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,15351,81,250),
(2062,198,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,9429,81,250),
(2063,199,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,10,81,250),
(2064,203,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,619,81,250),
(2065,205,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,851,81,250),
(2066,206,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,555,81,250),
(2067,207,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,13,81,250),
(2068,208,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,952,81,250),
(2069,209,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,532,81,250),
(2070,210,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,373,81,250),
(2071,214,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,599,81,250),
(2072,215,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,684,81,250),
(2073,218,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,210,81,250),
(2074,219,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,792,81,250),
(2075,220,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,203,81,250),
(2076,221,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4268,81,250),
(2077,222,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,606,81,250),
(2078,223,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,529,81,250),
(2079,226,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5,81,250),
(2080,229,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3392,81,250),
(2081,230,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,288,81,250),
(2082,234,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,623,81,250),
(2083,235,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,754,81,250),
(2084,239,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,3993,81,250),
(2085,243,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5,81,250),
(2086,244,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1271,81,250),
(2087,248,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,946,81,250),
(2088,249,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4458,81,250),
(2089,250,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,1583,81,250),
(2090,257,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5841,81,250),
(2091,261,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4815,81,250),
(2092,262,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,45,81,250),
(2093,264,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2992,81,250),
(2094,265,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,9,81,250),
(2095,266,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,44,81,250),
(2096,267,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,28,81,250),
(2097,268,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4,81,250),
(2098,269,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,15,81,250),
(2099,270,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,76,81,250),
(2100,271,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,13,81,250),
(2101,272,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,10,81,250),
(2102,273,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,9,81,250),
(2103,274,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,21,81,250),
(2104,275,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,5,81,250),
(2105,276,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,28,81,250),
(2106,277,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,52,81,250),
(2107,278,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,24,81,250),
(2108,279,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,81,81,250),
(2109,280,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,12,81,250),
(2110,281,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,2260,81,250),
(2111,282,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,50,81,250),
(2112,283,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,4,81,250),
(2113,284,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,68,81,250),
(2114,285,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,10,81,250),
(2115,286,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,11,81,250),
(2116,287,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,115,81,250),
(2117,288,'rast.central_group_chra_032023','zone19',0,'age',40,'ge',95,NULL,NULL,353,81,250);")

dbDisconnect (castordb)  

```

### harvestBlockPriority  
Closest to disturbance first, oldest second. Thus assumes the priority is to cluster forest harvest to minimize disturbance in caribou range. 

### adjacencyConstraint
Adjacency was set to 0 metres to allow for maximum clustering of forest harvest.

### partition
A partition was set as vol > 150 to ensure stands with a minimum of 150m3/ha were harvested, i.e., low productivity stands wouldn't be harvested. 

spatial partitions for TFL 48 and Dawson Creek TSA

### harvestFlow
TFL 48:  395,000 m3/year (440, 420, 410, 405, 400)
Dawson Creek TSA: 1,080,000 m3/year (1.25, 1.15, 1.12, 1.1)

 non-declining maximum harvest flow over a 200 year period.

### Road recovery
No road recovery was simulated (recovery = 300 years). 

#### Usage
Set parameters for running the model simulation below and run the code chunk. 

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/scenarios/central_group/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/central_group/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataCastor = list(dbName='castor',
                         saveCastorDB = FALSE,
                         sqlite_dbname = "central_group_tsu_march2023_castordb_chra_modified", 
                         useCastorDB = paste0(here::here(), "/R/scenarios/central_group/inputs/central_group_tsu_march2023_castordb_chra_modified.sqlite"),
                         nameBoundaryFile = "public.tsa_aac_bounds", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = c ("Dawson_Creek_TSA", "TFL48"), 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "rast.tsa_aac_boundary", 
                          nameCompartmentTable = "vat.tsa_aac_bounds_vat", 
                         nameMaskHarvestLandbaseRaster ='rast.thlb_2020', 
                          nameZoneTable = "zone.constraints", 
                          nameYieldsRaster = "rast.ycid_vdyp_2020_adj",
                          nameYieldTable = "yc_vdyp_2020_adj", 
                          nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                          nameYieldCurrentTable = "tipsy_prov_current_2020",
                          nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                          nameYieldTransitionTable = "tipsy_prov_2020",  
                          nameForestInventoryRaster = "rast.vri2020_id", 
                          nameForestInventoryKey = "feature_id", 
                          nameForestInventoryTable = "veg_comp_2020_adj",
                          nameForestInventoryAge = "proj_age_1",  
                          nameForestInventoryHeight = "proj_height_1",
                          nameForestInventoryCrownClosure = "crown_closure",                             
                          nameForestInventoryTreed = "bclcs_level_2",
                          nameForestInventoryBasalArea = "basal_area",
                          nameForestInventoryQMD = "quad_diam_125",
                          nameForestInventorySiteIndex = "site_index"
                    ),
  blockingCastor = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCastor = list(harvestBlockPriority = "dist, age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      adjacencyConstraint = 0,
                      activeZoneConstraint = c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw",
                                           "rast.central_grp_partner_areas_072022",
                                           "rast.central_group_chra_032023"

                              )),
  growingStockCastor = list (periodLength = 5),
  roadCastor = list(roadMethod = 'mst', # pre mst
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.ce_road_2019'),
  survivalCastor = list (caribou_herd_density = 0.05, 
                       nameRasCaribouHerd = "rast.caribou_herd", # if update, use rast.caribou_herd_20220725
                       tableCaribouHerd = "vat.caribou_herd_vat"), # if update, use vat.caribou_herd_20220725
  smcpopCastor = list (nameRasSMCHerd = "rast.smc_herd_habitat"),
  disturbanceCastor = list(calculateInterval =  1, 
                             criticalHabitatTable = "vat.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 300), # no road recovery
  volumebyareaReportCastor = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.central_group_chra_032023",
                                 AreaofInterestTable = "vat.central_group_chra_032023"),
  uploadCastor = list(aoiName = 'central_group_caribou', 
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  )
)

modules <- list("dataCastor", 
                "growingStockCastor", 
                "blockingCastor", 
                "forestryCastor", 
                "roadCastor",  
                "survivalCastor", 
                "disturbanceCastor", 
                "uploadCastor",
                "smcpopCastor",
                "volumebyareaReportCastor"
                )

scenario = data.table (name = "chra_nh_80y_95ge40_120y_tfl48_dawsonck_may2023",
                       description = "No Harvest in caribou Habitat Recovery Areas (CHRA) for first 80 years, then maximum 5% early seral (<40 y.o.) years 81 to 200. Max. non-declining harvest flow; TFL 48 = 400,000 m3/yr; Dawson Creek TSA = 1.1 M m3/yr. Adjacency was set to 0m. Priority queue = Closest to disturbance first, oldest second. Minimum volume: 150 m3/ha. No road recovery (300 years). Partnership areas included (A2, B2, B3, B4 = no harvest; A1, B1, B5 = 90% > 40 years old).")


harvestFlow <- rbindlist(list(data.table(compartment ="Dawson_Creek_TSA",
                                     partition = ' vol > 150 ', 
                                     period = rep( seq (from = 1,
                                                      to = 40, 
                                                      by = 1),
                                                1), 
                                     flow = 5500000, #1,100,000m3/year
                                     partition_type = 'live'),
                              data.table(compartment = "TFL48",
                                     partition = ' vol > 150 ', 
                                     period = rep( seq (from = 1,
                                                      to = 40, 
                                                      by = 1),
                                                1), 
                                     flow = 2000000, #400,000m3/year 
                                     partition_type = 'live')
))


patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,81,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport",
                                             "tableGrizzSurvivalReport",
                                             "tableAbundanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```




