---
title: "Business-asiusual Simulation for Central Group Caribou Recovery Planning"
author: ""
date: "21 July 2022"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

## Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

## Central Group Scenarios
Here we use forestryCLUS to assess the potential impact of a hypothetical land use orders and deferral areas on timber supply within the area-of-interest for central group caribou (east-central B.C.).

Here we simulate a deferral scenario where harvest is deferred for five zones in the area of interest. Harvest is deferred within these zones for the first 40 years of a 200 year simulation. We test whether the non-declining maximum annual harvest volume (1.65M m3/year) for the area of interest achieved under the 'business-as-usual' scenario can be achieved with the 40 year deferral, and if not the potential influence to timber supply. We also compare the relative influence of the deferral on caribou metrics relative to the BAU scenario. 

## Model Paramters
### BAU Zones 
zone_cond_beo = biodiversity emphasis options 
zone_cond_vqo = visual quality objectives
zone_wha_2021 = wildlife habitat areas
zone_uwr_2021 =  ungulate winter ranges
zone_cond_fsw = fisheries sensitive watersheds
zone_cond_nharv = parks and protected areas
zone_cond_cw = community watersheds
central_grp_partner_areas_072022 = Partnership Agreement areas, where no harvest is permitted in A2, B2, B3 and B4 zones

### Deferral areas
There are five proposed deferral areas; two zones occur in the Kennedy Siding (kennedy_siding_1, kennedy_siding_2), two in Narraway (narraway_1, narraway_2) and one in Quintette (quintette_2). 

```{r, set db for scenario}
require (DBI)
source (paste0 (here::here (), "/R/functions/R_Postgres.R"))
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/central_group/inputs/central_group_july2022_clusdb.sqlite"))

# check tables
check <- dbGetQuery (clusdb, "SELECT * from zoneconstraints WHERE reference_zone = 'rast.central_grp_partner_areas_072022'") # rast.central_grp_deferral_072022  rast.central_grp_partner_areas_072022
 
# run these (if necessary)
dbExecute (clusdb, "UPDATE zoneconstraints SET stop = 39 WHERE (id = 1129) OR (id = 1130) OR (id = 1131) OR (id = 1132) OR (id = 1133)") 
dbExecute (clusdb, "UPDATE zoneconstraints SET type = 'nh' WHERE reference_zone = 'rast.central_grp_partner_areas_072022' AND zoneid = 8") 
dbExecute (clusdb, "UPDATE zoneconstraints SET type = 'nh' WHERE reference_zone = 'rast.central_grp_deferral_072022' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute (clusdb, "UPDATE zoneconstraints SET stop = 39 WHERE reference_zone = 'rast.central_grp_deferral_072022' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute (clusdb, "UPDATE zoneconstraints SET type = '' WHERE (id = 1201) OR (id = 1202) OR (id = 1203) OR (id = 1204) OR (id = 1205)") 

dbDisconnect (clusdb)  

```

### harvestBlockPriority  
Closest to disturbance first, oldest second. Thus assumes the priority is to cluster forest harvest to minimize disturbance in caribou range. 

### adjacencyConstraint
Adjacency was set to 0 meters to allow for maximum clustering of forest harvest.

### partition
A partition was set as vol > 150 to ensure stands with a minimum of 150m3/ha were harvested, i.e., low productivity stands wouldn't be harvested. 

### harvestFlow
1,600,000 m3/year

### Road recovery
No road recovery was simulated (recovery = 300 years). 

#### Usage
Set parameters for running the model simulation below and run the code chunk. 

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/scenarios/central_group/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/central_group/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataCastor = list(dbName='castor',
                         saveCastorDB = FALSE,
                         sqlite_dbname = "central_group_july2022", 
                         useCastorDB = paste0(here::here(), "/R/scenarios/central_group/inputs/central_group_july2022_clusdb.sqlite"),
                         nameBoundaryFile ="central_grp_aoi_072022", 
                         nameBoundaryColumn = "tsa_name", 
                         nameBoundary = c ("central_group"), 
                         nameBoundaryGeom = 'wkb_geometry',
                         nameCompartmentRaster = "rast.central_grp_aoi",
                         nameCompartmentTable = "vat.central_grp_aoi",
                         nameMaskHarvestLandbaseRaster ='rast.thlb_2020', 
                         nameZoneTable="zone.constraints", 
                        # nameZonePriorityRaster = "rast.zone_cond_beo",
                        
                         nameYieldsRaster = "rast.ycid_vdyp_2020",
                         nameYieldTable ="yc_vdyp_2020",
                         nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                         nameYieldCurrentTable = "tipsy_current_prov_2020",
                         nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                         nameYieldTransitionTable = "tipsy_prov_2020", 
                         nameForestInventoryRaster = "rast.vri2020_id", 
                         nameForestInventoryKey = "feature_id",                     
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2020",
                         nameForestInventoryAge = "proj_age_1",  
                         nameForestInventoryHeight = "proj_height_1",
                         nameForestInventoryCrownClosure = "crown_closure",
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index",
                         nameForestInventoryBasalArea= "basal_area",
                         nameForestInventoryQMD = "quad_diam_125"
                    ),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCastor = list(harvestBlockPriority = "dist, age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      adjacencyConstraint = 0,
                      activeZoneConstraint = c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw",
                                           "rast.central_grp_deferral_072022",
                                           "rast.central_grp_partner_areas_072022")
                         ),
  growingStockCastor = list (periodLength = 5),
  roadCastor = list(roadMethod = 'mst', # pre mst
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.ce_road_2019'),
  survivalCastor = list (caribou_herd_density = 0.05, 
                       nameRasCaribouHerd = "rast.caribou_herd", # if update, use rast.caribou_herd_20220725
                       tableCaribouHerd = "vat.caribou_herd_vat"), # if update, use vat.caribou_herd_20220725
  smcpopCastor = list (nameRasSMCHerd = "rast.smc_herd_habitat", 
                                  tableSMCCoeffs = "vat.smc_coeffs"),
  survivalgrizzlyCastor = list (rasterGBPU = "rast.gbpu_2021", 
                              tableGBPU= "vat.gbpu", 
                              roadDensity = 10),
  disturbanceCastor = list(calculateInterval =  1, 
                             criticalHabitatTable = "vat.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 300), # no road recovery
  volumebyareaReportCastor = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "vat.vat_bc_crithab_and_herd"),
  uploadCastor = list(aoiName = 'central_group', 
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  )
)

modules <- list("dataCastor", 
                "growingStockCastor", 
                "blockingCLUS", 
                "forestryCastor", 
                "roadCastor",  
                "survivalCastor", 
                "disturbanceCastor", 
                "uploadCastor",
                "survivalgrizzlyCastor",
                "smcpopCastor",
                "volumebyareaReportCastor"
                )

scenario = data.table (name = "central_group_defer_all_40_july2022",
                       description = "No harvest in all five deferral areas for the first 40 years of the simulation scenario. Max. non-declining harvest flow = 1.6 M m3/yr. Adjacency was set to 0m. Priority queue = Closest to disturbance first, oldest second. Minimum volume: 150 m3/ha. No road recovery (300 years).")


harvestFlow <- rbindlist(list(data.table(compartment ="central_group",
                                     partition = ' vol > 150 ', 
                                     period = rep( seq (from = 1,
                                                      to = 40, 
                                                      by = 1),
                                                1), 
                                     flow = 8000000, #1,600,000m3/year 
                                     partition_type = 'live') 
))


patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport",
                                             "tableGrizzSurvivalReport",
                                             "tableAbundanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```




