---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Central Group Scenarios
Here we use forestryCLUS to assess the potential impact of a hypotehtical large land use order on timber supply in multiple timber suppyl areas and tree farm licenses 


business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat; these were completed for each specific TSA and TFL independently; applied here as the target



#  Parameters 
BAU = beo, vqo, wha, uwr, fsw (fisheries sensitive watersheds), parks and protected areas (nharv) and cw (community watersheds) 

In addtion to BAU :

An anthropogenic clearing is considered to contribute forage for moose if the area has two of the following attributes: 
o	clearings with a conifer stand density less than 1800 sph for pine leading stands and 1200 sph for spruce leading stands, or 
o	clearings less than 25 years old, or 
o	clearings with an average stand height under 2.5 meters.

=  "rast.zone_cond_central_group_luo"



```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/central_group/central_group_july2022_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zone;") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones

#STEP 3: Update the constraints available to a zone as specified in the scenario
dbExecute(clusdb, "UPDATE zoneconstraints set percentage = 85 where reference_zone = 'rast.zone_cond_partnership_agreement' and percentage = 65")
#This example will set the zones in the partnership agreement that have constraints on the variable 'dist' to a 85% disturbance threshold

dbExecute(clusdb, "UPDATE zoneconstraints set type = 'nh' where reference_zone = 'rast.zone_cond_partnership_agreement'") #This example will set all the zones in the partnership agreement to no harvest


#STEP 4: Remove the connection to the database
dbDisconnect(clusdb)
```

## 'harvestPriority' parameter 
- I used oldest first for consistency across units

- no discussion of this in MacKenzie PDP or determination that I could find

## 'harvestFlow'
these determined dependently in TSA specific forestryCLUS

 MacKenzie:
 MacKenzie SW:
 Prince George: 6,000,000m3/yr
 Dawson Creek:
 TFL 48
 



# Scenarios for Main Portion of TSA 
```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataCastor = list(dbName='castor',
                         saveCastorDB = FALSE,
                         sqlite_dbname = "central_group_july2022", 
                         useCastorDB = paste0(here::here(), "/R/scenarios/central_group/central_group_july2022.sqlite"),
                         nameBoundaryFile ="central_grp_aoi_072022", 
                         nameBoundaryColumn = "tsa_name", 
                         nameBoundary = c ("central_group"), 
                         nameBoundaryGeom = 'wkb_geometry',
                         nameCompartmentRaster = "rast.central_grp_aoi", #rast.study_area_chilcotin
                         nameCompartmentTable = "vat.central_grp_aoi",
                         nameMaskHarvestLandbaseRaster ='rast.thlb_2020', 
                         nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw",
                               "rast.zone_cond_noharvest_burnt_pine_crithab_or_herd",
                               "rast.zone_cond_noharvest_hart_ranges_crithab_or_herd",
                               "rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd",
                               "rast.zone_cond_noharvest_moberly_crithab_or_herd",
                               "rast.zone_cond_noharvest_quintette_crithab_or_herd",
                               "rast.zone_cond_noharvest_narraway_crithab_or_herd",
                               "rast.zone_cond_bc_burnt_pine_crithab",
                               "rast.zone_cond_bc_hart_ranges_crithab",
                               "rast.zone_cond_bc_kennedy_siding_crithab",
                               "rast.zone_cond_bc_moberly_crithab",
                               "rast.zone_cond_bc_quintette_crithab",
                               "rast.zone_cond_bc_narraway_crithab",
                               "rast.central_grp_deferral_072022",
                               "rast.central_grp_habitat_072022",
                               "rast.central_grp_partner_areas_072022"
                              ),
                         nameZoneTable="zone.constraints", 
                        # nameZonePriorityRaster = "rast.zone_cond_beo",
                        
                         nameYieldsRaster = "rast.ycid_vdyp_2020",
                         nameYieldTable ="yc_vdyp_2020",
                         nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                         nameYieldCurrentTable = "tipsy_current_prov_2020",
                         nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                         nameYieldTransitionTable = "tipsy_prov_2020", 
                         nameForestInventoryRaster = "rast.vri2020_id", 
                         nameForestInventoryKey = "feature_id",                     
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2020",
                         nameForestInventoryAge = "proj_age_1",  
                         nameForestInventoryHeight = "proj_height_1",
                         nameForestInventoryCrownClosure = "crown_closure",
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index",
                         nameForestInventoryBasalArea= "basal_area",
                         nameForestInventoryQMD = "quad_diam_125"
                    ),
  blockingCastor = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCastor = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      adjacencyConstraint = 3),
  growingStockCastor = list (periodLength = 5),
  roadCastor = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.ce_road_2019'),
  survivalCastor = list (caribou_herd_density = 0.05, 
                       nameRasCaribouHerd = "rast.caribou_herd", 
                       tableCaribouHerd = "public.caribou_herd_vat"), #
  disturbanceCastor = list(calculateInterval =  1, 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploadCastor = list(aoiName = 'central_group', 
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataCastor", 
                "growingStockCastor", 
                "blockingCastor", 
                "forestryCastor", 
                "roadCastor",  
                "survivalCastor", 
                "disturbanceCastor", 
                "uploadCastor"
                )


# scenario = data.table (name = "mackenzie_bau",
#                        description = "Business-as-usual case; sustainable flow = 1.7 M m3/yr .Adjacency was set to 3m.")



harvestFlow <- rbindlist(list(data.table(compartment ="MacKenzie_TSA",
                                     partition = ' vol > 150 ', # from 2014 determination
                                     period = rep( seq (from = 1, # run the 
                                                      to = 40, 
                                                      by =1),
                                                1), 
                                     flow = 8500000,
                                     partition_type = 'live') #1,700,000m3/yr
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```



