---
title: "Proportion of Forest Licensee Roads in Core Caribou Habitat"
author: "Tyler Muhly"
date: "10/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
Here I estimate for each forest licensee operating area in British Columbia that overlaps core caribou critical habitat, the proportion of roads in each area that are in core habitat. The analysis is intended to help understand which licensees might be more or less impacted by requirements to restore roads in core caribou habitat areas. 

## Methods
The analyses can be broadly described with the following steps:

1. Create a roads data set consisting of the [digital road atlas](https://catalogue.data.gov.bc.ca/dataset/digital-road-atlas-dra-master-partially-attributed-roads) and [forest tenure roads](https://catalogue.data.gov.bc.ca/dataset/forest-tenure-road-section-lines). To avoid duplicate roads they were merged then converted to a raster and then back to a single line. 

2. Union this roads data set with the timber harvest land base (THLB), licensee operating areas, timber supply areas (TSAs) and tree farm license (TFLs) areas, and core (high and low elevation summer and winter range) caribou habitat.

3. Calculate the length of roads in core critical habitat within the THLB, by licensee operating area and TSA or TFL. Road length was adjusted by multiplying road length by the THLB factor.

## Results
The table below summarizes the length and proportion of roads in core caribou critical habitat within the THLB, by licensee operating area and TSA or TFL. Note that the "Area" column is a concatenation of timber supply unit (TSA or TFL), and operating area licensee, oper_nm and genus_nm from the operating areas data set.

```{r table roads, warning = F, message = F, echo = F}
library (dplyr)
library (tidyr)
library (kableExtra)
library (foreign)
library (svglite)
library (knitr)

options (scipen = 999)

data <- read.dbf ("C:\\Work\\caribou\\clus_data\\caribou\\roads_thlb_areas.dbf")

data$road_length_thlb <- data$thlb_fact * data$length_km
data$type <- paste(data$manage_uni, "_", data$LICENSEE, "_", data$OPER_NM, "_", data$GENUS_NM)

road.prop.table <- data %>%
                      group_by(type, BCHab_code) %>%
                      summarise (road_length_type = sum (road_length_thlb)) %>%
                      mutate (road_prop = road_length_type / sum (road_length_type))
names (road.prop.table) [1] <- "Area"
names (road.prop.table) [2] <- "Caribou Core Habitat"
names (road.prop.table) [3] <- "Road Length (km)"
names (road.prop.table) [4] <- "Road Proportion"

road.prop.table[,3] <-round(road.prop.table[,3],0) 
road.prop.table[,4] <-round(road.prop.table[,4],2) 

 knitr::kable (road.prop.table,  
               caption = "Length and Proportion of Roads Inside and Outside of Core Caribou Habitat by Management Unit and Operating Area",
               align = 'lccc',
               format.args = list(big.mark = ",", scientific = FALSE)) %>%
                 kableExtra::kable_material(c("striped", "hover")) %>%
                 kableExtra::footnote (general = "HEWSR = High elevation winter and summer range; HESR = High elevation summer range; HEWR = High elevation winter range; LESR = Low elevation summer range; LEWR = Low elevation winter range.")
```

THLB in and out of core, by area


```{r table roads, warning = F, message = F, echo = F}
library (dplyr)
library (tidyr)
library (kableExtra)
library (foreign)
library (svglite)
library (knitr)

options (scipen = 999)

data.thlb <- read.dbf ("C:\\Work\\caribou\\clus_data\\caribou\\thlb_tsa_oparea_core.dbf")

data$road_length_thlb <- data.thlb$thlb_fact * data.thlb$length_km


data$type <- paste(data$manage_uni, "_", data$LICENSEE, "_", data$OPER_NM, "_", data$GENUS_NM)

road.prop.table <- data %>%
                      group_by(type, BCHab_code) %>%
                      summarise (road_length_type = sum (road_length_thlb)) %>%
                      mutate (road_prop = road_length_type / sum (road_length_type))
names (road.prop.table) [1] <- "Area"
names (road.prop.table) [2] <- "Caribou Core Habitat"
names (road.prop.table) [3] <- "Road Length (km)"
names (road.prop.table) [4] <- "Road Proportion"

road.prop.table[,3] <-round(road.prop.table[,3],0) 
road.prop.table[,4] <-round(road.prop.table[,4],2) 

 knitr::kable (road.prop.table,  
               caption = "Length and Proportion of Roads Inside and Outside of Core Caribou Habitat by Management Unit and Operating Area",
               align = 'lccc',
               format.args = list(big.mark = ",", scientific = FALSE)) %>%
                 kableExtra::kable_material(c("striped", "hover")) %>%
                 kableExtra::footnote (general = "HEWSR = High elevation winter and summer range; HESR = High elevation summer range; HEWR = High elevation winter range; LESR = Low elevation summer range; LEWR = Low elevation winter range.")

