---
title: "scheduleCLUS"
author: ""
date: "21 December 2018"
output: pdf_document
---

```{r, eval = FALSE}
# Copyright 2018 Province of British Columbia
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
# http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and limitations under the License.
```
# Overview
This module schedules and tracks various forestry activities. 

```{r module_usage}
library(SpaDES.core)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

indicators<-getTableQuery("SELECT * FROM study_area_tsa where study_area = 'northest'")
  
moduleDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules")
inputDir <- file.path("C:/Users/KLOCHHEA/clus/R") %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path("C:/Users/KLOCHHEA/clus/R")
cacheDir <- file.path("C:/Users/KLOCHHEA/clus/R")
times <- list(start = 0, end = 15)

parameters <- list(
)

modules <- list("scheduleCLUS")
objects <- list()
inputs <- list()
outputs <- list()
paths <- list(
  cachePath = cacheDir,
  modulePath = moduleDir,
  inputPath = inputDir,
  outputPath = outputDir
)

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)

mySimOut <- spades(mySim)


```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("scheduleCLUS", "path/to/modules/dir")` may be sufficient.

## Output data

Description of the module outputs.

# Links to other modules

Describe any anticipated linkages to other modules.

