---
title: "fisher_constraints"
author: "Kyle"
date: "01/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(raster)
library(sf)
library(fasterize)
library(ggplot2)
source("C:/Users/klochhea/castor/R/functions/R_Postgres.R")
#Get a provincial raster that follows the extent standard
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(getSpatialQuery("Select * from bec_zone limit 1"))$proj4string, resolution = c(100, 100), vals = 0)
```

## Purpose

To characterize historical fisher habitat defined according to the habitat categories found [here](https://www.bcfisherhabitat.ca/habitat-tools/) and referenced to various years. The [vegetation resources inventory](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/forest-inventory) was used to characterize historical forest attributes that define the habitat categories

**VRI 2003**
Note that not all forest attributes (e.g., crown closure) were projected to the year 2003 or 2020.

Comparing across two vintages of VRI is likely to produce issues given some areas in the older (VRI 2003) inventory could have NULL or missing information. Thus, any differences between the two inventory would be due to missing information rather than habitat change. 

#### Fisher forest attributes
1. Create a look up table for each vintage of the vri (e.g., 2003, 2020)
```{r, fsher_veg_comp, echo = FALSE}
#Note VRI 2020 uses shape as the geometry column; 2003 + 2010 uses geometry
#layer<-getSpatialQuery(paste0("SELECT feature_id, geometry FROM vri.veg_comp_lyr_r1_poly",year," where bec_zone_code in ('SBS', 'IDF', 'MS', 'SBPS', 'BWBS') "))
layer<-getSpatialQuery(paste0("SELECT feature_id, shape FROM forest_disturbance_draft_cef_brfn_area"))
```

##### Denning
The following queries specify the forest structure needed for fisher to create dens. Adjusted for Mah2.0
```{r, denning}
#SBS: WET
denning.sbs.wet<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where ((SPECIES_CD_1 LIKE 'AC%'  or SPECIES_CD_2 LIKE 'AC%' or  SPECIES_CD_3 LIKE 'AC%') or (SPECIES_CD_1 LIKE 'S%' and SPECIES_CD_2 IS NULL)) and  SIFA_2>=125 and CROWN_CLOSURE>=30 and QUAD_DIAM_125>=28.5 and BASAL_AREA>=29.75 and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')"))

#SBS DRY: Act leading, secondary, or tertiary species (or hybrid spruce (Sx) as only species) Crown closure ≥20% QMD_125 ≥28 cm Basal area ≥28 m²/ha Stand age ≥125 years 
denning.sbs.dry<- getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (((SPECIES_CD_1 LIKE 'AC%')  or (SPECIES_CD_2 LIKE 'AC%') or ( SPECIES_CD_3 LIKE 'AC%')) or ((SPECIES_CD_1 LIKE 'S%') and (SPECIES_CD_2 IS NULL))) and ( SIFA_2>=125) and (CROWN_CLOSURE>=20) and (QUAD_DIAM_125>=28) and (BASAL_AREA>=28) and (bec_zone_code = 'SBS') and (bec_subzone in ('dw','dh','dk'))"))
#DRY FOREST: cottonwood (Act) denning stands:Act leading or secondary species.Stand age ≥135 years 
#Trembling aspen (At) denning stands:At leading or secondary species Stand age ≥135 years
#Douglas-fir (Fd) denning stands:Fd as only species, Crown closure ≥20% QMD_125 ≥34.3 cm, Stand age ≥207 years
denning.dry.for<-getTableQuery(
  paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (((SPECIES_CD_1 LIKE 'A%'  or SPECIES_CD_2 LIKE 'A%') and  SIFA_2>=135) or ((SPECIES_CD_1 LIKE 'F%' and SPECIES_CD_2  IS NULL) and  SIFA_2>=207 and CROWN_CLOSURE>=20 and QUAD_DIAM_125>=34.3)) and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv','dm','xv', 'dk', 'dc')));"))
#BOREAL
denning.boreal<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (((SPECIES_CD_1 LIKE 'AC%'  or SPECIES_CD_2 LIKE 'AC%' or  SPECIES_CD_3 LIKE 'AC%') and  SIFA_2>=88 and QUAD_DIAM_125>=19.5 and PROJ_HEIGHT_1>=19) or ((SPECIES_CD_1 LIKE 'AT%'  or SPECIES_CD_2 LIKE 'AT%' or  SPECIES_CD_3 LIKE 'AT%') and  SIFA_2>=98 and QUAD_DIAM_125>=21.3 and PROJ_HEIGHT_1>=22.8)) AND ((bec_zone_code = 'BWBS' AND bec_subzone IN ('dk', 'mw', 'mk', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'));"))

denning<-rbindlist(list(denning.dry.for,denning.sbs.dry, denning.sbs.wet,denning.boreal))
denning<-unique(denning$feature_id)
denning.poly<-layer[layer$feature_id %in% denning,]
denning.poly$denning<-1
denning.ras <-fasterize::fasterize(denning.poly, prov.rast, field = "denning") 
denning.ras[is.na(denning.ras[])]<-0
writeRaster(denning.ras, file=paste0("denning.tif"), format="GTiff", overwrite=TRUE)
```

##### Resting: Rust Brooms
The following queries specify the forest structure needed for resting sites
```{r, rust_brooms}
#SBS: WET. Hybrid spruce (Sx) leading, secondary, or tertiary species. Crown closure ≥30% QMD_125 ≥22.7 cm Basal area ≥35 m²/ha Stand age ≥135 years Stand height ≥23.7 m
rest.rust.sbs.wet<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (SPECIES_CD_1 LIKE 'S%'  or SPECIES_CD_2 LIKE 'S%' or  SPECIES_CD_3 LIKE 'S%') and CROWN_CLOSURE>=30 and QUAD_DIAM_125>=22.7 and BASAL_AREA>=35 and PROJ_HEIGHT_1>=23.7 and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw');"))

#SBS DRY: Sx leading, secondary, or tertiary species Crown closure ≥25% QMD_125 ≥19.6 cm Basal area ≥32 m²/ha Stand age ≥72 years
rest.rust.sbs.dry<- getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (SPECIES_CD_1 LIKE 'S%'  or SPECIES_CD_2 LIKE 'S%' or SPECIES_CD_3 LIKE 'S%') and  SIFA_2>=72 and CROWN_CLOSURE>=25 and QUAD_DIAM_125>=19.6 and BASAL_AREA>=32 and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk')"))

#DRY FOREST:Sx leading, secondary, or tertiary species Crown closure ≥40% QMD_125 ≥20.1 cm Stand age ≥83 years
rest.rust.dry.for<-getTableQuery(paste0(
  "select feature_id from forest_disturbance_draft_cef_brfn_area where ((SPECIES_CD_1 LIKE 'S%'  or SPECIES_CD_2 LIKE 'S%' or SPECIES_CD_3 LIKE 'S%') and  SIFA_2>=83 and CROWN_CLOSURE>=40 and QUAD_DIAM_125>=20.1) and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv','dm', 'xv', 'dk', 'dc')));"))
  
#BOREAL
rest.rust.boreal<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (((SPECIES_CD_1 LIKE 'SW%'  or SPECIES_CD_2 LIKE 'SW%' or SPECIES_CD_3 LIKE 'SW%') and  SIFA_2>=78 and CROWN_CLOSURE>=50 and QUAD_DIAM_125>=18.5 and PROJ_HEIGHT_1>=19 and BASAL_AREA>=31.4) or ((SPECIES_CD_1 LIKE 'SB%'  or SPECIES_CD_2 LIKE 'SB%' or SPECIES_CD_3 LIKE 'SB%') and  SIFA_2>=68 and CROWN_CLOSURE>=35 and QUAD_DIAM_125>=17 and PROJ_HEIGHT_1>=14.8)) and ((bec_zone_code = 'BWBS' and bec_subzone in ('dk', 'mw', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'))"))

rest.rust<-rbindlist(list(rest.rust.dry.for,rest.rust.sbs.dry, rest.rust.sbs.wet,rest.rust.boreal))
rest.rust<-unique(rest.rust$feature_id)
rest.rust.poly<-layer[layer$feature_id %in% rest.rust,]
rest.rust.poly$rust<-1
rest.rust.ras <-fasterize::fasterize(rest.rust.poly, prov.rast, field = "rust") 
rest.rust.ras[is.na(rest.rust.ras[])]<-0
writeRaster(rest.rust.ras, file=paste0("rest_rust.tif"), format="GTiff", overwrite=TRUE)
```

##### Resting habitat: cavity
The following queries specify the forest structure needed for resting sites
```{r, rest_cavity}
#SBS-WET Act or At leading, secondary, or tertiary species  Crown closure ≥25% QMD_125 ≥30 cm Basal area ≥32 m²/ha Stand height ≥35 m 7
rest.cavity.sbs.wet<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (SPECIES_CD_1 LIKE 'A%'  or SPECIES_CD_2 LIKE 'A%' or  SPECIES_CD_3 LIKE 'A%') and CROWN_CLOSURE>=25 and QUAD_DIAM_125>=30 and BASAL_AREA>=32 and PROJ_HEIGHT_1>=35 and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')"))
  
#SBS-DRY Act or At leading, secondary, or tertiary species  Crown closure ≥25% QMD_125 ≥30 cm Basal area ≥32 m²/ha Stand height ≥35 m 
rest.cavity.sbs.dry<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (SPECIES_CD_1 LIKE 'A%'  or SPECIES_CD_2 LIKE 'A%' or SPECIES_CD_3 LIKE 'A%') and CROWN_CLOSURE>=25 and QUAD_DIAM_125>=30 and BASAL_AREA>=32 and PROJ_HEIGHT_1>=35 and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk');"))
  
rest.cavity<-rbindlist(list(rest.cavity.sbs.wet,rest.cavity.sbs.dry))
rest.cavity<-unique(rest.cavity$feature_id)
rest.cavity.poly<-layer[layer$feature_id %in% rest.cavity,]
rest.cavity.poly$cavity<-1
rest.cavity.ras <-fasterize::fasterize(rest.cavity.poly, prov.rast, field = "cavity") 
rest.cavity.ras[is.na(rest.cavity.ras[])]<-0
writeRaster(rest.cavity.ras, file=paste0("rest_cavity.tif"), format="GTiff", overwrite=TRUE)
```

##### Resting: coarse woody
The following queries specify the forest structure needed for resting sites
```{r, rest_cwd}
#SBS_WET. QMD_125 ≥22.7 cm Stand age ≥135 years  Stand height ≥23.7 m 
rest.cwd.sbs.wet<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where   SIFA_2>=135 and QUAD_DIAM_125>=22.7 and PROJ_HEIGHT_1>=23.7 and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')"))
  
#SBS-DRY. QMD_125 ≥22.7 cm Stand age ≥135 years Stand height ≥23.7 m 
rest.cwd.sbs.dry<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area  where  SIFA_2>=135 and QUAD_DIAM_125>=22.7 and PROJ_HEIGHT_1>=23.7 and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk')"))

#DRY_FOR.	Hybrid spruce (Sx) or Trembling aspen (At) >25% of stand (SPECIES_PCT) Stand age ≥100 years 
rest.cwd.dry.for<-getTableQuery(paste0(
  "select feature_id from forest_disturbance_draft_cef_brfn_area where (((SPECIES_CD_1 LIKE 'S%' and SPECIES_PCT_1>=25) or (SPECIES_CD_2 LIKE 'S%' and SPECIES_PCT_2>=25) or (SPECIES_CD_3 LIKE 'S%' and SPECIES_PCT_3>=25)) or ((SPECIES_CD_1 LIKE 'AT%' and SPECIES_PCT_1>=25) or (SPECIES_CD_2 LIKE 'AT%' and SPECIES_PCT_2>=25) or (SPECIES_CD_3 LIKE 'AT%' and SPECIES_PCT_3>=25))) and  SIFA_2>=100 and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv', 'xv','dm', 'dk', 'dc')))"))
  
rest.cwd.boreal <-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where  SIFA_2>=78 and QUAD_DIAM_125>=18.1 and PROJ_HEIGHT_1>=19 and CROWN_CLOSURE>=60 and ((bec_zone_code = 'BWBS' and bec_subzone in ('dk', 'mw', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'))"))
  
rest.cwd<-rbindlist(list(rest.cwd.sbs.wet,rest.cwd.sbs.dry,rest.cwd.dry.for,rest.cwd.boreal))
rest.cwd<-unique(rest.cwd$feature_id)
rest.cwd.poly<-layer[layer$feature_id %in% rest.cwd,]
rest.cwd.poly$cwd<-1
rest.cwd.ras <-fasterize::fasterize(rest.cwd.poly, prov.rast, field = "cwd")
rest.cwd.ras[is.na(rest.cwd.ras[])]<-0
writeRaster(rest.cwd.ras, file=paste0("rest_cwd.tif"), format="GTiff", overwrite=TRUE)
```

##### Movement habitat
The following queries specify the forest structure needed for movement
```{r, movement}
#SBS_WET. Total cover ≥50% (≥30% shrub and ≥20% tree cover)
#shrub cover max 30%
movement.sbs.wet<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where CROWN_CLOSURE is not null and ((CROWN_CLOSURE>30) OR (SHRUB_CROWN_CLOSURE is not null and CROWN_CLOSURE> 10 and ((SHRUB_CROWN_CLOSURE + CROWN_CLOSURE) > 30))) and  SIFA_2 > 1 and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')"))

#SBS-DRY. Total cover ≥50% (≥30% shrub and ≥20% tree cover)
movement.sbs.dry<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where CROWN_CLOSURE is not null and ((CROWN_CLOSURE>25) OR (SHRUB_CROWN_CLOSURE is not null and CROWN_CLOSURE> 10 and ((SHRUB_CROWN_CLOSURE + CROWN_CLOSURE) > 25))) and  SIFA_2 > 1 and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk')"))

#DRY_FOR.	Total cover ≥50% (≥30% shrub and ≥20% tree cover) 
movement.dry.for<-getTableQuery(paste0(
  "select feature_id from forest_disturbance_draft_cef_brfn_area where  CROWN_CLOSURE is not null and ((CROWN_CLOSURE>20) OR (SHRUB_CROWN_CLOSURE is not null and CROWN_CLOSURE> 10 and ((SHRUB_CROWN_CLOSURE + CROWN_CLOSURE) > 20))) and  SIFA_2 > 1 and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv','dm', 'xv', 'dk', 'dc')))"))

movement.boreal <-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where (CROWN_CLOSURE is not null and CROWN_CLOSURE>50) OR (SHRUB_CROWN_CLOSURE is not null and CROWN_CLOSURE> 10 and SHRUB_CROWN_CLOSURE + CROWN_CLOSURE > 50) and ((bec_zone_code = 'BWBS' and bec_subzone in ('dk', 'mw', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'))"))
  
movement<-rbindlist(list(movement.sbs.wet,movement.sbs.dry,movement.dry.for,movement.boreal))
movement<-unique(movement$feature_id)
movement.poly<-layer[layer$feature_id %in% movement,]
movement.poly$movement<-1
movement.ras <-fasterize::fasterize(movement.poly, prov.rast, field = "movement") 
movement.ras[is.na(movement.ras[])]<-0
writeRaster(movement.ras, file=paste0("movement.tif"), format="GTiff", overwrite=TRUE)
```

##### Openess
```{r, openess}
open<-getTableQuery(paste0("select feature_id from forest_disturbance_draft_cef_brfn_area where CROWN_CLOSURE is null or (CROWN_CLOSURE<=10) or  SIFA_2 <= 1;"))
open<-unique(open$feature_id)
open.poly<-layer[layer$feature_id %in% open,]
open.poly$open<-1
open.ras <-fasterize::fasterize(open.poly, prov.rast, field = "open") 
open.ras[is.na(open.ras[])]<-0
#removing openess outside of the fisher distribution (BEC zones)
writeRaster(open.ras, file=paste0("open.tif"), format="GTiff", overwrite=TRUE)

```
##### Crown Closure
```{r}
year = 2022
cc<-getSpatialQuery(paste0("select CROWN_CLOSURE as cc, shape from forest_disturbance_draft_cef_brfn_area where CROWN_CLOSURE is not null and bec_zone_code in ('SBS', 'IDF', 'MS', 'SBPS', 'BWBS');"))

cc.ras <-fasterize::fasterize(cc, prov.rast, field = "cc") 
cc.ras[is.na(cc.ras[])]<-0
#removing openess outside of the fisher distribution (BEC zones)
writeRaster(cc.ras, file=paste0("cc.tif"), format="GTiff", overwrite=TRUE)
```
###### Remove old objects
```{r}
rm(open, open.poly, open.ras, movement, movement.poly, movement.ras, movement.dry.for, movement.sbs.dry, movement.sbs.wet, denning, denning.poly, denning.ras, denning.dry.for, denning.sbs.dry, denning.sbs.wet, rest.cavity, rest.cavity.poly, rest.cavity.ras, rest.cavity.sbs.dry, rest.cavity.sbs.wet, rest.cwd, rest.cwd.dry.for, rest.cwd.sbs.dry, rest.cwd.sbs.wet, rest.cwd.poly, rest.cwd.ras, rest.rust, rest.rust.poly, rest.rust.ras,rest.rust.dry.for, rest.rust.sbs.dry, rest.rust.sbs.wet, layer)
gc()
```

##Calculate D2
```{r, d2}
fisher.distribution<-getSpatialQuery("select zone, subzone, variant, wkb_geometry from bec_zone where (zone = 'BWBS' and subzone in ('dk','mw','wk', 'mk')) OR (zone = 'ESSF' and subzone in('xv','xcp','xc','mk', 'mc')) OR (zone = 'ICH' and subzone in('mm','dk')) OR (zone = 'IDF' and ((subzone = 'dk' and variant in ('1','2','3','4')) OR (subzone = 'mw' and variant in ('2')) OR (subzone = 'ww'))) OR  (zone = 'MS' and subzone in('dc','dk','dm','dv','xk','xv', 'un')) OR (zone = 'SBS' and subzone in('dh','dk','dw','mc','mh','mk','mm','mw','wk', 'vk', 'un')) OR (zone = 'SBPS' and subzone in('dc','mc','mk','xc')) OR (zone = 'ICH' and subzone = 'mc' and variant in('1','2'))
                                     OR (zone = 'CWH' and subzone = 'ws' and variant in('1','2'));")
fisher.density<-getSpatialQuery("select * from fisher_density_2004 ;")
#fisher.distribution<-getSpatialQuery("select * from fisher_habitat_zones_2020 where hab_zone = 'Sub-Boreal moist';")

hex.grid<-st_as_sf(st_make_grid(fisher.distribution, cellsize = 5886, square = FALSE)) #6537 = 35 km2 territory
#hex.grid <- st_as_sf(st_make_grid(fisher.distribution, cellsize = 7599, square = FALSE))

hex.grid$fid<-1:nrow(hex.grid)
int.hex.dens<-st_intersects(fisher.density[fisher.density$fisher_cap %in% c('very high', 'high', 'med', 'low', 'rare'),], hex.grid)

hex.grid2<-hex.grid[hex.grid$fid %in% unique(unlist(int.hex.dens)),]

#intersect the territories/hexagon and the fisher capability classes
hex.int.fc<-st_intersection(hex.grid2, fisher.density[fisher.density$fisher_cap %in% c('very high', 'high','med', 'low', 'rare'),])
hex.int.fc$area<-NULL
#estimate the area in each newly formed polygon
hex.int.fc$area<- st_area(hex.int.fc$x)

#library(tidyverse)
library(dplyr)
#summarize the area by each fisher_cap class
out<-data.table(hex.int.fc %>% group_by(fid, fisher_cap) %>%
  summarise(areaFisherCap = sum(area)))

units(out$areaFisherCap)<-units::make_units(km2)

#Apply the fisher density per each fisher capability rating
#very high = (((76% + 100%)/2)/100) * 16.3 per 1000 km2 = 14.322 per 1000 km2
#high = (((51% + 75%)/2)/100) * 16.3 per 1000 km2 = 10.269 per 1000 km2
out[fisher_cap == 'very high', f_dens:= (areaFisherCap/1000)*((15.5+20.7)/2)]
out[fisher_cap == 'high', f_dens:= (areaFisherCap/1000)*((15.4+10.4)/2)]
out[fisher_cap == 'med', f_dens:= (areaFisherCap/1000)*((10.3+5.2)/2)]
out[fisher_cap == 'low', f_dens:= (areaFisherCap/1000)*((5.1+1.2)/2)]

out[fisher_cap == 'very high', f_dens_l:= (areaFisherCap/1000)*15.5]
out[fisher_cap == 'high', f_dens_l:= (areaFisherCap/1000)*10.4]
out[fisher_cap == 'med', f_dens_l:= (areaFisherCap/1000)*5.2]
out[fisher_cap == 'low', f_dens_l:= (areaFisherCap/1000)*1.2]

out[fisher_cap == 'very high', f_dens_h:= (areaFisherCap/1000)*20.7]
out[fisher_cap == 'high', f_dens_h:= (areaFisherCap/1000)*14.4]
out[fisher_cap == 'med', f_dens_h:= (areaFisherCap/1000)*10.3]
out[fisher_cap == 'low', f_dens_h:= (areaFisherCap/1000)*5.1]

out2<-units::drop_units(out[, list(nfish = sum(f_dens),nfishl = sum(f_dens_l), nfishh = sum(f_dens_h )), by = fid])

# order from highest to lowest
out3<- out2[,.SD[order(-nfish)]]
write.csv(out3, "C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_density.csv")

fetas.poly<-hex.grid2
### EXTRACT habitat--------------------------------------------------------
## extract the historic
if(FALSE){
fetas.poly$hab_den2003<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/denning2003.tif"),fetas.poly,c('sum'))
fetas.poly$hab_mov2003<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movement2003.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cwd2003<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cwd2003.tif"),fetas.poly,c('sum'))
fetas.poly$hab_rust2003<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_rust2003.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cav2003<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cavity2003.tif"),fetas.poly,c('sum'))
fetas.poly$hab_opn2003<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/open2003.tif"),fetas.poly,c('sum'))

fetas.poly$hab_den2010<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/denning2010.tif"),fetas.poly,c('sum'))
fetas.poly$hab_mov2010<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movement2010.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cwd2010<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cwd2010.tif"),fetas.poly,c('sum'))
fetas.poly$hab_rust2010<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_rust2010.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cav2010<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cavity2010.tif"),fetas.poly,c('sum'))
fetas.poly$hab_opn2010<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/open2010.tif"),fetas.poly,c('sum'))

fetas.poly$hab_den2015<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/denning2015.tif"),fetas.poly,c('sum'))
fetas.poly$hab_mov2015<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movement2015.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cwd2015<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cwd2015.tif"),fetas.poly,c('sum'))
fetas.poly$hab_rust2015<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_rust2015.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cav2015<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cavity2015.tif"),fetas.poly,c('sum'))
fetas.poly$hab_opn2015<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/open2015.tif"),fetas.poly,c('sum'))

fetas.poly$hab_den2018<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/denning2018.tif"),fetas.poly,c('sum'))
fetas.poly$hab_mov2018<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movement2018.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cwd2018<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cwd2018.tif"),fetas.poly,c('sum'))
fetas.poly$hab_rust2018<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_rust2018.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cav2018<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cavity2018.tif"),fetas.poly,c('sum'))
fetas.poly$hab_opn2018<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/open2018.tif"),fetas.poly,c('sum'))

fetas.poly$hab_den2021<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/denning2021.tif"),fetas.poly,c('sum'))
fetas.poly$hab_mov2021<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movement2021.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cwd2021<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cwd2021.tif"),fetas.poly,c('sum'))
fetas.poly$hab_rust2021<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_rust2021.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cav2021<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cavity2021.tif"),fetas.poly,c('sum'))
fetas.poly$hab_opn2021<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/open2021.tif"),fetas.poly,c('sum'))

fetas.poly$hab_den2022<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/denning2022.tif"),fetas.poly,c('sum'))
fetas.poly$hab_mov2022<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movement2022.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cwd2022<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cwd2022.tif"),fetas.poly,c('sum'))
fetas.poly$hab_rust2022<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_rust2022.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cav2022<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cavity2022.tif"),fetas.poly,c('sum'))
fetas.poly$hab_opn2022<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/open2022.tif"),fetas.poly,c('sum'))
}

fetas.poly$hab_den2023<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/denning2023.tif"),fetas.poly,c('sum'))
fetas.poly$hab_mov2023<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movement2023.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cwd2023<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cwd2023.tif"),fetas.poly,c('sum'))
fetas.poly$hab_rust2023<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_rust2023.tif"),fetas.poly,c('sum'))
fetas.poly$hab_cav2023<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/rest_cavity2023.tif"),fetas.poly,c('sum'))
fetas.poly$hab_opn2023<- exactextractr::exact_extract(raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/open2023.tif"),fetas.poly,c('sum'))

st_write(fetas.poly, "C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_time2023.shp", overwrite =T)

```
##### Calculate d2
```{r, d2}
fetas<-fetas.poly
fetas<-st_read("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_time2023.shp")
#get the fisher population
fetaid<-data.table( fid = fasterize::fasterize(fetas, prov.rast, field = "fid")[],mov_p = raster("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/movp.tif")[])
fetaid<-fetaid[mov_p>0,]
freq_fetaid<-fetaid[ ,.(count = .N), by = c("fid", "mov_p")]
feta_pop<-freq_fetaid[freq_fetaid[, .I[which.max(count)], by = fid]$V1]

#get table of information
d2_est<-fetas %>% st_drop_geometry()
d2_est<-data.table(d2_est)
d2_est<-merge(d2_est, feta_pop, by.y = "fid", by.x = "fid")
#get the cov
# 1: SBS-moist, 2: SBS-dry, 3: dry forest, 5: boreal
fisher.d2.cov <- list(matrix(c(0.536,	2.742,	0.603,	3.211,	-2.735,	1.816,	2.742,	82.721,	4.877,	83.281,	7.046,	-21.269,	0.603,	4.877,	0.872,	4.033,	-0.67,	-0.569,	3.211,	83.281,	4.033,	101.315,	-15.394,	-1.31,	-2.735,	7.046,	-0.67,	-15.394,	56.888,	-48.228,	1.816,	-21.269,	-0.569,	-1.31,	-48.228,	47.963), ncol =6, nrow =6),
                           matrix(c(0.525,	-1.909,	-0.143,	2.826,	-6.891,	3.264,	-1.909,	96.766,	-0.715,	-39.021,	69.711,	-51.688,	-0.143,	-0.715,	0.209,	-0.267,	1.983,	-0.176,	2.826,	-39.021,	-0.267,	58.108,	-21.928,	22.234,	-6.891,	69.711,	1.983,	-21.928,	180.113,	-96.369,	3.264,	-51.688,	-0.176,	22.234,	-96.369,	68.499), ncol =6, nrow =6),
                           matrix(c(2.905,	0.478,	4.04,	1.568,	-3.89,	0.478,	0.683,	6.131,	8.055,	-8.04,	4.04,	6.131,	62.64,	73.82,	-62.447,	1.568,	8.055,	73.82,	126.953,	-130.153,	-3.89,	-8.04,	-62.447,	-130.153,	197.783), ncol=5, nrow=5),
                           matrix(c(193.235,	5.418,	42.139,	125.177,	-117.128,	5.418,	0.423,	2.926,	5.229,	-4.498,	42.139,	2.926,	36.03,	46.52,	-42.571,	125.177,	5.229,	46.52,	131.377,	-101.195,	-117.128,	-4.498,	-42.571,	-101.195,	105.054), ncol =5, nrow =5))

d2_est[, denning:= (hb_d2023/3000)*100]
d2_est[, cavity:= (hb_cv2023/3000)*100]
d2_est[, rust:= (hb_r2023/3000)*100]
d2_est[, cwd:= (hb_cw2023/3000)*100]
d2_est[, mov:= (hb_m2023/3000)*100]
d2_est[, opn:= (hb_p2023/3000)*100]

#d2_est[, denning:= (hb_d2022/3000)*100]
#d2_est[, cavity:= (hb_cv2022/3000)*100]
#d2_est[, rust:= (hb_r2022/3000)*100]
#d2_est[, cwd:= (hb_cw2022/3000)*100]
#d2_est[, mov:= (hb_m2022/3000)*100]
#d2_est[, opn:= (hb_p2022/3000)*100]

#d2_est[, denning:= (hab_den2021/5000)*100]
#d2_est[, cavity:= (hab_cav2021/5000)*100]
#d2_est[, rust:= (hab_rust2021/5000)*100]
#d2_est[, cwd:= (hab_cwd2021/5000)*100]
#d2_est[, mov:= (hab_mov2021/5000)*100]
#d2_est[, opn:= (hab_opn2021/5000)*100]

d2_est[ mov_p == 1 & denning >= 0, denning:=log(denning + 1)][ mov_p == 1 & cavity >= 0, cavity:=log(cavity + 1)]
#d2_est[ mov_p == 2 & denning >= 0, denning:=log(denning + 1)][ mov_p == 2 & cavity >= 0, cavity:=log(cavity + 1)]
d2_est[ mov_p == 2 & denning >= 0, denning:=log(denning + 1)]
d2_est[ mov_p >= 3 & rust >= 0, rust:=log(rust + 1)]
   

d2_est[ mov_p == 1 & denning > 1.57 , denning := 1.57 ][ mov_p == 1 & rust > 36.2, rust :=36.2][ mov_p == 1 & cavity > 0.685 , cavity :=0.685][ mov_p == 1 & cwd > 30.38, cwd :=30.38][ mov_p == 1 & mov > 61.5, mov :=61.5][ mov_p == 1 & opn < 32.7, opn :=32.7]
#d2_est[ mov_p == 2 & denning > 1.57 , denning := 1.57 ][ mov_p == 2 & rust > 36.2, rust :=36.2][ mov_p == 2 & cavity > 0.685 , cavity :=0.685][ mov_p == 2 & cwd > 30.38, cwd :=30.38][ mov_p == 2 & mov > 61.5, mov :=61.5][ mov_p == 2 & opn < 32.7, opn :=32.7]
d2_est[ mov_p == 2 & denning > 1.16, denning := 1.16][ mov_p == 2 & rust > 19.1, rust :=19.1][ mov_p == 2 & cavity > 0.45 , cavity :=0.45][ mov_p == 2 & cwd > 12.7, cwd :=12.7][mov_p == 2 & mov > 51.3, mov :=51.3][ mov_p == 2 & opn < 37.3, opn :=37.3]

d2_est[ mov_p == 3 & denning > 2.3, denning := 2.3][ mov_p == 3 & rust > 1.6, rust :=1.6][ mov_p == 3 & cwd > 10.8, cwd :=10.8][ mov_p == 3 & mov > 58.1, mov := 58.1][ mov_p == 3 & opn < 15.58, opn := 15.58]
d2_est[ mov_p == 5 & denning > 24 , denning:=24 ][ mov_p ==5 & rust > 2.2, rust :=2.2][ mov_p ==5 & cwd > 17.4 , cwd :=17.4][ mov_p ==5 & mov > 56.2, mov :=56.2][ mov_p == 5 & opn < 31.2, opn := 31.2]
    
    
    #-----D2
d2_est<-d2_est[ mov_p == 1, d2_2023:= mahalanobis(d2_est[ mov_p == 1, c("denning", "rust", "cavity", "cwd", "mov", "opn")], c(1.57, 36.2, 0.68, 30.38, 61.5, 32.72), cov = fisher.d2.cov[[1]])]
d2_est<-d2_est[ mov_p == 2, d2_2023:= mahalanobis(d2_est[ mov_p == 2, c("denning", "rust", "cavity", "cwd", "mov", "opn")], c(1.16, 19.1, 0.4549, 12.76, 51.25, 37.27), cov = fisher.d2.cov[[2]])]
#d2_est<-d2_est[ mov_p %in% c(1,2), d2_2021:= mahalanobis(d2_est[ mov_p %in% c(1,2), c("denning", "rust", "cavity", "cwd", "mov", "opn")], c(1.16, 19.1, 0.4549, 12.76, 51.25, 37.27), cov = fisher.d2.cov[[2]])]
d2_est<-d2_est[ mov_p == 3, d2_2023:= mahalanobis(d2_est[ mov_p == 3, c("denning", "rust", "cwd", "mov", "opn")], c(2.31, 1.63, 10.8, 58.1, 15.58), cov = fisher.d2.cov[[3]])]
d2_est<-d2_est[ mov_p == 5, d2_2023:= mahalanobis(d2_est[ mov_p == 5, c("denning", "rust", "cwd", "mov", "opn")], c(23.98, 2.24, 17.4, 56.2, 31.2), cov = fisher.d2.cov[[4]])]

#d2_est<-d2_est[ denning < 0.001, d2_2021:= NA][mov < 0.001,  d2_2021:= NA][cwd  < 0.001,  d2_2021 := NA][rust  < 0.001,  d2_2021 := NA]
d2_est<-d2_est[ denning < 0.001, d2_2023:= NA][mov < 0.001,  d2_2023:= NA]

#fisher.poly.d2<-merge(fetas, d2_est[,c("fid", "mov_p", "d2_2003", "d2_2010", "d2_2015","d2_2018","d2_2021")], by.x = "fid", by.y = "fid", all.x = TRUE)
#fisher.poly.d2<-merge(fetas, d2_est[,c("fid", "mov_p", "d2_2015","d2_2018","d2_2021")], by.x = "fid", by.y = "fid", all.x = TRUE)
fisher.poly.d2<-merge(fetas, d2_est[,c("fid", "mov_p", "d2_2023")], by.x = "fid", by.y = "fid", all.x = TRUE)

st_write(fisher.poly.d2, "C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_historic_d2_2023.shp", overwrite= T, append =F)
```

##### Summaries
```{r, tsa}
fisher.poly.d2<-st_read("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_historic_d2.shp")
d2_est<-data.table(st_drop_geometry(fisher.poly.d2))
abund<-data.table(read.csv("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_density.csv"))
d2_est<-merge(d2_est, abund, by = "fid")

d2_est<-d2_est[nfish > 0 & nfish <= 0.033, hab_cap := "rare"]
d2_est<-d2_est[nfish > 0.033 & nfish <= 0.152998, hab_cap := "low"]
d2_est<-d2_est[nfish > 0.152998 & nfish <= 0.308994, hab_cap := "med"]
d2_est<-d2_est[nfish > 0.308994 & nfish <= 0.461986, hab_cap := "high"]
d2_est<-d2_est[nfish > 0.461986, hab_cap := "very high"]

out01<-d2_est[d2_2003 <= 7 , .N, by = mov_p][, year:=2003]
out02<-d2_est[d2_2010 <= 7 , .N, by = mov_p][, year:=2010]
out03<-d2_est[d2_2015 <= 7 , .N, by = mov_p][, year:=2015]
out04<-d2_est[d2_2021 <= 7 , .N, by = mov_p][, year:=2021]
out005<-rbindlist(list(out01, out02, out03, out04))
ggplot(data = out005, aes(x = year, y = N, group = mov_p, fill = mov_p)) + geom_bar(stat = "identity")
out005[mov_p == 3, n_adj:= N*0.25][mov_p == 2, n_adj:= N*0.75][mov_p == 1, n_adj:= N]
out005[, sum(n_adj), by = year]


overall<-data.table(year =c(2003, 2010,2015, 2021), 
                    suitable_7 = c(nrow(d2_est[d2_2003 <= 7 ,]), nrow(d2_est[d2_2010 <= 7 ,]),nrow(d2_est[d2_2015 <= 7 ,]) ,nrow(d2_est[d2_2021 <= 7 ,])), 
                    suitable_5 = c(nrow(d2_est[d2_2003 <= 5 ,]), nrow(d2_est[d2_2010 <= 5 ,]),nrow(d2_est[d2_2015 <= 5 ,]) ,nrow(d2_est[d2_2021 <= 5 ,])),
                    suitable_9 = c(nrow(d2_est[d2_2003 <= 9 ,]), nrow(d2_est[d2_2010 <= 9 ,]),nrow(d2_est[d2_2015 <= 9 ,]) ,nrow(d2_est[d2_2021 <= 9 ,])),
                    Vintage = "From year"
                    )
overall<-rbind(overall, data.table(year = c(2003, 2010, 2015, 2021), 
                                   suitable_7 = c(nrow(d2_est[d2_2003 <= 7 ,]), nrow(d2_est[d2_2003 <= 7 & d2_2010 <= 7 ,]), nrow(d2_est[d2_2003 <= 7 & d2_2015 <= 7 ,]) , nrow(d2_est[d2_2003 <= 7 & d2_2021 <= 7 ,])),
                                   suitable_5 = c(nrow(d2_est[d2_2003 <= 5 ,]), nrow(d2_est[d2_2003 <= 5 & d2_2010 <=5 ,]), nrow(d2_est[d2_2003 <= 5 & d2_2015 <= 5 ,]),nrow(d2_est[d2_2003 <= 5 & d2_2021 <= 5 ,])),
                    suitable_9 = c(nrow(d2_est[d2_2003 <= 9 ,]), nrow(d2_est[d2_2003 <= 9 & d2_2010 <= 9 ,]), nrow(d2_est[d2_2003 <= 9 & d2_2015 <= 9 ,]),nrow(d2_est[d2_2003 <= 9 & d2_2021 <= 9 ,])),
                                  Vintage = "From 2003" )
               )


ggplot(data=overall, aes(x = as.factor(year), y = suitable_7, fill = Vintage)) + 
  geom_bar(position = "dodge", stat= "identity") +
  geom_errorbar(aes(ymin = suitable_5, ymax = suitable_9),  position=position_dodge(width=0.9), width = 0.5) +
  geom_text(aes(label = suitable_7, color = Vintage),  position=position_dodge(width=0.9), vjust=-0.25) +
  ylab("Count Suitable FETA") +
  xlab("Year")

data_open<-rbindlist(list(data.table(open = nrow(d2_est[hb_m2003 > 1650,  ]), year = 2003),data.table(open = nrow(d2_est[hb_m2010 > 1650,  ]), year = 2010), data.table(open = nrow(d2_est[hb_m2015 > 1650,  ]), year = 2015),data.table(open = nrow(d2_est[hb_m2021 > 1650,  ]), year = 2021)))

ggplot(data=data_open, aes(x = as.factor(year), y = (open/13069)*100)) + 
  geom_bar(position = "dodge", stat= "identity") +
  ylab("Percent of FETA movement > 55%") +
  xlab("Year")



```




###### TSA
```{r}
### CLUSTERING?
fisher.poly.d2<-st_read("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_historic_d2.shp")
fish.table.d2<-data.table(st_drop_geometry(fisher.poly.d2))
fisher.table.d2<-fish.table.d2[, suit2003 :=0][d2_2003 <=7, suit2003 :=1][, suit2010:=0][d2_2010 <=7, suit2010 :=1][, suit2015:=0][d2_2015 <=7, suit2015 :=1][, suit2021:=0][d2_2021 <=7, suit2021 :=1]
#Check the totals
fisher.table.d2[,.(suit_2003 = sum(suit2003), suit_2010 = sum(suit2010), suit_2015 = sum(suit2015), suit_2021 = sum(suit2021))]

fisher.poly.d2<-merge(fisher.poly.d2,fisher.table.d2[,c("fid", "suit2003", "suit2010", "suit2015", "suit2021")], by = "fid")

tsa<-getSpatialQuery("SELECT * from tsa where rtrmntdt is null and tsnmbrdscr in ('Quesnel_TSA', '100_Mile_House_TSA', 'Williams_Lake_TSA');")
fisher.tsa<-st_intersection(fisher.poly.d2, tsa)

fisher.tsa$area<-st_area(fisher.tsa)
out_tsa<-data.table(st_drop_geometry(fisher.tsa))
out_tsa<-units::drop_units(out_tsa)

count_out<-out_tsa[, .(s2003 = sum(suit2003*(area/30000000)),s2010 = sum(suit2010*(area/30000000)),s2015 = sum(suit2015*(area/30000000)),s2021 = sum(suit2021*(area/30000000))), by = tsnmbrdscr]
write.csv(count_out, "summary_tsa.csv")
cnt_1<-rbindlist(list(data.table(tnmbrdscr = count_out$tsnmbrdscr, suitable_7 = count_out$s2003, year = 2003, Vintage = "From year"), data.table(tnmbrdscr = count_out$tsnmbrdscr, suitable_7 = count_out$s2010, year = 2010, Vintage = "From year"),data.table(tnmbrdscr = count_out$tsnmbrdscr, suitable_7 = count_out$s2015, year = 2015,Vintage = "From year"),data.table(tnmbrdscr = count_out$tsnmbrdscr, suitable_7 = count_out$s2021, year = 2021,Vintage = "From year")))

out2<-out_tsa[suit2003 == 1 & suit2010 == 1, suit03_10 := 1][suit2003 == 1 & suit2015 == 1, suit03_15 := 1][suit2003 == 1 & suit2021 == 1, suit03_21 := 1]
count_out2<-out_tsa[, .(s2010 = sum(suit03_10*(area/30000000), na.rm=T),s2015 = sum(suit03_15*(area/30000000), na.rm=T),s2021 = sum(suit03_21*(area/30000000), na.rm=T)), by = tsnmbrdscr]

write.csv(count_out2, "summary_tsa_prop2003.csv")
cnt_2<-rbindlist(list(data.table(tnmbrdscr = count_out2$tsnmbrdscr, suitable_7 = count_out2$s2010, year = 2010, Vintage = "From 2003"),data.table(tnmbrdscr = count_out2$tsnmbrdscr, suitable_7 = count_out2$s2015, year = 2015,Vintage = "From 2003"),data.table(tnmbrdscr = count_out2$tsnmbrdscr, suitable_7 = count_out2$s2021, year = 2021,Vintage = "From 2003")))

### compare graph
overall2<-rbindlist(list(cnt_1, cnt_2))
ggplot(data=overall2[tnmbrdscr %in% c('100_Mile_House_TSA', 'Williams_Lake_TSA', 'Quesnel_TSA', 'Prince_George_TSA', 'Lakes_TSA', 'Kamloops_TSA')], aes(x = as.factor(year), y = as.integer(suitable_7), fill = Vintage)) + 
  geom_bar(position = "dodge", stat= "identity") +
  facet_wrap(~tnmbrdscr) +
  geom_text(aes(label = as.integer(suitable_7), color = Vintage),  position=position_dodge(width=0.9), vjust=-0.25) +
  ylab("Count Suitable FETA") +
  xlab("Year")

           
overall3<-overall2[tnmbrdscr %in% c('100_Mile_House_TSA', 'Williams_Lake_TSA', 'Quesnel_TSA'),] [, .(suitable_7 = sum(suitable_7)), by=c("year", "Vintage")]

ggplot(data=overall3, aes(x = as.factor(year), y = as.integer(suitable_7), fill = Vintage)) + 
  geom_bar(position = "dodge", stat= "identity") +
  #geom_errorbar(aes(ymin = suitable_5, ymax = suitable_9),  position=position_dodge(width=0.9), width = 0.5) +
  geom_text(aes(label = as.integer(suitable_7), color = Vintage),  position=position_dodge(width=0.9), vjust=-0.25) +
  ylab("Count Suitable FETA") +
  xlab("Year")

```
#### model
```{r}
fisher.poly.d2<-st_read("C:/Users/klochhea/fetaMapper/data-raw/habitat_categories/feta_historic_d2.shp")
fish.table.d2<-data.table(st_drop_geometry(fisher.poly.d2))
fisher.table.d2<-fish.table.d2[, suit2003 :=0][d2_2003 <=7, suit2003 :=1][, suit2010:=0][d2_2010 <=7, suit2010 :=1][, suit2015:=0][d2_2015 <=7, suit2015 :=1][, suit2021:=0][d2_2021 <=7, suit2021 :=1]

test<-fisher.table.d2[suit2003 == 1 | suit2021 == 1,]
test[is.na(d2_2003) ,  d2_2003 := 100][is.na(d2_2021) ,  d2_2021 := 100]
test[ , deltad2 := d2_2003 - d2_2021][ , deltaHab_open := (hb_p2021-hb_p2003 )][ , deltaHab_den := (hb_d2021-hb_d2003)][ , deltaHab_mov := (hb_m2021-hb_m2003)][ , deltaHab_rcwd := (hb_cw2021-hb_cw2003)][ , deltaHab_rrust := (hb_r2021-hb_r2003)]

cor(test[,c("deltad2", "deltaHab_open", "deltaHab_den", "deltaHab_mov", "deltaHab_rcwd","deltaHab_rrust")])

summary(lm(data = test, formula= deltad2~ scale(deltaHab_mov) + scale(deltaHab_den) + scale(deltaHab_open) + scale(deltaHab_rcwd) + scale(deltaHab_rrust )))

ggplot(data = test[,c("deltaHab_open","deltad2")], aes(x = deltaHab_open, y = deltad2)) + geom_point() + geom_smooth()
```