---
title: "rsfCLUS"
author: ""
date: "15 April 2019"
output: pdf_document
---

<!--
Copyright 2018 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module tracks various Resource Selection Functions (RSF) within a CLUS simulation. 

```{r module_usage}
library(SpaDES.core)
library(data.table)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

moduleDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules")
inputDir <- file.path("C:/Users/KLOCHHEA/clus/R") %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path("C:/Users/KLOCHHEA/clus/R")
cacheDir <- file.path("C:/Users/KLOCHHEA/clus/R")
times <- list(start = 0, end = 15)
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(dbName='clus',
                        nameBoundaryFile="study_area_compart",
                        nameBoundaryColumn="tsa_name",
                        nameBoundary='Morice TSA', 
                        nameBoundaryGeom='wkb_geometry',
                        nameCutblockRaster ="rast.cns_cut_bl",
                        nameCutblockTable = "public.cns_cut_bl_polygon",
                        nameAgeRaster= "rast.vri2017_projage1",
                        nameHeightRaster= "rast.vri2017_projheight1",
                        nameCrownClosureRaster= "rast.vri2017_crownclosure"),
rsfCLUS = list()
                        )
modules <- list("dataLoaderCLUS","cutblockSeqPrepCLUS", "rsfCLUS")

rsf_model_coeff<-data.table(population = "DU6", 
                            season ="EW",
                            static = c('Y','Y','Y','Y','N','N','N','N','N','N'),
                            beta = c(-2.562923161, -0.017756076, -0.018701324, -0.022060543, -0.054817853,  -0.154907815, -0.103495695, 0.076301527,-0.155193551,0.004786669),
                            layer=c('int', "rast.bc_ha_slope", "rast.dt_waterbodies", "rast.dt_watercourses",'cut_1_4','cut_5_10','cut_gt_10','age','height', 'crownclosure'),
                            sql=c('','','','', 'blockid > 0 AND age BETWEEN 1 AND 4','blockid > 0 AND age BETWEEN 5 AND 10', 'blockid > 0 AND age > 10','','',''),
                            type =c('','','','','DT', 'DT','DT','UP','UP','UP'))

objects <- list(rsf_model_coeff=rsf_model_coeff)
paths <- list(
  cachePath = cacheDir,
  modulePath = moduleDir,
  inputPath = inputDir,
  outputPath = outputDir
)

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)

system.time({
mysimout<-spades(mySim)
})
#eventDiagram(mySimOut)
```

# Events

At each time step, the `rsfCLUS` module calculates the resource selection function for a user defined population and season.

# Data dependencies

## Input objects

The user provides the input object: `rsf_model_coeff` that contains the resource selection function coefficients for the various covariates. In addition to the coeffiecents (beta column in the table): 

* static := declares Y/N (yes/no) if the covariate is static, meaning its value will remain static throughout the simulation or if no, the covariate will be updated as a result of the simulation

* layer := the name of the raster stored in a psql database or the name of the updated variable in `clusdb`. 

>Note: In layer column an 'int' is needed for each rsf. If the rsf is fit with no intercept, 'int' is required but with beta = 0.

* type :=  declares the type of dynamic variable.  UP = 'Updatable' in `clusdb`, DT = 'Distance To'. A value in this column is needed if the static column = N.

* sql := the `WHERE` clause of a sql statement describing the `clusdb` variables used in the dynamic layer


```{r, example_rsf_coeff}
print(rsf_model_coeff)
```

## Output objects

The following objects are instantiated via rsfCLUS:

* pts:= A data.table of X,Y locations - used to find distances

* rsfCovar:= A data.table of covariates used to calculate the RSF. This could be uploaded into clusdb? Not implemented.

* rsfGLM:= Inherits a glm class used for prediction of the RSF

* rsf:= A table within the `clusdb` SQLite database that stores RSFs.    

# Links to other modules

Requires dataLoaderCLUS to instantiate the `clusdb` SQLite database.

