---
title: "rsfCLUS"
author: ""
date: "15 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2018 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module tracks various Resource Selection Functions (RSF) within a CLUS simulation. 

```{r module_usage}
library (SpaDES.core)
library (data.table)
library (here)
source (paste0 (here(),"/R/functions/R_Postgres.R"))

moduleDir <- file.path (paste0 (here(),"/R/SpaDES-modules"))
inputDir <- file.path (paste0 (here(), "/R")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path (paste0 (here(), "/R"))
cacheDir <- file.path (paste0 (here(), "/R"))
times <- list (start = 0, end = 1)
parameters <- list (
  .progress = list (type = NA, interval = NA),
  .globals = list (),
  dataLoaderCLUS = list (dbName = 'clus',
                         nameBoundaryFile = "study_area_compart",
                         nameBoundaryColumn = "tsb_number",
                         #nameBoundary = c ("41B", "41D"), #DU8
                         #nameBoundary = c ("26A", "29B", "29C"), #DU7
                         nameBoundary = c ("08B"), #DU6
                         #nameBoundary = c ("24E"), #DU6
                         nameBoundaryGeom="wkb_geometry",
                         nameAgeRaster= "rast.vri2017_projage1",
                         nameHeightRaster= "rast.vri2017_projheight1",
                         nameCrownClosureRaster= "rast.vri2017_crownclosure"),
cutblockSeqPrepCLUS = list(nameCutblockRaster ="rast.cns_cut_bl"),
roadCLUS = list(roadMethod = 'snap', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.dt_crds_resource'),
rsfCLUS = list(calculateInterval = 2,
               checkRasters = TRUE,
               criticalHabitatTable = 'public.criticalhabitat')
)

modules <- list ("dataLoaderCLUS", "cutblockSeqPrepCLUS", "roadCLUS",  "rsfCLUS")

rsf_model_coeff <- data.table(getTableQuery("SELECT * FROM rsf_model_coeff WHERE species = 'caribou' AND population = 'DU6' and season IN ('S', 'EW', 'LW')"))
#rsf_model_coeff[, bounds := 'rast.crithabitat']
rsf_model_coeff[, static := 'Y']
rsf_model_coeff[sql == 'blockid > 0 AND age BETWEEN 0 AND 4', sql := 'rast.dt_cutblock_1_4']
rsf_model_coeff[sql == 'blockid > 0 AND age BETWEEN 5 AND 60', sql := 'rast.dt_cutblock_5o']
rsf_model_coeff[sql == 'blockid > 0 AND age BETWEEN 5 AND 9', sql := 'rast.dt_cutblock_5_9']
rsf_model_coeff[sql == 'blockid > 0 AND age BETWEEN 10 AND 60', sql := 'rast.dt_cutblock_10o']
rsf_model_coeff[sql == 'blockid > 0 AND age BETWEEN 10 AND 29', sql := 'rast.dt_cutblock_10_29']
rsf_model_coeff[sql == 'blockid > 0 AND age BETWEEN 30 AND 60', sql := 'rast.dt_cutblock_30o']

rsf_model_coeff[sql == 'roadyear >= 0', sql := 'rast.dt_crds_resource']
rsf_model_coeff[sql == 'age', sql := 'rast.vri2017_projage1']
rsf_model_coeff[sql == 'crownclosure', sql := 'rast.vri2017_crownclosure']
rsf_model_coeff[sql == 'height', sql := 'rast.vri2017_projheight1']

objects <- list (rsf_model_coeff = rsf_model_coeff)
paths <- list(
  cachePath = cacheDir,
  modulePath = moduleDir,
  inputPath = inputDir,
  outputPath = outputDir
)

mySim <- simInit (times = times, params = parameters, modules = modules,
                  objects = objects, paths = paths)

system.time({
mysimout <- spades (mySim)
})
# eventDiagram (mySimOut)
```

# Events

At each user defined time step, the `rsfCLUS` module calculates the resource selection function for the user defined species, population and season.

# Data dependencies

## Input objects

The user provides the input object: `rsf_model_coeff` that contains the resource selection function coefficients for the various covariates. In addition to the coeffiecents (beta column in the table): 

* species = declares the wildlife species for which the RSF applies (e.g., moose, caribou, wolf)

* static := declares Y/N (yes/no) whether the covariate is static, yes meaning its value will remain the same (not updated) throughout the simulation or if no, the covariate is consiered 'dynamic' and will be updated as a result of the simulation

* layer := the name of the raster stored in a psql database or the name of the updated variable in `clusdb`. 

>Note: In layer column an 'int' (i.e., intercept) is needed for each rsf. If the rsf is fit with no intercept, 'int' is required but with beta = 0.

* type :=  declares the type of dynamic variable. A value in this column is needed if the static column = N. The following types are used in the model: 

    + UP = 'Updatable' in `clusdb`, meaning the model 'calls' a variable (e.g., forest stand age) 
           that is updated in the RSQLite db 

    + DT = 'Distance To', meaning the model recalculates a DT variable (e.g., distance to cutblock or             road) based on an updated variable  

    + RC = 'Reclass' meaning the model recalculates coefficient values as classes of the covariate

* sql := the `WHERE` clause of a sql statement describing the RSQLite `clusdb` variables used in the dynamic layer, or used to call the 'static' variable from the postgres clusdb 

* reclass := the SQL for [ST_Reclass](https://postgis.net/docs/RT_ST_Reclass.html), where type = 'RC'. used to convert the reclass covariate to the beta coefficent value - follows the [reclassexpr](https://postgis.net/docs/reclassarg.html) where '(' means greater than, '[' means greater then or equal to. Ex. [a-b] = a <= x <= b in comparison to (a-b) = a < x < b

* mean:= the mean of the covariate data used to calculate the rsf; this is used where data were standardized i.e., (x-mean)/sdev, to calculate standardized model coefficents and to faciliate fitting the logistic regression model; this is used to 'standardize' the covariatescalled to calcualte the rsf; set to 0 where covariates were not standardized 

* sdev := the standard deviation of the covariate data used to calculate the rsf; this is used where data were standardized i.e., (x-mean)/sdev; set to 1 where covariates were not standardized 

>Note: The mean and sdev are used to standardize covariates via $x_s = \frac{x - mean}{sdev}$


```{r, example_rsf_coeff}
print(rsf_model_coeff)
```

## Output objects

The following objects are instantiated via rsfCLUS:

* pts:= A data.table of X,Y locations - used to find distances; joined to the rsfCovar data.table (below)

* rsfCovar:= A data.table of covariates used to calculate the RSF. Includes the pixelid from the provincial raster so that covariate locations can be spatially identified and is joined to the 'pts' data. This could be uploaded into clusdb? Not implemented.

* rsfGLM:= Inherits a glm class used for prediction of the RSF; creates a 'dummy' glm class object for each RSF and then overides it with the coefficient values; simplifies the rsf 'prediction' calculation by taking advantage of the 'predict' function.

* rsf:= A table within the `clusdb` RSQLite database that stores the RSF scores for each pixelid.    

# Links to other modules

Requires dataLoaderCLUS to instantiate the `clusdb` RSQLite database.

