---
title: "Huckleberry_Data_Analysis_Plant_PerCov"
author: "Cora Skaien"
date: "25/01/2022"
output: html_document
---

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)
library(rgeos)
library(car)
library(rje)
library(caret)
library(pROC)
library(visreg)
library(arm)

source(here::here("R/functions/R_Postgres.R"))
```

#Overview
This file continues from Huckleberry_Data_analysis_Plant_PA, and works with locations where huckleberry did exist to assess patterns for percent cover.

#Load in data and prep
```{r}
cutblock_plots_openings_HuckBuff_ALL_df<-read.csv(file="D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_HuckBuff_ALL_df_Jan.csv")

cutblock_plots_openings_Huck_ALL_df_PA<-subset(cutblock_plots_openings_Huck_ALL_df, cutblock_plots_openings_Huck_ALL_df$Species.Pr=="1")

```

#####################  Begin Exploratory Analyses ###########################

#Explore these Harvesting Variables:
DN1_DIS_CD
DN1_SILSYS_GP
PREP_MA
PREP_ME
PREP_BU
BRUSH_MA
BRUSH_CM
G_BGC_ZONE
OPEN_GRSAR OR AREA_SQM
PLANTED
Origin
Origin.age
TimeSinceF
TimeSinceC
START_SEASON

#And:
PAS_total
Tave_wt_dec
Tave_sp_dec
Tave_sm_dec
PPT_sp_dec
PPT_sm_dec
DD5_dec
NFFD_dec

TSAND
PH2
MODIS_LC (land cover type)
SAI_rec
dem_ha_bc
LandsatCC_


```{r}
cutblock_plots_openings_Huck_ALL_df_PA$PAS_total_ann<-cutblock_plots_openings_Huck_ALL_df_PA$PAS_at+ cutblock_plots_openings_Huck_ALL_df_PA$PAS_sm + cutblock_plots_openings_Huck_ALL_df_PA$PAS_sp + cutblock_plots_openings_Huck_ALL_df_PA$PAS_wt
```


```{r}
cutblock_plots_openings_Huck_ALL_df_PA$MODIS_LC<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$MODIS_LC)
table(cutblock_plots_openings_Huck_ALL_df_PA$MODIS_LC)

cutblock_plots_openings_Huck_ALL_df_PA$PLANTED<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PLANTED)

cutblock_plots_openings_Huck_ALL_df_PA$DN1_DIS_CD<-as.factor(as.character(cutblock_plots_openings_Huck_ALL_df_PA$DN1_DIS_CD))

cutblock_plots_openings_Huck_ALL_df_PA$PREP_MA<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PREP_MA)
cutblock_plots_openings_Huck_ALL_df_PA$PREP_ME<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PREP_ME)
cutblock_plots_openings_Huck_ALL_df_PA$PREP_BU<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$PREP_BU)

cutblock_plots_openings_Huck_ALL_df_PA$BRUSH_MA<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA$BRUSH_MA)

```

Model exploration.

```{r}
#Species Present or Absent Huckleberry
model.new.1 <- lm (Species.Co ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME * PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total + Tave_wt_dec + Tave_sp_dec + Tave_sm_dec + PPT_sp_dec + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sp_dec + CMI_sm_dec + CMI_at_dec + SAI_cb + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3161.5

#Remove least significant
model.new.1 <- lm (Species.Co ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME + PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total + Tave_wt_dec + Tave_sp_dec + Tave_sm_dec + PPT_sp_dec + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sp_dec + CMI_sm_dec + CMI_at_dec + SAI_cb + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3160.2

#Remove least significant
model.new.1 <- lm (Species.Co ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME + PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total + Tave_wt_dec + Tave_sp_dec + Tave_sm_dec + PPT_sp_dec + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + CMI_at_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3157.1

#Remove least significant
model.new.1 <- lm (Species.Co ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME + PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + AREA_SQM + START_SEASON + PAS_total + PPT_sp_dec + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + CMI_at_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3152.3

#Remove least significant
model.new.1 <- lm (Species.Co ~ DN1_DIS_CD + DN1_SILSYS_GP + PREP_MA + PREP_ME + PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + TimeSinceC + START_SEASON + PAS_total + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + CMI_at_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3149.2

#Remove least significant
model.new.1 <- lm (Species.Co ~  DN1_SILSYS_GP + PREP_MA + PREP_ME + PREP_BU + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + START_SEASON + PAS_total + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + CMI_at_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3145.4

#Remove least significant
model.new.1 <- lm (Species.Co ~  DN1_SILSYS_GP + BRUSH_MA + BRUSH_CM + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + START_SEASON + PAS_total + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + CMI_at_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3139.7

#Remove least significant
model.new.1 <- lm (Species.Co ~  BRUSH_MA + G_BGC_ZONE + PLANTED + origin + origin.age + TimeSinceF + START_SEASON + PAS_total + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + CMI_at_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3133.6
summary(model.new.1)$r.squared #0.39
summary(model.new.1)$adj.r.squared #0.33

#Remove least significant
model.new.1 <- lm (Species.Co ~  BRUSH_MA + PLANTED + origin + origin.age + TimeSinceF + START_SEASON + PAS_total + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3128.2

#Remove least significant
model.new.1 <- lm (Species.Co ~  PLANTED + origin + origin.age + TimeSinceF + START_SEASON + PPT_sm_dec + DD5_dec + NFFD_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3124.9
summary(model.new.1)$r.squared #0.38
summary(model.new.1)$adj.r.squared #0.34

#Remove least significant
model.new.1 <- lm (Species.Co ~  PLANTED + origin + origin.age + TimeSinceF + START_SEASON + PPT_sm_dec + DD5_dec + TSAND + PH2 + MODIS_LC + CMI_sm_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3124.1

#Remove least significant
model.new.1 <- lm (Species.Co ~  PLANTED + origin + origin.age + TimeSinceF + START_SEASON + PPT_sm_dec + DD5_dec + PH2 + MODIS_LC + CMI_sm_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3122.95

#Remove least significant
model.new.1 <- lm (Species.Co ~  origin + origin.age + TimeSinceF + START_SEASON + PPT_sm_dec + DD5_dec + PH2 + MODIS_LC + CMI_sm_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3122.0
summary(model.new.1)$r.squared #0.38
summary(model.new.1)$adj.r.squared #0.34

#Remove TimeSinceFire because origin.age in model
model.new.1 <- lm (Species.Co ~  origin + origin.age + START_SEASON + PPT_sm_dec + DD5_dec + PH2 + MODIS_LC + CMI_sm_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3122.6
summary(model.new.1)$r.squared #0.37
summary(model.new.1)$adj.r.squared #0.34


```

#Plot partial residuals
```{r}
#Remove least significant
model.new.1 <- lm (Species.Co ~  origin + origin.age + START_SEASON + PPT_sm_dec + DD5_dec + PH2 + MODIS_LC + CMI_sm_dec + dem_ha_bc + LandsatCC_,
               data=cutblock_plots_openings_Huck_ALL_df_PA)

Anova(model.new.1, type=3) #
summary(model.new.1) #
AIC(model.new.1) #3122.0
summary(model.new.1)$r.squared #0.38
summary(model.new.1)$adj.r.squared #0.34

#Check model fit
# model diagnostic plots
binnedplot (fitted(model.new.1), 
            residuals(model.new.1), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

#Partial residual plots
visreg(model.new.1, "origin")
visreg(model.new.1, "origin.age")
visreg(model.new.1, "START_SEASON")

visreg(model.new.1, "PPT_sm_dec")
visreg(model.new.1, "DD5_dec")

visreg(model.new.1, "PH2")
visreg(model.new.1, "MODIS_LC")
visreg(model.new.1, "CMI_sm_dec")
visreg(model.new.1, "dem_ha_bc") #elevation
visreg(model.new.1, "LandsatCC_")
```


