---
title: "Huckleberry_Data_Analysis_Berry_PerCov"
author: "Cora Skaien"
date: "27/01/2022"
output: html_document
---


<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)
library(rgeos)
library(car)
library(rje)
library(caret)
library(pROC)
library(visreg)
library(arm)

source(here::here("R/functions/R_Postgres.R"))
```

#Overview
This file continues from Huckleberry_Data_analysis_Berry_PA, and works with locations where huckleberry did exist , and berries were present, to assess patterns for percent cover.


#Load in data and prep
```{r}
cutblock_plots_openings_HuckBuff_ALL_df<-read.csv(file="D:\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_HuckBuff_ALL_df_Jan.csv")

cutblock_plots_openings_Huck_ALL_df_PA<-subset(cutblock_plots_openings_Huck_ALL_df, cutblock_plots_openings_Huck_ALL_df$Species.Pr=="1")

cutblock_plots_openings_Huck_ALL_df_PA_berries<-subset(cutblock_plots_openings_Huck_ALL_df_PA, cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Pres!="0")
str(cutblock_plots_openings_Huck_ALL_df_PA_berries) #310 observations

#Berry cover
hist(cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Cove) #I would like to clarify what exactly fruit cover is
cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Cove #Lots of NAs so lots of data will be lost

#Berry abundance
hist(cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Abun)
cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Abun #Lots of NAs, so lots of data will be lost; similar as above
table(cutblock_plots_openings_Huck_ALL_df_PA$Fruit.Ab_1) #very little data, and must change one category to low if going to use

```

#####################  Begin Exploratory Analyses ###########################

#Explore these Harvesting Variables:
DN1_DIS_CD
DN1_SILSYS_GP
PREP_MA
PREP_ME
PREP_BU
BRUSH_MA
BRUSH_CM
G_BGC_ZONE
OPEN_GRSAR OR AREA_SQM
PLANTED
Origin
Origin.age
TimeSinceF
TimeSinceC
START_SEASON

#And:
PAS_total
Tave_wt
Tave_sp
Tave_sm
PPT_sp
PPT_sm
Tave_wt_1
Tave_sp_1
Tave_sm_1
PPT_sp_1
PPT_sm_1
Tave_wt_2
Tave_sp_2
Tave_sm_2
PPT_sp_2
PPT_sm_2
DD5_at
DD5_sp
DD5_sm
DD5_wt
NFFD_sp

TSAND
PH2
MODIS_LC (land cover type)
SAI_rec
dem_ha_bc
LandsatCC_

Species.Co
Species.He

```{r}
cutblock_plots_openings_Huck_ALL_df_PA_berries$PAS_total_ann<-cutblock_plots_openings_Huck_ALL_df_PA_berries$PAS_at+ cutblock_plots_openings_Huck_ALL_df_PA_berries$PAS_sm + cutblock_plots_openings_Huck_ALL_df_PA_berries$PAS_sp + cutblock_plots_openings_Huck_ALL_df_PA_berries$PAS_wt
```


```{r}
cutblock_plots_openings_Huck_ALL_df_PA_berries$MODIS_LC<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA_berries$MODIS_LC)
table(cutblock_plots_openings_Huck_ALL_df_PA_berries$MODIS_LC)

cutblock_plots_openings_Huck_ALL_df_PA_berries$PLANTED<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA_berries$PLANTED)

cutblock_plots_openings_Huck_ALL_df_PA_berries$DN1_DIS_CD<-as.factor(as.character(cutblock_plots_openings_Huck_ALL_df_PA_berries$DN1_DIS_CD))

cutblock_plots_openings_Huck_ALL_df_PA_berries$PREP_MA<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA_berries$PREP_MA)
cutblock_plots_openings_Huck_ALL_df_PA_berries$PREP_ME<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA_berries$PREP_ME)
cutblock_plots_openings_Huck_ALL_df_PA_berries$PREP_BU<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA_berries$PREP_BU)

cutblock_plots_openings_Huck_ALL_df_PA_berries$BRUSH_MA<-as.factor(cutblock_plots_openings_Huck_ALL_df_PA_berries$BRUSH_MA)

```
#Note: this is a long list to explore for a small dataset, and smaller models may need to be explored first and then combined and further assessed.

