---
title: "Productivity_Data_Prep"
author: "Cora Skaien"
date: "25/03/2022"
output: html_document
---
<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(sp)
library(keyring)
library(DBI)
library(rgeos)
library(car)
library(rje)
library(caret)
library(pROC)
library(visreg)
library(gtools)
```

Unsure about below anymore
```{r setup, include=FALSE}
source(here::here("R/functions/R_Postgres.R")) #maybe this is the problem after my update?
```

#Overview
In this file, we bring in each of our different datasets for produtcivity data, append the necessary data from spatial files, and then combine the necessary datasets together to be able to perform analyses for huckleberry and buffaloberry. In these analyses, we explore how both climatic elements, as well as silviculture practices, influence plant P/A, percent cover and berry P/A and abundance.

Below is a the procedure used in QGIS for the first dataset, with similar approach taken for subsequent datasets.

We have a dataset provided by Clayton Lamb and Garth Mowat that contains information on numerous shrub species occurrence, cover, fruit phenology, sugar content, etc. Using the consolidated cutblock layer available online (https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-), I was able to use the intersect tool in QGIS to determine which of the plots in the provided data occurred in cutblocks. Here, we will bring in both layers, append the data together between the two files, and then subset the huckleberry (Vaccinium membranaceum) and buffalo berry (Shepherdia canadensis) to see how large our dataset is.

Bring in the shape file with the coordinates within cutblocks. This data was processed in QGIS, using the consolidated cutblock layer. This data also has the relevant "Openings data" and "Activity Treatment" appended to it. Note, that when selecting points by polygons within Openings and Activity Treatment data sets, often points were duplicated. To fix this issue, we used the "Delete Duplicate Geometries" function in QGIS. Because of limitations with the data, each time we intersect with more RESULTS layers, we lose data. As a result, it is important to consider which factors (and specificity) are most important for the analysis as 30-50% of the data is lost when we use the ACTIVITY TREATMENT data as opposed to just the OPENINGS data. 

This link will be very useful for determining what the codes mean:
https://www.for.gov.bc.ca/hfp/publications/00026/fs708-14-appendix_d.htm#ad_16

This may also prove useful:
https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/silviculture/silviculture-reporting-results/technical-documentation

We have multiple datasets to work with.

##Notes from Clayton for Clayton files (Huckleberry and Buffaloberry)
Keep in mind the hierarchy of the processes as your filter the data— For Occurrence>cover>fruit occurrence>fruit abundance. For example, there are lots of cover==0% because the species didn’t occur. I chose to model each processes independently and then multiply them together, but you could shortcut and try to just model berry abundance all together, see how goes.

VegModData_BEC_CL is occurrence and cover data from BEC, my plots across BC and some Proctor Huck data. This is a big dataset useful for modelling occurrence and cover only. Not fruit occurrence or productivity. You’ll see the BEC Code (for example VACCMEM= huck), and then “_cover” or “_occ” for % cover and occurrence, respectively.

Productivity_Data is occurrence, cover, fruit presence, and fruit abundance data.I think I assigned NA’s to abundance and other values when the species didn’t occur. Some records where the species and fruit occurs don’t have fruit abundance data becuase these data weren’t always collected. These rows are NA’s too.

Time since cut and Time since Fire are in there, and are calculated relative to when the plot was done. I fixed all non-cut block and non-fire areas as 118. Lots of other variables in there for you to play with.”

##Additional considerations for data and variables
1. Temp and Rainfall in t-1 and t-2 (years before) --> ClimateBC data
   - Spring temperature
   - July temperature
   - Spring rainfall
   - July rainfall
2. Solar radiation --> but does not work from ClimateBC; need to find elsewhere; currently exploring heatload as a surrogate
3. PAS --> ClimateBC
4. Time since wildfire --> wildfire shape file
5. Whether site prep involved fire --> RESULTS OPENINGS data
6. Whether site prep involved scarification (mechanical) --> RESULTS OPENINGS data
7. Tree canopy
8. DEM: slope, elevation AND aspect all important (shift aspect to NE)


#Additional considerations for different types of analyses
Consider getting climatic variables at time t, t-1, t-2 (for berry production) and 10 year normal for cover and presence. Then append together with appropriate names for each set if variables at their timelines.

####################### BRING IN DATASETS ######################

#Dataset #1: Clayton Lamb and Garth Mowat data on huckleberry and Buffaloberry
This data has P/A of plants and of berries, and P/A of fruits and of berries. There is also a measure of sugar content (energetics) and other potentially useful and interesting response variables. This data has information for both huckleberry and buffalobery.
```{r}
cutblock_plots_openings_productivity_huck<- st_read ( dsn = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\Clayton_data_Huck_Cutblocks and RESULTS2.shp", stringsAsFactors = T) #986 observations
str(cutblock_plots_openings_productivity_huck) #230 observations

head(cutblock_plots_openings_productivity_huck)

st_crs(cutblock_plots_openings_productivity_huck)
plot(cutblock_plots_openings_productivity_huck)
table(cutblock_plots_openings_productivity_huck$ID2) 
```

Extrapolate berry abundance from 1 m-square plots as in data to 100 m-square plots like in subsequent Mackenzie data.

```{r}
cutblock_plots_openings_productivity_huck$Fruit.Abun.100<-(cutblock_plots_openings_productivity_huck$Fruit.Abun*cutblock_plots_openings_productivity_huck$Species.Co)

hist(cutblock_plots_openings_productivity_huck$Fruit.Abun.100)
cutblock_plots_openings_productivity_huck$Fruit.Abun.100 #283 data points

#Ensure all whole numbers
cutblock_plots_openings_productivity_huck$Fruit.Abun.100<-round(cutblock_plots_openings_productivity_huck$Fruit.Abun.100,0)
cutblock_plots_openings_productivity_huck$Fruit.Abun.100

hist(cutblock_plots_openings_productivity_huck$Fruit.Abun.100)

```


```{r}
DEM_slope <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc_3005.tif")
crs(DEM_slope) 

DEM_aspect <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc_3005.tif")
crs(DEM_aspect)

#Elevation
DEM_elevation <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\dem_ha_bc.tif")
crs(DEM_elevation)
crs(cutblock_plots_openings_productivity_huck) #Same!

#Stack rasters
rasStack = stack(DEM_slope, DEM_aspect, DEM_elevation)
crs(rasStack) #3005
head(rasStack)
str(rasStack)
extent(rasStack)

cutblock_plots_openings_productivity_huck$coords_x1<-st_coordinates(cutblock_plots_openings_productivity_huck)
head(cutblock_plots_openings_productivity_huck)

pointCoordinates<-data.frame(cutblock_plots_openings_productivity_huck$coords.x1, cutblock_plots_openings_productivity_huck$coords.x2)
head(pointCoordinates)

DEM_huck1=raster::extract(rasStack, pointCoordinates)
head(DEM_huck1)

#Append
cutblock_plots_openings_productivity_huck<-cbind(cutblock_plots_openings_productivity_huck, DEM_huck1)
head(cutblock_plots_openings_productivity_huck)
```

Get coordinates in decimal degrees for ClimateBC to get data at t-1 and t-2.

```{r}
crs(cutblock_plots_openings_productivity_huck)

test<-st_transform(cutblock_plots_openings_productivity_huck, crs="+proj=longlat  +datum=NAD83")
crs(test)
head(test)

test$coords_x1DD<-st_coordinates(test)
head(test)

pointCoordinatesDD<-data.frame(test$coords_x1DD[,1], test$coords_x1DD[,2])
head(pointCoordinatesDD)

head(test)
str(test)

cutblock_plots_openings_productivity_huck<-test

```

This data already has Soils data (complements of Clayton Lamb), so no need to append that data (will in datasets below).

This data also already has canopy cover, time since wildfire and RESULTS OPENINGS data appended.

Now, remove spatial elements and turn into dataframe, where we can then bring in the ClimateBC data for years t-1 and t-2 to append.

```{r}
cutblock_plots_openings_productivity_huck_df<-st_drop_geometry(cutblock_plots_openings_productivity_huck)
head(cutblock_plots_openings_productivity_huck_df)

write.csv(cutblock_plots_openings_productivity_huck_df, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Clayton_cutblocks_DEM_Huckleberry_March28.csv")

```

Take file and modify in excel to get unique ID values to append for Climate data. While here, I also created columns for the years and months in which PREP1 and PREP2 occured to better estimate when mechanical disturbance occurred for number of years since logging began, and for seasonality. No need to update climate data to have "_0" at end because does not have monthly values, so need to acquire with ClimateBC anyway.

Load back in.
```{r}
cutblock_plots_openings_productivity_huck_df<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Clayton_cutblocks_DEM_Huckleberry_March28b.csv")
head(cutblock_plots_openings_productivity_huck_df)
table(cutblock_plots_openings_productivity_huck_df$Species)


```

Once the above has been run through ClimateBC for the year of the data, the year prior, and 2 years prior for annual and seasonal variables, we will bring these files back in, append them to each other, and then append to our dataset above. Note that the conditions in the year of collection should already be present, and these do not need to be brought in at this time for this dataset.

#2013
```{r}
#Huckleberry
huck_Clayton_2013_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2013_Year_2013MSY.csv")
head(huck_Clayton_2013_0)

huck_Clayton_2013_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2013_Year_2012MSY.csv")
head(huck_Clayton_2013_1)

huck_Clayton_2013_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2013_Year_2011MSY.csv")
head(huck_Clayton_2013_2)

huck_Clayton_2013<-cbind(huck_Clayton_2013_0, huck_Clayton_2013_1, huck_Clayton_2013_2)
head(huck_Clayton_2013)
names(huck_Clayton_2013)
huck_Clayton_2013<-huck_Clayton_2013[-(541:545)]
huck_Clayton_2013<-huck_Clayton_2013[-(271:275)]

```

#2014
In newest data there is no longer any 2014 data with berry abundance information.
```{r}
#Huckleberry
#huck_Clayton_2014_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Huckleberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2014_Year_2013MSY.csv")
#head(huck_Clayton_2014_1)

#huck_Clayton_2014_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Huckleberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2014_Year_2012MSY.csv")

#huck_Clayton_2014<-cbind(huck_Clayton_2014_1, huck_Clayton_2014_2)
#head(huck_Clayton_2014)
#names(huck_Clayton_2014)
#huck_Clayton_2014<-huck_Clayton_2014[-(271:275)]

```

#2015
In newest data there is no longer any 2015 data with berry abundance information.
```{r}
#Huckleberry
#huck_Clayton_2015_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Huckleberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2015_Year_2014MSY.csv")
#head(huck_Clayton_2015_1)

#huck_Clayton_2015_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Huckleberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2015_Year_2013MSY.csv")

#huck_Clayton_2015<-cbind(huck_Clayton_2015_1, huck_Clayton_2015_2)
#head(huck_Clayton_2015)
#names(huck_Clayton_2015)
#huck_Clayton_2015<-huck_Clayton_2015[-(271:275)]

```

#2016
```{r}
#Huckleberry
huck_Clayton_2016_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2016_Year_2016MSY.csv")
head(huck_Clayton_2016_0)

huck_Clayton_2016_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2016_Year_2015MSY.csv")
head(huck_Clayton_2016_1)

huck_Clayton_2016_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2016_Year_2014MSY.csv")
head(huck_Clayton_2016_2)

huck_Clayton_2016<-cbind(huck_Clayton_2016_0, huck_Clayton_2016_1, huck_Clayton_2016_2)
head(huck_Clayton_2016)
names(huck_Clayton_2016)
huck_Clayton_2016<-huck_Clayton_2016[-(541:545)]
huck_Clayton_2016<-huck_Clayton_2016[-(271:275)]

```

#2017
```{r}
#Huckleberry
huck_Clayton_2017_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2017_Year_2017MSY.csv")
head(huck_Clayton_2017_0)

huck_Clayton_2017_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2017_Year_2016MSY.csv")
head(huck_Clayton_2017_1)

huck_Clayton_2017_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2017_Year_2015MSY.csv")
head(huck_Clayton_2017_2)

huck_Clayton_2017<-cbind(huck_Clayton_2017_0, huck_Clayton_2017_1, huck_Clayton_2017_2)
head(huck_Clayton_2017)
names(huck_Clayton_2017)
huck_Clayton_2017<-huck_Clayton_2017[-(541:545)]
huck_Clayton_2017<-huck_Clayton_2017[-(271:275)]
```

#2018
```{r}
#Huckleberry
huck_Clayton_2018_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2018_Year_2018MSY.csv")
head(huck_Clayton_2018_0)

huck_Clayton_2018_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2018_Year_2017MSY.csv")
head(huck_Clayton_2018_1)

huck_Clayton_2018_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Huck_Clayton\\ClimateBC_Huck_CLayton_2018_Year_2016MSY.csv")
head(huck_Clayton_2018_2)

huck_Clayton_2018<-cbind(huck_Clayton_2018_0, huck_Clayton_2018_1, huck_Clayton_2018_2)
head(huck_Clayton_2018)
names(huck_Clayton_2018)
huck_Clayton_2018<-huck_Clayton_2018[-(541:545)]
huck_Clayton_2018<-huck_Clayton_2018[-(271:275)]
```

Combine the data sets together.

```{r}
#huck_climate_data<-rbind(huck_Clayton_2018, huck_Clayton_2017, huck_Clayton_2016, huck_Clayton_2015, huck_Clayton_2014, huck_Clayton_2013)

huck_climate_data<-rbind(huck_Clayton_2018, huck_Clayton_2017, huck_Clayton_2016, huck_Clayton_2013)

head(huck_climate_data)
names(huck_climate_data)
  
#Join data
cutblock_plots_openings_productivity_huck_df_climate<-left_join(cutblock_plots_openings_productivity_huck_df, huck_climate_data, by="ID2") #238 pbservations as expected
head(cutblock_plots_openings_productivity_huck_df_climate) 

#Test random variable
cutblock_plots_openings_productivity_huck_df_climate$PPT01_1
cutblock_plots_openings_productivity_huck_df_climate$Species
```

Add heatload as a form of solar radiation. Equation and methodology taken from here: https://www.davidzeleny.net/anadat-r/doku.php/en:customized_functions:heatload

```{r}
# Function "heatload"
# Calculates heat load or potential annual direct incident radiation, using the formulas published in 
# McCune & Keon (2002) based on aspect, slope and latitude.
 
heatload <- function (aspect, slope, latitude, method = 'heatload', units = 'degrees', equation = 1)
{
  if (units == 'degrees')   # convert degrees to radians
    {
    aspect <- aspect/180*pi
    slope <- slope/180*pi
    aspect[slope == 0] <- 0
    latitude <- latitude/180*pi
    }  
  A <- if (method == 'heatload') abs (pi - abs (aspect - (5*pi/4))) else pi - abs (aspect-pi)
  S <- slope
  L <- if (length (latitude) == 1) rep (latitude, length (A)) else latitude
  if (equation == 1) res <- exp (-1.467 +1.582*cos(L)*cos(S) -1.500*cos(A)*sin(S)*sin(L) -0.262*sin(L)*sin(S) +0.607*sin(A)*sin(S))
  if (equation == 2) res <- exp (-1.236 +1.350*cos(L)*cos(S) -1.376*cos(A)*sin(S)*sin(L) -0.331*sin(L)*sin(S) +0.375*sin(A)*sin(S))
  if (equation == 3) res <-      +0.339 +0.808*cos(L)*cos(S)                             -0.196*sin(L)*sin(S)                       - 0.482*cos(A)*sin(S)
  return (res)
}
```

```{r}
cutblock_plots_openings_productivity_huck_df_climate$heatload <- heatload (aspect = cutblock_plots_openings_productivity_huck_df_climate$aspect_ha_bc_3005, slope = cutblock_plots_openings_productivity_huck_df_climate$slope_ha_bc_3005, latitude = cutblock_plots_openings_productivity_huck_df_climate$Latitude, equation = 3)
 
cutblock_plots_openings_productivity_huck_df_climate$heatload 
hist(cutblock_plots_openings_productivity_huck_df_climate$heatload)

```

Some other investigations.
```{r}
cutblock_plots_openings_productivity_huck_df_climate$Fruit.Abun.100
table(cutblock_plots_openings_productivity_huck_df_climate$CutBlock_O) #Indicated that 13 were not in cutblocks- investigate

Clayton_no_CB<-subset(cutblock_plots_openings_productivity_huck_df_climate, cutblock_plots_openings_productivity_huck_df_climate$CutBlock_O==0)
head(Clayton_no_CB)
table(Clayton_no_CB$YEAR, Clayton_no_CB$DST_STR_DT) #Many were cut in subsequent years; all 2016 cutblocks onwards in this subset can be removed. Investigate others.

library(stringi)
Clayton_no_CB$Cutblock_Year<-stri_sub(Clayton_no_CB$DST_STR_DT,1,4)
Clayton_no_CB2<-subset(Clayton_no_CB, Clayton_no_CB$Cutblock_Year<2016)
Clayton_no_CB2
Clayton_no_CB2$PREP1_TECH #Some have info, others not. 

#Let's remove the original 0s from the data, and then re-append the info that is not blank here.
Clayton_no_CB2$PREP1_TECH<-as.factor(Clayton_no_CB2$PREP1_TECH)
Clayton_no_CB3<-subset(Clayton_no_CB2, Clayton_no_CB2$PREP1_TECH!="NA")
str(Clayton_no_CB3)
Clayton_no_CB3$PREP1_TECH #Left with just one that was burned.

#Note, when looking on QGIS, ID2 of 3019 just on edge of cutblock and should be included.

```


```{r}
library(stringi)
cutblock_plots_openings_productivity_huck_df_climate$Cutblock_Year<-stri_sub(cutblock_plots_openings_productivity_huck_df_climate$DST_STR_DT,1,4)

cutblock_plots_openings_productivity_huck_df_climate<-subset(cutblock_plots_openings_productivity_huck_df_climate, cutblock_plots_openings_productivity_huck_df_climate$CutBlock_O=="1")

cutblock_plots_openings_productivity_huck_df_climate2<-rbind(cutblock_plots_openings_productivity_huck_df_climate, Clayton_no_CB3)

str(cutblock_plots_openings_productivity_huck_df_climate2) #226 observations

cutblock_plots_openings_productivity_huck_df_climate<-cutblock_plots_openings_productivity_huck_df_climate2
```

Investigate time since fire relative to cutblock.

```{r}
cutblock_plots_openings_productivity_huck_df_climate$TimeSinceF
cutblock_plots_openings_productivity_huck_df_climate$TimeSinceC
which(cutblock_plots_openings_productivity_huck_df_climate$TimeSinceC>cutblock_plots_openings_productivity_huck_df_climate$TimeSinceF)# 26, 27, 62, 100, 148
cutblock_plots_openings_productivity_huck_df_climate[26,] #Harvest year 1977; fire year 2007
cutblock_plots_openings_productivity_huck_df_climate[27,] #Harvest year 1977, fire year 2007
cutblock_plots_openings_productivity_huck_df_climate[62,] #Harvest 2000; fire 2007
cutblock_plots_openings_productivity_huck_df_climate[100,] #Harvest 1978, fire 2007
cutblock_plots_openings_productivity_huck_df_climate[148,] #Harvest 1972, fire 1973

cutblock_plots_openings_productivity_huck_df_climateb<-cutblock_plots_openings_productivity_huck_df_climate[-148,]
cutblock_plots_openings_productivity_huck_df_climateb<-cutblock_plots_openings_productivity_huck_df_climateb[-100,]
cutblock_plots_openings_productivity_huck_df_climateb<-cutblock_plots_openings_productivity_huck_df_climateb[-62,]
cutblock_plots_openings_productivity_huck_df_climateb<-cutblock_plots_openings_productivity_huck_df_climateb[-27,]
cutblock_plots_openings_productivity_huck_df_climateb<-cutblock_plots_openings_productivity_huck_df_climateb[-26,]

#Check to ensure correctly done
which(cutblock_plots_openings_productivity_huck_df_climateb$TimeSinceC>cutblock_plots_openings_productivity_huck_df_climateb$TimeSinceF) #None, excellent

```



Save file with processed data. 
```{r}
write.csv(cutblock_plots_openings_productivity_huck_df_climateb, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_huck_df_climate_March28.csv") #221 observations
```


If need to load back in:
```{r}
cutblock_plots_openings_productivity_huck_df_climate<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_huck_df_climate_March28.csv")
head(cutblock_plots_openings_productivity_huck_df_climate)

```


##Repeat for Buffaloberry####
```{r}
cutblock_plots_openings_productivity_buff<- st_read ( dsn = "C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\CLayton_Buff_Shifted_CutblocksANdResults_March29.shp", stringsAsFactors = T) #986 observations
str(cutblock_plots_openings_productivity_buff) #92 observations

head(cutblock_plots_openings_productivity_buff)

st_crs(cutblock_plots_openings_productivity_buff)
plot(cutblock_plots_openings_productivity_buff)
table(cutblock_plots_openings_productivity_buff$Site.ID)
```

```{r}
#DEM layer = rasStack
crs(rasStack) #3005
head(rasStack)
str(rasStack)
extent(rasStack)

crs(cutblock_plots_openings_productivity_buff)

cutblock_plots_openings_productivity_buff$coords_x1<-st_coordinates(cutblock_plots_openings_productivity_buff)
head(cutblock_plots_openings_productivity_buff)

pointCoordinates<-data.frame(cutblock_plots_openings_productivity_buff$coords.x1, cutblock_plots_openings_productivity_buff$coords.x2)
head(pointCoordinates)

DEM_buff1=raster::extract(rasStack, pointCoordinates)
head(DEM_buff1)

#Append
cutblock_plots_openings_productivity_buff<-cbind(cutblock_plots_openings_productivity_buff, DEM_buff1)
head(cutblock_plots_openings_productivity_buff)
```

Get coordinates in decimal degrees for ClimateBC to get data at t-1 and t-2.

```{r}
crs(cutblock_plots_openings_productivity_buff)

test<-st_transform(cutblock_plots_openings_productivity_buff, crs="+proj=longlat  +datum=NAD83")
crs(test)
head(test)

test$coords_x1DD<-st_coordinates(test)
head(test)

pointCoordinatesDD<-data.frame(test$coords_x1DD[,1], test$coords_x1DD[,2])
head(pointCoordinatesDD)

head(test)
str(test)

cutblock_plots_openings_productivity_buff<-test


```

This data already has Soils data (complements of Clayton Lamb), so no need to append that data (will in datasets below).

This data also already has canopy cover, time since wildfire and RESULTS OPENINGS data appended.

Now, remove spatial elements and turn into dataframe, where we can then bring in the ClimateBC data for years t, t-1 and t-2 to append.

```{r}
cutblock_plots_openings_productivity_buff_df<-st_drop_geometry(cutblock_plots_openings_productivity_buff)
head(cutblock_plots_openings_productivity_buff_df)

write.csv(cutblock_plots_openings_productivity_buff_df, file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\Clayton_cutblocks_DEM_buffaloberry_March28.csv")

```

Take file and modify in excel to get unique ID values to append for Climate data.  While here, I also created columns for the years and months in which PREP1 and PREP2 occured to better estimate when mechanical disturbance occurred for number of years since logging began, and for seasonality.

Load back in.
```{r}
cutblock_plots_openings_productivity_buff_df<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\Clayton_cutblocks_DEM_buffaloberry_March28b.csv")
head(cutblock_plots_openings_productivity_buff_df)
table(cutblock_plots_openings_productivity_buff_df$Species)
table(cutblock_plots_openings_productivity_buff_df$YEAR) #Only 2013 and 2016
```

Once the above has been run through ClimateBC for the year of the data, the year prior, and 2 years prior for annual and seasonal variables, we will bring these files back in, append them to each other, and then append to our dataset above. Note that the conditions in the year of collection should already be present, and these do not need to be brought in at this time for this dataset.

#2013
```{r}
#buffaloberry
buff_Clayton_2013_0<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Clayton\\Clayton_BUFF_Climate_2013_Year_2013MSY.csv")
head(buff_Clayton_2013_0)

buff_Clayton_2013_1<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Clayton\\Clayton_BUFF_Climate_2013_Year_2012MSY.csv")
head(buff_Clayton_2013_1)

buff_Clayton_2013_2<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Clayton\\Clayton_BUFF_Climate_2013_Year_2011MSY.csv")
head(buff_Clayton_2013_2)

buff_Clayton_2013<-cbind(buff_Clayton_2013_0, buff_Clayton_2013_1, buff_Clayton_2013_2)
head(buff_Clayton_2013)
#names(buff_Clayton_2013)
buff_Clayton_2013<-buff_Clayton_2013[-(541:545)]
buff_Clayton_2013<-buff_Clayton_2013[-(271:275)]

```

#2014
New data only had 2013 and 2016.
```{r}
#buffaloberry
#buff_Clayton_2014_1<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2014_Year_2013MSY.csv")
#head(buff_Clayton_2014_1)

#buff_Clayton_2014_2<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2014_Year_2012MSY.csv")

#buff_Clayton_2014<-cbind(buff_Clayton_2014_1, buff_Clayton_2014_2)
#head(buff_Clayton_2014)
#names(buff_Clayton_2014)
#buff_Clayton_2014<-buff_Clayton_2014[-(271:275)]

```

#2015
New data only had 2013 and 2016.
```{r}
#buffaloberry
#buff_Clayton_2015_1<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2015_Year_2014MSY.csv")
#head(buff_Clayton_2015_1)

#buff_Clayton_2015_2<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2015_Year_2013MSY.csv")

#buff_Clayton_2015<-cbind(buff_Clayton_2015_1, buff_Clayton_2015_2)
#head(buff_Clayton_2015)
#names(buff_Clayton_2015)
#buff_Clayton_2015<-buff_Clayton_2015[-(271:275)]

```

#2016
```{r}
#buffaloberry
buff_Clayton_2016_0<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Clayton\\Clayton_BUFF_Climate_2016_Year_2016MSY.csv")
head(buff_Clayton_2016_0)

buff_Clayton_2016_1<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Clayton\\Clayton_BUFF_Climate_2016_Year_2015MSY.csv")
head(buff_Clayton_2016_1)

buff_Clayton_2016_2<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Clayton\\Clayton_BUFF_Climate_2016_Year_2014MSY.csv")
head(buff_Clayton_2016_2)

buff_Clayton_2016<-cbind(buff_Clayton_2016_0, buff_Clayton_2016_1, buff_Clayton_2016_2)
head(buff_Clayton_2016)
#names(buff_Clayton_2016)
buff_Clayton_2016<-buff_Clayton_2016[-(541:545)]
buff_Clayton_2016<-buff_Clayton_2016[-(271:275)]

```

#2017
New data only had 2013 and 2016.
```{r}
#buffaloberry
#buff_Clayton_2017_1<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2017_Year_2016MSY.csv")
#head(buff_Clayton_2017_1)

#buff_Clayton_2017_2<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2017_Year_2015MSY.csv")

#buff_Clayton_2017<-cbind(buff_Clayton_2017_1, buff_Clayton_2017_2)
#head(buff_Clayton_2017)
#names(buff_Clayton_2017)
#buff_Clayton_2017<-buff_Clayton_2017[-(271:275)]
```

#2018
New data only had 2013 and 2016.
```{r}
#buffaloberry
#buff_Clayton_2018_1<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2018_Year_2017MSY.csv")
#head(buff_Clayton_2018_1)

#buff_Clayton_2018_2<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\buffaloberry_Clayton_data_ClimateBC\\Clayton_data_ClimateBC_2018_Year_2016MSY.csv")

#buff_Clayton_2018<-cbind(buff_Clayton_2018_1, buff_Clayton_2018_2)
#head(buff_Clayton_2018)
#names(buff_Clayton_2018)
#buff_Clayton_2018<-buff_Clayton_2018[-(271:275)]
```

Combine the data sets together.

```{r}
buff_climate_data<-rbind(buff_Clayton_2016, buff_Clayton_2013)

head(buff_climate_data)
names(buff_climate_data)
  
#Join data
cutblock_plots_openings_productivity_buff_df_climate<-left_join(cutblock_plots_openings_productivity_buff_df, buff_climate_data, by="ID")
head(cutblock_plots_openings_productivity_buff_df_climate)
str(cutblock_plots_openings_productivity_buff_df_climate) #92 variables
str(cutblock_plots_openings_productivity_buff_df) #92 variables

#Test random variable
cutblock_plots_openings_productivity_buff_df_climate$PPT01_1
cutblock_plots_openings_productivity_buff_df_climate$Species
```

Add heatload as a form of solar radiation. Equation and methodology taken from here: https://www.davidzeleny.net/anadat-r/doku.php/en:customized_functions:heatload

```{r}
# Function "heatload"
# Calculates heat load or potential annual direct incident radiation, using the formulas published in 
# McCune & Keon (2002) based on aspect, slope and latitude.
 
heatload <- function (aspect, slope, latitude, method = 'heatload', units = 'degrees', equation = 1)
{
  if (units == 'degrees')   # convert degrees to radians
    {
    aspect <- aspect/180*pi
    slope <- slope/180*pi
    aspect[slope == 0] <- 0
    latitude <- latitude/180*pi
    }  
  A <- if (method == 'heatload') abs (pi - abs (aspect - (5*pi/4))) else pi - abs (aspect-pi)
  S <- slope
  L <- if (length (latitude) == 1) rep (latitude, length (A)) else latitude
  if (equation == 1) res <- exp (-1.467 +1.582*cos(L)*cos(S) -1.500*cos(A)*sin(S)*sin(L) -0.262*sin(L)*sin(S) +0.607*sin(A)*sin(S))
  if (equation == 2) res <- exp (-1.236 +1.350*cos(L)*cos(S) -1.376*cos(A)*sin(S)*sin(L) -0.331*sin(L)*sin(S) +0.375*sin(A)*sin(S))
  if (equation == 3) res <-      +0.339 +0.808*cos(L)*cos(S)                             -0.196*sin(L)*sin(S)                       - 0.482*cos(A)*sin(S)
  return (res)
}
```

```{r}
cutblock_plots_openings_productivity_buff_df_climate$heatload <- heatload (aspect = cutblock_plots_openings_productivity_buff_df_climate$aspect_ha_bc_3005, slope = cutblock_plots_openings_productivity_buff_df_climate$slope_ha_bc_3005, latitude = cutblock_plots_openings_productivity_buff_df_climate$Latitude, equation = 3)
 
cutblock_plots_openings_productivity_buff_df_climate$heatload 
hist(cutblock_plots_openings_productivity_buff_df_climate$heatload)

```

Some other investigations.
```{r}
cutblock_plots_openings_productivity_buff_df_climate$Fruit.Abun 
table(cutblock_plots_openings_productivity_buff_df_climate$CutBlock_O) #Indicated that 8 were not in cutblocks- investigate
cutblock_plots_openings_productivity_buff_df_climate$Fruit_Abun_100

Clayton_no_CB_Buff<-subset(cutblock_plots_openings_productivity_buff_df_climate, cutblock_plots_openings_productivity_buff_df_climate$CutBlock_O==0)
head(Clayton_no_CB_Buff)
table(Clayton_no_CB_Buff$YEAR, Clayton_no_CB_Buff$DST_STR_DT) #Many were cut in subsequent years; all 2016 cutblocks onwards in this subset can be removed. Investigate others.

library(stringi)
Clayton_no_CB_Buff$Cutblock_Year<-stri_sub(Clayton_no_CB_Buff$DST_STR_DT,1,4)
Clayton_no_CB_Buff2<-subset(Clayton_no_CB_Buff, Clayton_no_CB_Buff$Cutblock_Year<2016)
Clayton_no_CB_Buff2
Clayton_no_CB_Buff2$PREP1_TECH #Only one left, and it has NA, so remove

```


```{r}
cutblock_plots_openings_productivity_buff_df_climate<-subset(cutblock_plots_openings_productivity_buff_df_climate, cutblock_plots_openings_productivity_buff_df_climate$CutBlock_O=="1")

str(cutblock_plots_openings_productivity_buff_df_climate) #84 observations
table(cutblock_plots_openings_productivity_buff_df_climate$CutBlock_O)

```

```{r}
cutblock_plots_openings_productivity_buff_df_climate$Fruit_Abun_100<-round(cutblock_plots_openings_productivity_buff_df_climate$Fruit_Abun_100,0)

cutblock_plots_openings_productivity_buff_df_climate$Fruit_Abun_100
```


Investigate time since fire relative to cutblock.

```{r}
cutblock_plots_openings_productivity_buff_df_climate$TimeSinceF
cutblock_plots_openings_productivity_buff_df_climate$TimeSinceC
which(cutblock_plots_openings_productivity_buff_df_climate$TimeSinceC>cutblock_plots_openings_productivity_buff_df_climate$TimeSinceF)# 26, 41
cutblock_plots_openings_productivity_buff_df_climate[26,] #Harvest 1972, fire 1973
cutblock_plots_openings_productivity_buff_df_climate[41,] #Harvest 1972, fire 1973

cutblock_plots_openings_productivity_buff_df_climateb<-cutblock_plots_openings_productivity_buff_df_climate[-41,]
cutblock_plots_openings_productivity_buff_df_climateb<-cutblock_plots_openings_productivity_buff_df_climateb[-26,]

#Check to ensure correctly done
which(cutblock_plots_openings_productivity_buff_df_climateb$TimeSinceC>cutblock_plots_openings_productivity_buff_df_climateb$TimeSinceF) #None, excellent

```

Save file with processed data. 
```{r}
write.csv(cutblock_plots_openings_productivity_buff_df_climateb, file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_buff_df_climate_March28.csv") #80 observations
```

Modify on own outside and then being back in.

If need to load back in:
```{r}
cutblock_plots_openings_productivity_buff_df_climate<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_buff_df_climate_March28b.csv")
head(cutblock_plots_openings_productivity_buff_df_climate)


```


#Datasets #3: Garth Mowat and new student's (Mackenzie) data on huckleberry and buffalo berry separately.
This dataset has repeated measures of huckleberry plots from 2011-2021.It should have the same features as the above overall, but column names differ and will need to be re-named for binding datasets together.

#Some notes
1. Some 0s in some columns are not true 0s, but rather NAs. See original excel document with comments for details.
2. Check in with Clayton about the shep_kcal field (from a map?)
3. Time Since Cut and Time Since Fire in provided document do not match up with intersection results from spatial layers from the BC government

##Buffaloberry
```{r}
cutblock_plots_openings_productivity_mowatBuff<- st_read ( dsn = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\Mack_Buff_FINAL_March29.shp", stringsAsFactors = T)
head(cutblock_plots_openings_productivity_mowatBuff)
names(cutblock_plots_openings_productivity_mowatBuff) #47 observations
table(cutblock_plots_openings_productivity_mowatBuff$Species) 

cutblock_plots_openings_productivity_mowatBuff$Species<-c("Shepherdia_canadensis")

cutblock_plots_openings_productivity_mowatBuff$PREP1_AREA 
cutblock_plots_openings_productivity_mowatBuff$PREP1_TECH

```

We could consider subsetting my whether file indicates clearcut or not, but this info does not line up with our data.
```{r}
#cutblock_plots_openings_productivity_mowatBuff2<-subset(cutblock_plots_openings_productivity_mowatBuff, cutblock_plots_openings_productivity_mowatBuff$Clear_Cut=="Yes")
#head(cutblock_plots_openings_productivity_mowatBuff2) #65 datapoints within cutblocks
table(cutblock_plots_openings_productivity_mowatBuff$Clear_Cut) #14 not in cutblocks, 54 yes
#60 total when Laura looks at raw data for yes or no in cutblocks - so some descrepencies

#Check 


```

#Append DEM

```{r}
crs(cutblock_plots_openings_productivity_mowatBuff)
#Set crs
cutblock_plots_openings_productivity_mowatBuff2 <- st_transform (cutblock_plots_openings_productivity_mowatBuff, 3005)
crs(cutblock_plots_openings_productivity_mowatBuff2)

#Extract GPS locations
names(cutblock_plots_openings_productivity_mowatBuff2)

##Try this first
test<-cbind(cutblock_plots_openings_productivity_mowatBuff2, st_coordinates(cutblock_plots_openings_productivity_mowatBuff2))
head(test)

pointCoordinates_Mowat<-data.frame(test$X, test$Y)
head(pointCoordinates_Mowat)


##Extract DEM values from stacked layer. Note: This DEM stack was created prior
rasValue2=raster::extract(rasStack, pointCoordinates_Mowat)
head(rasValue2) #
str(rasValue2) #47 values
str(cutblock_plots_openings_productivity_mowatBuff2)#47 values

#Append new information
cutblock_plots_openings_productivity_mowatBuff<-cbind(cutblock_plots_openings_productivity_mowatBuff2, rasValue2)
head(cutblock_plots_openings_productivity_mowatBuff)
crs(cutblock_plots_openings_productivity_mowatBuff)
```

Also need to append the soils data, layers provided by Clayton Lamb who did extensive processing to create these layers from:http://www.env.gov.bc.ca/esd/distdata/ecosystems/Soil_Data/SOIL_DATA_FGDB/

Note: The rasters provided by Clayton only cover the SE corner of BC and thus do not apply to all datapoints. For subsequent data analyses, if including soil properties, we will lose the data with NAs in the analyses.

```{r}
crs(SoilStack) #ESPG 3005

#Extract values from SoilStack_2 for GPS coordinates in data file
SOIL_huck_Mac=raster::extract(SoilStack, pointCoordinates_Mowat)
head(SOIL_huck_Mac)
SOIL_huck_Mac #Lots of NAs for the ones outside of the raster

#Combine back into original data set
cutblock_plots_openings_productivity_mowatBuff<-cbind(cutblock_plots_openings_productivity_mowatBuff, SOIL_huck_Mac)
head(cutblock_plots_openings_productivity_mowatBuff)

```

#Save current file
```{r}
cutblock_plots_openings_productivity_mowatBuff_df<-st_drop_geometry(cutblock_plots_openings_productivity_mowatBuff)

write.csv(cutblock_plots_openings_productivity_mowatBuff_df, file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_mowatBuff_March28.csv")
```

Bring back in.

```{r}
cutblock_plots_openings_productivity_mowatBuff_df<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_mowatBuff_March28b.csv")
head(cutblock_plots_openings_productivity_mowatBuff_df)
```

Append climate data.

```{r}
Mowat_Buff_Climate2020<-read.csv(file= "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Mackenzie\\Mack_Buff_Climate_2020_Year_2020MSY.csv")
head(Mowat_Buff_Climate2020)

Mowat_Buff_Climate2019<-read.csv(file= "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Mackenzie\\Mack_Buff_Climate_2020_Year_2019MSY.csv")
head(Mowat_Buff_Climate2019)

Mowat_Buff_Climate2018<-read.csv(file= "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_Buff_Mackenzie\\Mack_Buff_Climate_2020_Year_2018MSY.csv")
head(Mowat_Buff_Climate2018)

Mowat_Buff_Climate<-cbind(Mowat_Buff_Climate2020, Mowat_Buff_Climate2019, Mowat_Buff_Climate2018)

names(Mowat_Buff_Climate)
Mowat_Buff_Climate$ID

#Remove repeated columns
Mowat_Buff_Climate<-Mowat_Buff_Climate[-(541:545)]
Mowat_Buff_Climate<-Mowat_Buff_Climate[-(271:275)]

head(Mowat_Buff_Climate)

```

```{r}
cutblock_plots_openings_productivity_mowatBuff2<-left_join(cutblock_plots_openings_productivity_mowatBuff_df, Mowat_Buff_Climate, by="ID2") 
head(cutblock_plots_openings_productivity_mowatBuff2)
cutblock_plots_openings_productivity_mowatBuff2$Tave_at_0

str(cutblock_plots_openings_productivity_mowatBuff2)
head(cutblock_plots_openings_productivity_mowatBuff2)
```

Bring in the fire data. Note that the fire data in the provided data does not match the provincial layers. We may wish to replace the fire year, and investigate.

An investigation in QGIS shows that all of the fire points had fires that were older than the cutblocks.

Determine time since fire and clearcuts.

```{r}
names(cutblock_plots_openings_productivity_mowatBuff2)

cutblock_plots_openings_productivity_mowatBuff2$Year<-c(2020)
cutblock_plots_openings_productivity_mowatBuff2$Year


#Create cutblock year
library(stringi)
cutblock_plots_openings_productivity_mowatBuff2$Cutblock_Year<-stri_sub(cutblock_plots_openings_productivity_mowatBuff2$DST_STR_DT,1,4)

cutblock_plots_openings_productivity_mowatBuff2$Cutblock_Year
str(cutblock_plots_openings_productivity_mowatBuff2$Cutblock_Year)
cutblock_plots_openings_productivity_mowatBuff2$Cutblock_Year<-as.numeric(cutblock_plots_openings_productivity_mowatBuff2$Cutblock_Year)

cutblock_plots_openings_productivity_mowatBuff2$TimeSinceCutblock<-(cutblock_plots_openings_productivity_mowatBuff2$Year-cutblock_plots_openings_productivity_mowatBuff2$Cutblock_Year)
cutblock_plots_openings_productivity_mowatBuff2$TimeSinceCutblock 

```

Add heatload.
```{r}
cutblock_plots_openings_productivity_mowatBuff2$heatload <- heatload (aspect = cutblock_plots_openings_productivity_mowatBuff2$aspect_ha_bc_3005, slope = cutblock_plots_openings_productivity_mowatBuff2$slope_ha_bc_3005, latitude = cutblock_plots_openings_productivity_mowatBuff2$LATITUDE, equation = 3)
 
cutblock_plots_openings_productivity_mowatBuff2$heatload 
hist(cutblock_plots_openings_productivity_mowatBuff2$heatload)
```

Save new file.
```{r}
write.csv(cutblock_plots_openings_productivity_mowatBuff2, file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\MowatMac_Buff_Openings_DEM_Soil_Climate_March29.csv")
```

If need to load back in data.
```{r}
cutblock_plots_openings_productivity_mowatBuff2<-read.csv(file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\MowatMac_Buff_Openings_DEM_Soil_Climate_March29.csv")

```


##Mack's Huckleberry Data
```{r}
cutblock_plots_openings_productivity_mowathuck<- st_read ( dsn = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\Mack_Huck_CutblocksRESULTS_March29b.shp", stringsAsFactors = T)
head(cutblock_plots_openings_productivity_mowathuck)
names(cutblock_plots_openings_productivity_mowathuck) #16 observations
table(cutblock_plots_openings_productivity_mowathuck$Species) 

cutblock_plots_openings_productivity_mowathuck$PREP1_AREA 
cutblock_plots_openings_productivity_mowathuck$PREP1_TECH
table(cutblock_plots_openings_productivity_mowathuck$Clear.Cut)

```

We could consider subsetting my whether file indicates clearcut or not, but this info does not line up with our data.
```{r}

table(cutblock_plots_openings_productivity_mowathuck$Clear_Cut) #All in clearcut

#Check 


```

#Append DEM

```{r}
crs(cutblock_plots_openings_productivity_mowathuck)
#Set crs
cutblock_plots_openings_productivity_mowathuck2 <- st_transform (cutblock_plots_openings_productivity_mowathuck, 3005)
crs(cutblock_plots_openings_productivity_mowathuck2)

#Extract GPS locations
names(cutblock_plots_openings_productivity_mowathuck2)

##Try this first
test<-cbind(cutblock_plots_openings_productivity_mowathuck2, st_coordinates(cutblock_plots_openings_productivity_mowathuck2))
head(test)

pointCoordinates_Mowat<-data.frame(test$X, test$Y)
head(pointCoordinates_Mowat)


##Extract DEM values from stacked layer. Note: This DEM stack was created prior
rasValue2=raster::extract(rasStack, pointCoordinates_Mowat)
head(rasValue2) #
str(rasValue2) #47 values
str(cutblock_plots_openings_productivity_mowathuck2)#47 values

#Append new information
cutblock_plots_openings_productivity_mowathuck<-cbind(cutblock_plots_openings_productivity_mowathuck2, rasValue2)
head(cutblock_plots_openings_productivity_mowathuck)
crs(cutblock_plots_openings_productivity_mowathuck)
```

Also need to append the soils data, layers provided by Clayton Lamb who did extensive processing to create these layers from:http://www.env.gov.bc.ca/esd/distdata/ecosystems/Soil_Data/SOIL_DATA_FGDB/

Note: The rasters provided by Clayton only cover the SE corner of BC and thus do not apply to all datapoints. For subsequent data analyses, if including soil properties, we will lose the data with NAs in the analyses.

```{r}
crs(SoilStack) #ESPG 3005

#Extract values from SoilStack_2 for GPS coordinates in data file
SOIL_huck_Mac=raster::extract(SoilStack, pointCoordinates_Mowat)
head(SOIL_huck_Mac)
SOIL_huck_Mac #Lots of NAs for the ones outside of the raster

#Combine back into original data set
cutblock_plots_openings_productivity_mowathuck<-cbind(cutblock_plots_openings_productivity_mowathuck, SOIL_huck_Mac)
head(cutblock_plots_openings_productivity_mowathuck)

```

#Save current file
```{r}
cutblock_plots_openings_productivity_mowathuck_df<-st_drop_geometry(cutblock_plots_openings_productivity_mowathuck)

write.csv(cutblock_plots_openings_productivity_mowathuck_df, file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_mowathuck_March28.csv")
```

Bring back in.

```{r}
cutblock_plots_openings_productivity_mowathuck_df<-read.csv(file="C:\\cora\\hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_mowathuck_March28.csv")
head(cutblock_plots_openings_productivity_mowathuck_df)
```

Append climate data.

```{r}
Mowat_huck_Climate2020<-read.csv(file= "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_huck_Mackenzie\\Mack_Huck_Climate_Year_2020MSY.csv")
head(Mowat_huck_Climate2020)

Mowat_huck_Climate2019<-read.csv(file= "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_huck_Mackenzie\\Mack_Huck_Climate_Year_2019MSY.csv")
head(Mowat_huck_Climate2019)

Mowat_huck_Climate2018<-read.csv(file= "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\March 28 2022 Data Files\\ClimateBC_huck_Mackenzie\\Mack_Huck_Climate_Year_2018MSY.csv")
head(Mowat_huck_Climate2018)

Mowat_huck_Climate<-cbind(Mowat_huck_Climate2020, Mowat_huck_Climate2019, Mowat_huck_Climate2018)

names(Mowat_huck_Climate)
Mowat_huck_Climate$ID

#Remove repeated columns
Mowat_huck_Climate<-Mowat_huck_Climate[-(541:545)]
Mowat_huck_Climate<-Mowat_huck_Climate[-(271:275)]

head(Mowat_huck_Climate)

```

```{r}
cutblock_plots_openings_productivity_mowathuck2<-left_join(cutblock_plots_openings_productivity_mowathuck_df, Mowat_huck_Climate, by="ID") 
head(cutblock_plots_openings_productivity_mowathuck2)
cutblock_plots_openings_productivity_mowathuck2$Tave_at_0

str(cutblock_plots_openings_productivity_mowathuck2)
head(cutblock_plots_openings_productivity_mowathuck2)
```

Bring in the fire data. Note that the fire data in the provided data does not match the provincial layers. We may wish to replace the fire year, and investigate.

An investigation in QGIS shows that all of the fire points had fires that were older than the cutblocks.

Determine time since fire and clearcuts.

```{r}
names(cutblock_plots_openings_productivity_mowathuck2)

cutblock_plots_openings_productivity_mowathuck2$Year<-c(2020)
cutblock_plots_openings_productivity_mowathuck2$Year

#Create cutblock year
library(stringi)
cutblock_plots_openings_productivity_mowathuck2$Cutblock_Year<-stri_sub(cutblock_plots_openings_productivity_mowathuck2$DST_STR_DT,1,4)

cutblock_plots_openings_productivity_mowathuck2$Cutblock_Year
str(cutblock_plots_openings_productivity_mowathuck2$Cutblock_Year)
cutblock_plots_openings_productivity_mowathuck2$Cutblock_Year<-as.numeric(cutblock_plots_openings_productivity_mowathuck2$Cutblock_Year)

cutblock_plots_openings_productivity_mowathuck2$TimeSinceCutblock<-(cutblock_plots_openings_productivity_mowathuck2$Year-cutblock_plots_openings_productivity_mowathuck2$Cutblock_Year)
cutblock_plots_openings_productivity_mowathuck2$TimeSinceCutblock 

```

Add heatload.
```{r}
cutblock_plots_openings_productivity_mowathuck2$heatload <- heatload (aspect = cutblock_plots_openings_productivity_mowathuck2$aspect_ha_bc_3005, slope = cutblock_plots_openings_productivity_mowathuck2$slope_ha_bc_3005, latitude = cutblock_plots_openings_productivity_mowathuck2$Latitude, equation = 3)
 
cutblock_plots_openings_productivity_mowathuck2$heatload 
hist(cutblock_plots_openings_productivity_mowathuck2$heatload)
```

Save new file.
```{r}
write.csv(cutblock_plots_openings_productivity_mowathuck2, file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\MowatMac_huck_Openings_DEM_Soil_Climate_March29.csv")
```

If need to load back in data.
```{r}
cutblock_plots_openings_productivity_mowathuck2<-read.csv(file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\MowatMac_huck_Openings_DEM_Soil_Climate_March29.csv")

```












#Dataset #2: Additional dataset from Laura Smit for Huckleberry 2011-2021. 
This data comes from repeated measure plots. As a result, for percent cover, we will only use one year's worth of data and compare to climate variables for the decade. For berry abundance, annual data will be used to compare to climate annually.

#Some Notes
1. Percent cover of plant and canopy cover was not present in every year, and estimates have been extrapolated for those.

Bring data in. 
```{r}
#Data for percent cover
Huck_Laura_Plant<-st_read ( dsn = "C:\\cora\\Hucklberry\\Laura_Plots_PerCov_March2022.shp", stringsAsFactors = T)
head(Huck_Laura_Plant) #17 data points
crs(Huck_Laura_Plant) #Will need to convert to 3005, or 9001, to use rasters

#Data for abundance
Huck_Laura_Berries<-st_read ( dsn = "C:\\cora\\Hucklberry\\Laura_Plots_ALL_March2022.shp", stringsAsFactors = T)
head(Huck_Laura_Berries) #42 datapoints
crs(Huck_Laura_Berries) #Will need to convert to 3005, or 9001, to use rasters
names(Huck_Laura_Berries)
```
Alter CRS so can append DEM data. Start with the plant data and then repeat for the berry data.

```{r}
Huck_Laura_Plant_3005<-st_transform(Huck_Laura_Plant, 3005)
crs(Huck_Laura_Plant_3005)

#Check crs of DEM stack
crs(rasStack)

Huck_Laura_Plant_3005$coords_x1<-st_coordinates(Huck_Laura_Plant_3005)
head(Huck_Laura_Plant_3005)

pointCoordinates_LauraPlant<-data.frame(Huck_Laura_Plant_3005$coords_x1[,1], Huck_Laura_Plant_3005$coords_x1[,2])
head(pointCoordinates_LauraPlant)

DEM_huck1_Laura=raster::extract(rasStack, pointCoordinates_LauraPlant)
head(DEM_huck1_Laura)

#Append
Huck_Laura_Plant_3005<-cbind(Huck_Laura_Plant_3005, DEM_huck1_Laura)
head(Huck_Laura_Plant_3005)

```

#Repeat for berries

```{r}
Huck_Laura_Berries_3005<-st_transform(Huck_Laura_Berries, 3005)
crs(Huck_Laura_Berries_3005)

#Check crs of DEM stack
crs(rasStack)

Huck_Laura_Berries_3005$coords_x1<-st_coordinates(Huck_Laura_Berries_3005)
head(Huck_Laura_Berries_3005)

pointCoordinates_LauraBerries<-data.frame(Huck_Laura_Berries_3005$coords_x1[,1], Huck_Laura_Berries_3005$coords_x1[,2])
head(pointCoordinates_LauraBerries)

DEM_huck1_Laura=raster::extract(rasStack, pointCoordinates_LauraBerries)
head(DEM_huck1_Laura)

#Append
Huck_Laura_Berries_3005<-cbind(Huck_Laura_Berries_3005, DEM_huck1_Laura)
head(Huck_Laura_Berries_3005)


```

Also need to append the soils data, layers provided by Clayton Lamb who did extensive processing to create these layers from:http://www.env.gov.bc.ca/esd/distdata/ecosystems/Soil_Data/SOIL_DATA_FGDB/

Note: The rasters provided by Clayton only cover the SE corner of BC and thus do not apply to all datapoints. 

#First for P/A data
```{r}
cofrag <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\cofrag_3005.tif")
orgcarb <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\orgcarb_3005.tif")
PH2 <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\ph2_3005.tif")
phca <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\phca_3005.tif")
tclay <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\tclay_3005.tif")
tsand <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\tsand_3005.tif")
tsilt <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\tsilt_3005.tif")
vfsand <- raster("C:\\cora\\Hucklberry\\Soil_Layers_Clayton\\vfsand_3005.tif")

#Check crs
crs(cofrag) #ESPG 3005
crs(vfsand) #3005

SoilStack<- stack(cofrag, orgcarb, PH2, phca, tclay, tsand, tsilt, vfsand)
crs(SoilStack) #ESPG 3005

#Extract values from SoilStack_2 for GPS coordinates in data file
SOIL_huck1_LauraPlant=raster::extract(SoilStack, pointCoordinates_LauraPlant)
head(SOIL_huck1_LauraPlant) #Looks good

#Combine back into original data set
Huck_Laura_Plant_3005<-cbind(Huck_Laura_Plant_3005, SOIL_huck1_LauraPlant)
head(Huck_Laura_Plant_3005)

```

Repeat for berry data.

```{r}
#Extract values from SoilStack_2 for GPS coordinates in data file
SOIL_huck1_LauraBerries=raster::extract(SoilStack, pointCoordinates_LauraBerries)
head(SOIL_huck1_LauraBerries) #Looks good

#Combine back into original data set
Huck_Laura_Berries_3005<-cbind(Huck_Laura_Berries_3005, SOIL_huck1_LauraBerries)
head(Huck_Laura_Berries_3005)
```

We also have data on plots that experienced wildfire, but need to append it. Will be easiest to append after make into dataframes. So append soils and DEM data bove prior to this step.

Make into data frame.
```{r}
Huck_Laura_Plant_df<-st_drop_geometry(Huck_Laura_Plant_3005)
str(Huck_Laura_Plant_df)
names(Huck_Laura_Plant_df)

Huck_Laura_Berries_df<-st_drop_geometry(Huck_Laura_Berries_3005)
str(Huck_Laura_Berries_df)
names(Huck_Laura_Berries_df)
```

```{r}
#Data for percent cover
Huck_Laura_Plant_burn<-st_read ( dsn = "C:\\cora\\Hucklberry\\Laura_OPENINGS_PA_FirePoints.shp", stringsAsFactors = T)

Huck_Laura_Plant_burn_df<-st_drop_geometry(Huck_Laura_Plant_burn)

#Data for abundance
Huck_Laura_Berries_burn<-st_read ( dsn = "C:\\cora\\Hucklberry\\Laura_OPENINGS_All_FirePoints.shp", stringsAsFactors = T)

Huck_Laura_Berries_burn_df<-st_drop_geometry(Huck_Laura_Berries_burn)
```

Create a time since fire category.
```{r}
Huck_Laura_Plant_burn_df$TimeSinceFire<-(Huck_Laura_Plant_burn_df$Year - Huck_Laura_Plant_burn_df$FIRE_YEAR)
head(Huck_Laura_Plant_burn_df)

Huck_Laura_Berries_burn_df$TimeSinceFire<-(Huck_Laura_Berries_burn_df$Year - Huck_Laura_Berries_burn_df$FIRE_YEAR)
head(Huck_Laura_Berries_burn_df)
names(Huck_Laura_Berries_burn_df)
Huck_Laura_Berries_burn_df$ID


```


Now combine files.
```{r}
Huck_Laura_Plant_df2<-left_join(Huck_Laura_Plant_df, Huck_Laura_Plant_burn_df, by="ID")

head(Huck_Laura_Plant_df2) 

#Repeat for berries
Huck_Laura_Berries_df2<-left_join(Huck_Laura_Berries_df, Huck_Laura_Berries_burn_df, by="ID")

head(Huck_Laura_Berries_df2) 

```

Modify Time Since Fire so that NAs are maximum value in Clayton's data of 118.

```{r}
Huck_Laura_Plant_df2$TimeSinceFire[is.na(Huck_Laura_Plant_df2$TimeSinceFire)]<- 118
Huck_Laura_Plant_df2$TimeSinceFire

Huck_Laura_Berries_df2$TimeSinceFire[is.na(Huck_Laura_Berries_df2$TimeSinceFire)]<- 118
Huck_Laura_Berries_df2$TimeSinceFire
```



#Append ClimateBC Data
In the below data being brought in, ALL data points from the file are included. However, not all were present within cutblocks, and thus, there will be more data points below than there is in the data brought in above.

#First, we will get the data for the percent cover, which involves the decadal means
```{r}
huck_Laura_plantcover_climate<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_forPerCov_coords_Decade_2011_2020SY.csv")
head(huck_Laura_plantcover_climate)
```

Append to data.
```{r}
huck_Laura_plantcover_climate$ID1<-paste(huck_Laura_plantcover_climate$Site_ID, huck_Laura_plantcover_climate$Year)

Huck_Laura_Plant_df2$ID1<-paste(Huck_Laura_Plant_df2$Site_ID.x, Huck_Laura_Plant_df2$Year)

cutblock_plots_openings_productivity_Laura_Huck_Plant<-left_join(Huck_Laura_Plant_df2, huck_Laura_plantcover_climate, by="ID1")

head(cutblock_plots_openings_productivity_Laura_Huck_Plant) #22 observations turned into 122 - something wrong

names(cutblock_plots_openings_productivity_Laura_Huck_Plant)
cutblock_plots_openings_productivity_Laura_Huck_Plant$TimeSinceFire
table(cutblock_plots_openings_productivity_Laura_Huck_Plant$ID1)

duplicated(cutblock_plots_openings_productivity_Laura_Huck_Plant)
```

If duplicated, use below.
```{r}
cutblock_plots_openings_productivity_Laura_Huck_Plant<- cutblock_plots_openings_productivity_Laura_Huck_Plant %>% distinct() 

```


#This series will be for each year annually for the berry abundance data
2011
```{r}
huck_Laura_2011_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2011_Year_2011SY.csv")
head(huck_Laura_2011_0)

huck_Laura_2011_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2011_Year_2010SY.csv")
head(huck_Laura_2011_1)

huck_Laura_2011_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2011_Year_2009SY.csv")
head(huck_Laura_2011_2)

huck_Laura_2011<-cbind(huck_Laura_2011_0, huck_Laura_2011_1, huck_Laura_2011_2)
head(huck_Laura_2011)
names(huck_Laura_2011)
huck_Laura_2011<-huck_Laura_2011[-(181:185)]
huck_Laura_2011<-huck_Laura_2011[-(271:275)]
huck_Laura_2011<-huck_Laura_2011[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2011$Year<-c(2011)
head(huck_Laura_2011)
```

2012
```{r}
huck_Laura_2012_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2012_Year_2012SY.csv")
head(huck_Laura_2012_0)

huck_Laura_2012_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2012_Year_2011SY.csv")
head(huck_Laura_2012_1)

huck_Laura_2012_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2012_Year_2010SY.csv")
head(huck_Laura_2012_2)

huck_Laura_2012<-cbind(huck_Laura_2012_0, huck_Laura_2012_1, huck_Laura_2012_2)
head(huck_Laura_2012)
names(huck_Laura_2012)
huck_Laura_2012<-huck_Laura_2012[-(181:185)]
huck_Laura_2012<-huck_Laura_2012[-(271:275)]
huck_Laura_2012<-huck_Laura_2012[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2012$Year<-c(2012)
head(huck_Laura_2012)
```

2013
```{r}
huck_Laura_2013_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2013_Year_2013SY.csv")
head(huck_Laura_2013_0)

huck_Laura_2013_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2013_Year_2012SY.csv")
head(huck_Laura_2013_1)

huck_Laura_2013_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2013_Year_2011SY.csv")
head(huck_Laura_2013_2)

huck_Laura_2013<-cbind(huck_Laura_2013_0, huck_Laura_2013_1, huck_Laura_2013_2)
head(huck_Laura_2013)
names(huck_Laura_2013)
huck_Laura_2013<-huck_Laura_2013[-(181:185)]
huck_Laura_2013<-huck_Laura_2013[-(271:275)]
huck_Laura_2013<-huck_Laura_2013[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2013$Year<-c(2013)
head(huck_Laura_2013)
```

2014
```{r}
huck_Laura_2014_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2014_Year_2014SY.csv")
head(huck_Laura_2014_0)

huck_Laura_2014_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2014_Year_2013SY.csv")
head(huck_Laura_2014_1)

huck_Laura_2014_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2014_Year_2012SY.csv")
head(huck_Laura_2014_2)

huck_Laura_2014<-cbind(huck_Laura_2014_0, huck_Laura_2014_1, huck_Laura_2014_2)
head(huck_Laura_2014)
names(huck_Laura_2014)
huck_Laura_2014<-huck_Laura_2014[-(181:185)]
huck_Laura_2014<-huck_Laura_2014[-(271:275)]
huck_Laura_2014<-huck_Laura_2014[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2014$Year<-c(2014)
head(huck_Laura_2014)
```

2015
```{r}
huck_Laura_2015_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2015_Year_2015SY.csv")
head(huck_Laura_2015_0)

huck_Laura_2015_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2015_Year_2014SY.csv")
head(huck_Laura_2015_1)

huck_Laura_2015_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2015_Year_2013SY.csv")
head(huck_Laura_2015_2)

huck_Laura_2015<-cbind(huck_Laura_2015_0, huck_Laura_2015_1, huck_Laura_2015_2)
head(huck_Laura_2015)
names(huck_Laura_2015)
huck_Laura_2015<-huck_Laura_2015[-(181:185)]
huck_Laura_2015<-huck_Laura_2015[-(271:275)]
huck_Laura_2015<-huck_Laura_2015[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2015$Year<-c(2015)
head(huck_Laura_2015)
```

2016
```{r}
huck_Laura_2016_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2016_Year_2016SY.csv")
head(huck_Laura_2016_0)

huck_Laura_2016_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2016_Year_2015SY.csv")
head(huck_Laura_2016_1)

huck_Laura_2016_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2016_Year_2014SY.csv")
head(huck_Laura_2016_2)

huck_Laura_2016<-cbind(huck_Laura_2016_0, huck_Laura_2016_1, huck_Laura_2016_2)
head(huck_Laura_2016)
names(huck_Laura_2016)
huck_Laura_2016<-huck_Laura_2016[-(181:185)]
huck_Laura_2016<-huck_Laura_2016[-(271:275)]
huck_Laura_2016<-huck_Laura_2016[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2016$Year<-c(2016)
head(huck_Laura_2016)
```

2017
```{r}
huck_Laura_2017_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2017_Year_2017SY.csv")
head(huck_Laura_2017_0)

huck_Laura_2017_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2017_Year_2016SY.csv")
head(huck_Laura_2017_1)

huck_Laura_2017_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2017_Year_2015SY.csv")
head(huck_Laura_2017_2)

huck_Laura_2017<-cbind(huck_Laura_2017_0, huck_Laura_2017_1, huck_Laura_2017_2)
head(huck_Laura_2017)
names(huck_Laura_2017)
huck_Laura_2017<-huck_Laura_2017[-(181:185)]
huck_Laura_2017<-huck_Laura_2017[-(271:275)]
huck_Laura_2017<-huck_Laura_2017[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2017$Year<-c(2017)
head(huck_Laura_2017)
```

2018
```{r}
huck_Laura_2018_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2018_Year_2018SY.csv")
head(huck_Laura_2018_0)

huck_Laura_2018_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2018_Year_2017SY.csv")
head(huck_Laura_2018_1)

huck_Laura_2018_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2018_Year_2016SY.csv")
head(huck_Laura_2018_2)

huck_Laura_2018<-cbind(huck_Laura_2018_0, huck_Laura_2018_1, huck_Laura_2018_2)
head(huck_Laura_2018)
names(huck_Laura_2018)
huck_Laura_2018<-huck_Laura_2018[-(181:185)]
huck_Laura_2018<-huck_Laura_2018[-(271:275)]
huck_Laura_2018<-huck_Laura_2018[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2018$Year<-c(2018)
head(huck_Laura_2018)
```

2019
```{r}
huck_Laura_2019_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2019_Year_2019SY.csv")
head(huck_Laura_2019_0)

huck_Laura_2019_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2019_Year_2018SY.csv")
head(huck_Laura_2019_1)

huck_Laura_2019_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2019_Year_2017SY.csv")
head(huck_Laura_2019_2)

huck_Laura_2019<-cbind(huck_Laura_2019_0, huck_Laura_2019_1, huck_Laura_2019_2)
head(huck_Laura_2019)
names(huck_Laura_2019)
huck_Laura_2019<-huck_Laura_2019[-(181:185)]
huck_Laura_2019<-huck_Laura_2019[-(271:275)]
huck_Laura_2019<-huck_Laura_2019[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2019$Year<-c(2019)
head(huck_Laura_2019)
```

2020
```{r}
huck_Laura_2020_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2020_Year_2020SY.csv")
head(huck_Laura_2020_0)

huck_Laura_2020_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2020_Year_2019SY.csv")
head(huck_Laura_2020_1)

huck_Laura_2020_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2020_Year_2018SY.csv")
head(huck_Laura_2020_2)

huck_Laura_2020<-cbind(huck_Laura_2020_0, huck_Laura_2020_1, huck_Laura_2020_2)
head(huck_Laura_2020)
names(huck_Laura_2020)
huck_Laura_2020<-huck_Laura_2020[-(181:185)]
huck_Laura_2020<-huck_Laura_2020[-(271:275)]
huck_Laura_2020<-huck_Laura_2020[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2020$Year<-c(2020)
head(huck_Laura_2020)
```

2021
#2021 is complicated in that ClimateBC does not yet have annual data for 2021, so the best we can do is either the decadal average, or repeating 2020. We may also wish to try and get some of the similar variables from another source, like Environment Canada? 
I tried searching Environment Canada by GPS coordinates and turned up nothing (i.e., no nearby weather stations).

```{r}
table(Huck_Laura_Berries_df2$Year) #We have 12 data points in 2021
```


```{r}
#There is no 2021 data at this time. Need to decide what to use in its place.
#huck_Laura_2021_0<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2021_Year_2021SY.csv")
#head(huck_Laura_2021_0)

huck_Laura_2021_1<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2021_Year_2020SY.csv")
head(huck_Laura_2021_1)

huck_Laura_2021_2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\Laura_data_ClimateBC\\Laura_Data_Long_2021_Year_2019SY.csv")
head(huck_Laura_2021_2)

#huck_Laura_2021<-cbind(huck_Laura_2021_0, huck_Laura_2021_1, huck_Laura_2021_2)
huck_Laura_2021<-cbind(huck_Laura_2021_1, huck_Laura_2021_2)
head(huck_Laura_2021)
names(huck_Laura_2021)
#huck_Laura_2021<-huck_Laura_2021[-(181:185)]
huck_Laura_2021<-huck_Laura_2021[-(271:275)]
huck_Laura_2021<-huck_Laura_2021[-5] #Remove elevation since unknown here

#Add the Year back in for appending later
huck_Laura_2021$Year<-c(2021)
head(huck_Laura_2021)
```

Combine the data sets together. Note: within cutblocks, we only end up with data from 2019-2021, but the data from the 2011-2021 plots inclusive are now available.

For now, make same columns.
```{r}
names(huck_Laura_2021)
names(huck_Laura_2020)
```


```{r}
#Huck_Laura_climate_data<-rbind(huck_Laura_2021, huck_Laura_2020, huck_Laura_2019, huck_Laura_2018, huck_Laura_2017, huck_Laura_2016, huck_Laura_2015, huck_Laura_2014, huck_Laura_2013, huck_Laura_2012, huck_Laura_2011)

Huck_Laura_climate_data<-rbind(huck_Laura_2020, huck_Laura_2019, huck_Laura_2018, huck_Laura_2017, huck_Laura_2016, huck_Laura_2015, huck_Laura_2014, huck_Laura_2013, huck_Laura_2012, huck_Laura_2011) #2021 excluded for now until find solution

head(Huck_Laura_climate_data)
names(Huck_Laura_climate_data)

Huck_Laura_climate_data$ID1<-paste(Huck_Laura_climate_data$Site_ID, Huck_Laura_climate_data$Year) #312 observations

#Below may need updating once file brought in to proper names
Huck_Laura_Berries_df2$ID1<-paste(Huck_Laura_Berries_df2$Site_ID.x, Huck_Laura_Berries_df2$Year) #42 observations
  
cutblock_plots_openings_productivity_Laura_Huck_Berries<-left_join(Huck_Laura_Berries_df2, Huck_Laura_climate_data, by="ID1")
head(cutblock_plots_openings_productivity_Laura_Huck_Berries) #192 observations


cutblock_plots_openings_productivity_Laura_Huck_Berries<- cutblock_plots_openings_productivity_Laura_Huck_Berries %>% distinct() #42 observations

head(cutblock_plots_openings_productivity_Laura_Huck_Berries)

```

Add heatload.

```{r}
#Plant Data
cutblock_plots_openings_productivity_Laura_Huck_Plant$heatload <- heatload (aspect = cutblock_plots_openings_productivity_Laura_Huck_Plant$aspect_ha_bc, slope = cutblock_plots_openings_productivity_Laura_Huck_Plant$slope_ha_bc, latitude = cutblock_plots_openings_productivity_Laura_Huck_Plant$Lat.x, equation = 3) 
 
cutblock_plots_openings_productivity_Laura_Huck_Plant$heatload 
hist(cutblock_plots_openings_productivity_Laura_Huck_Plant$heatload)

#Berry Data
cutblock_plots_openings_productivity_Laura_Huck_Berries$heatload <- heatload (aspect = cutblock_plots_openings_productivity_Laura_Huck_Berries$aspect_ha_bc, slope = cutblock_plots_openings_productivity_Laura_Huck_Berries$slope_ha_bc, latitude = cutblock_plots_openings_productivity_Laura_Huck_Berries$Lat.x, equation = 3)
 
cutblock_plots_openings_productivity_Laura_Huck_Berries$heatload  
hist(cutblock_plots_openings_productivity_Laura_Huck_Berries$heatload)
```


#create Harvest year and time since Harvest

```{r}
#Berry data
cutblock_plots_openings_productivity_Laura_Huck_Berries$Cutblock_Year<-stri_sub(cutblock_plots_openings_productivity_Laura_Huck_Berries$DST_STR_DT.x,1,4)
cutblock_plots_openings_productivity_Laura_Huck_Berries$Cutblock_Year
str(cutblock_plots_openings_productivity_Laura_Huck_Berries$Cutblock_Year)
cutblock_plots_openings_productivity_Laura_Huck_Berries$Cutblock_Year<-as.numeric(cutblock_plots_openings_productivity_Laura_Huck_Berries$Cutblock_Year)

cutblock_plots_openings_productivity_Laura_Huck_Berries$TimeSinceCutblock<-(cutblock_plots_openings_productivity_Laura_Huck_Berries$Year.x-cutblock_plots_openings_productivity_Laura_Huck_Berries$Cutblock_Year)
cutblock_plots_openings_productivity_Laura_Huck_Berries$TimeSinceCutblock

#percent Cover data
cutblock_plots_openings_productivity_Laura_Huck_Plant$Cutblock_Year<-stri_sub(cutblock_plots_openings_productivity_Laura_Huck_Plant$DST_STR_DT.x,1,4)
cutblock_plots_openings_productivity_Laura_Huck_Plant$Cutblock_Year
cutblock_plots_openings_productivity_Laura_Huck_Plant$Cutblock_Year<-as.numeric(cutblock_plots_openings_productivity_Laura_Huck_Plant$Cutblock_Year)

cutblock_plots_openings_productivity_Laura_Huck_Plant$TimeSinceCutblock<-(cutblock_plots_openings_productivity_Laura_Huck_Plant$Year.x-cutblock_plots_openings_productivity_Laura_Huck_Plant$Cutblock_Year)
cutblock_plots_openings_productivity_Laura_Huck_Plant$TimeSinceCutblock

```

Save files.
```{r}
write.csv(cutblock_plots_openings_productivity_Laura_Huck_Plant, file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Laura_Huck_Plant.csv")

write.csv(cutblock_plots_openings_productivity_Laura_Huck_Berries, file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Laura_Huck_Berries.csv")
```

If need to bring files back in:
```{r}
cutblock_plots_openings_productivity_Laura_Huck_Plant<-read.csv(file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Laura_Huck_Plant.csv")
head(cutblock_plots_openings_productivity_Laura_Huck_Plant)

cutblock_plots_openings_productivity_Laura_Huck_Berries<-read.csv(file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Laura_Huck_Berries.csv")
head(cutblock_plots_openings_productivity_Laura_Huck_Berries)
```



#Datasets #4: Long-term Buffaloberry Plots Garth Mowat from Laura Smit
This dataset is provided by Laura Smit and contains data rom repeated measures plots for buffaloberry from 2016-2021. It contains the height and width of plants, canopy cover for some years (but not all), berry count, berry phenology, and information on percent infection present on berries and plant leaves.

Notes:
1. Often did not count the berries that were infected; so production may have been higher than stated, but useable berries lower.
2. In more recent years, often counted when green, so may not have as many infected accounted for. And not all green berries will turn into berries that are actually food.
3. Sometimes says 0 berries present, but 100% infected; so there were berries present, but all infected and thus not edible.

Bring in the data that occur within cutblocks.
```{r}
Laura_buffalo_data<-st_read ( dsn = "C:\\cora\\Hucklberry\\Laura_Buffaloberry_Plots_Cutblocks.shp", stringsAsFactors = T)
head(Laura_buffalo_data)
st_crs(Laura_buffalo_data) #9001, must convert

Laura_buffalo_data_3005<-st_transform(Laura_buffalo_data, 3005)
crs(Laura_buffalo_data_3005)

```

Append DEM data.
```{r}
crs(rasStack) #3005

Laura_buffalo_data_3005$coords_x1<-st_coordinates(Laura_buffalo_data_3005)
head(Laura_buffalo_data_3005)

pointCoordinates<-data.frame(Laura_buffalo_data_3005$coords_x1, Laura_buffalo_data_3005$coords_x1)
head(pointCoordinates)
pointCoordinates2<-pointCoordinates[1:2]
pointCoordinates2

DEM_buff2=raster::extract(rasStack, pointCoordinates2)
head(DEM_buff2)

#Append
Laura_buffalo_data_3005<-cbind(Laura_buffalo_data_3005, DEM_buff2)
head(Laura_buffalo_data_3005)

```

Append soils data for those that overlap.

```{r}
crs(SoilStack) #ESPG 3005

#Extract values from SoilStack_2 for GPS coordinates in data file
SOIL_buff2=raster::extract(SoilStack, pointCoordinates2)
head(SOIL_buff2) #Looks good

#Combine back into original data set
Laura_buffalo_data_3005<-cbind(Laura_buffalo_data_3005, SOIL_buff2)
head(Laura_buffalo_data_3005)
```

Make into data frame.
```{r}
Buff_Laura_df<-st_drop_geometry(Laura_buffalo_data_3005)
str(Buff_Laura_df)
names(Buff_Laura_df)

```

Save file.

```{r}
write.csv(Buff_Laura_df, file="C:\\cora\\Hucklberry\\Buff_Laura_df.csv")
```

Load in fire points for this dataset.

```{r}
##Need to update below file name
Buff_Laura_burn<-st_read ( dsn = "C:\\cora\\Hucklberry\\Laura_Buffaloberry_Plots_Cutblocks_Fire2.shp", stringsAsFactors = T)

Buff_Laura_burn_df<-st_drop_geometry(Buff_Laura_burn)
head(Buff_Laura_burn_df)
```

```{r}
Buff_Laura_burn_df$TimeSinceFire<-(Buff_Laura_burn_df$Visit_Year - Buff_Laura_burn_df$FIRE_YEAR)
head(Buff_Laura_burn_df)
Buff_Laura_burn_df$TimeSinceFire
```


Now combine files.
```{r}
str(Buff_Laura_df) #28 observations
str(Buff_Laura_burn_df) #36 observations. Some plots must have burned more than once.
table(Buff_Laura_burn_df$ID2) #2 replicates per location
table(Buff_Laura_burn_df$ID2, Buff_Laura_burn_df$FIRE_YEAR) #There was a 1929 fire and a 1936 fire in every plot

Buff_Laura_burn_df<-subset(Buff_Laura_burn_df, Buff_Laura_burn_df$FIRE_YEAR=="1936") #18 observations

Buff_Laura_df2<-left_join(Buff_Laura_df, Buff_Laura_burn_df, by="ID2")
str(Buff_Laura_df2) #28 observations

head(Buff_Laura_df2) 
Buff_Laura_df2$TimeSinceFire
```

Modify Time Since Fire so that NAs are maximum value in Clayton's data of 118.

```{r}
Buff_Laura_df2$TimeSinceFire[is.na(Buff_Laura_df2$TimeSinceFire)]<- 118
Buff_Laura_df2$TimeSinceFire
```

#Determine if cutblocks or fire more recent

```{r}

#Create cutblock year
library(stringi)
Buff_Laura_df2$Cutblock_Year<-stri_sub(Buff_Laura_df2$DSTRBSTDT.x,1,4)

Buff_Laura_df2$Cutblock_Year
Buff_Laura_df2$Cutblock_Year<-as.numeric(Buff_Laura_df2$Cutblock_Year)

Buff_Laura_df2$TimeSinceCutblock<-(Buff_Laura_df2$Visit_Year.x-Buff_Laura_df2$Cutblock_Year)
Buff_Laura_df2$TimeSinceCutblock

#Compare
Buff_Laura_df2$origin<-ifelse(Buff_Laura_df2$TimeSinceFire<Buff_Laura_df2$TimeSinceCutblock, 1,0)
Buff_Laura_df2$origin #All fires in 1936 and all cutblocks more recent. All data can be used.
Buff_Laura_df2$TimeSinceFire


```

Add heatload.
#Remember need in decimal degrees lat long
```{r}
Buff_Laura_df2$heatload <- heatload (aspect = Buff_Laura_df2$aspect_ha_bc_3005, slope = Buff_Laura_df2$slope_ha_bc_3005, latitude = Buff_Laura_df2$Shrub.Lati.x, equation = 3)
 
Buff_Laura_df2$heatload 
hist(Buff_Laura_df2$heatload)
```

#Append ClimateBC Data




##Investigate berries percent infected
```{r}
Buff_Laura_df2$Percent.Be.x

#Losing numbers in below
Buff_Laura_df2$Percent.Be<-as.numeric(as.factor(Buff_Laura_df2$Percent.Be.x))
Buff_Laura_df2$Percent.Be
Buff_Laura_df2$Percent.Be.x[is.na(Buff_Laura_df2$Percent.Be.x)]<-0

plot(Buff_Laura_df2$Berry.Coun.x, Buff_Laura_df2$Percent.Be.x)

```



```{r}
Buff_Laura_df2$Canopy.Cov.x #Use this one
Buff_Laura_df2$Canopy.Cov.y #Do not use this one - missing second half of data
```







################# Now that we have the data in, combine files as appropriate #################

#Combine appropriate files

```{r}
head(cutblock_plots_openings_productivity_HuckBuff_ALL_df3b)
table(cutblock_plots_openings_productivity_HuckBuff_ALL_df3b$Species.y) #240 buffaloberry; 699 huckleberry
head(cutblock_plots_openings_productivity_Laura_Huck_Berries) #Only Huckleberry
cutblock_plots_openings_productivity_Laura_Huck_Berries$Species.y<-c("Vaccinium_membranaceum")
cutblock_plots_openings_productivity_Laura_Huck_Berries$Species.x<-c("Vaccinium_membranaceum")
head(cutblock_plots_openings_productivity_mowatBuff2) #Only Buffaloberry
#head(cutblock_plots_openings_productivity_BECHuck_df) #only huckleberry

#Separate by species
cutblock_plots_openings_productivity_Buff_ALL_df<-subset(cutblock_plots_openings_productivity_HuckBuff_ALL_df3b, cutblock_plots_openings_productivity_HuckBuff_ALL_df3b$Species.y=="Shepherdia_canadensis")
cutblock_plots_openings_productivity_Huck_ALL_df<-subset(cutblock_plots_openings_productivity_HuckBuff_ALL_df3b, cutblock_plots_openings_productivity_HuckBuff_ALL_df3b$Species.y=="Vaccinium_membranaceum")

#Because sample size increased, see if in cutblocks
table(cutblock_plots_openings_productivity_Buff_ALL_df$CutBlock_O)#Suggests 49 not in cutblocks
table(cutblock_plots_openings_productivity_Huck_ALL_df$CutBlock_O) #Suggests 99 not in cutblocks

cutblock_plots_openings_productivity_Buff_ALL_df2<-subset(cutblock_plots_openings_productivity_Buff_ALL_df, cutblock_plots_openings_productivity_Buff_ALL_df$CutBlock_O=="1")

cutblock_plots_openings_productivity_Huck_ALL_df2<-subset(cutblock_plots_openings_productivity_Huck_ALL_df, cutblock_plots_openings_productivity_Huck_ALL_df$CutBlock_O=="1")
```

Save Buff data for later.

```{r}
write.csv(cutblock_plots_openings_productivity_Buff_ALL_df2, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Buff_ALL_df2.csv")
```


```{r}
#Ensure names consistent between files to be combined
## 1. cutblock_plots_openings_productivity_Huck_ALL_df_Huck, cutblock_plots_openings_productivity_BECHuck_df
names(cutblock_plots_openings_productivity_Huck_ALL_df2) # Key names: Species.Pr, Species.Co, Species.He, Fruit.Pres, Fruit.Cove, Fruit.Abun,  HARVEST_YE == CutBlock_Year, TimeSinceC, TimeSinceF, LandsatCC_ = Canopy Cover
head(cutblock_plots_openings_productivity_Huck_ALL_df2) #
names(cutblock_plots_openings_productivity_Laura_Huck_Berries) #  Fruit_Coun, Plant_Heig, Species_Co,  Canopy_Cov, TimeSinceCutblock, TimeSinceFire

cutblock_plots_openings_productivity_Laura_Huck_Berries$Project.x<-cutblock_plots_openings_productivity_Laura_Huck_Berries$ID

#names(cutblock_plots_openings_productivity_BECHuck_df) #key names: TotalB, HARVESTYR 
#Many other variables may qish to acquire for BEC data, like fire year, 
##Note, all climate variables NAs... need to run through climateBC and get
```

UPDATE NAMING
```{r}
#Update names in cutblock_plots_openings_productivity_Laura_Huck_Berries
cutblock_plots_openings_productivity_Laura_Huck_Berries<-rename(cutblock_plots_openings_productivity_Laura_Huck_Berries,
                   c("Species.Co"="Species_Co.x",
                     "HARVEST_YE"="Cutblock_Year",
                     "Species.He" = "Plant_Heig.x",
                     "Fruit.Abun" ="Fruit_Coun.x"))

#Change Canopy Cover name in other file
cutblock_plots_openings_productivity_Huck_ALL_df2<-rename(cutblock_plots_openings_productivity_Huck_ALL_df2,
                   c("Canopy_Cov.x"="LandsatCC_",
                     "TimeSinceFire" = "TimeSinceF",
                     "TimeSinceCutblock" = "TimeSinceC"))

cutblock_plots_openings_productivity_Laura_Huck_Berries$Species.Pr<-1
table(cutblock_plots_openings_productivity_Laura_Huck_Berries$Species.Pr)

#Combine
# fill in non-overlapping columns with NAs
cutblock_plots_openings_productivity_Huck_ALL_df2[setdiff(names(cutblock_plots_openings_productivity_Laura_Huck_Berries), names(cutblock_plots_openings_productivity_Huck_ALL_df2))] <- NA
cutblock_plots_openings_productivity_Laura_Huck_Berries[setdiff(names(cutblock_plots_openings_productivity_Huck_ALL_df2), names(cutblock_plots_openings_productivity_Laura_Huck_Berries))] <- NA

library(gtools)

cutblock_plots_openings_productivity_Huck_ALL_df_2022<-smartbind(cutblock_plots_openings_productivity_Huck_ALL_df2, cutblock_plots_openings_productivity_Laura_Huck_Berries)
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022)
```

Inspect
```{r}
cutblock_plots_openings_productivity_Huck_ALL_df_2022$HARVEST_YE
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Canopy_Cov.x
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Canopy_Cov<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Canopy_Cov.x)
cutblock_plots_openings_productivity_Huck_ALL_df_2022$TimeSinceCutblock 
cutblock_plots_openings_productivity_Huck_ALL_df_2022$TimeSinceFire
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Fruit.Abun #Many NAs because plant not present at those locations
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Fruit.Abun<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Fruit.Abun)
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.He
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.He<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.He)
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.Co
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.Co<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.Co)
```

```{r}
#Update names in cutblock_plots_openings_productivity_BECHuck_df
#cutblock_plots_openings_productivity_BECHuck_df<-rename(cutblock_plots_openings_productivity_BECHuck_df,
#                   c("Species.Cover"="TotalB",
#                     "HARVEST_YE"="HARVESTYR"))

#cutblock_plots_openings_productivity_BECHuck_df$Species.Present<-1
#table(cutblock_plots_openings_productivity_BECHuck_df$Species.Present)

#Combine
# fill in non-overlapping columns with NAs
#cutblock_plots_openings_productivity_Huck_ALL_df_Huck[setdiff(names(cutblock_plots_openings_productivity_BECHuck_df), names(cutblock_plots_openings_productivity_Huck_ALL_df_Huck))] <- NA
#cutblock_plots_openings_productivity_BECHuck_df[setdiff(names(cutblock_plots_openings_productivity_Huck_ALL_df_Huck), #names(cutblock_plots_openings_productivity_BECHuck_df))] <- NA

#cutblock_plots_openings_productivity_Huck_ALL_df<-rbind(cutblock_plots_openings_productivity_Huck_ALL_df_Huck, cutblock_plots_openings_productivity_BECHuck_df)
```


```{r}
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022) #May need to alter additional columns to be synonymous - will find out during data processing
names(cutblock_plots_openings_productivity_Huck_ALL_df_2022)

```

Save file.

```{r}
names(cutblock_plots_openings_productivity_Huck_ALL_df_2022)

#remove weird slope columns
cutblock_plots_openings_productivity_Huck_ALL_df_2022<-cutblock_plots_openings_productivity_Huck_ALL_df_2022[-500]

#remove weird aspect column
cutblock_plots_openings_productivity_Huck_ALL_df_2022<-cutblock_plots_openings_productivity_Huck_ALL_df_2022[-500]

write.csv(cutblock_plots_openings_productivity_Huck_ALL_df_2022, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Huck_ALL_df_2022b.csv")
```

Note that Laura's data when appended, did not get species name. So add now.
```{r}
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species)
cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species[is.na(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species)]<-"Vaccinium_membranaceum"

cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.x[is.na(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.x)]<-"Vaccinium_membranaceum"

cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.y[is.na(cutblock_plots_openings_productivity_Huck_ALL_df_2022$Species.y)]<-"Vaccinium_membranaceum"

```



keep in mind that we still have areas where plants did not occur, but reasonably could.
```{r}
table(cutblock_plots_openings_productivity_Huck_ALL_df2$Species.Pr)

cutblock_plots_openings_productivity_Huck_ALL_df2_PresenceOnly<-subset(cutblock_plots_openings_productivity_Huck_ALL_df2, cutblock_plots_openings_productivity_Huck_ALL_df2$Species.Pr=="1")

write.csv(cutblock_plots_openings_productivity_Huck_ALL_df2_PresenceOnly, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Huck_ALL_df2_PresenceOnly.csv")

```

If need to bring back in.

```{r}
cutblock_plots_openings_productivity_Huck_ALL_df2_PresenceOnly<-read.csv( file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Huck_ALL_df2_PresenceOnly.csv")
head(cutblock_plots_openings_productivity_Huck_ALL_df2_PresenceOnly)

cutblock_plots_openings_productivity_Huck_ALL_df_2022<-read.csv( file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Huck_ALL_df_2022.csv")
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022)
cutblock_plots_openings_productivity_Huck_ALL_df_2022$OPENING_ID
```

###### bring in Dave Wadell's additional information and append to dataframe

```{r}

silv_dt<- read.csv(file="C:\\cora\\Hucklberry\\Dave_Files\\silv_dt_b.csv")
head(silv_dt)

atu_subset<- read.csv(file="C:\\cora\\Hucklberry\\Dave_Files\\atu_subset_b.csv")
head(atu_subset)

msyt_sub<- read.csv(file="C:\\cora\\Hucklberry\\Dave_Files\\msyt_sub_b.csv")
head(msyt_sub)

```

Update Opening ID naming.

```{r}
silv_dt<-rename(silv_dt,
                   c("OPENING_ID"="opening_id"))
head(silv_dt)

atu_subset<-rename(atu_subset,
                   c("OPENING_ID"="opening_id"))
head(atu_subset)

msyt_sub<-rename(msyt_sub,
                   c("OPENING_ID"="opening_id"))
head(msyt_sub)

```

Bind using Leftjoin.
```{r}
cutblock_plots_openings_productivity_Huck_ALL_df_2022$OPENING_ID<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022$OPENING_ID)

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b<-left_join(cutblock_plots_openings_productivity_Huck_ALL_df_2022, silv_dt)
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b$pl_date_min #Mostly NAs, some not.
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b$OPENING_ID) #Mostly 1, some more, but some points were in more than one opening.

gc()
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b<-left_join(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b, msyt_sub) # recursive gc invocation if do not use gc() prior
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b$OPENING_ID) #Still the correct number of rows expected.

gc()
#Below is where we spring up from 642 attributes to 7016
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2<-left_join(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b, atu_subset) 
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$OPENING_ID)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$Species)
```

Explore below and see how to fix issue.
```{r}
#
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b)
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2)

table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b$ID3)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b$ID4<-1:nrow(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b$ID4 #Every row unique now

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2<-left_join(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b, atu_subset) 
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$OPENING_ID)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$Species)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$ID4)

#How do I represent the atu dataset fully without losing the data?
head(atu_subset) #silv_base_code, silv_technique_code, Silv_method_code,
# treatment amount, act_planted_no, 
#The above are the values that I want. So let's make a column that is 0 and 1 for the types of interest from the first 3, then summarize those columns by ID number.

#First take columns that are of interest for this data so we can work with it, and then append to original cutblock_plots_openings_productivity_Huck_ALL_df_2022_b as a summary
names(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2) #ID4 = 905; 909:911, 918:919
#cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2[646,650,651,652,659,660]

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22_a<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2[905]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22_b<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2[909:911]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22_c<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2[918:919]

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22<-cbind(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22_a, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22_b, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22_c)
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22) #All have gone to NA

#Determine what variables are present for each variable of interest, and which levels are of interest
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22$silv_base_code) 
#AU: Audit; BR: Brushing; DN: Denudation; DS: Direct Seeding (only 2); FE: Fertilization (37); JS: Juvenile Spacing; PC: Pest Control; PL: Planting; PR: Pruning (only 9); RD: Roads (only 9); SP: Site Preparation; SU: Surveys; SX: Silviculture Trials (only 3)
#Might be interested in brushing, denudation, fertilization, planting, Site Prep (but at this level, vague); investigate surveys.
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22$silv_technique_code)
#AE: Aerial (3); BI: Biological (6); BL Backlog Silviculture Prescription (5); BR: Brushing (65); BU: Burning (302); CA: Chemical Air (38); CG: Chemical Ground (65); DD: Site Disturbance (6); DE: Deactivation; DR: Drainage (2);FE: Fertilization (10); FG: Free Growinf (648); FH: Forest health; FP: Fill Planting (171); GR: Ground (?; 18); GS: Grass Seeding (18); HV: Harvest (543); HZ: Hazard; JS: Juvenile Spacing; MA: Manual (486); ME: Mechanical (466); MS: Mineral Soil Disturbance (31); OF Office Revuew (137); Pay (2)... PL: Planting (1220); RA: Regeneration Performance Assessment (77); RE: Reconnasaince (357); RG: Regn/stocking (1252); RP: Replanting (43); SP: Site Prep; SU: Surviuval (other codes but at low frequency)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22$silv_method_code)
#BROAD: Broadcast burn; BRUSH: Brush saw; cHAIN: Chain Drag; CTAIN: Container (1037); DISC: Disc trenching (5); EXCAV: Excavator; FILE: file review; HELI: Helicopter; LAND: Landings; MANCT: Manual Cutting; MOUND: Mounding; MXPLT: Mixed Stock; PATCH: machine patch scarification; PILE: Piling; PLOT: Plots; POST: Blade or Strip Post-scarification; Power: Power saw; SPOT: Spot treatment; TRAIL: Planting trail prep; WALK: Walkthrough; and many more at low frequency.
```


```{r}
#Many clear ones to remove for cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22$silv_technique_code
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b<-subset(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22$silv_technique_code!="RE")

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b<-subset(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code!="RA")

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b<-subset(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code!="OF")

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b<-subset(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code!="FH")
#Down to 5919

```

Some obvious ones to remove for cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22$silv_method_code as well

```{r}
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b<-subset(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code!="FILE")

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b<-subset(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code!="WALK") #Down to 4726
```

Now determine what remains and what is interesting within those categories
```{r}
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_base_code) 
#Interesting: BR: Brushing; FE: Fertilization (37); PL: Planting
#Unsure if these are interesting: SP: Site Preparation; SU: Surveys

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_base_code == "BR",1,0)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Fertilize<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_base_code == "FE",1,0)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_base_code == "PL",1,0)
```

Now investigate the next variable.
```{r}
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code)
#Interesting: BR: Brushing (19); BU: Burning (302); CA: Chemical Air (38); CG: Chemical Ground (65); FE: Fertilization (10); FP: Fill Planting (151); MA: Manual (485); ME: Mechanical (447); PL: Planting (1121); RP: Replanting (41)
#Not sure if this is interesting: FG: Free Growing (648); RG: Regn/stocking (1252)

#Brushing
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing2<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code == "BR",1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing2) #This is additional brushing

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing_ALL<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing2
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing_ALL<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing_ALL > 0,1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Brushing_ALL) #484 had brushing

#Fertilization
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Fert2<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code == "FE",1,0)

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Fert_ALL<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Fertilize + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Fert2
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Fert_ALL) #No repeats

#Planting: PL: Planting (1121); RP: Replanting (41); FP: Fill Planting (151)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted2<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code=="PL",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code=="RP",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code=="FP",1,0)))))
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted2)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted2, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code)

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted_ALL<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted2
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted_ALL)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted_ALL<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Planted_ALL)

#Burning
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code == "BU",1,0)

#Mechanical
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Mechanical<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code == "ME",1,0)

#Manual
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Manual<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code == "MA",1,0)

#Chemical
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Chemical<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code=="CA",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_technique_code=="CG",1,0)))
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Chemical)
```

Now investigate the last grouping

```{r}
#Last Grouping
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code)
#BROAD: Broadcast burn; BRUSH: Brush saw; CHAIN: Chain Drag;CROSS: cross-ditching; ; DISC: Disc trenching (5); EXCAV: Excavator; KNOCK: 3 meter knock down; MANCT: Manual Cutting; MANSB: Manual Stem Bending; MDOWN: Machine Knockdown; MOCUT: Motorized Cutting (Handheld); MOUND: Mounding; MXPLT: Mixed Stock; PATCH: machine patch scarification; PBUNR: Pile and burn; PILE: Piling; POST: Blade or Strip Post-scarification; PRE: Blade or Strip Pre-scarification; POWER: Power saw; SHARK: shark-fin drag; SHEAR: pruning Shears; WFIRE: wildfire.
#Unsure if interesting: CTAIN: Container (1037), PLOT: Plots

#MOUND: Mounding
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Mounding<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="MOUND",1,0)

#PILE: Piling
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Piling<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="PILE",1,0)

#Burned
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned2<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="BROAD",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="PBUNR",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="WFIRE",1,0)))))

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned_ALL<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned2
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned_ALL)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned_ALL<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned_ALL>0,1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Burned_ALL) #Still 302, so same as Burned

#BelowGroundDamage Mechanical
#CHAIN: Chain Drag;CROSS: cross-ditching; DISC: Disc trenching (5); EXCAV: Excavator; PATCH: machine patch scarification; POST: Blade or Strip Post-scarification; PRE: Blade or Strip Pre-scarification; SHARK: shark-fin drag;
#Include TRAIL and MOUND? RRIP?
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechBelowG<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="CHAIN",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="CROSS",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="DISC",1, 
                                                                        (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="EXCAV",1,
                                                                        (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="PATCH",1,
                                                                                (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="POST",1,
                                                                                                (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="PRE",1,
                                                                                                        (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="SHARK",1,
                                                                                                                (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="TRAIL",1,
                                                                                                                        (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="MOUND",1,
                                                                                                                              
                                                                               0)))))))))))))))))))
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechBelowG) #360 below ground disturbed cases; 4366 not.

#Above Ground Mechanical
#KNOCK: 3 meter knock down,  MDOWN: Machine Knockdown; MOCUT: Motorized Cutting (Handheld), BLADE, 
# Include WINDR? Winthrow. 13 are listed within mechanical, 9 not; so may have been some windthrow removal.
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Manual)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Mechanical)

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechAboveG<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="KNOCK",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="MDOWN",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="MOCUT",1, 
                                                                        (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="BLADE",1,
                                                                        (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="WINDR",1,
                                                                                (ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$silv_method_code=="PILE",1,
                                                                               0)))))))))))
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechAboveG) #93 yes, 4633 nos... might not be super useful to separate from below ground?

#Check how many had both above and below ground
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechAboveAndBelowG<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechAboveG + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechBelowG
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechAboveAndBelowG) #53 cases had both above and below ground, 400 only one or other.
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$MechAboveAndBelowG, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b$Mechanical ) #27 + 17 deemed not mechanical had mechanical above or below ground; 38 mechanical missed in designations. Which direction needs fixing?

```

Check names now and rid of names not needed
```{r}
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b

head(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2)
names(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2)
#Rid of columns not needed for appending

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-14]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-12]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-10]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-9]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-8]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-7]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-4]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-3]
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2[-2]
names(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2)
```
Get means for each group by ID4.

```{r}
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b22b2 %>%
  group_by(ID4, .drop=FALSE) %>%
  summarize(treatment_amount = sum(treatment_amount, na.rm = TRUE), 
           act_planted_no = sum(act_planted_no, na.rm = TRUE),
           Brushing_ALL = sum(Brushing_ALL, na.rm = TRUE),
           Fert_ALL = sum(Fert_ALL, na.rm = TRUE),
           Planted_ALL = sum(Planted_ALL, na.rm = TRUE),
           Burned = sum(Burned, na.rm = TRUE),
           Mechanical = sum(Mechanical, na.rm = TRUE),
           Manual= sum(Manual, na.rm = TRUE),
           Chemical = sum(Chemical, na.rm = TRUE),
           Mounding = sum(Mounding, na.rm = TRUE),
           Piling = sum(Piling, na.rm = TRUE),
           MechBelowG = sum(MechBelowG, na.rm = TRUE),
           MechAboveG = sum(MechAboveG, na.rm = TRUE)) #Get 642 variables; so missing 5 IDs. Not bad!

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Brushing_ALL<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Brushing_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Brushing_ALL) #188 brshed, 449 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Fert_ALL<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Fert_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Fert_ALL) #Only 28 plots fertilized, 609 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Planted_ALL<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Planted_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Planted_ALL) #552 planted, 85 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Burned<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Burned>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Burned) #236 burned, 401 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Mechanical<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Mechanical>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Mechanical) #279 mechanical treatment, 358 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Manual<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Manual>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Manual) #205 manual treatment, 432 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Chemical<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Chemical>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Chemical) #69 chemical treatmed, 568 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Mounding<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Mounding>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Mounding) #64 mounde, 573 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Piling<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Piling>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$Piling) #45 with pilings, 592 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$MechBelowG<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$MechBelowG>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$MechBelowG) #266 mechanical below ground, 371 not

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$MechAboveG<-ifelse(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$MechAboveG>0, 1,0)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu$MechAboveG) #75 above ground, 520 not
```

Now append data post-processing.
```{r}
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2<-left_join(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_atu) 
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2)
```

Inspect data.

```{r}

#Inspect each set
names(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2)

table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$Qa) #Main species planted
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_species2)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_species3)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_species4)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_species5)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$natural_species1)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$natural_species2)
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$natural_species3)

hist(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density1)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density_TOT<-cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density1 + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density2 + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density3 + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density4 + cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density5
hist(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density_TOT)

table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$op_cat) #Not useful
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$op_stat)

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$treatment_amount<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$treatment_amount)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$vri_age.<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$vri_age)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$rslt_age.<-as.numeric(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$rslt_age)

hist(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$treatment_amount)
hist(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$planted_density1)
hist(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$vri_age)
hist(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$rslt_age)
```

Also check because some opening IDs may have been for buffaloberry, and thus not have a species associated with it anymore.

```{r}
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$Species

cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$CutBlock_O[is.na(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$CutBlock_O)]<-1
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$CutBlock_O) #642 - fixed!
head(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2)

```


Save data.
```{r}
write.csv(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2_March.csv")

```

Can also make into presence only plots again:
```{r}
table(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$Species.Pr)
cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_PresenceOnly<-subset(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2, cutblock_plots_openings_productivity_Huck_ALL_df_2022_b2$Species.Pr=="1")
```

Save data.
```{r}
write.csv(cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_PresenceOnly, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Huck_ALL_df_2022_b_PresenceOnly.csv")
```



#######Repeat for Buffaloberry#############

bring data back in as needed.

```{r}
cutblock_plots_openings_productivity_Buff_ALL_df2<-read.csv(file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Buff_ALL_df2.csv")
head(cutblock_plots_openings_productivity_Buff_ALL_df2)
str(cutblock_plots_openings_productivity_Buff_ALL_df2) #191 observations, 490 variables

cutblock_plots_openings_productivity_mowatBuff2<-read.csv(file = "C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\MowatMac_Buff_Openings_DEM_Soil_Climate_March23b.csv")
head(cutblock_plots_openings_productivity_mowatBuff2)
str(cutblock_plots_openings_productivity_mowatBuff2) #68 observations of 474 variables
```


```{r}
## 2. cutblock_plots_openings_productivity_Buff_ALL_df2, cutblock_plots_openings_productivity_mowatBuff2
names(cutblock_plots_openings_productivity_Buff_ALL_df2)
names(cutblock_plots_openings_productivity_mowatBuff2)
head(cutblock_plots_openings_productivity_mowatBuff2)
#cutblock_plots_openings_productivity_mowatBuff2$Species<-c("Shepherdia_canadensis")

cutblock_plots_openings_productivity_mowatBuff2$Clear_Cut
cutblock_plots_openings_productivity_mowatBuff2$TimeSinceCutblock
cutblock_plots_openings_productivity_Buff_ALL_df2$TimeSinceC
cutblock_plots_openings_productivity_mowatBuff2$Canopy_Cov
cutblock_plots_openings_productivity_mowatBuff2$Canopy_C_1
cutblock_plots_openings_productivity_Buff_ALL_df2$LandsatCC_

cutblock_plots_openings_productivity_mowatBuff2$Species_Co #Buff Species Percent cover by category
cutblock_plots_openings_productivity_mowatBuff2$PERCENT__2
cutblock_plots_openings_productivity_Buff_ALL_df2$Species.Co

cutblock_plots_openings_productivity_mowatBuff2$Buffalober #Whether present or not. Some 0s.
cutblock_plots_openings_productivity_Buff_ALL_df2$Species.Pr #Lots of 0s where not present

#"Buff_Fruit" "Buff_Fru_1" "Buff_Fru_2" "count_of_B" "count_of_1" "Buff_Fru_3" "USED"
cutblock_plots_openings_productivity_mowatBuff2$Buffalob_1 #Buff_Fruit_Stage
cutblock_plots_openings_productivity_mowatBuff2$Buffalob_2 # Unsure - all 0s
cutblock_plots_openings_productivity_mowatBuff2$Buffalob_3
cutblock_plots_openings_productivity_mowatBuff2$Buffalob_4 # 
cutblock_plots_openings_productivity_mowatBuff2$Buffalob_5 
cutblock_plots_openings_productivity_mowatBuff2$Fruit_Coun #Very large numbers
cutblock_plots_openings_productivity_mowatBuff2$Fruit_Cove
cutblock_plots_openings_productivity_mowatBuff2$Fruit_Pres #0 and No same
cutblock_plots_openings_productivity_Buff_ALL_df2$Fruit.Pres
cutblock_plots_openings_productivity_Buff_ALL_df2$Fruit.Cove
cutblock_plots_openings_productivity_Buff_ALL_df2$Fruit.Abun #Also high numbers
cutblock_plots_openings_productivity_Buff_ALL_df2$Species.He

cutblock_plots_openings_productivity_mowatBuff2$count #--> count_of_Buff_Estimate_per_m2
cutblock_plots_openings_productivity_mowatBuff2$count_of_1 #--> count_of_Buffaloberrries_per_plot
cutblock_plots_openings_productivity_mowatBuff2$Buff_Fru_3 # --> Buff_Fruiting_Plant_Height_cm
cutblock_plots_openings_productivity_mowatBuff2$Latitude
cutblock_plots_openings_productivity_Buff_ALL_df2$Latitude

#mowat
cutblock_plots_openings_productivity_mowatBuff2b<-rename(cutblock_plots_openings_productivity_mowatBuff2,
                   c("Canopy_Cov"="DENSIOMETE",
                     "Species.Pr"="Buffalober",
                     "Species.Cover"="Plant_Cove",
                     "HARVEST_YE"="Harvest_Ye",
                     "CutBlock_Occurrence"="Clear_Cut",
                     "Canopy.Cov" = "DENSIOMETE",
                     "Fruit.Pres"="Fruit_Pres",
                     "Fruit.Cove"="Fruit_Cove",
                     "Species.He"="BUFF_PLANT",
                     "Fruit.Abun"="Fruit_Coun",
                     "Fruit.Phen"="Buffalob_3",
                     "TSAND"="tsand_3005",
                     "TSILT" ="tsilt_3005",
                     "VFSAND" = "vfsand_3005",
                     "TCLAY" = "tclay_3005", 
                    "PH2_0"= "ph2_3005",
                      "COFRAG_0" = "cofrag_3005",
                    "ORGCARB" = "orgcarb_3005"))

cutblock_plots_openings_productivity_Buff_ALL_df2b<-rename(cutblock_plots_openings_productivity_Buff_ALL_df2,
                   c("TimeSinceCutblock"="TimeSinceC",
                     "TimeSinceFire"="TimeSinceF",
                     "Canopy.Cov"="LandsatCC_"
                     ))


```
Now combine

```{r}
# fill in non-overlapping columns with NAs
cutblock_plots_openings_productivity_Buff_ALL_df2b[setdiff(names(cutblock_plots_openings_productivity_mowatBuff2b), names(cutblock_plots_openings_productivity_Buff_ALL_df2b))] <- NA
cutblock_plots_openings_productivity_mowatBuff2b[setdiff(names(cutblock_plots_openings_productivity_Buff_ALL_df2b), names(cutblock_plots_openings_productivity_mowatBuff2b))] <- NA

#Combine
str(cutblock_plots_openings_productivity_Buff_ALL_df2b) #191 observations, 610 variables
str(cutblock_plots_openings_productivity_mowatBuff2b) #68 observations, 610 variables

cutblock_plots_openings_productivity_Buff_ALL_df2b$DATASET<-c(1)
cutblock_plots_openings_productivity_mowatBuff2b$DATASET<-c(2)

cutblock_plots_openings_productivity_Buff_ALL_df<-smartbind(cutblock_plots_openings_productivity_Buff_ALL_df2b, cutblock_plots_openings_productivity_mowatBuff2b)
cutblock_plots_openings_productivity_Buff_ALL_df<-rbind(cutblock_plots_openings_productivity_Buff_ALL_df2b, cutblock_plots_openings_productivity_mowatBuff2b)

str(cutblock_plots_openings_productivity_Buff_ALL_df) #259 observations, 611 variables
head(cutblock_plots_openings_productivity_Buff_ALL_df)
names(cutblock_plots_openings_productivity_Buff_ALL_df)
```

Determine probelm below- it is not that data is lost; it is that it is not being plotted because naming of lat and long columns
```{r}
#The above looks like it should work, but we lose data? 
cutblock_plots_openings_productivity_Buff_ALL_df$Latitude #Not plotting because coordinates not same name

cutblock_plots_openings_productivity_Buff_ALL_df$Latitude
cutblock_plots_openings_productivity_Buff_ALL_df$LATITUDE

cutblock_plots_openings_productivity_Buff_ALL_df$Lat<-ifelse(is.na(cutblock_plots_openings_productivity_Buff_ALL_df$Latitude), cutblock_plots_openings_productivity_Buff_ALL_df$LATITUDE, cutblock_plots_openings_productivity_Buff_ALL_df$Latitude)

cutblock_plots_openings_productivity_Buff_ALL_df$Lat

cutblock_plots_openings_productivity_Buff_ALL_df$Long<-ifelse(is.na(cutblock_plots_openings_productivity_Buff_ALL_df$Latitude), cutblock_plots_openings_productivity_Buff_ALL_df$LONGITUDE, cutblock_plots_openings_productivity_Buff_ALL_df$Longitude)

cutblock_plots_openings_productivity_Buff_ALL_df$Long

```

Check other variables.
```{r}
cutblock_plots_openings_productivity_Buff_ALL_df$Fruit.Abun
cutblock_plots_openings_productivity_Buff_ALL_df$Fruit.Pres
cutblock_plots_openings_productivity_Buff_ALL_df$TCLAY
cutblock_plots_openings_productivity_Buff_ALL_df$Tave_at_0
```


Save Buffaloberry files.

```{r}
names(cutblock_plots_openings_productivity_Buff_ALL_df)

write.csv(cutblock_plots_openings_productivity_Buff_ALL_df, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Buff_ALL_df_March2022c.csv")
```



Bind using Leftjoin.
```{r}
cutblock_plots_openings_productivity_Buff_ALL_df$OPENING_ID<-as.numeric(cutblock_plots_openings_productivity_Buff_ALL_df$OPENING_ID)

cutblock_plots_openings_productivity_Buff_ALL_df_b<-left_join(cutblock_plots_openings_productivity_Buff_ALL_df, silv_dt)
head(cutblock_plots_openings_productivity_Buff_ALL_df_b)
cutblock_plots_openings_productivity_Buff_ALL_df_b$pl_date_min #Mostly NAs, some not.
table(cutblock_plots_openings_productivity_Buff_ALL_df_b$OPENING_ID) #

gc()
cutblock_plots_openings_productivity_Buff_ALL_df_b<-left_join(cutblock_plots_openings_productivity_Buff_ALL_df_b, msyt_sub) # recursive gc invocation if do not use gc() prior
table(cutblock_plots_openings_productivity_Buff_ALL_df_b$OPENING_ID) #Still the correct number of rows expected.
#Still 259 observations in above as expected.

gc()
#Below is where we spring up from 259 to 1977
cutblock_plots_openings_productivity_Buff_ALL_df_b2<-left_join(cutblock_plots_openings_productivity_Buff_ALL_df_b, atu_subset) 
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$OPENING_ID)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$Species)
```

Explore below and see how to fix issue.
```{r}
#
head(cutblock_plots_openings_productivity_Buff_ALL_df_b)
head(cutblock_plots_openings_productivity_Buff_ALL_df_b2)

table(cutblock_plots_openings_productivity_Buff_ALL_df_b$ID3)
cutblock_plots_openings_productivity_Buff_ALL_df_b$ID4<-1:nrow(cutblock_plots_openings_productivity_Buff_ALL_df_b)
cutblock_plots_openings_productivity_Buff_ALL_df_b$ID4 #Every row unique now

cutblock_plots_openings_productivity_Buff_ALL_df_b2<-left_join(cutblock_plots_openings_productivity_Buff_ALL_df_b, atu_subset) 
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$OPENING_ID)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$Species)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$ID4)

#How do I represent the atu dataset fully without losing the data?
head(atu_subset) #silv_base_code, silv_technique_code, Silv_method_code,
# treatment amount, act_planted_no, 
#The above are the values that I want. So let's make a column that is 0 and 1 for the types of interest from the first 3, then summarize those columns by ID number.

#First take columns that are of interest for this data so we can work with it, and then append to original cutblock_plots_openings_productivity_Buff_ALL_df_b as a summary
names(cutblock_plots_openings_productivity_Buff_ALL_df_b2) #ID4 = 716; 720:722, 729:730

cutblock_plots_openings_productivity_Buff_ALL_df_b22_a<-cutblock_plots_openings_productivity_Buff_ALL_df_b2[688]
cutblock_plots_openings_productivity_Buff_ALL_df_b22_b<-cutblock_plots_openings_productivity_Buff_ALL_df_b2[692:694]
cutblock_plots_openings_productivity_Buff_ALL_df_b22_c<-cutblock_plots_openings_productivity_Buff_ALL_df_b2[701:702]

cutblock_plots_openings_productivity_Buff_ALL_df_b22<-cbind(cutblock_plots_openings_productivity_Buff_ALL_df_b22_a, cutblock_plots_openings_productivity_Buff_ALL_df_b22_b, cutblock_plots_openings_productivity_Buff_ALL_df_b22_c)
head(cutblock_plots_openings_productivity_Buff_ALL_df_b22) #All have gone to NA

#Determine what variables are present for each variable of interest, and which levels are of interest
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22$silv_base_code) 
#AU: Audit; BR: Brushing; DN: Denudation; DS: Direct Seeding (only 2); FE: Fertilization (37); JS: Juvenile Spacing; PC: Pest Control; PL: Planting; RD: Roads (only 9); SP: Site Preparation; SU: Surveys; SX: Silviculture Trials (only 3)
#Might be interested in brushing, denudation, fertilization, planting, Site Prep (but at this level, vague); investigate surveys.
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22$silv_technique_code)
#BI: Biological (2); BL Backlog Silviculture Prescription (5); BR: Brushing (17); BU: Burning (60); CA: Chemical Air (26); CG: Chemical Ground (21); DD: Site Disturbance (3); DE: Deactivation (3); DR: Drainage (1);FE: Fertilization (10); FG: Free Growing (127); FH: Forest health (5); FP: Fill Planting (89); GR: Ground (?; 2); GS: Grass Seeding (1); HV: Harvest (137); HZ: Hazard (1); JS: Juvenile Spacing (7); MA: Manual (90); ME: Mechanical (131); MS: Mineral Soil Disturbance (5); OF Office Review (22); Pay (1)... PL: Planting (411); PO: Post Harvest Inspection (19); RA: Regeneration Performance Assessment (21); RE: Reconnasaince (110); RG: Regn/stocking (261); RO: Roadside (1); RP: Replanting (19); RR: Road Rehab (2); SE: Seedling Protection (20); SI:Silviculture Prescription (7); SM:Stand Management Prescription (2); SP: Site Prep (28); SR: Site Rebab (1); SU: Surviuval (51)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22$silv_method_code)
#BLADE: Blading; BROAD: Broadcast burn; BRUSH: Brush saw; CHAIN: Chain Drag; CTAIN: Container (1037); DISC: Disc trenching (5); EXCAV: Excavator; FILE: file review; HANDR: Hand pulling (removal); HELI: Helicopter; KNOCK: 3-meter knock down; LAND: Landings; MANCT: Manual Cutting; MANGI: Manual Girdling; MOUND: Mounding; MXPLT: Mixed Stock; PATCH: machine patch scarification; PILE: Piling; PLOT: Plots; POST: Blade or Strip Post-scarification; Power: Power saw; SHARK: Shark fin drag; SPOT: Spot treatment; TRAIL: Planting trail prep; WALK: Walkthrough; and many more at low frequency.
```


```{r}
#Many clear ones to remove for cutblock_plots_openings_productivity_Buff_ALL_df_b22$silv_technique_code
cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22, cutblock_plots_openings_productivity_Buff_ALL_df_b22$silv_technique_code!="RE")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="RA")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="OF")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="FH")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="PO")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="RO")
#Down to 1627

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="RR")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="PA")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="RO")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code!="SU")
#1570

```

Some obvious ones to remove for cutblock_plots_openings_productivity_Buff_ALL_df_b22$silv_method_code as well

```{r}
cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code!="FILE")

cutblock_plots_openings_productivity_Buff_ALL_df_b22b<-subset(cutblock_plots_openings_productivity_Buff_ALL_df_b22b, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code!="WALK") #Down to 1283
```

Now determine what remains and what is interesting within those categories
```{r}
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_base_code) 
#Interesting: BR: Brushing; FE: Fertilization (18); PC: Pest Control; PL: Planting
#Unsure if these are interesting: SP: Site Preparation; SU: Surveys
#Remove JS and RD; maybe SU? Surveys

cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_base_code == "BR",1,0)
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Fertilize<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_base_code == "FE",1,0)
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_base_code == "PL",1,0)
```

Now investigate the next variable.
```{r}
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code)
#Interesting: BI: Biological; BR: Brushing (6); BU: Burning (60); CA: Chemical Air (25); CG: Chemical Ground (21); DD: Site Disturbance; FE: Fertilization (10); FG: Free Growing; FP: Fill Planting (84); GS:Grass Seeding; MA: Manual (89); ME: Mechanical (126); MS: Mineral Soil Disturbance; PL: Planting (389); RG: Regen; RP: Replanting (19); SE: Seedling Protection
#Not sure if this is interesting: FG: Free Growing (648); RG: Regn/stocking (1252)

#Brushing
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing2<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code == "BR",1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing2) #This is additional brushing

cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing_ALL<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing + cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing2
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing_ALL<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing_ALL > 0,1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Brushing_ALL) #105 had brushing

#Fertilization
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Fert2<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code == "FE",1,0)

cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Fert_ALL<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Fertilize + cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Fert2
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Fert_ALL) #No repeats

#Planting: PL: Planting (1121); RP: Replanting (41); FP: Fill Planting (151)
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted2<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code=="PL",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code=="RP",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code=="FP",1,0)))))
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted2)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted2, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code)

cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted_ALL<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted + cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted2
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted_ALL)
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted_ALL<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Planted_ALL) #492 planted

#Burning
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code == "BU",1,0)

#Mechanical
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Mechanical<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code == "ME",1,0)

#Manual
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Manual<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code == "MA",1,0)

#Chemical
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Chemical<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code=="CA",1,                                       (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_technique_code=="CG",1,0)))
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Chemical)
```

Now investigate the last grouping

```{r}
#Last Grouping
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code)
#BLADE: Blading; BROAD: Broadcast burn; BRUSH: Brush saw; CHAIN: Chain Drag; CTAIN: Container (1037); DISC: Disc trenching (5); EXCAV: Excavator; FILE: file review; HANDR: Hand pulling (removal); HELI: Helicopter; KNOCK: 3-meter knock down; LAND: Landings; MANCT: Manual Cutting; MANGI: Manual Girdling; MOUND: Mounding; MXPLT: Mixed Stock; PATCH: machine patch scarification; PILE: Piling; PLOT: Plots; POST: Blade or Strip Post-scarification; Power: Power saw; SHARK: Shark fin drag; SPOT: Spot treatment; TRAIL: Planting trail prep; WALK: Walkthrough;
#Unsure if interesting: CTAIN: Container (1037), PLOT: Plots

#MOUND: Mounding
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Mounding<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="MOUND",1,0)

#PILE: Piling
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Piling<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="PILE",1,0)

#Burned
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned2<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="BROAD",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="PBUNR",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="WFIRE",1,0)))))

cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned_ALL<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned + cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned2
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned_ALL)
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned_ALL<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned_ALL>0,1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Burned_ALL) #60 burned

#BelowGroundDamage Mechanical
#BLADE; CHAIN: Chain Drag;CROSS: cross-ditching; DISC: Disc trenching (5); EXCAV: Excavator; PATCH: machine patch scarification; POST: Blade or Strip Post-scarification; PRE: Blade or Strip Pre-scarification; SHARK: shark-fin drag;
#Include TRAIL and MOUND? RRIP?
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechBelowG<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="CHAIN",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="CROSS",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="DISC",1, 
                                                                        (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="EXCAV",1,
                                                                        (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="PATCH",1,
                                                                                (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="POST",1,
                                                                                                (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="PRE",1,
                                                                                                        (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="SHARK",1,
                                                                                                                (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="TRAIL",1,
                                                                                                                        (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="MOUND",1,
                                                                                   (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="BLADE",1,                                           
                                                                               0)))))))))))))))))))))
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechBelowG) #360 below ground disturbed cases; 4366 not.

#SHould BLADE be below or above ground?

#Above Ground Mechanical
#KNOCK: 3 meter knock down,  MDOWN: Machine Knockdown; MOCUT: Motorized Cutting (Handheld), BLADE, 
# Include WINDR? Winthrow. 13 are listed within mechanical, 9 not; so may have been some windthrow removal.
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Manual)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Mechanical)

cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechAboveG<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="KNOCK",1,
                                                               (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="MDOWN",1,
                                                                       (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="MOCUT",1, 
                                                                        (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="BLADE",1,
                                                                        (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="WINDR",1,
                                                                                (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="PILE",1,
                                                                                        
                                                                                        (ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$silv_method_code=="MANGI",1,
                                                                               0)))))))))))))
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechAboveG) #93 yes, 4633 nos... might not be super useful to separate from below ground?

#Check how many had both above and below ground
cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechAboveAndBelowG<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechAboveG + cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechBelowG
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechAboveAndBelowG) #53 cases had both above and below ground, 400 only one or other.
table(cutblock_plots_openings_productivity_Buff_ALL_df_b22b$MechAboveAndBelowG, cutblock_plots_openings_productivity_Buff_ALL_df_b22b$Mechanical ) #27 + 17 deemed not mechanical had mechanical above or below ground; 38 mechanical missed in designations. Which direction needs fixing?

```

Check names now and rid of names not needed
```{r}
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b

head(cutblock_plots_openings_productivity_Buff_ALL_df_b22b2)
names(cutblock_plots_openings_productivity_Buff_ALL_df_b22b2)
#Rid of columns not needed for appending

cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-14]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-12]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-10]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-9]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-8]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-7]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-4]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-3]
cutblock_plots_openings_productivity_Buff_ALL_df_b22b2<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2[-2]
names(cutblock_plots_openings_productivity_Buff_ALL_df_b22b2)
```
Get means for each group by ID4.

```{r}
#If below results in one observation, unload "dplyr" library and load back in.
cutblock_plots_openings_productivity_Buff_ALL_df_b_atu<-cutblock_plots_openings_productivity_Buff_ALL_df_b22b2 %>%
  group_by(ID4, .drop=FALSE) %>%
  summarize(treatment_amount = sum(treatment_amount, na.rm = TRUE), 
           act_planted_no = sum(act_planted_no, na.rm = TRUE),
           Brushing_ALL = sum(Brushing_ALL, na.rm = TRUE),
           Fert_ALL = sum(Fert_ALL, na.rm = TRUE),
           Planted_ALL = sum(Planted_ALL, na.rm = TRUE),
           Burned = sum(Burned, na.rm = TRUE),
           Mechanical = sum(Mechanical, na.rm = TRUE),
           Manual= sum(Manual, na.rm = TRUE),
           Chemical = sum(Chemical, na.rm = TRUE),
           Mounding = sum(Mounding, na.rm = TRUE),
           Piling = sum(Piling, na.rm = TRUE),
           MechBelowG = sum(MechBelowG, na.rm = TRUE),
           MechAboveG = sum(MechAboveG, na.rm = TRUE)) #Get 642 variables; so missing 5 IDs. Not bad!

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Brushing_ALL<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Brushing_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Brushing_ALL) #69 brushed, 188 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Fert_ALL<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Fert_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Fert_ALL) #Only 18 plots fertilized, 239 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Planted_ALL<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Planted_ALL>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Planted_ALL) #231 planted, 26 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Burned<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Burned>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Burned) #45 burned, 212 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Mechanical<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Mechanical>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Mechanical) #91 mechanical treatment, 166 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Manual<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Manual>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Manual) #71 manual treatment, 186 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Chemical<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Chemical>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Chemical) #38 chemical treatmed, 219 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Mounding<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Mounding>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Mounding) #21 mounded, 236 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Piling<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Piling>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$Piling) #22 with pilings, 235 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$MechBelowG<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$MechBelowG>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$MechBelowG) #73 mechanical below ground, 184 not

cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$MechAboveG<-ifelse(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$MechAboveG>0, 1,0)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b_atu$MechAboveG) #39 above ground, 218 not
```

Now append data post-processing.
```{r}
cutblock_plots_openings_productivity_Buff_ALL_df_b2<-left_join(cutblock_plots_openings_productivity_Buff_ALL_df_b, cutblock_plots_openings_productivity_Buff_ALL_df_b_atu, by="ID4") 
head(cutblock_plots_openings_productivity_Buff_ALL_df_b2)
```

Inspect data.

```{r}
#Inspect each set
names(cutblock_plots_openings_productivity_Buff_ALL_df_b2)

table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$Qa) #Main species planted
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_species2)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_species3)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_species4)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_species5)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$natural_species1)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$natural_species2)
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$natural_species3)

hist(cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density1)
cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density_TOT<-cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density1 + cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density2 + cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density3 + cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density4 + cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density5
hist(cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density_TOT)

table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$op_cat) #Not useful
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$op_stat)

cutblock_plots_openings_productivity_Buff_ALL_df_b2$treatment_amount<-as.numeric(cutblock_plots_openings_productivity_Buff_ALL_df_b2$treatment_amount)
cutblock_plots_openings_productivity_Buff_ALL_df_b2$vri_age.<-as.numeric(cutblock_plots_openings_productivity_Buff_ALL_df_b2$vri_age)
cutblock_plots_openings_productivity_Buff_ALL_df_b2$rslt_age.<-as.numeric(cutblock_plots_openings_productivity_Buff_ALL_df_b2$rslt_age)

hist(cutblock_plots_openings_productivity_Buff_ALL_df_b2$treatment_amount)
hist(cutblock_plots_openings_productivity_Buff_ALL_df_b2$planted_density1)
hist(cutblock_plots_openings_productivity_Buff_ALL_df_b2$vri_age)
hist(cutblock_plots_openings_productivity_Buff_ALL_df_b2$rslt_age)
```

Also check because some opening IDs may have been for buffaloberry, and thus nothave a species associated with it anymore.

```{r}
cutblock_plots_openings_productivity_Buff_ALL_df_b2$Species
cutblock_plots_openings_productivity_Buff_ALL_df_b2$CutBlock_O

cutblock_plots_openings_productivity_Buff_ALL_df_b2$CutBlock_O[is.na(cutblock_plots_openings_productivity_Buff_ALL_df_b2$CutBlock_O)]<-1
table(cutblock_plots_openings_productivity_Buff_ALL_df_b2$CutBlock_O) #259 - fixed!
head(cutblock_plots_openings_productivity_Buff_ALL_df_b2)

```

Save File.
```{r}
write.csv(cutblock_plots_openings_productivity_Buff_ALL_df_b2, file="C:\\cora\\Hucklberry\\Grizzly Bear stuff\\berries\\data\\cutblock_plots_openings_productivity_Buff_ALL_df_b2.csv")
```


############################ PREP COMPLETE ####################
