---
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction
"When interpreting decisions support system output, as in all models, the major issue is whether the abstractions that the data and algorithms represent are sufficiently reliable to suffer the treatment of generalization from model output to practice in the real world" (Bunnell and Boyland 1999).

The size of a harvest unit (ie. a cutblock) and its spatial boundaries have important implications for forest management. Economic feasiblity, patch size distribution objectives and metrics important to wildlife habitat (Ie. distance to a cutblock) are all influenced by cutblock size, shape and location. While forest attributes information is often represented as polygons or pixels (depending on the data structure) and can be assumed as a harvest unit there are many cases where polygons or pixels will require aggregation or disaggregation to meet management assumptions. For example, the aggregation of forest polygons or pixels is often required given operations can capture economies of scale resulting from harvesting a number of stands in a spatially contiguous manner. Conversely, forest cover polygons may require disaggragation when the size of the polygon is too large to meet size restrictions on harvest units. Aggregating or disaggregating polygons or pixels into operational units is one of the intital steps for making deciions in forest management planning. Largely, becuase forest mangement activites (i.e., harvseting, silvicuture) are often prescribed and implemented on a harvest unit. Thus, how do we simulate the formation of harvesting units (including the size, shape and location) into the future? 

First, the size of a cutblock is generally predicated by law. The Forest Practices Code of British Columbia Act ["Operation and Site Planning Regulation"](http://www.bclaws.ca/civix/document/id/loo60/loo60/107_98) states (11(1)) - the maximum size of a harvest unit must not exceed 40 ha for coast forest region and some areas within the South interior region and 60 ha for the northern interior region and some areas within the south interior region. These maximal sizes can be increased further under a number of caveats including: objectives from a high level forest plan for the purposes of salvaging timber from natural disturbances; the cutblock retains 40% or more of the pre-harvest basal area; or at the discretion of the district manager. Given these spatial bounds, we need a block building alogirthum for segmenting information from forest cover polygons and other remote sensing products into harvest units or blocks that result in a shape that would emulate actual harvest units.

Two approaches to the block building algorithum can taken based on the assumption of information. Note that the term block here does not convey any information concerning the geometry of the harvest unit but rather the term is used to describe the operational harvesting boundary which can take on many shapes and include alternative harvesting systems to  clearcutting. The two approaches are: i) 'pre-blocking' which assumes perfect information into the future and ii) 'dynamic blocking' which assumes almost nill information about the future. Under a pre-blocking approach, the entire landscape is divided into blocks before the harvest schedule is determined. This assumption can be limiting given harvest unit configurations are known _a_ _priori_ and evidently restrict the flexibility of the modelled outcome. Conversely, dynamic blocking assigns harvest unit size and its geometry during the harvest scheduling simulation. This dynamic behaviour may better emulate flexible management strategies like salavage operations but is harder to achieve optimality by the blocking method. Typically, the choice of assumptions are made in concordance with the proposed harvest scheduling approach. Various harvest scheduling approaches can be linked with a blocking algorthuim, however, the various advantages and disadvantages will be left for another module.

In reality a combination of approaches is implemeneted (given the flexiblity of management and spectrum of future insight given to the model) which allows advantages from both approaches to be realized. For the caribou and land use simulator (CLUS), our interest is in the automated process of simulating the size and shape of future harvest units for purposes of tracking forestry landuses. We are interested in how future forestry landuses could impact the habitat of caribou across British Columbia. In particular, disturbed area, including harvesting can negatively impact caribou habitat through a vareity of pathways. As such harvest blocks are often buffered by 500 m or more to account for the degradation of caribou habitat that results from harvesting operations. Thus, the size, shape and location of harvest units are particulary sensitive to projections of caribou habitat. The following sections describes in greater detail the blocking algorithums considered in CLUS modelling efforts. 

### Dynamic blocking

The general dynamic blocking algorithum is as follows from Murray and Weintraub (2002):
1. the area is randomly seeded with harvest units 'growing' around these seeds 
2. polygons/pixels are then aggregated into harvest units based on the 'closest' seed point (i.e., 'closest' can mean both real and variable space)
3. the harvest unit size is thus controlled by the number of initial seed points or some target size

In particular, 'emergent processes' like salvage operations can be included to dictate harvest unit size. Further, this approach presents the ability of the simulation to account for reactive decision making when modelling land uses under uncertainty. When more than one harvest unit is needed, this algorthium is very similar to a [k-means clustering](https://en.wikipedia.org/wiki/K-means_clustering) which partions _n_ pixels into _k_ clusters with each pixel belonging to a cluster with the nearest mean. The result of this process is the ability to partition the data space into [Voronoi cells](https://en.wikipedia.org/wiki/Voronoi_diagram) which can be used to represent objects like harvest units. Various modifications to this approach have been made with consideration to i) randomly sampling a harvest unit size target distribution and ii) including various priorities for aggregating various layers of information (e.g., stand type, age, and terrain) while achieving objectives of harvest unit homogeneity. However, both pre-blocking and dynamic blocking approches can be implemented with this simple algorithum.


### Pre-blocking 

In cases where the total number of harvest units is known, the dynamic blocking algorithum can be run to provide a census of harvest units. The advantages of 'pre-blocking' are often a cost saving during run time of the simulation and leveraging _a_ _priori_ assumptions to support formulations of spatially exact optimization harvest schedulling problems. In particular, these assumptions allow the model to have greater insights into future outcomes and can be argued to result in improved decisions (intertemporal decision making). The unit restriction model (URM) is an example of an exact spatial harvest scheduling formulation that leverages the outputs of a pre-blocking algorithum (Murray 1999). This model is a spatial extension of a Model 1 aspatial formulation (Johnson and Scheurman 1977) which declares the decision variable as a binary represnting wheather a block is to be harvested or not (Murray 1999). Note that the URM has a similar formulation known as the Area restriction model (ARM) which endogenously includes the process of blocking. However, ARM are known to be very difficult to solve for large problems given the 'adjacency' and area restriction constraints impose a large amount of 'branching' in the solving algorithums. 

Various approaches to 'pre-blocking' have included optimization formulations and near optimal solutions via heuristics. Lu and Eriksson (1999) used a genetic algorithum to build harvest units and applied applied the algorithum to a 20 ha landscape with realtively long run-times. Boyland (2004) used simulated annealing to group polygons into harvest units based on area, age, species and shape criteria for the Invermere Timber Supply Area in British Columbia. Hueristic alorgithums offer a near optimal solution while accounting for the complexity of the problem. These characteristics are vitally important to the caribou and landscape simulator, which requires the simulation of land use events across very large spatial and temporal scales in a timely manner.  

A disadvantage with heuristic alogorithums is their inability to leave a local optimum and achieve a global optimum. For pre-blocking this means being able to accomodate variability in the forest which is often viewed as an image or photograph of the forest. Thus, the process of 'pre-blocking' for purposes of creating spatially contigous harvesting units has some similarities to the image segementation problem. The goal of image segmentation is to partion or cluster pixels into regions that represent meaningful objects or parts of objects. The problem of segementing an image into objects has been posed for many  applications ranging from improving the stratification of the forest which is needed in some forest inventory sampling regimes to  interpreting biomedical images (e.g., delineating oragans or tumours). Typically, image segmentation involves either top-down or bottom-up perspectives.

Keeping in line with forestry applications- a common commercial software used for image segemetnation is [eCognition](http://www.ecognition.com/). This software is proprietary, and uses a bottom-up region merging technique (Baatz and Schape 2000), that merges indiviudal pixels into larger objects based on a 'scale' parameter. However, as shown by Blaschke and Hay (2001), finding any relationship between this 'scale' parameter and spatial indicators is complicated, which forces a trial and error approach for meeting segementation objectives (i.e., size and homogenity). Hay et al. (2005) attempted to overcome this issue by developing multiscale object-specific segmentation (MOSS) which uses an integrative three-part approach. For purposes of blocking harvest units, the size constrained region merging (SCRM) part of the approach is of importance.

SCRM concept stems from the topographic view of a watershed. Watersheds define a network of 'ridges' that represent the boundaries of where each drop of rain would drain towards. In the harvest blocking problem these ridges are boundaries of stand types. To complete the region merging, the idea is to find sinks where the rain would drain to and then assume these areas are springs from which uplift of water would fill these areas. As water fills a sink, these areas represent contiguous areas with similar features (i.e., elevation). Various size constraints can then be used to stop the process of merging which allows objects to be delineated.

In blockingCLUS, we leverage ideas from image based segementation (Felzenszwalb and Huttenlocher 2004) and SCRM (Hay et al. 2005) to develop a graph based image segementation approach that spatialy clusters pixels into harvest units based on similarity between adjacent pixels and size constraints. 

The following steps are used:
1. Estimate the similarity of a vector of forest attributes into an image
2. Convert the similarity image into a undirected graph
3. Solve the minnimum spanning tree of the graph to get a list of edges (i.e., ridge lines)
4. Sort the edgelist according to the metric of similarity (i.e., multivariate distance)
5. Starting with the pixel with the largest [degree](https://en.wikipedia.org/wiki/Degree_(graph_theory)), cluster surounding pixels until the largest size constraint has been met
6. When there are no more adjacent pixels or the size has been met, go on to the next block
7. Complete 5-6 until the target distribution is achieved

The following is an example from using this algorithum

```{r, echo =FALSE, message=FALSE}
library(raster)
plot(raster("test.tif"))
title("Example 'homogenous' harvest units with some random variability")

plot(raster("simulated.tif"))
title("Simulated harvest unit boundaries")
```

Note: two improvements to this algorithum are needed for future work: i) if a size constraint is not met then determine if the current harvest unit could be 'placed' in the next largest size constraint; ii) rather than the degree of the graph, use the weights of the edges to determine the order from which to add pixels. For instance, the 'islands' within a harvest unit is a unintended result of this issue. 

## Objectives

Our goal for blockingCLUS is to be able to reproduce historical harvest units - including the size and shape that would impact the historical harvest disturbance for caribou. Note: this obejctive differs from trying to simultaneously optimize the size, shape and location of harvest units, as described earler by an area restiction model. The location of harvest units commonly includes a temporal decision making process which is determined by the harvest scheduler. It is important to note that the number of cutblocks and their respective sizes are largely related. If the size of a stand is artifically set too small, a greater footprint could result from the scheduler, as it looks to find more fibre for harvesting. Thus, we used historic harvest unit locations to test the ability of blocking methods to reproduce the historical harvest disturbance for caribou. As stated earlier, this disturbance metric is the total of area of harvest units with a buffer of 500 m. 

1. What forest attributes information (i.e., crown closure, ) directs the formation of historic harvest unit shape? 

2. Based on: 1, the historical harvest unit size distribution, and the centroid of historical harvest units which approach (i.e., dynamic or pre-blocking) best reproduces historical harvest disturbance for caribou.

3. Which approach is computationally faster?

## Case Study
### Study Areas

The study areas included various [caribou herd locations](https://catalogue.data.gov.bc.ca/dataset/caribou-herd-locations-for-bc) around the province. In the north-west, the herd locations are relatively large in area but with little forestry activity. Conversely, the south-eastern herd locations are smaller in area but with a greater density of harvest units.

```{r, echo = FALSE, message=FALSE,warning=FALSE}
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

library(ggplot2)
library(ggpmisc)
library(rpostgis)
library(sf)
library(bcmaps)
library(ggrepel)
library(dplyr)
library(purrr)

data<-read.table("validated.csv", sep = ",", head = TRUE)
data$METHOD <- factor(data$METHOD,levels=c('snap', 'lcp', 'mst'))
data2<-data[data$METHOD == 'snap',]

getSpatialQuery<-function(sql){
  conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host='localhost', dbname = 'clus', port='5432' ,user='app_user' ,password='clus')
  on.exit(dbDisconnect(conn))
  st_read(conn, query = sql)
}
#hrds<-cat(paste(shQuote(data2$BOUNDARY, type="cmd"), collapse=", "))
bc<-st_geometry(get_layer("bc_bound_hres"))
hrd_names<-c('Barkerville', 'Central Rockies', 'Chase', 'Chinchaga', 'Columbia North', 'Finlay', 'Graham', 'Groundhog', 'Horseranch', 'Itcha-Ilgachuz', 'Moberly', 'Muskwa', 'Nakusp', 'Narraway', 'North Cariboo', 'Quintette', 'Rainbows', 'Scott', 'South Selkirks', 'Takla', 'Telkwa', 'Tweedsmuir', 'Wells Gray', 'Wolverine')
carb<-getSpatialQuery("SELECT * FROM public.gcbp_carib_polygon WHERE herd_name IN ('Barkerville', 'Central Rockies', 'Chase', 'Chinchaga', 'Columbia North', 'Finlay', 'Graham', 'Groundhog', 'Horseranch', 'Itcha-Ilgachuz', 'Moberly', 'Muskwa', 'Nakusp', 'Narraway', 'North Cariboo', 'Quintette', 'Rainbows', 'Scott', 'South Selkirks', 'Takla', 'Telkwa', 'Tweedsmuir', 'Wells Gray', 'Wolverine')")

carb<-merge(carb, data2, by.x = 'herd_name', by.y = 'BOUNDARY' )
carb2<-st_zm(carb) %>%
 filter(carb$herd_name %in% hrd_names) %>% # filter to just the counties we want
  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]), # add centroid values for labels
         lat=map_dbl(geometry, ~st_centroid(.x)[[2]])) # add centroid values for labels
 
ggplot() +
  geom_sf(data=bc)+
  geom_sf(data = carb2, aes(fill= AREA)) +
  geom_text_repel(data=carb2, aes(x= lon, y= lat, label=herd_name), cex=2) 

ggplot() +
  geom_sf(data=bc)+
  geom_sf(data = carb2, aes(fill= LANDINGS))+
  geom_text_repel(data=carb2, aes(x= lon, y= lat, label=herd_name), cex=2) 
```

### Historical Harvest Unit Size Distribution

The cutblock polygons were sourced from [cns_cut_bl_polygon](https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-). The following query was used to select harvest unit size, shape and location.

```{sql, eval=FALSE}
Create Table cutseq_Centroid as
  SELECT a.areaha, a.harvestyr, a.geom, ST_X(a.point) as X , ST_Y(a.point) as Y, point 
  FROM (SELECT areaha, harvestyr, st_Force2D(wkb_geometry) as geom, ST_Centroid(st_Force2D(wkb_geometry)) as point
  FROM cns_cut_bl_polygon where areaha >= 1) a 
```

Below is a histogram of the historical (1908-2018) cutblock size. The negative "J" shaped curve is often similar to natural distrubance size - frequency which provides some empirical evidence of cutblock size emulating natural disturbances. This is useful because forested area lacking a comprehensive historical cutblock dataset could sample from this natural disturbance size distribution.

```{r}
dist.cutblk.size<-getTableQuery("select width_bucket(areaha, 0, 100, 100) as sizebin, count(*)
    from cns_cut_bl_polygon where harvestyr >= 1980 and datasource != 'Landsat'
    group by sizebin 
    order by sizebin;") 

ggplot(dist.cutblk.size, aes(x = sizebin,y =count)) +
  geom_bar(stat="identity") +
  xlab("Cutblock Size (ha)") + 
  ylab("Frequency")
```



#References

Felzenszwalb, P.F. and Huttenlocher, D.P., 2004. Efficient graph-based image segmentation. International journal of computer vision, 59(2), pp.167-181.

Gustafson, E.J. 1998. Clustering timber harvests and the effect of dynamic forest management policy on forest fragmentation.
Ecosystems 1:484-492.

Johnson, K.N., Scheurman, H.L. 1977. Techniques for prescribing optimal timber harvest and investment under different objectives--discussion and synthesis. Forest Sci. 23(1): a0001–z0001. doi: 10.1093/forestscience/23.s1.a0001.

Lu, F. and Eriksson, L.O. 2000. Formation of harvest units with genetic algorithms. For. Ecol. And Manage. 130:57-67.

Nelson, J.D. 2001. Assessment of harvest blocks generate from operational polygons and forest cover polygons in tactical and strategic planning. Can. J. For. Res. 31:682-693.

Murray, A.T. 1999. Spatial Restrictions in harvest scheduling. Forest Science 45(1): 45-52.

Murray, A.T., and Weintraub, A. 2002. Scale and unit specification influences in harvest scheduling with maximum area restrictions. For. Sci. 48(4):779-789.


