---
title: "fisherHabitatCastor"
author: ""
date: "26 October 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'

```

## Overview
This module is used to create fisher habitat data that can be loaded into the FLEX2 fisher agent based model. The fisher habitat data is created from forestryCastor, which updates forest stand attributes over time, and is outputed as a 'stack' of rasters stored in a .tif format. 

## Usage
There are no parameters within this module. It relies on parameters from dataCastor (database and boundary info) and growingStockCastor (time interval). It is meant to be run with forestryCastor, so that as forest stands are harvested and grow, stand characteristics change and subsequently fisher habitat changes. 


```{r module_usage}
library (SpaDES.core)
library (data.table)
library (terra)
library (keyring)
library (tidyverse)
library (here)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules"))
inputDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules/fisherHabitatCastor")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules/fisherHabitatCastor")) %>% reproducible::checkPath (create = TRUE)
cacheDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules/fisherHabitatCastor"))

times <- list (start = 0, end = 4)

parameters <- list(
  
  # "dummy" landscape method 
  dataCastor = list(saveCastorDB = TRUE, 
                    randomLandscape = list (500,500,0,500,0,500),
                    randomLandscapeClusterLevel = 0.3,
                    randomLandscapeZoneConstraint = data.table (zoneid = 1,
                                                                variable = 'age', 
                                                                threshold = 140, 
                                                                type = 'ge', percentage = 20)
                     ),
  
  blockingCastor = list (blockMethod = 'none'
                         ),
  growingStockCastor = list(periodLength = 5, maxYieldAge = 1000),
  roadCastor = list (roadMethod = 'mst'
                     ),
  disturbanceCastor = list (calculateInterval =  1, 
                            #criticalHabitatTable = "vat.vat_bc_crithab_and_herd",
                            #criticalHabRaster = "rast.bc_crithab_and_herd",
                            #permDisturbanceRaster = "rast.mine_ag_wind_rail",
                            recovery = 300),
  fisherHabitatCastor = list ()
)

scenario = data.table (name = "test",
                       description = "Testing fisher habitat module with random landscape.")

modules <- list ("dataCastor", "blockingCastor", "roadCastor", "growingStockCastor", "disturbanceCastor", "fisherHabitatCastor")
disturbanceFlow<- data.table(compartment ="all",
                                     partition = ' treed = 1 and age > 15 ',
                                     mean = log(2000),
                                     sd = 1,
                                     period = rep(seq(from = 1, to=500, by = 1),1), 
                                     flow = 162500)
objects <- list (scenario = data.table (name = "test", description = "test"), disturbanceFlow=disturbanceFlow) 
inputs <- list ()
outputs <- data.frame (objectName = c())
paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)

mySimOut <- spades(mySim)
```

