<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Database creation for Wolverine Scenario Analysis"
author: "Kyle Lochhead"
date: "2 Novemeber 2023"
output: pdf_document
---

# Overview
-	Need timber supply impact analysis for the wolverine herd


# Usage
Set parameters for creating the database in the code chunk below.

```{r module_usage}
library (SpaDES)
library (SpaDES.core)
library (data.table)
library (keyring)
library (terra)

source (here::here("R/functions/R_Postgres.R"))

Sys.setenv(JAVA_HOME = 'C:\\Program Files\\Java\\jdk-14.0.1') #throws an error if pointing to different version of java (i.e., 32 vs 64 bit)

moduleDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules"))
inputDir <- file.path (paste0 (here::here (), "/R/scenarios/revelstoke_wg/inputs")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path (paste0 (here::here (), "/R/scenarios/revelstoke_wg/outputs")) %>% reproducible::checkPath (create = TRUE)


times <- list (start = 0, end = 52)
parameters <-  list (
        .progress = list (type = NA, interval = NA),
        .globals = list (),
        dataCastor = list(dbName = 'castor',
                          saveCastorDB = FALSE,
                          sqlite_dbname = "revelstoke", 
                          nameBoundaryFile = "public.tsa_aac_bounds", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = "Revelstoke_TSA", 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "rast.tsa_aac_boundary", 
                          nameCompartmentTable = "vat.tsa_aac_bounds_vat" 
        ),
        roadCastor = list (roadMethod = 'pre',
                           nameCostSurfaceRas = 'rast.rd_cost_surface',
                           nameRoads =  'rast.ce_road_2022'
                           ),
        backCastor = list(startHarvestYear = 1970,
                             nameCutblockRaster= 'rast.cns_cutblk_2022', 
                             nameCutblockTable= 'cut_block_all_bc', 
                             queryCutblocks = 'cutseq_centroid_2022',
                             resetAge = T 
                              )
        
        )

scenario = data.table (name = "backCastor", description = "dataCastor output")

modules <- list("dataCastor",
                #"growingStockCastor",
                #"blockingCastor", 
                "roadCastor",
                #"survivalCastor",
                "backCastor"
                #"disturbanceCastor",
                #"volumebyareaReportCastor",
                #"uploadCastor"
                )

objects <- list (scenario = scenario
                 )

paths <- list(modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

inputs <- list()
outputs <- list()

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader

system.time({
mysimout<-spades(mySim)
})

```

## Update roadstatus
Use the script below to replicate the STSM approach of not creating 'blocks' (i.e., each pixel is a block) in the castor db.

```{r, create blocks}
rd.stat<-rast("C:/Users/klochhea/castor/R/scenarios/revelstoke_wg/outputs/backCastor_Revelstoke_TSA_pre_status_52.tif")
#clip harvest year with the aoi
cut.year<-rast("C:/Users/klochhea/castor/R/Params/cns_cutblk_year_2022.tif")
cut.year<-crop(cut.year, rd.stat)
cut.year[]<-cut.year[]-2022

rd.stat[rd.stat[] > -52] <- 0
rd.stat[rd.stat[] == -52] <- 1

in.block<-cut.year*rd.stat
in.block[in.block[] == 0]<- NA

writeRaster(in.block, "C:/Users/klochhea/castor/R/scenarios/revelstoke_wg/outputs/inblock_revelstoke.tif")

#Over write the inblock roads
rd.stat<-rast("C:/Users/klochhea/castor/R/scenarios/revelstoke_wg/outputs/backCastor_Revelstoke_TSA_pre_status_52.tif")
in.block<-rast("C:/Users/klochhea/castor/R/scenarios/revelstoke_wg/outputs/inblock_revelstoke.tif")
rd.stat[rd.stat[] == -52] <- 0
in.block[is.na(in.block[])]<-0
rd.stat<-rd.stat + in.block
writeRaster(rd.stat, "C:/Users/klochhea/castor/R/scenarios/revelstoke_wg/outputs/est_roadstatus_revelstoke.tif")

castordb <- dbConnect(RSQLite::SQLite(), dbname ="C:/Users/klochhea/castor/R/scenarios/revelstoke_wg/revelstoke_bau_20231205_castordb.sqlite")
ras.info<-dbGetQuery(castordb, "Select * from raster_info limit 1;")
ras<-raster(extent(ras.info$xmin, ras.info$xmax, ras.info$ymin, ras.info$ymax), nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow, vals =0, crs = 3005)

update_roadstatus<- data.table(est_rs=rd.stat[])[,pixelid:=seq_len(.N)]
setnames(update_roadstatus, "est_rs.layer", "est_rs")
update_roadstatus<-update_roadstatus[!is.na(est_rs),]

plot(rd.stat)
# update pixels table 
dbBegin (castordb)
rs <- dbSendQuery (castordb, "UPDATE pixels SET roadstatus = :est_rs where pixelid = :pixelid;", update_roadstatus)
dbClearResult (rs)
dbCommit (castordb)

dbDisconnect(castordb)
```

