---
title: "STSM-Castor comparison: oldest stands first, even flow harvest, no blocking, no roads."
author: "Tyler Muhly"
date: "06 January 2023"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2023 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

## Overview
This scenario was developed to compare the basic STSM-SELES timber supply model to the Castor timber supply model. Both of these models are deterministic, spatial, simulation models. The same datasets and parameters were used in each model to assess whether they determine similar spatial timber supply outcomes. 

## Scenario
This is a simple scenario where the harvest flow target is the maximum even flow over a 200 year period. The harvest priority queue is 'oldest first' and no constraints, blocking or roading is implemented in the model. 

## Calculate Some Diagnostics

## Update constraint

```{r, update constraints}

## add AFLB data to pixels table
tab.aflb <- data.table (pixelid = terra::rast ("G:\\!Workgrp\\Analysts\\tmuhly\\clus_stsm_comparison\\results\\pixelid.tif")[],
aflb = terra::rast ("G:\\!Workgrp\\Analysts\\tmuhly\\clus_stsm_comparison\\results\\tsa99_aflb.tif")[]/10000)

names (tab.aflb) <- c ("pixels", "aflb")

castordb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/comparison_stsm/stsm_compare_noroads_noblocks_constraint_aflb_castordb.sqlite")) # a copy of stsm_compare_noroads_noblocks_constraint_castordb

dbExecute (castordb, "ALTER TABLE pixels ADD COLUMN aflb numeric DEFAULT 0")

rs <- dbSendQuery(castordb, "UPDATE pixels SET aflb = :aflb WHERE pixelid = :pixels", tab.aflb)
dbClearResult(rs)
dbCommit(castordb) 

## Update zoneconstraints table
castordb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/comparison_stsm/stsm_compare_noroads_noblocks_constraint_aflb_castordb.sqlite"))
check <- dbGetQuery (castordb, "SELECT * from zoneconstraints WHERE reference_zone = 'castor_stsm_compare.rast_zone_test'") 
dbExecute (castordb, "UPDATE zoneconstraints SET multi_condition = NULL;") 
dbExecute (castordb, "UPDATE zoneconstraints SET type = 'ge' WHERE reference_zone = 'castor_stsm_compare.rast_zone_test'")
dbExecute (castordb, "UPDATE zoneconstraints SET percentage = 75 WHERE reference_zone = 'castor_stsm_compare.rast_zone_test'") 
dbExecute (castordb, "UPDATE zoneconstraints SET threshold = 175 WHERE reference_zone = 'castor_stsm_compare.rast_zone_test'") 
dbExecute (castordb, "UPDATE zoneconstraints SET denom = NULL WHERE reference_zone = 'castor_stsm_compare.rast_zone_test'") 

dbDisconnect(castordb)
```


## Parameters 
### Zone Constraints
None

### 'harvestPriority' parameter 
oldest first 

### 'harvestFlow'

### adjacencyConstraint
None

### Simulation Model

```{r module_usage}
library (SpaDES.core)
library (data.table)
library (dplyr)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/comparison_stsm/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor"))
times <- list(start = 0, end = 250) # 1 year interval; 250 years = 250 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataCastor = list (dbName='castor',
                     saveCastorDB = FALSE,
                     sqlite_dbname = "stsm_compare_noroads_noblocks_age0",
                     useCastorDB = paste0(here::here(), "/R/scenarios/comparison_stsm/stsm_compare_noroads_noblocks_constraint_aflb_castordb.sqlite"),
                     nameBoundaryFile = "castor_stsm_compare.bounds_tsa99", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = "tsa99", 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "castor_stsm_compare.rast_bounds_tsa99", 
                          nameCompartmentTable = "castor_stsm_compare.vat_bounds_tsa99", 
                          nameMaskHarvestLandbaseRaster = 'castor_stsm_compare.rast_thlb', 
                          nameZoneTable = "castor_stsm_compare.constraints", 
                          nameYieldsRaster = "castor_stsm_compare.rast_ycid_vdyp", 
                          nameYieldTable = "castor_stsm_compare.vdyp", 
                          nameYieldsTransitionRaster = "castor_stsm_compare.rast_ycid_tipsy", 
                          nameYieldTransitionTable = "castor_stsm_compare.tipsy", 
                          nameForestInventoryRaster = "castor_stsm_compare.rast_vri_id", 
                          nameForestInventoryKey = "vri_fid", 
                          nameForestInventoryTable = "castor_stsm_compare.vri",
                          nameForestInventoryAge = "proj_age_1",  
                          nameForestInventoryHeight = "proj_ht_1",
                          nameForestInventoryCrownClosure = "cr_closure",                             
                          nameForestInventoryTreed = "bclcs_lv_2",
                          nameForestInventorySiteIndex = "site_index"    
                     ),
  forestryCastor = list(harvestBlockPriority = " age DESC ", 
                        reportHarvestConstraints = F,
                        activeZoneConstraint = "castor_stsm_compare.rast_zone_test"
                        ),
  blockingCastor = list(blockMethod = 'pre',
                        patchZone = 'default',
                        patchVariation = 6),
  growingStockCastor = list (periodLength = 1,
                             maxYieldAge = 250),
  uploadCastor = list(aoiName = 'stsm_compare',
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL")))
  )

modules <- list("dataCastor", 
                "growingStockCastor", 
                "forestryCastor", 
                "blockingCastor",
                "uploadCastor"
                )

scenario = data.table (name = "oldest_annual_noroads_noblocks_constraint_modified_aflb",
                       description = "Priority queue = oldest first. Adjacency constraint = None. Constraint zone: 75% >= 175 years old. No roads or blocks. Maximum even live harvest flow: 123,500 m3/year. Minimum harvest age = 80 and minimum harvest volume = 150")


harvestFlow <- rbindlist(list(data.table(compartment ="tsa99",
                                     partition = ' age > 79 AND vol > 149 ', 
                                     period = rep( seq (from = 1,
                                                      to = 250, 
                                                      by = 1),
                                                1), 
                                     flow = 123500, # 123,500m3/year 123-124
                                     partition_type = 'live') 
))



objects <- list(harvestFlow = harvestFlow, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "blockingCastor",
                                             "growingStockReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```



