---
title: "STSM-Castor comparison: oldest stands first, even flow harvest, blocking, no roads."
author: "Tyler Muhly"
date: "06 January 2023"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2023 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

## Overview
This scenario was developed to compare the basic STSM-SELES timber supply model to the Castor timber supply model. Both of these models are deterministic, spatial, simulation models. The same datasets and parameters were used in each model to assess whether they determine similar spatial timber supply outcomes. 

## Scenario
This is a simple scenario where the harvest flow target is the maximum even flow over a 200 year period. The harvest priority queue is 'oldest first' and no constraints, blocking or roading is implemented in the model. 

## Calculate Some Diagnostics

```{r, Diagnostics}

db <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/comparison_stsm/stsm_compare_blocks_roads_castordb.sqlite"))

pixels <- data.table (dbGetQuery(db, "SELECT * FROM pixels;"))
thlb.area <- sum(pixels$thlb, na.rm = T) # 73,332 hectares
yields <- data.table (dbGetQuery(db, "SELECT * FROM yields;"))
yields [, mai := (tvol/age)]
max.yield <- yields [yields [, .I [which.max(mai)], by = yieldid]$V1]
yield.counts <- pixels  [, .(count = .N, count_thlb = sum (thlb, na.rm = T)), by = yieldid]
yield.counts <- merge (yield.counts, max.yield, by.x = "yieldid", by.y = "yieldid")
yield.counts [, total_vol := (mai*count_thlb)]
lrsy <- sum (yield.counts$total_vol) # 108,881 m3
yield.counts [, weight_vol := (tvol*(count_thlb/thlb.area))]
mean.vol.ha <- sum (yield.counts$weight_vol) # 179 m3
yield.counts [, weight_mai := (mai*(count_thlb/thlb.area))]
mean.mai <- sum (yield.counts$weight_mai) # 1.48 m3

```


## Parameters 
### Zone Constraints
None

### 'harvestPriority' parameter 
oldest first 

### 'harvestFlow'

### adjacencyConstraint
None

### Simulation Model

```{r module_usage}
library (SpaDES.core)
library (data.table)
library (dplyr)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/comparison_stsm/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor"))
times <- list(start = 0, end = 25) # 10 year interval; 250 years = 25 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataCastor = list (dbName='castor',
                     saveCastorDB = FALSE,
                     sqlite_dbname = "stsm_compare_roads_blocks",
                     useCastorDB = paste0(here::here(), "/R/scenarios/comparison_stsm/stsm_compare_blocks_roads_castordb.sqlite"),
                     nameBoundaryFile = "castor_stsm_compare.bounds_tsa99", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = "tsa99", 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "castor_stsm_compare.rast_bounds_tsa99", 
                          nameCompartmentTable = "castor_stsm_compare.vat_bounds_tsa99", 
                          nameMaskHarvestLandbaseRaster = 'castor_stsm_compare.rast_thlb', 
                          nameZoneTable = "castor_stsm_compare.constraints", 
                          nameYieldsRaster = "castor_stsm_compare.rast_ycid_vdyp", 
                          nameYieldTable = "castor_stsm_compare.vdyp", 
                          nameYieldsTransitionRaster = "castor_stsm_compare.rast_ycid_tipsy", 
                          nameYieldTransitionTable = "castor_stsm_compare.tipsy", 
                          nameForestInventoryRaster = "castor_stsm_compare.rast_vri_id", 
                          nameForestInventoryKey = "vri_fid", 
                          nameForestInventoryTable = "castor_stsm_compare.vri",
                          nameForestInventoryAge = "proj_age_1",  
                          nameForestInventoryHeight = "proj_ht_1",
                          nameForestInventoryCrownClosure = "cr_closure",                             
                          nameForestInventoryTreed = "bclcs_lv_2",
                          nameForestInventorySiteIndex = "site_index"    
                     ),
  forestryCastor = list(harvestBlockPriority = " age DESC ", 
                        reportHarvestConstraints = F
                        ),
  blockingCastor = list(blockMethod = 'pre',
                        patchZone = 'default',
                        patchVariation = 6),
  growingStockCastor = list (periodLength = 10,
                             maxYieldAge = 250),
  roadCastor = list (roadMethod = 'mst',
                     nameCostSurfaceRas = 'castor_stsm_compare.rast_road_cost',
                     nameRoads =  'castor_stsm_compare.rast_roads'
                     ),
  uploadCastor = list(aoiName = 'stsm_compare',
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL")))
  )

modules <- list("dataCastor", 
                "growingStockCastor", 
                "forestryCastor", 
                "blockingCastor",
                "roadCastor", 
                "uploadCastor"
                )

scenario = data.table (name = "oldest_decadal_roads_blocks",
                       description = "Priority queue = oldest first. Adjacency constraint = None. Includes roads (mst) and blocks (pre). Maximum even live harvest flow: 130,000 m3/year. Minimum harvest age = 80 and minimum harvest volume = 150")


harvestFlow <- rbindlist(list(data.table(compartment ="tsa99",
                                     partition = ' age > 79 AND vol > 149 ', 
                                     period = rep( seq (from = 1,
                                                      to = 25, 
                                                      by = 1),
                                                1), 
                                     flow = 1300000, # 130,000m3/year 
                                     partition_type = 'live') 
))



objects <- list(harvestFlow = harvestFlow, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "blockingCastor",
                                             "growingStockReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```



