---
title: "forestryCastor"
author: ""
date: "06 Dec 2022"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2023 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distributions, road densities, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCastor follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the analyst. For a historical selection of harvesting activities see [backCastor](https://github.com/bcgov/Castor/tree/master/R/SpaDES-modules/backCastor). Both  backCastor and forestryCastor build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataCastor (set up the castordb) 
2. blockingCastor (preforms the pixel aggregation into harvest units)
3. growingStockCastor (increments the age and volume in pixels)
4. (Optionally) rsfCastor (track resource selection functions)
5. (Optionally) roadCastor (preforms the access to the harvest units)
6. uploaderCastor (uploades the outputs to a shiny app)


```{r module_usage}
library(SpaDES.core)
library(data.table)
library(dplyr)
source(here::here("R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor/outputs"))


times <- list(start = 0, end = 2)
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataCastor = list(saveCastorDB = TRUE,
                     randomLandscape = list(100,100,0,100,0,100),
                     randomLandscapeZoneConstraint = data.table(zoneid = 1,  variable = 'age', threshold = 80, type = 'ge', percentage = 0)
                     ),
  growingStockCastor = list(periodLength = 5),
  blockingCastor = list(blockMethod='pre', 
                      patchZone = 'default',
                      patchVariation = 6),
  forestryCastor = list( activeZoneConstraint = 'default', 
                         harvestPriority = " vol DESC, age DESC ", 
                         adjacencyConstraint = TRUE),
  roadCastor = list (roadMethod = 'mst'
                     ),
  disturbanceCastor = list (calculateInterval =  1, 
                            recovery = 300)
)

modules <- list("dataCastor", "growingStockCastor", "blockingCastor", "forestryCastor")
#modules <- list("dataCastor", "growingStockCastor", "blockingCastor", "forestryCastor","roadCastor")
#modules <- list("dataCastor", "growingStockCastor", "blockingCastor", "forestryCastor","roadCastor", "disturbanceCastor")


scenario = data.table(name="test", description = "test")
harvestFlow<- data.table(compartment ="all",
                                     partition = ' (vol > 110) ',
                                     period = rep(seq(from = 1, to=2, by = 1),1), 
                                     flow = 220000,
                                     partition_type = 'live')

disturbanceFlow<- data.table(compartment ="all",
                                     partition = ' treed = 1 ',
                                     mean = log(30),
                                     sd = 1,
                                     period = rep(seq(from = 1, to=500, by = 1),1), 
                                     flow = 500)
objects <- list(harvestFlow = harvestFlow, disturbanceFlow=disturbanceFlow, scenario = scenario)

paths <- list(
  modulePath = moduleDir,
  outputPath = outputDir)

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)
outputs(mySim) <- data.frame (objectName = c("harvestReport", "growingStockReport"))
mysimout<-spades(mySim, debug = T)

```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## plots
```{r, plots}
userdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/forestryCastor/test_castordb.sqlite") ) 
 ras.info<-dbGetQuery(userdb, "Select * from raster_info limit 1;")
ras<-raster(extent(ras.info$xmin, ras.info$xmax, ras.info$ymin, ras.info$ymax), nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow, vals =0, crs = 3005)
ras[]<-dbGetQuery(userdb, "select age from pixels order by pixelid")$age
plot(ras)
#ras[]<-0
#ras[]<-dbGetQuery(userdb, "select roadyear from pixels order by pixelid")$roadyear
#plot(ras)
ras[]<-0
ras[]<-dbGetQuery(userdb, "select age from pixels order by pixelid")$age
plot(ras)
dbDisconnect(userdb)
```
## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataCastor). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the period at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataCastor is required.

