---
title: "fire_occurrence"
output: html_document
date: '2023-09-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
library(glmmTMB)
library(DHARMa)
library(sdmTMB)
library(INLA)
```

In this script we model the occurrence of lightning cause wildfires. This includes the number of fires and where they occur. to do this we rely on the historical incidents data reported in the data catalog of BC. The number of fires within a 10 km grid are estimated along with various predictor variables that relate to landcover and climate.The landcover data comes from the VRI using the previous year of the fire as the estimate of the amount of landcover types within the 10 km voxel.

## Data
```{r}
data.person<-readRDS("data_person_occurence_10k.rds")
data.person<-data.person[, count_person:= count]
data.lightning<-readRDS("data_lightning_occurence_10k.rds")
data.all<-merge(data.lightning, data.person[,c("pixelid", "FIRE_YEAR", "count_person")], by.x = c("pixelid", "FIRE_YEAR"), by.y = c("pixelid", "FIRE_YEAR"))
occ.model.data<-data.all[!is.na(CMI3yr),][,dCMI3yr:=CMI-(CMI3yr/3)][, coast:=0][frt==15, coast:=1][,flammable:=con + mix + dec + young + veg][flammable >0, ][, year:= as.factor(FIRE_YEAR)][!is.na(fire_centre),][, pcon:=(con/flammable)*100][, pdec:=(dec/flammable)*100][, pyoung:=(young/flammable)*100][, pmix:=(mix/flammable)*100][, proad:=scale(road/flammable)][,lroad:=log(road+1)]

occ.model.data<-occ.model.data[, avgCMIProv:=sum(CMI)/.N, by = c("FIRE_YEAR")][,dry:=0][,year:=as.integer(year)]

#Set the trainingset
occ.model.data.train<-occ.model.data[FIRE_YEAR < 2018, ]
spde <- make_mesh(occ.model.data.train[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 100)

```

## Model
```{r}
m0 <- sdmTMB(data = occ.model.data.train, count ~ 1  , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = F, spatiotemporal = FALSE, reml=F)

per0 <- sdmTMB(data = occ.model.data.train, count_person ~ 1  , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = F, spatiotemporal = FALSE, reml=F)

m0_gmrf <- sdmTMB(data = occ.model.data.train, count ~ 1  , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

per0_gmrf <- sdmTMB(data = occ.model.data.train, count_person ~ 1  , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m0_gmrf_fc <- sdmTMB(data = occ.model.data.train, count ~ 1 + as.factor(fire_centre) , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = 'iid', reml=F)

m1 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN, offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

per1 <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI, offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

per1b <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI + CMI06, offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m2 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  +  dCMI3yr + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

per2 <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI + CMI06+  lroad , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

m3 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN + dCMI3yr + avgCMIProv + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

per3 <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI+ CMI06  +  lroad  + avgCMIProv, offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

m4 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN + dCMI3yr + avgCMIProv + as.factor(frt) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

per4 <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI + CMI06 +  lroad  + avgCMIProv + as.factor(frt), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

##Vegetation typing
m5 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(veg+1) + log(dec+1) + log(mix+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE)

per5 <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI  + CMI06+  lroad  + avgCMIProv + as.factor(frt) +  log(con+1) + log(young+1) + log(veg+1) + log(dec+1) + log(mix+1), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

m6 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr+ avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(mix+1) + log(dec+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

per6 <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI + CMI06 +  lroad  + avgCMIProv + as.factor(frt) + log(young+1) + log(dec+1) , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

m7 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

per7 <- sdmTMB(data = occ.model.data.train, count_person ~ 1 + CMI + CMI06 +  lroad  + avgCMIProv + as.factor(frt) +log(young+1)+ log(dec+1)  + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

m7.reml <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=T)

m8 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv +as.factor(frt) + scale(log(con+1)) + scale(log(young+1)) + scale(log(dec+1)) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m9 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv +as.factor(frt) + log(con+1) + log(dec+1), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m10 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt)+ Tdelta07+ Tdelta08 + log(con+1) + log(dec+1), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m11 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt)+ Tdelta07 + log(con+1) + log(dec+1), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

#test99<-predict(m6)
#test99<-test99[, estres:=exp(est)]
#test99<-test99[, mu1:= exp(-13.15)]
#test99<-test99[, mu2:= mu1*(1 + exp(m6$model$par[["log_ratio_mix"]]))]
#test99<-test99[, est9:= ((1-plogis(m6$model$par[["logit_p_mix"]]))*mu1 + plogis(m6$model$par[["logit_p_mix"]])*mu2)*flammable]

AIC(m0, m0_gmrf, m0_gmrf_fc, m1, m2, m3, m4, m5,m6, m7, m8 , m9)
saveRDS(m11, "C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/m11.rds")
saveRDS(per7, "C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/per7.rds")

AIC(per0, per0_gmrf, per1, per2, per3, per4, per5,per6, per7)
```


## Diagnostics
```{r}
#model<-readRDS("C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/m7reml.rds")
model<-m11
#model<-per6
occ.model.data.train$resids <- residuals(model) # randomized quantile residuals
qqnorm(occ.model.data.train$resids)
qqline(occ.model.data.train$resids)

#get the random spatial effect
preds.all<-predict(model, re.form =NULL)
spat.int<-unique(data.table(preds.all)[, c("pixelid", "omega_s")])

occ.model.data.test<-occ.model.data[FIRE_YEAR >= 2018, ]
occ.model.data.test<-merge(occ.model.data.test,spat.int, by = "pixelid" )

occ.model.data.test<-occ.model.data.test[fire_centre == 1, fc := "Cariboo"][fire_centre == 2, fc := "Coast"][fire_centre == 3, fc := "Kamloops"][fire_centre == 4, fc := "Northwest"][fire_centre == 5, fc := "Prince George"][fire_centre == 6, fc := "Southeast"]

coefs<-tidy(model)
fc.coef<-data.table(fire_centre = c(1, 2,3,4,5,6), fc_coef = c(0, filter(coefs, term == "as.factor(fire_centre)2")$estimate ,filter(coefs, term == "as.factor(fire_centre)3")$estimate,filter(coefs, term == "as.factor(fire_centre)4")$estimate,filter(coefs, term == "as.factor(fire_centre)5")$estimate,filter(coefs, term == "as.factor(fire_centre)6")$estimate))
                                                                    
frt.coef<-data.table(frt = c(3, 5,7,9,10,11,12,13,14,15), frt_coef = c(0, filter(coefs, term == "as.factor(frt)5")$estimate ,                    filter(coefs, term == "as.factor(frt)7")$estimate, filter(coefs, term == "as.factor(frt)9")$estimate,  filter(coefs, term == "as.factor(frt)10")$estimate,  filter(coefs, term == "as.factor(frt)11")$estimate,  filter(coefs, term == "as.factor(frt)12")$estimate, filter(coefs, term == "as.factor(frt)13")$estimate,  filter(coefs, term == "as.factor(frt)14")$estimate,  filter(coefs, term == "as.factor(frt)15")$estimate))

fire.num<-merge(occ.model.data.test, frt.coef, by = "frt")
fire.num<-merge(fire.num, fc.coef, by = "fire_centre")
fire.num<-fire.num[, s_con:=scale(con)][, s_dec:=scale(dec)]

fire.num<-fire.num[ ,pred_mu:= exp(filter(coefs, term == "(Intercept)")$estimate + filter(coefs, term == "CMI_MIN")$estimate*CMI_MIN + filter(coefs, term == "dCMI3yr")$estimate*dCMI3yr + filter(coefs, term == "avgCMIProv")$estimate*avgCMIProv + filter(coefs, term == "log(con + 1)")$estimate*log(con+1) + filter(coefs, term == "log(dec + 1)")$estimate*log(dec+1)+ filter(coefs, term == "Tdelta07")$estimate*Tdelta07 + frt_coef  + omega_s + log(flammable))]

#fire.num<-fire.num[ ,pred_mu:= exp(filter(coefs, term == "(Intercept)")$estimate + filter(coefs, term == "CMI")$estimate*CMI +filter(coefs, term == "CMI06")$estimate*CMI06+ filter(coefs, term == "lroad")$estimate*lroad + filter(coefs, term == "avgCMIProv")$estimate*avgCMIProv + filter(coefs, term == "log(young + 1)")$estimate*log(young + 1) + filter(coefs, term == "log(dec + 1)")$estimate*log(dec + 1) + frt_coef + fc_coef + omega_s + log(flammable))]

#disp_parm<-0.32
disp_parm<-0.33
runs<-rbindlist(lapply(1:1000, function(x){
  rbindlist(lapply(2018:2022, function(i){
    occ<-fire.num[FIRE_YEAR == i, ]
    selected.seed<-sample(1:1000000,1)
    set.seed(selected.seed)
    occ<-occ[, fire:= rnbinom(n = 1, size = disp_parm, mu =pred_mu), by=1:nrow(occ)][fire>0,]
    
    occ[,sum(fire), by = fire_centre][,seed:=selected.seed][,FIRE_YEAR:=i][,run:=x]
  }))
  }))

obs<-occ.model.data.test[,sum(count), by = c("FIRE_YEAR")]
obs_fc<-occ.model.data.test[,sum(count), by = c("fire_centre", "FIRE_YEAR")]
#obs<-occ.model.data.test[,sum(count_person), by = c("FIRE_YEAR")]
#obs_fc<-occ.model.data.test[,sum(count_person), by = c("fire_centre", "FIRE_YEAR")]
#obs<-occ.model.data.test[,sum(count_person), by = c("FIRE_YEAR")]
runs_prov<-runs[, sum(V1), by=c("FIRE_YEAR", "run")]

ggplot()+
  geom_boxplot(data=runs_prov,  aes(x=as.factor(FIRE_YEAR), y =V1)) +
  geom_point(data=obs,  aes(x=as.factor(FIRE_YEAR), y =V1, color = 'red')) +
   ylab("Number of fires (>1 ha)")+ xlab("Year")+ theme(legend.position="none")

runs[fire_centre == 1, fc := "Cariboo"][fire_centre == 2, fc := "Coast"][fire_centre == 3, fc := "Kamloops"][fire_centre == 4, fc := "Northwest"][fire_centre == 5, fc := "Prince George"][fire_centre == 6, fc := "Southeast"]
obs_fc[fire_centre == 1, fc := "Cariboo"][fire_centre == 2, fc := "Coast"][fire_centre == 3, fc := "Kamloops"][fire_centre == 4, fc := "Northwest"][fire_centre == 5, fc := "Prince George"][fire_centre == 6, fc := "Southeast"]

ggplot()+
  geom_boxplot(data=runs[FIRE_YEAR<2023,],  aes(x=as.factor(FIRE_YEAR), y =V1)) +
  geom_point(data=obs_fc[FIRE_YEAR<2023,],  aes(x=as.factor(FIRE_YEAR), y =V1, color = 'red')) +
  facet_wrap(~fc, ncol =2, scales = "free") + ylab("Number of fires (>1 ha)")+ xlab("Year")+ theme(legend.position="none")

if(FALSE){
  
nd <- data.frame(
    dCMI3yr = mean(occ.model.data$dCMI3yr),  
    con = mean(occ.model.data$con), dec = mean(occ.model.data$dec), CMI_MIN = mean(occ.model.data$CMI_MIN), young = mean(occ.model.data$young), frt = 14,
    year = as.integer(2020), avgCMIProv = seq(min(occ.model.data$avgCMIProv), max(occ.model.data$avgCMIProv), length = 100), flammable = mean(occ.model.data$flammable), x = mean(occ.model.data$x), y = mean(occ.model.data$y))

p <- predict(m8_iid, extra_time = 2020:2025, se_fit = T, re_form = NA)

ggplot(p, aes(CMI, exp(est), 
              ymin = exp(est - 1.96 * est_se), 
              ymax = exp(est + 1.96 * est_se))) +
    geom_line() + geom_ribbon(alpha = 0.4)

}
```


#### APPENDIX: Gaussian Markov Random Fields
```{r}
#Some functions to use later
# Matern correlation
cMatern <- function(h, nu, kappa) {
  ifelse(h > 0, besselK(h * kappa, nu) * (h * kappa)^nu / 
    (gamma(nu) * 2^(nu - 1)), 1)
}

#create some data such that its a single line of 250 points each 1/25 away from each other
loc <- 1:10 / 10 
#Calculate the adjacency matrix
mdist <- as.matrix(dist(loc))
d <- dim(goshawkNestingHabitat)
mdist <-as.matrix(dist(matrix(values(goshawkNestingHabitat,), d[1], d[2], byrow=TRUE)))

#parameters to show sensitivity
nu <- c(0.5, 1, 2.5, 3, 4.5)
range <- c(1,2,3,4)
params <- cbind(nu = rep(nu, length(range)), range = rep(range, each = length(nu)))

params <- data.frame(nu = 0.5, range =1)
# Sample error five times - white noise gaussian standard normal ~ N(0, 1)
set.seed(123)
z <- matrix(rnorm(nrow(mdist) * 5), ncol = 5)

# Compute the correlated samples
# Scenarios (i.e., different set of parameters)
yy <- lapply(1:nrow(params), function(j) { 
  param <- c(params[j, 1], sqrt(8 * params[j, 1]) / params[j, 2], 
    params[j, 2])
  v <- cMatern(mdist, param[1], param[2])

  # fix the diagonal to avoid numerical issues
  diag(v) <- 1 + 1e-9 

  # Parameter scenario and computed sample
  return(list(params = param, y = crossprod(chol(v), z)))
})

#Conclusion: the nu parameter adds inflections, the range parameter add smoothness
```


#### sim with a raster
```{r}
# Matern correlation
cMatern <- function(h, nu, kappa) {
  ifelse(h > 0, besselK(h * kappa, nu) * (h * kappa)^nu / 
    (gamma(nu) * 2^(nu - 1)), 1)
}

ras<-rast(nrow =100, ncol =100, xmin = -180, xmax = 180, ymin = -180, ymax = 180)
d <- dim(ras)

pts<-xyFromCell(ras, 1:(d[1]*d[2]))
dmat <- as.matrix(dist(pts))

beta0 <- 10
sigma2e <- 0.3
sigma2u <- 5
kappa <- 7
nu <- 1

mcor <- cMatern(dmat, nu, kappa) 
mcov <- sigma2e * diag(nrow(mcor)) + sigma2u * mcor
Rc <- chol(mcov)
set.seed(234)
n <- d[1]*d[2]
y1 <- beta0 + drop(crossprod(Rc, rnorm(d[1]*d[2]))) 
ras[]<-y1
```