---
title: "fire_occurrence"
output: html_document
date: '2023-09-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
library(glmmTMB)
library(DHARMa)
library(sdmTMB)
```

In this script we model the occurrence of lightning cause wildfires. This includes the number of fires and where they occur. to do this we rely on the historical incidents data reported in the data catalog of BC. The number of fires within a 10 km grid are estimated along with various predictor variables that relate to landcover and climate.The landcover data comes from the VRI using the previous year of the fire as the estimate of the amount of landcover types within the 10 km voxel.

## Data
```{r}
data.lightning<-readRDS("data.lightning.rds")
occ.model.data<-data.lightning[!is.na(CMI3yr),][,dCMI3yr:=CMI-(CMI3yr/3)][, coast:=0][frt==15, coast:=1][,flammable:=con + mix + dec + young + veg][flammable >0, ][, year:= as.factor(FIRE_YEAR)][!is.na(fire_centre),]

occ.model.data<-occ.model.data[, avgCMIProv:=sum(CMI)/.N, by = c("FIRE_YEAR")][,dry:=0][avgCMIProv < -0.47, dry :=1]

# Determine threshold
threshold<-occ.model.data[, .(count = sum(count), avgCMIProv = min(avgCMIProv) ), by = FIRE_YEAR]
saveRDS(threshold, "avgCMIProv.rds")
```

## Model
```{r}

l12_nb_3yr <- glmmTMB(count ~ 1 + CMI + CMI3yr +avgCMIProv, offset = log(flammable), family = nbinom2(link = "log"), ziformula = ~0, data=occ.model.data)

simulationOutput <- simulateResiduals(fittedModel = l12_nb_3yr)
plot(simulationOutput)

occ.model.data$pred_mu<-data.table(mu= predict(l12_nb_3yr, newdata = occ.model.data[, c("flammable", "CMI", "CMI3yr", "avgCMIProv")][,FIRE_YEAR := NA][,frt := NA], type="response"))
ggplot2::ggplot(data=occ.model.data[ FIRE_YEAR %in% c( 2012, 2016, 2017, 2018, 2020, 2022)], aes(x=x, y=y, color = pred_mu)) + facet_wrap(~FIRE_YEAR) + geom_point()
occ.model.data[, sim:= rnbinom(n = 1, size = 0.251, mu =pred_mu )]
 
sim1=simulate(l12_nb_3yr, nsim = 1)
Simdat=occ.model.data[!is.na(CMI3yr),]
Simdat$count=sim1[[1]]
Simdat=transform(Simdat,  
            type="simulated")
occ.model.data$type = "observed"  
Dat=rbind(occ.model.data[!is.na(CMI3yr),], Simdat) 
ggplot(Dat[, sum(count), by = c("FIRE_YEAR", "type")],  aes(x=FIRE_YEAR, y =V1, colour=type))+geom_line()
ggplot(Dat,  aes(x=CMI, y =as.factor(count), colour=type))+geom_boxplot() + facet_grid(~type)

#Set the trainingset
occ.model.data.train<-occ.model.data[FIRE_YEAR < 2018, ]
spde <- make_mesh(occ.model.data.train[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)

m0 <- sdmTMB(data = occ.model.data.train, count ~ 1  , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = F, spatiotemporal = FALSE, reml=F)

m0_gmrf <- sdmTMB(data = occ.model.data.train, count ~ 1  , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m0_gmrf_fc <- sdmTMB(data = occ.model.data.train, count ~ 1 + as.factor(fire_centre) , offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m1 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m2 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  +  dCMI3yr + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

m3 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN + dCMI3yr + avgCMIProv + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

m4 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN + dCMI3yr + avgCMIProv + as.factor(frt) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year",  mesh = spde, spatial = T, spatiotemporal = FALSE)

##Vegetation typing
m5 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(veg+1) + log(dec+1) + log(mix+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE)

m6 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr+ avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=F)

m7 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = F, spatiotemporal = FALSE, reml=F)

m7.reml <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=T)

m8 <- sdmTMB(data = occ.model.data.train, count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1) + as.factor(fire_centre), offset = log(occ.model.data.train$flammable), family = nbinom2(), time = "year", mesh = spde, spatial = T, spatiotemporal = FALSE, reml=T)

#test99<-predict(m6)
#test99<-test99[, estres:=exp(est)]
#test99<-test99[, mu1:= exp(-13.15)]
#test99<-test99[, mu2:= mu1*(1 + exp(m6$model$par[["log_ratio_mix"]]))]
#test99<-test99[, est9:= ((1-plogis(m6$model$par[["logit_p_mix"]]))*mu1 + plogis(m6$model$par[["logit_p_mix"]])*mu2)*flammable]

AIC(m0, m0_gmrf, m0_gmrf_fc, m1, m2, m3, m4, m5,m6, m7)
saveRDS(m8, "C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/m8.rds")
saveRDS(m7.reml, "C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/m7reml.rds")

```


## Diagnostics
```{r}
m7.reml<-readRDS("C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/m7reml.rds")
occ.model.data.train$resids <- residuals(m7.reml) # randomized quantile residuals
qqnorm(occ.model.data.train$resids)
qqline(occ.model.data.train$resids)

sim1<-simulate(m7.reml, nsim=100, re_form = NULL)
#sim1<-simulate(m4, nsim=1000)
Simdat<-occ.model.data.train
simdata<-rbindlist(lapply(seq(1,100,1), function(rep_sim){
  Simdat$count<-sim1[,rep_sim]
  Simdat=transform(Simdat,  
            type=paste0("simulated_rep",rep_sim))
}))

occ.model.data.train$type = "observed"  
Dat=rbind(occ.model.data.train, simdata) 
data_sim_ag<-Dat[, sum(count), by = c("FIRE_YEAR", "type", "fire_centre")]


ggplot()+
  geom_boxplot(data=data_sim_ag[type != 'observed'],  aes(x=as.factor(FIRE_YEAR), y =V1)) +
  geom_point(data=data_sim_ag[type == 'observed'],  aes(x=as.factor(FIRE_YEAR), y =V1, color = 'red')) +
  facet_wrap(~fire_centre, ncol =2, scales = "free") + ylab("Number of fires (>1 ha)")+ xlab("Year")+ theme(legend.position="none")

data.count.pred<-predict(m7.reml, type = "link", re_form = NULL)[, frt:=as.factor(frt)]

data.count.pred<-cbind(data.count.pred, model.matrix( ~ 0 + frt, data=data.count.pred )) 
#data.count.pred[ ,est_noy:= -17.5 -0.125*CMI_MIN -0.162*dCMI3yr -0.998*frt5 -0.966*frt7 -1.61*frt9  -1.55*frt10  -1.15*frt11  -1.19*frt12 -1.39*frt13  -1.05*frt14  -2.45*frt15 +  0.478*log(con + 1) + 0.0882*log(young + 1) -0.0409*log(dec + 1)+ log(flammable) + est_rf]

#data.count.pred$est2<-exp(data.count.pred$est+log(data.count.pred$flammable))
data.count.pred$est2<-exp(data.count.pred$est)


number<-occ.model.data[, .(nfires = sum(count)), by = c('FIRE_YEAR', 'fire_centre')]
test_fo<-merge(data.count.pred[,.(pred = sum(est2)), by = c("FIRE_YEAR", 'fire_centre')], number, by = c("FIRE_YEAR", 'fire_centre'))

numberbc<-data.count.pred[, .(nfires = sum(count)), by = c('FIRE_YEAR')]
test_bc<-merge(data.count.pred[,.(pred = sum(est2)), by = c("FIRE_YEAR")], numberbc, by = c("FIRE_YEAR"))
plot(test_bc[,c("pred", "nfires")])
abline(1,1)

library(dplyr)
test_fo<-test_fo[fire_centre == 1, fc := "Cariboo"][fire_centre == 2, fc := "Coast"][fire_centre == 3, fc := "Kamloops"][fire_centre == 4, fc := "Northwest"][fire_centre == 5, fc := "Prince George"][fire_centre == 6, fc := "Southeast"]
r_label<-test_fo %>%
  group_by(fc) %>%
  summarize(COR=cor(pred,nfires))
r_label<-data.table(r_label)[,label:=paste0('r=',round(COR,3))]

ggplot(data=test_fo, aes(x = pred, y = nfires)) + geom_point()+ geom_abline( slope=1, intercept=0, col = 'black') + geom_smooth(method='lm',se=T) + ylab("Observed")+ xlab("Predicted")+ theme(legend.position="none") + facet_wrap(~fc, scales = "free", ncol =3) + geom_text(data = r_label, aes(Inf, -Inf, label = label), col = "red",  hjust = 1, vjust = -1)

if(FALSE){
  
nd <- data.frame(
    dCMI3yr = mean(occ.model.data$dCMI3yr),  
    con = mean(occ.model.data$con), dec = mean(occ.model.data$dec), CMI_MIN = mean(occ.model.data$CMI_MIN), young = mean(occ.model.data$young), frt = 14,
    year = as.factor(2020), avgCMIProv = seq(min(occ.model.data$avgCMIProv), max(occ.model.data$avgCMIProv), length = 100), flammable = mean(occ.model.data$flammable), x = mean(occ.model.data$x), y = mean(occ.model.data$y))

p <- predict(m8, newdata = nd, se_fit = T, re_form = NA)

ggplot(p, aes(avgCMIProv, exp(est), 
              ymin = exp(est - 1.96 * est_se), 
              ymax = exp(est + 1.96 * est_se))) +
    geom_line() + geom_ribbon(alpha = 0.4)

}
```


#### APPENDIX: Gaussian Markov Random Fields
```{r}
#Some functions to use later
# Matern correlation
cMatern <- function(h, nu, kappa) {
  ifelse(h > 0, besselK(h * kappa, nu) * (h * kappa)^nu / 
    (gamma(nu) * 2^(nu - 1)), 1)
}

#create some data such that its a single line of 250 points each 1/25 away from each other
loc <- 1:10 / 10 
#Calculate the adjacency matrix
mdist <- as.matrix(dist(loc))
d <- dim(goshawkNestingHabitat)
mdist <-as.matrix(dist(matrix(values(goshawkNestingHabitat,), d[1], d[2], byrow=TRUE)))

#parameters to show sensitivity
nu <- c(0.5, 1, 2.5, 3, 4.5)
range <- c(1,2,3,4)
params <- cbind(nu = rep(nu, length(range)), range = rep(range, each = length(nu)))

params <- data.frame(nu = 0.5, range =1)
# Sample error five times - white noise gaussian standard normal ~ N(0, 1)
set.seed(123)
z <- matrix(rnorm(nrow(mdist) * 5), ncol = 5)

# Compute the correlated samples
# Scenarios (i.e., different set of parameters)
yy <- lapply(1:nrow(params), function(j) { 
  param <- c(params[j, 1], sqrt(8 * params[j, 1]) / params[j, 2], 
    params[j, 2])
  v <- cMatern(mdist, param[1], param[2])

  # fix the diagonal to avoid numerical issues
  diag(v) <- 1 + 1e-9 

  # Parameter scenario and computed sample
  return(list(params = param, y = crossprod(chol(v), z)))
})

#Conclusion: the nu parameter adds inflections, the range parameter add smoothness
```
## Global model - train and test
```{r}
models.g<-readRDS("m7reml.rds")
spde_loo<- make_mesh(occ.model.data[FIRE_YEAR >= 2018, c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)

test.g<-lapply(1:1000, function(x){
  test<-data.table(sdmTMB_simulate(formula = ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1)+ as.factor(fire_centre), data = occ.model.data[FIRE_YEAR >= 2018 , ],  mesh =spde_loo, range = tidy(models.g, 'ran_par')$estimate[1], sigma_O = tidy(models.g, 'ran_par')$estimate[3],   phi =  tidy(models.g, 'ran_par')$estimate[2], B = tidy(models.g)$estimate, time = "year", family = nbinom2(), offset = log(occ.model.data[FIRE_YEAR >= 2018, ]$flammable)))
  
test$fire_centre<-occ.model.data[FIRE_YEAR >= 2018 ,]$fire_centre

out<-test[, .(pred = sum(mu)), by = c('fire_centre', 'year')]
out
})

out<-rbindlist(test.g)
out<-out[, FIRE_YEAR:= as.integer(as.character(year))]
out.bounds<-out[, .(nf_low = quantile(pred,p =0.025), nf_med = quantile(pred,p =0.5), nf_up = quantile(pred,p =0.975)), by = c('FIRE_YEAR', 'fire_centre')]

check.out<-merge(number, out.bounds, by.x = c('fire_centre', 'FIRE_YEAR'), by.y = c('fire_centre', 'FIRE_YEAR'), all.y =T)

saveRDS(check.out, "checkout.rds")
```

## Cariboo
```{r}
#Cariboo
  data.fit.fc1 <- occ.model.data[ FIRE_YEAR < 2018 & fire_centre == 1,]
  spde_fc1_loo <- make_mesh(data.fit.fc1[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
  models.fc1 <- sdmTMB(data = data.fit.fc1 , count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), offset = log(data.fit.fc1$flammable), family = nbinom2(), time = "year", mesh = spde_fc1_loo , spatial = T, spatiotemporal = FALSE, reml=T)

saveRDS(models.fc1, "loo_local_fc1_fit.rds")

spde_fc1_loo<- make_mesh(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==1, c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
test.fc1<-lapply(1:1000, function(x){
  test<-data.table(sdmTMB_simulate(formula = ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), data = occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==1, ],  mesh =spde_fc1_loo, range = tidy(models.fc1, 'ran_par')$estimate[1], sigma_O = tidy(models.fc1, 'ran_par')$estimate[3],   phi =  tidy(models.fc1, 'ran_par')$estimate[2], B = tidy(models.fc1)$estimate, time = "year", family = nbinom2(), offset = log(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==1, ]$flammable)))
  
test$fire_centre<-1

out<-test[, .(pred = sum(mu)), by = c('fire_centre', 'year')]
out
})

out.fc1<-rbindlist(test.fc1)
out.fc1<-out.fc1[, FIRE_YEAR:= as.integer(as.character(year))]
out.fc1.bounds<-out.fc1[, .(nf_low = quantile(pred,p =0.025), nf_med = quantile(pred,p =0.5), nf_up = quantile(pred,p =0.975)), by = c('FIRE_YEAR', 'fire_centre')]

check.out.fc1<-merge(number, out.fc1.bounds, by.x = c('fire_centre', 'FIRE_YEAR'), by.y = c('fire_centre', 'FIRE_YEAR'), all.y =T)
```

## Coast
```{r}
#Cariboo
  data.fit.fc2 <- occ.model.data[ FIRE_YEAR < 2018 & fire_centre == 2,]
  spde_fc2_loo <- make_mesh(data.fit.fc2[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
  models.fc2 <- sdmTMB(data = data.fit.fc2 , count ~ 1 + CMI_MIN + log(con + 1), offset = log(data.fit.fc2$flammable), family = nbinom2(), time = "year", mesh = spde_fc2_loo , spatial = F, spatiotemporal = FALSE, reml=T)

saveRDS(models.fc2, "loo_local_fc2_fit.rds")

spde_fc2_loo<- make_mesh(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==2, c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
test.fc2<-lapply(1:100, function(x){
  test<-data.table(sdmTMB_simulate(formula = ~ 1+ CMI_MIN + log(con + 1) , data = occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==2, ],  mesh =spde_fc2_loo, range = NULL, phi =  tidy(models.fc2, 'ran_par')$estimate[1], B = tidy(models.fc2)$estimate, time = "year", family = nbinom2(),spatial = F, offset = log(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==2, ]$flammable)))
  
test$fire_centre<-2

out<-test[, .(pred = sum(mu)), by = c('fire_centre', 'year')]
out
})

out.fc2<-rbindlist(test.fc2)
out.fc2<-out.fc2[, FIRE_YEAR:= as.integer(as.character(year))]
out.fc2.bounds<-out.fc2[, .(nf_low = quantile(pred,p =0.025), nf_med = quantile(pred,p =0.5), nf_up = quantile(pred,p =0.975)), by = c('FIRE_YEAR', 'fire_centre')]

check.out.fc2<-merge(number, out.fc2.bounds, by.x = c('fire_centre', 'FIRE_YEAR'), by.y = c('fire_centre', 'FIRE_YEAR'), all.y =T)
```

## Kamloops
```{r}
  data.fit.fc3 <- occ.model.data[ FIRE_YEAR < 2018 & fire_centre == 3,]
  spde_fc3_loo <- make_mesh(data.fit.fc3[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
  models.fc3 <- sdmTMB(data = data.fit.fc3 , count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), offset = log(data.fit.fc3$flammable), family = nbinom2(), time = "year", mesh = spde_fc3_loo , spatial = T, spatiotemporal = FALSE, reml=T)

saveRDS(models.fc3, "loo_local_fc3_fit.rds")

spde_fc3_loo<- make_mesh(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==3, c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
test.fc3<-lapply(1:1000, function(x){
  test<-data.table(sdmTMB_simulate(formula = ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), data = occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==3, ],  mesh =spde_fc3_loo, range = tidy(models.fc3, 'ran_par')$estimate[1], sigma_O = tidy(models.fc3, 'ran_par')$estimate[3],   phi =  tidy(models.fc3, 'ran_par')$estimate[2], B = tidy(models.fc3)$estimate, time = "year", family = nbinom2(), offset = log(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==3, ]$flammable)))
  
test$fire_centre<-3

out<-test[, .(pred = sum(mu)), by = c('fire_centre', 'year')]
out
})

out.fc3<-rbindlist(test.fc3)
out.fc3<-out.fc3[, FIRE_YEAR:= as.integer(as.character(year))]
out.fc3.bounds<-out.fc3[, .(nf_low = quantile(pred,p =0.025), nf_med = quantile(pred,p =0.5), nf_up = quantile(pred,p =0.975)), by = c('FIRE_YEAR', 'fire_centre')]

check.out.fc3<-merge(number, out.fc3.bounds, by.x = c('fire_centre', 'FIRE_YEAR'), by.y = c('fire_centre', 'FIRE_YEAR'), all.y =T)
```
## Northwest
```{r}
#Cariboo
  data.fit.fc4 <- occ.model.data[ FIRE_YEAR < 2018 & fire_centre == 4,]
  spde_fc4_loo <- make_mesh(data.fit.fc4[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
  models.fc4 <- sdmTMB(data = data.fit.fc4 , count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), offset = log(data.fit.fc4$flammable), family = nbinom2(), time = "year", mesh = spde_fc4_loo , spatial = T, spatiotemporal = FALSE, reml=T)

saveRDS(models.fc4, "loo_local_fc4_fit.rds")

spde_fc4_loo<- make_mesh(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==4, c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
test.fc4<-lapply(1:1000, function(x){
  test<-data.table(sdmTMB_simulate(formula = ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), data = occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==4, ],  mesh =spde_fc4_loo, range = tidy(models.fc4, 'ran_par')$estimate[1], sigma_O = tidy(models.fc4, 'ran_par')$estimate[3],   phi =  tidy(models.fc4, 'ran_par')$estimate[2], B = tidy(models.fc4)$estimate, time = "year", family = nbinom2(), offset = log(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==4, ]$flammable)))
  
test$fire_centre<-4

out<-test[, .(pred = sum(mu)), by = c('fire_centre', 'year')]
out
})

out.fc4<-rbindlist(test.fc4)
out.fc4<-out.fc1[, FIRE_YEAR:= as.integer(as.character(year))]
out.fc4.bounds<-out.fc4[, .(nf_low = quantile(pred,p =0.025), nf_med = quantile(pred,p =0.5), nf_up = quantile(pred,p =0.975)), by = c('FIRE_YEAR', 'fire_centre')]

check.out.fc4<-merge(number, out.fc4.bounds, by.x = c('fire_centre', 'FIRE_YEAR'), by.y = c('fire_centre', 'FIRE_YEAR'), all.y =T)
```


## PG
```{r}
  data.fit.fc5 <- occ.model.data[ FIRE_YEAR < 2018 & fire_centre == 5,]
  spde_fc5_loo <- make_mesh(data.fit.fc5[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
  models.fc5 <- sdmTMB(data = data.fit.fc5 , count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), offset = log(data.fit.fc5$flammable), family = nbinom2(), time = "year", mesh = spde_fc5_loo , spatial = T, spatiotemporal = FALSE, reml=T)

saveRDS(models.fc5, "loo_local_fc5_fit.rds")

spde_fc5_loo<- make_mesh(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==5, c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
test.fc5<-lapply(1:1000, function(x){
  test<-data.table(sdmTMB_simulate(formula = ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), data = occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==5, ],  mesh =spde_fc5_loo, range = tidy(models.fc5, 'ran_par')$estimate[1], sigma_O = tidy(models.fc5, 'ran_par')$estimate[3],   phi =  tidy(models.fc5, 'ran_par')$estimate[2], B = tidy(models.fc5)$estimate, time = "year", family = nbinom2(), offset = log(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==5, ]$flammable)))
  
test$fire_centre<-5

out<-test[, .(pred = sum(mu)), by = c('fire_centre', 'year')]
out
})

out.fc5<-rbindlist(test.fc5)
out.fc5<-out.fc5[, FIRE_YEAR:= as.integer(as.character(year))]
out.fc5.bounds<-out.fc5[, .(nf_low = quantile(pred,p =0.025), nf_med = quantile(pred,p =0.5), nf_up = quantile(pred,p =0.975)), by = c('FIRE_YEAR', 'fire_centre')]

check.out.fc5<-merge(number, out.fc5.bounds, by.x = c('fire_centre', 'FIRE_YEAR'), by.y = c('fire_centre', 'FIRE_YEAR'), all.y =T)
```

## Southeast
```{r}
#Cariboo
  data.fit.fc6 <- occ.model.data[ FIRE_YEAR < 2018 & fire_centre == 6,]
  spde_fc6_loo <- make_mesh(data.fit.fc6[,c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
  models.fc6 <- sdmTMB(data = data.fit.fc6 , count ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), offset = log(data.fit.fc6$flammable), family = nbinom2(), time = "year", mesh = spde_fc6_loo , spatial = T, spatiotemporal = FALSE, reml=T)

saveRDS(models.fc6, "loo_local_fc6_fit.rds")

spde_fc6_loo<- make_mesh(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==6, c("x", "y")], xy_cols = c("x", "y"), cutoff = 10)
test.fc6<-lapply(1:1000, function(x){
  test<-data.table(sdmTMB_simulate(formula = ~ 1 + CMI_MIN  + dCMI3yr + avgCMIProv + as.factor(frt) + log(con+1) + log(young+1) + log(dec+1), data = occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==6, ],  mesh =spde_fc6_loo, range = tidy(models.fc6, 'ran_par')$estimate[1], sigma_O = tidy(models.fc6, 'ran_par')$estimate[3],   phi =  tidy(models.fc6, 'ran_par')$estimate[2], B = tidy(models.fc6)$estimate, time = "year", family = nbinom2(), offset = log(occ.model.data[FIRE_YEAR >= 2018 & fire_centre ==6, ]$flammable)))
  
test$fire_centre<-6

out<-test[, .(pred = sum(mu)), by = c('fire_centre', 'year')]
out
})

out.fc6<-rbindlist(test.fc6)
out.fc6<-out.fc6[, FIRE_YEAR:= as.integer(as.character(year))]
out.fc6.bounds<-out.fc6[, .(nf_low = quantile(pred,p =0.025), nf_med = quantile(pred,p =0.5), nf_up = quantile(pred,p =0.975)), by = c('FIRE_YEAR', 'fire_centre')]

check.out.fc6<-merge(number, out.fc6.bounds, by.x = c('fire_centre', 'FIRE_YEAR'), by.y = c('fire_centre', 'FIRE_YEAR'), all.y =T)
```

##compare forecasts
```{r}
#locals
local.fits<-rbindlist(list(check.out.fc1,check.out.fc2,check.out.fc3,check.out.fc4,check.out.fc5,check.out.fc6))[fire_centre == 1, fc := "Cariboo"][fire_centre == 2, fc := "Coast"][fire_centre == 3, fc := "Kamloops"][fire_centre == 4, fc := "Northwest"][fire_centre == 5, fc := "Prince George"][fire_centre == 6, fc := "Southeast"]
check.out<-check.out[fire_centre == 1, fc := "Cariboo"][fire_centre == 2, fc := "Coast"][fire_centre == 3, fc := "Kamloops"][fire_centre == 4, fc := "Northwest"][fire_centre == 5, fc := "Prince George"][fire_centre == 6, fc := "Southeast"]
local.fits[fire_centre==2, nf_up := NA]

ggplot() + 
  geom_line(data = check.out, aes(x = FIRE_YEAR, y= nfires), col = 'red', lwd = 1.2)+ 
  geom_line(data = check.out, aes(x = FIRE_YEAR, y= nf_med), col = 'blue', lwd = 1.1)+ 
  geom_line(data = check.out, aes(x = FIRE_YEAR, y= nf_low), col = 'blue', lty = 2)+ 
  geom_line(data = check.out, aes(x = FIRE_YEAR, y= nf_up), col = 'blue', lty = 2)+
  geom_line(data = local.fits, aes(x = FIRE_YEAR, y= nf_med), col = 'green', lwd = 1.1)+ 
  geom_line(data = local.fits, aes(x = FIRE_YEAR, y= nf_low), col = 'green', lty = 2)+ 
  geom_line(data =local.fits, aes(x = FIRE_YEAR, y= nf_up), col = 'green', lty = 2)+ facet_wrap(~fc, scales="free_y")
```
## sim with a raster
```{r}
# Matern correlation
cMatern <- function(h, nu, kappa) {
  ifelse(h > 0, besselK(h * kappa, nu) * (h * kappa)^nu / 
    (gamma(nu) * 2^(nu - 1)), 1)
}

ras<-rast(nrow =100, ncol =100, xmin = -180, xmax = 180, ymin = -180, ymax = 180)
d <- dim(ras)

pts<-xyFromCell(ras, 1:(d[1]*d[2]))
dmat <- as.matrix(dist(pts))

beta0 <- 10
sigma2e <- 0.3
sigma2u <- 5
kappa <- 7
nu <- 1

mcor <- cMatern(dmat, nu, kappa) 
mcov <- sigma2e * diag(nrow(mcor)) + sigma2u * mcor
Rc <- chol(mcov)
set.seed(234)
n <- d[1]*d[2]
y1 <- beta0 + drop(crossprod(Rc, rnorm(d[1]*d[2]))) 
ras[]<-y1
```