---
title: "fire_occurrence"
output: html_document
date: '2023-09-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(rpostgis)
library(keyring)
library(bcdata)
```

In this script we develop the data sets used to model the occurrence and size of lightning cause wildfires. This includes the number of fires, where they occur and their size. To do this we rely on the historical incidents data reported in the data catalog of BC. The number of fires within a grid are estimated along with various predictor variables that relate to landcover and climate.The landcover data comes from the VRI using the previous year of the fire as the estimate of the amount of landcover types within the 10 km voxel.

## Data
```{r, data_capture}
# Create a grid
restest = c(10000, 10000)
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = restest,
  vals = 0)
pixel.grid <- data.table(V1 = as.integer(prov.rast[]))[, pixelid := seq_len(.N)]
setorder(pixel.grid, "pixelid")#sort the pixels table so that pixelid is in order.
pixel.grid$V1 <- NULL
prov.rast[]<-pixel.grid$pixelid

# Get the Fire Regime Types, Fire Centres and NDTs
ndt<-getSpatialQuery("SELECT case when ntrldstrbn = 'NDT1' then 1 when ntrldstrbn = 'NDT2' then 2 when ntrldstrbn = 'NDT3' then 3 when ntrldstrbn = 'NDT4' then 4 when ntrldstrbn = 'NDT5' then 5 end as ndt, wkb_geometry FROM public.bec_zone")
ras.ndt <- fasterize::fasterize (ndt, prov.rast, field = "ndt")

frt<-getSpatialQuery("SELECT * FROM frt_canada")
ras.frt <- fasterize::fasterize (frt, prov.rast, field = "Cluster")

frcentre<-getSpatialQuery("SELECT * FROM drpmffrcnt_polygon")
ras.frcentre <- fasterize::fasterize (frcentre, prov.rast, field = "ogc_fid")

if(terra::ext(prov.rast) == terra::ext(ras.frt)){ # need to check that each of the extents are the same
  pixel.frt <-cbind(pixel.grid , data.table(frt= as.numeric(ras.frt[]), ndt = ras.ndt[], fire_centre = ras.frcentre[]))
  rm(ras.frt, ras.frcentre)
  gc()
}else{
  stop(paste0("ERROR: extents are not the same check -"))
}

#Get road development
rds.prov<-rast("C:/Users/klochhea/castor/R/scenarios/bckcst_road/prov_rd_yr.tif")
prov.rast100 <- raster::raster ( # standardized provincial raster with no data in it
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = 100,
  vals = NA)
rds.prov<-merge(rds.prov, rast(prov.rast100))
rds.table<-rbindlist(lapply(2009:2022, function(x){
  temp<-rds.prov
  temp[temp[] <= x]<-1
  temp[temp[] > 1]<-0
  temp[is.na(temp[])]<-0
  test<-aggregate(temp, fact =100, fun =sum, na.rm =TRUE)
  test2<-crop(test, prov.rast)
  out<-data.table(year = x, road = values(test2))[,pixelid := seq_len(.N)]
  out
}))
setnames(rds.table, "road.lyr.1", "road")

#Get the climate data
bc_grid <- data.table::fread("C:/Data/localApps/Climatebc_v730/bc_dem_frt_Kyle.csv")
bc_sf <- st_transform(st_as_sf(bc_grid, coords = c("lon", "lat"), crs = 4326, agr = "constant"), crs = 3005)
bc_dem <- terra::rasterize(bc_sf, prov.rast, field = "el")

#note using 2005 climate to get the 5 year prior average
climateData<-rbindlist(lapply(seq(2005, 2023, 1), function(x){
  message(x)
  data<-data.table::fread(paste0("C:/Data/localApps/Climatebc_v730/test", x, ".csv"))
  data<-data[, `:=`(tdelta05 = Tmax05-Tmin05, tdelta06 = Tmax06-Tmin06, tdelta07 = Tmax07-Tmin07, tdelta08 = Tmax08-Tmin08 )]
    data<-data[, `:=`(CMI = rowMeans(.SD, na.rm=T)), .SDcols=c("CMI05", "CMI06","CMI07","CMI08")]
    data<-data[, `:=`(CMD = rowMeans(.SD, na.rm=T)), .SDcols=c("CMD05", "CMD06","CMD07","CMD08")]
    data<-data[, `:=`(CMD_sm = rowSums(.SD, na.rm=T)), .SDcols=c("CMD05", "CMD06","CMD07","CMD08")]
    data<-data[, `:=`(PPT_sm = rowSums(.SD, na.rm=T)), .SDcols=c("PPT05", "PPT06","PPT07","PPT08")]
    data<-data[, `:=`(DD18_sm = rowSums(.SD, na.rm=T)), .SDcols=c("DD18_05", "DD18_06","DD18_07","DD18_08")]
  data<-data[, TEMP_MAX:= do.call(pmax, .SD),.SDcols=c("Tmax05","Tmax06","Tmax07","Tmax08") ]
  data<-data[, CMI_MIN:= do.call(pmin, .SD),.SDcols=c("CMI05", "CMI06","CMI07","CMI08") ]
  
  data<-data[,c("ID1", "CMI","CMI_MIN", "CMI05", "CMI06","CMI07","CMI08", "CMD", "CMD_sm", "TEMP_MAX", "DD18_sm", "PPT_sm","tdelta05","tdelta06","tdelta07","tdelta08")]
  data<-merge(data, bc_grid[,c("ID1", "lat", "lon")] , by = "ID1")
  data_sf <- st_transform(st_as_sf(data, coords = c("lon", "lat"), crs = 4326, agr = "constant"), crs = 3005)
  data_ras_CMI <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "CMI")
    data_ras_CMI_min <- terra::rasterize(data_sf, prov.rast, fun = mean, field = "CMI_MIN")
  data_ras_CMD <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "CMD")
  data_ras_CMI05 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "CMI05")
 data_ras_CMI06 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "CMI06")
 data_ras_CMI07 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "CMI07")
 data_ras_CMI08 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "CMI08")
  data_ras_CMD_sm <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "CMD_sm")
  data_ras_TEMP_MAX <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "TEMP_MAX")
  data_ras_DD18_sm <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "DD18_sm")
  data_ras_PPT_sm <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "PPT_sm")
  data_ras_tdelta05 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "tdelta05")
   data_ras_tdelta06 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "tdelta06")
   data_ras_tdelta07 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "tdelta07")
   data_ras_tdelta08 <- terra::rasterize(data_sf, prov.rast,  fun = mean, field = "tdelta08")
  pixel.data <- data.table(TEMP_MAX = data_ras_TEMP_MAX [], CMI = data_ras_CMI [], CMI_MIN = data_ras_CMI_min[],CMI05 = data_ras_CMI05 [], CMI06 = data_ras_CMI06 [],CMI07 = data_ras_CMI07 [],CMI08 = data_ras_CMI08 [],CMD = data_ras_CMD [], CMD_sm = data_ras_CMD_sm [], DD18_sm = data_ras_DD18_sm [], PPT_sm = data_ras_PPT_sm [], Tdelta05 = data_ras_tdelta05[], Tdelta06 = data_ras_tdelta06[], Tdelta07 = data_ras_tdelta07[], Tdelta08 = data_ras_tdelta08[])[, pixelid := seq_len(.N)][, year := x]
  pixel.data
}))
#Rolling average
climateData<-climateData[, CMI5yr := frollsum(.SD, n=5), by = "pixelid", .SDcols = "CMI"]
climateData<-climateData[, CMI3yr := frollsum(.SD, n=3), by = "pixelid", .SDcols = "CMI"]
climateData<-climateData[, CMI2yr := frollsum(.SD, n=2), by = "pixelid", .SDcols = "CMI"]
#Join provincial raster data to the ignition data
# try extract pixel id's of each fire location and cbind it to the igntion data
ignit<-try(
  bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_INCIDENTS_SP") %>%
    filter(FIRE_YEAR >= 2009) %>%
    filter(FIRE_TYPE == "Fire") %>%
    filter(CURRENT_SIZE >= 1) %>%
    filter(FIRE_CAUSE %in% c("Lightning", "Person")) %>%
    collect()
)

head(ignit)
ignition2 <- sf::st_transform (ignit, 3005)
pixelid <- terra::extract(prov.rast, ignition2)
ignition2<-data.table(cbind(ignition2, pixelid))

ignit_unknown<-rbindlist(lapply(seq(2009,2023,1), function(y){
  yearx<-st_as_sf(ignition2[FIRE_YEAR == y,])
  test<-rbindlist(lapply(st_as_text(yearx$geometry), function(x){
    out<-getTableQuery(glue::glue("select bclcs_level_1 from vri.veg_comp_lyr_r1_poly{y-1} 
    where st_intersects(st_buffer(st_geomfromtext('{x}', 3005), 50),shape) = TRUE 
    order by bclcs_level_1 DESC limit 1;"))
    if(nrow(out) == 0) {
      out<- rbind(out, data.table(bclcs_level_1 = 'U')) 
    }
    out
    }))
  yearx$bclcs_level_1<-test$bclcs_level_1
  yearx
}))

ignit_unknown_climate<-merge(ignit_unknown, climateData, by.x =c("pixelid", "FIRE_YEAR"),  by.y=c("pixelid","year"), all.y = TRUE)
ignit_unknown_climate<-ignit_unknown_climate[!is.na(CMI),] # remove the banner voxels

# Fire causes
lightning.count<-ignit_unknown_climate[FIRE_CAUSE=="Lightning" & bclcs_level_1 != 'U', .(count=.N), by = c("pixelid", "FIRE_YEAR")]
person.count<-ignit_unknown_climate[FIRE_CAUSE=="Person" & bclcs_level_1 != 'U', .(count=.N), by = c("pixelid", "FIRE_YEAR")]

#FIRE SIZE
data.lightning.size<- ignit_unknown_climate[FIRE_CAUSE=="Lightning" & bclcs_level_1 != 'U', ]
data.lightning.size<-merge(data.lightning.size, pixel.frt, by = "pixelid")
data.lightning.size<-data.lightning.size[!is.na(frt),]

data.person.size<- ignit_unknown_climate[FIRE_CAUSE=="Person" & bclcs_level_1 != 'U', ]
data.person.size<-merge(data.person.size, pixel.frt, by = "pixelid")
data.person.size<-data.person.size[!is.na(frt),]

#Add wetland
#data.lightning.size<-merge(data.lightning.size, pixel.wet, by = "pixelid")
#Add simple fuel typing
pixel.simple_fueltype<-data.table(read.csv( "C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/fuel_type_10k_2009to2023.csv"))
data.lightning.size<-merge(data.lightning.size, pixel.simple_fueltype, by = c("pixelid", "FIRE_YEAR"))
data.person.size<-merge(data.person.size, pixel.simple_fueltype, by = c("pixelid", "FIRE_YEAR"))

#Add roads
data.lightning.size<-merge(data.lightning.size, rds.table, by.x = c("pixelid", "FIRE_YEAR"), by.y = c("pixelid", "year"), all.x = TRUE)
data.lightning.size[is.na(road), road:=0]
data.person.size<-merge(data.person.size, rds.table, by.x = c("pixelid", "FIRE_YEAR"), by.y = c("pixelid", "year"), all.x = TRUE)
data.person.size[is.na(road), road:=0]

XYs<-xyFromCell(prov.rast, data.lightning.size$pixelid)
data.lightning.size$x<-XYs[,1]/1000 #make units of kilometers
data.lightning.size$y<-XYs[,2]/1000
saveRDS(data.lightning.size, "data_lightning_size_10k.rds")

XYs<-xyFromCell(prov.rast, data.person.size$pixelid)
data.person.size$x<-XYs[,1]/1000 #make units of kilometers
data.person.size$y<-XYs[,2]/1000
saveRDS(data.person.size, "data_person_size_10k.rds")

#FIRE OCCURENCE
data.lightning<-lightning.count
data.lightning<-data.lightning[is.na(count), count :=0]

data.person<-person.count
data.person<-data.person[is.na(count), count :=0]

data.lightning<-merge(data.lightning, climateData, by.x =c("pixelid", "FIRE_YEAR"),  by.y=c("pixelid","year"), all.y = TRUE)
data.lightning<-merge(data.lightning, pixel.frt, by="pixelid")
data.lightning<-data.lightning[!is.na(frt),]
#data.lightning<-merge(data.lightning, pixel.wet, by = "pixelid")
data.lightning<-merge(data.lightning, pixel.simple_fueltype, by = c("pixelid", "FIRE_YEAR"), all.y =TRUE)

data.person<-merge(data.person, climateData, by.x =c("pixelid", "FIRE_YEAR"),  by.y=c("pixelid","year"), all.y = TRUE)
data.person<-merge(data.person, pixel.frt, by="pixelid")
data.person<-data.person[!is.na(frt),]
#data.lightning<-merge(data.lightning, pixel.wet, by = "pixelid")
data.person<-merge(data.person, pixel.simple_fueltype, by = c("pixelid", "FIRE_YEAR"), all.y =TRUE)

#Add roads
data.lightning<-merge(data.lightning, rds.table, by.x = c("pixelid", "FIRE_YEAR"), by.y = c("pixelid", "year"), all.x = TRUE)
data.lightning[is.na(road), road:=0]
data.person<-merge(data.person, rds.table, by.x = c("pixelid", "FIRE_YEAR"), by.y = c("pixelid", "year"), all.x = TRUE)
data.person[is.na(road), road:=0]

XYs<-xyFromCell(prov.rast, data.lightning$pixelid)
data.lightning$x<-XYs[,1]/1000 #make units of kilometers
data.lightning$y<-XYs[,2]/1000

XYs<-xyFromCell(prov.rast, data.person$pixelid)
data.person$x<-XYs[,1]/1000 #make units of kilometers
data.person$y<-XYs[,2]/1000

data.lightning<-data.lightning[!is.na(CMI),] # remove the banner voxels
data.lightning<-data.lightning[is.na(count), count:=0]
saveRDS(data.lightning, "data_lightning_occurence_10k.rds")

data.person<-data.person[!is.na(CMI),] # remove the banner voxels
data.person<-data.person[is.na(count), count:=0]
saveRDS(data.person, "data_person_occurence_10k.rds")
```

