---
title: "forecast_fires"
author: "Kyle Lochhead"
date: '2023-11-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sdmTMB)
library(raster)
library(terra)
```

## Fire occurrence model
The fire occurrence model uses a grid at 10km by 10 km to form voxels which contain the number of fires that occurred within a given year. Also, the various covariates that occur in the given year are calculated for the voxel. A generalized linear model with a negative binomial distribution was used to predict fire counts. An offset was use to account for fuel aviability in the given year. A spatialy varying parameter was included to account for spatial autocorrelation. The needed variables are:

flammability (hectares of flammable fuel within the voxel- this is the sum of fuel types other than N or W; used as an offset)
coast (indicator varaible 0 or 1 for fire regime type 15)
lconif (natural logarithm of the hectares of conifer fuel types)
CMI (Climate Moisture Index or the difference between precipitation and potential evaporation)
dCMI3yr (the difference between CMI and the average 3 year prior CMI)

**Note: The flammability is a "structural" predictor. Its coefficient is not estimated by the model but is assumed to have the value 1; thus, the values of the offset are simply added to the linear predictor. The `predict()` function doesn't account for the offset. Therefore, we have to add the log(flammability) since: 

count = exp(intercept + 1*log(flam))
count = exp(intercept)*exp(log(flam))
count/flam = exp(intercept)

For a complete description on the model fitting process refer to fire_occurrence.rmd

## Data objects
The fire occurrence model is the outcome of a sdmTMB object which contains the form, data, spde, etc. This object was saved into an .rds object and will be imported during the simulation.

```{r data_objects, echo=FALSE}
restest = c(10000, 10000)
prov.ras <- raster::raster ( # standardized provincial raster with no data in it
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = restest,
  vals = 0)

m8<-readRDS("C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/m8.rds")

#get the random spatial effect
preds.all<-predict(m8_iid)
spat.int<-data.table(preds.all)[, c("pixelid", "est_rf")]

est_rf <- prov.ras
spat.int<-unique(spat.int)
est_rf[spat.int$pixelid]<-spat.int$est_rf
writeRaster(est_rf, "m8_iid_est_rf.tif",overwrite=TRUE)

```

## Dynamic variables in the forecast
Get the information/covariates to parameterize the model. In this example using the information from 2012
```{r}
dynamic_vars<-preds.all[FIRE_YEAR == 2015, c("pixelid", "con", "young", "dec", "CMI_MIN", "dCMI3yr", "PPT_sm", "TEMP_MAX", "flammable", "frt", "avgCMIProv")]
ras.flam<-prov.ras
ras.flam[dynamic_vars$pixelid]<-dynamic_vars$flammable
ras.frt<-prov.ras
ras.frt[dynamic_vars$pixelid]<-dynamic_vars$frt
ras.pixelid<-prov.ras
ras.pixelid[dynamic_vars$pixelid]<-dynamic_vars$pixelid
ras.con<-prov.ras
ras.con[dynamic_vars$pixelid]<-dynamic_vars$con
ras.dec<-prov.ras
ras.dec[dynamic_vars$pixelid]<-dynamic_vars$dec
ras.cmi_min<-prov.ras
ras.cmi_min[dynamic_vars$pixelid]<-dynamic_vars$CMI_MIN
ras.avgCMIProv<-prov.ras
ras.avgCMIProv[dynamic_vars$avgCMIProv]<-dynamic_vars$avgCMIProv


fire.num <- data.table(pixelid = ras.pixelid[], flammable = ras.flam[], frt = ras.frt[], con = ras.con[], dec = ras.dec[],CMI_MIN = ras.cmi_min[], dCMI3yr = ras.dcmi3yr[], avgCMIProv = ras.avgCMIProv[], est_rf = est_rf[] )
```

### Predict the negative binomial mu
```{r}
frt.coef<-data.table(frt = c(5,7,9,10,11,12,13,14,15), frt_coef = c(-0.739 , -1.87, -2.00,  -1.97,  -1.37,  -1.48, -1.76,  -1.29,  -3.17))
fire.num<-merge(fire.num, frt.coef, by = "frt")

fire.num<-fire.num[ ,pred_mu:= exp(-16.6-0.104*CMI_MIN -0.203*dCMI3yr + 0.279*avgCMIProv + 0.480*log(con + 1) -0.0561*log(dec + 1) + frt_coef + est_rf + log(flammable))]
fire.num<-fire.num[!is.na(pred_mu),]
```

### Take random draws as an inhomogenous poisson process
```{r}
set.seed(sample(1:1000,1))
fire.num$sim_fire<-unlist(lapply (fire.num$pred_mu, function (x) { rnbinom(n = 1, size = 0.56, mu =x ) })) # note that the rnbinom follows same parameterization as rbinom2 in sdmTMB. Also, the dispersion parameter is fixed at 0.45 as per the model assumptions. This could change if we use another type of approach via distribution regression or other.

sum(fire.num$sim_fire, na.rm=T)
fire.locations<-prov.ras
fire.locations[]<-0
fire.loc<-fire.num[sim_fire > 0 & pixelid > 0, ]
fire.locations[fire.loc$pixelid]<-fire.loc$sim_fire
plot(fire.locations)
#writeRaster(fire.locations, "rep2_fire_locations.tif")
```

### Sample down at the hectare scale
Use the logistic ignition model to set the weights of each individual 100 by 100 m pixel. These available pixels are then sampled for fire starts in the fire spreading process

#### Example:
```{r}
vox.pix<-data.table(pixel=seq(1,10,1), prob= runif(10))
vox.pix[, wt:=sum(prob)][, freq_exp:= prob/wt]
vox.ex<-table(sample(vox.pix$pixel,10000,prob=vox.pix$prob, replace = T))
```

