---
title: "fire_count_model"
output: html_document
date: '2023-08-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(bcdata)

year_vri <- 2022
geom_column <- 'shape'
wet<-c("mc", "mcp", "mh", "mk", "mkp", "mks", "mm", "mmp", "mmw", "ms", "mv", "mvp", "mw", "mwp", "mww", "vc", "vcp", "vcw", "vh", "vk", "vks", "vm", "wc", "wcp", "wcw", "wh", "whp", "wk", "wm", "wmp", "wmu", "ws", "wv", "wvp", "ww")
conifer<-c("C","CW","Y","YC","F","FD","FDC","FDI","B","BB","BA","BG","BL","H","HM","HW","HXM","J","JR","JS","P","PJ","PF","PL","PR","PLI","PXJ","PY","PLC","PW","PA","S","SB","SE","SS","SW","SX","SXW","SXL","SXS","T","TW","X", "XC","XH", "ZC")
deciduous<-c("L", "LA", "LT", "LW", "D", "DR", "U", "UP", "A", "AC", "ACB", "ACT", "AX", "AT", "R", "RA", "E", "EA", "EXP", "EP", "EW", "K", "KC", "V", "VB", "VV", "VP", "G", "M", "MB", "MV", "Q", "QG", "W", "WB", "WP", "WA", "WD", "WS", "WT", "XH", "ZH")
```

### Pessaki Fuel Type Algorithm
#### Non-vegetated fuel types
```{r, non_veg}
non_veg_logged<-getTableQuery(glue::glue("select feature_id, (case 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) As integer)  <= 6 AND coast_interior_cd = 'C' then 'S-3' 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) AS integer) <= 6 AND coast_interior_cd = 'I' then 'S-1' 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) AS integer)  > 6 AND {year_vri} - CAST(EXTRACT('Year' FROM harvest_date) as integer) < 25 AND bec_zone_code in('CWH', 'MH', 'ICH') then 'D-1/2' 
when CAST(EXTRACT('Year' FROM projected_date)- EXTRACT('Year' FROM harvest_date) as integer)  > 6 AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) < 25 AND bec_zone_code not in('CWH', 'MH', 'ICH') then 'O-1a/b' 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code in ('CMA', 'IMA') then 'N' 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code in ('BAFA','MH') then 'D-1/2' 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code = 'CWH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'M-1/2' 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code = 'CWH' and bec_subzone in ('{glue::glue_collapse(wet,  sep ='\\',\\'')}') then 'C-5'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code = 'BWBS' then 'C-2'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code = 'SWB' then 'M-1/2'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code = 'SBS' then 'C-3'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND (bec_zone_code in ('SBPS', 'MS', 'ESSF') OR (bec_zone_code in('IDF', 'CDF') AND bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'C-7'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code = 'IDF' AND bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-3'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code in ('CDF', 'ICH') AND bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-5'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code = 'ICH' AND bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-3'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 25 AND bec_zone_code in ('PP', 'BG') then 'O-1a/b'
end) as fuel_type from vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'N' AND harvest_date is not NULL;"))

non_veg_non_logged<- getTableQuery(glue::glue("select feature_id, (
case when earliest_nonlogging_dist_type in ('B','BE','BG','BW','BR','NB') and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer)  <= 3 then 'N'
when earliest_nonlogging_dist_type in ('B','BE','BG','BW','BR','NB') and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) > 3 and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) <= 6 then 'D-1/2'
when earliest_nonlogging_dist_type in ('B','BE','BG','BW','BR','NB') and CAST( EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) > 6 and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) <= 10 then 'O-1a/b'
when bclcs_level_2 = 'L' or bclcs_level_2 is null and bclcs_level_3 = 'A' then 'N'
when bclcs_level_2 = 'L' or bclcs_level_2 is null and species_cd_1 is not null and bec_zone_code in('CWH', 'MH', 'ICH') then 'D-1/2'
when bclcs_level_2 = 'L' or bclcs_level_2 is null and species_cd_1 is not null then 'O-1a/b'
when bclcs_level_2 = 'L' or bclcs_level_2 is null and species_cd_1 is null then 'N'
when bclcs_level_2 = 'W' then 'W'
when earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') then 'N'
end) as fuel_type from vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'N' AND harvest_date is NULL;"))

non_veg<-data.table(rbind(non_veg_logged, non_veg_non_logged))

```

#### Vegetated fuel types
Instead of adding percent conifer to the VRI -- doing this in data.table 
##### Forested and Recently Burned
```{r, recent_burned}
veg_recent_burned <-data.table(getTableQuery(glue::glue("Select feature_id, species_cd_1, species_cd_2, species_cd_3, species_cd_4, species_cd_5, species_pct_1, species_pct_2, species_pct_3, species_pct_3, species_pct_4, species_pct_5, CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) as tsf, crown_closure FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND earliest_nonlogging_dist_type in ('B','BE','BG','BW','BR','NB');")))
veg_recent_burned[tsf< 0, tsf:=0][species_cd_1 %in% conifer, c1:= species_pct_1][species_cd_2 %in% conifer, c2:= species_pct_2][species_cd_3 %in% conifer, c3:= species_pct_3][species_cd_4 %in% conifer, c4:= species_pct_4][species_cd_5 %in% conifer, c5:= species_pct_5][, con_pct:=sum(c1,c2,c3,c4,c5, na.rm =T), by= seq_len(nrow(veg_recent_burned))]
#get rid of the 5 columns created for conifer percentage
veg_recent_burned<-veg_recent_burned[, `:=`(c1 = NULL,c2= NULL,c3= NULL,c4= NULL,c5= NULL)]

veg_recent_burned[con_pct >= 60 & crown_closure > 40 & tsf <=3, fuel_type := 'N']
veg_recent_burned[con_pct >= 60 & crown_closure > 40 & tsf > 3 & tsf <=6, fuel_type := 'D-1/2']
veg_recent_burned[con_pct >= 60 & crown_closure > 40 & tsf > 6 & tsf <=10, fuel_type := 'C-5']
veg_recent_burned[con_pct >= 60 & crown_closure <= 40 & tsf <=1, fuel_type := 'N']
veg_recent_burned[con_pct >= 60 & crown_closure <= 40 & tsf > 1 & tsf <=6, fuel_type := 'D-1/2']
veg_recent_burned[con_pct >= 60 & crown_closure <= 40 & tsf > 6 & tsf <=10, fuel_type := 'O-1a/b']
veg_recent_burned[con_pct < 60 & tsf < 1, fuel_type := 'N']
veg_recent_burned[con_pct < 60 & tsf > 1 & tsf <= 10, fuel_type := 'D-1/2']

veg_recent_burn<-veg_recent_burned[,c("feature_id", "fuel_type")]
```

##### Forested and Single Species
###### Lodgepole and Jack Pine
```{r, lodgepole_pine}
veg_con_pure_lodgepole_jack <-data.table(getTableQuery(glue::glue("Select feature_id, (case 
     when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  <= 7 then 'S-1'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 = 'SP' AND (bec_zone_code in('CWH', 'CDF', 'MH') OR (bec_zone_code = 'ICH' AND bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') )) then 'D-1/2'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 = 'SP' AND (bec_zone_code not in ('CWH', 'CDF', 'MH') OR (bec_zone_code not in ('ICH') AND bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') )) then 'C-7'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and COALESCE(proj_height_1,0)  < 4  then 'O-1a/b'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 4 and proj_height_1 < 12 and COALESCE(vri_live_stems_per_ha, 0) + COALESCE(vri_dead_stems_per_ha,0) > 8000  then 'C-4'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 4 and proj_height_1 < 12 and COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) < 8000 or (vri_live_stems_per_ha is null and vri_dead_stems_per_ha is null)  then 'C-3'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and crown_closure < 40 and bec_zone_code in ('BG', 'PP', 'IDF', 'MS')  then 'C-7'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and crown_closure < 40 and bec_zone_code in ('CWH', 'MH', 'ICH')  then 'C-5'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and crown_closure < 40 and bec_zone_code not in ('BG', 'PP', 'IDF', 'MS', 'CWH', 'MH', 'ICH')  then 'C-3'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and (crown_closure >= 40 or crown_closure is null) and earliest_nonlogging_dist_type = 'IBM' AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) <= 5 AND stand_percentage_dead > 50 then 'M-3'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and (crown_closure >= 40 or crown_closure is null) and earliest_nonlogging_dist_type = 'IBM' AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) <= 5 AND stand_percentage_dead < 50 AND stand_percentage_dead >= 25 then 'C-2'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and (crown_closure >= 40 or crown_closure is null) and earliest_nonlogging_dist_type = 'IBM' AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) <= 5 AND (stand_percentage_dead < 25 or stand_percentage_dead is null) then 'C-3'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and (crown_closure >= 40 or crown_closure is null) and earliest_nonlogging_dist_type = 'IBM' AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) > 5 AND stand_percentage_dead > 50 then 'C-2'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and (crown_closure >= 40 or crown_closure is null) and earliest_nonlogging_dist_type = 'IBM' AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) > 5 AND (stand_percentage_dead < 50 or stand_percentage_dead is null) then 'C-3'
     when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  >= 7 or harvest_date is null) and bclcs_level_5 in ('DE', 'OP') and proj_height_1 >= 12 and (crown_closure >= 40 or crown_closure is null) and (earliest_nonlogging_dist_type not in ('IBM') or earliest_nonlogging_dist_type is null)  then 'C-3'
     end) as fuel_type FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 in ('PL', 'PLI', 'PLC', 'PJ', 'P', 'PXJ', 'PLL') AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```

###### Ponderosa Pine
```{r, ponderosa_pine}
veg_con_pure_ponderosa <-data.table(getTableQuery(glue::glue("Select feature_id, (case 
when bclcs_level_5 in ('DE', 'OP') AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  <= 10 then 'S-1'                                                           when bclcs_level_5 in ('DE', 'OP') AND (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 10 OR harvest_date is null) and COALESCE(proj_height_1,0)  < 4 then 'O-1a/b'
when bclcs_level_5 in ('DE', 'OP') AND (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 10 OR harvest_date is null) and proj_height_1 >= 4 and proj_height_1 <= 12 and  COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) >= 8000  then 'C-4'
when bclcs_level_5 in ('DE', 'OP') AND (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 10 OR harvest_date is null) and proj_height_1 >= 4 and proj_height_1 <= 12 and  COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) >= 3000  and  COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) < 8000  then 'C-3' 
when bclcs_level_5 in ('DE', 'OP') AND (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 10 OR harvest_date is null) and proj_height_1 >= 4 and proj_height_1 <= 12 and  (COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) < 3000  
OR (vri_live_stems_per_ha is null and vri_dead_stems_per_ha is null))  then 'C-7'
when bclcs_level_5 = 'DE' AND (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 10 OR harvest_date is null) and proj_height_1 > 12 and proj_height_1 <=17 then 'C-3'
when bclcs_level_5 = 'OP' AND (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 10 OR harvest_date is null) and proj_height_1 > 12 and proj_height_1 <=17 then 'C-7'
when bclcs_level_5 in ('DE', 'OP') AND (EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date)  > 10 OR harvest_date is null) and proj_height_1 > 17 then 'C-7'
when bclcs_level_5 = 'SP' AND stand_percentage_dead >= 40 then 'O-1a/b'
when bclcs_level_5 = 'SP' AND COALESCE(stand_percentage_dead,0) < 40 and EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date)  <= 10 then 'S-1'
when bclcs_level_5 = 'SP' AND COALESCE(stand_percentage_dead,0) < 40 and (EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date)  > 10 or harvest_date is null) then 'C-7'
end) as fuel_type  
FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 = 'PY' AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```

###### Other Pine
```{r, other_pine}
veg_con_pure_other_pine <-data.table(getTableQuery(glue::glue("Select feature_id, (case 
when bclcs_level_5 = 'DE' then 'C-3' 
when bclcs_level_5 in ('SP', 'OP') and COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) >= 900 then 'C-3' 
when bclcs_level_5 in ('SP', 'OP') and COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) >= 600 and COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) < 900 then 'C-7' 
when bclcs_level_5 in ('SP', 'OP') and COALESCE(vri_live_stems_per_ha,0) + COALESCE(vri_dead_stems_per_ha,0) < 600  then 'C-5' 
end) as fuel_type  
FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 in ('PA', 'PF', 'PW') AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```

###### Douglas-fir
```{r, douglas_fir}
veg_con_pure_fd <-data.table(getTableQuery(glue::glue("Select feature_id, (case 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  <= 6 and (bec_zone_code in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'S-3' 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  <= 6 and (bec_zone_code not in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'S-1' 
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and COALESCE(proj_height_1,0) < 4  and (bec_zone_code  in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone  in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'D-1/2' 
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and COALESCE(proj_height_1,0)  < 4  and (bec_zone_code not in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'O-1a/b' 
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and proj_height_1 >= 4 and proj_height_1 < 12 and crown_closure >= 55 and (bec_zone_code in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'C-3' 
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and proj_height_1 >= 4 and proj_height_1 < 12 and crown_closure >= 55 and (bec_zone_code not in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) and stand_percentage_dead > 34 then 'C-4'
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and proj_height_1 >= 4 and proj_height_1 < 12 and crown_closure >= 55 and (bec_zone_code not in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) and COALESCE(stand_percentage_dead, 0) <= 34 then 'C-3'
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and proj_height_1 >= 12 and crown_closure >= 55 and (bec_zone_code  in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone  in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')))  then 'C-5'
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and  proj_height_1 >= 12 and crown_closure >= 55 and (bec_zone_code not in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone  not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')))  then 'C-7'
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and proj_height_1 >= 4 and (crown_closure >=26 and crown_closure < 55 or crown_closure is null) and (bec_zone_code in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')))  then 'C-5'
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and proj_height_1 >= 4 and (crown_closure >=26 and crown_closure < 55 or crown_closure is null) and (bec_zone_code not in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')))  then 'C-7'
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and proj_height_1 >= 4 and crown_closure < 26 and (bec_zone_code in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')))  then 'D-1/2'
when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and proj_height_1 >= 4 and crown_closure < 26 and (bec_zone_code not in ('CWH', 'MH', 'CDF') OR (bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')))  then 'O-1a/b'
end) as fuel_type  
FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 in ('F','FD','FDC','FDI') AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```

###### Spruce
```{r, spruce}
veg_con_pure_sx <-data.table(getTableQuery(glue::glue("Select feature_id, (case
when species_cd_1 = 'SE' and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  <= 10 then 'S-2'
when species_cd_1 = 'SE' and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 10 or harvest_date is null) and bclcs_level_5 = 'SP' then 'D-1/2'
when species_cd_1 = 'SE' and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 10 or harvest_date is null) and bclcs_level_5 = 'DE' then 'C-2'
when species_cd_1 = 'SE' and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 10 or harvest_date is null) and bclcs_level_5 = 'OP' then 'C-3'
when species_cd_1 = 'SS' and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <= 6 then 'S-3'
when species_cd_1 = 'SS' and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'SP' then 'D-1/2'
when species_cd_1 = 'SS' and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 6 or harvest_date is null) and bclcs_level_5 in('DE', 'OP') then 'C-5'
when species_cd_1  in ('SB', 'SW', 'SXW') and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <= 10 then 'S-3'
when species_cd_1  in ('SB', 'SW', 'SXW') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 10 or harvest_date is null)  and bclcs_level_5 in ('DE', 'OP') then 'C-2'
when species_cd_1  in ('SB', 'SW', 'SXW') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 10 or harvest_date is null)  and bclcs_level_5 = 'SP' and bec_zone_code in ('BWBS', 'SWB') then 'C-1'
when species_cd_1  in ('SB', 'SW', 'SXW') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 10 or harvest_date is null)  and bclcs_level_5 = 'SP' and bec_zone_code not in ('BWBS', 'SWB') then 'M-1/2'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  <= 7)  then 'S-2'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 7 or harvest_date is null) and bec_zone_code in ('BWBS', 'SWB') and bclcs_level_5 in ('DE', 'OP')  then 'C-2'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer)  > 7 or harvest_date is null) and bec_zone_code in ('BWBS', 'SWB') and bclcs_level_5 = 'SP'  then 'C-1'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 7 or harvest_date is null) and bec_zone_code not in ('BWBS', 'SWB') and bclcs_level_5  = 'SP' then 'C-7'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 7 or harvest_date is null) and bec_zone_code in ('CWH', 'CDF') and bclcs_level_5  in ('DE', 'OP')  then 'C-5'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 7 or harvest_date is null) and bec_zone_code not in ('BWBS', 'SWB','CWH', 'CDF') and bclcs_level_5 in ('DE', 'OP') and COALESCE (proj_height_1, 0 ) <= 4 then 'O-1a/b'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 7 or harvest_date is null) and bec_zone_code not in ('BWBS', 'SWB','CWH', 'CDF') and bclcs_level_5 ='DE' and COALESCE (proj_height_1, 0 ) > 4 then 'C-2'
when species_cd_1  in ('S', 'SX', 'SXL', 'SXS') and (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 7 or harvest_date is null) and bec_zone_code not in ('BWBS', 'SWB','CWH', 'CDF') and bclcs_level_5 ='OP' and COALESCE (proj_height_1, 0 ) > 4 then 'C-3'
end) as fuel_type  
FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 in ('S','SB','SE','SS','SW','SX','SXW','SXL','SXS') AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```

###### Hemlock
```{r, hemlock}
veg_con_pure_hw <-data.table(getTableQuery(glue::glue("Select feature_id, (case
   when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <= 6 then 'S-3'             
   when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'DE' and COALESCE(proj_height_1, 0) <= 4 then 'D-1/2' 
   when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'DE' and COALESCE(proj_height_1, 0) > 4 and proj_height_1 <= 15 then 'C-3'
   when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'DE' and proj_height_1 >  15 and COALESCE(proj_age_1,0) <= 60 then 'C-3' 
   when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'DE' and proj_height_1 >  15 and proj_age_1 > 60 and proj_age_1 <= 99 then 'M-1/2' 
   when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'DE' and proj_height_1 >  15 and proj_age_1 > 99 then 'C-5' 
   when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'OP' then 'C-5' 
   when (CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 6 or harvest_date is null) and bclcs_level_5 = 'SP' then 'D-1/2'
   end)  as fuel_type 
FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 in ('H','HM','HW','HXM', 'C','CW','Y','YC') AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```

###### True Fir
```{r, true_fir}
veg_con_pure_fir <-data.table(getTableQuery(glue::glue("Select feature_id, (case
when species_cd_1 = 'BG' then 'C-7'
when species_cd_1 = 'BA' then 'M-1/2'
when species_cd_1 in ('B','BB','BL') and bclcs_level_5 = 'SP' then 'C-7'
when species_cd_1 in ('B','BB','BL') and (bclcs_level_5 not in ('SP') or bclcs_level_5 is null) then 'C-3'
when species_cd_1 in ('T','TW') then 'C-5'
when species_cd_1 in ('J','JR','JS') then 'O-1a/b'
   end)  as fuel_type 
FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 in ('BG', 'BA', 'B','BB','BL', 'T','TW','J','JR','JS') AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```


###### Deciduous
```{r, deciduous}
veg_dec_pure <-data.table(getTableQuery(glue::glue("Select feature_id, 'D-1/2' as fuel_type 
FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 >= 80 AND species_cd_1 in ('{glue::glue_collapse(deciduous,  sep = '\\',\\'')}') AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
```

##### Forested and Mixed species
```{r, mixed}
veg_mixed <-data.table(getTableQuery(glue::glue("Select feature_id, coast_interior_cd, bclcs_level_5, bec_zone_code, bec_subzone, proj_height_1, COALESCE(vri_live_stems_per_ha,0) as vri_live_stems_per_ha, COALESCE(vri_dead_stems_per_ha,0) as vri_dead_stems_per_ha, COALESCE (stand_percentage_dead, 0) as stand_percentage_dead, species_cd_1, species_cd_2, species_cd_3, species_cd_4, species_cd_5,species_cd_6, species_pct_1, species_pct_2, species_pct_3, species_pct_3, species_pct_4, species_pct_5,species_pct_6, CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) as ys_log, CAST(EXTRACT('Year' FROM projected_date)- EXTRACT('Year' FROM earliest_nonlogging_dist_date) as integer) as ys_dist, earliest_nonlogging_dist_type, proj_age_1, crown_closure FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'T' AND species_pct_1 < 80 AND (earliest_nonlogging_dist_type not in ('B','BE','BG','BW','BR','NB') OR earliest_nonlogging_dist_type is null);")))
veg_mixed[species_cd_1 %in% conifer, c1:= species_pct_1][species_cd_2 %in% conifer, c2:= species_pct_2][species_cd_3 %in% conifer, c3:= species_pct_3][species_cd_4 %in% conifer, c4:= species_pct_4][species_cd_5 %in% conifer, c5:= species_pct_5][, con_pct:=sum(c1,c2,c3,c4,c5, na.rm =T), by= seq_len(nrow(veg_mixed))]
#Get the dominant conifer species
veg_mixed[, dcsp := ifelse(species_cd_1 %in% conifer, species_cd_1, 
                                   ifelse(species_cd_2 %in% conifer, species_cd_2,
                                          ifelse(species_cd_3 %in% conifer, species_cd_3,
                                                 ifelse(species_cd_4 %in% conifer, species_cd_4,
                                                        ifelse(species_cd_5 %in% conifer, species_cd_5,
                                                               ifelse(species_cd_6 %in% conifer, species_cd_6, NA))))))]
#get rid of the 5 columns created for conifer percentage
veg_mixed<-veg_mixed[, `:=`(c1 = NULL,c2= NULL,c3= NULL,c4= NULL,c5= NULL)]

# Conifer < 20%
veg_mixed[con_pct <= 20, fuel_type := 'D-1/2' ]

# Conifer 20 to 40%
veg_mixed[con_pct > 20 & con_pct <= 40 & ys_log <= 6, fuel_type := 'S-1' ]
veg_mixed[con_pct > 20 & con_pct <= 40 & (ys_log > 6 | is.na(ys_log)), fuel_type := 'M-1/2' ]

# Conifer 40 to 65%
veg_mixed[con_pct > 40 & con_pct <= 65 & ys_log <= 6, fuel_type := 'S-1' ]
veg_mixed[con_pct > 40 & con_pct <= 65 & (ys_log > 6 | is.na(ys_log)) & !(dcsp %in% c('T','TW', 'J','JR','JS')), fuel_type := 'M-1/2' ]
veg_mixed[con_pct > 40 & con_pct <= 65 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('T','TW'), fuel_type := 'C-5' ]
veg_mixed[con_pct > 40 & con_pct <= 65 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('J','JR','JS'), fuel_type := 'O-1a/b' ]

# Conifer 65 to 80%
veg_mixed[con_pct > 65 & con_pct <= 80 & ys_log <= 6, fuel_type := 'S-1' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('PLI', 'PL', 'PLC', 'PJ', 'P'), fuel_type := 'M-1/2' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp == 'PY', fuel_type := 'C-7' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('PA', 'PF', 'PW'), fuel_type := 'C-5' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('F', 'FDC', 'FDI', 'FD') & (bec_zone_code %in% c('CWH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)) , fuel_type := 'C-5' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('F', 'FDC', 'FDI', 'FD') & !(bec_zone_code %in% c('CWH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)) & bclcs_level_5 == 'DE', fuel_type := 'M-1/2' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('F', 'FDC', 'FDI', 'FD') & !(bec_zone_code %in% c('CWH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)) & !(bclcs_level_5 == 'DE'), fuel_type := 'C-7' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('SE', 'SB', 'SW') , fuel_type := 'M-1/2' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp == 'SS' , fuel_type := 'C-5' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('SX', 'S', 'SXL', 'SXS', 'SXW') & bec_zone_code %in% c('BWBS', 'SWB') , fuel_type := 'M-1/2' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('SX', 'S', 'SXL', 'SXS', 'SXW') & !(bec_zone_code %in% c('BWBS', 'SWB')) & bclcs_level_5 == 'SP' , fuel_type := 'M-1/2']
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('SX', 'S', 'SXL', 'SXS', 'SXW') & !(bec_zone_code %in% c('BWBS', 'SWB')) & bclcs_level_5 %in% c('OP', 'DE') & coast_interior_cd == 'I' , fuel_type := 'M-1/2']
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('SX', 'S', 'SXL', 'SXS', 'SXW') & !(bec_zone_code %in% c('BWBS', 'SWB')) & bclcs_level_5 %in% c('OP', 'DE') & coast_interior_cd == 'C' , fuel_type := 'C-5']
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('H','HM','HW', 'HXM','TW','T','CW','C','YC','Y') , fuel_type := 'C-5' ]
veg_mixed[con_pct > 65 & con_pct <= 80 & (ys_log > 6 | is.na(ys_log)) & dcsp %in% c('B','BA', 'BL', 'BB', 'BG', 'J', 'JR', 'JS') , fuel_type := 'C-7' ]

# Conifer 81 to 100%
####---PL/PJ
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & ys_log <= 7, fuel_type := 'S-1' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'SP' & (bec_zone_code %in% c('CWH', 'CDF', 'MH') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'D-1/2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'SP' & !(bec_zone_code %in% c('CWH', 'CDF', 'MH') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & (proj_height_1 < 4 | is.na(proj_height_1)), fuel_type := 'O-1a/b' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 <= 12 & vri_live_stems_per_ha + vri_dead_stems_per_ha >= 8000, fuel_type := 'C-4' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 <= 12 & (vri_live_stems_per_ha + vri_dead_stems_per_ha < 8000 | (vri_live_stems_per_ha == 0 & vri_dead_stems_per_ha == 0)), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & crown_closure < 40 & bec_zone_code %in% c('BG', 'PP','IDF', 'MS'), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & crown_closure < 40 & bec_zone_code %in% c('CWH', 'MH', 'ICH'), fuel_type := 'C-5' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & crown_closure < 40 & !(bec_zone_code %in% c('BG', 'PP','IDF', 'MS', 'CWH', 'MH', 'ICH')), fuel_type := 'C-3' ]

####---PL/PJ BEETLE
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist <=5 & bclcs_level_5 == 'DE' & stand_percentage_dead >= 50 & crown_closure >= 40, fuel_type := 'M-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist <=5 & bclcs_level_5 == 'DE' & stand_percentage_dead < 50 & crown_closure >= 40, fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist <=5 & !(bclcs_level_5 == 'DE') & stand_percentage_dead >= 50 & crown_closure >= 40, fuel_type := 'M-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist <=5 & !(bclcs_level_5 == 'DE') & stand_percentage_dead < 50 & stand_percentage_dead > 25 & crown_closure >= 40, fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist <=5 & !(bclcs_level_5 == 'DE') & stand_percentage_dead < 25 & crown_closure >= 40, fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist > 5 & bclcs_level_5 == 'DE' & stand_percentage_dead > 25 & crown_closure >= 40, fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist > 5 & bclcs_level_5 == 'DE' & stand_percentage_dead <= 25 & crown_closure >= 40, fuel_type := 'C-3' ]

veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist > 5 & !(bclcs_level_5 == 'DE') & stand_percentage_dead >= 50 & crown_closure >= 40, fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & earliest_nonlogging_dist_type == 'IBM' & ys_dist > 5 & !(bclcs_level_5 == 'DE') & stand_percentage_dead < 50 & crown_closure >= 40, fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW') & proj_height_1 > 12 & crown_closure >= 40, fuel_type := 'C-3' ]

veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & !(species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW')) & crown_closure < 40 & bec_zone_code %in% c('IDF', 'PP', 'BG', 'SBPS', 'MS'), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & !(species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW')) & crown_closure < 40 & bec_zone_code %in% c('CWH', 'CDF', 'ICH'), fuel_type := 'C-5' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & !(species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW')) & crown_closure < 40 & !(bec_zone_code %in% c('CWH', 'CDF', 'ICH', 'IDF', 'PP', 'BG', 'SBPS', 'MS')), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PLI', 'PL', 'PLC', 'PJ', 'P') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 %in% c('DE', 'OP') & proj_height_1 >= 4 & !(species_cd_2 %in% c('B','BA', 'BL', 'BB', 'BG', 'S', 'SE', 'SB', 'SW', 'SX', 'SS', 'SXL', 'SXS', 'SXW')) & (crown_closure >= 40 | is.na(crown_closure)) , fuel_type := 'C-3' ]

####---PY
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PY') & ys_log <= 7 , fuel_type := 'S-1' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PY') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 < 4 , fuel_type := 'O-1a/b' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PY') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 4 & bclcs_level_5 == 'DE', fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PY') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 4 & !(bclcs_level_5 == 'DE'), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PA', 'PF', 'PW') & bclcs_level_5 == 'DE' , fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PA', 'PF', 'PW') & !(bclcs_level_5 == 'DE') & vri_live_stems_per_ha + vri_dead_stems_per_ha >=900 , fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PA', 'PF', 'PW') & !(bclcs_level_5 == 'DE') & vri_live_stems_per_ha + vri_dead_stems_per_ha < 900 & vri_live_stems_per_ha + vri_dead_stems_per_ha > 600, fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('PA', 'PF', 'PW') & !(bclcs_level_5 == 'DE') & vri_live_stems_per_ha + vri_dead_stems_per_ha <= 600, fuel_type := 'C-5' ]

####---FD
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & ys_log <= 6 & (bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'S-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & ys_log <= 6 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'S-1' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 < 4 & (bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'D-1/2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 < 4 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'O-1a/b' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 4 & proj_height_1 < 12 & crown_closure > 55 & (bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 4 & proj_height_1 < 12 & crown_closure > 55 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)) & stand_percentage_dead > 34, fuel_type := 'C-4' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 4 & proj_height_1 < 12 & crown_closure > 55 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)) & stand_percentage_dead < 34 & species_cd_2 == 'PY', fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 4 & proj_height_1 < 12 & crown_closure > 55 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)) & stand_percentage_dead < 34 & !(species_cd_2 == 'PY'), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 12 & crown_closure > 55 & (bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'C-5' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & proj_height_1 >= 12 & crown_closure > 55 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & ((crown_closure < 55 & crown_closure > 26) | is.na(crown_closure)) & (bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'C-5' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & ((crown_closure < 55 & crown_closure > 26) | is.na(crown_closure)) & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & crown_closure <  26 & (bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'D-1/2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('F','FD','FDC','FDI') & (ys_log > 7 | is.na(ys_log)) & crown_closure <  26 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'O-1a/b' ]

####---S
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & ys_log <= 6 & (bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'S-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & ys_log <= 6 & !(bec_zone_code %in% c('CWH', 'MH', 'CDF') | (bec_zone_code == 'ICH' & bec_subzone %in% wet)), fuel_type := 'S-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SE' & bclcs_level_5 == 'SP', fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SE' & bclcs_level_5 == 'DE' & species_cd_2 %in% c('BL', 'B', 'PL', 'P', 'PLI'), fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SE' & bclcs_level_5 == 'OP' & species_cd_2 %in% c('BL', 'B', 'PL', 'P', 'PLI'), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SE' & bclcs_level_5 == 'DE' & species_cd_2 %in% c('HW', 'HM', 'CW', 'YC'), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SE' & bclcs_level_5 == 'OP' & species_cd_2 %in% c('HW', 'HM', 'CW', 'YC'), fuel_type := 'C-5' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SE' & bclcs_level_5 %in% c('OP', 'DE') & !(species_cd_2 %in% c('HW', 'HM', 'CW', 'YC', 'BL', 'B', 'PL', 'P', 'PLI')), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SS', fuel_type := 'C-5' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SB' & bclcs_level_5 %in% c('OP', 'DE'), fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SB' & bclcs_level_5 == 'SP' & bec_zone_code == 'BWBS', fuel_type := 'C-1' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S', 'SB','SE','SS','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & species_cd_1 == 'SB' & bclcs_level_5 == 'SP' & !(bec_zone_code == 'BWBS'), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'DE' & (bec_zone_code == 'BWBS'), fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'OP' & (bec_zone_code == 'BWBS'), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'SP' & (bec_zone_code == 'BWBS'), fuel_type := 'C-1' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'SP' & !(bec_zone_code == 'BWBS') & bec_zone_code %in% c('CWH', 'MH', 'CDF') & species_cd_2 %in% c('P', 'P','PJ','PF','PL','PR','PLI','PXJ','PY','PLC','PW','PA', 'BL', 'B'), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & !(bec_zone_code == 'BWBS') & bec_zone_code %in% c('CWH', 'MH', 'CDF') & species_cd_2 %in% c('P', 'P','PJ','PF','PL','PR','PLI','PXJ','PY','PLC','PW','PA', 'BL', 'B') & !(bclcs_level_5 == 'SP'), fuel_type := 'C-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'SP' & !(bec_zone_code == 'BWBS') & !(bec_zone_code %in% c('CWH', 'MH', 'CDF')), fuel_type := 'C-7' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'DE' & !(bec_zone_code == 'BWBS') & !(bec_zone_code %in% c('CWH', 'MH', 'CDF')), fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'OP' & !(bec_zone_code == 'BWBS') & !(bec_zone_code %in% c('CWH', 'MH', 'CDF')) & stand_percentage_dead > 34, fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'OP' & !(bec_zone_code == 'BWBS') & !(bec_zone_code %in% c('CWH', 'MH', 'CDF')) & (stand_percentage_dead <= 34 | is.na(stand_percentage_dead)) & species_cd_2 %in% c('P', 'PLI', 'PL'), fuel_type := 'C-2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('S','SW','SX','SXW','SXL','SXS') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'OP' & !(bec_zone_code == 'BWBS') & !(bec_zone_code %in% c('CWH', 'MH', 'CDF')) & (stand_percentage_dead <= 34 | is.na(stand_percentage_dead)) & !(species_cd_2 %in% c('P', 'PLI', 'PL')), fuel_type := 'C-3' ]

####---H, C, Y
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & ys_log <= 6 , fuel_type := 'S-3' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'DE' & proj_height_1 <= 4 , fuel_type := 'D-1/2' ]
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'DE' & proj_height_1 > 4 & proj_height_1 <= 15 , fuel_type := 'C-3']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'DE' & proj_height_1 > 15 & proj_age_1 <= 60, fuel_type := 'C-3']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'DE' & proj_height_1 > 15 & proj_age_1 > 60 & proj_age_1 <= 99, fuel_type := 'M-1/2']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'DE' & proj_height_1 > 15 & proj_age_1 >  99, fuel_type := 'C-5']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'OP', fuel_type := 'C-5']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('H','HW','HM','HXM','C','CW','Y','YC') & (ys_log > 7 | is.na(ys_log)) & bclcs_level_5 == 'SP', fuel_type := 'D-1/2']

####---BG
veg_mixed[con_pct > 80 & species_cd_1 == 'BG', fuel_type := 'C-7']
veg_mixed[con_pct > 80 & species_cd_1 == 'BA' & species_cd_2 %in% c('SE', 'SW', 'S'), fuel_type := 'C-3']
veg_mixed[con_pct > 80 & species_cd_1 == 'BA' & !(species_cd_2 %in% c('SE', 'SW', 'S')), fuel_type := 'M-1/2']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('BL', 'BB', 'B') & coast_interior_cd == 'C', fuel_type := 'M-1/2']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('BL', 'BB', 'B') & coast_interior_cd == 'I' & bclcs_level_5 == 'SP', fuel_type := 'C-7']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('BL', 'BB', 'B') & coast_interior_cd == 'I' & bclcs_level_5 == 'OP', fuel_type := 'C-3']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('BL', 'BB', 'B') & coast_interior_cd == 'I' & bclcs_level_5 == 'DE' & species_cd_2 %in% c('SE', 'SW', 'S'), fuel_type := 'C-2']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('BL', 'BB', 'B') & coast_interior_cd == 'I' & bclcs_level_5 == 'DE' & !(species_cd_2 %in% c('SE', 'SW', 'S')), fuel_type := 'C-3']

####---Left overs
veg_mixed[con_pct > 80 & species_cd_1 %in% c('T', 'TW') , fuel_type := 'C-5']
veg_mixed[con_pct > 80 & species_cd_1 %in% c('J', 'JR', 'JS') , fuel_type := 'C-7']

veg_mix<-veg_mixed[,c("feature_id", "fuel_type")]
```

##### Non-Forested 
###### Recently Burned
```{r, non_forest_burn}
non_forested_burned <-data.table(getTableQuery(glue::glue("Select feature_id, (case 
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) AS integer) < 2 then 'N'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) AS integer)  > 1 AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) AS integer) < 4 then 'D-1/2'
when CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) AS integer)  > 3 AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) AS integer)  < 11 then 'O-1a/b'
end) as fuel_type FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'N' AND earliest_nonlogging_dist_type in ('B', 'BE', 'BG', 'BW', 'BR', 'NB') AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM earliest_nonlogging_dist_date) AS integer) < 11; ")))
```

###### Harvested
```{r, non_forest_harvest}
non_forested_logged <-data.table(getTableQuery(glue::glue("Select feature_id, (case 
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=7 AND species_cd_1 in ('PL', 'PLI', 'PLC', 'PJ', 'P', 'PXJ', 'PLL', 'PY', 'PA', 'PF', 'PW') then 'S-1'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=7 AND species_cd_1 in ('S','SB','SE','SS','SW','SX','SXW','SXL','SXS', 'BG', 'BA', 'B','BB','BL') then 'S-2'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=7 AND species_cd_1 in ('H','HM','HW','HXM', 'C','CW','Y','YC') then 'S-3'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=7 AND species_cd_1 in ('F','FD','FDC','FDI') AND bec_zone_code in('CWH', 'ICH') then 'S-3'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=7 AND species_cd_1 in ('F','FD','FDC','FDI') AND bec_zone_code not in ('CWH', 'ICH') then 'S-1'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=7 AND species_cd_1 not in ('F','FD','FDC','FDI','H','HM','HW','HXM', 'C','CW','Y','YC','S','SB','SE','SS','SW','SX','SXW','SXL','SXS', 'BG', 'BA', 'B','BB','BL', 'PL', 'PLI', 'PLC', 'PJ', 'P', 'PXJ', 'PLL', 'PY', 'PA', 'PF', 'PW') then 'S-1'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 8 and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=24 AND (bec_zone_code in ('CWH', 'MH') OR (bec_zone_code = 'ICH' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'D-1/2'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 8 and CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <=24 AND (bec_zone_code not in ('CWH', 'MH') OR (bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}'))) then 'O-1a/b'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code in ('CMA', 'IMA') then 'N'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code in ('BAFA', 'MH') then 'D-1/2'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code in ('CWH', 'ICH', 'CDF') and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-5'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code = 'CWH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'M-1/2'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code = 'BWBS' then 'C-5'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code = 'SWB' then 'M-1/2'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code in ('SBS', 'MS', 'ESSF') then 'C-3'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code = 'SBPS' then 'C-7'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code in ('PP', 'BG') then 'O-1a/b'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code ='IDF' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-3'
when species_cd_1 is not null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) >= 25 AND bec_zone_code in ('IDF', 'CDF') and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-7'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <= 5 then 'S-1'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 5 AND  CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <= 24 and bec_zone_code in ('CWH', 'MH', 'ICH') then 'D-1/2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 5 AND  CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) <= 24 and bec_zone_code not in ('CWH', 'MH', 'ICH') then 'O-1a/b'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code in ('CMA', 'IMA') then 'N'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code in ('BAFA') then 'D-1/2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code in ('CWH') AND bec_subzone not in('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'M-1/2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code in ('CWH') AND bec_subzone in('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-5'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'BWBS' then 'C-2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'SWB' then 'M-1/2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'SBS' then 'C-3'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code in ('SBPS', 'MS', 'ESSF') then 'C-7'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'IDF' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-7'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'IDF' and bec_subzone  in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'M-1/2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code in ('PP', 'BG')  then 'O-1a/b'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'MH'  then 'D-1/2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'CDF' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-5'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'CDF' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-7'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'M-1/2'
when species_cd_1 is null AND CAST(EXTRACT('Year' FROM projected_date) - EXTRACT('Year' FROM harvest_date) as integer) > 24 and bec_zone_code = 'ICH' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-5'
end) as fuel_type FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'N' AND harvest_date is not null AND (earliest_nonlogging_dist_type not in ('B', 'BE', 'BG', 'BW', 'BR', 'NB') or earliest_nonlogging_dist_type is null); ")))
```

###### Non-harvested
```{r, non-harvested}
non_forested_non_logged <-data.table(getTableQuery(glue::glue("Select feature_id, (case
when species_cd_1 is not null and bec_zone_code in ('CMA', 'IMA') then 'N'
when species_cd_1 is not null and bec_zone_code in ('CWH', 'MH', 'ICH', 'BAFA') then 'D-1/2'
when species_cd_1 is not null and bec_zone_code not in ('CMA', 'IMA', 'CWH', 'MH', 'ICH', 'BAFA') then 'O-1a/b'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd in ('11','12','13') and bec_zone_code in ('CWH', 'MH', 'CH') then 'D-1/2'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd in ('11','12','13')  and bec_zone_code not in ('CWH', 'MH', 'CH') then 'O-1a/b'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd = '35' then 'W'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd = '42' then 'N'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd in ('60', '62', '63') then 'O-1a/b'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd is null and bec_zone_code in ('CMA', 'IMA') then 'N'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd is null and bec_zone_code in ('CWH', 'MH', 'ICH', 'BAFA') then 'D-1/2'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd is null and bec_zone_code not in ('CWH', 'MH', 'ICH', 'BAFA', 'CMA', 'IMA') then 'O-1a/b'
when species_cd_1 is null and inventory_standard_cd = 'F' and non_productive_cd not in ('11','12','13','35','42','60','62','63')  then 'N'
when species_cd_1 is null and inventory_standard_cd in ('V', 'I') and land_cover_class_cd_1 in ('LA', 'RI', 'RE', 'OC')   then 'W'
when species_cd_1 is null and inventory_standard_cd in ('V', 'I') and land_cover_class_cd_1 = 'HG'  then 'O-1a/b'
when species_cd_1 is null and inventory_standard_cd in ('V', 'I') and land_cover_class_cd_1 in ('BY', 'BM', 'BL') then 'D-1/2'
when species_cd_1 is null and inventory_standard_cd in ('V', 'I') and (land_cover_class_cd_1 in ('L','ST', 'HE', 'HF') or land_cover_class_cd_1 is null) and bec_zone_code in ('CMA', 'IMA') then 'N'
when species_cd_1 is null and inventory_standard_cd in ('V', 'I') and (land_cover_class_cd_1 in ('L','ST', 'HE', 'HF') or land_cover_class_cd_1 is null) and bec_zone_code in ('CWH', 'MH', 'ICH') then 'D-1/2'
when species_cd_1 is null and inventory_standard_cd in ('V', 'I') and (land_cover_class_cd_1 in ('L','ST', 'HE', 'HF') or land_cover_class_cd_1 is null) and bec_zone_code not in ('CMA', 'IMA', 'CWH', 'MH', 'ICH') then 'O-1a/b'
when species_cd_1 is null and inventory_standard_cd in ('V', 'I') and (land_cover_class_cd_1 not in ('L','ST', 'HE', 'HF') or land_cover_class_cd_1 is not null) then 'N'
end) as fuel_type FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'V' AND bclcs_level_2 = 'N' AND harvest_date is null AND (earliest_nonlogging_dist_type not in ('B', 'BE', 'BG', 'BW', 'BR', 'NB') or earliest_nonlogging_dist_type is null); ")))
```

#### Unknowns
```{r, unknowns}
if(FALSE){
unknown <-data.table(getTableQuery(glue::glue("Select feature_id, (case
when bclcs_level_4 = '101' then 'C-1'
end) as fuel_type FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_4 is null and bclcs_level_4 in ('101', '102', '103', '104', '105', '106', '107', '108', '109', '110', 
															   '111', '112', '113', '114', '115', '116', '117', '118', '119', '120', '121', '122', '123'); ")))
}

unknown <-data.table(getTableQuery(glue::glue("Select feature_id, (case
when non_veg_cover_type_1 = 'OC' then 'W'
when bec_zone_code in ('CMA', 'IMA') then 'N'
when bec_zone_code = 'BAFA' then 'D-1/2'
when bec_zone_code = 'CWH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'M-1/2'
when bec_zone_code = 'CWH' and bec_subzone  in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-5'
when bec_zone_code = 'BWBS' then 'C-2'
when bec_zone_code = 'SWB' then 'M-1/2'
when bec_zone_code in ('SBS', 'MS', 'ESSF') then 'C-3'
when bec_zone_code = 'SBPS' then 'C-2'
when bec_zone_code = 'PP' then 'C-7'
when bec_zone_code = 'IDF' and bec_subzone  in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'M-1/2'
when bec_zone_code = 'IDF' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}') then 'C-7'
when bec_zone_code = 'BG' then 'O-1a/b'
when bec_zone_code = 'MH' then 'C-5'
when bec_zone_code = 'CDF' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')  then 'C-7'
when bec_zone_code = 'CDF' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')  then 'C-5'
when bec_zone_code = 'ICH' and bec_subzone not in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')  then 'M-1/2'
when bec_zone_code = 'ICH' and bec_subzone in ('{glue::glue_collapse(wet,  sep = '\\',\\'')}')  then 'C-5'
end) as fuel_type FROM vri.veg_comp_lyr_r1_poly{year_vri} where bclcs_level_1 = 'U'")))
```

## Compilation
```{r, compile}
non_veg[, source:='non_veg']
veg_recent_burn[, source:='veg_recent_burn']
veg_con_pure_lodgepole_jack[, source:='veg_con_pure_lodgepole_jack']
veg_con_pure_ponderosa[, source:='veg_con_pure_ponderosa']
veg_con_pure_other_pine[, source:='veg_con_pure_other_pine']
veg_con_pure_fd[, source:='veg_con_pure_fd']
veg_con_pure_sx[, source:='veg_con_pure_sx']
veg_con_pure_hw[, source:='veg_con_pure_hw']
veg_con_pure_fir[, source:='veg_con_pure_fir']
 veg_dec_pure[, source:=' veg_dec_pure']
veg_mix[, source:='veg_mix']
non_forested_burned[, source:='non_forested_burned']
non_forested_logged[, source:='non_forested_logged']
non_forested_non_logged[, source:='non_forested_non_logged']
unknown[, source:='unknown']

ft_vri<-rbindlist(list(non_veg,veg_recent_burn, veg_con_pure_lodgepole_jack, veg_con_pure_ponderosa, veg_con_pure_other_pine ,veg_con_pure_fd , veg_con_pure_sx , veg_con_pure_hw , veg_con_pure_fir, veg_dec_pure, veg_mix, non_forested_burned, non_forested_logged ,non_forested_non_logged , unknown))

ft_vri$dups = duplicated(ft_vri, by = "feature_id")
check_dups<-ft_vri[feature_id %in% ft_vri[dups == T,]$feature_id, ][order(feature_id),]

ft_vri_out<-ft_vri[dups == F & !is.na(fuel_type), ]
ft_vri_out$dups <- NULL

rm(veg_con_pure_fd, veg_con_pure_fir, veg_con_pure_hw, veg_con_pure_lodgepole_jack, veg_con_pure_ponderosa, veg_con_pure_sx, veg_dec_pure, veg_mix, veg_mixed, veg_recent_burn, veg_recent_burned, ft_vri, non_forested_burned, non_forested_logged, non_forested_non_logged, non_veg, non_veg_logged, non_veg_non_logged)
gc()
```

### Spatial
```{r, spatial}
vri<- getSpatialQuery(glue::glue("SELECT feature_id, {geom_column} FROM vri.veg_comp_lyr_r1_poly{year_vri} "))

restest = c(100, 100)
prov.rast <- raster( # standardized provincial raster with no data in it
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = restest,
  vals = 0)

ras.prov<-fasterize::fasterize(vri, prov.rast, field = "feature_id")
rm(vri)
gc()

pixel.grid<-data.table(feature_id = ras.prov[])[, pixelid := seq_len(.N)]

out<-merge(pixel.grid, ft_vri_out, by.x= "feature_id", by.y = "feature_id", all.x = T)
out<-out[, flammable:=1][is.na(fuel_type) | fuel_type %in% c('W', 'N'), flammable:=0]
out<-out[order(pixelid)]
ras.prov[]<-out$flammable
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("flammable_{year_vri}_10k.tif "))
out$flammable<-NULL
#C1
out<-out[, c1:=0][fuel_type== 'C-1', c1:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$c1
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("c1_{year_vri}_10k.tif "))
out$c1<-NULL
#C2
out<-out[, c2:=0][fuel_type== 'C-2', c2:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$c2
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("c2_{year_vri}_10k.tif "))
out$c2<-NULL
#C3
out<-out[, c3:=0][fuel_type== 'C-3', c3:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$c3
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("c3_{year_vri}_10k.tif "))
out$c3<-NULL
#C4
out<-out[, c4:=0][fuel_type== 'C-4', c4:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$c4
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("c4_{year_vri}_10k.tif "))
out$c4<-NULL
#C5
out<-out[, c5:=0][fuel_type== 'C-5', c5:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$c5
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("c5_{year_vri}_10k.tif "))
out$c5<-NULL

#C7
out<-out[, c7:=0][fuel_type== 'C-7', c7:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$c7
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("c7_{year_vri}_10k.tif "))
out$c7<-NULL
#D-1/2
out<-out[, d:=0][fuel_type== 'D-1/2', d:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$d
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("d_{year_vri}_10k.tif "))
out$d<-NULL
#M-1/2
out<-out[, m:=0][fuel_type %in% c('M-1/2', 'M-3') , m:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$m
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("m_{year_vri}_10k.tif "))
out$m<-NULL
#'O-1a/b'
out<-out[, o:=0][fuel_type == c('O-1a/b') , o:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$o
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("o_{year_vri}_10k.tif "))
out$o<-NULL

#S-1,S-2,S-3
out<-out[, s:=0][fuel_type %in% c('S-1', 'S-2', 'S-3') , s:=1]
out<-out[order(pixelid)]
ras.prov[]<-out$s
ras.flame<-terra::crop(terra::aggregate(terra::rast(ras.prov), fact = 100, fun = sum ),ras.prov)
writeRaster(ras.flame, glue::glue("s_{year_vri}_10k.tif "))
out$s<-NULL
```

### Comparison with 2021 DataBC Fuel type map
The 2021 VRI fuel type mapping can be found [here](https://catalogue.data.gov.bc.ca/dataset/bc-wildfire-fire-fuel-types-public). The following is a confusion matrix for a sample area near Prince George with 199,843 polygons.
```{r, eval=F}
sample_ft2021<-data.table(st_drop_geometry(st_read(paste0("C:/Users/klochhea/castor/R/fire_sim/number_of_ignitions/PROT_FUEL_TYPE_SP/PROTFUELTY_polygon.shp"))))[, c("FEATURE_ID", "FL_TYP_CD")]

compare_2021<-merge(ft_vri_out, sample_ft2021, by.x = "feature_id", by.y = "FEATURE_ID", all.x= T)
compare_2021<-compare_2021[!is.na(FL_TYP_CD),][!(fuel_type %in% c('M-3', 'C-1', 'S-3')),]
caret::confusionMatrix(as.factor(compare_2021$fuel_type), reference= as.factor(compare_2021$FL_TYP_CD))
```
