<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Database creation for WhiteSail WHA Scenario Analysis"
author: "Kyle Lochhead"
date: "26-March-2024"
output: pdf_document
---

# Overview
-	Need timber supply impact analysis for the proposed whitesail WHA


# Usage
Set parameters for creating the database in the code chunk below.

```{r module_usage}
library (data.table)
library (keyring)
library (terra)

source (here::here("R/functions/R_Postgres.R"))

Sys.setenv(JAVA_HOME = 'C:\\Program Files\\Java\\jdk-14.0.1') #throws an error if pointing to different version of java (i.e., 32 vs 64 bit)

moduleDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules"))
inputDir <- file.path (paste0 (here::here (), "/R/scenarios/whitesail/inputs")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path (paste0 (here::here (), "/R/scenarios/whitesail/outputs")) %>% reproducible::checkPath (create = TRUE)


times <- list (start = 0, end = 0)
parameters <-  list (
        .progress = list (type = NA, interval = NA),
        .globals = list (),
        dataCastor = list(dbName = 'castor',
                         saveCastorDB = TRUE,
                          sqlite_dbname = "morice_whitesail", 
                          nameBoundaryFile = "public.tsa_aac_bounds", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = "Morice_TSA", 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "rast.tsa_aac_boundary", 
                          nameCompartmentTable = "vat.tsa_aac_bounds_vat", 
                          nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2022',  
                          nameZoneRasters = c ("rast.zone_cond_beo"),
                          nameZoneTable = "zone.constraints", 
                          # natural and managed stands yield curves are the same    
                          nameYieldsRaster = "rast.ycid_vdyp_2020", 
                          nameYieldTable = "yc_vdyp_2020", 
                          nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                          nameYieldCurrentTable = "tipsy_prov_current_2020",
                          nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                          nameYieldTransitionTable = "tipsy_prov_2020",  
                          nameForestInventoryRaster = "rast.vri2023_id", 
                          nameForestInventoryKey = "feature_id", 
                          nameForestInventoryTable = "vri.veg_comp_lyr_r1_poly2023",
                          nameForestInventoryAge = "proj_age_1",  
                          nameForestInventoryHeight = "proj_height_1",
                          nameForestInventoryCrownClosure = "crown_closure",                             
                          nameForestInventoryTreed = "bclcs_level_2",
                          nameForestInventoryBasalArea= "basal_area",
                          nameForestInventoryQMD = "quad_diam_125",
                          nameForestInventorySiteIndex = "site_index" 
                          ),
        growingStockCastor = list (periodLength = 5),
        blockingCastor = list(blockMethod = 'pre', 
                              patchZone = 'rast.zone_cond_beo',
                              patchVariation = 6,
                              nameCutblockRaster ="rast.cns_cutblk_2023",
                              useLandingsArea = FALSE),
        roadCastor = list (roadMethod = 'mst',
                           nameCostSurfaceRas = 'rast.rd_cost_surface',
                           nameRoads =  'rast.ce_road_2022'
                           ),
        disturbanceCastor = list(calculateInterval =  1, 
                                 criticalHabitatTable = "vat.criticalhabitat_tweedsmuir_vat",
                                 criticalHabRaster = "rast.zone_cond_bc_tweedsmuir_crithab",
                                 permDisturbanceRaster = "rast.mine_ag_wind_rail",
                                 recovery = 30), # 30 years road recovery
 volumebyareaReportCastor = list (calculateInterval = 1,
                                         AreaofInterestRaster = "rast.morice_wha",
                                         AreaofInterestTable = "vat.morice_wha"),
 survivalCastor = list (caribou_herd_density = 0.05, 
                               nameRasCaribouHerd = "rast.caribou_herd_20220725", 
                               tableCaribouHerd = "vat.caribou_herd_20220725"),
   
        uploadCastor = list(aoiName = 'whitesail_morice',
                              dbInfo  = list(keyring::key_get ("vmdbhost", keyring="postgreSQL"),
                                             keyring::key_get ("vmdbuser", keyring="postgreSQL"),
                                             keyring::key_get ("vmdbpass", keyring="postgreSQL"), 
                                             keyring::key_get ("vmdbname", keyring="postgreSQL")))
        )

scenario = data.table (name = "load_data_May2024", description = "dataCastor output")

modules <- list("dataCastor",
                "growingStockCastor",
                "blockingCastor", 
                "roadCastor",
                "survivalCastor",
                "disturbanceCastor",
                "volumebyareaReportCastor"
                #"uploadCastor"
                )

objects <- list (scenario = scenario
                 )

paths <- list(modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

inputs <- list()
outputs <- list()

mySim <- SpaDES.core::simInitAndSpades(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)



```

## Adjust last use date of roads in castordb
Before running this chuck make sure dataCastor_morice has been run to build the castordb and backCastor_morice has been run to estimates the time since last use.
```{r}
rd.stat<-rast("C:/Users/klochhea/castor/R/scenarios/whitesail/patchworks_seq/est_roadstatus_whitesail.tif")
update_roadstatus<- data.table(est_rs=rd.stat[])[,pixelid:=seq_len(.N)]
setnames(update_roadstatus, "est_rs.lyr.1", "est_rs")
update_roadstatus<-update_roadstatus[!is.na(est_rs),]

castordb <- dbConnect(RSQLite::SQLite(), dbname ="C:/Users/klochhea/castor/R/scenarios/whitesail/patchworks_seq/morice_whitesail_castordb.sqlite")

# update pixels table 
dbBegin (castordb)
rs <- dbSendQuery (castordb, "UPDATE pixels SET roadstatus = :est_rs where pixelid = :pixelid;", update_roadstatus)
dbClearResult (rs)
dbCommit (castordb)

dbDisconnect(castordb)
```

#Adjust the blocks table
```{r}
castordb <- dbConnect(RSQLite::SQLite(), dbname ="C:/Users/klochhea/castor/R/scenarios/whitesail/patchworks_seq/morice_whitesail_castordb.sqlite")
ras.info<-dbGetQuery(castordb, "SELECT * FROM raster_info where name = 'ras';")
print(ras.info)
ras<-rast(xmin= ras.info$xmin, xmax=ras.info$xmax, ymin=ras.info$ymin, ymax=ras.info$ymax, nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow)
crs(ras) <-st_crs(as.integer(ras.info$crs))$wkt

#remove old blocks from blockingCastor
dbExecute(castordb, "update pixels set blockid =1 where blockid > 0;")
dbExecute(castordb, "update pixels set blockid =1 where thlb > 0;")
dbExecute(castordb, "DElete from blocks;")

landing.info<-dbGetQuery(castordb, "select pixelid, dist, thlb from pixels order by pixelid")

edges.weight<-data.table(dbGetQuery(castordb, "select * from roadedges;"))
node.coords<-data.table(dbGetQuery(castordb, "select * from roadcoords;"))
g<-cppRouting::makegraph(edges.weight,directed=F, coords = node.coords) 
graph.df<-cppRouting::to_df(g)
dbDisconnect(castordb)

base.blocks<-st_read("C:/Users/klochhea/castor/R/scenarios/whitesail/data_raw/external/basecase_v1_250year_schedule.shp")

#rasterize all blockids
ras.blocks<-terra::rasterize(base.blocks, ras, field = 'stand')

#get the landings
base.blocks.tab<-data.table(blockid = ras.blocks[], pixelid = landing.info$pixelid, dist = landing.info$dist, thlb = landing.info$thlb)[ blockid.stand > 0, ]

base.blocks.tab<-base.blocks.tab[, mdist := min(dist), by = blockid.stand][order(blockid.stand)]

landings<-base.blocks.tab[ dist==mdist, ][, mpixelid := max(pixelid), by = blockid.stand][pixelid == mpixelid,]

#check to make sure in graph
verts<-unique(c(as.integer(graph.df$from), as.integer(graph.df$to)))
landings[pixelid %in% verts, in.graph:=1 ]
test<-landings[is.na(in.graph),] #3081 outside of graph...in perm roads

castordb <- dbConnect(RSQLite::SQLite(), dbname ="C:/Users/klochhea/castor/R/scenarios/whitesail/patchworks_seq/morice_whitesail_castordb.sqlite")

out<-landings[,c("blockid.stand", "pixelid")]
setnames(out, "blockid.stand", "blockid")

dbBegin (castordb)
rs <- dbSendQuery (castordb, "INSERT into blocks (blockid, landing) values (:blockid, :pixelid)", out)
dbClearResult (rs)
dbCommit (castordb)

dbGetQuery(castordb, "select * from blocks limit 10;")
dbDisconnect(castordb)
```
