---
title: "03b_MDC_for_month_of_fire"
author: "Cora Skaien"
date: "07/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this file, we will determine the month in which each fire occurred from 2002-2020 and get the MDC (monthly drought code) for that month. The intentions here is that this should allow us to better predict when fires might occur by month instead of just by year.

PROBLEM: The no ignition locations do not have a month for which they did not ignite.

```{r}
#Load the relevant libraries
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)

```

Now load in the data from the end of the last file, and inspect.

```{r}
#Load in the data

sample_locations_DEM<-st_read(dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_2.shp")

head(sample_locations_DEM)
sample_locations_DEM$ign_dat

```

