---
title: "Fire ignition model fit by BEC zone"
author: "Elizabeth Kleynhans"
date: "20/04/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

editor_options:
  chunk_output_type: console
  
<style> 
p.caption {
  font-size: 1.2em;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require (kableExtra)
require (data.table)
require (DBI)
require (RPostgreSQL)
require (dplyr)
require (ggplot2)
require (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
```


<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

## Introduction

Here I am running a glm for each separate bec zone to develop a predictive equation so that I can extrapolate fire ignitions into the future. The data that I include in these glms is both vegetation and climate date. The top climate variable for each BEC zone was determined in the script "04_ignition_climate_variable_selection.R". Vegetation data is a little complicated by the fact that the VRI does not have age, height or volume data for any vegetation types that are not classified as treed. Also, it seems like forests on private land lack age, volume and height data. Because I think volume, age and height are likely good predictors of fire severity and occurence I split up this analysis into two parts in each BEC zone. 
Firstly, in each BEC zone I split the data into treed and non-treed then I run a glm with climate and vegetation for areas that are classified as treed in the VRI and then I run another separate analysis for areas that are classified as not treed. The fixed effects I include in these analyses are slightly different, i.e. no age, volume or height data in the non-treed areas, which is why I split them up.  

# climate variable selection
In the script "04_ignition_climate_variable_selection.R" I perform an AIC and ROC analysis for each BEC zone including presence/available fire ignition points and a variety of climate variables. For this analysis I split the data into a training and a validation data set where 75% of the data was used for training and 25% was used for validation. I then fit the model and extracted the AIC and AUC values. This was repeated 100 times and at the end I calculated the average AIC and AUC values. The climate variable that results in the lowest average AIC value I decided to use in this analysis. Table 1 is a summary of which climate variables fitted best for each BEC zone. 

Note: Some climate variables resulted in delta AIC values that were very similar and had much less than 2 points difference. Also, the variable with the smallest AIC value did not always have the best AUC value. Regardless of these two issues I decided to take the climate variable with the smallest average AIC for simplicity. Results can be found in table 1 below.

```{r, AIC table, echo = F, message = F, eval = T}

 climate.aic <- read.csv ("D:/Fire/fire_data/raw_data/ClimateBC_Data/AIC_table.csv")

kable (climate.aic,
       caption = "<b>Table 1. Top candidate climate variables as selected through an AIC analysis for each BEC zone.<b>",
       digits = 2) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)

```
## Pull in the data
```{r}
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")
dat <- sf::st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM fire_ignitions_veg_climate_clean")
dbDisconnect (connKyle)

head(dat)

```
## Examining correlation between stand level variables
```{r}
# Examining the relationship between some stand level variables. Volume and height are fairly correlated (0.67) but age and volume are not (0.28) and neither are age and height (0.44). Because volume and height are very close to 0.7 in correlation I will leave out this combination of variables from my treed models.  
dat_t<- dat %>% dplyr::filter(bclcs_level_2=="T")


ggscatter(dat_t, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(dat_t, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(dat_t, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

```

## BEC ZONE BG
```{r bg figures}
bg<- dat %>% dplyr::filter(zone =="BG")
# I will run separate analyses for treed and non-treed areas because the non-treed areas dont have information for forest height, age or volume and so these variables cant be included in the model.
bg_t<- bg %>% dplyr::filter(bclcs_level_2=="T") # treed areas
bg_nt<- bg %>% dplyr::filter(bclcs_level_2!="T") # not treed

# examining  relationship between top climatic variable and ignition for bg  
p <- ggplot(bg, aes(ppt09, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("ppt09") + ylab("Pr (ignition)")
p

p1 <- ggplot(bg_t, aes(ppt09, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("ppt09") + ylab("Pr (ignition)")
p1

p2 <- ggplot(bg_nt, aes(ppt09, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("ppt09") + ylab("Pr (ignition)")
p2

hist(bg_t$ppt09)
hist(bg_nt$ppt09)

```

## BG treed statistical model 
```{r BG treed model fits}
################################
#### Fitting statistical models
################################


glm1<- glm(fire_pres ~ ppt09, 
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"ppt09"
table.glm[1,3]<-AICc(glm1)

glm2<- glm(fire_pres ~ ppt09 +
             proj_age_1, 
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"ppt09 + proj_age_1"
table.glm[i,3]<-AICc(glm2)


glm3<- glm(fire_pres ~ ppt09 +
             proj_height_1, 
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + proj_height_1"
table.glm[i,3]<-AICc(glm3)

glm4<- glm(fire_pres ~ ppt09 +
             live_stand_volume_125, 
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + live_stand_volume_125"
table.glm[i,3]<-AICc(glm4)

glm5<- glm(fire_pres ~ ppt09 +
             bclcs_level_4, # classification of tree type in the VRI 
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + bclcs_level_4"
table.glm[i,3]<-AICc(glm5)

glm6<- glm(fire_pres ~ ppt09 +
             live_stand_volume_125 + 
             proj_age_1,
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + live_stand_volume_125 +proj_age_1"
table.glm[i,3]<-AICc(glm6)

glm7<- glm(fire_pres ~ ppt09 +
             proj_age_1 + 
             proj_height_1,
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + proj_age_1 + proj_height_1"
table.glm[i,3]<-AICc(glm7)

glm8<- glm(fire_pres ~ ppt09 +
             proj_age_1 + 
             bclcs_level_4,
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm8)

glm9<- glm(fire_pres ~ ppt09 +
             proj_height_1 + 
             bclcs_level_4,
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + proj_height_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm9)

glm10<- glm(fire_pres ~ ppt09 +
             live_stand_volume_125 + 
             bclcs_level_4,
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + live_stand_volume_125 + bclcs_level_4"
table.glm[i,3]<-AICc(glm10)

glm11<- glm(fire_pres ~ ppt09 +
             live_stand_volume_125 + 
              proj_age_1 +
             bclcs_level_4,
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + live_stand_volume_125 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm11)

glm12<- glm(fire_pres ~ ppt09 +
              proj_height_1 +
              proj_age_1 +
             bclcs_level_4,
           data= bg_t,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"ppt09 + proj_height_1 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm12)


table.glm$deltaAIC<- table.glm$AIC-min(table.glm$AIC)

table.glm.bg<- table.glm
table.glm.bg[order(table.glm.bg$deltaAIC),]
# # 
#    Model                                                   Variable      AIC deltaAIC
# 3   glm3                                      ppt09 + proj_height_1 46.69131 0.000000
# 2   glm2                                         ppt09 + proj_age_1 46.99776 0.306443
# 4   glm4                              ppt09 + live_stand_volume_125 47.89195 1.200636
# 1   glm1                                                      ppt09 48.27350 1.582185
# 7   glm7                         ppt09 + proj_age_1 + proj_height_1 48.62752 1.936213
# 9   glm9                      ppt09 + proj_height_1 + bclcs_level_4 48.74371 2.052398
# 6   glm6                  ppt09 + live_stand_volume_125 +proj_age_1 48.86550 2.174189
# 8   glm8                         ppt09 + proj_age_1 + bclcs_level_4 49.60401 2.912703
# 12 glm12         ppt09 + proj_height_1 + proj_age_1 + bclcs_level_4 50.56154 3.870232
# 5   glm5                                      ppt09 + bclcs_level_4 51.51365 4.822336
# 10 glm10              ppt09 + live_stand_volume_125 + bclcs_level_4 51.63845 4.947142
# 11 glm11 ppt09 + live_stand_volume_125 + proj_age_1 + bclcs_level_4 52.17844 5.487132

#TOP MODEL = glm3    ppt09 + proj_height_1 45.80242 0.0000000


####################################################
##### TOP MODEL####

bg_t2<-bg_t %>% drop_na(proj_height_1)

glm_best<- glm(fire_pres ~ ppt09 +
             proj_height_1, 
           data= bg_t2,
           family = binomial,
           na.action=na.omit)

summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


bg_t2$resids<-resid(glm_best)

binnedplot (bg_t2$proj_height_1, 
            bg_t2$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (bg_t2$ppt09, 
            bg_t2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look ok, but my sample sizes in this BEC zone are low!

# Looking at effect of forest height at the average amount of rainfall in September
plot(bg_t2$proj_height_1,bg_t2$fire_pres)
curve(invlogit(coef(glm_best)[1] +coef(glm_best)[2]*mean(bg_t2$ppt09) + coef(glm_best)[3]*x), add=TRUE)

# looking at effect of ppt09 at the average forest height.
plot(bg_t2$ppt09,bg_t2$fire_pres)
curve(invlogit(coef(glm_best)[1] +coef(glm_best)[2]*x + coef(glm_best)[3]*mean(bg_t2$proj_height_1)), add=TRUE)


# create model table (only do this once) and add the relevant data
top_mod_table <- data.frame (matrix (ncol = 7, nrow = 0))
colnames (top_mod_table) <- c ("ZONE", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2",  "coef_stand_height")
top_mod_table[1,1]<-"BG"
top_mod_table[1,2]<-"Y"
top_mod_table[1,3]<-"fire_pres ~ ppt09 + proj_height_1"
top_mod_table[1,4]<- coef(glm_best)[1]
top_mod_table[1,5]<- coef(glm_best)[2]
#top_mod_table[1,6]<- coef(glm_best)[2]
top_mod_table[1,7]<- coef(glm_best)[3]

```

## BEC ZONE BWBS Figures
```{r bg figures}
bwbs<- dat %>% dplyr::filter(zone =="BWBS")
# I will run separate analyses for treed and non-treed areas because the non-treed areas dont have information for forest height, age or volume and so these variables cant be included in the model.
bwbs_t<- bwbs %>% dplyr::filter(bclcs_level_2=="T") # treed areas
bwbs_nt<- bwbs %>% dplyr::filter(bclcs_level_2!="T") # not treed

# examining  relationship between top climatic variable (tave07 + ppt07) and ignition for bwbs
p <- ggplot(bwbs, aes(mean_tave06_tave07_tave08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("mean_tave06_tave07_tave08") + ylab("Pr (ignition)")
p


p <- ggplot(bwbs_t, aes(mean_tave06_tave07_tave08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("mean_tave06_tave07_tave08") + ylab("Pr (ignition)")
p



hist(bwbs_t$mean_tave06_tave07_tave08)

# Examining the relationship between some stand level variables. Volume and height are fairly correlated (0.72) but age and volume are not. 
ggscatter(bwbs_t, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(bwbs_t, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(bwbs_t, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

```

## BWBS treed statistical model 
```{r BG treed model fits}
################################
#### Fitting statistical models
################################


glm1<- glm(fire_pres ~ mean_tave06_tave07_tave08, 
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"mean_tave06_tave07_tave08"
table.glm[1,3]<-AICc(glm1)

glm2<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             proj_age_1, 
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"mean_tave06_tave07_tave08 + proj_age_1"
table.glm[i,3]<-AICc(glm2)


glm3<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             proj_height_1, 
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + proj_height_1"
table.glm[i,3]<-AICc(glm3)

glm4<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             live_stand_volume_125, 
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + live_stand_volume_125"
table.glm[i,3]<-AICc(glm4)

glm5<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             bclcs_level_4, # classification of tree type in the VRI 
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + bclcs_level_4"
table.glm[i,3]<-AICc(glm5)

glm6<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             live_stand_volume_125 + 
             proj_age_1,
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + live_stand_volume_125 +proj_age_1"
table.glm[i,3]<-AICc(glm6)

glm7<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             proj_age_1 + 
             proj_height_1,
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + proj_age_1 + proj_height_1"
table.glm[i,3]<-AICc(glm7)

glm8<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             proj_age_1 + 
             bclcs_level_4,
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm8)

glm9<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             proj_height_1 + 
             bclcs_level_4,
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + proj_height_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm9)

glm10<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             live_stand_volume_125 + 
             bclcs_level_4,
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + live_stand_volume_125 + bclcs_level_4"
table.glm[i,3]<-AICc(glm10)

glm11<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
             live_stand_volume_125 + 
              proj_age_1 +
             bclcs_level_4,
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + live_stand_volume_125 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm11)

glm12<- glm(fire_pres ~ mean_tave06_tave07_tave08 +
              proj_height_1 +
              proj_age_1 +
             bclcs_level_4,
           data= bwbs_t,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tave06_tave07_tave08 + proj_height_1 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm12)


table.glm$deltaAIC<- table.glm$AIC-min(table.glm$AIC)

table.glm.bwbs<- table.glm
table.glm.bwbs[order(table.glm.bwbs$deltaAIC),]


#    Model                                                            Variable      AIC     deltaAIC
# 10 glm10              tave07 + ppt07 + live_stand_volume_125 + bclcs_level_4 2978.315    0.0000000
# 11 glm11 tave07 + ppt07 + live_stand_volume_125 + proj_age_1 + bclcs_level_4 2978.591    0.2759201
# 6   glm6                  tave07 + ppt07 + live_stand_volume_125 +proj_age_1 3037.320   59.0055587
# 4   glm4                              tave07 + ppt07 + live_stand_volume_125 3054.007   75.6919814
# 8   glm8                         tave07 + ppt07 + proj_age_1 + bclcs_level_4 3913.293  934.9783335
# 12 glm12         tave07 + ppt07 + proj_height_1 + proj_age_1 + bclcs_level_4 3915.140  936.8249623
# 9   glm9                      tave07 + ppt07 + proj_height_1 + bclcs_level_4 3915.469  937.1541952
# 5   glm5                                      tave07 + ppt07 + bclcs_level_4 3964.378  986.0631628
# 7   glm7                         tave07 + ppt07 + proj_age_1 + proj_height_1 3983.478 1005.1634768
# 2   glm2                                         tave07 + ppt07 + proj_age_1 4000.481 1022.1662710
# 3   glm3                                      tave07 + ppt07 + proj_height_1 4013.383 1035.0685117
# 1   glm1                                                      tave07 + ppt07 4062.787 1084.4722965

####################################################
##### TOP MODEL####

bwbs_t2<-bwbs_t %>% drop_na(live_stand_volume_125)

glm_best<- glm(fire_pres ~ scale(mean_tave06_tave07_tave08)+
             scale(live_stand_volume_125) + 
             bclcs_level_4, 
           data= bwbs_t2,
           family = binomial,
           na.action=na.omit)

summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = "Binned Residual Plot - glm")


bwbs_t2$resids<-resid(glm_best)

binnedplot (bwbs_t2$live_stand_volume_125, 
            bwbs_t2$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (bwbs_t2$mean_tave06_tave07_tave08, 
            bwbs_t2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))



# Diagnostic plots look ok, not great! Im reluctant to transform variables that are skewed especially stand volume because stand volume might change over time during the clus simulation and I dont know how to implement a changing distribution.


```

## CMA treed statistical model 
```{r BG treed model fits}
################################
#### Fitting statistical models
################################

cma<- dat %>% dplyr::filter(zone =="CMA")
# I will run separate analyses for treed and non-treed areas because the non-treed areas dont have information for forest height, age or volume and so these variables cant be included in the model.
cma_t<- cma %>% dplyr::filter(bclcs_level_2=="T") # treed areas
cma_nt<- cma %>% dplyr::filter(bclcs_level_2!="T") # not treed


glm1<- glm(fire_pres ~ tave08 * ppt08, 
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"tave08 * ppt08"
table.glm[1,3]<-AICc(glm1)

glm2<- glm(fire_pres ~ tave08 * ppt08 +
             proj_age_1, 
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"tave08 * ppt08 + proj_age_1"
table.glm[i,3]<-AICc(glm2)


glm3<- glm(fire_pres ~ tave08 * ppt08 +
             proj_height_1, 
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_height_1"
table.glm[i,3]<-AICc(glm3)

glm4<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125, 
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125"
table.glm[i,3]<-AICc(glm4)

glm5<- glm(fire_pres ~ tave08 * ppt08 +
             bclcs_level_4, # classification of tree type in the VRI 
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + bclcs_level_4"
table.glm[i,3]<-AICc(glm5)

glm6<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125 + 
             proj_age_1,
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125 +proj_age_1"
table.glm[i,3]<-AICc(glm6)

glm7<- glm(fire_pres ~ tave08 * ppt08 +
             proj_age_1 + 
             proj_height_1,
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_age_1 + proj_height_1"
table.glm[i,3]<-AICc(glm7)

glm8<- glm(fire_pres ~ tave08 * ppt08 +
             proj_age_1 + 
             bclcs_level_4,
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm8)

glm9<- glm(fire_pres ~ tave08 * ppt08 +
             proj_height_1 + 
             bclcs_level_4,
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_height_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm9)

glm10<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125 + 
             bclcs_level_4,
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125 + bclcs_level_4"
table.glm[i,3]<-AICc(glm10)

glm11<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125 + 
              proj_age_1 +
             bclcs_level_4,
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm11)

glm12<- glm(fire_pres ~ tave08 * ppt08 +
              proj_height_1 +
              proj_age_1 +
             bclcs_level_4,
           data= cma_t,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_height_1 + proj_age_1 + bclcs_level_4"
table.glm[i,3]<-AICc(glm12)


table.glm$deltaAIC<- table.glm$AIC-min(table.glm$AIC)

table.glm.bwbs<- table.glm
table.glm.bwbs[order(table.glm.bwbs$deltaAIC),]


#    Model                                                            Variable      AIC     deltaAIC
# 10 glm10              tave07 + ppt07 + live_stand_volume_125 + bclcs_level_4 2978.315    0.0000000
# 11 glm11 tave07 + ppt07 + live_stand_volume_125 + proj_age_1 + bclcs_level_4 2978.591    0.2759201
# 6   glm6                  tave07 + ppt07 + live_stand_volume_125 +proj_age_1 3037.320   59.0055587
# 4   glm4                              tave07 + ppt07 + live_stand_volume_125 3054.007   75.6919814
# 8   glm8                         tave07 + ppt07 + proj_age_1 + bclcs_level_4 3913.293  934.9783335
# 12 glm12         tave07 + ppt07 + proj_height_1 + proj_age_1 + bclcs_level_4 3915.140  936.8249623
# 9   glm9                      tave07 + ppt07 + proj_height_1 + bclcs_level_4 3915.469  937.1541952
# 5   glm5                                      tave07 + ppt07 + bclcs_level_4 3964.378  986.0631628
# 7   glm7                         tave07 + ppt07 + proj_age_1 + proj_height_1 3983.478 1005.1634768
# 2   glm2                                         tave07 + ppt07 + proj_age_1 4000.481 1022.1662710
# 3   glm3                                      tave07 + ppt07 + proj_height_1 4013.383 1035.0685117
# 1   glm1                                                      tave07 + ppt07 4062.787 1084.4722965

####################################################
##### TOP MODEL####

cma_t2<-cma_t %>% drop_na(live_stand_volume_125)

glm_best<- glm(fire_pres ~ scale(mean_tave06_tave07_tave08)+
             scale(live_stand_volume_125) + 
             bclcs_level_4, 
           data= cma_t2,
           family = binomial,
           na.action=na.omit)

summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = "Binned Residual Plot - glm")


cma_t2$resids<-resid(glm_best)

binnedplot (cma_t2$live_stand_volume_125, 
            cma_t2$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (cma_t2$mean_tave06_tave07_tave08, 
            cma_t2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))



# Diagnostic plots look ok, not great! Im reluctant to transform variables that are skewed especially stand volume because stand volume might change over time during the clus simulation and I dont know how to implement a changing distribution.


```






## BEC ZONE ESSF
```{r essf climate figure}
# look at the data graphically in this BEC zone

# top climatic variables for essf were 
essf<- dat %>%
  filter(zone=="ESSF")

# Plotting Probability of ignition versus temp and precipitation.
p <- ggplot(essf, aes(tave08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("TAve08") + ylab("Pr (ignition)")
p

p <- ggplot(essf, aes(ppt08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("ppt08") + ylab("Pr (ignition)")
p


hist(essf$tave08)
hist(essf$ppt08, breaks=30)

# Examining the relationship between some stand level variables. Volume and height are fairly correlated but age and volume are not. However, none of the variables are more correlated than 0.7. So Ill try all combinations
ggscatter(essf, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(essf, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(essf, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

hist(essf$proj_age_1)
hist(scale(essf$proj_age_1))
hist(essf$proj_height_1)
hist(scale(essf$proj_height_1))
hist(essf$live_stand_volume_125, breaks=30)
hist(scale(essf$live_stand_volume_125), breaks=30)
```

```{r essf model fits}
################################
#### Fitting statistical models
################################
essf$proj_age_1_scale<-scale(essf$proj_age_1)
essf$live_stand_volume_125_scale<-scale(essf$live_stand_volume_125)
essf$proj_height_1_scale<-scale(essf$proj_height_1)


glm1<- glm(fire_pres ~ tave08 * ppt08, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"tave08 * ppt08"
table.glm[1,3]<-AIC(glm1)

glm2<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"tave08 * ppt08 + vegtype"
table.glm[i,3]<-AIC(glm2)


glm3<- glm(fire_pres ~ tave08 * ppt08 +
             proj_age_1_scale, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_age_1_scale"
table.glm[i,3]<-AIC(glm3)

glm4<- glm(fire_pres ~ tave08 * ppt08 +
             proj_height_1_scale, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_height_1_scale"
table.glm[i,3]<-AIC(glm4)

glm5<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125_scale, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125_scale"
table.glm[i,3]<-AIC(glm5)

glm6<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125_scale +
             proj_age_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125_scale + proj_age_1_scale"
table.glm[i,3]<-AIC(glm6)

glm7<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125_scale + proj_height_1_scale"
table.glm[i,3]<-AIC(glm7)

glm8<- glm(fire_pres ~ tave08 * ppt08 +
             proj_age_1_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_height_1_scale + proj_age_1_scale"
table.glm[i,3]<-AIC(glm8)

glm9<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             live_stand_volume_125_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + live_stand_volume_125_scale"
table.glm[i,3]<-AIC(glm9)

glm10<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             proj_age_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + proj_age_1_scale"
table.glm[i,3]<-AIC(glm10)

glm11<- glm(fire_pres ~ tave08 * ppt08 +
              vegtype + 
              proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + proj_height_1_scale"
table.glm[i,3]<-AIC(glm11)

glm12<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             live_stand_volume_125_scale +
             proj_age_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + live_stand_volume_125_scale + proj_age_1_scale"
table.glm[i,3]<-AIC(glm12)

glm13<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             live_stand_volume_125_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm13)
i=13
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + live_stand_volume_125_scale + proj_height_1_scale"
table.glm[i,3]<-AIC(glm13)

glm14<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             proj_age_1_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm14)
i=14
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + proj_age_1_scale + proj_height_1_scale"
table.glm[i,3]<-AIC(glm14)


table.glm$delta.aic<- table.glm$AIC - min(table.glm$AIC)
table.glm[order(table.glm$delta.aic),]

# TOP MODEL IS glm13: tave08 * ppt08 + vegtype + live_stand_volume_125_scale + proj_height_1_scale


####################################################
##### TOP MODEL####

essf_red<-essf %>% drop_na(live_stand_volume_125_scale, proj_age_1_scale, vegtype)

glm_best<- glm(fire_pres ~ scale(tave08) * scale(ppt08) +
             vegtype +
             live_stand_volume_125_scale +
             proj_age_1_scale,
           data= essf_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


essf_red$resids<-resid(glm_best)

binnedplot (essf_red$live_stand_volume_125_scale, 
            essf_red$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (essf_red$proj_age_1_scale, 
            essf_red$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

```


## BEC ZONE SBS

```{r sbs climate figure}
# look at the data graphically in this BEC zone

# top climatic variables for SBS were mean_tmax07_tmax08
sbs<- dat %>%
  filter(zone=="SBS")

# Plotting Probability of ignition versus temp and precipitation.
p <- ggplot(sbs, aes(mean_tmax07_tmax08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("Mean Tmax_07 and Tmax_08") + ylab("Pr (ignition)")
p

hist(sbs$mean_tmax07_tmax08)

# Examining the relationship between some stand level variables. Volume and height are fairly correlated but age and volume are not. However, none of the variables are more correlated than 0.7. So Ill try all combinations
ggscatter(dat, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(dat, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(dat, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

hist(dat$proj_age_1, breaks=30)
hist(dat$live_stand_volume_125, breaks=30)

```

```{r sbs model fits}
################################
#### Fitting statistical models
################################

glm1<- glm(fire_pres ~ mean_tmax07_tmax08, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"mean_tmax07_tmax08"
table.glm[1,3]<-AIC(glm1)
binnedplot (fitted(glm1), 
            residuals(glm1), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = "Binned Residual Plot - glm1")

#veg_variables<- c("vegtype", "proj_age_1", "proj_height_1", "live_stand_volume_125", "subzone")

glm2<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype"
table.glm[i,3]<-AIC(glm2)
binnedplot (fitted(glm2), 
            residuals(glm2), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = "Binned Residual Plot - glm2")

glm3<- glm(fire_pres ~ mean_tmax07_tmax08 +
             proj_age_1, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + proj_age_1"
table.glm[i,3]<-AIC(glm3)

glm4<- glm(fire_pres ~ mean_tmax07_tmax08 +
             proj_height_1, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + proj_height_1"
table.glm[i,3]<-AIC(glm4)

glm5<- glm(fire_pres ~ mean_tmax07_tmax08 +
             live_stand_volume_125, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + live_stand_volume_125"
table.glm[i,3]<-AIC(glm5)

glm6<- glm(fire_pres ~ mean_tmax07_tmax08 +
             live_stand_volume_125 +
             proj_age_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm6)

glm7<- glm(fire_pres ~ mean_tmax07_tmax08 +
             live_stand_volume_125 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm7)

glm8<- glm(fire_pres ~ mean_tmax07_tmax08 +
             proj_age_1 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + proj_height_1 + proj_age_1"
table.glm[i,3]<-AIC(glm8)

glm9<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + live_stand_volume_125"
table.glm[i,3]<-AIC(glm9)

glm10<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             proj_age_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + proj_age_1"
table.glm[i,3]<-AIC(glm10)

glm11<- glm(fire_pres ~ mean_tmax07_tmax08 +
              vegtype + 
              proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + proj_height_1"
table.glm[i,3]<-AIC(glm11)

glm12<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm12)

glm13<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm13)
i=13
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm13)

glm14<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             proj_age_1 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm14)
i=14
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + proj_age_1 + proj_height_1"
table.glm[i,3]<-AIC(glm14)

table.glm$delta.aic<- table.glm$AIC - min(table.glm$AIC)
table.glm[order(table.glm$delta.aic),]

# TOP MODEL IS glm13: mean_tmax07_tmax08 + vegtype + live_stand_volume_125 + proj_age_1


####################################################
##### TOP MODEL####

sbs_red<-sbs %>% drop_na(live_stand_volume_125, proj_age_1, vegtype)

glm_best<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbs_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


sbs_red$resids<-resid(glm_best)

binnedplot (sbs_red$live_stand_volume_125, 
            sbs_red$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (sbs_red$proj_age_1, 
            sbs_red$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# this one has a slight up down trend. Ill try to scale proj_age_1 and see if this helps

glm_best_scale<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             scale(live_stand_volume_125) +
             scale(proj_age_1),
           data= sbs_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best_scale)
binnedplot (fitted(glm_best_scale), 
            residuals(glm_best_scale), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = ("Binned Residual Plot - glm_best_log"))

sbs_red$resids_log<-resid(glm_best_scale)
binnedplot (scale(sbs_red$proj_age_1), 
            sbs_red$resids_log, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# BETTER I THINK! Also the AIC confirms this as it dropped by another 10 points.

# FINAL MODEL EQUATION TO USE IN FIRE PROJECTIONS IS:
# Pr(ignition) = logit^(-1)(-4.47115 + 
#       0.132*mean_tmax07_tmax08 + 
#       -1.12*vegtypeOP)

```

## BEC ZONE SBPS

```{r sbps climate figure}
# look at the data graphically in this BEC zone

# top climatic variables for SBS were mean_tmax07_tmax08
sbps<- dat %>%
  filter(zone=="SBPS")

# Plotting Probability of ignition versus temp and precipitation.
p <- ggplot(sbps, aes(mean_tmax05_tmax06_tmax07_tmax08_tmax09, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("mean_tmax05_tmax06_tmax07_tmax08_tmax09") + ylab("Pr (ignition)")
p

hist(sbps$mean_tmax05_tmax06_tmax07_tmax08_tmax09)

# Examining the relationship between some stand level variables. Volume and height are fairly correlated but age and volume are not. However, none of the variables are more correlated than 0.7. So Ill try all combinations
ggscatter(sbps, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(sbps, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(sbps, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

hist(sbps$proj_age_1, breaks=30)
hist(sbps$live_stand_volume_125, breaks=30)

```

```{r sbps model fits}
################################
#### Fitting statistical models
################################

glm1<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09"
table.glm[1,3]<-AIC(glm1)

glm2<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype"
table.glm[i,3]<-AIC(glm2)

glm3<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             proj_age_1, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + proj_age_1"
table.glm[i,3]<-AIC(glm3)

glm4<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             proj_height_1, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + proj_height_1"
table.glm[i,3]<-AIC(glm4)

glm5<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             live_stand_volume_125, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + live_stand_volume_125"
table.glm[i,3]<-AIC(glm5)

glm6<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             live_stand_volume_125 +
             proj_age_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm6)

glm7<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             live_stand_volume_125 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm7)

glm8<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             proj_age_1 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + proj_height_1 + proj_age_1"
table.glm[i,3]<-AIC(glm8)

glm9<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125"
table.glm[i,3]<-AIC(glm9)

glm10<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             proj_age_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + proj_age_1"
table.glm[i,3]<-AIC(glm10)

glm11<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
              vegtype + 
              proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + proj_height_1"
table.glm[i,3]<-AIC(glm11)

glm12<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm12)

glm13<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm13)
i=13
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm13)

glm14<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             proj_age_1 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm14)
i=14
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + proj_age_1 + proj_height_1"
table.glm[i,3]<-AIC(glm14)

table.glm$delta.aic<- table.glm$AIC - min(table.glm$AIC)
table.glm[order(table.glm$delta.aic),]

# TOP MODEL IS glm13: mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125 + proj_age_1


####################################################
##### TOP MODEL####

sbps_red<-sbps %>% drop_na(live_stand_volume_125, proj_age_1, vegtype)

glm_best<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbps_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


sbps_red$resids<-resid(glm_best)

binnedplot (sbps_red$live_stand_volume_125, 
            sbps_red$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (sbps_red$proj_age_1, 
            sbps_red$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# this one has a slight up down trend. Ill try to scale proj_age_1 and see if this helps

glm_best_scale<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             scale(live_stand_volume_125) +
             scale(proj_age_1),
           data= sbps_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best_scale)
binnedplot (fitted(glm_best_scale), 
            residuals(glm_best_scale), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = ("Binned Residual Plot - glm_best_log"))

sbps_red$resids_log<-resid(glm_best_scale)
binnedplot (scale(sbps_red$proj_age_1), 
            sbps_red$resids_log, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# BETTER I THINK! Also the AIC confirms this as it dropped by another 10 points.

# FINAL MODEL EQUATION TO USE IN FIRE PROJECTIONS IS:
# Pr(ignition) = logit^(-1)(-4.47115 + 
#       0.132*mean_tmax05_tmax06_tmax07_tmax08_tmax09 + 
#       -1.12*vegtypeOP)

```

