---
title: "Wind_Speed_Data_Prep"
author: "Cora Skaien"
date: "13/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Overview
In this file, we will bring in shape files that indicate wind speed averaged over 43 years to get an idea of the spring and summer wind speeds experienced in an area. 

These files were acquired from the Wind Atlas from the government of Canada:http://www.windatlas.ca/index-en.php

Spring is represented by MAM (March, April, May). Summer is represented by JJA (representing June, July and August). You will also receive the winter, fall and annual values in one folder.

These files were downloaded as mif. files and converted to shape files using OsGeo4W. Sample code is provided below:

ogr2ogr -f 'ESRI Shapefile' output.shp input.mif

Specific example:
ogr2ogr -f “ESRI Shapefile” D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\064_30\\JJA\\7\\4_30_we_dos.shp D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\064_30\\JJA\\7\\4_30_we_dos.mif

Once all files were converted, then analysis in R can begin. The intended process is to bring in each shape file, append the layers together (for spring and summer separately), ensure the CRS is that as provided, then convert crs to 3005, then clip to BC boundary, then use location of sample points to determine the mean wind speed for both spring and summer for each location. 

The crs for the mif file is :CoordSys Earth Projection 20, 999, 12, 0, 0, 0, 7, -100.0000 , 90, 0.9330127, 0, 0

The MID files are column files and contain seven variables, the first two (E1 and EU) being the results of the statistical processing and the five others being related to the input data:

E1 (W/m2), mean wind power,
EU (m/s), mean wind speed,
ME (m), topography,
MG, land/water mask (1=land, 0=water),
2B (m), rugosity length,
LA, latitude,
LO, longitude given between 0 and 360°.

#Load libraries

```{r}
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(bcmaps)
library(ggplot2)
require (RPostgreSQL)
require (rpostgis)
require (fasterize)
require (dplyr)
library(keyring)

source(here::here("R/functions/R_Postgres.R"))
```


####### Summer layers ##########
Bring in the shape files
```{r}
#Bring in each of the files for summer

summer1<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\046_30\\JJA\\7\\8_30_we_dos.shp", stringsAsFactors = T)

summer2<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\045_30\\JJA\\7\\6_30_we_dos.shp", stringsAsFactors = T)

summer3<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\047_30\\JJA\\9\\8_30_we_dos.shp", stringsAsFactors = T)

summer4<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\048_30\\JJA\\11\\8_30_we_dos.shp", stringsAsFactors = T)

summer5<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\051_30\\JJA\\9\\6_30_we_dos.shp", stringsAsFactors = T)

summer6<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\052_30\\JJA\\11\\6_30_we_dos.shp", stringsAsFactors = T)

summer7<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\053_30\\JJA\\13\\8_30_we_dos.shp", stringsAsFactors = T)

summer8<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\055_30\\JJA\\9\\4_30_we_dos.shp", stringsAsFactors = T)

summer9<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\056_30\\JJA\\11\\4_30_we_dos.shp", stringsAsFactors = T)

summer10<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\057_30\\JJA\\13\\6_30_we_dos.shp", stringsAsFactors = T)

summer11<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\060_30\\JJA\\13\\4_30_we_dos.shp", stringsAsFactors = T)

summer12<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\061_30\\JJA\\15\\4_30_we_dos.shp", stringsAsFactors = T)

summer13<-st_read(dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\064_30\\JJA\\7\\4_30_we_dos.shp", stringsAsFactors = T)

```

Because these files were originally .mif files, they have no defined crs. We must define the crs for each one.

The Coordsys clause
CoordSys Earth Projection 20, 999, 12, 0, 0, 0, 7, -100.0000 , 90, 0.9330127, 0, 0
describes the mathematical approximation of the earth's shape and orientation. It reads:

Projection 20 == Stereographics projection  
999  == custom datum with shift parameters only (no rotation, no scale correction)
12 == datum ellipsoid number, refers to a sphere
0, 0, 0 == datum X,Y, Z shifts
7 == unit = meter
-100.0000	 == longitude of the origin (# 100° W)
90	== latitude of the origin (# 90° N)
0.9330127	== scale factor (adjusted to have a true scale at 60° N)
0 == false easting
0 == false northing


```{r}
##Try 4326 but uncertain if this is correct... hard to find the info.
 

#May need to work with below
#+proj=stere +lat_0=90 +lat_ts=70 +lon_0=-45 +k=1 +x_0=0 +y_0=0 +a=6378273 +b=6356889.449 +units=m +no_defs

#crs(r) <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"

#crs(summer1)<-+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs #+ellps=WGS84 #Note ellips might be wrong; lat_ts scale factor is 0.9330127 to be at 60 degrees north


summer1.sf <- st_set_crs(summer1, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
crs(summer1.sf)
summer2.sf <- st_set_crs(summer2, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer3.sf <- st_set_crs(summer3, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer4.sf <- st_set_crs(summer4, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer5.sf <- st_set_crs(summer5, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer6.sf <- st_set_crs(summer6, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer7.sf <- st_set_crs(summer7, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer8.sf <- st_set_crs(summer8, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer9.sf <- st_set_crs(summer9, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer10.sf <- st_set_crs(summer10, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer11.sf <- st_set_crs(summer11, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer12.sf <- st_set_crs(summer12, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 
summer13.sf <- st_set_crs(summer13, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs") 

head(st_coordinates(summer1.sf))
head(summer1.sf)
str(summer1.sf)
crs(summer1.sf)

```


```{r}
summer1.sf2<-st_transform(summer1.sf, 3005)
summer2.sf2<-st_transform(summer2.sf, 3005)
summer3.sf2<-st_transform(summer3.sf, 3005)
summer4.sf2<-st_transform(summer4.sf, 3005)
summer5.sf2<-st_transform(summer5.sf, 3005)
summer6.sf2<-st_transform(summer6.sf, 3005)
summer7.sf2<-st_transform(summer7.sf, 3005)
summer8.sf2<-st_transform(summer8.sf, 3005)
summer9.sf2<-st_transform(summer9.sf, 3005)
summer10.sf2<-st_transform(summer10.sf, 3005)
summer11.sf2<-st_transform(summer11.sf, 3005)
summer12.sf2<-st_transform(summer12.sf, 3005)
summer13.sf2<-st_transform(summer13.sf, 3005)

```


```{r}
max(summer1.sf$EU_12007_J)
min(summer1.sf$EU_12007_J) # I do not know how to interpret -1. Missing data? I will assume it is missing data.
table(summer1.sf$EU_12007_J) #3654 -1s present from 30276 observations
hist(summer1.sf$EU_12007_J)
str(summer1.sf)

#Inspect second element
hist(summer1.sf$EU2_12007_)

#Check histograms some other areas
hist(summer2.sf$EU_12007_J)
hist(summer3.sf$EU_12007_J)
hist(summer4.sf$EU_12007_J)

```

Plot the rasters to ensure all looks well

```{r}

ggplot() +
  geom_sf(data=summer1.sf, col='red') +
  geom_sf(data=summer2.sf, col='blue') +
  geom_sf(data=summer3.sf, col='green') +
  geom_sf(data=summer4.sf, col='pink') +
  geom_sf(data=summer5.sf, col='black') +
  geom_sf(data=summer6.sf, col='red') +
  geom_sf(data=summer7.sf, col='blue') +
  geom_sf(data=summer8.sf, col='purple') +
  geom_sf(data=summer9.sf, col='green') +
  geom_sf(data=summer10.sf, col='pink') +
  geom_sf(data=summer11.sf, col='black') +
  geom_sf(data=summer12.sf, col='red') +
  geom_sf(data=summer13.sf, col='blue')


```


Project in 3005 crs with BC map

```{r}
prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
bc.bnd <- st_transform (prov.bnd, 3005) #Transform coordinate system
```


```{r}
ggplot() + 
  geom_sf(data=summer2.sf2, col='blue') +
  geom_sf(data=summer3.sf2, col='green') +
  geom_sf(data=summer4.sf2, col='pink') +
  geom_sf(data=summer5.sf2, col='black') +
  geom_sf(data=summer6.sf2, col='red') +
  geom_sf(data=summer7.sf2, col='blue') +
  geom_sf(data=summer8.sf2, col='purple') +
  geom_sf(data=summer9.sf2, col='green') +
  geom_sf(data=summer10.sf2, col='pink') +
  geom_sf(data=summer11.sf2, col='black') +
  geom_sf(data=summer12.sf2, col='red') +
  geom_sf(data=summer13.sf2, col='blue') +
  geom_sf(data=summer1.sf2, col='red') +
  geom_sf(data=bc.bnd, col='red')
```
At a glance, looks approximately right? Will need to spot check some GPS locations by entering them online once we have them.

Given substantial overlap, we may not need all the files. Try to see which we might consider dropping.

```{r}
ggplot() +
  geom_sf(data=summer1.sf, col='red') +
  geom_sf(data=summer2.sf, col='blue') +
  geom_sf(data=summer3.sf, col='green') +
  geom_sf(data=summer4.sf, col='pink') +
  #geom_sf(data=summer5.sf, col='black') + # we lose a tiny bit here
  #geom_sf(data=summer6.sf, col='red') +
  geom_sf(data=summer7.sf, col='blue') +
  geom_sf(data=summer8.sf, col='purple') +
  geom_sf(data=summer9.sf, col='green') +
  #geom_sf(data=summer10.sf, col='pink') +
  geom_sf(data=summer11.sf, col='black') +
  geom_sf(data=summer12.sf, col='red') +
  geom_sf(data=summer13.sf, col='blue')

#Conclusion: need all polygons!
```

Now that we see we have the coverage we need, we can bind all of the shape files together. We may need to buffer the polygon before proceeding (buffer by 0), like we did with the bec zones in file 02_climate_data_prep_all.

Now that the files have a coordinate system, we may also want to bring the files into QGis to combine to make one layer and then bring it back into R. 

In QGis, bring in all of the files and visualize them. Start in one corner and visualize wherew they are overlapping. Now choose two at a time and use the "Difference" function under Vector --> Geoprocessing Tools. Then, take this difference and the relevant original tile and use "union" from the same window to combine them. Do this for all layers until you have one element. Now, we might need to use "Dissolve" to ensure it is one polygon.


#Save files with projection and manage in QGis. R and the computer crash each time we try to do it here.

```{r}

st_write(summer1.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer1.shp", delete_layer=TRUE)

st_write(summer2.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer2.shp", delete_layer=TRUE)

st_write(summer3.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer3.shp", delete_layer=TRUE)

st_write(summer4.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer4.shp", delete_layer=TRUE)

st_write(summer5.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer5.shp", delete_layer=TRUE)

st_write(summer6.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer6.shp", delete_layer=TRUE)

st_write(summer7.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer7.shp", delete_layer=TRUE)

st_write(summer8.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer8.shp", delete_layer=TRUE)

st_write(summer9.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer9.shp", delete_layer=TRUE)

st_write(summer10.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer10.shp", delete_layer=TRUE)

st_write(summer11.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer11.shp", delete_layer=TRUE)

st_write(summer12.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer12.shp", delete_layer=TRUE)

st_write(summer13.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer13.shp", delete_layer=TRUE)


```

st_write(summer1, dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\fire_ignitions_veg_climate_ALL_5x.shp", delete_layer=TRUE)




```{r}
str(summer1.sf)
str(summer2.sf)

summer.moasic<-raster::mosaic(summer1.sf, summer1.sf, fun=mean)
```


```{r}
#The code below crashed R. Need a different solution.
summer_bind<-bind(summer1.sf, summer2.sf)

test2 <- gDifference(summer1.sf, summer2.sf)
plot(test2)
plot(test2, add = T, col = 'red')


summer_union<-st_union(summer1.sf, summer2.sf)
summer_union<-st_union(summer_union, summer3.sf)
summer_union<-st_union(summer_union, summer4.sf)
summer_union<-st_union(summer_union, summer5.sf)
summer_union<-st_union(summer_union, summer6.sf)
summer_union<-st_union(summer_union, summer7.sf)
summer_union<-st_union(summer_union, summer8.sf)
summer_union<-st_union(summer_union, summer9.sf)
summer_union<-st_union(summer_union, summer10.sf)
summer_union<-st_union(summer_union, summer11.sf)
summer_union<-st_union(summer_union, summer12.sf)
summer_union<-st_union(summer_union, summer13.sf)


summer_union<-union(summer1.sf, summer2.sf)
summer_union<-union(summer_union, summer3.sf)
summer_union<-union(summer_union, summer4.sf)
summer_union<-union(summer_union, summer5.sf)
summer_union<-union(summer_union, summer6.sf)
summer_union<-union(summer_union, summer7.sf)
summer_union<-union(summer_union, summer8.sf)
summer_union<-union(summer_union, summer9.sf)
summer_union<-union(summer_union, summer10.sf)
summer_union<-union(summer_union, summer11.sf)
summer_union<-union(summer_union, summer12.sf)
summer_union<-union(summer_union, summer13.sf)

str(summer_union)


ggplot() +
  geom_sf(data=summer_union, col='green')

```

