---
title: "STSM-Castor comparison: oldest stands first, even flow harvest, no blocking, no roads."
author: "Tyler Muhly"
date: "06 January 2023"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2023 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview
This scenario was developed to compare the basic STSM-SELES timber supply model to the Castor timber supply model. Both of these models are deterministic, spatial, simulation models. The same datasets and parameters were used in each model to assess whether they determine similar spatial timber supply outcomes. 

# Scenario
This is scenario where treplicates the 'sustainble' even flow over a 200 year period where the growing stock does not decline after 100 years. The harvest priority queue is 'oldest first' and no constraints, blocking or roading is implemented in the model. 

 

# Parameters 
## Zone Constraints
None

## 'harvestPriority' parameter 
oldest first 

## 'harvestFlow'

## adjacencyConstraint
None

## Simulation Model

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/chilcotin"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCastor"))
times <- list(start = 0, end = 20) # 10 year interval; 200 years = 20 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataCastor = list (dbName='castor',
                     saveCastorDB = FALSE,
                     sqlite_dbname = "ftnelson_stsmcompare_noroads_noblocks",
                     useCastorDB = paste0(here::here(), "/R/scenarios/comparison_ft_nelson/ftnelson_stsmcompare_noroads_noblocks_castordb.sqlite"),
                     nameBoundaryFile = "fort_nelson_tsa.bounds_fort_nelson_tsa", 
                     nameBoundaryColumn = "tsa_name", 
                     nameBoundary = "Fort_Nelson_TSA", 
                     nameBoundaryGeom = 'wkb_geometry',
                     nameCompartmentRaster = "fort_nelson_tsa.rast_bounds_fort_nelson_tsa", 
                     nameCompartmentTable = "fort_nelson_tsa.vat_bounds_fort_nelson_tsa", 
                     nameMaskHarvestLandbaseRaster = 'fort_nelson_tsa.rast_thlb', 
                     nameZoneTable = "fort_nelson_tsa.constraints", 
                     # natural and managed stands yield curves are the same    
                     nameYieldsRaster = "fort_nelson_tsa.rast_ycid_fort_nelson_tsa", 
                     nameYieldTable = "fort_nelson_tsa.yc_table", # fort_nelson_tsa.yc_table
                     nameYieldsTransitionRaster = "fort_nelson_tsa.rast_ycid_fort_nelson_tsa", 
                     nameYieldTransitionTable = "fort_nelson_tsa.yc_table", 
                     nameForestInventoryRaster = "fort_nelson_tsa.rast_vri_id_fort_nelson_tsa", 
                     nameForestInventoryKey = "vri_fid", # unique id of each polygon 
                     nameForestInventoryTable = "fort_nelson_tsa.vri_fort_nelson_tsa",
                     nameForestInventoryAge = "proj_age_1",  
                     nameForestInventoryHeight = "proj_ht_1",
                     nameForestInventoryCrownClosure = "cr_closure",                             
                     nameForestInventoryTreed = "bclcs_lv_2",
                     nameForestInventorySiteIndex = "site_index"     
                     ),
  forestryCastor = list(harvestBlockPriority = " age DESC ", 
                        #harvestZonePriority = "age DESC",
                        #harvestZonePriorityInterval = 1,
                        #adjacencyConstraint = 0,
                        #activeZoneConstraint = c ("fort_nelson_tsa.rast_oldgrw_prod")
                        reportHarvestConstraints = T
                        ),
  blockingCastor = list(blockMethod = 'pre', 
                        patchZone = 'default',
                        patchVariation = 6),
  growingStockCastor = list (periodLength = 10),
  uploadCastor = list(aoiName = 'ftnelson_stsm_compare',
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL")))
  )

modules <- list("dataCastor", 
                "growingStockCastor", 
                "forestryCastor", 
                "blockingCastor",
                "uploadCastor"
                )

scenario = data.table (name = "oldest_stsm_sustain_noroads_noblocks_",
                       description = "Priority queue = oldest first. Adjacency constraint = None. No roads or blocks. Maximum live harvest flow: 2,450,000 m3/year, which assumes growing stock is non-declining after 100 years, replicating the SELES-STSM run. Minimum harvest age = 50")


harvestFlow <- rbindlist(list(data.table(compartment ="Fort_Nelson_TSA",
                                     partition = ' age > 50 ', 
                                     period = rep( seq (from = 1,
                                                      to = 20, 
                                                      by = 1),
                                                1), 
                                     flow = 24500000, # 2,450,000m3/year 
                                     partition_type = 'live') 
))



objects <- list(harvestFlow = harvestFlow, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvivalReport",
                                             "disturbanceReport",
                                             "volumebyareaReport",
                                             "tableGrizzSurvivalReport",
                                             "tableAbundanceReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithm

The general algorithm (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

