---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Central Group Scenarios
Here we use forestryCLUS to assess the potential impact of a hypotehtical large land use order on timber supply in multiple timber suppyl areas and tree farm licenses 


business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat; these were completed for each specific TSA and TFL independently; applied here as the target



#  Parameters 
BAU = beo, vqo, wha, uwr, fsw (fisheries sensitive watersheds), parks and protected areas (nharv) and cw (community watersheds) 

In addtion to BAU :

An anthropogenic clearing is considered to contribute forage for moose if the area has two of the following attributes: 
o	clearings with a conifer stand density less than 1800 sph for pine leading stands and 1200 sph for spruce leading stands, or 
o	clearings less than 25 years old, or 
o	clearings with an average stand height under 2.5 meters.

=  "rast.zone_cond_central_group_luo"



```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Mackenzie_SW_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zone;") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones

#STEP 3: Update the constraints available to a zone as specified in the scenario
dbExecute(clusdb, "UPDATE zoneconstraints set percentage = 85 where reference_zone = 'rast.zone_cond_partnership_agreement' and percentage = 65")
#This example will set the zones in the partnership agreement that have constraints on the variable 'dist' to a 85% disturbance threshold

dbExecute(clusdb, "UPDATE zoneconstraints set type = 'nh' where reference_zone = 'rast.zone_cond_partnership_agreement'") #This example will set all the zones in the partnership agreement to no harvest


#STEP 4: Remove the connection to the database
dbDisconnect(clusdb)
```

## 'harvestPriority' parameter 
- I used oldest first for consistency across units

- no discussion of this in MacKenzie PDP or determination that I could find

## 'harvestFlow'
these determined dependently in TSA specific forestryCLUS

 MacKenzie:
 MacKenzie SW:
 Prince George: 6,000,000m3/yr
 Dawson Creek:
 TFL 48
 



# Scenarios for Main Portion of TSA 
```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( 
                           dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/MacKenzie_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = c ("MacKenzie_TSA", "MacKenzie_SW_TSA", "Dawson_Creek_TSA", 
                                             "Prince_George_TSA", "TFL48"),
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_cw",
                                           
                                          # "rast.zone_cond_noharvest_moberly_crithab_or_herd",
                                          # "rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_graham_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_wolverine_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_chase_crithab_or_herd"
                                          
                                           # "rast.zone_cond_eccc_moberly_crithab_or_herd",
                                           # "rast.zone_cond_eccc_kennedy_siding_crithab_or_herd",
                                           # "rast.zone_cond_eccc_gataga_crithab_or_herd"
                                          
                                           #  "rast.zone_cond_partnership_agreement"
                                          
                                           "rast.central_grp_proposed_luo_matrix"
                                             ),
                           nameZoneTable = "zone_constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriority = 1,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'central_group', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "mackenzie_bau",
#                        description = "Business-as-usual case; sustainable flow = 1.7 M m3/yr .Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_centgrp_nh",
#                        description = "No harvest in all central group critical habitat (Moberly and Kennedy Siding). Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_centgrp_ch_hele0d_m15d",
#                        description = "No harvest in Central group high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central group matrix critical habitat (Moberly and Kennedy Siding). Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_centgrp_pa_ch_a2b2b3_0d_a1b1b4b5_15d",
#                        description = "No harvest in Central group partnership agreement areas A2, B2, and B3, maximum 35% buffered disturbance (15% harvest) in  Central group partnership agreement areas A1, B1, B4 and B5. Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_centgrp_pa_nh",
#                        description = "No harvest in all central group partnership agreement areas. Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_all_nh",
#                        description = "No harvest in all critical habitat of all herds that overlap with the unit. Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_all_ch_hele0d_m15d",
#                        description = "No harvest in high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit. Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_all_sm_herdbounds_nh",
#                        description = "No harvest in all southern mountain herds that overlap with the harvest unit. Adjacency was set to 3m.")
# scenario = data.table (name = "mackenzie_wct_nh",
#                        description = "No harvest in Wolverine, Chase and Takla herds that overlap with the harvest unit. Adjacency was set to 3m.")
scenario = data.table (name = "mackenzie_luo_35p_25yo",
                       description = "Central group proposed land use order. Maximum 35% less than 25 years old.")



harvestFlow <- rbindlist(list(data.table(compartment ="MacKenzie_TSA",
                                     partition = ' vol > 150 ', # from 2014 determination
                                     year = rep( seq (from = 2018, # run the 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 8500000) #1,700,000m3/yr
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Scenarios for SW Portion of the TSA 

mackenzie_bau: Business-as-usual case; sustainable flow = 1.7 M m3/yr + 0.5 M m3 in SW portion.Adjacency was set to 3m.

mackenzie_wct_nh:No harvest in Wolverine, Chase and Takla herds that overlap with the harvest unit (e.g., TSA or TFL)

mackenzie_all_nh: No harvest in all critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL)

----No different than BAU but added anyways
mackenzie_centgrp_nh : No harvest in all central group critical habitat

mackenzie_centgrp_ch_hele0d_m15d: No harvest in Central group high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central group matrix critical habitat

mackenzie_centgrp_pa_ch_a2b2b3_0d_a1b1b4b5_15d:No harvest in Central group partnership agreement areas A2, B2, and B3, maximum 35% buffered disturbance (15% harvest) in  Central group partnership agreement areas A1, B1, B4 and B5

mackenzie_centgrp_pa_nh: No harvest in all central group partnership agreement areas


mackenzie_all_ch_hele0d_m15d:No harvest in high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL)

mackenzie_all_sm_herdbounds_nh:No harvest in all southern mountain herds that overlap with the harvest unit (e.g., TSA or TFL). Wolverine, Moberly and scott are sm - northern /central group

"rast.zone_cond_eccc_moberly_crithab_or_herd",
"rast.zone_cond_eccc_scott_crithab_or_herd",
"rast.zone_cond_eccc_wolverine_crithab_or_herd"


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( 
                           dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/MacKenzie_SW_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "MacKenzie_SW_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_noharvest_moberly_crithab_or_herd",
"rast.zone_cond_noharvest_scott_crithab_or_herd",
"rast.zone_cond_noharvest_wolverine_crithab_or_herd"
                                              
                                               ),
                           nameZoneTable = "zone_constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestPriority = "dist, age DESC, vol DESC",
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval = 5, 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'mackenzie_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

scenario = data.table (name = "mackenzie_all_sm_herdbounds_nh",
                       description = "No harvest in all southern mountain herds that overlap with the harvest unit (e.g., TSA or TFL). Wolverine, Moberly and scott are sm - northern /central group")

harvestFlow <- rbindlist(list(data.table(compartment ="MacKenzie_SW_TSA",
                                     partition = ' vol > 150 ', # from 2014 determination
                                     year = rep( seq (from = 2018, # run the 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 2500000) #500,000m3/yr
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

