---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Golden TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Central Selkirks caribou critical habtiat; to support Central Selkirks herd planning, we run a sceanrio with no harvest in the  Central Selkirks HEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Central Selkirks only, assuming other herds unprotected

"ECCC" in Central Selkirks caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Central Selkirks only

No harvest in all Columbia North, Columbia South and Frisbee/Boulder critical habitat caribou critical habtiat; to support Columbia/Frisbee herd planning, we run a sceanrio with no harvest in the Columbia/Frisbee HEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Columbia/Frisbee only, assuming other herds unprotected

"ECCC" in Columbia North, Columbia South and Frisbee/Boulder caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Columbia/Frisbee only

no harvest in caribou critical habtait areas; where there is cirtical habitat, no harvest in any types (including matrix); establishes the 'maximum impact' that protection of caribou habitat might potentially have on forest harvest; in Golden these include Central Rockies HEWSR, Central Rockies Matrix, Columbia North HEWSR, Columbia North Matrix, Columbia South Matrix, Columbia South HEWSR, Central Selkirks HEWSR, Central Selkirks Matrix

'ECCC' in caribou critical habtait areas; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low eleavtion cirtcial habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected

# Golden TSA Parameters 

## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in all herds = rast.zone_cond_noharvest_central_rockies_crithab_or_herd,
                          rast.zone_cond_noharvest_columbia_north_crithab_or_herd,
                          rast.zone_cond_noharvest_columbia_south_crithab_or_herd,
                          rast.zone_cond_noharvest_central_selkirks_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_central_rockies_crithab_or_herd,
                    rast.zone_cond_eccc_columbia_north_crithab_or_herd,
                    rast.zone_cond_eccc_columbia_south_crithab_or_herd,
                    rast.zone_cond_eccc_central_selkirks_crithab_or_herd

No harvest in Central Selkirks = rast.zone_cond_noharvest_central_selkirks_crithab_or_herd

ECCC Central Selkirks = rast.zone_cond_eccc_central_selkirks_crithab_or_herd

No harvest in Columbia North, Columbia South and Frisbee/Boulder = rast.zone_cond_noharvest_columbia_north_crithab_or_herd,
rast.zone_cond_noharvest_columbia_south_crithab_or_herd

ECCC in Columbia North, Columbia South and Frisbee/Boulder = rast.zone_cond_eccc_columbia_north_crithab_or_herd,
                                                             rast.zone_cond_eccc_columbia_south_crithab_or_herd

## 'harvestPriority' parameter 
- used oldest first

- as alternative,  could focus on minimizing 'disturbance' for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' prioritize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

## 'harvestFlow'
from 2010 analysis report:  maximum even flow harvest was 513,000m^3^/year; from determination, June 3, 2010, the  AAC was set at 485 000 cubic meters 

- First, I tested a harvest flow of 450,000m^3^/year (2,250,000m^3^/5-year); 500,000, 475,000, 465,000


- stable harvest flow at 465,000m^3^/year 

From 2016 analysis report, used a minimum harvest age to achieve 95% of the stands maximum mean annual increment; never declared what this age was

- I used 150 m3/ha as minimum harvest volume instead

For cutblock adjacency, I used 3 m adjacency; no real mention fo this in analysis report; used 'green-up' targets at coarser scales

## Modify Constraints

```{r, zone_update}
library (DBI)
# STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Golden_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

# STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_du9_scenarios'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones


# CENTRAL ROCKIES Update the constraints available to a zone as specified in the scenario
#Below will set Central Rockies old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 19) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 62) OR (zoneid = 64) OR (zoneid = 65)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 2) OR (zoneid = 17) OR (zoneid = 32) OR (zoneid = 46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 61") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 61")
#Below will set Central Rockies old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 19) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 62) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 32) OR (zoneid = 46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 2) OR (zoneid = 17)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 61") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 61")


# COLUMBIA SOUTH 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 5) OR (zoneid = 20) OR (zoneid = 35) OR (zoneid = 49)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 2) OR (zoneid = 4) OR (zoneid = 17) OR (zoneid = 19) OR (zoneid = 32) OR (zoneid = 34) OR (zoneid = 61) OR (zoneid = 62) OR (zoneid = 64)") 
#Below will set Columbia South old and recruit as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 5) OR (zoneid = 20)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 2) OR (zoneid = 4) OR (zoneid = 17) OR (zoneid = 19) OR (zoneid = 32) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 49) OR (zoneid = 61) OR (zoneid = 62) OR (zoneid = 64)") 


# CENTRAL SELKIRKS
# NO old forest, recruit forest or buffer core habitat in the TSA
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 62") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 62")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 2) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 17) OR (zoneid = 19) OR (zoneid = 32) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 61)  OR (zoneid = 64)  OR (zoneid = 65)") 


dbDisconnect(clusdb)
```



```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list (  dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Golden_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Golden_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_cw",
                              # "rast.zone_cond_eccc_central_rockies_crithab_or_herd"
                              # "rast.zone_cond_eccc_columbia_north_crithab_or_herd"
                              # "rast.zone_cond_eccc_columbia_south_crithab_or_herd"
                              # "rast.zone_cond_eccc_central_selkirks_crithab_or_herd"
                              # "rast.zone_cond_noharvest_central_rockies_crithab_or_herd"
                              # " rast.zone_cond_noharvest_columbia_north_crithab_or_herd"
                              # "rast.zone_cond_noharvest_columbia_south_crithab_or_herd"
                              # "rast.zone_cond_noharvest_central_selkirks_crithab_or_herd"
                               "rast.zone_du9_scenarios"
                                               ),
                           nameZoneTable = "zone_constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriority = 1,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'golden_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "golden_bau",
#                        description = "Business-as-usual case. Harvest flow = 465,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_columbia_north_nh",
#                         description = "No harvest in Columbia North critical habitat. Harvest flow = 465,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_central_rockies_nh",
#                        description = "No harvest in Central Rockies critical habitat. Harvest flow = 465,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_central_rockies_ch_he0d_m15d",
#                        description = "No harvest in Central Rockies high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central Rockies matrix critical habitat in the TSA. Harvest flow = 465,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_central_rockies_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered Central Rockies core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Central Rockies matrix habitat areas. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_central_rockies_scen3b",
#                        description = "No harvest in old forest and recruitment forest Central Rockies core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Central Rockies matrix habitat areas. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_columbia_south_nh",
#                        description = "No harvest in Columbia South critical habitat. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_columbia_south_ch_he0d_m15d",
#                        description = "No harvest in Columbia South high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia South matrix critical habitat in the TSA. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_columbia_south_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered Columbia South core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Columbia South matrix habitat areas. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_columbia_south_scen3b",
#                        description = "No harvest in old forest and recruitment forest Columbia South core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Columbia South matrix habitat areas. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_centselk_nh",
#                        description = "No harvest in Central Selkirks critical habitat. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "golden_centselk_ch_he0d_m15d",
#                        description = "No harvest in Central Selkirks high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central Selkirks matrix critical habitat. Harvest flow = 465,000m^3^/year.  Adjacency = 3m. Oldest first.")

scenario = data.table (name = "golden_centselk_scen3a3b",
                       description = "No old forest, recruitment forest or buffered core critical habitat areas, as defined by Bevan Ernst, in the Golden TSA; maximum 35% buffered disturbance (unbuffered) in Central Selkirks matrix habitat areas. Harvest flow = 465,000m^3^/year. Adjacency = 3m. Oldest first.")





# scenario = data.table (name = "golden_colnsfb_nh",
#                        description = "No harvest in all Columbia North, Columbia South and Frisbee/Boulder critical habitat in the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_colnsfb_ch_he0d_m15d",
#                        description = "No harvest in CN, CS, FB high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in CN, CS, FB matrix critical habitat in the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_all_nh",
#                        description = "No harvest in all critical habitat of all herds that overlap with the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_all_ch_he0d_m15d",
#                        description = "No harvest in high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap the TSA. Adjacency was set to 3m.")



# scenario = data.table (name = "golden_columbia_north_ch_he0d_m15d",
#                        description = "No harvest in Columbia North high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia North matrix critical habitat in the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_columbia_north_nh",
#                        description = "No harvest in Columbia North critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_columbia_north_ch_he0d_m15d",
#                        description = "No harvest in Columbia North high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia North matrix critical habitat in the TSA. Adjacency was set to 3m.")

# scenario = data.table (name = "golden_central_selkirks_nh",
#                        description = "No harvest in Central Selkirks critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_central_selkirks_ch_he0d_m15d",
#                        description = "No harvest in Central Selkirks high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central Selkirks matrix critical habitat in the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_columbia_south_ch_he10d_m15d",
#                        description = "No harvest in Columbia South high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Columbia South matrix habitat areas as defined by Bevan Ernst. Adjacency was set to 3m.")
# scenario = data.table (name = "golden_columbia_north_ch_he10d_m15d",
#                        description = "No harvest in Columbia North high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Columbia North matrix habitat areas as defined by Bevan Ernst. Adjacency was set to 3m.")

harvestFlow <- rbindlist(list(data.table(compartment ="Golden_TSA",
                                         partition = ' vol > 150 ', 
                                         year = rep(seq (from = 2018, 
                                                         to = 2218, 
                                                         by = 5),
                                                    1), 
                                         flow = 2325000) # 465,000m^3^/year
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

