---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Chilcotin Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat


# Parameters 
## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 




## 'harvestPriority' parameter 


## 'harvestFlow'






#UPDATE SCENARIO

## Chilcotin Planning Scenarios Aug. 2021
```{r, zone_update}
require (DBI)
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite")) # connect to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_wha_2021'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones rast.zone_cond_noharvest_barkerville_crithab_or_herd
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab'")  # rast.zone_cond_noharvest_barkerville_crithab_or_herd
# rast.zone_cond_bc_itcha_ilgachuz_crithab  rast.zone_cond_bc_tweedsmuir_crithab    rast.zone_du7_scenario_20210330 rast.zone_wha_2021  


# Chilcotin Scenarios - Aug. 2021
## Existing caribou WHA GARs removed; forest age constraints applied to critical habitat
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' WHERE reference_zone = 'rast.zone_wha_2021' AND (zoneid = 263) OR (zoneid = 264) OR (zoneid = 3779) OR (zoneid = 3780) OR (zoneid = 3781)") 


dbDisconnect(clusdb)
```



## Simulation Model

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( dbName='clus',
                         save_clusdb = TRUE,
                         useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite"),
                         nameBoundaryFile="study_area_chilcotin",
                         nameBoundaryColumn = "tsa_name",
                         nameBoundary = c ('Quesnel_TSA_Matrix', 'Quesnel_TSA_HEWSR', 'Quesnel_TSA_LESR',
                                           'Quesnel_TSA_LEWR', 'Quesnel_TSA_out', 'Williams_Lake_TSA_HEWSR',
                                           'Williams_Lake_TSA_LESR', 'Williams_Lake_TSA_LEWR', 'Williams_Lake_TSA_Matrix',
                                           'Williams_Lake_TSA_out'),
                         nameBoundaryGeom = 'wkb_geometry',
                         nameCompartmentRaster = "rast.study_area_chilcotin",
                         nameCompartmentTable = "vat.study_area_chilcotin",
                         nameMaskHarvestLandbaseRaster='rast.thlb_2020_chilcotin',  
                         nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw"
                                           
                                           # "rast.zone_cond_noharvest_barkerville_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_charlotte_alplands_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_itcha_ilgachuz_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_narrow_lake_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_north_cariboo_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_rainbows_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_wells_gray_north_crithab_or_herd",
                                           # 
                                           # "rast.zone_cond_eccc_barkerville_crithab_or_herd",
                                           # "rast.zone_cond_eccc_charlotte_alplands_crithab_or_herd",
                                           # "rast.zone_cond_eccc_itcha_ilgachuz_crithab_or_herd",
                                           # "rast.zone_cond_eccc_narrow_lake_crithab_or_herd",
                                           # "rast.zone_cond_eccc_north_cariboo_crithab_or_herd",
                                           # "rast.zone_cond_eccc_rainbows_crithab_or_herd",
                                           # "rast.zone_cond_eccc_tweedsmuir_crithab_or_herd",
                                           # "rast.zone_cond_eccc_wells_gray_north_crithab_or_herd",
                                           # 
                                           # "rast.zone_cond_bc_barkerville_crithab",
                                           # "rast.zone_cond_bc_charlotte_alplands_crithab",
                                           # "rast.zone_cond_bc_itcha_ilgachuz_crithab",
                                           # "rast.zone_cond_bc_narrow_lake_crithab",
                                           # "rast.zone_cond_bc_north_cariboo_crithab",
                                           # "rast.zone_cond_bc_rainbows_crithab",
                                           # "rast.zone_cond_bc_tweedsmuir_crithab",
                                           # "rast.zone_cond_bc_wells_gray_north_crithab", 
                                           # 
                                           # "rast.zone_barkerville_groundhog_zones_20210303",
                                           # "rast.zone_smc_zones_20210315"
                                           ),
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "CASE WHEN dist < 1000 THEN 3 WHEN dist < 2500 THEN 2 WHEN dist < 5000 THEN 1 ELSE 0 END DESC, age DESC", # query to prioritize blocks within 1km of disturbance, then 2.5km, then 5km, then everythign >5km, then oldest first after that
                      # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      reportHarvestConstraints = T,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance)
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  smcaribouAbundanceCLUS = list (nameRasSMCHerd = "rast.smc_herd_habitat", 
                                  tableSMCCoeffs = "vat.smc_coeffs"),
  uploaderCLUS = list(aoiName = 'chilcotin_caribou_plan', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "smcaribouAbundanceCLUS",
                "uploaderCLUS"
                )




# scenario = data.table (name = "quesnel_bau",
#                        description = "Business as usual (BAU). Adjacency = 3m. Oldest first. Even harvest flow = 1,900,000m3/year")



harvestFlow <- rbindlist(list(data.table(compartment ="Quesnel_TSA",
                                     partition = ' vol > 150 ', 
                                     year = rep( seq (from = 2018, 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 9250000)
                                    # 9500000 // 1,900,000 m3/yr for oldest first
                                    # 8000000 // 1,600,000 m3/yr for closest dist 1st
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

'Quesnel_TSA_Matrix', 'Quesnel_TSA_HEWSR', 'Quesnel_TSA_LESR',
                                           'Quesnel_TSA_LEWR', 'Quesnel_TSA_out', 'Williams_Lake_TSA_HEWSR',
                                           'Williams_Lake_TSA_LESR', 'Williams_Lake_TSA_LEWR', 'Williams_Lake_TSA_Matrix',
                                           'Williams_Lake_TSA_out'



patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithm

The general algorithm (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

