---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Dawson Creek TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

DU7 (Northern group) specific scenarios developed by caribou recovery science team. These were done for each groups of herds that overlaps the TSA. For Morice TSA, this included Tweedsmuir (group 1).

First set of scenarios uses rast.zone_du7_scenario_20210305; this raster defines priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. Scenarios:
* 3a = No harvest in old forest, recruitment forest and buffered high elevation core and low elevation summer critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance (unbuffered) in low elevation winter and matrix habitat areas

# Fort St John TSA Parameters 

## New Caribou Constraints
BAU = beo, vqo, wha, uwr, fsw (fisheries senstive watersheds),parks and protected areas (nharv) and cw (community watersheds) 


DU7 - Northern group priority forest stand areas = "rast.zone_du7_scenario_20210305"

## 'harvestPriority' parameter 
- used oldest first; in TSR model base case used highest volume first, but they also tested oldest first, which harvested more of the THLB adn achieved higher harvest levels

- as alternative,  could focus on minimizing 'disturbance' for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' prioritize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)
      
- Minimum harvest criteria: 140 m3/ha (same as TSR base case) 


## 'harvestFlow'
The allowable annual cut (AAC) is 2,115,000 cubic metres, as of May 10, 2018. The TSA is partitioned with 1,200,000 cubic metres attributable to coniferous-leading stands of which at 672,000 cubic metres annually may be taken from the 'core' area. Deciduous species may be harvested up to 915,000 cubic metres, of which 512,000 cubic metres  may be taken from the 'core'.

- harvest flow for outside core: first tried 1,250,000 m^3^/yr; 1.5M; 2 M; 1.75M; 1.65M; 1.6M; 1.55M - final

## Modify Zones


```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Fort_St_John_TSA_clusdb.sqlite")) #  Fort_St_John_Core_TSA_clusdb.sqlite  Fort_St_John_TSA_clusdb.sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneconstraints where reference_zone = 'rast.boreal_caribou_zones_2019'") 


# NORTHERN GROUP - Graham
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_graham_crithab' AND (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_graham_crithab' AND (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_graham_crithab' AND (zoneid = 3)") 
# Below makes priority forest stands no harvest and all of the matrix and LEWR habitat areas max 15% disturbance; NOTE all zones high priority
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 13) OR (zoneid = 14) OR (zoneid = 16) OR (zoneid = 17) OR (zoneid = 19) OR (zoneid = 20) OR (zoneid = 22) OR (zoneid = 23) OR (zoneid = 24)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25) OR (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25) OR (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25) OR (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25) OR (zoneid = 26)") 
# Below makes priority forest stands in high  priority zones no harvest and high  priority zones of the matrix and LEWR habitat areas max 15% disturbance; low priority zones available to harvest; no medium priority zones in this unit
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 14) OR (zoneid = 17) OR (zoneid = 20) OR (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 13) OR (zoneid = 16)  OR (zoneid = 19)  OR (zoneid = 22) OR (zoneid = 23) OR (zoneid = 24)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 



#STEP 4: Remove the connection to the database
dbDisconnect(clusdb)
```


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( 
                           dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Fort_St_John_TSA_clusdb.sqlite"), 
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Fort_St_John_TSA", # "Fort_St_John_Core_TSA"  Fort_St_John_TSA
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_cw",
                                               
                                             # "rast.zone_cond_noharvest_graham_crithab_or_herd"  
                                             # "rast.zone_cond_noharvest_pink_mountain_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_chinchaga_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_snake_sahtaneh_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_westside_fort_nelson_crithab_or_herd",
                                             # 
                                             # "rast.zone_cond_eccc_graham_crithab_or_herd",                                                                             "rast.zone_cond_eccc_chinchaga_crithab_or_herd",
                                             # "rast.zone_cond_eccc_pink_mountain_crithab_or_herd",
                                             # "rast.zone_cond_eccc_snake_sahtaneh_crithab_or_herd",
                                             # "rast.zone_cond_eccc_westside_fort_nelson_crithab_or_herd",
                                             # 
                                             # "rast.zone_cond_bc_graham_crithab"
                                             # 
                                             # "rast.zone_du7_scenario_20210330"
                                             
                                             "rast.pink_mtn_habitat",
                                             "rast.fn_aoi_fsj_tsa",
                                             "rast.graham_caribou_core_habitat",
                                             "rast.old_growth_fsj_tsa",
                                             "rast.brfn_areas_fsj",
                                             "rast.boreal_caribou_zones_2019"
                                               ),
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      # reportHarvestConstraints = T
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
    volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  uploaderCLUS = list(aoiName = 'fort_st_john_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# scenario = data.table (name = "fsj_nocore_bau",
#                        description = "Business-as-usual case. Harvest flow = 1,550,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "fsj_nocore_graham_nh",
#                        description = "No harvest in Graham critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow = 1,550,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "fsj_nocore_graham_he0d_mlewr12d",
#                        description = "No harvest in Graham HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 1,550,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "fsj_nocore_graham_hi_med_lo_priority",
#                        description = "No harvest priority stands in all priority zones in Graham HEWSR and LESR critical habitat; harvest allowed in all priority zones in LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest flow = 1,550,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "fsj_nocore_graham_hi_priority",
#                        description = "No harvest priority stands in high priority zones in group 2 Graham) HEWSR and LESR critical habitat; harvest allowed in high priority zones in LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in low priority zones. No medium priority zones in this unit. Harvest flow = 1,550,000m3/yr. Adjacency = 3m. Oldest first.")

scenario = data.table (name = "fsj_nocore_multi_plan",
                       description = "No harvest in multiple planning areas, including: old growth, Chinchaga caribou zones A and B, Pink Mtn caribou core habitat, Graham caribou core habitat, First Nations AOIs, and RSEA/Blueberry River First Nations protection and restoration areas. Harvest flow = 1,550,000m3/yr. Adjacency = 3m. Oldest first.")



harvestFlow <- rbindlist(list(data.table(compartment = "Fort_St_John_TSA", 
                                     partition = ' vol > 139 ', 
                                     year = rep( seq (from = 2018, 
                                                      to = 2222, 
                                                      by = 5),
                                                1), 
                                     flow = 7750000) # 1,550,000
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

