---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# TFL 48 Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Central Group critical habtiat; to support Central Group herd planning, we run a scenario with no harvest in the Central Group HEWSR and Matrix; assesses the potential maximum impact of protecting Central Group only, assuming other herds unprotected

ECCC in Central Group caribou critical habitat; an alterantive to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no harvest in high and low elevation critical habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Central Group only

Partnership Agreement Scenario; BC, West Moberly First Nation, Saulteau First Nation and Canada have an agreement to protect certain areas in the central group; No harvest in Central group partnership agreement areas A2, B2, and B3, maximum 35%  disturbance (15%) harvest in  Central group partnership agreement areas A1, B1, B4 and B5.

No harvest in all Partnership Agreement areas; this scenario assesses the potential maximum impact of protecting all the partnership agreement areas, assuming other herds unprotected

No harvest in all caribou critical habitat areas (Quintette, Burnt Pine, Moberly, Graham)

ECCC in all caribou critical habitat area (Quintette, Burnt Pine, Moberly, Graham); no harvest in high and low elevation critical habitat, and up to 35% disturabnce in matrix habtiat;


# TFL 48 Parameters 

## New Caribou Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in Central Group = rast.zone_cond_noharvest_quintette_crithab_or_herd,
                              rast.zone_cond_noharvest_burnt_pine_crithab_or_herd,
                              rast.zone_cond_noharvest_moberly_crithab_or_herd,
                              rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd

ECCC - No harvest in Central Group high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) matrix critical habitat = rast.zone_cond_eccc_quintette_crithab_or_herd,
                           rast.zone_cond_eccc_burnt_pine_crithab_or_herd,
                           rast.zone_cond_eccc_moberly_crithab_or_herd,
                           rast.zone_cond_eccc_kennedy_siding_crithab_or_herd


Parntership Agreement = rast.zone_cond_partnership_agreement

Parntership Agreement - ho harvest = rast.zone_cond_partnership_agreement (but change constraint to no harvest 'nh')


No harvest in all herds = rast.zone_cond_noharvest_quintette_crithab_or_herd,
                          rast.zone_cond_noharvest_burnt_pine_crithab_or_herd,
                          rast.zone_cond_noharvest_moberly_crithab_or_herd,
                          rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd,
                          rast.zone_cond_noharvest_graham_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_quintette_crithab_or_herd,
                     rast.zone_cond_eccc_burnt_pine_crithab_or_herd,
                     rast.zone_cond_eccc_moberly_crithab_or_herd,
                     rast.zone_cond_eccc_kennedy_siding_crithab_or_herd,
                     rast.zone_cond_eccc_graham_crithab_or_herd

## 'harvestPriority' parameter 
- focus on minimizzing 'disturabnce; for cariobu, then older, higher vlomue stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)
      
## 'harvestFlow'
from 2015 determination: base case started at 1,731,000m^3^/year for 5 years, followed by 838,000m^3^/year for 5 years, followed by 779,000m^3^/year for the next ten years 763,000m^3^/year for the next 30 years and 808,000m^3^/year in the long term; AAC was set at 1,550,000m^3^/year for the first five years and 871,000m^3^/year for the second five years  
- First, I tested a harvest flow of 1,000,000m^3^/year (5,000,000m^3^/5-year); way too high, dropped to 500,000m^3^/year, 400,000, 300,000, 350,000, 325,000, 335,000; drop off at the last interval, but used 335,000 


- I used 150 m3/ha as minimum harvest volume; nothing in determination on this

- I used 3 m adjacency; nothing in determination on this


## Partnership agreement
There is a Partnership Agreement for these caribou herds that has designated zones and constraints for those zones. These can be modified using the code below.

```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/TFL48_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneconstraints where reference_zone = 'rast.zone_cond_partnership_agreement'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones

#STEP 3: Update the constraints available to a zone as specified in the scenario
dbExecute(clusdb, "UPDATE zoneconstraints set type = 'nh' where reference_zone = 'rast.zone_cond_partnership_agreement'") #This example will set all the zones in the partnership agreement to no harvest

dbExecute(clusdb, "UPDATE zoneconstraints set percentage = 85 where reference_zone = 'rast.zone_cond_partnership_agreement' and percentage = 65")
#This example will set the zones in the partnership agreement that have constraints on the variable 'dist' to a 85% disturbance threshold

#STEP 4: Remove the connection to the database
dbDisconnect(clusdb)
```


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/TFL48_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "TFL48",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_cw", 
                                               
                                               # 'rast.zone_cond_partnership_agreement'
                                               
                                               # "rast.zone_cond_noharvest_quintette_crithab_or_herd",
                                              # "rast.zone_cond_noharvest_burnt_pine_crithab_or_herd",
                                               # "rast.zone_cond_noharvest_moberly_crithab_or_herd",
                                          # "rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd",
                                               # "rast.zone_cond_noharvest_graham_crithab_or_herd"
                                                
                                               # "rast.zone_cond_eccc_quintette_crithab_or_herd",
                                               # "rast.zone_cond_eccc_burnt_pine_crithab_or_herd",
                                               # "rast.zone_cond_eccc_moberly_crithab_or_herd",
                                               # "rast.zone_cond_eccc_kennedy_siding_crithab_or_herd",
                                               # "rast.zone_cond_eccc_graham_crithab_or_herd",
                                               
                                               "rast.central_grp_proposed_luo_matrix"
                                               ),
                           nameZoneTable = "zone_constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestPriority = "dist, age DESC, vol DESC",
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'tfl48', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "tfl48_bau",
#                        description = "Business-as-usual (BAU); harvest flow 335,000 m3/yr. Adjacency was set to 3m.")
# scenario = data.table (name = "tfl48_centgrp_nh",
#                        description = "No harvest in Central group critical habitat; harvest flow 335,000 m3/yr. Adjacency was set to 3m.")
# scenario = data.table (name = "tfl48_centgrp_ch_he0d_m15d",
#                        description = "No harvest in Central group HEWSR critical habitat, 35% buffered disturbance (15% harvest) in matrix critical habitat; harvest flow 335,000 m3/yr. Adjacency was set to 3m.")
# scenario = data.table (name = "tfl48_centgrp_pa_ch_a2b2b3_0d_a1b1b4b5_15d",
#                        description = "No harvest in Central group partnership agreement areas A2, B2, and B3, maximum 35% buffered disturbance (15% havrest) in  Central group partnership agreement areas A1, B1, B4 and B5; harvest flow 335,000 m3/yr. Adjacency was set to 3m.") 
# scenario = data.table (name = "tfl48_centgrp_pa_nh",
#                        description = "No harvest in Central group partnership agreement areas; harvest flow 335,000 m3/yr. Adjacency was set to 3m.")
# scenario = data.table (name = "tfl48_all_nh",
#                        description = "No harvest in all critical habitat of all herds that overlap with the harvest unit; harvest flow 335,000 m3/yr. Adjacency was set to 3m.")
# scenario = data.table (name = "tfl48_all_ch_he0d_m15d",
#                        description = "No harvest in HEWSR, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit; harvest flow 335,000 m3/yr. Adjacency was set to 3m.")
scenario = data.table (name = "tfl48_luo_35p_25yo",
                       description = "Central group proposed land use order. Maximum 35% less than 25 years old.")

harvestFlow <- rbindlist(list(data.table(compartment ="TFL48",
                                         partition = ' vol > 150 ', 
                                         year = rep( seq (from = 2018, 
                                                          to = 2218, 
                                                          by = 5),
                                                    1), 
                                         flow = 1675000) # 335,000m3/yr 
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

