---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Okanagan TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Columbia North and Frisbee/Boulder caribou critical habtiat; to support herd planning, we run a sceanrio with no harvest in the HEWSR and Matrix habitats of these herds; harvest is BAU in other herds; assesses the potential maximum impact of protecting Columbia North and Frisbee/Boulder only, assuming other herds unprotected

"ECCC" in Columbia North and Frisbee/Boulder caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Central Selkirks only

no harvest in caribou critical habtait areas; where there is cirtical habitat, no harvest in any types (including matrix); establishes the 'maximum impact' that protection of caribou habitat might potentially have on forest harvest; in Okanagan these include Columbia North HEWSR, Columbia North Matrix, Monashee Matrix, Monashee HEWSR, Frisby Boulder HEWSR, Frisby Boulder Matrix

'ECCC' in caribou critical habtait areas; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low eleavtion cirtcial habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected

# Okanagan TSA Parameters 

## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in all herds = rast.zone_cond_noharvest_columbia_north_crithab_or_herd,
                          rast.zone_cond_noharvest_frizby_boulder_crithab_or_herd,
                          rast.zone_cond_noharvest_monashee_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_columbia_north_crithab_or_herd,
                          rast.zone_cond_eccc_frizby_boulder_crithab_or_herd,
                          rast.zone_cond_eccc_monashee_crithab_or_herd

No harvest in columbia north and Frisbee/Boulder = rast.zone_cond_noharvest_columbia_north_crithab_or_herd,
                          rast.zone_cond_noharvest_frizby_boulder_crithab_or_herd

ECCC Columbia North and Frisbee/Boulder = rast.zone_cond_eccc_columbia_north_crithab_or_herd,
                          rast.zone_cond_eccc_frizby_boulder_crithab_or_herd rast.zone_cond_eccc_columbia_south_crithab_or_herd

## 'harvestPriority' parameter 
- used oldest first

- as alternative,  could focus on minimizing 'disturbance' for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' prioritize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

## 'harvestFlow'
from 2011 analysis report:  maximum even flow harvest was 2,469,000m^3^/year; from determination, January 1, 2013, the  AAC was set at 3 078 405 cubic meters 

- First, I tested a harvest flow of 2,500,000m^3^/year (12,500,000m^3^/5-year); 2,000,000, 1,750,000, 1,500,000, 1,400,000, 1,450,000

- stable flow at 1,400,000

From the 2011 analysis report, they say that in the future the average age of harvested volume will be 80yrs old so maybe we are restricting the model to wood that is too old. However, the average volume of harvested wood per ha is predicted to be above 250 m^3/ha which is higher than the value we specify in our model. I used 150 m3/ha as minimum harvest volume instead

For cutblock adjacency, I used 3 m adjacncey; no real mention fo this in analysis report; used 'green-up' targets at coarser scales

## Modify Constraints

```{r, zone_update}
library (DBI)
# STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Okanagan_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

# STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_du9_scenarios'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_eccc_columbia_north_crithab_or_herd'")

dbGetQuery(clusdb, "SELECT * from zoneConstraints where reference_zone = 'rast.zone_cond_eccc_frisby_boulder_crithab_or_herd'")
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_frisby_boulder_crithab_or_herd' AND zoneid = 2")

# COLUMBIA NORTH Update the constraints available to a zone as specified in the scenario
# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_eccc_columbia_north_crithab_or_herd' AND zoneid = 1") 

dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_columbia_north_crithab_or_herd' AND zoneid = 1")

#Scen3a
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315'")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid in (46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid in (46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid in (46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid in (43,44,45)") 

# COLUMBIA NORTH Update the constraints available to a zone as specified in the scenario
#Below will set Columbia North old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 19) OR (zoneid = 34) OR (zoneid = 48)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 6) OR  (zoneid = 8) OR (zoneid = 21) OR (zoneid = 23) OR (zoneid = 36) OR (zoneid = 38) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 69)") 
#Below will set Columbia North old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 19)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 6) OR  (zoneid = 8) OR (zoneid = 21) OR (zoneid = 23) OR (zoneid = 34) OR (zoneid = 48) OR (zoneid = 36) OR (zoneid = 38) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 69)") 


# MONASHEE Update the constraints available to a zone as specified in the scenario
#Below will set Monashee old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 8) OR (zoneid = 23) OR (zoneid = 38) OR (zoneid = 52)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 69") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 69")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR  (zoneid = 6) OR (zoneid = 19) OR (zoneid = 21) OR (zoneid = 34) OR (zoneid = 36) OR (zoneid = 64) OR (zoneid = 66) OR (zoneid = 67)") 
#Below will set Monashee old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 8) OR (zoneid = 23)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 69") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 69")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR  (zoneid = 6) OR (zoneid = 19) OR (zoneid = 21) OR (zoneid = 38) OR (zoneid = 52) OR (zoneid = 34) OR (zoneid = 36) OR (zoneid = 64) OR (zoneid = 66) OR (zoneid = 67)") 


# FRISBY-BOULDER Update the constraints available to a zone as specified in the scenario
#Below will set Frisby-Boulder old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 6) OR (zoneid = 21) OR (zoneid = 36) OR (zoneid = 50)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 8) OR (zoneid = 19) OR (zoneid = 23) OR (zoneid = 34) OR (zoneid = 8) OR (zoneid = 38) OR (zoneid = 64) OR (zoneid = 67) OR (zoneid = 69)")
#Below will set Frisby-Boulder old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 6) OR (zoneid = 21)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 8) OR (zoneid = 19) OR (zoneid = 23) OR (zoneid = 34) OR (zoneid = 8) OR (zoneid = 38) OR (zoneid = 64) OR (zoneid = 67) OR (zoneid = 69) OR (zoneid = 36) OR (zoneid = 50)")


#Frisby-boulder
dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_smc_zones_20210315'")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315'")

dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_eccc_monashee_crithab_or_herd'")
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_monashee_crithab_or_herd' and zoneid = 2")

dbDisconnect(clusdb)
```


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = FALSE,
                           sqlite_dbname = "Okanagan_TSA",
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Okanagan_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Okanagan_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.thlb_2020', #'rast.bc_thlb2018' 
                           nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", #"rast.zone_cond_wha"  
                                           "rast.zone_uwr_2021", #"rast.zone_cond_uwr"
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw",
                                            #"rast.zone_cond_noharvest_columbia_north_crithab_or_herd"
                                            #"rast.zone_cond_noharvest_frisby_boulder_crithab_or_herd"
                                            #"rast.zone_cond_noharvest_monashee_crithab_or_herd"
                                            #"rast.zone_cond_eccc_columbia_north_crithab_or_herd"
                                            #"rast.zone_cond_eccc_frisby_boulder_crithab_or_herd"
                                            "rast.zone_cond_eccc_monashee_crithab_or_herd"
                                          # "rast.zone_smc_zones_20210315"
                                           ),
                                            
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      # reportHarvestConstraints = T
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  uploaderCLUS = list(aoiName = 'okanagan_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "volumebyareaReportCLUS",
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

#  scenario = data.table (name = "okanagan_bau",description = "Business as usual (BAU). Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_columbia_north_nh",description = "No harvest in all Columbia North critical habitat. Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_columbia_north_ch_he0d_m12d", description = "No harvest in Columbia North high elevation critical habitat, maximum 12% disturbance in Columbia North matrix critical habitat. Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")
 #scenario = data.table (name = "okanagan_columbia_north_scen3a",description = "No harvest in old forest, recruitment forest and buffered Columbia North core critical habitat areas, as defined by Bevan Ernst, maximum 15% buffered disturbance (unbuffered) in Columbia North matrix habitat areas. Harvest flow = 1,400,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_columbia_north_scen3b", description = "No harvest in old forest and recruitment forest Columbia North core critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance in Columbia North matrix habitat areas. Harvest flow = 1,400,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_monashee_nh", description = "No harvest in all Monashee critical habitat. Harvest flow = 1,400,000m^3^/year.  Adjacency = 3m. Oldest first.")
 scenario = data.table (name = "okanagan_monashee_ch_he0d_m12d", description = "No harvest in Monashee high elevation critical habitat, maximum 12% disturbance in Monashee matrix critical habitat. Harvest flow = 1,400,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_monashee_scen3a",
#                         description = "No harvest in old forest, recruitment forest and buffered Monashee core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Monashee matrix habitat areas. Harvest flow = 1,400,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_monashee_scen3b",
#                        description = "No harvest in old forest and recruitment forest Monashee core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Monashee matrix habitat areas. Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_frisby_boulder_nh", description = "No harvest in all Frisby Boulder critical habitat. Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_frisby_boulder_ch_he0d_m12d", description = "No harvest in Frisby Boulder high elevation critical habitat, maximum 12%  disturbance in Frisby Boulder matrix critical habitat. Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_frisby_boulder_scen3a",description = "No harvest in old forest, recruitment forest and buffered Frisby Boulder core critical habitat areas, as defined by Bevan Ernst, maximum 15%  disturbance (unbuffered) in Frisby Boulder matrix habitat areas. Harvest flow = 1,400,000m^3^/year.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "okanagan_frisby_boulder_scen3b",
#                        description = "No harvest in old forest and recruitment forest Frisby Boulder core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Frisby Boulder matrix habitat areas. Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")

#scenario = data.table (name = "okanagan_columbia_north_he0d",description = "No harvest in Columbia North high elevation critical habitat; harvest allowed in matrix critical habitat. Harvest flow = 1,400,000m^3^/year. Adjacency = 3m. Oldest first.")



# BELOW ARE OLD SCENARIOS THAT NEED TO BE RE-RUN WITH NEW MODEL PARAMS
 # scenario = data.table (name = "okanagan_colnsfb_nh",
 #                        description = "No harvest in all CN, CS and FB critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "okanagan_colnsfb_ch_he0d_m15d",
#                         description = "No harvest in CN, CS and FB high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in CN, CS and FB matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "okanagan_all_nh",
#                         description = "No harvest in all critical habitat of all herds that overlap with the harvest unit.")
# scenario = data.table (name = "okanagan_all_ch_he0d_m15d",
#                         description = "No harvest in high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit.")
# scenario = data.table (name = "okanagan_columbia_north_ch_he10d_m15d",
#                        description = "No harvest in Columbia North high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Columbia North matrix habitat areas as defined by Bevan Ernst. Adjacency was set to 3m.")
# scenario = data.table (name = "okanagan_frisby_boulder_ch_he10d_m15d",
#                        description = "No harvest in Frisby Boulder high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Frisby Boulder matrix habitat areas as defined by Bevan Ernst. Adjacency was set to 3m.")



harvestFlow <- rbindlist(list(data.table(compartment ="Okanagan_TSA",
                                     partition = ' vol > 150 ', 
                                     period = rep( seq (from = 1, # run the 
                                                      to = 40, 
                                                      by = 1),
                                                1), 
                                     flow = 7000000,
                                     partition_type = 'live') # 1,400,000 m3/yr
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

