---
title: "forestryCLUS"
author: "Elizabeth Kleynhans"
date: "10 Aug 2020"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Great Bear Rainforest North TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in caribou critical habtait areas; where there is critical habitat, no harvest in any types (includign matrix); establishes the 'maximum impact' that protection fo cariobu habtait might potentially have on forest harvest; in GRB north this includes Charlotte Alplands

'ECCC' in caribou critical habtait areas; an alterantive to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no harvest in high and low eleavtion cirtcial habtiat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected


# GBR North TSA Parameters 

## New Caribou Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds.
Note: for GBR I created new spatial layers for wha, uwr, fsw, and parks and protecte areas. This is because the original layers were missing some details relevant for GBR.

No harvest in all herds = rast.zone_cond_noharvest_charlotte_alplands_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_charlotte_alplands_crithab_or_herd

## 'harvestPriority' parameter 
- focus on minimizzing 'disturabnce; for cariobu, then older, higher volume stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

## 'harvestFlow'
No information for current harvest flow projects are available for GBR North. However, old information from the data packeges for the North and Midcoast TSA's do have projections for even flow harvests. According to the 2006 Timber Supply Analysis Report for the North Coast TSA an even flow harvest would be ~429,900m^3/yr. For the Mid Coast TSA the even flow harvest rate is ~ 764,000m^3.yr according to the 2010 Timber Supply Review Analysis Report. Thus if we add these two harvest flows together we might expect an even flow harvest rate of 1,193,900 m^3/yr.  However,this I think is too high as since these TSA reports were cretated, quite a few more areas have been designated as no harvest e.g. Grizzly Bear Habitat and some important watersheds. Thus, I decided to start testing the harvest flow at the current AAC (803,000 m^3/yr). This value was too high so I reduced it as follows: 660,000 m^3/yr, 600,000m^3/yr, 580,000

For cutblock adjacency, in data package, allowed maximum 33% height ≤ 2.5 m THLB by landscape unit; I used 3 m adjacncey; thus is a bit conservative

```{r module_usage}
library (SpaDES.core)
library (data.table)
library(dplyr)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # this was originally increased by 5 years and 40 intervals i.e. to get a 200 year simulation
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Great_Bear_Rainforest_North_TSA_clusdb.sqlite"),
                           nameBoundaryFile = "tsa_aac_bounds_gbr",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Great_Bear_Rainforest_North_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary_gbr",
                           nameCompartmentTable = "tsa_aac_bounds_vat_gbr",
                           nameMaskHarvestLandbaseRaster = 'rast.thlb_2020', #'rast.bc_thlb2018' 
                           nameZoneRasters=c(#"rast.zone_cond_beo", # beo might not be correct for GBR. Should probably include harvest constraints
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_cond_wha_gbr", 
                                           "rast.zone_cond_uwr_gbr", 
                                           "rast.zone_cond_nharv_gbr", 
                                           "rast.zone_cond_fsw_gbr", 
                                           "rast.zone_cond_cw",
                                           "rast.zone_cond_mofrl_gbr", # for gbr include this layer instead of beo
 #                                         "rast.zone_cond_noharvest_charlotte_alplands_crithab_or_herd",
 # "rast.zone_cond_noharvest_rainbows_crithab_or_herd",
 # "rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd"
                                           "rast.zone_cond_eccc_charlotte_alplands_crithab_or_herd",
                                           "rast.zone_cond_eccc_rainbows_crithab_or_herd",
                                           "rast.zone_cond_eccc_tweedsmuir_crithab_or_herd"
),

                           nameZoneTable = "zone.constraints_gbr",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp", 
                         nameYieldTable = "yc_vdyp", 
                         nameYieldsTransitionRaster = "rast.tipsy2018_id", 
                         nameYieldTransitionTable = "yc_tipsy", 
                         nameForestInventoryRaster = "rast.vri2019_id", 
                         nameForestInventoryKey = "feature_id", 
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2019", 
                         nameForestInventoryAge = "proj_age_1", 
                         nameForestInventoryHeight = "proj_height_1", 
                         nameForestInventoryCrownClosure = "crown_closure", 
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index" 
                    ),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      # reportHarvestConstraints = T
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, 
                       nameRasCaribouHerd = "rast.caribou_herd", 
                       tableCaribouHerd = "public.caribou_herd_vat"), 
  disturbanceCalcCLUS = list(calculateInterval = 1, # should be 1 if using constraints on 'dist' (disturbance)
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'great_bear_rainforest_north_tsa', # name of the schema that gets uploaded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "gbrn_bau",
#                         description = "Business as usual (bau)")
 # scenario = data.table (name = "gbrn_chil_nh",
 #                        description = "No harvest in Chilcotin herds and habitat that overlap with the harvest unit (e.g., TSA or TFL)")

 scenario = data.table (name = "gbrn_chil_ch_he0d_m15d",
                        description = "No harvest in Chilcotin high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat")

harvestFlow <- rbindlist(list(data.table(compartment ="Great_Bear_Rainforest_North_TSA",
                                     partition = ' vol > 250', # was set at vol > 250 because the Sunshine Coast TSA had a minimum harvest volume per ha set at 250m3 or 300m3 depending on species. See table 19 (pg 28) from the Sunshine Coast TSA TSR Data Package April 2011 report. 

                                     year = rep( seq (from = 2018, 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 

                                     flow = 4800000))) # 1.) try 5000000 did not worked, 2.) 4500 000 worked, 3.) 4 600 000 worked, 4 700 000 worked, 4900000 did not work, 4800000 worked but 4 850 000 did not.


#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "zoneManagement"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

