---
title: "forestryCLUS"
author: "Elizabeth Kleynhans"
date: "23 Nov 2020"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# UBC study area within Great Bear Rainforest North TSA Scenarios
BAU (business as usual) = all the usual constraints i.e. beo, vqo, wha, uwr, nharv, fsw, cw

old growth constraints = as above (beo, vqo, wha, uwr, nharv, fsw, cw) and art (average retention targets, set by the UBC group)


## 'harvestPriority' parameter 
- focus on minimizzing 'disturabnce; for cariobu, then older, higher volume stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

## 'harvestFlow'
No information for current harvest flow projects are available for GBR North. However, old information from the data packeges for the North and Midcoast TSA's do have projections for even flow harvests. According to the 2006 Timber Supply Analysis Report for the North Coast TSA an even flow harvest would be ~429,900m^3/yr. For the Mid Coast TSA the even flow harvest rate is ~ 764,000m^3.yr according to the 2010 Timber Supply Review Analysis Report. Thus if we add these two harvest flows together we might expect an even flow harvest rate of 1,193,900 m^3/yr.  However,this I think is too high as since these TSA reports were cretated, quite a few more areas have been designated as no harvest e.g. Grizzly Bear Habitat and some important watersheds. Thus, I decided to start testing the harvest flow at the current AAC (803,000 m^3/yr). This value was too high so I reduced it as follows: 660,000 m^3/yr, 600,000m^3/yr, 580,000

For cutblock adjacency, in data package, allowed maximum 33% height ≤ 2.5 m THLB by landscape unit; I used 3 m adjacncey; thus is a bit conservative

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 2) # this was originally increased by 5 years and 40 intervals i.e. to get a 200 year simulation
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/UBC_study_boundary_clusdb.sqlite"),
                           nameBoundaryFile="ubc_gbr_boundaries",
                         nameBoundaryColumn="tsa_name",
                         nameBoundary = "UBC_study_boundary",
                         nameBoundaryGeom='wkb_geometry',
                         nameCompartmentRaster = "rast.ubc_gbr_boundaries",
                         nameCompartmentTable = "ubc_gbr_boundaries_vat",
                         nameMaskHarvestLandbaseRaster='rast.bc_thlb2018',
                         nameZoneRasters=c("rast.zone_cond_beo", 
                                           #"rast.zone_cond_vqo", 
                                           "rast.zone_cond_wha_gbr", 
                                           #"rast.zone_cond_uwr_gbr", 
                                           "rast.zone_cond_nharv_gbr", 
                                           "rast.zone_cond_fsw_gbr"
                                           #"rast.zone_cond_cw"
                                           #"rast.zone_cond_art" # average retention targets set by UBC group. These targets likely overlap with beo targets so Ill probably have to remove beo during the forestry clus run.
                                           ),
                        
                         nameZoneTable = "zone_constraints_gbr", 
                        # nameZonePriorityRaster = "rast.zone_cond_beo",
                         nameYieldsRaster = "rast.ycid_vdyp", 
                         nameYieldTable = "yc_vdyp", 
                         nameYieldsTransitionRaster = "rast.tipsy2018_id", 
                         nameYieldTransitionTable = "yc_tipsy", 
                         nameForestInventoryRaster = "rast.vri2019_id", 
                         nameForestInventoryKey = "feature_id", 
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2019", 
                         nameForestInventoryAge = "proj_age_1", 
                         nameForestInventoryHeight = "proj_height_1", 
                         nameForestInventoryCrownClosure = "crown_closure", 
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index" 
                    ),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestPriority = "age DESC, vol DESC",
                      reportHarvestConstraints = TRUE, # this should spit out a report of the zonal constraints in the global environment.
                      adjacencyConstraint = 3), # try tweak adjacencyHeight=3m
  # dont know how good growth and yield is for coast. Look at growing stock now and what it says it is in the TSR. Divide growing stock by 200 to get quick and dirty AAC.
  growingStockCLUS = list (periodLength = 5), # was 5
  # roadCLUS = list(roadMethod = 'pre', 
  #                 nameCostSurfaceRas = 'rast.rd_cost_surface', 
  #                 nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),

   # survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
   #                      nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
   #                      tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  # disturbanceCalcCLUS = list(calculateInterval = 5,
  #                            criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                            criticalHabRaster = "rast.bc_crithab_and_herd",
  #                            permDisturbanceRaster = "rast.mine_ag_wind_rail",
  #                            recovery = 40),
  uploaderCLUS = list(aoiName = 'ubc_gbr_study', # name of schema that gets uploaded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                #"roadCLUS",  
                #"yieldUncertaintyCLUS", 
                #"survivalCLUS", 
                #"disturbanceCalcCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )


#  scenario = data.table (name = "ubc_gbrn_art_only",
#                          description = "removed all constraints except art (average retention targets")
#  
    scenario = data.table (name = "ubc_gbrn_bau",
                            description = "includes all constraints (wha, fsa, and nharv) except art (average retention targets")

  # scenario = data.table (name = "ubc_gbrn_with_art",
  #                         description = "includes constraints wha, fsa, nharv, and art")

  
harvestFlow <- rbindlist(list(data.table(compartment ="UBC_study_boundary",
                                     partition = ' vol > 250 ',# was set at vol > 250 because the Sunshine Coast TSA had a minimum harvest volume per ha set at 250m3 or 300m3 depending on species. See table 19 (pg 28) from the Sunshine Coast TSA TSR Data Package April 2011 report. 

                                     year = rep( seq (from = 2018, 
                                                      to = 2218, # was 2218
                                                      by = 5), # was 5
                                                1), 

                                     flow = 4020000))) #I tried many values above this that did not work while 2100000 - 4000000 all resulted in an even flow. With art evenflow was achieved at 4010000

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "zoneManagement"))
                                             #"tableSurvival"))
                                             #"disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)

library(RSQLite)
# Create an ephemeral in-memory RSQLite database
con <- dbConnect(RSQLite::SQLite(), "UBC_study_boundary_clusdb.sqlite")

dbListTables(con)
zoneManagement<-dbGetQuery(con, "SELECT * FROM zoneManagement")
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

