---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Quesnel TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Chilcotin herds critical habtiat; to support Chilcotin herd planning, we run a sceanrio with no harvest in the  Chilcotin (Tweeds/Itchas/Rainbow/Charlotte Alplands) HEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Central Selkirks only, assuming other herds unprotected

"ECCC" in Chilcotin caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Chilcotin only

no harvest in caribou critical habtait areas; where there is cirtical habitat, no harvest in any types (including matrix); establishes the 'maximum impact' that protection of caribou habitat might potentially have on forest harvest; in Quesnel these include Tweedsmuir LEWR, Tweedsmuir Matrix, Itcha-Ilgachuz HEWSR, Itcha-Ilgachuz LEWR, Itcha-Ilgachuz LESR, Itcha-Ilgachuz Matrix, Barkerville HEWSR, Barkerville Matrix, Narrow Lake Matrix, North Cariboo HEWSR, North Cariboo Matrix, Wells Gray North HEWSR, Wells Gray North Matrix

'ECCC' in caribou critical habtait areas; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low eleavtion cirtcial habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected

DU9 specific scenarios developed by caribou recovery science team. These were doen for each herd indivudalls that overlaps the TSA:
First set of scenarios uses rast.zone_du9_scenarios; this raster defines priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. Scenarios:
* 3a = No harvest in old forest, recruitment forest and buffered Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas
* 3b = No harvest in old forest and recruitment forest Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas.

Second set of scenarios uses rast.zone_barkerville_groundhog_zones_20210303; this raster defines some priority matrix and core areas, and priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. scenarios:
* 2 or he0d_m12d; sets no harvest in all core priority zones and 12% max disturbance in all matrix priority zones
* high_med_low_priority (new 3a): sets no harvest in priority stands in all core priority zones and 15% max disturbance in all matrix priority zones
* high_med_priority (new 3b); sets no harvest in priority stands in high and medium core priority zones and 15% max disturbance in high and medium matrix priority zones
* high_priority (new 3c); sets no harvest in priority stands in high core priority zones and 15% max disturbance in high and medium matrix priority zones

DU7 (Northern group) specific scenarios developed by caribou recovery science team. These were done for each groups of herds that overlaps the TSA. For Williams Lake TSA, this included Itcha, Tweeds and Charlotte (group 1).
First set of scenarios uses rast.zone_du7_scenario_20210305; this raster defines priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. Scenarios:
* 3a = No harvest in old forest, recruitment forest and buffered high elevation core and low elevation summer critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance (unbuffered) in low elevation winter and matrix habitat areas

# Quesnel TSA Parameters 
## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in all herds = rast.zone_cond_noharvest_barkerville_crithab_or_herd,
                          rast.zone_cond_noharvest_itcha_ilgachuz_crithab_or_herd,
                          rast.zone_cond_noharvest_narrow_lake_crithab_or_herd,
                          rast.zone_cond_noharvest_north_cariboo_crithab_or_herd,
                          rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd,
                          rast.zone_cond_noharvest_wells_gray_north_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_barkerville_crithab_or_herd,
                    rast.zone_cond_eccc_itcha_ilgachuz_crithab_or_herd,
                    rast.zone_cond_eccc_narrow_lake_crithab_or_herd,
                    rast.zone_cond_eccc_north_cariboo_crithab_or_herd,
                    rast.zone_cond_eccc_tweedsmuir_crithab_or_herd,
                    rast.zone_cond_eccc_wells_gray_north_crithab_or_herd

No harvest in Chilcotin = rast.zone_cond_noharvest_itcha_ilgachuz_crithab_or_herd
                          rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd

ECCC in Chilcotin = rast.zone_cond_eccc_itcha_ilgachuz_crithab_or_herd
                    rast.zone_cond_eccc_tweedsmuir_crithab_or_herd

DU 9 scenarios version 1 = rast.zone_du9_scenarios

DU 9 Barkerville scenarios version 2 = rast.zone_barkerville_groundhog_zones_20210303

DU7 - Northern group priority forest stand areas = "rast.zone_du7_scenario_20210305"


## 'harvestPriority' parameter 
- used oldest first

- as alternative,  could focus on minimizzing 'disturabnce; for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

## 'harvestFlow'
from 2016 analysis report:  maximum even flow harvest was 2,139,000m^3^/year; from detemrination, June 6, 2017, the  AAC was set at 2,607,000 cubic metres 

the predicted sustainable harvest flow in Quesnel was between 1,617,000 and 2,139,000 (https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/stewardship/forest-analysis-inventory/tsr-annual-allowable-cut/quesnel_tsa_discussion_paper.pdf) pg 12


Annual volume
  - First, I tested a harvest flow of 2,139,000m^3^/year, dropped to 1.9M m^3^/year, was final for oldest first
  - for closest to disturbance, oldest, highest volume first = 1.6 M m^3^/year
  

- I used 150 m3/ha as minimum harvest volume

For cutblock adjacency, I used 3 m adjacency

#UPDATE SCENARIO

## Chilcotin Planning Scenarios Aug. 2021
```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite")) # connect to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_wha_2021'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones rast.zone_cond_noharvest_barkerville_crithab_or_herd
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab'")  # rast.zone_cond_noharvest_barkerville_crithab_or_herd
# rast.zone_cond_bc_itcha_ilgachuz_crithab  rast.zone_cond_bc_tweedsmuir_crithab    rast.zone_du7_scenario_20210330 rast.zone_wha_2021  


# Chilcotin Scenarios - Aug. 2021
## Existing caribou WHA GARs removed; forest age constraints applied to critical habitat
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' WHERE reference_zone = 'rast.zone_wha_2021' AND (zoneid = 263) OR (zoneid = 264) OR (zoneid = 3779) OR (zoneid = 3780) OR (zoneid = 3781)") 

## Scenario 1 forest age constraints applied to all to critical habitat
## Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 141 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
## Need to create some new rows for multiple age constraints
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(498,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',121,'ge',30,NULL,NULL,82524,0,250),
(499,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',121,'ge',30,NULL,NULL,157428,0,250),
(500,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',121,'ge',30,NULL,NULL,264988,0,250),
(501,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',101,'ge',37,NULL,NULL,82524,0,250),
(502,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',101,'ge',37,NULL,NULL,157428,0,250),
(503,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',101,'ge',37,NULL,NULL,264988,0,250),
(504,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',81,'ge',45,NULL,NULL,82524,0,250),
(505,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',81,'ge',45,NULL,NULL,157428,0,250),
(506,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',81,'ge',45,NULL,NULL,264988,0,250);")

## Scenario 2 forest age constraints applied to all to critical habitat
## Seral stage >80 = 37%; Seral stage >100 = 30%; Seral stage >120 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 435) OR (id = 436) OR (id = 437)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 498) OR (id = 499) OR (id = 500)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 501) OR (id = 502) OR (id = 503)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 504) OR (id = 505) OR (id = 506)")

## Scenario 3 forest age constraints applied to all to critical habitat
## Seral stage >80 = 30%; Seral stage >100 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 435) OR (id = 436) OR (id = 437) OR (id = 498) OR (id = 499) OR (id = 500)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 501) OR (id = 502) OR (id = 503)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 504) OR (id = 505) OR (id = 506)")


## Scenario 1, with rotation age
## Need to create some new rows for rotation age
## Here I am saying, allow harvest in up to 3% of the area in a five year period (equivalent to 0.6% harvested annually), and make all stands available to harvest (i.e., age <= 99,999 years old)
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(507,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',99999,'le',3,NULL,NULL,82524,0,250),
(508,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',99999,'le',3,NULL,NULL,157428,0,250),
(509,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',99999,'le',3,NULL,NULL,264988,0,250);")

## Scenario 2, with rotation age 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 435) OR (id = 436) OR (id = 437)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 498) OR (id = 499) OR (id = 500)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 501) OR (id = 502) OR (id = 503)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 504) OR (id = 505) OR (id = 506)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 4 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 507) OR (id = 508) OR (id = 509)")

## Scenario 3, with rotation age 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 435) OR (id = 436) OR (id = 437) OR (id = 498) OR (id = 499) OR (id = 500)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 501) OR (id = 502) OR (id = 503)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 504) OR (id = 505) OR (id = 506)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 5 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 507) OR (id = 508) OR (id = 509)")

## Scenario 4, 150 yo rotation age with early seral constaint added to seral constraints
# Seral stage >40 = 85%; Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 435) OR (id = 436) OR (id = 437) OR (id = 498) OR (id = 499) OR (id = 500)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 435) OR (id = 436) OR (id = 437)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 498) OR (id = 499) OR (id = 500)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 501) OR (id = 502) OR (id = 503)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 45 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 504) OR (id = 505) OR (id = 506)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 3 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 507) OR (id = 508) OR (id = 509)")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(510,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',41,'ge',85,NULL,NULL,82524,0,250),
(511,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',41,'ge',85,NULL,NULL,157428,0,250),
(512,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone22',0,'age',41,'ge',85,NULL,NULL,264988,0,250);")



dbDisconnect(clusdb)
```


## Northern Group Disturabnce Scenarios

```{r, northern grp disturbance scenarios}

#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite")) # connect to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_wha_2021'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones rast.zone_cond_noharvest_barkerville_crithab_or_herd
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab'")  # rast.zone_cond_noharvest_barkerville_crithab_or_herd
# rast.zone_cond_bc_itcha_ilgachuz_crithab  rast.zone_cond_bc_tweedsmuir_crithab    rast.zone_du7_scenario_20210330 rast.zone_wha_2021  


# NORTHERN GROUP - Tweedsmuir
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5) OR (zoneid = 4)") 
# Below makes priority forest stands in high priority zones no harvest and high priority zones of the matrix and LEWR high, medium and low priority zones  max 15% disturbance; NOTE: Only high priority zones in this unit
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55)")
# dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 


# NORTHERN GROUP - Itcha
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
# Below makes priority forest stands in high, medium and low priority zones no harvest and all of the matrix and LEWR high, medium and low priority zones  max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55)") 
# Below makes priority forest stands in high and medium priority zones no harvest, and high and medium priority matrix and LEWR max 15% disturbance; low priority available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86) OR (zoneid = 37) OR (zoneid = 40) OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 49) OR (zoneid = 52) OR (zoneid = 55)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 53) OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 53) OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 53) OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 53) OR (zoneid = 54)") 
# Below makes priority forest stands in high priority zones no harvest, and high priority matrix and LEWR max 15% disturbance; low and medium priority available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86) OR (zoneid = 37) OR (zoneid = 40) OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 49) OR (zoneid = 52) OR (zoneid = 55) OR (zoneid = 38) OR (zoneid = 41) OR (zoneid = 44) OR (zoneid = 47) OR (zoneid = 50) OR (zoneid = 53)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36) OR (zoneid = 39) OR (zoneid = 42)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54)")


# NORTHERN GROUP - GROUP 1 (Itcha, Rainbows, Charlotte, Tweeds, Telkwa)
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5) OR (zoneid = 4)") 
# Below makes priority forest stands no harvest and all of the matrix and LEWR habitat areas max 15% disturbance
# dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = ) OR (zoneid = )") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
# Below makes high and medium priority forest stands no harvest and high and medium the matrix and LEWR habitat areas max 15% disturbance; low priority available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 49) OR (zoneid = 37) OR (zoneid = 40) OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 52) OR (zoneid = 55)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36)  OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45)  OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51)  OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 53) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
# Below makes high priority forest stands no harvest and high matrix and LEWR habitat areas max 15% disturbance; low and medium priority available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 49) OR (zoneid = 37) OR (zoneid = 40) OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 52) OR (zoneid = 55) OR (zoneid = 38) OR (zoneid = 41) OR (zoneid = 44) OR (zoneid = 47) OR (zoneid = 50) OR (zoneid = 53)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 36)  OR (zoneid = 39) OR (zoneid = 42)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45)  OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 86)") 

dbDisconnect(clusdb)

```

## Wells Gray North, Barkerville, and Narrow Lake Disturbance Scenarios

```{r wells gray north, barkerville, narrow lake disturbance scenarios}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite")) # connect to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_wha_2021'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones rast.zone_cond_noharvest_barkerville_crithab_or_herd
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab'")  # rast.zone_cond_noharvest_barkerville_crithab_or_herd
# rast.zone_cond_bc_itcha_ilgachuz_crithab  rast.zone_cond_bc_tweedsmuir_crithab    rast.zone_du7_scenario_20210330 rast.zone_wha_2021  


# WELLS GRAY NORTH Update the constraints available to a zone as specified in the scenario
#Below will set Wells Gray North old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR (zoneid = 29) OR (zoneid = 44) OR (zoneid = 58)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR  (zoneid = 16) OR (zoneid = 45) OR (zoneid = 60) OR (zoneid = 71)") 
#Below will set Wells Gray North old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR (zoneid = 29)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR  (zoneid = 16) OR (zoneid = 45) OR (zoneid = 44) OR (zoneid = 58) OR (zoneid = 60) OR (zoneid = 71)")
# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_eccc_wells_gray_north_crithab_or_herd' AND zoneid = 2") 
# Below makes the core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_wells_gray_north_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_wells_gray_north_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_wells_gray_north_crithab_or_herd' AND (zoneid = 2)") 


# BARKERVILLE Update the constraints available to a zone as specified in the scenario
# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND zoneid = 2") 
#Below will set Barkerville old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 16) OR (zoneid = 31) OR (zoneid = 45)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR  (zoneid = 29) OR (zoneid = 58) OR (zoneid = 70) OR (zoneid = 71) OR (zoneid = 75)") #Below will set Barkerville old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 16)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR  (zoneid = 29) OR (zoneid = 31) OR (zoneid = 45) OR (zoneid = 58) OR (zoneid = 70) OR (zoneid = 71) OR (zoneid = 75)")
# Below makes the core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_barkerville_crithab' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_barkerville_crithab' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_barkerville_crithab' AND (zoneid = 2)") 
# Below makes priority stands in all priority zones no harvest, core outside of priority stands available, and all the matrix priority zones max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 10) OR (zoneid = 22) OR (zoneid = 30) OR (zoneid = 36) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 96) OR (zoneid = 102)") 
# Below makes priority stands in high and medium priority zones no harvest; core outside of priority stands available, and high and medium the matrix priority zones max 15% disturbance; low priority zones in core and matrix available
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 10) OR (zoneid = 22) OR (zoneid = 27) OR (zoneid = 30) OR (zoneid = 36) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 96) OR (zoneid = 102)") 
# Below makes priority stands in high priority zones no harvest; core outside of priority stands available, and high matrix priority zones max 15% disturbance; medium and low priority zones in core and matrix available
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 10) OR (zoneid = 22) OR (zoneid = 27) OR (zoneid = 30) OR (zoneid = 36) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 96) OR (zoneid = 102) OR (zoneid = 28)")



# NARROW LAKE Update the constraints available to a zone as specified in the scenario
#Below will set Narrow Lake old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 9) OR (zoneid = 24) OR (zoneid = 39) OR (zoneid = 53)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 70") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 70")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 14) OR (zoneid = 16) OR (zoneid = 29) OR (zoneid = 45) OR (zoneid = 58) OR (zoneid = 60) OR (zoneid = 71) OR (zoneid = 75)") 
#Below will set Narrow Lake old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 7) OR (zoneid = 22)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 68") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 68")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 9) OR (zoneid = 10) OR (zoneid = 24) OR (zoneid = 25) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 70) OR (zoneid = 71) OR (zoneid = 37) OR (zoneid = 51)") 

 
dbDisconnect(clusdb)

```

## Southern Mtn Caribou Scenarios

```{r, SMC scenarios}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite")) # connect to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_wha_2021'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones rast.zone_cond_noharvest_barkerville_crithab_or_herd
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab'")  # rast.zone_cond_noharvest_barkerville_crithab_or_herd
# rast.zone_cond_bc_itcha_ilgachuz_crithab  rast.zone_cond_bc_tweedsmuir_crithab    rast.zone_du7_scenario_20210330 rast.zone_wha_2021  

# Below makes priority forest stands no harvest and all of the matrix and LEWR habitat areas max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 30) OR (zoneid = 27) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69) OR (zoneid = 70) OR (zoneid = 71)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69) OR (zoneid = 70) OR (zoneid = 71)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69) OR (zoneid = 70) OR (zoneid = 71)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 22) OR (zoneid = 26) OR (zoneid = 25) OR (zoneid = 27) OR (zoneid = 28) OR (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69) OR (zoneid = 70) OR (zoneid = 71)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 22) OR (zoneid = 26)")

dbDisconnect(clusdb)

```



```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = TRUE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Quesnel_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.thlb_2020', #'rast.bc_thlb2018' 
                           nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", #"rast.zone_cond_wha" 
                                           "rast.zone_uwr_2021", #"rast.zone_cond_uwr" 
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw",
                                    # "rast.zone_cond_noharvest_barkerville_crithab_or_herd"
                                    # "rast.zone_cond_noharvest_itcha_ilgachuz_crithab_or_herd"
                                    # "rast.zone_cond_noharvest_narrow_lake_crithab_or_herd"
                                    # "rast.zone_cond_noharvest_north_cariboo_crithab_or_herd"
                                    # "rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd"
                                    # "rast.zone_cond_noharvest_wells_gray_north_crithab_or_herd"
                                           # "rast.zone_cond_eccc_barkerville_crithab_or_herd"
                                           # "rast.zone_cond_eccc_itcha_ilgachuz_crithab_or_herd"
                                           # "rast.zone_cond_eccc_narrow_lake_crithab_or_herd"
                                           # "rast.zone_cond_eccc_north_cariboo_crithab_or_herd",
                                           # "rast.zone_cond_eccc_tweedsmuir_crithab_or_herd",
                                         # "rast.zone_cond_eccc_wells_gray_north_crithab_or_herd"
                                         #  "rast.zone_smc_zones_20210315"
                                          # "rast.zone_barkerville_groundhog_zones_20210303"
                                      # "rast.zone_cond_bc_barkerville_crithab"
                                       "rast.zone_cond_bc_itcha_ilgachuz_crithab"
                                      #"rast.zone_cond_bc_narrow_lake_crithab",
                                      #"rast.zone_cond_bc_north_cariboo_crithab",
                                      # "rast.zone_cond_bc_tweedsmuir_crithab"
                                      #"rast.zone_cond_bc_wells_gray_north_crithab",
                                      #      "rast.zone_du7_scenario_20210330"
                                           ),
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "dist, age DESC, vol DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      reportHarvestConstraints = T,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance)
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  smcaribouAbundanceCLUS = list (nameRasSMCHerd = "rast.smc_herd_habitat", 
                                  tableSMCCoeffs = "vat.smc_coeffs"),
  uploaderCLUS = list(aoiName = 'quesnel_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "smcaribouAbundanceCLUS",
                "uploaderCLUS"
                )


# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "quesnel_bau",
#                        description = "Business as usual (BAU). Adjacency = 3m. Oldest first. Even harvest flow = 1,900,000m3/year")
# scenario = data.table (name = "quesnel_north_cariboo_nh",
#                        description = "No harvest in North Cariboo critical habitat that overlap with the harvest unit (e.g., TSA or TFL). Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year")
# scenario = data.table (name = "quesnel_narrow_lake_nh",
#                        description = "No harvest in Narrow Lake critical habitat that overlap with the harvest unit (e.g., TSA or TFL). Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_narrow_lake_he0d_m15d",
#                        description = "No harvest in Narrow Lake high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat. Oldest first. Adjacency = 3m. Even harvest flow = 1,950,000m3/year.")
# scenario = data.table (name = "quesnel_narrow_lake_scen3a_or_scen3b",
#                        description = "No Narrow Lake old forest, recruitment forest and buffered core critical habitat areas in the TSA, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Narrow Lake matrix habitat areas. Oldest first. Adjacency = 3m. Even harvest flow = 1,950,000m3/year.")
# scenario = data.table (name = "quesnel_barkerville_nh",
#                        description = "No harvest in Barkerville critical habitat that overlap with the harvest unit (e.g., TSA or TFL). Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year")
# scenario = data.table (name = "quesnel_barkerville_he0d_m15d",
#                        description = "No harvest in Barkerville high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_barkerville_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_barkerville_scen3b",
#                        description = "No harvest in old forest and recruitment forest Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_wells_north_nh",
#                        description = "No harvest in Wells Gray North critical habitat that overlap with the harvest unit (e.g., TSA or TFL). Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_wells_north_ch_hele0d_m15d",
#                        description = "No harvest in Wells Gray North high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Wells Gray North matrix critical habitat. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_wells_north_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered Wells Gray North core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Wells Gray North matrix habitat areas. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_wells_north_scen3b",
#                        description = "No harvest in old forest and recruitment forest in Wells Gray North core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Wells Gray North matrix habitat areas. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_wells_gray_north_he0d",
#                        description = "No harvest in Wells Gray North high elevation critical habitat; harvest allowed in matrix critical habitat.  Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_barkerville_north_he0d",
#                        description = "No harvest in Barkerville high elevation critical habitat; harvest allowed in matrix critical habitat.  Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_chil_nh",
#                        description = "No harvest in Chilcotin (Itcha, Charlotte, Rainbows) herds and habitat that overlap with the harvest unit (e.g., TSA or TFL). Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_barkerville_he0d_m12d",
#                        description = "No harvest in Barkerville high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_barkerville_hi_m_lo_priority",
#                        description = "No harvest in Barkerville high priority stands in all high elevation critical habitat; harvest allowed in all matrix critical habitat up to 15% disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_barkerville_high_med_priority",
#                        description = "No harvest in Barkerville high priority stands in high and medium priority areas in high elevation critical habitat; harvest allowed in high and medium priority matrix critical habitat up to 15% disturbance (no buffer) in forested area; no constraint in low priority high elevation and matrix zones. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_barkerville_high_priority",
#                        description = "No harvest in Barkerville high priority stands in high priority areas in high elevation critical habitat; harvest allowed in high priority matrix critical habitat up to 15% disturbance (no buffer) in forested area; no constraint in medium and low priority high elevation and matrix zones. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_northgrp_nh",
#                        description = "No harvest in Northern Group, group 1 (Itcha, Tweedsmuir) critical habitat types. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_northgrp_scen2",
#                        description = "No harvest in Northern Group high elevation (HEWSR) and low elevation summer (LESR) critical habitat; harvest allowed in low elevation winter (LEWR) and matrix critical habitat up to 12% forest disturbance (no buffer) in forested area. Harvest flow 1,900,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_northgrp_high_med_low_priority",
#                        description = "No harvest in Northern Group high elevation (HEWSR) and low elevation summer (LESR) critical habitat; harvest allowed in low elevation winter and matrix critical habitat up to 15% forest disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_wells_north_he0d_m12d",
#                        description = "No harvest in Wells Gray North high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Oldest first. Adjacency = 3m. Even harvest flow = 1,900,000m3/year.")
# scenario = data.table (name = "quesnel_wells_north_hi_med_lo_priority",
#                        description = "No harvest in high priority stands and priority areas in Wells Gray North high elevation critical habitat; harvest allowed in matrix alll priority areas up to 15% forest disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_du7_grp1_nh",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_du7_grp1_he0d_mlewr12d",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_du7_grp1_hi_med_lo_priority",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_du7_grp1_hi_med_priority",
#                        description = "No harvest in high and medium priority group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) HEWSR and LESR critical habitat; harvest allowed in  high and medium priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in low prioirty zones. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_du7_grp1_hi_priority",
#                        description = "No harvest in high priority group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) HEWSR and LESR critical habitat; harvest allowed in high priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in low and medium prioirty zones. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_itcha_nh",
#                        description = "No harvest in Itcha-Ilgachuz critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_itcha_he0d_mlewr12d",
#                        description = "No harvest in Itcha-Ilgachuz HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_itcha_hi_med_lo_priority",
#                        description = "No harvest in Itcha-Ilgachuz priority stands in high, medium and low priority zone HEWSR and LESR critical habitat; harvest allowed in high, medium and low priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_itcha_hi_med_priority",
#                        description = "No harvest in Itcha-Ilgachuz priority stands in high and medium priority zone HEWSR and LESR critical habitat; harvest allowed in high and medium priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allwoed in low priority areas. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_itcha_hi_priority",
#                        description = "No harvest in Itcha-Ilgachuz priority stands in high priority zone HEWSR and LESR critical habitat; harvest allowed in high priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in medium and low priority areas. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_tweeds_nh",
#                        description = "No harvest in Tweedsmuir critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_tweeds_he0d_mlewr12d",
#                        description = "No harvest in Tweedsmuir HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "quesnel_tweeds_hi_priority",
#                        description = "No harvest in Tweedsmuir priority stands in high priority zone HEWSR and LESR critical habitat; harvest allowed in high priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NOTE: only high priority zones in this unit. Even harvest flow = 1,900,000m3/year. Adjacency = 3m. Oldest first.")

# scenario = data.table (name = "quesnel_bau_chil_0821",
#                        description = "Business as usual (BAU) for Chilcotin scenarios (existing constaints in place, including beo, vqo, wha, uwr, cw, pa, fsw). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Even harvest flow = 1,600,000m3/year.")
# scenario = data.table (name = "quesnel_scen1_chil_0821",
#                        description = "Chilcotin scenario 1: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Harvest flow = 1,600,000m3/year.")
# scenario = data.table (name = "quesnel_scen2_chil_0821",
#                        description = "Chilcotin scenario 2: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 37%; Seral stage >100 = 30%; Seral stage >120 = 25%). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Harvest flow = 1,600,000m3/year.")
# scenario = data.table (name = "quesnel_scen3_chil_0821",
#                        description = "Chilcotin scenario 3: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 30%; Seral stage >100 = 25%). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Harvest flow = 1,600,000m3/year.")
# scenario = data.table (name = "quesnel_scen1ra_chil_0821",
#                        description = "Chilcotin scenario 1 with rotation age: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%). Rotation age = 150 years, or 0.67% area harvested annually or 3% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Harvest flow = 1,600,000m3/year.")
# scenario = data.table (name = "quesnel_scen2ra_chil_0821",
#                        description = "Chilcotin scenario 2 with rotation age: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 37%; Seral stage >100 = 30%; Seral stage >120 = 25%). Rotation age = 120 years, or 0.83% area harvested annually or 4% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Harvest flow = 1,600,000m3/year.")
# scenario = data.table (name = "quesnel_scen3ra_chil_0821",
#                        description = "Chilcotin scenario 3 with rotation age: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 30%; Seral stage >100 = 25%).). Rotation age = 100 years, or 1% area harvested annually or 5% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Harvest flow = 1,600,000m3/year.")

scenario = data.table (name = "quesnel_scen4_chil_0821",
                       description = "Chilcotin scenario 4: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >40 = 85%; Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%). Rotation age = 150 years, or 0.67% area harvested annually or 3% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first. Harvest flow = 1,600,000m3/year.")




# BELOW ARE OLD SCENARIOS THAT NEED TO BE RE-RUN
# scenario = data.table (name = "quesnel_chil_ch_hele0d_m15d",
#                        description = "No harvest in Chilcotin high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "quesnel_all_nh",
#                        description = "No harvest in all critical habitat of all herds that overlap with the harvest unit. Adjacency was set to 3m.")
# scenario = data.table (name = "quesnel_all_ch_he0d_m15d",
#                        description = "No harvest in high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit. Adjacency was set to 3m.")
# scenario = data.table (name = "quesnel_chil_notweeds_nh",
#                        description = "No harvest in Chilcotin (Itcha, Rainbows and Charlotte only) habitat that overlap with the harvest unit (e.g., TSA or TFL). Adjacency was set to 3m.")
# scenario = data.table (name = "quesnel_chil_notweeds_ch_hele0d_m15d",
#                        description = "No harvest in Chilcotin (Itcha, Rainbows and Charlotte only) high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat. Adjacency was set to 3m.")


harvestFlow <- rbindlist(list(data.table(compartment ="Quesnel_TSA",
                                     partition = ' vol > 150 ', 
                                     year = rep( seq (from = 2018, 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 8000000) # 1,600,000
                                    # 9500000 // 1,900,000 m3/yr for oldest first
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithm

The general algorithm (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

