---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# 100 Mile TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Wells Gray North critical habtiat; to support  herd planning, we run a sceanrio with no harvest in the Wells Gray North  HEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Wells Gray North only, assuming other herds unprotected

"ECCC" in Wells Gray North caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Wells Gray North only

no harvest in Wells Gray South critical habtiat; to support  herd planning, we run a sceanrio with no harvest in the Wells Gray South  HEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Wells Gray South only, assuming other herds unprotected

"ECCC" in Wells Gray South caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Wells Gray South only


# 100 Mile TSA Parameters 

## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in Wells Gray North = rast.zone_cond_noharvest_wells_gray_north_crithab_or_herd

ECCC in Wells Gray North = rast.zone_cond_eccc_wells_gray_north_crithab_or_herd

No harvest in  Wells Gray South = rast.zone_cond_noharvest_wells_gray_south_crithab_or_herd

ECCC in  Wells Gray South = rast.zone_cond_eccc_wells_gray_south_crithab_or_herd

## 'harvestPriority' parameter 
- focus on minimizzing 'disturabnce; for cariobu, then older, higher vlomue stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)
      
- in 2013 TSR, stands were prioritized for salvage harvest: 
  - stands with more than 70 percent pine and with more than 50 percent mortality (primary salvage); 
  - stands with 50 to 70 percent pine and more than 50 percent mortality (secondary salvage); 
  - stands with more than 70 percent spruce in areas of spruce bark beetle infestation (spruce salvage);
  - then all other species and/or stands with less than 50 percent mortality

## 'harvestFlow'
- from 2013 AAC determination: 
  - November 7, 2013 to November 7, 2018, the AAC will be 2 000 000 cubic metres, of which no more than 500 000 cubic metres are attributable to live trees.
  - From November 7, 2018 until the next determination, the AAC will be 1 000 000 cubic metres, of which no more than 500 000 cubic metres are attributable to live trees
  
  
- from base case: 
  - Starting in 2012, the initial harvest level in the 150-year base case was set at 2.0 million cubic metres per year.  This rate, which is the level of the AAC determined in 2006, can be maintained for seven years.After 2019, the harvest level decreases to 890 000 cubic metres per year and remains at this level for 48 years (2067), after which it begins to increase to the long-term sustainable level of 1.6 million cubic metres per year in 2086. 

-  I tested a harvest flow of 1,500,000m^3^/year (7,500,000m^3^/5-year), 

- stable at 







from detemiantion: used 'oldest first' priority queue

From data package: 
  - minimum stand age for harvest of 60 for pine and 80 for non-pine, and minimum volume of 65 for pine and 100 for non-pine

- I used 150 m3/ha as minimum harvest volume to be consistent with other units

For cutblock adjacency, I used 3 m adjacncey; this was consistent with the data package


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list (  dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Onehundred_Mile_House_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Onehundred_Mile_House_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                             "rast.zone_cond_vqo", 
                                             "rast.zone_cond_wha", 
                                             "rast.zone_cond_uwr",
                                             "rast.zone_cond_fsw", 
                                             "rast.zone_cond_nharv", 
                                             "rast.zone_cond_cw" 
                              # "rast.zone_cond_noharvest_wells_gray_north_crithab_or_herd"
                              # "rast.zone_cond_noharvest_wells_gray_south_crithab_or_herd"
                              # "rast.zone_cond_eccc_wells_gray_north_crithab_or_herd"
                              # "rast.zone_cond_eccc_wells_gray_south_crithab_or_herd"   
                                               ),
                           nameZoneTable = "zone_constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestPriority = "dist, age DESC, vol DESC",
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'onehundred_mile_tsa', # name of the schema that gets uploaded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']



scenario = data.table (name = "OnehundredMile_bau",
                       description = "Business-as-usual case; sustainable flow = 1,400,000m^3^/year. Adjacency was set to 3m.")
# scenario = data.table (name = "OnehundredMile_wells_north_nh",
#                        description = "No harvest in Wells Gray North critical habitat that overlap with the harvest unit (e.g., TSA or TFL). Adjacency was set to 3m.")
# scenario = data.table (name = "OnehundredMile_wells_north_ch_hele0d_m15d",
#                        description = "No harvest in Wells Gray North high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Wells Gray North matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "OnehundredMile_wells_south_nh",
#                        description = "No harvest in Wells Gray South critical habitat that overlap with the harvest unit (e.g., TSA or TFL). Adjacency was set to 3m.")


scenario = data.table (name = "OnehundredMile_wells_south_ch_hele0d_m15d",
                       description = "No harvest in Wells Gray South high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Wells Gray South matrix critical habitat. Adjacency was set to 3m.")



harvestFlow <- rbindlist(list(data.table(compartment ="Onehundred_Mile_House_TSA",
                                         partition = ' vol > 150 ', 
                                         year = rep(seq (from = 2018, 
                                                         to = 2218, 
                                                         by = 5),
                                                    1), 
                                         flow = 7000000) # 1,400,000m^3^/year
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

