---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Revelstoke TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Columbia North, Columbia South and Frisby-Boulder critical habtiat; to support Columbia North, Columbia South and Frisby-Boulder herd planning, we run a sceanrio with no harvest in the Columbia North, Columbia South and Frisby-Boulder HEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Columbia North, Columbia South and Frisby-Boulder only, assuming other herds unprotected

"ECCC" in Columbia North, Columbia South and Frisby-Boulder caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Columbia North, Columbia South and Frisby-Boulder only

no harvest in caribou critical habtait areas; where there is cirtical habitat, no harvest in any types (including matrix); establishes the 'maximum impact' that protection of caribou habitat might potentially have on forest harvest; in Kootenay Lake TSA these include Monashee Matrix, Frisby Boulder HEWSR, Frisby Boulder Matrix, Columbia South HEWSR, Columbia South Matrix, Central Rockies Matrix, Central Rockies HEWSR, Columbia North Matrix, Columbia North HEWSR

'ECCC' in caribou critical habtait areas; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low eleavtion cirtcial habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected


# Revelstoke TSA Parameters 

## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in all herds = rast.zone_cond_noharvest_monashee_crithab_or_herd
                          rast.zone_cond_noharvest_frisby_boulder_crithab_or_herd
                          rast.zone_cond_noharvest_columbia_south_crithab_or_herd
                          rast.zone_cond_noharvest_central_rockies_crithab_or_herd
                          rast.zone_cond_noharvest_columbia_north_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_monashee_crithab_or_herd
                    rast.zone_cond_eccc_frisby_boulder_crithab_or_herd
                    rast.zone_cond_eccc_columbia_south_crithab_or_herd
                    rast.zone_cond_eccc_central_rockies_crithab_or_herd
                    rast.zone_cond_eccc_columbia_north_crithab_or_herd

No harvest in Columbia North, Columbia South and Frisby-Boulder = rast.zone_cond_noharvest_columbia_north_crithab_or_herd
rast.zone_cond_noharvest_columbia_south_crithab_or_herd
rast.zone_cond_noharvest_frisby_boulder_crithab_or_herd

ECCC in Columbia North, Columbia South and Frisby-Boulder = rast.zone_cond_eccc_columbia_north_crithab_or_herd
                                                            rast.zone_cond_eccc_columbia_south_crithab_or_herd
                                                            rast.zone_cond_eccc_frisby_boulder_crithab_or_herd

## 'harvestPriority' parameter 
- focus on minimizzing 'disturabnce; for cariobu, then older, higher vlomue stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

## 'harvestFlow'
- based on interpretation of analysis report, I tested a harvest flow of 200,000m^3^/year (1,000,000m^3^/5-year); 250,000, 225,000, 215,000, 205,000, 210,000; used 210,000 as bau

from detemiantion: used 'oldest first' priority queue; here I used the same 

From analysis report: large majority of minimum harvest ages used in the base case scenario was based on achieving 95% of the stands maximum mean annual increment (MAI). 

- I used 150 m3/ha as minimum harvest volume instead

For cutblock adjacency, I used 3 m adjacency; in analysis report: 25% of the THLB in each LU was allowed to be less than the greenup age (13 years old)

## Modify Constraints

```{r, zone_update}
library (DBI)
# STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Revelstoke_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

# STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_smc_zones_20210315'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_eccc_monashee_crithab_or_herd'")

# MONASHEE
#Below will set Monashee old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 8) OR (zoneid = 23) OR (zoneid = 38) OR (zoneid = 52)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 69") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 69")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 19) OR (zoneid = 20) OR (zoneid = 21) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 61) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 66) OR (zoneid = 67)") 
# Below makes the core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_monashee_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_monashee_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_monashee_crithab_or_herd' AND (zoneid = 2)")







# Frisby-Boulder
#Below will set Frisby-Boulder old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 6) OR (zoneid = 21) OR (zoneid = 36) OR (zoneid = 50)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 19) OR (zoneid = 20) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 61) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 67) OR (zoneid = 69)") 
#Below will set Frisby-Boulder  old and recruit as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 6) OR (zoneid = 21)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 66")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 19) OR (zoneid = 20) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 61) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 67) OR (zoneid = 69) OR (zoneid = 36) OR (zoneid = 50)") 
# Below makes the core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_frisby_boulder_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_frisby_boulder_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_frisby_boulder_crithab_or_herd' AND (zoneid = 2)")


# COLUMBIA SOUTH 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 5) OR (zoneid = 20) OR (zoneid = 35) OR (zoneid = 49)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 6) OR (zoneid = 19) OR (zoneid = 21) OR (zoneid = 34) OR (zoneid = 36) OR (zoneid = 61) OR (zoneid = 64) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 69)") 
#Below will set Columbia SOuth old and recruit as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 5) OR (zoneid = 20)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 65")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 6) OR (zoneid = 19) OR (zoneid = 21) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 49) OR (zoneid = 61) OR (zoneid = 64) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 69)") 
# Below makes the core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_columbia_south_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_columbia_south_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_columbia_south_crithab_or_herd' AND (zoneid = 2)")


# COLUMBIA NORTH Update the constraints available to a zone as specified in the scenario
# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_eccc_columbia_north_crithab_or_herd' AND zoneid = 1") 
#Below will set Columbia North old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 19) OR (zoneid = 34) OR (zoneid = 48)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 5) OR (zoneid = 6) OR (zoneid = 20) OR (zoneid = 21) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 61) OR (zoneid = 65) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 69)") 
#Below will set Columbia North old and recruit as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 19) ")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 63) OR (zoneid = 64)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 5) OR (zoneid = 6) OR (zoneid = 20) OR (zoneid = 21) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 61) OR (zoneid = 65) OR (zoneid = 66) OR (zoneid = 67) OR (zoneid = 69) OR (zoneid = 34) OR (zoneid = 48)") 
# Below makes the core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_columbia_north_crithab_or_herd' AND (zoneid = 1)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_columbia_north_crithab_or_herd' AND (zoneid = 1)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_columbia_north_crithab_or_herd' AND (zoneid = 1)")
# Below makes priority stands in all priority zones no harvest, core outside of priority stands available, and all the matrix priority zones max 15% disturbance NOTE: Only high priority areas here
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 43) OR (zoneid = 44) OR (zoneid = 45)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 46)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 14) OR (zoneid = 33) OR (zoneid = 47) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 50) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 53)  OR (zoneid = 54)  OR (zoneid = 55)  OR (zoneid = 57) OR (zoneid = 74)") 


dbDisconnect(clusdb)
```


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list (  dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Revelstoke_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Revelstoke_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                             "rast.zone_cond_vqo", 
                                             "rast.zone_cond_wha", 
                                             "rast.zone_cond_uwr",
                                             "rast.zone_cond_fsw", 
                                             "rast.zone_cond_nharv", 
                                             "rast.zone_cond_cw",
                            # "rast.zone_cond_noharvest_monashee_crithab_or_herd"
                            # "rast.zone_cond_noharvest_frisby_boulder_crithab_or_herd"
                            # "rast.zone_cond_noharvest_columbia_south_crithab_or_herd"
                            # "rast.zone_cond_noharvest_central_rockies_crithab_or_herd"
                            # "rast.zone_cond_noharvest_columbia_north_crithab_or_herd"
                             "rast.zone_cond_eccc_monashee_crithab_or_herd"
                            # "rast.zone_cond_eccc_frisby_boulder_crithab_or_herd"
                            # "rast.zone_cond_eccc_columbia_south_crithab_or_herd"
                            # "rast.zone_cond_eccc_central_rockies_crithab_or_herd"
                            # "rast.zone_cond_eccc_columbia_north_crithab_or_herd"
                            # "rast.zone_smc_zones_20210315"
                            # "rast.zone_cond_bc_columbia_north_crithab",
                            # "rast.zone_cond_bc_columbia_south_crithab",
                            # "rast.zone_cond_bc_central_rockies_crithab",
                            # "rast.zone_cond_bc_frisby_boulder_crithab",
                            # "rast.zone_cond_bc_monashee_crithab"
                                               ),
                           nameZoneTable = "zone_constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriority = 1,
                      #reportHarvestConstraints = TRUE,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, 
                       nameRasCaribouHerd = "rast.caribou_herd", 
                       tableCaribouHerd = "public.caribou_herd_vat"), 
  disturbanceCalcCLUS = list(calculateInterval = 1, # should be 1 if using constraints on 'dist' (disturbance)
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  uploaderCLUS = list(aoiName = 'revelstoke_tsa', 
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']


### SCENARIOS ###
# scenario = data.table (name = "revelstoke_bau", description = "Business-as-usual case; sustainable flow = 210,000m^3^/year. Adjacency was set to 3m.")
# scenario = data.table (name = "test",
#                        description = "No harvest in all Columbia North. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_colnsfb_nh",
#                        description = "No harvest in all Columbia North, Columbia South and Frisby-Boulder critical habitat. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_colnsfb_ch_he0d_m15d",
#                        description = "No harvest in Columbia North, Columbia South and Frisby-Boulder high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia North, Columbia South and Frisby-Boulder matrix critical habitat. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_all_nh",
#                        description = "No harvest in all critical habitat of all herds that overlap with the TSA. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_all_ch_he0d_m15d",
#                        description = "No harvest in high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap the TSA. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_north_nh",
#                        description = "No harvest in all Columbia North critical habitat. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_north_he0d_m15d",
#                        description = "No harvest in Columbia North high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia North matrix critical habitat. Adjacency was set to 3m. Flow = 210,000m^3^/year. Oldest first.")
# scenario = data.table (name = "revelstoke_central_rockies_nh",
#                        description = "No harvest in all Central Rockies critical habitat. Oldest first. Adjacency = 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_central_rockies_he0d_m15d",
#                        description = "No harvest in Central Rockies high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central Rockies matrix critical habitat. Oldest first. Adjacency = 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_south_nh",
#                        description = "No harvest in all Columbia South critical habitat. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_south_he0d_m15d",
#                        description = "No harvest in Columbia South high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia South matrix critical habitat. Oldest first. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_frisby_boulder_nh",
#                        description = "No harvest in all Frisby Boulder critical habitat. Oldest first. Adjacency = 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_frisby_boulder_he0d_m15d",
#                        description = "No harvest in Frisby Boulder high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Frisby Boulder matrix critical habitat.  Oldest first. Adjacency = 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_monashee_nh",
#                        description = "No harvest in all Monashee critical habitat. Oldest first. Adjacency = 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_monashee_he0d_m15d",
#                        description = "No harvest in Monashee high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Monashee matrix critical habitat. Oldest first. Adjacency = 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_ernst",
#                        description = "No harvest in Columbia North, Columbia South and Frisby-Boulder high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Columbia North, Columbia South and Frisby-Boulder matrix critical habitat areas as defined by Bevan Ernst. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_north_he10d_m15d",
#                        description = "No harvest in Columbia North high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Columbia North martix habitat areas as defined by Bevan Ernst. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_south_he10d_m15d",
#                        description = "No harvest in Columbia South high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Columbia South martix habitat areas as defined by Bevan Ernst. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_frisby_boulder_he10d_m15d",
#                        description = "No harvest in Frisby Boulder high elevation critical habitat areas as defined by Bevan Ernst, maximum 35% buffered disturbance (15% harvest) in Frisby Boulder martix habitat areas as defined by Bevan Ernst. Adjacency was set to 3m. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_bau_v2",
#                        description = "Business-as-usual case; sustainable flow = 250,000m^3^/year. Adjacency was set to 3m.")
# scenario = data.table (name = "revelstoke_colnsfb_nh_v2",
#                        description = "No harvest in all Columbia North, Columbia South and Frisby-Boulder critical habitat. Sustainable flow = 155,000m^3^/year. Adjacency was set to 3m.")
# scenario = data.table (name = "revelstoke_columbia_north_nh_v2",
#                        description = "No harvest in all Columbia North critical habitat. Sustainable flow = 155,000m^3^/year. Adjacency was set to 3m.")
# scenario = data.table (name = "revelstoke_columbia_north_he0d_m15d_v2",
#                        description = "No harvest in Columbia North high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia North matrix critical habitat. Sustainable flow = 155,000m^3^/year. Adjacency was set to 3m.")
# scenario = data.table (name = "revelstoke_columbia_north_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered core critical habitat areas in Columbia North, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Columbia North matrix habitat areas. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_north_scen3b",
#                        description = "No harvest in old forest and recruitment forest core critical habitat areas in Columbia North, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Columbia North matrix habitat areas. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_south_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered core critical habitat areas in Columbia South, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Columbia South matrix habitat areas. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_south_scen3b",
#                        description = "No harvest in old forest and recruitment forest  core critical habitat areas in Columbia South, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Columbia South matrix habitat areas. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_frisby_boulder_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered core critical habitat areas in Frisby Boulder, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Frisby Boulder matrix habitat areas. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_frisby_boulder_scen3b",
#                        description = "No harvest in old forest and recruitment forest core critical habitat areas in Frisby Boulder, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Frisby Boulder matrix habitat areas. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_monashee_scen3a3b",
#                        description = "Maximum 35% buffered disturbance (unbuffered) in Monashee matrix habitat areas (No Monashee core habitat, as defined by Ernst, in TSA). Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_north_he0d",
#                        description = "No harvest in Columbia North high elevation critical habitat; harvest allowed in matrix critical habitat. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_north_he0d_m12d",
#                        description = "No harvest in Columbia North high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_north_hi_priority",
#                        description = "No harvest in high priority stands and all priority areas in Columbia North high elevation critical habitat; harvest allowed in matrix all priority areas up to 15% forest disturbance (no buffer) in forested area. NTOE: only high priority zones in this area. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_columbia_south_he0d_m12d",
#                        description = "No harvest in Columbia South high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_frisby_boulder_he0d_m12d",
#                        description = "No harvest in Frisby Boulder high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")
# scenario = data.table (name = "revelstoke_frisby_boulder_hi_med_lo",
#                        description = "No harvest in high priority stands and all priority areas in Frisby Boulder high elevation critical habitat; harvest allowed in matrix all priority areas up to 15% forest disturbance (no buffer) in forested area.  Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")

scenario = data.table (name = "revelstoke_monashee_he0d_m12d",
                       description = "No harvest in Monashee high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Note: no core here. Adjacency = 3m. Oldest first. Flow = 210,000m^3^/year.")






harvestFlow <- rbindlist(list(data.table(compartment ="Revelstoke_TSA",
                                         partition = ' vol > 150 ', 
                                         year = rep(seq (from = 2018, 
                                                         to = 2218, 
                                                         by = 5),
                                                    1), 
                                         flow = 1050000) # 210,000m^3^/year
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvivalReport",
                                             "disturbanceReport",
                                             "volumebyareaReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

