---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Williams Lake TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

No harvest in Chilcotin critical habitat that overlap with the harvest unit (e.g., TSA or TFL). This implies no harvest in caribou herd or critical habtait areas; where there is critical habtait, no harvest in any types (including matrix), and where therre is no critical habtiat, no harvest anywhere in the herd boudanries (assumes all critical hbaitat); establishes the 'maximum impact' that protection fo caribou habitat might potentially have on forest harvest. 

No harvest in Chilcotin high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat

No harvest in all herds that overlap with the harvest unit (e.g., TSA or TFL)

No harvest in high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit


# Williams Lake TSA Parameters 

## New Caribou Constraints
BAU = beo, vqo, wha, uwr, fsw (fisheries senstive watersheds),parks and protected areas (nharv) and cw (community watersheds) 

willake_chil_nh = BAU + no harvest in Chilcotin critical habitat that overlap with the harvest unit (e.g., TSA or TFL)

willake_chil_ch_hle0d_m15d = BAU + no harvest in Chilcotin high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat

willake_all_nh = BAU + No harvest in all herds that overlap with the harvest unit (e.g., TSA or TFL). All (Charlotte Alplands HEWSR, Charlotte Alplands LEWR, Charlotte Alplands Matrix, Itcha-Ilgachuz HEWSR, Itcha-Ilgachuz LESR, Itcha-Ilgachuz LEWR, Itcha-Ilgachuz Matrix, Rainbows HEWSR, Rainbows LESR, Rainbows LEWR, Rainbows Matrix, Barkerville HEWSR, Barkerville Matrix, Wells Gray North HEWSR, Wells Gray North Matrix).

willake_all_ch_hele0d_m15d = BAU + No harvest in high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL)


## 'harvestPriority' parameter 
- focus on minimizzing 'disturabnce; for cariobu, then older, higher vlomue stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

-Minimum harest criteria - 80 m3/ha for pine and 120 m3/ha for non pine.

## 'harvestFlow'

The allowable annual cut (AAC) for the Williams Lake TSA is 3 million cubic metres as of February 25, 2015. This includes a partition of a maximum of 1 500 000 cubic metres per year for live volume which means the remainder of the AAC is for salvaging dead trees

- I tested a harvest flow of 1.5 Mm3 (7,500,000m3/5yr) and the model was successful at meeting this demand.
- I increased the harvest flow to 1.856 Mm3 (9,280,000m3/5yr) from an earlier analysis



```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( 
                           dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Williams_Lake_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Williams_Lake_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_cw",
                            # "rast.zone_cond_noharvest_itcha_ilgachuz_crithab_or_herd",
                            # "rast.zone_cond_noharvest_charlotte_alplands_crithab_or_herd",
                            # "rast.zone_cond_noharvest_rainbows_crithab_or_herd",
                            # "rast.zone_cond_noharvest_wells_gray_north_crithab_or_herd"
                            #"rast.zone_cond_noharvest_barkerville_crithab_or_herd"
                            # "rast.zone_cond_eccc_itcha_ilgachuz_crithab_or_herd",
                            # "rast.zone_cond_eccc_charlotte_alplands_crithab_or_herd",
                            # "rast.zone_cond_eccc_rainbows_crithab_or_herd",
                             "rast.zone_cond_eccc_wells_gray_north_crithab_or_herd"
                            # "rast.zone_cond_eccc_barkerville_crithab_or_herd" 
                           ),
                           nameZoneTable = "zone_constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestPriority = "dist, age DESC, vol DESC",
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval = 5, 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'williams_lake_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# scenario = data.table (name = "williams_lake_barkerville_nh",
#                        description = "No harvest in Barkerville critical habitat; harvest flow 1,856,000 m3/yr. Adjacency was set to 3m.")
# scenario = data.table (name = "williams_lake_barkerville_ch_hele0d_m15d",
#                        description = "No harvest in Barkerville high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL)")
# scenario = data.table (name = "williams_lake_wells_gray_north_nh",
#                        description = "No harvest in Wells Gray North critical habitat; harvest flow 1,856,000 m3/yr. Adjacency was set to 3m.")

scenario = data.table (name = "williams_lake_wells_gray_north_ch_hele0d_m15d",
                       description = "No harvest in Wells Gray North high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Wells Gray North matrix critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL). Harvest flow 1,856,000 m3/yr. Adjacency was set to 3m.")



harvestFlow <- rbindlist(list(data.table(compartment ="Williams_Lake_TSA",
                                     partition = ' vol > 110 ', 
                                     year = rep( seq (from = 2018, # run the 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 9280000)  # 1,856,000m3/year
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

