---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# TFL 52 Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Columbia North and South caribou critical habtiat; to support Columbia North and South herd planning, we run a sceanrio with no harvest in the Columbia North and South HEWSR and Matrix; assesses teh potential maximum impact of protecting Columbia North and South only, assuming other herds unprotected

ECCC in Columbia North and South caribou critical habitat; an alterantive to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no harvest in high and low elevation critical habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Columbia North and South only

No harvest in all caribou herd areas (Columbia North and Central Rockies)

ECCC in Columbia North and Central Rockies; no harvest in high and low elevation critical habitat, and up to 35% disturabnce in matrix habtiat;

DU9 specific scenarios developed by caribou recovery science team. These were doen for each herd indivudalls that overlaps the TSA:
First set of scenarios uses rast.zone_du9_scenarios; this raster defines priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. Scenarios:
* 3a = No harvest in old forest, recruitment forest and buffered Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas
* 3b = No harvest in old forest and recruitment forest Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas.

Second set of scenarios uses rast.zone_barkerville_groundhog_zones_20210303; this raster defines some priority matrix and core areas, and priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. scenarios:
* he0d_m12d (new 2); sets no harvest in all core priority zones and 12% max disturbance in all matrix priority zones
* high_med_low_priority (new 3a): sets no harvest in priority stands in all core priority zones and 15% max disturbance in all matrix priority zones
* high_med_priority (new 3b); sets no harvest in priority stands in high and medium core priority zones and 15% max disturbance in high and medium matrix priority zones (NOTE: there are no medium and low core or medium priority matrix overlapping the TSA, so this scenario was not run)
* high_priority (new 3c); sets no harvest in priority stands in high core priority zones and 15% max disturbance in high and medium matrix priority zones

# TFL 52 Parameters 
## New Caribou Constraints
The TFL overlaps with critical habitat of the North Cariboo, Narrow Lake	and Barkerville cariobu herds in DU9.

BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in North Cariboo = rast.zone_cond_noharvest_north_cariboo_crithab_or_herd

No harvest in Narrow Lake = rast.zone_cond_noharvest_narrow_lake_crithab_or_herd

No harvest in Barkerville = rast.zone_cond_noharvest_barkerville_crithab_or_herd

No harvest in North Cariboo high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) matrix critical habitat = rast.zone_cond_eccc_north_cariboo_crithab_or_herd

No harvest in Narrow Lake high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) matrix critical habitat = rast.zone_cond_eccc_narrow_lake_crithab_or_herd

No harvest in Barkerville high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) matrix critical habitat = rast.zone_cond_eccc_barkerville_crithab_or_herd

DU 9 scenarios version 1 = rast.zone_du9_scenarios

DU 9 Barkerville scenarios version 2 = rast.zone_barkerville_groundhog_zones_20210303

## 'harvestPriority' parameter 
- used oldest first

- as alternative,  could focus on minimizzing 'disturabnce; for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)
      
## 'harvestFlow'
from 2019 determination: AAC was 592,500 cubic metres, of which 570,000 cubic meters was partitioned for conifer.

- First, I tested a harvest flow of 550,000m^3^/year, then 600,000 m^3^/year, 575,000 m^3^/year, 585,000 m^3^/year, 595,000  m^3^/year

- I used 150 m3/ha as minimum harvest volume;  determination used 120m3/ha and a minimum age of 95% mean annual increment (not sure what the actual number was)

- I used 3 m adjacency; nothing in determination on this

#UPDATE SCENARIO
```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/TFL52_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_du9_scenarios'") # Note: the reference_zone is the name of the raster in the rast schema. If there is no 'WHERE' clause this may return 1000's of zones
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd'")
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_smc_zones_20210315'")






# BARKERVILLE Update the constraints available to a zone as specified in the scenario
# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND zoneid = 2")
# BARKERVILLE Update the constraints available to a zone as specified in the scenario
# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND zoneid = 2")
#Below will set Barkerville old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 16) OR (zoneid = 31) OR (zoneid = 45)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 9) OR (zoneid = 10) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 70) OR (zoneid = 71)") 
#Below will set Barkerville old and recruit as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 16)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 9) OR (zoneid = 10) OR (zoneid = 31) OR (zoneid = 45) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 70) OR (zoneid = 71)") 
# Below makes the all of core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND (zoneid = 1) ")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND (zoneid = 2)") 
# Below makes priority stands in all priority zones no harvest, core outside of priority stands available, and all the matrix priority zones max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 10) OR (zoneid = 22) OR (zoneid = 25) OR (zoneid = 82) OR (zoneid = 75) OR (zoneid = 76) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28)") 
# Below makes priority stands in high and medium priority zones no harvest, and high and medium the matrix priority zones max 15% disturbance; core and matrix outside of priority stands and areas available
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 10) OR (zoneid = 22) OR (zoneid = 25) OR (zoneid = 82) OR (zoneid = 75) OR (zoneid = 76) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 27)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26) OR (zoneid = 28)") 
# Below makes priority stands in high priority zones no harvest, and high matrix priority zones max 15% disturbance; core and matrix outside of priority stands and areas available
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 10) OR (zoneid = 22) OR (zoneid = 25) OR (zoneid = 82) OR (zoneid = 75) OR (zoneid = 76) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 27) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9) OR (zoneid = 28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 26)") 






# Below makes priority stands in high and medium priority zones no harvest; core outside of priority stands available, and high and medium the matrix priority zones max 15% disturbance; low priority zones in core and matrix available
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 2) OR (zoneid = 6)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 1) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 8)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 9)") 
# Below makes priority stands in high  priority zones no harvest; core outside of priority stands available, and high matrix priority zones max 15% disturbance; medium and low priority zones in core and matrix available
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid = 2") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 8) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid = 7") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid = 7") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid = 7") 



# NORTH CARIBOO Update the constraints available to a zone as specified in the scenario
#Below will set North Cariboo old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 10) OR (zoneid = 25) OR (zoneid = 40) OR (zoneid = 54)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 71") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 71")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 9) OR (zoneid = 16) OR (zoneid = 39) OR (zoneid = 45) OR (zoneid = 60) OR (zoneid = 70)") 
#Below will set North Cariboo old and recruit as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 10) OR (zoneid = 25)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 71") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 71") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 4) OR (zoneid = 7) OR (zoneid = 14) OR (zoneid = 15) OR (zoneid = 19) OR (zoneid = 22) OR (zoneid = 30) OR (zoneid = 34) OR (zoneid = 37) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 64) OR (zoneid = 68) OR (zoneid = 75) OR (zoneid = 76) OR (zoneid = 40) OR (zoneid = 54)")
# Below makes all of core no harvest and matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9) OR (zoneid = 10) OR (zoneid = 22) OR (zoneid = 25) OR (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28) OR (zoneid = 75) OR (zoneid = 76) OR (zoneid = 77) OR (zoneid = 78)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid = 82") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid = 82") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_smc_zones_20210315' AND zoneid = 82")
# Below makes priority stands in all priority zones no harvest, core outside of priority stands available, and all the matrix priority zones max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9) OR (zoneid = 10) OR (zoneid = 22) OR (zoneid = 25) OR (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28) OR (zoneid = 75) OR (zoneid = 76) OR (zoneid = 77) OR (zoneid = 78)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 82) OR (zoneid = 97)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 82) OR (zoneid = 97)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 82) OR (zoneid = 97)")
# Below makes priority stands in high and medium priority HESR zones no harvest, and high and medium priority matrix priority zones max 15% disturbance; core and amtrix outside of priority areas and stands available,
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9) OR (zoneid = 10) OR (zoneid = 22) OR (zoneid = 25) OR (zoneid = 26) OR (zoneid = 27) OR (zoneid = 28) OR (zoneid = 75) OR (zoneid = 76) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 97)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 82)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 82)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_smc_zones_20210315' AND (zoneid = 82)")







# NARROW LAKE Update the constraints available to a zone as specified in the scenario
#Below will set Narrow Lake old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 9) OR (zoneid = 24) OR (zoneid = 39) OR (zoneid = 53)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 70") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 70")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 10) OR (zoneid = 16) OR (zoneid = 40) OR (zoneid = 45) OR (zoneid = 60) OR (zoneid = 71)") 
#Below will set Narrow Lake old and recruit as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 9) OR (zoneid = 24)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 70") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 70")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 10) OR (zoneid = 16) OR (zoneid = 39) OR (zoneid = 53) OR (zoneid = 40) OR (zoneid = 45) OR (zoneid = 60) OR (zoneid = 71)") 
#Below will set Narrow Lake HEWSR as no harvest and matrix as 12% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_narrow_lake_crithab_or_herd' AND zoneid = 2")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_narrow_lake_crithab_or_herd' AND zoneid = 2")
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_narrow_lake_crithab_or_herd' AND zoneid = 2")





dbDisconnect(clusdb)

```


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = TRUE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/TFL52_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "TFL52",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_cw", 
                                 # "rast.zone_cond_noharvest_north_cariboo_crithab_or_herd"
                                 # "rast.zone_cond_eccc_north_cariboo_crithab_or_herd"
                                 #  rast.zone_cond_noharvest_narrow_lake_crithab_or_herd" 
                                 # "rast.zone_cond_eccc_narrow_lake_crithab_or_herd"
                                 # "rast.zone_cond_noharvest_barkerville_crithab_or_herd"
                                 # "rast.zone_cond_eccc_barkerville_crithab_or_herd"
                                   "rast.zone_smc_zones_20210315"
                                 #  "rast.zone_barkerville_groundhog_zones_20210303"
                           ),
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      reportHarvestConstraints = T,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  uploaderCLUS = list(aoiName = 'tfl52', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "tfl52_bau",
#                        description = "Business-as-usual (BAU); harvest flow 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_north_cariboo_nh",
#                        description = "No harvest in North Cariboo critical habitat. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_north_cariboo_ch_he0d_m15d",
#                        description = "No harvest in North Cariboo HEWSR, maximum 35% buffered disturbance (15% harvest) in North Cariboo matrix critical habitat that overlap with the harvest unit; harvest flow 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_north_cariboo_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered North Cariboo core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in North Cariboo matrix habitat areas. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_north_cariboo_scen3b",
#                        description = "No harvest in old forest amd recruitment forest North Cariboo core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in North Cariboo matrix habitat areas. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_narrow_lake_nh",
#                        description = "No harvest in Narrow Lake critical habitat. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_narrow_lake_ch_he0d_m15d",
#                        description = "No harvest in Narrow Lake HEWSR, maximum 35% buffered disturbance (15% harvest) in Narrow Lake matrix critical habitat that overlap with the harvest unit. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_narrow_lake_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered Narrow Lake core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Narrow Lake matrix habitat areas. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_narrow_lake_scen3b",
#                        description = "No harvest in old forest and recruitment forest Narrow Lake core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Narrow Lake matrix habitat areas. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_nh",
#                        description = "No harvest in Barkerville critical habitat. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_ch_he0d_m15d",
#                        description = "No harvest in Barkerville HEWSR, maximum 35% buffered disturbance (15% harvest) in Barkerville matrix critical habitat that overlap with the harvest unit. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_scen3a",
#                        description = "No harvest in old forest, recruitment forest and buffered Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_scen3b",
#                        description = "No harvest in old forest and recruitment forest Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance (unbuffered) in Barkerville matrix habitat areas. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_he0d",
#                        description = "No harvest in Barkerville high elevation critical habitat. Harvest permitted in Barkerville matrix critical habitat. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_he0d_m12d",
#                        description = "No harvest in Barkerville high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_hi_med_lo_priority",
#                        description = "No harvest in Barkerville high priority stands in all priority HEWSR; harvest allowed in all priority matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in non-priority areas. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_barkerville_high_med_priority",
#                        description = "No harvest in Barkerville high priority stands in high and medium priority areas in high elevation critical habitat; harvest allowed in high and medium priority matrix critical habitat up to 15% disturbance (no buffer) in forested area; no constraint in low priority high elevation and matrix zones. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
scenario = data.table (name = "tfl52_barkerville_high_priority",
                       description = "No harvest in Barkerville high priority stands in high priority areas in high elevation critical habitat; harvest allowed in high priority matrix critical habitat up to 15% disturbance (no buffer) in forested area; no constraint in medium and low priority high elevation and matrix zones. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_north_cariboo_hi_med_lo_priority",
#                        description = "No harvest in North Cariboo high priority stands in all high elevation critical habitat; harvest allowed in non-priority stands; harvest allowed in all matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_north_cariboo_he0d_m12d",
#                        description = "No harvest in North Cariboo high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_north_cariboo_hi_med_priority",
#                        description = "No harvest in North Cariboo high priority stands in high and medium prioirty high elevation critical habitat. Harvest allowed in high and medium priority matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in non-priority stands and low priority HEWSR and matrix areas. Note: all areas low priority except for some high priority matrix. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_narrow_lk_he0d_m12d",
#                        description = "No harvest in Narrow Lake high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "tfl52_narrow_lk_hi_med_lo",
#                        description = "No harvest in Narrow Lake high priority stands in all high elevation critical habitat; harvest allowed in non-priority stands; harvest allowed in all matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest flow = 595,000 m3/yr. Adjacency = 3m. Oldest first.")




harvestFlow <- rbindlist(list(data.table(compartment ="TFL52",
                                         partition = ' vol > 150 ', 
                                         year = rep( seq (from = 2018, 
                                                          to = 2218, 
                                                          by = 5),
                                                    1), 
                                         flow = 2975000) #595,000m3/yr 
))


#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

