---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Morice TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Wolverine, Chase and Takla herds; to support herd planning in Wolverine, Chase and Takla, we run a sceanrio with no harvest in the  Takla HEWSR and Matrix (the other two did not overlap with the TSA); harvest is BAU in other herds; assesses the potential maximum impact of protecting these herds, assuming other herds unprotected

No harvest in all Chilcotin caribou critical habtiat; to support Chilcotin herd planning, we run a sceanrio with no harvest in the Tweedsmuir HEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Chilcotin herds only, assuming other herds unprotected

"ECCC" in chilcotin caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Tweedsmuir only

no harvest in caribou critical habtait areas; where there is cirtical habitat, no harvest in any types (including matrix); establishes the 'maximum impact' that protection of caribou habitat might potentially have on forest harvest; in Morice these include Takla herd, Telkwa HEWSR, Telkwa Matrix, Tweesdmuir HEWSR, Tweesdmuir LESR, Tweesdmuir Matrix

'ECCC' in caribou critical habtait areas; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low eleavtion cirtcial habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected

DU7 (Northern group) specific scenarios developed by caribou recovery science team. These were done for each groups of herds that overlaps the TSA. For Morice TSA, this included Tweedsmuir (group 1).

First set of scenarios uses rast.zone_du7_scenario_20210305; this raster defines priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. Scenarios:
* 3a = No harvest in old forest, recruitment forest and buffered high elevation core and low elevation summer critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance (unbuffered) in low elevation winter and matrix habitat areas

A set of scenarios were developed for the proposed Whitesail WHA. These included variaous zones with no harvest or age-based constraints, as developed by Mark Wong and Anne-Marie Roberts, Skeena region.

# Morice TSA Parameters 

## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in all herds = rast.zone_cond_noharvest_takla_crithab_or_herd,
                          rast.zone_cond_noharvest_telkwa_crithab_or_herd,
                          rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_takla_crithab_or_herd,
                          rast.zone_cond_eccc_telkwa_crithab_or_herd,
                          rast.zone_cond_eccc_tweedsmuir_crithab_or_herd

No harvest in Wolverine, Chase and Takla  = rast.zone_cond_noharvest_takla_crithab_or_herd

No harvest in Chilcotin caribou (Tweedsmuir) = rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd

ECCC in Chilcotin = rast.zone_cond_eccc_tweedsmuir_crithab_or_herd

DU7 - Northern group priority forest stand areas = "rast.zone_du7_scenario_20210305"

Whitesail:
  - "rast.whitesail_bec_20210527"
  - "rast.whitesail_management_20210527"
  - "rast.whitesail_smz_movecorr_20210527"
  - "rast.whitesail_smz_highelev_20210527"
  - "rast.whitesail_smz_calving_20210527"
  - "rast.whitesail_noharvest_20210527"

## 'harvestPriority' parameter 
- used oldest first

- as alternative,  could focus on minimizzing 'disturabnce; for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)
      
      
## 'harvestFlow'
from 2014 public discussion paper:  maximum even flow harvest was 1,600,000m^3^/year; from determination, March 16, 2020, the  AAC was set at 1,600,000 cubic metres 

- First, I tested a harvest flow of 1,500,000m^3^/year (8,000,000 m^3^/5-year); 1,400,000m^3^/year; 1.45M m^3^/year

- The discussion paper says they assumed a minimum volume of 150 cubic meters per ha.

From 2016 analysis report, used a minimum harvest age to achieve 95% of the stands maximum mean annual increment; never declared what this age was

For cutblock adjacency, I used 3 m adjacency; no real mention of this in analysis report; used 'green-up' targets at coarser scales

#UPDATE SCENARIO
```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Morice_TSA_clusdb.sqlite")) # connect to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.whitesail_bec_20210527'") 


# Whitesail scenarios
# Below makes everything a no harvest zone
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.whitesail_management_20210527'") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.whitesail_noharvest_20210527'") 

# Set no harvest zone only
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.whitesail_noharvest_20210527' AND zoneid = 2") 

# Set no harvest zone and SMZ age constraints
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.whitesail_noharvest_20210527' AND zoneid = 2") 

# Set no harvest zone and BEC 'Steventon Observed' age constraints
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.whitesail_noharvest_20210527' AND zoneid = 2") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '61' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 82")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '21' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 83") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '81' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 84") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '5' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 85") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '76' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 86") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '6' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 87") 

# Set no harvest zone and BEC 'Steventon Modeled' age constraints
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.whitesail_noharvest_20210527' AND zoneid = 2") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '48' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 82") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '28' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 83") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '85' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 84") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '7' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 85") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '64' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 86") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = '18' where reference_zone = 'rast.whitesail_bec_20210527' AND id = 87") 



# NORTHERN GROUP - Takla
# Below makes priority forest stands, all priority zones no harvest and all priority zones of the matrix and LEWR habitat areas max 15% disturbance; NOTE: all zones high priority
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 86) OR (zoneid = 71) OR (zoneid = 72) OR (zoneid = 73)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 


# NORTHERN GROUP - Telkwa
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_telkwa_crithab' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_telkwa_crithab' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_telkwa_crithab' AND (zoneid = 2)") 
# Below makes priority forest stands, all priority zones no harvest and all priority zones of the matrix and LEWR habitat areas max 15% disturbance; NOTE: all zones high priority
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69) OR (zoneid = 70) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 71) OR (zoneid = 72) OR (zoneid = 73)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74)") 


# NORTHERN GROUP - Tweedsmuir
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5)") 
# Below makes priority forest stands, all priority zones no harvest and all priority zones of the matrix and LEWR habitat areas max 15% disturbance; NOTE: all zones high priority
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69) OR (zoneid = 70) OR (zoneid = 71) OR (zoneid = 72) OR (zoneid = 73) OR (zoneid = 74)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 86)") 


# NORTHERN GROUP - GROUP 1 (Itcha, Rainbows, Charlotte, Tweeds, Telkwa)
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_telkwa_crithab' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_telkwa_crithab' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_telkwa_crithab' AND (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 5)") 
# Below makes priority forest stands, all priority zones no harvest and all priority zones of the matrix and LEWR habitat areas max 15% disturbance; NOTE: all zones high priority
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69) OR (zoneid = 70)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 71) OR (zoneid = 72) OR (zoneid = 73) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 74) OR (zoneid = 86)") 


# NORTHERN GROUP - GROUP 3 (Wolverine, Chase, Takla)
# Below makes priority forest stands, all priority zones no harvest and all priority zones of the matrix and LEWR habitat areas max 15% disturbance; NOTE: all zones high priority
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 71) OR (zoneid = 72) OR (zoneid = 73) OR (zoneid = 74) OR (zoneid = 77) OR (zoneid = 78) OR (zoneid = 79) OR (zoneid = 80) OR (zoneid = 81) OR (zoneid = 82) OR (zoneid = 86)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 67) OR (zoneid = 68) OR (zoneid = 69)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 70)") 

```









```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = TRUE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Morice_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Morice_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_cond_wha", 
                                           "rast.zone_uwr_2021", #"rast.zone_cond_uwr" 
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw",
                                           # "rast.zone_cond_noharvest_takla_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_telkwa_crithab_or_herd",
                                           # "rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd",
                                           # "rast.zone_cond_eccc_takla_crithab_or_herd",
                                           # "rast.zone_cond_eccc_telkwa_crithab_or_herd",
                                           # "rast.zone_cond_eccc_tweedsmuir_crithab_or_herd",
                                           # "rast.zone_cond_bc_takla_crithab",
                                           # "rast.zone_cond_bc_telkwa_crithab",
                                           # "rast.zone_cond_bc_tweedsmuir_crithab",
                                           # "rast.zone_du7_scenario_20210330",
                                            "rast.whitesail_bec_20210527",
                                           # "rast.whitesail_management_20210527",
                                           # "rast.whitesail_smz_movecorr_20210527",
                                           # "rast.whitesail_smz_highelev_20210527",
                                           # "rast.whitesail_smz_calving_20210527",
                                            "rast.whitesail_noharvest_20210527"
                           ),
                                           
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      reportHarvestConstraints = T,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  uploaderCLUS = list(aoiName = 'morice_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS",
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "morice_bau",
# description = "Business as usual. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_du7_grp1_nh",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_du7_grp1_he0d_mlewr12d",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# # scenario = data.table (name = "morice_du7_grp1_hi_priority",
# #                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) priority stands and all priority zones HEWSR and LESR critical habitat; harvest allowed in all priority zones of LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NOTE: all zones high priority in this unit. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# # scenario = data.table (name = "morice_du7_grp3_hi_priority",
# #                        description = "No harvest in group 3 (Wolverine, Chase, Takla) priority stands and high priority zones HEWSR and LESR critical habitat; harvest allowed in high priority zones of LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NOTE: all zones high prioirty in this unit. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_tweeds_nh",
#                        description = "No harvest in Tweedsmuir critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_tweeds_he0d_mlewr12d",
#                        description = "No harvest in Tweedsmuir HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_tweeds_hi_priority",
#                         description = "No harvest in Tweedsmuir priority stands in all priority zones HEWSR and LESR critical habitat; harvest allowed in all priority zones of LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NOTE: all zones high priority in this unit. NOTE: all zones high priority in this unit. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_telkwa_nh",
#                        description = "No harvest in Telkwa critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_telkwa_he0d_mlewr12d",
#                       description = "No harvest in Telkwa HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_telkwa_hi_priority",
#                         description = "No harvest in Telkwa priority stands in all priority zones HEWSR and LESR critical habitat; harvest allowed in all priority zones of LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NOTE: all zones high priority in this unit. NOTE: all zones are high priority in this unit. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_takla_nh",
#                        description = "No harvest in Takla critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_takla_hi_priority",
#                         description = "No harvest in Takla priority stands in all priority zones HEWSR and LESR critical habitat; harvest allowed in all priority zones of LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NOTE: all zones high priority in this unit. NOTE: all zones are high priority in this unit. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_whitesail_nh",
#                         description = "No harvest in all zones in proposed Whitesail WHA; May 2021. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_whitesail_nh_only",
#                         description = "No harvest in the no harvest zone only in the proposed Whitesail WHA; May 2021. Other harvest zones available to harvest. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_whitesail_nh_smz_age",
#                         description = "No harvest in the no harvest zone, and age constraints in special management zones in the proposed Whitesail WHA; May 2021. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_whitesail_bec1",
#                         description = "No harvest in the no harvest zone, and Steventon Observed BEC-specific age constraints within management zones in the proposed Whitesail WHA; May 2021. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")
 
scenario = data.table (name = "morice_whitesail_bec2",
                        description = "No harvest in the no harvest zone, and Steventon Modelled BEC-specific age constraints within management zones in the proposed Whitesail WHA; May 2021. Harvest flow = 1,450,000 m3/yr. Adjacency = 3m. Oldest first.")


# BELOW ARE OLD SCENARIOS THAT NEED TO BE RE-RUN
# scenario = data.table (name = "morice_northgrp_nh",
#                        description = "No harvest in Northern Group, group 1 (Telkwa, Tweedsmuir) critical habitat types. Even harvest flow = 1,700,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_northgrp_scen2",
#                        description = "No harvest in Northern Group high elevation (HEWSR) and low elevation summer (LESR) critical habitat; harvest allowed in low elevation winter (LEWR) and matrix critical habitat up to 12% forest disturbance (no buffer) in forested area. Even harvest flow = 1,700,000m3/year. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "morice_northgrp_high_med_low_priority",
#                        description = "No harvest in Northern Group high elevation (HEWSR) and low elevation summer (LESR) critical habitat priority stand types; harvest allowed in low elevation winter and matrix critical habitat up to 15% forest disturbance (no buffer) in forested area. Even harvest flow = 1,700,000m3/year. Adjacency = 3m. Oldest first.")
#scenario = data.table (name = "morice_wct_nh",
                       #description = "No harvest in Wolverine, Chase and Takla herds that overlap with the harvest unit. Adjacency was set to 3m.")
#scenario = data.table (name = "morice_chil_nh",
#                       description = "No harvest in Chilcotin herds and habitat that overlap with the harvest unit (e.g., TSA or TFL). Adjacency was set to 3m.")
#scenario = data.table (name = "morice_chil_ch_hele0d_m15d",
#                       description = "No harvest in Chilcotin high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "morice_all_herdbounds_nh",
#                        description = "No harvest in all herds that overlap with the harvest uni. Adjacency was set to 3m.")


harvestFlow <- rbindlist(list(data.table(compartment ="Morice_TSA",
                                     partition = ' vol > 150 ', #  this is the value that was used in Morice TSR 
                                     year = rep( seq (from = 2018, 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 7250000) # 1,450,000m3/yr 
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

