---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Dawson Creek TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in Central Group caribou critical habtiat; to support Central groups  planning, we run a sceanrio with no harvest in the  Central Group HEWSR, LEWSR and Matrix; harvest is BAU in other herds; assesses the potential maximum impact of protecting Central groups only, assuming other herds unprotected

"ECCC" in Central groups caribou critical habtiat; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low elevation critical habitat, and up to 35% disturbance in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Central group only

Partnership Agreement Scenario; BC, West Moberly First Nation, Saulteau First Nation and Canada have an agreement to protect certain areas in the central group; No harvest in Central group partnership agreement areas A2, B2, and B3, maximum 35%  disturbance (15%) harvest in  Central group partnership agreement areas A1, B1, B4 and B5.

No harvest in all Partnership Agreement areas; this scenario assesses the potential maximum impact of protecting all the partnership agreement areas, assuming other herds unprotected

no harvest in caribou critical habtait areas; where there is cirtical habitat, no harvest in any types (including matrix); establishes the 'maximum impact' that protection of caribou habitat might potentially have on forest harvest; in Dawson Creek TSA these include: Narraway HEWSR, Narraway HESR, Narraway HEWR, Narraway LEWR, Narraway Matrix, Quintettes HESR, Quintette HEWR, Quintette HEWSR, Quintette LEWR, Quintette Matrix, Burnt Pine HESR, Burnt Pine HEWR, Burnt Pine HEWSR, Burnt Pine Matrix, Kennedy Siding HEWSR, Kennedy Siding HESR, Kennedy Siding HEWR, Kennedy Siding Matrix, Moberly HESR, Moberly HEWSR, Moberly Matrix, Graham HEWSR, Graham HESR, Graham Matrix

'ECCC' in caribou critical habtait areas; an alternative to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no disturbance in high and low eleavtion cirtcial habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected

# Dawson Creek  TSA Parameters 

## New Caribou Constraints
BAU = beo, vqo, wha, uwr, fsw (fisheries senstive watersheds),parks and protected areas (nharv) and cw (community watersheds) 

No harvest in Central Group = "rast.zone_cond_noharvest_quintette_crithab_or_herd",
                              "rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd",
                               "rast.zone_cond_noharvest_narraway_crithab_or_herd",
                               "rast.zone_cond_noharvest_burnt_pine_crithab_or_herd",
                               "rast.zone_cond_noharvest_moberly_crithab_or_herd",

ECCC Central Group = "rast.zone_cond_eccc_burnt_pine_crithab_or_herd",
                      "rast.zone_cond_eccc_quintette_crithab_or_herd",
                      "rast.zone_cond_eccc_kennedy_siding_crithab_or_herd",
                      "rast.zone_cond_eccc_narraway_crithab_or_herd",
                      "rast.zone_cond_eccc_moberly_crithab_or_herd",

Parntership Agreement = rast.zone_cond_partnership_agreement

Parntership Agreement - ho harvest = rast.zone_cond_partnership_agreement (but change constraint to no harvest 'nh')

No harvest in all herds = "rast.zone_cond_noharvest_quintette_crithab_or_herd",
                              "rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd",
                               "rast.zone_cond_noharvest_narraway_crithab_or_herd",
                               "rast.zone_cond_noharvest_burnt_pine_crithab_or_herd",
                               "rast.zone_cond_noharvest_moberly_crithab_or_herd",
                            rast.zone_cond_noharvest_graham_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_central_rockies_crithab_or_herd,
                    rast.zone_cond_eccc_columbia_north_crithab_or_herd,
                    rast.zone_cond_eccc_columbia_south_crithab_or_herd,
                    rast.zone_cond_eccc_central_selkirks_crithab_or_herd
                    "rast.zone_cond_eccc_graham_crithab_or_herd"
                    
BAU plus the new B2 and B3 areas (new Klinse-za/Twin Sisters Park) of the caribou partnership agreement areas as protected areas (rast.central_grp_proposed_luo zones 1 and 2 = no harvest)

Also included a scenario with a harvest flow of conifer leading stands only. AAC was partitioned into confier stadns, adn there was interest in exploring that impact specifically. I included the caribou partnership agreement areas as protected areas (rast.central_grp_proposed_luo zones 1 and 2 = no harvest) in this one too. 


## 'harvestPriority' parameter 
- used oldest first

- as alternative,  could focus on minimizing 'disturbance' for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' prioritize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)
      
- Minimum harvest criteria: 120 m3/ ha 
"For the base case minimum harvestable ages were defined using height, diameter and volume
criteria. While the height and diameter minima varied according to stand quality and species, all
stands, including small pine stands (see “small pine stands” above) had to exceed a minimum
stand volume of 120 cubic metres per hectare in order to be eligible for harvest."

## 'harvestFlow'

The AAC for the Dawson Creek TSA was initially set at
1 250 000 cubic metres, of which 570 00 cubic metres and 680 000 cubic metres were for
deciduous stands and coniferous stands, respectively. Dawson Creek TSA’s allowable annual cut (AAC) is 1,860,000 cubic metres, as of October 30, 2014. 978 000 cubic metres attributable to coniferous-leading stands of which at least 100 000 cubic metres annually must be taken from stands classified as small pine; and 882 000 cubic metres attributable to deciduous-leading stands.

Harvest flow with 
- harvest flow: first tried 2M m^3^/yr, 1.75M, 1.85M, 1.8M; 
- stable harvest flow at 1.8M m^3^/yr
  - also identified non-declining harvest flow for BAU plus the B2 and B3 areas (new Klinse-za/Twin Sisters Park) of the        partnership agreement areas as protected areas; at 1.75M m^3^/yr
  
Conifer only harvest flow with (AND dec_pcnt < 0.26)
- partition to deciduous percentage (dec_pcnt) < 0.26 (26%), as per AAC determination, which defined mixedwood as anything less than 75% either conifer or deciduous.
- harvest flow: first tried 500,000m^3^/yr; 400k, 375k, 350k, 345k, 340k final

## Partnership agreement
There is a Partnership Agreement for these caribou herds that has designated zones and constraints for those zones. These can be modified using the code below.

```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Dawson_Creek_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneconstraints where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab'")


# Central Group - Draft Land Use Orders - April 23, 2021
# Below makes the B2 and B3 areas (new Klinse-za/Twin Sisters Park) of the partnership agreement areas as protected areas; everything else as available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.central_grp_proposed_luo' AND (zoneid = 1) OR (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.central_grp_proposed_luo' AND (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8)") 

# Below sets proposed maximum NRV age targets for LUO for critical habitat overlapping this unit with AGE 29 threshold
## Kennedy Siding
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 29 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 7 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 17 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 5)") 
## Moberly / Klinse-Za
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 29 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 28 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 4)") 
## Burnt Pine
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 29 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 24 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 36 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3)") 
## Quintette
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 29 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 24 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 50 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 5)") 
## Narraway
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 29 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 26 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 46 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 33 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 5)") 

# Below sets proposed maximum NRV age targets for LUO for critical habitat overlapping this unit 
## Kennedy Siding
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 7 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 17 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 5)") 
## Moberly / Klinse-Za
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 28 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 4)") 
## Burnt Pine
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 24 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 36 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3)") 
## Quintette
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 24 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 50 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 5)") 
## Narraway
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 26 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 46 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 33 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 5)") 


# Below sets proposed median NRV age targets for LUO for critical habitat overlapping this unit 
## Kennedy Siding
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 5 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 5)") 
## Moberly / Klinse-Za
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 9 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 21 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 4)") 
## Burnt Pine
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 18 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 27 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3)") 
## Quintette
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 18 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 38 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 28 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 5)") 
## Narraway
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 20 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 34 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 24 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 5)") 

# Below sets proposed minimum NRV age targets for LUO for critical habitat overlapping this unit 
## Kennedy Siding
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 3 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 7 where reference_zone = 'rast.zone_cond_bc_kennedy_siding_crithab' AND (zoneid = 5)") 
## Moberly / Klinse-Za
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 6 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 13 where reference_zone = 'rast.zone_cond_bc_moberly_crithab' AND (zoneid = 4)") 
## Burnt Pine
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3) OR (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 17 where reference_zone = 'rast.zone_cond_bc_burnt_pine_crithab' AND (zoneid = 3)") 
## Qunitette
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 18 where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 5)") 
## Narraway
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 39 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0) OR (zoneid = 4) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 14 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 0)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 23 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 16 where reference_zone = 'rast.zone_cond_bc_narraway_crithab' AND (zoneid = 5)") 


# NORTHERN GROUP - GROUP 2 (Graham)
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_graham_crithab' AND (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_graham_crithab' AND (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_graham_crithab' AND (zoneid = 3)") 
# Below makes priority forest stands no harvest and all of the matrix and LEWR habitat areas max 15% disturbance; NOTE all zones high priority
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 22) OR (zoneid = 24)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 25)") 

# LUO constraints
dbExecute(clusdb, "UPDATE zoneconstraints set multi_condition = NULL where reference_zone = 'rast.central_grp_proposed_luo_feb2021'") # age < 12 OR height < 2.5
dbExecute(clusdb, "UPDATE zoneconstraints set variable = 'height' where reference_zone = 'rast.central_grp_proposed_luo_feb2021'") # height, age
dbExecute(clusdb, "UPDATE zoneconstraints set threshold = '2.5' where reference_zone = 'rast.central_grp_proposed_luo_feb2021'") # 2.5, 25


#STEP 4: Remove the connection to the database
dbDisconnect(clusdb)
```

## Below is a code for switching from a disturbance ('dist') to forest attribute ('age', height') constraint type
Disturbance constraint types calculates the percent area disturbed over forested area, whereas forest stand attributes constraint types are calculated over total area of the zone. Thus, if you have a zone initially parameterized with a disturbance constraint and want to use the same zone with a forest stand attributes constraint, you need to change the total area (t_area) from forested area to total zone area (or vice-versa). The code chunk below demonstrates how to do that,

```{r, change dist to forest attribute constraint type}

# connect to the db
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Dawson_Creek_TSA_clusdb.sqlite"))

# identify zone column names of the zones of interest
dbGetQuery(clusdb, "SELECT reference_zone, zone_column, zoneid from zoneConstraints where 
reference_zone = 'rast.zone_cond_bc_quintette_crithab'") 
# rast.zone_cond_bc_moberly_crithab, rast.zone_cond_bc_burnt_pine_crithab, rast.zone_cond_bc_quintette_crithab, rast.zone_cond_bc_kennedy_siding_crithab, rast.zone_cond_bc_narraway_crithab
 
 
# for each zone that you want to change:
## calc the total area of the zone 
count <- dbGetQuery(clusdb, "SELECT count() from pixels where zone26 = 5") 

## update to the total area in the constraint table for the zone
dbExecute(clusdb, paste0("UPDATE zoneConstraints SET t_area = ", count, " where reference_zone = 'rast.zone_cond_bc_quintette_crithab' AND (zoneid = 5)")) 

# to check it
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneconstraints where reference_zone = 'rast.zone_cond_bc_quintette_crithab'")                  
 

```


## Below is the code chunk for running the sim

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( 
                           dbName='clus',
                           save_clusdb = TRUE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Dawson_Creek_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Dawson_Creek_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c(
                                               # "rast.zone_cond_beo",
                                               # "rast.zone_cond_vqo",
                                               # "rast.zone_cond_wha",
                                               # "rast.zone_uwr_2021", #"rast.zone_cond_uwr"
                                               # "rast.zone_cond_fsw",
                                               # "rast.zone_cond_nharv",
                                               # "rast.zone_cond_cw",
                                               # 
                                             # 'rast.zone_cond_partnership_agreement',
                                             # 'rast.zone_cond_partnership_agreement',
                                             # "rast.zone_cond_noharvest_graham_crithab_or_herd",                                                                        "rast.zone_cond_noharvest_moberly_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_hart_ranges_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_burnt_pine_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_quintette_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd",
                                             # "rast.zone_cond_noharvest_narraway_crithab_or_herd",
                                             # "rast.zone_cond_eccc_graham_crithab_or_herd",                                                                             "rast.zone_cond_eccc_moberly_crithab_or_herd",
                                             # "rast.zone_cond_eccc_hart_ranges_crithab_or_herd",
                                             # "rast.zone_cond_eccc_burnt_pine_crithab_or_herd",
                                             # "rast.zone_cond_eccc_quintette_crithab_or_herd",
                                             # "rast.zone_cond_eccc_kennedy_siding_crithab_or_herd",
                                             # "rast.zone_cond_eccc_narraway_crithab_or_herd",
                                             # "rast.zone_cond_bc_graham_crithab",
                             
                                              "rast.zone_cond_bc_moberly_crithab",
                                             "rast.zone_cond_bc_burnt_pine_crithab",
                                             "rast.zone_cond_bc_quintette_crithab",
                                             "rast.zone_cond_bc_kennedy_siding_crithab",
                                             "rast.zone_cond_bc_narraway_crithab"
                                             
                                             # "rast.zone_cond_bc_hart_ranges_crithab",
                                             # "rast.central_grp_proposed_luo"
                                             # "rast.central_grp_proposed_luo_buffer",
                                             # "rast.central_grp_proposed_luo_matrix",
                                             # "rast.central_grp_proposed_luo_feb2021"
                                             # "rast.zone_du7_scenario_20210330"
                                               ),
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "age DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      reportHarvestConstraints = T,
                      adjacencyConstraint = 0), #3
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
    volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  uploaderCLUS = list(aoiName = 'dawson_creek_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# scenario = data.table (name = "dawson_creek_bau",
#                        description = "Business-as-usual case. Harvest flow = 1,800,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_luo_35p_25yo_250cm",
#                        description = "Central group proposed land use order; area less than 35% less than 25 years old or less than 2.5 m tall. Oldest first. Adjacency = 3. Harvest flow = 1,800,000m3/yr.")
# scenario = data.table (name = "dawson_luo_35p_25yo",
#                        description = "Central group proposed land use order; area less than 35% less than 25 years old. Oldest first. Adjacency = 3. Harvest flow = 1,800,000m3/yr.")
# scenario = data.table (name = "dawson_luo_35p_250cm",
#                        description = "Central group proposed land use order; area less than 35% less than 2.5 m tall. Oldest first. Adjacency = 3. Harvest flow = 1,800,000m3/yr.")
# scenario = data.table (name = "dawson_ck_du7_grp2_nh",
#                        description = "No harvest in group 2 (Graham) critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow = 1,800,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_ck_du7_grp2_he0d_mlewr12d",
#                        description = "No harvest in group 2 (Graham)  HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 1,800,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_ck_du7_grp2_hi_priority",
#                        description = "No harvest priority stands in high priority zones in group 2 Graham) HEWSR and LESR critical habitat; harvest allowed in high priority zones in LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in low and medium priority zones. NOTE: all zones in this unit are high priority. Harvest flow = 1,800,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_creek_bau_newpark",
#                        description = "Business-as-usual case with Klinse-za/Twin Sisters park (B2 and B3 areas) from parntership agreement  added as no harvest. Harvest flow = 1,750,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_creek_centgrp_luo_age_le40",
#                        description = "Draft land use order early seral (age) thresholds for central group critical habitat, April 26, 2021.  Harvest flow = 1,750,000m3/yr. Adjacency = 3m. Oldest first.")

# scenario = data.table (name = "dawson_creek_centgrp_luo_age_le40_modNRV",
#                        description = "Draft land use order early seral (age) thresholds for central group critical habitat, April 26, 2021. Moderate natural range of variability (NRV) early seral targets. Harvest flow = 1,750,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_creek_bau_newpark_conif",
#                        description = "Business-as-usual case with Klinse-za/Twin Sisters park (B2 and B3 areas) from parntership agreement added as no harvest. Conifer leading stands (deciduous percentage < 26%) only. Harvest flow = 340,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_creek_bau_newpark_conif_age_le40_minNRV",
#                        description = "Business-as-usual case with Klinse-za/Twin Sisters park (B2 and B3 areas) from parntership agreement added as no harvest. Minimum natural range of variability (NRV) early seral targets in caribou critical habitat.  Conifer leading stands (deciduous percentage < 26%) only. Harvest flow = 340,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_creek_bau_newpark_conif_age_le40_modNRV",
#                        description = "Business-as-usual case with Klinse-za/Twin Sisters park (B2 and B3 areas) from parntership agreement added as no harvest. Moderate natural range of variability (NRV) early seral targets in caribou critical habitat.  Conifer leading stands (deciduous percentage < 26%) only. Harvest flow = 340,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_creek_centgrp_luo_age_le40_maxNRV",
#                        description = "Draft land use order early seral (age) thresholds for central group critical habitat, April 26, 2021. Maximum natural range of variability (NRV) early seral targets. Harvest flow = 1,750,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawsonck_centgrp_agele30_maxnrv",
#                        description = "Draft land use order early seral (age) thresholds for central group critical habitat, April 26, 2021. Early seral targets set for maximum natural range of variability (NRV) for each area, using age <30 as early seral. Harvest flow = 1,750,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawsonck_centgrp_agele20_maxnrv",
#                        description = "Draft land use order early seral (age) thresholds for central group critical habitat, April 26, 2021. Early seral targets set for maximum natural range of variability (NRV) for each area, using age <20 as early seral. Harvest flow = 1,750,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawsonck_centgrp_agele10_maxnrv",
#                        description = "Draft land use order early seral (age) thresholds for central group critical habitat, April 26, 2021. Early seral targets set for maximum natural range of variability (NRV) for each area, using age <10 as early seral. Harvest flow = 1,750,000m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "dawson_creek_bau_newpark_noadj",
#                        description = "Business-as-usual case with Klinse-za/Twin Sisters park (B2 and B3 areas) from parntership agreement  added as no harvest. Harvest flow = 1,800,000m3/yr. No adjacency. Oldest first.")
# scenario = data.table (name = "dawson_creek_bau_no_constraints",
#                        description = "Business-as-usual case with no constraints. Harvest flow = 2,050,000m3/yr. No adjacency. Oldest first.")
# scenario = data.table (name = "dawson_creek_agele40_maxnrv_no_constraints",
#                        description = "No constraints except Early seral targets set for maximum natural range of variability (NRV) for each area, using age <40 as early seral. Harvest flow = 2,050,000m3/yr. No adjacency. Oldest first.")
# scenario = data.table (name = "dawson_creek_bau_no_constraints_no_min",
#                        description = "Business-as-usual case with no constraints. Harvest flow = 2,150,000m3/yr. No adjacency. No minimum volume. Oldest first.")
# scenario = data.table (name = "dawson_creek_agele20_maxnrv_no_const_no_min",
#                        description = "No constraints except Early seral targets set for maximum natural range of variability (NRV) for each area, using age <20 as early seral. Harvest flow = 2,150,000m3/yr. No adjacency. No minimum volume. Oldest first.")
# scenario = data.table (name = "dawson_creek_agele40_maxnrv_no_adj",
#                        description = "Draft land use order early seral (age) thresholds for central group critical habitat, April 26, 2021. Early seral targets set for maximum natural range of variability (NRV) for each area, using age <40 as early seral. Harvest flow = 1,750,000m3/yr. No adjacency. Oldest first.")
# scenario = data.table (name = "dawson_creek_agele20_maxnrv_no_adj",
#                        description = "No constraints except Early seral targets set for maximum natural range of variability (NRV) for each area, using age <20 as early seral. Harvest flow = 1,750,000m3/yr. No adjacency. Minimum volume = 120m3/ha. Oldest first.")

scenario = data.table (name = "dawson_creek_agele20_maxnrv_no_constraints",
                       description = "No constraints except Early seral targets set for maximum natural range of variability (NRV) for each area, using age <20 as early seral. Harvest flow = 2,050,000m3/yr. No adjacency. Oldest first.")

# BELOW ARE OLD SCENARIOS THAT NEED TO BE RE-RUN
# scenario = data.table (name = "dawson_centgrp_nh",
#                        description = "No harvest in all central group critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "dawson_centgrp_ch_hele0d_m15d",
#                        description = "No harvest in Central group high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central group matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "dawson_centgrp_pa_ch_a2b2b3_0d_a1b1b4b5_15d",
#                        description = "No harvest in Central group partnership agreement areas A2, B2, and B3, maximum 35% buffered disturbance (15% havrest) in  Central group partnership agreement areas A1, B1, B4 and B5. Adjacency was set to 3m.")
# scenario = data.table (name = "dawson_centgrp_pa_nh",
#                        description = "No harvest in all Central group partnership agreement areas. Adjacency was set to 3m.")
# scenario = data.table (name = "dawson_all_nh",
#                        description = "No harvest in all critical habitat of all herds that overlap with the harvest unit. Adjacency was set to 3m.")
# scenario = data.table (name = "dawson_all_ch_hele0d_m15d",
#                        description = "No harvest in high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit↨. Adjacency was set to 3m.")
# scenario = data.table (name = "dawson_luo_35p_25yo",
#                        description = "Central group proposed land use order. Maximum 35% less than 25 years old.")




# harvestFlow <- rbindlist(list(data.table(compartment ="Dawson_Creek_TSA",
#                                      partition = ' vol > 120 ', 
#                                      year = rep( seq (from = 2018, 
#                                                       to = 2222, 
#                                                       by = 5),
#                                                 1), 
#                                      flow = 9000000) # 1,800,000m3/yr / BAU, no new protected area
# ))

harvestFlow <- rbindlist(list(data.table(compartment ="Dawson_Creek_TSA",
                                     partition = ' vol > 120 ', # 120
                                     year = rep( seq (from = 2018,
                                                      to = 2222,
                                                      by = 5),
                                                1),
                                     flow = 8750000) #1,750,000m3/yr / BAU with new protected area
))
# 
# harvestFlow <- rbindlist(list(data.table(compartment ="Dawson_Creek_TSA",
#                                      partition = ' vol > 120 AND dec_pcnt < 0.26 ', #
#                                      year = rep( seq (from = 2018,
#                                                       to = 2222,
#                                                       by = 5),
#                                                 1),
#                                      flow = 1700000) #340,000m3/yr / conifer leading stands only / BAU with new protected area
#                         ))


#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

