---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Arrow TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

no harvest in caribou critical habtait areas; where there is cirtical habitat, no harvest in any types (includign matrix); establishes the 'maximum impact' that protection fo cariobu habtait might potentially have on forest harvest; in Arrow these include Central Selkirks HEWSR, Central Selkirks Matrix, Columbia South Matrix, Monashee Matrix, Monashee HEWSR, South Selkirks Matrix, South Selkirks HEWSR

'ECCC' in caribou critical habtait areas; an alterantive to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no harvest in high adn low eleavtion cirtcial habtiat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order; assumes all herds protected

no harvest in Central Selkirks caribou critical habtiat; to support Central Selkirks herd planning, we run a sceanrio with no harvest in the  Central Selkirks HEWSR and Matrix; harvest is BAU in other herds; assesses teh potential maximum impact of protecting Central Selkirks  only, assuming other herds unprotected

ECCC in Central Selkirks caribou critical habtiat; an alterantive to a no harvest scenario, attemps to interpret the federal recovery strategy that stipulates no harvest in high and low elevation critical habitat, and up to 35% disturabnce in matrix habtiat; this is a possible scenario if Canada were to enact an emergency order on Central Selkirks only


# Arrow TSA Parameters 

## New Caribou Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 

No harvest in all herds = rast.zone_cond_noharvest_central_selkirks_crithab_or_herd,
                          rast.zone_cond_noharvest_columbia_south_crithab_or_herd,
                          rast.zone_cond_noharvest_monashee_crithab_or_herd,
                          rast.zone_cond_noharvest_south_selkirks_crithab_or_herd

ECCC in all herds = rast.zone_cond_eccc_central_selkirks_crithab_or_herd,
                    rast.zone_cond_eccc_columbia_south_crithab_or_herd,
                    rast.zone_cond_eccc_monashee_crithab_or_herd,
                    rast.zone_cond_eccc_south_selkirks_crithab_or_herd

No harvest in Central Selkirks = rast.zone_cond_noharvest_central_selkirks_crithab_or_herd

ECCC Central Selkirks = rast.zone_cond_eccc_central_selkirks_crithab_or_herd

## 'harvestPriority' parameter 
- focus on minimizzing 'disturabnce; for cariobu, then older, higher vlomue stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

## 'harvestFlow'
from 2017 determination: maximum even flow harvest was 540,000m^3^/year 
- First, I tested a harvest flow of 540,000m^3^/year (2,780,000m^3^/5-year); was nto able to achieve this after 50 years, so dropped to 450,000, then 400,000, 350,000, 325,000, 335,000, 340,000, and 345,000; the latetr provided max. even flow

why was this model max even flow at 2/3 or previosu model? maybe adjacney?, maybe min. volume? or maybe harvest queue? no dications in TSR documentation of signficant inventory or yeidl probelms 


From 2016 data package, "In natural stands a minimum volume of 150 cubic metres per hectare will be used as a surrogate for minimum age in the model. In managed stands the age at which the stands reaches 95% culmination of mean annual increment will be used as minimum harvestable age." "With genetic gain and new PEM/SIBEC site indices, using only a volume of 150 m3 is unrealistic as some of the higher SI sites could achieve this in as little as 40 years."

- I used 150 m3/ha as minimum harvest volume, thus may be a bit low

For cutblock adjacency, in data package, allowed maximum 33% height ≤ 2.5 m THLB by landscape unit; I used 3 m adjacncey; thus is a bit conservative


```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list(   dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Arrow_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Arrow_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018',
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_cond_wha", 
                                               "rast.zone_cond_uwr",
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               # "rast.zone_cond_eccc_central_selkirks_crithab_or_herd"
                                              #"rast.zone_cond_noharvest_central_selkirks_crithab_or_herd"
                                               # "rast.zone_cond_noharvest_columbia_south_crithab_or_herd"
                                               # "rast.zone_cond_noharvest_monashee_crithab_or_herd"
                                               # "rast.zone_cond_noharvest_south_selkirks_crithab_or_herd"
                                               # "rast.zone_cond_eccc_columbia_south_crithab_or_herd"
                                               # "rast.zone_cond_eccc_monashee_crithab_or_herd"
                                                "rast.zone_cond_eccc_south_selkirks_crithab_or_herd"
                                               ),
                           nameZoneTable = "zone_constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestPriority = "dist, age DESC, vol DESC",
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval = 5, 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  uploaderCLUS = list(aoiName = 'arrow_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS", 
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU7' and  species = 'caribou' and season IN ('A')"))
# rsf_model_coeff[, bounds := 'rast.bc_crithab_and_herd']

# scenario = data.table (name = "arrow_bau",
#                        description = "Business-as-usual case; sustainable flow = 345,000m3/yr.Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_centselk_nh",
#                        description = "No harvest in Central Selkirks critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_centselk_ch_he0d_m15d",
#                        description = "No harvest in Central Selkirks high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central Selkirks matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_all_nh",
#                        description = "No harvest in all critical habitat of all herds that overlap with the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_all_ch_he0d_m15d",
#                        description = "No harvest in high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_columbia_south_nh",
#                        description = "No harvest in critical habitat of Columbia South herd that overlaps with the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_ccolumbia_south_ch_he0d_m15d",
#                        description = "No harvest in Columbia South high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Columbia South matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_monashee_nh",
#                        description = "No harvest in critical habitat of Monashee herd that overlaps with the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_monashee_ch_he0d_m15d",
#                        description = "No harvest in Monashee high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Monashee matrix critical habitat. Adjacency was set to 3m.")
# 
# scenario = data.table (name = "arrow_central_selkirks_nh",
#                        description = "No harvest in critical habitat of Central Selkirks herd that overlaps with the TSA. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_central_selkirks_ch_he0d_m15d",
#                        description = "No harvest in Central Selkirks high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Central Selkirks matrix critical habitat. Adjacency was set to 3m.")
# scenario = data.table (name = "arrow_south_selkirks_nh",
#                        description = "No harvest in critical habitat of South Selkirks herd that overlaps with the TSA. Adjacency was set to 3m.")
scenario = data.table (name = "arrow_south_selkirks_ch_he0d_m15d",
                       description = "No harvest in South Selkirks high elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in South Selkirks matrix critical habitat. Adjacency was set to 3m.")



harvestFlow <- rbindlist(list(data.table(compartment ="Arrow_TSA",
                                     partition = ' vol > 150 ', 
                                     year = rep( seq (from = 2018, 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 1725000) #345,000m3/yr 
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC)) # if > 1 harvest flow

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

