---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the anlayst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Williams Lake TSA Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat

No harvest in Chilcotin critical habitat that overlap with the harvest unit (e.g., TSA or TFL). This implies no harvest in caribou herd or critical habtait areas; where there is critical habtait, no harvest in any types (including matrix), and where therre is no critical habtiat, no harvest anywhere in the herd boudanries (assumes all critical hbaitat); establishes the 'maximum impact' that protection fo caribou habitat might potentially have on forest harvest. 

No harvest in Chilcotin high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat

No harvest in all herds that overlap with the harvest unit (e.g., TSA or TFL)

No harvest in high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit

DU9 specific scenarios developed by caribou recovery science team. These were done for each herd indivudalls that overlaps the TSA:
First set of scenarios uses rast.zone_du9_scenarios; this raster defines priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. Scenarios:
* 3a = No harvest in old forest, recruitment forest and buffered Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance in Barkerville matrix habitat areas
* 3b = No harvest in old forest and recruitment forest Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 35% buffered disturbance in Barkerville matrix habitat areas.

Second set of scenarios uses rast.zone_barkerville_groundhog_zones_20210303; this raster defines some priority matrix and core areas, and priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. scenarios:
* 2 or he0d_m12d; sets no harvest in all core priority zones and 12% max disturbance in all matrix priority zones
* high_med_low_priority (new 3a): sets no harvest in priority stands in all core priority zones and 15% max disturbance in all matrix priority zones
* high_med_priority (new 3b); sets no harvest in priority stands in high and medium core priority zones and 15% max disturbance in high and medium matrix priority zones
* high_priority (new 3c); sets no harvest in priority stands in high core priority zones and 15% max disturbance in high and medium matrix priority zones

DU7 (Northern group) specific scenarios developed by caribou recovery science team. These were done for each groups of herds that overlaps the TSA. For Williams Lake TSA, this included Itcha, Rainbows and Charlotte (group 1).
First set of scenarios uses rast.zone_du7_scenario_20210305; this raster defines priority forest stands for 'protection', i.e., old or close to old stands, plus a 500m buffer. Scenarios:
* 3a = No harvest in old forest, recruitment forest and buffered high elevation core and low elevation summer critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance (unbuffered) in low elevation winter and matrix habitat areas


# Williams Lake TSA Parameters 

## New Caribou Constraints
BAU = beo, vqo, wha, uwr, fsw (fisheries senstive watersheds),parks and protected areas (nharv) and cw (community watersheds) 

willake_chil_nh = BAU + no harvest in Chilcotin critical habitat that overlap with the harvest unit (e.g., TSA or TFL)

willake_chil_ch_hle0d_m15d = BAU + no harvest in Chilcotin high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in Chilcotin matrix critical habitat

willake_all_nh = BAU + No harvest in all herds that overlap with the harvest unit (e.g., TSA or TFL). All (Charlotte Alplands HEWSR, Charlotte Alplands LEWR, Charlotte Alplands Matrix, Itcha-Ilgachuz HEWSR, Itcha-Ilgachuz LESR, Itcha-Ilgachuz LEWR, Itcha-Ilgachuz Matrix, Rainbows HEWSR, Rainbows LESR, Rainbows LEWR, Rainbows Matrix, Barkerville HEWSR, Barkerville Matrix, Wells Gray North HEWSR, Wells Gray North Matrix).

willake_all_ch_hele0d_m15d = BAU + No harvest in high and low elevation critical habitat, maximum 35% buffered disturbance (15% harvest) in matrix critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL)

DU 9 scenarios version 1 = rast.zone_du9_scenarios

DU 9 Groundhog scenarios version 2 = rast.zone_barkerville_groundhog_zones_20210303

DU7 - Northern group priority forest stand areas = "rast.zone_du7_scenario_20210305"

## 'harvestPriority' parameter 
- used oldest first

- as alternative,  could focus on minimizzing 'disturabnce; for caribou, then older, higher volume stands
  - 'dist, age DESC, vol DESC' priortize based on:
      - 'dist', i.e., distance to disturbed pixel (closest first), then
      - 'age DESC', i.e., descending age (oldest first), then
      - 'vol DESC', i.e., descending volume (highest volume first)

-Minimum harest criteria - 80 m3/ha for pine and 120 m3/ha for non pine.

## 'harvestFlow'

The allowable annual cut (AAC) for the Williams Lake TSA is 3 million cubic metres as of February 25, 2015. This includes a partition of a maximum of 1 500 000 cubic metres per year for live volume which means the remainder of the AAC is for salvaging dead trees

With oldest first priority
- I tested a harvest flow of 1.5 Mm3 (7,500,000m3/5yr) and the model was successful at meeting this demand with 
- I increased the harvest flow to 1.856 Mm3 (9,280,000m3/5yr) from an earlier analysis
- tested 1.75M m3/year 2M m3/year, 2.5M m3/year, 2.25M m3/year, 2.4M m3/year, 2.35M m3/year
- able to achieve 2.35M m3/year for 200 years

Closest to disturbance, oldest, highest volume first:
- tested 2.35, 1.85, 1.75, 1.7, 1.65 m3/year


#UPDATE SCENARIO

## Chilcotin Planning Scenarios Aug. 2021 
```{r, zone_update}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Williams_Lake_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab'") 
# rast.zone_cond_bc_itcha_ilgachuz_crithab",  "rast.zone_cond_bc_charlotte_alplands_crithab", "rast.zone_cond_bc_rainbows_crithab", "rast.zone_cond_bc_tweedsmuir_crithab"  rast.zone_du7_scenario_20210330  rast.zone_wha_2021


# Chilcotin Scenarios - Aug. 2021
## Existing caribou WHA GARs removed; forest age constraints applied to critical habitat
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' WHERE reference_zone = 'rast.zone_wha_2021' AND (zoneid = 263) OR (zoneid = 264) OR (zoneid = 3779) OR (zoneid = 3780) OR (zoneid = 3781)") 

## Scenario 1 forest age constraints applied to all to critical habitat
## Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 141 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 4)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 141 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'age' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 141 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 0) OR (zoneid = 3) OR (zoneid = 2)")
## Need to create some new rows for multiple age constraints
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2844,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',121,'ge',30,NULL,NULL,160617,0,250),
(2845,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',121,'ge',30,NULL,NULL,585069,0,250),
(2846,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',121,'ge',30,NULL,NULL,529995,0,250),
(2847,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',101,'ge',37,NULL,NULL,160617,0,250),
(2848,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',101,'ge',37,NULL,NULL,585069,0,250),
(2849,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',101,'ge',37,NULL,NULL,529995,0,250),
(2850,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',81,'ge',45,NULL,NULL,160617,0,250),
(2851,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',81,'ge',45,NULL,NULL,585069,0,250),
(2852,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',81,'ge',45,NULL,NULL,529995,0,250);")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2853,0,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',121,'ge',30,NULL,NULL,93677,0,250),
(2854,2,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',121,'ge',30,NULL,NULL,44178,0,250),
(2855,3,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',121,'ge',30,NULL,NULL,79918,0,250),
(2856,0,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',101,'ge',37,NULL,NULL,93677,0,250),
(2857,2,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',101,'ge',37,NULL,NULL,44178,0,250),
(2858,3,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',101,'ge',37,NULL,NULL,79918,0,250),
(2859,0,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',81,'ge',45,NULL,NULL,93677,0,250),
(2860,2,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',81,'ge',45,NULL,NULL,44178,0,250),
(2861,3,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',81,'ge',45,NULL,NULL,79918,0,250);")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2862,0,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',121,'ge',30,NULL,NULL,41182,0,250),
(2863,3,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',121,'ge',30,NULL,NULL,45116,0,250),
(2864,4,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',121,'ge',30,NULL,NULL,10929,0,250),
(2865,0,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',101,'ge',37,NULL,NULL,41182,0,250),
(2866,3,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',101,'ge',37,NULL,NULL,45116,0,250),
(2867,4,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',101,'ge',37,NULL,NULL,10929,0,250),
(2868,0,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',81,'ge',45,NULL,NULL,41182,0,250),
(2869,3,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',81,'ge',45,NULL,NULL,45116,0,250),
(2870,4,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',81,'ge',45,NULL,NULL,10929,0,250);")

## Scenario 2 forest age constraints applied to all to critical habitat
## Seral stage >80 = 37%; Seral stage >100 = 30%; Seral stage >120 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2678) OR (id = 2679) OR (id = 2680)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2844) OR (id = 2845) OR (id = 2846)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2847) OR (id = 2848) OR (id = 2849)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2850) OR (id = 2851) OR (id = 2852)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2681) OR (id = 2682) OR (id = 2683)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2853) OR (id = 2854) OR (id = 2855)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2856) OR (id = 2857) OR (id = 2858)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2859) OR (id = 2860) OR (id = 2861)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2684) OR (id = 2685) OR (id = 2686)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2862) OR (id = 2863) OR (id = 2864)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2865) OR (id = 2866) OR (id = 2867)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2868) OR (id = 2869) OR (id = 2870)")

## Scenario 3 forest age constraints applied to all to critical habitat
## Seral stage >80 = 30%; Seral stage >100 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2678) OR (id = 2679) OR (id = 2680) OR (id = 2844) OR (id = 2845) OR (id = 2846)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2847) OR (id = 2848) OR (id = 2849)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2850) OR (id = 2851) OR (id = 2852)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2681) OR (id = 2682) OR (id = 2683) OR (id = 2853) OR (id = 2854) OR (id = 2855)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2856) OR (id = 2857) OR (id = 2858)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2859) OR (id = 2860) OR (id = 2861)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2684) OR (id = 2685) OR (id = 2686) OR (id = 2862) OR (id = 2863) OR (id = 2864)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2865) OR (id = 2866) OR (id = 2867)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2868) OR (id = 2869) OR (id = 2870)")

## Scenario 1, with rotation age
## Need to create some new rows for rotation age
## Here I am saying, allow harvest in up to 3% of the area in a five year period (equivalent to 0.6% harvested annually), and make all stands available to harvest (i.e., age <= 99,999 years old)
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2871,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',99999,'le',3,NULL,NULL,160617,0,250),
(2872,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',99999,'le',3,NULL,NULL,585069,0,250),
(2873,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',99999,'le',3,NULL,NULL,529995,0,250);")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2874,0,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',99999,'le',3,NULL,NULL,93677,0,250),
(2875,2,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',99999,'le',3,NULL,NULL,44178,0,250),
(2876,3,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',99999,'le',3,NULL,NULL,79918,0,250);")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2877,0,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',99999,'le',3,NULL,NULL,41182,0,250),
(2878,3,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',99999,'le',3,NULL,NULL,45116,0,250),
(2879,4,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',99999,'le',3,NULL,NULL,10929,0,250);")

## Scenario 2, with rotation age 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2678) OR (id = 2679) OR (id = 2680)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2844) OR (id = 2845) OR (id = 2846)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2847) OR (id = 2848) OR (id = 2849)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2850) OR (id = 2851) OR (id = 2852)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 4 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2871) OR (id = 2872) OR (id = 2873)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2681) OR (id = 2682) OR (id = 2683)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2853) OR (id = 2854) OR (id = 2855)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2856) OR (id = 2857) OR (id = 2858)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2859) OR (id = 2860) OR (id = 2861)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 4 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2874) OR (id = 2875) OR (id = 2876)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2684) OR (id = 2685) OR (id = 2686)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2862) OR (id = 2863) OR (id = 2864)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2865) OR (id = 2866) OR (id = 2867)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2868) OR (id = 2869) OR (id = 2870)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 4 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2877) OR (id = 2878) OR (id = 2879)")

## Scenario 3, with rotation age 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2678) OR (id = 2679) OR (id = 2680) OR (id = 2862) OR (id = 2863) OR (id = 2864)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2865) OR (id = 2866) OR (id = 2867)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2868) OR (id = 2869) OR (id = 2870)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 5 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2877) OR (id = 2878) OR (id = 2879)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2681) OR (id = 2682) OR (id = 2683) OR (id = 2853) OR (id = 2854) OR (id = 2855)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2856) OR (id = 2857) OR (id = 2858)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2859) OR (id = 2860) OR (id = 2861)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 5 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2874) OR (id = 2875) OR (id = 2876)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2678) OR (id = 2679) OR (id = 2680) OR (id = 2844) OR (id = 2845) OR (id = 2846)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2847) OR (id = 2848) OR (id = 2849)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2850) OR (id = 2851) OR (id = 2852)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 5 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2871) OR (id = 2872) OR (id = 2873)")

## Scenario 4
# Seral stage >40 = 85%; Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2678) OR (id = 2679) OR (id = 2680) OR (id = 2844) OR (id = 2845) OR (id = 2846)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2678) OR (id = 2679) OR (id = 2680)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2844) OR (id = 2845) OR (id = 2846)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2847) OR (id = 2848) OR (id = 2849)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 45 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2850) OR (id = 2851) OR (id = 2852)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 3 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (id = 2871) OR (id = 2872) OR (id = 2873)")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2880,0,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',41,'ge',85,NULL,NULL,160617,0,250),
(2881,3,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',41,'ge',85,NULL,NULL,585069,0,250),
(2882,4,'rast.zone_cond_bc_itcha_ilgachuz_crithab','zone21',0,'age',41,'ge',85,NULL,NULL,529995,0,250);")

dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2681) OR (id = 2682) OR (id = 2683) OR (id = 2853) OR (id = 2854) OR (id = 2855)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2681) OR (id = 2682) OR (id = 2683)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2853) OR (id = 2854) OR (id = 2855)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2856) OR (id = 2857) OR (id = 2858)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 45 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2859) OR (id = 2860) OR (id = 2861)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 3 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (id = 2874) OR (id = 2875) OR (id = 2876)")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2883,0,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',41,'ge',85,NULL,NULL,93677,0,250),
(2884,2,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',41,'ge',85,NULL,NULL,44178,0,250),
(2885,3,'rast.zone_cond_bc_charlotte_alplands_crithab','zone22',0,'age',41,'ge',85,NULL,NULL,79918,0,250);")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2684) OR (id = 2685) OR (id = 2686) OR (id = 2862) OR (id = 2863) OR (id = 2864)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 25 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2684) OR (id = 2685) OR (id = 2686)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 30 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2862) OR (id = 2863) OR (id = 2864)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 37 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2865) OR (id = 2866) OR (id = 2867)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 45 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2868) OR (id = 2869) OR (id = 2870)")
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 3 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (id = 2877) OR (id = 2878) OR (id = 2879)")
dbExecute(clusdb, "INSERT INTO zoneconstraints (id, zoneid, reference_zone, zone_column, ndt, variable, threshold, type, percentage, denom, multi_condition, t_area, start, stop)
VALUES 
(2886,0,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',41,'ge',85,NULL,NULL,41182,0,250),
(2887,3,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',41,'ge',85,NULL,NULL,45116,0,250),
(2888,4,'rast.zone_cond_bc_rainbows_crithab','zone23',0,'age',41,'ge',85,NULL,NULL,10929,0,250);")



dbDisconnect(clusdb)
```

## Chilcotion Disturbance-based Scenarios

```{r chilcotin disturbance scenarios}
#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Williams_Lake_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab'") 
# rast.zone_cond_bc_itcha_ilgachuz_crithab",  "rast.zone_cond_bc_charlotte_alplands_crithab", "rast.zone_cond_bc_rainbows_crithab", "rast.zone_cond_bc_tweedsmuir_crithab"  rast.zone_du7_scenario_20210330  rast.zone_wha_2021

# Charlotte
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 3) OR (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 3) OR (zoneid = 2)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 3) OR (zoneid = 2)") 
# Below makes HEWSR and LESR high and low priority areas no harvest and high and low priority matrix and LEWR habitat areas max 15% disturbance; NOTE: only high and low priority zones in this unit
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND      (zoneid = 28) OR (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR
(zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61) OR
(zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8)")
# Below makes HEWSR and LESR high priority areas no harvest and high priority matrix and LEWR habitat areas max 15% disturbance; low priority zones available to forest harvest; NOTE: only high and low priority zones in this unit
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND      (zoneid = 28) OR (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR
(zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61) OR
(zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 8)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7)")


# Rainbows
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
# Below makes HEWSR and LESR high priority areas no harvest and high priority matrix and LEWR habitat areas max 15% disturbance; NOTE: only high priority zones in this unit
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND      (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 28) OR (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65)")


# ITCHA-ILGACHUZ
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
# Below makes HEWSR and LESR priority areas no harvest and all priority matrix and LEWR habitat areas max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND      (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61) OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 28) OR (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44) ") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR  (zoneid = 55)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR  (zoneid = 55)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR  (zoneid = 55)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55)") 
# Below makes HEWSR and LESR high and medium priority areas no harvest and high and medium priority matrix and LEWR habitat areas max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND      (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61) OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 29) OR (zoneid = 32) OR (zoneid = 34) OR (zoneid = 37) OR (zoneid = 40)  OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 49) OR (zoneid = 52) OR  (zoneid = 55)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 28)OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 33)  OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51)  OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51)  OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51)  OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54)") 
# Below makes HEWSR and LESR high priority areas no harvest and high priority matrix and LEWR habitat areas max 15% disturbance; medium an low priority zones available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND      (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61) OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85) OR (zoneid = 29) OR (zoneid = 32) OR (zoneid = 34) OR (zoneid = 37) OR (zoneid = 40)  OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 49) OR (zoneid = 52) OR  (zoneid = 55) OR (zoneid = 30) OR (zoneid = 35) OR (zoneid = 38) OR (zoneid = 41) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 28) OR (zoneid = 31) OR (zoneid = 33)  OR (zoneid = 36) OR (zoneid = 39) OR (zoneid = 42)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND  (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51)  OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51)  OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51)  OR (zoneid = 54)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 45) OR (zoneid = 48) OR (zoneid = 51) OR (zoneid = 54)") 


# NORTHERN GROUP - GROUP 1 (Itcha, Rainbows, Charlotte, Tweeds, Telkwa)
# Below makes the HEWSR and LESR no harvest and matrix and LEWR habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab' AND (zoneid = 3) OR (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 2) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 2) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_charlotte_alplands_crithab' AND (zoneid = 2) OR (zoneid = 3)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 4) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 4) OR (zoneid = 3)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_rainbows_crithab' AND (zoneid = 4) OR (zoneid = 3)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 4)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_bc_tweedsmuir_crithab' AND (zoneid = 4)")
# Below makes HEWSR and LESR priority areas no harvest and all priority matrix and LEWR habitat areas max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 28) OR (zoneid = 29) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 32) OR (zoneid = 33) OR (zoneid = 34) OR (zoneid = 35) OR (zoneid = 36) OR (zoneid = 37) OR (zoneid = 38) OR (zoneid = 39) OR (zoneid = 40) OR (zoneid = 41) OR (zoneid = 42) OR (zoneid = 43) OR (zoneid = 44) OR (zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 8) OR (zoneid = 45) OR (zoneid = 46) OR (zoneid = 48) OR (zoneid = 49) OR (zoneid = 51) OR (zoneid = 52) OR (zoneid = 54) OR (zoneid = 55) OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
# Below makes priority forest stands in high and medium priority HEWSR and LESR no harvest and  high and medium priority  matrix and LEWR habitat areas max 15% disturbance; low priority available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 29) OR (zoneid = 32) OR (zoneid = 34) OR (zoneid = 37) OR (zoneid = 40) OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 49) OR (zoneid = 52) OR (zoneid = 55) OR (zoneid = 8)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 28) OR (zoneid = 30) OR (zoneid = 31) OR (zoneid = 33)  OR (zoneid = 35) OR (zoneid = 36)  OR (zoneid = 38) OR (zoneid = 39)  OR (zoneid = 41) OR (zoneid = 42)  OR (zoneid = 44) OR (zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7)  OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
# Below makes priority forest stands in high priority HEWSR and LESR no harvest and  high priority  matrix and LEWR habitat areas max 15% disturbance; low and medium priority available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 29) OR (zoneid = 32) OR (zoneid = 34) OR (zoneid = 37) OR (zoneid = 40) OR (zoneid = 43) OR (zoneid = 46) OR (zoneid = 49) OR (zoneid = 52) OR (zoneid = 55) OR (zoneid = 8) OR (zoneid = 30) OR (zoneid = 35) OR (zoneid = 38) OR (zoneid = 41) OR (zoneid = 44)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 1) OR (zoneid = 2) OR (zoneid = 3) OR (zoneid = 28) OR (zoneid = 31) OR (zoneid = 33) OR (zoneid = 36) OR (zoneid = 39) OR (zoneid = 42) OR (zoneid = 56) OR (zoneid = 57) OR (zoneid = 58) OR (zoneid = 59) OR (zoneid = 60) OR (zoneid = 61)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET variable = 'dist' where reference_zone = 'rast.zone_du7_scenario_20210330' AND (zoneid = 4) OR (zoneid = 5) OR (zoneid = 6) OR (zoneid = 7) OR (zoneid = 45)  OR (zoneid = 48)  OR (zoneid = 51)  OR (zoneid = 54)  OR (zoneid = 62) OR (zoneid = 63) OR (zoneid = 64) OR (zoneid = 65) OR (zoneid = 83) OR (zoneid = 84) OR (zoneid = 85)") 




dbDisconnect(clusdb)


```

## Wells Gray North and Barkerville Disturbance-based Scenarios

```{r wgn and barkerville disturbance scenarios}

#STEP 1: Connect to the clusdb.sqlite database for the AOI
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Williams_Lake_TSA_clusdb.sqlite")) # connext to clusdb -- set the locations of the sqlite

#STEP 2: View the constraints available to a zone
zoneconstraints<-dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_bc_itcha_ilgachuz_crithab'") 
# rast.zone_cond_bc_itcha_ilgachuz_crithab",  "rast.zone_cond_bc_charlotte_alplands_crithab", "rast.zone_cond_bc_rainbows_crithab", "rast.zone_cond_bc_tweedsmuir_crithab"  rast.zone_du7_scenario_20210330  rast.zone_wha_2021


# WELLS GRAY NORTH Update the constraints available to a zone as specified in the scenario
# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_cond_eccc_wells_gray_north_crithab_or_herd' AND zoneid = 2") 

# BARKERVILLE Update the constraints available to a zone as specified in the scenario
dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_smc_zones_20210315'")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' and zoneid in (1,2,3,4,5,6,7,8,9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_smc_zones_20210315' and zoneid in (26,27,28)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' and zoneid in (7,8,9,28)") 

# Below makes the matrix habitat available to harvest
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND zoneid = 2") 
#Below will set Barkerville old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 16) OR (zoneid = 31) OR (zoneid = 45)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR  (zoneid = 29) OR (zoneid = 58) OR (zoneid = 75)") 
#Below will set Barkerville old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR (zoneid = 16)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 60")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR  (zoneid = 29) OR (zoneid = 31) OR (zoneid = 45) OR (zoneid = 58) OR (zoneid = 75)") 
# Below makes the matrix habitat max 12% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND zoneid = 2") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND zoneid = 2") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 12 where reference_zone = 'rast.zone_cond_eccc_barkerville_crithab_or_herd' AND zoneid = 2")
# Below makes priority stands in all priority zones no harvest, core outside of priority stands available, and all the matrix priority zones max 15% disturbance
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 2) OR (zoneid = 4) OR (zoneid = 6)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 1) OR (zoneid = 3) OR (zoneid = 5)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 8) OR (zoneid = 9)")
# Below makes priority stands in high and medium priority zones no harvest; core outside of priority stands available, and high and medium the matrix priority zones max 15% disturbance; low priority zones in core and matrix available
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 2) OR (zoneid = 6)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 1) OR (zoneid = 3) OR (zoneid = 4) OR (zoneid = 5) OR (zoneid = 8)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'le' where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 9)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 15 where reference_zone = 'rast.zone_barkerville_groundhog_zones_20210303' AND (zoneid = 7) OR (zoneid = 9)") 


# WELLS GRAY NORTH Update the constraints available to a zone as specified in the scenario
#Below will set Wells Gray North old, recruit and buffer as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR (zoneid = 29) OR (zoneid = 44) OR (zoneid = 58)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR  (zoneid = 16) OR (zoneid = 45) OR (zoneid = 60)") 
#Below will set Wells Gray North old and recruit forest as no harvest and matrix as 35% disturbance (no buffer)
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 14) OR (zoneid = 29)")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'ge' where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75") 
dbExecute(clusdb, "UPDATE zoneconstraints SET percentage = 65 where reference_zone = 'rast.zone_du9_scenarios' AND zoneid = 75")
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_du9_scenarios' AND (zoneid = 1) OR  (zoneid = 16) OR (zoneid = 45) OR (zoneid = 44) OR (zoneid = 58) OR (zoneid = 60) OR (zoneid = 71)") 

dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_cond_eccc_wells_gray_north_crithab_or_herd'") 
dbExecute(clusdb, "UPDATE zoneconstraints SET threshold = 0 where reference_zone = 'rast.zone_cond_eccc_wells_gray_north_crithab_or_herd' AND zoneid = 2 ") 

dbGetQuery(clusdb, "SELECT * from zoneConstraints WHERE reference_zone = 'rast.zone_smc_zones_20210315'") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = 'nh' where reference_zone = 'rast.zone_smc_zones_20210315' and zoneid in (90,91,92,93,94,95)") 
dbExecute(clusdb, "UPDATE zoneconstraints SET type = '' where reference_zone = 'rast.zone_smc_zones_20210315' and zoneid in (93,94,95,101)") 



dbDisconnect(clusdb)

```


#SIM
```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( 
                           dbName='clus',
                           save_clusdb = FALSE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Williams_Lake_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile = "tsa_aac_bounds",
                           nameBoundaryColumn = "tsa_name",
                           nameBoundary = "Williams_Lake_TSA",
                           nameBoundaryGeom = 'wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster = 'rast.thlb_2020', #'rast.bc_thlb2018' 
                           nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_wha_2021", #"rast.zone_cond_wha"  
                                               "rast.zone_uwr_2021", #"rast.zone_cond_uwr"
                                               "rast.zone_cond_fsw",
                                               "rast.zone_cond_nharv",
                                               "rast.zone_cond_cw",
                                               
                                               # "rast.zone_cond_noharvest_itcha_ilgachuz_crithab_or_herd"
                                              # "rast.zone_cond_noharvest_charlotte_alplands_crithab_or_herd"
                                             # "rast.zone_cond_noharvest_rainbows_crithab_or_herd"
                                             # "rast.zone_cond_noharvest_tweedsmuir_crithab_or_herd"
                             #               "rast.zone_cond_noharvest_wells_gray_north_crithab_or_herd",
                             #               "rast.zone_cond_noharvest_barkerville_crithab_or_herd",
                                            
                             #               "rast.zone_cond_eccc_itcha_ilgachuz_crithab_or_herd",                                                                     "rast.zone_cond_eccc_charlotte_alplands_crithab_or_herd",                                                                 "rast.zone_cond_eccc_rainbows_crithab_or_herd",
                             #               "rast.zone_cond_eccc_wells_gray_north_crithab_or_herd",
                             #               "rast.zone_cond_eccc_barkerville_crithab_or_herd",
                             #               "rast.zone_cond_eccc_tweedsmuir_crithab_or_herd",
                             #               "rast.zone_smc_zones_20210315",
                             
                                             "rast.zone_cond_bc_itcha_ilgachuz_crithab",
                                             "rast.zone_cond_bc_charlotte_alplands_crithab",
                                            "rast.zone_cond_bc_rainbows_crithab"
                                           # "rast.zone_cond_bc_tweedsmuir_crithab"

                             #               "rast.zone_cond_bc_wells_gray_north_crithab",
                             #               "rast.zone_cond_bc_barkerville_crithab",
                             #               "rast.zone_barkerville_groundhog_zones_20210303",
                                           # "rast.zone_du7_scenario_20210330"
                           ),
                           nameZoneTable = "zone.constraints",
                           # nameZonePriorityRaster = "rast.zone_cond_beo",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = "dist, age DESC, vol DESC", # "dist, age DESC, vol DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      # reportHarvestConstraints = T,
                      adjacencyConstraint = 3),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"), # look-up table of herd names
  disturbanceCalcCLUS = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance) 
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 40),
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                 AreaofInterestTable = "public.vat_bc_crithab_and_herd"),
  smcaribouAbundanceCLUS = list (nameRasSMCHerd = "rast.smc_herd_habitat", 
                                  tableSMCCoeffs = "vat.smc_coeffs"),
  uploaderCLUS = list(aoiName = 'williams_lake_tsa', # name of the schema that gets uplaoded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  ),
  yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",  
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCalcCLUS",
                "volumebyareaReportCLUS",
                "smcaribouAbundanceCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "uploaderCLUS"
                )

              

#scenario = data.table (name = "williams_lake_bau",description = "Business-as-usual (BAU). Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_barkerville_nh", description = "No harvest in Barkerville critical habitat. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_barkerville_ch_hele0d_m15d", description = "No harvest in Barkerville high and low elevation critical habitat, maximum 12% disturbance in matrix critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL). Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_barkerville_scen3a",description = "No harvest in old forest, recruitment forest and buffered Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance in Barkerville matrix habitat areas. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
#scenario = data.table (name = "williams_lake_barkerville_scen3c", description = "No harvest in old forest and recruitment forest Barkerville core critical habitat areas, as defined by Bevan Ernst, maximum 12% disturbance in Barkerville matrix habitat areas. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_wells_gray_north_nh", description = "No harvest in Wells Gray North critical habitat. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_wells_gray_north_ch_hele0d_m12d", description = "No harvest in Wells Gray North high and low elevation critical habitat, maximum 12% disturbance in Wells Gray North matrix critical habitat of all herds that overlap with the harvest unit (e.g., TSA or TFL). Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_wells_gray_north_scen3a", description = "No harvest in old forest, recruitment forest and buffered Wells Gray North core critical habitat areas, as defined by Bevan Ernst, maximum 15%  disturbance in Wells Gray North matrix habitat areas. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_wells_gray_north_scen3b", description = "No harvest in old forest and recruitment forest in Wells Gray North core critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance in Wells Gray North matrix habitat areas. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_wells_gray_north_scen3c", description = "No harvest in old forest and recruitment forest in Wells Gray North core critical habitat areas, as defined by Bevan Ernst, maximum 15% disturbance in Wells Gray North matrix habitat areas. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_wells_gray_north_he0d",
#                        description = "No harvest in Wells Gray North high elevation critical habitat; harvest allowed in matrix critical habitat. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_barkerville_he0d",
#                        description = "No harvest in Barkerville high elevation critical habitat; harvest allowed in matrix critical habitat. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_chil_nh",
#                        description = "No harvest in Chilcotin (Itcha, Charlotte, Rainbows) critical habitat. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_barkerville_he0d_m12d",
#                        description = "No harvest in Barkerville high elevation critical habitat; harvest allowed in matrix critical habitat up to 12% forest disturbance (no buffer) in forested area. Harvest flow 2,350,000 m3/yr.  Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lake_barkerville_high_med_low_priority",
#                        description = "No harvest in Barkerville high priority stands in all high elevation critical habitat; harvest allowed in all matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lk_barkerville_high_med_priority",
#                        description = "No harvest in Barkerville high priority stands in high and medium prioirty high elevation critical habitat; harvest allowed in high and medium matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest available low priority martix and core habitat. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_lk_barkerville_high_med_priority",
#                        description = "No harvest in Barkerville high priority stands in high and medium prioirty high elevation critical habitat; harvest allowed in high and medium matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest available low priority martix and core habitat. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_northgrp_nh",
#                        description = "No harvest in Northern Group, group 1 (Itcha, Charlotte, Rainbows) critical habitat types. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_northgrp_scen2",
#                        description = "No harvest in Northern Group (Itcha, Charlotte, Rainbows) high elevation and low elevation summer critical habitat; harvest allowed in low elevation winter and matrix critical habitat up to 12% forest disturbance (no buffer) in forested area. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_northgrp_high_med_low_priority",
#                        description = "No harvest in Northern Group high elevation (HEWSR) and low elevation summer (LESR) critical habitat; harvest allowed in low elevation winter and matrix critical habitat up to 15% forest disturbance (no buffer) in forested area.  Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_du7_grp1_nh",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_du7_grp1_he0d_mlewr12d",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_du7_grp1_hi_med_lo_priority",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_du7_grp1_hi_med_priority",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) high and medium priority HEWSR and LESR critical habitat; harvest allowed in high and medium priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in low priority areas. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_du7_grp1_hi_priority",
#                        description = "No harvest in group 1 (Itcha, Rainbows, Charlotte, Tweeds, and Telkwa) high priority HEWSR and LESR critical habitat; harvest allowed in high priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in low and medium priority areas. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_itcha_nh",
#                        description = "No harvest in Itcha-Ilgachuz critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_itcha_he0d_mlewr12d",
#                        description = "No harvest in Itcha-Ilgachuz  HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_itcha_hi_med_lo_priority",
#                        description = "No harvest in Itcha-Ilgachuz HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_itcha_hi_med_priority",
#                        description = "No harvest in priority stands in high and medium priority zones in Itcha-Ilgachuz HEWSR and LESR critical habitat; harvest allowed in  high and medium priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in all low priority zones. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_itcha_hi_priority",
#                        description = "No harvest in priority stands in high priority zones in Itcha-Ilgachuz HEWSR and LESR critical habitat; harvest allowed in high priority LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Harvest allowed in all low and medium priority zones. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_rainbows_nh",
#                        description = "No harvest in Rainbows critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_rainbows_he0d_mlewr12d",
#                        description = "No harvest in Rainbows HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_rainbows_hi_priority",
#                        description = "No harvest in priority forest stands in high priority zones of Rainbows HEWSR and LESR critical habitat; harvest allowed in high priority zones LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NTOE: no medium and low priority in this unit. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_charlotte_nh",
#                        description = "No harvest in Charlotte-Alplands critical habitat that overlaps with the harvest unit (e.g., TSA or TFL). Harvest flow 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_charlotte_he0d_mlewr12d",
#                        description = "No harvest in Charlotte-Alplands HEWSR and LESR critical habitat; harvest allowed in LEWR and matrix critical habitat up to 12% disturbance (no buffer) in forested area. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_charlotte_hi_lo_priority",
#                        description = "No harvest in priority forest stands in high and low priority zones of Rainbows HEWSR and LESR critical habitat; harvest allowed in high and low  priority zones LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. NOTE: no medium priority in this unit. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")
# scenario = data.table (name = "williams_charlotte_hi_priority",
#                        description = "No harvest in priority forest stands in high  priority zones of Rainbows HEWSR and LESR critical habitat; harvest allowed in high priority zones LEWR and matrix critical habitat up to 15% disturbance (no buffer) in forested area. Low priority zones available to forest harvest. NOTE: no medium priority in this unit. Harvest flow = 2,350,000 m3/yr. Adjacency = 3m. Oldest first.")

# scenario = data.table (name = "williams_lake_bau_chil_0821", description = "Business as usual (BAU) for Chilcotin scenarios (existing constaints in place, including beo, vqo, wha, uwr, cw, pa, fsw). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")
# scenario = data.table (name = "williams_lake_scen1_chil_0821", description = "Chilcotin scenario 1: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")
# scenario = data.table (name = "williams_lake_scen2_chil_0821", description = "Chilcotin scenario 2: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 37%; Seral stage >100 = 30%; Seral stage >120 = 25%). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")
# scenario = data.table (name = "williams_lake_scen3_chil_0821", description = "Chilcotin scenario 3: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 30%; Seral stage >100 = 25%). Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")
# scenario = data.table (name = "williams_lake_scen1ra_chil_0821", description = "Chilcotin scenario 1: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%). Rotation age = 150 years, or 0.67% area harvested annually or 3% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")
# scenario = data.table (name = "williams_lake_scen2ra_chil_0821", description = "Chilcotin scenario 2: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 37%; Seral stage >100 = 30%; Seral stage >120 = 25%).  Rotation age = 120 years, or 0.83% area harvested annually or 4% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")
# scenario = data.table (name = "williams_lake_scen3ra_chil_0821", description = "Chilcotin scenario 3: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >80 = 30%; Seral stage >100 = 25%). Rotation age = 100 years, or 1% area harvested annually or 5% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")

scenario = data.table (name = "williams_lake_scen4_chil_0821", description = "Chilcotin scenario 4: WHAs 5-086, 5-087, 5-118, 5-872, 5-873, 5-118 are removed; other existing constraints remain in place, including beo, vqo, wha, uwr, cw, pa, fsw; forest age constraints are added to caribou critical habitat, including, Seral stage >40 = 85%; Seral stage >80 = 45%; Seral stage >100 = 37%; Seral stage >120 = 30%; Seral stage >140 = 25%). Rotation age = 150 years, or 0.67% area harvested annually or 3% area harvested every 5 years. Adjacency = 3m. Priority queue: closest to disturbance, then oldest first, then highest volume first.  Harvest flow 1,650,000 m3/yr.")





harvestFlow <- rbindlist(list(data.table(compartment ="Williams_Lake_TSA",
                                     partition = ' vol > 110 ', 
                                     year = rep( seq (from = 2018, # run the 
                                                      to = 2218, 
                                                      by = 5),
                                                1), 
                                     flow = 8250000)  # 8250000 / 1,650,000m3/year
                              # oldest first priority: 11750000 / 2,350,000m3/year
))

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport"
                                              ))

           
#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

