---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview



```{r module_usage}
library(SpaDES.core)
library(data.table)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/outputs"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 5)
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( 
                         dbName='clus',
                           #save_clusdb = TRUE,
                           useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/dataLoaderCLUS/Quesnel_TSA_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile="tsa_aac_bounds",
                           nameBoundaryColumn="tsa_name",
                           nameBoundary = "Quesnel_TSA",
                           nameBoundaryGeom='wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster='rast.bc_thlb2018',
                           nameZoneRasters=c("rast.zone_cond_beo", "rast.zone_cond_vqo", "rast.zone_cond_wha", "rast.zone_cond_uwr", "rast.zone_cond_nharv", "rast.zone_cond_fsw",                                      "rast.zone_cond_eccc_barkerville_crithab","rast.zone_cond_nh_crit_itcha_ilgachuz_crithab","rast.zone_cond_nh_crit_wells_gray_north_crithab", "rast.zone_cond_nh_crit_charlotte_alplands_crithab", "rast.zone_cond_nh_crit_rainbows_crithab"),
                           nameZoneTable="zone.constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable ="yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable ="yc_tipsy",
                           nameForestInventoryRaster ="rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea=FALSE, 
                      useSpreadProbRas=FALSE),
  forestryCLUS = list( harvestPriority = " dist, age DESC, vol DESC "),
  growingStockCLUS = list(periodLength = 5),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'),
  #rsfCLUS = list(calculateInterval = 5, criticalHabitatTable = "public.criticalhabitat", writeRSFRasters = TRUE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd"),
  disturbanceCalcCLUS = list(calculateInterval = 1, 
                   criticalHabitatTable = "public.criticalhabitat_bc_vat",
                   criticalHabRaster = "rast.bc_crithab",
                   permDisturbanceRaster = "rast.mine_ag_wind_rail",
                   recovery = 40),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.bc_crithab", # raster of herd boundaries
                       tableCaribouHerd = "public.criticalhabitat_bc_vat"),
  uploaderCLUS = list(aoiName = 'itcha_ilgachuz_plan',
                        dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), keyring::key_get("vmdbuser", keyring="postgreSQL"), keyring::key_get("vmdbpass", keyring="postgreSQL"),  keyring::key_get("vmdbname", keyring="postgreSQL"))
                    )
)

modules <- list("dataLoaderCLUS", "growingStockCLUS", "blockingCLUS", "forestryCLUS", "roadCLUS", "survivalCLUS", "disturbanceCalcCLUS","uploaderCLUS")
#scenario = data.table(name="itchas_bau_a3_rNA", description = "business as usual - projecting current trends. Adjacency constraint > 3 m.")
#scenario = data.table(name="itchas_bau_a1p5_rNA", description = "business as usual - projecting current trends. Adjacency constraint > 1.5 m.")
#scenario = data.table(name="bau_aNa_rNA", description = "business as usual - projecting current trends. No adjacency constraint")

#scenario = data.table(name="itchas_eccc_a3_r40", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for itchas. Adjacency constraint > 3 m. Recovery > 40 years")
#scenario = data.table(name="itchas_bc_herd_plan_a3_r40", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for itchas. Adjacency constraint > 3 m. Recovery > 40 years.")
#scenario = data.table(name="itchas_eccc_a3_r30", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for itchas. Adjacency constraint > 3 m. Recovery > 30 years")
#scenario = data.table(name="itchas_bc_herd_plan_a3_r30", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for itchas. Adjacency constraint > 3 m. Recovery > 30 years.")
#scenario = data.table(name="itchas_eccc_a1p5_r40", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for itchas. Adjacency constraint > 1 m. Recovery > 40 years")
#scenario = data.table(name="itchas_bc_herd_plan_a1p5_r40", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for itchas. Adjacency constraint > 1.5 m. Recovery > 40 years.")
#scenario = data.table(name="itchas_eccc_a1p5_r30", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for itchas. Adjacency constraint > 1 m. Recovery > 30 years")
#scenario = data.table(name="itchas_bc_herd_plan_a1p5_r30", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for itchas. Adjacency constraint > 1.5 m. Recovery > 30 years.")
#scenario = data.table(name="itchas_nh_crit_aNA_rNA", description = "No harvest in critical habitat for itcha_ilgachuz")
#scenario = data.table(name="barkerville_nh_crit_aNA_rNA", description = "No harvest in critical habitat for barkerville")
#scenario = data.table(name="wells_gray_north_nh_crit_aNA_rNA", description = "No harvest in critical habitat for barkerville")
#scenario = data.table(name="nh_crit_aNA_rNA", description = "No harvest in critical habitat for itchas, barkerville, wells gray north")

#scenario = data.table(name="barkerville_eccc_a3_r40", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for barkerville. Adjacency constraint > 3 m. Recovery > 40 years")
#scenario = data.table(name="barkerville_bc_herd_plan_a3_r40", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for barkerville. Adjacency constraint > 3 m. Recovery > 40 years.")
#scenario = data.table(name="barkerville_eccc_a3_r30", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for barkerville. Adjacency constraint > 3 m. Recovery > 30 years")
#scenario = data.table(name="barkerville_bc_herd_plan_a3_r30", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for barkerville. Adjacency constraint > 3 m. Recovery > 30 years.")
#scenario = data.table(name="barkerville_eccc_a1p5_r40", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for barkerville. Adjacency constraint > 1.5 m. Recovery > 40 years")
#scenario = data.table(name="barkerville_bc_herd_plan_a1p5_r40", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for barkerville. Adjacency constraint > 1.5 m. Recovery > 40 years.")
#scenario = data.table(name="barkerville_eccc_a1p5_r30", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for barkerville. Adjacency constraint > 1.5 m. Recovery > 30 years")
#scenario = data.table(name="barkerville_bc_herd_plan_a1p5_r30", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for barkerville. Adjacency constraint > 1.5 m. Recovery > 30 years.")

#scenario = data.table(name="wgn_eccc_a3_r40", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for wells gray north. Adjacency constraint > 3 m. Recovery > 40 years")
#scenario = data.table(name="wgn_bc_herd_plan_a3_r40", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for wells gray north. Adjacency constraint > 3 m. Recovery > 40 years.")
#scenario = data.table(name="wgn_eccc_a3_r30", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for wells gray north. Adjacency constraint > 3 m. Recovery > 30 years")
#scenario = data.table(name="wgn_bc_herd_plan_a3_r30", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for wells gray north. Adjacency constraint > 3 m. Recovery > 30 years.")
#scenario = data.table(name="wgn_eccc_a1p5_r40", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for wells gray north. Adjacency constraint > 1.5 m. Recovery > 40 years")
#scenario = data.table(name="wgn_bc_herd_plan_a1p5_r40", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for wells gray north. Adjacency constraint > 1.5 m. Recovery > 40 years.")
#scenario = data.table(name="wgn_eccc_a1p5_r30", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for wells gray north. Adjacency constraint > 1.5 m. Recovery > 30 years")
#scenario = data.table(name="wgn_bc_herd_plan_a1p5_r30", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for wells gray north. Adjacency constraint > 1.5 m. Recovery > 30 years.")

#scenario = data.table(name="bc_herd_plan_a3_r40", description = "BC herd plan- No harvest in high elevation range, less than 35% disturbance in low elevation (buffered) and matrix (not buffered) for itchas, barkerville and wells gray north. Adjacency constraint > 3 m. Recovery > 40 years.")
#scenario = data.table(name="eccc_a3_r40", description = "ECCC- No harvest in high elevation range or low elevation summer range, 35% disturbance in matrix for itchas, barkerville and wells gray north. Adjacency constraint > 3 m. Recovery > 40 years.")

scenario = data.table(name="nh_all_crit_test99", description = "No harvest in any of the critical habitat types")

#harvestFlow<- rbindlist(list(data.table(compartment ="Quesnel_TSA",partition = ' vol > 110 ', year = rep(seq(from = 2018, to=2027, by = 1),1), flow = 1250000), data.table(compartment ="Quesnel_TSA", partition = ' vol > 110 ',year = rep(seq(from = 2028, to=2219, by = 1),1), flow = 1250000)))

harvestFlow<- data.table(compartment ="Quesnel_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2018, to=2218, by = 5),1),  flow = 8000000)

#harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))

#calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
#calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd

objects <- list (harvestFlow = harvestFlow, 
                 patchSizeDist = patchSizeDist, 
                 scenario = scenario)

paths <- list(
  cachePath = cacheDir,
  modulePath = moduleDir,
  inputPath = inputDir,
  outputPath = outputDir)

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)


outputs(mySim) <- data.frame (objectName = c("harvestReport", # outputs to keep; these are tables that get used int eh uploader
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport"))

#Run the model 1 time
mysimout<-spades(mySim)

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

