---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
  html_document: 
    keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

Scenario describing the federal implementation of critical habitat constraints

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


```{r module_usage}
library(snow)
library(parallel)
library(doParallel)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")
library(data.table)
library(SpaDES.core)

pars_scenario<-list(list("Prince_George_TSA", rbindlist(list(data.table(compartment ="Prince_George_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2018, to=2021, by = 1),1), 
                                     flow = 6038000), 
                                     data.table(compartment ="Prince_George_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2022, to=2119, by = 1),1), 
                                     flow =5038000 )
                                     ))), 
                    list("Invermere_TSA", rbindlist(list(data.table(compartment ="Invermere_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2018, to=2021, by = 1),1), 
                                     flow = 496720), 
                                     data.table(compartment ="Invermere_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2022, to=2119, by = 1),1), 
                                     flow =424800 )
                                     ))),
                    list("Cascadia_TKO_TSA", rbindlist(list(data.table(compartment ="Cascadia_TKO_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2018, to=2037, by = 1),1), 
                                     flow = 101420), 
                                     data.table(compartment ="Cascadia_TKO_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2038, to=2057, by = 1),1), 
                                     flow =91570 ),
                                     data.table(compartment ="Cascadia_TKO_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2058, to=2077, by = 1),1), 
                                     flow =82440 ),
                                     data.table(compartment ="Cascadia_TKO_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2078, to=2119, by = 1),1), 
                                     flow =76000 )
                                     )))
                    )

pars_scenario<-list(list("Revelstoke_TSA", rbindlist(list(data.table(compartment ="Revelstoke_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2018, to=2119, by = 1),1), 
                                     flow = 200000)
                                     ))), 
                    list("Golden_TSA", rbindlist(list(data.table(compartment ="Golden_TSA",
                                     partition = ' vol > 110 ',
                                     year = rep(seq(from = 2018, to=2119, by = 1),1), 
                                     flow = 485000)
                                     )))
)
                    
                 

test<-lapply(pars_scenario, function(x){
  
  moduleDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules")
  inputDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules/forestryCLUS/inputs") %>% reproducible::checkPath(create = TRUE)
  outputDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules/forestryCLUS/outputs")
  cacheDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules/forestryCLUS")
  times <- list(start = 0, end = 100)
  parameters <- list(
    .progress = list(type = NA, interval = NA),
    .globals = list(),
  dataLoaderCLUS = list( 
                           #Database connection
                           dbName='clus',
                           #save_clusdb = TRUE,
                           useCLUSdb = paste0("C:/Users/KLOCHHEA/clus/R/SpaDES-modules/dataLoaderCLUS/",x[][[1]],"_clusdb.sqlite"),
                           #Study Area
                           nameBoundaryFile="tsa_aac_bounds",
                           nameBoundaryColumn="tsa_name",
                           nameBoundary = x[][[1]],
                           nameBoundaryGeom='wkb_geometry',
                           nameCompartmentRaster = "rast.tsa_aac_boundary",
                           nameCompartmentTable = "tsa_aac_bounds_vat",
                           nameMaskHarvestLandbaseRaster='rast.bc_thlb2018',
                           #nameZoneRasters=c("rast.zone_cond_beo", "rast.zone_cond_vqo", "rast.zone_cond_wha", "rast.zone_cond_uwr", "rast.zone_cond_nharv", "rast.zone_cond_crithab"),
                           nameZoneRasters=c("rast.zone_cond_beo", "rast.zone_cond_vqo", "rast.zone_cond_wha", "rast.zone_cond_uwr", "rast.zone_cond_nharv"),
                           nameZoneTable="zone.constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable ="yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable ="yc_tipsy",
                           nameForestInventoryRaster ="rast.vri2018_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2018",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventorySiteIndex = "site_index"),
   blockingCLUS = list(blockMethod='pre', 
                        patchZone = 'rast.zone_cond_beo',
                        patchVariation = 6,
                        nameCutblockRaster ="rast.cns_cut_bl",
                        useLandingsArea=FALSE, 
                        useSpreadProbRas=FALSE),
    forestryCLUS = list( harvestPriority = "vol DESC, age DESC"),
    #roadCLUS = list(roadMethod = 'snap', 
    #                nameCostSurfaceRas = 'rast.rd_cost_surface', 
    #                nameRoads =  'rast.crds_resource'),
    #rsfCLUS = list(calculateInterval = 5, 
    #               criticalHabitatTable = "public.criticalhabitat",
    #               writeRSFRasters = TRUE),
    survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                         nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                         tableCaribouHerd = "public.caribou_herd"), # look-up table of herd names
    uploaderCLUS = list(aoiName = 'columbia_river',
                        dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), keyring::key_get("vmdbuser", keyring="postgreSQL"), keyring::key_get("vmdbpass", keyring="postgreSQL"),  keyring::key_get("vmdbname", keyring="postgreSQL"))
                    )
  )
  
  modules <- list("dataLoaderCLUS", "growingStockCLUS", "blockingCLUS", "forestryCLUS", "survivalCLUS", "uploaderCLUS")
  
  #rsf_model_coeff <- data.table(getTableQuery("SELECT * FROM rsf_model_coeff WHERE species = 'caribou' AND population = 'DU7' and season IN ('S', 'EW', 'LW')"))
  #rsf_model_coeff[, bounds := 'rast.crithabitat']
  #harvestFlow<-rbindlist(list(harvestFlowA,harvestFlowB,harvestFlowC))

  #calb_ymodel<-readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")) #See linkHBS_VRI_Calibration.Rmd
  #calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd
  
  objects <- list(harvestFlow = x[][[2]], 
                  patchSizeDist= data.table(ndt= c(1,1,1,1,1,1,
                                    2,2,2,2,2,2,
                                    3,3,3,3,3,3,
                                    4,4,4,4,4,4,
                                    5,5,5,5,5,5), 
                             sizeClass = c(40,80,120,160,200,240), 
                             freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                      0.3,0.3,0.1,0.1,0.1, 0.1,
                                      0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                      0.1,0.02,0.02,0.02,0.02,0.8,
                                      0.3,0.3,0.1,0.1,0.1, 0.1)), 
                  scenario = data.table(name="test_nogs", description = "checking flow assumptions with no growingstock constraint"),
                  #scenario =data.table(name="federal_recovery", description = "Upper bound ditchline representing Canadas federal caribou recovery strategy"),
                  calb_ymodel=readRDS(paste0(here::here(), "/R/Params/calb_ymodel.rds")))
  
  paths <- list(
    cachePath = cacheDir,
    modulePath = moduleDir,
    inputPath = inputDir,
    outputPath = outputDir)
  
  mySim <- simInit(times = times, params = parameters, modules = modules,
                   objects = objects, paths = paths)
  
  mySim
})

calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")) #See linkHBS_VRI_Calibration.Rmd
#mysimout<-SpaDES.core::spades(test[[1]])
nCores<-3 # set this to the number of cores you want to use.
cl <- makeCluster(nCores, type="SOCK") # type SOCK is a socket connection.
worker.init <- function(packages) {
  for (p in packages) {
    library(p, character.only=TRUE) #need character.only=TRUE to evaluate p as a character
  }
  NULL #return NULL to avoid sending unnecessary data back to the master process
}
clusterCall(cl, worker.init, c('SpaDES.core','data.table','gamlss','velox'))
clusterEvalQ(cl, {source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R"); NULL})
clusterEvalQ(cl, {calb_data4<-readRDS(paste0(here::here(), "/R/Params/calb_data.rds")); NULL})
registerDoParallel(cl)#requires this

foreach(i = 1:length(test)) %dopar% {
  mysimout<-SpaDES.core::spades(test[[i]])
}

stopCluster(cl)

```

# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithum

The general algorithum (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

