---
title: "escape_climate_variable_selection and data prep"
author: "Cora Skaien"
date: "06/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 11_escape_climate_variable_selection.R
#  Script Version: 1.0
#  Script Purpose: Data prep for climate variables, plus model selection for climate variables
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
# Script contributor: Elizabeth Kleynhans, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Overview
In Marchal et al. 2020, they define escape as "the probability that a fire will reach a size of at least 1 ha". We will inspect the ignition data and see the size of each fire. We will then separate them into those that are <1 ha in size, and those that are > 1 ha in size. From this, we can use logistic regression, including climate variables, topography (aspect and slope), and VRI data. Below currently only accounts for lightning caused fires. Human caused fires will be modelled down the road.

Note: Other papers use 3 ha (e.g., Wang et al. 2016, International Journal of Wildland Fire) and others use 10 ha (e.g., Parisien et al. 2013, Natural Hazards) for their definition of escape.

Must think whether or not we want VRI data. These become polygons instead of spatial points.

```{r}
#Load relevant libraries.

library(sf)
library(tidyverse)
library(ggplot2)
library (ggcorrplot)
library (RPostgreSQL)
library (rpostgis)
library (dplyr)
library (lme4)
library (arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(bcdata)

source(here::here("R/functions/R_Postgres.R"))

```

Import the data created at the end of the last file (named Escape_data_lightning_lightning and Escape_data_lightning_person)

```{r}
#Can use below if working straight from last file. Otherwise bring in from castor.
#Escape_data_lightning<-fire_veg_DEM_climate_2

#connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
#                      host = key_get('dbhost', keyring = 'postgreSQL'),
#                      user = key_get('dbuser', keyring = 'postgreSQL'),
#                      dbname = key_get('dbname', keyring = 'postgreSQL'),
#                      password = key_get('dbpass', keyring = 'postgreSQL'),
#                      port = "5432")

#Escape_data_lightning <- sf::st_read  (dsn = connKyle, # connKyle
 #                              query = "SELECT * FROM public.Escape_data_lightning")

#dbDisconnect (connKyle)
```


```{r}
fire_escapes_final <- st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\Fire_escape_data_all.gpkg")


```


Now create a new category where if <= 10 ha, then have 0, and if > 10 ha, have 1 value.
I chose 10 because I was getting odd patterns in the data. See below.


```{r}
dim(fire_escapes_final %>% filter(size_ha==0))
fire_escapes_final$escape10<- NA
fire_escapes_final$escape10[fire_escapes_final$size_ha > 10] <- 1
fire_escapes_final$escape10[fire_escapes_final$size_ha <= 10] <- 0

table(fire_escapes_final$escape10) # note originally I had escape size at 1ha but i was getting strange trends for maximum temperature and probability of escape. So I tried various sizes and decided to go with 10ha.
table(fire_escapes_final$escape10, fire_escapes_final$fire_cs)
```

Before i appended wind speed to timing of fire to create a variable called wind at fire, but Im not sure I want to do wind at fire because when I create a probability of spread map I dont know where the fire has started or when it started so I dotn think this is a very good idea. Same with temp at fire, precipt at fire etc


```{r}
bla<-fire_escapes_final%>% filter(Cluster==10 & escape10==1)
Cluster10 <- ggplot(bla, aes(as.numeric(ig_mnth))) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12")) + 
    labs(title="FRT 10", 
         x="ignition month")

bla<-fire_escapes_final%>% filter(Cluster==12 & escape10==1)
Cluster12 <- ggplot(bla, aes(as.numeric(ig_mnth))) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12")) + 
    labs(title="FRT 12", 
         x="ignition month")

bla<-fire_escapes_final%>% filter(Cluster==13 & escape10==1)
Cluster13 <- ggplot(bla, aes(as.numeric(ig_mnth))) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12")) + 
    labs(title="FRT 13", 
         x="ignition month")

bla<-fire_escapes_final%>% filter(Cluster==14 & escape10==1)
Cluster14 <- ggplot(bla, aes(as.numeric(ig_mnth))) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12")) + 
    labs(title="FRT 14", 
         x="ignition month")

bla<-fire_escapes_final%>% filter(Cluster==15 & escape10==1)
Cluster15 <- ggplot(bla, aes(as.numeric(ig_mnth))) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12")) + 
    labs(title="FRT 15", 
         x="ignition month")

ggarrange(Cluster12, Cluster10, Cluster13, Cluster14, Cluster15,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2, 
          common.legend = TRUE, legend = "bottom")

# is there a difference in weather between human and lightning caused fires?

bla<-fire_escapes_final%>% filter(Cluster==10 & escape10==1)
Cluster10 <- ggplot(bla, aes(Tmax07)) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
    labs(title="Density plot of fire cause in FRT 5", 
         x="Tmax07")

bla<-fire_escapes_final%>% filter(Cluster==12 & escape10==1)
Cluster12 <- ggplot(bla, aes(Tmax07)) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
    labs(title="Density plot of fire cause in FRT 5", 
         x="Tmax07")

bla<-fire_escapes_final%>% filter(Cluster==13 & escape10==1)
Cluster13 <- ggplot(bla, aes(Tmax07)) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
    labs(title="Density plot of fire cause in FRT 5", 
         x="Tmax07")

bla<-fire_escapes_final%>% filter(Cluster==14 & escape10==1)
Cluster14 <- ggplot(bla, aes(Tmax07)) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv") + 
    labs(title="Density plot of fire cause in FRT 5", 
         x="Tmax07")

bla<-fire_escapes_final%>% filter(Cluster==15 & escape10==1)
Cluster15 <- ggplot(bla, aes(Tmax07)) +
  geom_density(aes(fill=factor(fire_cs)), alpha=0.8, bw = "bcv")+ 
    labs(title="Density plot of fire cause in FRT 5", 
         x="Tmax07")

ggarrange(Cluster12, Cluster10, Cluster13, Cluster14, Cluster15,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2, 
          common.legend = TRUE, legend = "bottom")


```


```{r}
fire_escapes_final$ig_mnth<- as.numeric(as.character(fire_escapes_final$ig_mnth))

Cluster5<-ggplot(fire_escapes_final%>% filter(Cluster==5), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 5",x="Escape month", y = "Count")

Cluster7<-ggplot(fire_escapes_final%>% filter(Cluster==7), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 7",x="Escape month", y = "Count")

Cluster9<-ggplot(fire_escapes_final%>% filter(Cluster==9), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 9",x="Escape month", y = "Count")

Cluster10<-ggplot(fire_escapes_final%>% filter(Cluster==10), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 10",x="Escape month", y = "Count")

Cluster11<-ggplot(fire_escapes_final%>% filter(Cluster==11), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 11",x="Escape month", y = "Count")

Cluster12<-ggplot(fire_escapes_final%>% filter(Cluster==12), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 12",x="Escape month", y = "Count")

Cluster13<-ggplot(fire_escapes_final%>% filter(Cluster==13), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 13",x="Escape month", y = "Count")

Cluster14<-ggplot(fire_escapes_final%>% filter(Cluster==14), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 14",x="Escape month", y = "Count")

Cluster15<-ggplot(fire_escapes_final%>% filter(Cluster==15), aes(x=ig_mnth, color=as.factor(escape10), fill=as.factor(escape10))) +geom_histogram(position="dodge")+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  theme(legend.position="right") +
  #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  theme_classic() +
  labs(title="Cluster = 15",x="Escape month", y = "Count")

library(ggpubr)

ggarrange(Cluster5, Cluster7, Cluster9, Cluster10,
          labels = c("A", "B", "C", "D", "E"),
          ncol = 2, nrow = 2, 
          common.legend = TRUE, legend = "bottom")


ggarrange(Cluster11, Cluster12, Cluster13, Cluster14, Cluster15,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2, 
          common.legend = TRUE, legend = "bottom")

ggarrange(Cluster10, Cluster12, Cluster13, Cluster14, Cluster15,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2, 
          common.legend = TRUE, legend = "bottom")


```



Inspect probability of escape10 by MDC, PPT, Tmax and Tave.

```{r}

# nice alternative figure
library(popbio)


logi.hist.plot(fire_escapes_final$Tmax07,fire_escapes_final$escape10,boxp=FALSE,type="hist",col="gray") # this seems counter intuitive. Is there something wrong?
# Maybe some of the spreads at very low temperatures where not true. 

ggplot(fire_escapes_final,aes(Tmax07, size_ha)) +
  geom_point() +
  geom_smooth(method='lm')

x<-fire_escapes_final%>%filter(escape10==1)
y<-fire_escapes_final%>%filter(escape10==0)
summary(x$Tmax07)
summary(y$Tmax07)

# checking the data here. It looks like the fire sizes and causes are correct at least for the largest fires.
x %>% filter (fire_yr==2021) %>% arrange(desc(size_ha))
x %>% filter (fire_yr==2003) %>% arrange(desc(size_ha))
# largest fires
x %>% arrange(desc(size_ha))


x %>% filter(temp_atfire==-10.3)
min(y$temp_atfire)

logi.hist.plot(fire_escapes_final$ppt_atfire,fire_escapes_final$escape10,boxp=FALSE,type="hist",col="gray") # this seems more what I expect
logi.hist.plot(fire_escapes_final$tempave_atfire,fire_escapes_final$escape10,boxp=FALSE,type="hist",col="gray") # this seems counter intuitive. Is there something wrong?

logi.hist.plot(fire_escapes_final$mdc_atfire,fire_escapes_final$escape10,boxp=FALSE,type="hist",col="gray")


```



#Overview
We will do the same method we did for selecting climate variables for the ignition model for the escape model. We will start by using the data that was generated at the end of 04_vri_data_prep.

Now we create variable categories for model selection on climate variables

Before we begin, we will create additional climate variables.

```{r}
#Climate variable creation for lightning data

### creating amalgamations of variables to test different combinations of variables.##
fire_escapes_final$tot_spring_PPT<-fire_escapes_final$Tmax03+ fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05
fire_escapes_final$tot_summer_PPT<-fire_escapes_final$Tmax06+ fire_escapes_final$Tmax07 + fire_escapes_final$Tmax08

fire_escapes_final$mean_Tmax03_Tmax04<- (fire_escapes_final$Tmax03+ fire_escapes_final$Tmax04)/2
fire_escapes_final$mean_Tmax04_Tmax05<- (fire_escapes_final$Tmax04+ fire_escapes_final$Tmax05)/2
fire_escapes_final$mean_Tmax05_Tmax06<- (fire_escapes_final$Tmax05+ fire_escapes_final$Tmax06)/2
fire_escapes_final$mean_Tmax06_Tmax07<- (fire_escapes_final$Tmax06+ fire_escapes_final$Tmax07)/2
fire_escapes_final$mean_Tmax07_Tmax08<- (fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08)/2
fire_escapes_final$mean_Tmax08_Tmax09<- (fire_escapes_final$Tmax08+ fire_escapes_final$Tmax09)/2
fire_escapes_final$mean_Tmax09_Tmax10<- (fire_escapes_final$Tmax09+ fire_escapes_final$Tmax10)/2
fire_escapes_final$mean_Tmax10_Tmax11<- (fire_escapes_final$Tmax10+ fire_escapes_final$Tmax11)/2

fire_escapes_final$mean_Tmax03_Tmax04_Tmax05<- (fire_escapes_final$Tmax03+ fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05)/3
fire_escapes_final$mean_Tmax04_Tmax05_Tmax06<- (fire_escapes_final$Tmax04+ fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06)/3
fire_escapes_final$mean_Tmax05_Tmax06_Tmax07<- (fire_escapes_final$Tmax05+ fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07)/3
fire_escapes_final$mean_Tmax06_Tmax07_Tmax08<- (fire_escapes_final$Tmax06+ fire_escapes_final$Tmax07 + fire_escapes_final$Tmax08)/3
fire_escapes_final$mean_Tmax07_Tmax08_Tmax09<- (fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09)/3
fire_escapes_final$mean_Tmax08_Tmax09_Tmax10<- (fire_escapes_final$Tmax08+ fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10)/3
fire_escapes_final$mean_Tmax09_Tmax10_Tmax11<- (fire_escapes_final$Tmax09+ fire_escapes_final$Tmax10 + fire_escapes_final$Tmax11)/3

fire_escapes_final$mean_Tmax03_Tmax04_Tmax05_Tmax06<- (fire_escapes_final$Tmax03 + fire_escapes_final$Tmax04+ fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06)/4
fire_escapes_final$mean_Tmax04_Tmax05_Tmax06_Tmax07<- (fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05+ fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07)/4
fire_escapes_final$mean_Tmax05_Tmax06_Tmax07_Tmax08<- (fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06+ fire_escapes_final$Tmax07 + fire_escapes_final$Tmax08)/4
fire_escapes_final$mean_Tmax06_Tmax07_Tmax08_Tmax09<- (fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09)/4
fire_escapes_final$mean_Tmax07_Tmax08_Tmax09_Tmax10<- (fire_escapes_final$Tmax07 + fire_escapes_final$Tmax08+ fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10)/4
fire_escapes_final$mean_Tmax08_Tmax09_Tmax10_Tmax11<- (fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09+ fire_escapes_final$Tmax10 + fire_escapes_final$Tmax11)/4

fire_escapes_final$mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07<- (fire_escapes_final$Tmax03 + fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05+ fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07)/5
fire_escapes_final$mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08<- (fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06+ fire_escapes_final$Tmax07 + fire_escapes_final$Tmax08)/5
fire_escapes_final$mean_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09<- (fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09)/5
fire_escapes_final$mean_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10<- ( fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10)/5
fire_escapes_final$mean_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11<- ( fire_escapes_final$Tmax07 + fire_escapes_final$Tmax08+ fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10 + fire_escapes_final$Tmax11)/5

fire_escapes_final$mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08<- (fire_escapes_final$Tmax03 + fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08)/6
fire_escapes_final$mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax9<- (fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09)/6
fire_escapes_final$mean_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10<- (fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10)/6
fire_escapes_final$mean_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11<- (fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10 + fire_escapes_final$Tmax11)/6

fire_escapes_final$mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09<- (fire_escapes_final$Tmax03 + fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09)/7
fire_escapes_final$mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10<- ( fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10)/7
fire_escapes_final$mean_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11<- (fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10 + fire_escapes_final$Tmax11)/7

fire_escapes_final$mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11<- (fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10 + fire_escapes_final$Tmax11)/8
fire_escapes_final$mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10<- ( fire_escapes_final$Tmax03 + fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10)/8

fire_escapes_final$mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11<- ( fire_escapes_final$Tmax03 + fire_escapes_final$Tmax04 + fire_escapes_final$Tmax05 + fire_escapes_final$Tmax06 + fire_escapes_final$Tmax07+ fire_escapes_final$Tmax08 + fire_escapes_final$Tmax09 + fire_escapes_final$Tmax10 + fire_escapes_final$Tmax11)/9

#### Tave

fire_escapes_final$mean_Tave03_Tave04<- (fire_escapes_final$Tave03+ fire_escapes_final$Tave04)/2
fire_escapes_final$mean_Tave04_Tave05<- (fire_escapes_final$Tave04+ fire_escapes_final$Tave05)/2
fire_escapes_final$mean_Tave05_Tave06<- (fire_escapes_final$Tave05+ fire_escapes_final$Tave06)/2
fire_escapes_final$mean_Tave06_Tave07<- (fire_escapes_final$Tave06+ fire_escapes_final$Tave07)/2
fire_escapes_final$mean_Tave07_Tave08<- (fire_escapes_final$Tave07+ fire_escapes_final$Tave08)/2
fire_escapes_final$mean_Tave08_Tave09<- (fire_escapes_final$Tave08+ fire_escapes_final$Tave09)/2
fire_escapes_final$mean_Tave09_Tave10<- (fire_escapes_final$Tave09+ fire_escapes_final$Tave10)/2
fire_escapes_final$mean_Tave10_Tave11<- (fire_escapes_final$Tave10+ fire_escapes_final$Tave11)/2

fire_escapes_final$mean_Tave03_Tave04_Tave05<- (fire_escapes_final$Tave03+ fire_escapes_final$Tave04 + fire_escapes_final$Tave05)/3
fire_escapes_final$mean_Tave04_Tave05_Tave06<- (fire_escapes_final$Tave04+ fire_escapes_final$Tave05 + fire_escapes_final$Tave06)/3
fire_escapes_final$mean_Tave05_Tave06_Tave07<- (fire_escapes_final$Tave05+ fire_escapes_final$Tave06 + fire_escapes_final$Tave07)/3
fire_escapes_final$mean_Tave06_Tave07_Tave08<- (fire_escapes_final$Tave06+ fire_escapes_final$Tave07 + fire_escapes_final$Tave08)/3
fire_escapes_final$mean_Tave07_Tave08_Tave09<- (fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09)/3
fire_escapes_final$mean_Tave08_Tave09_Tave10<- (fire_escapes_final$Tave08+ fire_escapes_final$Tave09 + fire_escapes_final$Tave10)/3
fire_escapes_final$mean_Tave09_Tave10_Tave11<- (fire_escapes_final$Tave09+ fire_escapes_final$Tave10 + fire_escapes_final$Tave11)/3

fire_escapes_final$mean_Tave03_Tave04_Tave05_Tave06<- (fire_escapes_final$Tave03 + fire_escapes_final$Tave04+ fire_escapes_final$Tave05 + fire_escapes_final$Tave06)/4
fire_escapes_final$mean_Tave04_Tave05_Tave06_Tave07<- (fire_escapes_final$Tave04 + fire_escapes_final$Tave05+ fire_escapes_final$Tave06 + fire_escapes_final$Tave07)/4
fire_escapes_final$mean_Tave05_Tave06_Tave07_Tave08<- (fire_escapes_final$Tave05 + fire_escapes_final$Tave06+ fire_escapes_final$Tave07 + fire_escapes_final$Tave08)/4
fire_escapes_final$mean_Tave06_Tave07_Tave08_Tave09<- (fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09)/4
fire_escapes_final$mean_Tave07_Tave08_Tave09_Tave10<- (fire_escapes_final$Tave07 + fire_escapes_final$Tave08+ fire_escapes_final$Tave09 + fire_escapes_final$Tave10)/4
fire_escapes_final$mean_Tave08_Tave09_Tave10_Tave11<- (fire_escapes_final$Tave08 + fire_escapes_final$Tave09+ fire_escapes_final$Tave10 + fire_escapes_final$Tave11)/4

fire_escapes_final$mean_Tave03_Tave04_Tave05_Tave06_Tave07<- (fire_escapes_final$Tave03 + fire_escapes_final$Tave04 + fire_escapes_final$Tave05+ fire_escapes_final$Tave06 + fire_escapes_final$Tave07)/5
fire_escapes_final$mean_Tave04_Tave05_Tave06_Tave07_Tave08<- (fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06+ fire_escapes_final$Tave07 + fire_escapes_final$Tave08)/5
fire_escapes_final$mean_Tave05_Tave06_Tave07_Tave08_Tave09<- (fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09)/5
fire_escapes_final$mean_Tave06_Tave07_Tave08_Tave09_Tave10<- ( fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10)/5
fire_escapes_final$mean_Tave07_Tave08_Tave09_Tave10_Tave11<- ( fire_escapes_final$Tave07 + fire_escapes_final$Tave08+ fire_escapes_final$Tave09 + fire_escapes_final$Tave10 + fire_escapes_final$Tave11)/5

fire_escapes_final$mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08<- (fire_escapes_final$Tave03 + fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08)/6
fire_escapes_final$mean_Tave04_Tave05_Tave06_Tave07_Tave08_Tave9<- (fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09)/6
fire_escapes_final$mean_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10<- (fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10)/6
fire_escapes_final$mean_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11<- (fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10 + fire_escapes_final$Tave11)/6

fire_escapes_final$mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09<- (fire_escapes_final$Tave03 + fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09)/7
fire_escapes_final$mean_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10<- ( fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10)/7
fire_escapes_final$mean_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11<- (fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10 + fire_escapes_final$Tave11)/7

fire_escapes_final$mean_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11<- (fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10 + fire_escapes_final$Tave11)/8
fire_escapes_final$mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10<- ( fire_escapes_final$Tave03 + fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10)/8

fire_escapes_final$mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11<- ( fire_escapes_final$Tave03 + fire_escapes_final$Tave04 + fire_escapes_final$Tave05 + fire_escapes_final$Tave06 + fire_escapes_final$Tave07+ fire_escapes_final$Tave08 + fire_escapes_final$Tave09 + fire_escapes_final$Tave10 + fire_escapes_final$Tave11)/9

#### PPT
fire_escapes_final$mean_PPT03_PPT04<- (fire_escapes_final$PPT03+ fire_escapes_final$PPT04)/2
fire_escapes_final$mean_PPT04_PPT05<- (fire_escapes_final$PPT04+ fire_escapes_final$PPT05)/2
fire_escapes_final$mean_PPT05_PPT06<- (fire_escapes_final$PPT05+ fire_escapes_final$PPT06)/2
fire_escapes_final$mean_PPT06_PPT07<- (fire_escapes_final$PPT06+ fire_escapes_final$PPT07)/2
fire_escapes_final$mean_PPT07_PPT08<- (fire_escapes_final$PPT07+ fire_escapes_final$PPT08)/2
fire_escapes_final$mean_PPT08_PPT09<- (fire_escapes_final$PPT08+ fire_escapes_final$PPT09)/2
fire_escapes_final$mean_PPT09_PPT10<- (fire_escapes_final$PPT09+ fire_escapes_final$PPT10)/2
fire_escapes_final$mean_PPT10_PPT11<- (fire_escapes_final$PPT10+ fire_escapes_final$PPT11)/2

fire_escapes_final$mean_PPT03_PPT04_PPT05<- (fire_escapes_final$PPT03+ fire_escapes_final$PPT04 + fire_escapes_final$PPT05)/3
fire_escapes_final$mean_PPT04_PPT05_PPT06<- (fire_escapes_final$PPT04+ fire_escapes_final$PPT05 + fire_escapes_final$PPT06)/3
fire_escapes_final$mean_PPT05_PPT06_PPT07<- (fire_escapes_final$PPT05+ fire_escapes_final$PPT06 + fire_escapes_final$PPT07)/3
fire_escapes_final$mean_PPT06_PPT07_PPT08<- (fire_escapes_final$PPT06+ fire_escapes_final$PPT07 + fire_escapes_final$PPT08)/3
fire_escapes_final$mean_PPT07_PPT08_PPT09<- (fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09)/3
fire_escapes_final$mean_PPT08_PPT09_PPT10<- (fire_escapes_final$PPT08+ fire_escapes_final$PPT09 + fire_escapes_final$PPT10)/3
fire_escapes_final$mean_PPT09_PPT10_PPT11<- (fire_escapes_final$PPT09+ fire_escapes_final$PPT10 + fire_escapes_final$PPT11)/3

fire_escapes_final$mean_PPT03_PPT04_PPT05_PPT06<- (fire_escapes_final$PPT03 + fire_escapes_final$PPT04+ fire_escapes_final$PPT05 + fire_escapes_final$PPT06)/4
fire_escapes_final$mean_PPT04_PPT05_PPT06_PPT07<- (fire_escapes_final$PPT04 + fire_escapes_final$PPT05+ fire_escapes_final$PPT06 + fire_escapes_final$PPT07)/4
fire_escapes_final$mean_PPT05_PPT06_PPT07_PPT08<- (fire_escapes_final$PPT05 + fire_escapes_final$PPT06+ fire_escapes_final$PPT07 + fire_escapes_final$PPT08)/4
fire_escapes_final$mean_PPT06_PPT07_PPT08_PPT09<- (fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09)/4
fire_escapes_final$mean_PPT07_PPT08_PPT09_PPT10<- (fire_escapes_final$PPT07 + fire_escapes_final$PPT08+ fire_escapes_final$PPT09 + fire_escapes_final$PPT10)/4
fire_escapes_final$mean_PPT08_PPT09_PPT10_PPT11<- (fire_escapes_final$PPT08 + fire_escapes_final$PPT09+ fire_escapes_final$PPT10 + fire_escapes_final$PPT11)/4

fire_escapes_final$mean_PPT03_PPT04_PPT05_PPT06_PPT07<- (fire_escapes_final$PPT03 + fire_escapes_final$PPT04 + fire_escapes_final$PPT05+ fire_escapes_final$PPT06 + fire_escapes_final$PPT07)/5
fire_escapes_final$mean_PPT04_PPT05_PPT06_PPT07_PPT08<- (fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06+ fire_escapes_final$PPT07 + fire_escapes_final$PPT08)/5
fire_escapes_final$mean_PPT05_PPT06_PPT07_PPT08_PPT09<- (fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09)/5
fire_escapes_final$mean_PPT06_PPT07_PPT08_PPT09_PPT10<- ( fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10)/5
fire_escapes_final$mean_PPT07_PPT08_PPT09_PPT10_PPT11<- ( fire_escapes_final$PPT07 + fire_escapes_final$PPT08+ fire_escapes_final$PPT09 + fire_escapes_final$PPT10 + fire_escapes_final$PPT11)/5

fire_escapes_final$mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08<- (fire_escapes_final$PPT03 + fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08)/6
fire_escapes_final$mean_PPT04_PPT05_PPT06_PPT07_PPT08_PPT9<- (fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09)/6
fire_escapes_final$mean_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10<- (fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10)/6
fire_escapes_final$mean_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11<- (fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10 + fire_escapes_final$PPT11)/6

fire_escapes_final$mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09<- (fire_escapes_final$PPT03 + fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09)/7
fire_escapes_final$mean_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10<- ( fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10)/7
fire_escapes_final$mean_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11<- (fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10 + fire_escapes_final$PPT11)/7

fire_escapes_final$mean_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11<- (fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10 + fire_escapes_final$PPT11)/8
fire_escapes_final$mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10<- ( fire_escapes_final$PPT03 + fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10)/8

fire_escapes_final$mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11<- ( fire_escapes_final$PPT03 + fire_escapes_final$PPT04 + fire_escapes_final$PPT05 + fire_escapes_final$PPT06 + fire_escapes_final$PPT07+ fire_escapes_final$PPT08 + fire_escapes_final$PPT09 + fire_escapes_final$PPT10 + fire_escapes_final$PPT11)/9

#### RH
fire_escapes_final$mean_RH03_RH04<- (fire_escapes_final$RH03+ fire_escapes_final$RH04)/2
fire_escapes_final$mean_RH04_RH05<- (fire_escapes_final$RH04+ fire_escapes_final$RH05)/2
fire_escapes_final$mean_RH05_RH06<- (fire_escapes_final$RH05+ fire_escapes_final$RH06)/2
fire_escapes_final$mean_RH06_RH07<- (fire_escapes_final$RH06+ fire_escapes_final$RH07)/2
fire_escapes_final$mean_RH07_RH08<- (fire_escapes_final$RH07+ fire_escapes_final$RH08)/2
fire_escapes_final$mean_RH08_RH09<- (fire_escapes_final$RH08+ fire_escapes_final$RH09)/2
fire_escapes_final$mean_RH09_RH10<- (fire_escapes_final$RH09+ fire_escapes_final$RH10)/2
fire_escapes_final$mean_RH10_RH11<- (fire_escapes_final$RH10+ fire_escapes_final$RH11)/2

fire_escapes_final$mean_RH03_RH04_RH05<- (fire_escapes_final$RH03+ fire_escapes_final$RH04 + fire_escapes_final$RH05)/3
fire_escapes_final$mean_RH04_RH05_RH06<- (fire_escapes_final$RH04+ fire_escapes_final$RH05 + fire_escapes_final$RH06)/3
fire_escapes_final$mean_RH05_RH06_RH07<- (fire_escapes_final$RH05+ fire_escapes_final$RH06 + fire_escapes_final$RH07)/3
fire_escapes_final$mean_RH06_RH07_RH08<- (fire_escapes_final$RH06+ fire_escapes_final$RH07 + fire_escapes_final$RH08)/3
fire_escapes_final$mean_RH07_RH08_RH09<- (fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09)/3
fire_escapes_final$mean_RH08_RH09_RH10<- (fire_escapes_final$RH08+ fire_escapes_final$RH09 + fire_escapes_final$RH10)/3
fire_escapes_final$mean_RH09_RH10_RH11<- (fire_escapes_final$RH09+ fire_escapes_final$RH10 + fire_escapes_final$RH11)/3

fire_escapes_final$mean_RH03_RH04_RH05_RH06<- (fire_escapes_final$RH03 + fire_escapes_final$RH04+ fire_escapes_final$RH05 + fire_escapes_final$RH06)/4
fire_escapes_final$mean_RH04_RH05_RH06_RH07<- (fire_escapes_final$RH04 + fire_escapes_final$RH05+ fire_escapes_final$RH06 + fire_escapes_final$RH07)/4
fire_escapes_final$mean_RH05_RH06_RH07_RH08<- (fire_escapes_final$RH05 + fire_escapes_final$RH06+ fire_escapes_final$RH07 + fire_escapes_final$RH08)/4
fire_escapes_final$mean_RH06_RH07_RH08_RH09<- (fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09)/4
fire_escapes_final$mean_RH07_RH08_RH09_RH10<- (fire_escapes_final$RH07 + fire_escapes_final$RH08+ fire_escapes_final$RH09 + fire_escapes_final$RH10)/4
fire_escapes_final$mean_RH08_RH09_RH10_RH11<- (fire_escapes_final$RH08 + fire_escapes_final$RH09+ fire_escapes_final$RH10 + fire_escapes_final$RH11)/4

fire_escapes_final$mean_RH03_RH04_RH05_RH06_RH07<- (fire_escapes_final$RH03 + fire_escapes_final$RH04 + fire_escapes_final$RH05+ fire_escapes_final$RH06 + fire_escapes_final$RH07)/5
fire_escapes_final$mean_RH04_RH05_RH06_RH07_RH08<- (fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06+ fire_escapes_final$RH07 + fire_escapes_final$RH08)/5
fire_escapes_final$mean_RH05_RH06_RH07_RH08_RH09<- (fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09)/5
fire_escapes_final$mean_RH06_RH07_RH08_RH09_RH10<- ( fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10)/5
fire_escapes_final$mean_RH07_RH08_RH09_RH10_RH11<- ( fire_escapes_final$RH07 + fire_escapes_final$RH08+ fire_escapes_final$RH09 + fire_escapes_final$RH10 + fire_escapes_final$RH11)/5

fire_escapes_final$mean_RH03_RH04_RH05_RH06_RH07_RH08<- (fire_escapes_final$RH03 + fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08)/6
fire_escapes_final$mean_RH04_RH05_RH06_RH07_RH08_RH9<- (fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09)/6
fire_escapes_final$mean_RH05_RH06_RH07_RH08_RH09_RH10<- (fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10)/6
fire_escapes_final$mean_RH06_RH07_RH08_RH09_RH10_RH11<- (fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10 + fire_escapes_final$RH11)/6

fire_escapes_final$mean_RH03_RH04_RH05_RH06_RH07_RH08_RH09<- (fire_escapes_final$RH03 + fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09)/7
fire_escapes_final$mean_RH04_RH05_RH06_RH07_RH08_RH09_RH10<- ( fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10)/7
fire_escapes_final$mean_RH05_RH06_RH07_RH08_RH09_RH10_RH11<- (fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10 + fire_escapes_final$RH11)/7

fire_escapes_final$mean_RH04_RH05_RH06_RH07_RH08_RH09_RH10_RH11<- (fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10 + fire_escapes_final$RH11)/8
fire_escapes_final$mean_RH03_RH04_RH05_RH06_RH07_RH08_RH09_RH10<- ( fire_escapes_final$RH03 + fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10)/8

fire_escapes_final$mean_RH03_RH04_RH05_RH06_RH07_RH08_RH09_RH10_RH11<- ( fire_escapes_final$RH03 + fire_escapes_final$RH04 + fire_escapes_final$RH05 + fire_escapes_final$RH06 + fire_escapes_final$RH07+ fire_escapes_final$RH08 + fire_escapes_final$RH09 + fire_escapes_final$RH10 + fire_escapes_final$RH11)/9

### MDC
fire_escapes_final$mean_MDC_03_MDC_04<- (fire_escapes_final$MDC_03+ fire_escapes_final$MDC_04)/2
fire_escapes_final$mean_MDC_04_MDC_05<- (fire_escapes_final$MDC_04+ fire_escapes_final$MDC_05)/2
fire_escapes_final$mean_MDC_05_MDC_06<- (fire_escapes_final$MDC_05+ fire_escapes_final$MDC_06)/2
fire_escapes_final$mean_MDC_06_MDC_07<- (fire_escapes_final$MDC_06+ fire_escapes_final$MDC_07)/2
fire_escapes_final$mean_MDC_07_MDC_08<- (fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08)/2
fire_escapes_final$mean_MDC_08_MDC_09<- (fire_escapes_final$MDC_08+ fire_escapes_final$MDC_09)/2
fire_escapes_final$mean_MDC_09_MDC_10<- (fire_escapes_final$MDC_09+ fire_escapes_final$MDC_10)/2
fire_escapes_final$mean_MDC_10_MDC_11<- (fire_escapes_final$MDC_10+ fire_escapes_final$MDC_11)/2

fire_escapes_final$mean_MDC_03_MDC_04_MDC_05<- (fire_escapes_final$MDC_03+ fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05)/3
fire_escapes_final$mean_MDC_04_MDC_05_MDC_06<- (fire_escapes_final$MDC_04+ fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06)/3
fire_escapes_final$mean_MDC_05_MDC_06_MDC_07<- (fire_escapes_final$MDC_05+ fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07)/3
fire_escapes_final$mean_MDC_06_MDC_07_MDC_08<- (fire_escapes_final$MDC_06+ fire_escapes_final$MDC_07 + fire_escapes_final$MDC_08)/3
fire_escapes_final$mean_MDC_07_MDC_08_MDC_09<- (fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09)/3
fire_escapes_final$mean_MDC_08_MDC_09_MDC_10<- (fire_escapes_final$MDC_08+ fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10)/3
fire_escapes_final$mean_MDC_09_MDC_10_MDC_11<- (fire_escapes_final$MDC_09+ fire_escapes_final$MDC_10 + fire_escapes_final$MDC_11)/3

fire_escapes_final$mean_MDC_03_MDC_04_MDC_05_MDC_06<- (fire_escapes_final$MDC_03 + fire_escapes_final$MDC_04+ fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06)/4
fire_escapes_final$mean_MDC_04_MDC_05_MDC_06_MDC_07<- (fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05+ fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07)/4
fire_escapes_final$mean_MDC_05_MDC_06_MDC_07_MDC_08<- (fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06+ fire_escapes_final$MDC_07 + fire_escapes_final$MDC_08)/4
fire_escapes_final$mean_MDC_06_MDC_07_MDC_08_MDC_09<- (fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09)/4
fire_escapes_final$mean_MDC_07_MDC_08_MDC_09_MDC_10<- (fire_escapes_final$MDC_07 + fire_escapes_final$MDC_08+ fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10)/4
fire_escapes_final$mean_MDC_08_MDC_09_MDC_10_MDC_11<- (fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09+ fire_escapes_final$MDC_10 + fire_escapes_final$MDC_11)/4

fire_escapes_final$mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07<- (fire_escapes_final$MDC_03 + fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05+ fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07)/5
fire_escapes_final$mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08<- (fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06+ fire_escapes_final$MDC_07 + fire_escapes_final$MDC_08)/5
fire_escapes_final$mean_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09<- (fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09)/5
fire_escapes_final$mean_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10<- ( fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10)/5
fire_escapes_final$mean_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11<- ( fire_escapes_final$MDC_07 + fire_escapes_final$MDC_08+ fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10 + fire_escapes_final$MDC_11)/5

fire_escapes_final$mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08<- (fire_escapes_final$MDC_03 + fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08)/6
fire_escapes_final$mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_9<- (fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09)/6
fire_escapes_final$mean_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10<- (fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10)/6
fire_escapes_final$mean_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11<- (fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10 + fire_escapes_final$MDC_11)/6

fire_escapes_final$mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09<- (fire_escapes_final$MDC_03 + fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09)/7
fire_escapes_final$mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10<- ( fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10)/7
fire_escapes_final$mean_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11<- (fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10 + fire_escapes_final$MDC_11)/7

fire_escapes_final$mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11<- (fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10 + fire_escapes_final$MDC_11)/8
fire_escapes_final$mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10<- ( fire_escapes_final$MDC_03 + fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10)/8

fire_escapes_final$mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11<- ( fire_escapes_final$MDC_03 + fire_escapes_final$MDC_04 + fire_escapes_final$MDC_05 + fire_escapes_final$MDC_06 + fire_escapes_final$MDC_07+ fire_escapes_final$MDC_08 + fire_escapes_final$MDC_09 + fire_escapes_final$MDC_10 + fire_escapes_final$MDC_11)/9
# maybe also try maximum temperature, precipitation, RH and MDC for the season.

```

##### Create variables for Model Selection ########
Create groupings of variables to put into model selection loop.

```{r}

variables<- c(
              "Tmax03",
              "Tmax04",
              "Tmax05",
              "Tmax06",
              "Tmax07", 
              "Tmax08", 
              "Tmax09",
              #"Tmax10", 
              #"Tmax11", 
              "mean_Tmax03_Tmax04",
              "mean_Tmax04_Tmax05",
              "mean_Tmax05_Tmax06",
              "mean_Tmax06_Tmax07", 
              "mean_Tmax07_Tmax08", 
              "mean_Tmax08_Tmax09",
              #"mean_Tmax09_Tmax10",
              #"mean_Tmax10_Tmax11", 
              "mean_Tmax03_Tmax04_Tmax05",
              "mean_Tmax04_Tmax05_Tmax06",
              "mean_Tmax05_Tmax06_Tmax07", 
              "mean_Tmax06_Tmax07_Tmax08",
              "mean_Tmax07_Tmax08_Tmax09",
              #"mean_Tmax08_Tmax09_Tmax10",
              #"mean_Tmax09_Tmax10_Tmax11", 
              "mean_Tmax03_Tmax04_Tmax05_Tmax06",
              "mean_Tmax04_Tmax05_Tmax06_Tmax07",
              "mean_Tmax05_Tmax06_Tmax07_Tmax08",
              "mean_Tmax06_Tmax07_Tmax08_Tmax09",
              #"mean_Tmax07_Tmax08_Tmax09_Tmax10",
              #"mean_Tmax08_Tmax09_Tmax10_Tmax11",
              "mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07",
              "mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08",
              "mean_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09",
              #"mean_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10",
              #"mean_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11",
              "mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08",
              "mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax9",
              #"mean_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10",
              #"mean_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11",
              "mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09",
              #"mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10",
              #"mean_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11",
              #"mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10",
              #"mean_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11",
              #"mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08_Tmax09_Tmax10_Tmax11",
              
              "Tave03",
              "Tave04",
              "Tave05",
              "Tave06",
              "Tave07", 
              "Tave08", 
              "Tave09",
              #"Tave10", 
              #"Tave11", 
              "mean_Tave03_Tave04",
              "mean_Tave04_Tave05",
              "mean_Tave05_Tave06",
              "mean_Tave06_Tave07", 
              "mean_Tave07_Tave08", 
              "mean_Tave08_Tave09",
              #"mean_Tave09_Tave10",
              #"mean_Tave10_Tave11", 
              "mean_Tave03_Tave04_Tave05",
              "mean_Tave04_Tave05_Tave06",
              "mean_Tave05_Tave06_Tave07", 
              "mean_Tave06_Tave07_Tave08",
              "mean_Tave07_Tave08_Tave09",
              #"mean_Tave08_Tave09_Tave10",
              #"mean_Tave09_Tave10_Tave11", 
              "mean_Tave03_Tave04_Tave05_Tave06",
              "mean_Tave04_Tave05_Tave06_Tave07",
              "mean_Tave05_Tave06_Tave07_Tave08",
              "mean_Tave06_Tave07_Tave08_Tave09",
              #"mean_Tave07_Tave08_Tave09_Tave10",
              #"mean_Tave08_Tave09_Tave10_Tave11",
              "mean_Tave03_Tave04_Tave05_Tave06_Tave07",
              "mean_Tave04_Tave05_Tave06_Tave07_Tave08",
              "mean_Tave05_Tave06_Tave07_Tave08_Tave09",
              #"mean_Tave06_Tave07_Tave08_Tave09_Tave10",
              #"mean_Tave07_Tave08_Tave09_Tave10_Tave11",
              "mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08",
              "mean_Tave04_Tave05_Tave06_Tave07_Tave08_Tave9",
              #"mean_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10",
              #"mean_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11",
              "mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09",
              #"mean_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10",
              #"mean_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11",
              #"mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10",
              #"mean_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11",
              #"mean_Tave03_Tave04_Tave05_Tave06_Tave07_Tave08_Tave09_Tave10_Tave11",
              
              
              "PPT03",
              "tot_spring_PPT",
              "tot_summer_PPT",
              "PPT04",
              "PPT05",
              "PPT06",
              "PPT07", 
              "PPT08", 
              "PPT09",
              #"PPT10", 
              #"PPT11", 
              "mean_PPT03_PPT04",
              "mean_PPT04_PPT05",
              "mean_PPT05_PPT06",
              "mean_PPT06_PPT07", 
              "mean_PPT07_PPT08", 
              "mean_PPT08_PPT09",
              #"mean_PPT09_PPT10",
              #"mean_PPT10_PPT11", 
              "mean_PPT03_PPT04_PPT05",
              "mean_PPT04_PPT05_PPT06",
              "mean_PPT05_PPT06_PPT07", 
              "mean_PPT06_PPT07_PPT08",
              "mean_PPT07_PPT08_PPT09",
              #"mean_PPT08_PPT09_PPT10",
              #"mean_PPT09_PPT10_PPT11", 
              "mean_PPT03_PPT04_PPT05_PPT06",
              "mean_PPT04_PPT05_PPT06_PPT07",
              "mean_PPT05_PPT06_PPT07_PPT08",
              "mean_PPT06_PPT07_PPT08_PPT09",
              #"mean_PPT07_PPT08_PPT09_PPT10",
              #"mean_PPT08_PPT09_PPT10_PPT11",
              "mean_PPT03_PPT04_PPT05_PPT06_PPT07",
              "mean_PPT04_PPT05_PPT06_PPT07_PPT08",
              "mean_PPT05_PPT06_PPT07_PPT08_PPT09",
              #"mean_PPT06_PPT07_PPT08_PPT09_PPT10",
              #"mean_PPT07_PPT08_PPT09_PPT10_PPT11",
              "mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08",
              "mean_PPT04_PPT05_PPT06_PPT07_PPT08_PPT9",
              #"mean_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10",
              #"mean_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11",
              "mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09",
              #"mean_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10",
              #"mean_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11",
              #"mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10",
              #"mean_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11",
              #"mean_PPT03_PPT04_PPT05_PPT06_PPT07_PPT08_PPT09_PPT10_PPT11",
              
              "RH03",
              "RH04",
              "RH05",
              "RH06",
              "RH07", 
              "RH08", 
              "RH09",
              #"RH10", 
              #"RH11", 
              "mean_RH03_RH04",
              "mean_RH04_RH05",
              "mean_RH05_RH06",
              "mean_RH06_RH07", 
              "mean_RH07_RH08", 
              "mean_RH08_RH09",
              #"mean_RH09_RH10",
              #"mean_RH10_RH11", 
              "mean_RH03_RH04_RH05",
              "mean_RH04_RH05_RH06",
              "mean_RH05_RH06_RH07", 
              "mean_RH06_RH07_RH08",
              "mean_RH07_RH08_RH09",
              #"mean_RH08_RH09_RH10",
              #"mean_RH09_RH10_RH11", 
              "mean_RH03_RH04_RH05_RH06",
              "mean_RH04_RH05_RH06_RH07",
              "mean_RH05_RH06_RH07_RH08",
              "mean_RH06_RH07_RH08_RH09",
              #"mean_RH07_RH08_RH09_RH10",
              #"mean_RH08_RH09_RH10_RH11",
              "mean_RH03_RH04_RH05_RH06_RH07",
              "mean_RH04_RH05_RH06_RH07_RH08",
              "mean_RH05_RH06_RH07_RH08_RH09",
              #"mean_RH06_RH07_RH08_RH09_RH10",
              #"mean_RH07_RH08_RH09_RH10_RH11",
              "mean_RH03_RH04_RH05_RH06_RH07_RH08",
              "mean_RH04_RH05_RH06_RH07_RH08_RH9",
              #"mean_RH05_RH06_RH07_RH08_RH09_RH10",
              #"mean_RH06_RH07_RH08_RH09_RH10_RH11",
              "mean_RH03_RH04_RH05_RH06_RH07_RH08_RH09",
              #"mean_RH04_RH05_RH06_RH07_RH08_RH09_RH10",
              #"mean_RH05_RH06_RH07_RH08_RH09_RH10_RH11",
              #"mean_RH03_RH04_RH05_RH06_RH07_RH08_RH09_RH10",
              #"mean_RH04_RH05_RH06_RH07_RH08_RH09_RH10_RH11",
              #"mean_RH03_RH04_RH05_RH06_RH07_RH08_RH09_RH10_RH11",
              
             
              "MDC_03",
              "MDC_04",
              "MDC_05",
              "MDC_06",
              "MDC_07", 
              "MDC_08", 
              "MDC_09",
              #"MDC_10", 
              #"MDC_11", 
              "mean_MDC_03_MDC_04",
              "mean_MDC_04_MDC_05",
              "mean_MDC_05_MDC_06",
              "mean_MDC_06_MDC_07", 
              "mean_MDC_07_MDC_08", 
              "mean_MDC_08_MDC_09",
              #"mean_MDC_09_MDC_10",
              #"mean_MDC_10_MDC_11", 
              "mean_MDC_03_MDC_04_MDC_05",
              "mean_MDC_04_MDC_05_MDC_06",
              "mean_MDC_05_MDC_06_MDC_07", 
              "mean_MDC_06_MDC_07_MDC_08",
              "mean_MDC_07_MDC_08_MDC_09",
              #"mean_MDC_08_MDC_09_MDC_10",
              #"mean_MDC_09_MDC_10_MDC_11", 
              "mean_MDC_03_MDC_04_MDC_05_MDC_06",
              "mean_MDC_04_MDC_05_MDC_06_MDC_07",
              "mean_MDC_05_MDC_06_MDC_07_MDC_08",
              "mean_MDC_06_MDC_07_MDC_08_MDC_09",
              #"mean_MDC_07_MDC_08_MDC_09_MDC_10",
              #"mean_MDC_08_MDC_09_MDC_10_MDC_11",
              "mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07",
              "mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08",
              "mean_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09",
              #"mean_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10",
              #"mean_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11",
              "mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08",
              "mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_9",
              #"mean_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10",
              #"mean_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11",
              "mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09")
              #"mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10")
              #"mean_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11",
              #"mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10",
              #"mean_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11",
              #"mean_MDC_03_MDC_04_MDC_05_MDC_06_MDC_07_MDC_08_MDC_09_MDC_10_MDC_11")

 variables1<-c("Tmax04", "Tmax05", "Tmax06", "Tmax07", "Tmax08", "Tmax09", "mean_Tmax03_Tmax04_Tmax05", "mean_Tmax04_Tmax05_Tmax06", "mean_Tmax06_Tmax07_Tmax08", "mean_Tmax07_Tmax08_Tmax09", "mean_Tmax04_Tmax05_Tmax06_Tmax07", "mean_Tmax05_Tmax06_Tmax07_Tmax08",
               "Tave04","Tave05", "Tave06", "Tave07", "Tave08", "Tave09", "mean_Tave03_Tave04_Tave05", "mean_Tave04_Tave05_Tave06", "mean_Tave06_Tave07_Tave08", "mean_Tave07_Tave08_Tave09", "mean_Tave04_Tave05_Tave06_Tave07", "mean_Tave05_Tave06_Tave07_Tave08",
               "RH04","RH05", "RH06", "RH07", "RH08", "RH09", "mean_RH03_RH04_RH05", "mean_RH04_RH05_RH06", "mean_RH06_RH07_RH08", "mean_RH07_RH08_RH09", "mean_RH04_RH05_RH06_RH07", "mean_RH05_RH06_RH07_RH08")
 
variables2<-c("PPT04","PPT05", "PPT06", "PPT07", "PPT08", "PPT09", "mean_PPT03_PPT04_PPT05", "mean_PPT04_PPT05_PPT06", "mean_PPT06_PPT07_PPT08", "mean_PPT07_PPT08_PPT09", "mean_PPT04_PPT05_PPT06_PPT07", "mean_PPT05_PPT06_PPT07_PPT08",
              "PPT04","PPT05", "PPT06", "PPT07", "PPT08", "PPT09", "mean_PPT03_PPT04_PPT05", "mean_PPT04_PPT05_PPT06", "mean_PPT06_PPT07_PPT08", "mean_PPT07_PPT08_PPT09", "mean_PPT04_PPT05_PPT06_PPT07", "mean_PPT05_PPT06_PPT07_PPT08",
              "PPT04","PPT05", "PPT06", "PPT07", "PPT08", "PPT09", "mean_PPT03_PPT04_PPT05", "mean_PPT04_PPT05_PPT06", "mean_PPT06_PPT07_PPT08", "mean_PPT07_PPT08_PPT09","mean_PPT04_PPT05_PPT06_PPT07", "mean_PPT05_PPT06_PPT07_PPT08") 
# precipitation and MDC and temperature and MDC are quite correlated so I'm leaving this combination of variables out. 

```

Inspect data and create dataframe

```{r}
table(fire_escapes_final$fire_yr, fire_escapes_final$escape)
table(fire_escapes_final$fire_yr, fire_escapes_final$escape, fire_escapes_final$Cluster)

# put Cluster 3 into Cluster5
fire_escapes_final$Cluster[fire_escapes_final$Cluster==3]<-5

# remove geometry column
fire_escape<-st_set_geometry(fire_escapes_final,NULL) # remove geometry column for dataset

#esc<-st_set_geometry(fire_escapes_final,NULL)
#write.csv(esc, "C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\escape_data.csv")


```

Run the loop to determine the best climate variable for each of the Cluster's.


```{r}
# create loop to do variable selection of climate data
fire_escape$Cluster[fire_escape$Cluster==3]<-5

unique(fire_escape$Cluster)
str(fire_escape$Cluster)
fire_escape$Cluster<-as.factor(fire_escape$Cluster)
zones<- c("5", "12", "15", "7", "9", "10", "11", "13", "14")

filenames<-list()
prop<-0.75

```


```{r}

for (g in 1:100){
   print(paste(g))

for (h in 1:length(zones)) {
  #print(paste((variables[i]), (zones[h]), sep=" "))
  print(paste(zones[h], g, sep=" --"))
  dat2<- fire_escape %>% dplyr::filter(Cluster ==zones[h])
  
#Create frame of AIC table
# summary table
table.glm.climate.simple <- data.frame (matrix (ncol = 4, nrow = 0))
colnames (table.glm.climate.simple) <- c ("Zone", "Variable", "AIC", "AUC")

# Create test and training datasets
dat_0<-dat2 %>% filter(escape10==0)
dt_0 = sort(sample(nrow(dat_0), nrow(dat_0)*prop))
train_0<-dat_0[dt_0,]
test_0<-dat_0[-dt_0,]

dat_1<-dat2 %>% filter(escape10==1)
dt_1 = sort(sample(nrow(dat_1), nrow(dat_1)*prop))
train_1<-dat_1[dt_1,]
test_1<-dat_1[-dt_1,]

dat_train<-rbind(train_0,train_1)
dat_test<-rbind(test_0,test_1)

model1 <- glm (escape10 ~ 1 ,
               data=dat_train,
               family = binomial (link = "logit"))

table.glm.climate.simple[1,1]<-zones[h]
table.glm.climate.simple[1,2]<-"intercept"
table.glm.climate.simple[1,3]<-extractAIC(model1)[2]

# lets look at fit of the Valid (validation) dataset
dat_test$model1_predict <- predict.glm(model1,newdata = dat_test,type="response")
roc_obj <- roc(dat_test$escape10, dat_test$model1_predict, quiet=TRUE)
auc(roc_obj)
table.glm.climate.simple[1,4]<-auc(roc_obj)

#rm(model_dat,dat1,Valid)

for (i in 1: length(variables)){
  #print(paste((variables[i]), (zones[h]), sep=" "))
  
  #model_dat<- dat2 %>% dplyr::select(escape10, variables[i])
  dat_test1<-dat_test %>% dplyr::select(escape10, variables[i])
  dat_train1<-dat_train %>% dplyr::select(escape10,variables[i])
  
  model1 <- glm (escape10 ~ . ,
                 data=dat_train1,
                 family = binomial (link = "logit"))
  
  table.glm.climate.simple[i+1,1]<-zones[h]
  table.glm.climate.simple[i+1,2]<-variables[i]
  table.glm.climate.simple[i+1,3]<-extractAIC(model1)[2]
  
  # lets look at fit of the Valid (validation) dataset
  dat_test1$model1_predict <- predict.glm(model1,newdata = dat_test1,type="response")
  roc_obj <- roc(dat_test1$escape10, dat_test1$model1_predict, quiet=TRUE)
  auc(roc_obj)
  table.glm.climate.simple[i+1,4]<-auc(roc_obj)
  
}

# This is an addition to the table above allowing combinations of temperature and precipitation

for (i in 1: length(variables1)){
  #print(paste((variables1[i]), variables2[i], (zones[h]), sep=" "))
  dat_train2<- dat_train %>% dplyr::select(escape10, variables1[i], variables2[i])
  dat_test2<-dat_test %>% dplyr::select(escape10, variables1[i], variables2[i])
  
  model2 <- glm (escape10 ~ . ,
                 data=dat_train2,
                 family = binomial (link = "logit"))
  
  table.glm.climate.simple[(i+length(variables))+1,1]<-zones[h]
  table.glm.climate.simple[(i+length(variables))+1,2]<-paste0(variables1[i],"+", variables2[i])
  table.glm.climate.simple[(i+length(variables))+1,3]<-extractAIC(model2)[2]
  
  dat_test2$model2_predict <- predict.glm(model2,newdata = dat_test2,type="response")
  roc_obj <- roc(dat_test2$escape10, dat_test2$model2_predict,quiet=TRUE)
  auc(roc_obj)
  table.glm.climate.simple[(i+length(variables))+1,4]<-auc(roc_obj)
  
}

for (i in 1: length(variables1)){
  #print(paste((variables1[i]), "x",variables2[i], (zones[h]), sep=" "))

  if (dim(dat_1)[1]>150) {
  model2 <- glm (escape10 ~ (.)^2,
                 data=dat_train2,
                 family = binomial (link = "logit"))

  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),1]<-zones[h]
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),2]<-paste0(variables1[i],"x", variables2[i])
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),3]<-extractAIC(model2)[2]

  dat_test2$model2_predict <- predict.glm(model2,newdata = dat_test2,type="response")
  roc_obj <- roc(dat_test2$escape10, dat_test2$model2_predict, quiet=TRUE)
  auc(roc_obj)
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),4]<-auc(roc_obj)
  } 
  
  else {
      table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),1]<-zones[h]
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),2]<-paste0(variables1[i],"x", variables2[i])
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),3]<-"missing"
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),4]<-"missing"
  }

}

#table.glm.climate1<-table.glm.climate.simple %>% drop_na(AIC)


#assign file names to the work
nam1<-paste("AIC",zones[h],"run",g,sep="_") #defining the name
assign(nam1,table.glm.climate.simple)
filenames<-append(filenames,nam1)
}
}
# Common warning message: glm.fit: fitted probabilities numerically 0 or 1 occurred


```

Save output:

```{r}

mkFrameList <- function(nfiles) {
  d <- lapply(seq_len(nfiles),function(i) {
    eval(parse(text=filenames[i]))
  })
  do.call(rbind,d)
}

n<-length(filenames)
aic_bec_lightning<-mkFrameList(n) 

str(aic_bec_lightning)

aic_bec_lightning_a<-aic_bec_lightning %>% 
  filter(AIC != "missing") 

aic_bec_lightning$AIC<- as.numeric(aic_bec_lightning$AIC)
aic_bec_lightning$AUC<-as.numeric(aic_bec_lightning$AUC)
table(is.na(aic_bec_lightning$AIC))

aic_bec_lightning2<- aic_bec_lightning %>% na.omit()
  
aic_bec_lightning_summary<- aic_bec_lightning2 %>%
  group_by(Zone, Variable) %>%
  summarise(meanAIC=mean(AIC),
            meanAUC=mean(AUC),
            sdAUC=sd(AUC),
            )

aic_bec_lightning_summary2<- aic_bec_lightning_summary %>%
  group_by(Zone) %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

aic_bec_lightning_summary2

```

Save files.

```{r}
#Save AIC table
write.csv(aic_bec_lightning_summary2, file="C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\tmp\\escape_climate_AIC_results_allData.csv")

```


```{r}
###
# connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
#                       host = key_get('dbhost', keyring = 'postgreSQL'),
#                       user = key_get('dbuser', keyring = 'postgreSQL'),
#                       dbname = key_get('dbname', keyring = 'postgreSQL'),
#                       password = key_get('dbpass', keyring = 'postgreSQL'),
#                       port = "5432")
# st_write (obj = Escape_data_ALL_LandPb, 
#           dsn = connKyle, 
#           layer = c ("public", "Escape_data_ALL_LandP"))
# 
# dbDisconnect (connKyle)
# 
# ## use this for middle code to loadback in later
# Escape_data_ALL_LandP <- sf::st_read  (dsn = connKyle, # connKyle
#                                query = "SELECT * FROM public.Escape_data_ALL_LandP")

```

Create frequency distribution of the number of escaped fires per year by each BEC zone.

```{r}
table(fire_escape$fire_yr, fire_escape$escape, fire_escape$Cluster)
escaped_table_BEC<-table(fire_escape$fire_yr, fire_escape$escape, fire_escape$Cluster)
str(escaped_table_BEC)
#escaped_table_BEC[3]<-(escaped_table_BEC$[2]/(escaped_table_BEC$[2]+escaped_table_BEC$[1]))

##Create by month? Might be able to do with just the ignition data

table(Escape_data_ALL_LandP$fire_yr, Escape_data_ALL_LandP$escape, Escape_data_ALL_LandP$ntrl_ds)
escaped_table_ntrl_ds<-table(Escape_data_ALL_LandP$fire_yr, Escape_data_ALL_LandP$escape, Escape_data_ALL_LandP$ntrl_ds)
str(escaped_table_ntrl_ds)

```

