---
title: "Model_coefficient_table"
author: "Elizabeth Kleynhans"
date: "2023-06-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Varying coefficients for fire castor 

Here Im creating a look up table with the value of the model coefficients i.e. slopes (b1, b2, b3 etc) for each variable and each fire cause. I initally thought of hard coding it into fireCastor. But if I ever update or add values it will be annoying to change the values. so instead Ill make a script so that I can more easily update it. 


## Coefficient table for lightning 

# get coefficient data
```{r cars}

###############################
#Import climate data per ignition and sample location
###############################

#Depending on where you saved your output, you may need to update the directory below
file.list1<-list.files("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables", pattern="top_mod_table", all.files=FALSE, full.names=FALSE)
y1<-gsub(".csv","",file.list1)
the_dir <- "C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables"

for (i in 1:length(file.list1)){
  assign(paste0(y1[i]),read.csv (file=paste0(the_dir, "\\", file.list1[i])))
}


```

# create and empty table and populate
```{r}
coef_table <- data.frame (matrix (ncol = 20, nrow = 0))
colnames (coef_table ) <- c ("cause", "frt","coef_climate_1", "coef_climate_2",  "coef_c1", "coef_c2", "coef_c3", "coef_c4","coef_c5", "coef_c7", "coef_d12","coef_m12", "coef_m3",  "coef_N", "coef_o1ab", "coef_s1", "coef_s2", "coef_s3", "coef_road_dist", "coef_log_road_dist")

for (i in 1: length(y1)){
  
  x<-eval(as.name(y1[i]))


coef_table[i,"cause"]<-x$Cause
coef_table[i,"frt"]<-x$FRT
if("coef_climate_1" %in% names(x)){
  coef_table[i, "coef_climate_1"]<-x$coef_climate_1
} else {
    coef_table[i, "coef_climate_1"]<-NA}

if("coef_climate_2" %in% names(x)){
  coef_table[i, "coef_climate_2"]<-x$coef_climate_2
} else {
    coef_table[i, "coef_climate_2"]<-NA}

if("coef_FWI_veg_C.1" %in% names(x)){
  coef_table[i, "coef_c1"]<-x$coef_FWI_veg_C.1
} else {
    coef_table[i, "coef_c1"]<-NA}

if("coef_FWI_veg_C.2" %in% names(x)){
  coef_table[i, "coef_c2"]<-x$coef_FWI_veg_C.2
} else {
    coef_table[i, "coef_c2"]<-NA}

if("coef_FWI_veg_C.3" %in% names(x)){
  coef_table[i, "coef_c3"]<-x$coef_FWI_veg_C.3
} else {
    coef_table[i, "coef_c3"]<-NA}

if("coef_FWI_veg_C.4" %in% names(x)){
  coef_table[i, "coef_c4"]<-x$coef_FWI_veg_C.4
} else {
    coef_table[i, "coef_c4"]<-NA}

if("coef_FWI_veg_C.5" %in% names(x)){
  coef_table[i, "coef_c5"]<-x$coef_FWI_veg_C.5
} else {
    coef_table[i, "coef_c5"]<-NA}

if("coef_FWI_veg_C.7" %in% names(x)){
  coef_table[i, "coef_c7"]<-x$coef_FWI_veg_C.7
} else {
    coef_table[i, "coef_c7"]<-NA}

if("coef_FWI_veg_D.1.2" %in% names(x)){
  coef_table[i, "coef_d12"]<-x$coef_FWI_veg_D.1.2
} else {
    coef_table[i, "coef_d12"]<-NA}

if("coef_FWI_veg_M.1.2" %in% names(x)){
  coef_table[i, "coef_m12"]<-x$coef_FWI_veg_M.1.2
} else {
    coef_table[i, "coef_m12"]<-NA}

if("coef_FWI_veg_M.3" %in% names(x)){
  coef_table[i, "coef_m3"]<-x$coef_FWI_veg_M.3
} else {
    coef_table[i, "coef_m3"]<-NA}

if("coef_FWI_veg_N" %in% names(x)){
  coef_table[i, "coef_N"]<-x$coef_FWI_veg_N
} else {
    coef_table[i, "coef_N"]<-NA}

if("coef_FWI_veg_O.1a.b" %in% names(x)){
  coef_table[i, "coef_o1ab"]<-x$coef_FWI_veg_O.1a.b
} else {
    coef_table[i, "coef_o1ab"]<-NA}

if("coef_FWI_veg_S.1" %in% names(x)){
  coef_table[i, "coef_s1"]<-x$coef_FWI_veg_S.1
} else {
    coef_table[i, "coef_s1"]<-NA}

if("coef_FWI_veg_S.2" %in% names(x)){
  coef_table[i, "coef_s2"]<-x$coef_FWI_veg_S.2
} else {
    coef_table[i, "coef_s2"]<-NA}

if("coef_FWI_veg_S.3" %in% names(x)){
  coef_table[i, "coef_s3"]<-x$coef_FWI_veg_S.3
} else {
    coef_table[i, "coef_s3"]<-NA}

if("coef_road_dist" %in% names(x)){
  coef_table[i, "coef_road_dist"]<-x$coef_road_dist
  } else if ("coef_dist_roads" %in% names(x)){
  coef_table[i, "coef_road_dist"]<-x$coef_dist_roads
  } else {
    coef_table[i, "coef_road_dist"]<-NA
    }

if("coef_log_road_dist" %in% names(x)){
  (coef_table[i, "coef_log_road_dist"]<-x$coef_log_road_dist) 
  } else if ("coef_log_road_dist_m" %in% names(x)){
  coef_table[i, "coef_log_road_dist"]<-x$coef_log_road_dist_m
  } else {
    coef_table[i, "coef_log_road_dist"]<-NA
    }

}


```

### Upload table to postgres database

```{r}
library(data.table)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "fire_model_coef_tbl"), value= coef_table, row.names = FALSE, overwrite = TRUE)
dbDisconnect(conn)
```

