---
title: "mooseforageCASTOR"
author: ""
date: "10 January 2022"
output: pdf_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hold")
```

# Overview
Module to estimate moose forage biomass from forest inventory data using the method developed by Doug Lewis. 



# Usage

```{r module_usage}
library(SpaDES.core)

setPaths(modulePath = file.path("C:/Work/caribou/clus_repo/clus/R/SpaDES-modules"))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 1)

parameters <- list(
  .progress = list (type = NA, interval = NA),
  .globals = list (),
  dataCASTOR = list (nameForestInventoryTable = "veg_comp_lyr_r1_poly2020", 
                         nameForestInventoryKey = "feature_id"),
  mooseforageCASTOR = list (nameForestInventoryWetland = "bclcs_level_3", 
                          nameForestInventoryWetlandClass = "W", 
                          nameForestInventoryRiparianField = "bclcs_level_5",
                          nameForestInventoryRiparianClass = "RI",
                          climateRaster = "rast.moose_ces",
                          updateclimateRaster = FALSE
                          ) 
)
modules <- list ("mooseforageCASTOR")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

mySimOut <- spades(mySim)
```

# Parameters

nameForestInventoryWetland = "bclcs_level_3", 
                          nameForestInventoryWetlandClass = "W", 
                          nameForestInventoryRiparianField = "bclcs_level_5",
                          nameForestInventoryRiparianClass = "RI",
                          climateRaster = "rast.moose_ces",
                          updateclimateRaster = FALSE




```{r moduleParams, echo = FALSE}
df_params <- moduleParams("mooseforageCASTOR", "C:/Work/caribou/clus_repo/clus/R/SpaDES-modules")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("mooseforageCASTOR", "C:/Work/caribou/clus_repo/clus/R/SpaDES-modules")` may be sufficient.

```{r moduleInputs, echo = FALSE}
df_inputs <- moduleInputs("mooseforageCASTOR", "C:/Work/caribou/clus_repo/clus/R/SpaDES-modules")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE}
df_outputs <- moduleOutputs("mooseforageCASTOR", "C:/Work/caribou/clus_repo/clus/R/SpaDES-modules")
knitr::kable(df_outputs)
```

# Links to other modules

Describe any anticipated linkages to other modules.
