---
title: "dataLoaderCLUS"
author: ""
date: "04 September 2018"
output: pdf_document
---

```{r, eval =FALSE}
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
# http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and limitations under the License.

#===========================================================================================
```

# Overview

The data loader preps the database connectivitiy and other objects required to run CLUS

# Usage

```{r module_usage}
library(SpaDES)
library(SpaDES.core)

moduleDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules")
inputDir <- file.path(moduleDir, "inputs") %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(moduleDir, "outputs")
cacheDir <- file.path(outputDir, "cache")
times <- list(start = 0, end = 10)
parameters <- list()
modules <- list("dataLoaderCLUS")
objects <- list()
paths <- list(
  cachePath = cacheDir,
  modulePath = moduleDir,
  inputPath = inputDir,
  outputPath = outputDir
)

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)

spades(mySim)
```

# Events

The module only has an inititialization event for connecting to a database and establishing database objects


## Output data

The outputs contain the database connection object, functions needed to generate queries and the boundary and bounding box of the boundary needed for other queries

# Links to other modules

Links to every module required by CLUS

