<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Database creation for Mackenzie TSA Analyses Version 1.0"
author: "Kyle Lochhead and Tyler Muhly"
date: "7 July 2020"
output: pdf_document
---

# Overview

The dataloaderCLUS preps the database and other objects required to run CLUS. A SQLite database is stored in memory called clusdb. This database can be saved to file using `save_clusdb = TRUE` or an existing clusdb can be used by specifying the path with `useCLUSdb = ".../clusdb.sqlite"`.

Here I set the parameters to create a database for the [Mackenzie timber supply area (TSA)](https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/timber-supply-review-and-allowable-annual-cut/allowable-annual-cut-timber-supply-areas/mackenzie-tsa). The TSA is British Columbia’s fourth largest, covering 6.41 million hectares in B.C.’s northeast. The Mackenzie TSA’s allowable annual cut (AAC) is 4.5 million cubic metres as of November 14, 2014. A maximum of 2 M m3 is attributable to live uninfested timber and of this 500 000 can be taken from the south west portion of the TSA. Below the databases are divided into the main portion of the TSA (MacKenzie_TSA) adn teh southwest portion (MacKenzie_SW_TSA)

The TSA (excluding the SW portion) overlaps with the Gataga, Rabbit, Frog, Chase, Wolverine, Finlay, Graham, Moberly, Kennedy Siding, and Thutade caribou herds. This partnership also overlaps with some fo the Section 11 Partnership Agreement areas, which are included here.

The SW portion of the TSA overlaps with the Scott and Wolverine herds.

# Main portion of Mackenzie
Set parameters for creating the database for the main portion of the TSA in the code chunk below. 
```{r module_usage}
library (SpaDES)
library (SpaDES.core)
library (data.table)
library (keyring)

source (here::here("R/functions/R_Postgres.R"))

Sys.setenv (JAVA_HOME='C:\\Program Files\\Java\\jdk-14.0.1')
#Sys.setenv(JAVA_HOME = 'C:\\Program Files (x86)\\Java\\jre1.8.0_241') #throws an error if pointing to different version of java (i.e., 32 vs 64 bit)

setPaths (modulePath = here::here("R/SpaDES-modules"))

getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 0)
parameters <-  list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list (dbName = 'clus', # name of the postgres database
                         save_clusdb = TRUE,
                         nameBoundaryFile = "tsa_aac_bounds", # name of the TSA boundary data in postgres
                         nameBoundaryColumn = "tsa_name", # name of the column in the boundary (TSA) data with the boundary (TSA) name
                         nameBoundary = "MacKenzie_TSA", # MacKenzie_SW_TSA MacKenzie_TSA
                         nameBoundaryGeom = 'wkb_geometry', # geometry column name in the boundary file
                         nameCompartmentRaster = "rast.tsa_aac_boundary", # name of the raster with boundaries (TSAs) id's (integers); note the 'raster' schema in postgres
                         nameCompartmentTable = "tsa_aac_bounds_vat", # boundary (TSA) names corresponding to raster id's
                         nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018', # THLB raster in postgres
                         nameZoneRasters = c("rast.zone_cond_beo", # rasters of the zone constraints to include
                                             "rast.zone_cond_vqo", 
                                             "rast.zone_cond_wha", 
                                             "rast.zone_uwr_2021", #"rast.zone_cond_uwr"
                                             "rast.zone_cond_fsw", # there are no FSWs, but this includes ECA
                                             "rast.zone_cond_nharv", # includes parks and no harvest OGMAs
                                             "rast.zone_cond_cw",
                                             "rast.zone_cond_partnership_agreement",
                                              "rast.zone_cond_noharvest_moberly_crithab_or_herd",
                                              "rast.zone_cond_noharvest_gataga_crithab_or_herd",
                                              "rast.zone_cond_noharvest_wolverine_crithab_or_herd",
                                              "rast.zone_cond_noharvest_chase_crithab_or_herd",
                                              "rast.zone_cond_noharvest_finlay_crithab_or_herd",
                                              "rast.zone_cond_noharvest_kennedy_siding_crithab_or_herd",
                                              "rast.zone_cond_noharvest_graham_crithab_or_herd",
                                              "rast.zone_cond_noharvest_rabbit_crithab_or_herd",
                                              "rast.zone_cond_noharvest_frog_crithab_or_herd",
                                              "rast.zone_cond_noharvest_thutade_crithab_or_herd",
                                              "rast.zone_cond_eccc_moberly_crithab_or_herd",
                                              "rast.zone_cond_eccc_gataga_crithab_or_herd",
                                              "rast.zone_cond_eccc_wolverine_crithab_or_herd",
                                              "rast.zone_cond_eccc_chase_crithab_or_herd",
                                              "rast.zone_cond_eccc_finlay_crithab_or_herd",
                                              "rast.zone_cond_eccc_kennedy_siding_crithab_or_herd",
                                              "rast.zone_cond_eccc_graham_crithab_or_herd",
                                              "rast.zone_cond_eccc_rabbit_crithab_or_herd",
                                              "rast.zone_cond_eccc_frog_crithab_or_herd",
                                              "rast.zone_cond_eccc_thutade_crithab_or_herd",
                                              "rast.zone_cond_bc_graham_crithab",
                                              "rast.zone_cond_bc_moberly_crithab",
                                              "rast.zone_cond_bc_kennedy_siding_crithab",
                                              "rast.central_grp_proposed_luo",
                                              "rast.central_grp_proposed_luo_buffer",
                                              "rast.central_grp_proposed_luo_matrix",
                                              "rast.central_grp_proposed_luo_feb2021",
                                              "rast.zone_du7_scenario_20210330"
                                          ), 
                         nameZoneTable = "zone.constraints",
                        # nameZonePriorityRaster = "rast.zone_cond_beo",
                         nameYieldsRaster = "rast.ycid_vdyp", 
                         nameYieldTable = "yc_vdyp", 
                         nameYieldsTransitionRaster = "rast.tipsy2018_id", 
                         nameYieldTransitionTable = "yc_tipsy", 
                         nameForestInventoryRaster = "rast.vri2019_id", 
                         nameForestInventoryKey = "feature_id", 
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2019", 
                         nameForestInventoryAge = "proj_age_1", 
                         nameForestInventoryHeight = "proj_height_1", 
                         nameForestInventoryCrownClosure = "crown_closure",
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index" 
                    ),
  blockingCLUS = list(blockMethod = 'pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl", 
                      useLandingsArea = FALSE),
  roadCLUS = list(roadMethod = 'pre', 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'
                  ),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"),
  uploaderCLUS = list(aoiName = 'mackenzie_tsa',
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))),
  yieldUncertaintyCLUS = list (elevationRaster = 'rast.dem'), # elevation parameter needed to estimate uncertainty
  disturbanceCalcCLUS = list(calculateInterval = 5, # at what time interval to calculate disturbance
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.perm_dist_rds", # permanently disturbed features (never recover)
                             recovery = 40) # time for roads adn cutblocks to 'recover' from disturbance
  )

# rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU8' and  species = 'caribou' and season IN ('A')")) # use annual caribou RSF model coefficients for DU7
#rsf_model_coeff[, population := 'Tweedsmuir'] 

scenario = data.table(name = "load_data", 
                      description = "dataloader")

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))
modules <- list("dataLoaderCLUS", 
                "blockingCLUS",
                "roadCLUS",
                #"rsfCLUS",
                "survivalCLUS", 
                "disturbanceCalcCLUS",
                "uploaderCLUS" 
                )

objects <- list(patchSizeDist = patchSizeDist, 
                #rsf_model_coeff = rsf_model_coeff,
                scenario = scenario)

inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

system.time({
mysimout<-spades(mySim)
})
```

# Southwest portion of Mackenzie
Set parameters for creating the SW portion of the database in the code chunk below. 
```{r module_usage}
library(SpaDES)
library(SpaDES.core)
library(data.table)
library (keyring)

source(here::here("R/functions/R_Postgres.R"))

Sys.setenv(JAVA_HOME='C:\\Program Files\\Java\\jdk-14.0.1')
#Sys.setenv(JAVA_HOME = 'C:\\Program Files (x86)\\Java\\jre1.8.0_241') #throws an error if pointing to different version of java (i.e., 32 vs 64 bit)

setPaths(modulePath = here::here("R/SpaDES-modules"))

getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 0)
parameters <-  list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list (dbName = 'clus', # name of the postgres database
                         save_clusdb = TRUE,
                         nameBoundaryFile = "tsa_aac_bounds", # name of the TSA boundary data in postgres
                         nameBoundaryColumn = "tsa_name", # name of the column in the boundary (TSA) data with the boundary (TSA) name
                         nameBoundary = "MacKenzie_SW_TSA", # the boudnary (TSA) name
                         nameBoundaryGeom = 'wkb_geometry', # geometry column name in the boundary file
                         nameCompartmentRaster = "rast.tsa_aac_boundary", # name of the raster with boundaries (TSAs) id's (integers); note the 'raster' schema in postgres
                         nameCompartmentTable = "tsa_aac_bounds_vat", # boundary (TSA) names corresponding to raster id's
                         nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2018', # THLB raster in postgres
                         nameZoneRasters = c("rast.zone_cond_beo", # rasters of the zone constraints to include
                                             "rast.zone_cond_vqo", 
                                             "rast.zone_cond_wha", 
                                             "rast.zone_cond_uwr",
                                             "rast.zone_cond_fsw", # there are no FSWs, but this includes ECA
                                             "rast.zone_cond_nharv", # includes parks and no harvest OGMAs
                                             "rast.zone_cond_cw",
                                             "rast.zone_cond_noharvest_wolverine_crithab_or_herd",                                                                  "rast.zone_cond_noharvest_scott_crithab_or_herd",
                                             "rast.zone_cond_eccc_wolverine_crithab_or_herd", 
                                             "rast.zone_cond_eccc_scott_crithab_or_herd"
                                          ), 
                         nameZoneTable = "zone_constraints", # table that defines the constraints in the rasters
                         nameYieldsRaster = "rast.ycid_vdyp", # raster of stand id for VDYP ("natural origin") yields
                         nameYieldTable = "yc_vdyp", # VDYP yield  table
                         nameYieldsTransitionRaster = "rast.tipsy2018_id", # raster of stand id for TIPSY ("managed") yeilds
                         nameYieldTransitionTable = "yc_tipsy", # table that transitions stands onto TIPSY yield curve once they are cut
                         nameForestInventoryRaster = "rast.vri2018_id", # raster of the forest inventory 
                         nameForestInventoryKey = "feature_id", # unique id of each polygon (stand) in the inventory 
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2018", # the invenotry data
                         nameForestInventoryAge = "proj_age_1", # name of the age column in the inventory data
                         nameForestInventoryHeight = "proj_height_1", # name of the height column in the inventory data
                         nameForestInventoryCrownClosure = "crown_closure", # name of the crown closure column in the inventory data
                         nameForestInventorySiteIndex = "site_index" # name of the site index column in the inventory data
                    ),
  blockingCLUS = list(blockMethod = 'pre', # 'pre' sets the model to identify homegenuous forest stands for cutting 
                      patchZone = 'rast.zone_cond_beo', # patch sizes to meet biodiversity emphasiss option standards
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl", # existing cutblocks data
                      useLandingsArea = FALSE),
  roadCLUS = list(roadMethod = 'pre', # 'pre' creates the road network using a a minimum spanning tree to all potential 'ladndings (created in blockingCLUS)
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.crds_all'# existign road network
                  ),
  rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
                  criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                  randomEffectsTable = "public.rsf_re_coeff",
                  writeRSFRasters = TRUE,
                  checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "public.caribou_herd_vat"),
  uploaderCLUS = list(aoiName = 'mackenzie_sw_tsa',
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))),
  yieldUncertaintyCLUS = list (elevationRaster = 'rast.dem'), # elevation parameter needed to estimate uncertainty
  disturbanceCalcCLUS = list(calculateInterval = 5, # at what time interval to calculate disturbance
                             criticalHabitatTable = "public.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.perm_dist_rds", # permanently disturbed features (never recover)
                             recovery = 40) # time for roads adn cutblocks to 'recover' from disturbance
  )

rsf_model_coeff <- data.table (getTableQuery ("SELECT * FROM rsf_model_coeff WHERE population = 'DU9' and  species = 'caribou' and season IN ('A')")) # use annual caribou RSF model coefficients for DU7
#rsf_model_coeff[, population := 'Tweedsmuir'] 

scenario = data.table(name = "load_data", 
                      description = "dataloader")

patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))
modules <- list("dataLoaderCLUS", 
                "blockingCLUS",
                "roadCLUS",
                #"rsfCLUS",
                "survivalCLUS", 
                "uploaderCLUS", 
                "disturbanceCalcCLUS")

#objects <- list(patchSizeDist=patchSizeDist, rsf_model_coeff=rsf_model_coeff , scenario = scenario)
objects <- list(patchSizeDist = patchSizeDist, 
                scenario = scenario, 
                rsf_model_coeff = rsf_model_coeff)

inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

system.time({
mysimout<-spades(mySim)
})
```