---
title: "Great Bear Rainforest analysis for UBC cummulative effects study"
author: "Elizabeth Kleynhans, Kyle Lochhead and Tyler Muhly"
date: "07/12/2020"
output: html_document
---
<style> 
p.caption {
  font-size: 1.2em;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require (kableExtra)
require (data.table)
require (DBI)
require (RPostgreSQL)
require (dplyr)
require (ggplot2)
```

## Introduction
GBR analysis with the harvest constraints that were supplied to me by UBC folks.

With all constraints (biodiversity ecosystem options, visual quality objectives, wildlife habitat areas,ungulate winter range, no harvest constraints, fisheries sensitive watersheds, community watersheds, and average retention harvests) I found an even flow at 400 000 m3/yr when the minimum harvest volume of stands was set to 250m3 and the harvest priority was as follows: stand age descending, stand volume descending, and adjacency Constraints set to 3m. 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
