---
title: "landscape simulator"
author: "Tyler Muhly"
date: '2023-01-12'
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (terra)
library (data.table)
```

## Landscape Simulator
Here I try create 'dummy' landscapes for estimating the effects of landscape configuration on simulation models. For example, to test for the effects of habitat amount, patch size and patch size distribution on fisher population abundance using an agent-based model (ABMs).

## Methods
First, create a raster. This example creates a 100km x 100km landscape centered (roughly) around 100 Mile House. Also create a table to document the scenario characteristics. 
```{r, raster of area of interest}
raster.land <- terra::rast (nrows = 1000, #1,000 * 1 ha cells = 100 km 
                            ncols = 1000, 
                            xmin = 1279755, 
                            xmax = 1279755 + 1000, 
                            ymin = 686680, 
                            ymax = 686680 + 1000, 
                            vals = 0)

crs (raster.land) <-  "epsg:3005"

tab.scenario <- data.table (scenario = character (),
                            habitat_area_km2 = numeric (),
                            patch_size_km2 = numeric (),
                            n_patches = numeric (),
                            patch_dist_km = numeric (),
                            patch_quality = character ())
```

Next create a series of landscapes with different amounts of habitat and patch configurations. Here, *h* is the percentage of the landscape that is habitat, *p* is the number of habitat patches and *d* is the distance between patches in kilometers. 

### All Habitat 
The entire landscape is habitat.
```{r, all habitat, h100.p1.d0}
h100.p1.d0 <- raster.land
h100.p1.d0 [] <- 1

tab.temp <- data.table (scenario = as.character ("h100.p1.d0"),
                        habitat_area_km2 = as.numeric (10000),
                        patch_size_km2 = as.numeric (10000),
                        n_patches = as.numeric (1),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

### 50% Habitat
Half the landscape is habitat. 

#### One Patch, Fully Connected
Habitat occurs in a single contiguous patch. 
```{r, h50.p1.d0}
h50.p1.d0 <- raster.land 
h50.p1.d0 [250:750, 1:1000] <- 1

tab.temp <- data.table (scenario = as.character ("h50.p1.d0"),
                        habitat_area_km2 = as.numeric (5000),
                        patch_size_km2 = as.numeric (5000),
                        n_patches = as.numeric (1),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

#### Two Patches, Partially Connected
The landscape is divided into two patches of equal size that make up 50% of the landscape in top left and bottom right quadrants. Connected via 'queens' case. 
```{r, h50.p2.d0}
h50.p2.d0 <- raster.land 
h50.p2.d0 [1:500, 1:500] <- 1
h50.p2.d0 [501:1000, 501:1000] <- 1

tab.temp <- data.table (scenario = as.character ("h50.p2.d0"),
                        habitat_area_km2 = as.numeric (5000),
                        patch_size_km2 = as.numeric (2500),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Two Patches, Not Connected, Close
The landscape is divided into two patches of equal size that make up 50% of the landscape, separated by 25km.  
```{r, h50.p2.d25}
h50.p2.d25 <- raster.land 
h50.p2.d25 [1:1000, 125:375] <- 1
h50.p2.d25 [1:1000, 625:875] <- 1

tab.temp <- data.table (scenario = as.character ("h50.p2.d25"),
                        habitat_area_km2 = as.numeric (5000),
                        patch_size_km2 = as.numeric (2500),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (25),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Two Patches, Not Connected, Far
The landscape is divided into two patches of equal size that make up 50% of the landscape, separated by 50km.
```{r, h50.p2.d50}
h50.p2.d50 <- raster.land 
h50.p2.d50 [1:1000, 1:250] <- 1
h50.p2.d50 [1:1000, 751:1000] <- 1

tab.temp <- data.table (scenario = as.character ("h50.p2.d50"),
                        habitat_area_km2 = as.numeric (5000),
                        patch_size_km2 = as.numeric (2500),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (50),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```                                   

#### Four Patches, Partially Connected
The landscape is divided into four patches of equal size that make up 50% of the landscape. Connected via 'queens' case. 
```{r, h50.p4.d0}
h50.p4.d0 <- raster.land 
h50.p4.d0 [1:500, 1:250] <- 1
h50.p4.d0 [501:1000, 251:500] <- 1
h50.p4.d0 [1:500, 501:750] <- 1
h50.p4.d0 [501:1000, 751:1000] <- 1

tab.temp <- data.table (scenario = as.character ("h50.p4.d0"),
                        habitat_area_km2 = as.numeric (5000),
                        patch_size_km2 = as.numeric (1250),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Four Patches, Not Connected, Close
The landscape is divided into four patches of equal size that make up 50% of the landscape. Not connected, has one patch (25km) of spacing between patches. 
```{r, h50.p4.d25}
h50.p4.d25 <- raster.land 
h50.p4.d25 [21:375, 625:979] <- 1
h50.p4.d25 [625:979, 21:375] <- 1
h50.p4.d25 [21:375, 21:375] <- 1
h50.p4.d25 [625:979, 625:979] <- 1

tab.temp <- data.table (scenario = as.character ("h50.p4.d25"),
                        habitat_area_km2 = as.numeric (5000),
                        patch_size_km2 = as.numeric (1250),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (25),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

### 25% Habitat
One quarter of the landscape is habitat. 

#### One Patch, Fully Connected
Habitat occurs in a single contiguous patch. 
```{r, h25.p1.d0}
h25.p1.d0 <- raster.land 
h25.p1.d0 [251:750, 251:750] <- 1

tab.temp <- data.table (scenario = as.character ("h25.p1.d0"),
                        habitat_area_km2 = as.numeric (2500),
                        patch_size_km2 = as.numeric (2500),
                        n_patches = as.numeric (1),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

#### Two Patches, Partially Connected
The landscape is divided into two patches of equal size that make up 25% of the landscape. Connected via 'queens' case. 
```{r, h25.p2.d0}
h25.p2.d0 <- raster.land 
h25.p2.d0 [146:500, 146:500] <- 1
h25.p2.d0 [501:854, 501:854] <- 1

tab.temp <- data.table (scenario = as.character ("h25.p2.d0"),
                        habitat_area_km2 = as.numeric (2500),
                        patch_size_km2 = as.numeric (1250),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Two Patches, Not Connected, Close
The landscape is divided into two patches of equal size that make up 25% of the landscape, separated by 25km.  
```{r, h25.p2.d25}
h25.p2.d25 <- raster.land 
h25.p2.d25 [323:677, 21:375] <- 1
h25.p2.d25 [323:677, 625:979] <- 1

tab.temp <- data.table (scenario = as.character ("h25.p2.d25"),
                        habitat_area_km2 = as.numeric (2500),
                        patch_size_km2 = as.numeric (1250),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (25),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Two Patches, Not Connected, Far
The landscape is divided into two patches of equal size that make up 25% of the landscape, separated by 50 km  
```{r, h25.p2.d50}
h25.p2.d50 <- raster.land 
h25.p2.d50 [251:750, 1:250] <- 1
h25.p2.d50 [251:750, 751:1000] <- 1

tab.temp <- data.table (scenario = as.character ("h25.p2.d50"),
                        habitat_area_km2 = as.numeric (2500),
                        patch_size_km2 = as.numeric (1250),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (50),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

#### Four Patches, Partially Connected
The landscape is divided into four patches of equal size that make up 25% of the landscape. Connected via 'queens' case. 
```{r, h25.p4.d0}
h25.p4.d0 <- raster.land 
h25.p4.d0 [1:250, 251:500] <- 1
h25.p4.d0 [251:500, 501:750] <- 1
h25.p4.d0 [501:750, 251:500] <- 1
h25.p4.d0 [751:1000, 501:750] <- 1

tab.temp <- data.table (scenario = as.character ("h25.p4.d0"),
                        habitat_area_km2 = as.numeric (2500),
                        patch_size_km2 = as.numeric (625),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Four Patches, Not Connected, Close
The landscape is divided into four patches of equal size that make up 25% of the landscape, separated by 25km.  
```{r, h25.p4.d25}
h25.p4.d25 <- raster.land 
h25.p4.d25 [125:375, 125:375] <- 1
h25.p4.d25 [125:375, 625:875] <- 1
h25.p4.d25 [625:875, 125:375] <- 1
h25.p4.d25 [625:875, 625:875] <- 1

tab.temp <- data.table (scenario = as.character ("h25.p4.d25"),
                        habitat_area_km2 = as.numeric (2500),
                        patch_size_km2 = as.numeric (625),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (25),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

#### Four Patches, Not Connected, Far
The landscape is divided into four patches of equal size that make up 25% of the landscape, separated by 50km.  
```{r, h25.p4.d50}
h25.p4.d50 <- raster.land 
h25.p4.d50 [1:250, 1:250] <- 1
h25.p4.d50 [751:1000, 1:250] <- 1
h25.p4.d50 [1:250, 751:1000] <- 1
h25.p4.d50 [751:1000, 751:1000] <- 1

tab.temp <- data.table (scenario = as.character ("h25.p4.d50"),
                        habitat_area_km2 = as.numeric (2500),
                        patch_size_km2 = as.numeric (625),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (50),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

### 10% Habitat
Approximately one tenth of the landscape is habitat. 

#### One Patch, Fully Connected
Habitat occurs in a single contiguous patch. 
```{r, h10.p1.d0}
h10.p1.d0 <- raster.land 
h10.p1.d0 [342:658, 342:658] <- 1

tab.temp <- data.table (scenario = as.character ("h10.p1.d0"),
                        habitat_area_km2 = as.numeric (1000),
                        patch_size_km2 = as.numeric (1000),
                        n_patches = as.numeric (1),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

#### Two Patches, Partially Connected
The landscape is divided into two patches of equal size that make up ~10% of the landscape. Connected via 'queens' case. 
```{r, h10.p2.d0}
h10.p2.d0 <- raster.land 
h10.p2.d0 [276:500, 276:500] <- 1
h10.p2.d0 [501:725, 501:725] <- 1

tab.temp <- data.table (scenario = as.character ("h10.p2.d0"),
                        habitat_area_km2 = as.numeric (1000),
                        patch_size_km2 = as.numeric (500),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Two Patches, Not Connected, Close
The landscape is divided into two patches of equal size that make up 10% of the landscape, separated by 25km.  
```{r, h10.p2.d25}
h10.p2.d25 <- raster.land 
h10.p2.d25 [388:612, 151:375] <- 1
h10.p2.d25 [388:612, 625:849] <- 1

tab.temp <- data.table (scenario = as.character ("h10.p2.d25"),
                        habitat_area_km2 = as.numeric (1000),
                        patch_size_km2 = as.numeric (500),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (25),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Two Patches, Not Connected, Far
The landscape is divided into two patches of equal size that make up 10% of the landscape, separated by 50km.  
```{r, h10.p2.d50}
h10.p2.d50 <- raster.land 
h10.p2.d50 [388:612, 26:250] <- 1
h10.p2.d50 [388:612, 750:974] <- 1

tab.temp <- data.table (scenario = as.character ("h10.p2.d50"),
                        habitat_area_km2 = as.numeric (1000),
                        patch_size_km2 = as.numeric (500),
                        n_patches = as.numeric (2),
                        patch_dist_km = as.numeric (50),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Four Patches, Partially Connected
The landscape is divided into four patches of equal size that make up ~10% of the landscape . Connected via 'queens' case. 
```{r, h10.p4.d0}
h10.p4.d0 <- raster.land 
h10.p4.d0 [184:342, 342:500] <- 1
h10.p4.d0 [343:501, 501:659] <- 1
h10.p4.d0 [502:660, 342:500] <- 1
h10.p4.d0 [661:819, 501:659] <- 1

tab.temp <- data.table (scenario = as.character ("h10.p4.d0"),
                        habitat_area_km2 = as.numeric (1000),
                        patch_size_km2 = as.numeric (250),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (0),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)
```

#### Four Patches, Not Connected, Close
The landscape is divided into four patches of equal size that make up 10% of the landscape, separated by 25km.  
```{r, h10.p4.d25}
h10.p4.d25 <- raster.land 
h10.p4.d25 [217:375, 625:783] <- 1
h10.p4.d25 [217:375, 217:375] <- 1
h10.p4.d25 [625:783, 625:783] <- 1
h10.p4.d25 [625:783, 217:375] <- 1

tab.temp <- data.table (scenario = as.character ("h10.p4.d25"),
                        habitat_area_km2 = as.numeric (1000),
                        patch_size_km2 = as.numeric (250),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (25),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

#### Four Patches, Not Connected, Far
The landscape is divided into four patches of equal size that make up 10% of the landscape, separated by 50km.  
```{r, h10.p4.d50}
h10.p4.d50 <- raster.land 
h10.p4.d50 [92:250, 750:908] <- 1
h10.p4.d50 [750:908, 92:250] <- 1
h10.p4.d50 [92:250, 92:250] <- 1
h10.p4.d50 [750:908, 750:908] <- 1

tab.temp <- data.table (scenario = as.character ("h10.p4.d50"),
                        habitat_area_km2 = as.numeric (1000),
                        patch_size_km2 = as.numeric (250),
                        n_patches = as.numeric (4),
                        patch_dist_km = as.numeric (50),
                        patch_quality = as.character ("High"))
tab.scenario <- rbind (tab.scenario, tab.temp)

```

### Save Data
Combine all data together into a raster "stack" (multi-band .tif). Save the .tif and 'landscape design' table. 
```{r, save data }

raster.stack <- c (h100.p1.d0, h50.p1.d0, h50.p2.d0, h50.p2.d25, h50.p2.d50, h50.p4.d0, h50.p4.d25,
                   h25.p1.d0, h25.p2.d0, h25.p2.d25, h25.p2.d50, h25.p4.d0, h25.p4.d25, h25.p4.d50,
                   h10.p1.d0, h10.p2.d0, h10.p2.d25, h10.p2.d50, h10.p4.d0, h10.p4.d25, h10.p4.d50)

names (raster.stack) <- c ("h100.p1.d0", 
                           "h50.p1.d0", 
                           "h50.p2.d0", "h50.p2.d25", "h50.p2.d50", 
                           "h50.p4.d0", "h50.p4.d25",
                           "h25.p1.d0", 
                           "h25.p2.d0", "h25.p2.d25", "h25.p2.d50", 
                           "h25.p4.d0", "h25.p4.d25", "h25.p4.d50",
                           "h10.p1.d0", 
                           "h10.p2.d0", "h10.p2.d25", "h10.p2.d50",
                           "h10.p4.d0", "h10.p4.d25", "h10.p4.d50")

terra::writeRaster (x = raster.stack, 
                    filename = paste0 (here::here(),  "/R/SpaDES-modules/FLEX2/rast_sim_landscapes.tif"), 
                    overwrite = TRUE) 

write.csv (tab.scenario, paste0 (here::here(), "/R/SpaDES-modules/FLEX2/table_sim_landscapes.csv"))
                     
```


Notes:
* minimum patch size = fisher mean home range size = 3,000 ha
* high habitat quality cell value = 4 = ~ mean d2 score and no adjustment to litter size
* low habitat quality cell value = 4 > mean d2 + 2 sd's, = 50% reduction to litter size