---
title: "12_2c_fire_escape_model_selection_NDT3_person_treed"
author: "Cora Skaien"
date: "18/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load relevant libraries
library(sf)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(RPostgreSQL)
library(rpostgis)
library(dplyr)
library(lme4)
library(arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(ggcorrplot) 
library(kableExtra)
library(data.table)
library(DBI)
library(here)
library(AICcmodavg)
library(rje)
library(base)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 12_2c_fire_escape_model_selection_NDT3_person_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection for escape by NDT.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

Load in the prepped data.

```{r}
Escape_data_person_t<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_person_trees_NDT_Oct.csv")

head(Escape_data_person_t)

```

################ PART 1: Person Caused Fires ################

We will make a loop that does something very similar to our last loop, but with the selected climate variable plus other variables of interest. For person caused fires with trees, the variables of interest include:

1. Climate variable(s)
2. Projected Height (proj_height_1)
3. projected age (proj_age_1)  
4. live_stand_volume_125
5. vegtype2
6. slope
7. aspect (cos)
8. elevation
9. Various distance to infrastructure variables (dist_mun, dist_dam, dist_nat, dist_pow, dist_mine) - no interactions
10. Land use (bclcs_level_5_2)
11. windspeed (wind_atfire)
12. roads_km (road density, which may relate to ability to fight fires)
13. Tdif_atfire (temperature difference from the month prior to the month of the fire)

Interactions of interest: two-way interactions between climate (1) and vegtype (5); two-way interactions between topography measures (6-8). 

This will be done separately for trees and non-treed areas. 

##We will do each loop separately for each NDT zone given the large number of possible models for each zone.

First we will create the variable lists that contain all of our variables of interest.

```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(climate1 = "climate1", climate2 = "climate2", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2", bclcs_level_5_2 = "bclcs_level_5_2", dist_mun = "dist_mun", dist_dam ="dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", wind_atfire = "wind_atfire", roads_km="roads_km") 

variables_all_c1<-c(climate1 = "climate1", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2", bclcs_level_5_2 = "bclcs_level_5_2", dist_mun = "dist_mun", dist_dam ="dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", wind_atfire = "wind_atfire", roads_km="roads_km") 


vars.clim<-c("climate1")
vars.clim.vegtype<-c("climate1", "vegtype2")
vars.oth<-c("proj_height_1", "proj_age_1", "live_stand_volume_125") 
vars.topo<-c("slope", "aspect", "elevation", "wind_atfire")
vars.infra<-c("dist_mun", "dist_dam", "dist_nat", "dist_pow", "dist_mine", "roads_km")

#Also for later with 2 climate variables
vars.clim.vegtype2<-c("climate1", "climate2","vegtype2")
vars.clim.vegtype2b<-c("climate1", "climate2")

##Create interaction for climate and vegtype
inputs.me <- c(vars.clim.vegtype)
inputs.me2 <- c(vars.clim.vegtype2)
inputs.me2b <- c(vars.clim.vegtype2b)
```

Now, we will generate two-way interactions for each of these lists. 

```{r}

#####1a. For those with one climate variable
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints <- NULL
for (i in 1:(length(inputs.me)-1)) {
  for (j in (i+1):length(inputs.me)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me[i], inputs.me[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints)#1

#
#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}


#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype) 
#add climate vars to all of the above
mods.me.climate <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate
mods.me.climate<-mods.me.climate[-1]

#complete list of two-way interactions
mods.twoway <- powerSet(twoway.ints)
length(mods.twoway) #2
mods.twoway
mods.twoway<-mods.twoway[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter <- list()
counter <- 0
for (i in 1: length(mods.twoway)) {
   s1 <- unique(unlist( strsplit(mods.twoway[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate)) {
      if (all(s1 %in% mods.me.climate[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate[[j]], mods.twoway[[i]])
        mods.inter[[counter]] <- both
      }
   }
}

length(mods.inter) #1
mods.inter


#####1b. For those with two climate variables
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2 <- NULL
for (i in 1:(length(inputs.me2)-1)) {
  for (j in (i+1):length(inputs.me2)) {
     twoway.ints2 <- cbind(twoway.ints2, paste(inputs.me2[i], inputs.me2[j], sep=":"))
  }
}
twoway.ints2
length(twoway.ints2) #3

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2) 
#add climate vars to all of the above
mods.me.climate2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2
mods.me.climate2<-mods.me.climate2[-1]

#complete list of two-way interactions
mods.twoway2 <- powerSet(twoway.ints2)
length(mods.twoway2) #8
mods.twoway2
mods.twoway2<-mods.twoway2[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2 <- list()
counter <- 0
for (i in 1: length(mods.twoway2)) {
   s1 <- unique(unlist( strsplit(mods.twoway2[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2)) {
      if (all(s1 %in% mods.me.climate2[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2[[j]], mods.twoway2[[i]])
        mods.inter2[[counter]] <- both
      }
   }
}

length(mods.inter2) #10
#mods.inter2
mods.inter2


####1c. Two variables, no variation in vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2b <- NULL
for (i in 1:(length(inputs.me2b)-1)) {
  for (j in (i+1):length(inputs.me2b)) {
     twoway.ints2b <- cbind(twoway.ints2b, paste(inputs.me2b[i], inputs.me2b[j], sep=":"))
  }
}
twoway.ints2b
length(twoway.ints2b) #1

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2b) 
#add climate vars to all of the above
mods.me.climate2b <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2b[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2b
mods.me.climate2b<-mods.me.climate2b[-1]

#complete list of two-way interactions
mods.twoway2b <- powerSet(twoway.ints2b)
length(mods.twoway2b) #2
mods.twoway2b
mods.twoway2b<-mods.twoway2b[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2b <- list()
counter <- 0
for (i in 1: length(mods.twoway2b)) {
   s1 <- unique(unlist( strsplit(mods.twoway2b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2b)) {
      if (all(s1 %in% mods.me.climate2b[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2b[[j]], mods.twoway2b[[i]])
        mods.inter2b[[counter]] <- both
      }
   }
}

length(mods.inter2b)
#mods.inter2b


#########2. Now for topography data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT) #6

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT
mods.meT<-mods.meT[-1]

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #64
mods.twowayT
mods.twowayT<-mods.twowayT[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT) #97
#mods.interT


####3.For other VRI data, get without interactions

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.oth
mods.me.oth<-mods.me.oth[-1]


#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI) #15

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI
mods.meI<-mods.meI[-1]

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsI)
length(mods.twowayI) #32768 -
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI) #80136
#mods.interI


#the list of all possible model RHSs. 
#all.poss.mods <- c(1, vars.clim, twoway.ints, mods.me.oth, mods.me2, mods.inter2)
#all.poss.mods

all.poss.mods.clim.vegtype<-c(1, mods.me.climate, mods.inter)
all.poss.mods.clim.vegtype 

all.poss.mods.clim.vegtype2<-c(1, mods.me.climate2, mods.inter2)
all.poss.mods.clim.vegtype2

all.poss.mods.clim.vegtype2b<-c(1, mods.me.climate2b, mods.inter2b)
all.poss.mods.clim.vegtype2b

all.poss.mods.VRI<-c(1, mods.me.oth)
all.poss.mods.VRI

all.poss.mods.topo<-c(1, mods.interT)
all.poss.mods.topo

all.poss.mods.infra<-c(1, mods.meI) #I don't think we want interactions here actually... we will in the next stage when we include bclcs_level_5_2 after some initial pattern exploration


#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim.vegtype) #None duplicated
duplicated(all.poss.mods.clim.vegtype2)
duplicated(all.poss.mods.clim.vegtype2b)
duplicated(all.poss.mods.VRI)
duplicated(all.poss.mods.topo)
duplicated(all.poss.mods.infra)

```

############### Part 1 of 4 Model Series: person Caused Fires, Trees ##########

Because of the large number of models with all variables included, we will test the climate and vegtype first, then the VRI variables, then the topography variables. Then we will test the top models together in additional combinations, with determining best AIC model from there. 

Select NDT: NDT3
#Only one climate variables

```{r}
zones1<-c("NDT3") #Do one zone at a time
prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

########### 1. Climate and vegtype ############
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_person_t %>% dplyr::filter(ntrl_ds ==zones1[h])
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim.vegtype[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim.vegtype, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT3")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}

```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_person_NDT3_escape_treed_climate<-table.glm.climate.simple

AIC_person_NDT3_escape_treed_summary_climate<- AIC_person_NDT3_escape_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT3_escape_treed_summary_climate2<- AIC_person_NDT3_escape_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT3_escape_treed_summary_climate2)
```

#Now repeat for VRI data

```{r}
########### 2. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_person_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.VRI)){
#  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$NDT<-c("NDT3")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_person_NDT3_escape_treed_VRI<-table.glm.VRI.simple

AIC_person_NDT3_escape_treed_summary_VRI<- AIC_person_NDT3_escape_treed_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT3_escape_treed_summary_VRI2<- AIC_person_NDT3_escape_treed_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT3_escape_treed_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 3. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_person_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$NDT<-c("NDT3")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_person_NDT3_escape_treed_topo<-table.glm.topo.simple

AIC_person_NDT3_escape_treed_summary_topo<- AIC_person_NDT3_escape_treed_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT3_escape_treed_summary_topo2<- AIC_person_NDT3_escape_treed_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT3_escape_treed_summary_topo2)
```

#Now repeat for infrastructure

```{r}
########### 4. Distance to Infrastructure ############
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_person_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT3")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_person_NDT3_escape_treed_infra<-table.glm.infra.simple

AIC_person_NDT3_escape_treed_summary_infra<- AIC_person_NDT3_escape_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT3_escape_treed_summary_infra2<- AIC_person_NDT3_escape_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT3_escape_treed_summary_infra2)

```

#Now combine the datatables and save to computer

```{r}
NDT3_l_models_treed<-rbind(AIC_person_NDT3_escape_treed_summary_climate2, AIC_person_NDT3_escape_treed_summary_VRI2, AIC_person_NDT3_escape_treed_summary_topo2, AIC_person_NDT3_escape_treed_summary_infra2)
NDT3_l_models_treed
NDT3_l_models_treed$NDT<-"NDT3"

write.csv(NDT3_l_models_treed, file="D:\\Fire\\fire_data\\raw_data\\NDT3_person_models_treed_escape.csv")
```


################################ STAGE TWO ########################

#STAGE TWO: PUT TOGETHER MORE VARIABLES
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Models:
1. climate1 + vegtype2
2. proj_height_1 + proj_age_1 + live_stand_volume_125
3. slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire
4. dist_mun + dist_dam + dist_nat + dist_mine + roads_km

Additional Variables:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)
**We will leave vegtype2 in final model selection to test.
2. Tdif_atfire

#Interactions to investigate:
1. elevation*climate1
2. wind_atfire*climate1
3. wind_atfire*vegtype2
4. Tdif_atfire*climate1
5. Tdif_atfire*wind_atfire
6. bclcs_level_5_2*dist_mun
7. bclcs_level_5_2*dist_dam
8. bclcs_level_5_2*dist_nat
9. bclcs_level_5_2*dist_mine
10. bclcs_level_5_2*roads_km
11. dist_mun*roads_km
12. dist_dam*roads_km
13. dist_nat*roads_km
14. dist_mine*roads_km

#Next investigation
Because there would be far too many models to investigate including all variables and their interactions, we will start with the above and make educated guesses for what may need to be enhanced. We will seek the best model from the above informed progress.

```{r}
escape_person_t_NDT3<-subset(Escape_data_person_t, Escape_data_person_t$ntrl_ds=="NDT3") #4506

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_person_t_NDT3$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_person_t_NDT3[ trainIndex,]
   Valid <- escape_person_t_NDT3[-trainIndex,]

#Run model using dat1
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + elevation*climate1 + wind_atfire*climate1 + wind_atfire*vegtype2 + Tdif_atfire*climate1 + Tdif_atfire*wind_atfire +  bclcs_level_5_2*dist_mun +  bclcs_level_5_2*dist_dam + bclcs_level_5_2*dist_pow + bclcs_level_5_2*dist_mine + bclcs_level_5_2*roads_km + dist_mun*roads_km + dist_dam*roads_km + dist_pow*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2384.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*climate1 + wind_atfire*vegtype2 + Tdif_atfire*climate1 + Tdif_atfire*wind_atfire +  bclcs_level_5_2*dist_mun + bclcs_level_5_2*dist_pow + bclcs_level_5_2*dist_mine + bclcs_level_5_2*roads_km + dist_mun*roads_km + dist_dam*roads_km + dist_pow*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2378.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*climate1 + wind_atfire*vegtype2 + Tdif_atfire*climate1 + Tdif_atfire*wind_atfire +  bclcs_level_5_2*dist_mun + bclcs_level_5_2*dist_pow + bclcs_level_5_2*dist_mine + dist_mun*roads_km + dist_dam*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2373.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*climate1 + wind_atfire*vegtype2 + Tdif_atfire*climate1 + Tdif_atfire*wind_atfire +  bclcs_level_5_2*dist_mun + dist_mun*roads_km + dist_dam*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2367.1

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*climate1 + wind_atfire*vegtype2 + Tdif_atfire*wind_atfire +  bclcs_level_5_2*dist_mun + dist_mun*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2364.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + Tdif_atfire*wind_atfire +  bclcs_level_5_2*dist_mun + dist_mun*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2363.0

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mun*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2360.8

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mun*roads_km + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2358.8

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + aspect:elevation + elevation:wind_atfire +  dist_mun + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2358.3

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + aspect:elevation + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2356.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #2356.2

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.74 --> good fit!
   
Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

```

Remove NAs and run multiple times.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT3_escape_t<-escape_person_t_NDT3 %>% drop_na(climate1, vegtype2, proj_height_1, proj_age_1, live_stand_volume_125, dist_dam, dist_nat, dist_mine, slope, aspect, elevation, wind_atfire, Tdif_atfire, roads_km, bclcs_level_5_2 ) #4309 observations

#Run Model again with this data; but uses all data here
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km, family = binomial, data = NDT3_escape_t)

Anova(model.NDT3.E, type=3)
#Anova(model.NDT3.E, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT3.E), 
            residuals(model.NDT3.E), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT3_escape_t$resids<-resid(model.NDT3.E)

binnedplot (NDT3_escape_t$live_stand_volume_125, 
            NDT3_escape_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT3_escape_t$climate1, 
            NDT3_escape_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good

#Partial Residuals
#climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km

visreg(model.NDT3.E, "climate1")
visreg(model.NDT3.E, "vegtype2", by="wind_atfire")
visreg(model.NDT3.E, "proj_height_1")
visreg(model.NDT3.E, "proj_age_1")
visreg(model.NDT3.E, "live_stand_volume_125")
visreg(model.NDT3.E, "Tdif_atfire")

#slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire
visreg(model.NDT3.E, "slope", by="aspect")
visreg(model.NDT3.E, "slope", by="wind_atfire")
visreg(model.NDT3.E, "elevation", by="wind_atfire")
visreg(model.NDT3.E, "aspect", by="slope")
visreg(model.NDT3.E, "wind_atfire", by="slope")
visreg(model.NDT3.E, "wind_atfire", by="elevation")
visreg(model.NDT3.E, "wind_atfire", by="vegtype2", overlay=TRUE)

#dist_dam + dist_nat + dist_mine + roads_km  + bclcs_level_5_2 + dist_mine*roads_km
visreg(model.NDT3.E, "dist_mine", by="roads_km")
visreg(model.NDT3.E, "dist_dam")
visreg(model.NDT3.E, "dist_nat")
visreg(model.NDT3.E, "roads_km", by="dist_mine")
visreg(model.NDT3.E, "bclcs_level_5_2")

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT3.E)

#Create a new blank table and get AUC too
top_mod_table_NDT3_person_t_ALL <- data.frame (matrix (ncol = 31, nrow = 0))
colnames (top_mod_table_NDT3_person_t_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_proj_height_1", "coef_proj_age_1", "coef_live_stand_volume_125",  "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_dam", "coef_dist_nat", "coef_dist_mine", "coef_roads_km", "coef_Tdif_atfire", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope:aspect", "coef_slope:wind_atfire", "coef_elevation:wind_atfire", "coef_vegtype2TB:wind_atfire", "coef_vegtype2TC:wind_atfire", "coef_vegtype2TM:wind_atfire", "coef_dist_mine:roads_km", "AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT3_escape_t$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT3_escape_t[ trainIndex,]
   Valid <- NDT3_escape_t[-trainIndex,]
   
#Model   
model.NDT3.E<-glm(escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3_person_t <- data.frame (matrix (ncol = 31, nrow = 0))
colnames (top_mod_table_NDT3_person_t ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_proj_height_1", "coef_proj_age_1", "coef_live_stand_volume_125",  "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_dam", "coef_dist_nat", "coef_dist_mine", "coef_roads_km", "coef_Tdif_atfire", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope:aspect", "coef_slope:wind_atfire", "coef_elevation:wind_atfire", "coef_vegtype2TB:wind_atfire", "coef_vegtype2TC:wind_atfire", "coef_vegtype2TM:wind_atfire", "coef_dist_mine:roads_km", "AUC")

##Add data for NDT3
top_mod_table_NDT3_person_t[1,1]<-"person"
top_mod_table_NDT3_person_t[1,2]<-"NDT3"
top_mod_table_NDT3_person_t[1,3]<-"Y"
top_mod_table_NDT3_person_t[1,4]<-"escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km" 
top_mod_table_NDT3_person_t[1,5]<- coef(model.NDT3.E)[1] #Intercept
top_mod_table_NDT3_person_t[1,6]<- coef(model.NDT3.E)[2] #C
top_mod_table_NDT3_person_t[1,7]<- coef(model.NDT3.E)[3] #C
top_mod_table_NDT3_person_t[1,8]<- coef(model.NDT3.E)[4] #co
top_mod_table_NDT3_person_t[1,9]<- coef(model.NDT3.E)[5] #co
top_mod_table_NDT3_person_t[1,10]<- coef(model.NDT3.E)[6] #c
top_mod_table_NDT3_person_t[1,11]<- coef(model.NDT3.E)[7] #l
top_mod_table_NDT3_person_t[1,12]<- coef(model.NDT3.E)[8] #co
top_mod_table_NDT3_person_t[1,13]<- coef(model.NDT3.E)[9] #c
top_mod_table_NDT3_person_t[1,14]<- coef(model.NDT3.E)[10] #coeff
top_mod_table_NDT3_person_t[1,15]<- coef(model.NDT3.E)[11] #co
top_mod_table_NDT3_person_t[1,16]<- coef(model.NDT3.E)[12] #coe
top_mod_table_NDT3_person_t[1,17]<- coef(model.NDT3.E)[13] #co
top_mod_table_NDT3_person_t[1,18]<- coef(model.NDT3.E)[14] #co
top_mod_table_NDT3_person_t[1,19]<- coef(model.NDT3.E)[15] #
top_mod_table_NDT3_person_t[1,20]<- coef(model.NDT3.E)[16] # cl
top_mod_table_NDT3_person_t[1,21]<- coef(model.NDT3.E)[17] # c
top_mod_table_NDT3_person_t[1,22]<- coef(model.NDT3.E)[18] #coefficien
top_mod_table_NDT3_person_t[1,23]<- coef(model.NDT3.E)[19] #coefficien
top_mod_table_NDT3_person_t[1,24]<- coef(model.NDT3.E)[20] #coefficien
top_mod_table_NDT3_person_t[1,25]<- coef(model.NDT3.E)[21] #coefficien
top_mod_table_NDT3_person_t[1,26]<- coef(model.NDT3.E)[22] #coefficien
top_mod_table_NDT3_person_t[1,27]<- coef(model.NDT3.E)[23] #coefficien
top_mod_table_NDT3_person_t[1,28]<- coef(model.NDT3.E)[24] #coefficien
top_mod_table_NDT3_person_t[1,29]<- coef(model.NDT3.E)[25] #coefficien
top_mod_table_NDT3_person_t[1,30]<- coef(model.NDT3.E)[26] #coefficien
top_mod_table_NDT3_person_t[1,31]<- mod.auc

top_mod_table_NDT3_person_t_ALL<-rbind(top_mod_table_NDT3_person_t_ALL, top_mod_table_NDT3_person_t)

}

```

Check.
```{r}
head(top_mod_table_NDT3_person_t_ALL)

```

#Save coefficient table

```{r}
write.csv(top_mod_table_NDT3_person_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT3_person_t_ALL.csv")
```


#Get Mean Values

```{r}
names(top_mod_table_NDT3_person_t_ALL)

top_mod_table_NDT3_escape_person_t_means<-top_mod_table_NDT3_person_t_ALL %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table_NDT3_escape_person_t_means

top_mod_table_NDT3_escape_person_t_means[1,1]<-"person"
top_mod_table_NDT3_escape_person_t_means[1,2]<-"NDT3"
top_mod_table_NDT3_escape_person_t_means[1,3]<-"Treed"
top_mod_table_NDT3_escape_person_t_means[1,4]<- "escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km" 
top_mod_table_NDT3_escape_person_t_means
```
Save table.

```{r}
write.csv(top_mod_table_NDT3_escape_person_t_means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT3_person_t_Means.csv")
```

Standard deviation.

```{r}
top_mod_table_NDT3_escape_person_t_sd<-top_mod_table_NDT3_person_t_ALL %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT3_escape_person_t_sd

top_mod_table_NDT3_escape_person_t_sd[1,1]<-"person"
top_mod_table_NDT3_escape_person_t_sd[1,2]<-"NDT3"
top_mod_table_NDT3_escape_person_t_sd[1,3]<-"Treed"
top_mod_table_NDT3_escape_person_t_sd[1,4]<-"escape ~ climate1 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_nat + dist_mine + roads_km + Tdif_atfire + bclcs_level_5_2  + wind_atfire*vegtype2 + dist_mine*roads_km" 
top_mod_table_NDT3_escape_person_t_sd
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT3_escape_person_t_sd, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT3_person_t_SD.csv")
```













We want to include interactions between variables from within each list. This will make for many models, which may be hard to process in R.

```{r}
##Create variable lists to be used in the model loop.
variables_all_NDT3<-c(climate1 = "climate1", climate2 = "climate2", vegtype2 = "vegtype2", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", elevation ="elevation",  dist_dam = "dist_dam", roads_km = "roads_km", bclcs_level_5_2 = "bclcs_level_5_2", wind_atfire = "wind_atfire")

#Too many permutations to be able to include two-way interactions and all possible models, so need to divide into what we think may have interactions and which not.
#variables_clim_VRI_NDT3<-c(climate1 = "climate1", climate2 = "climate2", vegtype2 = "vegtype2", live_stand_volume_125 = "live_stand_volume_125" )

#Only one climate variable
variables_clim_VRI_NDT3<-c(climate1 = "climate1", vegtype2 = "vegtype2", live_stand_volume_125 = "live_stand_volume_125" )


#treat slope, aspect and elevation as their own thing. And we have already done this analysis with them.
#slope = "slope", aspect = "aspect", elevation ="elevation")

variables_all_infra_landuse_NDT3<-c(dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_mine = "dist_mine", roads_km = "roads_km", bclcs_level_5_2 = "bclcs_level_5_2") #I don't think it makes sense to have interactions between the distance elements, but maybe with land use and each distance element?

##
inputs.me.NDT3 <- c(variables_all_NDT3)
#inputs.me.clim_VRI_DEM_NDT3 <- c(variables_clim_VRI_DEM_NDT3)
inputs.me.clim_VRI_NDT3 <- c(variables_clim_VRI_NDT3)
inputs.me.infra_landuse_NDT3 <- c(variables_all_infra_landuse_NDT3)

```

Now, we will generate two-way interactions for each of these lists. We cannot make two-way interactions between them all because apparently it will be >2 GB in size.

```{r}
twoway.ints <- NULL
for (i in 1:(length(inputs.me.NDT3)-1)) {
  for (j in (i+1):length(inputs.me.NDT3)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.NDT3[i], inputs.me.NDT3[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #45

#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(inputs.me.NDT3) 
#add climate vars to all of the above
mods.me.NDT3 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.NDT3[[i]] <- c(mods.me.tmp[[i]])
}

#mods.me.NDT3
length(mods.me.NDT3) #1024
mods.me.NDT3[1]
mods.me.NDT3<-mods.me.NDT3[-1]

#complete list of two-way interactions
#mods.twoway.NDT3 <- powerSet(twoway.ints) # Do not run; will take hours if it succeeds at all
#length(mods.twoway.NDT3) #
#mods.twoway.NDT3

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
# DO NOT RUN BELOW IF DID NOT RUN LAST BIT
mods.inter.NDT3 <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT3)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT3[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.clim_VRI_NDT3)) {
      if (all(s1 %in% mods.me.clim_VRI_NDT3[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.clim_VRI_NDT3[[j]], mods.twoway.NDT3[[i]])
        mods.inter.NDT3[[counter]] <- both
      }
   }
}

length(mods.inter.NDT3) #97

```

There are too many two-way interactions to be able to include them all, so need to break it up into smaller chunks.

```{r}
####Reduce further
twoway.ints <- NULL
for (i in 1:(length(inputs.me.clim_VRI_NDT3)-1)) {
  for (j in (i+1):length(inputs.me.clim_VRI_NDT3)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.clim_VRI_NDT3[i], inputs.me.clim_VRI_NDT3[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #3

#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(variables_clim_VRI_NDT3) 
#add climate vars to all of the above
mods.me.clim_VRI_NDT3 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.clim_VRI_NDT3[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.clim_VRI_NDT3
length(mods.me.clim_VRI_NDT3) #8

#complete list of two-way interactions
mods.twoway.NDT3 <- powerSet(twoway.ints) # 
length(mods.twoway.NDT3) #8
mods.twoway.NDT3
mods.twoway.NDT3<-mods.twoway.NDT3[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter.NDT3 <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT3)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT3[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.clim_VRI_NDT3)) {
      if (all(s1 %in% mods.me.clim_VRI_NDT3[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.clim_VRI_NDT3[[j]], mods.twoway.NDT3[[i]])
        mods.inter.NDT3[[counter]] <- both
      }
   }
}

length(mods.inter.NDT3) #10
mods.inter.NDT3

##Subset 2: Infrastructure and land use ########
#inputs.me.infra_landuse_NDT3
twoway.ints <- NULL
for (i in 1:(length(inputs.me.infra_landuse_NDT3)-1)) {
  for (j in (i+1):length(inputs.me.infra_landuse_NDT3)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.infra_landuse_NDT3[i], inputs.me.infra_landuse_NDT3[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #15
#Review. If we do not want interactions between the different distance measurements, but only those between land use and distance, subset those.
twoway.ints
twoway.ints_dist<-twoway.ints[c(4,5,8,9,11,12,13,14,15)]
twoway.ints_dist

#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(variables_all_infra_landuse_NDT3) 
#add climate vars to all of the above
mods.me.infra_landuse_NDT3 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.infra_landuse_NDT3[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.infra_landuse_NDT3
length(mods.me.infra_landuse_NDT3) #64

#complete list of two-way interactions
#mods.twoway.NDT3b <- powerSet(twoway.ints) #
#Or use subset of interactions
mods.twoway.NDT3b <- powerSet(twoway.ints_dist) 
length(mods.twoway.NDT3b) #512
#mods.twoway.NDT3b
mods.twoway.NDT3b[1]
mods.twoway.NDT3b<-mods.twoway.NDT3b[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter.NDT3b <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT3b)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT3b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.infra_landuse_NDT3)) {
      if (all(s1 %in% mods.me.infra_landuse_NDT3[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.infra_landuse_NDT3[[j]], mods.twoway.NDT3b[[i]])
        mods.inter.NDT3b[[counter]] <- both
      }
   }
}

length(mods.inter.NDT3b) #1364
#mods.inter.NDT3b
```

Make final list of variables to assess.

```{r}
## 1. climate and VRI
#the list of all possible model RHSs. 
all.poss.mods.clim_VRI_NDT3<-c(1, mods.me.clim_VRI_NDT3, mods.inter.NDT3)
#all.poss.mods.clim_VRI_NDT3
length(mods.me.clim_VRI_NDT3) #8
length(all.poss.mods.clim_VRI_NDT3) #19
#all.poss.mods.clim_VRI_NDT3


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim_VRI_NDT3) #Need to remove 
#all.poss.mods.clim_VRI_NDT3b<-all.poss.mods.clim_VRI_NDT3[-(65:127)]
#duplicated(all.poss.mods.clim_VRI_NDT3b) 
#length(all.poss.mods.clim_VRI_NDT3b) 

all.poss.mods.infra_landuse_NDT3<-c(1, mods.me.infra_landuse_NDT3, mods.inter.NDT3b)
all.poss.mods.infra_landuse_NDT3[2]
all.poss.mods.infra_landuse_NDT3<-all.poss.mods.infra_landuse_NDT3[-2]

duplicated(all.poss.mods.infra_landuse_NDT3)

#Need to remove 
#all.poss.mods.infra_landuse_NDT3b<-all.poss.mods.infra_landuse_NDT3[-(34:65)]
#duplicated(all.poss.mods.infra_landuse_NDT3b) 
#all.poss.mods.infra_landuse_NDT3b[2]
#all.poss.mods.infra_landuse_NDT3b<-all.poss.mods.infra_landuse_NDT3b[-2]
```


```{r}
#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 

#Below does not work
lapply(biglist, all.poss.mods.infra_landuse_NDT3b {length(all.poss.mods.infra_landuse_NDT3b) == 0L} ) 

```

```{r}
all.poss.mods.clim_VRI_NDT3[2]
all.poss.mods.clim_VRI_NDT3<-all.poss.mods.clim_VRI_NDT3[-2]
```

Run models.

```{r}
zones1<-"NDT3"
prop<-0.75

#Create empty table
table.glm.clim_VRI.NDT3 <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.clim_VRI.NDT3) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#Run 100 times
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_person_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim_VRI_NDT3[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim_VRI_NDT3, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT3")
tab.sum.climate 

table.glm.clim_VRI.NDT3<-rbind(table.glm.clim_VRI.NDT3, tab.sum.climate)

}
}
}

```


```{r}
head(table.glm.clim_VRI.NDT3)
table(table.glm.clim_VRI.NDT3$model) # 100 per model

AIC_person_NDT3_escape_treed_climate<-table.glm.clim_VRI.NDT3

AIC_person_NDT3_escape_treed_summary_climate<- AIC_person_NDT3_escape_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT3_escape_treed_summary_climate2<- AIC_person_NDT3_escape_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT3_escape_treed_summary_climate2)
```

Save.
```{r}
write.csv(AIC_person_NDT3_escape_treed_summary_climate2, file="D:\\Fire\\fire_data\\raw_data\\table.glm.clim_VRI.NDT3_ALL_escape.csv")
```

#Now repeat for all.poss.mods.infra_landuse_NDT3

```{r}
########### 2. Distance to Infrastructure ############
#Create empty table
table.glm.infra.lu.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.lu.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_person_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra_landuse_NDT3[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all_infra_landuse_NDT3)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_landuse_NDT3, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra.lu <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra.lu$NDT<-c("NDT3")
tab.sum.infra.lu 

table.glm.infra.lu.simple<-rbind(table.glm.infra.lu.simple, tab.sum.infra.lu)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination. Also determine deltaAIC.

```{r}
head(table.glm.infra.lu.simple)
table(table.glm.infra.lu.simple$model) # 100 per model

AIC_person_NDT3_escape_treed_infra<-table.glm.infra.lu.simple

AIC_person_NDT3_escape_treed_summary_infra<- AIC_person_NDT3_escape_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT3_escape_treed_summary_infra2<- AIC_person_NDT3_escape_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT3_escape_treed_summary_infra2)
```

Save to computer.

```{r}
write.csv(AIC_person_NDT3_escape_treed_summary_infra2, file="D:\\Fire\\fire_data\\raw_data\\AIC_person_NDT3_escape_treed_summary_infra.csv")
```

Determine the top models.

#1. Climate and VRI

#2. Infrastructure

#3. DEM


#Interactions to investigate:
1. elevation*climate1
2. elevation*climate2
3. wind_atfire*climate1
4. wind_atfire*climate2
5. wind_atfire*vegtype2
6. Tdif_atfire*climate1
7. Tdif_atfire*climate2
8. Tdif_atfire*wind_atfire

#Next investigation
Because there would be far too many models to investigate including all variables and their interactions, we will start with the above and make educated guesses for what may need to be enhanced. We will seek the best model from the above informed progress.

