---
title: "12a_fire_escape_model_selection_NDT1_ALLPL_ALLTNT"
author: "Cora Skaien"
date: "27/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load relevant libraries
library(sf)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(RPostgreSQL)
library(rpostgis)
library(dplyr)
library(lme4)
library(arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(ggcorrplot) 
library(kableExtra)
library(data.table)
library(DBI)
library(here)
library(AICcmodavg)
library(rje)
library(base)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 12a_fire_escape_model_selection_NDT1_ALLPL_ALLTNT.R
#  Script Version: 1.0
#  Script Purpose: Model selection for escape by NDT.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

Load in the prepped data.

```{r}
Escape_data_ALL<-read.csv("D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\All_data_escape_Dec.csv")
head(Escape_data_ALL)

```

################ PART 1: Initial Model Selection for Subset Variables ################

We will make a loop that does something very similar to our last loop, but with the selected climate variable plus other variables of interest. For lightning caused fires with trees, the variables of interest include:

1. Climate variable(s) (Tave09 = climate1; ppt09=climate2; mdc_atfire)
2. Projected Height (proj_height_1)*bclcs_level_2
3. projected age (proj_age_1)*bclcs_level_2
4. live_stand_volume_125*bclcs_level_2
5. vegtype2*bclcs_level_2
6. slope
7. aspect (cos)
8. elevation
9. dist_infra
10. windspeed (wind_atfire)
11. roads_km (road density, which may relate to ability to fight fires)
12. Tdif_atfire (temperature difference from the month prior to the month of the fire)
13. Fire cause (fire_cs)
#14. Land use (bclcs_level_5_2)

Interactions of interest: two-way interactions between climate (1) and vegtype (5); two-way interactions between topography measures (6-8). 

##We will do each loop separately for each NDT zone given the large number of possible models for each zone.

First we will create the variable lists that contain all of our variables of interest.

```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(climate1 = "climate1", climate2 = "climate2", mdc_atfire="mdc_atfire", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2",  dist_infra = "dist_infra", wind_atfire = "wind_atfire", roads_km="roads_km", Tdif_atfire="Tdif_atfire", bclcs_level_2 ="bclcs_level_2", fire_cs ="fire_cs") 

vars.clim.vegtype2<-c("climate1", "climate2","vegtype2", "mdc_atfire")
vars.clim.vegtype2b<-c("climate1", "climate2", "mdc_atfire")
vars.oth<-c("proj_height_1", "proj_age_1", "live_stand_volume_125", "bclcs_level_2") 
vars.topo<-c("slope", "aspect", "elevation", "wind_atfire")
vars.infra<-c("dist_infra", "roads_km")
vars.oth2<-c("wind_atfire", "Tdif_atfire")


##Create interaction for climate and vegtype
inputs.me2 <- c(vars.clim.vegtype2)
inputs.me2b <- c(vars.clim.vegtype2b)
```

Now, we will generate two-way interactions for each of these lists. 

```{r}
#####1a. For those with two climate variables and vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2 <- NULL
for (i in 1:(length(inputs.me2)-1)) {
  for (j in (i+1):length(inputs.me2)) {
     twoway.ints2 <- cbind(twoway.ints2, paste(inputs.me2[i], inputs.me2[j], sep=":"))
  }
}
twoway.ints2
length(twoway.ints2) #6

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2) 
#add climate vars to all of the above
mods.me.climate2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2
mods.me.climate2<-mods.me.climate2[-1] #n = 15

#complete list of two-way interactions
mods.twoway2 <- powerSet(twoway.ints2)
length(mods.twoway2) #64
mods.twoway2[1]
mods.twoway2<-mods.twoway2[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2 <- list()
counter <- 0
for (i in 1: length(mods.twoway2)) {
   s1 <- unique(unlist( strsplit(mods.twoway2[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2)) {
      if (all(s1 %in% mods.me.climate2[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2[[j]], mods.twoway2[[i]])
        mods.inter2[[counter]] <- both
      }
   }
}

length(mods.inter2) #97
#mods.inter2
mods.inter2


####1c. Climate variables but no vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2b <- NULL
for (i in 1:(length(inputs.me2b)-1)) {
  for (j in (i+1):length(inputs.me2b)) {
     twoway.ints2b <- cbind(twoway.ints2b, paste(inputs.me2b[i], inputs.me2b[j], sep=":"))
  }
}
twoway.ints2b
length(twoway.ints2b) #3

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2b) 
#add climate vars to all of the above
mods.me.climate2b <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2b[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2b
mods.me.climate2b<-mods.me.climate2b[-1]

#complete list of two-way interactions
mods.twoway2b <- powerSet(twoway.ints2b)
length(mods.twoway2b) #8
mods.twoway2b
mods.twoway2b<-mods.twoway2b[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2b <- list()
counter <- 0
for (i in 1: length(mods.twoway2b)) {
   s1 <- unique(unlist( strsplit(mods.twoway2b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2b)) {
      if (all(s1 %in% mods.me.climate2b[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2b[[j]], mods.twoway2b[[i]])
        mods.inter2b[[counter]] <- both
      }
   }
}

length(mods.inter2b) #10
mods.inter2b
```


```{r}
#########2. Now for topography data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT) #6

#No reason to believe aspect*wind_atfire would have an effect, so remove
twoway.intsT<-twoway.intsT[-5]

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT
mods.meT<-mods.meT[-1]

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #32
mods.twowayT
mods.twowayT<-mods.twowayT[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT) #56
#mods.interT
```


```{r}
####3.For other VRI data, get without interactions

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.oth
mods.me.oth<-mods.me.oth[-1]

#get the names of all possible two-way interactions
twoway.intsOTH <- NULL
for (i in 1:(length(vars.oth)-1)) {
  for (j in (i+1):length(vars.oth)) {
     twoway.intsOTH <- cbind(twoway.intsOTH, paste(vars.oth[i], vars.oth[j], sep=":"))
  }
}
twoway.intsOTH
length(twoway.intsOTH) #6

#Do not want interactions between VRI variables
twoway.intsOTH<-twoway.intsOTH[c(3,5,6)]
twoway.intsOTH

#complete list of two-way interactions
mods.twowayOTH <- powerSet(twoway.intsOTH)
length(mods.twowayOTH) #8
mods.twowayOTH
mods.twowayOTH<-mods.twowayOTH[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.inter.OTH <- list()
counter <- 0
for (i in 1: length(mods.twowayOTH)) {
   s1 <- unique(unlist( strsplit(mods.twowayOTH[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.oth)) {
      if (all(s1 %in% mods.me.oth[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.oth[[j]], mods.twowayOTH[[i]])
        mods.inter.OTH[[counter]] <- both
      }
   }
}

length(mods.inter.OTH) #19
mods.inter.OTH


```


```{r}
#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI) #1

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI
mods.meI<-mods.meI[-1]

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsI)
length(mods.twowayI) #2
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms 

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI) #4
mods.interI
```


```{r}
########5. Lastly for last list of other variables
#get the names of all possible two-way interactions
twoway.ints.O2 <- NULL
for (i in 1:(length(vars.oth2)-1)) {
  for (j in (i+1):length(vars.oth2)) {
     twoway.ints.O2 <- cbind(twoway.ints.O2, paste(vars.oth2[i], vars.oth2[j], sep=":"))
  }
}
twoway.ints.O2
length(twoway.ints.O2) #1

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.oth2) 
#add climate vars to all of the above
mods.me.O2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.O2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.O2
mods.me.O2<-mods.me.O2[-1]

#complete list of two-way interactions
mods.twoway.O2 <- powerSet(twoway.ints.O2)
length(mods.twoway.O2) #2
mods.twowayI
```

Determine final models for testing.

```{r}
all.poss.mods.clim.vegtype2<-c(1, mods.me.climate2, mods.inter2)
all.poss.mods.clim.vegtype2 #113

all.poss.mods.clim.vegtype2b<-c(1, mods.me.climate2b, mods.inter2b)
all.poss.mods.clim.vegtype2b #18

all.poss.mods.VRI<-c(1, mods.inter.OTH)
all.poss.mods.VRI

all.poss.mods.topo<-c(1, mods.interT)
all.poss.mods.topo

all.poss.mods.infra<-c(1, mods.interI) 
all.poss.mods.infra

all.poss.mods.Oth2<-c(1, mods.me.O2) 
all.poss.mods.Oth2
```


```{r}
#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim.vegtype2)
duplicated(all.poss.mods.clim.vegtype2b)
duplicated(all.poss.mods.VRI)
duplicated(all.poss.mods.topo)
duplicated(all.poss.mods.infra)

```

Create all possible models for all models

```{r}
##Try all variables together with main interactions of interest

#get the names of all possible two-way interactions
twoway.ints_ALL <- NULL
for (i in 1:(length(variables_all)-1)) {
  for (j in (i+1):length(variables_all)) {
     twoway.ints_ALL <- cbind(twoway.ints_ALL, paste(variables_all[i], variables_all[j], sep=":"))
  }
}
twoway.ints_ALL
length(twoway.ints_ALL) #105
#Many of these we do not wish to investigate

#twoway.ints_ALL2<-twoway.ints_ALL[c(1,2,3,4,7,8,10,13,14,15,18,19,21,23,51,52,55,58,66,70,72,74,77)] #This was too many interactions
twoway.ints_ALL2<-twoway.ints_ALL[c(1,7,8,10,20,21,23,25,51,52,55,58,66,74,77)]
twoway.ints_ALL2 #We will see if 23 interactions is too many or not

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(variables_all) 
#add climate vars to all of the above
mods.me_ALL <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me_ALL[[i]] <- c(mods.me.tmp[[i]])
}

mods.me_ALL
length(mods.me_ALL) #8192 --> already too many models without interactions
mods.me_ALL[1]
mods.me_ALL<-mods.me_ALL[-1]

#complete list of two-way interactions
mods.twoway_ALL <- powerSet(twoway.ints_ALL2)
length(mods.twoway_ALL) #32768
mods.twoway_ALL[1]
mods.twoway_ALL<-mods.twoway_ALL[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.inter_ALL <- list()
counter <- 0
for (i in 1: length(mods.twoway_ALL)) {
   s1 <- unique(unlist( strsplit(mods.twoway_ALL[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me_ALL)) {
      if (all(s1 %in% mods.me_ALL[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me_ALL[[j]], mods.twoway_ALL[[i]])
        mods.inter_ALL[[counter]] <- both
      }
   }
}

length(mods.inter_ALL) #  1822648 - too much to run through a loop though...
mods.inter_ALL[1]

all.poss.mods.twoclim<-c(1, mods.me_ALL, mods.inter_ALL)
length(all.poss.mods.twoclim) #1830840

duplicated(all.poss.mods.twoclim)

```

Because of the large number of models with all variables included, we will test the climate and vegtype first, then the VRI variables, then the topography variables. Then we will test the top models together in additional combinations, with determining best AIC model from there. 

Select NDT: NDT1

```{r}
all.poss.mods.twoclim_1<-all.poss.mods.twoclim[1:100000]
all.poss.mods.twoclim_2<-all.poss.mods.twoclim[100001:200000]
all.poss.mods.twoclim_3<-all.poss.mods.twoclim[200001:300000]
all.poss.mods.twoclim_4<-all.poss.mods.twoclim[300001:400000]
all.poss.mods.twoclim_5<-all.poss.mods.twoclim[400001:500000]
```


```{r}
zones1<-c("NDT1") #Do one zone at a time
prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

########### 1. Climate and vegtype ############
for (g in 1:1){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.twoclim_1[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.twoclim_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT1")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}


```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_lightning_NDT1_escape_treed_climate<-table.glm.climate.simple

AIC_lightning_NDT1_escape_treed_summary_climate<- AIC_lightning_NDT1_escape_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_escape_treed_summary_climate2<- AIC_lightning_NDT1_escape_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_escape_treed_summary_climate2)
```








```{r}
zones1<-c("NDT1") #Do one zone at a time
prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

########### 1. Climate and vegtype ############
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim.vegtype2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT1")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}


```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_lightning_NDT1_escape_treed_climate<-table.glm.climate.simple

AIC_lightning_NDT1_escape_treed_summary_climate<- AIC_lightning_NDT1_escape_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_escape_treed_summary_climate2<- AIC_lightning_NDT1_escape_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_escape_treed_summary_climate2)
```

#Now repeat for VRI data

```{r}
########### 2. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.VRI)){
#  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$NDT<-c("NDT1")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_lightning_NDT1_escape_treed_VRI<-table.glm.VRI.simple

AIC_lightning_NDT1_escape_treed_summary_VRI<- AIC_lightning_NDT1_escape_treed_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_escape_treed_summary_VRI2<- AIC_lightning_NDT1_escape_treed_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_escape_treed_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 3. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$NDT<-c("NDT1")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_lightning_NDT1_escape_treed_topo<-table.glm.topo.simple

AIC_lightning_NDT1_escape_treed_summary_topo<- AIC_lightning_NDT1_escape_treed_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_escape_treed_summary_topo2<- AIC_lightning_NDT1_escape_treed_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_escape_treed_summary_topo2)
```

#Now repeat for infrastructure

```{r}
########### 4. Distance to Infrastructure ############
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT1")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_lightning_NDT1_escape_treed_infra<-table.glm.infra.simple

AIC_lightning_NDT1_escape_treed_summary_infra<- AIC_lightning_NDT1_escape_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_escape_treed_summary_infra2<- AIC_lightning_NDT1_escape_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_escape_treed_summary_infra2)

```

#Now combine the datatables and save to computer

```{r}
NDT1_l_models_treed<-rbind(AIC_lightning_NDT1_escape_treed_summary_climate2, AIC_lightning_NDT1_escape_treed_summary_VRI2, AIC_lightning_NDT1_escape_treed_summary_topo2, AIC_lightning_NDT1_escape_treed_summary_infra2)
NDT1_l_models_treed
NDT1_l_models_treed$NDT<-"NDT1"

write.csv(NDT1_l_models_treed, file="D:\\Fire\\fire_data\\raw_data\\NDT1_lightning_models_treed_escape.csv")
```


################################ STAGE TWO ########################

#STAGE TWO: PUT TOGETHER MORE VARIABLES
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Models:
1. climate1 + climate2 + climate1:climate2
2. live_stand_volume_125
3. slope + elevation + wind_atfire + slope:elevation
4. dist_dam + roads_km

Additional Variables:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)
**We will leave vegtype2 in final model selection to test.
2. Tdif_atfire

We want to include interactions between variables from within each list. This will make for many models, which may be hard to process in R.

```{r}
##Create variable lists to be used in the model loop.
variables_all_NDT1<-c(climate1 = "climate1", climate2 = "climate2", vegtype2 = "vegtype2", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", elevation ="elevation",  dist_dam = "dist_dam", roads_km = "roads_km", bclcs_level_5_2 = "bclcs_level_5_2", wind_atfire = "wind_atfire")

#Too many permutations to be able to include two-way interactions and all possible models, so need to divide into what we think may have interactions and which not.
variables_clim_VRI_NDT1<-c(climate1 = "climate1", climate2 = "climate2", vegtype2 = "vegtype2", live_stand_volume_125 = "live_stand_volume_125" )

#treat slope, aspect and elevation as their own thing. And we have already done this analysis with them.
#slope = "slope", aspect = "aspect", elevation ="elevation")

variables_all_infra_landuse_NDT1<-c(dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_mine = "dist_mine", roads_km = "roads_km", bclcs_level_5_2 = "bclcs_level_5_2") #I don't think it makes sense to have interactions between the distance elements, but maybe with land use and each distance element?

##
inputs.me.NDT1 <- c(variables_all_NDT1)
#inputs.me.clim_VRI_DEM_NDT1 <- c(variables_clim_VRI_DEM_NDT1)
inputs.me.clim_VRI_NDT1 <- c(variables_clim_VRI_NDT1)
inputs.me.infra_landuse_NDT1 <- c(variables_all_infra_landuse_NDT1)

```

Now, we will generate two-way interactions for each of these lists. We cannot make two-way interactions between them all because apparently it will be >2 GB in size.

```{r}
twoway.ints <- NULL
for (i in 1:(length(inputs.me.NDT1)-1)) {
  for (j in (i+1):length(inputs.me.NDT1)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.NDT1[i], inputs.me.NDT1[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #45

#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(inputs.me.NDT1) 
#add climate vars to all of the above
mods.me.NDT1 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.NDT1[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.NDT1
length(mods.me.NDT1) #1024
mods.me.NDT1[1]
mods.me.NDT1<-mods.me.NDT1[-1]

#complete list of two-way interactions
#mods.twoway.NDT1 <- powerSet(twoway.ints) # Do not run; will take hours if it succeeds at all
length(mods.twoway.NDT1) #
#mods.twoway.NDT1

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
# DO NOT RUN BELOW IF DID NOT RUN LAST BIT
mods.inter.NDT1 <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT1)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT1[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.clim_VRI_NDT1)) {
      if (all(s1 %in% mods.me.clim_VRI_NDT1[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.clim_VRI_NDT1[[j]], mods.twoway.NDT1[[i]])
        mods.inter.NDT1[[counter]] <- both
      }
   }
}

length(mods.inter.NDT1) #97
mods.inter.NDT1

```

There are too many two-way interactions to be able to include them all, so need to break it up into smaller chunks.

```{r}
####Reduce further
twoway.ints <- NULL
for (i in 1:(length(inputs.me.clim_VRI_NDT1)-1)) {
  for (j in (i+1):length(inputs.me.clim_VRI_NDT1)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.clim_VRI_NDT1[i], inputs.me.clim_VRI_NDT1[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #6

#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(variables_clim_VRI_NDT1) 
#add climate vars to all of the above
mods.me.clim_VRI_NDT1 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.clim_VRI_NDT1[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.clim_VRI_NDT1
length(mods.me.clim_VRI_NDT1) #16


#complete list of two-way interactions
mods.twoway.NDT1 <- powerSet(twoway.ints) # 
length(mods.twoway.NDT1) #64
mods.twoway.NDT1
mods.twoway.NDT1<-mods.twoway.NDT1[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter.NDT1 <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT1)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT1[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.clim_VRI_NDT1)) {
      if (all(s1 %in% mods.me.clim_VRI_NDT1[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.clim_VRI_NDT1[[j]], mods.twoway.NDT1[[i]])
        mods.inter.NDT1[[counter]] <- both
      }
   }
}

length(mods.inter.NDT1) #97
mods.inter.NDT1

##Subset 2: Infrastructure and land use ########
#inputs.me.infra_landuse_NDT1
twoway.ints <- NULL
for (i in 1:(length(inputs.me.infra_landuse_NDT1)-1)) {
  for (j in (i+1):length(inputs.me.infra_landuse_NDT1)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.infra_landuse_NDT1[i], inputs.me.infra_landuse_NDT1[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #15
#Review. If we do not want interactions between the different distance measurements, but only those between land use and distance, subset those.
twoway.ints
twoway.ints_dist<-twoway.ints[c(4,5,8,9,11,12,13,14,15)]
twoway.ints_dist


#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(variables_all_infra_landuse_NDT1) 
#add climate vars to all of the above
mods.me.infra_landuse_NDT1 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.infra_landuse_NDT1[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.infra_landuse_NDT1
length(mods.me.infra_landuse_NDT1) #64


#complete list of two-way interactions
#mods.twoway.NDT1b <- powerSet(twoway.ints) #
#Or use subset of interactions
mods.twoway.NDT1b <- powerSet(twoway.ints_dist) 
length(mods.twoway.NDT1b) #512
#mods.twoway.NDT1b
mods.twoway.NDT1b[1]
mods.twoway.NDT1b<-mods.twoway.NDT1b[-1]
head(mods.twoway.NDT1b)

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter.NDT1b <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT1b)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT1b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.infra_landuse_NDT1)) {
      if (all(s1 %in% mods.me.infra_landuse_NDT1[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.infra_landuse_NDT1[[j]], mods.twoway.NDT1b[[i]])
        mods.inter.NDT1b[[counter]] <- both
      }
   }
}

length(mods.inter.NDT1b) #1364
#mods.inter.NDT1b
```

Make final list of variables to assess.

```{r}
## 1. climate and VRI
#the list of all possible model RHSs. 
all.poss.mods.clim_VRI_NDT1<-c(1, mods.me.clim_VRI_NDT1, mods.inter.NDT1)
#all.poss.mods.clim_VRI_NDT1
length(mods.me.clim_VRI_NDT1) #16
length(all.poss.mods.clim_VRI_NDT1) #114
#all.poss.mods.clim_VRI_NDT1


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim_VRI_NDT1) #Need to remove 
#all.poss.mods.clim_VRI_NDT1b<-all.poss.mods.clim_VRI_NDT1[-(65:127)]
#duplicated(all.poss.mods.clim_VRI_NDT1b) 
#length(all.poss.mods.clim_VRI_NDT1b) 

all.poss.mods.infra_landuse_NDT1<-c(1, mods.me.infra_landuse_NDT1, mods.inter.NDT1b)
all.poss.mods.infra_landuse_NDT1[2]
all.poss.mods.infra_landuse_NDT1<-all.poss.mods.infra_landuse_NDT1[-2]

duplicated(all.poss.mods.infra_landuse_NDT1)

#Need to remove 
#all.poss.mods.infra_landuse_NDT1b<-all.poss.mods.infra_landuse_NDT1[-(34:65)]
#duplicated(all.poss.mods.infra_landuse_NDT1b) 
#all.poss.mods.infra_landuse_NDT1b[2]
#all.poss.mods.infra_landuse_NDT1b<-all.poss.mods.infra_landuse_NDT1b[-2]
```


```{r}
#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 

#Below does not work
lapply(biglist, all.poss.mods.infra_landuse_NDT1b {length(all.poss.mods.infra_landuse_NDT1b) == 0L} ) 

```

```{r}
all.poss.mods.clim_VRI_NDT1[2]
all.poss.mods.clim_VRI_NDT1<-all.poss.mods.clim_VRI_NDT1[-2]
```


Run models.

```{r}
zones1<-"NDT1"
prop<-0.75

#Create empty table
table.glm.clim_VRI.NDT1 <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.clim_VRI.NDT1) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#Run 100 times
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim_VRI_NDT1[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim_VRI_NDT1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT1")
tab.sum.climate 

table.glm.clim_VRI.NDT1<-rbind(table.glm.clim_VRI.NDT1, tab.sum.climate)

}
}
}


```


```{r}
head(table.glm.clim_VRI.NDT1)
table(table.glm.clim_VRI.NDT1$model) # 100 per model

AIC_lightning_NDT1_escape_treed_climate<-table.glm.clim_VRI.NDT1

AIC_lightning_NDT1_escape_treed_summary_climate<- AIC_lightning_NDT1_escape_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_escape_treed_summary_climate2<- AIC_lightning_NDT1_escape_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_escape_treed_summary_climate2)
```

Save.
```{r}
write.csv(AIC_lightning_NDT1_escape_treed_summary_climate2, file="D:\\Fire\\fire_data\\raw_data\\table.glm.clim_VRI.NDT1_ALL_escape.csv")
```

#Now repeat for all.poss.mods.infra_landuse_NDT1

```{r}
all.poss.mods.infra_landuse_NDT1<-all.poss.mods.infra_landuse_NDT1[-2]
```


```{r}
########### 2. Distance to Infrastructure ############
#Create empty table
table.glm.infra.lu.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.lu.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra_landuse_NDT1[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all_infra_landuse_NDT1)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_landuse_NDT1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra.lu <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra.lu$NDT<-c("NDT1")
tab.sum.infra.lu 

table.glm.infra.lu.simple<-rbind(table.glm.infra.lu.simple, tab.sum.infra.lu)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination. Also determine deltaAIC.

```{r}
head(table.glm.infra.lu.simple)
table(table.glm.infra.lu.simple$model) # 100 per model

AIC_lightning_NDT1_escape_treed_infra<-table.glm.infra.lu.simple

AIC_lightning_NDT1_escape_treed_summary_infra<- AIC_lightning_NDT1_escape_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_escape_treed_summary_infra2<- AIC_lightning_NDT1_escape_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_escape_treed_summary_infra2)
```

Save to computer.

```{r}
write.csv(AIC_lightning_NDT1_escape_treed_summary_infra2, file="D:\\Fire\\fire_data\\raw_data\\AIC_lightning_NDT1_escape_treed_summary_infra_escape.csv")
```

Determine the top models.

#1. Climate and VRI
climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:climate2 + climate1:vegtype2 + climate2:vegtype2

#2. Infrastructure
dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_nat:bclcs_level_5_2

#3. DEM
slope + elevation + wind_atfire + slope:elevation

#Interactions to investigate:
1. elevation*climate1
2. elevation*climate2
3. wind_atfire*climate1
4. wind_atfire*climate2
5. wind_atfire*vegtype2
6. Tdif_atfire*climate1
7. Tdif_atfire*climate2
8. Tdif_atfire*wind_atfire

#Next investigation
Because there would be far too many models to investigate including all variables and their interactions, we will start with the above and make educated guesses for what may need to be enhanced. We will seek the best model from the above informed progress.

```{r}
escape_lightning_t_NDT1<-subset(Escape_data_ALL, Escape_data_ALL$ntrl_ds=="NDT1")

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_lightning_t_NDT1$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_lightning_t_NDT1[ trainIndex,]
   Valid <- escape_lightning_t_NDT1[-trainIndex,]

#Run model using dat1
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:climate2 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_nat:bclcs_level_5_2 + slope + elevation + wind_atfire + slope:elevation + elevation*climate2 + wind_atfire*climate1 + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1922.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:climate2 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_nat:bclcs_level_5_2 + slope + elevation + wind_atfire + slope:elevation + elevation*climate2 + wind_atfire*climate1 + wind_atfire*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1918.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:climate2 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_nat:bclcs_level_5_2 + slope + elevation + wind_atfire + slope:elevation + elevation*climate2 + wind_atfire*climate1 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1916.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:climate2 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + elevation + wind_atfire + slope:elevation + elevation*climate2 + wind_atfire*climate1 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1914.6

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:climate2 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + wind_atfire*climate1 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1912.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + wind_atfire*climate1 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1910.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1909.5

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)


#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + roads_km + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1908.1

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)


#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire*wind_atfire + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1906.6

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1905.8

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)


#Remove least significant interaction
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire, family = binomial, data = dat1)

AIC(model.NDT1.E) #1905.2

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.73 --> good fit!
   
Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)


```

Remove NAs and run multiple times.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT1_escape_t<-escape_lightning_t_NDT1 %>% drop_na(climate1, climate2, vegtype2, live_stand_volume_125, dist_dam, dist_nat, bclcs_level_5_2, slope, elevation, wind_atfire, Tdif_atfire)

#Run Model again with this data; but uses all data here
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire, family = binomial, data = NDT1_escape_t)

#Anova(model.NDT1.E, type=3)
Anova(model.NDT1.E, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT1.E), 
            residuals(model.NDT1.E), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT1_escape_t$resids<-resid(model.NDT1.E)

binnedplot (NDT1_escape_t$live_stand_volume_125, 
            NDT1_escape_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT1_escape_t$climate1, 
            NDT1_escape_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good

#Partial Residuals
library(visreg)
#climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire

visreg(model.NDT1.E, "climate1", by="vegtype2", overlay=TRUE, ylim=c(-50,50))
visreg(model.NDT1.E, "climate1", by="vegtype2", overlay=TRUE, ylim=c(-40,40))
visreg(model.NDT1.E, "climate1", by="Tdif_atfire")

visreg(model.NDT1.E, "climate2", by="elevation")
visreg(model.NDT1.E, "climate2", by="vegtype2", overlay=TRUE, ylim=c(-75,75))
#visreg2d
visreg2d(model.NDT1.E, "climate2", "elevation") #Another way to visualize

visreg(model.NDT1.E, "vegtype2", by="climate1")
visreg(model.NDT1.E, "vegtype2", by="climate1", ylim=c(-50,50))
visreg(model.NDT1.E, "vegtype2", by="climate1", ylim=c(-20,20))
visreg(model.NDT1.E, "vegtype2", by="climate2", ylim=c(-20,20))

visreg(model.NDT1.E, "live_stand_volume_125")

visreg(model.NDT1.E, "dist_dam")
visreg(model.NDT1.E, "dist_nat")

visreg(model.NDT1.E, "bclcs_level_5_2")

visreg(model.NDT1.E, "slope")
visreg(model.NDT1.E, "elevation", by="climate2")
visreg(model.NDT1.E, "wind_atfire")

visreg(model.NDT1.E, "Tdif_atfire", by="climate1")

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT1.E)

#Create a new blank table and get AUC too
top_mod_table_NDT1_light_t_ALL <- data.frame (matrix (ncol = 28, nrow = 0))
colnames (top_mod_table_NDT1_light_t_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_live_stand_volume_125",  "coef_dist_dam", "coef_dist_nat", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_elevation", "coef_wind_atfire", "coef_Tdif_atfire", "coef_climate1:vegtype2TB", "coef_climate1:vegtype2TC", "coef_climate1:vegtype2TM", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_elevation:climate2", "coef_climate1:Tdif_atfire", "AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT1_escape_t$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT1_escape_t[ trainIndex,]
   Valid <- NDT1_escape_t[-trainIndex,]
   
#Model   
model.NDT1.E<-glm(escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT1.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT1_light_t <- data.frame (matrix (ncol = 28, nrow = 0))
colnames (top_mod_table_NDT1_light_t ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_live_stand_volume_125",  "coef_dist_dam", "coef_dist_nat", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_elevation", "coef_wind_atfire", "coef_Tdif_atfire", "coef_climate1:vegtype2TB", "coef_climate1:vegtype2TC", "coef_climate1:vegtype2TM", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_elevation:climate2", "coef_climate1:Tdif_atfire", "AUC")

##Add data for NDT1
top_mod_table_NDT1_light_t[1,1]<-"lightning"
top_mod_table_NDT1_light_t[1,2]<-"NDT1"
top_mod_table_NDT1_light_t[1,3]<-"Y"
top_mod_table_NDT1_light_t[1,4]<-"escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire" 
top_mod_table_NDT1_light_t[1,5]<- coef(model.NDT1.E)[1] #Intercept
top_mod_table_NDT1_light_t[1,6]<- coef(model.NDT1.E)[2] #Climate variable 1
top_mod_table_NDT1_light_t[1,7]<- coef(model.NDT1.E)[3] #Climate variable 2
top_mod_table_NDT1_light_t[1,8]<- coef(model.NDT1.E)[4] #coefficient vegtypeTB
top_mod_table_NDT1_light_t[1,9]<- coef(model.NDT1.E)[5] #coefficient vegtypeTC
top_mod_table_NDT1_light_t[1,10]<- coef(model.NDT1.E)[6] #coefficient vegtypeTM
top_mod_table_NDT1_light_t[1,11]<- coef(model.NDT1.E)[7] #live stand volume
top_mod_table_NDT1_light_t[1,12]<- coef(model.NDT1.E)[8] #coefficient dist_dam
top_mod_table_NDT1_light_t[1,13]<- coef(model.NDT1.E)[9] #coefficient dist_nat
top_mod_table_NDT1_light_t[1,14]<- coef(model.NDT1.E)[10] #coefficient bclcs_level_5_2OP
top_mod_table_NDT1_light_t[1,15]<- coef(model.NDT1.E)[11] #coefficient bclcs_level_5_2SP
top_mod_table_NDT1_light_t[1,16]<- coef(model.NDT1.E)[12] #coefficient slope
top_mod_table_NDT1_light_t[1,17]<- coef(model.NDT1.E)[13] #coefficient elevation
top_mod_table_NDT1_light_t[1,18]<- coef(model.NDT1.E)[14] #coefficient wind_atfire
top_mod_table_NDT1_light_t[1,19]<- coef(model.NDT1.E)[15] #Tdif_atfire
top_mod_table_NDT1_light_t[1,20]<- coef(model.NDT1.E)[16] # climate1:vegtype2TB 
top_mod_table_NDT1_light_t[1,21]<- coef(model.NDT1.E)[17] # climate1:vegtype2TC 
top_mod_table_NDT1_light_t[1,22]<- coef(model.NDT1.E)[18] #coefficient climate1:vegtype2TM
top_mod_table_NDT1_light_t[1,23]<- coef(model.NDT1.E)[19] #coefficient climate2:vegtype2TB
top_mod_table_NDT1_light_t[1,24]<- coef(model.NDT1.E)[20] #coefficient climate2:vegtype2TC
top_mod_table_NDT1_light_t[1,25]<- coef(model.NDT1.E)[21] #coefficient climate2:vegtype2TM
top_mod_table_NDT1_light_t[1,26]<- coef(model.NDT1.E)[22] #coefficient climate2:elevation
top_mod_table_NDT1_light_t[1,27]<- coef(model.NDT1.E)[23] #coefficient climate1:Tdif_atfire 
top_mod_table_NDT1_light_t[1,28]<- mod.auc

top_mod_table_NDT1_light_t_ALL<-rbind(top_mod_table_NDT1_light_t_ALL, top_mod_table_NDT1_light_t)

}

```

Check.
```{r}
head(top_mod_table_NDT1_light_t_ALL)

```

#Save coefficient table

```{r}
write.csv(top_mod_table_NDT1_light_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT1_light_t_ALL.csv")
```

Get mean values.

```{r}
names(top_mod_table_NDT1_light_t_ALL)
mean(top_mod_table_NDT1_light_t_ALL$AUC) #0.715

# create model table (only do this once) and add the relevant data
top_mod_table_NDT1_light_t_Means <- data.frame (matrix (ncol = 28, nrow = 0))
colnames (top_mod_table_NDT1_light_t_Means ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_live_stand_volume_125",  "coef_dist_dam", "coef_dist_nat", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_elevation", "coef_wind_atfire", "coef_Tdif_atfire", "coef_climate1:vegtype2TB", "coef_climate1:vegtype2TC", "coef_climate1:vegtype2TM", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_elevation:climate2", "coef_climate1:Tdif_atfire", "AUC")

head(top_mod_table_NDT1_light_t_Means)

##Add data for NDT1
top_mod_table_NDT1_light_t_Means[1,1]<-"lightning"
top_mod_table_NDT1_light_t_Means[1,2]<-"NDT1"
top_mod_table_NDT1_light_t_Means[1,3]<-"Y"
top_mod_table_NDT1_light_t_Means[1,4]<-"escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire" 
top_mod_table_NDT1_light_t_Means[1,5]<- mean(top_mod_table_NDT1_light_t_ALL$intercept) #Intercept
top_mod_table_NDT1_light_t_Means[1,6]<- mean(top_mod_table_NDT1_light_t_ALL$coef_climate_1, na.rm=TRUE) #Climate variable 1
top_mod_table_NDT1_light_t_Means[1,7]<- mean(top_mod_table_NDT1_light_t_ALL$coef_climate_2, na.rm=TRUE) #Climate variable 2
top_mod_table_NDT1_light_t_Means[1,8]<- mean(top_mod_table_NDT1_light_t_ALL$coef_vegtypeTB, na.rm=TRUE) #coefficient vegtypeTB
top_mod_table_NDT1_light_t_Means[1,9]<- mean(top_mod_table_NDT1_light_t_ALL$coef_vegtypeTC, na.rm=TRUE) #coefficient vegtypeTC
top_mod_table_NDT1_light_t_Means[1,10]<- mean(top_mod_table_NDT1_light_t_ALL$coef_vegtypeTM, na.rm=TRUE) #coefficient vegtypeTM
top_mod_table_NDT1_light_t_Means[1,11]<- mean(top_mod_table_NDT1_light_t_ALL$coef_live_stand_volume_125, na.rm=TRUE) #coef_live_stand_volume_125
top_mod_table_NDT1_light_t_Means[1,12]<- mean(top_mod_table_NDT1_light_t_ALL$coef_dist_dam, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,13]<- mean(top_mod_table_NDT1_light_t_ALL$coef_dist_nat, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,14]<- mean(top_mod_table_NDT1_light_t_ALL$coef_bclcs_level_5_2OP, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,15]<- mean(top_mod_table_NDT1_light_t_ALL$coef_bclcs_level_5_2SP, na.rm=TRUE)
top_mod_table_NDT1_light_t_Means[1,16]<- mean(top_mod_table_NDT1_light_t_ALL$coef_slope, na.rm=TRUE) #
top_mod_table_NDT1_light_t_Means[1,17]<- mean(top_mod_table_NDT1_light_t_ALL$coef_elevation, na.rm=TRUE) #
top_mod_table_NDT1_light_t_Means[1,18]<- mean(top_mod_table_NDT1_light_t_ALL$coef_wind_atfire, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,19]<- mean(top_mod_table_NDT1_light_t_ALL$coef_Tdif_atfire, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,20]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_climate1:vegtype2TB`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,21]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_climate1:vegtype2TC`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,22]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_climate1:vegtype2TM`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,23]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_climate2:vegtype2TB`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_Means[1,24]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_climate2:vegtype2TC`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_Means[1,25]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_climate2:vegtype2TM`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_Means[1,26]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_elevation:climate2`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_Means[1,27]<- mean(top_mod_table_NDT1_light_t_ALL$`coef_climate1:Tdif_atfire`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_Means[1,28]<-mean(top_mod_table_NDT1_light_t_ALL$AUC, na.rm=TRUE)

top_mod_table_NDT1_light_t_Means

```

Save mean coefficient table.

```{r}
write.csv(top_mod_table_NDT1_light_t_Means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT1_light_t_Means.csv")
```

Get sd values.

```{r}
# create model table (only do this once) and add the relevant data
top_mod_table_NDT1_light_t_SD <- data.frame (matrix (ncol = 28, nrow = 0))
colnames (top_mod_table_NDT1_light_t_SD ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_live_stand_volume_125",  "coef_dist_dam", "coef_dist_nat", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_elevation", "coef_wind_atfire", "coef_Tdif_atfire", "coef_climate1:vegtype2TB", "coef_climate1:vegtype2TC", "coef_climate1:vegtype2TM", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_elevation:climate2", "coef_climate1:Tdif_atfire", "AUC")

head(top_mod_table_NDT1_light_t_SD)

##Add data for NDT1
top_mod_table_NDT1_light_t_SD[1,1]<-"lightning"
top_mod_table_NDT1_light_t_SD[1,2]<-"NDT1"
top_mod_table_NDT1_light_t_SD[1,3]<-"Y"
top_mod_table_NDT1_light_t_SD[1,4]<-"escape ~ climate1 + climate2 + vegtype2 + live_stand_volume_125 + climate1:vegtype2 + climate2:vegtype2 + dist_dam + dist_nat + bclcs_level_5_2 + slope + elevation + wind_atfire + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire" 
top_mod_table_NDT1_light_t_SD[1,5]<- sd(top_mod_table_NDT1_light_t_ALL$intercept) #Intercept
top_mod_table_NDT1_light_t_SD[1,6]<- sd(top_mod_table_NDT1_light_t_ALL$coef_climate_1, na.rm=TRUE) #Climate variable 1
top_mod_table_NDT1_light_t_SD[1,7]<- sd(top_mod_table_NDT1_light_t_ALL$coef_climate_2, na.rm=TRUE) #Climate variable 2
top_mod_table_NDT1_light_t_SD[1,8]<- sd(top_mod_table_NDT1_light_t_ALL$coef_vegtypeTB, na.rm=TRUE) #coefficient vegtypeTB
top_mod_table_NDT1_light_t_SD[1,9]<- sd(top_mod_table_NDT1_light_t_ALL$coef_vegtypeTC, na.rm=TRUE) #coefficient vegtypeTC
top_mod_table_NDT1_light_t_SD[1,10]<- sd(top_mod_table_NDT1_light_t_ALL$coef_vegtypeTM, na.rm=TRUE) #coefficient vegtypeTM
top_mod_table_NDT1_light_t_SD[1,11]<- sd(top_mod_table_NDT1_light_t_ALL$coef_live_stand_volume_125, na.rm=TRUE) #coef_live_stand_volume_125
top_mod_table_NDT1_light_t_SD[1,12]<- sd(top_mod_table_NDT1_light_t_ALL$coef_dist_dam, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,13]<- sd(top_mod_table_NDT1_light_t_ALL$coef_dist_nat, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,14]<- sd(top_mod_table_NDT1_light_t_ALL$coef_bclcs_level_5_2OP, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,15]<- sd(top_mod_table_NDT1_light_t_ALL$coef_bclcs_level_5_2SP, na.rm=TRUE)
top_mod_table_NDT1_light_t_SD[1,16]<- sd(top_mod_table_NDT1_light_t_ALL$coef_slope, na.rm=TRUE) #
top_mod_table_NDT1_light_t_SD[1,17]<- sd(top_mod_table_NDT1_light_t_ALL$coef_elevation, na.rm=TRUE) #
top_mod_table_NDT1_light_t_SD[1,18]<- sd(top_mod_table_NDT1_light_t_ALL$coef_wind_atfire, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,19]<- sd(top_mod_table_NDT1_light_t_ALL$coef_Tdif_atfire, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,20]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_climate1:vegtype2TB`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,21]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_climate1:vegtype2TC`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,22]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_climate1:vegtype2TM`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,23]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_climate2:vegtype2TB`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_SD[1,24]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_climate2:vegtype2TC`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_SD[1,25]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_climate2:vegtype2TM`, na.rm=TRUE) 
top_mod_table_NDT1_light_t_SD[1,26]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_elevation:climate2`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_SD[1,27]<- sd(top_mod_table_NDT1_light_t_ALL$`coef_climate1:Tdif_atfire`, na.rm=TRUE) #
top_mod_table_NDT1_light_t_SD[1,28]<-sd(top_mod_table_NDT1_light_t_ALL$AUC, na.rm=TRUE)

top_mod_table_NDT1_light_t_SD

```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT1_light_t_SD, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT1_light_t_SD.csv")
```

