---
title: "Create summary figures from simulation reps"
author: "Elizabeth Kleynhans"
date: "2024-06-28"
output: html_document
---

There are two different types of scripts here. The first set is for a single run of fireCastorSingleYearRep.R. In this R script I repeat the calculation for number of ignitions, fire size, and locations burned for a predetermined number of reps for a single year. 

The second set of figures are for if I use the experiemnt function in Spades where a single run in repreated a predetermined number of times. From this script different folders are created and in each folder is the results for a single run. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(RSQLite)
library(terra)
library(raster)
```

## Figure 1 for fireCastorSingleYearRep.R

```{r figure1, include=FALSE}
#import RDS file
y<-readRDS("C:\\Work\\caribou\\castor\\R\\scenarios\\test_fire\\outputs\\firedisturbanceTableForReps_1.rds")
y<-data.table(y)
y<-y[order(pixelid)]

# plot the number of times burned on the landscap

sqlite <- dbDriver("SQLite")

castordb <- dbConnect(sqlite,"C:/Work/caribou/castor/boundary_tsa_fire_test_20june24_castordb.sqlite")
ras.info<-dbGetQuery(castordb, "Select * from raster_info limit 1;")
areaBurned<-raster::raster(extent(ras.info$xmin, ras.info$xmax, ras.info$ymin, ras.info$ymax), nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow, vals =0)
    
areaBurned[]<-(y$numberTimesBurned/y$reps)

plot(areaBurned)
```



## Figure 1

The first figure I make is the number of times on a landscape a particular pixel was burned. I.e. I sum up all the reps of the fire disturbancetable. Each table has every pixel number on the landscape and if that pixel was burned it gets a value of 1 otherwise its a zero. Then I sum up all the values for each pixel individually to get a number of times burned at a specific location and divide that by the total number of reps to get  an indication of the probabiliity that a location will burne.

```{r figure1, include=FALSE}
dirs <- list.dirs("C:\\Work\\caribou\\castor\\R\\scenarios\\test_fire\\outputs\\")

#take the first file from the first directory
y<-readRDS(paste0(dirs[2], "\\firedisturbanceTable_test_1.rds"))
y<-data.table(y)
y<-y[order(pixelid)]
#create a new column called total number of times burned
y[,total_burns:=numberTimesBurned]
y[, noreps:=1]

#cycle through all directories
for(i in 3:length(dirs)) {
x<-readRDS(paste0(dirs[i], "\\firedisturbanceTable_test_1.rds"))
x<-data.table(x)
x<-x[order(pixelid)]
x[, reps:=1]
#setnames(x, "numberTimesBurned", paste0("burned_", i))
#x[, paste0("burned_", i):=x[,"numberTimesBurned"]]
y[,total_burns:=total_burns+x[,"numberTimesBurned"]]
y[,noreps:=noreps+x[,"reps"]]
}


# plot the number of times burned on the landscap

sqlite <- dbDriver("SQLite")

castordb <- dbConnect(sqlite,"C:/Work/caribou/castor/boundary_tsa_fire_test_20june24_castordb.sqlite")
ras.info<-dbGetQuery(castordb, "Select * from raster_info limit 1;")
areaBurned<-raster::raster(extent(ras.info$xmin, ras.info$xmax, ras.info$ymin, ras.info$ymax), nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow, vals =0)
    
areaBurned[]<-y$total_burns

plot(areaBurned)
```

