---
title: "Comparison between fireCastor results and actual number of fires in the Boundary TSA for the year 2023"
author: "Elizabeth Kleynhans"
date: "2024-07-16"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.align = "left",
                      fig.width = 4, 
                      fig.height = 4, 
                      dev = "png",
                      cache = TRUE)
```


```{r library, include = FALSE}

library(data.table)
library(RSQLite)
library(terra)
library(raster)
require (dplyr)
library(bcdata)
library(ggplot2)
source (here::here("R/functions/R_Postgres.R"))
```

## Introduction
To test whether fireCastor is performing accurately we used fireCastor to simulate fires started by lightning in the Boundary TSA for the year 2023. Vegetation data from the 2022 VRI and climate data from climr for the year 2023 were used as inputs into fireCastor. Then 10 000 simulations were performed to get distributions of the number of ignitions and total area burned in the Boundary TSA. These simulation results we compare to actual burn data from lightning caused fires for the year 2023 in the same area. 

## Actual fire data for the Boundary TSA in 2023

In 2023 there were only three fires larger than 1ha that were started by lightning in the Boundary TSA. These three fires were all small (1.7ha, 1.8ha, and 3.3ha). Figure 1 is a map of the actual locations of the three fires. 
```{r boundary_map, echo=FALSE, fig.cap = "**Figure 1.** Map of Boundary TSA with the locations of actual fires caused by lightning in 2023"}
# get latest data off BCGW

study_area<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM public.boundary_tsa where tsa_name in ('Boundary TSA')")

study_area<-st_transform (study_area, 3005)

perimeters<-try(
  bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_FIRE_POLYS_SP") %>%
    filter(FIRE_YEAR > 2022) %>%
    collect()
)
perimeters<-st_transform (perimeters, 3005)
perimeters<-perimeters %>% filter( FIRE_SIZE_HECTARES > 1 & FIRE_CAUSE == "Lightning")
perim_subset <- perimeters[study_area, ]
#hist(perim_subset$FIRE_SIZE_HECTARES)
perim_subset_total<-sum(perim_subset$FIRE_SIZE_HECTARES)


ignitions<- try(
  bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_INCIDENTS_SP") %>%
    filter(FIRE_YEAR > 2022) %>%
    collect()
)

ignit<-st_transform (ignitions, 3005)
ignit<-ignit %>% filter( FIRE_CAUSE == "Lightning" & FIRE_NUMBER %in% c("N52826","N60465", "N62590"))

# get study area
#ignit_subset <- ignit[study_area, ]
#hist(ignit_subset$CURRENT_SIZE)

ggplot() +
  geom_sf(data=study_area) + 
  geom_sf(data=ignit) +
  geom_sf(data = perim_subset, col = "red")

```
## FireCastor results

On average fireCastor simulated 4.5 ignitions per run although this number varied between 1 and 14 ignitions across all reps (figure 2).  

```{r fireCastor_number_ignitions, fig.cap = "**Figure 2.** Number of ignitions simulated by fireCastor relative to the actual number of ignitions observed (black dashed) in the Boundary TSA for the year 2023"}
fireReportForReps_test_1 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/outputs/fireReportForReps_test_1.rds")
fireReportForReps_test_1<-as.data.frame(fireReportForReps_test_1)

fireReportForReps_test_1$numberstarts<-as.numeric(fireReportForReps_test_1$numberstarts)

ggplot(fireReportForReps_test_1, (aes(x=numberstarts, y = ..density..))) +
  geom_histogram(bins = 14, fill = "#B3E4F7")+
  geom_density(  adjust = 5) + 
  #xlim(0,10000)+
  geom_vline(aes(xintercept=3), color="black", linetype="dashed", size=0.75) +
  labs(x = "Number of ignitions", y = "Density")
```


The fire sizes simulated by fire castor ranged between 1ha and 1 238 677 ha with the median being 23 ha. The average fire size observed in Boundary in 2023 was 2.3h which is essentially the same as the most commonly simulated fire size (2ha) by fireCastor (figure 3).
```{r individual_firesize, fig.cap = "**Figure 3.** Distribution of fire sizes simulated by fireCastor. The average actual fire size observed in Boundary TSA in 2023 is represented by the dashed black line. Note the x-axis was cut off at 150 ha so that the distribution of smaller fire sizes could be more clearly seen."}
firesize<-readRDS("C:\\Work\\caribou\\castor\\R\\scenarios\\test_fire\\outputs\\perFireReportForReps_test_1.rds")

#summary(firesize$areaburned_estimated)
#hist(firesize$areaburned_estimated, breaks = 100)

ggplot(data=firesize, (aes(x=areaburned_estimated, y=..density..))) +  
  geom_histogram(bins = 150, fill = "#B3E4F7")+
  geom_density() + 
  xlim(0,150)+
  geom_vline(aes(xintercept=2.3), color="black", linetype="dashed", size=0.75) +
  labs(x = "Simulated size of individual fires", y = "Density")

```

Similar to fire size the total area burned during a single simulation of fireCastor varied significantly with the minimum area burned being 1ha, the maximum being 1 240 711 ha and the median being 818ha (figure 4).  
```{r, fig.cap="**Figure 4.** Simulated total area burned during a single rep with actual area burned represented by the dashed black line."}
total_area_burned<- firesize[ ,list(sum=sum(areaburned_estimated)), by=rep]

ggplot(data=total_area_burned, (aes(x=sum, y=..density..))) +  
  geom_histogram(bins = 150, fill = "#B3E4F7")+
  geom_density() + 
  xlim(0,2000)+
  geom_vline(aes(xintercept=perim_subset_total), color="black", linetype="dashed", size=0.75) +
  labs(x = "Simulated total area burned in 2023", y = "Density")

# summary(fireReportForReps_test_1$totalareaburned)
# 
# 
# 
# total_area_burned<- firesize[ ,list(sum=sum(areaburned_estimated)), by=rep]
# summary(meanAreaBurned)
# 
# hist(total_area_burned$sum, breaks = 100)
# plot(
#   density(total_area_burned$sum ), 
#   main="Density Plot of Total Area burned",
#   xlab="Area (ha)", ylab="Density",
#   xlim=c(0, 30000)
#   )
# 
# ggplot(data=total_area_burned) +    
#   geom_histogram(aes(x=sum), fill = "grey70", boundary =0, binwidth = 20) + 
#   xlim(0,5000)+
#   geom_vline(aes(xintercept=perim_subset_total), color="black", linetype="dashed", size=0.75)
# 
# ggplot(data=total_area_burned) +    
#   geom_density(aes(x=sum), fill = "grey70", boundary =0, binwidth = 20) + 
#   xlim(0,10000)+
#   geom_vline(aes(xintercept=perim_subset_total), color="black", linetype="dashed", size=0.75) +
#   labs(x = "Total area burned", y = "Y-axis title")
# 
# ggplot(data=meanAreaBurned) +    
#   geom_histogram(aes(x=mean), fill = "grey70", boundary =0, binwidth = 20) + 
#   xlim(0,3000)+
#   geom_vline(aes(xintercept=perim_subset_total), color="black", linetype="dashed", size=0.75)
#   
# 
# plot(
#   density(meanAreaBurned$mean ), 
#   main="Density Plot of mean Area burned",
#   xlab="Area (ha)", ylab="Density",
#   xlim = c(0,8000)
#   )
# 
# mean(total_area_burned$sum)
# sd(total_area_burned$sum)


```


Because the simulation is repeated 10 000 times we can examine which areas on the landscape have a higher probability of burning because they burned more frequently across all the simulations. 

```{r, fig.cap= "**Figure 5.** Location of areas with highest probability of burning from 10 000 simulations of fire in the Boundary TSA for the year 2023"}
#import RDS file
y<-readRDS("C:\\Work\\caribou\\castor\\R\\scenarios\\test_fire\\outputs\\firedisturbanceTableForReps_1.rds")
y<-data.table(y)
y<-y[order(pixelid)]

# plot the number of times burned on the landscap

sqlite <- dbDriver("SQLite")

castordb <- dbConnect(sqlite,"C:/Work/caribou/castor/R/scenarios/test_fire/boundary_tsa_fire_test_12July24_castordb.sqlite")
ras.info<-dbGetQuery(castordb, "Select * from raster_info limit 1;")
areaBurned<-raster::raster(xmn=ras.info$xmin, xmx =ras.info$xmax, ymn=ras.info$ymin, ymx=ras.info$ymax, nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow,crs="+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", vals =0)
    
areaBurned[]<-(y$numberTimesBurned/y$reps)
#ignit_subset2<-ignit_subset[,c("CURRENT_SIZE", "geometry")]

plot(areaBurned)
plot(study_area,  col=NA, add=TRUE)
plot(ignit, add=TRUE, col="black", pch=1,type="p", bg=1)

```