---
title: "Updated BEC Raster"
author: "Elizabeth Kleynhans"
date: "30-05-2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose
This rmd produces a raster that specifies the BEC zones and BEC subzones in British Columbia, as defined by [Biogeoclimatic Ecosystem Classification Program](https://www.for.gov.bc.ca/hre/becweb/). 

It was developed to be used in fireCastor.

## Spatial Data on Protected Areas
BEC data is available from  [DataBC](https://catalogue.data.gov.bc.ca/dataset/f358a53b-ffde-4830-a325-a5a03ff672c3). 

```{r, get BEC data from BCGW}
#library (bcdata)
library (sf)
library(bcdata)
library(dplyr)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))

# grab most recent version of BEC from the data warehouse.
bec<-try(
  bcdc_query_geodata("WHSE_FOREST_VEGETATION.BEC_BIOGEOCLIMATIC_POLY") %>%
    collect()
)

bec_df<-st_drop_geometry(bec)
bec.unique<-unique(bec_df[c('ZONE', 'SUBZONE')])
bec.unique$idkey<-1:length(bec.unique$ZONE)

bec2<-left_join(bec, bec.unique)

bec.unique<-bec.unique %>% rename(zone=ZONE,
                       subzone=SUBZONE)

bec2<- bec2 %>% rename(zone=ZONE,
                       subzone=SUBZONE)
```

## Rasterize the Data
Here we convert the polygon to a raster, following the provincial hectares BC raster convention that we are using in the CLUS model to ensure all rasters overlap.

```{r, convert polygon to raster}
library (raster)
library (fasterize)

prov.rast <- raster::raster ( # create the standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216, 
                              xmn = 159587.5, xmx = 1881187.5, 
                              ymn = 173787.5, ymx = 1748187.5, 
                              crs = st_crs(bec)$proj4string, resolution = c(100, 100), 
                              vals = 0)

ras.bec <- fasterize::fasterize (st_collection_extract(bec2, "POLYGON"), prov.rast, field = "idkey") 
# turn the polygon into a raster

plot (ras.bec) # make sure the raster looks good
```

## Create Look-up Table
Here we create a look-up table for the raster so we can translate the raster into herd names later.

```{r, create look-up table for raster}
library (data.table)

lu_bec_cat <- data.table(bec.unique)
```

## Commit the Data to the PostgreSQL database
Now we need to save the data. We save the raster to the raster schema and look-up table to the public schema in our postgreSQL database. 

```{r, commit data to the dbase}
conn <- DBI::dbConnect (dbDriver ("PostgreSQL"), host = keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432', user = keyring::key_get('dbuser', keyring = 'postgreSQL'), password = keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable (conn, c("vat", "bec_zone_vat"), value = lu_bec_cat, 
                   row.names = FALSE, overwrite = TRUE)

writeRaster (ras.bec, file = "bec.tif", format = "GTiff", overwrite = TRUE)

#Upload to PostgreSQL
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/bec.tif -t 100x100 rast.bec_current |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

#upload vector
#DBI::dbWriteTable (conn, c("public", "bec_zone3"), value = bec, row.names = FALSE, overwrite = TRUE)
#ogr2ogr -f PostgreSQL PG:"dbname=clus port = 5432 user=postgres password=postgres" C:\Users\klochhea\Downloads\BCGW_7113060B_1711643177122_14632\BEC_BIOGEOCLIMATIC_POLY\BEC_POLY_polygon.shp -overwrite -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI -lco precision=NO -nln bec_zone


```

