---
title: "caribou_southern_mtn_pop_model"
author: "Tyler Muhly"
date: "27/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Southern Mountain Caribou Disturbance-Abundance Model
This .Rmd creates raster dataset (*nameRasSMCHerd*) that defines the location of 'core' and 'matrix' critical habitat for each southern mountain caribou subpopulation (a.k.a herd), and a table (*tableSMCCoeffs*), that defines the name of each subpopulation and coefficients for a model to estimate abundance from the amount fo forestry disturbance in each habitat type (Lochhead et al. In Review).

#### Core and Matrix Habitat
Core and matrix habitat was defined by government of British Columbia biologists. Core areas were defined as areas providing enough suitable habitat to support the life history requirements of caribou across all seasons and allow for movements on the landscape over time in response to disturbances. They were delineated using subpopulation specific information such as habitat models, telemetry data, BEC, elevation and forest type information, when available. There are up to four types of core habitat, including high or low elevation summer or winter range. This types were amalgamated into a single type called 'core'. 

Matrix habitat was defined as areas adjacent to core, that had periodic or low known use by caribou, but were used by primary prey and predators associated with caribou. Matrix habitat was delineated using subpopulation specific spatial buffers that ranged upwards of 30 km from core areas and were further modified based on data on: local predator or prey distributions (where available), natural or topographic boundaries impeding predator movement (e.g., large water bodies, glaciers, human settlement) and expert knowledge. 

#### Caribou Abundance-Disturbance Model
The caribou abundance-disturbance model coefficients were obtained from an exponential non-linear mixed model of longitudinal caribou abundance data as a function of historical forestry disturbances in forested areas of core and matrix habitat, simulated from forest harvest data.

Here we provide coefficients for 3 of the top 4 models, which include combinations of the amount of area converted to roads or cutblocks (<80 years old) in core and matrix habitat.

#### Code chunk

```{r, raster and table creation}



# TO-DO/CHECK: Matrix random effects? Coefficients for herd size and which are large/small?



conn <- DBI::dbConnect (dbDriver ("PostgreSQL"), host = keyring::key_get ('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

bc.crit <- getSpatialQuery("SELECT * from bc_critical_habitat_all_herds_20200615;") # current version of BC critical habitat
bc.crit <- bc.crit[bc.crit$bc_habitat_type != "No critical habitat",] # remove subpops/herds without critical habitat defined
bc.crit$herd_hab_name <- paste (bc.crit$herd_name, bc.crit$bc_habitat_type) # create unique id ("value") for each unique herd name and habitat type

# Coefficients Table
table.coeffs <- data.table (st_drop_geometry (bc.crit))
table.coeffs <- table.coeffs [, list(herd_name, bc_habitat_type, herd_hab_name)]
table.coeffs <- table.coeffs[!duplicated(herd_hab_name),] # remove duplicates
table.coeffs[, value := seq_len(.N)] # integer id

## assign fixed effects
table.coeffs$r50fe_int <- 7.689 
table.coeffs$r50fe_core <- 0.108 
table.coeffs$r50fe_matrix <- -0.551 

table.coeffs$c80r50fe_int <- 7.389   
table.coeffs$c80r50fe_core <- -0.109
table.coeffs$c80r50fe_matrix <- -0.093 

table.coeffs$c80fe_int <- 7.140
table.coeffs$c80fe_core <- -0.122
table.coeffs$c80fe_matrix <- -0.102 

## assign random effects
### R50
#### intercepts
table.coeffs <- table.coeffs [herd_name == "Barkerville", r50re_int := -3.374]
table.coeffs <- table.coeffs [herd_name == "Burnt_Pine", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Graham", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Groundhog", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Moberly", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Monashee", r50re_int := -2.484]
table.coeffs <- table.coeffs [herd_name == "Narraway", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Central_Rockies", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Quintette", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Rainbows", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Telkwa", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Tweedsmuir", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Narrow_Lake", r50re_int := 2.493]
table.coeffs <- table.coeffs [herd_name == "Itcha_Ilgachuz", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Central_Selkirks", r50re_int := 1.429]
table.coeffs <- table.coeffs [herd_name == "Charlotte_Alplands", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Columbia_North", r50re_int := -0.670]
table.coeffs <- table.coeffs [herd_name == "Columbia_South", r50re_int := 1.239]
table.coeffs <- table.coeffs [herd_name == "Frisby_Boulder", r50re_int := -1.499]
table.coeffs <- table.coeffs [herd_name == "Hart_Ranges", r50re_int := 1.523] # we'll apply Hart south to whole Hart range
table.coeffs <- table.coeffs [herd_name == "Kennedy_Siding", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "North_Cariboo", r50re_int := 1.686]
table.coeffs <- table.coeffs [herd_name == "Purcell_Central", r50re_int := -2.719]
table.coeffs <- table.coeffs [herd_name == "Purcells_South", r50re_int := 0.818]
table.coeffs <- table.coeffs [herd_name == "South_Selkirks", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Wells_Gray_North", r50re_int := 1.558]
table.coeffs <- table.coeffs [herd_name == "Wells_Gray_South", r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Redrock_Prairie_Creek", r50re_int := 0]
#### core 
table.coeffs <- table.coeffs [herd_name ==  "Barkerville", r50re_core := 0.945]
table.coeffs <- table.coeffs [herd_name ==  "Burnt_Pine", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Graham", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Groundhog", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Moberly", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Monashee", r50re_core := 0.636]
table.coeffs <- table.coeffs [herd_name ==  "Narraway", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Rockies", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Quintette", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Rainbows", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Telkwa", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Tweedsmuir", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narrow_Lake", r50re_core := -0.718]
table.coeffs <- table.coeffs [herd_name ==  "Itcha_Ilgachuz", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Selkirks", r50re_core := -0.387]
table.coeffs <- table.coeffs [herd_name ==  "Charlotte_Alplands", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_North", r50re_core := 0.326]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_South", r50re_core := -0.840]
table.coeffs <- table.coeffs [herd_name ==  "Frisby_Boulder", r50re_core := 0.663]
table.coeffs <- table.coeffs [herd_name ==  "Hart_Ranges", r50re_core := -0.450] 
table.coeffs <- table.coeffs [herd_name ==  "Kennedy_Siding", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "North_Cariboo", r50re_core := -0.515]
table.coeffs <- table.coeffs [herd_name ==  "Purcell_Central", r50re_core := 0.791]
table.coeffs <- table.coeffs [herd_name ==  "Purcells_South", r50re_core := -0.303]
table.coeffs <- table.coeffs [herd_name ==  "South_Selkirks", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_North", r50re_core := -0.146]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_South", r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Redrock_Prairie_Creek", r50re_core := 0]
####  TO-DO
table.coeffs <- table.coeffs [herd_name ==  "Barkerville", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Burnt_Pine", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Graham", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Groundhog", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Moberly", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Monashee", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narraway", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Rockies", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Quintette", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Rainbows", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Telkwa", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Tweedsmuir", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narrow_Lake", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Itcha_Ilgachuz", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Selkirks", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Charlotte_Alplands", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_North", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_South", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Frisby_Boulder", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Hart_Ranges", r50re_matrix := -0] 
table.coeffs <- table.coeffs [herd_name ==  "Kennedy_Siding", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "North_Cariboo", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Purcell_Central", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Purcells_South", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "South_Selkirks", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_North", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_South", r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Redrock_Prairie_Creek", r50re_matrix := 0]

### C80R50
#### intercepts
table.coeffs <- table.coeffs [herd_name == "Barkerville", c80r50re_int := -4.363]
table.coeffs <- table.coeffs [herd_name == "Burnt_Pine", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Graham", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Groundhog", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Moberly", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Monashee", c80r50re_int := -3.749]
table.coeffs <- table.coeffs [herd_name == "Narraway", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Central_Rockies", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Quintette", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Rainbows", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Telkwa", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Tweedsmuir", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Narrow_Lake", c80r50re_int := 4.919]
table.coeffs <- table.coeffs [herd_name == "Itcha_Ilgachuz", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Central_Selkirks", c80r50re_int := 1.212]
table.coeffs <- table.coeffs [herd_name == "Charlotte_Alplands", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Columbia_North", c80r50re_int := -0.563]
table.coeffs <- table.coeffs [herd_name == "Columbia_South", c80r50re_int := 0.917]
table.coeffs <- table.coeffs [herd_name == "Frisby_Boulder", c80r50re_int := -0.483]
table.coeffs <- table.coeffs [herd_name == "Hart_Ranges", c80r50re_int := 1.250] # apply Hart south to whole Hart range
table.coeffs <- table.coeffs [herd_name == "Kennedy_Siding", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "North_Cariboo", c80r50re_int := 2.492]
table.coeffs <- table.coeffs [herd_name == "Purcell_Central", c80r50re_int := -3.979]
table.coeffs <- table.coeffs [herd_name == "Purcells_South", c80r50re_int :=1.334]
table.coeffs <- table.coeffs [herd_name == "South_Selkirks", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Wells_Gray_North", c80r50re_int := 1.013]
table.coeffs <- table.coeffs [herd_name == "Wells_Gray_South", c80r50re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Redrock_Prairie_Creek", c80r50re_int := 0]
#### 
table.coeffs <- table.coeffs [herd_name ==  "Barkerville", c80r50re_core := 0.380]
table.coeffs <- table.coeffs [herd_name ==  "Burnt_Pine", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Graham", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Groundhog", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Moberly", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Monashee", c80r50re_core := 0.243]
table.coeffs <- table.coeffs [herd_name ==  "Narraway", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Rockies", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Quintette", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Rainbows", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Telkwa", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Tweedsmuir", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narrow_Lake", c80r50re_core := -0.265]
table.coeffs <- table.coeffs [herd_name ==  "Itcha_Ilgachuz", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Selkirks", c80r50re_core := -0.191]
table.coeffs <- table.coeffs [herd_name ==  "Charlotte_Alplands", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_North", c80r50re_core := 0.129]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_South", c80r50re_core := -0.260]
table.coeffs <- table.coeffs [herd_name ==  "Frisby_Boulder", c80r50re_core := 0.048]
table.coeffs <- table.coeffs [herd_name ==  "Hart_Ranges", c80r50re_core := -0.098] 
table.coeffs <- table.coeffs [herd_name ==  "Kennedy_Siding", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "North_Cariboo", c80r50re_core := -0.178]
table.coeffs <- table.coeffs [herd_name ==  "Purcell_Central", c80r50re_core := 0.293]
table.coeffs <- table.coeffs [herd_name ==  "Purcells_South", c80r50re_core := -0.120]
table.coeffs <- table.coeffs [herd_name ==  "South_Selkirks", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_North", c80r50re_core := 0.019]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_South", c80r50re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Redrock_Prairie_Creek", c80r50re_core := 0]
####  TO-DO
table.coeffs <- table.coeffs [herd_name ==  "Barkerville", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Burnt_Pine", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Graham", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Groundhog", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Moberly", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Monashee", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narraway", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Rockies", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Quintette", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Rainbows", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Telkwa", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Tweedsmuir", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narrow_Lake", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Itcha_Ilgachuz", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Selkirks", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Charlotte_Alplands", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_North", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_South", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Frisby_Boulder", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Hart_Ranges", c80r50re_matrix := -0] 
table.coeffs <- table.coeffs [herd_name ==  "Kennedy_Siding", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "North_Cariboo", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Purcell_Central", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Purcells_South", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "South_Selkirks", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_North", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_South", c80r50re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Redrock_Prairie_Creek", c80r50re_matrix := 0]

### C80
#### intercepts
table.coeffs <- table.coeffs [herd_name == "Barkerville", c80re_int := -4.259]
table.coeffs <- table.coeffs [herd_name == "Burnt_Pine", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Graham", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Groundhog", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Moberly", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Monashee", c80re_int := -3.438]
table.coeffs <- table.coeffs [herd_name == "Narraway", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Central_Rockies", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Quintette", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Rainbows", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Telkwa", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Tweedsmuir", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Narrow_Lake", c80re_int := 4.205]
table.coeffs <- table.coeffs [herd_name == "Itcha_Ilgachuz", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Central_Selkirks", c80re_int := 1.215]
table.coeffs <- table.coeffs [herd_name == "Charlotte_Alplands", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Columbia_North", c80re_int := -0.460]
table.coeffs <- table.coeffs [herd_name == "Columbia_South", c80re_int := 0.772]
table.coeffs <- table.coeffs [herd_name == "Frisby_Boulder", c80re_int := -0.441]
table.coeffs <- table.coeffs [herd_name == "Hart_Ranges", c80re_int := 1.467] # apply Hart south to whole Hart range
table.coeffs <- table.coeffs [herd_name == "Kennedy_Siding", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "North_Cariboo", c80re_int := 2.685]
table.coeffs <- table.coeffs [herd_name == "Purcell_Central", c80re_int := -3.949]
table.coeffs <- table.coeffs [herd_name == "Purcells_South", c80re_int := 1.176]
table.coeffs <- table.coeffs [herd_name == "South_Selkirks", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Wells_Gray_North", c80re_int := 1.027]
table.coeffs <- table.coeffs [herd_name == "Wells_Gray_South", c80re_int := 0]
table.coeffs <- table.coeffs [herd_name == "Redrock_Prairie_Creek", c80re_int := 0]
#### 
table.coeffs <- table.coeffs [herd_name ==  "Barkerville", c80re_core := 0.454]
table.coeffs <- table.coeffs [herd_name ==  "Burnt_Pine", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Graham", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Groundhog", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Moberly", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Monashee", c80re_core := 0.209]
table.coeffs <- table.coeffs [herd_name ==  "Narraway", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Rockies", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Quintette", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Rainbows", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Telkwa", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Tweedsmuir", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narrow_Lake", c80re_core := -0.133]
table.coeffs <- table.coeffs [herd_name ==  "Itcha_Ilgachuz", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Selkirks", c80re_core := -0.269]
table.coeffs <- table.coeffs [herd_name ==  "Charlotte_Alplands", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_North", c80re_core := 0.141]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_South", c80re_core := -0.343]
table.coeffs <- table.coeffs [herd_name ==  "Frisby_Boulder", c80re_core := 0.035]
table.coeffs <- table.coeffs [herd_name ==  "Hart_Ranges", c80re_core := -0.126] 
table.coeffs <- table.coeffs [herd_name ==  "Kennedy_Siding", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "North_Cariboo", c80re_core := -0.166]
table.coeffs <- table.coeffs [herd_name ==  "Purcell_Central", c80re_core := 0.306]
table.coeffs <- table.coeffs [herd_name ==  "Purcells_South", c80re_core := -0.148]
table.coeffs <- table.coeffs [herd_name ==  "South_Selkirks", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_North", c80re_core := 0.041]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_South", c80re_core := 0]
table.coeffs <- table.coeffs [herd_name ==  "Redrock_Prairie_Creek", c80re_core := 0]
####  TO-DO
table.coeffs <- table.coeffs [herd_name ==  "Barkerville", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Burnt_Pine", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Graham", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Groundhog", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Moberly", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Monashee", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narraway", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Rockies", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Quintette", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Rainbows", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Telkwa", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Tweedsmuir", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Narrow_Lake", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Itcha_Ilgachuz", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Central_Selkirks", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Charlotte_Alplands", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_North", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Columbia_South", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Frisby_Boulder", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Hart_Ranges", c80re_matrix := -0] 
table.coeffs <- table.coeffs [herd_name ==  "Kennedy_Siding", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "North_Cariboo", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Purcell_Central", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Purcells_South", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "South_Selkirks", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_North", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Wells_Gray_South", c80re_matrix := 0]
table.coeffs <- table.coeffs [herd_name ==  "Redrock_Prairie_Creek", c80re_matrix := 0]

# Create the Raster
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216, 
                              xmn = 159587.5, xmx = 1881187.5, 
                              ymn = 173787.5, ymx = 1748187.5, 
                              crs = st_crs(bc.crit)$proj4string, resolution = c(100, 100), 
                              vals = 0)
bc.crit <- merge (bc.crit, table.coeffs, by.x = "herd_hab_name", by.y = "herd_hab_name") # merge id with the polygon data
ras.bc.crit  <-fasterize::fasterize(bc.crit , prov.rast, field = "value") # rasterize the polygon data to the provicnal raster
writeRaster(ras.bc.crit, "bccrithab.tif", overwrite = TRUE)

# Write the data to Postgres
## Raster
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/bccrithab.tif -t 100x100 rast.smc_herd_habitat | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)
## Table
DBI::dbWriteTable(conn, c("vat", "smc_coeffs"), value = table.coeffs, row.names = FALSE, overwrite = TRUE)

dbDisconnect(conn)
```


 
 
