---
title: "BC Caribou Population Estimates"
author: "Tyler Muhly"
date: "22/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rpostgis)
library(data.table)
```

# Background
We need data on caribou population estimates. This creates a table of that information, including source of the information, to be uploaded into our database for use in moduels or as part of information summary.

Note: currently in contact with Nicola Dodd about getting this data

### Caribou population data
```{r, pop}
caribou_pop<-read.csv("S:/ANA/PROJECTS/CLUS/Data/caribou/population/herd_estimates_simple_20200106.csv")
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "caribou_pop_simple"), value= caribou_pop, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)
```


### Wolf control data

Tyler pulled this dataset together -- to determine in which years population control activities take place.

```{r, pop_control}

wolf_actions<-read.csv("S:/ANA/PROJECTS/CLUS/Data/caribou/population/table_wolf_control_20200302.csv")
colnames(wolf_actions)<-c("herd_name", "year", "type")
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "wolf_control"), value= wolf_actions, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

```

### Merge wolf and pop data

```{r, final}
data_new<-data.table(merge(caribou_pop, wolf_actions, by.x = c("herd_name", "year"), by.y =c("herd_name", "year"), all.x = TRUE))
#Remove minimum counts and exper opinion estimates
data_new<-data_new[!(estimate_type %in% c("Expert Opinion", "Minimum count", "Minimum Count", "Unknown"))]

#remove dates confounded by population control resposnes
data_new<-data_new[is.na(type),]

#sort by herd_name and year
data_new[order(herd_name, year)]

#remove 'old' estimaste so this agrees with disturbance data
data_new<-data_new[year > 1980,]

#remove functionally extirpated populations
data_new<-data_new[pop_estimate > 20,]

#remove herds with only one data point
herds_counts <- data_new[, .(rowCount = .N), by = herd_name][rowCount > 1,]
data_new<-data_new[herd_name %in% herds_counts$herd_name,]

#calc the averaged census lambda
data_new[, pop_lag:= lapply(.SD, function(x) c(NA,x[-.N])), by = herd_name, .SDcols = "pop_estimate"]

data_new[, year_lag:= lapply(.SD, function(x) c(NA,x[-.N])), by = herd_name, .SDcols = "year"]
data_new[, lambda:= (pop_lag/pop_estimate)**(1/(year_lag-year))]
data_new[,c("pop_lag", "year_lag"):= list(NULL, NULL)]  

#calc the averaged census lambda
data_new[, year.0 := min(year), by=herd_name]
pop0<-data_new[year==year.0, c("herd_name","pop_estimate")]
setnames(pop0, "pop_estimate", "pop.0")
data_new<-merge(data_new, pop0, by.x = "herd_name", by.y = "herd_name")
data_new[, lambda.finite:= (pop_estimate/pop.0)]
data_new[year==year.0, lambda.finite:= NA]

# The number of observations
#nrow(data_new[!is.na(lambda),])

#rename the herds so that they link with CLUS
data_new[, herd_name:= lapply(.SD, function(x) { gsub("-", "_", x)}), .SDcols = "herd_name"]
data_new[, herd_name:= lapply(.SD, function(x) { gsub(" ", "_", x)}), .SDcols = "herd_name"]
unique(data_new$herd_name)

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "caribou_trend"), value= data_new, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

```

#### Graph of population data
```{r, graph_pop}
ggplot(data = data_new, aes(x=year, y = lambda.finite, color = herd_name))+
  geom_point() + geom_line()
```

#### GEt the disturbance information

```{r, disturbance}
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('vmdbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('vmdbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('vmdbuser', keyring = 'postgreSQL') ,password= keyring::key_get('vmdbpass', keyring = 'postgreSQL'))

disturb<-data.table(dbGetQuery(conn, paste0("SELECT * from disturbance_indicators.disturbance where scenario in ('", paste(unique(data_new$herd_name), collapse = "', '"),"');")))

dbDisconnect(conn)

disturb<-disturb[,year:=as.integer(timeperiod+1975)]
setnames(disturb, "scenario", "herd_name")
```


### Create the linkage
```{r, linkage}
data.0<-merge(disturb, data_new, by = c("herd_name", "year"))
```