---
title: "Caribou Herd Boundary Raster"
author: "Tyler Muhly"
date: "21/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose
This rmd produces a raster that specifies the caribou herd boundaries in British Columbia. It can be used in the CLUS model to summarize or calculate information by caribou herd area. Currently, it is used in the survivalCLUS SpaDES module to estimate caribou survival rates by herd as a function of forest age there. 

## Spatial Data on Caribou Herds
First, we'll get the caribou herd boundary data from the British Columbia government data warehouse (BCGW). TO do this we use the [bcdata](https://github.com/bcgov/bcdata) package. The data can also be downloaded [here](https://catalogue.data.gov.bc.ca/dataset/caribou-herd-locations-for-bc). 

```{r, get herd data from BCGW}
library (bcdata)
library (sf)

poly.caribou <- bcdata::bcdc_get_data ("caribou-herd-locations-for-bc") # herd boundary data is named "caribou-herd-locations-for-bc" in the BCGW; can use bcdc_search ("caribou") as a way to search for the data using the bcdata package
# when I developed htis it worked, now I get "Error: No Web Service resource available for this dataset." Download data as shapefile if needed
poly.caribou <- st_read ("C:\\Work\\caribou\\clus_data\\caribou\\caribou_herd\\bcdata_herds\\GCPB_CARIBOU_POPULATION_SP\\GCBP_CARIB_polygon.shp",  stringsAsFactors = FALSE)
# plot (st_geometry (poly.caribou))
```

## Rasterize the Data
Here we convert the polygon to a raster, following the provincial hectares BC raster convention that we are using in the CLUS model to ensure all rasters overlap.

```{r, convert polygon to raster}
library (raster)
library (fasterize)

prov.rast <- raster::raster ( # create the standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216, 
                              xmn = 159587.5, xmx = 1881187.5, 
                              ymn = 173787.5, ymx = 1748187.5, 
                              crs = st_crs(poly.caribou)$proj4string, resolution = c(100, 100), 
                              vals = 0)

poly.caribou$herd_integer <- as.integer (as.factor (poly.caribou$HERD_NAME)) # create an integer equivalent to herd name

ras.caribou.herd <-fasterize::fasterize (poly.caribou, prov.rast, field = "herd_integer") 
# turn the polygon into a raster

plot (ras.caribou.herd) # make sure the raster looks good
```

## Create Look-up Table
Here we create a look-up table for the raster so we can translate the raster into herd names later.

```{r, create look-up table for raster}
library (data.table)

lu_caribouHerd <- unique (data.table (cbind (poly.caribou$herd_integer, poly.caribou$HERD_NAME)))
lu_caribouHerd <- lu_caribouHerd [order(V1)]
setnames (lu_caribouHerd, c("V1", "V2"), c("raster_integer", "herd_name"))

```

## Commit the Data to the PostgreSQL database
Now we need to save the data. We save the raster to the raster schema and look-up table to the public schema in our postgreSQL database. 

```{r, commit data to the dbase}
library (DBI)
library (RPostgreSQL)
library (here)

conn <- DBI::dbConnect (dbDriver ("PostgreSQL"), host = keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable (conn, c("public", "caribou_herd"), value = lu_caribouHerd, 
                   row.names = FALSE, overwrite = TRUE)

writeRaster (ras.caribou.herd, file = "caribou_herd.tif", format = "GTiff", overwrite = TRUE)

#upload to db
system ("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here (), '/R/params/caribou_herd.tif -t 100x100 rast.caribou_herd | psql postgresql://clus_project:clus@DC052586:5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

```
