---
title: "Critical Habitat Raster"
author: "Kyle Lochhead"
date: "August 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

The critical habitat raster specifies the spatial zones used to summarize rsfCLUS outputs. In the case of caribou the critical habitats refer to core low elevation winter, core low elevation summer, core high elevation winter/summer, matrix etc.

## Spatial data

The critical habitats may come in various data structure forms like .shp or .gdb. In this chunk the data is loaded in R.
```{r, data}
library(sf)
#Chilcotin
chilcotin<-sf::st_read("Z:/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/caribou/critical_habitat/BC/chilcotin_lpu/eis_19_004_bc_core_chilcotin_v20190731.gdb", layer ='BCHabitat_20190731')
chilcotin<-st_cast(chilcotin, "MULTIPOLYGON")
chilcotin$critCode<-paste(chilcotin$Herd_Code,chilcotin$BCHab_code, sep = "_")

```

## Rasterize
The critical habitat spatial zones need to be rasterized to the same extent as the other layers to ensure that the pixels match

```{r, rasterize}
#Make a dummy raster with the same extent as the other provincial rasters
#build a default/empty provincial raster
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(chilcotin)$proj4string, resolution = c(100, 100), vals = 0)

chilcotin$critCode2<-as.integer(as.factor(chilcotin$critCode))
ras.chilcotin <-fasterize::fasterize(chilcotin, prov.rast, field = "critCode2") #this is a
plot(ras.chilcotin)
```

## Lookup Table
```{r, lookup}
lu_critHab<-unique(data.table(cbind(chilcotin$critCode2,chilcotin$critCode)))
lu_critHab<-lu_critHab[order(V1)]
setnames(lu_critHab, c("V1", "V2"), c("value", "crithab"))
```

## Commit to postgreSQL
```{r, commit_db}
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "criticalhabitat"), value= lu_critHab, row.names = FALSE, overwrite = TRUE)


writeRaster(ras.chilcotin, file="criticalhabitat.tif", format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here(), '/R/params/criticalhabitat.tif -t 100x100 rast.crithabitat | psql -d clus-h ', keyring::key_get('dbhost', keyring = 'postgreSQL'), ' -U ',user = keyring::key_get('dbuser', keyring = 'postgreSQL') ,'-W ', password = keyring::key_get('dbpass', keyring = 'postgreSQL')), show.output.on.console = FALSE, invisible = TRUE)
```
