---
title: "Critical Habitat Raster"
author: "Kyle Lochhead"
date: "August 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(data.table)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")
library(tidyverse)
```

## Purpose

The critical habitat raster specifies the spatial zones used to summarize rsfCLUS outputs. In the case of caribou the critical habitats refer to core low elevation winter, core low elevation summer, core high elevation winter/summer, matrix etc.

## Souther Mountain

### Central Group

The critical habitats may come in various data structure forms like .shp or .gdb. In this chunk the data is loaded in R.
```{r, sm.cg}
#Canadian (Federal) contraints
sm.cg.crit<-sf::st_read("S:/ANA/PROJECTS/CLUS/Data/caribou/critical_habitat/Canada/Southern_Mtn/Central_Group/data/DraftSMCcg_CHLPU_20181016/DraftCHLPU_20181016.gdb", layer ='CH_638_Rangifer_tarandus_caribou_SouthMountain_CentralGroup')

sm.cg.crit<-sm.cg.crit[!is.na(sm.cg.crit$CHVariant), c("SHAPE", "CHVariant")] #keep only the needed features
sm.cg.crit<-st_zm(sm.cg.crit) #remove the z dimension
sm.cg.crit<-st_cast(sm.cg.crit, "MULTIPOLYGON") #cast to a multipolygon

sm.cg.crit3<-sm.cg.crit %>% group_by(CHVariant) %>% 
        summarise() #unique polygons for each CHVariant
sm.cg.crit3[sm.cg.crit3$CHVariant == 'Connectivity Range',]$CHVariant<-'Matrix Range'
st_write(sm.cg.crit3, "sm_cg.shp")

```
### Northern Group
```{r, sm.cg}
#Canadian (Federal) contraints
sm.ng.crit<-sf::st_read("S:/ANA/PROJECTS/CLUS/Data/caribou/critical_habitat/Canada/Southern_Mtn/Northern_Group/data/DraftSMCng_CHLPU_20181016/DraftCHLPU_20181016.gdb", layer ='CH_638_Rangifer_tarandus_caribou_SouthMountain_NorthernGroup')

sm.ng.crit<-sm.ng.crit[!is.na(sm.ng.crit$CHVariant), c("SHAPE", "CHVariant")] #keep only the needed features
sm.ng.crit<-st_zm(sm.ng.crit) #remove the z dimension
sm.ng.crit<-st_cast(sm.ng.crit, "MULTIPOLYGON") #cast to a multipolygon
sm.ng.crit<-sm.ng.crit[!(sm.ng.crit$CHVariant == ''),]
  
sm.ng.crit3<-sm.ng.crit %>% group_by(CHVariant) %>% 
        summarise() #unique polygons for each CHVariant

sm.ng.crit3[sm.ng.crit3$CHVariant == 'Connectivity Range',]$CHVariant<-'Matrix Range'
st_write(sm.ng.crit3, "sm_ng.shp")

```
### Southern Group
```{r, sm.cg}
#Canadian (Federal) contraints
sm.sg.crit<-sf::st_read("S:/ANA/PROJECTS/CLUS/Data/caribou/critical_habitat/Canada/Southern_Mtn/Southern_Group/data/DraftSMCsg_CHLPU_20181016/DraftCHLPU_20181016.gdb", layer ='CH_638_Rangifer_tarandus_caribou_SouthMountain_SouthernGroup')

sm.sg.crit<-sm.sg.crit[!is.na(sm.sg.crit$CHVariant), c("Shape", "CHVariant")] #keep only the needed features
sm.sg.crit<-st_zm(sm.sg.crit) #remove the z dimension
sm.sg.crit<-st_cast(sm.sg.crit, "MULTIPOLYGON") #cast to a multipolygon
sm.sg.crit<-sm.sg.crit[!(sm.sg.crit$CHVariant == ''),]
sm.sg.crit<-sm.sg.crit[!is.null(sm.sg.crit$CHVariant),]
  
sm.sg.crit3<-sm.sg.crit %>% group_by(CHVariant) %>% 
        summarise() #unique polygons for each CHVariant

sm.sg.crit3[sm.sg.crit3$CHVariant == 'Connectivity Range',]$CHVariant<-'Matrix Range'
st_write(sm.sg.crit3, "sm_sg.shp")

```

## Rasterize critical habitat types
The critical habitat spatial zones need to be rasterized to the same extent as the other layers to ensure that the pixels match

```{r, rasterize}
#Make a dummy raster with the same extent as the other provincial rasters
#build a default/empty provincial raster
sm.ng<-st_read(paste0(here::here(),"/R/Params/sm_ng.shp"))
sm.cg<-st_read(paste0(here::here(),"/R/Params/sm_cg.shp"))
sm.sg<-st_read(paste0(here::here(),"/R/Params/sm_sg.shp"))

sm<-rbind(sm.ng,sm.cg,sm.sg)
sm1<-sm[sm$CHVariant %in% c('Matrix Range', 'High Elevation Winter/Summer Range', 'Low Elevation Summer Range',  'High Elevation Winter Range', 'Core Range', 'Low Elevation Winter Range' ),]

crit.vat<-data.table(CHVariant=unique(sm1$CHVariant))
crit.vat[, critid:=seq_len(.N)]

sm2<-merge(sm1, crit.vat)

#rasterize the critical habitats
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(sm.ng)$proj4string, resolution = c(100, 100), vals = 0)

ras.sm <-fasterize::fasterize(sm2, prov.rast, field = "critid") #this is a
raster::plot(ras.sm)
```

## Caribou Herds or LPUs 
```{r, carib}
carib_poly<-getSpatialQuery("SELECT herd_name, wkb_geometry from bc_carib_poly_20090904;")
carib.vat<-data.table(herd_name=unique(carib_poly$herd_name))
carib.vat[,caribid := seq_len(.N)*10]#multiply by 10 so the first digit can be a unique critical habitat (1-6)
carib_poly2<-merge(carib_poly,carib.vat)

#Create a provincial raster
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(carib_poly)$proj4string, resolution = c(100, 100), vals = 0)

ras.carib <-fasterize::fasterize(carib_poly2, prov.rast, field = "caribid") 
raster::plot(ras.carib)
```
## Create the zone raster
```{r, zon.ras}
ras.sm[is.na(ras.sm[])]<-0
ras.carib[is.na(ras.carib[])]<-0
ras.zone<-ras.sm+ras.carib

#Clip to the bc boundary
bcb <-bcmaps::bc_bound_hres()
bcb$bc <-1
ras.bc <-fasterize::fasterize(bcb, prov.rast, field = "bc") 
ras.zone <-ras.zone*ras.bc


test<-data.table(freq(ras.zone))
test[, critid:= as.integer(substr(as.character(value), nchar(as.character(value)), nchar(as.character(value))))] 

#get rid of the pixels that do not have a critical habitat
remove<-test[critid == 0, value]
ras.zone[ras.zone[] %in% remove]<-0
ras.zone[ras.zone[] == 0]<-NA


#create the value attribute table (vat)
sm.vat<- test[!(critid == 0), ]
sm.vat[,caribid:= value - critid]
sm.vat<-merge(sm.vat, carib.vat, all.x = TRUE)
sm.vat<-merge(sm.vat, crit.vat, all.x = TRUE, by.x = 'critid', by.y ='critid')

#zoneid reference_zone ndt variable threshold type percentage
setnames(sm.vat, "value", "zoneid")
sm.vat[, reference_zone:= 'rast.zone_cond_crithab']
sm.vat[, variable:= 'age']
sm.vat[, type:= 'le']
sm.vat[, threshold:= '40']

sm.vat[CHVariant == 'Matrix Range', percentage:= 35]
sm.vat[CHVariant == 'Low Elevation Winter Range', percentage:= 35]
sm.vat[CHVariant == 'Core Range', percentage:= NA]

nh.zones<-sm.vat[is.na(percentage), zoneid]
ras.zone[ras.zone[] %in% nh.zones]<-0

zone.crithab<-sm.vat[!(zoneid %in% nh.zones),]
zone.crithab<-zone.crithab[,ndt:=0]

zone.crithab<-zone.crithab[, c('zoneid', 'reference_zone', 'ndt', 'variable', 'threshold','type','percentage' )]
zone.crithab.nh<-data.table(zoneid =0, reference_zone = 'rast.zone_cond_crithab', ndt =0, variable ='', threshold = 0, type = 'nh', percentage =0)

zone.crithab<-rbindlist(list(zone.crithab, zone.crithab.nh))

writeRaster(ras.zone, "test.tif", overwrite = TRUE)
```



## Commit to postgreSQL
```{r, commit_db}

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

zone.crithab<-zone.crithab[,zoneid:=as.integer(zoneid)]
zone.crithab<-zone.crithab[,ndt:=as.integer(ndt)]
zone.crithab<-zone.crithab[,threshold:=as.numeric(threshold)]
DBI::dbWriteTable(conn, c("public", "zone_crithab"), value= zone.crithab, row.names = FALSE, overwrite = TRUE)

#dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone_constraints")
dbDisconnect(conn)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/test.tif -t 100x100 rast.zone_cond_crithab | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)
```
