---
title: "Critical Habitat Raster"
author: "Kyle Lochhead"
date: "August 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(data.table)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")
library(tidyverse)
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(getSpatialQuery("Select * from bc_carib_poly_20090904 limit 1"))$proj4string, resolution = c(100, 100), vals = 0)
```

## Purpose

Here we develop rasters that specify the location of caribou herds and critical habitat types across British Columbia. When running the dataLoaderCLUS module, the herd and critical habitat areas that overlap the timber supply unit of interest get imported into the SQLite database as 'zones' in the 'pixels' table of the database (see [dataLoaderCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/dataLoaderCLUS)). These data provide spatial areas to summarize information and apply constraints related to caribou, for example, habitat disturbance indicators.   

Caribou herd boundaries are essentially the outer spatial boundaries of habitat used by the same group or 'sub-population' of caribou, and they are typically surveyed together to estimate population numbers.    

Caribou critical habitat has not been defined for all cariobu herds in BC, but where it has been delineated, it typically occurs within herd boundaries, is divided into various types, including:
- high elevation winter and summer range (HEWSR)
- high elevation winter range (HEWR)
- high elevation summer range (HESR)
- low elevation winter range (LEWR)
- low elevation summer range (LESR)
- matrix

Caribou critical habitat boudnaries have been defined independently by the government of Canada and more recently, by the government of British Columbia. Both types are create below.

## Caribou critical habitat
### British Columbia
- this data is currently (as of June 2020) 'draft' and not for distribution







```{r, sm.cg}
#Canadian (Federal) contraints
#bc.crit<-getSpatialQuery("SELECT * from bc_caribou_core_matrix_habitat_v20190904_1;")
bc.crit<-getSpatialQuery("SELECT * from bc_caribou_linework_v20200507_shp_core_matrix;")

#all
all.bc<-bc.crit
all.bc$crithab<-paste(all.bc$herd_name, all.bc$bchab_code)
all.vat<-data.table(unique(all.bc$crithab))
setnames(all.vat, "V1", "crithab")
all.vat[, value:= seq_len(.N)]
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
DBI::dbWriteTable(conn, c("public", "criticalhabitat_bc_vat"), value= all.vat, row.names = FALSE, overwrite = TRUE)
dbDisconnect(conn)

all.bc2<-merge(all.bc, all.vat, by.x = "crithab",by.y = "crithab")

ras.all.bc <-fasterize::fasterize(all.bc2, prov.rast, field = "value") #this is a
writeRaster(ras.all.bc, "bccrithab.tif", overwrite = TRUE)
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/bccrithab.tif -t 100x100 rast.bc_crithab | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)



#c("Rainbows","Charlotte_Alplands", "Itcha_Ilgachuz", "Groundhog", "Monashee", "Barkerville",  "Telkwa", "Central_Rockies","Central_Selkirks","Columbia_North","Columbia_South","Frisby_Boulder", "Purcell_Central","Purcell_South","South_Selkirks","Wells_Gray_South","Narrow_Lake","North_Cariboo","Wells_Gray_North","Hart_Ranges","Redrock_Prairie_Creek")
herds<-c("Barkerville", "Graham", "Groundhog",  "Moberly",  "Burnt_Pine", "Monashee","Narraway", "Quintette" ,  "Rainbows", "Telkwa",  "Itcha_Ilgachuz",  "Central_Rockies", "Central_Selkirks" ,  "Charlotte_Alplands", "Columbia_North", "Columbia_South", "Frisby_Boulder","Hart_Ranges",         "Kennedy_Siding","Narrow_Lake", "North_Cariboo" , "Purcell_Central",  "Purcells_South", "South_Selkirks", "Wells_Gray_North", "Wells_Gray_South", "Redrock_Prairie_Creek")

#herds<-c("Narrow_Lake","North_Cariboo")
for(herd in herds){
  bc.crit.selected<-eval(parse(text = paste0("bc.crit[bc.crit$herd_name == '", 
                                             herd,"',]")))
  vat<-data.table(unique(bc.crit.selected$bchab_code))
  setnames(vat, "V1", "crithab")
  vat[, zoneid:= seq_len(.N)]
  
  conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
  DBI::dbWriteTable(conn, c("public", paste0("criticalhabitat_",tolower(herd),"_vat")), value= vat, row.names = FALSE, overwrite = TRUE)
  dbDisconnect(conn)
  
  bc.crit.selected2 <-merge(bc.crit.selected, vat, by.x = "bchab_code",by.y = "crithab")
  ras.bc.crit.selected <-fasterize::fasterize(bc.crit.selected2, prov.rast, field = "zoneid")

  eccc.vat<-vat
  eccc.vat[, reference_zone:= paste0('rast.zone_cond_eccc_', tolower(herd),'_crithab')]
  eccc.vat[, variable:= 'dist']
  eccc.vat[, type:= 'ge']
  eccc.vat[, ndt:= 0]
  eccc.vat[, threshold:= 500]
  eccc.vat[ crithab %in% c('Matrix'), percentage:= 85]
  eccc.nh.zones<-eccc.vat[is.na(percentage), zoneid]
  
  ras.eccc<-ras.bc.crit.selected
  ras.eccc[ras.eccc[] %in% eccc.nh.zones]<-0
  
  zone.eccc.crithab<-eccc.vat[!(zoneid %in% eccc.nh.zones),]
  zone.eccc.crithab<-zone.eccc.crithab[, c('zoneid', 'reference_zone', 'ndt', 'variable', 'threshold','type','percentage' )]
  zone.eccc.crithab.nh<-data.table(zoneid =0, reference_zone = paste0('rast.zone_cond_eccc_', tolower(herd),'_crithab'), ndt =0, variable ='', threshold = 0, type = 'nh', percentage =0)

  zone.eccc.crithab<-rbindlist(list(zone.eccc.crithab, zone.eccc.crithab.nh))
  writeRaster(ras.eccc, "rasecccrit.tif", overwrite = TRUE)

  zone.eccc.crithab<-zone.eccc.crithab[,zoneid:=as.integer(zoneid)]
  zone.eccc.crithab<-zone.eccc.crithab[,ndt:=as.integer(ndt)]
  zone.eccc.crithab<-zone.eccc.crithab[,threshold:=as.numeric(threshold)]

  conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

  DBI::dbWriteTable(conn, c("public", paste0("zone_eccc_",tolower(herd),"_crithab")), value= zone.eccc.crithab, row.names = FALSE, overwrite = TRUE)
 dbExecute(conn, paste0("ALTER TABLE zone_eccc_",tolower(herd),"_crithab INHERIT zone_constraints"))
 dbDisconnect(conn)

#upload to db
  system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/rasecccrit.tif -t 100x100', paste0(' rast.zone_cond_eccc_', tolower(herd),'_crithab'),' | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)


  bc.vat<-vat
  bc.vat[, reference_zone:= paste0('rast.zone_cond_bc_', tolower(herd),'_crithab')]
  bc.vat[, variable:= 'dist']
  bc.vat[, type:= 'ge']
  bc.vat[, threshold:= 500]
  bc.vat[ crithab %in% c('Matrix'), percentage:= 65]
  bc.vat[ crithab %in% c('Matrix'), threshold:= 0]
  bc.vat[ crithab %in% c('LEWR', 'LEWSR'), percentage:= 85]
  bc.nh.zones<-bc.vat[is.na(percentage), zoneid]
  
  ras.bc<-ras.bc.crit.selected
  ras.bc[ras.bc[] %in% bc.nh.zones]<-0
  writeRaster(ras.bc, "rasbccrit.tif", overwrite = TRUE)
  
  zone.bc.crithab<-bc.vat[!(zoneid %in% bc.nh.zones),]
  zone.bc.crithab<-zone.bc.crithab[, c('zoneid', 'reference_zone', 'ndt', 'variable', 'threshold','type','percentage' )]
  zone.bc.crithab.nh<-data.table(zoneid =0, reference_zone = paste0('rast.zone_cond_bc_', tolower(herd),'_crithab'), ndt =0, variable ='', threshold = 0, type = 'nh', percentage =0)

  zone.bc.crithab<-rbindlist(list(zone.bc.crithab, zone.bc.crithab.nh))
  zone.bc.crithab<-zone.bc.crithab[,zoneid:=as.integer(zoneid)]
  zone.bc.crithab<-zone.bc.crithab[,ndt:=as.integer(ndt)]
  zone.bc.crithab<-zone.bc.crithab[,threshold:=as.numeric(threshold)]
  
  conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

  DBI::dbWriteTable(conn, c("public", paste0("zone_bc_",tolower(herd),"_crithab")), value= zone.bc.crithab, row.names = FALSE, overwrite = TRUE)
 dbExecute(conn, paste0("ALTER TABLE zone_bc_",tolower(herd),"_crithab INHERIT zone_constraints"))
 dbDisconnect(conn)

#upload to db
  system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/rasbccrit.tif -t 100x100', paste0(' rast.zone_cond_bc_', tolower(herd),'_crithab'),' | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

}


```



### No harvest in any critical habitat 
```{r, noharvet}
#Canadian (Federal) contraints
#bc.crit<-getSpatialQuery("SELECT * from bc_caribou_core_matrix_habitat_v20190904_1;")
bc.crit<-getSpatialQuery("SELECT * from bc_caribou_linework_v20200507_shp_core_matrix;")

#herds<-c("Rainbows","Charlotte_Alplands", "Itcha_Ilgachuz", "Barkerville", "Wells_Gray_South","Narrow_Lake","North_Cariboo","Wells_Gray_North")
herds<-c("Barkerville", "Graham", "Groundhog",  "Moberly",  "Burnt_Pine", "Monashee","Narraway", "Quintette" ,  "Rainbows", "Telkwa",  "Itcha_Ilgachuz",  "Central_Rockies", "Central_Selkirks" ,  "Charlotte_Alplands", "Columbia_North", "Columbia_South", "Frisby_Boulder","Hart_Ranges",         "Kennedy_Siding","Narrow_Lake", "North_Cariboo" , "Purcell_Central",  "Purcells_South", "South_Selkirks", "Wells_Gray_North", "Wells_Gray_South", "Redrock_Prairie_Creek")

for(herd in herds){
bc.crit.selected<-eval(parse(text = paste0("bc.crit[bc.crit$herd_name == '", 
                                             herd,"',]")))
bc.crit.selected$zoneid<-0
  
ras.bc.crit.selected <-fasterize::fasterize(bc.crit.selected, prov.rast, field = "zoneid")
writeRaster(ras.bc.crit.selected , "rasnhcrit.tif", overwrite = TRUE)

zone.eccc.crithab<-data.table(zoneid =0, reference_zone = paste0('rast.zone_cond_nh_crit_', tolower(herd),'_crithab'), ndt =0, variable ='', threshold = 0, type = 'nh', percentage =0)
zone.eccc.crithab<-zone.eccc.crithab[,zoneid:=as.integer(zoneid)]
zone.eccc.crithab<-zone.eccc.crithab[,ndt:=as.integer(ndt)]
zone.eccc.crithab<-zone.eccc.crithab[,threshold:=as.numeric(threshold)]

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", paste0("zone_nh_crit_",tolower(herd),"_crithab")), value= zone.eccc.crithab, row.names = FALSE, overwrite = TRUE)
 dbExecute(conn, paste0("ALTER TABLE zone_nh_crit_",tolower(herd),"_crithab INHERIT zone_constraints"))
 dbDisconnect(conn)

#upload to db
  system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/rasnhcrit.tif -t 100x100', paste0(' rast.zone_cond_nh_crit_', tolower(herd),'_crithab'),' | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

}
```

---

## Fed line work

## Southern Mountain

### Central Group

The critical habitats may come in various data structure forms like .shp or .gdb. In this chunk the data is loaded in R.
```{r, sm.cg}
#Canadian (Federal) contraints
sm.cg.crit<-sf::st_read("S:/ANA/PROJECTS/CLUS/Data/caribou/critical_habitat/Canada/Southern_Mtn/Central_Group/data/DraftSMCcg_CHLPU_20181016/DraftCHLPU_20181016.gdb", layer ='CH_638_Rangifer_tarandus_caribou_SouthMountain_CentralGroup')

unique(sm.cg.crit$CHVariant)

sm.cg.crit<-sm.cg.crit[!is.na(sm.cg.crit$CHVariant), c("SHAPE", "CHVariant")] #keep only the needed features
sm.cg.crit<-st_zm(sm.cg.crit) #remove the z dimension
sm.cg.crit<-st_cast(sm.cg.crit, "MULTIPOLYGON") #cast to a multipolygon

sm.cg.crit3<-sm.cg.crit %>% group_by(CHVariant) %>% 
        summarise() #unique polygons for each CHVariant
sm.cg.crit3<-sm.cg.crit3[!(sm.cg.crit3$CHVariant == 'Connectivity Range'),]
st_write(sm.cg.crit3, "sm_cg.shp")

```
### Northern Group
```{r, sm.cg}
#Canadian (Federal) contraints
sm.ng.crit<-sf::st_read("S:/ANA/PROJECTS/CLUS/Data/caribou/critical_habitat/Canada/Southern_Mtn/Northern_Group/data/DraftSMCng_CHLPU_20181016/DraftCHLPU_20181016.gdb", layer ='CH_638_Rangifer_tarandus_caribou_SouthMountain_NorthernGroup')

unique(sm.ng.crit$CHVariant)

sm.ng.crit<-sm.ng.crit[!is.na(sm.ng.crit$CHVariant), c("SHAPE", "CHVariant")] #keep only the needed features
sm.ng.crit<-st_zm(sm.ng.crit) #remove the z dimension
sm.ng.crit<-st_cast(sm.ng.crit, "MULTIPOLYGON") #cast to a multipolygon
sm.ng.crit<-sm.ng.crit[!(sm.ng.crit$CHVariant == ''),]
  
sm.ng.crit3<-sm.ng.crit %>% group_by(CHVariant) %>% 
        summarise() #unique polygons for each CHVariant

sm.ng.crit3<-sm.ng.crit3[!(sm.ng.crit3$CHVariant == 'Connectivity Range'),]
st_write(sm.ng.crit3, "sm_ng.shp")

```
### Southern Group
```{r, sm.cg}
#Canadian (Federal) contraints
sm.sg.crit<-sf::st_read("S:/ANA/PROJECTS/CLUS/Data/caribou/critical_habitat/Canada/Southern_Mtn/Southern_Group/data/DraftSMCsg_CHLPU_20181016/DraftCHLPU_20181016.gdb", layer ='CH_638_Rangifer_tarandus_caribou_SouthMountain_SouthernGroup')

unique(sm.sg.crit$CHVariant)

sm.sg.crit<-sm.sg.crit[!is.na(sm.sg.crit$CHVariant), c("Shape", "CHVariant")] #keep only the needed features
sm.sg.crit<-st_zm(sm.sg.crit) #remove the z dimension
sm.sg.crit<-st_cast(sm.sg.crit, "MULTIPOLYGON") #cast to a multipolygon
sm.sg.crit<-sm.sg.crit[!(sm.sg.crit$CHVariant == ''),]
sm.sg.crit<-sm.sg.crit[!is.null(sm.sg.crit$CHVariant),]
  
sm.sg.crit3<-sm.sg.crit %>% group_by(CHVariant) %>% 
        summarise() #unique polygons for each CHVariant

sm.sg.crit3<-sm.sg.crit3[!(sm.sg.crit3$CHVariant == 'Connectivity Range'),]
sm.sg.crit3<-sm.sg.crit3[!(sm.sg.crit3$CHVariant == 'Matrix Range'),]
st_write(sm.sg.crit3, "sm_sg.shp")

```

## Rasterize critical habitat types
The critical habitat spatial zones need to be rasterized to the same extent as the other layers to ensure that the pixels match

```{r, rasterize}
#Make a dummy raster with the same extent as the other provincial rasters
#build a default/empty provincial raster
sm.ng<-st_read(paste0(here::here(),"/R/Params/sm_ng.shp"))
sm.cg<-st_read(paste0(here::here(),"/R/Params/sm_cg.shp"))
sm.sg<-st_read(paste0(here::here(),"/R/Params/sm_sg.shp"))

sm<-rbind(sm.ng,sm.cg,sm.sg)
unique(sm$CHVariant)
sm1<-sm[sm$CHVariant %in% c('Matrix Range', 'High Elevation Winter/Summer Range', 'Low Elevation Summer Range',  'High Elevation Winter Range', 'Core Range', 'Low Elevation Winter Range' ),]

crit.vat<-data.table(CHVariant=unique(sm1$CHVariant))
crit.vat[, critid:=seq_len(.N)]

sm2<-merge(sm1, crit.vat)

#rasterize the critical habitat

ras.sm <-fasterize::fasterize(sm2, prov.rast, field = "critid") #this is a
raster::plot(ras.sm)
```

## Caribou Herds or LPUs 
```{r, carib}
carib_poly<-getSpatialQuery("SELECT herd_name, wkb_geometry from bc_carib_poly_20090904;")
carib.vat<-data.table(herd_name=unique(carib_poly$herd_name))
carib.vat[,caribid := seq_len(.N)*10]#multiply by 10 so the first digit can be a unique critical habitat (1-6)
carib_poly2<-merge(carib_poly,carib.vat)

#Create a provincial raster
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(carib_poly)$proj4string, resolution = c(100, 100), vals = 0)

ras.carib <-fasterize::fasterize(carib_poly2, prov.rast, field = "caribid") 
raster::plot(ras.carib)
```
## Create the zone raster
```{r, zon.ras}
ras.sm[is.na(ras.sm[])]<-0
ras.carib[is.na(ras.carib[])]<-0
ras.zone<-ras.sm+ras.carib

#Clip to the bc boundary
bcb <-bcmaps::bc_bound_hres()
bcb$bc <-1
ras.bc <-fasterize::fasterize(bcb, prov.rast, field = "bc") 
ras.zone <-ras.zone*ras.bc


test<-data.table(freq(ras.zone))
test[, critid:= as.integer(substr(as.character(value), nchar(as.character(value)), nchar(as.character(value))))] 

#get rid of the pixels that do not have a critical habitat
remove<-test[critid == 0, value]
ras.zone[ras.zone[] %in% remove]<-NA

#create the value attribute table (vat)
sm.vat<- test[!(critid == 0), ]
sm.vat[,caribid:= value - critid] #get the caribou herd identifier
sm.vat<-merge(sm.vat, carib.vat, all.x = TRUE)
sm.vat<-merge(sm.vat, crit.vat, all.x = TRUE, by.x = 'critid', by.y ='critid')

#zoneid reference_zone ndt variable threshold type percentage
setnames(sm.vat, "value", "zoneid")
sm.vat[, reference_zone:= 'rast.zone_cond_crithab']
sm.vat[, variable:= 'age']
sm.vat[, type:= 'le']
sm.vat[, threshold:= '40']

sm.vat[CHVariant == 'Matrix Range', percentage:= 18]
sm.vat[CHVariant == 'Low Elevation Winter Range', percentage:= 18]

nh.zones<-sm.vat[is.na(percentage), zoneid]
ras.zone[ras.zone[] %in% nh.zones]<-0

zone.crithab<-sm.vat[!(zoneid %in% nh.zones),]
zone.crithab<-zone.crithab[,ndt:=0]

zone.crithab<-zone.crithab[, c('zoneid', 'reference_zone', 'ndt', 'variable', 'threshold','type','percentage' )]
zone.crithab.nh<-data.table(zoneid =0, reference_zone = 'rast.zone_cond_crithab', ndt =0, variable ='', threshold = 0, type = 'nh', percentage =0)

zone.crithab<-rbindlist(list(zone.crithab, zone.crithab.nh))

writeRaster(ras.zone, "test.tif", overwrite = TRUE)
```



## Commit to postgreSQL
```{r, commit_db}

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

zone.crithab<-zone.crithab[,zoneid:=as.integer(zoneid)]
zone.crithab<-zone.crithab[,ndt:=as.integer(ndt)]
zone.crithab<-zone.crithab[,threshold:=as.numeric(threshold)]
DBI::dbWriteTable(conn, c("public", "zone_crithab"), value= zone.crithab, row.names = FALSE, overwrite = TRUE)

#dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone_constraints")
dbDisconnect(conn)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/test.tif -t 100x100 rast.zone_cond_crithab | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)
```



- need anotehr column in one of the tables 

