---
title: "Scripts for creating parameters to create a delivered wood costs model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source (here::here("R/functions/R_Postgres.R"))
library (data.table)
library (sf)
library (tidyverse)
library (raster)
library (fasterize)
library (rpostgis)
library (janitor)

conn <- DBI::dbConnect (RPostgreSQL::PostgreSQL(), 
                        host=keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                        dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                        port='5432',
                        user = keyring::key_get('dbuser', keyring = 'postgreSQL'),
                        password = keyring::key_get('dbpass', keyring = 'postgreSQL'))

#Create a provincial raster
prov.rast <- raster::raster (nrows = 15744, ncols = 17216, 
                             xmn = 159587.5, xmx = 1881187.5, 
                             ymn = 173787.5, ymx = 1748187.5, 
                             crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", 
                             resolution = c (100, 100), vals = 0)

```



## Roads

```{r, updated integrated roads data from CE program}

# data form Cumulative Effects Program; obtained with permission; 2021 version
# ogr2ogr -f PostgreSQL PG:"dbname=clus port=xxxx user=xxxx password=xxxx host=xxxx" D:\clus_data\roads\BC_CE_Integrated_Roads_2021_20210805.gdb integrated_roads_2021 -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI -nln integrated_roads_2021


# Roads layers to make
# the key provincial-scale roads data source here is the cumulative effects program integrated roads data; public.integrated_roads
roads_sf_perm <- getSpatialQuery ("SELECT shape,  -2  as road FROM public.integrated_roads_2021 where integrated_road_class_num <= 2 or (dra_road_name_full is not null AND dra_road_class <> 'trail');")
roads_sf <- getSpatialQuery("SELECT shape,  -1  as road FROM public.integrated_roads_2021 where integrated_road_class_num > 2")
# the above logic defines highways and roads with a name that are not trails as 'permanent' roads (-2), and all other roads types as non-permanent (-1)

# integrated_road_class_num definitions are below:
# class 1 = Highway/Arterial (freeway, highway, arterial, collector, ramp, yield )
# class 2 = Primary - Paved (local, resource, strata, alleyway, lane, driveway)
# class 3 = Secondary, FSR, Local (FSR, Local, service, recreational, resource, OGC long-term all weather)
# class 4 = Tertiary, Other (permit roads, in-block, restricted, proposed, seasonal, overgrown, decommissioned, trail, runway) 


#Buffer the MULTILINESTRINGS
roads_sf_perm<-roads_sf_perm %>% st_buffer(dist = 51)
roads_sf<-roads_sf %>% st_buffer(dist = 51)

#Rasterize
road_perm<-fasterize::fasterize(st_cast(roads_sf_perm, "MULTIPOLYGON"), prov.rast, field = "road")
road_perm[is.na(road_perm[])]<-0

road<-fasterize::fasterize(st_cast(roads_sf, "MULTIPOLYGON"), prov.rast, field = "road")
road[is.na(road[])]<-0

out_road<-road_perm + road
out_road[out_road[] < -2]<- -2
writeRaster(out_road, "ce_road_class_2021.tif", overwrite = TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/ce_road_class_2021.tif -t 100x100 rast.ce_road_2021 | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

### ROAD SPEEDS
### Not used
# road_type <- getSpatialQuery ("SELECT shape,  dra_road_surface, dra_road_name_full, integrated_road_class_descr  FROM public.integrated_roads_2021 where dra_road_class <> 'trail';")
# 
# road_type$class <- as.numeric (0)
# 
# ### set the classes
# # paved highways are class 1: these are main highways with some urban streets
# # unpaved highways are class 2: these are highways that arent paved; there aren't a lot of them, but they do connect some roads so are improtant to track
# # fsr roads are class 3: these look like main FSR roads, but there are some road fragments that are problematic
# # secondary non-fsr roads and tertiary loose, unknown, seasonal and rough roads and quaternary roads are 4: these look like a combination of road networks that interconnect FSR roads and fragments of spurs, in-block roads, that connect to FSR roads
# # primary paved roads are 5: mostly urban streets
# road_type$class [road_type$integrated_road_class_descr == "Hwy, Arterial" & road_type$dra_road_surface == "paved"] <- 1
# road_type$class [road_type$integrated_road_class_descr == "Hwy, Arterial" & road_type$dra_road_surface != "paved"] <- 2
# road_type$class [road_type$integrated_road_class_descr == "Secondary, FSR" & road_type$dra_road_name_full != ""] <- 3
# road_type$class [road_type$integrated_road_class_descr == "Secondary, FSR" & road_type$dra_road_name_full == ""] <- 4
# road_type$class [road_type$integrated_road_class_descr == "Tertiary, Operational, Local, Blank" & road_type$dra_road_surface == "loose" | road_type$dra_road_surface == "unknown" | road_type$dra_road_surface == "seasonal" | road_type$dra_road_surface == "rough"] <- 4
# road_type$class [road_type$integrated_road_class_descr == "Quaternary, In-Block"] <- 4
# road_type$class [road_type$integrated_road_class_descr == "Primary, Paved"] <- 5
# 
# # filter
# road_type <- road_type [road_type$class > 0, ]
# 
# #rasterie 
# road <- fasterize::fasterize(road_type, prov.rast, field = "class")



```



## ECAS Harvest System and Cycle Time
Create a spatial point dataset of cycle time and harvest system too use as predictors of costs

```{r, cycle time and harvest system location data}

data.dir <- "D:\\clus_data\\dlvd_wood_cost\\"

#### Compile ECAS  data for cycle time and harvest system data 
#### using data form last 10 years...
#### Source: G:\!Transfr\Stone_queries
ecas2023 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2023.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% # ^ matches the start of string and remove
                            clean_names () %>% # make labels snake case
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% # if numeric replace NAs with zeros
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2022 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2022.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2021 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2021.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2020 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2020.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2019 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2019.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2018 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2018.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2017 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2017.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2016 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2016.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2015 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2015.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2014 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2014.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)
ecas2013 <- read_csv (paste0 (data.dir, "InteriorStoneQuery_2013.csv")) %>%
                            rename_all(~ str_replace(., "^\\S* ", "")) %>% 
                            clean_names () %>% 
                            mutate (man_unit = as.numeric(man_unit)) %>%
                            mutate_if (is.numeric, ~ replace_na(., 0)) %>% 
                            dplyr::select (mark, prim_cyc_time_all, sec_cycle_time_all, man_unit, licence, gscc_vol_ha, chgcc_vol_ha, ncv,
                                           tot_merch_area, gscc_vol, chgcc_vol, app_eff_date)

ecas <- bind_rows (
  list(e2023 = ecas2023, e2022 = ecas2022, e2021 = ecas2021, e2020 = ecas2020, e2019 = ecas2019, 
       e2018 = ecas2018, e2017 = ecas2017,  e2016 = ecas2016),
  .id = "id"
) %>%
  mutate_if(is.numeric, ~ replace_na(., 0)) %>%
  remove_empty("cols") %>%
  group_by(mark) %>%
  arrange(desc(app_eff_date)) %>% # order from latest to earliest date
  slice(1) %>% # keep the record with the latest date
  ungroup()

#### Use RESULTS data to get locations to apply ECAS data
#### Uses timber mark as spatial linkage
#### Source: https://catalogue.data.gov.bc.ca/dataset/results-openings-svw
openings <- st_make_valid (st_read (paste0 (data.dir, "delivered_wood_cost.gdb"), 
                                    "results_openings", 
                                    stringsAsFactors = FALSE))
vect.openings <- terra::vect (openings) 
vect.openings <- na.omit (vect.openings, field = NA, geom = TRUE) # drop empty geometries
vect.openings.reduce <- vect.openings [, c ("OPENING_ID", "TIMBER_MARK")] # simplify
vect.openings.reduce$TIMBER_MARK <- paste0("_", vect.openings.reduce$TIMBER_MARK) # add underscore to match with ecas data

# create centroid from blocks
vect.opening.centroid <- terra::centroids (vect.openings.reduce) 

#join locations to ecas data
point.ecas <- merge (vect.opening.centroid, ecas, by.x = "TIMBER_MARK", by.y = "mark")

# make names 10 characters long for stupid ESRI
names (point.ecas) <- c ("timb_mark", "open_id", "id", "p_cyc_time", "s_cyc_time", "man_unit", "licence", "gscc_v_ha", "chgcc_v_ha", "ncv", "t_mrch_area", "gscc_vol", "chgcc_vol", "ap_ef_date")

### intersect with distance to roads
# Roads
rast.roads <- pgGetRast (conn,
              					 name = c("rast", "ce_road_2021"), # schema, table
              					 rast = "rast", bands = 1)

m <- c(-2, -2, 1,  -2, 0, NA)
rclmat <- matrix(m, ncol=3, byrow=TRUE)
rast.roads.rc <- reclassify (rast.roads, rclmat)



# roads_sf_perm <- getSpatialQuery ("SELECT shape,  -2  as road FROM public.integrated_roads_2021 where integrated_road_class_num <= 2 or (dra_road_name_full is not null AND dra_road_class <> 'trail');")






# dist.perm.rd <- sf::st_distance (point.ecas, roads_sf_perm) too big....


)






writeVector (point.ecas, filename = paste0 (data.dir, "ecas_cycle_time_harvest_system_points.shp"), filetype = "ESRI Shapefile", overwrite = TRUE)

#point file with cycle time and harvest system
# ogr2ogr -f PostgreSQL PG:"dbname=clus port=xxxx user=xxxx password=xxxx host=xxxx" D:\clus_data\dlvd_wood_cost\ecas_cycle_time_harvest_system_points.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI -nln ecas_cycle_time_harvest_system_points

```

# Regional Districts
Regional district boundaries for determining interior vs. coastal areas. Source: https://catalogue.data.gov.bc.ca/dataset/d1aff64e-dbfe-45a6-af97-582b7f6418b9

The following are considered interior districts:
Bulkley-Nechako, Cariboo, Central Kootenay, Central Okanagan, Columbia-Shuswap, East Kootenay, Fraser-Fort George, Kootenay Boundary, North Okanagan, Northern Rockies, Okanagan-Similkameen, Peace River, Stikine Region, Thompson-Nicola


```{r, admin bonudaries}

regional.bnds <- st_read ("D:\\clus_data\\admin_boundaries\\regional_districts_2023.shp")
regional.bnds$interior <- 0

regional.bnds$interior[regional.bnds$ADMIN_AREA == "Regional District of Bulkley-Nechako" | regional.bnds$ADMIN_AREA == "Cariboo Regional District" | regional.bnds$ADMIN_AREA == "Regional District of Fraser-Fort George" | regional.bnds$ADMIN_AREA == "Peace River Regional District" | regional.bnds$ADMIN_AREA == "Regional District of Central Okanagan" | regional.bnds$ADMIN_AREA == "Regional District of Okanagan-Similkameen" | regional.bnds$ADMIN_AREA == "Thompson-Nicola Regional District" | regional.bnds$ADMIN_AREA == "Regional District of Central Kootenay" | regional.bnds$ADMIN_AREA == "Columbia Shuswap Regional District" | regional.bnds$ADMIN_AREA == "Regional District of East Kootenay" | regional.bnds$ADMIN_AREA == "Regional District of Kootenay Boundary" | regional.bnds$ADMIN_AREA == "Regional District of North Okanagan" | regional.bnds$ADMIN_AREA == "Stikine Region (Unincorporated)"] <- 1

regional.bnds$area_ha <- regional.bnds$FEATURE_AR * 0.0001
regional.bnds$perim_km <- regional.bnds$FEATURE_LE / 1000

regional.bnds <- regional.bnds [c ("LGL_ADMIN_", "ADMIN_AREA", "ADMIN_AR_1", "WHEN_UPDAT", "area_ha", "perim_km", "interior", "geometry")]
colnames (regional.bnds) <- c ("lgl_id", "name", "abbrev", "update_date", "area_ha", "perim_km", "interior", "geometry")

st_write (regional.bnds, "D:\\scratch\\regional_districts_2023.shp")

# ogr2ogr -f PostgreSQL PG:"dbname=clus port=xxxx user=xxxx password=xxxx host=xxxx" D:\scratch\regional_districts_2023.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI -nln regional_districts_2023


```




