---
title: "fisher_wetland"
author: "Kyle"
date: "10/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library (keyring)
source(here::here("R/functions/R_Postgres.R"))
```

## Wetland and permanent open areas

This script builds the wetlands and permanent open areas layer needed for the Weir and Corbould 2010 model of relative probability of fisher occupancy.

Wetlands and other permanently open areas:
*o*	all BCLCS_LEVEL_1 = 'N' (Non-Vegetated)
*o*	BCLCS_LEVEL_2 = 'N' and LINE_7B_DISTURBANCE_HISTORY  Is Null and (CROWN_CLOSURE<6 or CROWN_CLOSURE Is Null) and (BASAL_AREA <5 or BASAL_AREA Is Null))
*o*	BCLCS_LEVEL_3 = 'W' and (BCLCS_LEVEL_5='SP' or BCLCS_LEVEL_5='OP'))
*o*	TRIM wetlands (WHSE_BASEMAPPING.TRIM_EBM_WETLANDS)


## Get Layers
```{r, layers}
vri_layer<-getSpatialQuery("SELECT 1 as wetland, shape as geom FROM veg_comp_lyr_r1_poly2019 
where bclcs_level_1 = 'N' 
OR (bclcs_level_2 = 'N' and line_7b_disturbance_history Is Null and 
	(crown_closure < 6 or crown_closure Is Null) and (basal_area < 5 or basal_area Is Null)) 
OR (bclcs_level_3 = 'W' and (bclcs_level_5='SP' or bclcs_level_5='OP'))")

#trim_layer<-getSpatialQuery("Select 1 as wetland, wkb_geometry as geom FROM  ebm_wetlnd_polygon")

rich.layer<-st_read("T:/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/fisher/perm_wetland.shp")
rich.layer$wetland<-1

#Provincial raster at hectares BC extent
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(vri_layer)$proj4string, resolution = c(100, 100), vals = 0
)
```

## Rasterize

```{r, rasterize}
#ras.vri<-fasterize::fasterize(vri_layer, ProvRast, "wetland")
#ras.vri[is.na(ras.vri[])]<-0 #Need to do this in order to add the rasters together
#ras.trim<-fasterize::fasterize(trim_layer, ProvRast, "wetland")
#ras.trim[is.na(ras.trim[])]<-0
ras.phe<-fasterize::fasterize(rich.layer, ProvRast, "wetland")

#ras.wetland<-ras.vri + ras.trim
#ras.wetland<-ras.vri
ras.wetland<-ras.phe

ras.wetland[ras.wetland[] > 1]<-1

```

## Export to postgres
```{r, postgres}
writeRaster(ras.wetland, file=paste0(here::here(),"/wetland.tif"), format="GTiff", overwrite=TRUE)#print the raster

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here::here(), '/wetland.tif -t 100x100 rast.wetland |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = FALSE)
```