---
title: "fisher_constraints"
author: "Kyle"
date: "01/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(raster)
library(sf)
library(fasterize)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))
#Get a provincial raster that follows the extent standard
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(getSpatialQuery("Select * from bc_carib_poly_20090904 limit 1"))$proj4string, resolution = c(100, 100), vals = 0)
```

## Purpose

This work documents the intital version of the constraint set needed to strategize fisher habitat requirements. The following describes the range, habitat zone, territories and critical habitat used to characterize these requirements.

**Range** includes the natural resource districts:

*	Coast: Sea to Sky, Sunshine Coast, Campbell River, North Island – Central Coast

*	North: Mackenzie, Stuart Nechako, Prince George, Coast Mountains, Nadina

* South: 100 Mile House, Cariboo – Chilcotin, Quesnel, Rocky Mountain, Selkirk, Cascades, Okanagan Shuswap, Thompson Rivers

**Habitat zone** the area that is within the range of fishers and is located in a biogeoclimatic zones or subzone. **Territory** means the area providing a female fisher with all her habitat requirements. Size requirements vary by fisher habitat zone
```{r, constraints}
knitr::kable(rbindlist(list(data.table(habitat_zone=c('sub-boreal Habitat Zone: Moist or wet'),bec_zone=c('SBS','SBS','SBS','SBS'), subzone=c('wk','mk','mm','mw'), territory_size=50), data.table(habitat_zone=c('Sub-boreal Habitat Zone: Dry'),bec_zone=c('SBS','SBS','SBS'), subzone=c('dw','dh','dk'), territory_size=25),data.table(habitat_zone=c('Dry Forest Habitat Zone'),bec_zone=c('SBPS','SBPS','SBPS','SBPS', 'IDF', 'IDF', 'IDF','IDF','IDF', 'MS','MS','MS','MS','MS','MS'), subzone=c('xc','mc','dc','mk','dk','dc','mw','dw','ww','xc','xk','dv','dm','dk','dc'), territory_size=30))))
```

**Critical habitat** includes the following categories:
```{r, categories}
knitr::kable(data.table(critical_habitat = c('Reproductive Denning Habitat', 'Resting Habitat: Rust broom sites', 'Resting Habitat: Cavity sites', 'Resting Habitat: Coarse woody habitat','Movement Habitat'),description = c('Cavities required to successfully give birth and rear young', 'Secure locations required during daily activity bouts', 'Secure locations required during daily activity bouts','Secure locations required during daily activity bouts','Required to safely travel between important habitats within and between territories')) )
```

Fisher habitat requirements must meet the following constraints:

* Within a 12-year period the net area of harvesting within a fisher territory can not exceed 10%. **This will be modelled in CLUS as per each fisher territory the age <= 12 years must be less than equal to 10%** 

* The total area each habitat category affected by the cutblocks does not fall below that values described below within the area related to the cutblocks.**This will be modelled in CLUS as per each fisher territory as area not eligible for harvesting in a given time period that meets these conditions**

```{r, cutblock_area}
knitr::kable(data.table(habitat_zone=c('sub-boreal Habitat Zone: Moist or wet'),critical_habitat=c('Reproductive Denning Habitat', 'Resting Habitat: Rust broom sites', 'Resting Habitat: Cavity sites', 'Resting Habitat: Coarse woody habitat','Movement Habitat'),attribute=c('age','age','height', 'age'), type=c('ge'), threshold=c(125,135,35,135), percentage =c(4.9, 21.9, 0.2, 28.2, 61.2)))
```

* Meet the minimum reserve tree requirements in fisher habitat zones are as follows (Insert Table here). If minimum reserve tree requirements cannot be met within the stand the deficiencies will be made up by the next largest available tree to provide for recruitment.


## Spatial Data

The spatial layer that outlines the fisher territories was provided by Rich Weir.`ogr2ogr -f PostgreSQL PG:"dbname=xxxxxx port = xxxx user=xxxxxx password=xxxxxx" D:\Data\Fisher\xxxxx.shp -overwrite -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI -lco precision=NO`. Steps to create the spatial input into forestryCLUS.

* Create a territory raster for each of the fisher ranges.

### Forest attributes from VRI

The forest attributes required from the VRI include: age, height, basal area, quadratic mean diameter, crown closure, shrub cover, species and percentages - up to 3.

#### Fisher forest attributes
This id links to polygon level attribution. 
```{r, fsher_veg_comp2019, echo = FALSE}
#Harvest locations year
layer<-getSpatialQuery("SELECT feature_id, shape FROM public.veg_comp_lyr_r1_poly2020 where bec_zone_code in ('SBS', 'IDF', 'MS', 'SBPS', 'BWBS') ")
layer2<-layer
layer2$shape<-NULL #get rid of geometry
habitat<-data.table(layer2)
```

#### Old growth
```{r ,og}
library(data.table)
library(raster)
library(sf)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))
library(fasterize)
lu<-getSpatialQuery("SELECT wkb_geometry 
FROM public.rmp_lu_sp_polygon limit 1")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)

#ogma RMP_OGMA_LEGAL_CURRENT_SVW
ogma<-getSpatialQuery("SELECT ogma_type, wkb_geometry FROM public.ogma_leg_c_polygon")
ogma$harvest<-1
ogma.ras<-fasterize::fasterize(sf= ogma, raster = ProvRast , field = "harvest")
ogma.ras[is.na(ogma.ras)]<-0

defer.ras<-raster("F:/Fisher/spatial/og/Map1_PriorityDeferral_2021_10_24.tif")
defer.ras[defer.ras[] > 3] <-0
defer.ras[defer.ras[] == 2] <-1
defer.ras[defer.ras[] == 3] <-1

writeRaster(ogma.ras, "ogma.tif")
writeRaster(defer.ras, "defer.tif")
#hab.units<-getSpatialQuery("select * from fisher_ci_boreal_units_fine")
#hab.units<-hab.units %>%
#  group_by(pop_unit) %>% 
#  summarize(geometry = st_union(wkb_geometry))


```

##### Denning
```{r, denning}
#SBS: WET
#denning.sbs.wet<- habitat[(species_cd_1 %in% c( 'ACT') | species_cd_2 %in% c( 'ACT') | (species_cd_1 %in% c('SX') & species_pct_1 == 100)) & crown_closure >= 30 & quad_diam_125 >= 28.5 & basal_area >= 29.7 & proj_age_1 >= 125 & bec_zone_code == 'SBS' & bec_subzone %in% c('wk','mk','mm','mw'), "feature_id"]

denning.sbs.wet<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where (((SPECIES_CD_1 LIKE 'AC%')  or (SPECIES_CD_2 LIKE 'AC%') or ( SPECIES_CD_3 LIKE 'AC%')) or ((SPECIES_CD_1 LIKE 'S%') and (SPECIES_CD_2 IS NULL))) and (PROJ_AGE_1>=125) and (CROWN_CLOSURE>=30) and (QUAD_DIAM_125>=28.5) and (BASAL_AREA>=29.75) and (bec_zone_code = 'SBS') and (bec_subzone in('wk','mk','mm','mw'))")

#SBS DRY: Act leading, secondary, or tertiary species (or hybrid spruce (Sx) as only species) Crown closure ≥20% QMD_125 ≥28 cm Basal area ≥28 m²/ha Stand age ≥125 years 
#denning.sbs.dry<- habitat[(species_cd_1 %in% c( 'ACT') | species_cd_2 %in% c( 'ACT') | (species_cd_1 %in% c('SX') & species_pct_1 == 100)) & crown_closure >= 20 & quad_diam_125 >= 28 & basal_area >= 28 & proj_age_1 >= 125 & bec_zone_code == 'SBS' & bec_subzone %in% c('dw','dh','dk'), "feature_id"]

denning.sbs.dry<- getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where (((SPECIES_CD_1 LIKE 'AC%')  or (SPECIES_CD_2 LIKE 'AC%') or ( SPECIES_CD_3 LIKE 'AC%')) or ((SPECIES_CD_1 LIKE 'S%') and (SPECIES_CD_2 IS NULL))) and (PROJ_AGE_1>=125) and (CROWN_CLOSURE>=20) and (QUAD_DIAM_125>=28) and (BASAL_AREA>=28) and (bec_zone_code = 'SBS') and (bec_subzone in ('dw','dh','dk'))")

#DRY FOREST: cottonwood (Act) denning stands:Act leading or secondary species.Stand age ≥135 years 
#Trembling aspen (At) denning stands:At leading or secondary species Stand age ≥135 years
#Douglas-fir (Fd) denning stands:Fd as only species, Crown closure ≥20% QMD_125 ≥34.3 cm, Stand age ≥207 years
#denning.dry.for<- habitat[((species_cd_1 %in% c( 'ACT') | species_cd_2 %in% c( 'ACT') & proj_age_1 >= 135) | (species_cd_1 %in% c( 'AT') | species_cd_2 %in% c( 'AT') & proj_age_1 >= 135)| ((species_cd_1 %in% c('FDI', 'FD') & species_pct_1 == 100) & proj_age_1 >= 207 & crown_closure >= 20 & quad_diam_125 >= 34.3)) & ((bec_zone_code == 'SBPS' & bec_subzone %in% c('xc','mc','dc','mk')) | (bec_zone_code == 'IDF' & bec_subzone %in% c('dk','dc','mw','dw','ww')) | (bec_zone_code == 'MS' & bec_subzone %in% c('xc','xk','dv','dm', 'dk', 'dc'))), "feature_id"]

denning.dry.for<-getTableQuery(
  "select feature_id from public.veg_comp_lyr_r1_poly2020 where (((SPECIES_CD_1 LIKE 'A%')  or (SPECIES_CD_2 LIKE 'A%')) and PROJ_AGE_1>=135) or (((SPECIES_CD_1 LIKE 'F%') and (SPECIES_CD_2  IS NULL)) and PROJ_AGE_1>=207 and CROWN_CLOSURE>=20 and QUAD_DIAM_125>=34.3) and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv','dm', 'dk', 'dc')))")

#BOREAL
#denning.boreal<- habitat[(((species_cd_1 %in% c( 'ACB') | species_cd_2 %in% c( 'ACB') | species_cd_3 %in% c( 'ACTB')) & proj_age_1 >= 88 & proj_height_1 >= 19 & quad_diam_125 >= 19.5) | ((species_cd_1 %in% c( 'AT') | species_cd_2 %in% c( 'AT') | species_cd_3 %in% c( 'AT')) & proj_age_1 >= 98 & proj_height_1 >= 22.8 & quad_diam_125 >= 21.3)) & ((bec_zone_code == 'BWBS' & bec_subzone %in% c('dk', 'mw', 'wk'))|(bec_zone_code == 'SBS' & bec_subzone == 'wk' & bec_variant == '2')), "feature_id"]

denning.boreal<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where (((SPECIES_CD_1 LIKE 'AC%')  or (SPECIES_CD_2 LIKE 'AC%') or ( SPECIES_CD_3 LIKE 'AC%')) and (PROJ_AGE_1>=88) and (QUAD_DIAM_125>=19.5) and (PROJ_HEIGHT_1>=19)) or (((SPECIES_CD_1 LIKE 'AT%')  or (SPECIES_CD_2 LIKE 'AT%') or ( SPECIES_CD_3 LIKE 'AT%')) and (PROJ_AGE_1>=98) and (QUAD_DIAM_125>=21.3) and (PROJ_HEIGHT_1>=22.8)) and ((bec_zone_code = 'BWBS' and bec_subzone in ('dk', 'mw', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'))")

denning<-rbindlist(list(denning.dry.for,denning.sbs.dry, denning.sbs.wet,denning.boreal))
denning<-unique(denning$feature_id)
denning.poly<-layer[layer$feature_id %in% denning,]
denning.poly$denning<-1
denning.ras <-fasterize::fasterize(denning.poly, prov.rast, field = "denning") 
writeRaster(denning.ras, file="denning.tif", format="GTiff", overwrite=TRUE)
```

##### Resting: Rust Brooms
```{r, rust_brooms}
#SBS: WET. Hybrid spruce (Sx) leading, secondary, or tertiary species. Crown closure ≥30% QMD_125 ≥22.7 cm Basal area ≥35 m²/ha Stand age ≥135 years Stand height ≥23.7 m
#rest.rust.sbs.wet<- habitat[(species_cd_1 %in% c('SX') | species_cd_2 %in% c('SX') | species_cd_3 %in% c('SX') ) & crown_closure >= 30 & quad_diam_125 >= 22.7 & basal_area >= 35 & proj_age_1 >= 135 & bec_zone_code == 'SBS' & bec_subzone %in% c('wk','mk','mm','mw'), "feature_id"]
rest.rust.sbs.wet<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((SPECIES_CD_1 LIKE 'S%')  or (SPECIES_CD_2 LIKE 'S%') or ( SPECIES_CD_3 LIKE 'S%')) and (CROWN_CLOSURE>=30) and (QUAD_DIAM_125>=22.7) and (BASAL_AREA>=35) and (PROJ_HEIGHT_1>=23.7) and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')")

#SBS DRY: Sx leading, secondary, or tertiary species Crown closure ≥25% QMD_125 ≥19.6 cm Basal area ≥32 m²/ha Stand age ≥72 years
#rest.rust.sbs.dry<- habitat[(species_cd_1 %in% c('SX') | species_cd_2 %in% c('SX') | species_cd_3 %in% c('SX') ) & crown_closure >= 25 & quad_diam_125 >= 19.6 & basal_area >= 32 & proj_age_1 >= 72 & bec_zone_code == 'SBS' & bec_subzone %in% c('dw','dh','dk'), "feature_id"]

rest.rust.sbs.dry<- getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((SPECIES_CD_1 LIKE 'S%')  or (SPECIES_CD_2 LIKE 'S%') or ( SPECIES_CD_3 LIKE 'S%')) and (PROJ_AGE_1>=72) and (CROWN_CLOSURE>=25) and (QUAD_DIAM_125>=19.6) and (BASAL_AREA>=32) and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk')")

#DRY FOREST:Sx leading, secondary, or tertiary species Crown closure ≥40% QMD_125 ≥20.1 cm Stand age ≥83 years
#rest.rust.dry.for<- habitat[(species_cd_1 %in% c('SX') | species_cd_2 %in% c('SX') | species_cd_3 %in% c('SX') ) & proj_age_1 >= 83 & crown_closure >= 40 & quad_diam_125 >= 20.1 & ((bec_zone_code == 'SBPS' & bec_subzone %in% c('xc','mc','dc','mk')) | (bec_zone_code == 'IDF' & bec_subzone %in% c('dk','dc','mw','dw','ww')) | (bec_zone_code == 'MS' & bec_subzone %in% c('xc','xk','dv','dm', 'dk', 'dc'))), "feature_id"]
rest.rust.dry.for<-getTableQuery(
  "select feature_id from public.veg_comp_lyr_r1_poly2020 where (((SPECIES_CD_1 LIKE 'S%')  or (SPECIES_CD_2 LIKE 'S%') or ( SPECIES_CD_3 LIKE 'S%')) and (PROJ_AGE_1>=83) and (CROWN_CLOSURE>=40) and (QUAD_DIAM_125>=20.1)) and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv','dm', 'dk', 'dc')))")
  
#BOREAL
#rest.rust.boreal <- habitat[(((species_cd_1 %in% c( 'SW') | species_cd_2 %in% c( 'SW') | species_cd_3 %in% c( 'SW')) & crown_closure >= 50 & proj_age_1 >= 78 & proj_height_1 >= 19 & quad_diam_125 >= 18.5) | ((species_cd_1 %in% c( 'SB') | species_cd_2 %in% c( 'SB') | species_cd_3 %in% c( 'SB')) & crown_closure >= 35 & proj_age_1 >= 68 & proj_height_1 >= 14.8 & quad_diam_125 >= 17)) & ((bec_zone_code == 'BWBS' & bec_subzone %in% c('dk', 'mw', 'wk'))|(bec_zone_code == 'SBS' & bec_subzone == 'wk' & bec_variant == '2')), "feature_id"]
rest.rust.boreal<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((((SPECIES_CD_1 LIKE 'SW%')  or (SPECIES_CD_2 LIKE 'SW%') or (SPECIES_CD_3 LIKE 'SW%')) and (PROJ_AGE_1>=78) and (CROWN_CLOSURE>=50) and (QUAD_DIAM_125>=18.5) and (PROJ_HEIGHT_1>=19) and (BASAL_AREA>=31.4 )) or (((SPECIES_CD_1 LIKE 'SB%')  or (SPECIES_CD_2 LIKE 'SB%') or ( SPECIES_CD_3 LIKE 'SB%')) and (PROJ_AGE_1>=68) and (CROWN_CLOSURE>=35) and (QUAD_DIAM_125>=17) and (PROJ_HEIGHT_1>=14.8))) and ((bec_zone_code = 'BWBS' and bec_subzone in ('dk', 'mw', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'))")

rest.rust<-rbindlist(list(rest.rust.dry.for,rest.rust.sbs.dry, rest.rust.sbs.wet, rest.rust.boreal))
rest.rust<-unique(rest.rust$feature_id)
rest.rust.poly<-layer[layer$feature_id %in% rest.rust,]
rest.rust.poly$rust<-1
rest.rust.ras <-fasterize::fasterize(rest.rust.poly, prov.rast, field = "rust") 
writeRaster(rest.rust.ras, file="rest_rust.tif", format="GTiff", overwrite=TRUE)
```

##### Resting habitat: cavity
```{r, rest_cavity}
#SBS-WET Act or At leading, secondary, or tertiary species  Crown closure ≥25% QMD_125 ≥30 cm Basal area ≥32 m²/ha Stand height ≥35 m 7
#rest.cavity.sbs.wet<- habitat[(species_cd_1 %in% c('ACT', 'AT') | species_cd_2 %in% c('ACT', 'AT') | species_cd_3 %in% c('ACT', 'AT') ) & crown_closure >= 25 & quad_diam_125 >= 30 & basal_area >= 32 & proj_height_1 >= 35 & bec_zone_code == 'SBS' & bec_subzone %in% c('wk','mk','mm','mw'), "feature_id"]
rest.cavity.sbs.wet<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((SPECIES_CD_1 LIKE 'A%')  or (SPECIES_CD_2 LIKE 'A%') or ( SPECIES_CD_3 LIKE 'A%')) and (CROWN_CLOSURE>=25) and (QUAD_DIAM_125>=30) and (BASAL_AREA>=32) and (PROJ_HEIGHT_1>=35) and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')")
  
#SBS-DRY Act or At leading, secondary, or tertiary species  Crown closure ≥25% QMD_125 ≥30 cm Basal area ≥32 m²/ha Stand height ≥35 m 
#rest.cavity.sbs.dry<- habitat[(species_cd_1 %in% c('ACT', 'AT') | species_cd_2 %in% c('ACT', 'AT') | species_cd_3 %in% c('ACT', 'AT') ) & crown_closure >= 25 & quad_diam_125 >= 30 & basal_area >= 32 & proj_height_1 >= 35 & ((bec_zone_code == 'SBPS' & bec_subzone %in% c('xc','mc','dc','mk')) | (bec_zone_code == 'IDF' & bec_subzone %in% c('dk','dc','mw','dw','ww')) | (bec_zone_code == 'MS' & bec_subzone %in% c('xc','xk','dv','dm', 'dk', 'dc'))), "feature_id"]
rest.cavity.sbs.dry<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where (((SPECIES_CD_1 LIKE 'A%')  or (SPECIES_CD_2 LIKE 'A%') or (SPECIES_CD_3 LIKE 'A%')) and PROJ_HEIGHT_1>=35 and BASAL_AREA>=32) and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk')")
  
rest.cavity<-rbindlist(list(rest.cavity.sbs.wet,rest.cavity.sbs.dry))
rest.cavity<-unique(rest.cavity$feature_id)
rest.cavity.poly<-layer[layer$feature_id %in% rest.cavity,]
rest.cavity.poly$cavity<-1
rest.cavity.ras <-fasterize::fasterize(rest.cavity.poly, prov.rast, field = "cavity") 
writeRaster(rest.cavity.ras, file="rest_cavity.tif", format="GTiff", overwrite=TRUE)
```

##### Resting: coarse woody
```{r, rest_cwd}
#SBS_WET. QMD_125 ≥22.7 cm Stand age ≥135 years  Stand height ≥23.7 m 
#rest.cwd.sbs.wet<- habitat[ quad_diam_125 >= 22.7 & proj_age_1 >= 135 & proj_height_1 >= 23.7 & bec_zone_code == 'SBS' & bec_subzone %in% c('wk','mk','mm','mw'), "feature_id"]
rest.cwd.sbs.wet<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where  (PROJ_AGE_1>=135) and (QUAD_DIAM_125>=22.7) and (PROJ_HEIGHT_1>=23.7) and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')")

  
#SBS-DRY. QMD_125 ≥22.7 cm Stand age ≥135 years Stand height ≥23.7 m 
#rest.cwd.sbs.dry<- habitat[ quad_diam_125 >= 22.7 & proj_age_1 >= 135 & proj_height_1 >= 23.7 & bec_zone_code == 'SBS' & bec_subzone %in% c('dw','dh','dk'), "feature_id"]
rest.cwd.sbs.dry<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where (PROJ_AGE_1>=135) and (CROWN_CLOSURE>=25) and (QUAD_DIAM_125>=22.7) and (PROJ_HEIGHT_1>=23.7) and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk')")
  
  
#DRY_FOR.	Hybrid spruce (Sx) or Trembling aspen (At) >25% of stand (SPECIES_PCT) Stand age ≥100 years 
#rest.cwd.dry.for<- habitat[((species_cd_1 %in% c('SX', 'SE', 'SXW', 'AT') & species_pct_1 >= 25)| (species_cd_2 %in% c('SX', 'SE', 'SXW', 'AT') & species_pct_2 >= 25) | (species_cd_3 %in% c('SX', 'SE', 'SXW', 'AT') & species_pct_3 >= 25) ) & proj_age_1 >= 100 & ((bec_zone_code == 'SBPS' & bec_subzone %in% c('xc','mc','dc','mk')) | (bec_zone_code == 'IDF' & bec_subzone %in% c('dk','dc','mw','dw','ww')) | (bec_zone_code == 'MS' & bec_subzone %in% c('xc','xk','dv','dm', 'dk', 'dc'))), "feature_id"]
rest.cwd.dry.for<-getTableQuery(
  "select feature_id from public.veg_comp_lyr_r1_poly2020 where ((((SPECIES_CD_1 LIKE 'S%' and SPECIES_PCT_1>=25) or (SPECIES_CD_2 LIKE 'S%' and SPECIES_PCT_2>=25) or (SPECIES_CD_3 LIKE 'S%' and SPECIES_PCT_3>=25)) or ((SPECIES_CD_1 LIKE 'AT%' and SPECIES_PCT_1>=25) or (SPECIES_CD_2 LIKE 'AT%' and SPECIES_PCT_2>=25) or (SPECIES_CD_3 LIKE 'AT%' and SPECIES_PCT_3>=25))) and (PROJ_AGE_1>=100)) and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv','dm', 'dk', 'dc')))")
  
  
#rest.cwd.boreal <- habitat[(crown_closure >= 60 & proj_age_1 >= 78 & proj_height_1 >= 19 & quad_diam_125 >= 18.1) & ((bec_zone_code == 'BWBS' & bec_subzone %in% c('dk', 'mw', 'wk'))|(bec_zone_code == 'SBS' & bec_subzone == 'wk' & bec_variant == '2')), "feature_id"]
rest.cwd.boreal <-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((PROJ_AGE_1>=78) and (QUAD_DIAM_125>=18.1) and (PROJ_HEIGHT_1>=19) and (CROWN_CLOSURE>=60)) and ((bec_zone_code = 'BWBS' and bec_subzone in ('dk', 'mw', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'))")
  
rest.cwd<-rbindlist(list(rest.cwd.sbs.wet,rest.cwd.sbs.dry,rest.cwd.dry.for,rest.cwd.boreal))
rest.cwd<-unique(rest.cwd$feature_id)
rest.cwd.poly<-layer[layer$feature_id %in% rest.cwd,]
rest.cwd.poly$cwd<-1
rest.cwd.ras <-fasterize::fasterize(rest.cwd.poly, prov.rast, field = "cwd") 
writeRaster(rest.cwd.ras, file="rest_cwd.tif", format="GTiff", overwrite=TRUE)
```

##### Movement habitat
```{r, movement}
#SBS_WET. Total cover ≥50% (≥30% shrub and ≥20% tree cover)
#shrub cover max 30%
#movement.sbs.wet<- habitat[ (crown_closure + shrub_crown_closure >=50 & crown_closure > 30) & bec_zone_code == 'SBS' & bec_subzone %in% c('wk','mk','mm','mw'), "feature_id"]
movement.sbs.wet<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((crown_closure + shrub_crown_closure >= 50 and crown_closure > 30) or crown_closure >= 50) and bec_zone_code = 'SBS' and bec_subzone in('wk','mk','mm','mw')")

#SBS-DRY. Total cover ≥50% (≥30% shrub and ≥20% tree cover)
#movement.sbs.dry<- habitat[ (crown_closure + shrub_crown_closure >=50 & crown_closure > 30) & bec_zone_code == 'SBS' & bec_subzone %in% c('dw','dh','dk'), "feature_id"]
movement.sbs.dry<-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((crown_closure + shrub_crown_closure >= 50 and crown_closure > 30) or crown_closure >= 50) and bec_zone_code = 'SBS' and bec_subzone in ('dw','dh','dk')")

#DRY_FOR.	Total cover ≥50% (≥30% shrub and ≥20% tree cover) 
#movement.dry.for<- habitat[(crown_closure + shrub_crown_closure >=50 & crown_closure > 30) & ((bec_zone_code == 'SBPS' & bec_subzone %in% c('xc','mc','dc','mk')) | (bec_zone_code == 'IDF' & bec_subzone %in% c('dk','dc','mw','dw','ww')) | (bec_zone_code == 'MS' & bec_subzone %in% c('xc','xk','dv','dm', 'dk', 'dc'))), "feature_id"]
movement.dry.for<-getTableQuery(
  "select feature_id from public.veg_comp_lyr_r1_poly2020 where  ((crown_closure + shrub_crown_closure >= 50 and crown_closure > 30) or crown_closure >= 50) and ((bec_zone_code = 'SBPS' and bec_subzone in('xc','mc','dc','mk')) or (bec_zone_code = 'IDF' and bec_subzone in('dk','dc','mw','dw','ww')) or (bec_zone_code = 'MS' and bec_subzone in('xc','xk','dv','dm', 'dk', 'dc')))")

#movement.boreal <- habitat[(crown_closure + shrub_crown_closure >=50 & crown_closure > 30) & ((bec_zone_code == 'BWBS' & bec_subzone %in% c('dk', 'mw', 'wk'))|(bec_zone_code == 'SBS' & bec_subzone == 'wk' & bec_variant == '2')), "feature_id"]
movement.boreal <-getTableQuery("select feature_id from public.veg_comp_lyr_r1_poly2020 where ((crown_closure + shrub_crown_closure >= 50 and crown_closure > 30) or crown_closure >= 50) and ((bec_zone_code = 'BWBS' and bec_subzone in ('dk', 'mw', 'wk')) or (bec_zone_code ='SBS' and bec_subzone = 'wk' and bec_variant ='2'))")
  
movement<-rbindlist(list(movement.sbs.wet,movement.sbs.dry,movement.dry.for,movement.boreal))
movement<-unique(movement$feature_id)
movement.poly<-layer[layer$feature_id %in% movement,]
movement.poly$movement<-1
movement.ras <-fasterize::fasterize(movement.poly, prov.rast, field = "movement") 
writeRaster(movement.ras, file="movement.tif", format="GTiff", overwrite=TRUE)
```

#### Make territories and apply density
```{r, hex_grid}

#fisher.density<-getSpatialQuery("select * from fisher_density_2004 where bgc_zone != 'BWBS'  and (bgc_zone != 'SBS' AND bgc_subzon != 'wk' AND bgc_vrt != 2);")
fisher.density<-getSpatialQuery("select * from fisher_density_2004;")

hex.grid<-st_as_sf(st_make_grid(fisher.density, cellsize = 5886, square = FALSE)) #6537 = 35 km2 territory
hex.grid$fid<-1:nrow(hex.grid)

#Get the hexagons that intersect with fisher capability high and very high - helps reduce the problem size
int.hex.dens<-st_intersects(fisher.density[fisher.density$fisher_cap %in% c('very high', 'high', 'med', 'low'),], hex.grid)

hex.grid<-hex.grid[hex.grid$fid %in% unique(unlist(int.hex.dens)),]
#View the result
plot(hex.grid)

#intersect the territories/hexagon and the fisher capability classes
hex.int.fc<-st_intersection(hex.grid, fisher.density[fisher.density$fisher_cap %in% c('very high', 'high','med', 'low'),])
hex.int.fc$area<-NULL
#estimate the area in each newly formed polygon
hex.int.fc$area<- st_area(hex.int.fc$x)

library(tidyverse)
#summarize the area by each fisher_cap class
out<-data.table(hex.int.fc %>% group_by(fid, fisher_cap) %>%
  summarise(areaFisherCap = sum(area)))

units(out$areaFisherCap)<-units::make_units(km2)

#Apply the fisher density per each fisher capability rating
#very high = (((76% + 100%)/2)/100) * 16.3 per 1000 km2 = 14.322 per 1000 km2
#high = (((51% + 75%)/2)/100) * 16.3 per 1000 km2 = 10.269 per 1000 km2
out[fisher_cap == 'very high', f_dens:= (areaFisherCap/1000)*14.344]
out[fisher_cap == 'high', f_dens:= (areaFisherCap/1000)*10.2690]
out[fisher_cap == 'med', f_dens:= (areaFisherCap/1000)*6.1640]
out[fisher_cap == 'low', f_dens:= (areaFisherCap/1000)*2.5265]

out2<-units::drop_units(out[, sum(f_dens), by = fid])
setnames(out2, 'V1', 'n_fish')

# order from highest to lowest
out3<- out2[,.SD[order(-n_fish)]]

den.ras<-raster("denning.tif")
den.ras[is.na(den.ras[])]<-0

mov.ras<-raster("movement.tif")
mov.ras[is.na(mov.ras[])]<-0

ogma.ras<-raster("ogma.tif")
ogma.ras[is.na(ogma.ras[])]<-0

defer.ras<-raster("defer.tif")
defer.ras[is.na(defer.ras[])]<-0

thlb.ras<-raster("thlb2020.tif")
thlb.ras[is.na(thlb.ras[])]<-0

#Overlap
den.overlap.ogma<-den.ras*ogma.ras
den.overlap.defer<-den.ras*defer.ras
den.overlap.defer.thlb<-den.ras*defer.ras*thlb.ras

mov.overlap.ogma<-mov.ras*ogma.ras
mov.overlap.defer<-mov.ras*defer.ras
mov.overlap.defer.thlb<-mov.ras*defer.ras*thlb.ras

#Add in habitat categgoires to break any ties
hex.grid$hab_den<- exactextractr::exact_extract(den.ras,hex.grid,c('sum'))
hex.grid$hab_rus<- exactextractr::exact_extract(raster("rest_rust.tif"),hex.grid,c('sum'))
hex.grid$hab_cav<- exactextractr::exact_extract(raster("rest_cavity.tif"),hex.grid,c('sum'))
hex.grid$hab_cwd<- exactextractr::exact_extract(raster("rest_cwd.tif"),hex.grid,c('sum'))
hex.grid$hab_mov<- exactextractr::exact_extract(mov.ras,hex.grid,c('sum'))
hex.grid$ogma<- exactextractr::exact_extract(ogma.ras,hex.grid,c('sum'))
hex.grid$defer<- exactextractr::exact_extract(defer.ras,hex.grid,c('sum'))
hex.grid$thlb<- exactextractr::exact_extract(thlb.ras,hex.grid,c('sum'))
hex.grid$den_ogma<- exactextractr::exact_extract(den.overlap.ogma,hex.grid,c('sum'))
hex.grid$den_defer<- exactextractr::exact_extract(den.overlap.defer,hex.grid,c('sum'))
hex.grid$den_defer_thlb<- exactextractr::exact_extract(den.overlap.defer.thlb,hex.grid,c('sum'))
hex.grid$mov_ogma<- exactextractr::exact_extract(mov.overlap.ogma,hex.grid,c('sum'))
hex.grid$mov_defer<- exactextractr::exact_extract(mov.overlap.defer,hex.grid,c('sum'))
hex.grid$mov_defer_thlb<- exactextractr::exact_extract(mov.overlap.defer.thlb,hex.grid,c('sum'))

#Add in relative prob of occupancy
if(FALSE){
   conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
   
  wtland<-pgGetRast(conn, c('rast','wetland'), boundary =c(1698241, 594552.1,  1525996, 503198.2))
}
###Get age
#Harvest locations year
if(FALSE){
  layer<-getSpatialQuery("SELECT shape FROM public.veg_comp_lyr_r1_poly2020 where proj_age_1 <= 12 and proj_age_1 >= 0 and bec_zone_code in ('SBS', 'IDF', 'MS', 'SBPS')")
  layer$openess<-1
  openess.ras <-fasterize::fasterize(layer, prov.rast, field = "openess")
  openess.ras[is.na(openess.ras[])]<-0
  writeRaster(openess.ras, file="openess.tif", format="GTiff", overwrite=TRUE)
}
openess.ras<-raster("openess.tif")
wetlands.ras<-raster("wetland.tif")
wetlands.ras[is.na(wetlands.ras[])]<-0
openess.ras2<- openess.ras + wetlands.ras
openess.ras2[openess.ras2[]> 1]<-1

hex.grid$openess<- exactextractr::exact_extract(openess.ras2,hex.grid,c('sum'))

#Calculate the number of habit requirement
hab_crit<-data.table(hex.grid)
hab_crit$x<-NULL
hab_crit[is.na(hab_den), hab_den:=0]
hab_crit[is.na(hab_rus), hab_rus:=0]
hab_crit[is.na(hab_cav), hab_cav:=0]
hab_crit[is.na(hab_cwd), hab_cwd:=0]
hab_crit[is.na(hab_mov), hab_mov:=0]
hab_crit[is.na(thlb), thlb:=0]
hab_crit[is.na(ogma), ogma:=0]
hab_crit[is.na(defer), defer:=0]

out4<-merge(out3, hab_crit, by.x = 'fid', by.y = 'fid', all.x = TRUE)

#out4$hab_chr<-as.integer(out4$hab_chr)
out4$n_fish<-round(out4$n_fish, 4)
out4$p_occ<-exp(-0.219*((out4$openess/3000)*100))/(1+exp(-0.219*((out4$openess/3000)*100)))/0.5

#calculate abundance
out4$abund<-out4$n_fish*out4$p_occ
sum(out4$abund)

#keycol <-c("n_fish", "hab_chr","p_occ")
#setorderv(out4, keycol, order=c(-1,-1,-1))
fish.constraints0<-merge(out4, hex.grid[1:2], by.x = 'fid', by.y = 'fid', all.x = TRUE)
fish.constraints0<-st_as_sf(fish.constraints0)
st_write(fish.constraints0, "feta_v0.shp")
```

##### summaries by different boundaries
```{r, admin_bounds}
#get hab zones
hab.units<-getSpatialQuery("select * from fisher_ci_boreal_units_fine")
boreal<-unique(unlist(st_intersects(hab.units[hab.units$pop_unit == 'Boreal',], fish.constraints0)))
columbia<-unique(unlist(st_intersects(hab.units[!hab.units$pop_unit == 'Boreal',],fish.constraints0)))

fish.constraints1<-fish.constraints0
#remove gemoetry
fish.constraints1$x<-NULL
fish.constraints1<-data.table(fish.constraints1)

fish.constraints1[n_fish >= 0.43,cap:= "vh"][n_fish >= 0.3 & n_fish < 0.43, cap:= "h"][n_fish >= 0.18 & n_fish < 0.3, cap:="m"][n_fish >= 0.07 & n_fish < 0.18, cap:= "l"][n_fish < 0.07, cap:="r"]

fish.constraints.boreal<-fish.constraints1[boreal,]
fish.constraints.boreal$n_feta<-1
fish.constraints.columbia<-fish.constraints1[columbia,]
fish.constraints.columbia$n_feta<-1

c_table<-fish.constraints.columbia[, lapply(.SD, sum, na.rm=TRUE), by = cap]
write.csv(c_table, "ctable.csv")
b_table<-fish.constraints.boreal[, lapply(.SD, sum, na.rm=TRUE), by = cap]
write.csv(b_table, "btable.csv")

```

#### TSA summaries
```{r , sum_tsa}

#Get tsa boundary
tsa<-getSpatialQuery("SeLECT * from tsa_aac_bounds")
test99<-st_intersects(tsa, fish.constraints0)

temp<-data.table(tsa = as.character(), fid = as.integer())
test22<-unique(tsa$tsa_name)
for(i in 1:59){
  temp<-rbindlist(list(temp, data.table(tsa= test22[i], fids= test99[[i]])))
}
temp<-temp[!is.na(temp$fid),]
notin2<-unique(temp$fid)

fish.constraints1<-fish.constraints0[unique(temp$fid),]

st_write(fish.constraints1, "feta_v2.shp")

test100<-st_intersects(tsa, fish.constraints1)
test22<-unique(tsa$tsa_name)

temp<-data.table(tsa = as.character(), fid = as.integer())

for(i in 1:59){
  temp<-rbindlist(list(temp, data.table(tsa= test22[i], fids= test100[[i]])))
}
temp<-temp[!is.na(temp$fid),]
notin3<-unique(temp$fid)

temp$tsa<-gsub("_TSA", " ", temp$tsa)
temp$tsa<-trimws(temp$tsa)
temp$tsa<-gsub("_", " ", temp$tsa)
temp[temp$tsa =='Onehundred Mile House',]$tsa<-'100_Mile_House'
temp[temp$tsa =='MacKenzie SW',]$tsa<-'MacKenzie'
temp[temp$tsa =='Prince George North',]$tsa<-'Prince George'
temp[temp$tsa =='Fort St John Core',]$tsa<-'Fort St John'
saveRDS(temp, "tsa_fids_v2.rds")

```


