---
title: "Protected Area Raster"
author: "Tyler Muhly"
date: "16/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose
This rmd produces a raster that specifies protected areas in British Columbia, as defined by [Environmental Reporting BC](https://www2.gov.bc.ca/gov/content/environment/research-monitoring-reporting/reporting/environmental-reporting-bc). 

It was developed to use in the CLUS scenario app to map protected areas, but could be used in the CLUS model to summarize or calculate information by protected area. C

## Spatial Data on Protected Areas
Spatial protected areas data is available from  [DataBC](https://catalogue.data.gov.bc.ca/dataset/land-designations-that-contribute-to-conservation-in-bc-spatial-data). The documentation and code for how the data was created is availabel on [GitHub](https://github.com/bcgov/land-designations-indicator). 

```{r, get herd data from BCGW}
#library (bcdata)
library (sf)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))
# poly.pa <- st_read ("C:\\Work\\caribou\\clus_data\\admin_boundaries\\protected_areas\\provincial\\designatedlands\\designatedlands.shp",  stringsAsFactors = FALSE)

poly.pa<-getSpatialQuery("SELECT * FROM designatedlands")
```

## Rasterize the Data
Here we convert the polygon to a raster, following the provincial hectares BC raster convention that we are using in the CLUS model to ensure all rasters overlap.

```{r, convert polygon to raster}
library (raster)
library (fasterize)

prov.rast <- raster::raster ( # create the standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216, 
                              xmn = 159587.5, xmx = 1881187.5, 
                              ymn = 173787.5, ymx = 1748187.5, 
                              crs = st_crs(poly.pa)$proj4string, resolution = c(100, 100), 
                              vals = 0)

poly.pa$category_int <- as.integer (as.factor (poly.pa$category)) # create an integer equivalent to category

ras.pa <- fasterize::fasterize (st_collection_extract(poly.pa, "POLYGON"), prov.rast, field = "category_int") 
# turn the polygon into a raster

plot (ras.pa) # make sure the raster looks good
```

## Create Look-up Table
Here we create a look-up table for the raster so we can translate the raster into herd names later.

```{r, create look-up table for raster}
library (data.table)

lu_protected_cat <- unique (data.table (cbind (poly.pa$category_int, poly.pa$category)))
lu_protected_cat <- lu_protected_cat [order(V1)]
setnames (lu_protected_cat, c("V1", "V2"), c("raster_integer", "category"))

```

## Commit the Data to the PostgreSQL database
Now we need to save the data. We save the raster to the raster schema and look-up table to the public schema in our postgreSQL database. 

```{r, commit data to the dbase}
conn <- DBI::dbConnect (dbDriver ("PostgreSQL"), host = keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432', user = keyring::key_get('dbuser', keyring = 'postgreSQL'), password = keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable (conn, c("public", "designatedland_vat"), value = lu_protected_cat, 
                   row.names = FALSE, overwrite = TRUE)

writeRaster (ras.pa, file = "prot_area.tif", format = "GTiff", overwrite = TRUE)

#upload to db
system ("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here (), '/R/params/prot_area.tif -t 100x100 rast.designatedlands | psql postgresql://clus_project:clus@DC052586:5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

```

