<!--
Copyright 2018 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Provincial Forest Management Objectives"
author: "Kyle Lochhead"
date: "March 15, 2019"
output: 
  html_document: 
    keep_md: yes
    toc: true
---

## Purpose

Create a provincial scale forest management objective raster(s) based on two categories: i) zonal constraints; ii) no-harvesting constraints and iii) conditional harvesting constraints. For iii) condition harvesting constraints refer to: [uwr_cond_harvest](https://github.com/bcgov/clus/blob/master/R/Params/uwr_cond_harvest.Rmd) and [wha_cond_harvest](https://github.com/bcgov/clus/blob/master/R/Params/wha_cond_harvest.Rmd). The various management objectives being considered and sources include:

```{r table_objs, echo=FALSE}
library(data.table)
knitr::kable(data.table(objective = c(
                        "Aspatial Old Growth Retention",
                        "Fisheries Sensitive Watersheds",
                        "Visual Quality Objectives"), 
             source = c("https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf",
                       "http://www.env.gov.bc.ca/wld/frpa/fsw/approved.html" ,
                       "https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/visual-resource-management"
                        )),
             caption = "Zonal Constraints")

knitr::kable(data.table(objective = c(
                        "Wildlife Habitat Areas",
                        "Ungulate Winter Range",
                        "Wildlife Management Areas",
                        "Visual Quality Objectives",
                        "Spatial Old Growth Management Areas"),
             source = c(
               "http://www.env.gov.bc.ca/cgi-bin/apps/faw/wharesult.cgi?search=show_approved",
               "http://www.env.gov.bc.ca/wld/frpa/uwr/approved_uwr.html",
               "https://catalogue.data.gov.bc.ca/dataset/tantalis-wildlife-management-areas",
               "https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/visual-resource-mgmt/vrm_a_guide_to_visual_quality_objectives.pdf",
               "https://catalogue.data.gov.bc.ca/dataset/old-growth-management-areas-legal-current"
             )),
             caption = "Harvesting Constraint")
```

>Note: these management objectives are not inclusive of all objectives - but rather they are a set of common constraints considered in timber supply review. Remaining detailed layers indicating either zonal or harvesting constraints will be incorporated at a later time

## Biodiversity Emphasis Options - Zonal Constraints

Biodiversity Emphasis Options (BEO) are defined during landscape level planning, typically an a landscape unit or on BEC zones (natural disturbance types) within a landscape unit. If no landscape unit has been designated for an area, or an emphasis option has not been assigned for a particular landscape unit, the default is that the area is managed using the lower biodiversity emphasis option. see [Biodiversity Guidebook](https://www.for.gov.bc.ca/ftp/hfp/external/!publish/FPC%20archive/old%20web%20site%20contents/fpc/fpcguide/BIODIV/chap1.htm#bid)

#### Get data  
```{r zoneStep1, echo=FALSE}
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

lu<-getSpatialQuery("SELECT lu_id, 
case 
	when beo = 'High' then 1 
	when beo = 'Intermediate' then 2
	else 3 
end as beo2, wkb_geometry 
FROM public.rmp_lu_sp_polygon 
WHERE beo <> 'Multiple' AND rt_dt Is NULL Order by gis_ch_dt")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)

#Rasterize the bidodiversity emphasis options
beo.ras<-fasterize::fasterize(sf= lu, raster = ProvRast , field = "beo2")
luid.ras<-fasterize::fasterize(sf= lu, raster = ProvRast , field = "lu_id")

#Get the natural disturbance types
ndt<-getSpatialQuery("SELECT  wkb_geometry,
case
  WHEN natural_disturbance = 'NDT1' then 1
  WHEN natural_disturbance = 'NDT2' then 2
  WHEN natural_disturbance = 'NDT3' then 3
  WHEN natural_disturbance = 'NDT4' then 4
  else 5
end as ndt from public.bec_zone")

#Rasterize the NDT
ndt.ras<-fasterize::fasterize(sf= ndt, raster = ProvRast , field = "ndt")

#Get the bec zones and assign them a key called zone
bec<- getSpatialQuery("SELECT wkb_geometry, 
case
  WHEN zone = 'BWBS' then 1
  WHEN zone = 'CDF' then 2
  WHEN zone = 'CWH' then 3
  WHEN zone = 'ESSF' then 4
  WHEN zone = 'ICH' then 5
  WHEN zone = 'IDF' then 6
  WHEN zone = 'MH' then 7
  WHEN zone = 'MS' then 8
  WHEN zone = 'PP' then 9
  WHEN zone = 'SBPS' then 10
  WHEN zone = 'SBS' then 11
  WHEN zone = 'SWB' then 12
end as zone FROM public.bec_zone") #Alpine Tundra and Bunchgrass are not included?

#Rasterize the BEC zone (key for BEC zones)
bec.ras<-fasterize::fasterize(sf= bec, raster = ProvRast , field = "zone")

rm(lu,bec,ndt) # free some memory
gc()# Clean up

#Make a stack raster with all the information needed for BEO contraints
ogm<-stack(bec.ras, ndt.ras, luid.ras, beo.ras)
names(ogm)<-c("BEC", "NDT", "LU_ID", "BEO")
raster::plot(ogm) #plot the stack
```

#### Make unique zones within Landscape Units

```{r zoneStep2, echo=FALSE}
library(data.table)
library(here)

#------------------------------------
#Biodiversity Emphasis Options on Age
#------------------------------------
ogm.table<-data.table(as.data.frame(ogm)) #ogn is the stacked raster of the BEO
ogm.table[, id := seq_len(.N)]#assign a unique id for each pixel

rm(ogm, bec.ras, beo.ras, ndt.ras, luid.ras) #clear up some memory
gc() # clean up

#concactenate and join in old growth percentage
print(head(ogm.table))
ogm.table[, ogm := paste0(BEC, '_', NDT, '_', BEO)]
#print(ogm.table[!is.na(BEC)])#CHECK

#Create oldgrowth look up table. Note for ndt 3 in the BWBS there is a further difference between conifer and deciduous. I omitted this level of precision and used the most conservative one -- the conifer percentage . This adds an extra 2-3 percent!!! see Table 3 in https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf

NDT1<-data.table(BEC = c("CWH", "CWH", "CWH", 
                         "ICH", "ICH", "ICH",
                         "ESSF","ESSF","ESSF",
                         "MH",  "MH",  "MH"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          28, 19, 19,
                          28, 19, 19), AGE = 250, NDT = 1, BEO = 1:3)

NDT2<-data.table(BEC = c("CWH", "CWH", "CWH",
                         "CDF", "CDF", "CDF", 
                         "ICH", "ICH", "ICH",
                         "SBS", "SBS", "SBS",
                         "ESSF","ESSF","ESSF",
                         "SWB", "SWB", "SWB"),
                 p_OGR= c(13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9), AGE = 250, NDT = 2, BEO = 1:3)

NDT3<-data.table(BEC = c("BWBS","BWBS","BWBS", 
                         "SBPS","SBPS","SBPS",
                         "SBS", "SBS", "SBS",
                         "MS",  "MS",  "MS",
                         "ESSF","ESSF","ESSF",
                         "ICH", "ICH", "ICH",
                         "CWH", "CWH", "CWH"),
                 p_OGR= c(19, 13, 13,
                          10, 7, 7,
                          16, 11, 11,
                          21, 14, 14,
                          21, 14, 14,
                          21, 14, 14,
                          16, 11, 11), 
                 AGE = c(100, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140), NDT = 3, BEO = 1:3)

NDT4<-data.table(BEC = c("ICH", "ICH", "ICH",
                         "IDF", "IDF", "IDF",
                         "PP",  "PP",  "PP"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          19, 13, 13), AGE = 250, NDT = 4, BEO = 1:3)

p_OGR<-rbind(NDT1, NDT2, NDT3, NDT4) #this is the lookup for geting the percentage of old growth required for retention by bec and ndt

#Create a value attribute table which assigns an integer key called BEC2 to each BEC zone
vat<-data.table(BEC  = 
                c('BWBS', 'CDF', 'CWH', 'ESSF', 'ICH', 'IDF', 'MH', 'MS', 'PP','SBPS', 'SBS', 'SWB'),
                BEC2 = 1:12)

p_OGR<-merge(x=p_OGR, y=vat, by.x= "BEC", by.y= "BEC") # join vat and p_OGR to get BEC2 key
p_OGR[, ogm := paste0(BEC2, '_', NDT, '_', BEO)] # concatenate to get a unique constraint
p_OGR<-p_OGR[, c(2:3,7)] #Keep only the unique constraint, the p_OGR and age threshold

setkey(ogm.table, ogm) # assign a data.table key thats the unique constraint for joining
setkey(p_OGR, ogm)# assign a data.table key thats the unique constraint for joining

ogm.final<-merge(x=p_OGR, y=ogm.table, by="ogm", all.y=TRUE) # merge the constraint with each spatial landscape unit

rm(ogm.table) # clear memory
gc() # clean up
#----Checking----
#print(ogm.final[!is.na(p_OGR)])
#out<-data.frame(ogm.final[order(id)])
#print(head(out[]))
#ogm.ras<-ProvRast
#ogm.ras[]<-out[,2]
#writeRaster(ogm.ras, file="ogm_ret_thres.tif", format="GTiff", overwrite=TRUE)
rm(ogm.ras, out, NDT1, NDT2, NDT3, NDT4, vat, p_OGR)
gc()

ogm.final[, zone := .GRP, by=.(LU_ID,BEC,NDT)] #Creates a unique id for each zone grouped by Lu_ID, BEC and NDT
#remove zones that are ndt5 or other wise do not have a ogr, age
print(head(ogm.final[is.na(AGE),]))
ogm.final[is.na(AGE), zone:=NA]
out<-data.frame(ogm.final[order(id)])
gc()
zone.ras<-ProvRast
zone.ras[]<-out[,9] #assign the zone to each pixel


writeRaster(zone.ras, file=paste0(here(),"/zone_beo.tif"), format="GTiff", overwrite=TRUE)#print the raster
rm(zone.ras, out)

# Upload to postgres database
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_beo.tif -t 100x100 rast.zone_cond_beo |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = FALSE)

library(RPostgreSQL)
ogm.final[zone == 2435,]
zone_beo_table<-setDT(ogm.final)[, .SD[which.max(AGE)], by=zone]

zone_beo_table<-zone_beo_table[,c(1,3:4, 6)]
zone_beo_table[, reference_zone := 'rast.zone_beo']
zone_beo_table[, variable := 'age']
zone_beo_table[, type := 'ge']

setnames(zone_beo_table, c("zoneid", "percentage", 
                  "threshold","ndt", "reference_zone", 
                  "variable", "type"))
zone_beo_table[, ndt := as.integer(ndt)]
df<-as.data.frame(zone_beo_table)
df$label<-'beo' #TODO: label this is as high/I/L ?

#Upload the constraint table to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("public", "zone_beo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(zone_beo_table, df, ogm.final)
gc()

```

# Fisheries Sensitive Areas and Equivalent Clearcut Area
```{r, fsw}
#Fisheries Sensitive Areas
fsw<-getSpatialQuery("SELECT fsw_id, wkb_geometry FROM public.wcp_f_s_ws_polygon")

#Rasterize the fisher sensitive areas
fsw.ras<-fasterize::fasterize(sf= fsw, raster = ProvRast , field = "fsw_id")
writeRaster(fsw.ras, file=paste0(here(),"/zone_fsw.tif"), format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_fsw.tif -t 100x100 rast.zone_cond_fsw |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(fsw.ras)
gc()
df<-as.data.frame(fsw)
df$type<-'le'
df$variable<-'eca'
df$threshold<-25
df$reference_zone<-'rast.zone_cond_fsw'
df$percentage<-100
df$ndt<-as.integer(0)
df<-df[,c(1,3:8)]
colnames(df) <- c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")
df$zoneid<-as.integer(df$zoneid)#assign integer
df$label<-'fsw'

#upload the constraint table for FSW to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("public", "zone_fsw"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)
```

# Visual Quality Constraints
```{r, vqo}
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

lu<-getSpatialQuery("SELECT wkb_geometry 
FROM public.rmp_lu_sp_polygon limit 1")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)
#Visual Quality Constraints on height
#see https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/visual-resource-mgmt/vrm_a_guide_to_visual_quality_objectives.pdf
vqo<-getSpatialQuery("SELECT 
case
  WHEN evqo_cd = 'P' then 0
  WHEN evqo_cd = 'R' then 2
  WHEN evqo_cd = 'PR' then 7
  WHEN evqo_cd = 'M' then 18
  WHEN evqo_cd = 'MM' then 30
end as vqo, 
case
WHEN evqo_cd = 'P' then 0 else vli_id
end as vli_id, wkb_geometry FROM public.rec_vlnd_polygon WHERE evqo_cd <> 'SCO'")

vqo.ras<-fasterize::fasterize(sf= vqo, raster = ProvRast , field = "vli_id")
writeRaster(vqo.ras, file=paste0(here(),"/zone_vqo.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_vqo.tif -t 100x100 rast.zone_cond_vqo |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

df<-as.data.frame(vqo)
df<-df[,1:2]
df$type<-'le'
df$variable<-'height'
df$threshold<-5
df$reference_zone<-'rast.zone_vqo'
df$ndt<-as.integer(0)
colnames(df) <- c("percentage", "zoneid", "type", "variable", "threshold", "reference_zone", "ndt") # the vqo column gets labeled as percentage
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'vqo'

df<-data.table(unique(df))# get rid of the multiple zoneid = 0 )
df[zoneid == 0, type := 'nh']

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "zone_vqo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(df, fsw, vqo.ras, vqo)
gc()
```

# Spatial No Harvesting Constraints 

These are areas that can contribute to zonal constraints but cannot harvest within these boundaries. For instance a spatial OGMA constraint refers to a mapped out spatial location for no harvesting. This area may be within a larger BEO that would include these pixels as part of the landscape level age constraint.

The steps involved in the harvesting constraints:
1. Get spatial old growth management areas (OGMA) - legal - no harvesting
2. Get Parks and Protected Areas (parks)

```{r hc_step1, echo=FALSE}
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")
library(here)
lu<-getSpatialQuery("SELECT wkb_geometry 
FROM public.rmp_lu_sp_polygon limit 1")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)

#ogma
ogma<-getSpatialQuery("SELECT ogma_type, wkb_geometry FROM public.ogma_legal_polygon WHERE rt_dt Is NOT NULL")
ogma$harvest<-1
ogma.ras<-fasterize::fasterize(sf= ogma, raster = ProvRast , field = "harvest")
ogma.ras[is.na(ogma.ras)]<-0

#parks
parks<-getSpatialQuery("SELECT wkb_geometry FROM public.ta_pep_svw_polygon")
parks$harvest<-1
parks.ras<-fasterize::fasterize(sf= parks, raster = ProvRast , field = "harvest")
parks.ras[is.na(parks.ras)]<-0

#conservancies
conserv<-getSpatialQuery("SELECT wkb_geometry FROM public.ta_ca_svw_polygon")
conserv$harvest<-1
conserv.ras<-fasterize::fasterize(sf= conserv, raster = ProvRast , field = "harvest")
conserv.ras[is.na(conserv.ras)]<-0

nharv.ras<- ogma.ras + parks.ras+ conserv.ras
plot(nharv.ras)
nharv.ras[nharv.ras[] == 0 ] <- NA
nharv.ras[nharv.ras[] > 0 ] <- 0
writeRaster(nharv.ras, file=paste0(here(),"/nharv.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/nharv.tif -t 100x100 rast.zone_cond_nharv | psql -d clus'), show.output.on.console = FALSE, invisible = TRUE)



df<-data.frame(type='nh', variable= '', threshold=0, reference_zone='rast.zone_nharv',
ndt=0,percentage = 0, zoneid =0)
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'parks or OGMA'
df$ndt<-as.integer(0)
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "zone_nharv"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(uwr.ras, wha.ras ,ogma.ras , pres.ras , parks.ras, parks, ogma, pres, wha, uwr)
gc()
```

### Community Watersheds
Water in community watersheds is a value identified under the Forest and Range Practices Act. From the Kamloops TSR:  The approach was to ensure that no more than an equivalent clear-cut area (ECA) of 20% of the gross land base that applies to the upper 60% of all community watersheds and that standard management practices applies to the lower 40% of the watershed. The upper 60% (snow pack area) is considered hydrologically recovered upon
reaching 9 metres in height and the lower 40% being a 3 metre green up height. Therefore, averaging the above, in each community watershed the modelled practice was that no more than 25.2% of the gross area in a community watershed could be less than 6.6 metres in height.
```{r, com_water}
com_wat<-getSpatialQuery("SELECT * FROM com_ws_pub_polygon;")

#Rasterize the community watersheds
com_wat.ras<-fasterize::fasterize(sf= com_wat, raster = ProvRast , field = "ogc_fid")
writeRaster(com_wat.ras, file=paste0(here::here(),"/zone_cw.tif"), format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here::here(), '/zone_cw.tif -t 100x100 rast.zone_cond_cw |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(com_wat.ras)
gc()
df<-as.data.frame(com_wat)
df$zoneid<-df$ogc_fid
df$type<-'le'
df$variable<-'eca'
df$threshold<-20
df$reference_zone<-'rast.zone_cond_cw'
df$percentage<-100
df$ndt<-as.integer(0)
df<-df[,c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")]
colnames(df) <- c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")
df$zoneid<-as.integer(df$zoneid)#assign integer
df$label<-'cw'

#upload the constraint table for CW to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("public", "zone_cw"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)
```

# Setting PostgreSQL Inheritance
PostgreSQL implements table inheritance. See [here]("https://www.postgresql.org/docs/9.5/ddl-inherit.html")

```{r zoneCleanUp, echo=FALSE, eval=FALSE}
#----------------------------
#Inheritability in PostgreSQL
#----------------------------
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

dbExecute(conn, "CREATE TABLE IF NOT EXISTS zone_constraints (zoneid integer, reference_zone text, ndt integer, variable text, threshold double precision, type text, percentage double precision)")

dbExecute(conn, "ALTER TABLE zone_nharv INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_wha INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_beo INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_fsw INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_uwr INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_cw INHERIT zone_constraints")#Note from uwr_cond_harvest.rmd
dbDisconnect(conn)
```
