<!--
Copyright 2018 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Provincial Forest Management Objectives"
author: "Kyle Lochhead"
date: "March 15, 2019"
output: 
  html_document: 
    keep_md: yes
    toc: true
---

## Purpose

Create a provincial scale forest management objective raster(s) based on two categories: i) zonal constraints; ii) no-harvesting constraints and iii) conditional harvesting constraints. For iii) condition harvesting constraints refer to: [uwr_cond_harvest](https://github.com/bcgov/clus/blob/master/R/Params/uwr_cond_harvest.Rmd) and [wha_cond_harvest](https://github.com/bcgov/clus/blob/master/R/Params/wha_cond_harvest.Rmd). The various management objectives being considered and sources include:

```{r table_objs, echo=FALSE}
library(dplyr)
library(data.table)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(getSpatialQuery("select * from bec_zone limit 1;"))$proj4string, resolution = c(100, 100), vals = 0
)

knitr::kable(data.table(objective = c(
                        "Aspatial Old Growth Retention",
                        "Fisheries Sensitive Watersheds",
                        "Visual Quality Objectives"), 
             source = c("https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf",
                       "http://www.env.gov.bc.ca/wld/frpa/fsw/approved.html" ,
                       "https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/visual-resource-management"
                        )),
             caption = "Zonal Constraints")

knitr::kable(data.table(objective = c(
                        "Wildlife Habitat Areas",
                        "Ungulate Winter Range",
                        "Wildlife Management Areas",
                        "Visual Quality Objectives",
                        "Spatial Old Growth Management Areas"),
             source = c(
               "http://www.env.gov.bc.ca/cgi-bin/apps/faw/wharesult.cgi?search=show_approved",
               "http://www.env.gov.bc.ca/wld/frpa/uwr/approved_uwr.html",
               "https://catalogue.data.gov.bc.ca/dataset/tantalis-wildlife-management-areas",
               "https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/visual-resource-mgmt/vrm_a_guide_to_visual_quality_objectives.pdf",
               "https://catalogue.data.gov.bc.ca/dataset/old-growth-management-areas-legal-current"
             )),
             caption = "Harvesting Constraint")
```

>Note: these management objectives are not inclusive of all objectives - but rather they are a set of common constraints considered in timber supply review. Remaining detailed layers indicating either zonal or harvesting constraints will be incorporated at a later time

## Watershed units
```{r}
wau<-getSpatialQuery("select * from wau;")
wau.ras<-fasterize::fasterize(wau, raster = ProvRast, field="ogc_fid")
writeRaster(wau.ras, "wau.tif")

zone.wau<-data.table(zoneid =  unique(wau.ras[]), reference_zone = 'rast.zone_cond_wau', ndt =0, variable= 'eca', threshold = 100, type = 'le', percentage = 100, multi_condition =NA, denom =NA, start = 0, stop = 250, label = 'watershed_analysis')
zone.wau<-zone.wau[!is.na(zone.wau$zoneid),]

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
DBI::dbWriteTable(conn, c("zone", "zone_wau"), value= zone.wau, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

```

## Biodiversity Emphasis Options - Zonal Constraints

Biodiversity Emphasis Options (BEO) are defined during landscape level planning, typically an a landscape unit or on BEC zones (natural disturbance types) within a landscape unit. If no landscape unit has been designated for an area, or an emphasis option has not been assigned for a particular landscape unit, the default is that the area is managed using the lower biodiversity emphasis option. see [Biodiversity Guidebook](https://www.for.gov.bc.ca/ftp/hfp/external/!publish/FPC%20archive/old%20web%20site%20contents/fpc/fpcguide/BIODIV/chap1.htm#bid)

The targets for each of the LUS is broken down by bec zone, subzone and variant. The specifc seral distributions needed are found in https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf and Caribou Chilcotin land use plan.


#### Get data  
```{r zoneStep1, echo=FALSE}

#get the data from rmp_lg_pl_polygon --> legal planning polygons
## Princ george biodiversity order
pg_bio<-getSpatialQuery("SELECT atrb1_val as bec_label, atrb2_val as ndu, atrb5_val as unit, atrb3_val as district,  atrb7_val as old_targ, wkb_geometry FROM rmp_lg_pl_polygon where slrp_name = 'Prince George Timber Supply Area (TSA) Legal Order - Landscape Biodiversity Objective Order - Extent'")
pg_bio<-pg_bio %>% group_by(unit, old_targ) %>% summarize(wkb_geometry = st_union(wkb_geometry))
pg_bio$unit<-as.factor(pg_bio$unit)
pg_bio.ras<-fasterize::fasterize(sf= pg_bio, raster = ProvRast , field = "unit")
pg_bio.table<-data.table(unit = pg_bio$unit, old_targ = pg_bio$old_targ)
pg_bio.table<-pg_bio.table[, pgbio_id := seq_len(.N)]
pg_bio.table<-pg_bio.table[!is.na(unit),]


##CCLUP
qu<-st_read("F:/Fisher/early_seral_rating/dqu.shp")
hm<-st_read("F:/Fisher/early_seral_rating/dmh.shp")
cc<-st_read("F:/Fisher/early_seral_rating/dcc.shp")

cclup.lut<-rbindlist(list(data.table(link_key = qu$link_key) , data.table(link_key = hm$link_key), data.table(link_key = cc$link_key)))
cclup.lut$cclup_id<-1:nrow(cclup.lut)
cclup.qu<-merge(qu, cclup.lut, by.x = "link_key",by.y = "link_key", all.x =T)
cclup.hm<-merge(hm, cclup.lut, by.x = "link_key",by.y = "link_key", all.x =T)
cclup.cc<-merge(cc, cclup.lut, by.x = "link_key",by.y = "link_key", all.x =T)

cclup.qu.ras<-fasterize::fasterize(sf= cclup.qu, raster = ProvRast , field = "cclup_id")
cclup.hm.ras<-fasterize::fasterize(sf= cclup.hm, raster = ProvRast , field = "cclup_id")
cclup.cc.ras<-fasterize::fasterize(sf= cclup.cc, raster = ProvRast , field = "cclup_id")


#Get the landscape units
lu<-getSpatialQuery("SELECT lu_id, lu_name,
case 
	when beo = 'High' then 1 
	when beo = 'Intermediate' then 2
	when beo = 'Low' then 3
	when beo = 'NA' then 3
end as beo, wkb_geometry 
FROM public.rmp_lu_sp_polygon 
WHERE beo <> 'Multiple' AND rt_dt Is NULL Order by gis_ch_dt")
lu[is.na(lu$beo),]$beo<-3 # assign low to all that are blank

luid.ras<-fasterize::fasterize(sf= lu, raster = ProvRast , field = "lu_id")

#Get the bec
bec<-getSpatialQuery("SELECT  wkb_geometry, zone, subzone, variant, bec_zone.map_label, b.bec_id,
case
  WHEN natural_disturbance = 'NDT1' then 1
  WHEN natural_disturbance = 'NDT2' then 2
  WHEN natural_disturbance = 'NDT3' then 3
  WHEN natural_disturbance = 'NDT4' then 4
  else 5
end as ndt from public.bec_zone 
LEFT JOIN (select ROW_NUMBER() 
		   OVER(ORDER BY map_label ASC) as bec_id, map_label  
		   from (select distinct(map_label) as map_label from bec_zone) as a) as b
on b.map_label = bec_zone.map_label
where zone in ('CWH','ICH','ESSF','MH','CDF','SBS','SWB','BWBS','SBPS','MS','IDF','PP','BG') and natural_disturbance in ('NDT1','NDT2','NDT3','NDT4');")

bec.ras<-fasterize::fasterize(sf= bec, raster = ProvRast , field = "bec_id")

#Get the forested landbase
treed<-getSpatialQuery("sELECT  shape, 1 as treed, 
case when species_cd_1 in ('AX', 'EP', 'ACB', 'EA', 'AC', 'ACT', 'AT', 'E') and bec_zone_code = 'BWBS'
then 1 else 0 end as dec
from public.veg_comp_lyr_r1_poly2021 
where bclcs_level_2 = 'T' 
and site_index >= 5")

#Rasterize the treed
treed.ras<-fasterize::fasterize(sf= treed, raster = ProvRast , field = "treed")
dec.ras<-fasterize::fasterize(sf= treed, raster = ProvRast , field = "dec")

#beo.table<-data.table(lu_id = luid.ras[], bec_id=bec.ras[], pgbio_id = pg_bio.ras[], treed=treed.ras[], dec = dec.ras[], fir=fir.ras[], pine = pine.ras[])

beo.table<-data.table(lu_id = luid.ras[], bec_id=bec.ras[], pgbio_id = pg_bio.ras[], treed=treed.ras[], dec = dec.ras[], cclup_qu_id=cclup.qu.ras[], cclup_cc_id=cclup.cc.ras[], cclup_hm_id=cclup.hm.ras[])

beo.table<-beo.table[, pixelid := seq_len(.N)]
beo.table<-beo.table[!is.na(treed),]

rm(treed.ras, dec.ras, bec.ras, luid.ras, pg_bio.ras, cclup.cc.ras, cclup.qu.ras, cclup.hm.ras)
gc()

#get labels for pg bio order
beo.table<-merge(beo.table, pg_bio.table[,c("pgbio_id", "unit")], by.x = "pgbio_id", by.y = "pgbio_id", all.x =T)

#get labels for landscape units
luid.table<-st_drop_geometry(lu)
beo.table<-merge(beo.table, luid.table, by.x = "lu_id", by.y = "lu_id", all.x =T)

#get labels for bec
bec.table<-st_drop_geometry(bec)
bec.table<-unique(bec.table) #get rid of duplicates that result from non contigous zones
beo.table<-merge(beo.table, bec.table, by.x = "bec_id", by.y = "bec_id", all.x =T)
beo.table<-beo.table[!is.na(bec_id),]
beo.table<-beo.table[!is.na(lu_id),]

#get labels for cclup
beo.table[, cclup_id:=cclup_cc_id][!is.na(cclup_qu_id), cclup_id:=cclup_qu_id][!is.na(cclup_hm_id), cclup_id:=cclup_hm_id]
beo.table[, c("cclup_cc_id", "cclup_hm_id", "cclup_qu_id"):=NULL]

beo.table<-merge(beo.table, cclup.lut, by.x = "cclup_id", by.y = "cclup_id", all.x =T)

```

#### Biodiversity guide book
```{r, guidebook}
#this is the guidance from biodiversity guide book                      
beo.table<-beo.table[, key_beo:=paste0(lu_name, "_", beo, "_", ndt, "_", zone)] 
beo.table<-beo.table[zone == 'BWBS' & dec == 1, key_beo:=paste0(lu_name, "_", beo, "_", ndt, "_", zone,"_", "D")] 
beo.table<-beo.table[zone == 'BWBS' & dec == 0, key_beo:=paste0(lu_name, "_", beo, "_", ndt, "_", zone,"_", "C")]
```

#### CCLUP
```{r, cclup}
beo.table<-beo.table[!is.na(cclup_id), key_beo:=link_key]
```

#### Prince george biodiversity order
```{r, pg_bio_order}
beo.table<-beo.table[!is.na(unit), key_beo:= unit]
```

### Create the spatial zones for the BEO 
```{r, spat_zones_beo}
beo.lut<-data.table(key_beo = unique(beo.table$key_beo))
beo.lut<-beo.lut[, id_beo := seq_len(.N)]
saveRDS(beo.lut, "beo_lut.rds")

#merge back to beo.table and write the id to raster
beo.table<-merge(beo.table, beo.lut, by.x = "key_beo", by.y = "key_beo", all.x =T)
saveRDS(beo.table, "beo_table.rds")
```

### Create constraints raster
```{r}
beo.table<-readRDS("beo_table.rds")
beo.lut<-readRDS("beo_lut.rds")

# CCLUP
qu<-st_read("F:/Fisher/early_seral_rating/dqu.shp")
hm<-st_read("F:/Fisher/early_seral_rating/dmh.shp")
cc<-st_read("F:/Fisher/early_seral_rating/dcc.shp")

cclup.lut<-rbindlist(list(data.table(link_key = qu$link_key) , data.table(link_key = hm$link_key), data.table(link_key = cc$link_key)))
cclup.lut$cclup_id<-1:nrow(cclup.lut)
cclup.qu<-st_drop_geometry(merge(qu, cclup.lut, by.x = "link_key",by.y = "link_key", all.x =T))
cclup.hm<-st_drop_geometry(merge(hm, cclup.lut, by.x = "link_key",by.y = "link_key", all.x =T))
cclup.cc<-st_drop_geometry(merge(cc, cclup.lut, by.x = "link_key",by.y = "link_key", all.x =T))

cclup.table<-rbindlist(list(cclup.qu[,c("link_key", "analysis_g", "BGC_LABEL", "ZONE", "NATURAL_DI", "legal_earl", "legal_ea_1", "legal_ea_2", "legal_mato", "legal_ma_1", "legal_ma_2", "legal_old_", "legal_ol_1", "legal_ol_2")],cclup.cc[,c("link_key", "analysis_g", "BGC_LABEL","ZONE", "NATURAL_DI","legal_earl", "legal_ea_1", "legal_ea_2", "legal_mato", "legal_ma_1", "legal_ma_2", "legal_old_", "legal_ol_1", "legal_ol_2")],cclup.hm[,c("link_key", "analysis_g", "BGC_LABEL","ZONE","NATURAL_DI", "legal_earl", "legal_ea_1", "legal_ea_2", "legal_mato", "legal_ma_1", "legal_ma_2", "legal_old_", "legal_ol_1", "legal_ol_2")]))

cclup.table[,"lu":=substr(analysis_g, 5, nchar(analysis_g))]
cclup_beo<-read.csv("lu_beo_cclup.csv")
cclup.table<-merge(cclup.table, cclup_beo, by.x = "lu", by.y = "lu", all.x =T)

beo.lut.info<-merge(beo.lut, cclup.table, by.x = "key_beo", by.y = "link_key", all.x = TRUE)

# PG bio order
pg_bio<-getSpatialQuery("SELECT atrb1_val as bec_label, atrb2_val as ndu, atrb5_val as unit, atrb3_val as district,  atrb7_val as old_targ, wkb_geometry FROM rmp_lg_pl_polygon where slrp_name = 'Prince George Timber Supply Area (TSA) Legal Order - Landscape Biodiversity Objective Order - Extent'")
pg_bio<-pg_bio %>% group_by(unit, old_targ) %>% summarize(wkb_geometry = st_union(wkb_geometry))
pg_bio$unit<-as.factor(pg_bio$unit)
pg_bio.table<-data.table(unit = pg_bio$unit, old_targ = pg_bio$old_targ)
pg_bio.table<-pg_bio.table[, pgbio_id := seq_len(.N)]
pg_bio.table<-pg_bio.table[!is.na(unit),]
beo.lut.info<-merge(beo.lut.info, pg_bio.table, by.x = "key_beo", by.y = "unit", all.x = TRUE)

beo.lut.info<-beo.lut.info[!is.na(pgbio_id), lu_name:= key_beo][!is.na(pgbio_id), old_targ:= as.numeric(old_targ)*100][!is.na(pgbio_id), O_targ:=paste0(">", old_targ)][!is.na(pgbio_id), O_targ_num:=old_targ][!is.na(pgbio_id), O_def:=">140"][!is.na(pgbio_id), O_def_num:=140]  
# the Moist Interior – plateau sub-unit – all biogeoclimatic variants;D2-D7, E2-E5, A7-A13
# the Omineca Valley – SBSdk, SBSdw3, BWBSdk1, SBSmc2, SBSmk1; E12, E14, E15, E16
# the McGregor Plateau – SBS mk1 and SBSmh; A3
beo.lut.info[key_beo %in% c('D2','D3','D4','D5','D6','D7','E2','E3','E4', 'E5', 'A7', 'A8', 'A9', 'A10', 'A11', 'A12', 'A13', 'E12', 'E14', 'E15', 'E16', 'A3'), O_def:=">120"]
beo.lut.info[key_beo %in% c('D2','D3','D4','D5','D6','D7','E2','E3','E4', 'E5', 'A7', 'A8', 'A9', 'A10', 'A11', 'A12', 'A13', 'E12', 'E14', 'E15', 'E16', 'A3'), O_def_num:=120] 


#Create oldgrowth look up table.see Table 3 in https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf
beo.lut.info[is.na(lu_name) & is.na(analysis_g), c("lu_name", "beo", "ndt", "map_label", "species") := tstrsplit(key_beo, "_", fixed=TRUE)][!is.na(analysis_g), ndt:=substr(NATURAL_DI,4,4)][!is.na(analysis_g), map_label:=ZONE]

bg.beo<-data.table(read.csv("seral_targets_BiodiversityGuidebook.csv", header =T,sep=","))#This is stored in /R/Params/
setnames(bg.beo, "ï..bec", "bec")
bg.beo<-bg.beo[species == "", species:=NA][, ndt:=as.character(ndt)]

beo.lut.info<-merge(beo.lut.info, bg.beo, by.x =c("ndt", "beo", "map_label", "species"), by.y =c("ndt", "beo", "bec", "species"), all.x=T)

##add ndt types to pg bio order: https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/omineca-region/princegeorge-biodiversity-order/biodiversity_order.pdf
# unit, >1000, 101 -1000, 51 – 100, <50; labels
# McGregor Plateau 40 45 5 10; A2-4,
# Moist Interior - Mountain 40 30 10 20; A5, A6, D1, E1
# Moist Interior - Plateau 70 20 5 5; A7-13, D2-D7, E2-5
# Northern Boreal Mountains 60 30 5 5; A1, E6-8
# Omineca - Mountain 40 30 10 20, E9-11
# Omineca - Valley 60 30 5 5, E12-17
# Wet Mountain 10 60 10 20; A14-17
# Wet Trench - Mountain 10 60 10 20; A18-21
# Wet Trench - Valley 10 60 10 20; A22-25
beo.lut.info[lu_name %in% c('A2', 'A3', 'A4'), ndt :=6][lu_name %in% c('A5', 'A6', 'D1', 'E1'), ndt :=7][lu_name %in% c('A7', 'A8', 'A9', 'A10', 'A11', 'A12', 'A13', 'D2', 'D3', 'D4', 'D5','D6', 'D7', 'E2', 'E3', 'E4', 'E5'), ndt :=8][lu_name %in% c('A1', 'E6', 'E7', 'E8'), ndt :=9][lu_name %in% c('E9', 'E10', 'E11'), ndt :=10][lu_name %in% c('E12', 'E13', 'E14', 'E15', 'E16', 'E17'), ndt :=11][lu_name %in% c('A14', 'A15', 'A16', 'A17'), ndt :=12][lu_name %in% c('A18', 'A19', 'A20', 'A21'), ndt :=13][lu_name %in% c('A22', 'A23', 'A24', 'A25'), ndt :=14]


### Get the targets and definitions
#setnames(beo.lut3, c("MpO_targ.x", "O_targ.x", "M_def.x", "O_def.x", "MpO_targ_num.x", "O_targ_num.x", "M_def_num.x", "O_def_num.x"), c("MpO_targ", "O_targ", "M_def", "O_def", "MpO_targ_num","O_targ_num", "M_def_num", "O_def_num"))
pg.old<-beo.lut.info[!is.na(O_targ.x), c("id_beo", "O_targ_num.x","O_def_num.x", "ndt", "key_beo")]
setnames(pg.old, c("id_beo", "ndt", "key_beo", "O_targ_num.x", "O_def_num.x"), c("id_beo", "ndt", "key_beo", "O_targ_num.y", "O_def_num.y"))
cclup.old<-beo.lut.info[!is.na(legal_old_), c("id_beo", "ndt", "key_beo", "beo", "legal_old_","legal_ol_1","legal_ol_2", "O_def_num.y")]
cclup.old[beo == 1, O_targ_num.y:=legal_ol_2][beo == 2, O_targ_num.y:=legal_ol_1][beo == 3, O_targ_num.y:=legal_old_]
cclup.old<-cclup.old[!is.na(O_targ_num.y), c("id_beo", "ndt", "key_beo", "O_targ_num.y", "O_def_num.y")][!(O_targ_num.y == "na"), ]
bgb.old<-beo.lut.info[!is.na(lu_name) & !is.na(beo),c("id_beo", "ndt", "key_beo", "O_targ_num.y", "O_def_num.y")]
old.zone<-rbindlist(list(pg.old, cclup.old, bgb.old), use.names =TRUE)

#Mature plus Old
cclup.mat<-beo.lut.info[!is.na(legal_mato), c("id_beo", "ndt", "key_beo", "beo", "legal_mato","legal_ma_1","legal_ma_2", "M_def_num")]
cclup.mat[beo == 1, MpO_targ_num:=legal_ma_2][beo == 2, MpO_targ_num:=legal_ma_1][beo == 3, MpO_targ_num:=legal_mato]
cclup.mat<-cclup.mat[!is.na(MpO_targ_num), c("id_beo", "ndt", "key_beo", "MpO_targ_num", "M_def_num")][!(MpO_targ_num == "na"), ]
bgb.mat<-beo.lut.info[!is.na(lu_name) & !is.na(beo),c("id_beo", "ndt", "key_beo", "MpO_targ_num", "M_def_num")]
mat.zone<-rbindlist(list(cclup.mat, bgb.mat), use.names =TRUE)

#EARLY
cclup.early<-beo.lut.info[!is.na(legal_earl), c("id_beo", "ndt", "key_beo", "beo", "legal_earl","legal_ea_1","legal_ea_2")]
cclup.early[beo == 1, E_targ_num:=legal_ea_2][beo == 2, E_targ_num:=legal_ea_1][beo == 3, E_targ_num:=legal_earl]
cclup.early<-cclup.early[!is.na(E_targ_num), c("id_beo", "ndt", "key_beo", "E_targ_num" )][!(E_targ_num == "na"), ]
early.zone<-cclup.early

# ALL id_bep
id.beos<-unique(old.zone$id_beo)

omitted<-beo.lut.info[!(id_beo %in% id.beos),]
#write.csv(omitted, "mannualy_edit_cclup_beos2.csv")
additions<-data.table(read.csv("mannualy_edit_cclup_beos.csv"))
setnames(additions, c("O_targ_num", "O_def_num", "E_targ"),c("O_targ_num.y", "O_def_num.y","E_targ_num"), skip_absent = T)

old.zone<-rbindlist(list(old.zone, additions[,c("id_beo", "ndt", "key_beo", "O_targ_num.y", "O_def_num.y")]), use.names = T)
mat.zone<-rbindlist(list(mat.zone, additions[,c("id_beo", "ndt", "key_beo", "MpO_targ_num", "M_def_num")]), use.names = T)
early.add<-additions[!is.na(additions$E_targ_num), ]
early.zone<-rbindlist(list(early.zone, early.add[,c("id_beo", "ndt", "key_beo", "E_targ_num" )]), use.names = T)


#### Create Raster
beo.ras<-ProvRast
beo.ras[beo.table$pixelid]<-beo.table$id_beo

beo.ras[beo.table[!(id_beo %in% old.zone$id_beo),]$pixelid]<-0
if(FALSE){
writeRaster(beo.ras, "beo.tif", overwrite =TRUE)
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here::here(), '/R/params/beo.tif -t 100x100 rast.zone_cond_beo_pg_cclup |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = FALSE)
}
```


```{r, create_table}

#Create constraints table

zone_beo_table.old<-data.table(zoneid = old.zone$id_beo, reference_zone = 'rast.zone_cond_beo_pg_cclup', ndt =old.zone$ndt, variable= 'age', threshold = old.zone$O_def_num, type = 'ge', percentage = old.zone$O_targ_num, multi_condition =NA, denom =NA, start = 0, stop = 250, label = paste0('old_seral_beo_', old.zone$key_beo))

zone_beo_table.mpo<-data.table(zoneid = mat.zone$id_beo, reference_zone = 'rast.zone_cond_beo_pg_cclup', ndt =mat.zone$ndt, variable= 'age', threshold = mat.zone$M_def_num, type = 'ge', percentage = mat.zone$MpO_targ_num, multi_condition =NA, denom =NA, start = 0, stop = 250, label = paste0('mature_seral_beo_', mat.zone$key_beo))

zone_beo_table.early<-data.table(zoneid =  early.zone$id_beo, reference_zone = 'rast.zone_cond_beo_pg_cclup', ndt =early.zone$ndt, variable= 'age', threshold = 40, type = '', percentage = early.zone$E_targ_num, multi_condition =NA, denom =NA, start = 0, stop = 250, label = paste0('early_seral_beo_', early.zone$key_beo))

#fill in the NAs
zone_beo_table.old[is.na(threshold), threshold:= min(zone_beo_table.old$threshold, na.rm =T)][is.na(percentage), percentage:= min(zone_beo_table.old$percentage, na.rm =T)]

zone_beo_table.mpo[is.na(threshold), threshold:= min(zone_beo_table.mpo$threshold, na.rm =T)][is.na(percentage), percentage:= min(zone_beo_table.mpo$percentage, na.rm =T)]

zone_beo_table.early[is.na(threshold), threshold:= min(zone_beo_table.early$threshold, na.rm =T)][is.na(percentage), percentage:= min(zone_beo_table.early$percentage, na.rm =T)]


zone_beo_table<-rbindlist(list(zone_beo_table.old, zone_beo_table.mpo, zone_beo_table.early))
zone_beo_table$threshold<-as.numeric(zone_beo_table$threshold)
zone_beo_table$percentage<-as.numeric(zone_beo_table$percentage)
zone_beo_table$multi_condition<-as.character(zone_beo_table$multi_condition)
zone_beo_table$denom<-as.character(zone_beo_table$denom)
zone_beo_table$start<-as.integer(zone_beo_table$start)
zone_beo_table$stop<-as.integer(zone_beo_table$stop)
zone_beo_table$ndt<-as.integer(zone_beo_table$ndt)

#Upload the constraint table to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("zone", "zone_beo_pg_cclup"), value= zone_beo_table, row.names = FALSE, overwrite = TRUE) 
dbExecute(conn, "ALTER TABLE zone.zone_beo_pg_cclup ALTER COLUMN denom  TYPE varchar;")
dbExecute(conn, "ALTER TABLE zone.zone_beo_pg_cclup INHERIT zone.constraints;")
dbDisconnect(conn)

```

# Fisheries Sensitive Areas and Equivalent Clearcut Area
```{r, fsw}
#Fisheries Sensitive Areas
fsw<-getSpatialQuery("SELECT fsw_id, wkb_geometry FROM public.wcp_f_s_ws_polygon")

#Rasterize the fisher sensitive areas
fsw.ras<-fasterize::fasterize(sf= fsw, raster = ProvRast , field = "fsw_id")
writeRaster(fsw.ras, file=paste0(here(),"/zone_fsw.tif"), format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_fsw.tif -t 100x100 rast.zone_cond_fsw |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(fsw.ras)
gc()
df<-as.data.frame(fsw)
df$type<-'le'
df$variable<-'eca'
df$threshold<-25
df$reference_zone<-'rast.zone_cond_fsw'
df$percentage<-100
df$ndt<-as.integer(0)
df<-df[,c(1,3:8)]
colnames(df) <- c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")
df$zoneid<-as.integer(df$zoneid)#assign integer
df$label<-'fsw'

#upload the constraint table for FSW to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("zone", "zone_fsw"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)
```

# Visual Quality Constraints
```{r, vqo}
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

lu<-getSpatialQuery("SELECT wkb_geometry 
FROM public.rmp_lu_sp_polygon limit 1")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)
#Visual Quality Constraints on height
#see https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/visual-resource-mgmt/vrm_a_guide_to_visual_quality_objectives.pdf
vqo<-getSpatialQuery("SELECT 
case
  WHEN evqo_cd = 'P' then 0
  WHEN evqo_cd = 'R' then 2
  WHEN evqo_cd = 'PR' then 7
  WHEN evqo_cd = 'M' then 18
  WHEN evqo_cd = 'MM' then 30
end as vqo, 
case
WHEN evqo_cd = 'P' then 0 else vli_id
end as vli_id, wkb_geometry FROM public.rec_vlnd_polygon WHERE evqo_cd <> 'SCO'")

vqo.ras<-fasterize::fasterize(sf= vqo, raster = ProvRast , field = "vli_id")
writeRaster(vqo.ras, file=paste0(here(),"/zone_vqo.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_vqo.tif -t 100x100 rast.zone_cond_vqo |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

df<-as.data.frame(vqo)
df<-df[,1:2]
df$type<-'le'
df$variable<-'height'
df$threshold<-5
df$reference_zone<-'rast.zone_vqo'
df$ndt<-as.integer(0)
colnames(df) <- c("percentage", "zoneid", "type", "variable", "threshold", "reference_zone", "ndt") # the vqo column gets labeled as percentage
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'vqo'

df<-data.table(unique(df))# get rid of the multiple zoneid = 0 )
df[zoneid == 0, type := 'nh']

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("zone", "zone_vqo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(df, fsw, vqo.ras, vqo)
gc()
```

# Spatial No Harvesting Constraints 

These are areas that can contribute to zonal constraints but cannot harvest within these boundaries. For instance a spatial OGMA constraint refers to a mapped out spatial location for no harvesting. This area may be within a larger BEO that would include these pixels as part of the landscape level age constraint.

The steps involved in the harvesting constraints:
1. Get spatial old growth management areas (OGMA) - legal - no harvesting
2. Get Parks and Protected Areas (parks)

```{r hc_step1, echo=FALSE}
source (paste0(here::here(),"/R/functions/R_Postgres.R"))
library(here)
lu<-getSpatialQuery("SELECT wkb_geometry 
FROM public.rmp_lu_sp_polygon limit 1")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)

#ogma
ogma<-getSpatialQuery("SELECT ogma_type, wkb_geometry FROM public.ogma_legal_polygon WHERE rt_dt Is NOT NULL")
ogma$harvest<-1
ogma.ras<-fasterize::fasterize(sf= ogma, raster = ProvRast , field = "harvest")
ogma.ras[is.na(ogma.ras)]<-0

#parks
parks<-getSpatialQuery("SELECT wkb_geometry FROM public.ta_pep_svw_polygon")
parks$harvest<-1
parks.ras<-fasterize::fasterize(sf= parks, raster = ProvRast , field = "harvest")
parks.ras[is.na(parks.ras)]<-0

#conservancies
conserv<-getSpatialQuery("SELECT wkb_geometry FROM public.ta_ca_svw_polygon")
conserv$harvest<-1
conserv.ras<-fasterize::fasterize(sf= conserv, raster = ProvRast , field = "harvest")
conserv.ras[is.na(conserv.ras)]<-0

nharv.ras<- ogma.ras + parks.ras+ conserv.ras
plot(nharv.ras)
nharv.ras[nharv.ras[] == 0 ] <- NA
nharv.ras[nharv.ras[] > 0 ] <- 0
writeRaster(nharv.ras, file=paste0(here(),"/nharv.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/nharv.tif -t 100x100 rast.zone_cond_nharv | psql -d clus'), show.output.on.console = FALSE, invisible = TRUE)



df<-data.frame(type='nh', variable= '', threshold=0, reference_zone='rast.zone_cond_nharv',
ndt=0,percentage = 0, zoneid =0)
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'parks or OGMA'
df$ndt<-as.integer(0)
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("zone", "zone_nharv"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(uwr.ras, wha.ras ,ogma.ras , pres.ras , parks.ras, parks, ogma, pres, wha, uwr)
gc()
```

### Community Watersheds
Water in community watersheds is a value identified under the Forest and Range Practices Act. From the Kamloops TSR:  The approach was to ensure that no more than an equivalent clear-cut area (ECA) of 20% of the gross land base that applies to the upper 60% of all community watersheds and that standard management practices applies to the lower 40% of the watershed. The upper 60% (snow pack area) is considered hydrologically recovered upon
reaching 9 metres in height and the lower 40% being a 3 metre green up height. Therefore, averaging the above, in each community watershed the modelled practice was that no more than 25.2% of the gross area in a community watershed could be less than 6.6 metres in height.
```{r, com_water}
com_wat<-getSpatialQuery("SELECT * FROM com_ws_pub_polygon;")

#Rasterize the community watersheds
com_wat.ras<-fasterize::fasterize(sf= com_wat, raster = ProvRast , field = "ogc_fid")
writeRaster(com_wat.ras, file=paste0(here::here(),"/zone_cw.tif"), format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here::here(), '/zone_cw.tif -t 100x100 rast.zone_cond_cw |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(com_wat.ras)
gc()
df<-as.data.frame(com_wat)
df$zoneid<-df$ogc_fid
df$type<-'le'
df$variable<-'eca'
df$threshold<-20
df$reference_zone<-'rast.zone_cond_cw'
df$percentage<-100
df$ndt<-as.integer(0)
df<-df[,c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")]
colnames(df) <- c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage", "ndt")
df$zoneid<-as.integer(df$zoneid)#assign integer
df$label<-'cw'

#upload the constraint table for CW to the db
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

 
DBI::dbWriteTable(conn, c("zone", "zone_cw"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)
```

# Setting PostgreSQL Inheritance
PostgreSQL implements table inheritance. See [here]("https://www.postgresql.org/docs/9.5/ddl-inherit.html")

```{r zoneCleanUp, echo=FALSE, eval=FALSE}
#----------------------------
#Inheritability in PostgreSQL
#----------------------------
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

dbExecute(conn, "CREATE TABLE IF NOT EXISTS zone.constraints (zoneid integer, reference_zone text, ndt integer, variable text, threshold double precision, type text, percentage double precision)")

dbExecute(conn, "ALTER TABLE zone_nharv INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone_wha INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone_beo INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone_fsw INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone_uwr INHERIT zone.constraints")
dbExecute(conn, "ALTER TABLE zone_cw INHERIT zone.constraints")#Note from uwr_cond_harvest.rmd
dbDisconnect(conn)
```
