<!--
Copyright 2018 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Provincial Forest Management Objectives"
author: "Kyle Lochhead"
date: "March 15, 2019"
output: 
  html_document: 
    keep_md: yes
---

## Purpose

Create a provincial scale forest management objective raster(s) based on two categories: i) zonal constraints and ii) harvesting constraints. The various management objectives being considered and sources include:

```{r table_objs, echo=FALSE}
library(data.table)
knitr::kable(data.table(objective = c(
                        "Aspatial Old Growth Retention",
                        "Fisheries Sensitive Watersheds",
                        "Visual Quality Objectives"), 
             source = c("https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/policies-guides/old_growth_order_may18th_final.pdf",
                       "http://www.env.gov.bc.ca/wld/frpa/fsw/approved.html" ,
                       "https://www2.gov.bc.ca/gov/content/industry/forestry/managing-our-forest-resources/visual-resource-management"
                        )),
             caption = "Zonal Constraints")

knitr::kable(data.table(objective = c(
                        "Wildlife Habitat Areas",
                        "Ungulate Winter Range",
                        "Wildlife Management Areas",
                        "Visual Quality Objectives",
                        "Spatial Old Growth Management Areas"),
             source = c(
               "http://www.env.gov.bc.ca/cgi-bin/apps/faw/wharesult.cgi?search=show_approved",
               "http://www.env.gov.bc.ca/wld/frpa/uwr/approved_uwr.html",
               "https://catalogue.data.gov.bc.ca/dataset/tantalis-wildlife-management-areas",
               "https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/visual-resource-mgmt/vrm_a_guide_to_visual_quality_objectives.pdf",
               "https://catalogue.data.gov.bc.ca/dataset/old-growth-management-areas-legal-current"
             )),
             caption = "Harvesting Constraint")
```

>Note: these management objectives are not inclusive of all objectives - but rather they are a set of common constraints considered in timber supply review. Remaining detailed layers indicating either zonal or harvesting constraints will be incorporated at a later time

## Zonal Constraints

The steps in this process involve:

1. Get data
a)the BEC, NDT, BEO and LU_ID, fs,vqo 
i) clean the landscape units (removing overlapping geometry)
ii) Create a raster of biodiversity emphasis options
iii) Create a raster of natural disturbance type from provincial BEC map
b) Merge the layers into a data.table
c) Create a unique identifier for each of the zone constraints 

>If no landscape unit has been designated for an area, or an emphasis option has not been assigned for a landscape unit, the default is that the area is managed using the lower biodiversity emphasis option.[Biodiversity Guidebook](https://www.for.gov.bc.ca/ftp/hfp/external/!publish/FPC%20archive/old%20web%20site%20contents/fpc/fpcguide/BIODIV/chap1.htm#bid)

2. Make unique zones
a) Create a raster of the percentage threshold for old-growth.
b) Create a raster of the zones for fisheries sensitve watershed
c) Create a raster of the zones for visula quality
d) Create a look up table for the respective thresholds
e) Write the rasters and lookups into postgres

### Step 1: Get data  
```{r zoneStep1, echo=FALSE}
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")
pswrd<-'clus'
lu<-getSpatialQuery("SELECT lu_id, 
case 
	when beo = 'High' then 1 
	when beo = 'Intermediate' then 2
	else 3 
end as beo2, wkb_geometry 
FROM public.rmp_lu_sp_polygon 
WHERE beo <> 'Multiple' AND rt_dt Is NULL Order by gis_ch_dt")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)

beo.ras<-fasterize::fasterize(sf= lu, raster = ProvRast , field = "beo2")
luid.ras<-fasterize::fasterize(sf= lu, raster = ProvRast , field = "lu_id")

#writeRaster(beo, file="beo.tif", format="GTiff", overwrite=TRUE)
#writeRaster(luid, file="luid.tif", format="GTiff", overwrite=TRUE)

ndt<-getSpatialQuery("SELECT  wkb_geometry,
case
  WHEN natural_disturbance = 'NDT1' then 1
  WHEN natural_disturbance = 'NDT2' then 2
  WHEN natural_disturbance = 'NDT3' then 3
  WHEN natural_disturbance = 'NDT4' then 4
  else 5
end as ndt from public.bec_zone")
ndt.ras<-fasterize::fasterize(sf= ndt, raster = ProvRast , field = "ndt")
#writeRaster(ndt.ras, file="ndt.tif", format="GTiff", overwrite=TRUE)

bec<- getSpatialQuery("SELECT wkb_geometry, 
case
  WHEN zone = 'BWBS' then 1
  WHEN zone = 'CDF' then 2
  WHEN zone = 'CWH' then 3
  WHEN zone = 'ESSF' then 4
  WHEN zone = 'ICH' then 5
  WHEN zone = 'IDF' then 6
  WHEN zone = 'MH' then 7
  WHEN zone = 'MS' then 8
  WHEN zone = 'PP' then 9
  WHEN zone = 'SBPS' then 10
  WHEN zone = 'SBS' then 11
  WHEN zone = 'SWB' then 12
end as zone FROM public.bec_zone")
bec.ras<-fasterize::fasterize(sf= bec, raster = ProvRast , field = "zone")

rm(lu,bec,ndt)
gc()

ogm<-stack(bec.ras, ndt.ras, luid.ras, beo.ras)
names(ogm)<-c("BEC", "NDT", "LU_ID", "BEO")
raster::plot(ogm)

#Visual Quality Constraints on height
vqo_all<-getSpatialQuery("SELECT evqo_cd, wkb_geometry FROM public.rec_vlnd_polygon WHERE evqo_cd <> 'SCO'")

#Fisheries Sensitive Areas
fsw<-getSpatialQuery("SELECT fsw_id, wkb_geometry FROM public.wcp_f_s_ws_polygon")

```

### Step 2: Make unique zones

```{r zoneStep2, echo=FALSE}
library(data.table)
library(here)

#------------------------------------
#Biodiversity Emphasis Options on Age
#------------------------------------

ogm.table<-data.table(as.data.frame(ogm))
ogm.table[, id := seq_len(.N)]

rm(ogm, bec.ras, beo.ras, ndt.ras, luid.ras)
gc()

#concactenate and join in old growth percentage
print(head(ogm.table))
ogm.table[, ogm := paste0(BEC, '_', NDT, '_', BEO)]
#print(ogm.table[!is.na(BEC)])#CHECK

#Create oldgrowth table to look up
NDT1<-data.table(BEC = c("CWH", "CWH", "CWH", 
                         "ICH", "ICH", "ICH",
                         "ESSF","ESSF","ESSF",
                         "MH",  "MH",  "MH"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          28, 19, 19,
                          28, 19, 19), AGE = 250, NDT = 1, BEO = 1:3)

NDT2<-data.table(BEC = c("CWH", "CWH", "CWH",
                         "CDF", "CDF", "CDF", 
                         "ICH", "ICH", "ICH",
                         "SBS", "SBS", "SBS",
                         "ESSF","ESSF","ESSF",
                         "SWB", "SWB", "SWB"),
                 p_OGR= c(13, 9, 9,
                          13, 9, 9,
                          13, 9, 9,
                          13, 9, 9), AGE = 250, NDT = 2, BEO = 1:3)

NDT3<-data.table(BEC = c("BWBS","BWBS","BWBS", 
                         "SBPS","SBPS","SBPS",
                         "SBS", "SBS", "SBS",
                         "MS",  "MS",  "MS",
                         "ESSF","ESSF","ESSF",
                         "ICH", "ICH", "ICH",
                         "CWH", "CWH", "CWH"),
                 p_OGR= c(9999, 9999, 9999,
                          10, 7, 7,
                          16, 11, 11,
                          21, 14, 14,
                          21, 14, 14,
                          21, 14, 14,
                          16, 11, 11), 
                 AGE = c(100, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140,
                         140, 140, 140), NDT = 3, BEO = 1:3)

NDT4<-data.table(BEC = c("ICH", "ICH", "ICH",
                         "IDF", "IDF", "IDF",
                         "PP",  "PP",  "PP"),  
                 p_OGR= c(19, 13, 13,
                          19, 13, 13,
                          19, 13, 13), AGE = 250, NDT = 4, BEO = 1:3)

p_OGR<-rbind(NDT1, NDT2, NDT3, NDT4)
vat<-data.table(BEC  = 
                c('BWBS', 'CDF', 'CWH', 'ESSF', 'ICH', 'IDF', 'MH', 'MS',       'PP','SBPS', 'SBS', 'SWB'),
                BEC2 = 1:12)

p_OGR<-merge(x=p_OGR, y=vat, by.x= "BEC", by.y= "BEC")
p_OGR[, ogm := paste0(BEC2, '_', NDT, '_', BEO)]
p_OGR<-p_OGR[, c(2:3,7)]

setkey(ogm.table, ogm)
setkey(p_OGR, ogm)

ogm.final<-merge(x=p_OGR, y=ogm.table, by="ogm", all.y=TRUE)

rm(ogm.table)
gc()
print(ogm.final[!is.na(p_OGR)])
#out<-data.frame(ogm.final[order(id)])
#print(head(out[]))
#ogm.ras<-ProvRast
#ogm.ras[]<-out[,2]
#writeRaster(ogm.ras, file="ogm_ret_thres.tif", format="GTiff", overwrite=TRUE)
rm(ogm.ras, out, NDT1, NDT2, NDT3, NDT4, vat, p_OGR)
gc()

ogm.final[, zone := .GRP, by=.(LU_ID,BEC,NDT)] #Creates a unique id for each zone grouped by Lu_ID, BEC and NDT
out<-data.frame(ogm.final[order(id)])
gc()
zone.ras<-ProvRast
zone.ras[]<-out[,9]

writeRaster(zone.ras, file=paste0(here(),"/zone_beo.tif"), format="GTiff", overwrite=TRUE)#print the raster
rm(zone.ras, out)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_beo.tif -t 100x100 rast.zone_beo | psql -d clus'), show.output.on.console = FALSE, invisible = FALSE)

library(RPostgreSQL)
zone_beo_table<-setDT(ogm.final)[, .SD[which.max(AGE)], by=zone]
zone_beo_table<-zone_beo_table[,c(1,3:4)]
zone_beo_table[, reference_zone := 'rast.zone_beo']
zone_beo_table[, variable := 'age']
zone_beo_table[, type := 'ge']

df<-as.data.frame(zone_beo_table)
colnames(df) <- c("zoneid", "percentage", 
                  "threshold", "reference_zone", 
                  "variable", "type")

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host='localhost', dbname = 'clus', port='5432' ,user='app_user' ,password=pswrd)
DBI::dbWriteTable(conn, c("public", "zone_beo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(zone_beo_table, df, ogm.final)
gc()

#-----------------------------------------------------
#Fisheries Sensitive Areas on Equivalent Clearcut Area
#-----------------------------------------------------

fsw.ras<-fasterize::fasterize(sf= fsw, raster = ProvRast , field = "fsw_id")
writeRaster(fsw.ras, file=paste0(here(),"/zone_fsw.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_fsw.tif -t 100x100 rast.zone_fsw | psql -d clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(fsw.ras)
gc()
df<-as.data.frame(fsw)
df$type<-'le'
df$variable<-'eca'
df$threshold<-25
df$reference_zone<-'rast.zone_fsw'
df$percentage<-25
df<-df[,c(1,3:7)]
colnames(df) <- c("zoneid", "type", "variable", "threshold", "reference_zone", "percentage")
df$zoneid<-as.integer(df$zoneid)#assign integer

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host='localhost', dbname = 'clus', port='5432' ,user='app_user' ,password=pswrd)
DBI::dbWriteTable(conn, c("public", "zone_fsw"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

#------------------------------------
#Visual Quality Constraints On Height
#------------------------------------

vqo<-getSpatialQuery("SELECT 
case
  WHEN evqo_cd = 'R' then 1
  WHEN evqo_cd = 'PR' then 2
  WHEN evqo_cd = 'M' then 3
  WHEN evqo_cd = 'MM' then 4
end as vqo, 
vli_id, wkb_geometry FROM public.rec_vlnd_polygon WHERE evqo_cd <> 'SCO' AND evqo_cd <> 'P'")

plot(vqo["vqo"])

vqo.ras<-fasterize::fasterize(sf= vqo, raster = ProvRast , field = "vli_id")
writeRaster(vqo.ras, file=paste0(here(),"/zone_vqo.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_vqo.tif -t 100x100 rast.zone_vqo | psql -d clus'), show.output.on.console = FALSE, invisible = TRUE)

df<-as.data.frame(vqo)
df<-df[,1:2]
df$type<-'le'
df$variable<-'height'
df$threshold<-5
df$reference_zone<-'rast.zone_vqo'
colnames(df) <- c("percentage", "zoneid", "type", "variable", "threshold", "reference_zone")
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host='localhost', dbname = 'clus', port='5432' ,user='app_user' ,password=pswrd)
DBI::dbWriteTable(conn, c("public", "zone_vqo"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

rm(df, fsw, vqo.ras, vqo)
gc()
```

PostgreSQL implements table inheritance. See [here]("https://www.postgresql.org/docs/9.5/ddl-inherit.html")

```{r zoneCleanUp, echo=FALSE}
#----------------------------
#Inheritability in PostgreSQL
#----------------------------
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host='localhost', dbname = 'clus', port='5432' ,user='app_user' ,password=pswrd)
dbExecute(conn, "CREATE TABLE IF NOT EXISTS zone_constraints (zoneid integer, reference_zone text, variable text, threshold double precision, type text, percentage double precision)")

dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_beo INHERIT zone_constraints")
dbExecute(conn, "ALTER TABLE zone_fsw INHERIT zone_constraints")

dbDisconnect(conn)
```

# Harvesting Constraints

The steps involved in the harvesting constraints:
1. Get spatial old growth management areas (OGMA) - legal - no harvesting
2. Get Visual Quality Objectives (VQO) - P - preserved
3. Get Ungulate Winter Range (UWR) - no harvesting
4. Get Wildlife Habitat Areas (WHA)
5. Get Parks and Protected Areas (parks)

```{r hc_step1, echo=FALSE}

pres<-vqo_all[vqo_all$evqo_cd == "P",]
pres$harvest<-1
pres.ras<-fasterize::fasterize(sf= pres, raster = ProvRast , field = "harvest")
pres.ras[is.na(pres.ras)]<-0

ogma<-getSpatialQuery("SELECT ogma_type, wkb_geometry FROM public.ogma_legal_polygon WHERE rt_dt Is NOT NULL")
ogma$harvest<-1
ogma.ras<-fasterize::fasterize(sf= ogma, raster = ProvRast , field = "harvest")
ogma.ras[is.na(ogma.ras)]<-0

wha<-getSpatialQuery("SELECT wkb_geometry FROM public.wcp_whaply_polygon WHERE harvest = 'NO HARVEST ZONE'")
wha$harvest<-1
wha.ras<-fasterize::fasterize(sf= wha, raster = ProvRast , field = "harvest")
wha.ras[is.na(wha.ras)]<-0

uwr<-getSpatialQuery("SELECT wkb_geometry FROM public.wcp_uwr_sp_polygon WHERE harvest = 'NO HARVEST ZONE'")
uwr$harvest<-1
uwr.ras<-fasterize::fasterize(sf= uwr, raster = ProvRast , field = "harvest")
uwr.ras[is.na(uwr.ras)]<-0

parks<-getSpatialQuery("SELECT wkb_geometry FROM public.ta_pep_svw_polygon")
parks$harvest<-1
parks.ras<-fasterize::fasterize(sf= parks, raster = ProvRast , field = "harvest")
parks.ras[is.na(parks.ras)]<-0

nharv.ras<-uwr.ras + wha.ras + ogma.ras + pres.ras + parks.ras

nharv.ras[nharv.ras[] > 0 ] <- 1
writeRaster(nharv.ras, file=paste0(here(),"/nharv.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/nharv.tif -t 100x100 rast.zone_nharv | psql -d clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(uwr.ras, wha.ras ,ogma.ras , pres.ras , parks.ras, parks, ogma, pres, wha, uwr)
gc()


```

