<!--
Copyright 2018 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Rasterize public layers"
author: "Kyle Lochhead"
date: "April 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

The clus database is oraganized into a set of [schemas](https://www.postgresql.org/docs/9.1/ddl-schemas.html) or logical groupings that correspond to the origin and type of data structure.

* `public` layers downloaded from data bc.
* `rast` all compiled raster layers.
* `caribou` all caribou outputs.

> This .rmd documents the rasterization process of `public` layers into the `rast` schema

## Layers being rasterized

Following table is a list of vector layers that are rasterized at 1 ha resoultion for the province using the [hectares BC](https://hectaresbc.org/app/habc/HaBC.html) extent which follows the [raster standard](https://www2.gov.bc.ca/assets/gov/government/services-for-government-and-broader-public-sector/information-technology-services/standards-files/raster_standards.pdf)

```{r layer_table}
library(data.table)
data.table(layer=c('bc timber harvesting landbase', 'Coast timber harvesting landbase',
                   'Southern Interior timber harvesting landbase',
                   'Northern Interior timber harvesting landbase',
                   'Generalized Forest Cover Ownership',
                   'Consolidated cutblocks ID',
                   'VEG_COMP feature id',
                   'Waterbodies',
                   'Watercoures',
                   'Caribou Designatable Unit 6 Boundary',
                   'Caribou Designatable Unit 8 Boundary'
                   ),
           public = c('bc_thlb'
                    , 'thlb_data_rco', 'thlb_data_sir', 'thlb_data_nir', 'f_own_polygon', 'cns_cut_bl_polygon' ,'veg_comp_lyr_r1_poly_final_spatialv2_2003', 'trim_ebm_waterbodies','trim_ebm_watercourses', 'caribou_boreal_study_area'),
           rast = c('bc_thlb', 'thlb_rco_lyr2018','thlb_sir_lyr2018','thlb_nir_lyr2018', 'f_own', 'cns_cut_bl','veg_comp2003_id','waterbodies','watercourses', 'du6_bounds','du8_bounds'),
           source=c('INTERNAL','INTERNAL','INTERNAL','INTERNAL',
                    'https://catalogue.data.gov.bc.ca/dataset/generalized-forest-cover-ownership', 'https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-' ,'INTERNAL', 'https://catalogue.data.gov.bc.ca/dataset/waterbodies-trim-enhanced-base-map-ebm','https://catalogue.data.gov.bc.ca/dataset/watercourses-trim-enhanced-base-map-ebm', 'INTERNAL', 'INTERNAL'))
```

## Set empty raster
```{r, faster_raster}
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

#Get dummy layer for projection (too lazy to write it) 
lyr<-getSpatialQuery(paste("SELECT geom FROM public.gcbp_carib_polygon"))

#Make an empty provincial raster aligned with hectares BC
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lyr)$proj4string, resolution = c(100, 100), vals = 0
)
```

## THLB
```{r, thlb}
#Get coast data 
layer<-getSpatialQuery(paste("SELECT thlb_fact, wkb_geometry FROM public.thlb_data_rco"))
layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "thlb_fact")
writeRaster(layer.ras, file="thlb_rco_Lyr.tif", format="GTiff", overwrite=TRUE)

#Get southern interior data 
layer<-getSpatialQuery(paste("SELECT thlb_fact, wkb_geometry FROM public.thlb_data_sir"))
layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "thlb_fact")
writeRaster(layer.ras, file="thlb_sir_Lyr.tif", format="GTiff", overwrite=TRUE)

#Get northern interior data 
layer<-getSpatialQuery(paste("SELECT thlb_fact, wkb_geometry FROM public.thlb_data_nir"))
layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "thlb_fact")
writeRaster(layer.ras, file="thlb_nir_Lyr.tif", format="GTiff", overwrite=TRUE)

#Get thlb 2018 data 
layer<-getSpatialQuery(paste("SELECT thlb_fact, wkb_geometry FROM public.bc_thlb"))
layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "thlb_fact")
writeRaster(layer.ras, file="thlb2018", format="GTiff", overwrite=TRUE)

#Upload to PostgreSQL
system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/thlb_nir_Lyr.tif -t 100x100 public.ras_thlb_nir_Lyr2018 | psql -d clus")
system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/thlb_rco_Lyr.tif -t 100x100 public.ras_thlb_rco_Lyr2018 | psql -d clus")
system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/thlb_sir_Lyr.tif -t 100x100 public.ras_thlb_sir_Lyr2018 | psql -d clus")
system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/thlb2018.tif -t 100x100 public.ras_bc_thlb2018 | psql -d clus")
```


## Tenure reduction

Location for administrative layers used in TSR: \\Orbital\s63016\!Publish\TSR Documentation.
The [Generalized Forest Ownership layer](https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/stewardship/forest-analysis-inventory/data-management/standards/generalized_forest_cover_ownership_layer_2018.pdf) is used to arrive at a contributing forest landbase

```{r, admin}
#Forest Ownership
layer<-getSpatialQuery("SELECT own, wkb_geometry FROM public.f_own_polygon")

layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "own")
writeRaster(layer.ras, file="own.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/own.tif -t 100x100 rast.f_own| psql -d clus")
```

## Consolidated cutblocks

[Harvested areas of bc](https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-). Used to depict the timing of harvest operations.

```{r, cutblocks}
#Harvest locations year
layer<-getSpatialQuery("SELECT harvestyr, wkb_geometry FROM public.cns_cut_bl_polygon WHERE areaha >= 1 ORDER BY harvestyr")

layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "harvestyr")
writeRaster(layer.ras, file="cns_cutblk.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/cns_cutblk.tif -t 100x100 rast.cns_cut_bl_year | psql -d clus")

#Harvest locations id
layer<-getSpatialQuery("SELECT cutblockid, wkb_geometry FROM public.cns_cut_bl_polygon WHERE areaha >= 1 ORDER BY cutblockid")

layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "cutblockid")
writeRaster(layer.ras, file="cns_cutblk.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/cns_cutblk.tif -t 100x100 rast.cns_cut_bl | psql -d clus")

```

## VEG COMP feature id

This id links to polygon level attribution. Also links to yield curve generation from results - TIPSY and feature projection - VDYP
```{r, veg_comp, echo = FALSE}
#Harvest locations year
layer<-getSpatialQuery("SELECT feature_id, wkb_geometry FROM public.veg_comp_lyr_r1_poly_final_spatialv2_2003")

layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "feature_id")
writeRaster(layer.ras, file="veg_comp_2003_id.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/veg_comp_2003_id.tif -t 100x100 rast.veg_comp2003_id | psql -d clus")
```

## Water

The BC [waterbodies dataset](https://catalogue.data.gov.bc.ca/dataset/waterbodies-trim-enhanced-base-map-ebm) is found on the BCGW oracle server under a user restriction. There are a few options for connecting to the BCGW

* Use citrix to connect to the GTS and save it to a `.gdb` using ArcGIS
* Use FME to create a connection between BCGW and Postgres
* Use rOracle to create a connection between BCGW and R
* Use ora2pg to create a connection between BCGW and Postgres
* Use ogr2ogr to create a connection between BCGW and Postgres

For the later (quicker?) option:

>system("cmd.exe", input = 'ogr2ogr -f PostgreSQL PG:"dbname=clus port = 5432 user=postgres" OCI:"user/pass@(DESCRIPTION = (ADDRESS_LIST = (ADDRESS = (PROTOCOL = TCP)(HOST = BCGW.BCGOV)(PORT = 1521)))(CONNECT_DATA = (SERVICE_NAME=IDWPROD1.BCGOV))):WHSE_BASEMAPPING.TRIM_EBM_WATERBODIES" -lco SCHEMA=public -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -gt 65536')

```{r, waterbodies}
water<-st_as_sf(getSpatialQuery("SELECT feature_type,wkb_geometry FROM public.trim_ebm_waterbodies"))
ras.water <- fasterize::fasterize(st_cast(water), ProvRast, 
                        field = NULL,#cells that are waterbodies get a value of 1
                        background = 0) 
writeRaster(ras.water, file="water.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/water.tif -t 100x100 rast.waterbodies| psql -d clus")
```

The BC [watercourses dataset](https://catalogue.data.gov.bc.ca/dataset/watercourses-trim-enhanced-base-map-ebm). Location of rivers, streams and waterways.

```{r, watercourses}
water<-st_as_sf(getSpatialQuery("SELECT feature_type,wkb_geometry FROM public.trim_ebm_watercourses"))
ras.water <- fasterize::fasterize(st_cast(water), ProvRast, 
                        field = NULL,#cells that are waterbodies get a value of 1
                        background = 0) 
writeRaster(ras.water, file="water.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/water.tif -t 100x100 rast.watercourses| psql -d clus")
```

# Designatable Units (for Caribou)

Designatable units are comglomerations of herds that share the same behaviour and range. In BC, the herd and designatable unit look up is as follows:

```{r, du_table}
du_herd<-data.table(DU= c(6,	6,	6,	6,	6,	6,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	7,	8,	8,	8,	8,	8,	8,	7,	7,	7,	7,	7,	7,	7,	7,	7,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9,	9),
                    Herd =c('Maxhamish',	'Chinchaga',	'Snake-Sahtaneh',	'Calendar',	'Parker',	'Prophet',	'Atlin',	'Carcross',	'Edziza',	'Finlay',	'Frog',	'Gataga',	'Horseranch',	'Level Kawdy',	'Liard Plateau',	'Little Rancheria',	'Muskwa',	'Pink Mountain',	'Rabbit',	'Spatsizi',	'Swan Lake',	'Thutade',	'Tsenaglode',	'Burnt Pine',	'Kennedy Siding',	'Moberly',	'Quintette',	'Scott',	'Narraway',	'Charlotte Alplands',	'Chase',	'Graham',	'Itcha-Ilgachuz',	'Rainbows',	'Takla',	'Telkwa',	'Tweedsmuir',	'Wolverine',	'Hart Ranges',	'Narrow Lake',	'North Cariboo',	'None',	'Barkerville',	'Wells Gray North',	'Wells Gray South',	'Groundhog',	'Columbia North',	'Central Rockies',	'Columbia South',	'Frisby-Boulder',	'Monashee',	'Duncan',	'Nakusp',	'South Selkirks',	'Purcells South'),
                    Ecotype = c('boreal',	'boreal',	'boreal',	'boreal',	'boreal',	'boreal',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'northern',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain',	'mountain'),
                    Local=c('Maxhamish',	'Chinchaga',	'Snake-Sahtaneh',	'Calendar',	'Parker',	'Prophet',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'None',	'Pine River',	'Pine River',	'Pine River',	'Quintette',	'Pine River',	'Narraway',	'Chilcotin',	'Chase',	'Graham',	'Chilcotin',	'Chilcotin',	'Takla',	'Telkwa',	'Tweedsmuir',	'Wolverine',	'Hart Ranges',	'Upper Fraser',	'Upper Fraser',	'Upper Fraser',	'Quesnel Highlands',	'Quesnel Highlands',	'Wells Gray - Thompson',	'Wells Gray - Thompson',	'Revelstoke-Shuswap',	'Kinbasket',	'Revelstoke-Shuswap',	'Revelstoke-Shuswap',	'South Monashee',	'Central Kootenay',	'Central Kootenay',	'Southwest Kootenay',	'Southeast Kootenay'),
                    National=c('boreal',	'boreal',	'boreal',	'boreal',	'boreal',	'boreal',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'northern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain',	'southern mountain'))
print(du_herd)
```

To translate the herd boundaries into DU boundaries a 25 km buffer around each herd boundary that makes up the DU was estimated, then the resulting boundaries were dissolved into one shape. The following documents the rasterization process

```{r, carb_desig}
#DU6 - Boreal Caribou
du6<-getSpatialQuery("SELECT wkb_geometry FROM public.caribou_boreal_study_area")
ras.du6<-fasterize::fasterize(du6, ProvRast, 
                        field = NULL,#cells that are waterbodies get a value of 1
                        background = 0) 

writeRaster(ras.du6, file="du6.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/du6.tif -t 100x100 rast.du6_bounds | psql -d clus",invisible = TRUE, show.output.on.console = FALSE)

#DU7 - Northern Mountain
du7<-getSpatialQuery("SELECT wkb_geometry FROM public.du7_herds_buff25km")
ras.du7<-fasterize::fasterize(du7, ProvRast, 
                        field = NULL,#cells that are waterbodies get a value of 1
                        background = 0) 

writeRaster(ras.du7, file="du7.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/du7.tif -t 100x100 rast.du7_bounds | psql -d clus",invisible = TRUE, show.output.on.console = FALSE)

#DU8 - Southern Mountain
du8<-getSpatialQuery("SELECT wkb_geometry FROM public.du8_herds_buff25km")
ras.du8<-fasterize::fasterize(du8, ProvRast, 
                        field = NULL,#cells that are waterbodies get a value of 1
                        background = 0) 

writeRaster(ras.du8, file="du8.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/du8.tif -t 100x100 rast.du8_bounds | psql -d clus",invisible = TRUE, show.output.on.console = FALSE)


#DU9 - Southern Mountain
du9<-getSpatialQuery("SELECT wkb_geometry FROM public.du9_herds_buff25km")
ras.du9<-fasterize::fasterize(du8, ProvRast, 
                        field = NULL,#cells that are waterbodies get a value of 1
                        background = 0) 

writeRaster(ras.du9, file="du9.tif", format="GTiff", overwrite=TRUE)

system("cmd.exe", input = "raster2pgsql -s 3005 -d -I -C -M  C:/Users/KLOCHHEA/clus/R/Params/du9.tif -t 100x100 rast.du9_bounds | psql -d clus",invisible = TRUE, show.output.on.console = FALSE)

```