---
title: "BC Roading Cost Surface"
author: "Kyle Lochhead"
date: "July 18, 2019"
output: html_document
---

<!--
Copyright 2019 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

The simulation of roads using a least cost paths approach requires a map of the cost surface.The interior and coast appraisal mannuals document simple linear models (SLM) that are conditional on TSA, BEC zones and various crossings of lakes, rivers, pipelines. The following code spatially maps the cost estimates from these SLMs at the provincial scale. 

```{r, table_roadCostTSA, echo = FALSE}
roadCost.lookUp<-read.table("C:/Users/KLOCHHEA/clus/R/roads/roadCostTSA.csv", sep = ",", head = TRUE)
roadCost.lookUp
```

> In this table: Road_cost is the identifier for the SLM to use; Inter is the intercept; SlpCoef is the coeffeicent for topographic slope; and ESSFCoef is the intercept modifier that indicates if the area within the ESSF.

```{r, costsurf}
#Cost Surface for igraph
library(sf)
library(rpostgis)
library(dplyr)
library(raster)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

#Get the TSA numbers that match in the lookup table above
tsa<-getSpatialQuery("SELECT * FROM public.forest_tenure;")
tsa.rc<-tsa %>% 
        right_join(roadCost.lookUp, by = "tsa_number") #join in the lookup table

#build a default/empty provincial raster
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(tsa.rc)$proj4string, resolution = c(100, 100), vals = 0)

#assigning road group 1 to any TSA outside the polygons
tsa.rc$Road_Cost[is.na(tsa.rc$Road_Cost)] <- 1
tsa.rc$Inter[is.na(tsa.rc$Inter)] <- 37130 #assign default intercept
tsa.rc$SlpCoef[is.na(tsa.rc$SlpCoef)] <- 156.68 #assign default slope
tsa.rc$ESSFCoef[is.na(tsa.rc$ESSFCoef)] <- 0 #assig default essf indicator flag
#---check
plot(tsa.rc["SlpCoef"])
slope.rc10<-tsa.rc[tsa.rc$Road_Cost == 10,]

#Make rasters of the equation components
ras.slope.rc10<-fasterize::fasterize(slope.rc10, prov.rast, field = "Road_Cost") #this is a special road cost group because it squares the slope
tsa.ras.int<-fasterize::fasterize(tsa.rc, prov.rast, field = "Inter")
tsa.ras.slpCoef<-fasterize::fasterize(tsa.rc, prov.rast, field = "SlpCoef")
tsa.ras.essfCoef<-fasterize::fasterize(tsa.rc, prov.rast, field = "ESSFCoef")
```


#Slope

For road group 10 the slope is a squared slope.
```{r, slope}
#mask for road group 10 -- it has slope**2
ras.slope.rc10[ras.slope.rc10[]== 10]<-1
ras.slope.rc10[is.na(ras.slope.rc10[])]<-0
#plot(ras.slope.rc10)

# get the slope
slope<-raster("//spatialfiles2.bcgov/archive/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/dem/all_bc/bc_ha_slope2.tif") #this file was modified by gdalwarp to put it in the correct alignment
#ras.slope.rc10<-resample(ras.slope.rc10, slope, method = 'bilinear')

rc10.slope<-slope*ras.slope.rc10 #get the slope for road group 10
rc10.slope2<-rc10.slope*rc10.slope #square the slope

rc10.mask<-ras.slope.rc10
rc10.mask[ras.slope.rc10[]==1]<-0
rc10.mask[ras.slope.rc10[]==0]<-1

#plot(rc10.mask)
slope.cost<- rc10.mask*slope + rc10.slope2 #add the slope and the square slope for road group 10

#writeRaster(slope.cost, file="//spatialfiles2.bcgov/archive/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/Roads/slope_rc10.tif", format="GTiff", overwrite=TRUE)

#free up some memory
rm(rc10,rc10.slope2,rc10.slope)
```

## Crossings

Crossings include pipeline crossings and water crossings.
```{r, other}
#pipeline crossings
pipelines <-raster("//spatialfiles2.bcgov/archive/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/pipelines/raster_pipelines_20180815.tif") 

pipe.cost<- pipelines*1911 #cost to cross a multiple pipeline per pipe

#watercrossings
waterx <-raster("//spatialfiles2.bcgov/archive/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/water/raster_watercourses_20180816.tif") 
waterx.cost<-waterx*2130 #assuming a 0.8 diameter at 14 m
```

## Barriers
```{r, barriers}
#Lake barriers
lake <-raster("//spatialfiles2.bcgov/archive/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/water/raster_lakes_20180816.tif") 
```

## Other costs
```{r, other}
#ESSF
#Call Mikes raster functions???
essf<-getSpatialQuery("SELECT * FROM public.bec_zone WHERE zone = 'ESSF'")
essf$zoneInt<-1
essf.ras<- fasterize::fasterize(essf, prov.rast, field = "zoneInt")
```

## Calculate road cost
```{r, cost}
#Calcualte the road cost
#tsa.ras.slpCoef2<-resample(tsa.ras.slpCoef, slope.cost, method = 'bilinear')
#tsa.ras.int2<-resample(tsa.ras.int, slope.cost, method = 'bilinear')
#tsa.ras.essfCoef2<-resample(tsa.ras.essfCoef, slope.cost, method = 'bilinear')
#lake2<-resample(lake, slope.cost, method = 'bilinear')
#pipe.cost2<-resample(pipe.cost, slope.cost, method = 'bilinear')
#waterx.cost2<-resample(waterx.cost, slope.cost, method = 'bilinear')
#essf2<-resample(essf.ras, slope.cost, method = 'bilinear')
essf.ras[is.na(essf.ras[])]<-0
cost.surface<-waterx.cost + pipe.cost + tsa.ras.int + slope.cost*tsa.ras.slpCoef + tsa.ras.essfCoef*essf.ras #estimate the cost surface
cost.surface[lake==1]<-NA # add the barriers
plot(cost.surface) #check the raster

library(here)
writeRaster(cost.surface, file=paste0(here(), "/cost_surface.tif"), format="GTiff", overwrite=TRUE) #print to disk

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here(), '/cost_surface.tif -t 100x100 rast.rd_cost_surface | psql -d clus'), show.output.on.console = FALSE, invisible = TRUE)
```

