---
title: "Study Area Boundaries"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
layeraoi<-getSpatialQuery("SELECT * FROM study_area_compart limit 1")
#Create a provincial raster
prov.rast <- raster::raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(layeraoi)$proj4string, resolution = c(100, 100), vals = 0)
```


## Timber Supply Units (timber supply areas and tree farm licenses)
```{r, data4}
forest.tenure<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM study_area_compart where tsa_name in ('Quesnel TSA', 'Lakes TSA', 'Morice TSA', 'Bulkley TSA', 'Williams Lake TSA', 'Kamloops TSA', '100 Mile House TSA', 'Golden TSA', 'Revelstoke TSA', 'Okanagan TSA', 'Kootenay Lake TSA', 'Invermere TSA', 'Cranbrook TSA', 'Arrow TSA', 'Dawson Creek TSA', 'Robson Valley TSA') or tsb_number in ('24C', '24D','24E','24F','24G','24H','24I', '16A', '16B', '16C', '16D', '16E', '16F', '16G', '16H', '16I', '16J', '16K', '16P')")

#forest.tenure<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM public.tsa_nw_coast_no_tfl")

forest.tenure2<-forest.tenure %>% group_by ( tsa_name) %>% summarise()
st_crs(forest.tenure2)
plot(forest.tenure2["tsa_name"]) #check 

#Spatial partitions
pg_north<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM study_area_compart where tsb_number in ('24A', '24B')")
pg_north$tsa_name<-"Prince George North TSA"
pg_north<- pg_north %>% group_by (tsa_name) %>% summarise()
st_crs(pg_north)

fort_st_john_core<-sf::st_read("//spatialfiles2.bcgov/work/FOR/VIC/HTS/ANA/Workarea/dstuart/TSA40_FtStJohn/SENSITIVITIES/GeographicPartition/Core_ForLegal/TSA40_Core_shapes/TSA40_core.shp")
fort_st_john_core$tsa_name<-"Fort St John Core TSA"
fort_st_john_core<- fort_st_john_core %>% group_by (tsa_name) %>% summarise()
st_crs(fort_st_john_core)<-st_crs(pg_north)
names(fort_st_john_core)<-c("tsa_name", "wkb_geometry")
st_geometry(fort_st_john_core) <- "wkb_geometry"
plot(fort_st_john_core["tsa_name"]) 

fort_st_john <-sf::st_read("//spatialfiles2.bcgov/work/FOR/VIC/HTS/ANA/Workarea/dstuart/TSA40_FtStJohn/SENSITIVITIES/GeographicPartition/Core_ForLegal/TSA40_Core_shapes/iLU_TSA40_.shp", query = "SELECT * FROM \"iLU_TSA40_\" where c_p =2")
fort_st_john$tsa_name <- "Fort St John TSA"
fort_st_john <- fort_st_john  %>% group_by (tsa_name) %>% summarise()
st_crs(fort_st_john)<-st_crs(pg_north)
names(fort_st_john)<-c("tsa_name", "wkb_geometry")
st_geometry(fort_st_john) <- "wkb_geometry"
plot(fort_st_john["tsa_name"]) 

cascadia_toc<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM study_area_compart where tsb_number in ('45O')")
cascadia_toc$tsa_name<-'Cascadia TOC TSA'
cascadia_toc<-cascadia_toc %>% group_by (tsa_name) %>% summarise()

cascadia_tko<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM study_area_compart where tsb_number in ('45K', '45K1', '45K2')")
cascadia_tko$tsa_name<-'Cascadia TKO TSA'
cascadia_tko<- cascadia_tko%>% group_by (tsa_name) %>% summarise()

cascadia_tcc<-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM study_area_compart where tsb_number in ('45C5','45C6','45C7','45C8')")
cascadia_tcc$tsa_name<-'Cascadia TCC TSA'
cascadia_tcc<- cascadia_tcc %>% group_by (tsa_name) %>% summarise()

mackenzie_sw <-getSpatialQuery("SELECT tsa_name, wkb_geometry FROM study_area_compart where tsb_number in ('16L', '16O', '16M', '16N')")
mackenzie_sw$tsa_name<-'MacKenzie SW TSA'
mackenzie_sw <-mackenzie_sw %>% group_by (tsa_name) %>% summarise()
st_crs(mackenzie_sw)

forest.tenure3<-rbind(forest.tenure2, pg_north, mackenzie_sw, fort_st_john, fort_st_john_core, cascadia_tcc, cascadia_toc, cascadia_tko) 

forest.tenure.vat<-unique(forest.tenure3$tsa_name)
#forest.tenure.vat<-unique(forest.tenure$tsa_name)

forest.tenure.vat2<-unlist(lapply(forest.tenure.vat, function(x){
  gsub( " ", "_", x)
}), use.names = FALSE)
forest.tenure.vat3<-data.table(cbind(forest.tenure.vat, forest.tenure.vat2))
setnames(forest.tenure.vat3, c("tsa_name", "tsa_name2"))
forest.tenure.vat3<-forest.tenure.vat3[,value:=seq_len(.N)]
forest.tenure4<-merge(forest.tenure3,forest.tenure.vat3)

#get ride of the tsa_name -- its sperated by spaces
forest.tenure4$tsa_name<-NULL
setnames(forest.tenure4, c("tsa_name2"), c("tsa_name"))

#Call value tsa_number
forest.tenure5<-forest.tenure4
setnames(forest.tenure5, c("value"), c("tsa_number"))
st_write(forest.tenure5, "forest_ten.shp", delete_layer=TRUE)
#ogr2ogr -f PostgreSQL PG:"dbname=clus port = 5432 user=klochhea" C:\Users\klochhea\clus\R\Params\forest_ten.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI

#Alter table forest_ten rename to tsa_aac_bounds;
#GRANT ALL ON TABLE public.tsa_aac_bounds TO postgres;
#GRANT ALL ON TABLE public.tsa_aac_bounds TO clus_project;
#GRANT ALL ON TABLE public.tsa_aac_bounds TO tmuhly;


#RAsterize 
ras.forest.tenure <-fasterize::fasterize(st_cast(forest.tenure4, "MULTIPOLYGON"), prov.rast, field = "tsa_number") 
raster::plot(ras.forest.tenure)
writeRaster(ras.forest.tenure, "forest_ten.tif")

```

### Commit to postgreSQL
```{r, commit_db}

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

forest.tenure.vat3$tsa_name<-NULL
setnames(forest.tenure.vat3, c("tsa_name2"), c("tsa_name"))
DBI::dbWriteTable(conn, c("public", "tsa_aac_bounds_vat"), value= forest.tenure.vat3, row.names = FALSE, overwrite = TRUE)

#dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone_constraints")
dbDisconnect(conn)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/forest_ten.tif -t 100x100 rast.tsa_aac_boundary | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)
```

## Chilcotin Study Area
Process for the Chilcotin caribou planning study area.

'Version 1' included the Quesnel and Williams Lake TSAs, with compartments for caribou critical habitat areas to allow for habitat-type specific harvest prescriptions (e.g., age targets). A specific dataset was built for this.
```{r chilcotin study area version 1}

studyarea <- getSpatialQuery ("SELECT tsa_name, wkb_geometry FROM public.study_area_chilcotin WHERE tsa_name IN ('Quesnel_TSA_Matrix', 'Quesnel_TSA_HEWSR', 'Quesnel_TSA_LESR', 'Quesnel_TSA_LEWR', 'Quesnel_TSA_out', 'Williams_Lake_TSA_HEWSR', 'Williams_Lake_TSA_LESR', 'Williams_Lake_TSA_LEWR', 'Williams_Lake_TSA_Matrix', 'Williams_Lake_TSA_out');")

studyarea.vat <- as.data.table (unique (studyarea$tsa_name))
setnames (studyarea.vat, "tsa_name")
studyarea.vat [, value := seq_len(.N)]

studyarea2 <- merge (studyarea, studyarea.vat, by = "tsa_name")

# Rasterize 
ras.study.area <-fasterize::fasterize (st_cast (studyarea2, "MULTIPOLYGON"), prov.rast, field = "int_id") 
writeRaster (ras.study.area, "study_area_chilcotin.tif")

# write data
DBI::dbWriteTable(conn, c("vat", "study_area_chilcotin"), value= studyarea.vat, row.names = FALSE, overwrite = TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/caribou/clus_repo/clus/R/Params/study_area_chilcotin.tif -t 100x100 rast.study_area_chilcotin | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

dbDisconnect(conn)

```
'Version 2' was created to focus the analysis in the operating area of the licensees, which are teh western portions of the Quesnel and Williams Lake TSAs. 

```{r chilcotin study area version 2}
studyarea <- getSpatialQuery ("SELECT * FROM public.chilcotin_area_of_interest;")

studyarea$name <- "chilctoin_aoi"
studyarea$value <- 1
studyarea.vat <- as.data.table (unique(studyarea$name))
setnames (studyarea.vat, "name")
studyarea.vat [, value := seq_len(.N)]

# Rasterize 
ras.study.area <-fasterize::fasterize (st_cast (studyarea, "MULTIPOLYGON"), prov.rast, field = "value") 
writeRaster (ras.study.area, "chilcotin_aoi.tif")

# write data
DBI::dbWriteTable(conn, c("vat", "chilcotin_aoi_v2"), value= studyarea.vat, row.names = FALSE, overwrite = TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/Params/chilcotin_aoi.tif -t 100x100 rast.chilcotin_aoi_v2 | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

dbDisconnect(conn)

```
