<!--
Copyright 2018 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "GBR North Forest Management Objectives for a cummulative effects study with UBC"
author: "Elizabeth Kleynhans"
date: "November 16, 2020"
output: 
  html_document: 
    keep_md: yes
    toc: true
---

## Purpose

Create forest management objective raster(s) based on old growth retention targets in Great Bear Rainforest North. This is a project with UBC - Viv Tulloch, Bryant DeRoy, and others such as Tara Martin. The goal is to examine cummulative effects within a small region of GBR. We are providing forestry simulation data.

# Average Retention Targets in GBR (UBC Project with Viv Tulloch, Bryant DeRoy, Liz and Tyler)

Old growth retention targets were set in the 2016 GBR landuse order (https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/timber-pricing/coast-timber-pricing/maps-and-graphics/great_bear_rainforest_order_-_jan_21_2016.pdf). 

These retention targets differ by BEC zone and landscape unit and site series group. See:

https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/westcoast-region/great-bear-rainforest/gbr_old_forest_targets_landscape_unit.pdf

https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/westcoast-region/great-bear-rainforest/gbr_schedule_f_site_series_group_minimum_old_forest_retention_levels_less_than_twenty_percent_by_landscape_unit.pdf

https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/natural-resource-use/land-water-use/crown-land/land-use-plans-and-objectives/westcoast-region/great-bear-rainforest/gbr_schedule_g_old_forest_targets_order_area.pdf

For ease, the UBC team decided to aggregate the average retention targets in 10% increments (.25,.35,.45 etc.) for each dominant ssg, then they clipped those to the THLB polygons and then dissolved by retention target across the study area. This hopefully avoids the need to include data on LU and BEC variants. 


```{r zoneStep2, echo=FALSE}
library(data.table)
source (paste0(here(),"/R/functions/R_Postgres.R"))


art<-getSpatialQuery("SELECT ogc_fid, 
                     case
                     WHEN retention = 0.00 then 0
                     WHEN retention = 0.25 then 25
                     WHEN retention = 0.35 then 35
                     WHEN retention = 0.45 then 45
                     WHEN retention = 0.55 then 55
                     WHEN retention = 0.65 then 65
                     WHEN retention = 0.75 then 75
                     WHEN retention = 0.85 then 85
                     end as retention, wkb_geometry FROM public.ssg_retention_thlb_dslv")

art<- art %>% dplyr::rename(art_fid = ogc_fid)

plot(art[,"retention"], lwd=0.01) # looks ok

lu<-getSpatialQuery("SELECT wkb_geometry 
FROM public.rmp_lu_sp_polygon limit 1")

ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)

#Rasterize the average retention targets
art.ras<-fasterize::fasterize(sf=art , raster = ProvRast , field = "art_fid")
writeRaster(art.ras, file=paste0(here(),"/zone_art.tif"), format="GTiff", overwrite=TRUE)

system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M ', here(), '/zone_art.tif -t 100x100 rast.zone_cond_art |  psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

rm(art.ras)
gc()
library(dplyr)

##Maintain 66 percent of the area ge than 30 years. See http://www.env.gov.bc.ca/wld/documents/uwr/u-3-006_ORAM_Order.pdf
#u3006_table[, `:=`(reference_zone = 'rast.zone_uwr', variable = 'age', type = 'ge', percentage = 66, threshold = 30, ndt =0, label = 'u-3-006')]

# here we are trying to maintain some proportion of old growth forest. I assume old growth forest to be forest older than 250 years. 

df<-as.data.frame(art)
df<-df[,1:2]
df$type<-'ge'
df$variable<-'age'
df$threshold<-250
df$reference_zone<-'rast.zone_art'
df$ndt<-as.integer(0)
colnames(df) <- c( "zoneid","percentage", "type", "variable", "threshold", "reference_zone", "ndt") # the vqo column gets labeled as percentage
df$zoneid<-as.integer(df$zoneid)#assign integer
df$percentage<-as.numeric(df$percentage)#assign integer
df$label<-'art'
df$multi_condition<-NULL

#df<-data.table(unique(df))# get rid of the multiple zoneid = 0 )

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "zone_art"), value= df, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)
```


# Setting PostgreSQL Inheritance
PostgreSQL implements table inheritance. See [here]("https://www.postgresql.org/docs/9.5/ddl-inherit.html")

```{r zoneCleanUp, echo=FALSE, eval=FALSE}
#----------------------------
#Inheritability in PostgreSQL
#----------------------------
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

dbExecute(conn, "CREATE TABLE IF NOT EXISTS zone_constraints_gbr (zoneid integer, reference_zone text, ndt integer, variable text, threshold double precision, type text, percentage double precision)")

dbExecute(conn, "ALTER TABLE zone_nharv INHERIT zone_constraints_gbr")
dbExecute(conn, "ALTER TABLE zone_vqo INHERIT zone_constraints_gbr")
dbExecute(conn, "ALTER TABLE zone_wha_gbr INHERIT zone_constraints_gbr")
dbExecute(conn, "ALTER TABLE zone_beo INHERIT zone_constraints_gbr")
dbExecute(conn, "ALTER TABLE zone_fsw_gbr INHERIT zone_constraints_gbr")
dbExecute(conn, "ALTER TABLE zone_uwr_gbr INHERIT zone_constraints_gbr")
dbExecute(conn, "ALTER TABLE zone_cw INHERIT zone_constraints_gbr")
dbExecute(conn, "ALTER TABLE zone_art INHERIT zone_constraints_gbr")#Note from uwr_cond_harvest.rmd
dbDisconnect(conn)
```
