---
title: "Imputing crown closure"
author: "Kyle"
date: "17/02/2021"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
library(yaImpute)
source(paste0(here::here(), "/R/functions/R_Postgres.R"))
```

## Purpose

Natural orgin stands do not have a projection of crown closure - VDYP doesn't output crown closure over time. Thus, we will impute its value using the corresponding TIPSY curve. To do this, a strata based imputation will be used, where only observations with the same leading species group will be used.

## Imputation parameter selection

Test some of the parameter options for nearest neighbor imputation. This inlcudes the distance metric and number of neighbors, k.
```{r, ycs}
species<-data.table(species = c('Dr', 'E', 'Ac', 'At', 'B', 'Cw','Yc', 'Fd', 'H', 'L', 'Mb', 'P', 'Sb', 'Ss','Se','Sw'), sql=c("('D','DG','DM','DR')","('E','EB','EE','ES','EW','EX','EXP','EXW','EA','EP')","('A','AC','ACB','ACT','AD','AX')","('AT')","('B','BB','BC','BM','BP','BL','BG','BA')", "('C','CW')","('Y','YC')","('F','FD','FDC','FDI')", "('H','HX','HXM', 'HM','HW')", "('L','LD','LS','LW','LA','LT')","('M','MB','ME','MN','MR','MS','MV')","('P','PM','PR','PS','PX', 'PL','PLC','PLI','PY','PW','PJ','PXJ','PF','PA')","('SB')","('SS')","('SE','SXE')","('SW', 'SXW','S','SA','SN','SX','SXB','SXL','SXS','SXX')"))
strata<-lapply(seq_len(nrow(species)), function(i) species[i])

if(TRUE){
  
error<-lapply(strata, function(x){
  ref_vri<-data.table(getTableQuery(paste0("SELECT crown_closure, basal_area, proj_age_1 as age, quad_diam_125 as qmd, proj_height_1 as height, vri_live_stems_per_ha as tph, live_stand_volume_125 as tvol, bec_zone_code, species_cd_1  FROM veg_comp_lyr_r1_poly2018 where bclcs_level_2 = 'T' and reference_year >= 2008 and species_cd_1 is not null and crown_closure >= 0 and basal_area >= 0 and  proj_height_1 >= 0 and vri_live_stems_per_ha >= 0 and quad_diam_125 >= 0 and UPPER(species_cd_1) IN ", x$sql ,";")))
  preds_euc_k1<-impute(yai(x=ref_vri[,c("basal_area", "age", "tvol", "height", "tph")], y=ref_vri$crown_closure, method="euclidean", k=1), k=1, method = 'closest')
  preds_mal_k1<-impute(yai(x=ref_vri[,c("basal_area", "age", "tvol","height", "tph")], y=ref_vri$crown_closure, method="mahalanobis", k=1), k=1, method = 'closest')
  #preds_rf_k1<-impute(yai(x=ref_vri[,c("basal_area", "age", "height", "tph")], y=ref_vri$crown_closure, method="randomForest", k=1), k=1, method = 'closest')
   preds_euc_k3<-impute(yai(x=ref_vri[,c("basal_area", "age","tvol", "height", "tph")], y=ref_vri$crown_closure, method="euclidean", k=3), k=3, method = 'mean')
  preds_mal_k3<-impute(yai(x=ref_vri[,c("basal_area", "age", "tvol","height", "tph")], y=ref_vri$crown_closure, method="mahalanobis", k=3), k=3, method = 'mean') 
  #preds_rf_k3<-impute(yai(x=ref_vri[,c("basal_area", "age", "height", "tph")], y=ref_vri$crown_closure, method="randomForest", k=3), k=3, method = 'dstWeighted')
  preds_euc_k5<-impute(yai(x=ref_vri[,c("basal_area", "age", "tvol","height", "tph")], y=ref_vri$crown_closure, method="euclidean", k=5), k=5, method = 'mean')
  preds_mal_k5<-impute(yai(x=ref_vri[,c("basal_area", "age", "tvol","height", "tph")], y=ref_vri$crown_closure, method="mahalanobis", k=5), k=5, method = 'mean') 
  #preds_rf_k5<-impute(yai(x=ref_vri[,c("basal_area", "age", "height", "tph")], y=ref_vri$crown_closure, method="randomForest", k=5), k=5, method = 'dstWeighted')
  preds_euc_k10<-impute(yai(x=ref_vri[,c("basal_area", "age","tvol", "height", "tph")], y=ref_vri$crown_closure, method="euclidean", k=10), k=10, method = 'mean')
  preds_mal_k10<-impute(yai(x=ref_vri[,c("basal_area", "age","tvol", "height", "tph")], y=ref_vri$crown_closure, method="mahalanobis", k=10), k=10, method = 'mean') 
  preds_euc_k15<-impute(yai(x=ref_vri[,c("basal_area", "age", "tvol","height", "tph")], y=ref_vri$crown_closure, method="euclidean", k=15), k=15, method = 'mean')
  preds_mal_k15<-impute(yai(x=ref_vri[,c("basal_area", "age","tvol", "height", "tph")], y=ref_vri$crown_closure, method="mahalanobis", k=15), k=15, method = 'mean') 
  avg.y<-mean(preds_euc_k1$y.o)
  data.table(species = x$species, null = sqrt(sum((preds_euc_k1$y.o-avg.y)**2)/nrow(preds_euc_k1)),rmsd_euc_k1 = rmsd(na.omit(preds_euc_k1),scale= FALSE)["y",],rmsd_mal_k1 = rmsd(na.omit(preds_mal_k1),scale= FALSE)["y",],rmsd_euc_k3 = rmsd(na.omit(preds_euc_k3),scale= FALSE)["y",],rmsd_mal_k3 = rmsd(na.omit(preds_mal_k3),scale= FALSE)["y",],rmsd_euc_k5 = rmsd(na.omit(preds_euc_k5),scale= FALSE)["y",],rmsd_mal_k5 = rmsd(na.omit(preds_mal_k5),scale= FALSE)["y",],rmsd_euc_k10 = rmsd(na.omit(preds_euc_k10),scale= FALSE)["y",],rmsd_mal_k10 = rmsd(na.omit(preds_mal_k10),scale= FALSE)["y",],rmsd_euc_k15 = rmsd(na.omit(preds_euc_k15),scale= FALSE)["y",],rmsd_mal_k15 = rmsd(na.omit(preds_mal_k15),scale= FALSE)["y",])
})

out<-rbindlist(error)
saveRDS(out, file = "cc_imputation_params.rds")
}

readRDS("cc_imputation_params.rds")

```

## Impute

The resulting leave one out validation suggested the RF distance metric which uses 1 minus the proportion of trees with the target observation is in the same node as the reference.

```{r, imput_cc}
if(FALSE){
  conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
  
  dbExecute(conn, "ALTER TABLE yc_vdyp_all add column cc integer default 0")
  dbDisconnect(conn)
}

###Set the list needed for running a stratified imputation
species_imp<-data.table(species = c("('Dr')", "('E','Ea','Ep')", "('Ac')", "('At')", "('B','Bl','Bg','Ba')", "('Cw')","('Yc')", "('Fd')", "('H', 'Hm', 'Hw')", "('L', 'Lw', 'La', 'Lt')", "('Mb')", "('P', 'Pl', 'Pj', 'Py', 'Pw', 'Pa', 'Pf')", "('Sb')", "('Ss')","('Se')","('Sw', 'S')"), sql=c("('D','DG','DM','DR')","('E','EB','EE','ES','EW','EX','EXP','EXW','EA','EP')","('A','AC','ACB','ACT','AD','AX')","('AT')","('B','BB','BC','BM','BP','BL','BG','BA')", "('C','CW')","('Y','YC')","('F','FD','FDC','FDI')", "('H','HX','HXM', 'HM','HW')", "('L','LD','LS','LW','LA','LT')","('M','MB','ME','MN','MR','MS','MV')","('P','PM','PR','PS','PX', 'PL','PLC','PLI','PY','PW','PJ','PXJ','PF','PA')","('SB')","('SS')","('SE','SXE')","('SW', 'SXW','S','SA','SN','SX','SXB','SXL','SXS','SXX')"))
strata_imp<-lapply(seq_len(nrow(species_imp)), function(i) species_imp[i])

#Run the imputation by strata
imp_results<-lapply(strata_imp, function(x){
  ref_vri<-data.table(getTableQuery(paste0("SELECT crown_closure, basal_area, proj_age_1 as age, quad_diam_125 as qmd, proj_height_1 as height, vri_live_stems_per_ha as tph, live_stand_volume_125 as tvol, bec_zone_code, species_cd_1  FROM veg_comp_lyr_r1_poly2018 where bclcs_level_2 = 'T' and reference_year >= 2008 and species_cd_1 is not null and crown_closure >= 0 and basal_area >= 0 and  proj_height_1 >= 0 and vri_live_stems_per_ha >= 0 and quad_diam_125 >= 0 and UPPER(species_cd_1) IN ", x$sql)))

  yc_vdyp<-data.table(getTableQuery(paste0("SELECT ycid, yc_grp, age, tvol, height, qmd, baha as basal_area, tph from yc_vdyp_all where yc_grp in (select distinct(yc_grp) from vdyp_vri2018 where species_cd_1 IN ", x$species,") and baha >=0 and tph >= 0;")))

  mal <- yai(x=ref_vri[,c("basal_area", "tvol", "height", "tph")], y=ref_vri$crown_closure, method="mahalanobis", k=10, noRefs=TRUE)

rownames(yc_vdyp) <- paste0("test.",rownames(yc_vdyp))
m10 <- newtargets(mal , newdata=yc_vdyp, k=10)
yc_vdyp$cc<-as.integer(impute(m10,k=10,method = 'dstWeighted', vars=yvars(m10))$y)
yc_vdyp[height<5,cc:=0 ] #Donpt include crown closure of small trees.
  
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

#sql_string <- "Update yc_vdyp_all set cc = %s where ycid = %s and age = %s;"
#dbSendStatement(conn, paste(sprintf(sql_string, yc_vdyp[ycid==-23919,]$cc, yc_vdyp[ycid==-23919,]$ycid, yc_vdyp[ycid==-23919,]$age), collapse=""))

dbWriteTable(conn, "pred_cc_impute", yc_vdyp[,c("ycid", "age", "cc")], append=TRUE)
  
dbDisconnect(conn)               
})

```

## Set the yc table

Merge the imputed cc with the yield curve table.

```{r, yc_table}
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
dbExecute(conn, "UPDATE yc_vdyp_all
SET cc = pred_cc_impute.cc
FROM pred_cc_impute
WHERE yc_vdyp_all.ycid = pred_cc_impute.ycid and yc_vdyp_all.age = pred_cc_impute.age;")
dbDisconnect(conn) 
```

## Validation

