---
title: "WHA_Conditional_Harvest"
author: "Kyle Lochhead"
date: "June 24, 2019"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Conditional harvesting: Land cover Constraints

Conditional harvesting means that there is some level of retention required during harvest operations. This may require a percentage of the management unit being retained according to a descriptive class - this can be age, crownclosure, height and even species specific. The table below provides a list of Wildlife habitat Area and ungulate winter range conditional harvesting constraints and the corresponding coarse assumption for achieving these constraints. The focus here is on conditional harvesting constraints at a landscape unit scale - not a cutblock level - that would impact caribou.

## WHA

```{r, WHA_cond_harv}
library(data.table)
library(sf)
library(here)
source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

wha_poly<-getSpatialQuery("SELECT ogc_fid, wha_tag, feat_notes, aprv_date, wkb_geometry FROM public.wcp_whaply_polygon WHERE harvest ='CONDITIONAL HARVEST ZONE' AND wha_tag IN 
(SELECT a.wha_tag  FROM public.wcp_whaply_polygon  a , public.study_area_tsa b WHERE  ST_INTERSECTS (a.wkb_geometry, b.wkb_geometry)) ORDER BY aprv_date ASC")

lu<-getSpatialQuery("SELECT *
FROM public.rmp_lu_sp_polygon LIMIT 1") #just a dummy query to get the projection

#Get the raster and projection
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lu)$proj4string, resolution = c(100, 100), vals = 0
)

#fasterize 
wha.ras<-fasterize::fasterize(sf= wha_poly, raster = ProvRast , field = "ogc_fid")

#Create empty zone constraint table
zone_wha<-data.table(zoneid=integer(), type=character(), variable=character(), threshold=numeric(), reference_zone=character(), percentage=numeric(), ndt=integer(),
                     label = character())

#get the ogc_fid from raster
ogc_fids<-data.table(unique(c(t(raster::as.matrix(wha.ras)))))
ogc_fids<-ogc_fids[!(is.na(V1)),]
wha_cond<-getTableQuery(paste0("SELECT ogc_fid, wha_tag, feat_notes, aprv_date FROM public.wcp_whaply_polygon WHERE ogc_fid IN(",paste(ogc_fids$V1, collapse = ","), ") ORDER BY wha_tag"))

```

### 3-071 to 3-088 Lewis Woodpecker, Kamloops
When harvest is approved follow: Protect or retain all ponderosa pine and block cottonwood live or dead > 30 cm. Use partial cutting silvicutural systems to mainain widely spaced <25% later seral ponderosa pine and Douglas fir. Do not use pesticides. Do not construct roads unless there is not other practicable option. see http://www.env.gov.bc.ca/wld/documents/wha/LEWO_3-071to088_ord.pdf
```{r, w3071}
#get the ogc_fids that belong to these.
wha_tags<-c('3-071', '3-072', '3-073', '3-074', '3-075', '3-076','3-077','3-078','3-079','3-080','3-081', '3-082', '3-083', '3-084', '3-085', '3-086', '3-087','3-088')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 3-117 to 3-120 and 3-122 Badger, Kamloops
Do not construct roads. Do not use pesticides. Do not conduct timber harvesting, except when harvesting is required to support ecological restoration where stocking <75 tph
see http://www.env.gov.bc.ca/wld/documents/wha/TATA_3_117to120_122_ord.pdf
```{r, w3117}
#No harvesting in these areas
```

### 3-147 American Badger
Do not construct roads. Do not use pesticides. Do not conduct timber harvesting, except when harvesting is required to support ecological restoration where stocking <75 tph. see http://www.env.gov.bc.ca/wld/documents/wha/TATA_3-147_Order.pdf
```{r, w3147}
#No harvesting in these areas
```

### 3-171 to 3-181
Data sensitve? Thompson Rivers
```{r, w3171}
#get the ogc_fids that belong to these.
wha_tags<-c('3-171', '3-172', '3-173', '3-174', '3-175', '3-176','3-177','3-178','3-179','3-180','3-181')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 4-011 to 4-045
Data sensitve? Kootney Lake
```{r, w4011}
#get the ogc_fids that belong to these.
wha_tags<-c('4-011','4-012','4-013','4-014','4-015','4-016','4-017','4-018','4-019','4-020','4-021','4-022','4-023','4-024','4-025','4-026','4-027','4-028','4-029','4-030','4-031','4-032','4-033','4-034','4-035','4-036','4-037','4-038','4-039','4-040','4-041','4-042','4-043','4-044','4-045')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 4-046 to 4-055 Rocky mountain tailed frog
Do not harvest in the core area. Maintain atleast 70% basal area with the approprate structure. Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/ASMO-4-046-055.pdf
```{r, w4046}
#Maintain basal area of ? for 70% of the unit
```

### 4-056 to 4-064 Rocky mountain tailed frog
Do not harvest in the core area. Maintain atleast 70% basal area with the approprate structure. Do not use pesticides.see http://www.env.gov.bc.ca/wld/documents/wha/ASMO-4-056-064.pdf
```{r, w4056}
#Maintain basal area of ? for 70% of the unit
```

### 4-077 to 4-085 Flammulated owl
Do not salvage or harvest in the core area. Do not harvest on xeric sites. In mesic or subhydric sires use selective harvesting systems that retain 50% of the co-dominant trees.see http://www.env.gov.bc.ca/wld/documents/wha/FLOW-4-077-85.pdf
```{r, w4077}
#Assumed while harvesting? or mainain crownclosure > 50% for 50% of the area?
```

### 4-088 to 4-092, 4-102, 4-103 American Badger 
Do not use pesticide. Harvest as required to support ecological restoration. Reduce stocking densities < 75 stems
see http://www.env.gov.bc.ca/wld/documents/wha/TATA_4-088-092,102,103_ord.pdf
```{r, w4088}
#No harvesting in these areas
```

### 4-098 Western screech Owl 
Do not harvest or salvage in the core area. Using selectin harvest < 20% basal area for PP, IDF and ICH zone. Retain deciduous trees. Retain > 60% of tree in riparian zones. see http://www.env.gov.bc.ca/wld/documents/wha/WSOW_4-098_ord.pdf
```{r, w4098}
#crownclosure > 60% in riparian. crown closure > 20 for other area 
```

### 4-099 to 4-101 Flammulated owl 
Do not salvage or harvest in the core area. Do not harvest on xeric sites. In mesic or subhydric sires use selective harvesting systems that retain 50% of the co-dominant trees.see http://www.env.gov.bc.ca/wld/documents/wha/FLOW_4-099to101_ord.pdf
```{r, w4099}
#Assumed while harvesting? or mainain crownclosure > 50% for 50% of the area?
```

### 4-105  
Data sensitive Kootney Lake
```{r, w4105}
#get the ogc_fids that belong to these.
wha_tags<-c('4-105')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 4-107  American Badger
Do not use pesticide. Harvest as required to support ecological restoration. Reduce stocking densities < 75 stems. see http://www.env.gov.bc.ca/wld/documents/wha/TATA_4-107_ord.pdf
```{r, w4107}
#No harvesting in these areas
```

### 4-109  American Badger
Data sensitive Rocky Mountain
```{r, w4109}
#get the ogc_fids that belong to these.
wha_tags<-c('4-109')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 4-112  American Badger
Data sensitive Rocky Mountain
```{r, w4112}
#get the ogc_fids that belong to these.
wha_tags<-c('4-112')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 4-113 to 4-115  Western Screech Owl
Do not cross streams or construct roads. Do not conduct timber harvesting or salvage within the core area. Within the management zone use selective harvest of < 20% basal area. Retain deciduous trees and retain > 60% of trees within riparian management zones. see http://www.env.gov.bc.ca/wld/documents/wha/WSOW_4-113to115_Order.pdf
```{r, w4113}
#crownclosure > 60% in riparian. crown closure > 20 for other area
```

### 4-121 to 4-126, 4-130 to 4-132, 4-134 to 4-135 Lewis Woodpecker
Do not construct roads. Do not use pesticides. Do not harvest unless to adess ecosystem restoration. Ponderos pine and dead trees > 30 cm dbh are maintained. Treatments are managed to promote shrub structure for berry and nut production. see http://www.env.gov.bc.ca/wld/documents/wha/LEWO_4-121_135_ord.pdf
```{r, w4121}
#No harvest in these areas
```

### 4-151 to 4-170, 4-177 Gillettes Checkerspot
Do not construct roads except in 4-160, 4-162, 4-166 and 4-169. Do not use pesticides/herbicides. Avoid silviculture that would result in closed canopies. see http://www.env.gov.bc.ca/wld/documents/wha/EUPGIL_4-151to170_177_ord.pdf
```{r, w4151}
#Harvest 50% crownclosure for 50% of the area?
```

### 4-178 to 4-179 Western Screech Owl
In the core area do not construct roads or stream crossings. Do not conduct harvesting or salvage within the core area. When conducting harvesting in the management zone use selective harvesting <= 20% basal area removal. Do not remove deciduous. In riparian areas retain > 60% of trees. see http://www.env.gov.bc.ca/wld/documents/wha/WSOW_4-178_to_4-179_Order.pdf
```{r, w4178}
#crownclosure > 60% in riparian. crown closure > 20 for other area
```

### 4-180 Grizzly Bear
Enhance Vaccinium spp which include ICDdw1, ICHdm, ESSFdm (table 2). Ratain large CWD (> 30 cm dbh). Do not use pesticides, see http://www.env.gov.bc.ca/wld/documents/wha/URAR_4-180_SA_Order.pdf
S--Assume the model does this at an operational scale.
```{r, w4180}
#get the ogc_fids that belong to these.
wha_tags<-c('4-180')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 4-209 Interior Western Screech Owl–
Do not construct roads or crossings in the core area. Do not timber harvest or salvage in the core area. Use selective harvesting <= 20% basal area removal. Do not remove deciduous trees. Retain > 60% of trees in riparian areas. see http://www.env.gov.bc.ca/wld/documents/wha/WESO_4-205_4-209_Order.pdf
```{r, w4209}
#crownclosure > 60% in riparian. crown closure > 20 for other area
```

### 4-217 to 4-323, 4-234 to 4-242 Gillettes Checkerspot
Do not construct roads. Avoid closed canopies. see http://www.env.gov.bc.ca/wld/documents/wha/EUGI_4-217_to_232_234_to242_GAR_Order.pdf
```{r, w4217}
#Harvest 50% crownclosure for 50% of the area? Maybe I can implement a partial harvesting constraint? Remove this from the cover constraints and put into a harvesting system constraint?
```
 
### 4-243 to 4-276 Western Screech Owl
Do not construct roads or crossings in the core area. Do not timber harvest or salvage in the core area. Use selective harvesting <= 20% basal area removal. Do not remove deciduous trees. Retain > 60% of trees in riparian areas. see http://www.env.gov.bc.ca/wld/documents/wha/WSOW_4-243_to_276_GAR_Order.pdf
```{r, w4243}
#crownclosure > 60% in riparian. crown closure > 20 for other area
```

### 5-003 
Data Sensitive? Chilcotin
```{r, w5003}
#get the ogc_fids that belong to these.
wha_tags<-c('5-003')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 5-007 - 5-035 American White Pelican
Do Not harvest from April 1 to August 31 -- model assumes this. see http://www.env.gov.bc.ca/wld/documents/wha/AWPE-5-007_ord.pdf
```{r, w5007}
#get the ogc_fids that belong to these.
wha_tags<-c('5-007','5-008','5-009','5-010','5-011','5-012','5-013','5-014','5-015','5-016','5-017','5-018','5-019','5-020','5-021','5-022','5-023','5-024','5-025','5-026','5-027','5-028','5-029','5-030','5-031','5-032','5-033','5-034','5-035')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 5-037 to 5-043 Grizzly Bear
Do not use pesticides. Protect forest cover and plant communities. see http://www.env.gov.bc.ca/wld/documents/wha/URAR_5-037to043_CentalCariboo.pdf
```{r, w5037}
#Harvest 50% crownclosure for 50% of the area?
```

### 5-072
Data Sensitve Central Cariboo
```{r, w5007}
#get the ogc_fids that belong to these.
wha_tags<-c('5-072')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 5-086 to 5-087, 5-118, 5-872 and 5-873 Caribou Northern
Retain all forest in 5-118. In caribou modified harvest zone (table 1) - Age >80 for 45%. Age > 100 for 37%. Age 120 for 30%. Age 140 for 25%. In caribou modified harvest for wha 5-086 retain lichen sites where 33% of the area on arboreal sites is on an 80 year cutting cycle. In caribou modified harvest for wha 5-086 retain lichen sites where 50% of the area on terrestrial lichen sites is on an 70 year cutting cycle. Caribou enhanced conventional harvest - in wha 5-872 and 5-873, 25% is left unlogged with an age > 100 years. see http://www.env.gov.bc.ca/wld/documents/wha/RATA_5-086-873_ord.pdf
```{r, w5086}
# lots here to add. For now just consider the cover constraints for  5-086 Age >80 for 45%. Age > 100 for 37%. Age 120 for 30%. Age 140 for 25%. Caribou enhanced conventional harvest - in wha 5-872 and 5-873, 25% is left unlogged with an age > 100 years
```

### 5-088 to 5-117 Mountain Caribou 
Do not harvest in the caribou No-harvest. Caribou modified harvest in wha 5-088, 5-091, 5-093, 5-111 and 5-116 use group selection harvesting up to 33% of each stand area on a 80 year cutting cycle.  see http://www.env.gov.bc.ca/wld/documents/wha/RATA_5-088_%205-117_ord_09Dec09.pdf
```{r, w5088}
#For the wha's that have modfied harvesting --consider harvesting constraints not cover constraints?
```

### 5-120 to 5-123, 5-126 to 5-128, 5-131, 5-133 , 5-136 to 5-150, 5-168 to 5-171 + many more  Grizzly Bear
Primary forestry activites will result in protections of the forest cover and plant communities within the boundaries of the wha. Pesticides shall not be used. Salvage harvesting shall not be used. see http://www.env.gov.bc.ca/wld/documents/wha/URAR-5-121to541_MidCoastTSA.pdf
```{r, w5120}
#get the ogc_fids that belong to these.
wha_tags<-c('5-120','5-121','5-122','5-123','5-126','5-128','5-131','5-133','5-136','5-137','5-138','5-139','5-140','5-141','5-142','5-143','5-144','5-145','5-146','5-147','5-148','5-149','5-150','5-168','5-169','5-170','5-171','5-172','5-173','5-174','5-175','5-176','5-177','5-178','5-179','5-180','5-181','5-182','5-183','5-184','5-185','5-186','5-187','5-188','5-190',	'5-191',	'5-192',	'5-193',	'5-194',	'5-195',	'5-196',	'5-197',	'5-198',	'5-199',	'5-200',	'5-201',	'5-202',	'5-203',	'5-204',	'5-205',	'5-206',	'5-207',	'5-208',	'5-209',	'5-210',	'5-211',	'5-212',	'5-213',	'5-214',	'5-215',	'5-216',	'5-217',	'5-218',  '5-224',	'5-225',	'5-226',	'5-227',	'5-228',	'5-229',	'5-230',	'5-231',	'5-232',	'5-233',	'5-234',	'5-235',	'5-236',	'5-237',	'5-238',	'5-239',	'5-240',	'5-241',	'5-242',	'5-243',	'5-244',	'5-245',	'5-246',	'5-247',	'5-248',	'5-249',	'5-250',	'5-251',	'5-252',	'5-253',	'5-254',	'5-255',	'5-256',	'5-257',	'5-258',	'5-259',	'5-260',	'5-261',	'5-262',	'5-263',	'5-264',	'5-265',	'5-266',	'5-267',	'5-268',	'5-269',	'5-270',	'5-271',	'5-272',	'5-273',	'5-274',	'5-275',	'5-276',	'5-277','5-279', '5-280', '5-281', '5-282', '5-283', '5-285',	'5-286',	'5-287',	'5-288',	'5-289',	'5-290',	'5-291',	'5-292',	'5-293',	'5-294',	'5-295',	'5-296',	'5-297',	'5-298',	'5-299',	'5-300',	'5-301',	'5-302',	'5-303',	'5-304',	'5-305',
'5-307',	'5-308',	'5-309',	'5-310',	'5-311',	'5-312',	'5-313',	'5-314',	'5-315',	'5-316',	'5-317',	'5-318',	'5-319',	'5-320',	'5-321',	'5-322',	'5-323',	'5-324',	'5-325',	'5-326',	'5-327',	'5-328',	'5-329','5-331',	'5-332',	'5-333',	'5-334',	'5-335',	'5-336',	'5-337',	'5-338',	'5-339',	'5-340',	'5-341',	'5-342',	'5-343',	'5-344',	'5-345',	'5-346',	'5-347',	'5-348',	'5-349',	'5-350',	'5-351','5-354',	'5-355',	'5-356',	'5-357',	'5-358','5-361',	'5-362',	'5-363',	'5-364',	'5-365',	'5-366',	'5-367',	'5-368',	'5-369',	'5-370',	'5-371',	'5-372',	'5-373',	'5-374',	'5-375',	'5-376',	'5-377',	'5-378',	'5-379',	'5-380',	'5-381',	'5-382',	'5-383',	'5-384',	'5-385',	'5-386',	'5-387',	'5-388',	'5-389',	'5-390',	'5-391',	'5-392',	'5-393',	'5-394',	'5-395',	'5-396',	'5-397',	'5-398',	'5-399',	'5-400',	'5-401',	'5-402',	'5-403',	'5-404',	'5-405',	'5-406',	'5-407',	'5-408',	'5-409',	'5-410',	'5-411',	'5-412',	'5-413',	'5-414',	'5-415',	'5-416',	'5-417',	'5-418',	'5-419',	'5-420',	'5-421',	'5-422',	'5-423',	'5-424',	'5-425',	'5-426',	'5-427',	'5-428',	'5-429',	'5-430',	'5-431',	'5-432',	'5-433',	'5-434',	'5-435',	'5-436',	'5-437',	'5-438',	'5-439',	'5-440',	'5-441',	'5-442', '5-456','5-457','5-458','5-459','5-499',	'5-500',	'5-501',	'5-502',	'5-503',	'5-504',	'5-505',	'5-506',	'5-507',	'5-508',	'5-509',	'5-510',	'5-511',	'5-512',	'5-513','5-515',	'5-516',	'5-517',	'5-518',	'5-519',	'5-520',	'5-521',	'5-522',	'5-523',	'5-524',	'5-525', '5-527',	'5-528',	'5-529',	'5-530',	'5-531',	'5-532',	'5-533',	'5-534',	'5-535',	'5-536',	'5-537',	'5-538',	'5-539',	'5-540',	'5-541')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```
### 5-730
Data Sensitive Quesnel
```{r, w5730}
#get the ogc_fids that belong to these.
wha_tags<-c('5-730')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 5-752
Data Sensitive Central Cariboo
```{r, w5752}
#get the ogc_fids that belong to these.
wha_tags<-c('5-752')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 6-056 to 6-057 Coastal Tailed Frog
For wha 6-056: do not harvest within the core area of special management zone.For what 6-057: Use partial harvesting system that maintain 70% basal area with the apropriate structure. No salavage should be carried out. see http://www.env.gov.bc.ca/wld/documents/wha/ASTR_6-056-57_ord.pdf
```{r, w6056}
#for 6-057 maintain 70% crownclosure for 100%
```

### 6-060 to 6-067 Coastal Tailed Frog
Use a silvicutlural system that maintains 70% residual stand volume and attributes of the natural stand structure profile. see http://www.env.gov.bc.ca/wld/documents/wha/ASTR_6-060-067_ord.pdf
```{r, w6060}
#maintain 70% crownclosure for 100%
```

### 6-283 to 6-286
Data Sensitive
```{r, w6283}
#get the ogc_fids that belong to these.
wha_tags<-c('6-283','6-284','6-285','6-286')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 6-333 Caribou
Primary forestry activties will focus in-block retention to include keey cariobu features and provide sufficient forest retantion to proviode visual screening. Within the Bulkley TSA: >60% of the SBSmc > 80 years,  < 28% of SBSmc < 40 year, > 45 % of SBSdk > 80 years, < 39% of SBSdk < 40 years. Within the Morice TSA: > 17% of SBSmc > 140 years, < 48 SBSmc < 40 years, > 8 % of SBSdk > 140 years, < 64% of SBSdk < 40 years  see http://www.env.gov.bc.ca/wld/documents/wha/RATA_6-333_ord_replaced_2018.pdf and http://www.env.gov.bc.ca/wld/documents/wha/RATA_6-333_amend_2018.pdf
```{r, w6333}
#Bulkley TSA: >60% of the SBSmc > 80 years,  < 28% of SBSmc < 40 year, > 45 % of SBSdk > 80 years, < 39% of SBSdk < 40 years. 

#Morice TSA: > 17% of SBSmc > 140 years, < 48 SBSmc < 40 years, > 8 % of SBSdk > 140 years, < 64% of SBSdk < 40 years
```

### 8-003 to 8-004 Grasshopper Sparrow
see http://www.env.gov.bc.ca/wld/documents/wha/GRSP_%208-003_8-004_ord.pdf
Do not construct roads. Do not use pesticides.
```{r, w8003}
#get the ogc_fids that belong to these.
wha_tags<-c('8-003','8-004')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 8-006 to 8-010 Bighorn Sheep
Follow a guide : https://www.for.gov.bc.ca/tasb/legsregs/fpc/fpcguide/other/wild/part2-21.htm#P1655_118642. For bighorn sheep there are no forestry constraints. see http://www.env.gov.bc.ca/wld/documents/wha/OVCC-8-006_ord.pdf
```{r, w8006}
#get the ogc_fids that belong to these.
wha_tags<-c('8-006','8-007','8-008','8-009','8-010')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 8-014 to 8-017 White-headed Woodpecker
Do not salvage timber. Protect and retain all ponderosa pine and douglas-fir >60cm. Use a partial cutting silvicultural system to maintain widely spaced late seral ponderosa pine and douglas fir. Group, single tree are recommended
see http://www.env.gov.bc.ca/wld/documents/wha/WHWO-8-014_ord.pdf
see http://www.env.gov.bc.ca/wld/documents/wha/WHWO-8-015_ord.pdf
see http://www.env.gov.bc.ca/wld/documents/wha/WHWO-8-016_ord.pdf
see http://www.env.gov.bc.ca/wld/documents/wha/WHWO-8-017_ord.pdf
```{r, w8014}
#get the ogc_fids that belong to these.
wha_tags<-c('8-014','8-015','8-016','8-017')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```


### 8-047, 8-051, 8-319 to 8-324 Brewer's Sparrow
Do not use pesticide - assumed in the model
see http://www.env.gov.bc.ca/wld/documents/wha/BRSP_8-051_8-319_to_8-324_ord.pdf
```{r, w8047}
#get the ogc_fids that belong to these.
wha_tags<-c('8-047','8-051','8-319','8-320','8-321','8-322','8-323','8-324')
ogc_fids_rm<-wha_cond[wha_cond$wha_tag %in% wha_tags, "ogc_fid"]
wha.ras[wha.ras[] %in% ogc_fids_rm]<-NA
```

### 8-053 to 8-064
Data Sensitive

### 8-090 to 8-094 Blotched Tiger Salamander
Do dont scarify harvested areas, do not place landings within management zone. Do not use pesticides
see http://www.env.gov.bc.ca/wld/documents/wha/AMTI_8-090_to_8-094_ord.pdf.

### 8-124 to 8-126 Western Screech Owl
Do not use pesticides. Do not salvage or harvest in core area. Do not construct roads or crossings in the core area. Use selective harvesting <= 20% basal area removal. Do not remove deciduous trees. Retain > 60% of trees in riparian areas. see http://www.env.gov.bc.ca/wld/documents/wha/WSOW_8-124_ord.pdf
```{r, w8124}
#crownclosure > 60% in riparian. crown closure > 20 for other area
```

### 8-232 Grizzly Bear
Forest practices will result in at least 10% of each management unit containing forest stands that exhibit a height of at least 19.5 m in patches that are at least 5 ha in size. Management units are defined as the area of each BEC subsonze within each landscape unit. see http://www.env.gov.bc.ca/wld/documents/wha/URAR_8-232_ord.pdf
```{r, w8232}
#10% of the area > 19.5 m height. 
```

### 8-233 Caribou 
GWM 1: Forest practises will result in a minimum of 30% of the timber exhibiting heights of at least 14 m, or have undergone self-pruning of the loer branches to allow for suitable securituy and movement between winter ranges. see http://www.env.gov.bc.ca/wld/documents/wha/RATA_8-233_ord.pdf
```{r, w8233}
# > 30 % having height > 14 m
```

### 8-261 to 8-262 Western Screech Owl
Do not use pesticides. Do not salvage or harvest in core area. Do not construct roads or crossings in the core area. Use selective harvesting <= 20% basal area removal. Do not remove deciduous trees. Retain > 60% of trees in riparian areas.see http://www.env.gov.bc.ca/wld/documents/wha/WSOW_8-261,8-262_ord.pdf
```{r, w8261}
#crownclosure > 60% in riparian. crown closure > 20 for other area
```

### 8-325 Grasshopper Sparrow
Do not construct roads or trails; Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/GRSP_8-325_ord.pdf

### 8-328 and 8-331 American badger
Do not ocnstruct roads, Do not harvest unless required to support ecological restoration. Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/TATA_8_328and331_ord.pdf
```{r, w8328}
# do not harvest 
```

### 8-332, 8-333, 8-357 to 8-361 Half-moon Hairstreak
Do not construct roads or trails; Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/SATSEM_%208-332_8-333_8-357_to_8-361_ord.pdf

### 8-335, 8-336 Great Basin Spadefoot
Do not construct roads or trails; Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/SPIN_8-335_8-336_ord.pdf

### 8-368 to 8-372
Data Sensitive

### 8-373 Grizzly Bear
Do not conduct primary forest activities between May 1 and June 20th. Do not plant trees within a 500 m specified area of polygons. Do not construct roads within 50 m of habitat features. Primary forest activities adjacent to avalanche tracks must retain forest cover that is at least 15 meters in ehight for a width of 100 meters. Do not use herbicide. see http://www.env.gov.bc.ca/wld/documents/wha/URAR_8-373_Ord.pdf
S-- Assuming these are operational ground rules. 

### 8-416 to 8-420 Great Basin Spadefoot
Do not construct roads or trails; Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/AMTI_SPIN_8-416_ord.pdf

### 8-424 Lewis' Woodpecker
Do not construct roads or trails; Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/LEWO_8-424_ord.pdf

### 8-426 to 8-433 Half-moon Hairstreak
Do not construct roads or trails; Do not use pesticides. see http://www.env.gov.bc.ca/wld/documents/wha/SATSEM_%208-426_to_8-433_ord.pdf

### 9-003 to 9-017 Mountain Goat
Refer to a guidebook: https://www.for.gov.bc.ca/tasb/legsregs/fpc/fpcguide/other/wild/index.htm. For Mountain goat: Do not construct roads. http://www.env.gov.bc.ca/wld/documents/wha/ORAM-9-003_ord.pdf

### 9-025 to 9-031
Data Sensitive 

### 9-032 to 9-034, 9-041 to 9-073, 9-104 to 9-106, 9-144 to 9-145 Caribou
For 9-032 to 9-034, 9-041 to 9-048, 9-050 to 9-072 and 9-106 No Harvest, no roads no pesticides. For remaining whas: Will no adversely effect lichen productivity, result in a network of conencted forest cover, result in pre-harvest pine leading stands to be established as pine leading stands. see http://www.env.gov.bc.ca/wld/documents/wha/RATA_9-032_034_041_073,104_106,144,145_ord.pdf

### 9-035 to 9-040, 9-102, 9-103 Caribou
No Harvest. No roads. see http://www.env.gov.bc.ca/wld/documents/wha/RATA_9-035_040,102,103_ord.pdf
```{r, w9035}
# no harvest
```

### Clean up and Commit data
```{r, clean_commit}
writeRaster(wha.ras, file=paste0(here(), "/wha.tif"), format="GTiff", overwrite=TRUE)

#upload to db
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here(), '/wha.tif -t 100x100 rast.zone_cond_wha | psql -d clus'), show.output.on.console = FALSE, invisible = TRUE)
```