---
title: "yieldCurveGeneration"
output: github_document
date: '2022-05-17'
---

```{r setup, include=FALSE, eval = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
source("C:/Users/KLOCHHEA/castor/R/functions/R_Postgres.R")
```

## Background

Two growth and yield models are being used to forecast the development of forested stands in British Columbia; TIPSY for human origin stands and VDYP for natural origin stands. The purpose of this code is generate a yield curve for every forested polygon in the forest inventory (VRI), as well as what the development of these stands will be post harvesting. The steps to complete this undertaking follow:

1. Create batch files for processing in VDYP and TIPSY

2. Import the outputs and inputs from 1. into postgresql

3. Choose a level of aggregation (if any) and any formatting (vdyp foreign keys are negative integers, tipsy foreign keys are positive integers with the exception of current tipsy yields)

4. Create rasters of the foreign key linking to the respective yield curve table (vdyp or tipsy output)

### Batch Files and Import

```{r, vdyp_batch_file}

#----VDYP
cmd <- paste0("\\copy vdyp_input_poly_2020 from program 'cmd /c \"type D:\\Data\\VDYP\\2020\\VEG_COMP_VDYP7_INPUT_POLY_TBL_2020.csv" , "\"' delimiter ',' csv header")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)

cmd <- paste0("\\copy vdyp_input_layer_2020 from program 'cmd /c \"type D:\\Data\\VDYP\\2020\\VEG_COMP_VDYP7_INPUT_LAYER_TBL_2020.csv" , "\"' delimiter ',' csv header")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)

cmd <- paste0("\\copy vdyp_output_2020 from program 'cmd /c \"type D:\\Data\\VDYP\\2020\\output_125.csv" , "\"' csv header")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)

cmd <- paste0("\\copy vdyp_error from program 'cmd /c \"type E:\\Data\\error_125.txt" , "\"' ")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)

#----Tipsy
meta_tbl<-read.table("F:/Data/TIPSY/2021/msyt_2021_prov/prov/MSYT_prov_reference.csv", sep= ",", header = TRUE)
colnames(meta_tbl)<-tolower(colnames(meta_tbl))

current_tbl<-read.table("F:/Data/TIPSY/2021/msyt_2021_prov/prov/MSYT_prov_current_input_output.csv", sep= ",", header = FALSE,nrows = 5000)
names(current_tbl)<-c("feature_id,", "stand1", "stand2", "year", "height", " vol_gross", "vol_conifer", "basal_area", "qmd", "sph", "vpt", "crown_closure", "vol_dec", "tvol")

future_tbl<-read.table("D:/Data/TIPSY/2020/MSYT_prov_future_input_output.csv", sep= ",", header = FALSE,nrows = 5000)
names(future_tbl)<-c("feature_id,", "stand1", "stand2", "year", "height", " vol_gross", "vol_conifer", "basal_area", "qmd", "sph", "vpt", "crown_closure", "vol_dec", "tvol")

#future_logged_tbl<-read.table("D:/Data/TIPSY/2020/MSYT_prov_future_logged_vdyp_input_output.csv", sep= ",", header = FALSE,nrows = 5000)
#names(future_logged_tbl)<-c("feature_id,", "stand1", "stand2", "year", "height", " vol_gross", "vol_conifer", "basal_area", "qmd", "sph", "vpt", "crown_closure", "vol_dec", "tvol")

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "tipsy_meta_2020"), value= meta_tbl, row.names = FALSE, overwrite = TRUE) 
DBI::dbWriteTable(conn, c("public", "tipsy_future_2020"), value= future_tbl, row.names = FALSE, overwrite = TRUE)
dbDisconnect(conn)
## Renamed table to tipsy_prov_2020
cmd <- paste0("\\copy tipsy_prov_2020 from program 'cmd /c \"type D:\\Data\\TIPSY\\2020\\MSYT_prov_future_input_output.csv" , "\"' delimiter ',' csv header")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)

## REnameed to tipsy_current_prov_2020
cmd <- paste0("\\copy tipsy_current_prov_2020 from program 'cmd /c \"type D:\\Data\\TIPSY\\2020\\MSYT_prov_current_input_output.csv" , "\"' delimiter ',' csv header")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)

```


## AR2021 is the 2020 VRI
Wildlife2 report is:
year, volume, height, qmd,crownclosure,basalarea,vol_dec, sph,vol_total, age,vol_conifer, vpt

## Choose level of aggregation
For VDYP curves run the following SQL : params/develop_vdyp_table_2020.sql
### Create raster of yield curve ids
```{r, yld_raster, eval = FALSE}
vri<-data.table(getSpatialQuery("SELECT yc_grp, geometry FROM vdyp_vri2020 where yc_grp IS NOt NULL"))
lu_table<-data.table(getTableQuery("SELECT distinct(yc_grp) FROM vdyp_2020 ORDER by yc_grp;"))
lu_table[,ycid:= seq_len(.N)]
lu_table[,ycid := ycid*-1]

colnames(lu_table)<-tolower(colnames(lu_table))
conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
DBI::dbWriteTable(conn, c("public", "yc_vdyp_vat_2020"), value= lu_table, row.names = FALSE, overwrite = TRUE) 
dbDisconnect(conn)

vri<-merge(vri, lu_table, by.x = 'yc_grp', by.y = 'yc_grp', all.x = TRUE)
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(getSpatialQuery("SELECT geometry FROM vdyp_vri2020 limit 1"))$proj4string, resolution = c(100, 100), vals = 0
)
class(vri)

yc.ras<-fasterize::fasterize(sf= st_as_sf(vri), raster = ProvRast , field = 'ycid')
yc.ras[is.na(yc.ras)]<-0
writeRaster(yc.ras, file="yc.tif", format="GTiff",  overwrite=TRUE)
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/yc.tif -t 100x100 rast.ycid_vdyp_2020 | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

```

For TIPSY curves the level of aggregation is determined by the RESULTS database. This results in polygons with data (they are reported in RESULTS) and polygons that get a BEC zone average (they are not resported in RESULTS). The latter is a result of future forested stands that have not been harvested but could be harvested in the future.

### Impute Crown closure for yields
see params/vdyp_crown_closure_imputation.rmd to preform the imputation


## TIPSY
### Load output to postgres
```{r, tcurrent}
meta_tbl<-read.table("D:/Data/TIPSY/2020/MSYT_prov_reference.csv", sep= ",", header = TRUE)
colnames(meta_tbl)<-tolower(colnames(meta_tbl))

current_tbl<-read.table("D:/Data/TIPSY/2020/MSYT_prov_current_input_output.csv", sep= ",", header = FALSE,nrows = 1)
names(current_tbl)<-c("feature_id,", "stand1", "stand2", "year", "height", " vol_gross", "vol_conifer", "basal_area", "qmd", "sph", "vpt", "crown_closure", "vol_dec", "tvol")

future_tbl<-read.table("D:/Data/TIPSY/2020/MSYT_prov_future_input_output.csv", sep= ",", header = FALSE,nrows = 1)
names(future_tbl)<-c("feature_id,", "stand1", "stand2", "year", "height", " vol_gross", "vol_conifer", "basal_area", "qmd", "sph", "vpt", "crown_closure", "vol_dec", "tvol")

future_logged_tbl<-read.table("D:/Data/TIPSY/2020/MSYT_prov_future_logged_vdyp_input_output.csv", sep= ",", header = FALSE,nrows = 1)
names(future_logged_tbl)<-c("feature_id,", "stand1", "stand2", "year", "height", " vol_gross", "vol_conifer", "basal_area", "qmd", "sph", "vpt", "crown_closure", "vol_dec", "tvol")

conn<-DBI::dbConnect(dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable(conn, c("public", "tipsy_meta_2020"), value= meta_tbl, row.names = FALSE, overwrite = TRUE) 
DBI::dbWriteTable(conn, c("public", "tipsy_future_2020"), value= future_tbl, row.names = FALSE, overwrite = TRUE)
dbDisconnect(conn)

#----Delete rows in the table then copy via below
cmd <- paste0("\\copy tipsy_prov_2020 from program 'cmd /c \"type D:\\Data\\TIPSY\\2020\\MSYT_prov_future_input_output.csv" , "\"' delimiter ',' csv header")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)

## REnameed to tipsy_current_prov_2020
cmd <- paste0("\\copy tipsy_current_prov_2020 from program 'cmd /c \"type D:\\Data\\TIPSY\\2020\\MSYT_prov_current_input_output.csv" , "\"' delimiter ',' csv header")
cmd <- shQuote(cmd)
system2("psql",args=c('-d clus -c',cmd),wait=TRUE,stderr=TRUE)
```

### Create the ycid rasters
```{r, ras_current}
current<- getSpatialQuery("select shape, feature_id*-1 as feature_id from veg_comp_lyr_r1_poly2019 where feature_id in (select distinct(ycid)*-1 from tipsy_current_prov_2020);")
yc.ras<-fasterize::fasterize(sf= current, raster = ProvRast , field = 'feature_id')
yc.ras[is.na(yc.ras[])]<-0

cns_cutblock<-getSpatialQuery("select wkb_geometry, 1 as cut from cns_cut_bl_polygon;")
cns_cutblock.ras<-fasterize::fasterize(sf= cns_cutblock, raster = ProvRast , field = 'cut')
cns_cutblock[is.na(cns_cutblock[])]<-0

yc.ras<-yc.ras*cns_cutblock.ras

writeRaster(yc.ras, "ycid_tipsy_current_2020.tif", datatype = 'INT4S', overwrite =T)
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/ycid_tipsy_current_2020.tif -t 100x100 rast.ycid_tipsy_current_2020 | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)

```

```{r, ras_future}
future<- getSpatialQuery("select shape, feature_id as feature_id from veg_comp_lyr_r1_poly2019 where feature_id in (select distinct(feature_id) from tipsy_prov_2020);")
yc.future.ras<-fasterize::fasterize(sf= future, raster = ProvRast , field = 'feature_id')
yc.future.ras[is.na(yc.future.ras)]<-0
writeRaster(yc.future.ras, "ycid_tipsy_prov_2020.tif", datatype = 'INT4U', overwrite =T)
system("cmd.exe", input = paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here::here(), '/R/params/ycid_tipsy_prov_2020.tif -t 100x100 rast.ycid_tipsy_prov_2020 | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/clus'), show.output.on.console = FALSE, invisible = TRUE)


```




