---
title: "Caribou RSF 3.0"
author: "Tyler Muhly"
date: "28/01/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (dplyr)
library (ggplot2)
library (lme4)
library (arm)
library (car)
library (optimx)
library (dfoptim)
library (kableExtra)
library (here)
```

## Introduction
Here I create a statistical model to quantify the effect of forestry disturbance on caribou distribution. The intent is to use the model to indicate the influence of current and potential future forestry development on caribou use of habitat, implemented as a module (i.e., rsfCLUS) in the caribou and land use simulator (CLUS). Statistical models were fit for the four caribou designatable units (DUs) in British Columbia (BC), (DU6, boreal; DU7, northern moutain; DU8, central mountain; DU9, southern moutnain), as defined by the [Committee on the Status of Endangered Wildlife in Canada (COSEWIC)](https://www.registrelep-sararegistry.gc.ca/default.asp?lang=En&n=E6271D78-1&offset=2#_01_4). DUs were modeled indepdently, as they are intended to represent groups with unique ecologicla characteristics, and potentially different responses to forestry disturbance. 

I use a resource selection function (RSF) framework to develop the statistical model ( [Boyce et al. 1999](https://www.sciencedirect.com/science/article/pii/S0169534799015931), [Johnson et al. 2006](https://wildlife.onlinelibrary.wiley.com/doi/abs/10.2193/0022-541X(2006)70[347:RSFBOU]2.0.CO;2)). This framework uses a logit model to calculate the relationship between caribou occurence and  habitat 'resources' measured using spatial data. Here I am only considering the effect of forestry disturbance 'resources', i.e., cutblocks and roads, on caribou occurrence. This approach simplifies and focuses the RSF onto modeling the effect of forestry disturbance on caribou dsitribution, and is not designed to accurately identify other factors that influence cariobu distribution.  

The caribou-forestry disturbance model (CFDM) created here can be used as a spatial indicator of current and simulated future effects of forestry activity on caribou habitat quality. For example, the sum of CFDM outputs can be calculated within caribou herd ranges or critical habitat types, and changes in the sum value can be used to indicate changes in forstry disturbance influencing caribou habitat quality over time. 

## Methods
I calculated the CFDM using a generalized linear mixed model (GLMM) with a logit link, using the [glmer function](https://www.rdocumentation.org/packages/lme4/versions/1.1-21/topics/glmer) from the [lme4](https://cran.r-project.org/web/packages/lme4/lme4.pdf) package in [program R](https://www.r-project.org/). I fit the model using caribou location data from telemetry collars placed on a sample of caribou (n = 468 animals, 507,987 locations) from across BC, between 2008 to 2018. These data were compiled from the government of BC's [Species Inventory (SPI) database](https://www2.gov.bc.ca/gov/content/environment/plants-animals-ecosystems/wildlife/wildlife-data-information/search-for-wildlife-data-information), [BC Oil and Gas Research and Innovation Society (OGRIS) data](http://www.bcogris.ca/boreal-caribou-home), and data from regional wildlife biologists in the BC government that was not yet entered into these databases. These data specified the locations on the landscape that were 'used' by caribou (*sensu* Boyce et al. 1999), i.e., the 1's in the binomial distribution of the dependent variable. I had no capture data for these animals, but it is likely the majority of the animals sampled were adult females, as the focus of caribou monitoring in BC is on measuring survival of adult females and recruitment of calves. Data was collected using a wide variety of telemetry collar technologies (e.g., GPS, ARGOS) and suppliers (e.g., Lotek, ATS, Telonics), and with varying location fix rates (e.g., 2 hours to 12 hours). All data were collected under provincial government permits amd following provincial animal care and handling protocols.

I sampled locations 'available' to caribou, i.e., the 0's in the binomial distribution of the dependent variable, by calculating the seasonal home ranges of individual animals and randomly sampling locations within these areas. I calculated home ranges using the kernelUD function in the adehabitatHR ( [Calenge et al. 2011](https://cran.r-project.org/web/packages/adehabitatHR/vignettes/adehabitatHR.pdf)) package of Program R. I varied the smoothing parameter (*h*) in the bivariate normal kernel algorithm and visually assesed the fit of 95% kernel polygons to the telemetry data. I selected the polygons with an *h* value that appeared to best fit the data ( [Hemson et al. 2005](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2656.2005.00944.x), [Calenge et al. 2011](https://cran.r-project.org/web/packages/adehabitatHR/vignettes/adehabitatHR.pdf)), i.e., that reasonably formed contiguous habitat areas (i.e., connected patches) without including large extents greater than 1km from telemetry locations. Animals with less than 50 locations in a season were removed from the analysis, as this is considered the minimum number of locations needed to calculate a home range ( [Seaman et al. 1999](https://www.jstor.org/stable/3802664?seq=1), [Kernohan et al. 2001](https://www.sciencedirect.com/science/article/pii/B9780124977815500062)). Seasons were defined as: summer (15-May to 31-Oct), early winter (01-Nov to 15-Jan) and late winter	(16-Jan to 14-May), based on a review of the literature on variation in the seasonal distribution of caribou in British Columbia. Within each seasonal home range, I randomly sampled 1,000 locations. 

I estimated the distance of 'used' and 'available' locations to the nearest resource road and cutblock. Cutblock locations were estimated using the [consolidated cutblocks](https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-) data compiled by the BC government. Road locations were estimated using data compiled to support the [British Columbia Cumulative Effects Framework](https://www2.gov.bc.ca/gov/content/environment/natural-resource-stewardship/cumulative-effects-framework). This data is not as easily accessible to the public, but is not private or proprietary, and thus can be requested from the cumulative effects program. The data classifies roads into various types. Our focus was on roads developed for resource extraction (particularly forestry), thus, we classified all unpaved road types as 'resource roads'. Cutblock and roads data were rasterized at a 1ha resolution, and the Euclidean distance of each raster with a cutblock or resource road was calculated in ArcGIS at 1 ha resolution and attributed to corresponding 'used' and 'available' caribou locations. 

I fit GLMMs with distance to cutblock and distance to road covariates as fixed effects and random effects at the individual animal level. These random effects accounted for individual variation in response to cutblocks and roads in the model, so that the fixed effects can be considered as 'population‐level' effects (i.e.,the effect on an 'average' animal) of cutblocks and roads on caribou distribution ( [Gillies et al. 2006](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2656.2006.01106.x)). I examined the data for variability in the response to cutblocks and roads at the herd-level, assuming animals from the same herd had similar reponses, and also fit GLMMs with random effects for cutblocks and roads at the herd level.   

I also fit models with functional reponses by caribou to cutblocks and roads. 
Individual wildlife, including caribou, likely respond to habitat differently (i.e., avoid or use roads or cutblocks) depending on the availability of that habitat to them (i.e., the degree that their home range is fragmented by roads or cutblocks). Functional response models in RSFs empirically account for this theroetical response by including an interaction term between the habitat feature at a location and the availability of that feature in the surronding environment ( [Matthiopoulos et al. 2011](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/10-0751.1)). I fit models with and without functional responses to roads and cutblocks and visualy assessed whether a functional response was evident, i.e., caribou use of cutblocks and roads varied as the average distance to cutblocks and roads changed within their home ranges. I calculated the availability of cutblocks and roads to an individual animal as the average distance to cutblocks and roads at 'available' locations sampled in the home range of that animal (see [Matthiopoulos et al. 2011](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/10-0751.1)). 

This model fitting process was completed to identify the statistical relationship between caribou distribution and forestry disturbance that was generalizable across a caribou DU, without considering the effect of other factors that influence caribou distribution. The theoretical basis for this approach is that these disturbance factors have a significant influence on caribou distribution, regardless of other habitat features. Indeed, cutblocks and linear features from forestry have routinely been shown to have a strong influence on caribou distribution (e.g., [Courbin et al. 2009](https://link.springer.com/article/10.1007/s10980-009-9389-x), [DeCesare et al. 2012](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/11-1610.1), [Mumma et al. 2018](https://www.sciencedirect.com/science/article/pii/S0006320718307225)) and survival ( [Wittmer et al. 2007](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2656.2007.01220.x), [Johnson et al. 2015](https://www.sciencedirect.com/science/article/pii/S0006320715001160)).

Clearly, other habitat characteristics besides forestry disturbance influence caribou distribution (e.g., terrain and vegetation, as they relate to food and predation risk; see for example, [Terry et al. 2000](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1046/j.1365-2664.2000.00523.x), [Apps et al. 2001]( http://www.env.gov.bc.ca/cariboo/env_stewardship/wildlife/inventory/caribou/northcar/hmi/hsi06-01.pdf), [Johnson et al. 2004](https://besjournals.onlinelibrary.wiley.com/doi/10.1111/j.0021-8901.2004.00899.x), [Apps & McLellan 2006](https://www.sciencedirect.com/science/article/pii/S000632070500546X)), and I initially attempted to fit models with some of these other factors. However, this led to the development of complex habitat models that did not improve my ability to estimate the effects of disturbance on caribou distribution. Instead, model building and interpretation became bogged down due to the difficulty in fitting a generalizable habitat model to unique habitats acorss a given DU. However, I did evaluate correlation between the forestry disturbance factors modeled here and other habtiat features (e.g., elevation, slope, forest stand characteristics) to ensure they were not completely confounded. Specifically, I tested for correlations using a Spearman correlation, ensuring correlation coefficients between covariates were less than 0.7, and by evalauting variance inflation factors (VIFs) in simple generalized linear models (GLMs), and ensuring VIFs were less than 10 ( [DeCesare et al. 2012](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/11-1610.1)). This provided reassurance that distance to cublocks or roads was not completely confounded with some other habitat feature driving caribou distribution.      

```{r, Load data and transform, eval = T, echo = F, message = F, error = F, results = 'hide'}
# load data
rsf.data.du6 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du6.csv"))
rsf.data.du7 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du7.csv"))
rsf.data.du8 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du8.csv"))
rsf.data.du9 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du9.csv"))

# calculate fxn response covars
avail.rsf.data.du6 <- subset (rsf.data.du6, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du6$distance_to_resource_road,  
                          avail.rsf.data.du6$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du6$dist_cut_min,  
                          avail.rsf.data.du6$animal_id, mean)
inds <- as.character (rsf.data.du6$animal_id)
rsf.data.du6 <- cbind (rsf.data.du6, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

avail.rsf.data.du7 <- subset (rsf.data.du7, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du7$distance_to_resource_road, 
                           avail.rsf.data.du7$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du7$dist_cut_min, 
                          avail.rsf.data.du7$animal_id, mean)
inds <- as.character (rsf.data.du7$animal_id)
rsf.data.du7 <- cbind (rsf.data.du7, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

avail.rsf.data.du8 <- subset (rsf.data.du8, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du8$distance_to_resource_road, 
                                   avail.rsf.data.du8$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du8$dist_cut_min, 
                          avail.rsf.data.du8$animal_id, mean)
inds <- as.character (rsf.data.du8$animal_id)
rsf.data.du8 <- cbind (rsf.data.du8, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

avail.rsf.data.du9 <- subset (rsf.data.du9, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du9$distance_to_resource_road, 
                           avail.rsf.data.du9$animal_id, mean)
dist_cut_min_E <- tapply (rsf.data.du9$dist_cut_min, 
                          rsf.data.du9$animal_id, mean)
inds <- as.character (rsf.data.du9$animal_id)
rsf.data.du9 <- cbind (rsf.data.du9, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

rsf.data.du6$pttype <- as.factor (rsf.data.du6$pttype)
rsf.data.du7$pttype <- as.factor (rsf.data.du7$pttype)
rsf.data.du8$pttype <- as.factor (rsf.data.du8$pttype)
rsf.data.du9$pttype <- as.factor (rsf.data.du9$pttype)

rm (avail.rsf.data.du6, avail.rsf.data.du7, avail.rsf.data.du8, avail.rsf.data.du9, inds, 
    dist_cut_min_E, dist_res_road_E)
gc ()
```

## Results
### DU6
Caribou location data in DU6 was collected from 160 animals from the Calendar, Chinchaga, Maxhamish, Westside Fort Nelson (formerly Parker and Prophet ranges), and Snake-Sahtaneh herds. The number of animals sampled in each herd ranged from 5 to 43 and the number of telemetry locations ranged from 8,144 to 57,307 per herd (Table 1).

```{r, du6, data summary, eval = T, echo = F, message = F, eval = T}
# number of animals, by herd
count.animals.herd <- rsf.data.du6  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du6  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 1. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU6 (Boreal).<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd-Level Effect of Forestry on Caribou Distribution
There were some small differences in herd response to resource roads in DU6 (Fig. 1). For example, caribou in the Calendar, Chinchaga and Prophet herds tended to be further from roads then in other herds. A random effect for distance to road was included in the GLMM to account for this variability.  
```{r, du6 Herd road effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du6, aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 1. Distance to Resource Road at Available (0) and Used (1) Locations by Caribou Herd in DU6",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6),
         plot.title = element_text (size = 12))
```

There was variability in caribou response to cutblocks across herds in DU6 (Fig. 2). For example, caribou in the Calendar adn Maxhamish herds used areas closer to cutblocks compared to other herds. A random effect for distance to cutblock was included in the GLMM to account for this variability.

```{r, du6 Herd cutblock effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du6, aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 2. Distance to Cutblock at Available (0) and Used (1) Locations by Caribou Herd in DU6",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6),
         plot.title = element_text (size = 12))
```

#### Caribou-Forestry Disturbance Model
I fit a model with a functional response for distance to road but not cutblock (Table 4). The model indicated a weak (non-significant), negative effect of cutblocks on caribou distribution. Visual assessment of model predictions indicated no clear change in caribou use of habitat near cutblocks as the average distance to cublock in their home ranges changed. However, there was clearly greater avoidance of roads by caribou as the distance to roads sampled within home ranges decreased (see interactive plot below). 

```{r, du6 model, echo = T, message = F, eval = F}
# model spec
model.lme4.du6.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all + 
                                                distance_to_resource_road +
                                                dist_rd_E +
                                                distance_to_resource_road*dist_rd_E +
                                      (dist_cut_min_all + distance_to_resource_road || HERD_NAME) +
                                      (dist_cut_min_all + distance_to_resource_road || animal_id),
                                      data = rsf.data.du6, 
                                      family = binomial (link = "logit"),
                                      verbose = T) 
# check residuals
binnedplot (fitted (model.lme4.du6.cut.rd.fxn), 
             residuals(model.lme4.du6.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "DU6 Model Binned Residual Plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
```

```{r, du6 model fixed effects coeffs, echo = F, message = F, eval = T}
# model.coeffs <- as.data.frame (coef (summary (model.lme4.du6.cut.rd.fxn)))

du6.fe <- read.csv (here ("R/caribou_habitat/data", "table_du6_model_fixed_coeffs_v3.csv"))

kable (du6.fe,
       caption = "<b>Table 4. Fixed Effect Coefficients of the DU6 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)

```

```{r, du6 model road fxn response, echo = F, message = F, eval = T}
data.road.test <- read.csv (here ("R/caribou_habitat/data", "rd_fxn_test_data.csv"))
data.road.test <- data.road.test [c(1:248),] # first 10km only  
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_res_road_E,
           data.road.test$predict_du6, 
           xlab = "Distance to Road",
           ylab = "Average Distance to Road (HR)", 
           zlab = "Caribou Use",
           surface = F,
           pch = 6, point.col = "blue",
           axis.ticks = T,
           grid = T)
```

Random effects in the DU6 model indicated that caribou response to roads was relatively consistent across herds (Table 5). However, there was much more variability in the caribou response to cutblocks. Cariobu in the Calendar, Chinchaga and Prophet herds showed weak use of habtiat near cutblocks, whereas caribou in teh Maxhamish, Parker and Snake-Sahtaneh showed avoidance of cutblocks.

```{r, du6 model random effects coeffs, echo = F, message = F, eval = T}
du6.re <- read.csv (here ("R/caribou_habitat/data", "table_du6_model_herd_re_coeffs_v3.csv"))

kable (du6.re,
       caption = "<b>Table 5. Random Effect Herd-Level Coefficients of the DU6 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

### DU7
Caribou location data in DU7 was collected from 131 animals from the Charlotte Alplands, Chase, Finlay, Frog, Graham, Itch-Ilgachuz, Muskwa, Pink Mountain, Rainbows, Spatsizi, Telkwa, Tsenaglode and Tweedsmuir herds. The number of animals sampled ranged from 1 to 35 per herd and the number of telemetry locations ranged from 856 to 41,837 per herd (Table 6).

```{r, DU7, data summary, echo = F, message = F, eval = T}
count.animals.herd <- rsf.data.du7  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du7  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 6. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU7.<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd-Level Effect of Forestry on Caribou Distribution
There was variability in caribou response to resource roads across caribou herds in DU7 (Fig. 3). For example, caribou in the Chase, Graham, Itcha-Ilgachuz, Tsenaglode and Tweedsmuir tended to be further from roads, whereas caribou in the Frog tended ot be closer to roads. A random effect for distance to road was included in the GLMM to account for this variability.

```{r, du7 Herd road effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du7, aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 3. Distance to Resource Road at Available (0) and Used (1) Locations by Caribou Herd in DU7",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6),
         plot.title = element_text (size = 12))
```

There was variability in caribou response to cutblocks across herds in DU7 (Fig. 4). For example, caribou in the Itcha-Ilgachuz, Muskwa, Pink Mountain and Rainbows herds used areas further from cutblocks, whereas cariou in the Frog and Tsenaglode herds used areas closer to cutblocks. A random effect for distance to cutblock was included in the GLMM to account for this variability.

```{r, du7 Herd cutblock effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du7, aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 4. Distance to Cutblock at Available (0) and Used (1) Locations by Caribou Herd in DU7",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6),
         plot.title = element_text (size = 12))
```

#### Caribou-Forestry Disturbance Model
I fit a model with a functional response for distance to road but not cutblock (Table 5). The model indicated a weak (non-significant), negative effect of cutblocks on caribou distribution. Visual assessment of model predictions indicated no clear change in caribou use of habitat near cutblocks as the average distance to cublock in their home ranges changed. However, there was greater avoidance of roads by caribou as the distance to roads sampled within home ranges decreased (see interactive plot below). 

```{r, du7 model, echo = T, message = F, eval = F}
# model spec
model.lme4.du7.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all +
                                             distance_to_resource_road +
                                             dist_rd_E +
                                             distance_to_resource_road*dist_rd_E +
                                        (dist_cut_min_all + distance_to_resource_road || animal_id) +                                         (dist_cut_min_all + distance_to_resource_road || HERD_NAME),
                                  data = rsf.data.du7,
                                  family = binomial (link = "logit"),
                                  verbose = T)
# check residuals
binnedplot (fitted (model.lme4.du7.cut.rd.fxn), 
             residuals(model.lme4.du7.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "DU7 Model Binned Residual Plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
```

```{r, du7 model fixed effects coeffs, echo = F, message = F, eval = T}
# model.coeffs <- as.data.frame (coef (summary (model.lme4.du7.cut.rd.fxn)))
du7.fe <- read.csv (here ("R/caribou_habitat/data", "table_du7_model_fixed_coeffs_v3.csv"))
kable (du7.fe,
       caption = "<b>Table 5. Fixed Effect Coefficients of the DU7 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

```{r, du7 model road fxn response, echo = F, message = F, eval = T}
data.road.test <- read.csv (here ("R/caribou_habitat/data", "rd_fxn_test_data.csv"))
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_res_road_E,
           data.road.test$predict_du7, 
           xlab = "Distance to Road",
           ylab = "Average Distance to Road (HR)", 
           zlab = "Caribou Use",
           surface = F,
           pch = 6, point.col = "blue",
           axis.ticks = T,
           grid = T)
```

Random effects in the DU7 model indicated that caribou avodied roads consistently across herds, although there was significant variability in the strength of avoidance (Table 6). There was more variability in the caribou response to cutblocks. Cariobu in the Charlotte Alplands, Finlay, Frog, Graham, Pink Mountain, Spatsizi, Tsenaglode and TWeedsmuir tended to be closer to cutblocks, whereas caribou in other herds tended to avoid cutblocks. 

```{r, du7 model random effects coeffs, echo = F, message = F, eval = T}
du7.re <- read.csv (here ("R/caribou_habitat/data", "table_du7_model_herd_re_coeffs_v3.csv"))

kable (du7.re,
       caption = "<b>Table 6. Random Effect Herd-Level Coefficients of the DU7 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

### DU8
Caribou location data in DU8 was collected from 152 animals from the Burnt Pine, Kennedy Siding, Moberly, Narraway, Quintette and Scott herds. The number of animals sampled per herd ranged from 8 to 35 and the number of telemetry locations per herd ranged from 5,414 to 65,431 per herd (Table 6).

```{r, DU8, data summary, echo = F, message = F, eval = T}
count.animals.herd <- rsf.data.du8  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du8  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 7. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU8.<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd-Level Effect of Forestry on Caribou Distribution
There was variability in caribou response to resource roads across caribou herds in DU8 (Fig. 5). For example, caribou in the Burnt Pine, Kennedy Siding and Scott herds tended to be closer to roads, whereas caribou in the Moberly, Narraway and Quintette tended to be further from roads. A random effect for distance to road was included in the GLMM to account for this variability.

```{r, du8 Herd road effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du8, aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 5. Distance to Resource Road at Available (0) and Used (1) Locations by Caribou Herd in DU8",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 7),
         plot.title = element_text (size = 10))
```

There was variability in caribou response to cutblocks across herds in DU8 (Fig. 6). For example, caribou in the Quintette herd tended to use areas further from cutblocks, whereas caribou in the Narraway herd tended to be closer to cutblocks. A random effect for distance to cutblock was included in the GLMM to account for this variability.

```{r, du8 Herd cutblock effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du8, aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 4. Distance to Cutblock at Available (0) and Used (1) Locations by Caribou Herd in DU8",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6),
         plot.title = element_text (size = 12))
```

#### Caribou-Forestry Disturbance Model
I fit a model with a functional response for distance to road but not cutblock (Table 8). The model indicated a positive populaiton-level effect of cutblocks on caribou distribution and negative popaultion-level effect of roads on caribou distribution. Visual assessment of model predictions indicated no clear change in caribou use of habitat near cutblocks as the average distance to cublock in their home ranges changed. However, there was greater avoidance of roads by caribou as the distance to roads sampled within home ranges decreased (see interactive plot below). 

```{r, du8 model, echo = T, message = F, eval = F}
# model spec
model.lme4.du8.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all + 
                                            distance_to_resource_road +
                                            dist_rd_E + 
                                            distance_to_resource_road*dist_rd_E +
                                  (dist_cut_min_all + distance_to_resource_road || HERD_NAME) +
                                  (dist_cut_min_all + distance_to_resource_road || animal_id),
                                  data = rsf.data.du8, 
                                  family = binomial (link = "logit"),
                                  verbose = T) 
# check residuals
binnedplot (fitted (model.lme4.du8.cut.rd.fxn), 
             residuals(model.lme4.du8.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "DU8 Model Binned Residual Plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
```

```{r, du8 model fixed effects coeffs, echo = F, message = F, eval = T}
# model.coeffs <- as.data.frame (coef (summary (model.lme4.du8.cut.rd.fxn)))
du8.fe <- read.csv (here ("R/caribou_habitat/data", "table_du8_model_fixed_coeffs_v3.csv"))
kable (du8.fe,
       caption = "<b>Table 8. Fixed Effect Coefficients of the DU8 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

```{r, du8 model road fxn response, echo = F, message = F, eval = T}
data.road.test <- read.csv (here ("R/caribou_habitat/data", "rd_fxn_test_data.csv"))
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_res_road_E,
           data.road.test$predict_du8, 
           xlab = "Distance to Road",
           ylab = "Average Distance to Road (HR)", 
           zlab = "Caribou Use",
           surface = F,
           pch = 6, point.col = "blue",
           axis.ticks = T,
           grid = T)
```

Random effects in the DU8 model indicated that caribou avoided roads consistently across herds, although there was variability in the strength of avoidance (Table 9). There was also generally consistent use of areas close to cutblocks acorss herds, with the exception of the Quintette herd, where caribou avoided cutblocks.

```{r, du8 model random effects coeffs, echo = F, message = F, eval = T}
du8.re <- read.csv (here ("R/caribou_habitat/data", "table_du8_model_herd_re_coeffs_v3.csv"))

kable (du8.re,
       caption = "<b>Table 9. Random Effect Herd-Level Coefficients of the DU8 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

### DU9
Caribou location data in DU9 was collected from 25 animals from the Hart Ranges, Nakusp and South Selkirks herds. The number of animals sampled per herd ranged from 6 to 11 and the number of telemetry locations per herd ranged from 1,821 to 4,917 per herd (Table 10).

```{r, du9, data summary, echo = F, message = F, eval = T}
count.animals.herd <- rsf.data.du9  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du9  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 10. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU9.<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd-Level Effect of Forestry on Caribou Distribution
There was variability in caribou response to resource roads across caribou herds in DU9 (Fig. 7). For example, caribou in the Hart Ranges tended to be closer to roads, whereas caribou in the Nakusp and South Slekirks tended to be further from roads. A random effect for distance to road was included in the GLMM to account for this variability.

```{r, du9 Herd road effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du9, aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 7. Distance to Resource Road at Available (0) and Used (1) Locations by Caribou Herd in DU9",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 8),
         plot.title = element_text (size = 11))
```

There was variability in caribou response to cutblocks across herds in DU9 (Fig. 8). For example, caribou in the Hart Ranges herd tended to use areas closer to cutblocks, whereas caribou in the Nakusp herd tended to be further from cutblocks. A random effect for distance to cutblock was included in the GLMM to account for this variability.

```{r, du9 Herd cutblock effect plot, echo = F, message = F, eval = T}
ggplot (rsf.data.du9, aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 8. Distance to Cutblock at Available (0) and Used (1) Locations by Caribou Herd in DU9",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 8),
         plot.title = element_text (size = 11))
```

#### Caribou-Forestry Disturbance Model
I fit a model with a functional response for distance to road but not cutblock (Table 11). The model included negative population-level effects of cutblocks and roads on caribou distribution. However, the effect of cutblocks was weaker than for roads. Visual assessment of model predictions indicated no clear change in caribou use of habitat near cutblocks as the average distance to cublock in their home ranges changed. However, there was greater avoidance of roads by caribou as the distance to roads sampled within home ranges decreased (see interactive plot below). 

```{r, du9 model, echo = T, message = F, eval = F}
# model spec
model.lme4.du9.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all + 
                                                distance_to_resource_road +
                                                dist_rd_E +
                                                distance_to_resource_road*dist_rd_E +
                                      (dist_cut_min_all + distance_to_resource_road || HERD_NAME) +
                                      (dist_cut_min_all + distance_to_resource_road || animal_id),
                                      data = rsf.data.du9, 
                                      family = binomial (link = "logit"),
                                      verbose = T) 
# check residuals
binnedplot (fitted (model.lme4.du9.cut.rd.fxn), 
             residuals(model.lme4.du9.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "DU9 Model Binned Residual Plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
```

```{r, du9 model fixed effects coeffs, echo = F, message = F, eval = T}
# model.coeffs <- as.data.frame (coef (summary (model.lme4.du9.cut.rd.fxn)))
du9.fe <- read.csv (here ("R/caribou_habitat/data", "table_du9_model_fixed_coeffs_v3.csv"))
kable (du9.fe,
       caption = "<b>Table 11. Fixed Effect Coefficients of the DU9 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

```{r, du9 model road fxn response, echo = F, message = F, eval = T}
data.road.test <- read.csv (here ("R/caribou_habitat/data", "rd_fxn_test_data.csv"))
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_res_road_E,
           data.road.test$predict_du9, 
           xlab = "Distance to Road",
           ylab = "Average Distance to Road (HR)", 
           zlab = "Caribou Use",
           surface = F,
           pch = 6, point.col = "blue",
           axis.ticks = T,
           grid = T)
```

Random effects in the DU9 model indicated that caribou avoided roads consistently across herds, although there was variability in the strength of avoidance (Table 12). There was variability in use of areas close to cutblocks acorss herds, where caribou in teh Nakuysp herd tended to strongly avoid cutblocks, whereas cariobu in the other herds did not.

```{r, du9 model random effects coeffs, echo = F, message = F, eval = T}
du9.re <- read.csv (here ("R/caribou_habitat/data", "table_du9_model_herd_re_coeffs_v3.csv"))

kable (du9.re,
       caption = "<b>Table 12. Random Effect Herd-Level Coefficients of the DU9 Caribou-Forestry Disturbance Model.<b>",
       digits = 3) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

### Conclusions





difference sin effect, but consistent avoidance and fxn reponseot to roads

efefct of cutblocks interstingly ambiguous, but egenral avoindace

road efefct could be overall disturabnce efefct; many types; confounded to soem degree, btu not overly corralted with other factors, e.g., elevation, cliamte



concluisn - simialr to decesare, third order dirven by lienar, second order by numericla response (cut)
