---
title: "Caribou RSF 3.0"
author: "Tyler Muhly"
date: "28/01/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (dplyr)
library (ggplot2)
library (lme4)
library (arm)
library (car)
library (optimx)
library (dfoptim)
library (kableExtra)
library (here)
```

## Introduction
Here I create a statistical model to quantify the effect of forestry disturbance on caribou distribution. The intent is to use the model to indicate the influence of current and potential future forestry development on caribou use of habitat, implemented as a module (i.e., rsfCLUS) in the caribou and land use simulator (CLUS). Statistical models were fit for the four caribou designatable units (DUs) in British Columbia (BC), (DU6, boreal; DU7, northern moutain; DU8, central mountain; DU9, southern moutnain), as defined by the [Committee on the Status of Endangered Wildlife in Canada (COSEWIC)](https://www.registrelep-sararegistry.gc.ca/default.asp?lang=En&n=E6271D78-1&offset=2#_01_4). DUs were modeled indepdently, as they are intended to represent groups with unique ecologicla characteristics, and potentially different responses to forestry disturbance. 

I use a resource selection function (RSF) framework to develop the statistical model ( [Boyce et al. 1999](https://www.sciencedirect.com/science/article/pii/S0169534799015931), [Johnson et al. 2006](https://wildlife.onlinelibrary.wiley.com/doi/abs/10.2193/0022-541X(2006)70[347:RSFBOU]2.0.CO;2)). This framework uses a logit model to calculate the relationship between caribou occurence and  habitat 'resources' measured using spatial data. Here I am only considering the effect of forestry disturbance 'resources', i.e., cutblocks and roads, on caribou occurrence. This approach simplifies and focuses the RSF onto modeling the effect of forestry disturbance on caribou dsitribution, and is not designed to accurately identify other factors that influence cariobu distribution.  

The caribou-forestry disturbance model (CFDM) created here can be used as a spatial indicator of current and simulated future effects of forestry activity on caribou habitat quality. For example, the sum of CFDM outputs can be calculated within caribou herd ranges or critical habitat types, and changes in the sum value can be used to indicate changes in forstry disturbance influencing caribou habitat quality over time. 

## Methods
I calculated the CFDM using a generalized linear mixed model (GLMM) with a logit link, using the [glmer function](https://www.rdocumentation.org/packages/lme4/versions/1.1-21/topics/glmer) from the [lme4](https://cran.r-project.org/web/packages/lme4/lme4.pdf) package in [program R](https://www.r-project.org/). I fit the model using caribou location data from telemetry collars placed on a sample of caribou (n = 468 animals, 507,987 locations) from across BC, between 2008 to 2018. These data were compiled from the government of BC's [Species Inventory (SPI) database](https://www2.gov.bc.ca/gov/content/environment/plants-animals-ecosystems/wildlife/wildlife-data-information/search-for-wildlife-data-information), [BC Oil and Gas Research and Innovation Society (OGRIS) data](http://www.bcogris.ca/boreal-caribou-home), and data from regional wildlife biologists in the BC government that was not yet entered into these databases. These data specified the locations on the landscape that were 'used' by caribou (*sensu* Boyce et al. 1999), i.e., the 1's in the binomial distribution of the dependent variable. I had no capture data for these animals, but it is likely the majority of the animals sampled were adult females, as the focus of caribou monitoring in BC is on measuring survival of adult females and recruitment of calves. Data was collected using a wide variety of telemetry collar technologies (e.g., GPS, ARGOS) and suppliers (e.g., Lotek, ATS, Telonics), and with varying location fix rates (e.g., 2 hours to 12 hours). All data were collected under provincial government permits amd following provincial animal care and handling protocols.

I sampled locations 'available' to caribou, i.e., the 0's in the binomial distribution of the dependent variable, by calculating the seasonal home ranges of individual animals and randomly sampling locations within these areas. I calculated home ranges using the kernelUD function in the adehabitatHR ( [Calenge et al. 2011](https://cran.r-project.org/web/packages/adehabitatHR/vignettes/adehabitatHR.pdf)) package of Program R. I varied the smoothing parameter (*h*) in the bivariate normal kernel algorithm and visually assesed the fit of 95% kernel polygons to the telemetry data. I selected the polygons with an *h* value that appeared to best fit the data ( [Hemson et al. 2005](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2656.2005.00944.x), [Calenge et al. 2011](https://cran.r-project.org/web/packages/adehabitatHR/vignettes/adehabitatHR.pdf)), i.e., that reasonably formed contiguous habitat areas (i.e., connected patches) without including large extents greater than 1km from telemetry locations. Animals with less than 50 locations in a season were removed from the analysis, as this is considered the minimum number of locations needed to calculate a home range ( [Seaman et al. 1999](https://www.jstor.org/stable/3802664?seq=1), [Kernohan et al. 2001](https://www.sciencedirect.com/science/article/pii/B9780124977815500062)). Seasons were defined as: summer (15-May to 31-Oct), early winter (01-Nov to 15-Jan) and late winter	(16-Jan to 14-May), based on a review of the literature on variation in the seasonal distribution of caribou in British Columbia. Within each seasonal home range, I randomly sampled 1,000 locations. 

I estimated the distance of 'used' and 'available' locations to the nearest resource road and cutblock. Cutblock locations were estimated using the [consolidated cutblocks](https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-) data compiled by the BC government. Road locations were estimated using data compiled to support the [British Columbia Cumulative Effects Framework](https://www2.gov.bc.ca/gov/content/environment/natural-resource-stewardship/cumulative-effects-framework). This data is not as easily accessible to the public, but is not private or proprietary, and thus can be requested from the cumulative effects program. The data classifies roads into various types. Our focus was on roads developed for resource extraction (particularly forestry), thus, we classified all unpaved road types as 'resource roads'. Cutblock and roads data were rasterized at a 1ha resolution, and the Euclidean distance of each raster with a cutblock or resource road was calculated in ArcGIS at 1 ha resolution and attributed to corresponding 'used' and 'available' caribou locations. 

I fit GLMMs with distance to cutblock and distance to road covariates as fixed effects and random effects at the individual animal level. These random effects accounted for individual variation in response to cutblocks and roads in the model, so that the fixed effects can be considered as 'population‐level' effects (i.e.,the effect on an 'average' animal) of cutblocks and roads on caribou distribution ( [Gillies et al. 2006](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2656.2006.01106.x)). I examined the data for variability in the response to cutblocks and roads at the herd-level, assuming animals from the same herd had similar reponses, and also fit GLMMs with random effects for cutblocks and roads at the herd level.   

I also fit models with functional reponses by caribou to cutblocks and roads. 
Individual wildlife, including caribou, likely respond to habitat differently (i.e., avoid or use roads or cutblocks) depending on the availability of that habitat to them (i.e., the degree that their home range is fragmented by roads or cutblocks). Functional response models in RSFs empirically account for this theroetical response by including an interaction term between the habitat feature at a location and the availability of that feature in the surronding environment ( [Matthiopoulos et al. 2011](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/10-0751.1)). I fit models with and without functional responses to roads and cutblocks and visualy assessed whether a functional response was evident, i.e., caribou use of cutblocks and roads varied as the average distance to cutblocks and roads changed within their home ranges. I calculated the availability of cutblocks and roads to an individual animal as the average distance to cutblocks and roads at 'available' locations sampled in the home range of that animal (see [Matthiopoulos et al. 2011](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/10-0751.1)). 

This model fitting process was completed to identify the statistical relationship between caribou distribution and forestry disturbance that was generalizable across a caribou DU, without considering the effect of other factors that influence caribou distribution. The theoretical basis for this approach is that these disturbance factors have a significant influence on caribou distribution, regardless of other habitat features. Indeed, cutblocks and linear features from forestry have routinely been shown to have a strong influence on caribou distribution (e.g., [Courbin et al. 2009](https://link.springer.com/article/10.1007/s10980-009-9389-x), [DeCesare et al. 2012](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/11-1610.1), [Mumma et al. 2018](https://www.sciencedirect.com/science/article/pii/S0006320718307225)) and survival ( [Wittmer et al. 2007](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2656.2007.01220.x), [Johnson et al. 2015](https://www.sciencedirect.com/science/article/pii/S0006320715001160)).

Clearly, other habitat characteristics besides forestry disturbance influence caribou distribution (e.g., terrain and vegetation, as they relate to food and predation risk; see for example, [Terry et al. 2000](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1046/j.1365-2664.2000.00523.x), [Apps et al. 2001]( http://www.env.gov.bc.ca/cariboo/env_stewardship/wildlife/inventory/caribou/northcar/hmi/hsi06-01.pdf), [Johnson et al. 2004](https://besjournals.onlinelibrary.wiley.com/doi/10.1111/j.0021-8901.2004.00899.x), [Apps & McLellan 2006](https://www.sciencedirect.com/science/article/pii/S000632070500546X)), and I initially attempted to fit models with some of these other factors. However, this led to the development of complex habitat models that did not improve my ability to estimate the effects of disturbance on caribou distribution. Instead, model building and interpretation became bogged down due to the difficulty in fitting a generalizable habitat model to unique habitats acorss a given DU. However, I did evaluate correlation between the forestry disturbance factors modeled here and other habtiat features (e.g., elevation, slope, forest stand characteristics) to ensure they were not completely confounded. Specifically, I tested for correlations using a Spearman correlation, ensuring correlation coefficients between covariates were less than 0.7, and by evalauting variance inflation factors (VIFs) in simple generalized linear models (GLMs), and ensuring VIFs were less than 10 ( [DeCesare et al. 2012](https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/11-1610.1)). This provided reassurance that distance to cublocks or roads was not completely confounded with some other habitat feature driving caribou distribution.      

```{r, Load data and transform, eval = T, echo = F, message = F, error = F, results = 'hide'}
# load data
rsf.data.du6 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du6.csv"))
rsf.data.du7 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du7.csv"))
rsf.data.du8 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du8.csv"))
rsf.data.du9 <- read.csv (here ("R/caribou_habitat/data", "rsf_data_du9.csv"))

# calculate fxn response covars
avail.rsf.data.du6 <- subset (rsf.data.du6, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du6$distance_to_resource_road,  
                          avail.rsf.data.du6$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du6$dist_cut_min,  
                          avail.rsf.data.du6$animal_id, mean)
inds <- as.character (rsf.data.du6$animal_id)
rsf.data.du6 <- cbind (rsf.data.du6, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

avail.rsf.data.du7 <- subset (rsf.data.du7, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du7$distance_to_resource_road, 
                           avail.rsf.data.du7$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du7$dist_cut_min, 
                          avail.rsf.data.du7$animal_id, mean)
inds <- as.character (rsf.data.du7$animal_id)
rsf.data.du7 <- cbind (rsf.data.du7, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

avail.rsf.data.du8 <- subset (rsf.data.du8, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du8$distance_to_resource_road, 
                                   avail.rsf.data.du8$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du8$dist_cut_min, 
                          avail.rsf.data.du8$animal_id, mean)
inds <- as.character (rsf.data.du8$animal_id)
rsf.data.du8 <- cbind (rsf.data.du8, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

avail.rsf.data.du9 <- subset (rsf.data.du9, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du9$distance_to_resource_road, 
                           avail.rsf.data.du9$animal_id, mean)
dist_cut_min_E <- tapply (rsf.data.du9$dist_cut_min, 
                          rsf.data.du9$animal_id, mean)
inds <- as.character (rsf.data.du9$animal_id)
rsf.data.du9 <- cbind (rsf.data.du9, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "dist_cut_min_E" = dist_cut_min_E[inds])

rsf.data.du6$pttype <- as.factor (rsf.data.du6$pttype)
rsf.data.du7$pttype <- as.factor (rsf.data.du7$pttype)
rsf.data.du8$pttype <- as.factor (rsf.data.du8$pttype)
rsf.data.du9$pttype <- as.factor (rsf.data.du9$pttype)

rm (avail.rsf.data.du6, avail.rsf.data.du7, avail.rsf.data.du8, avail.rsf.data.du9, inds, 
    dist_cut_min_E, dist_res_road_E)
gc ()
```

## Results
### DU6
Telemetry data in DU6 was collected from 160 animals from the Calendar, Chinchaga, Maxhamish, Westside Fort Nelson (formerly Parker and Prophet ranges), and Snake-Sahtaneh herds. The number of animals sampled in each herd ranged form 5 to 43 animals and the numeber of telmetry locations ranged 8,144 to 57,307 (Table 1).

```{r, du6, data summary, eval = T, echo = F, message = F}
# number of animals, by herd
count.animals.herd <- rsf.data.du6  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du6  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 1. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU6 (Boreal).<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd-Level Effect of FOrestry on Caribou Distribution
There were some small differences in herd response to resoruce roads in DU6 (Fig. 1). For example, caribou in the Calendar, Chinchaga and Prophet herds tended to be further from roads then in other herds. A random efefct for distance to road was included in the   

```{r, du6 Herd road effect plot, echo = F, message = F}
ggplot (rsf.data.du6, aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 1. Distance to Resource Road at Available (0) and Used (1) Locations by Caribou Herd in DU6",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6),
         plot.title = element_text (size = 12))
```



more variability in distance to cutblocks across herds, e.g., in Calendar, use closer to roads in area far from roads, but use further from roads in area closer to roads (Chinchaga)



```{r, du6 Herd cutblock effect plot, echo = F, message = F}
ggplot (rsf.data.du6, aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Figure 2. Distance to Cutblock at Available (0) and Used (1) Locations by Caribou Herd in DU6",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6),
         plot.title = element_text (size = 12))
```







#### Fit Models
Fit models with fixed effects including cut + roads with  fucntioanl repsonse adn with RE slope,

fucntional response calcualte at indivual level, i.e., available 'resrouce' calcualted within hoem rnage (coudl also try at herd level model); assumption is thta indivudal in herd will acocutn for herd varaibility (i.e., inidvudlas are rpeseeantiative untis of the herd); still incl RE for slope at herd scale to alow for vaariabiltiy there

looked at fxn reponse predcitons and evaluated visually if clear fxn response; no clear fxn response with cutblcks when incl road fxn responses in models, so only incl road fxn response; 

some high resiudlas at ~16 km form roads. looked at indivudals and no clear pattern (ddfiferen inds, herds, saeasons), so didn;t remove; perhasps males?

```{r, du6 model, echo = F, message = F}
model.lme4.du6.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all + 
                                                distance_to_resource_road +
                                                dist_rd_E +
                                                distance_to_resource_road*dist_rd_E +
                                      (dist_cut_min_all + distance_to_resource_road || HERD_NAME) +
                                      (dist_cut_min_all + distance_to_resource_road || animal_id),
                                      data = rsf.data.du6, 
                                      family = binomial (link = "logit"),
                                      verbose = T) 
# check residuals
binnedplot (fitted (model.lme4.du6.cut.rd.fxn), 
             residuals(model.lme4.du6.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du6$distance_to_resource_road, 
             residuals(model.lme4.du6.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Road", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du6$dist_cut_min_all, 
             residuals(model.lme4.du6.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Cut", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")

# check fxn response
scatter3d (rsf.data.du6$distance_to_resource_road, 
           rsf.data.du6$dist_res_road_E,
           (predict (model.lme4.du6.cut.rd.fxn,
                     newdata = rsf.data.du6, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           theta = 15, phi = 20)

data.road.test <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou\\telemetry_habitat_model_20180904\\rd_fxn_test_data.csv")
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_res_road_E,
           (predict (model.lme4.du6.cut.rd.fxn,
                     newdata = data.road.test, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           theta = 15, phi = 20)

# save the top model
save (model.lme4.du6.cut.rd.fxn, 
      file = "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\Rmodels\\model_du6_top_v3.rda")

# Create table of model coefficients from top model
model.coeffs <- as.data.frame (coef (summary (model.lme4.du6.cut.rd.fxn)))
write.table (model.coeffs, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du6_model_fixed_coeffs_v3.csv", sep = ",")

# random effects by herd
re_coeffs.herd <- as.data.frame (coef(model.lme4.du6.cut.rd.fxn)$HERD_NAME)
write.table (re_coeffs.herd, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du6_model_herd_re_coeffs_v3.csv", sep = ",")

```


### DU7
northern mtn, included animals from Itcha-Ilgachuz, Rainbows, Charlotte Alplands, Tweedsmuir, Spatsizi, Pink Mountain, Muskwa, Frog, Chase, Finlay, Graham, Tsenaglode, Telkwa (Table 1).

Ranged from 1 to 35 aniamls and 856 to 41,837 locations by herd. 

```{r, DU7, data summary, echo = F, message = F}
count.animals.herd <- rsf.data.du7  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du7  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 1. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU7.<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd Effect of Disturbance
show that response to roads and cutbocks varies by herd

possible fucntional repsonse; difernt response dependnign on hoem rnage context, by herd

```{r, DU7 Herd effect plots, echo = F, message = F}

ggplot (rsf.data.du7, 
        aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Resource Road at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

ggplot (rsf.data.du7, 
        aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Cutblock at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

```


#### Fit Models
Fit models with fixed effects including cut + roads with  fucntioanl repsonse adn with RE slope,

fucntional response calcualte at indivual level, i.e., available 'resrouce' calcualted within hoem rnage (coudl also try at herd level model); assumption is thta indivudal in herd will acocutn for herd varaibility (i.e., inidvudlas are rpeseeantiative untis of the herd); still incl RE for slope at herd scale to alow for vaariabiltiy there

looked at fxn reponse predcitons and evaluated visually if clear fxn response; no clear fxn response with cutblcks when incl road fxn responses in models, so only incl road fxn response; 

some high resiudlas at ~16 km form roads. looked at indivudals and no clear pattern (ddfiferen inds, herds, saeasons), so didn;t remove; perhasps males?

```{r, du7 model, echo = F, message = F}
model.lme4.du7.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all +
                                             distance_to_resource_road +
                                             dist_rd_E +
                                             distance_to_resource_road*dist_rd_E +
                                        (dist_cut_min_all + distance_to_resource_road || animal_id) +                                         (dist_cut_min_all + distance_to_resource_road || HERD_NAME),
                                  data = rsf.data.du7,
                                  family = binomial (link = "logit"),
                                  verbose = T)

summary (model.lme4.du7.cut.rd.fxn)

model.lme4.du7.cut.rd.fxn.all <- allFit (model.lme4.du7.cut.rd.fxn) # did not converge, ran with many optimizers and got very similar coeffecients, so model considered ok (see hlep ('convergence'))
ss <- summary (model.lme4.du7.cut.rd.fxn.all)
ss$which.OK
ss$fixef

# check residuals
rsf.data.du7$resids <- residuals (model.lme4.du7.cut.rd.fxn, type = "response")
rsf.data.du7$fit <- fitted (model.lme4.du7.cut.rd.fxn)
ggplot (rsf.data.du7, aes (x = fit, y = resids)) +
  geom_point ()
binnedplot (fitted (model.lme4.du7.cut.rd.fxn), 
             residuals(model.lme4.du7.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du7$distance_to_resource_road, 
             residuals(model.lme4.du7.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Road", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du7$dist_cut_min_all, 
             residuals(model.lme4.du7.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Cutblock", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")

# check fxn response
scatter3d (rsf.data.du7$distance_to_resource_road, 
           rsf.data.du7$dist_rd_E,
           (predict (model.lme4.du7.cut.rd.fxn,
                     newdata = rsf.data.du7, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           surface = T)
data.road.test <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou\\telemetry_habitat_model_20180904\\rd_fxn_test_data.csv")
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_rd_E,
           (predict (model.lme4.du7.cut.rd.fxn,
                     newdata = data.road.test, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           surface = T,
           fit = "smooth")

# save the top model
save (model.lme4.du7.cut.rd.fxn, 
      file = "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\Rmodels\\model_du7_top_v3.rda")

# Create table of model coefficients from top model
model.coeffs <- as.data.frame (coef (summary (model.lme4.du7.cut.rd.fxn)))
write.table (model.coeffs, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du7_model_fixed_coeffs_v3.csv", sep = ",")

# random effects by herd adn season
re_coeffs.herd <- as.data.frame (coef(model.lme4.du7.cut.rd.fxn)$HERD_NAME)
write.table (re_coeffs.herd, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du7_model_herd_re_coeffs_v3.csv", sep = ",")

```


### DU8
Central mtn, included animals from Burnt Pine, Kennedy Siding, Moberly, Narraway, Qunittet adn Scott (Table 2).

Ranged from 8 to 57 animals and 5,414 to 65,431 locations by herd. 

```{r, DU8, data summary, echo = F, message = F}
count.animals.herd <- rsf.data.du8  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du8  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 2. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU8.<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd Effect of Disturbance
show that response to roads and cutbocks varies by herd

pssobiel fucntional repsonse; difernt response dependnign on hoem rnage context, by herd, e.g., more avodiance of roads in NArrawya and Quintette, no clear efefct in Kennedy Siging or Burnt Pine (note that Burtn Pine now extirpated); avoidance of cutblock in Quintette, but maybe selction in Narraway adn Burtn Pine

```{r, DU8 Herd effect plots, echo = F, message = F}

ggplot (rsf.data.du8, 
        aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Resource Road at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

ggplot (rsf.data.du8, 
        aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Cutblock at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

```

#### Fit Models
Fit models with fixed effects including cut + roads with  fucntioanl repsonse adn with RE slope,

fucntional response calcualte at indivual level, i.e., available 'resrouce' calcualted within hoem rnage (coudl also try at herd level model); assumption is thta indivudal in herd will acocutn for herd varaibility (i.e., inidvudlas are rpeseeantiative untis of the herd); still incl RE for slope at herd scale to alow for vaariabiltiy there

looked at fxn reponse predcitons and evaluated visually if clear fxn response; no clear fxn response with cutblcks when incl road fxn responses in models, so only incl road fxn response; 

some high resiudlas at ~16 km form roads. looked at indivudals and no clear pattern (ddfiferen inds, herds, saeasons), so didn;t remove; perhasps males?

```{r, DU8 model, echo = F, message = F}
model.lme4.du8.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all + 
                                            distance_to_resource_road +
                                            dist_rd_E + 
                                            distance_to_resource_road*dist_rd_E +
                                  (dist_cut_min_all + distance_to_resource_road || HERD_NAME) +
                                  (dist_cut_min_all + distance_to_resource_road || animal_id),
                                  data = rsf.data.du8, 
                                  family = binomial (link = "logit"),
                                  verbose = T) 

summary (model.lme4.du8.cut.rd.fxn)

# check residuals
rsf.data.du8$resids <- residuals (model.lme4.du8.cut.rd.fxn, type = "response")
rsf.data.du8$fit <- fitted (model.lme4.du8.cut.rd.fxn)
ggplot (rsf.data.du8, aes (x = fit, y = resids)) +
  geom_point ()
binnedplot (fitted (model.lme4.du8.cut.rd.fxn), 
             residuals(model.lme4.du8.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du8$distance_to_resource_road, 
             residuals(model.lme4.du8.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Road", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du8$dist_cut_min_all, 
             residuals(model.lme4.du8.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Cut", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")

# fxn response
scatter3d (rsf.data.du8$distance_to_resource_road, 
           rsf.data.du8$dist_rd_E,
           (predict (model.lme4.du8.cut.rd.fxn,
                     newdata = rsf.data.du8, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           fir = "smooth")

data.road.test <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou\\telemetry_habitat_model_20180904\\rd_fxn_test_data.csv")
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_rd_E,
           (predict (model.lme4.du8.cut.rd.fxn,
                     newdata = data.road.test, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           fir = "smooth")

# save the top model
save (model.lme4.du8.cut.rd.fxn, 
      file = "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\Rmodels\\model_du8_top_v3.rda")

# Create table of model coefficients from top model
model.coeffs <- as.data.frame (coef (summary (model.lme4.du8.cut.rd.fxn)))
write.table (model.coeffs, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du8_model_fixed_coeffs_v3.csv", sep = ",")

# random effects by herd
re_coeffs.herd <- as.data.frame (coef(model.lme4.du8.cut.rd.fxn)$HERD_NAME)
write.table (re_coeffs.herd, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du8_model_herd_re_coeffs_v3.csv", sep = ",")

```


### DU9
Southern mtn, included animals from HArt Ranges, Nakusp and Sotuh Selkirks

(Table 3).

Ranged from 6 to 11 animals and 1,821 to 4,917 locations by herd. 

```{r, du9, data summary, echo = F, message = F}
# numebr of animals, by herd
count.animals.herd <- rsf.data.du9  %>%
  group_by(HERD_NAME) %>%
  summarise(count = n_distinct(animal_id))

count.locs.herd <- rsf.data.du9  %>%
  group_by(HERD_NAME) %>%
  filter (pttype == 1) %>%
  summarise(count = n())

table <- full_join(count.animals.herd, count.locs.herd, by = "HERD_NAME")

table <- table %>% 
  rename (Herd = HERD_NAME,
          Animals = count.x,
          Locations = count.y)

kable (table,
       caption = "<b>Table 3. Number of Animals and Telemetry Locations Sampled by Caribou Herd in DU9.<b>") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11) 

```

#### Herd Effect of Disturbance
show that response to roads and cutbocks varies by herd

pssobiel fucntional repsonse; difernt response dependnign on hoem rnage context, by herd, e.g., more further from roads in Nakusp and South Selkirks, closer to roads in HArt Ranges ; use further form of cutblock in Nakusp, but closer in Hart Rnages and South Selkirks

```{r, du9 Herd effect plots, echo = F, message = F}

ggplot (rsf.data.du9, 
        aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Resource Road at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

ggplot (rsf.data.du9, 
        aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Cutblock at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

```

#### Fit Models
Fit models with fixed effects including cut + roads with  fucntioanl repsonse adn with RE slope,

fucntional response calcualte at indivual level, i.e., available 'resrouce' calcualted within hoem rnage (coudl also try at herd level model); assumption is thta indivudal in herd will acocutn for herd varaibility (i.e., inidvudlas are rpeseeantiative untis of the herd); still incl RE for slope at herd scale to alow for vaariabiltiy there

looked at fxn reponse predcitons and evaluated visually if clear fxn response; no clear fxn response with cutblcks when incl road fxn responses in models, so only incl road fxn response; 

some high resiudlas at ~16 km form roads. looked at indivudals and no clear pattern (ddfiferen inds, herds, saeasons), so didn;t remove; perhasps males?

```{r, DU9 model, echo = F, message = F}
model.lme4.du9.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all + 
                                                distance_to_resource_road +
                                                dist_rd_E +
                                                distance_to_resource_road*dist_rd_E +
                                      (dist_cut_min_all + distance_to_resource_road || HERD_NAME) +
                                      (dist_cut_min_all + distance_to_resource_road || animal_id),
                                      data = rsf.data.du9, 
                                      family = binomial (link = "logit"),
                                      verbose = T) 
summary (model.lme4.du9.cut.rd.fxn)

# check residuals
rsf.data.du9$resids <- residuals (model.lme4.du9.cut.rd.fxn, type = "response")
rsf.data.du9$fit <- fitted (model.lme4.du9.cut.rd.fxn)
ggplot (rsf.data.du9, aes (x = fit, y = resids)) +
  geom_point ()
binnedplot (fitted (model.lme4.du9.cut.rd.fxn), 
             residuals(model.lme4.du9.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Expected Values", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du9$distance_to_resource_road, 
             residuals(model.lme4.du9.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Road", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")
binnedplot (rsf.data.du9$dist_cut_min_all, 
             residuals(model.lme4.du9.cut.rd.fxn, type = "response"), 
             nclass = NULL, 
             xlab = "Distance to Cut", 
             ylab = "Average residual", 
             main = "Binned residual plot", 
             cex.pts = 0.4, 
             col.pts = 1, 
             col.int = "red")

# check fxn response
scatter3d (rsf.data.du9$distance_to_resource_road, 
           rsf.data.du9$dist_rd_E,
           (predict (model.lme4.du9.cut.fxn.rd.fxn,
                     newdata = rsf.data.du9, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           theta = 15, phi = 20)

data.road.test <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou\\telemetry_habitat_model_20180904\\rd_fxn_test_data.csv")
scatter3d (data.road.test$distance_to_resource_road, 
           data.road.test$dist_rd_E,
           (predict (model.lme4.du9.cut.fxn.rd.fxn,
                     newdata = data.road.test, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           theta = 15, phi = 20)

# save the top model
save (model.lme4.du9.cut.rd.fxn, 
      file = "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\Rmodels\\model_du9_top_v3.rda")

# Create table of model coefficients from top model
model.coeffs <- as.data.frame (coef (summary (model.lme4.du9.cut.rd.fxn)))
write.table (model.coeffs, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du9_model_fixed_coeffs_v3.csv", sep = ",")

# random effects by herd
re_coeffs.herd <- as.data.frame (coef(model.lme4.du9.cut.rd.fxn)$HERD_NAME)
write.table (re_coeffs.herd, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du9_model_herd_re_coeffs_v3.csv", sep = ",")

```


### Conclusions
difference sin effect, but consistent avoidance and fxn reponseot to roads

efefct of cutblocks interstingly ambiguous, but egenral avoindace

road efefct could be overall disturabnce efefct; many types; confounded to soem degree, btu not overly corralted with other factors, e.g., elevation, cliamte



concluisn - simialr to decesare, third order dirven by lienar, second order by numericla response (cut)
