---
title: "Caribou RSF 3.0"
author: "Tyler Muhly"
date: "28/01/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (dplyr)
library (ggcorrplot)
library (ggplot2)
library (lme4)
library (raster)
library (rgdal)
library (arm)
library (car)
library (optimx)
library (dfoptim)
```

## Introduction
Here I create a caribou disturbance model using an RSF framework to develop the model. Purpose is to create a model that links forestry disturbance to cariobu habitat quality. disturabnce avoidance fucntion (DAF)

didn;t try to model other direvers of habtait selection or use; modle is naive to those. Juits truign to ciofucs on distruanbcem efefct. Philosphy here is to focus on distruabcen effect only, not build a habtait model. So this si a 'targeted RSF', nto desinged to accurately idnetify cariobu habtait, just accruately identify the fefcts of forestry on caribou.

RSF's created for each DU. r
Use fucntional repsonse. comapred osme models usign AIC and looked at fxn response fit to dtemrine 'best' model


### Methods

Data from GPS collars across BC, 2008 - 2018;  no capture info, but assume mostly females. (add these detials)

Calcualted annual home rnages usign kernbel density to defien 'available sample' (add these detials)

average size of hiomre nrages, bu DU = 

RSF with GLMM appraoch, with random effects, random effect for season,herd and animal


### Prepare data

Load data and transform covariates


Transform distance to covars as exponentinal function, following Demars (2018)[http://www.bcogris.ca/sites/default/files/bcip-2019-01-final-report-demars-ver-2.pdf]
decay.distance = exp (-0.002 * distance to road)

This essentialyl limtis the lienar efefct to 1.5km to 2km from the feature, and limited effect thereafter

create fxn response covariate by takign average value for each covariet in each aniamls annual HR


```{r, Load data and transform, echo = F, message = F}
# load data
rsf.data.du6 <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\rsf_data_du6.csv")
rsf.data.du7 <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\rsf_data_du7.csv")
rsf.data.du8 <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\rsf_data_du8.csv")
rsf.data.du9 <- read.csv ("C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\rsf_data_du9.csv")

# Create new covars to deal with corelations, for fxn repsonse 
rsf.data.du6$dist_cut_min_all <- pmin (rsf.data.du6$distance_to_cut_1to4,
                                       rsf.data.du6$distance_to_cut_5to9yo,
                                       rsf.data.du6$distance_to_cut_10yoorOver)

rsf.data.du7 <- dplyr::mutate (rsf.data.du7, 
                               distance_to_cut_over4 = pmin (distance_to_cut_5to9yo, 
                                                             distance_to_cut_10to29yo,
                                                             distance_to_cut_30orOveryo))
rsf.data.du7$dist_cut_min_all <- pmin (rsf.data.du7$distance_to_cut_1to4,
                                       rsf.data.du7$distance_to_cut_over4)

rsf.data.du8 <- rsf.data.du8 %>% # removed outlier locations really far from  (>200km) from cutblocks
                  dplyr::filter (distance_to_cut_30orOveryo < 27500)
rsf.data.du8$dist_cut_min_all <- pmin (rsf.data.du8$distance_to_cut_1to4,
                                       rsf.data.du8$distance_to_cut_5to9yo,
                                       rsf.data.du8$distance_to_cut_10to29yo,
                                       rsf.data.du8$distance_to_cut_30orOveryo)
rsf.data.du9$dist_cut_min_all <- pmin (rsf.data.du9$distance_to_cut_1to4,
                                       rsf.data.du9$distance_to_cut_5to9yo,
                                       rsf.data.du9$distance_to_cut_10to29yo,
                                       rsf.data.du9$distance_to_cut_30orOveryo)

# convert m to km 
rsf.data.du6$distance_to_resource_road <- rsf.data.du6$distance_to_resource_road/1000
rsf.data.du6$distance_to_cut_1to4yo <- rsf.data.du6$distance_to_cut_1to4yo/1000
rsf.data.du6$distance_to_cut_5to9yo <- rsf.data.du6$distance_to_cut_5to9yo/1000
rsf.data.du6$distance_to_cut_10yoorOver <- rsf.data.du6$distance_to_cut_10yoorOver/1000
rsf.data.du6$dist_cut_min_all <- rsf.data.du6$dist_cut_min_all/1000

rsf.data.du7$distance_to_resource_road <- rsf.data.du7$distance_to_resource_road/1000
rsf.data.du7$distance_to_cut_1to4yo <- rsf.data.du7$distance_to_cut_1to4yo/1000
rsf.data.du7$distance_to_cut_over4 <- rsf.data.du7$distance_to_cut_over4/1000
rsf.data.du7$dist_cut_min_all <- rsf.data.du7$dist_cut_min_all/1000

rsf.data.du8$distance_to_resource_road <- rsf.data.du8$distance_to_resource_road/1000
rsf.data.du8$distance_to_cut_1to4yo <- rsf.data.du8$distance_to_cut_1to4yo/1000
rsf.data.du8$distance_to_cut_5to9yo <- rsf.data.du8$distance_to_cut_5to9yo/1000
rsf.data.du8$distance_to_cut_10to29yo <- rsf.data.du8$distance_to_cut_10to29yo/1000
rsf.data.du8$distance_to_cut_30orOveryo <- rsf.data.du8$distance_to_cut_30orOveryo/1000
rsf.data.du8$dist_cut_min_all <- rsf.data.du8$dist_cut_min_all/1000

rsf.data.du9$distance_to_resource_road <- rsf.data.du9$distance_to_resource_road/1000
rsf.data.du9$distance_to_cut_1to4yo <- rsf.data.du9$distance_to_cut_1to4yo/1000
rsf.data.du9$distance_to_cut_5to9yo <- rsf.data.du9$distance_to_cut_5to9yo/1000
rsf.data.du9$dist_cut_min_all <- rsf.data.du9$dist_cut_min_all/1000

# calculate fxn response covars
avail.rsf.data.du6 <- subset (rsf.data.du6, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du6$distance_to_resource_road, 
                                   avail.rsf.data.du6$animal_id, mean)
distance_to_cut_1to4yo_E <- tapply (avail.rsf.data.du6$distance_to_cut_1to4yo, 
                           avail.rsf.data.du6$animal_id, mean)
distance_to_cut_5to9yo_E <- tapply (avail.rsf.data.du6$distance_to_cut_5to9yo, 
                                   avail.rsf.data.du6$animal_id, mean)
distance_to_cut_10yoorOver_E <- tapply (avail.rsf.data.du6$distance_to_cut_10yoorOver, 
                                 avail.rsf.data.du6$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du6$dist_cut_min,  
                                  avail.rsf.data.du6$animal_id, mean)
inds <- as.character (rsf.data.du6$animal_id)
rsf.data.du6 <- cbind (rsf.data.du6, "dist_res_road_E" = dist_res_road_E[inds], 
                       "distance_to_cut_1to4yo_E" = distance_to_cut_1to4yo_E[inds],
                       "distance_to_cut_5to9yo_E" = distance_to_cut_5to9yo_E[inds],
                       "distance_to_cut_10yoorOver_E" = distance_to_cut_10yoorOver_E[inds],
                       "dist_cut_min_E" = dist_cut_min_E[inds])

avail.rsf.data.du7 <- subset (rsf.data.du7, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du7$distance_to_resource_road, 
                           avail.rsf.data.du7$animal_id, mean)
distance_to_cut_1to4yo_E <- tapply (avail.rsf.data.du7$distance_to_cut_1to4yo, 
                           avail.rsf.data.du7$animal_id, mean)
distance_to_cut_over4_E <- tapply (avail.rsf.data.du7$distance_to_cut_over4, 
                            avail.rsf.data.du7$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du7$dist_cut_min, 
                                  avail.rsf.data.du7$animal_id, mean)
inds <- as.character (rsf.data.du7$animal_id)
rsf.data.du7 <- cbind (rsf.data.du7, 
                       "dist_rd_E" = dist_res_road_E[inds], 
                       "distance_to_cut_1to4yo_E" = distance_to_cut_1to4yo_E[inds],
                       "distance_to_cut_over4_E" = distance_to_cut_over4_E[inds],
                       "dist_cut_min_E" = dist_cut_min_E[inds])


avail.rsf.data.du8 <- subset (rsf.data.du8, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du8$distance_to_resource_road, 
                                   avail.rsf.data.du8$animal_id, mean)
distance_to_cut_1to4yo_E <- tapply (avail.rsf.data.du8$distance_to_cut_1to4yo, 
                                   avail.rsf.data.du8$animal_id, mean)
distance_to_cut_5to9yo_E <- tapply (avail.rsf.data.du8$distance_to_cut_5to9yo, 
                                   avail.rsf.data.du8$animal_id, mean)
distance_to_cut_10to29_E <- tapply (avail.rsf.data.du8$distance_to_cut_10to29yo, 
                                     avail.rsf.data.du8$animal_id, mean)
dist_cut_30_E <- tapply (avail.rsf.data.du8$distance_to_cut_30orOveryo, 
                                 avail.rsf.data.du8$animal_id, mean)
dist_cut_min_E <- tapply (avail.rsf.data.du8$dist_cut_min, 
                          avail.rsf.data.du8$animal_id, mean)
inds <- as.character (rsf.data.du8$animal_id)
rsf.data.du8 <- cbind (rsf.data.du8, "dist_rd_E" = dist_res_road_E[inds], 
                       "distance_to_cut_1to4yo_E" = distance_to_cut_1to4yo_E[inds],
                       "distance_to_cut_5to9yo_E" = distance_to_cut_5to9yo_E[inds],
                       "distance_to_cut_10yoorOverto29_E" = distance_to_cut_10to29_E[inds],
                       "dist_cut_30_E" = dist_cut_30_E[inds],
                       "dist_cut_min_E" = dist_cut_min_E[inds])


avail.rsf.data.du9 <- subset (rsf.data.du9, pttype == 0)
dist_res_road_E <- tapply (avail.rsf.data.du9$distance_to_resource_road, 
                           avail.rsf.data.du9$animal_id, mean)
distance_to_cut_1to4yo_E <- tapply (avail.rsf.data.du9$distance_to_cut_1to4yo, 
                           avail.rsf.data.du9$animal_id, mean)
distance_to_cut_5to9yo_E <- tapply (avail.rsf.data.du9$distance_to_cut_5to9yo, 
                           avail.rsf.data.du9$animal_id, mean)
rsf.data.du9$dist_cut_min_all <- pmin (rsf.data.du9$distance_to_cut_1to4,
                                       rsf.data.du9$distance_to_cut_5to9yo)
inds <- as.character (rsf.data.du9$animal_id)
rsf.data.du9 <- cbind (rsf.data.du9, "dist_rd_E" = dist_res_road_E[inds], 
                       "distance_to_cut_1to4yo_E" = distance_to_cut_1to4yo_E[inds],
                       "distance_to_cut_5to9yo_E" = distance_to_cut_5to9yo_E[inds],
                       "dist_cut_min_E" = dist_cut_min_E[inds])

rsf.data.du6$pttype <- as.factor (rsf.data.du6$pttype)
rsf.data.du7$pttype <- as.factor (rsf.data.du7$pttype)
rsf.data.du8$pttype <- as.factor (rsf.data.du8$pttype)
rsf.data.du9$pttype <- as.factor (rsf.data.du9$pttype)
```

### Herd Effect of Disturbance


show that response to roads and cutbocks varies by herd

pssobiel fucntional repsonse; difernt response dep[dnign on hoem rnage context, by herd

```{r, DU7 Herd effect plots, echo = F, message = F}

ggplot (rsf.data.du7, 
        aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Resource Road at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

ggplot (rsf.data.du7, 
        aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Cutblock at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ HERD_NAME, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 6))

```


### Season efefct

not clearly different, so only include random intercept 


```{r, DU7 season effect, echo = F, message = F}
ggplot (rsf.data.du7, 
        aes (x = pttype, y = distance_to_resource_road)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Resource Road at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Resource Road") +
  facet_grid (. ~ season, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 8))

ggplot (rsf.data.du7, 
        aes (x = pttype, y = dist_cut_min_all)) +
  geom_boxplot (outlier.colour = "red") +
  labs (title = "Distance to Cutblock at Available (0) and Used (1) Locations",
        x = "Available (0) and Used (1) Locations",
        y = "Distance to Cutblock") +
  facet_grid (. ~ season, scales='free_x', space='free_x') +
  theme (strip.text.x = element_text (size = 8))

```





### Fit Models
Fit models with fixed effects including cut + roads with no fucntioanl repsonse adn with RE slope,

then fit models with fucntional repsonse, 

fucntional response calcualte at indivual level, i.e., available 'resrouce' calcualted within hoem rnage (coudl also try at herd level model); assumption is thta indivudal in herd will acocutn for herd varaibility (i.e., inidvudlas are rpeseeantiative untis of the herd); still incl RE for slope at herd scale to alow for vaariabiltiy there




coamrped usign AIC

looked at fxn reponse predcitons and evaluated visually if clear fxn response



```{r, du7 model, echo = F, message = F}
### Build an AIC Table ###
table.aic <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.aic) <- c ("DU", "Fixed Effects Covariates", "Random Effects Covariates", "AIC", "AICw")

## DU7 ##
# RE only model
model.lme4.du7.re <- glmer (pttype ~ 1 + (1 | animal_id) + (1 | HERD_NAME), 
                                 data = rsf.data.du7, 
                                 family = binomial (link = "logit"),
                                 verbose = T) 
# AIC
table.aic [1, 1] <- "DU7"
table.aic [1, 2] <- "Random Effect Model"
table.aic [1, 3] <- "(1 | animal) + (1 | herd)"
table.aic [1, 4] <-  AIC (model.lme4.du7.re)

# Dist Road model
model.lme4.du7.road <- glmer (pttype ~ distance_to_resource_road + 
                                        (distance_to_resource_road || animal_id) + 
                                        (distance_to_resource_road || HERD_NAME),
                              data = rsf.data.du7, 
                              family = binomial (link = "logit"),
                              verbose = T) 
# AIC
table.aic [2, 1] <- "DU7"
table.aic [2, 2] <- "Distance to Resource Road"
table.aic [2, 3] <- "(1 | animal) + (Distance to Resource Road | animal) + (1 | herd) + (Distance to Resource Road | herd)"
table.aic [2, 4] <-  AIC (model.lme4.du7.road)

# Dist Cut model
model.lme4.du7.cut <- glmer (pttype ~ dist_cut_min_all + 
                                        (dist_cut_min_all || animal_id) + 
                                        (dist_cut_min_all || HERD_NAME),
                              data = rsf.data.du7, 
                              family = binomial (link = "logit"),
                              verbose = T) 
# AIC
table.aic [3, 1] <- "DU7"
table.aic [3, 2] <- "Distance to Cutblock"
table.aic [3, 3] <- "(1 | animal)  + (Distance to Cutblock | animal) + (1 | herd) + (Distance to Cutblock | herd)"
table.aic [3, 4] <-  AIC (model.lme4.du7.cut)

# Dist Road fxn model
model.lme4.du7.road.fxn <- glmer (pttype ~ distance_to_resource_road + dist_rd_E +
                                        distance_to_resource_road*dist_rd_E + 
                                        (distance_to_resource_road || animal_id) + 
                                        (distance_to_resource_road || HERD_NAME),
                              data = rsf.data.du7, 
                              family = binomial (link = "logit"),
                              # control = glmerControl (optimizer = "nloptwrap"), # Nelder_Mead, bobyqa, nloptwrap, "optimx", optCtrl  = list(method="nlminb"
                              verbose = T) 
# AIC
table.aic [4, 1] <- "DU7"
table.aic [4, 2] <- "Distance to Resource Road +  Available Distance to Resource Road + Distance to Resource Road*Available Distance to Resource Road"
table.aic [4, 3] <- "(1 | animal) + (Distance to Resource Road | animal) + (1 | herd) + (Distance to Resource Road | herd)"
table.aic [4, 4] <-  AIC (model.lme4.du7.road.fxn)

# Dist Cut fxn model
model.lme4.du7.cut.fxn <- glmer (pttype ~ dist_cut_min_all + dist_cut_min_E +
                                        dist_cut_min_all*dist_cut_min_E + 
                                        (dist_cut_min_all || animal_id) + 
                                        (dist_cut_min_all || HERD_NAME),
                              data = rsf.data.du7, 
                              family = binomial (link = "logit"),
                              verbose = T) 
# AIC
table.aic [5, 1] <- "DU7"
table.aic [5, 2] <- "Distance to Cutblock +  Available Distance to Cutblock + Distance to Cutblock*Available Distance to Cutblock"
table.aic [5, 3] <- "(1 | animal) + (Distance to Cutblock | animal) + (1 | herd) + (Distance to Cutblock | herd)"
table.aic [5, 4] <-  AIC (model.lme4.du7.cut.fxn)

# Dist Cut and Road model
model.lme4.du7.cut.rd <- glmer (pttype ~ dist_cut_min_all + 
                                        distance_to_resource_road +
                                        (dist_cut_min_all || animal_id) + 
                                        (dist_cut_min_all || HERD_NAME) +
                                    (distance_to_resource_road || animal_id) + 
                                    (distance_to_resource_road || HERD_NAME),
                                  data = rsf.data.du7, 
                                  family = binomial (link = "logit"),
                                  verbose = T) 
# AIC
table.aic [6, 1] <- "DU7"
table.aic [6, 2] <- "Distance to Cutblock + Distance to Resource Road"
table.aic [6, 3] <- "(1 | animal)  + (Distance to Cutblock | animal) + (Distance to Resource Road | animal) + (1 | herd) + (Distance to Cutblock | herd) + (Distance to Resource Road | herd)"
table.aic [6, 4] <-  AIC (model.lme4.du7.cut.rd)

# Dist Cut and Road fxn model
model.lme4.du7.cut.rd.fxn <- glmer (pttype ~ dist_cut_min_all + 
                                        distance_to_resource_road +
                                        dist_cut_min_E +
                                        dist_cut_min_all*dist_cut_min_E +
                                        dist_rd_E +
                                        distance_to_resource_road*dist_rd_E +
                                        (dist_cut_min_all || animal_id) + 
                                        (dist_cut_min_all || HERD_NAME) +
                                    (distance_to_resource_road || animal_id) + 
                                    (distance_to_resource_road || HERD_NAME),
                                  data = rsf.data.du7, 
                                  family = binomial (link = "logit"),
                                  verbose = T) 
# AIC
table.aic [7, 1] <- "DU7"
table.aic [7, 2] <- "Distance to Cutblock + Distance to Resource Road +  Available Distance to Cutblock + Distance to Cutblock*Available Distance to Cutblock + Available Distance to Resource Road + Distance to Resource Road*Available Distance to Resource Road"
table.aic [7, 3] <- "(1 | animal)  + (Distance to Cutblock | animal) + (Distance to Resource Road | animal) + (1 | herd) + (Distance to Cutblock | herd) + (Distance to Resource Road | herd)"
table.aic [7, 4] <-  AIC (model.lme4.du7.cut.rd.fxn)
                                        
# Dist Cut and Road fxn model
model.lme4.du7.cut.rd.fxn2 <- glmer (pttype ~ dist_cut_min_all + 
                                        distance_to_resource_road +
                                        dist_rd_E +
                                        distance_to_resource_road*dist_rd_E +
                                        (dist_cut_min_all || animal_id) + 
                                        (dist_cut_min_all || HERD_NAME) +
                                    (distance_to_resource_road || animal_id) + 
                                    (distance_to_resource_road || HERD_NAME),
                                  data = rsf.data.du7, 
                                  family = binomial (link = "logit"),
                                  verbose = T) 
# AIC
table.aic [8, 1] <- "DU7"
table.aic [8, 2] <- "Distance to Cutblock + Distance to Resource Road +  Available Distance to Resource Road + Distance to Resource Road*Available Distance to Resource Road"
table.aic [8, 3] <- "(1 | animal)  + (Distance to Cutblock | animal) + (Distance to Resource Road | animal) + (1 | herd) + (Distance to Cutblock | herd) + (Distance to Resource Road | herd)"
table.aic [8, 4] <-  AIC (model.lme4.du7.cut.rd.fxn2)








model.lme4.du7.cut.rd.fxn.all <- allFit (model.lme4.du7.cut.rd.fxn) # did not converge, ran with many optimizers and got very similar coeffecients, so model considered ok (see hlep ('convergence'))
ss <- summary (model.lme4.du7.cut.rd.fxn.all)
ss$which.OK
ss$fixef


binnedplot(fitted(model.lme4.du7.cut.rd.fxn2), 
           residuals(model.lme4.du7.cut.rd.fxn2, type = "response"), 
           nclass = NULL, 
           xlab = "Expected Values", 
           ylab = "Average residual", 
           main = "Binned residual plot", 
           cex.pts = 0.4, 
           col.pts = 1, 
           col.int = "red")

binnedplot(rsf.data.du7$distance_to_resource_road, 
           residuals(model.lme4.du7.cut.rd.fxn2, type = "response"), 
           nclass = NULL, 
           xlab = "Distance to Road", 
           ylab = "Average residual", 
           main = "Binned residual plot", 
           cex.pts = 0.4, 
           col.pts = 1, 
           col.int = "red")

scatter3D (rsf.data.du7$distance_to_resource_road, 
           rsf.data.du7$dist_rd_E,
           (predict (model.lme4.du7.cut.rd.fxn2,
                     newdata = rsf.data.du7, 
                     re.form = NA, type = "response")), 
           xlab = "Dist Road",
           ylab = "HR Dist Road", 
           zlab = "Use/Select",
           theta = 15, phi = 20)

















rsf.data.du7$resids <- residuals(model.lme4.du7.road, type = "response")
rsf.data.du7$fit <- fitted(model.lme4.du7.road)
ggplot (rsf.data.du7, aes (x = fit, y = resids)) +
  geom_point ()

#mean resids by animal
mean_resids <- tapply (rsf.data.du7$resids,  
                       rsf.data.du7$animal_id, mean)
inds <- as.character (rsf.data.du7$animal_id)
rsf.data.du7 <- cbind (rsf.data.du7, "mean_resids" = mean_resids[inds])



ggplot (rsf.data.du7, aes (x = HERD_NAME, y = resids)) +
  geom_boxplot ()


del <- rsf.data.du7 %>% filter (dist_cut_min_all > 24 & dist_cut_min_all < 25 )






model.lme4.du7.itch <- glmer (pttype ~ distance_to_resource_road +
                                       (1 + distance_to_resource_road | animal_id), 
                                 data = rsf.data.du7 %>% filter (HERD_NAME == "Itcha-Ilgachuz"), 
                                 family = binomial (link = "logit"),
                                 verbose = T) 







## AIC comparison of MODELS ## 
list.aic.like <- c ((exp (-0.5 * (table.aic [6, 4] - min (table.aic [6:12, 4])))), 
                    (exp (-0.5 * (table.aic [7, 4] - min (table.aic [6:12, 4])))),
                    (exp (-0.5 * (table.aic [8, 4] - min (table.aic [6:12, 4])))),
                    (exp (-0.5 * (table.aic [9, 4] - min (table.aic [6:12, 4])))),
                    (exp (-0.5 * (table.aic [10, 4] - min (table.aic [6:12, 4])))),
                    (exp (-0.5 * (table.aic [11, 4] - min (table.aic [6:12, 4])))),
                    (exp (-0.5 * (table.aic [12, 4] - min (table.aic [6:12, 4])))))
table.aic [6, 5] <- round ((exp (-0.5 * (table.aic [6, 4] - min (table.aic [6:12, 4])))) / sum (list.aic.like), 3)
table.aic [7, 5] <- round ((exp (-0.5 * (table.aic [7, 4] - min (table.aic [6:12, 4])))) / sum (list.aic.like), 3)
table.aic [8, 5] <- round ((exp (-0.5 * (table.aic [8, 4] - min (table.aic [6:12, 4])))) / sum (list.aic.like), 3)
table.aic [9, 5] <- round ((exp (-0.5 * (table.aic [9, 4] - min (table.aic [6:12, 4])))) / sum (list.aic.like), 3)
table.aic [10, 5] <- round ((exp (-0.5 * (table.aic [10, 4] - min (table.aic [6:12, 4])))) / sum (list.aic.like), 3)
table.aic [11, 5] <- round ((exp (-0.5 * (table.aic [11, 4] - min (table.aic [6:12, 4])))) / sum (list.aic.like), 3)
table.aic [12, 5] <- round ((exp (-0.5 * (table.aic [12, 4] - min (table.aic [6:12, 4])))) / sum (list.aic.like), 3)


write.table (table.aic, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\table_aic_v3.csv", sep = ",")

# used model with road functional response only (even though cutblock model was a better fit according to AIC) because cutblock fxn didn't appear to improve interpretation of model, i.e., the distance to cut covariate didn't change much over variability in available distance to cut

# save the top model
save (model.lme4.du7.rd.fxn.cut, 
      file = "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\Rmodels\\model_du7_top_v3.rda")

# Create table of model coefficients from top model
model.coeffs <- as.data.frame (coef (summary (model.lme4.du7.rd.fxn.cut)))
model.coeffs$mean_exp_neg0002 <- 0
model.coeffs$sd_exp_neg0002 <- 0

model.coeffs [2, 5] <- mean (exp ((rsf.data.du7$distance_to_cut_1to4yo * -0.002)))
model.coeffs [3, 5] <- mean (exp ((rsf.data.du7$distance_to_cut_over4 * -0.002)))
model.coeffs [4, 5] <- mean (exp ((rsf.data.du7$distance_to_resource_road * -0.002)))

model.coeffs [2, 6] <- sd (exp ((rsf.data.du7$distance_to_cut_1to4yo * -0.002)))
model.coeffs [3, 6] <- sd (exp ((rsf.data.du7$distance_to_cut_over4 * -0.002)))
model.coeffs [4, 6] <- sd (exp ((rsf.data.du7$distance_to_resource_road * -0.002)))

write.table (model.coeffs, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du7_model_fixed_coeffs.csv", sep = ",")

# random effects
re_coeffs.season <- as.data.frame (coef(model.lme4.du7.rd.fxn.cut)$season[1])
re_coeffs.herd <- as.data.frame (coef(model.lme4.du7.rd.fxn.cut)$HERD_NAME[1])

write.table (re_coeffs.season, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du7_model_season_re_coeffs.csv", sep = ",")
write.table (re_coeffs.herd, "C:\\Work\\caribou\\clus_data\\caribou_habitat_model\\model_coefficients\\table_du7_model_herd_re_coeffs.csv", sep = ",")




```






