---
title: "Creating FLEX Cloud Deployment image"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating base image

A new droplet is created with the following parameters:

-   Distro: Ubuntu 22.04 LTS x64

-   Plan: Shared CPU - Basic

-   CPU Options:

    -   Regular with SSD

    -   2GB / 1 CPU

    -   50GB SSD Disk

    -   2TB transfer

-   Data center: Toronto (TOR1)

-   SSH keys: `sasha` (to be replaced by key created by FAIB team)

-   Enabled monitoring

-   Host name: `flex-cloud-image`

## Initial Server Setup

As documented at <https://www.digitalocean.com/community/tutorials/initial-server-setup-with-ubuntu-22-04>.

SSH to droplet and update OS:

```{bash}
ssh root@167.99.186.59 -i ~/.ssh/sasha
apt update
apt upgrade -y
```

Create new user:

```{bash}
adduser flex
```

Pass: F15XP4ss128#$(

The rest of the steps as per doc.

## Add swap space

From the tutorial at https://www.digitalocean.com/community/tutorials/how-to-add-swap-space-on-ubuntu-20-04.

```{bash}
sudo fallocate -l 4G /swapfile
sudo chmod 600 /swapfile
sudo mkswap /swapfile
sudo swapon /swapfile
sudo swapon --show
sudo cp /etc/fstab /etc/fstab.bak
echo '/swapfile none swap sw 0 0' | sudo tee -a /etc/fstab
sudo sysctl vm.swappiness=10
sudo sysctl vm.vfs_cache_pressure=50
sudo nano /etc/sysctl.conf
```

Add the following settings at the bottom of the file:

```
vm.swappiness=10
vm.vfs_cache_pressure=50
```

## Install OS Libraries

Start a `screen` session on the server (so that any running jobs will keep running
if the connection is dropped, and you can reconnect and continue as needed).

```{bash}
screen -S install
```

`screen` tips:

- To detach from the `screen` session and return to the main ssh connection, 
press and hold `Ctrl` key and then press `A` and `D` in sequence.

- If the connection is dropped, you can reconnect with `screen -x install`.

- When the job is done, you can end the session by typing `exit`.

- If you are not sure if you are inside the screen session or not, type `echo $STY`.
If the output is empty, you are not in the `screen` session but in the main ssh 
connection session. If the output is not empty, it is the name of the `screen` 
session you are in.

Install system dependencies:

``` bash
apt install -y libsodium-dev \
    libudunits2-dev \
    libgdal-dev \
    libproj-dev \
    libfontconfig1-dev \
    libharfbuzz-dev \
    libfribidi-dev \
    vim \
    curl \
    git \
    fonts-roboto \
    ghostscript \
    libssl-dev \
    libxml2-dev \
    gdebi-core
```

## Install Java

As per guide at https://www.digitalocean.com/community/tutorials/how-to-install-java-with-apt-on-ubuntu-20-04.

```
sudo apt install default-jre
sudo apt install default-jdk
```

## Install R

Use guide at https://www.digitalocean.com/community/tutorials/how-to-install-r-on-ubuntu-20-04

Start `R` session:

```{bash}
sudo -i R
```

Install packages:

```{r}

install.packages('remotes')

if (!'sqldf' %in% installed.packages()) remotes::install_version('sqldf', '0.4-11')
if (!'RSQLite' %in% installed.packages()) remotes::install_version('RSQLite', '2.2.18')
if (!'gsubfn' %in% installed.packages()) remotes::install_version('gsubfn', '0.7')  
if (!'proto' %in% installed.packages()) remotes::install_version('proto', '1.0.0')
if (!'rgdal' %in% installed.packages()) remotes::install_version('rgdal', '1.5-32')
if (!'raster' %in% installed.packages()) remotes::install_version('raster', '3.6-3')
if (!'sp' %in% installed.packages()) remotes::install_version('sp', '1.5-0')
if (!'sf' %in% installed.packages()) remotes::install_version('sf', '1.0-8')
if (!'rpostgis' %in% installed.packages()) remotes::install_version('rpostgis', '1.4.3')
if (!'RPostgreSQL' %in% installed.packages()) remotes::install_version('RPostgreSQL', '0.7-4')
if (!'DBI' %in% installed.packages()) remotes::install_version('DBI', '1.1.3')
if (!'RANN' %in% installed.packages()) remotes::install_version('RANN', '2.6.1')
if (!'truncnorm' %in% installed.packages()) remotes::install_version('truncnorm', '1.0-8')
if (!'here' %in% installed.packages()) remotes::install_version('here', '1.0.1')
if (!'forcats' %in% installed.packages()) remotes::install_version('forcats', '0.5.2')
if (!'stringr' %in% installed.packages()) remotes::install_version('stringr', '1.4.1')
if (!'dplyr' %in% installed.packages()) remotes::install_version('dplyr', '1.0.10')
if (!'purrr' %in% installed.packages()) remotes::install_version('purrr', '0.3.5')
if (!'readr' %in% installed.packages()) remotes::install_version('readr', '2.1.3')
if (!'tidyr' %in% installed.packages()) remotes::install_version('tidyr', '1.2.1')
if (!'tibble' %in% installed.packages()) remotes::install_version('tibble', '3.1.8')
if (!'ggplot2' %in% installed.packages()) remotes::install_version('ggplot2', '3.3.6')
if (!'tidyverse' %in% installed.packages()) remotes::install_version('tidyverse', '1.3.2')
if (!'keyring' %in% installed.packages()) remotes::install_version('keyring', '1.3.0')
if (!'terra' %in% installed.packages()) remotes::install_version('terra', '1.6-17')
if (!'data.table' %in% installed.packages()) remotes::install_version('data.table', '1.14.4')
if (!'SpaDES.core' %in% installed.packages()) remotes::install_version('SpaDES.core', '1.1.0')
```

If installation of `SpaDES.core` fails, run the following
(reference https://github.com/PredictiveEcology/SpaDES.core/issues/232):

Proceed with other packages:

```{r}
if (!'SpaDES.tools' %in% installed.packages()) remotes::install_version('SpaDES.tools', '1.0.0')
if (!'reproducible' %in% installed.packages()) remotes::install_version('reproducible', '1.2.10')
if (!'quickPlot' %in% installed.packages()) remotes::install_version('quickPlot', '0.1.8')
if (!'CircStats' %in% installed.packages()) remotes::install_version('CircStats', '0.2-6')
if (!'fastdigest' %in% installed.packages()) remotes::install_version('fastdigest', '0.6-3')
if (!'fs' %in% installed.packages()) remotes::install_version('fs', '1.5.2')
if (!'fpCompare' %in% installed.packages()) remotes::install_version('fpCompare', '0.2.4')
if (!'lubridate' %in% installed.packages()) remotes::install_version('lubridate', '1.8.0')
if (!'bit64' %in% installed.packages()) remotes::install_version('bit64', '4.0.5')
if (!'RColorBrewer' %in% installed.packages()) remotes::install_version('RColorBrewer', '1.1-3')
if (!'httr' %in% installed.packages()) remotes::install_version('httr', '1.4.4')
if (!'rprojroot' %in% installed.packages()) remotes::install_version('rprojroot', '2.0.3')
if (!'tools' %in% installed.packages()) remotes::install_version('tools', '4.1.2')
if (!'backports' %in% installed.packages()) remotes::install_version('backports', '1.4.1')
if (!'utf8' %in% installed.packages()) remotes::install_version('utf8', '1.2.2')
if (!'R6' %in% installed.packages()) remotes::install_version('R6', '2.5.1')
if (!'KernSmooth' %in% installed.packages()) remotes::install_version('KernSmooth', '2.23-20')
if (!'rgeos' %in% installed.packages()) remotes::install_version('rgeos', '0.5-9')
if (!'colorspace' %in% installed.packages()) remotes::install_version('colorspace', '2.0-3')
if (!'withr' %in% installed.packages()) remotes::install_version('withr', '2.5.0')
if (!'tidyselect' %in% installed.packages()) remotes::install_version('tidyselect', '1.2.0')
if (!'chron' %in% installed.packages()) remotes::install_version('chron', '2.3-58')
if (!'bit' %in% installed.packages()) remotes::install_version('bit', '4.0.4')
if (!'compiler' %in% installed.packages()) remotes::install_version('compiler', '4.1.2')
if (!'cli' %in% installed.packages()) remotes::install_version('cli', '3.4.1')
if (!'rvest' %in% installed.packages()) remotes::install_version('rvest', '1.0.3')
if (!'xml2' %in% installed.packages()) remotes::install_version('xml2', '1.3.3')
if (!'stringfish' %in% installed.packages()) remotes::install_version('stringfish', '0.15.7')
if (!'scales' %in% installed.packages()) remotes::install_version('scales', '1.2.1')
if (!'checkmate' %in% installed.packages()) remotes::install_version('checkmate', '2.1.0')
if (!'classInt' %in% installed.packages()) remotes::install_version('classInt', '0.4-8')
if (!'proxy' %in% installed.packages()) remotes::install_version('proxy', '0.4-27')
if (!'digest' %in% installed.packages()) remotes::install_version('digest', '0.6.30')
if (!'pkgconfig' %in% installed.packages()) remotes::install_version('pkgconfig', '2.0.3')
if (!'dbplyr' %in% installed.packages()) remotes::install_version('dbplyr', '2.2.1')
if (!'fastmap' %in% installed.packages()) remotes::install_version('fastmap', '1.1.0')
if (!'rlang' %in% installed.packages()) remotes::install_version('rlang', '1.0.6')
if (!'readxl' %in% installed.packages()) remotes::install_version('readxl', '1.4.1')
if (!'rstudioapi' %in% installed.packages()) remotes::install_version('rstudioapi', '0.14')
if (!'generics' %in% installed.packages()) remotes::install_version('generics', '0.1.3')
if (!'RApiSerialize' %in% installed.packages()) remotes::install_version('RApiSerialize', '0.1.2')
if (!'jsonlite' %in% installed.packages()) remotes::install_version('jsonlite', '1.8.3')
if (!'googlesheets4' %in% installed.packages()) remotes::install_version('googlesheets4', '1.0.1')
if (!'magrittr' %in% installed.packages()) remotes::install_version('magrittr', '2.0.3')
if (!'Rcpp' %in% installed.packages()) remotes::install_version('Rcpp', '1.0.9.5')
if (!'munsell' %in% installed.packages()) remotes::install_version('munsell', '0.5.0')
if (!'fansi' %in% installed.packages()) remotes::install_version('fansi', '1.0.3')
if (!'lifecycle' %in% installed.packages()) remotes::install_version('lifecycle', '1.0.3')
if (!'lobstr' %in% installed.packages()) remotes::install_version('lobstr', '1.1.2')
if (!'stringi' %in% installed.packages()) remotes::install_version('stringi', '1.7.8')
if (!'whisker' %in% installed.packages()) remotes::install_version('whisker', '0.4')
if (!'MASS' %in% installed.packages()) remotes::install_version('MASS', '7.3-58.1')
if (!'grid' %in% installed.packages()) remotes::install_version('grid', '4.1.2')
if (!'blob' %in% installed.packages()) remotes::install_version('blob', '1.2.3')
if (!'parallel' %in% installed.packages()) remotes::install_version('parallel', '4.1.2')
if (!'crayon' %in% installed.packages()) remotes::install_version('crayon', '1.5.2')
if (!'Require' %in% installed.packages()) remotes::install_version('Require', '0.1.4')
if (!'lattice' %in% installed.packages()) remotes::install_version('lattice', '0.20-45')
if (!'haven' %in% installed.packages()) remotes::install_version('haven', '2.5.1')
if (!'hms' %in% installed.packages()) remotes::install_version('hms', '1.1.2')
if (!'pillar' %in% installed.packages()) remotes::install_version('pillar', '1.8.1')
if (!'tcltk' %in% installed.packages()) remotes::install_version('tcltk', '4.1.2')
if (!'igraph' %in% installed.packages()) remotes::install_version('igraph', '1.3.5')
if (!'boot' %in% installed.packages()) remotes::install_version('boot', '1.3-28')
if (!'codetools' %in% installed.packages()) remotes::install_version('codetools', '0.2-18')
if (!'fastmatch' %in% installed.packages()) remotes::install_version('fastmatch', '1.1-3')
if (!'reprex' %in% installed.packages()) remotes::install_version('reprex', '2.0.2')
if (!'glue' %in% installed.packages()) remotes::install_version('glue', '1.6.2')
if (!'evaluate' %in% installed.packages()) remotes::install_version('evaluate', '0.17')
if (!'RcppParallel' %in% installed.packages()) remotes::install_version('RcppParallel', '5.1.5')
if (!'modelr' %in% installed.packages()) remotes::install_version('modelr', '0.1.9')
if (!'vctrs' %in% installed.packages()) remotes::install_version('vctrs', '0.5.0')
if (!'tzdb' %in% installed.packages()) remotes::install_version('tzdb', '0.3.0')
if (!'cellranger' %in% installed.packages()) remotes::install_version('cellranger', '1.1.0')
if (!'gtable' %in% installed.packages()) remotes::install_version('gtable', '0.3.1')
if (!'qs' %in% installed.packages()) remotes::install_version('qs', '0.25.4')
if (!'assertthat' %in% installed.packages()) remotes::install_version('assertthat', '0.2.1')
if (!'cachem' %in% installed.packages()) remotes::install_version('cachem', '1.0.6')
if (!'gridBase' %in% installed.packages()) remotes::install_version('gridBase', '0.4-7')
if (!'broom' %in% installed.packages()) remotes::install_version('broom', '1.0.1')
if (!'e1071' %in% installed.packages()) remotes::install_version('e1071', '1.7-12')
if (!'class' %in% installed.packages()) remotes::install_version('class', '7.3-20')
if (!'googledrive' %in% installed.packages()) remotes::install_version('googledrive', '2.0.0')
if (!'gargle' %in% installed.packages()) remotes::install_version('gargle', '1.2.1')
if (!'memoise' %in% installed.packages()) remotes::install_version('memoise', '2.0.1')
if (!'units' %in% installed.packages()) remotes::install_version('units', '0.8-0')
if (!'ellipsis' %in% installed.packages()) remotes::install_version('ellipsis', '0.3.2')
if (!'knitr' %in% installed.packages()) remotes::install_version('knitr', '1.37')


<!-- if (!'latticeExtra' %in% installed.packages()) remotes::install_version('latticeExtra', '0.6-29') -->
<!-- if (!'cppRouting' %in% installed.packages()) remotes::install_version('cppRouting', '2.0') -->
<!-- if (!'snow' %in% installed.packages()) remotes::install_version('snow', '0.4-4') -->
<!-- if (!'gdalUtilities' %in% installed.packages()) remotes::install_version('gdalUtilities', '1.2.0') -->
<!-- if (!'rmarkdown' %in% installed.packages()) remotes::install_version('rmarkdown', '2.13') -->
<!-- if (!'jpeg' %in% installed.packages()) remotes::install_version('jpeg', '0.1-9') -->
<!-- if (!'htmltools' %in% installed.packages()) remotes::install_version('htmltools', '0.5.2') -->
<!-- if (!'yaml' %in% installed.packages()) remotes::install_version('yaml', '2.3.5') -->
<!-- if (!'png' %in% installed.packages()) remotes::install_version('png', '0.1-7') -->
<!-- if (!'openssl' %in% installed.packages()) remotes::install_version('openssl', '2.0.0') -->
<!-- if (!'xfun' %in% installed.packages()) remotes::install_version('xfun', '0.30') -->
<!-- if (!'rJava' %in% installed.packages()) remotes::install_version('rJava', '1.0-6') -->

<!-- if (!'velox' %in% installed.packages()) remotes::install_version('velox', '0.2.1') -->
