---
title: Results from 10 000 reps of fireCastor when run using actual and predicted climate for the year 2023 in the Boundary TSA
author: "Elizabeth Kleynhans"
date: "2024-09-09"
output:
  html_document: default
  keep_md: yes
  pdf_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.align = "left",
                      #fig.width = 5, 
                      #fig.height = 4, 
                      dev = "png",
                      cache = TRUE)
```


```{r library, include = FALSE}

library(data.table)
library(RSQLite)
library(ggplot2)
library(cowplot)
library(dplyr)
source (here::here("R/functions/R_Postgres.R"))
```

## Introduction
We used fire Castor to predict number of ignitions and fire size (area encompassed within the fire perimeter) when climate data was extracted from two different runs of two different GCM's (MPI-ESM1-2-HR and CanESM2) at SSP 2-4.5 and compared these results to simulations run on the actual climate data for the year 2023. This comparison gives us an idea of how different the predicted climate is from the observed climate and how different each GCM run is to the others as well as to the actual observed climate. Lastly, it also helps us understand how climate impacts fireCastor i.e. how sensitive it is. As before vegetation data from the 2022 VRI was used as inputs into fireCastor. 10 000 simulations were performed to get distributions of the number of ignitions and total area burned in the Boundary TSA. These simulation results were also compared to actual burn data from lightning caused fires for the year 2023 in the same area. 

## Observed and predicted climate data for 2023


```{r, climate_data, fig.cap = "**Figure 1.** Climate data obtained from ClimR for two runs of two GCM's and compared to the observed climate data for the year 2023 in the Boundary TSA. cmi = climate moisture index (CMI), cmi3yr = CMI over the past 3 years, Tmax = Maximum temperature recorded between May and August , Summer precipitation = Total precipitation recorded between May and August"}
# plot the number of times burned on the landscap

sqlite <- dbDriver("SQLite")

castordb1 <- dbConnect(sqlite,"C:/Work/caribou/castor/R/scenarios/test_fire/boundary_climate_canesm_ssp245_r1_2023_castordb.sqlite")
climatedat1<-dbGetQuery(castordb1, "SELECT * from climate_canesm_ssp245")
climatedat1<-data.table(climatedat1)
climatedat1<-climatedat1[period==2023,]
canesm<-climatedat1[,c("gcm", "run", "cmi", "cmi3yr", "tmax_04", "tmax_05", "tmax_06", "tmax_07", "tmax_08", "ppt_04", "ppt_05", "ppt_06","ppt_07", "ppt_08")]
canesm<- canesm[run %in% c("r1i1p1f1", "r2i1p1f1"),]

castordb2 <- dbConnect(sqlite,"C:/Work/caribou/castor/R/scenarios/test_fire/boundary_tsa_fire_test_12July24_castordb.sqlite")
#dbListTables(castordb2)
climatedat2<-dbGetQuery(castordb2, "SELECT * from climate_climatena_none")
climatedat2<-data.table(climatedat2)
climatedat2<-climatedat2[period==2023,]
climatedat2$gcm<-"observed"

observed<-climatedat2[,c("gcm", "run", "cmi", "cmi3yr", "tmax_04", "tmax_05", "tmax_06", "tmax_07", "tmax_08", "ppt_04", "ppt_05", "ppt_06","ppt_07", "ppt_08")]

castordb3 <- dbConnect(sqlite,"C:/Work/caribou/castor/R/scenarios/test_fire/boundary_climate_mpi_ssp245_r2_2023_castordb.sqlite")
climatedat3<-dbGetQuery(castordb3, "SELECT * from climate_mpi_ssp245")
climatedat3<-data.table(climatedat3)
climatedat3<-climatedat3[period==2023,]
mpi<-climatedat3[,c("gcm", "run", "cmi", "cmi3yr", "tmax_04", "tmax_05", "tmax_06", "tmax_07", "tmax_08", "ppt_04", "ppt_05", "ppt_06","ppt_07", "ppt_08")]
mpi<- mpi[run %in% c("r1i1p1f1", "r2i1p1f1"),]

dat<-rbind(canesm, mpi)
dat<-rbind(dat, observed)
#table(dat$gcm)
dat$cmi<-as.numeric(dat$cmi)


p1 <- ggplot(dat, aes(x=gcm, y=cmi, fill=run)) + 
  geom_boxplot()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank()) + ylab("cmi") +
  theme(legend.position="none")

p2 <- ggplot(dat, aes(x=gcm, y=cmi3yr, fill=run)) + 
  geom_boxplot()+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank()) + ylab("cmi3yr") 

dat[, tmax_sum:=(tmax_07+tmax_08)/2]

  dat<-dat[, `:=`(PPT_sm = rowSums(.SD, na.rm=T)), .SDcols=c("ppt_05", "ppt_06","ppt_07","ppt_08")]
  dat<-dat[, TEMP_MAX:= do.call(pmax, .SD),.SDcols=c("tmax_05","tmax_06","tmax_07","tmax_08") ]
  
p3 <- ggplot(dat, aes(x=gcm, y=TEMP_MAX,  fill=run)) + 
  geom_boxplot()+
  labs(x = "GCM", y = "Tmax") +
  theme(legend.position="none")


p4 <- ggplot(dat, aes(x=gcm, y=PPT_sm, fill=run)) + 
  geom_boxplot()+
  labs(x = "GCM", y = "Summer precipitation") +
  theme(legend.position="none")

# dat[, tmax_04_05_06:=(tmax_04+tmax_05+tmax_06)/3]
# p5 <- ggplot(dat, aes(x=gcm, y=tmax_04_05_06, fill=run)) + 
#   geom_boxplot()+
#   theme(axis.title.x=element_blank(),
#         axis.text.x=element_blank()) +
#   ylab("Tmax 04_05_06") +
#   theme(legend.position="none")
# 
# dat[, ppt_04_05_06:=(ppt_04+ppt_05+ppt_06)/3]
# p6 <- ggplot(dat, aes(x=gcm, y=ppt_04_05_06, fill=run)) + 
#   geom_boxplot()+theme(axis.title.x=element_blank(),
#         axis.text.x=element_blank()) + ylab ("ppt_04_05_06") +
#   theme(legend.position="none")

plot_grid(p1,p2,p3,p4, labels="AUTO",ncol = 2, align = 'v')


```



## FireCastor results

In general number of ignitions was predicted to be low in the Boundary TSA for all models which is in accordance with the actual data (figure2). Fire size was more variable (figure 3). Note that fire size is on the log scale. Interestingly the actual climate data predicted larger fire sizes than were actually observed.  

```{r fireCastor_number_ignitions, fig.cap = "**Figure 2.** Number of ignitions simulated by fireCastor when using climate data obtained from two different runs of two different GCMs and the observed climate relative to the actual number of ignitions observed (black dashed) in the Boundary TSA for the year 2023"}
fireReportForReps_test <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/outputs/fireReportForReps_test_1.rds")
fireReportForReps_test<-data.table(fireReportForReps_test)
fireReportForReps_test[, gcm:="observed"]

fireReportForReps_test_1 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/CanESM_ssp245_boundaryTSA/outputs/fireReportForReps_CanESM_ssp245_r1i1p1f1_1.rds")

fireReportForReps_test_2 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/CanESM_ssp245_boundaryTSA/outputs/fireReportForReps_CanESM_ssp245_r2i1p1f1_1.rds")

fireReportForReps_test_3 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/mpi_ssp245_boundaryTSA/outputs/fireReportForReps_MPI_ssp245_r2i1p1f1_1.rds")

fireReportForReps_test_4 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/mpi_ssp245_boundaryTSA/outputs/fireReportForReps_MPI_ssp245_r1i1p1f1_1.rds")

fireReportForReps_test_1<-data.table(fireReportForReps_test_1)
fireReportForReps_test_1[, gcm:="CanESM_r1"]
fireReportForReps_test_2<-data.table(fireReportForReps_test_2)
fireReportForReps_test_2[, gcm:="CanESM_r2"]
fireReportForReps_test_3<-data.table(fireReportForReps_test_3)
fireReportForReps_test_3[, gcm:="MPI_r2"]
fireReportForReps_test_4<-data.table(fireReportForReps_test_4)
fireReportForReps_test_4[, gcm:="MPI_r1"]

dat1<-bind_rows(list(fireReportForReps_test, fireReportForReps_test_1, fireReportForReps_test_2, fireReportForReps_test_3, fireReportForReps_test_4))


dat1$numberstarts<-as.numeric(dat1$numberstarts)

# Basic box plot
p <- ggplot(dat1, aes(x=gcm, y=numberstarts)) + 
  geom_boxplot()+
  geom_hline(aes(yintercept = 3),colour = "blue", linetype="dashed", size=0.5) +
  labs(x = "climate data", y = "Number of ignitions")
p


```

```{r individual_firesize, fig.cap = "**Figure 3.** Distribution of fire sizes simulated by fireCastor. The average actual fire size observed in Boundary TSA in 2023 is represented by the dashed black line. Note that area burned is on a log  scale"}
firesize<-readRDS("C:\\Work\\caribou\\castor\\R\\scenarios\\test_fire\\outputs\\perFireReportForReps_test_1.rds")

firesize_can_esm_r1 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/CanESM_ssp245_boundaryTSA/outputs/perFireReportForReps_CanESM_ssp245_r1i1p1f1_1.rds")

firesize_can_esm_r2 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/CanESM_ssp245_boundaryTSA/outputs/perFireReportForReps_CanESM_ssp245_r2i1p1f1_1.rds")

firesize_mpi_r1 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/mpi_ssp245_boundaryTSA/outputs/perFireReportForReps_MPI_ssp245_r1i1p1f1_1.rds")

firesize_mpi_r2 <- readRDS("C:/Work/caribou/castor/R/scenarios/test_fire/mpi_ssp245_boundaryTSA/outputs/perFireReportForReps_MPI_ssp245_r2i1p1f1_1.rds")

firesize<-data.table(firesize)
firesize[, gcm:="observed"]
firesize_can_esm_r1<-data.table(firesize_can_esm_r1)
firesize_can_esm_r1[, gcm:="CanESM_r1"]
firesize_can_esm_r2<-data.table(firesize_can_esm_r2)
firesize_can_esm_r2[, gcm:="CanESM_r2"]
firesize_mpi_r2<-data.table(firesize_mpi_r2)
firesize_mpi_r2[, gcm:="MPI_r2"]
firesize_mpi_r1<-data.table(firesize_mpi_r1)
firesize_mpi_r1[, gcm:="MPI_r1"]

dat1<-bind_rows(list(firesize, firesize_can_esm_r1, firesize_can_esm_r2, firesize_mpi_r2, firesize_mpi_r1))


dat1$areaburned_estimated<-as.numeric(dat1$areaburned_estimated)
dat1$log_areaburned<-log(dat1$areaburned_estimated)

# Basic box plot
p <- ggplot(dat1, aes(x=gcm, y=log_areaburned)) + 
  geom_boxplot()+
  #ylim(0,10)+
  geom_hline(aes(yintercept = log(3)),colour = "blue", linetype="dashed", size=0.5) +
  labs(x = "climate data", y = "Log area burned")
p


```


