<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Database creation for Boundary"
author: "Kyle Lochhead"
date: "26-March-2024"
output: pdf_document
---

# Overview
Simulate climate impacted fire regimes in the Boundary TSA. Build the castordb to allow the forest structure to change given harvest schedule determined by STSM.

# Usage
Set parameters for creating the database in the code chunk below.

```{r module_usage}
library (SpaDES)
library (SpaDES.core)
library (data.table)
library (keyring)
library (terra)

source (here::here("R/functions/R_Postgres.R"))

Sys.setenv(JAVA_HOME = 'C:\\Program Files\\Java\\jdk-14.0.1') #throws an error if pointing to different version of java (i.e., 32 vs 64 bit)

moduleDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules"))
inputDir <- file.path (paste0 (here::here (), "/R/scenarios/boundary_fire/inputs")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path (paste0 (here::here (), "/R/scenarios/boundary_fire/outputs")) %>% reproducible::checkPath (create = TRUE)


times <- list (start = 0, end = 0)
parameters <-  list (
        .progress = list (type = NA, interval = NA),
        .globals = list (),
        dataCastor = list(dbHost=keyring::key_get('dbhost', keyring = 'postgreSQL'),
                          dbName = keyring::key_get('dbname', keyring = 'postgreSQL'),
                    dbPort='5432' ,
                    dbUser=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                    dbPass= keyring::key_get('dbpass', keyring = 'postgreSQL'),
                         saveCastorDB = TRUE,
                          sqlite_dbname = "boundary_fire", 
                          nameBoundaryFile = "public.boundary_fire", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = "Boundary_TSA", 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "rast.tsa", 
                          nameCompartmentTable = "vat.tsa", 
                          nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2022',  
                          nameZoneRasters = c ("rast.zone_cond_nharv","rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo",
                                               "rast.zone_wha_2021", 
                                               "rast.zone_uwr_2021"
                                               ),
                          nameZoneTable = "zone.constraints", 
                          # natural and managed stands yield curves are the same    
                          nameYieldsRaster = "rast.ycid_vdyp_2020", 
                          nameYieldTable = "yc_vdyp_2020", 
                          nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                          nameYieldCurrentTable = "tipsy_prov_current_2020",
                          nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                          nameYieldTransitionTable = "tipsy_prov_2020",  
                          nameForestInventoryRaster = "rast.vri2023_id", 
                          nameForestInventoryKey = "feature_id", 
                          nameForestInventoryTable = "vri.veg_comp_lyr_r1_poly2023",
                          nameForestInventoryAge = "proj_age_1",  
                          nameForestInventoryHeight = "proj_height_1",
                          nameForestInventoryCrownClosure = "crown_closure",                             
                          nameForestInventoryTreed = "bclcs_level_2",
                          nameForestInventoryBasalArea= "basal_area",
                          nameForestInventoryQMD = "quad_diam_125",
                          nameForestInventorySiteIndex = "site_index" 
                          ),
        growingStockCastor = list (periodLength = 1),
        blockingCastor = list(blockMethod = 'pre', 
                              patchZone = 'rast.zone_cond_beo',
                              patchVariation = 6,
                              nameCutblockRaster ="rast.cns_cutblk_2023",
                              useLandingsArea = FALSE),
        roadCastor = list (roadMethod = 'mst',
                           nameCostSurfaceRas = 'rast.rd_cost_surface',
                           nameRoads =  'rast.ce_road_2022'
                           ),
        forestryCastor = list(),
        fireCastor = list(calculateInterval =1,
                    ignitionMethod = 'poissonProcess', # options are poissonProcess, historicalDist, static
                    #calendarStartYear = 2020,
                    nameFrtRaster = "rast.frt",
                    nameAspectRaster = "rast.bc_ha_aspect",
                    nameSlopeRaster = "rast.bc_ha_slope",
                    nameDistInfrastructureRaster = "rast.dist_infrastructure",
                    nameRoadsRast = "rast.ce_road_2022",
                    #recovery = 300,
                    nameElevationRaster = "rast.dem",
                    #nameClimateIdnoRast="rast.climate_prism_base_layer",
                    #nameClimateTable = "vat.climate_prism_lat_lon_lookup",
                    simStartYear = 2023,
                    nameBecRast = "rast.bec_current",
                    nameBecTable = "vat.bec_zone_vat",
                    #nameForestInventoryRaster = "rast.vri2023_id",
                    #nameForestInventoryTable = "vri.veg_comp_lyr_r1_poly2023",
                    #nameForestInventoryKey = "feature_id",
                    nameForestInventorybclcs_level_1 = "bclcs_level_1",
                    nameForestInventorybec_zone_code = '99999',
                    pixelid_10kmRast = "rast.pixelId10km",
                    nameFirepixel10km = "vat.spatially_varying_10km_vat",
                    numberFireReps = 1),
        climateCastor= list(gcm='MPI-ESM1-2-HR', #"ACCESS_ESM1_5", "CanESM5", "MPI_ESM1_2_HR" Note that MPI_ESM1_2HR seems to only have r1i1p1f1 and r2i1p1f1 for ssp 126 and ssp245. 
                            gcmname='MPI_ESM1_2_HR', 
                            ssp ='ssp370', #"ssp126", ""ssp245", "ssp370"
                            climateData = "future",
                            run = "r1i1p1f1",
                            maxRun =2,
                            climateYears = 2021:2060, nameClimateIdnoRast ='rast.climate_prism_base_layer', nameClimateTable='vat.climate_prism_lat_lon_lookup', vars_aoi=c("PPT_03","PPT_04", "PPT_05","PPT_06","PPT_07", "PPT_08", "PPT_09","Tmax_04", "Tmax_05", "Tmax_06", "Tmax_07", "Tmax_08", "Tmax_09", "Tave_03","Tave_04", "Tave_05", "Tave_06", "Tave_07", "Tave_08", "Tave_09", "Tmin_03", "Tmin_04", "Tmin_05", "Tmin_06", "Tmin_07", "Tmin_08" ,"CMD_04", "CMD_05", "CMD_06", "CMD_07", "CMD_08", "CMI_03", "CMI_04", "CMI_05", "CMI_06", "CMI_07", "CMI_08", "CMI_09"),
nameProvCMITable = "public.prov_cmi_ave",
                               vars_prov = c("CMI05", "CMI06", "CMI07", "CMI08")),
        disturbanceCastor = list(calculateInterval =  1, 
                                 permDisturbanceRaster = "rast.mine_ag_wind_rail",
                                 recovery = 300),
        uploadCastor = list(aoiName = 'boundary',
                              dbInfo  = list(keyring::key_get ("vmdbhost", keyring="postgreSQL"),
                                             keyring::key_get ("vmdbuser", keyring="postgreSQL"),
                                             keyring::key_get ("vmdbpass", keyring="postgreSQL"), 
                                             keyring::key_get ("vmdbname", keyring="postgreSQL")))
        )

scenario = data.table (name = "load_data_2024oct10", description = "dataCastor output")

modules <- list("dataCastor",
                "growingStockCastor",
                "blockingCastor", 
                "roadCastor",
                "forestryCastor",
                "disturbanceCastor",
                "climateCastor",
                "fireCastor"
                #"uploadCastor"
                )

objects <- list (scenario = scenario
                 )

paths <- list(modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

inputs <- list()
outputs <- list()

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)

system.time({
mysimout<-spades(mySim)
})

```

#Adjust the blocks table
Each pixel is its own block from stsm
```{r}
library(readr)
#Outputs from STSM
harvest.schedule<-data.table(read_tsv("harvest_sched/logDebug.txt", col_names = TRUE))
#currBlockId is not unique across the sim. It resets back to one by each period. Assign a unique blockid to each block
harvest.schedule[, blockid:=paste0( yr, yearInPeriod,"0", currBlockId)][, blockid:=as.integer(blockid)]

#connect to castordb
castordb <- dbConnect(RSQLite::SQLite(), dbname ="boundary_fire_castordb.sqlite")

#Get castordb blank/dummy raster
ras.info<-dbGetQuery(castordb, "SELECT * FROM raster_info where name = 'ras';")
print(ras.info)
ras<-rast(xmin= ras.info$xmin, xmax=ras.info$xmax, ymin=ras.info$ymin, ymax=ras.info$ymax, nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow)
crs(ras) <-st_crs(as.integer(ras.info$crs))$wkt


#Update the pixels table
dbBegin (castordb)
rs <- dbSendQuery (castordb, "UPDATE pixels set blockid = :blockid where pixelid = :ogc_fid", harvest.schedule[,c("blockid", "ogc_fid")])
dbClearResult (rs)
dbCommit (castordb)


#remove old blocks from blockingCastor
dbExecute(castordb, "DElete from blocks;")

landing.info<-dbGetQuery(castordb, "select pixelid, dist, thlb from pixels order by pixelid")

edges.weight<-data.table(dbGetQuery(castordb, "select * from roadedges;"))
node.coords<-data.table(dbGetQuery(castordb, "select * from roadcoords;"))
g<-cppRouting::makegraph(edges.weight,directed=F, coords = node.coords) 
graph.df<-cppRouting::to_df(g)
dbDisconnect(castordb)

blocks<-unique(harvest.schedule[, c("ogc_fid", "blockid")])
ras.blocks<-ras
ras.blocks[blocks$ogc_fid]<-blocks$blockid

#get the landings
base.blocks.tab<-data.table(blockid = ras.blocks[], pixelid = landing.info$pixelid, dist = landing.info$dist, thlb = landing.info$thlb)
setnames(base.blocks.tab, "blockid.lyr.1", "blockid")

base.blocks.tab<-base.blocks.tab[ blockid > 0, ][, mdist := min(dist), by = blockid][order(blockid)]

landings<-base.blocks.tab[ dist==mdist, ][, mpixelid := max(pixelid), by = blockid][pixelid == mpixelid,]

#check to make sure in graph
verts<-unique(c(as.integer(graph.df$from), as.integer(graph.df$to)))
landings[pixelid %in% verts, in.graph:=1 ]
test<-landings[is.na(in.graph),] #616 outside of graph...in perm roads since dist ==0

castordb <- dbConnect(RSQLite::SQLite(), dbname ="boundary_fire_castordb.sqlite")
out<-landings[,c("blockid", "pixelid")]

dbBegin (castordb)
rs <- dbSendQuery (castordb, "INSERT into blocks (blockid, landing) values (:blockid, :pixelid)", out)
dbClearResult (rs)
dbCommit (castordb)

dbGetQuery(castordb, "select * from blocks limit 10;")
dbDisconnect(castordb)
```

## Harvest Schedule from STSM
forestryCastor needs a raster stack of harvest units in each time period

### Get the harvest seqeuence and raster grid
```{r}
library(sf)
library(terra)
#the outputs from STSM
ras.pixelid<-rast("harvest_sched/tsa02_ogc_id.tif") 
harvest.schedule<-data.table(read_tsv("harvest_sched/logDebug.txt", col_names = TRUE))
#currBlockId is not unique across the sim. It resets back to one by each period. Assign a unique blockid to each block
harvest.schedule[, blockid:=paste0( yr, yearInPeriod,"0", currBlockId)][, blockid:=as.integer(blockid)]

#check for duplicates
if(length(unique(harvest.schedule$ogc_fid)) == nrow(harvest.schedule)){
  message("no dups")
}else{
  message("dups")
}

#Connect to the Castordb to get the raster information
con = dbConnect(RSQLite::SQLite(), dbname = "boundary_fire_castordb.sqlite")
ras.info<-dbGetQuery(con, "SELECT * FROM raster_info where name = 'ras';")
print(ras.info)
ras<-rast(xmin= ras.info$xmin, xmax=ras.info$xmax, ymin=ras.info$ymin, ymax=ras.info$ymax, nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow)
crs(ras) <-st_crs(as.integer(ras.info$crs))$wkt
dbDisconnect(con)

#Check the castordb rastor is the same as the input
if(ext(ras) == ext(ras.pixelid)){
  message("same raster")
  ras[]<-0
}else{
  message("wrong raster extents")
}

#Need to convert the pixels values in ras.harvest.schedule into blockids. All I need is the logDebug.txt file and the ogc_fid
harvest.schedule$sim_year<- 1 + harvest.schedule$yr + harvest.schedule$yearInPeriod #Annualize - the current set up for fireCastor

ras.hseq<-lapply(1:max(harvest.schedule$sim_year), function(x){
  temp<-harvest.schedule[sim_year ==x, ]
  ras.temp<-ras
  ras.temp[temp$ogc_fid]<-temp$blockid
  names(ras.temp) <- paste0("hsq_", x)
  ras.temp
})

out<-rast(ras.hseq)
writeRaster(out, "boundary_fire_hsq.tif", overwrite = TRUE)


```