---
title: "FLEX2"
author: ""
date: "26 October 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'

```

## Overview
This is an agent based model (ABM) to simulate fisher life history on a landscape. This version is written to input habitat data that was written as a raster output from the fisherHabitatLoader module. The fisherHabitatLoader saves rasters of the occurrence of fisher habitat types (denning, rust, cavity, resting and movement) at each interval of a forestry simulation using forestryCLUS. The forestryCLUS module is a simulation model that returns a single solution for a set of parameters (i.e., it's a deterministic model). Thus fisherHabitatLoader updates fisher habitat conditions over a simulation period. This approach  allows for faster simulation of multiple iterations of a fisher population on a landscape. as it can read the habitat conditions as predtemined by the simualtion model. I is more efficient to run the fisher ABM as a *post-hoc* analysis, rather than concurrently with forestryCLUS.

## Usage
Below runs the module

```{r module_usage}
library (SpaDES.core)
library (data.table)
library (terra)
library (keyring)
library (tidyverse)
library (here)
library (stringr)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2/inputs")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2/outputs")) %>% reproducible::checkPath (create = TRUE)
cacheDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2"))

times <- list (start = 0, end = 1)

parameters <- list(
  dataLoaderCLUS = list(dbName='clus',
                         save_clusdb = FALSE, # Set to TRUE first time running the analysis
                         sqlite_dbname = "fisherABM_test", 
                         nameBoundaryFile = "tsa_aac_bounds",
                         useCLUSdb = paste0(here::here(), "/R/scenarios/test_flex2/fisherABM_test_clusdb.sqlite"),
                         nameBoundaryColumn = "tsa_name", 
                         nameBoundary = c ("Williams_Lake_TSA"), 
                         nameBoundaryGeom = 'wkb_geometry',
                         nameCompartmentRaster = "rast.tsa_aac_boundary",
                         nameCompartmentTable = "vat.tsa_aac_bounds_vat",
                         nameMaskHarvestLandbaseRaster ='rast.thlb_2020', 
                         nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw"
                              ),
                         nameZoneTable="zone.constraints", 
                         nameYieldsRaster = "rast.ycid_vdyp_2020",
                         nameYieldTable ="yc_vdyp_2020",
                         nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                         nameYieldCurrentTable = "tipsy_current_prov_2020",
                         nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                         nameYieldTransitionTable = "tipsy_prov_2020", 
                         nameForestInventoryRaster = "rast.vri2020_id", 
                         nameForestInventoryKey = "feature_id",                     
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2020",
                         nameForestInventoryAge = "proj_age_1",  
                         nameForestInventoryHeight = "proj_height_1",
                         nameForestInventoryCrownClosure = "crown_closure",
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index",
                         nameForestInventoryBasalArea= "basal_area",
                         nameForestInventoryQMD = "quad_diam_125"
                    ),
  growingStockCLUS = list (periodLength = 5),
  FLEX2 = list (female_max_age = 9,
                den_target = 0.003, 
                rest_target = 0.028,
                move_target = 0.091,
                #reproductive_age = 2,
                sex_ratio = 0.5,
                female_dispersal = 785000,  # ha; radius = 500 pixels = 50km = 7850km2 area
                timeInterval = 1,
                iterations = 1,
                rasterStack = paste0 (here::here(), "/R/scenarios/test_flex2/outputs/test_fisher_habitat_Williams_Lake_TSA_fisher_habitat.tif")
                ),
    uploaderCLUS = list(aoiName = 'fisher_abm_test', 
                        dbInfo  = list(keyring::key_get ("vmdbhost", keyring="postgreSQL"), 
                                       keyring::key_get ("vmdbuser", keyring="postgreSQL"), 
                                       keyring::key_get ("vmdbpass", keyring="postgreSQL"),  
                                       keyring::key_get ("vmdbname", keyring="postgreSQL")))
)

scenario = data.table (name = "test",
                       description = "Testing fisher ABM.")

modules <- list ("FLEX2",
                 "growingStockCLUS",
                 "uploaderCLUS",
                 "dataLoaderCLUS")

objects <- list (scenario = scenario)
inputs <- list ()
outputs <- data.frame (objectName = c("harvestReport",
                                      "growingStockReport",
                                      "fisherABMReport"
                                      ))

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)

mySimOut <- spades(mySim)
```

