---
title: "FLEX2"
author: ""
date: "26 October 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'

```

## Overview
This is an agent based model (ABM) to simulate fisher life history on a landscape. This version is written to input habitat data that was written as a raster output from the fisherHabitatLoader module. The fisherHabitatLoader saves rasters of the occurrence of fisher habitat types (denning, rust, cavity, resting and movement) at each interval of a forestry simulation using forestryCLUS. The forestryCLUS module is a simulation model that returns a single solution for a set of parameters (i.e., it's a deterministic model). Thus fisherHabitatLoader updates fisher habitat conditions over a simulation period. This approach  allows for faster simulation of multiple iterations of a fisher population on a landscape. as it can read the habitat conditions as predetermined by the simulation model. I is more efficient to run the fisher ABM as a *post-hoc* analysis, rather than concurrently with forestryCLUS.

## Usage
Below runs the module

```{r module_usage}
library (SpaDES.core)
library (data.table)
library (terra)
library (keyring)
library (tidyverse)
library (here)
library (stringr)
library (truncnorm)
source (paste0 (here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2/inputs")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2/outputs")) %>% reproducible::checkPath (create = TRUE)
cacheDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2"))

times <- list (start = 0, end = 2)

parameters <- list(FLEX2 = list (female_max_age = 9,
                                 den_target = 0.003, 
                                 rest_target = 0.028,
                                 move_target = 0.091,
                                 reproductive_age = 2, 
                                 sex_ratio = 0.5,
                                 female_dispersal = 785000,  # ha; radius = 500 pixels = 50km = 7850km2 area
                                 timeInterval = 5, # should be consistent with the time interval used to model habitat
                                                    # e.g., growingstockLCUS periodLength
                                 iterations = 1, # not currently implemented
                                 rasterStack = paste0 (here::here(), "/R/scenarios/test_flex2/inputs/test2_fisher_habitat_Williams_Lake_TSA_fisher_habitat.tif")
                )
)

scenario = data.table (name = "test",
                       description = "Testing fisher ABM.")

modules <- list ("FLEX2")

objects <- list (scenario = scenario)
inputs <- list ()
outputs <- data.frame (objectName = c())

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)

mySimOut <- spades(mySim)
```

