---
title: "wolverine"
output: html_document
date: '2023-11-02'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(raster)
prov_rast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = 3005, resolution = c(100, 100), vals = 0
)
```

## Wolverine Spatial Boundary
The spatial boundary for the herd was sourced bc_caribou_herd_boundary_v20220725. The spatial line work for high eleveation and low elevation habitat (These are the current draft Wolverine Caribou High and Low elevation areas as discussed) was sent Mon October 23, 2023 by Tyler using the files: Wolverine_Caribou_HE_Polygon.shp and Wolverine_Caribou_LE_Polygon.shp

### Create an area of interest boundary
#### Get information 
```{r}
setwd("C:\\Users\\klochhea\\castor\\R\\scenarios\\wolverine\\spatial")
herd<-st_read("wolverine_herd_boundary.shp")
low<-st_zm(st_read("Wolverine_Caribou_LE_Polygon.shp"), drop = TRUE, what = "ZM")
high<-st_zm(st_read("Wolverine_Caribou_HE_Polygon.shp"), drop = TRUE, what = "ZM")
```
#### Union the layers together
```{r}
setwd("C:\\Users\\klochhea\\castor\\R\\scenarios\\wolverine\\spatial")
aoi<-st_union(herd, low) # a small section from the low is outside the herd boundary
#
aoi<-st_as_sf(st_union(aoi))
aoi$herd <-1
aoi$herd_name<-"Wolverine"
st_write(aoi, "wolverine_aoi.shp", append = FALSE)
aoi.ras<-fasterize::fasterize(aoi, prov_rast, "herd")
aoi.ras[is.na(aoi.ras[])]<-0
writeRaster(aoi.ras, "wolverine_boundary.tif")
```

### Create constraint layer
```{r}
setwd("C:\\Users\\klochhea\\castor\\R\\scenarios\\wolverine\\spatial\\")

high$crit_hab<-1
high.ras<-fasterize::fasterize(high, prov_rast, "crit_hab")
high.ras[is.na(high.ras[])]<-0
low$crit_hab<-2
low.ras<-fasterize::fasterize(low, prov_rast, "crit_hab")
low.ras[is.na(low.ras[])]<-0
crit.ras<-low.ras + high.ras
writeRaster(crit.ras, "wolverine_crit.tif")
```

### Calculate LRSY
```{r}
castordb <- dbConnect(RSQLite::SQLite(), dbname ="C:/Users/klochhea/castor/R/scenarios/wolverine/wolverine_castordb.sqlite")

mai<-dbGetQuery(castordb, "select max(tvol/age) as mai, yieldid from yields where yieldid  > 0 group by yieldid ;")

pixels<-dbGetQuery(castordb, "select thlb, yieldid_trans from pixels where thlb > 0 ;")

lrsy<-data.table(merge(pixels, mai, by.x= "yieldid_trans", by.y = "yieldid"), all.x =T)
lrsy[,mean(mai, na.rm =T)]


```