---
title: "fisherabmCLUS"
author: ""
date: "25 July 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'

```

## Overview
This is an agent based model (ABM) to simulate fisher life history on a landscape. This version is written to integrate in 'real-time' with Castor/CLUS modules and database. That is, the Castor/CLUS database is called at each time interval to update the fisher habitat conditions. Note that this approach is 'slow', as it waits on forestryCLUS, etc. to update the habitat conditions before simulating fishers. 

As an alternative, we're working on a version that integrates with a raster stack object, which is the output of fisher habitat conditions, as calculated from forest stand characteristics simulated in forestryCLUS, from each time interval. This approach will allow for faster simulation of multiple iterations of a fisher population. Currently, forestryCLUS is a simulation model that returns a single solution for a set of parameters (i.e., it's a deterministic model). However, the fisher agent based model includes individual randomness (i.e., it's stochastic), for example, for survival and reproduction. Since the habitat dynamics returned from forestryCLUS will always be the same result for a given simulation, it is more efficient to run the fisher ABM as a *post-hoc* analysis, rather than concurrently with forestryCLUS.

## Castor/CLUS SQLite Database
Below is some code to connect to and query the clusdb, which is needed to run this version of the fisher ABM.

```{r some code to acces the sqlite db}
library (DBI)
library (data.table)
library (here)
source (paste0 (here::here (), "/R/functions/R_Postgres.R"))

# connect to the db
clusdb <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/test_flex2/fisherABM_test_clusdb.sqlite"))

# show tables in the db
dbListTables (clusdb)

# select all contents in a table, e.g., agents
table <- as.data.table (dbGetQuery (clusdb, "SELECT * FROM pixels"))


```


## Usage
Below runs the module, in 'real-time' integration with other Castor/CLUS modules.

```{r module_usage}
library (SpaDES.core)
library (data.table)
library (terra)
library (keyring)
library (tidyverse)
library (here)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2/inputs")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2/outputs")) %>% reproducible::checkPath (create = TRUE)
cacheDir <- file.path(paste0(here::here(), "/R/scenarios/test_flex2"))

times <- list (start = 0, end = 1)

parameters <- list(
  dataLoaderCLUS = list(dbName='clus',
                         save_clusdb = FALSE, # Set to TRUE first time running the analysis
                         sqlite_dbname = "fisherABM_test", 
                         nameBoundaryFile = "tsa_aac_bounds",
                         useCLUSdb = paste0(here::here(), "/R/scenarios/test_flex2/fisherABM_test_clusdb.sqlite"),
                         nameBoundaryColumn = "tsa_name", 
                         nameBoundary = c ("Williams_Lake_TSA"), 
                         nameBoundaryGeom = 'wkb_geometry',
                         nameCompartmentRaster = "rast.tsa_aac_boundary",
                         nameCompartmentTable = "vat.tsa_aac_bounds_vat",
                         nameMaskHarvestLandbaseRaster ='rast.thlb_2020', 
                         nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw"
                              ),
                         nameZoneTable="zone.constraints", 
                         nameYieldsRaster = "rast.ycid_vdyp_2020",
                         nameYieldTable ="yc_vdyp_2020",
                         nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                         nameYieldCurrentTable = "tipsy_current_prov_2020",
                         nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                         nameYieldTransitionTable = "tipsy_prov_2020", 
                         nameForestInventoryRaster = "rast.vri2020_id", 
                         nameForestInventoryKey = "feature_id",                     
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2020",
                         nameForestInventoryAge = "proj_age_1",  
                         nameForestInventoryHeight = "proj_height_1",
                         nameForestInventoryCrownClosure = "crown_closure",
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index",
                         nameForestInventoryBasalArea= "basal_area",
                         nameForestInventoryQMD = "quad_diam_125"
                    ),
  growingStockCLUS = list (periodLength = 5),
  fisherabmCLUS = list (female_max_age = 9,
                        den_target = 0.003, 
                        rest_target = 0.028,
                        move_target = 0.091,
                        #reproductive_age = 2,
                        sex_ratio = 0.5,
                        female_dispersal = 785000,  # ha; radius = 500 pixels = 50km = 7850km2 area
                        timeInterval = 1,
                        iterations = 1),
    uploaderCLUS = list(aoiName = 'fisher_abm_test', 
                        dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL")))
)

scenario = data.table (name = "test",
                       description = "Testing fisher ABM.")

modules <- list ("fisherabmCLUS",
                 "growingStockCLUS",
                 "uploaderCLUS",
                 "dataLoaderCLUS")

objects <- list (scenario = scenario)
inputs <- list ()
outputs <- data.frame (objectName = c("harvestReport",
                                      "growingStockReport",
                                      "fisherABMReport"
                                      ))

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)

mySimOut <- spades(mySim)
```

