---
title: "fisherabmCLUS"
author: ""
date: "25 July 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'
```

# Overview

This is an agent based model (ABM) to simulate fisher life history on a landscape. 
For help writing in R Markdown, see https://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

setPaths(modulePath = file.path("C:/Work/git/clus/R/SpaDES-modules"))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 10)

parameters <- list(
  dataLoaderCLUS = list(dbName='clus',
                         save_clusdb = FALSE,
                         sqlite_dbname = "central_group_july2022", 
                         nameBoundaryFile = "central_grp_aoi_072022",
                         useCLUSdb = paste0(here::here(), "/R/SpaDES-modules/fisherabmCLUS/test.sqlite"),
                         nameBoundaryColumn = "tsa_name", 
                         nameBoundary = c ("central_group"), 
                         nameBoundaryGeom = 'wkb_geometry',
                         nameCompartmentRaster = "rast.central_grp_aoi",
                         nameCompartmentTable = "vat.central_grp_aoi",
                         nameMaskHarvestLandbaseRaster ='rast.thlb_2020', 
                         nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw"
                              ),
                         nameZoneTable="zone.constraints", 
                         nameYieldsRaster = "rast.ycid_vdyp_2020",
                         nameYieldTable ="yc_vdyp_2020",
                         nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                         nameYieldCurrentTable = "tipsy_current_prov_2020",
                         nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                         nameYieldTransitionTable = "tipsy_prov_2020", 
                         nameForestInventoryRaster = "rast.vri2020_id", 
                         nameForestInventoryKey = "feature_id",                     
                         nameForestInventoryTable = "veg_comp_lyr_r1_poly2020",
                         nameForestInventoryAge = "proj_age_1",  
                         nameForestInventoryHeight = "proj_height_1",
                         nameForestInventoryCrownClosure = "crown_closure",
                         nameForestInventoryTreed = "bclcs_level_2",
                         nameForestInventorySiteIndex = "site_index",
                         nameForestInventoryBasalArea= "basal_area",
                         nameForestInventoryQMD = "quad_diam_125"
                    ),
  fisherabmCLUS = list (n_females = 100,
                        female_hr_table = "call the table from the pgdb",
                        female_max_age = 10,
                        female_search_radius = 5,
                        den_target = 0.1, # set to a proportion/data table?
                        rest_target = 0.2,
                        move_target = 0.4,
                        survival_rate_table = "call the table from the pgdb",
                        d2_reproduction_adj = "fxn, multiplier...?",
                        reproductive_age = 2,
                        repro_rate_table = "call the table from the pgdb",
                        sex_ratio = 0.5,
                        max_female_dispersal_dist = 10,
                        timeInterval = 1
                        )
    
  #.progress = list(type = "text", interval = 1), # for a progress bar
  ## If there are further modules, each can have its own set of parameters:
  #module1 = list(param1 = value1, param2 = value2),
  #module2 = list(param1 = value1, param2 = value2)
)
modules <- list("fisherabmCLUS")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

mySimOut <- spades(mySim)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("fisherabmCLUS", "C:/Work/git/clus/R/SpaDES-modules")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("fisherabmCLUS", "C:/Work/git/clus/R/SpaDES-modules")` may be sufficient.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("fisherabmCLUS", "C:/Work/git/clus/R/SpaDES-modules")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("fisherabmCLUS", "C:/Work/git/clus/R/SpaDES-modules")
knitr::kable(df_outputs)
```

# Links to other modules

Describe any anticipated linkages to other modules.
