---
title: "01_Fire_ignition_data_prep"
author: "Elizabeth Kleynhans, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests"
        "Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests"  
date: "2024-07-24"
output: html_document
---

<!-- # Copyright 2024 Province of British Columbia -->
<!-- #  -->
<!-- # Licensed under the Apache License, Version 2.0 (the "License"); -->
<!-- # you may not use this file except in compliance with the License. -->
<!-- # You may obtain a copy of the License at -->
<!-- #  -->
<!-- # http://www.apache.org/licenses/LICENSE-2.0 -->
<!-- #  -->
<!-- # Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS, -->
<!-- # WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied. -->
<!-- # See the License for the specific language governing permissions and limitations under the License. -->

##Overview -->

The aim of this script is to get fire ignition data for all lightning caused fires. Then I join this fire ignition data to all the associated covariate data to run analyses on. The covariates that I use in the analysis include fire regime type, elevation, slope, aspect, climate data, distance to roads and infrastructure, and vegetation data.

The analysis investiages what variables best predict whether a fire will grow larger than 1ha i.e. escapes or whether it will not i.e. the fire never reaches 1ha in size. Its a simple logistic regression analysis. See 02_ignition_model_fit.Rmd for this analysis.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(bcdata)
require (dplyr)
require (RPostgreSQL)
require (rpostgis)
library(ggplot2)
library(terra)
library(climr)
library(data.table)
library(sf)

library(keyring)

source(here::here("R/functions/R_Postgres.R"))
```

##Get ignition data off the the BC data catalogue (https://catalogue.data.gov.bc.ca/dataset/bc-wildfire-fire-incident-locations-historical)
```{r}
ignit<-try(
  bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_INCIDENTS_SP") %>%
    filter(FIRE_YEAR > 2008) %>%
    filter(FIRE_TYPE == "Fire") %>%
    collect()
)

#get FRT
#FRT<-getSpatialQuery("SELECT * FROM public.frt_canada")

FRT<-st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\frt_clipped.shp")

#get provincial boundary for clipping the layers to the area of interest
prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
crs(prov.bnd)# this one needs to be transformed to 3005
bc.bnd <- st_transform (prov.bnd, 3005) #Transform coordinate system
st_crs(bc.bnd)

#Clip FRT to BC boundary
frt_clipped<-st_intersection(bc.bnd, FRT)
#plot(st_geometry(frt_clipped), col=sf.colors(10,categorical=TRUE))
length(unique(frt_clipped$Cluster))
frt_sf<-st_as_sf(frt_clipped)

# note clipping the fire locations to the BC boundary removes a few ignition points in several of the years
fire.ignition.clipped<-ignit[bc.bnd,] # making sure all fire ignitions have coordinates within BC boundary
table(ignit$FIRE_YEAR)
table(fire.ignition.clipped$FIRE_YEAR) #We have lost a few but its not many.

fire.ignition_sf<-st_as_sf(fire.ignition.clipped) #convert to sf object
# join the ignition points to frt
fire.ignt.frt <- st_join(fire.ignition_sf, frt_sf)
fire.ignt.frt$ig_mnth<-stringi::stri_sub(fire.ignt.frt$IGNITION_DATE,6,7)
fire.ignt.frt <- fire.ignt.frt %>% dplyr::select(id:FIRE_TYPE,LATITUDE:CURRENT_SIZE, geometry, Cluster, ig_mnth) %>% filter(FIRE_CAUSE =="Lightning")
table(is.na(fire.ignt.frt$Cluster))


```

look at the size of the fires by year and frt
```{r}
ggplot(data=fire.ignt.frt, (aes(x=CURRENT_SIZE))) +  
  geom_histogram()+
  facet_wrap(~FIRE_YEAR, scales="free")+
  labs(x = "Fire size", y = "Number")

ggplot(data=fire.ignt.frt, (aes(x=CURRENT_SIZE))) +  
  geom_histogram()+
  facet_wrap(~Cluster, scales="free")+
  labs(x = "fire size", y = "Number")

rm(bc.bnd, fire.ignition.clipped, fire.ignition_sf, FRT, frt_clipped, frt_sf, ignit, prov.bnd)
gc()

```


## Extract distance to infrastructure and get elevation, slope, aspect, and elevation
```{r}
# bring distance rasters back in
#Get road development
rds.prov<-rast("D:/Fire/fire_data/raw_data/prov_rd_yr.tif")
prov.rast100 <- raster::raster ( # standardized provincial raster with no data in it
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = 100,
  vals = NA)

rds.prov<-merge(rds.prov, rast(prov.rast100))
rds.table<-rbindlist(lapply(2009:2011, function(x){
  temp<-rds.prov
  temp[temp[] <= x]<-1
  temp[temp[] > 1]<-0
  temp[is.na(temp[])]<-0
  
  #test<-aggregate(temp, fact =100, fun =sum, na.rm =TRUE)
  test2<-crop(temp, prov.rast100)
  out<-data.table(year = x, road = values(test2))[,pixelid := seq_len(.N)]
      out
  
}))
gc()

XYs<-xyFromCell(prov.rast100, rds.table[year==2014,]$pixelid)

rds.table.dist<-rbindlist(lapply(2009:2011, function(x){
  temp<-rds.table[year==x,]
  out<-cbind(temp, XYs)
  out[road.lyr.1 > 0, field := 0] 
      nearNeigh_rds <- RANN::nn2(out[field == 0, c('x', 'y')], 
                                 out[is.na(field), c('x', 'y')], 
                                 k = 1)
      
      out<-out[is.na(field) , rds_dist := nearNeigh_rds$nn.dists] # assign the distances
      out[is.na(rds_dist), rds_dist:=0] # those that are the distance to pixels, assign 
      out[,c("x","y","field"):=NULL]
      rm(temp)
      gc()
      
      out
}))

write.csv(rds.table.dist,"D:/Fire/fire_data/raw_data/rds.table.dist.09_11.csv")

rm(nearNeigh_rds, XYs, rds.table, rds.table.dist)
gc()

```


```{r}
#setnames(rds.table, "road.lyr.1", "road")


# import infrastructure data
dist_rail<- rast("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_rail.tif")
dist_power<- rast("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_power.tif")
dist_oil<- rast("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_oil.tif")
dist_mines<- rast("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_mines.tif")
dist_urban<- rast("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\dist_urban.tif")

##Slope
DEM_slope <- rast("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\dem\\all_bc\\slope_ha_bc_3005.tif")
##Aspect
DEM_aspect <- rast("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\dem\\all_bc\\aspect_ha_bc_3005.tif")
#Elevation
DEM <- rast("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CASTOR\\Data\\dem\\all_bc\\dem_ha_bc.tif")

rasStack = rast(list(DEM_slope, DEM_aspect, DEM, roads_dist, dist_rail, dist_power, dist_oil, dist_mines, dist_urban))
crs(rasStack)<- "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs" # EPSG 9001. Hmm should probably change to 3005
res(rasStack)

##Try this first
test<-cbind(fire.ignt.frt, st_coordinates(fire.ignt.frt))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)

##Extract  values from stacked layer
rasValue2=terra::extract(rasStack, pointCoordinates)
head(rasValue2)
dim(rasValue2) 
dim(fire.ignt.frt)

fire.ignt.frt<-cbind(fire.ignt.frt, rasValue2)

#Get value for infrastructure that is closest
fire.ignt.frt$dist_infrastructure_m<-0
fire.ignt.frt$dist_infrastructure_m<-
  ifelse(fire.ignt.frt$dist_rail < fire.ignt.frt$dist_power, fire.ignt.frt$dist_rail, fire.ignt.frt$dist_power)

fire.ignt.frt$dist_infrastructure_m<-
  ifelse(fire.ignt.frt$dist_oil < fire.ignt.frt$dist_infrastructure, fire.ignt.frt$dist_oil, fire.ignt.frt$dist_infrastructure)

fire.ignt.frt$dist_infrastructure_m<-
  ifelse(fire.ignt.frt$dist_mines < fire.ignt.frt$dist_infrastructure, fire.ignt.frt$dist_mines, fire.ignt.frt$dist_infrastructure)

fire.ignt.frt$dist_infrastructure_m<-
  ifelse(fire.ignt.frt$dist_urban < fire.ignt.frt$dist_infrastructure, fire.ignt.frt$dist_urban, fire.ignt.frt$dist_infrastructure)

# change distance from the scale of ha to m
fire.ignt.frt$dist_infrastructure_m<-fire.ignt.frt$dist_infrastructure_m*100
fire.ignt.frt$dist_roads_m<-fire.ignt.frt$dist_roads*100

rm(DEM_slope, DEM_aspect, DEM, roads_dist, dist_rail, dist_power, dist_oil, dist_mines, dist_urban, rasStack, test, rasValue2, frt_clipped, frt_sf, ignit, FRT, fire.ignition.clipped, fire.ignition_sf, prov.bnd, pointCoordinates, bc.bnd)
gc()

```

## Get climate data

```{r}

years<-min(fire.ignt.frt$FIRE_YEAR):max(fire.ignt.frt$FIRE_YEAR)
clim_dat<-list()

for (i in 1:length(years)){
fire_clim<-fire.ignt.frt %>% 
  filter(FIRE_YEAR == years[i]) %>% 
  dplyr::select(ID, LATITUDE, LONGITUDE, dem_ha_bc) %>%
  rename(id=ID,
         lon=LONGITUDE,
         lat = LATITUDE,
         elev = dem_ha_bc)
fire_clim<-data.table::data.table(fire_clim)
fire_clim[, geometry:=NULL]

ds_out <- downscale(
          xyz = fire_clim,
          which_refmap = "auto",
          obs_years = years[i],
          obs_ts_dataset = "climatena",
          vars = c("PAS_01", "PAS_02", "PAS_03", "PAS_04", "PAS_05","PPT_02","PPT_03","PPT_04", "PPT_05","PPT_06","PPT_07", "PPT_08", "PPT_09","Tmax_02", "Tmax_03","Tmax_04", "Tmax_05", "Tmax_06", "Tmax_07", "Tmax_08", "Tmax_09", "Tave_02","Tave_03","Tave_04", "Tave_05", "Tave_06", "Tave_07", "Tave_08", "Tave_09", "Tmin_02","Tmin_03", "Tmin_04", "Tmin_05", "Tmin_06", "Tmin_07", "Tmin_08", "Tmin_09" ,"CMD_02", "CMD_03","CMD_04", "CMD_05", "CMD_06", "CMD_07", "CMD_08", "CMD_09", "CMI_02","CMI_03", "CMI_04", "CMI_05", "CMI_06", "CMI_07", "CMI_08", "CMI_09"))

ds_out<-ds_out[DATASET == "climatena",]

clim_dat<-rbind(clim_dat, ds_out)
rm(ds_out, fire_clim)
}

fire.ignt.frt$FIRE_YEAR<-as.numeric(fire.ignt.frt$FIRE_YEAR)
clim_dat$PERIOD<-as.numeric(clim_dat$PERIOD)
fire.ignt.frt.clim<-left_join(fire.ignt.frt, clim_dat, join_by(id==id, FIRE_YEAR == PERIOD))

#check I did not loose any data.
table(fire.ignt.frt.clim$FIRE_YEAR)
table(fire.ignt.frt$FIRE_YEAR)

rm(clim_dat, fire.ignt.frt)
gc()

```

## Get VRI data

There are two ways to get the VRI data:
1.) I can either directly extract it for the ignition location on record but sometimes these ignition locations and the VRI are not very accurate OR
2.) I can get summary information for the 1km pixel within which the ignition location occured. 

Ill try it both ways

This next section is for the 1st way to extract VRI data i.e. directly extracting it for the location of interest
This next section takes a long time to run. there may be a more efficient way to do it but for now this is how ill go about it. 

```{r}
#Get dummy layer for projection (too lazy to write it) 
lyr<-getSpatialQuery(paste("SELECT geom FROM public.forest_tenure limit 1") )

#Make an empty provincial raster aligned with hectares BC
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(lyr)$proj4string, resolution = c(100, 100), vals = 0
)

year_vri<-min(fire.ignt.frt.clim$FIRE_YEAR):max(fire.ignt.frt.clim$FIRE_YEAR)
#use the vri layer from the year before the fire because e.g. 2022 vri data is the vegetation represeted up till the end of 2022 

vri_layers<-c("vri.veg_comp_lyr_r1_poly2008", "vri.veg_comp_lyr_r1_poly2009", "vri.veg_comp_lyr_r1_poly2010", "vri.veg_comp_lyr_r1_poly2011", "vri.veg_comp_lyr_r1_poly2012", "vri.veg_comp_lyr_r1_poly2013", "vri.veg_comp_lyr_r1_poly2014", "vri.veg_comp_lyr_r1_poly2015", "vri.veg_comp_lyr_r1_poly2016", "vri.veg_comp_lyr_r1_poly2017", "vri.veg_comp_lyr_r1_poly2018", "vri.veg_comp_lyr_r1_poly2019", "vri.veg_comp_lyr_r1_poly2020", "vri.veg_comp_lyr_r1_poly2021", "vri.veg_comp_lyr_r1_poly2022")

#create empty sf object to rbind data too
dat_joined<-st_sf(geometry = st_sfc(crs=3005))

for (i in 12:length(vri_layers)) {
  
  print(year_vri[i])
#get feature id for the year of interest
layer<-getSpatialQuery(paste0("SELECT feature_id, shape FROM ", vri_layers[i], ";"))
#create a raster out of the feature id
layer.ras <-fasterize::fasterize(sf= layer, raster = ProvRast , field = "feature_id")
rm(layer)
gc()
#get the fire data for year of interest
dat<-fire.ignt.frt.clim %>% filter(FIRE_YEAR == years[i])
#get coordintes of fire locations
test<-cbind(dat, st_coordinates(dat))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
##Extract feature_id values from raster for the fire locations using the coordinates
rasValue2=terra::extract(layer.ras, pointCoordinates)
dat<-cbind(dat, rasValue2)

dat2<-dat %>% dplyr::select(rasValue2)
dat2<-data.table(dat2)
dat2<-dat2[!is.na(rasValue2), ]
dat2<-unique(dat2$rasValue2)
# query the vri layer using the feature id
attrib_inv<-data.table::data.table(getTableQuery(paste0("SELECT feature_id AS fid, bclcs_level_1, bclcs_level_4, basal_area, proj_height_1, species_cd_1, species_pct_1, species_cd_2, species_pct_2, species_cd_3, species_pct_3, species_cd_4, species_pct_4, species_cd_5, species_pct_5, species_cd_6, species_pct_6 FROM ", vri_layers[i], " WHERE feature_id IN (", paste(dat2, collapse = ","),");" )))

#join the vri data to the fire data
dat<-left_join(dat, attrib_inv, join_by(rasValue2==fid))
#add all the data to a new dataframe
dat_joined<-rbind(dat_joined, dat)
#clean up to reduce memory ussage
rm(dat, attrib_inv, rasValue2, pointCoordinates, test)
gc()
}

head(dat_joined)
dat_joined<-st_as_sf(dat_joined)
drops <- c("ID") # list of col names
dat_joined2 <- dat_joined[,!(names(dat_joined) %in% drops)] #remove column
```

## save the data file for use in the analysis
```{r}
st_write(dat_joined2, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\ignition_2009_2023.gpkg")
```


This next section creates summary information for each 1km pixel of the VRI and then extracts it from there

### A simple fuel type
Beverly et al. (2022) showed that distance to hazzardous fuel types are the best predictor of fire exposure. While the Pessaki Fuel Type Algorithm has been used in BC the main components of the classification are based on forest structural attributes: bec zone, species composition, density and height of the forest.

Simply coniferous and mixedwood fuel types are hazardous (Beverly et al. 2022), thus fuel typing may only need  bclcs_level_5 in ('TC', 'TM'), crown closure > 25% to indicate "dense or open" and height > 4 m to indicate not recently disturbed (O1-a/b).

```{r}
restest = c(100, 100)
prov.rast <- raster( # standardized provincial raster with no data in it
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = restest,
  vals = 0)

lapply(seq(2019, 2023, 1), function(x) {
  year_vri <- x
  geom_column <- 'shape'
  
  vri<- getSpatialQuery(glue::glue("SELECT case 
                                   when proj_height_1 >=4 and basal_area >= 8 and bclcs_level_4 in ('TC') then 1 when proj_height_1 >=4 and basal_area >= 8 and bclcs_level_4 in ('TM') then 2 when proj_height_1 >=4 and basal_area >= 8 and bclcs_level_4 in ('TB') then 3 when (proj_height_1 < 4 or basal_area < 8 or basal_area is null or proj_height_1 is null) and bclcs_level_4 in ('TC','TM','TB') then 4
                                  when bclcs_level_4 not in ('TC','TM','TB') then 5
                                  when bclcs_level_1 <> 'V' then 6
                                end as hazard, {geom_column} FROM vri.veg_comp_lyr_r1_poly{year_vri} "))
  ras.haz<-fasterize::fasterize(vri, prov.rast, field = "hazard")
  rm(vri)
  gc()
  ras.haz[is.na(ras.haz[])]<-0
  
  ras1<-ras.haz
  ras1[ras1[] > 1 ]<-0
  ras.fuel1<-terra::crop(terra::aggregate(ras1, fact = 10, fun = sum ),prov.rast) 

  ras2<-ras.haz
  ras2[ras2[] != 2 ]<-0
  ras2[ras2[] == 2 ]<-1
  ras.fuel2<-terra::crop(terra::aggregate(ras2, fact = 10, fun = sum ),prov.rast)
  
  ras3<-ras.haz
  ras3[ras3[] != 3 ]<-0
  ras3[ras3[] == 3 ]<-1
  ras.fuel3<-terra::crop(terra::aggregate(ras3, fact = 10, fun = sum ),prov.rast)
  
  ras4<-ras.haz
  ras4[ras4[] != 4 ]<-0
  ras4[ras4[] == 4 ]<-1
  ras.fuel4<-terra::crop(terra::aggregate(ras4, fact = 10, fun = sum ),prov.rast)
  
  ras5<-ras.haz
  ras5[ras5[] != 5 ]<-0
  ras5[ras5[] == 5 ]<-1
  ras.fuel5<-terra::crop(terra::aggregate(ras5, fact = 10, fun = sum ),prov.rast)
  
  ras6<-ras.haz
  ras6[ras6[] != 6 ]<-0
  ras6[ras6[] == 6 ]<-1
  ras.fuel6<-terra::crop(terra::aggregate(ras6, fact = 10, fun = sum ),prov.rast)
  
  out<-data.table(con = ras.fuel1[], mix = ras.fuel2[], dec = ras.fuel3[] , young = ras.fuel4[], veg = ras.fuel5[], noflame = ras.fuel6[] )[,pixelid := seq_len(.N)]
  write.csv(out, glue::glue("fueltype_1k_{year_vri}.csv"))
  rm(ras1, ras2, ras3, ras4, ras5, ras6, ras.fuel1, ras.fuel2, ras.fuel3, ras.fuel4, ras.fuel5, ras.fuel6, out)
  gc()
  x
})

```

### Compile
```{r}
fuel_type<-rbindlist(
  lapply(seq(2009, 2023, 1), function(x){
    data<-data.table(read.csv(glue::glue("C:/Work/caribou/castor/fueltype_1k_{x}.csv")))
    data$FIRE_YEAR<-x
    data
}))
write.csv(fuel_type, "fuel_type_1k_2009to2023.csv")
```

## open fuel type layer and get values into dat2_joined

```{r}

dat_joined2<-st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\ignition_2009_2023.gpkg")

vri1k<-data.table(read.csv("C:/Work/caribou/castor/fuel_type_1k_2009to2023.csv"))

restest = c(1000, 1000)
prov.rast <- raster( # standardized provincial raster with no data in it
  nrows = 15744, ncols = 17216,
  xmn = 159587.5, xmx = 1881187.5,
  ymn = 173787.5, ymx = 1748187.5,
  crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs",
  resolution = restest,
  vals = 0)

pixel.grid <- data.table(V1 = as.integer(prov.rast[]))[, pixelid := seq_len(.N)]
setorder(pixel.grid, "pixelid")#sort the pixels table so that pixelid is in order.
pixel.grid$V1 <- NULL
prov.rast[]<-pixel.grid$pixelid

test<-cbind(dat_joined2, st_coordinates(dat_joined2))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)

##Extract  values from stacked layer
rasValue2=terra::extract(prov.rast, pointCoordinates)
head(rasValue2)
length(rasValue2) 
dim(dat_joined2)

dat_joined2<-cbind(dat_joined2, rasValue2)

dat_joined3<-merge(dat_joined2, vri1k, by.x=c("FIRE_YEAR", "rasValue2"), by.y=c("FIRE_YEAR","pixelid"))

dim(dat_joined3)
```


## save the data file for use in the analysis
```{r}
st_write(dat_joined3, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\ignition_all_2009_2023.gpkg")
```

```{r}
dat_joined3<-st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\ignition_all_2009_2023.gpkg")
```

