---
title: "01_future_climate_data_prep"
author: "Elizabeth Kleynhans"
date: "2021-03-29"
output: 
  html_document:
  keep_md: yes
---
<!--
Copyright 2020 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf) 
library(sp)
library(ncdf4)
library(raster)
library(rasterVis)
library(RColorBrewer)
library(dplyr)
library(data.table)
library(data.table)
library(here)
source (paste0(here(),"/R/functions/R_Postgres.R"))



```

## Introduction

Here I am trying to downscale global climate change models to a 800 x 800m scale (or finer) so that they can be used to predict fire occurence in the future. ClimateBC has a little program that you can use to extract future climate values for any number of locations within BC, but manually extracting millions of locations for each year (2019 - 2100) and for multiple difference gcm's is time consuming and repetitive. Also, CMIP 5 is shortly going to be replaced with CMIP 6 but this data has not come out on climateBC yet. I chatted to Colin Mahony and he suggested I do the downscaling myself. He outlined the steps I should take and its pretty straight forward so thats the path Im following. 

## Methods

 The delta downscaling approach is described in https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0156720#sec017, but basically is:
 1.	Start with your high-resolution observational climate normals (800m PRISM (https://www.pacificclimate.org/data/prism-climatology-and-monthly-timeseries-portal), or finer ClimateBC data) for a reference period (e.g., 1971-2000)

 2.	For each GCM, convert simulated values to deviations (anomalies) from the grand-mean reference period climate of multiple historical simulations.
 2a. Each GCM has several historical runs from 1850 to 2014. For each month of each element (e.g., January Tmin), calculate the mean of each of these runs for the reference period (1971-2000). Then calculate the mean of these reference period means; that’s the grand mean. for each grid cell of each gcm, you will have one raster for jan Tmin, one for feb Tmin, etc.
 2b. then subtract this value from each GCM time series that you want to use. For precipitation, you divide instead of subtracting, using this value as the denominator.

 3.	Bilinearly interpolate these anomaly rasters to the grid scale of the observational climate normals.

 4.	Add (or multiply for precipitation) these anomalies to the observational climate normals (PRISM data).

 Colin suggested I start with MPI-ESM1-2-HR as my first GCM run because its at a 60x60km resolution.

## Information about MPI-ESM1-2-HR from http://www.glisaclimate.org/model-inventory/max-planck-institute-for-meteorology-earth-system-model-mr

 Temperature
 Mean Temperature Output Name: tas
 Mean Temperature Temporal Frequency: Daily
 Min/Max Temperature Output Name: tasmin/tasmax
 Min/Max Temperature Temporal Frequency: Daily
 Temperature Units: Kelvin

 Precipitation
 Total Precipitation Output Name: pr
 Total Precipitation Temporal Frequency: Daily
 Convective Precipitation Output Name: prc
 Convective Precipitation Temporal Frequency: Daily
 Precipitation Units: kg m-2 s-1


## Starting with part of Step 2a i.e. obtaining the grand mean reference period

```{r Step2a, echo=FALSE}
#2a. Each GCM has several historical runs from 1850 to 2014. For each month of each element (e.g., January Tmin), calculate the mean of each of these runs for the reference period (1971-2000). Then calculate the mean of these reference period means; that’s the grand mean. for each grid cell of each gcm, you will have one raster for jan Tmin, one for feb Tmin, etc.

# first get mean jan/feb/mar etc temp or pr of each replicate gcm run from 1971 to 2000
monthdays <- c(31, 28.25, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)
monthcodes <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")

dirs <- list.dirs("D:\\Fire\\fire_data\\raw_data\\Future_climate")
gcms <- unique(sapply(strsplit(dirs, "/"), "[", 2))
select <- c(3)
gcms[select]

#i=1
#for(i in select[1:length(select)]){
  gcm <- gcms[3]
  
  #process the climate elements
  dir <- paste("D:\\Fire\\fire_data\\raw_data\\Future_climate", gcm, sep="\\")
  files <- list.files(dir)
  element.list <- sapply(strsplit(files, "_"), "[", 1)
  scenario.list <- sapply(strsplit(files, "_"), "[", 4)
  ripf.list <- sapply(strsplit(files, "_"), "[", 5)
  run.list <- paste(scenario.list, ripf.list, sep="_")
  elements <- unique(element.list)[c(3,4,1)]
  runs2 <- unique(run.list)
  runs<-runs2[grep("historical", runs2)]
  years<- c("197001", "197501", "198001", "198501", "199001", "199501", "200001")
  
  # units of pr are in mm/s
  # library(ncdf4)
  # element="pr"
  # data <- nc_open(paste(dir, files.run[grep(element, files.run)], sep="\\"))
  # print(data)
  
  #run=runs[2]
  for(run in runs){
    files.run <- files[grep(run, files)] # get all files from a specific GCM run e.g. historical_r1i1p1f1
    
    #element=elements[3]
    for(element in elements){
      files.element <- files.run[grep(element, files.run)] # get all tasmax/tasmin/pr files from the specific GCM run
      
      for(year in 1:length(years)){
        files.years<-files.element[grep(years[year], files.element)] # get the 
       #did this rather than stack import becuase it preserves the variable (month) names
        temp2 <- brick(paste(dir, files.years, sep="\\"))
        temp <- if(year==1) temp2 else brick(c(temp, temp2))
        #print(year)
      }
      
      #m=1
      for(m in 1:12){
        r <- temp[[which(substr(names(temp),7,8)==monthcodes[m])]] # get all Januaries or Februaries etc
        if(element=="pr") r <- r*86400*monthdays[m] else r <- r-273.15  #convert units to /month (86400 seconds / day) and to degrees C
        
        r1<- r[[1:31]] # select columns 1970 - 2000
        r.mean<- mean(r1)
        #plot(r.mean) # looks like its working
        
        temp.rast <- if(m==1) r.mean else brick(c(temp.rast, r.mean))
      }
      names(temp.rast) <- c(paste0(element,"_01"), paste0(element,"_02"), paste0(element,"_03"), paste0(element,"_04"), paste0(element,"_05"), paste0(element,"_06"), paste0(element,"_07"), paste0(element,"_08"), paste0(element,"_09"), paste0(element,"_10"), paste0(element,"_11"), paste0(element,"_12"))
      writeRaster(temp.rast, paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\", element,"_", gcm, "_", run, "_", "ref_1971_2000", ".nc", sep=""), format="CDF", overwrite=TRUE)
      print(element)
      }
    print(run)
    }
  

#############################################
# Then calculate grand mean of reference period
#############################################

#get average of climate in each month across all runs.
dir <- paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs", gcm, sep="\\")
files <- list.files(dir)
element.list <- sapply(strsplit(files, "_"), "[", 1)
elements <- unique(element.list)
monthcodes <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")

rm(temp2, temp, files.element)

#element=elements[2]
for(element in elements){
  files.element <- files[grep(element, files)] # get all tasmax/tasmin/pr files from the specific GCM run
  for (i in 1: length(files.element)) {
  temp2 <- stack(paste(dir, files.element[i], sep="\\"))
  names(temp2) <- c(paste0(element,"_01"), paste0(element,"_02"), paste0(element,"_03"), paste0(element,"_04"), paste0(element,"_05"), paste0(element,"_06"), paste0(element,"_07"), paste0(element,"_08"), paste0(element,"_09"), paste0(element,"_10"), paste0(element,"_11"), paste0(element,"_12"))
  #print(i)
  temp <- if(i==1) temp2 else brick(c(temp, temp2))
  }

  #m=1
  sapply(strsplit(names(temp), "_"), "[", 2)
  
  for(m in 1:12){
    r.temp<-sapply(strsplit(names(temp), "_"), "[", 2)
    r <- temp[[which(substr(r.temp,1,2)==monthcodes[m])]] # get all Januaries or Februaries etc
    r.mean<- mean(r)
    #plot(r.mean) # looks like its working
    writeRaster(r.mean, filename=paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\grand_mean_ref_period_1971_2000\\", element,"_", gcm, "_", "ref_1971_2000_mnth_",monthcodes[m], ".tif", sep=""), format="GTiff", overwrite=TRUE)
    }
   print(element)
}
```

## Step 2b - subtract the grand mean value from each GCM time series that you want to use. For precipitation, you divide instead of subtracting, using this value as the denominator.

The naming convention of the CMIP6 GCM's is a little confusing but here are some details I found in Turnock et al. Historical and future changes in air pollutants from CMIP6 models. 
 (https://acp.copernicus.org/preprints/acp-2019-1211/acp-2019-1211.pdf)

"The SSPs are divided into the following 5 different pathways depending on their social, economic and environmental development: SSP1 – sustainability, SSP2 - middle-of-the-road, SSP3 – regional rivalry, SSP4 - inequality, SSP5 – fossil fuel development. An assumption about the degree of air pollution control (strong, medium or weak) is included on top of the baseline pathway, with stricter air pollution controls assumed to be tied to economic 125 development (Rao et al., 2016). Weak air pollution controls occur in SSP3 and SSP4, with medium controls in SSP2 and strong air pollution controls in SSP1 and SSP5 (Gidden et al., 2019)."

From the above I will focus my future climate measures on SSP245

```{r Step2b, echo=FALSE}
#### This script runs the historical period after the reference period (2002-2015)

rm(dirs, gcms, dir, files, element.list, scenario.list, ripf.list, run.list, elements, runs2, runs, years)
dirs <- list.dirs("D:\\Fire\\fire_data\\raw_data\\Future_climate")
gcms <- unique(sapply(strsplit(dirs, "/"), "[", 2))
select <- c(3)
gcms[select]
monthdays <- c(31, 28.25, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)
monthcodes <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")


#i=1
#for(i in select[1:length(select)]){
  gcm <- gcms[3]
  
  #process the climate elements
  dir <- paste("D:\\Fire\\fire_data\\raw_data\\Future_climate", gcm, sep="\\")
  files <- list.files(dir)
  element.list <- sapply(strsplit(files, "_"), "[", 1)
  scenario.list <- sapply(strsplit(files, "_"), "[", 4)
  ripf.list <- sapply(strsplit(files, "_"), "[", 5)
  run.list <- paste(scenario.list, ripf.list, sep="_")
  elements <- unique(element.list)[c(3,4,1)]
  runs2 <- unique(run.list)
  toMatch<-c("historical") # ,"ssp245"
  runs<-runs2[grep(paste(toMatch, collapse="|"), runs2)]
  years<-c("200001", "200501", "201001")
  
   #get the global mean reference rasters 
  ref.dir <- "D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\grand_mean_ref_period_1971_2000\\"
  ref.files <- list.files(ref.dir)
  
  #run=runs[2]
  for(run in runs){
    files.run <- files[grep(run, files)] # get all files from a specific GCM run e.g. historical_r1i1p1f1
    
    #element=elements[1]
    for(element in elements){
      files.element <- files.run[grep(element, files.run)] # get all tasmax/tasmin/pr files from the specific GCM run
      ref.files.element <- ref.files[grep(element, ref.files)] # get the associated grand mean reference file
      
      for(year in 1:length(years)){
        files.years<-files.element[grep(years[year], files.element)] # get the 
       #did this rather than stack import becuase it preserves the variable (month) names
        temp2 <- brick(paste(dir, files.years, sep="\\"))
        temp3<- if (year==1) temp2[[13:60]] else temp2 # remove 2000 values because those are in the reference period
        temp <- if(year==1) temp3 else brick(c(temp, temp3))
      }
      
      #m=1
      for(m in 1:12){
        ref.rast<-raster(paste0(ref.dir, ref.files.element[grep(monthcodes[m], ref.files.element)]))
        
        r <- temp[[which(substr(names(temp),7,8)==monthcodes[m])]] # get all Januaries or Februaries etc
        if(element=="pr") r <- r*86400*monthdays[m] else r <- r-273.15  #convert units to /month (86400 seconds / day) and to degrees C
        if (element =="pr") delta.r.hist<- r/ref.rast else delta.r.hist<- r-ref.rast
        names(delta.r.hist) <- names(r)
        temp.delta.rast.hist <- if(m==1) delta.r.hist else brick(c(temp.delta.rast.hist, delta.r.hist))
      }
      print(element)
      #writeRaster(temp.delta.rast.hist, paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_delta_values\\", element,"_", gcm,"_",run, "_",years[1],years[3], "_delta.nc", sep=""), format="CDF", overwrite=TRUE) # this worked but the names of each layer were not written which is a problem!
      
      writeRaster(temp.delta.rast.hist, paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_delta_values\\", element,"_", gcm,"_",run, "_",years[1],years[3], "_delta.grd", sep=""), bandorder='BIL', overwrite=TRUE) # this one wrote the names of the layers
      
      }
    
  }
  
  x<-brick("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_delta_values\\tasmax_MPI-ESM1-2-HR_historical_r1i1p1f1_200001201001_delta.grd")
  
```

```{r Step2b, echo=FALSE}
#### This script runs the predicted future climate after the end of the historical period (2016 -2100). I think Im going to have to join the historical run to this one before I interpolate the delta gcm runs to the scale of the prism data. 
rm(dirs, gcms, dir, files, element.list, scenario.list, ripf.list, run.list, elements, runs2, runs, years)
dirs <- list.dirs("D:\\Fire\\fire_data\\raw_data\\Future_climate")
gcms <- unique(sapply(strsplit(dirs, "/"), "[", 2))
select <- c(3)
gcms[select]

#i=1
#for(i in select[1:length(select)]){
  gcm <- gcms[3]
  
  #process the climate elements
  dir <- paste("D:\\Fire\\fire_data\\raw_data\\Future_climate", gcm, sep="\\")
  files <- list.files(dir)
  element.list <- sapply(strsplit(files, "_"), "[", 1)
  scenario.list <- sapply(strsplit(files, "_"), "[", 4)
  ripf.list <- sapply(strsplit(files, "_"), "[", 5)
  run.list <- paste(scenario.list, ripf.list, sep="_")
  elements <- unique(element.list)[c(3,4,1)]
  runs2 <- unique(run.list)
  toMatch<-c("ssp245")
  runs<-runs2[grep(paste(toMatch, collapse="|"), runs2)]
  years<-c("201501", "202001", "202501", "203001", "203501", "204001", "204501", "205001", "205501", "206001", "206501", "207001", "207501", "208001", "208501", "209001", "209501", "210001")
  
   #get the global mean reference rasters 
  ref.dir <- "D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\grand_mean_ref_period_1971_2000\\"
  ref.files <- list.files(ref.dir)
  
  #run=runs[2]
  for(run in runs){
    files.run <- files[grep(run, files)] # get all files from a specific GCM run e.g. historical_r1i1p1f1
    
    #element=elements[1]
    for(element in elements){
      files.element <- files.run[grep(element, files.run)] # get all tasmax/tasmin/pr files from the specific GCM run
      ref.files.element <- ref.files[grep(element, ref.files)] # get the associated grand mean reference file
      
      for(year in 1:length(years)){
        files.years<-files.element[grep(years[year], files.element)] # get the 
       #did this rather than stack import becuase it preserves the variable (month) names
        temp2 <- brick(paste(dir, files.years, sep="\\"))
        temp <- if(year==1) temp2 else brick(c(temp, temp2))
      }
      
      #m=1
      for(m in 1:12){
        ref.rast<-raster(paste0(ref.dir, ref.files.element[grep(monthcodes[m], ref.files.element)]))
        
        r <- temp[[which(substr(names(temp),7,8)==monthcodes[m])]] # get all Januaries or Februaries etc
        if(element=="pr") r <- r*86400*monthdays[m] else r <- r-273.15  #convert units to /month (86400 seconds / day) and to degrees C
        if (element =="pr") delta.r<- r/ref.rast else delta.r<- r-ref.rast
        names(delta.r) <- names(r)
        temp.delta.rast <- if(m==1) delta.r else brick(c(temp.delta.rast, delta.r))
      }
      
      #writeRaster(temp.delta.rast, paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_delta_values\\", element,"_", gcm,"_",run, "_",years[1],years[length(years)], "_delta.nc", sep=""), format="CDF", overwrite=TRUE)
      writeRaster(temp.delta.rast, paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_delta_values\\", element,"_", gcm,"_",run, "_",years[1],years[length(years)], "_delta.grd", sep=""), bandorder='BIL', overwrite=TRUE) # this one wrote the names of the layers
      print(element)
      }
    
  }
  
  
```

## 3.	Bilinearly interpolate these anomaly rasters to the grid scale of the observational climate normals.

```{r Step3, echo=FALSE}
rm(dirs, gcms, dir, files, element.list, scenario.list, ripf.list, run.list, elements, runs2, runs, years, temp, ref.rast, r, delta.r, delta.r.hist, temp.delta.rast, temp.delta.rast.hist, temp2, temp3)
gc()

# Get the file path of the PRISM data so that I can import this data and interpolate my runs to the same scale
PRISMpath <- "D:\\Fire\\fire_data\\raw_data\\Future_climate\\PRISM_historical_19710101-20001231"
PRISMfiles <- list.files(PRISMpath)

# Then second join the historic runs (2001 - 2015) to the future climate runs (2016 - 2100) and down scale them to the scale of the PRISM data. Then add (for tmax and tmin) or multiply (for pr) the delta raster to the prism raster

  dir <- "D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_delta_values"
  files <- list.files(dir)
  element.list <- sapply(strsplit(files, "_"), "[", 1)
  elements <- unique(element.list)
  scenario.list <- sapply(strsplit(files, "_"), "[", 3)
  ripf.list <- sapply(strsplit(files, "_"), "[", 4)
  run.list <- paste(scenario.list, ripf.list, sep="_")
  runs2 <- unique(run.list)
  toMatch<-c("r1i1p1f1", "r2i1p1f1")
  runs<-runs2[grep(paste(toMatch, collapse="|"), runs2)]
  
  for(i in 1: length(toMatch)){
    files.run <- files[grep(toMatch[i], files)] # get all files from a specific GCM run e.g. historical_r1i1p1f1
    
    #element=elements[2]
    for(element in elements){
      files.element <- files.run[grep(element, files.run)] # get all tasmax/tasmin/pr files from the specific GCM run
      files.element1<- files.element[grep(".grd",files.element)]
      history<-brick(paste(dir, files.element1[grep("historical", files.element1)], sep="\\"))
      ssp245<-brick(paste(dir, files.element1[grep("ssp245", files.element1)], sep="\\"))
      
      # get the prism data
      PRISM_dat <- paste(PRISMpath, PRISMfiles[grep(element, PRISMfiles)], sep="\\")
      prism_dat <- brick(PRISM_dat)
      #prism_dat_scale <- raster(prism_dat, layer=1)
      
      for(m in 1:12){
        r.hist <- history[[which(substr(names(history),7,8)==monthcodes[m])]] # get all Januaries or Februaries etc
        r.ssp245 <- ssp245[[which(substr(names(ssp245),7,8)==monthcodes[m])]] # get all Januaries or Februaries etc
        #temp.rast.run <- if(names(r.hist)[1]=="X2001.01.16") r.hist else brick(c(r.hist, r.ssp245))
        temp.rast.run <-brick(c(r.hist, r.ssp245))
        
        # Bilinearly interpolate the future climate values to match the grid scale of the reference climate
        r.prism.dat <- prism_dat[[which(substr(names(prism_dat),7,8)==monthcodes[m])]] # get all Januaries or Februaries etc
        temp.rast.run1<- crop(temp.rast.run,r.prism.dat)
        temp_raster_resampled<-resample(temp.rast.run, r.prism.dat, method='bilinear')
        #plot(raster(temp_raster_resampled, layer=1)) #check that it looks ok
        # add or multiply the future climate delta values to the prism data to get elevation adjusted future climate values
        if (element =="pr") adjusted.climate<- r.prism.dat*temp_raster_resampled  else adjusted.climate<- r.prism.dat+temp_raster_resampled 
        names(adjusted.climate)<- names(temp_raster_resampled)
        
        #writeRaster(adjusted.climate, filename=paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_adjusted_values\\", element,"_", gcm,"_",names(adjusted.climate), ".tif", sep=""), bylayer=TRUE, format="GTiff", overwrite=TRUE)  
        writeRaster(adjusted.climate, filename=paste("D:\\Fire\\fire_data\\raw_data\\Future_climate\\outputs\\MPI-ESM1-2-HR_adjusted_values\\temp\\", element,"_", gcm, "_", toMatch[i], "_", "_2001-2100_mnth_",monthcodes[m], ".grd", sep=""), bandorder='BIL', overwrite=TRUE) # this one wrote the names of the layers
        
        # do a little cleanup 
        rm(r.hist, r.prism.dat, temp.rast.run, temp.rast.run1, r.prism.dat, temp_raster_resampled)
        gc()
      
        }
     print(element) 
      }
  }
  
```

