---
title: "Model fitting escaped lightning caused fires"
author: "Elizabeth Kleynhans"
date: "2024-09-17"
output: html_document
---

```{r setup, include=FALSE}

library(data.table)
library(ggplot2)
library(tidyverse)
library(sf)
library(randomForest)
library(caret)
library(visreg)
library(car)
library(caret)
library(e1071)
library(pROC)

fire_ignitions<-st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\ignition_all_2009_2023.gpkg")
```

Create some new summary variables
```{r}
fire_ignitions2<-data.table(fire_ignitions)

fire_ignitions2<-fire_ignitions2[FIRE_CAUSE=="Lightning",]
fire_ignitions2<-fire_ignitions2[, Tmax_MAX:= do.call(pmax, .SD),.SDcols=c("Tmax_05","Tmax_06","Tmax_07","Tmax_08") ]
fire_ignitions2<-fire_ignitions2[, Tave_MAX:= do.call(pmax, .SD),.SDcols=c("Tave_05","Tave_06","Tave_07","Tave_08") ]
fire_ignitions2<-fire_ignitions2[, Tmin_MAX:= do.call(pmax, .SD),.SDcols=c("Tmin_05","Tmin_06","Tmin_07","Tmin_08") ]
fire_ignitions2<-fire_ignitions2[, CMD_MAX:= do.call(pmax, .SD),.SDcols=c("CMD_05","CMD_06","CMD_07","CMD_08") ]

fire_ignitions2<-fire_ignitions2[, CMI_Min:= do.call(pmin, .SD),.SDcols=c("CMI_05","CMI_06","CMI_07","CMI_08") ]
fire_ignitions2<-fire_ignitions2[, PPT_Min:= do.call(pmin, .SD),.SDcols=c("PPT_05","PPT_06","PPT_07","PPT_08") ]

fire_ignitions2<-fire_ignitions2[,Tmax04_05:=(Tmax_04+Tmax_05)/2]
fire_ignitions2<-fire_ignitions2[,Tave04_05:=(Tave_04+Tave_05)/2]
fire_ignitions2<-fire_ignitions2[,Tmin04_05:=(Tmin_04+Tmin_05)/2]
fire_ignitions2<-fire_ignitions2[,PPT04_05:=PPT_04+PPT_05]
fire_ignitions2<-fire_ignitions2[,CMI04_05:=(CMI_04+CMI_05)/2]

fire_ignitions2<-fire_ignitions2[,Tmax06_07:=(Tmax_06+Tmax_07)/2]
fire_ignitions2<-fire_ignitions2[,Tave06_07:=(Tave_06+Tave_07)/2]
fire_ignitions2<-fire_ignitions2[,Tmin06_07:=(Tmin_06+Tmin_07)/2]
fire_ignitions2<-fire_ignitions2[,PPT06_07:=PPT_06+PPT_07]
fire_ignitions2<-fire_ignitions2[,CMI06_07:=(CMI_06+CMI_07)/2]

fire_ignitions2<-fire_ignitions2[,Tmax06_07_08:=(Tmax_06 + Tmax_07 + Tmax_08)/3]
fire_ignitions2<-fire_ignitions2[,Tave06_07_08:=(Tave_06 + Tave_07 + Tave_08)/3]
fire_ignitions2<-fire_ignitions2[,Tmin06_07_08:=(Tmin_06 + Tmin_07 + Tmin_08)/3]
fire_ignitions2<-fire_ignitions2[,PPT06_07_08:=PPT_06 + PPT_07 + PPT_08]
fire_ignitions2<-fire_ignitions2[,CMI06_07_08:=(CMI_06+CMI_07+CMI_08)/3]

fire_ignitions2<-fire_ignitions2[,Tmax05_06_07_08:=(Tmax_05+Tmax_06 + Tmax_07 + Tmax_08)/4]
fire_ignitions2<-fire_ignitions2[,Tave05_06_07_08:=(Tave_05+Tave_06 + Tave_07 + Tave_08)/4]
fire_ignitions2<-fire_ignitions2[,Tmin05_06_07_08:=(Tmin_05+Tmin_06 + Tmin_07 + Tmin_08)/4]
fire_ignitions2<-fire_ignitions2[,PPT05_06_07_08:=PPT_05 + PPT_06 + PPT_07 + PPT_08]
fire_ignitions2<-fire_ignitions2[,CMI05_06_07_08:=(CMI_05 + CMI_06+CMI_07+CMI_08)/4]

fire_ignitions2[, aspect_cardinal:="O"]
fire_ignitions2[aspect_ha_bc_3005 >315, aspect_cardinal:="N"]
fire_ignitions2[aspect_ha_bc_3005 <=45, aspect_cardinal:="N"]
fire_ignitions2[aspect_ha_bc_3005 >45 & aspect_ha_bc_3005 <=135, aspect_cardinal:="O"]
fire_ignitions2[aspect_ha_bc_3005 >135 & aspect_ha_bc_3005<=225, aspect_cardinal:="S"]
fire_ignitions2[aspect_ha_bc_3005 >225 & aspect_ha_bc_3005 <=315, aspect_cardinal:="O"]

fire_ignitions2[bclcs_level_1 =='V', veg_cat:=5]
fire_ignitions2[proj_height_1>=4 & basal_area>=8 & con>=25, veg_cat:=2]
fire_ignitions2[proj_height_1>=4 & basal_area>=8 & con>=75, veg_cat:=1]
fire_ignitions2[proj_height_1>=4 & basal_area>=8 & con<25, veg_cat:=3]
fire_ignitions2[(proj_height_1<4 | basal_area<8) & con >=0 & bclcs_level_1 == 'V', veg_cat:=4]
fire_ignitions2[bclcs_level_1 !='V', veg_cat:=6]
fire_ignitions2$veg_cat<-as.factor(fire_ignitions2$veg_cat)
table(fire_ignitions2$veg_cat)

# get % conifer
conifer<-c("C","CW","Y","YC","F","FD","FDC","FDI","B","BB","BA","BG","BL","H","HM","HW","HXM","J","JR","JS","P","PJ","PF","PL","PR","PLI","PXJ","PY","PLC","PW","PA","S","SB","SE","SS","SW","SX","SXW","SXL","SXS","T","TW","X", "XC","XH", "ZC")

fire_ignitions2<- fire_ignitions2 %>%
  mutate(pct1 = ifelse(species_cd_1 %in% conifer, species_pct_1, NA),
         pct2 = ifelse(species_cd_2 %in% conifer, species_pct_2, NA),
         pct3 = ifelse(species_cd_3 %in% conifer, species_pct_3, NA),
         pct4 = ifelse(species_cd_4 %in% conifer, species_pct_4, NA),
         pct5 = ifelse(species_cd_5 %in% conifer, species_pct_5, NA),
         pct6 = ifelse(species_cd_6 %in% conifer, species_pct_6, NA),
         dominant_conifer = ifelse(species_cd_1 %in% conifer, species_cd_1, 
                                   ifelse(species_cd_2 %in% conifer, species_cd_2,
                                          ifelse(species_cd_3 %in% conifer, species_cd_3,
                                                 ifelse(species_cd_4 %in% conifer, species_cd_4,
                                                        ifelse(species_cd_5 %in% conifer, species_cd_5,
                                                               ifelse(species_cd_6 %in% conifer, species_cd_6, NA)))))))

table(unknown_pts$dominant_conifer)

fire_ignitions2<-fire_ignitions2 %>% mutate(conifer_pct_cover_total=rowSums(across(c(pct1:pct6)), na.rm=TRUE))

# test if some variables are correlated
cor.test(fire_ignitions2$PPT04_05, fire_ignitions2$PPT06_07)
cor.test(fire_ignitions2$CMI04_05, fire_ignitions2$CMI06_07)
cor.test(fire_ignitions2$CMI04_05, fire_ignitions2$Tmin04_05)


```

# I think I will try to fit a random forest model to help me figure out which are the most important variables in determining whetehr a fire escapes.

```{r}
fire_ignitions2$CURRENT_SIZE<-as.numeric(fire_ignitions2$CURRENT_SIZE)
table(fire_ignitions2$CURRENT_SIZE>1)
fire_ignitions2[CURRENT_SIZE>1, escape:=1]
fire_ignitions2[CURRENT_SIZE<=1, escape:=0]

# remove NA values 
fire_ignitions2<-fire_ignitions2[!is.na(escape),]
fire_ignitions2<-fire_ignitions2[!is.na(Cluster),]
fire_ignitions2<-fire_ignitions2[!is.na(slope_ha_bc_3005),]
fire_ignitions2<-fire_ignitions2[!is.na(Tmax_05),]
fire_ignitions2<-fire_ignitions2[!is.na(proj_height_1),]
fire_ignitions2<-fire_ignitions2[!is.na(basal_area),]
fire_ignitions2$log_road<-log(fire_ignitions2$dist_roads_m+1)
fire_ignitions2$log_infra<-log(fire_ignitions2$dist_infrastructure_m+1)
#fire_ignitions2[Cluster==3, Cluster:=5]

# Put all the variables I want for the random forest model into on data.frame
data<- fire_ignitions2 %>% dplyr::select(escape, Cluster, slope_ha_bc_3005, dem_ha_bc, aspect_cardinal, log_road, log_infra,  basal_area, proj_height_1, con:noflame, Tmax_MAX :CMI05_06_07_08, veg_cat, conifer_pct_cover_total)
colSums(is.na(data))

# make sure that cluster (frt) and my escape (0, or 1) values area  factor
data$Cluster<-as.factor(data$Cluster)
data$escape<-as.factor(data$escape)

# create training and testing datasets
set.seed(222)
ind <- sample(2, nrow(data), replace = TRUE, prob = c(0.75, 0.25))
train <- data[ind==1,]
table(train$escape)
test <- data[ind==2,]

# random forest is sensitive to imbalanced sample sizes so will over and under sample
library(ROSE)
over <- ovun.sample(escape~., data = train, method = "over", N = 14826)$data
table(over$escape)


rf <- randomForest(escape~., data=over, proximity=TRUE) 
print(rf)

p1 <- predict(rf, train)
confusionMatrix(p1, train$escape, positive="1")

p2 <- predict(rf, test)
confusionMatrix(p2, test$escape, positive="1")
plot(rf)

varImpPlot(rf,
           sort = T,
           n.var = 30,
           main = "Top 10 - Variable Importance at 10km scale")
importance(rf)


# over and under sample. It looks like over and undersampling the data is better than just over sampling the 1 category. 
both <- ovun.sample(escape~., data = train, method = "both", p=0.5, N = 12164)$data
table(both$escape)


rf <- randomForest(escape~., data=both, proximity=TRUE) 
print(rf)

p1 <- predict(rf, train)
confusionMatrix(p1, train$escape, positive="1")

p2 <- predict(rf, test)
confusionMatrix(p2, test$escape, positive="1")
plot(rf)

varImpPlot(rf,
           sort = T,
           n.var = 30,
           main = "Top 10 - Variable Importance at 10km scale")
importance(rf)



```

Its intereating the variables distance to infrastructure, distance to roads, slope, PPT_04_05, Tmin_04_05 are always the most important. Although if you go from escaped fires at 100ha and 10ha versus 1ha veg is important at the larger scale i.e. 10ha and greater but at the 1ha scale height and basal area are the most important variables for vegetation. veg is way down the list.

### Plot the climate data to look at some trends
```{r}

ggplot(fire_ignitions2, aes(x=CURRENT_SIZE, y=Tmin04_05)) + 
  geom_point() + 
  geom_smooth(method=lm) +
  facet_wrap(~as.factor(Cluster),scales = "free_x")

ggplot(fire_ignitions2, aes(x=CURRENT_SIZE, y=PPT04_05)) + 
  geom_point() + 
  geom_smooth(method=lm) +
  facet_wrap(~as.factor(Cluster),scales = "free")

ggplot(fire_ignitions2, aes(x=CURRENT_SIZE, y=CMI04_05)) + 
  geom_point() + 
  geom_smooth(method=lm) +
  facet_wrap(~as.factor(Cluster),scales = "free")

fire_ignitions2[CURRENT_SIZE>1, pttype:=1]
fire_ignitions2[CURRENT_SIZE<=1, pttype:=0]
# there are 5 observations with no associated fire size so Ill remove these.
fire_ignitions2<-fire_ignitions2[!is.na(pttype),]

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=CMI_Min)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=CMI04_05)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=dist_infrastructure_m)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=dist_roads_m)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=basal_area)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=proj_height_1)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=slope_ha_bc_3005)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=veg)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")

ggplot(fire_ignitions2, aes(x=as.factor(pttype), y=conifer_pct_cover_total)) + 
  geom_boxplot() + 
  facet_wrap(~as.factor(Cluster),scales = "free_y")


```

Test for correlations between variables and leave out dont include two highly correlated variables
```{r}

cor.test(data$log_road, data$log_infra)
cor.test(data$PPT04_05, data$dem_ha_bc)
cor.test(data$CMI04_05, data$dem_ha_bc)
cor.test(data$PPT06_07, data$dem_ha_bc)
cor.test(data$PPT06_07, data$dem_ha_bc)
cor.test(data$PPT04_05, data$Tave_MAX)
cor.test(data$PPT04_05, data$PPT06_07)
cor.test(data$Tave_MAX, data$dem_ha_bc)
cor.test(data$proj_height_1, data$basal_area)#correlated
cor.test(data$PPT04_05, data$CMI04_05) # hightly correlated
cor.test(data$PPT06_07, data$CMI06_07) # hightly correlated
cor.test(data$Tmin04_05, data$CMI04_05)
cor.test(data$PPT_Min, data$CMI04_05)
cor.test(data$Tmax_MAX, data$CMI04_05)

# centre and scale the variables 
data$scale_log_road<-(data$log_road-mean(data$log_road))/sd(data$log_road)
data$scale_log_infra<-(data$log_infra-mean(data$log_infra))/sd(data$log_infra)
data$scale_slope<-(data$slope_ha_bc_3005-mean(data$slope_ha_bc_3005))/sd(data$slope_ha_bc_3005)
data$scale_PPT04_05<-(data$PPT04_05-mean(data$PPT04_05))/sd(data$PPT04_05)
data$scale_PPT06_07<-(data$PPT06_07-mean(data$PPT06_07))/sd(data$PPT06_07)
data$scale_CMI04_05<-(data$CMI04_05-mean(data$CMI04_05))/sd(data$CMI04_05)
data$scale_CMI06_07<-(data$CMI06_07-mean(data$CMI06_07))/sd(data$CMI06_07)
data$scale_dem<-(data$dem_ha_bc-mean(data$dem_ha_bc))/sd(data$dem_ha_bc)
data$scale_height<-(data$proj_height_1-mean(data$proj_height_1))/sd(data$proj_height_1)
data$scale_Tmin_04_05<-(data$Tmin04_05-mean(data$Tmin04_05))/sd(data$Tmin04_05)
data$scale_Tmax_MAX<-(data$Tmax_MAX-mean(data$Tmax_MAX))/sd(data$Tmax_MAX)
data$scale_basal_area<-(data$basal_area-mean(data$basal_area))/sd(data$basal_area)
data$scale_con<-(data$con-mean(data$con))/sd(data$con)
data$scale_conifer_pct_cover_total<-(data$conifer_pct_cover_total-mean(data$conifer_pct_cover_total))/sd(data$conifer_pct_cover_total)


# create test and training set to test how good the model is
ind <- sample(2, nrow(data), replace = TRUE, prob = c(0.75, 0.25))
train <- data[ind==1,]
table(train$escape)
test <- data[ind==2,]


train<-train[veg_cat!=6,]

model1 <- glm (escape ~ log_road + log_infra + scale_slope + scale_dem + scale_height + scale_CMI04_05  + scale_CMI06_07 + veg_cat + Cluster + scale_CMI04_05:scale_CMI06_07 + scale_CMI04_05:veg_cat + scale_Tmin_04_05 + I(scale_Tmin_04_05^2) + I(scale_Tmin_04_05^3) +scale_conifer_pct_cover_total,
                 data=data,
                 family = binomial (link = "logit"))
Anova(model1, type=3)

model2 <- glm (escape ~ log_road + log_infra + scale_slope + scale_dem + scale_height + scale_CMI04_05  + scale_CMI06_07 + veg_cat + Cluster + scale_CMI04_05:scale_CMI06_07 +  scale_Tmin_04_05 + I(scale_Tmin_04_05^2) + I(scale_Tmin_04_05^3) +scale_conifer_pct_cover_total,
                 data=train,
                 family = binomial (link = "logit"))
Anova(model2, type=3)


### Try with segmented to see whetehr Tmin04_05 has a plateu. 
model4 <- glm (escape ~ log_road + log_infra + scale_slope + scale_dem + scale_height + scale_CMI04_05 +scale_CMI06_07 + veg_cat + scale_Tmin_04_05 + Cluster,
                 data=train,
                 family = binomial (link = "logit"))

fit.seg<-segmented(model4, seg.Z = ~scale_Tmin_04_05, psi=1)

AIC(model1,model2,model4, fit.seg)
# consensis is that including the cube root makes more sense.


Anova(model2, type=3)
visreg(model2)
visreg(model2, "scale_CMI06_07", by = "scale_CMI04_05")

library(arm)
# model diagnostic plots
binnedplot (fitted(model2), 
            residuals(model2), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")

# good enough!
```

To check that I had written the parameterization of the model correctly I manually parameterize the model and look at the predicted value from bot the predic function and my manual parameterization. The are the same.
```{r}
test<-test[veg_cat!=6,]
test[, veg_cat2:=0][veg_cat==2, veg_cat2:=1]
test[, veg_cat3:=0][veg_cat==3, veg_cat3:=1]
test[, veg_cat4:=0][veg_cat==4, veg_cat4:=1]

test[, frt5:=0][Cluster==5, frt5:=1]
test[, frt7:=0][Cluster==7, frt7:=1]
test[, frt9:=0][Cluster==9, frt9:=1]
test[, frt10:=0][Cluster==10, frt10:=1]
test[, frt11:=0][Cluster==11, frt11:=1]
test[, frt12:=0][Cluster==12, frt12:=1]
test[, frt13:=0][Cluster==13, frt13:=1]
test[, frt14:=0][Cluster==14, frt14:=1]
test[, frt15:=0][Cluster==15, frt15:=1]

# get predicted values from the model directly

model3 <- glm (escape ~ log_road + log_infra + scale_slope + scale_dem + scale_height + scale_CMI04_05  + scale_CMI06_07 + veg_cat + Cluster + scale_CMI04_05:scale_CMI06_07 +  scale_Tmin_04_05 + I(scale_Tmin_04_05^2) + I(scale_Tmin_04_05^3) +scale_conifer_pct_cover_total,
                 data=train,
                 family = binomial (link = "logit"))
test$modelPredictP<-predict(model3, newdata=test, type="response")

# test if I can get the same values by using the slope and intercept values produced by the model


test$equationPredict<-(coef(model3)[1])+
  (coef(model3)[2])*test$log_road + 
  (coef(model3)[3])*test$log_infra +
  (coef(model3)[4])*test$scale_slope +
  (coef(model3)[5])*test$scale_dem +
  (coef(model3)[6])*test$scale_height+
  (coef(model3)[7])*test$scale_CMI04_05 +
  (coef(model3)[8])*test$scale_CMI06_07+
  (coef(model3)[9])*test$veg_cat2 +
  (coef(model3)[10]) * test$veg_cat3 +
  (coef(model3)[11]) * test$veg_cat4 +
  (coef(model3)[12])*test$frt5 +
  (coef(model3)[13]) * test$frt7 +
  (coef(model3)[14]) * test$frt9 +
  (coef(model3)[15]) * test$frt10 +
  (coef(model3)[16]) * test$frt11 +
  (coef(model3)[17]) * test$frt12 +
  (coef(model3)[18]) * test$frt13 + 
  (coef(model3)[19]) * test$frt14 +
  (coef(model3)[20]) * test$frt15 +
  (coef(model3)[21])*test$scale_Tmin_04_05 +
  (coef(model3)[22])*test$scale_Tmin_04_05^2 +
  (coef(model3)[23])*test$scale_Tmin_04_05^3 +
  (coef(model3)[24])*test$scale_conifer_pct_cover_total +
  (coef(model3)[25])*test$scale_CMI04_05 *test$scale_CMI06_07
  
   test$equationPredict2<-exp(test$equationPredict)/(1+exp(test$equationPredict))
  

```

To get confidence intervals for the parameters and also more accurate parameter values I create 500 versions of the testing and training datasets and then get parameters and AUC for each run. 

```{r}
summary(model3)

#Create a new blank table and get AUC too
top_mod_table_FRT5_ALL <- data.frame (matrix (ncol = 27, nrow = 0))
colnames (top_mod_table_FRT5_ALL ) <- c ("Model_terms", "intercept",
                                         "coef_log_road",
                                         "coef_log_infra",
                                         "coef_slope_c",
                                         "coef_dem_c",
                                         "coef_height_c",
                                         "coef_CMI04_05_c",
                                         "coef_CMI06_07_c",
                                         "coef_veg_cat2",
                                         "coef_veg_cat3",
                                         "coef_veg_cat4",
                                         "coef_frt5",
                                         "coef_frt7",
                                         "coef_frt9",
                                         "coef_frt10",
                                         "coef_frt11",
                                         "coef_frt12",
                                         "coef_frt13",
                                         "coef_frt14",
                                         "coef_frt15",
                                         "coef_Tmin04_05_c",
                                         "coef_Tmin04_05_^2",
                                         "coef_Tmin04_05_^3",
                                         "coef_percent_con_c",
                                         "coef_CMI04_05_by_CMI06_07",
                                         "AUC")

data<-as.data.frame(data)
```


```{r}
#Let's run it 500 times to get good mean values.

for (g in 1:500){
  
  print(g)
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data
ind <- sample(2, nrow(data), replace = TRUE, prob = c(0.75, 0.25))
train <- data[ind==1,]
test <- data[ind==2,]


model1 <- glm (escape ~ log_road + log_infra + scale_slope + scale_dem + scale_height + scale_CMI04_05  + scale_CMI06_07 + veg_cat+ Cluster + scale_CMI04_05:scale_CMI06_07 +  scale_Tmin_04_05 + I(scale_Tmin_04_05^2) + I(scale_Tmin_04_05^3) +scale_conifer_pct_cover_total,
                 data=train,
                 family = binomial (link = "logit"))

mod.valid <- predict.glm(model1, newdata=test, type="response")
   roc_obj <- roc(test$escape, mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT5 <- data.frame (matrix (ncol = 27, nrow = 0))
colnames (top_mod_table_FRT5 ) <- c ("Model_terms", "intercept",
                                         "coef_log_road",
                                         "coef_log_infra",
                                         "coef_slope_c",
                                         "coef_dem_c",
                                         "coef_height_c",
                                         "coef_CMI04_05_c",
                                         "coef_CMI06_07_c",
                                         "coef_veg_cat2",
                                         "coef_veg_cat3",
                                         "coef_veg_cat4",
                                         "coef_frt5",
                                         "coef_frt7",
                                         "coef_frt9",
                                         "coef_frt10",
                                         "coef_frt11",
                                         "coef_frt12",
                                         "coef_frt13",
                                         "coef_frt14",
                                         "coef_frt15",
                                         "coef_Tmin04_05_c",
                                         "coef_Tmin04_05_^2",
                                         "coef_Tmin04_05_^3",
                                         "coef_percent_con_c",
                                         "coef_CMI04_05_by_CMI06_07",
                                         "AUC")
##Add data for NDT1
top_mod_table_FRT5[1,1]<-"log_road + log_infra + scale_slope + scale_dem + scale_height + scale_CMI04_05  + scale_CMI06_07 + veg_cat + Cluster scale_CMI04_05:scale_CMI06_07 +  scale_Tmin_04_05 + I(scale_Tmin_04_05^2) + I(scale_Tmin_04_05^3) + scale_conifer_pct_cover_total" 
top_mod_table_FRT5[1,2]<- coef(model1)[1] #Intercept
top_mod_table_FRT5[1,3]<- coef(model1)[2] #
top_mod_table_FRT5[1,4]<- coef(model1)[3] #
top_mod_table_FRT5[1,5]<- coef(model1)[4] #coefficient 
top_mod_table_FRT5[1,6]<- coef(model1)[5] #coefficient 
top_mod_table_FRT5[1,7]<- coef(model1)[6] #coefficient
top_mod_table_FRT5[1,8]<- coef(model1)[7] #
top_mod_table_FRT5[1,9]<- coef(model1)[8] #coefficient 
top_mod_table_FRT5[1,10]<- coef(model1)[9] #coefficient
top_mod_table_FRT5[1,11]<- coef(model1)[10] #coefficient 
top_mod_table_FRT5[1,12]<- coef(model1)[11] #coefficient
top_mod_table_FRT5[1,13]<- coef(model1)[12] 
top_mod_table_FRT5[1,14]<- coef(model1)[13]
top_mod_table_FRT5[1,15]<- coef(model1)[14] 
top_mod_table_FRT5[1,16]<- coef(model1)[15]
top_mod_table_FRT5[1,17]<- coef(model1)[16] #coefficient 
top_mod_table_FRT5[1,18]<- coef(model1)[17] #coefficient 
top_mod_table_FRT5[1,19]<- coef(model1)[18] #coefficient
top_mod_table_FRT5[1,20]<- coef(model1)[19] #
top_mod_table_FRT5[1,21]<- coef(model1)[20] #coefficient 
top_mod_table_FRT5[1,22]<- coef(model1)[21] #coefficient
top_mod_table_FRT5[1,23]<- coef(model1)[22] #coefficient 
top_mod_table_FRT5[1,24]<- coef(model1)[23] #coefficient
top_mod_table_FRT5[1,25]<- coef(model1)[24] #coefficient 
top_mod_table_FRT5[1,26]<- coef(model1)[25] #coefficient
top_mod_table_FRT5[1,27]<- mod.auc

top_mod_table_FRT5_ALL<-rbind(top_mod_table_FRT5_ALL, top_mod_table_FRT5)

}

names(top_mod_table_FRT5_ALL)
str(top_mod_table_FRT5_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

FRT5_summary_table_mean<- top_mod_table_FRT5_ALL %>% summarize_if(is.numeric,mean)
FRT5_summary_table_mean$AUC_se<-stderror(top_mod_table_FRT5_ALL$AUC)

write.csv(FRT5_summary_table_mean, file="D:\\Fire\\fire_data\\raw_data\\Escape_allfrt.csv")


```

