---
title: "04_DEM_data_prep"
author: "Cora Skaien"
date: "29/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Because slope and aspect have been shown to influence both ignition and spread of fires, we will use the provincial DEM layer to acquire the slope and aspect of each location. The provincial DEM has already had the slope and aspect extracted for the entire province. We will bring in these layers (100 m x 100 m resolution), and then extract the slope and aspect for each of the sample location points that we have generated at the end of file 02_climate_data.prep.

Later, we may need to know the slope of each adjacent cell as well when we model spread.


```{r}
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)

source(here::here("R/functions/R_Postgres.R"))
```

The Provincial DEM layers accessible to us is located here: T:\FOR\VIC\HTS\ANA\PROJECTS\CLUS\Data\dem\all_bc 
Load in the relevant files and inspect.

```{r}
##Slope
DEM_slope <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc.tif")
plot(DEM_slope)

GDALinfo("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc.tif")
DEM_slope

DEM_slope_df <- as.data.frame(DEM_slope, xy = TRUE) #Dataframe created for mapping; but we see later that the files is >2GB and thus too large to map in R
str(DEM_slope_df)

##Aspect
DEM_aspect <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc.tif")
plot(DEM_aspect)

GDALinfo("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc.tif")
DEM_aspect

DEM_aspect_df <- as.data.frame(DEM_aspect, xy = TRUE)#Dataframe created for mapping; but we see later that the files is >2GB and thus too large to map in R
str(DEM_aspect_df)

##Determine resolution
res(DEM_aspect)
res(DEM_slope)

##Plot (must use dataframe version for plotting)
## Files too large to plot; view in QGis
#ggplot() +
#geom_raster(data = DEM_slope_df,
#    aes(x = x, y = y,)) +
#scale_fill_gradientn(name = "Slope", colors = terrain.colors(10)) + 
#coord_quickmap()

#ggplot() +
#geom_raster(data = DEM_aspect_df,
#    aes(x = x, y = y,)) +
#scale_fill_gradientn(name = "Aspect", colors = terrain.colors(10)) + 
#coord_quickmap()
```

Stack the two rasters. Stacking the two rasters will make extracting slope and aspect values for our data points easier downstream (https://gisday.wordpress.com/2014/03/24/extract-raster-values-from-points-using-r/comment-page-1/)

```{r}
##Stack the two rasters
rasStack = stack(DEM_slope, DEM_aspect)
crs(rasStack)

```

Bring in data points for which we want data for slope and aspect (i.e, sample locations). This is the data that we uploaded at the end of the 02_climate_data_prep. Check CRS.

```{r}
#connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
#                      host = key_get('dbhost', keyring = 'postgreSQL'),
#                      user = key_get('dbuser', keyring = 'postgreSQL'),
#                      dbname = key_get('dbname', keyring = 'postgreSQL'),
#                      password = key_get('dbpass', keyring = 'postgreSQL'),
#                      port = "5432")
#sample_locations <- sf::st_read  (dsn = connKyle, # connKyle
 #                              query = "SELECT * FROM public.fire_ignitions_veg_climate")
#dbDisconnect (connKyle)

#head(sample_locations)
#crs(sample_locations)
#sample_locations$geometry

#
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")
sample_locations2 <- sf::st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM public.DC_data")
dbDisconnect (connKyle)

head(sample_locations2)
crs(sample_locations2)
sample_locations2$wkb_geometry


##Compare to DEM layer
crs(DEM_aspect) #Numbers similar, but these ones missing +datum, and sample_locations missing +ellps
crs(DEM_slope)

res(DEM_aspect)
res(DEM_slope)

```

Next, we will create a file with just latitude and longitude so that we can extract the raster values at these points. Then we will attach the aspect and slope values back to data.
https://stackoverflow.com/questions/54734771/sf-write-lat-long-from-geometry-into-separate-column-and-keep-id-column

```{r}
names(sample_locations2)


##Try this first
test<-cbind(sample_locations2, st_coordinates(sample_locations2))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)
crs(pointCoordinates) #No CRS when a dataframe

##Extract DEM values from stacked layer
rasValue2=extract(rasStack, pointCoordinates)
head(rasValue2)
str(rasValue2) #180590 values
str(sample_locations2)#180590 values

#Append new information
sample_locations_DEM<-cbind(sample_locations2, rasValue2)
head(sample_locations_DEM)
crs(sample_locations_DEM)

```

Save this file and use for next file (04_vri_data_prep).

```{r}

st_write(sample_locations_DEM, dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_2.shp", delete_layer=TRUE)

#Also write to local machine on OSGeo4W
#ogr2ogr -f "PostgreSQL" PG:"host=localhost user=postgres dbname=postgres password=postgres port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_2.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI


```



############## Now move on to file 04_VRI_data_prep#############
