---
title: "03_DEM_data_prep"
author: "Cora Skaien and Elizabeth Kleynhans"
date: "29/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 03_DEM_data_prep.R
#  Script Version: 1.0
#  Script Purpose: Determine the elevation, slope and aspect of each location in the dataset.
#  Script Author: Cora Skaien and Elizabeth Kleynhans Ecological Modeling Specialists, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================


#Overview
Because slope and aspect have been shown to influence both ignition and spread of fires, we will use the provincial DEM layer to acquire the slope and aspect of each location. The provincial DEM has already had the slope and aspect extracted for the entire province at 1 ha resolution. We will bring in these layers (100 m x 100 m resolution), and then extract the slope and aspect for each of the sample location points that we have generated at the end of file 02_climate_data.prep.

Later, we may need to know the slope of each adjacent cell as well when we model spread.

Many papers also bring elevation into their models. This ma be a consideration to add in the future.

```{r}
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)

source(here::here("R/functions/R_Postgres.R"))
```

The Provincial DEM layers accessible to us is located here: T:\FOR\VIC\HTS\ANA\PROJECTS\CLUS\Data\dem\all_bc 
Load in the relevant files and inspect.

```{r}
##Slope
DEM_slope <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc_3005.tif")
#plot(DEM_slope) #you may wish to plot this to inspect

GDALinfo("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc.tif")
#DEM_slope

#DEM_slope_df <- as.data.frame(DEM_slope, xy = TRUE) #Dataframe created for mapping; but we see later that the files is >2GB and thus too large to map in R
#str(DEM_slope_df)

##Aspect
DEM_aspect <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc_3005.tif")
#plot(DEM_aspect) #you may wish to plot this to inspect

GDALinfo("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc.tif")
#DEM_aspect

#DEM_aspect_df <- as.data.frame(DEM_aspect, xy = TRUE)#Dataframe created for mapping; but we see later that the files is >2GB and thus too large to map in R
#str(DEM_aspect_df)

#Elevation
DEM <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\dem_ha_bc.tif")
#plot(DEM)

GDALinfo("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\dem_ha_bc.tif")
#DEM_slope

##Determine resolution
res(DEM_aspect)
res(DEM_slope)
res(DEM)

##Plot (must use dataframe version for plotting)
## Files too large to plot; view in QGis
#ggplot() +
#geom_raster(data = DEM_slope_df,
#    aes(x = x, y = y,)) +
#scale_fill_gradientn(name = "Slope", colors = terrain.colors(10)) + 
#coord_quickmap()

#ggplot() +
#geom_raster(data = DEM_aspect_df,
#    aes(x = x, y = y,)) +
#scale_fill_gradientn(name = "Aspect", colors = terrain.colors(10)) + 
#coord_quickmap()
```
NOTE: the following I leave out to keep things simple but I could consider doing this.

Check this out for estimating heatload, which may be more useful for ignition models and may also be useful for escape and spread:
https://rdrr.io/cran/spatialEco/man/hli.html

Get heatload for each location. Make heatload for BC.

"Describes A southwest facing slope should have warmer temperatures than a southeast facing slope, even though the amount of solar radiation they receive is equivalent. The McCune and Keon (2002) method accounts for this by "folding" the aspect so that the highest values are southwest and the lowest values are northeast. Additionally, this method account for steepness of slope, which is not addressed in most other aspect rescaling equations. HLI values range from 0 (coolest) to 1 (hottest). The equations follow McCune (2007) and support northern and southern hemisphere calculations. The folded aspect for northern hemispheres use (180 - (Aspect – 225) ) and for Southern hemisphere ( 180 - ( Aspect – 315) ). If a country is split at the equator you can use the force.hemisphere argument to choose which equation to use. Valid values for this argument are "southern" and "northern" with the default "none"."

```{r}
library(spatialEco)
heatload_BC<-hli(DEM, check = TRUE)

plot(heatload_BC)

```

We can use this same package to calculate the Topographic radiation aspect.
https://rdrr.io/cran/spatialEco/man/trasp.html

"Calculates the Roberts and Cooper (1989) Solar-radiation Aspect Index Roberts and Cooper (1989) rotates (transforms) the circular aspect to assign a value of zero to land oriented in a north-northeast direction, (typically the coolest and wettest orientation), and a value of one on the hotter, dryer south-southwesterly slopes. The result is a continuous variable between 0 - 1. The metric is defined as: trasp = ( 1 - cos((pi/180)(a-30) ) / 2 where; a = aspect in degrees."


```{r}
TRASP<-trasp(DEM)

plot(TRASP) #Almost all values <0.10... suspicious when on a scale from 0 to 1

TRASP2<-trasp(DEM_aspect) #Attempting to provide the aspect layer instead of elevation layer, even though example in documentation appears to use an elevation layer

plot(TRASP2) #This looks more accurate/likely. When lookinjg at a histogtam later though, something still seems wrong.

```


Stack the rasters. Stacking the rasters will make extracting slope and aspect values for our data points easier downstream (https://gisday.wordpress.com/2014/03/24/extract-raster-values-from-points-using-r/comment-page-1/)


```{r}
##Stack the rasters
#rasStack = stack(DEM_slope, DEM_aspect)
#rasStack = stack(DEM_slope, DEM_aspect, DEM, heatload_BC, TRASP2)
rasStack = stack(DEM_slope, DEM_aspect, DEM)
crs(rasStack)
head(rasStack)
str(rasStack)

```

Bring in data points for which we want data for elevation, slope and aspect (i.e, sample locations). This is the data that we uploaded at the end of the 02_non_fire_point_sampling. If you are continuing from this file immediately, you may not need to bring it back in again. 

Be aware that when being saved prior, some of the column names may have been shortened. If so, then renaming may need to occur. Here are the names you want:

 [1] "idno"                "fire_year"           "Latitude"            "Longitude"          
 [5] "Tmax05"              "Tmax06"              "Tmax07"              "Tmax08"             
 [9] "Tmax09"              "Tave05"              "Tave06"              "Tave07"             
[13] "Tave08"              "Tave09"              "PPT05"               "PPT06"              
[17] "PPT07"               "PPT08"               "PPT09"               "MDC_04"             
[21] "MDC_05"              "MDC_06"              "MDC_07"              "MDC_08"             
[25] "MDC_09"              "ogc_fid"             "fire_no"             "ign_date"           
[29] "fire_cause"          "fire_id"             "fire_type"           "latitude"           
[33] "longitude"           "size_ha"             "objectid"            "feature_class_skey" 
[37] "zone"                "subzone"             "natural_disturbance" "zone_name"          
[41] "fire"                "wkb_geometry"   

Check CRS.

```{r}
#
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")
sample_locations2 <- sf::st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM public.DC_data_5x_AllMonths")
dbDisconnect (connKyle)

# if using data straight from 02b_climate_data_prep_all.Rmd script
sample_locations2<- samp_locations_sf

head(sample_locations2)
crs(sample_locations2)
sample_locations2$wkb_geometry

#Or can load in locally
# sample_locations2<-st_read(dsn = "C:\\Work\\caribou\\clus\\R\\fire_sim\\data\\DC_data_5x_AllMonths_frt.shp")


##Compare to DEM layer
crs(DEM_aspect) #Numbers similar, but these ones missing +datum, and sample_locations missing +ellps
crs(DEM_slope)
crs(DEM)

res(DEM_aspect)
res(DEM_slope)

```

Next, we will create a file with just latitude and longitude so that we can extract the raster values at these points. Then we will attach the aspect and slope values back to data.
https://stackoverflow.com/questions/54734771/sf-write-lat-long-from-geometry-into-separate-column-and-keep-id-column

```{r}
names(sample_locations2)

##Try this first
test<-cbind(sample_locations2, st_coordinates(sample_locations2))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)
#crs(pointCoordinates) #No CRS when a dataframe

##Extract DEM values from stacked layer
rasValue2=raster::extract(rasStack, pointCoordinates)
head(rasValue2)
str(rasValue2) #200298 values
str(sample_locations2)#200298 values

#Append new information
sample_locations_DEM<-cbind(sample_locations2, rasValue2)
head(sample_locations_DEM)
crs(sample_locations_DEM)

```

Save this file and use for next R Markdown file (04_Road). Make sure you save it to the local machine via OSGeo4W for use in code in the next file.

```{r}

st_write(sample_locations_DEM, dsn = "C:\\Work\\caribou\\clus\\R\\fire_sim\\tmp\\DEM_5x_AllMonths_frt.shp", delete_layer=TRUE)

rm(pointCoordinates, rasValue2, test, DEM, DEM_aspect, DEM_slope, rasStack, rasValue2,samp_joined, samp_joined2, samp_joined_new, sample_locations2, samp_locations_sf) # remove some files out of memory
gc()

#Also write to local machine on OSGeo4W
#ogr2ogr -f "PostgreSQL" PG:"host=localhost user=postgres dbname=postgres password=postgres port=5432" C:\\Work\\caribou\\clus\\R\\fire_sim\\tmp\\DC_data_DEM_5x_AllMonths_frt.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI

##Below needs: (1) update to relevant credentials and (2) then enter into the OSGeo4W command line and hit enter. 
#ogr2ogr -f PostgreSQL PG:"host=DC052586 user= dbname=clus password= port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_DEM_5x_AllMonths.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI
##Above may not work because ogc_fid is NA or not right character type, and the code is trying to set this as the FID when uploading.

#key_get('dbpass', keyring = 'postgreSQL')

```



############## Now move on to file 04_climate_data_prep#############
