---
title: "03_DEM_data_prep"
author: "Cora Skaien"
date: "29/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Copyright 2021 Province of British Columbia
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
# http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and limitations under the License.

#===================

Because slope and aspect have been shown to influence both ignition and spread of fires, we will use the provincial DEM layer to acquire the slope and aspect of each location. The provincial DEM has already had the slope and aspect extracted for the entire province at 1 ha resolution. We will bring in these layers (100 m x 100 m resolution), and then extract the slope and aspect for each of the sample location points that we have generated at the end of file 02_climate_data.prep.

Later, we may need to know the slope of each adjacent cell as well when we model spread.

Many papers also bring elevation into their models. This ma be a consideration to add in the future.

```{r}
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(cleangeo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(rgdal)
library(keyring)
library(DBI)

source(here::here("R/functions/R_Postgres.R"))
```

The Provincial DEM layers accessible to us is located here: T:\FOR\VIC\HTS\ANA\PROJECTS\CLUS\Data\dem\all_bc 
Load in the relevant files and inspect.

```{r}
##Slope
DEM_slope <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc.tif")
plot(DEM_slope)

GDALinfo("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\slope_ha_bc.tif")
DEM_slope

DEM_slope_df <- as.data.frame(DEM_slope, xy = TRUE) #Dataframe created for mapping; but we see later that the files is >2GB and thus too large to map in R
str(DEM_slope_df)

##Aspect
DEM_aspect <- raster("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc.tif")
plot(DEM_aspect)

GDALinfo("T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\dem\\all_bc\\aspect_ha_bc.tif")
DEM_aspect

DEM_aspect_df <- as.data.frame(DEM_aspect, xy = TRUE)#Dataframe created for mapping; but we see later that the files is >2GB and thus too large to map in R
str(DEM_aspect_df)

##Determine resolution
res(DEM_aspect)
res(DEM_slope)

##Plot (must use dataframe version for plotting)
## Files too large to plot; view in QGis
#ggplot() +
#geom_raster(data = DEM_slope_df,
#    aes(x = x, y = y,)) +
#scale_fill_gradientn(name = "Slope", colors = terrain.colors(10)) + 
#coord_quickmap()

#ggplot() +
#geom_raster(data = DEM_aspect_df,
#    aes(x = x, y = y,)) +
#scale_fill_gradientn(name = "Aspect", colors = terrain.colors(10)) + 
#coord_quickmap()
```

Stack the two rasters. Stacking the two rasters will make extracting slope and aspect values for our data points easier downstream (https://gisday.wordpress.com/2014/03/24/extract-raster-values-from-points-using-r/comment-page-1/)

```{r}
##Stack the two rasters
rasStack = stack(DEM_slope, DEM_aspect)
crs(rasStack)

```

Bring in data points for which we want data for slope and aspect (i.e, sample locations). This is the data that we uploaded at the end of the 02_climate_data_prep_all. If you are contuning from this file immediately, you may not need to bring it back in again. 

Be aware that when being saved prior, some of the column names may have been shortened. If so, then renaming may need to occur. Here are the names you want:

 [1] "idno"                "fire_year"           "Latitude"            "Longitude"          
 [5] "Tmax05"              "Tmax06"              "Tmax07"              "Tmax08"             
 [9] "Tmax09"              "Tave05"              "Tave06"              "Tave07"             
[13] "Tave08"              "Tave09"              "PPT05"               "PPT06"              
[17] "PPT07"               "PPT08"               "PPT09"               "MDC_04"             
[21] "MDC_05"              "MDC_06"              "MDC_07"              "MDC_08"             
[25] "MDC_09"              "ogc_fid"             "fire_no"             "ign_date"           
[29] "fire_cause"          "fire_id"             "fire_type"           "latitude"           
[33] "longitude"           "size_ha"             "objectid"            "feature_class_skey" 
[37] "zone"                "subzone"             "natural_disturbance" "zone_name"          
[41] "fire"                "wkb_geometry"   

Check CRS.

```{r}
#
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")
sample_locations2 <- sf::st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM public.DC_data_July")
dbDisconnect (connKyle)

head(sample_locations2)
crs(sample_locations2)
sample_locations2$wkb_geometry

#Or can load in locally
# sample_locations2<-st_read(dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_July.shp")

#Or if continuing from last file
#sample_locations2<-ignition_weather_crs
crs(sample_locations2)

##Compare to DEM layer
crs(DEM_aspect) #Numbers similar, but these ones missing +datum, and sample_locations missing +ellps
crs(DEM_slope)

res(DEM_aspect)
res(DEM_slope)

```

Next, we will create a file with just latitude and longitude so that we can extract the raster values at these points. Then we will attach the aspect and slope values back to data.
https://stackoverflow.com/questions/54734771/sf-write-lat-long-from-geometry-into-separate-column-and-keep-id-column

```{r}
names(sample_locations2)


##Try this first
test<-cbind(sample_locations2, st_coordinates(sample_locations2))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)
crs(pointCoordinates) #No CRS when a dataframe

##Extract DEM values from stacked layer
rasValue2=raster::extract(rasStack, pointCoordinates)
head(rasValue2)
str(rasValue2) #501353 values
str(sample_locations2)#501353 values

#Append new information
sample_locations_DEM<-cbind(sample_locations2, rasValue2)
head(sample_locations_DEM)
crs(sample_locations_DEM)

```

Save this file and use for next R Markdpwn file (04_vri_data_prep). Make sure you save it to the local machine via OSGeo4W for use in code in the next file.

```{r}

st_write(sample_locations_DEM, dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_DEM.shp", delete_layer=TRUE)

#Also write to local machine on OSGeo4W
#ogr2ogr -f "PostgreSQL" PG:"host=localhost user=postgres dbname=postgres password=postgres port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_DEM.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI

##Below needs: (1) update to relevant credentials and (2) then enter into the OSGeo4W command line and hit enter. 
#ogr2ogr -f PostgreSQL PG:"host=DC052586 user= dbname=clus password= port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_DEM.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI
##Above may not work because ogc_fid is NA or not right character type, and the code is trying to set this as the FID when uploading.

#key_get('dbpass', keyring = 'postgreSQL')


```

############## Now move on to file 04_VRI_data_prep#############
