---
title: "Road_Density_Data_prep"
author: "Cora Skaien"
date: "12/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#Overview
Many studies have shown that road density is highly correlated with person-caused fires (e.g., Marchal et al. 2017), and they often use km of road per km^2 area. Here, we will attempt to bring in the roads layer from clus, investigate differences in number of roads present between 2002-2020, consider using the road clus to back-cast where roads were from 2002 to 2020, and then determine annual road density per km^2. This data will be utilized only in the person-caused fire model, and not in the lightning caused fire model. 

```{r}
#Libraries
library(keyring)
library(sf)
library(raster)
library(dplyr)

```

Bring in the data. This is a very large file and R may have a hard time bringing it in. This data was created in 2018 and represents the road network as of 2017/2018. It is possible to use the road clus to back-cast with other files. For now and for simplicity, we will assume constant road density from 2002-2018 and into the future, but future refinements may wish to alter this and get more accurate road data annually.

```{r}
conn <- DBI::dbConnect (dbDriver ("PostgreSQL"), 
                        host = keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                        dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                        port = '5432',
                        user = keyring::key_get('dbuser', keyring = 'postgreSQL'),
                        password = keyring::key_get('dbpass', keyring = 'postgreSQL'))

roads_layer<- st_read (dsn = conn, 
          layer = c ("public", "integrated_roads"))
dbDisconnect (conn)

```
Inspect the file. Check the coordinate system. Determine the names of items in the file.

```{r}
crs(roads_layer)
head(roads_layer)
names(roads_layer)

```

Bring in the BC boundary, transform, and inspec - plot the provincial boundary with the roads layer to ensure that they align properly.

```{r}

prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
bc.bnd <- st_transform (prov.bnd, 3005) #Transform coordinate system

ggplot() +
  geom_sf(data=bc.bnd, col='red') +
  geom_sf(data=roads_layer, col='black') #Looks good! Roads are all contained within the BC Boundary

```

Now we will then bring in the data layer from the DEM_data_prep file. 

```{r}
sample_locations_DEM <- st_read(dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\DC_data_DEM_5x.shp")

```
Inspect the data. See what the names of columns are, geometry type, etc. We will also plot this one again to ensure that it falls within the BC Boundary properly.

```{r}
head(sample_locations_DEM)

ggplot() +
  geom_sf(data=bc.bnd, col='red') +
  geom_sf(data=sample_locations_DEM, col='black')
```

Now, we need to buffer each point from the sample_locations_DEM file by 0.564 km or 564 m to get a 1 km^2 area. Once we have this buffer, we can then perform an intersect to determine how many km of road we have per km^2 of area for each data point. This will involve summing over multiple rows because each road segment will create a new row within the dataframe but the same polygon id may appear multiple times.

```{r}
sample_locations_DEM_buf<- st_buffer(sample_locations_DEM, 564) #Set the buffer to 564 m to get a circle with a radius of 564 m and an area of 1 km2

crs(sample_locations_DEM_buf)
head(sample_locations_DEM_buf) #Note, now these are polygon features instead of point features because we have buffers.

```
Because 'idno' have caused issues in previous files, duplicate this column as 'oid' to be safe.

```{r}
sample_locations_DEM_buf$oid<-sample_locations_DEM_buf$idno

```

Perform st_intersection between the roads layer and our buffered layer to get roads clipped to the area of the polygons.

```{r}
roads_100ha_buffers<-st_intersection(sample_locations_DEM_buf, roads_layer)
head(roads_100ha_buffers)
table(roads_100ha_buffers$idno) #Quick inspection to see that multiple roads do indeed return multiple reports for each idno

#Check what the distribution of shape length is
hist(roads_100ha_buffers$shape_length)
mean(roads_100ha_buffers$shape_length) #Mean shape length is 548 m

```

Once we have the roads intersected with the polygon, we can then get the sums for each. Note, however, that if there are no roads for a location, that a 0 will be returned for those polygons (buffered circles) and that a special match will need to be performed to get the correct points appended back to the original data. Ensure you change the file to a data frame first so that it takes < 5 seconds to run instead of 4 hours.

```{r}
str(roads_100ha_buffers)
roads_100ha_buffers_df<-as.data.frame(roads_100ha_buffers)

road_sums_df<- roads_100ha_buffers_df %>%
  group_by(idno) %>%
  summarize(
    shape_length = sum(shape_length)
  )

table(road_sums_df$idno)
head(road_sums_df)
str(road_sums_df)#Check how many rows there are in the data and compare to our initial data
#181,356
str(sample_locations_DEM) # 274594 obs
#Note that there is a difference because not all cells had roads!

```

Now we will append this new data back to our original sample_locations_DEM data. We also need to replace all of the NA values with 0s, as an NA indicates that there were no roads present in that polygon buffer.

```{r}
crs(road_sums_df) #Check if it has a coordinate system - no (as expected)

sample_locations_DEM_roads<- merge(sample_locations_DEM, road_sums_df, by = 'idno', all=TRUE)
crs(sample_locations_DEM_roads) #has coordinate system as expected
head(sample_locations_DEM_roads) #check if you can see any with NA in the 

str(sample_locations_DEM_roads)
#Check if need this below?
#sample_locations_DEM_roads_sf<-st_as_sf(sample_locations_DEM_roads)

#Replace NAs in shape_length column with 0s
sample_locations_DEM_roads$shape_length[is.na(sample_locations_DEM_roads$shape_length)] <- 0
head(sample_locations_DEM_roads) #We can see that NAs have not been switched to 0

```

Inspect the results to ensure nothing seems too crazy

```{r}
hist(sample_locations_DEM_roads$shape_length)
mean(sample_locations_DEM_roads$shape_length) #Mean is 3841.987 m of road per km square
max(sample_locations_DEM_roads$shape_length) #Max is 207,868.7 m of road per km square. This seems impossible.

##Convert to kms worth of road
sample_locations_DEM_roads$shape_length_km<-(sample_locations_DEM_roads$shape_length/1000)
hist(sample_locations_DEM_roads$shape_length_km, n=100)
mean(sample_locations_DEM_roads$shape_length_km) #Mean is 3.8 km of road per km square
max(sample_locations_DEM_roads$shape_length_km) #max is 207 km of road per km square... seems unlikely!

sample_locations_DEM_roads_2<-subset(sample_locations_DEM_roads, sample_locations_DEM_roads$shape_length_km < 100)
hist(sample_locations_DEM_roads_2$shape_length_km, n=100) #Is outlier removed? New max is 138 if subset at the 200 km level.
max(sample_locations_DEM_roads_2$shape_length_km)
str(sample_locations_DEM_roads_2) #274573 observations -- only lose 21 observations and likely more accurate
str(sample_locations_DEM_roads) #274594 observations
```

Now that we have the roads data appended to our data, we can save the file and move on to the next step.

```{r}

st_write(sample_locations_DEM_roads_2, dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_climate_DEM_roads.shp", delete_layer=TRUE)
##Can also open in QGis to assess for any physical outliers and their information.

#str(ignition_weather_crs)
#head(ignition_weather_crs)
#ignition_weather_crs<-st_as_sf(ignition_weather_crs)

##Save to personal drive
#ogr2ogr -f "PostgreSQL" PG:"host=localhost user=postgres dbname=postgres password=postgres port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_climate_DEM_roads.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI

##Below needs: (1) update to relevant credentials and (2) then enter into the OSGeo4W command line and hit enter. 
#ogr2ogr -f PostgreSQL PG:"host=DC052586 user= dbname=clus password= port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_climate_DEM_roads.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI
##Above may not work because ogc_fid is NA or not right character type, and the code is trying to set this as the FID when uploading.

#key_get('dbpass', keyring = 'postgreSQL')
```

############## Now move on to file 05_VRI_data_prep#############
