---
title: "04b_Road_density_per_ha"
author: "Elizabeth Kleynhans, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations."
date: "22/04/2022"
purpose: "To create a raster spatial layer that determines the length of roads per ha for the entire province. This script is based off https://github.com/bcgov/bc-raster-roads/. "
output: html_document
---

<!--
Copyright 2022 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

# B.C. Roads in Raster Format
This analysis generates a raster spatial layer with the total length of roads per hectare for British Columbia. 

### Data

This analysis uses the British Columbia [Digital Road Atlas (DRA) available from the B.C. Data Catalogue]((https://catalogue.data.gov.bc.ca/dataset/bb060417-b6e6-4548-b837-f9060d94743e)) and distributed under the [Access Only - B.C. Crown Copyright ](https://www2.gov.bc.ca/gov/content?id=1AAACC9C65754E4D89A118B875E0FBDA) licence.

The Digital Road Atlas is the [best available single source of road data for the Province of B.C.](https://www2.gov.bc.ca/gov/content?id=21FFEC94B0AD40818D2D2AF06D522714) Metadata details for the Digital Road Atlas (DRA) are available in PDF format from the [B.C. Data Catalogue](https://catalogue.data.gov.bc.ca/dataset/bb060417-b6e6-4548-b837-f9060d94743e).

This analysis _excludes_ some surface and road types in the [Digital Road Atlas (DRA) ](https://catalogue.data.gov.bc.ca/dataset/bb060417-b6e6-4548-b837-f9060d94743e). Boat (B), overgrown (O) & decomissioned (D) roads are excluded from ```TRANSPORT_LINE_SURFACE_CODE``` and ferry routes (F, FP, FR, RWA), non-motorized trails (T, TD), road proposed (RP), and road pedestrian mall (RPM) are excluded from ```TRANSPORT_LINE_TYPE_CODE```.



```{r setup, include=FALSE}
# Raw road file 
# DRA from BCDC:
# https://catalogue.data.gov.bc.ca/dataset/digital-road-atlas-dra-master-partially-attributed-roads/resource/a06a2e11-a0b1-41d4-b857-cb2770e34fb0
RdsZip <- 'dra.gdb.zip'
download.file("ftp://ftp.geobc.gov.bc.ca/sections/outgoing/bmgs/DRA_Public/dgtl_road_atlas.gdb.zip",
              destfile = file.path(DataDir, RdsZip))
unzip(file.path(DataDir, RdsZip), exdir = file.path(DataDir, "DRA"))

# List feature classes in the geodatabase
Rd_gdb <- list.files(file.path(DataDir, "DRA"), pattern = ".gdb", full.names = TRUE)[1]
fc_list <- st_layers(Rd_gdb)

# Read as sf and calculate road lengths
roads_sf <- read_sf(Rd_gdb, layer = "TRANSPORT_LINE") %>% 
  mutate(rd_len = st_length(.))

# Write metadata from gdb to csv files
# (sf >= 0.6-1 supports reading non-spatial tables))
lapply(fc_list$name[grepl("CODE$", fc_list$name)], function(l) {
  metadata <- st_read(Rd_gdb, layer = l, stringsAsFactors = FALSE)
  write_csv(metadata, path = file.path("data", paste0(l, ".csv")))
})

# Determine the FC extent, projection, and attribute information
summary(roads_sf)

# Save as RDS for quicker access later
saveRDS(roads_sf, file = "tmp/DRA_roads_sf.rds")
```


```{r cars}
roads_sf <- readRDS("tmp/DRA_roads_sf.rds")

# Make table of all possible combinations to determine how to classify roads
# into use types, capture all cases and if contribute to non-intact land
Rd_Tbl <- st_set_geometry(roads_sf, NULL) %>% 
  count(TRANSPORT_LINE_SURFACE_CODE, TRANSPORT_LINE_TYPE_CODE)
write_csv(Rd_Tbl, "out/Rd_x_tbl.csv")

# Not roads - TYPE = Ferry routes, non motorized Trails, proposed, pedestrian mall
notRoads <- c("F", "FP", "FR", "RP", "TD", "RWA", "RPM", "T") 
# No longer roads - SURFACE_TYPE = decomissioned, overgrown, and boat
NoLongerRoads <- c("D", "O", "B")

roads_sf <- roads_sf %>% 
  filter(!TRANSPORT_LINE_TYPE_CODE %in% notRoads, 
         !TRANSPORT_LINE_SURFACE_CODE %in% NoLongerRoads)

# Save as RDS for quicker access later.
saveRDS(roads_sf, file = "tmp/DRA_roads_sf_clean.rds")
# Also save as geopackage format for use in other software
write_sf(roads_sf, "out/data/roads_clean.gpkg")
```


```{r pressure, echo=FALSE}
library(raster)
library(spex) # fast conversion of raster to polygons
# For parallel processing tiles to rasters
library(foreach)
#library(doMC)

roads_sf <- readRDS("tmp/DRA_roads_sf_clean.rds")
p<- roads_sf %>% filter(TRANSPORT_LINE_SURFACE_CODE =="P")


# Set up Provincial raster based on hectares BC extent, 1ha resolution and projection
ProvRast <- raster(
  nrows = 15744, ncols = 17216, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(roads_sf)$proj4string, resolution = c(100, 100), vals = 0
)

# checking that the roads and ProvRast line up. They should since one was created from the other
plot(ProvRast)
plot(st_geometry(p), add=TRUE)


#ProvRast <- raster(extent(roads_sf), crs = st_crs(roads_sf)$proj4string,
#                   resolution = c(100, 100), vals = 0)

#---------------------
#split Province into tiles for processing

# extent of input layer
ProvBB <- st_bbox(ProvRast)

#Number of tile rows, number of columns will be the same
nTileRows <- 10

prov_grid <- st_make_grid(st_as_sfc(ProvBB), n = rep(nTileRows, 2))
prov_grid <- st_sf(tile_id = seq_along(prov_grid), 
                   geometry = prov_grid, crs = 3005)

# Plot grid and Prov bounding box just to check
#plot(prov_grid, add=TRUE)
ProvPlt <- st_as_sfc(ProvBB, crs = 3005)
plot(ProvPlt, add = TRUE, border = "red", lwd=8)
plot(prov_grid, add=TRUE)

# Chop the roads up by the 10x10 tile grid. This takes a while but you only have to 
# do it once.
roads_gridded <- st_intersection(roads_sf, prov_grid)

# Loop through each tile and calculate road density for each 1ha cell.
# Choose number of cores to use in parallel carefully... too many and
# it will fill up memory and grind to a halt.
registerDoMC(3) # note I could not get this to work. It told me the package was not compatible with my current R version. So I skipped this. it still worked fine and went fairly fast on a machine with 64GB of ram.

ptm <- proc.time()
foreach(i = prov_grid$tile_id) %dopar% {
  Pcc <- raster::extent(prov_grid[prov_grid$tile_id == i, ])
  DefaultRaster <- raster(Pcc, crs = st_crs(roads_gridded)$proj4string, 
                          resolution = c(100, 100), vals = 0, ext = Pcc)
  
  ## Use the roads layer that has already been chopped into tiles
  TilePoly <- roads_gridded[roads_gridded$tile_id == i, ]
  
  if (nrow(TilePoly) > 0) {
    
    ##  This calculates lengths more directly than psp method...
    DefaultRaster[] <- 1:ncell(DefaultRaster)
    rsp <- spex::polygonize(DefaultRaster) # spex pkg for quickly making polygons from raster
    # Split tile poly into grid by the polygonized raster
    rp1 <- st_intersection(TilePoly[,1], rsp)
    rp1$rd_len <- as.numeric(st_length(rp1)) # road length in m for each grid cell
    # Sum of road lengths in each grid cell
    x <- tapply(rp1$rd_len, rp1$layer, sum, na.rm = TRUE)
    # Create raster and populate with sum of road lengths
    roadlengthT <- raster(DefaultRaster)
    roadlengthT[as.integer(names(x))] <- x
    roadlengthT[is.na(roadlengthT)] <- 0
    
    rm(rsp, rp1, x)
  } else {
    roadlengthT <- DefaultRaster
  }
  fname <- file.path(tileOutDir, paste0("rdTile_", i, ".tif"))
  writeRaster(roadlengthT, filename = fname, format = "GTiff", overwrite = TRUE)
  message(fname)
  rm(Pcc, DefaultRaster, TilePoly, roadlengthT, fname)
  gc()
}

#Memory functions - object.size(roadsIN), gc(), rm()

```

```{r}
#code to read rasters from a directory and mosaic - faster than merge or mosaic
#Code snippet from: https://stackoverflow.com/questions/15876591/merging-multiple-rasters-in-r

#Build list of all raster files you want to join (in your current working directory).
Tiles<- list.files(path=tileOutDir, pattern='rdTile_', full.names = TRUE)

#Make a template raster file to build onto

template<-ProvRast
proj4string(template) <- CRS('+init=epsg:3005') 
writeRaster(template, file=file.path(tileOutDir,"RoadDensR.tif"), format="GTiff", overwrite=TRUE)

# Note I never managed to get the next step to work. Again issues with out of date libraries and other problems I could not solve. So eventually I went to QGIS and just merged the files there. This was super fast, so a good alternative!!!

#Merge all raster tiles into one big raster.
# RoadDensR<-mosaic_rasters(gdalfile=file.path(tileOutDir,Tiles),
#                           dst_dataset=file.path(tileOutDir,"RoadDensR.tif"),
#                           of="GTiff",
#                           output_Raster=TRUE)
# gdalinfo(file.path(tileOutDir,"RoadDensR.tif"))
# #Plot to test
# plot(RoadDensR)
#lines(roadsIN,col='red')

# Check total sum of road lengths and compare to total sum from vector object
rast_sum_len <- cellStats(RoadDensR, "sum")
as.numeric(sum(roads_sf$rd_len)) - rast_sum_len
# ~ 250 km difference - pretty good!

file.copy("out/data/tile/RoadDensR.tif", "../roadless-areas-indicator/data/", overwrite = TRUE)

```

The final step after making the roads raster is to sample the density of roads at each of my fire ignition points. 

```{r}
roads <- raster("C:\\Work\\caribou\\clus\\R\\fire_sim\\data\\Roads_length_per_ha_BC.tif")
rast_sum_len <- cellStats(roads, "sum")
cellStats(roads, "max")
cellStats(roads, "min")
GDALinfo("C:\\Work\\caribou\\clus\\R\\fire_sim\\data\\Roads_length_per_ha_BC.tif")

#plot(roads) #you may wish to plot this to inspect but just opening the tif files makes it look like its all good

names(sample_locations_DEM)

##Try this first
test<-cbind(sample_locations_DEM, st_coordinates(sample_locations_DEM))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)
#crs(pointCoordinates) #No CRS when a dataframe

##Extract DEM values from stacked layer
rasValue2=raster::extract(roads, pointCoordinates)
head(rasValue2)
str(rasValue2) #200292 values
str(sample_locations_DEM)#200292 values

#Append new information
sample_locations_DEM_roads<-cbind(sample_locations_DEM, rasValue2)
head(sample_locations_DEM_roads)
sample_locations_DEM_roads <- sample_locations_DEM_roads %>%
  rename(road_ha=rasValue2)

crs(sample_locations_DEM_roads)

st_write(sample_locations_DEM_roads, dsn = "C:\\Work\\caribou\\clus\\R\\fire_sim\\tmp\\DC_data_DEM_roads.shp", delete_layer=TRUE)


```

