---
title: "Fire ignition model fit by BEC zone"
author: "Elizabeth Kleynhans"
date: "20/04/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

editor_options:
  chunk_output_type: console
  
<style> 
p.caption {
  font-size: 1.2em;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require (kableExtra)
require (data.table)
require (DBI)
require (RPostgreSQL)
require (dplyr)
require (ggplot2)
require (here)
library(ggpubr)
library(arm)
library(tidyr)
```


<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

## Introduction

Here I am running a glm for each bec zone to develop a predictive equation so that I can extrapolate fire ignitions into the future. In the script "02_ignition_climate_variable_selection.R" I perform an AIC and ROC analysis for each BEC zone including presence/available fire ignition points and a variety of climate variables. For this analysis I split the data into a training and a validation data set where 75% of the data was used for training and 25% was used for validation. I then fit the model and extracted the AIC and AUC values. This was repeated 100 times and at the end I calculated the average AIC and AUC values. The climate variable that results in the lowest average AIC value I decided to use in this analysis. Table 1 is a summary of which climate variables fitted best for each BEC zone. 

Note: Some climate variables resulted in delta AIC values that were very similar and had much less than 2 points difference. Also, the variable with the smallest AIC value did not always have the best AUC value. Regardelss of these two issues I decided to take the climate variable with the smallest average AIC, except for BEC zone BG. The top model for BG turned out to be the model with the intercept only, thus for this BEC zone I will use the second best model (see table 1 below).

```{r, AIC table, echo = F, message = F, eval = T}

 climate.aic <- read.csv ("D:/Fire/fire_data/raw_data/ClimateBC_Data/AIC_table.csv")

kable (climate.aic,
       caption = "<b>Table 1. Top candidate climate variables as selected through an AIC analysis for each BEC zone.<b>",
       digits = 2) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)

```
## Pull in the data
```{r}
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")
dat <- sf::st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM fire_ignitions_veg_climate_clean")
dbDisconnect (connKyle)

head(dat)
```

## BEC ZONE ESSF
```{r essf climate figure}
# look at the data graphically in this BEC zone

# top climatic variables for essf were 
essf<- dat %>%
  filter(zone=="ESSF")

# Plotting Probability of ignition versus temp and precipitation.
p <- ggplot(essf, aes(tave08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("TAve08") + ylab("Pr (ignition)")
p

p <- ggplot(essf, aes(ppt08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("ppt08") + ylab("Pr (ignition)")
p


hist(essf$tave08)
hist(essf$ppt08, breaks=30)

# Examining the relationship between some stand level variables. Volume and height are fairly correlated but age and volume are not. However, none of the variables are more correlated than 0.7. So Ill try all combinations
ggscatter(essf, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(essf, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(essf, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

hist(essf$proj_age_1)
hist(scale(essf$proj_age_1))
hist(essf$proj_height_1)
hist(scale(essf$proj_height_1))
hist(essf$live_stand_volume_125, breaks=30)
hist(scale(essf$live_stand_volume_125), breaks=30)
```

```{r essf model fits}
################################
#### Fitting statistical models
################################
essf$proj_age_1_scale<-scale(essf$proj_age_1)
essf$live_stand_volume_125_scale<-scale(essf$live_stand_volume_125)
essf$proj_height_1_scale<-scale(essf$proj_height_1)


glm1<- glm(fire_pres ~ tave08 * ppt08, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"tave08 * ppt08"
table.glm[1,3]<-AIC(glm1)

glm2<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"tave08 * ppt08 + vegtype"
table.glm[i,3]<-AIC(glm2)


glm3<- glm(fire_pres ~ tave08 * ppt08 +
             proj_age_1_scale, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_age_1_scale"
table.glm[i,3]<-AIC(glm3)

glm4<- glm(fire_pres ~ tave08 * ppt08 +
             proj_height_1_scale, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_height_1_scale"
table.glm[i,3]<-AIC(glm4)

glm5<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125_scale, 
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125_scale"
table.glm[i,3]<-AIC(glm5)

glm6<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125_scale +
             proj_age_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125_scale + proj_age_1_scale"
table.glm[i,3]<-AIC(glm6)

glm7<- glm(fire_pres ~ tave08 * ppt08 +
             live_stand_volume_125_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + live_stand_volume_125_scale + proj_height_1_scale"
table.glm[i,3]<-AIC(glm7)

glm8<- glm(fire_pres ~ tave08 * ppt08 +
             proj_age_1_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + proj_height_1_scale + proj_age_1_scale"
table.glm[i,3]<-AIC(glm8)

glm9<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             live_stand_volume_125_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + live_stand_volume_125_scale"
table.glm[i,3]<-AIC(glm9)

glm10<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             proj_age_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + proj_age_1_scale"
table.glm[i,3]<-AIC(glm10)

glm11<- glm(fire_pres ~ tave08 * ppt08 +
              vegtype + 
              proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + proj_height_1_scale"
table.glm[i,3]<-AIC(glm11)

glm12<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             live_stand_volume_125_scale +
             proj_age_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + live_stand_volume_125_scale + proj_age_1_scale"
table.glm[i,3]<-AIC(glm12)

glm13<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             live_stand_volume_125_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm13)
i=13
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + live_stand_volume_125_scale + proj_height_1_scale"
table.glm[i,3]<-AIC(glm13)

glm14<- glm(fire_pres ~ tave08 * ppt08 +
             vegtype +
             proj_age_1_scale +
             proj_height_1_scale,
           data= essf,
           family = binomial,
           na.action=na.omit)
summary(glm14)
i=14
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"tave08 * ppt08 + vegtype + proj_age_1_scale + proj_height_1_scale"
table.glm[i,3]<-AIC(glm14)


table.glm$delta.aic<- table.glm$AIC - min(table.glm$AIC)
table.glm[order(table.glm$delta.aic),]

# TOP MODEL IS glm13: tave08 * ppt08 + vegtype + live_stand_volume_125_scale + proj_height_1_scale


####################################################
##### TOP MODEL####

essf_red<-essf %>% drop_na(live_stand_volume_125_scale, proj_age_1_scale, vegtype)

glm_best<- glm(fire_pres ~ scale(tave08) * scale(ppt08) +
             vegtype +
             live_stand_volume_125_scale +
             proj_age_1_scale,
           data= essf_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


essf_red$resids<-resid(glm_best)

binnedplot (essf_red$live_stand_volume_125_scale, 
            essf_red$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (essf_red$proj_age_1_scale, 
            essf_red$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

```


## BEC ZONE SBS

```{r sbs climate figure}
# look at the data graphically in this BEC zone

# top climatic variables for SBS were mean_tmax07_tmax08
sbs<- dat %>%
  filter(zone=="SBS")

# Plotting Probability of ignition versus temp and precipitation.
p <- ggplot(sbs, aes(mean_tmax07_tmax08, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("Mean Tmax_07 and Tmax_08") + ylab("Pr (ignition)")
p

hist(sbs$mean_tmax07_tmax08)

# Examining the relationship between some stand level variables. Volume and height are fairly correlated but age and volume are not. However, none of the variables are more correlated than 0.7. So Ill try all combinations
ggscatter(dat, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(dat, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(dat, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

hist(dat$proj_age_1, breaks=30)
hist(dat$live_stand_volume_125, breaks=30)

```

```{r sbs model fits}
################################
#### Fitting statistical models
################################

glm1<- glm(fire_pres ~ mean_tmax07_tmax08, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"mean_tmax07_tmax08"
table.glm[1,3]<-AIC(glm1)
binnedplot (fitted(glm1), 
            residuals(glm1), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = "Binned Residual Plot - glm1")

#veg_variables<- c("vegtype", "proj_age_1", "proj_height_1", "live_stand_volume_125", "subzone")

glm2<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype"
table.glm[i,3]<-AIC(glm2)
binnedplot (fitted(glm2), 
            residuals(glm2), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = "Binned Residual Plot - glm2")

glm3<- glm(fire_pres ~ mean_tmax07_tmax08 +
             proj_age_1, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + proj_age_1"
table.glm[i,3]<-AIC(glm3)

glm4<- glm(fire_pres ~ mean_tmax07_tmax08 +
             proj_height_1, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + proj_height_1"
table.glm[i,3]<-AIC(glm4)

glm5<- glm(fire_pres ~ mean_tmax07_tmax08 +
             live_stand_volume_125, 
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + live_stand_volume_125"
table.glm[i,3]<-AIC(glm5)

glm6<- glm(fire_pres ~ mean_tmax07_tmax08 +
             live_stand_volume_125 +
             proj_age_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm6)

glm7<- glm(fire_pres ~ mean_tmax07_tmax08 +
             live_stand_volume_125 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm7)

glm8<- glm(fire_pres ~ mean_tmax07_tmax08 +
             proj_age_1 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + proj_height_1 + proj_age_1"
table.glm[i,3]<-AIC(glm8)

glm9<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + live_stand_volume_125"
table.glm[i,3]<-AIC(glm9)

glm10<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             proj_age_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + proj_age_1"
table.glm[i,3]<-AIC(glm10)

glm11<- glm(fire_pres ~ mean_tmax07_tmax08 +
              vegtype + 
              proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + proj_height_1"
table.glm[i,3]<-AIC(glm11)

glm12<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm12)

glm13<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm13)
i=13
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm13)

glm14<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             proj_age_1 +
             proj_height_1,
           data= sbs,
           family = binomial,
           na.action=na.omit)
summary(glm14)
i=14
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax07_tmax08 + vegtype + proj_age_1 + proj_height_1"
table.glm[i,3]<-AIC(glm14)

table.glm$delta.aic<- table.glm$AIC - min(table.glm$AIC)
table.glm[order(table.glm$delta.aic),]

# TOP MODEL IS glm13: mean_tmax07_tmax08 + vegtype + live_stand_volume_125 + proj_age_1


####################################################
##### TOP MODEL####

sbs_red<-sbs %>% drop_na(live_stand_volume_125, proj_age_1, vegtype)

glm_best<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbs_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


sbs_red$resids<-resid(glm_best)

binnedplot (sbs_red$live_stand_volume_125, 
            sbs_red$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (sbs_red$proj_age_1, 
            sbs_red$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# this one has a slight up down trend. Ill try to scale proj_age_1 and see if this helps

glm_best_scale<- glm(fire_pres ~ mean_tmax07_tmax08 +
             vegtype +
             scale(live_stand_volume_125) +
             scale(proj_age_1),
           data= sbs_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best_scale)
binnedplot (fitted(glm_best_scale), 
            residuals(glm_best_scale), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = ("Binned Residual Plot - glm_best_log"))

sbs_red$resids_log<-resid(glm_best_scale)
binnedplot (scale(sbs_red$proj_age_1), 
            sbs_red$resids_log, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# BETTER I THINK! Also the AIC confirms this as it dropped by another 10 points.

# FINAL MODEL EQUATION TO USE IN FIRE PROJECTIONS IS:
# Pr(ignition) = logit^(-1)(-4.47115 + 
#       0.132*mean_tmax07_tmax08 + 
#       -1.12*vegtypeOP)

```

## BEC ZONE SBPS

```{r sbps climate figure}
# look at the data graphically in this BEC zone

# top climatic variables for SBS were mean_tmax07_tmax08
sbps<- dat %>%
  filter(zone=="SBPS")

# Plotting Probability of ignition versus temp and precipitation.
p <- ggplot(sbps, aes(mean_tmax05_tmax06_tmax07_tmax08_tmax09, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("mean_tmax05_tmax06_tmax07_tmax08_tmax09") + ylab("Pr (ignition)")
p

hist(sbps$mean_tmax05_tmax06_tmax07_tmax08_tmax09)

# Examining the relationship between some stand level variables. Volume and height are fairly correlated but age and volume are not. However, none of the variables are more correlated than 0.7. So Ill try all combinations
ggscatter(sbps, x = "live_stand_volume_125", y = "proj_age_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand age")

ggscatter(sbps, x = "live_stand_volume_125", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "live stand volume", ylab = "Stand height")

ggscatter(sbps, x = "proj_age_1", y = "proj_height_1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "proj_age_1", ylab = "Stand height")

hist(sbps$proj_age_1, breaks=30)
hist(sbps$live_stand_volume_125, breaks=30)

```

```{r sbps model fits}
################################
#### Fitting statistical models
################################

glm1<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm1)

table.glm <- data.frame (matrix (ncol = 3, nrow = 0))
colnames (table.glm) <- c ("Model", "Variable", "AIC")
table.glm[1,1]<-"glm1"
table.glm[1,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09"
table.glm[1,3]<-AIC(glm1)

glm2<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm2)
i=2
table.glm[i,1]<-"glm2"
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype"
table.glm[i,3]<-AIC(glm2)

glm3<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             proj_age_1, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm3)
i=3
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + proj_age_1"
table.glm[i,3]<-AIC(glm3)

glm4<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             proj_height_1, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm4)
i=4
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + proj_height_1"
table.glm[i,3]<-AIC(glm4)

glm5<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             live_stand_volume_125, 
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm5)
i=5
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + live_stand_volume_125"
table.glm[i,3]<-AIC(glm5)

glm6<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             live_stand_volume_125 +
             proj_age_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm6)
i=6
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm6)

glm7<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             live_stand_volume_125 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm7)
i=7
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm7)

glm8<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             proj_age_1 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm8)
i=8
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + proj_height_1 + proj_age_1"
table.glm[i,3]<-AIC(glm8)

glm9<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm9)
i=9
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125"
table.glm[i,3]<-AIC(glm9)

glm10<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             proj_age_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm10)
i=10
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + proj_age_1"
table.glm[i,3]<-AIC(glm10)

glm11<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
              vegtype + 
              proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm11)
i=11
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + proj_height_1"
table.glm[i,3]<-AIC(glm11)

glm12<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm12)
i=12
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125 + proj_age_1"
table.glm[i,3]<-AIC(glm12)

glm13<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm13)
i=13
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125 + proj_height_1"
table.glm[i,3]<-AIC(glm13)

glm14<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             proj_age_1 +
             proj_height_1,
           data= sbps,
           family = binomial,
           na.action=na.omit)
summary(glm14)
i=14
table.glm[i,1]<-paste0("glm",i)
table.glm[i,2]<-"mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + proj_age_1 + proj_height_1"
table.glm[i,3]<-AIC(glm14)

table.glm$delta.aic<- table.glm$AIC - min(table.glm$AIC)
table.glm[order(table.glm$delta.aic),]

# TOP MODEL IS glm13: mean_tmax05_tmax06_tmax07_tmax08_tmax09 + vegtype + live_stand_volume_125 + proj_age_1


####################################################
##### TOP MODEL####

sbps_red<-sbps %>% drop_na(live_stand_volume_125, proj_age_1, vegtype)

glm_best<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             live_stand_volume_125 +
             proj_age_1,
           data= sbps_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best)

# model diagnostic plots
binnedplot (fitted(glm_best), 
            residuals(glm_best), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


sbps_red$resids<-resid(glm_best)

binnedplot (sbps_red$live_stand_volume_125, 
            sbps_red$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (sbps_red$proj_age_1, 
            sbps_red$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# this one has a slight up down trend. Ill try to scale proj_age_1 and see if this helps

glm_best_scale<- glm(fire_pres ~ mean_tmax05_tmax06_tmax07_tmax08_tmax09 +
             vegtype +
             scale(live_stand_volume_125) +
             scale(proj_age_1),
           data= sbps_red,
           family = binomial,
           na.action=na.omit)
summary(glm_best_scale)
binnedplot (fitted(glm_best_scale), 
            residuals(glm_best_scale), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = ("Binned Residual Plot - glm_best_log"))

sbps_red$resids_log<-resid(glm_best_scale)
binnedplot (scale(sbps_red$proj_age_1), 
            sbps_red$resids_log, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))
# BETTER I THINK! Also the AIC confirms this as it dropped by another 10 points.

# FINAL MODEL EQUATION TO USE IN FIRE PROJECTIONS IS:
# Pr(ignition) = logit^(-1)(-4.47115 + 
#       0.132*mean_tmax05_tmax06_tmax07_tmax08_tmax09 + 
#       -1.12*vegtypeOP)

```

