---
title: "Wind_Speed_Data_Prep"
author: "Cora Skaien"
date: "13/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 05_Wind_Speed_Data_Prep.R
#  Script Version: 1.0
#  Script Purpose: Determine the wind speed in the spring and summer at each location, after initially creating a raster from the Canadian Wind Atlas.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Overview
Wind speed and direction are important factors in modelling fire behaviour and spread. The classic tool used for regional data is WindNinja, but this has some limitations and is usually performed on 50 m x 50 m areas, as opposed to the entirely of a large area like BC. Ideally, WindNinja would be used to create better predictions for wind speed and direction (although it has problems as well, wherein it utilizes weather stations that may not capture variation at different elevations, etc), but here we will use the Canadian Wind Atlas to get average wind speed for each season (spring, summer, fall). SOme limitations of using the Canadian Wind Atlas for modelling fire behaviour include:

1. Canadian (FBPS, CFIS, etc.) and U.S. models require wind speeds measured at 10m, 20ft, or at mid-flame height to be used as inputs. Speeds generated by the Canadian Wind Atlas are at 30m, 50m and 80m heights.
2. Wind direction is not provided in the most recent release.
3. You can't parse out data for fire season months (May-August, April-September, etc.), it only provides by season (Spring, Summer, etc.).
4. Only average wind speeds are provided, rather than 90th percentile speeds (or any other percentile).

Future model refinements may choose to utilize different wind speed information, especially if wind direction can be acquired. For this first model, we deemed it adequate since we are predicting probability of fire spread to specific areas over a longer period of time, and wind direction in most areas can change between day and night, and on different days. This certainly does leave room for error in the most likely direction for fires to spread in some areas, however.

#Data prep
In this file, we will bring in shape files that indicate wind speed averaged over 43 years to get an idea of the spring and summer wind speeds experienced in an area from the Canadian Wind Atlas. Much of the work in this file will be initially performed in QGIS, and once these layers are created, they do not need to be created again unless you do not have access to the generated layers.

These files were acquired from the Wind Atlas from the government of Canada:http://www.windatlas.ca/index-en.php

Spring is represented by MAM (March, April, May). Summer is represented by JJA (representing June, July and August). You will also receive the winter, fall and annual values in one folder.

The MIF files are column files and contain seven variables, the first two (E1 and EU) being the results of the statistical processing and the five others being related to the input data:

E1 (W/m2), mean wind power,
EU (m/s), mean wind speed,
ME (m), topography,
MG, land/water mask (1=land, 0=water),
2B (m), rugosity length,
LA, latitude,
LO, longitude given between 0 and 360°.

I believe that any values of -1 for EU represent missing data.

#Because the wind ratsers have been created now, skip to Step 5 if you have access to the created rasters.

############# Step 1: Download files and convert to Shape files ################
These files were downloaded as mif. files and converted to shape files using OsGeo4W. Sample code is provided below:

ogr2ogr -f 'ESRI Shapefile' output.shp input.mif

Specific example:
ogr2ogr -f “ESRI Shapefile” D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\064_30\\JJA\\7\\4_30_we_dos.shp D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\064_30\\JJA\\7\\4_30_we_dos.mif


################### Step 2: Use QGIS to set coordinate system and merge together ############
You will need to bring in each of the files separately for summer and for spring. Bring in all of the summer layers first to merge into one larger file. This will be done in QGIS because otherwise R crashes for me.

In QGIS, bring in all of the files and visualize them.

The crs for the mif file is :CoordSys Earth Projection 20, 999, 12, 0, 0, 0, 7, -100.0000 , 90, 0.9330127, 0, 0

This can be input as espg 3996 in QGIS. Set the coordinate system for all layers.

Next, once all layers are in QGIS and have had their coordinate systems set, we select the first 2 overlapping layers. We will use the "Difference" function under Vector --> Geoprocessing Tools. Then, take this difference and the relevant original tile and use "Merge" function fromVector --> Data Management Tools. Now, select your merged object and the next overlapping layer and repeat. Do this for all layers until you have one element. Save/Export as a shape file.


################## Step 3: Bring into R #################
Once all files were combined in QGIS, then we do some processing in R before we return to QGIS. We will bring in the created shape file, then convert crs to 3005 and then save the file to use in QGIS. 

#Load libraries

```{r}
library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(bcmaps)
library(ggplot2)
require (RPostgreSQL)
require (rpostgis)
require (fasterize)
require (dplyr)
library(keyring)

source(here::here("R/functions/R_Postgres.R"))
```

Load shape files for both the created summer file, and for BC Boundaries.

```{r}
wind_data<- st_read ( dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\BC_Wind_summer.shp", stringsAsFactors = T)

st_crs(wind_data) #Check crs

```

Graph.

```{r}
ggplot() +
  geom_sf(data=wind_data2, col='red') 

ggplot() +
  geom_sf(data=wind_data, col='red') 

```

We see with the above projections that the appropriate rotation did not come in. So we will set the crs and then transform.

```{r}
wind_data.sf <- st_set_crs(wind_data, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs")

wind_data2b <- st_transform (wind_data.sf , 3005)

ggplot() +
  geom_sf(data=wind_data.sf, col='red') 

ggplot() +
  geom_sf(data=wind_data2b, col='red') 
```
We will now rite the file so that we can use it in QGIS to get the clipped layer we want.

```{r}
st_write(wind_data2b, overwrite = TRUE,  dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\BC_Wind_summer_3005.shp", delete_dsn = TRUE)
```

Now let's bring in the provincial boundary layer and change the crs.

```{r}
prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
bc.bnd <- st_transform (prov.bnd, 3005)
```
```{r}
#You may wish to write this to the same folder for ease of use in QGIS
st_write(bc.bnd, overwrite = TRUE,  dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\bc.bnd.shp", delete_dsn = TRUE)
```

Graph.

```{r}
ggplot() +
  geom_sf(data=bc.bnd, col='red') 
```
Ensure overlap.

```{r}
ggplot() +
  geom_sf(data=wind_data2b, col='pink') +
  geom_sf(data=bc.bnd, col='red') 

```
At a glance, the above looks good, but hard to tell without a basemap if the alignment is correct or not. If we open in QGIS, and set the symbology on the wind layer to that of EU_1200 in a graduated division, with 6 levels, and removing -1 from the input, we can assess how good of a fit the BC Boundary is. It looks good.

Next, we will clip the Canadian Wind Atlas aggregated layer to the BC Boundaries. This will take quite a long time, so have other work ready or run overnight. I recommend doing the clip in QGIS. If doing the clip in QGIS, use the Vector --> Processing Tools --> Clip function. You may need to use the toolbox and search for "Fix Geometries" and perform on both layers first to get the Clip tool to work. Save the output. 

```{r}
#Clip the wind layer to the BC Boundaries.
#wind.clipped<-wind_data2b[bc.bnd,]
#str(wind.clipped)
#head(wind.clipped)
#wind.clipped$EU_1200

```

If you did not make the file in R, but instead made it in QGIS, bring it back in to investigate. You may need to change destination and file name below to what you named it.

```{r}
wind.clipped<- st_read ( dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\Wind_summer_clipped.shp", stringsAsFactors = T)

str(wind.clipped)
min(wind.clipped$EU_1200) #once clipped, there are no longer any -1 (null values)

```

Check the clipped file. This may only work if you created the file in R as opposed to bringing it back in.

```{r}
ggplot() +
  geom_sf(wind.clipped, col='pink')

```

Save file if you made it in R above. If you made it in QGIS, no need to save it again.

```{r}
st_write(wind.clipped, overwrite = TRUE,  dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\Wind_summer_clipped.shp", delete_dsn = TRUE)
```


#Repeat the above for the spring file. Note, here, I did not set the CRS in QGIS.

```{r}
wind_data_spring<- st_read ( dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\BC_Wind_spring.shp", stringsAsFactors = T)

wind_data.spring.sf <- st_set_crs(wind_data_spring, "+proj=stere +lat_0=90 +lat_ts=60 +lon_0=-100 +x_0=0 +y_0=0 +a= 6371000 +units=m +no_defs")

wind_data.spring2 <- st_transform (wind_data.spring.sf , 3005)

ggplot() +
  geom_sf(data=wind_data.spring2, col='pink') +
  geom_sf(data=bc.bnd, col='red')

```

```{r}
st_write(wind_data.spring2, overwrite = TRUE,  dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\BC_Wind_spring_3005.shp", delete_dsn = TRUE)
```

If maps look good, clip layers. You can do this in R, which will take a very long time, or do this in QGIS. Use the saved file with the 3005 coordinate system from here.

```{r}
#Clip the wind layer to the BC Boundaries
#wind.clipped.spring<-wind_data.spring2[bc.bnd,]
#str(wind.clipped.spring)
#head(wind.clipped.spring)
```

If you made the file in QGIS, bring it back in to R.

```{r}
wind.clipped.spring<- st_read ( dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\Wind_spring_clipped.shp", stringsAsFactors = T)
```

Check the clipped file.

```{r}
ggplot() +
  geom_sf(wind.clipped.spring, col='pink')

```

Save file.

```{r}
st_write(wind.clipped.spring, overwrite = TRUE,  dsn="D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\BC_Wind_spring_clipped.shp", delete_dsn = TRUE)
```


#################Step 4: Turn the clipped vector files into raster files ############

Now that we have the clipped file, we will turn it into a raster file in QGIS. 

#Convert vector into raster with interpolated values
In QGIS, open the clipped vector files that you have generated (these may still be open from prior when you clipped it). Once this is complete, then use Raster--> Conversion --> Rasterize to turn the point data into a raster. You will need to specify the point layer as your input layer, select EU_1200 (wind speed) as your value to interpolate on, and specify the resolution (the polygons are 223.6 m x 223.6 m, so use this as your height and width specification).


Note: One could consider making rasters of wind direction by time period for thousands of points with this: http://www.atlaseolien.ca/series/variables-en.php. This might be something to look into in the future.

The thinking I (Cora) have is that you could get the values for specific hour and dates across multiple dates in a season, and multiple years. Then take an average for a specified time period (perhaps 4 different intervals per day is adequate) and then get those rasters to cycle through daily for modelling. For now, we will keep it simple and not have wind direction.

####################Step 5: Bring in newly created rasters##############

```{r}
summer_wind_raster<- raster("D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\wind_summer_clipped_224.tif")
res(summer_wind_raster)#res seems out of wack

spring_wind_raster<- raster("D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\wind_spring_raster_224.tif")
res(spring_wind_raster) #resolution seems a bit out of wack...

```

Visualize rasters
```{r}
plot(summer_wind_raster)
plot(spring_wind_raster)
```

Stack the rasters.

```{r}
rasStackWind = stack(summer_wind_raster, spring_wind_raster)
crs(rasStackWind)
head(rasStackWind)
str(rasStackWind)
```


Bring data back in from the end of 04_Road_Density_Data_Prep

```{r}
sample_locations_DEM_roads_2<-st_read(dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_climate_DEM_roads_.shp")
str(sample_locations_DEM_roads_2)
crs(sample_locations_DEM_roads_2)

```


```{r}
##Extract Coordinates
test<-cbind(sample_locations_DEM_roads_2, st_coordinates(sample_locations_DEM_roads_2))
head(test)

pointCoordinates<-data.frame(test$X, test$Y)
head(pointCoordinates)
#crs(pointCoordinates) #No CRS when a dataframe

##Extract Wind values from stacked layer
rasValue3=raster::extract(rasStackWind, pointCoordinates)
head(rasValue3)
str(rasValue3) # 274573 values
str(sample_locations_DEM_roads_2)# 274573 values

#Append new information
sample_locations_DEM_roads_wind<-cbind(sample_locations_DEM_roads_2, rasValue3)
head(sample_locations_DEM_roads_wind)
crs(sample_locations_DEM_roads_wind)
```

Rename some columns to make shorter

```{r}
names(sample_locations_DEM_roads_wind)
sample_locations_DEM_roads_wind2<- sample_locations_DEM_roads_wind %>% rename(
  win_sum=wind_summer_clipped_224,
  win_spg=wind_spring_raster_224)
names(sample_locations_DEM_roads_wind2)


```


Save file.

```{r}

sf::st_write(sample_locations_DEM_roads_wind2, dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_clim_DEM_roads_wind_.shp", delete_layer=TRUE)


##Save to personal drive
#ogr2ogr -f "PostgreSQL" PG:"host=localhost user=postgres dbname=postgres password=postgres port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_clim_DEM_roads_wind.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI

##Below needs: (1) update to relevant credentials and (2) then enter into the OSGeo4W command line and hit enter. 
#ogr2ogr -f PostgreSQL PG:"host=DC052586 user= dbname=clus password= port=5432" D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_clim_DEM_roads_wind.shp -overwrite -a_srs EPSG:3005 -progress --config PG_USE_COPY YES -nlt PROMOTE_TO_MULTI
##Above may not work because ogc_fid is NA or not right character type, and the code is trying to set this as the FID when uploading.

#key_get('dbpass', keyring = 'postgreSQL')

```



############# Additional Code Below for vizualizing before clipping ################

```{r}
max(summer1.sf$EU_12007_J)
min(summer1.sf$EU_12007_J) # I do not know how to interpret -1. Missing data? I will assume it is missing data.
table(summer1.sf$EU_12007_J) #3654 -1s present from 30276 observations
hist(summer1.sf$EU_12007_J)
str(summer1.sf)

#Inspect second element
hist(summer1.sf$EU2_12007_)

#Check histograms some other areas
hist(summer2.sf$EU_12007_J)
hist(summer3.sf$EU_12007_J)
hist(summer4.sf$EU_12007_J)

```

Plot the rasters to ensure all looks well

```{r}

ggplot() +
  geom_sf(data=summer1.sf, col='red') +
  geom_sf(data=summer2.sf, col='blue') +
  geom_sf(data=summer3.sf, col='green') +
  geom_sf(data=summer4.sf, col='pink') +
  geom_sf(data=summer5.sf, col='black') +
  geom_sf(data=summer6.sf, col='red') +
  geom_sf(data=summer7.sf, col='blue') +
  geom_sf(data=summer8.sf, col='purple') +
  geom_sf(data=summer9.sf, col='green') +
  geom_sf(data=summer10.sf, col='pink') +
  geom_sf(data=summer11.sf, col='black') +
  geom_sf(data=summer12.sf, col='red') +
  geom_sf(data=summer13.sf, col='blue')


```


Project in 3005 crs with BC map

```{r}
prov.bnd <- st_read ( dsn = "T:\\FOR\\VIC\\HTS\\ANA\\PROJECTS\\CLUS\\Data\\admin_boundaries\\province\\gpr_000b11a_e.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(prov.bnd) #Retrieve coordinate reference system from sf or sfc object
prov.bnd <- prov.bnd [prov.bnd$PRENAME == "British Columbia", ] 
bc.bnd <- st_transform (prov.bnd, 3005) #Transform coordinate system
```


```{r}
ggplot() + 
  geom_sf(data=summer2.sf2, col='blue') +
  geom_sf(data=summer3.sf2, col='green') +
  geom_sf(data=summer4.sf2, col='pink') +
  geom_sf(data=summer5.sf2, col='black') +
  geom_sf(data=summer6.sf2, col='red') +
  geom_sf(data=summer7.sf2, col='blue') +
  geom_sf(data=summer8.sf2, col='purple') +
  geom_sf(data=summer9.sf2, col='green') +
  geom_sf(data=summer10.sf2, col='pink') +
  geom_sf(data=summer11.sf2, col='black') +
  geom_sf(data=summer12.sf2, col='red') +
  geom_sf(data=summer13.sf2, col='blue') +
  geom_sf(data=summer1.sf2, col='red') +
  geom_sf(data=bc.bnd, col='red')
```
At a glance, looks approximately right? Will need to spot check some GPS locations by entering them online once we have them.

Given substantial overlap, we may not need all the files. Try to see which we might consider dropping.

```{r}
ggplot() +
  geom_sf(data=summer1.sf, col='red') +
  geom_sf(data=summer2.sf, col='blue') +
  geom_sf(data=summer3.sf, col='green') +
  geom_sf(data=summer4.sf, col='pink') +
  #geom_sf(data=summer5.sf, col='black') + # we lose a tiny bit here
  #geom_sf(data=summer6.sf, col='red') +
  geom_sf(data=summer7.sf, col='blue') +
  geom_sf(data=summer8.sf, col='purple') +
  geom_sf(data=summer9.sf, col='green') +
  #geom_sf(data=summer10.sf, col='pink') +
  geom_sf(data=summer11.sf, col='black') +
  geom_sf(data=summer12.sf, col='red') +
  geom_sf(data=summer13.sf, col='blue')

#Conclusion: need all polygons!
```

Now that we see we have the coverage we need, we can bind all of the shape files together. We may need to buffer the polygon before proceeding (buffer by 0), like we did with the bec zones in file 02_climate_data_prep_all.

Now that the files have a coordinate system, we may also want to bring the files into QGis to combine to make one layer and then bring it back into R. 

In QGis, bring in all of the files and visualize them. Start in one corner and visualize wherew they are overlapping. Now choose two at a time and use the "Difference" function under Vector --> Geoprocessing Tools. Then, take this difference and the relevant original tile and use "union" from the same window to combine them. Do this for all layers until you have one element. Now, we might need to use "Dissolve" to ensure it is one polygon.


#Save files with projection and manage in QGis. R and the computer crash each time we try to do it here.

```{r}

st_write(summer1.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer1.shp", delete_layer=TRUE)

st_write(summer2.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer2.shp", delete_layer=TRUE)

st_write(summer3.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer3.shp", delete_layer=TRUE)

st_write(summer4.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer4.shp", delete_layer=TRUE)

st_write(summer5.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer5.shp", delete_layer=TRUE)

st_write(summer6.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer6.shp", delete_layer=TRUE)

st_write(summer7.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer7.shp", delete_layer=TRUE)

st_write(summer8.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer8.shp", delete_layer=TRUE)

st_write(summer9.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer9.shp", delete_layer=TRUE)

st_write(summer10.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer10.shp", delete_layer=TRUE)

st_write(summer11.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer11.shp", delete_layer=TRUE)

st_write(summer12.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer12.shp", delete_layer=TRUE)

st_write(summer13.sf, dsn = "D:\\Fire\\fire_data\\raw_data\\GovCanadaWindFiles\\withCRS\\summer13.shp", delete_layer=TRUE)


```


If you are missing variables later for some reason, here is some handy code to reappend the missing columns.

```{r}
sample_locations_DEM_roads_wind2_test<-st_read(dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Data_clim_DEM_roads_wind.shp")

names(sample_locations_DEM_roads_wind2_test)
names(dat_lightning_) #elevation, win_sum, wun_spg
names(dat_person_)#elevation, win_sum, wun_spg

names(sample_locations_DEM)

missingcolumns<-sample_locations_DEM_roads_wind2_test[c(1,40,43,44)] #select idno and all other missing columns
missingcolumns<-sample_locations_DEM[c(2,45)]
missingcolumns

missingcolumns<- missingcolumns %>% rename(
  elevation = dm_h_bc)

dat_lightning_<-left_join(dat_lightning_, missingcolumns)
dat_person_<-left_join(dat_person_, missingcolumns)

head(dat_lightning_)
head(dat_person_)

```

################## Move on to 06_Distance_to_Development #############
