---
title: "09c_fire_ignition_model_selection_NDT3_lightning_treed"
author: "Cora Skaien"
date: "22/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 09c_fire_ignition_model_selection_NDT3_lightning_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection, using various initial models to inform the final model selection.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_lightning_t<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\data_lightning_trees_NDT_Oct.csv")
head(dat_lightning_t)

```

######################### ANALYSES: TREED, LIGHTNING #########################

Now, we will make a loop that does something very similar to our last loop, but with the selected climate variable plus other variables of interest. For lightning caused fires with trees, the variables of interest include:

1. Climate variable(s)
2. Projected Height (proj_height_1)
3. projected age (proj_age_1)  
4. live_stand_volume_125
5. vegtype2 (with additional categories)
6. slope
7. aspect_cos (cos)
8. elevation
9. Various distance to infrastructure variables (dist_mun, dist_dam, dist_nat, dist_pow, dist_mine, dist_any) - no interactions
10. Some measure of death or mountain pine beetle damage -- TBD

Variables to be added after initial model selection for next round model selection:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)

Interactions of interest: two-way interactions between climate (1) and vegtype (6); two-way interactions between topography measures (7-9); interactions between VRI variables.

This will be done separately for trees and non-treed areas. 

##We will do each loop separately for each NDT zone given the large number of possible models for each zone.

First we will create the variable lists that contain all of our variables of interest.

```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(climate1 = "climate1", climate2 = "climate2", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect_cos = "aspect_cos", elevation ="elevation", vegtype2 = "vegtype2", dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", dist_any = "dist_any") #heatload="heatload",

variables_all_c1<-c(climate1 = "climate1", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect_cos = "aspect_cos", elevation ="elevation", vegtype2 = "vegtype2", dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", dist_any = "dist_any") #heatload="heatload",

vars.clim<-c("climate1")
vars.clim.vegtype<-c("climate1", "vegtype2")
vars.clim.vegtype2<-c("climate1", "climate2","vegtype2")
vars.clim.vegtype2b<-c("climate1", "climate2")

vars.oth<-c("proj_height_1", "proj_age_1", "live_stand_volume_125") 
vars.topo<-c("slope", "aspect_cos", "elevation")
vars.heatload<-c("heatload")
vars.infra<-c("dist_mun", "dist_dam", "dist_nat", "dist_pow", "dist_mine", "dist_any")


##Create interaction for climate and vegtype
inputs.me <- c(vars.clim.vegtype)
inputs.me2 <- c(vars.clim.vegtype2)
inputs.me2b <- c(vars.clim.vegtype2b)
```

Now, we will generate two-way interactions for each of these lists. 

```{r}

#####1a. For those with one climate variable
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints <- NULL
for (i in 1:(length(inputs.me)-1)) {
  for (j in (i+1):length(inputs.me)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me[i], inputs.me[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints)

#
#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}


#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype) 
#add climate vars to all of the above
mods.me.climate <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate


#####1b. For those with two climate variables
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2 <- NULL
for (i in 1:(length(inputs.me2)-1)) {
  for (j in (i+1):length(inputs.me2)) {
     twoway.ints2 <- cbind(twoway.ints2, paste(inputs.me2[i], inputs.me2[j], sep=":"))
  }
}
twoway.ints2
length(twoway.ints2)

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2) 
#add climate vars to all of the above
mods.me.climate2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2

#complete list of two-way interactions
mods.twoway2 <- powerSet(twoway.ints2)
length(mods.twoway2) #7
mods.twoway2

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2 <- list()
counter <- 0
for (i in 1: length(mods.twoway2)) {
   s1 <- unique(unlist( strsplit(mods.twoway2[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2)) {
      if (all(s1 %in% mods.me.climate2[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2[[j]], mods.twoway2[[i]])
        mods.inter2[[counter]] <- both
      }
   }
}

length(mods.inter2)
#mods.inter2


####1c. Two variables, no variation in vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2b <- NULL
for (i in 1:(length(inputs.me2b)-1)) {
  for (j in (i+1):length(inputs.me2b)) {
     twoway.ints2b <- cbind(twoway.ints2b, paste(inputs.me2b[i], inputs.me2b[j], sep=":"))
  }
}
twoway.ints2b
length(twoway.ints2b)

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2b) 
#add climate vars to all of the above
mods.me.climate2b <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2b[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2b

#complete list of two-way interactions
mods.twoway2b <- powerSet(twoway.ints2b)
length(mods.twoway2b) #7
mods.twoway2b

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2b <- list()
counter <- 0
for (i in 1: length(mods.twoway2b)) {
   s1 <- unique(unlist( strsplit(mods.twoway2b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2b)) {
      if (all(s1 %in% mods.me.climate2b[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2b[[j]], mods.twoway2b[[i]])
        mods.inter2b[[counter]] <- both
      }
   }
}

length(mods.inter2b)
#mods.inter2b


#########2. Now for topography data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT)

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #7
mods.twowayT

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT)
#mods.interT
mods.interTb<-c(mods.interT,vars.heatload)
#mods.interTb

####3.For other VRI data, get without interactions

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

#mods.me.oth


#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI)

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsI)
length(mods.twowayI) #32768
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI)
#mods.interI


#the list of all possible model RHSs. 
#all.poss.mods <- c(1, vars.clim, twoway.ints, mods.me.oth, mods.me2, mods.inter2)
#all.poss.mods

all.poss.mods.clim.vegtype<-c(1, mods.me.climate, twoway.ints)
all.poss.mods.clim.vegtype 
all.poss.mods.clim.vegtype<-all.poss.mods.clim.vegtype [-2] #Use this line only if there is an odd character(0) added to list
all.poss.mods.clim.vegtype2<-c(1, mods.inter2, twoway.ints2)
all.poss.mods.clim.vegtype2
all.poss.mods.clim.vegtype2<-all.poss.mods.clim.vegtype2[-2]
#all.poss.mods.clim.vegtype2<-all.poss.mods.clim.vegtype2[-9]
all.poss.mods.clim.vegtype2b<-c(1, mods.inter2b, twoway.ints2b)
#all.poss.mods.clim.vegtype2b<-c(1, mods.me.climate2b, mods.inter2b)
all.poss.mods.clim.vegtype2b
all.poss.mods.clim.vegtype2b<-all.poss.mods.clim.vegtype2b[-2]
#all.poss.mods.clim.vegtype2b<-all.poss.mods.clim.vegtype2b[-5]

all.poss.mods.VRI<-c(1, mods.me.oth)
all.poss.mods.VRI
all.poss.mods.VRI<-all.poss.mods.VRI[-2]
#all.poss.mods.topo<-c(1, mods.meT, mods.interT)
all.poss.mods.topo<-c(1, mods.interT)
all.poss.mods.topo
#all.poss.mods.topo<-all.poss.mods.topo[-10]
all.poss.mods.topo<-all.poss.mods.topo[-2]
all.poss.mods.infra<-c(1, mods.meI) #I don't think we want interactions here actually...
#all.poss.mods.infra<-c(1, mods.meI, mods.interI)
all.poss.mods.infra<-all.poss.mods.infra[-2] #See if have future errors to see if need to remove

#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim.vegtype) #None duplicated
duplicated(all.poss.mods.clim.vegtype2)
duplicated(all.poss.mods.clim.vegtype2b)
duplicated(all.poss.mods.VRI)
duplicated(all.poss.mods.topo)
duplicated(all.poss.mods.infra)

```

############### Part 1 of 4 Model Series: Lightning Caused Fires, Trees ##########

Because of the large number of models with all variables included, we will test the climate and vegtype first, then the VRI variables, then the topography variables. Then we will test the top models together, with determining best AIC model from there. Or perhaps we will just combine the top models for each together, and eliminate models if the intercept was the best predictor.

Select NDT: NDT3

```{r}
zones1<-c("NDT3") #Do one zone at a time

prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

########### 1. Climate and vegtype ############
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim.vegtype2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT3")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}


```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_lightning_NDT3_treed_climate<-table.glm.climate.simple

AIC_lightning_NDT3_treed_summary_climate<- AIC_lightning_NDT3_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT3_treed_summary_climate2<- AIC_lightning_NDT3_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT3_treed_summary_climate2)
```

#Now repeat for VRI data

```{r}
########### 2. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.VRI)){
#  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$NDT<-c("NDT3")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_lightning_NDT3_treed_VRI<-table.glm.VRI.simple

AIC_lightning_NDT3_treed_summary_VRI<- AIC_lightning_NDT3_treed_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT3_treed_summary_VRI2<- AIC_lightning_NDT3_treed_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT3_treed_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 3. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$NDT<-c("NDT3")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_lightning_NDT3_treed_topo<-table.glm.topo.simple

AIC_lightning_NDT3_treed_summary_topo<- AIC_lightning_NDT3_treed_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT3_treed_summary_topo2<- AIC_lightning_NDT3_treed_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT3_treed_summary_topo2)
```

#Now repeat for infrastructure

```{r}
########### 4. Distance to Infrastructure ############
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT3")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_lightning_NDT3_treed_infra<-table.glm.infra.simple

AIC_lightning_NDT3_treed_summary_infra<- AIC_lightning_NDT3_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT3_treed_summary_infra2<- AIC_lightning_NDT3_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT3_treed_summary_infra2)

```

#Now combine the datatables and save to computer

```{r}
NDT3_l_models_treed<-rbind(AIC_lightning_NDT3_treed_summary_climate2, AIC_lightning_NDT3_treed_summary_VRI2, AIC_lightning_NDT3_treed_summary_topo2, AIC_lightning_NDT3_treed_summary_infra2)
NDT3_l_models_treed
NDT3_l_models_treed$NDT<-"NDT3"

write.csv(NDT3_l_models_treed, file="D:\\Fire\\fire_data\\raw_data\\NDT3_lightning_models_treed.csv")
```

#STAGE TWO: PUT TOGETHER MORE VARIABLES
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Models:
1. climate1 + climate2 + vegtype2 + climate1:climate2 + climate2:vegtype2
2. proj_height_1 + live_stand_volume_125
3. slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation
4. dist_mun + dist_dam + dist_nat + dist_pow + dist_mine 

Additional Variables:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)

We want to include interactions between variables from within each list. This will make for many models, which may be hard to process in R.


```{r}
##Create variable lists to be used in the model loop.
variables_all_NDT3<-c(climate1 = "climate1", climate2 = "climate2", vegtype2 = "vegtype2", proj_height_1 = "proj_height_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect_cos = "aspect_cos", elevation ="elevation", dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", bclcs_level_5_2 = "bclcs_level_5_2")


#Too many permutations to be able to include two-way interactions and all possible models, so need to divide into what we think may have interactions and which not.
variables_clim_VRI_NDT3<-c(climate1 = "climate1", climate2 = "climate2", vegtype2 = "vegtype2", proj_height_1 = "proj_height_1", live_stand_volume_125 = "live_stand_volume_125")

#treat slope, aspect_cos and elevation as their own thing. And we have already done this analysis with them.
#slope = "slope", aspect_cos = "aspect_cos", elevation ="elevation")

variables_all_infra_landuse_NDT3<-c(dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_mine = "dist_mine", dist_pow = "dist_pow", bclcs_level_5_2 = "bclcs_level_5_2") #I don't think it makes sense to have interactions between the distance elements, but maybe with land use and each distance element?

##
inputs.me.NDT3 <- c(variables_all_NDT3)
#inputs.me.clim_VRI_DEM_NDT3 <- c(variables_clim_VRI_DEM_NDT3)
inputs.me.clim_VRI_NDT3 <- c(variables_clim_VRI_NDT3)
inputs.me.infra_landuse_NDT3 <- c(variables_all_infra_landuse_NDT3)

```

Now, we will generate two-way interactions for each of these lists. We cannot make two-way interactions between them all because apparently it will be >2 GB in size.

```{r}
###
twoway.ints <- NULL
for (i in 1:(length(inputs.me.clim_VRI_NDT3)-1)) {
  for (j in (i+1):length(inputs.me.clim_VRI_NDT3)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.clim_VRI_NDT3[i], inputs.me.clim_VRI_NDT3[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #10

#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(variables_clim_VRI_NDT3) 
#add climate vars to all of the above
mods.me.clim_VRI_NDT3 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.clim_VRI_NDT3[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.clim_VRI_NDT3
length(mods.me.clim_VRI_NDT3) #32


#complete list of two-way interactions
mods.twoway.NDT3 <- powerSet(twoway.ints) # 
length(mods.twoway.NDT3) #1024
#mods.twoway.NDT3

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter.NDT3 <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT3)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT3[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.clim_VRI_NDT3)) {
      if (all(s1 %in% mods.me.clim_VRI_NDT3[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.clim_VRI_NDT3[[j]], mods.twoway.NDT3[[i]])
        mods.inter.NDT3[[counter]] <- both
      }
   }
}

length(mods.inter.NDT3) #1450
#mods.inter.NDT3

##Subset 2: Infrastructure and land use ########
#inputs.me.infra_landuse_NDT3
twoway.ints <- NULL
for (i in 1:(length(inputs.me.infra_landuse_NDT3)-1)) {
  for (j in (i+1):length(inputs.me.infra_landuse_NDT3)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.infra_landuse_NDT3[i], inputs.me.infra_landuse_NDT3[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #15
#Review. If we do not want interactions between the different distance measurements, but only those between land use and distance, subset those.
twoway.ints
twoway.ints_dist<-twoway.ints[c(5,9,12,14,15)]
twoway.ints_dist


#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(variables_all_infra_landuse_NDT3) 
#add climate vars to all of the above
mods.me.infra_landuse_NDT3 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.infra_landuse_NDT3[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.infra_landuse_NDT3
length(mods.me.infra_landuse_NDT3) #64


#complete list of two-way interactions
#mods.twoway.NDT3b <- powerSet(twoway.ints) #
#Or use subset of interactions
mods.twoway.NDT3b <- powerSet(twoway.ints_dist) 
length(mods.twoway.NDT3b) #32
mods.twoway.NDT3b

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter.NDT3b <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT3b)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT3b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.infra_landuse_NDT3)) {
      if (all(s1 %in% mods.me.infra_landuse_NDT3[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.infra_landuse_NDT3[[j]], mods.twoway.NDT3b[[i]])
        mods.inter.NDT3b[[counter]] <- both
      }
   }
}

length(mods.inter.NDT3b) #275
#mods.inter.NDT3b
```

Make final list of variables to assess.
```{r}
## 1. climate and VRI
#the list of all possible model RHSs. 
all.poss.mods.clim_VRI_NDT3<-c(1, mods.me.clim_VRI_NDT3, mods.inter.NDT3)
#all.poss.mods.clim_VRI_NDT3
length(mods.me.clim_VRI_NDT3) #62
all.poss.mods.clim_VRI_NDT3[2]
all.poss.mods.clim_VRI_NDT3[34] #character 0
all.poss.mods.clim_VRI_NDT3<-all.poss.mods.clim_VRI_NDT3[-34]
all.poss.mods.clim_VRI_NDT3<-all.poss.mods.clim_VRI_NDT3[-2] #Use this line only if there is an odd character(0) added to list
length(all.poss.mods.clim_VRI_NDT3) #1481

##Check and rid of any duplicated models
duplicated(all.poss.mods.clim_VRI_NDT3) #Need to remove 
all.poss.mods.clim_VRI_NDT3b<-all.poss.mods.clim_VRI_NDT3[-(33:63)]
duplicated(all.poss.mods.clim_VRI_NDT3b) 
length(all.poss.mods.clim_VRI_NDT3b) #1450


#####2. Infrastructure and land use
all.poss.mods.infra_landuse_NDT3<-c(1,mods.me.infra_landuse_NDT3, mods.inter.NDT3b)

##Check and rid of any duplicated models
duplicated(all.poss.mods.infra_landuse_NDT3) #Need to remove 
all.poss.mods.infra_landuse_NDT3b<-all.poss.mods.infra_landuse_NDT3[-(66:129)]
duplicated(all.poss.mods.infra_landuse_NDT3b) 
all.poss.mods.infra_landuse_NDT3b[2]
all.poss.mods.infra_landuse_NDT3b<-all.poss.mods.infra_landuse_NDT3b[-2]
```

```{r}
#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 

#Below does not work
lapply(biglist, all.poss.mods.infra_landuse_NDT3b {length(all.poss.mods.infra_landuse_NDT3b) == 0L} ) 

```


#all.poss.mods.clim_VRI_NDT3b
We cannot run the model 100 times without R crashing. Instead, we will run it 25 times, then save the output, then run that another 3 times (for a total of 100 runs). Then we will combine all 100 runs, and calculate the deltaAIC from that.

```{r}
zones1<-"NDT3"

#Create empty table
table.glm.clim_VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.clim_VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:25){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim_VRI_NDT3b[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_clim_VRI_NDT3)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim_VRI_NDT3b, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.clim_VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.clim_VRI$NDT<-c("NDT3")
tab.sum.clim_VRI 

table.glm.clim_VRI.simple<-rbind(table.glm.clim_VRI.simple, tab.sum.clim_VRI)

}
}
}
```

For the below chunks, they will need to be run in specific order, with repeating the previous chunk in between. DO NOT RUN THIS CHUNK MORE THAN ONCE! RUN EACH ONE ONCE, AFTER EACH SUBSEQUENT RUN OF THE ABOVE.

```{r}
table.glm.clim_VRI.simple_run1<-table.glm.clim_VRI.simple
head(table.glm.clim_VRI.simple_run1)
```

STOP! RUN the model x25 again.
```{r}
table.glm.clim_VRI.simple_run2<-table.glm.clim_VRI.simple
head(table.glm.clim_VRI.simple_run2)
```

STOP! RUN the model x25 again.
```{r}
table.glm.clim_VRI.simple_run3<-table.glm.clim_VRI.simple
```

STOP! RUN the model x25 again.
```{r}
table.glm.clim_VRI.simple_run4<-table.glm.clim_VRI.simple
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination. First, combine the 4 runs back together.

```{r}
table.glm.clim_VRI.simple<-rbind(table.glm.clim_VRI.simple_run1, table.glm.clim_VRI.simple_run2, table.glm.clim_VRI.simple_run3, table.glm.clim_VRI.simple_run4)
```

Now determine deltaAIC.

```{r}
head(table.glm.clim_VRI.simple)
table(table.glm.clim_VRI.simple$model) # 100 per model

AIC_lightning_NDT3_treed_clim_VRI<-table.glm.clim_VRI.simple

AIC_lightning_NDT3_treed_summary_clim_VRI<- AIC_lightning_NDT3_treed_clim_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT3_treed_summary_clim_VRI2<- AIC_lightning_NDT3_treed_summary_clim_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT3_treed_summary_clim_VRI2)
```

Save file.
```{r}
write.csv(AIC_lightning_NDT3_treed_summary_clim_VRI2, file="D:\\Fire\\fire_data\\raw_data\\AIC_lightning_NDT3_treed_summary_clim_VRI2.csv")
```


#Now repeat for all.poss.mods.infra_landuse_NDT3b
There are not nearly as many models to compare, so we should not need to divide the number of runs ups. Try running it all in one go of 100.

```{r}
########### 2. Distance to Infrastructure ############
#Create empty table
table.glm.infra.lu.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.lu.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra_landuse_NDT3b[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all_infra_landuse_NDT3)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_landuse_NDT3b, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra.lu <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra.lu$NDT<-c("NDT3")
tab.sum.infra.lu 

table.glm.infra.lu.simple<-rbind(table.glm.infra.lu.simple, tab.sum.infra.lu)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination. Also determine deltaAIC.

```{r}
head(table.glm.infra.lu.simple)
table(table.glm.infra.lu.simple$model) # 100 per model

AIC_lightning_NDT3_treed_infra<-table.glm.infra.lu.simple

AIC_lightning_NDT3_treed_summary_infra<- AIC_lightning_NDT3_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT3_treed_summary_infra2<- AIC_lightning_NDT3_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT3_treed_summary_infra2)
```

Save to computer.

```{r}
write.csv(AIC_lightning_NDT3_treed_summary_infra2, file="D:\\Fire\\fire_data\\raw_data\\AIC_lightning_NDT3_treed_summary_infra.csv")
```

############# Manually Determine Best Model ############

Determine the top models based off prior results. Remember to check elevation*climate1 and elevation*climate2

#Climate and VRI
1. climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1

#Infrastructure
2. dist_mun + dist_dam + dist_nat + dist_mine + bclcs_level_5_2 + dist_nat:bclcs_level_5_2

#DEM
3. slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation

#Next investigation
Because there would be far too many models to investigate including all variables and their interactions, we will start with the above and make educated guesses for what may need to be enhanced.

```{r}
dat_lightning_t_NDT3<-subset(dat_lightning_t, dat_lightning_t$ntrl_ds=="NDT3")

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(dat_lightning_t_NDT3$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- dat_lightning_t_NDT3[ trainIndex,]
   Valid <- dat_lightning_t_NDT3[-trainIndex,]

#Run model using dat1
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam + dist_nat + dist_mine + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate1 + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #10856.6

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6289 --> not great
   
Anova(model.NDT3, type=3)
Anova(model.NDT3, type=3, singular.ok = TRUE) 

#Least sig
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam + dist_nat + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate1 + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #10856.1

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6292 --> not great
   
Anova(model.NDT3, type=3)
Anova(model.NDT3, type=3, singular.ok = TRUE) 

#Least sig
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam + dist_nat + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #10856.3

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6288 --> not great
   
Anova(model.NDT3, type=3)
Anova(model.NDT3, type=3, singular.ok = TRUE)

#Least sig
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam + dist_nat + bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #10856.8

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6278 --> not great
   
Anova(model.NDT3, type=3)
Anova(model.NDT3, type=3, singular.ok = TRUE)

#Least sig
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam + dist_nat + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #10856.8

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6284 --> not great
   
Anova(model.NDT3, type=3)
Anova(model.NDT3, type=3, singular.ok = TRUE)

#Least sig
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #10855.2

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6285 --> not great
   
Anova(model.NDT3, type=3)
Anova(model.NDT3, type=3, singular.ok = TRUE)

```

Remove NAs to make comparable.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT3_t<-dat_lightning_t_NDT3 %>% drop_na(climate1, climate2, proj_height_1, live_stand_volume_125, dist_mun, dist_dam, vegtype2, slope, aspect_cos, elevation)

#Run Model again with this data; but uses all data here
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2, family = binomial, data = NDT3_t)

Anova(model.NDT3, type=3)
Anova(model.NDT3, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT3), 
            residuals(model.NDT3), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT3_t$resids<-resid(model.NDT3)

binnedplot (NDT3_t$live_stand_volume_125, 
            NDT3_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT3_t$climate1, 
            NDT3_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good overall... but not perfect (especially last one)

#Partial Residuals
#climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2
visreg(model.NDT3, "climate1", by="climate2")
visreg(model.NDT3, "climate1", by="live_stand_volume_125")

visreg(model.NDT3, "climate2", by="climate1")
visreg(model.NDT3, "climate2", by="vegtype2", overlay=TRUE)
visreg(model.NDT3, "climate2", by="proj_height_1")
visreg(model.NDT3, "climate2", by="elevation")

visreg(model.NDT3, "vegtype2", by="climate2")

visreg(model.NDT3, "proj_height_1", by="climate2")
visreg(model.NDT3, "live_stand_volume_125", by="climate1")

#dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2
visreg(model.NDT3, "dist_mun")
visreg(model.NDT3, "dist_dam")
visreg(model.NDT3, "bclcs_level_5_2")
visreg(model.NDT3, "bclcs_level_5_2", ylim=c(-1,1))

visreg(model.NDT3, "slope", by="elevation")
visreg(model.NDT3, "aspect_cos", by="elevation")
visreg(model.NDT3, "elevation", by="slope")
visreg(model.NDT3, "elevation", by="climate2")
visreg(model.NDT3, "elevation", by="aspect_cos")

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT3)

#Create a new blank table and get AUC too
top_mod_table_NDT3_light_t_ALL <- data.frame (matrix (ncol = 30, nrow = 0))
colnames (top_mod_table_NDT3_light_t_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_climate_interaction", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_stand_height", "coef_live_stand_volume_125",  "coef_dist_mun", "coef_dist_dam", "coef_bclcs_level_5_2DIST", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_climate1:live_stand_volume_125", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_climate2:proj_height_1", "coef_slope:elevation", "aspect_cos:elevation", "climate2:elevation", "AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT3_t$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT3_t[ trainIndex,]
   Valid <- NDT3_t[-trainIndex,]
   
#Model   
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3_light_t <- data.frame (matrix (ncol = 30, nrow = 0))
colnames (top_mod_table_NDT3_light_t ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_climate_interaction", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_stand_height", "coef_live_stand_volume_125",  "coef_dist_mun", "coef_dist_dam", "coef_bclcs_level_5_2DIST", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_climate1:live_stand_volume_125", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_climate2:proj_height_1", "coef_slope:elevation", "aspect_cos:elevation", "climate2:elevation", "AUC")

##Add data for NDT3
top_mod_table_NDT3_light_t[1,1]<-"lightning"
top_mod_table_NDT3_light_t[1,2]<-"NDT3"
top_mod_table_NDT3_light_t[1,3]<-"Y"
top_mod_table_NDT3_light_t[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2" 
top_mod_table_NDT3_light_t[1,5]<- coef(model.NDT3)[1] #Intercept
top_mod_table_NDT3_light_t[1,6]<- coef(model.NDT3)[2] #Climate variable 1
top_mod_table_NDT3_light_t[1,7]<- coef(model.NDT3)[3] #Climate variable 2
top_mod_table_NDT3_light_t[1,8]<- coef(model.NDT3)[17] #Interaction climate variables
top_mod_table_NDT3_light_t[1,9]<- coef(model.NDT3)[4] #coefficient vegtypeTB
top_mod_table_NDT3_light_t[1,10]<- coef(model.NDT3)[5] #coefficient vegtypeTC
top_mod_table_NDT3_light_t[1,11]<- coef(model.NDT3)[6] #coefficient vegtypeTM
top_mod_table_NDT3_light_t[1,12]<- coef(model.NDT3)[7] #coefficient proj_height
top_mod_table_NDT3_light_t[1,13]<- coef(model.NDT3)[8] #coef live_stand_volume_125
top_mod_table_NDT3_light_t[1,14]<- coef(model.NDT3)[9] #coef dist_mun
top_mod_table_NDT3_light_t[1,15]<- coef(model.NDT3)[10] #coefficient dist_dam
top_mod_table_NDT3_light_t[1,16]<- coef(model.NDT3)[11] #coefficient bclcs_level_5_2DIST 
top_mod_table_NDT3_light_t[1,17]<- coef(model.NDT3)[12] #coefficient bclcs_level_5_2OP
top_mod_table_NDT3_light_t[1,18]<- coef(model.NDT3)[13] #coefficient bclcs_level_5_2SP
top_mod_table_NDT3_light_t[1,19]<- coef(model.NDT3)[14] #coefficient slope
top_mod_table_NDT3_light_t[1,20]<- coef(model.NDT3)[15] #coefficient aspect_cos
top_mod_table_NDT3_light_t[1,21]<- coef(model.NDT3)[16] #coefficient elevation
top_mod_table_NDT3_light_t[1,22]<- coef(model.NDT3)[18] #coefficient climate1:live_stand_volume_125
top_mod_table_NDT3_light_t[1,23]<- coef(model.NDT3)[19] #coefficient climate2:vegtype2TB
top_mod_table_NDT3_light_t[1,24]<- coef(model.NDT3)[20] #coefficient climate2:vegtype2TC
top_mod_table_NDT3_light_t[1,25]<- coef(model.NDT3)[21] #coefficient climate2:vegtype2TM
top_mod_table_NDT3_light_t[1,26]<- coef(model.NDT3)[22] #coefficient climate2:proj_height_1
top_mod_table_NDT3_light_t[1,27]<- coef(model.NDT3)[23] #coefficient slope:elevation
top_mod_table_NDT3_light_t[1,28]<- coef(model.NDT3)[24] #coefficient aspect_cos:elevation
top_mod_table_NDT3_light_t[1,29]<- coef(model.NDT3)[25] #coefficient climate2:elevation
top_mod_table_NDT3_light_t[1,30]<- mod.auc

top_mod_table_NDT3_light_t_ALL<-rbind(top_mod_table_NDT3_light_t_ALL, top_mod_table_NDT3_light_t)

}

```

Check.
```{r}
head(top_mod_table_NDT3_light_t_ALL)
```

#Save coefficient table

```{r}
write.csv(top_mod_table_NDT3_light_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_light_t_ALL.csv")

```

Get mean values.

```{r}
names(top_mod_table_NDT3_light_t_ALL)
mean(top_mod_table_NDT3_light_t_ALL$AUC) #0.65

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3_light_t_Means <- data.frame (matrix (ncol = 30, nrow = 0))
colnames (top_mod_table_NDT3_light_t_Means ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_climate_interaction", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_stand_height", "coef_live_stand_volume_125",  "coef_dist_mun", "coef_dist_dam", "coef_bclcs_level_5_2DIST", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_climate1:live_stand_volume_125", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_climate2:proj_height_1", "coef_slope:elevation", "aspect_cos:elevation", "climate2:elevation", "AUC")

head(top_mod_table_NDT3_light_t_Means)

##Add data for NDT3
top_mod_table_NDT3_light_t_Means[1,1]<-"lightning"
top_mod_table_NDT3_light_t_Means[1,2]<-"NDT3"
top_mod_table_NDT3_light_t_Means[1,3]<-"Y"
top_mod_table_NDT3_light_t_Means[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2" 
top_mod_table_NDT3_light_t_Means[1,5]<- mean(top_mod_table_NDT3_light_t_ALL$intercept) #Intercept
top_mod_table_NDT3_light_t_Means[1,6]<- mean(top_mod_table_NDT3_light_t_ALL$coef_climate_1, na.rm=TRUE) #Climate variable 1
top_mod_table_NDT3_light_t_Means[1,7]<- mean(top_mod_table_NDT3_light_t_ALL$coef_climate_2, na.rm=TRUE) #Climate variable 2
top_mod_table_NDT3_light_t_Means[1,8]<- mean(top_mod_table_NDT3_light_t_ALL$coef_climate_interaction, na.rm=TRUE) #Interaction climate variables
top_mod_table_NDT3_light_t_Means[1,9]<- mean(top_mod_table_NDT3_light_t_ALL$coef_vegtypeTB, na.rm=TRUE) #coefficient vegtypeTB
top_mod_table_NDT3_light_t_Means[1,10]<- mean(top_mod_table_NDT3_light_t_ALL$coef_vegtypeTC, na.rm=TRUE) #coefficient vegtypeTC
top_mod_table_NDT3_light_t_Means[1,11]<- mean(top_mod_table_NDT3_light_t_ALL$coef_vegtypeTM, na.rm=TRUE) #coefficient vegtypeTM
top_mod_table_NDT3_light_t_Means[1,12]<- mean(top_mod_table_NDT3_light_t_ALL$coef_stand_height, na.rm=TRUE) #coefficient stand height
top_mod_table_NDT3_light_t_Means[1,13]<- mean(top_mod_table_NDT3_light_t_ALL$coef_live_stand_volume_125, na.rm=TRUE) #stand_volume
top_mod_table_NDT3_light_t_Means[1,14]<- mean(top_mod_table_NDT3_light_t_ALL$coef_dist_mun, na.rm=TRUE) #dist_mun
top_mod_table_NDT3_light_t_Means[1,15]<- mean(top_mod_table_NDT3_light_t_ALL$coef_dist_dam, na.rm=TRUE) #dist_dam
top_mod_table_NDT3_light_t_Means[1,16]<- mean(top_mod_table_NDT3_light_t_ALL$coef_bclcs_level_5_2DIST, na.rm=TRUE) #coef_bclcs_level_5_2DIST
top_mod_table_NDT3_light_t_Means[1,17]<- mean(top_mod_table_NDT3_light_t_ALL$coef_bclcs_level_5_2OP, na.rm=TRUE)#coefficient coef_bclcs_level_5_2OP
top_mod_table_NDT3_light_t_Means[1,18]<- mean(top_mod_table_NDT3_light_t_ALL$coef_bclcs_level_5_2SP, na.rm=TRUE) #coef_bclcs_level_5_2SP
top_mod_table_NDT3_light_t_Means[1,19]<- mean(top_mod_table_NDT3_light_t_ALL$coef_slope, na.rm=TRUE) #coefficient coef_slope
top_mod_table_NDT3_light_t_Means[1,20]<- mean(top_mod_table_NDT3_light_t_ALL$coef_aspect_cos, na.rm=TRUE) #coefficient aspect_cos
top_mod_table_NDT3_light_t_Means[1,21]<- mean(top_mod_table_NDT3_light_t_ALL$coef_elevation, na.rm=TRUE) #coefficient elevation
top_mod_table_NDT3_light_t_Means[1,22]<- mean(top_mod_table_NDT3_light_t_ALL$`coef_climate1:live_stand_volume_125`, na.rm=TRUE) #coef_climate1:live_stand_volume_125
top_mod_table_NDT3_light_t_Means[1,23]<- mean(top_mod_table_NDT3_light_t_ALL$`coef_climate2:vegtype2TB`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_Means[1,24]<- mean(top_mod_table_NDT3_light_t_ALL$`coef_climate2:vegtype2TC`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_Means[1,25]<- mean(top_mod_table_NDT3_light_t_ALL$`coef_climate2:vegtype2TM`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_Means[1,26]<- mean(top_mod_table_NDT3_light_t_ALL$`coef_climate2:proj_height_1`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_Means[1,27]<- mean(top_mod_table_NDT3_light_t_ALL$`coef_slope:elevation`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_Means[1,28]<- mean(top_mod_table_NDT3_light_t_ALL$`aspect_cos:elevation`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_Means[1,29]<- mean(top_mod_table_NDT3_light_t_ALL$`climate2:elevation`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_Means[1,30]<- mean(top_mod_table_NDT3_light_t_ALL$AUC, na.rm=TRUE)

top_mod_table_NDT3_light_t_Means

```

Save mean coefficient table.

```{r}
write.csv(top_mod_table_NDT3_light_t_Means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_light_t_Means.csv")
```

Get sd values.

```{r}

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3_light_t_SD <- data.frame (matrix (ncol = 30, nrow = 0))
colnames (top_mod_table_NDT3_light_t_SD ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_climate_interaction", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_stand_height", "coef_live_stand_volume_125",  "coef_dist_mun", "coef_dist_dam", "coef_bclcs_level_5_2DIST", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_climate1:live_stand_volume_125", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_climate2:proj_height_1", "coef_slope:elevation", "aspect_cos:elevation", "climate2:elevation", "AUC")

head(top_mod_table_NDT3_light_t_SD)

##Add data for NDT3
top_mod_table_NDT3_light_t_SD[1,1]<-"lightning"
top_mod_table_NDT3_light_t_SD[1,2]<-"NDT3"
top_mod_table_NDT3_light_t_SD[1,3]<-"Y"
top_mod_table_NDT3_light_t_SD[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2  + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_mun + dist_dam  + bclcs_level_5_2  + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation  + elevation:climate2" 
top_mod_table_NDT3_light_t_SD[1,5]<- sd(top_mod_table_NDT3_light_t_ALL$intercept) #Intercept
top_mod_table_NDT3_light_t_SD[1,6]<- sd(top_mod_table_NDT3_light_t_ALL$coef_climate_1, na.rm=TRUE) #Climate variable 1
top_mod_table_NDT3_light_t_SD[1,7]<- sd(top_mod_table_NDT3_light_t_ALL$coef_climate_2, na.rm=TRUE) #Climate variable 2
top_mod_table_NDT3_light_t_SD[1,8]<- sd(top_mod_table_NDT3_light_t_ALL$coef_climate_interaction, na.rm=TRUE) #Interaction climate variables
top_mod_table_NDT3_light_t_SD[1,9]<- sd(top_mod_table_NDT3_light_t_ALL$coef_vegtypeTB, na.rm=TRUE) #coefficient vegtypeTB
top_mod_table_NDT3_light_t_SD[1,10]<- sd(top_mod_table_NDT3_light_t_ALL$coef_vegtypeTC, na.rm=TRUE) #coefficient vegtypeTC
top_mod_table_NDT3_light_t_SD[1,11]<- sd(top_mod_table_NDT3_light_t_ALL$coef_vegtypeTM, na.rm=TRUE) #coefficient vegtypeTM
top_mod_table_NDT3_light_t_SD[1,12]<- sd(top_mod_table_NDT3_light_t_ALL$coef_stand_height, na.rm=TRUE) #coefficient stand height
top_mod_table_NDT3_light_t_SD[1,13]<- sd(top_mod_table_NDT3_light_t_ALL$coef_live_stand_volume_125, na.rm=TRUE) #stand_volume
top_mod_table_NDT3_light_t_SD[1,14]<- sd(top_mod_table_NDT3_light_t_ALL$coef_dist_mun, na.rm=TRUE) #dist_mun
top_mod_table_NDT3_light_t_SD[1,15]<- sd(top_mod_table_NDT3_light_t_ALL$coef_dist_dam, na.rm=TRUE) #dist_dam
top_mod_table_NDT3_light_t_SD[1,16]<- sd(top_mod_table_NDT3_light_t_ALL$coef_bclcs_level_5_2DIST, na.rm=TRUE) #coef_bclcs_level_5_2DIST
top_mod_table_NDT3_light_t_SD[1,17]<- sd(top_mod_table_NDT3_light_t_ALL$coef_bclcs_level_5_2OP, na.rm=TRUE)#coefficient coef_bclcs_level_5_2OP
top_mod_table_NDT3_light_t_SD[1,18]<- sd(top_mod_table_NDT3_light_t_ALL$coef_bclcs_level_5_2SP, na.rm=TRUE) #coef_bclcs_level_5_2SP
top_mod_table_NDT3_light_t_SD[1,19]<- sd(top_mod_table_NDT3_light_t_ALL$coef_slope, na.rm=TRUE) #coefficient coef_slope
top_mod_table_NDT3_light_t_SD[1,20]<- sd(top_mod_table_NDT3_light_t_ALL$coef_aspect_cos, na.rm=TRUE) #coefficient aspect_cos
top_mod_table_NDT3_light_t_SD[1,21]<- sd(top_mod_table_NDT3_light_t_ALL$coef_elevation, na.rm=TRUE) #coefficient elevation
top_mod_table_NDT3_light_t_SD[1,22]<- sd(top_mod_table_NDT3_light_t_ALL$`coef_climate1:live_stand_volume_125`, na.rm=TRUE) #coef_climate1:live_stand_volume_125
top_mod_table_NDT3_light_t_SD[1,23]<- sd(top_mod_table_NDT3_light_t_ALL$`coef_climate2:vegtype2TB`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_SD[1,24]<- sd(top_mod_table_NDT3_light_t_ALL$`coef_climate2:vegtype2TC`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_SD[1,25]<- sd(top_mod_table_NDT3_light_t_ALL$`coef_climate2:vegtype2TM`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_SD[1,26]<- sd(top_mod_table_NDT3_light_t_ALL$`coef_climate2:proj_height_1`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_SD[1,27]<- sd(top_mod_table_NDT3_light_t_ALL$`coef_slope:elevation`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_SD[1,28]<- sd(top_mod_table_NDT3_light_t_ALL$`aspect_cos:elevation`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_SD[1,29]<- sd(top_mod_table_NDT3_light_t_ALL$`climate2:elevation`, na.rm=TRUE) #
top_mod_table_NDT3_light_t_SD[1,30]<- sd(top_mod_table_NDT3_light_t_ALL$AUC, na.rm=TRUE)

top_mod_table_NDT3_light_t_SD

```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT3_light_t_SD, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_light_t_SD.csv")
```

#Redo with redued variables

```{r}
dat_lightning_t_NDT3<-subset(dat_lightning_t, dat_lightning_t$ntrl_ds=="NDT3")

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(dat_lightning_t_NDT3$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- dat_lightning_t_NDT3[ trainIndex,]
   Valid <- dat_lightning_t_NDT3[-trainIndex,]

#Run model using dat1
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate1 + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #11027.1

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6425--> ok
   
Anova(model.NDT3, type=3)
#Anova(model.NDT3, type=3, singular.ok = TRUE) 

#Remove least significant
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2, family = binomial, data = dat1)

AIC(model.NDT3) #11024.6

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.6425--> ok
   
Anova(model.NDT3, type=3)
#Anova(model.NDT3, type=3, singular.ok = TRUE) 
```

Remove NAs to make comparable.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT3_t<-dat_lightning_t_NDT3 %>% drop_na(climate1, climate2, proj_height_1, live_stand_volume_125, dist_infra, vegtype2, slope, aspect_cos, elevation)

#Run Model again with this data; but uses all data here
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2, family = binomial, data = NDT3_t)

Anova(model.NDT3, type=3)
#Anova(model.NDT3, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT3), 
            residuals(model.NDT3), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT3_t$resids<-resid(model.NDT3)

binnedplot (NDT3_t$live_stand_volume_125, 
            NDT3_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT3_t$climate1, 
            NDT3_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good overall... but not perfect (especially last one)

#Partial Residuals
#climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2

visreg(model.NDT3, "climate1", by="climate2")
visreg(model.NDT3, "climate1", by="live_stand_volume_125")

visreg(model.NDT3, "climate2", by="climate1")
visreg(model.NDT3, "climate2", by="vegtype2", overlay=TRUE)
visreg(model.NDT3, "climate2", by="proj_height_1")
visreg(model.NDT3, "climate2", by="elevation")

visreg(model.NDT3, "vegtype2", by="climate2")

visreg(model.NDT3, "proj_height_1", by="climate2")
visreg(model.NDT3, "live_stand_volume_125", by="climate1")

# dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2
visreg(model.NDT3, "dist_infra")

visreg(model.NDT3, "slope", by="elevation")
visreg(model.NDT3, "aspect_cos", by="elevation")
visreg(model.NDT3, "elevation", by="slope")
visreg(model.NDT3, "elevation", by="climate2")
visreg(model.NDT3, "elevation", by="aspect_cos")

```


We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT3)

#Create a new blank table and get AUC too
top_mod_table_NDT3_light_t_ALL <- data.frame (matrix (ncol = 26, nrow = 0))
colnames (top_mod_table_NDT3_light_t_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_proj_height_1", "coef_live_stand_volume_125",  "coef_dist_infra", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_climate1:climate2", "coef_climate1:live_stand_volume_125", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_climate2:proj_height_1", "coef_slope:elevation", "aspect_cos:elevation", "climate2:elevation", "AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT3_t$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT3_t[ trainIndex,]
   Valid <- NDT3_t[-trainIndex,]
   
#Model   
model.NDT3<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT3, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3_light_t <- data.frame (matrix (ncol = 26, nrow = 0))
colnames (top_mod_table_NDT3_light_t ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_proj_height_1", "coef_live_stand_volume_125",  "coef_dist_infra", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_climate1:climate2", "coef_climate1:live_stand_volume_125", "coef_climate2:vegtype2TB", "coef_climate2:vegtype2TC", "coef_climate2:vegtype2TM", "coef_climate2:proj_height_1", "coef_slope:elevation", "aspect_cos:elevation", "climate2:elevation", "AUC")

##Add data for NDT3
top_mod_table_NDT3_light_t[1,1]<-"lightning"
top_mod_table_NDT3_light_t[1,2]<-"NDT3"
top_mod_table_NDT3_light_t[1,3]<-"Y"
top_mod_table_NDT3_light_t[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2" 
top_mod_table_NDT3_light_t[1,5]<- coef(model.NDT3)[1] #Intercept
top_mod_table_NDT3_light_t[1,6]<- coef(model.NDT3)[2] #Climate variable 1
top_mod_table_NDT3_light_t[1,7]<- coef(model.NDT3)[3] #Climate variable 2
top_mod_table_NDT3_light_t[1,8]<- coef(model.NDT3)[4] #
top_mod_table_NDT3_light_t[1,9]<- coef(model.NDT3)[5] #coefficien
top_mod_table_NDT3_light_t[1,10]<- coef(model.NDT3)[6] #coefficienC
top_mod_table_NDT3_light_t[1,11]<- coef(model.NDT3)[7] #coefficient v
top_mod_table_NDT3_light_t[1,12]<- coef(model.NDT3)[8] #coefficien
top_mod_table_NDT3_light_t[1,13]<- coef(model.NDT3)[9] #coef li
top_mod_table_NDT3_light_t[1,14]<- coef(model.NDT3)[10] #coef
top_mod_table_NDT3_light_t[1,15]<- coef(model.NDT3)[11] #coefficie
top_mod_table_NDT3_light_t[1,16]<- coef(model.NDT3)[12] #coefficien
top_mod_table_NDT3_light_t[1,17]<- coef(model.NDT3)[13] #coeffi
top_mod_table_NDT3_light_t[1,18]<- coef(model.NDT3)[14] #coeffici
top_mod_table_NDT3_light_t[1,19]<- coef(model.NDT3)[15] #coefficient 
top_mod_table_NDT3_light_t[1,20]<- coef(model.NDT3)[16] #coefficient 
top_mod_table_NDT3_light_t[1,21]<- coef(model.NDT3)[17] #coefficient
top_mod_table_NDT3_light_t[1,22]<- coef(model.NDT3)[18] #coeffici
top_mod_table_NDT3_light_t[1,23]<- coef(model.NDT3)[19] #coeff
top_mod_table_NDT3_light_t[1,24]<- coef(model.NDT3)[20] #coeff
top_mod_table_NDT3_light_t[1,25]<- coef(model.NDT3)[21] #coeffi
top_mod_table_NDT3_light_t[1,26]<- mod.auc

top_mod_table_NDT3_light_t_ALL<-rbind(top_mod_table_NDT3_light_t_ALL, top_mod_table_NDT3_light_t)

}

```

Check.
```{r}
head(top_mod_table_NDT3_light_t_ALL)
```

#Save coefficient table

```{r}
write.csv(top_mod_table_NDT3_light_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_light_t_ALL_Jan.csv")
```


Get mean values.

```{r}
names(top_mod_table_NDT3_light_t_ALL)

top_mod_table_NDT3_light_t_Means<-top_mod_table_NDT3_light_t_ALL %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table_NDT3_light_t_Means

top_mod_table_NDT3_light_t_Means[1,1]<-"lightning"
top_mod_table_NDT3_light_t_Means[1,2]<-"NDT3"
top_mod_table_NDT3_light_t_Means[1,3]<-"Treed"
top_mod_table_NDT3_light_t_Means[1,4]<- "fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2" 
top_mod_table_NDT3_light_t_Means
```

Save table.

```{r}
write.csv(top_mod_table_NDT3_light_t_Means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_light_t_Means_Jan.csv")
```

Standard deviation.

```{r}
top_mod_table_NDT3_light_t_SD<-top_mod_table_NDT3_light_t_ALL %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT3_light_t_SD

top_mod_table_NDT3_light_t_SD[1,1]<-"lightning"
top_mod_table_NDT3_light_t_SD[1,2]<-"NDT3"
top_mod_table_NDT3_light_t_SD[1,3]<-"Treed"
top_mod_table_NDT3_light_t_SD[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + climate1:climate2 + climate1:live_stand_volume_125 + climate2:vegtype2 + climate2:proj_height_1 + dist_infra + slope + aspect_cos + elevation + slope:elevation + aspect_cos:elevation + elevation:climate2" 
top_mod_table_NDT3_light_t_SD
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT3_light_t_SD, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_light_t_SD_Jan.csv")
```
