---
title: "09e_fire_ignition_model_selection_NDT5_lightning_treed"
author: "Cora Skaien"
date: "22/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)

source(here::here("R/functions/R_Postgres.R"))
```

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_lightning_t<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\data_lightning_trees_NDT.csv")
head(dat_lightning_t)

dat_lightning_nt<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\data_lightning_notrees_NDT.csv")
head(dat_lightning_nt)

dat_person_t<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\data_person_trees_NDT.csv")
head(dat_person_t)

dat_person_nt<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\data_person_notrees_NDT.csv")
head(dat_person_nt)
```

######################### ANALYSES: TREED, LIGHTNING #########################

Now, we will make a loop that does something very similar to our last loop, but with the selected climate variable plus other variables of interest. For lightning caused fires with trees, the variables of interest include:

1. Climate variable(s)
2. Projected Height (proj_height_1)
3. projected age (proj_age_1)  
4. live_stand_volume_125
5. vegtype2 (with additional categories)
6. slope
7. aspect (cos)
8. elevation
9. Various distance to infrastructure variables (dist_mun, dist_dam, dist_nat, dist_pow, dist_mine, dist_any) - no interactions
10. Some measure of death or mountain pine beetle damage -- TBD

Variables to be added after initial model selection for next round model selection:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)

Interactions of interest: two-way interactions between climate (1) and vegtype (6); two-way interactions between topography measures (7-9); interactions between VRI variables.

This will be done separately for trees and non-treed areas. 

Consider modelling by landuse type spread_data_lightning$bclcs_level_5.

First, let's do this for treed areas (with the lightning-caused fires dataset).

##We will do each loop separately for each NDT zone given the large number of possible models for each zone.

First we will create the variable lists that contain all of our variables of interest.

```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(climate1 = "climate1", climate2 = "climate2", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2", dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", dist_any = "dist_any") #heatload="heatload",

variables_all_c1<-c(climate1 = "climate1", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2", dist_mun = "dist_mun", dist_dam = "dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", dist_any = "dist_any") #heatload="heatload",

vars.clim<-c("climate1")
vars.clim.vegtype<-c("climate1", "vegtype2")
vars.clim.vegtype2<-c("climate1", "climate2","vegtype2")
vars.clim.vegtype2b<-c("climate1", "climate2")

vars.oth<-c("proj_height_1", "proj_age_1", "live_stand_volume_125") 
vars.topo<-c("slope", "aspect", "elevation")
vars.heatload<-c("heatload")
vars.infra<-c("dist_mun", "dist_dam", "dist_nat", "dist_pow", "dist_mine", "dist_any")


##Create interaction for climate and vegtype
inputs.me <- c(vars.clim.vegtype)
inputs.me2 <- c(vars.clim.vegtype2)
inputs.me2b <- c(vars.clim.vegtype2b)
```

Now, we will generate two-way interactions for each of these lists. 

```{r}

#####1a. For those with one climate variable
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints <- NULL
for (i in 1:(length(inputs.me)-1)) {
  for (j in (i+1):length(inputs.me)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me[i], inputs.me[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints)

#
#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}


#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype) 
#add climate vars to all of the above
mods.me.climate <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate


#####1b. For those with two climate variables
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2 <- NULL
for (i in 1:(length(inputs.me2)-1)) {
  for (j in (i+1):length(inputs.me2)) {
     twoway.ints2 <- cbind(twoway.ints2, paste(inputs.me2[i], inputs.me2[j], sep=":"))
  }
}
twoway.ints2
length(twoway.ints2)

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2) 
#add climate vars to all of the above
mods.me.climate2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2

#complete list of two-way interactions
mods.twoway2 <- powerSet(twoway.ints2)
length(mods.twoway2) #7
mods.twoway2

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2 <- list()
counter <- 0
for (i in 1: length(mods.twoway2)) {
   s1 <- unique(unlist( strsplit(mods.twoway2[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2)) {
      if (all(s1 %in% mods.me.climate2[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2[[j]], mods.twoway2[[i]])
        mods.inter2[[counter]] <- both
      }
   }
}

length(mods.inter2)
#mods.inter2


####1c. Two variables, no variation in vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2b <- NULL
for (i in 1:(length(inputs.me2b)-1)) {
  for (j in (i+1):length(inputs.me2b)) {
     twoway.ints2b <- cbind(twoway.ints2b, paste(inputs.me2b[i], inputs.me2b[j], sep=":"))
  }
}
twoway.ints2b
length(twoway.ints2b)

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2b) 
#add climate vars to all of the above
mods.me.climate2b <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2b[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2b

#complete list of two-way interactions
mods.twoway2b <- powerSet(twoway.ints2b)
length(mods.twoway2b) #7
mods.twoway2b

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2b <- list()
counter <- 0
for (i in 1: length(mods.twoway2b)) {
   s1 <- unique(unlist( strsplit(mods.twoway2b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2b)) {
      if (all(s1 %in% mods.me.climate2b[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2b[[j]], mods.twoway2b[[i]])
        mods.inter2b[[counter]] <- both
      }
   }
}

length(mods.inter2b)
#mods.inter2b


#########2. Now for topography data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT)

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #7
mods.twowayT

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT)
#mods.interT
mods.interTb<-c(mods.interT,vars.heatload)
#mods.interTb

####3.For other VRI data, get without interactions

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

#mods.me.oth


#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI)

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsI)
length(mods.twowayI) #32768
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI)
#mods.interI


#the list of all possible model RHSs. 
#all.poss.mods <- c(1, vars.clim, twoway.ints, mods.me.oth, mods.me2, mods.inter2)
#all.poss.mods

all.poss.mods.clim.vegtype<-c(1, mods.me.climate, twoway.ints)
all.poss.mods.clim.vegtype 
all.poss.mods.clim.vegtype<-all.poss.mods.clim.vegtype [-2] #Use this line only if there is an odd character(0) added to list
all.poss.mods.clim.vegtype2<-c(1, mods.inter2)
all.poss.mods.clim.vegtype2
all.poss.mods.clim.vegtype2<-all.poss.mods.clim.vegtype2[-2]
#all.poss.mods.clim.vegtype2<-all.poss.mods.clim.vegtype2[-9]
all.poss.mods.clim.vegtype2b<-c(1, mods.inter2b)
#all.poss.mods.clim.vegtype2b<-c(1, mods.me.climate2b, mods.inter2b)
all.poss.mods.clim.vegtype2b
all.poss.mods.clim.vegtype2b<-all.poss.mods.clim.vegtype2b[-2]
#all.poss.mods.clim.vegtype2b<-all.poss.mods.clim.vegtype2b[-5]

all.poss.mods.VRI<-c(1, mods.me.oth)
all.poss.mods.VRI
all.poss.mods.VRI<-all.poss.mods.VRI[-2]
#all.poss.mods.topo<-c(1, mods.meT, mods.interT)
all.poss.mods.topo<-c(1, mods.interT)
all.poss.mods.topo
#all.poss.mods.topo<-all.poss.mods.topo[-10]
all.poss.mods.topo<-all.poss.mods.topo[-2]
all.poss.mods.infra<-c(1, mods.meI) #I don't think we want interactions here actually...
#all.poss.mods.infra<-c(1, mods.meI, mods.interI)
all.poss.mods.infra<-all.poss.mods.infra[-2] #See if have future errors to see if need to remove

#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim.vegtype) #None duplicated
duplicated(all.poss.mods.clim.vegtype2)
duplicated(all.poss.mods.clim.vegtype2b)
duplicated(all.poss.mods.VRI)
duplicated(all.poss.mods.topo)
duplicated(all.poss.mods.infra)

```


############### Part 1 of 4 Model Series: Lightning Caused Fires, Trees ##########

Because of the large number of models with all variables included, we will test the climate and vegtype first, then the VRI variables, then the topography variables. Then we will test the top models together, with determining best AIC model from there. Or perhaps we will just combine the top models for each together, and eliminate models if the intercept was the best predictor.

Select NDT: NDT5

```{r}
zones1<-c("NDT5") #Do one zone at a time

prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

########### 1. Climate and vegtype ############
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim.vegtype2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT5")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}


```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_lightning_NDT5_treed_climate<-table.glm.climate.simple

AIC_lightning_NDT5_treed_summary_climate<- AIC_lightning_NDT5_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT5_treed_summary_climate2<- AIC_lightning_NDT5_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT5_treed_summary_climate2)
```

#Now repeat for VRI data

```{r}
########### 2. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.VRI)){
#  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$NDT<-c("NDT5")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_lightning_NDT5_treed_VRI<-table.glm.VRI.simple

AIC_lightning_NDT5_treed_summary_VRI<- AIC_lightning_NDT5_treed_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT5_treed_summary_VRI2<- AIC_lightning_NDT5_treed_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT5_treed_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 3. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$NDT<-c("NDT5")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_lightning_NDT5_treed_topo<-table.glm.topo.simple

AIC_lightning_NDT5_treed_summary_topo<- AIC_lightning_NDT5_treed_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT5_treed_summary_topo2<- AIC_lightning_NDT5_treed_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT5_treed_summary_topo2)
```

#Now repeat for infrastructure

```{r}
########### 4. Distance to Infrastructure ############
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire_pres") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT5")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_lightning_NDT5_treed_infra<-table.glm.infra.simple

AIC_lightning_NDT5_treed_summary_infra<- AIC_lightning_NDT5_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT5_treed_summary_infra2<- AIC_lightning_NDT5_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT5_treed_summary_infra2)

```

#Now combine the datatables and save to computer

```{r}
NDT5_l_models_treed<-rbind(AIC_lightning_NDT5_treed_summary_climate2, AIC_lightning_NDT5_treed_summary_VRI2, AIC_lightning_NDT5_treed_summary_topo2, AIC_lightning_NDT5_treed_summary_infra2)
NDT5_l_models_treed
NDT5_l_models_treed$NDT<-"NDT5"

write.csv(NDT5_l_models_treed, file="D:\\Fire\\fire_data\\raw_data\\NDT5_lightning_models_treed.csv")
```
