---
title: "fire_escape_data_prep"
author: "Cora Skaien"
date: "06/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#Overview
In Marchal et al. 2020, they define escape as "the probability that a fire will reach a size of at least 1 ha". We will inspect the ignition data and see the size of each fire. We will then separate them into those that are <1 ha in size, and those that are > 1 ha in size. From this, we can use logistic regression, including climate variables, topography (aspect and slope), and VRI data. Below currently only accounts for lightning caused fires. Human caused fires will be modelled down the road.

Note: Other papers use 3 ha (e.g., Wang et al. 2016, International Journal of Wildland Fire) and others use 10 ha (e.g., Parisien et al. 2013, Natural Hazards) for their definition of escape.

Must think whether or not we want VRI data. These become polygons instead of spatial points.

```{r}
#Load relevant libraries. Note, below may not all be needed for this code chunk.

library(sf)
library(tidyverse)
library(ggplot2)
library (ggcorrplot)
library (RPostgreSQL)
library (rpostgis)
library (dplyr)
library (lme4)
library (arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)

source(here::here("R/functions/R_Postgres.R"))

```

#Below are dataframes, so st_read will only return a dataframe with no geometry column
```{r}

##Data already prepped at end of ignition model file 04_vri_data_prep.Bring in data from end of this step.
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")

dat_lightning_ <- sf::st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM public.dat_lightning_for_analysis")



dbDisconnect (connKyle)

head(dat_lightning_)

##Person caused fires
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")

dat_person_ <- st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM public.dat_person_for_analysis")



dbDisconnect (connKyle)


head(dat_person_)

```

Now, select only those locations where a fire did occur. And then create a new category where if < 1 ha, then have 0, and if > 1 ha, have 1 value.

#NOTE: in below, it is determined that both lightning and person caused fires have exactly 3989 fires of size 0 hectares... this is concerning...

```{r}
dat_lightning_<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\data_lightning_Sept.csv")

```


```{r}
table(dat_lightning_$fire)

dat_lightning_escape<-subset(dat_lightning_, dat_lightning_$fire=="1")
head(dat_lightning_escape)

str(dat_lightning_escape$size_ha)
dat_lightning_escape$size_ha<-as.numeric(dat_lightning_escape$size_ha)
hist(dat_lightning_escape$size_ha) #lots of little fires
dat_lightning_escape_2<- dat_lightning_escape %>% drop_na(size_ha)
str(dat_lightning_escape_2) #15143
min(dat_lightning_escape_2$size_ha) #Size 0 is here because we have not subset by size yet
table(dat_lightning_escape_2$size_ha) #3989
max(dat_lightning_escape_2$size_ha) 
mean(dat_lightning_escape_2$size_ha) #262.2081 hectares for mean size
table(dat_lightning_escape_2$fire_cs)
hist(dat_lightning_escape_2$size_ha, n=100)

dat_lightning_escape_2$escape<- 0
dat_lightning_escape_2$escape[dat_lightning_escape_2$size_ha >= 1] <- 1

table(dat_lightning_escape_2$escape) #We have 12234 that did not escape, and 2909 that did escape. So ~23% escaped. Is this too high?


#Compare to a 3 ha threshold
dat_lightning_escape_2$escape3<- 0
dat_lightning_escape_2$escape3[dat_lightning_escape_2$size_ha >= 3] <- 1

table(dat_lightning_escape_2$escape3) #Not a huge change; ~850 difference: 13074 that did not escape and 2083 that did.

table(dat_lightning_escape_2$bclcs_level_2) 

#Compare to a 10 ha threshold
dat_lightning_escape_2$escape10<- 0
dat_lightning_escape_2$escape10[dat_lightning_escape_2$size_ha >= 10] <- 1

table(dat_lightning_escape_2$escape10) #Not a huge change; 13641 that did not escape and 1516 that did.

table(dat_lightning_escape_2$bclcs_level_2) 


```

Append wind speed to timing of fire

```{r}
dat_lightning_escape_2$wind_atfire<-0
dat_lightning_escape_2$ign_month<-as.numeric(dat_lightning_escape_2$ign_month)
head(dat_lightning_escape_2)
dat_lightning_escape_2<-dat_lightning_escape_2 %>%
    mutate(wind_atfire = case_when(ign_month == 1 ~ win_spg, #even though not quite accurate
                                  ign_month == 2 ~ win_spg, #even though not quite accurate
                                  ign_month == 3 ~ win_spg,
                                  ign_month == 4 ~ win_spg,
                                  ign_month == 5 ~ win_spg,
                                  ign_month == 6 ~ win_sum,
                                  ign_month == 7 ~ win_sum,
                                  ign_month == 8 ~ win_sum,
                                  ign_month == 9 ~ win_sum,#even though not quite accurate
                                  ign_month == 10 ~ win_sum,#even though not quite accurate
                                  ign_month == 11 ~ win_spg,#even though not quite accurate
                                  ign_month == 12 ~ win_spg,#even though not quite accurate
                                  TRUE ~ win_spg))

dat_lightning_escape_2$wind_atfire
hist(dat_lightning_escape_2$wind_atfire)

```

Inspect probability of escape by MDC

```{r}
hist(dat_lightning_escape$mdc_atfire)
str(dat_lightning_escape_2$escape)

p <- ggplot(dat_lightning_escape_2, aes(mdc_atfire, as.numeric(escape))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("MDC at fire") + ylab("Pr (ignition)")
p

p <- ggplot(dat_lightning_escape_2, aes(mdc_atfire, as.numeric(escape3))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("MDC at fire") + ylab("Pr (ignition)")
p

p <- ggplot(dat_lightning_escape_2, aes(mdc_atfire, as.numeric(escape10))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("MDC at fire") + ylab("Pr (ignition)")
p

#Of just ignition

p <- ggplot(dat_lightning_, aes(mdc_atfire, as.numeric(fire_pres))) +
  geom_smooth(method="glm", formula=y~x,
              method.args=list(family="binomial"),
              alpha=0.3, size=1) +
  geom_point(position=position_jitter(height=0.03, width=0)) +
  xlab("MDC at fire") + ylab("Pr (ignition)")
p

```

Save data on local machine.

```{r}

#st_write(dat_lightning_escape_2, dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_lightning.shp", delete_layer=TRUE)

#Loaded in as df and not a shape file
write.csv(dat_lightning_escape_2, "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_lightning.csv")

# If need to read back in, use below code, but note that because geometry was not removed, you may need to manually shift the column headings (there is a comma in the geometry cell, causing everything to shift one after the geometry statement).
#dat_lightning_escape_2<-read.csv("D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_lightning.csv")

```

Repeat for person caused fires.

```{r}
dat_person_<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\data_person_Sept.csv")
```


```{r}
table(dat_person_$fire)

dat_person_escape<-subset(dat_person_, dat_person_$fire=="1")
head(dat_person_escape)

str(dat_person_escape$size_ha)
dat_person_escape$size_ha<-as.numeric(dat_person_escape$size_ha)
hist(dat_person_escape$size_ha) #lots of little fires
dat_person_escape_2<- dat_person_escape %>% drop_na(size_ha)
str(dat_person_escape_2) #20973 obs
min(dat_person_escape_2$size_ha) #
table(dat_person_escape_2$size_ha) #3989 size 0 fires to be exact...
table(dat_person_escape_2$fire_pres) #Claims all are fire present locations...
max(dat_person_escape_2$size_ha) 
mean(dat_person_escape_2$size_ha) #24.82 hectares for mean size (1/10 the size for lightning caused average!)
table(dat_person_escape_2$fire_cs)

dat_person_escape_2$escape<- 0
dat_person_escape_2$escape[dat_person_escape_2$size_ha >= 1] <- 1

table(dat_person_escape_2$escape) #We have 18435 that did not escape, and 2538 that did escape. Is this too high?

#Compare to a 3 ha threshold
dat_person_escape_2$escape3<- 0
dat_person_escape_2$escape3[dat_person_escape_2$size_ha >= 3] <- 1

table(dat_person_escape_2$escape3) #~1000 difference: 19411 that did not escape and 1562 that did.

table(dat_person_escape_2$bclcs_level_2) 

#Because one large fire, remove
dat_person_escape_2b<-subset(dat_person_escape_2, dat_person_escape_2$size_ha<50000)
hist(dat_person_escape_2b$size_ha, n=50) 

dat_person_escape_2c<-subset(dat_person_escape_2, dat_person_escape_2$size_ha<500)
hist(dat_person_escape_2c$size_ha, n=50) 

```

Append wind speed to timing of fire

```{r}
dat_person_escape_2$wind_atfire<-0
dat_person_escape_2$ign_month<-as.numeric(dat_person_escape_2$ign_month)
head(dat_person_escape_2)
dat_person_escape_2<-dat_person_escape_2 %>%
    mutate(wind_atfire = case_when(ign_month == 1 ~ win_spg, #even though not quite accurate
                                  ign_month == 2 ~ win_spg, #even though not quite accurate
                                  ign_month == 3 ~ win_spg,
                                  ign_month == 4 ~ win_spg,
                                  ign_month == 5 ~ win_spg,
                                  ign_month == 6 ~ win_sum,
                                  ign_month == 7 ~ win_sum,
                                  ign_month == 8 ~ win_sum,
                                  ign_month == 9 ~ win_sum,#even though not quite accurate
                                  ign_month == 10 ~ win_sum,#even though not quite accurate
                                  ign_month == 11 ~ win_spg,#even though not quite accurate
                                  ign_month == 12 ~ win_spg,#even though not quite accurate
                                  TRUE ~ win_spg))

dat_person_escape_2$wind_atfire
str(dat_person_escape_2$wind_atfire)

```

Determine if all fires adequately have dates
```{r}
head(dat_person_escape_2)
names(dat_person_escape_2)
table(dat_person_escape_2$ign_month)

```

Inspect number of fires by MDC

```{r}
hist(dat_person_escape_2$mdc_atfire)
hist(dat_person_escape_2$wind_atfire)
```

Save data on local machine.

```{r}

#st_write(dat_person_escape_2, dsn = "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_person.shp", delete_layer=TRUE)

#Loaded in as df and not a shape file
write.csv(dat_person_escape_2, "D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_person.csv")

# If need to read back in, use below code, but note that because geometry was not removed, you may need to manually shift the column headings (there is a comma in the geometry cell, causing everything to shift one after the geometry statement).
#dat_person_escape_2<-read.csv("D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_person.csv")

```

Data preparations are now complete. Move on to model selection.
