---
title: "escape_climate_variable_selection"
author: "Cora Skaien"
date: "06/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#Overview
We will do the same method we did for selecting climate variables for the ignition model for the escape model. We will start by using the data that was generated at the end of 04_vri_data_prep.

```{r}
#Load relevant libraries.

library(sf)
library(tidyverse)
library(ggplot2)
library (ggcorrplot)
library (RPostgreSQL)
library (rpostgis)
library (dplyr)
library (lme4)
library (arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)

source(here::here("R/functions/R_Postgres.R"))

```

Import the data created at the end of the last file (named Escape_data_lightning_lightning and Escape_data_lightning_person)

```{r}
#Can use below if working straight from last file. Otherwise bring in from clus.
#Escape_data_lightning<-fire_veg_DEM_climate_2

#connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
#                      host = key_get('dbhost', keyring = 'postgreSQL'),
#                      user = key_get('dbuser', keyring = 'postgreSQL'),
#                      dbname = key_get('dbname', keyring = 'postgreSQL'),
#                      password = key_get('dbpass', keyring = 'postgreSQL'),
#                      port = "5432")

#Escape_data_lightning <- sf::st_read  (dsn = connKyle, # connKyle
 #                              query = "SELECT * FROM public.Escape_data_lightning")

#dbDisconnect (connKyle)
```


```{r}
Escape_data_lightning<-read.csv("D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_lightning.shp")
head(Escape_data_lightning)

#If continuing from last file (09_fire_escape_data_prep)
Escape_data_lightning<-dat_lightning_escape_2

```

Inspect the data. Make necessary changes.

```{r}
head(Escape_data_lightning)

```

Now we create variable categories for model selection on climate variables

```{r}
variables<- c("tmax05","tmax06", "tmax07", "tmax08", "tmax09", 
              "mean_tmax05_tmax06","mean_tmax06_tmax07", "mean_tmax07_tmax08", "mean_tmax08_tmax09", 
              "mean_tmax05_tmax06_tmax07", "mean_tmax06_tmax07_tmax08","mean_tmax07_tmax08_tmax09", 
              "mean_tmax05_tmax06_tmax07_tmax08", "mean_tmax06_tmax07_tmax08_tmax09", "mean_tmax05_tmax06_tmax07_tmax08_tmax09",
              
              "tave05","tave06", "tave07", "tave08", "tave09", 
              "mean_tave05_tave06","mean_tave06_tave07", "mean_tave07_tave08", "mean_tave08_tave09", 
              "mean_tave05_tave06_tave07", "mean_tave06_tave07_tave08","mean_tave07_tave08_tave09", 
              "mean_tave05_tave06_tave07_tave08", "mean_tave06_tave07_tave08_tave09", "mean_tave05_tave06_tave07_tave08_tave09",
              
              "ppt05","ppt06", "ppt07", "ppt08", "ppt09",
              "mean_ppt05_ppt06", "mean_ppt06_ppt07", "mean_ppt07_ppt08", "mean_ppt08_ppt09", 
              "mean_ppt05_ppt06_ppt07","mean_ppt06_ppt07_ppt08", "mean_ppt07_ppt08_ppt09",
              "mean_ppt05_ppt06_ppt07_ppt08", "mean_ppt06_ppt07_ppt08_ppt09",
              "mean_ppt05_ppt06_ppt07_ppt08_ppt09",
              
              "mdc_05","mdc_06", "mdc_07", "mdc_08", "mdc_09",
              "mean_mdc05_mdc06", "mean_mdc06_mdc07", "mean_mdc07_mdc08", "mean_mdc08_mdc09", 
              "mean_mdc05_mdc06_mdc07", "mean_mdc06_mdc07_mdc08", "mean_mdc07_mdc08_mdc09", 
              "mean_mdc05_mdc06_mdc07_mdc08", "mean_mdc06_mdc07_mdc08_mdc09",
              "mean_mdc05_mdc06_mdc07_mdc08_mdc09")

 variables1<-c("tmax05", "tmax06", "tmax07", "tmax08", "tmax09",
               "tave05", "tave06", "tave07", "tave08", "tave09"
#               "tmax05","tmax06", "tmax07", "tmax08", "tmax09",
#               "mdc_05", "mdc_06", "mdc_07", "mdc_08", "mdc_09"
)
variables2<-c("ppt05", "ppt06", "ppt07", "ppt08", "ppt09",
              "ppt05", "ppt06", "ppt07", "ppt08", "ppt09"
              # "mdc_05", "mdc_06", "mdc_07", "mdc_08", "mdc_09",
              # "ppt05", "ppt06", "ppt07", "ppt08", "ppt09"
) 
#
```

Inspect data and create dataframe

```{r}
table(Escape_data_lightning$fire_yr, Escape_data_lightning$escape)
table(Escape_data_lightning$fire_yr, Escape_data_lightning$escape, Escape_data_lightning$zone)

table(Escape_data_lightning$fire_yr, Escape_data_lightning$escape, Escape_data_lightning$ntrl_ds)

str(Escape_data_lightning)

```

Run the loop to determine the best climate variable for each of the five Natural Disturbance Types for lightning-caused fires.

```{r}
#################################
#### Running simple logistic regression mode: lightning-caused fires
#################################
# create loop to do variable selection of climate data
unique(Escape_data_lightning$ntrl_ds)
zones_escape<- c("NDT1", "NDT2", "NDT3", "NDT4", "NDT5")

filenames<-list()
prop<-0.75

#Begin loop
for (g in 1:100){

for (h in 1:length(zones_escape)) {
  dat2<- Escape_data_lightning %>% dplyr::filter(ntrl_ds ==zones_escape[h])
  
#Create frame of AIC table
# summary table
table.glm.climate.simple <- data.frame (matrix (ncol = 4, nrow = 0))
colnames (table.glm.climate.simple) <- c ("Zone", "Variable", "AIC", "AUC")

model_dat<- dat2 %>% dplyr::select(escape)
trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                  list = FALSE,
                                  times = 1)
dat1 <- as.data.frame(model_dat[ trainIndex,])
names(dat1)[1] <- "escape"
Valid <- as.data.frame(model_dat[-trainIndex,])
names(Valid)[1] <- "escape"


model1 <- glm (escape ~ 1 ,
               data=dat1,
               family = binomial (link = "logit"))

table.glm.climate.simple[1,1]<-zones_escape[h]
table.glm.climate.simple[1,2]<-"intercept"
table.glm.climate.simple[1,3]<-extractAIC(model1)[2]

# lets look at fit of the Valid (validation) dataset
Valid$model1_predict <- predict.glm(model1,newdata = Valid,type="response")
roc_obj <- roc(Valid$escape, Valid$model1_predict)
auc(roc_obj)
table.glm.climate.simple[1,4]<-auc(roc_obj)

rm(model_dat,dat1,Valid)

for (i in 1: length(variables)){
  print(paste((variables[i]), (zones_escape[h]), sep=" "))
  
  model_dat<- dat2 %>% dplyr::select(escape, variables[i])
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  dat1 <- model_dat[ trainIndex,]
  Valid <- model_dat[-trainIndex,]
  
  model1 <- glm (escape ~ . ,
                 data=dat1,
                 family = binomial (link = "logit"))
  
  table.glm.climate.simple[i+1,1]<-zones_escape[h]
  table.glm.climate.simple[i+1,2]<-variables[i]
  table.glm.climate.simple[i+1,3]<-extractAIC(model1)[2]
  
  # lets look at fit of the Valid (validation) dataset
  Valid$model1_predict <- predict.glm(model1,newdata = Valid,type="response")
  roc_obj <- roc(Valid$escape, Valid$model1_predict)
  auc(roc_obj)
  table.glm.climate.simple[i+1,4]<-auc(roc_obj)
  
}

# This is an addition to the table above allowing combinations of temperature and precipitation

for (i in 1: length(variables1)){
  print(paste((variables1[i]), variables2[i], (zones_escape[h]), sep=" "))
  model_dat<- dat2 %>% dplyr::select(escape, variables1[i], variables2[i])
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  dat1 <- model_dat[ trainIndex,]
  Valid <- model_dat[-trainIndex,]
  
  model2 <- glm (escape ~ . ,
                 data=dat1,
                 family = binomial (link = "logit"))
  
  table.glm.climate.simple[(i+length(variables))+1,1]<-zones_escape[h]
  table.glm.climate.simple[(i+length(variables))+1,2]<-paste0(variables1[i],"+", variables2[i])
  table.glm.climate.simple[(i+length(variables))+1,3]<-extractAIC(model2)[2]
  
  Valid$model2_predict <- predict.glm(model2,newdata = Valid,type="response")
  roc_obj <- roc(Valid$escape, Valid$model2_predict)
  auc(roc_obj)
  table.glm.climate.simple[(i+length(variables))+1,4]<-auc(roc_obj)
  
}

for (i in 1: length(variables1)){
  print(paste((variables1[i]), "x",variables2[i], (zones_escape[h]), sep=" "))

  model_dat<- dat2 %>% dplyr::select(escape, variables1[i], variables2[i])
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  dat1 <- model_dat[ trainIndex,]
  Valid <- model_dat[-trainIndex,]

  model2 <- glm (escape ~ (.)^2,
                 data=dat1,
                 family = binomial (link = "logit"))

  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),1]<-zones_escape[h]
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),2]<-paste0(variables1[i],"x", variables2[i])
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),3]<-extractAIC(model2)[2]

  Valid$model2_predict <- predict.glm(model2,newdata = Valid,type="response")
  roc_obj <- roc(Valid$escape, Valid$model2_predict)
  auc(roc_obj)
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),4]<-auc(roc_obj)

}
table.glm.climate1<-table.glm.climate.simple %>% drop_na(AIC)


#assign file names to the work
nam1<-paste("AIC",zones_escape[h],"run",g,sep="_") #defining the name
assign(nam1,table.glm.climate.simple)
filenames<-append(filenames,nam1)
}
}
##

mkFrameList <- function(nfiles) {
  d <- lapply(seq_len(nfiles),function(i) {
    eval(parse(text=filenames[i]))
  })
  do.call(rbind,d)
}

n<-length(filenames)
aic_bec_escape<-mkFrameList(n) 

aic_bec_escape_summary<- aic_bec_escape %>%
  group_by(Zone, Variable) %>%
  summarise(meanAIC=mean(AIC),
            meanAUC=mean(AUC),
            sdAUC=sd(AUC),
            )

aic_bec_escape_summary2<- aic_bec_escape_summary %>%
  group_by(Zone) %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

aic_bec_escape_summary2

```

Save files.

```{r}
#Save AIC table
write.csv(aic_bec_escape_summary2, file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_climate_AIC_results_lightning.csv")
```


```{r}
#Save csv
write.csv(Escape_data_lightningb, file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\Escape_data_lightning_df.csv")
#tried saving shape file, but could not on account of the name in the file


###
connKyle <- dbConnect(drv = RPostgreSQL::PostgreSQL(), 
                      host = key_get('dbhost', keyring = 'postgreSQL'),
                      user = key_get('dbuser', keyring = 'postgreSQL'),
                      dbname = key_get('dbname', keyring = 'postgreSQL'),
                      password = key_get('dbpass', keyring = 'postgreSQL'),
                      port = "5432")
st_write (obj = Escape_data_lightningb, 
          dsn = connKyle, 
          layer = c ("public", "Escape_data_lightning"))

dbDisconnect (connKyle)

## use this for middle code to loadback in later
Escape_data_lightningb <- sf::st_read  (dsn = connKyle, # connKyle
                               query = "SELECT * FROM public.Escape_data_lightning")



```


##Repeat for person-caused fires

```{r}
Escape_data_person<-read.csv("D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_person.shp")
head(Escape_data_person)

#If continuing from last file (09_fire_escape_data_prep)
Escape_data_person<-dat_person_escape_2

```

Inspect the data. Make necessary changes.

```{r}
head(Escape_data_person)

```

Now we create variable categories for model selection on climate variables

```{r}
variables<- c("tmax05","tmax06", "tmax07", "tmax08", "tmax09", 
              "mean_tmax05_tmax06","mean_tmax06_tmax07", "mean_tmax07_tmax08", "mean_tmax08_tmax09", 
              "mean_tmax05_tmax06_tmax07", "mean_tmax06_tmax07_tmax08","mean_tmax07_tmax08_tmax09", 
              "mean_tmax05_tmax06_tmax07_tmax08", "mean_tmax06_tmax07_tmax08_tmax09", "mean_tmax05_tmax06_tmax07_tmax08_tmax09",
              
              "tave05","tave06", "tave07", "tave08", "tave09", 
              "mean_tave05_tave06","mean_tave06_tave07", "mean_tave07_tave08", "mean_tave08_tave09", 
              "mean_tave05_tave06_tave07", "mean_tave06_tave07_tave08","mean_tave07_tave08_tave09", 
              "mean_tave05_tave06_tave07_tave08", "mean_tave06_tave07_tave08_tave09", "mean_tave05_tave06_tave07_tave08_tave09",
              
              "ppt05","ppt06", "ppt07", "ppt08", "ppt09",
              "mean_ppt05_ppt06", "mean_ppt06_ppt07", "mean_ppt07_ppt08", "mean_ppt08_ppt09", 
              "mean_ppt05_ppt06_ppt07","mean_ppt06_ppt07_ppt08", "mean_ppt07_ppt08_ppt09",
              "mean_ppt05_ppt06_ppt07_ppt08", "mean_ppt06_ppt07_ppt08_ppt09",
              "mean_ppt05_ppt06_ppt07_ppt08_ppt09",
              
              "mdc_05","mdc_06", "mdc_07", "mdc_08", "mdc_09",
              "mean_mdc05_mdc06", "mean_mdc06_mdc07", "mean_mdc07_mdc08", "mean_mdc08_mdc09", 
              "mean_mdc05_mdc06_mdc07", "mean_mdc06_mdc07_mdc08", "mean_mdc07_mdc08_mdc09", 
              "mean_mdc05_mdc06_mdc07_mdc08", "mean_mdc06_mdc07_mdc08_mdc09",
              "mean_mdc05_mdc06_mdc07_mdc08_mdc09")

 variables1<-c("tmax05", "tmax06", "tmax07", "tmax08", "tmax09",
               "tave05", "tave06", "tave07", "tave08", "tave09"
#               "tmax05","tmax06", "tmax07", "tmax08", "tmax09",
#               "mdc_05", "mdc_06", "mdc_07", "mdc_08", "mdc_09"
)
variables2<-c("ppt05", "ppt06", "ppt07", "ppt08", "ppt09",
              "ppt05", "ppt06", "ppt07", "ppt08", "ppt09"
              # "mdc_05", "mdc_06", "mdc_07", "mdc_08", "mdc_09",
              # "ppt05", "ppt06", "ppt07", "ppt08", "ppt09"
) 
#
```

Inspect data and create dataframe

```{r}
table(Escape_data_person$fire_yr, Escape_data_person$escape)
table(Escape_data_person$fire_yr, Escape_data_person$escape, Escape_data_person$zone)

table(Escape_data_person$fire_yr, Escape_data_person$escape, Escape_data_person$ntrl_ds)

str(Escape_data_person)

table(Escape_data_person$ntrl_ds)
table(Escape_data_person$ntrl_ds, Escape_data_person$escape) #Almost no escaped fires in NDT5
str(Escape_data_person$tmax05)

```

Run the loop to determine the best climate variable for each of the five Natural Disturbance Types for person-caused fires.

```{r}
#################################
#### Running simple logistic regression mode: person-caused fires
#################################
# create loop to do variable selection of climate data
unique(Escape_data_person$ntrl_ds)
zones_escape<- c("NDT1", "NDT2", "NDT3", "NDT4", "NDT5")
zones_escape<- c("NDT1", "NDT2", "NDT3", "NDT4") #Almost no fires escape in NDT5 so model cannot run for it. We will give it a percentage chance instead in final model (4/90) - 4.4%

filenames<-list()
prop<-0.75

#Begin loop
for (g in 1:100){

for (h in 1:length(zones_escape)) {
  dat2<- Escape_data_person %>% dplyr::filter(ntrl_ds ==zones_escape[h])
  
#Create frame of AIC table
# summary table
table.glm.climate.simple <- data.frame (matrix (ncol = 4, nrow = 0))
colnames (table.glm.climate.simple) <- c ("Zone", "Variable", "AIC", "AUC")

model_dat<- dat2 %>% dplyr::select(escape)
trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                  list = FALSE,
                                  times = 1)
dat1 <- as.data.frame(model_dat[ trainIndex,])
names(dat1)[1] <- "escape"
Valid <- as.data.frame(model_dat[-trainIndex,])
names(Valid)[1] <- "escape"


model1 <- glm (escape ~ 1 ,
               data=dat1,
               family = binomial (link = "logit"))

table.glm.climate.simple[1,1]<-zones_escape[h]
table.glm.climate.simple[1,2]<-"intercept"
table.glm.climate.simple[1,3]<-extractAIC(model1)[2]

# lets look at fit of the Valid (validation) dataset
Valid$model1_predict <- predict.glm(model1,newdata = Valid,type="response")
roc_obj <- roc(Valid$escape, Valid$model1_predict)
auc(roc_obj)
table.glm.climate.simple[1,4]<-auc(roc_obj)

rm(model_dat,dat1,Valid)

for (i in 1: length(variables)){
  print(paste((variables[i]), (zones_escape[h]), sep=" "))
  
  model_dat<- dat2 %>% dplyr::select(escape, variables[i])
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  dat1 <- model_dat[ trainIndex,]
  Valid <- model_dat[-trainIndex,]
  
  model1 <- glm (escape ~ . ,
                 data=dat1,
                 family = binomial (link = "logit"))
  
  table.glm.climate.simple[i+1,1]<-zones_escape[h]
  table.glm.climate.simple[i+1,2]<-variables[i]
  table.glm.climate.simple[i+1,3]<-extractAIC(model1)[2]
  
  # lets look at fit of the Valid (validation) dataset
  Valid$model1_predict <- predict.glm(model1,newdata = Valid,type="response")
  roc_obj <- roc(Valid$escape, Valid$model1_predict)
  auc(roc_obj)
  table.glm.climate.simple[i+1,4]<-auc(roc_obj)
  
}

# This is an addition to the table above allowing combinations of temperature and precipitation

for (i in 1: length(variables1)){
  print(paste((variables1[i]), variables2[i], (zones_escape[h]), sep=" "))
  model_dat<- dat2 %>% dplyr::select(escape, variables1[i], variables2[i])
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  dat1 <- model_dat[ trainIndex,]
  Valid <- model_dat[-trainIndex,]
  
  model2 <- glm (escape ~ . ,
                 data=dat1,
                 family = binomial (link = "logit"))
  
  table.glm.climate.simple[(i+length(variables))+1,1]<-zones_escape[h]
  table.glm.climate.simple[(i+length(variables))+1,2]<-paste0(variables1[i],"+", variables2[i])
  table.glm.climate.simple[(i+length(variables))+1,3]<-extractAIC(model2)[2]
  
  Valid$model2_predict <- predict.glm(model2,newdata = Valid,type="response")
  roc_obj <- roc(Valid$escape, Valid$model2_predict)
  auc(roc_obj)
  table.glm.climate.simple[(i+length(variables))+1,4]<-auc(roc_obj)
  
}

for (i in 1: length(variables1)){
  print(paste((variables1[i]), "x",variables2[i], (zones_escape[h]), sep=" "))

  model_dat<- dat2 %>% dplyr::select(escape, variables1[i], variables2[i])
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  dat1 <- model_dat[ trainIndex,]
  Valid <- model_dat[-trainIndex,]

  model2 <- glm (escape ~ (.)^2,
                 data=dat1,
                 family = binomial (link = "logit"))

  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),1]<-zones_escape[h]
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),2]<-paste0(variables1[i],"x", variables2[i])
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),3]<-extractAIC(model2)[2]

  Valid$model2_predict <- predict.glm(model2,newdata = Valid,type="response")
  roc_obj <- roc(Valid$escape, Valid$model2_predict)
  auc(roc_obj)
  table.glm.climate.simple[(i+length(variables) +length(variables1) + 1),4]<-auc(roc_obj)

}
table.glm.climate1<-table.glm.climate.simple %>% drop_na(AIC)


#assign file names to the work
nam1<-paste("AIC",zones_escape[h],"run",g,sep="_") #defining the name
assign(nam1,table.glm.climate.simple)
filenames<-append(filenames,nam1)
}
}
##

mkFrameList <- function(nfiles) {
  d <- lapply(seq_len(nfiles),function(i) {
    eval(parse(text=filenames[i]))
  })
  do.call(rbind,d)
}

n<-length(filenames)
aic_bec_escape_person<-mkFrameList(n) 

aic_bec_escape_summary_person<- aic_bec_escape_person %>%
  group_by(Zone, Variable) %>%
  summarise(meanAIC=mean(AIC),
            meanAUC=mean(AUC),
            sdAUC=sd(AUC),
            )

aic_bec_escape_summary_person2<- aic_bec_escape_summary_person %>%
  group_by(Zone) %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

aic_bec_escape_summary_person2

```

Save files.

```{r}
#Save AIC table
write.csv(aic_bec_escape_summary_person2, file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_climate_AIC_results_person.csv")
```






Create frequency distribution of the number of escaped fires per year by each BEC zone.

```{r}
table(Escape_data_lightningb$fire_yr, Escape_data_lightning$escape, Escape_data_lightning$zone)
escaped_table_BEC<-table(Escape_data_lightningb$fire_yr, Escape_data_lightning$escape, Escape_data_lightning$zone)
str(escaped_table_BEC)
#escaped_table_BEC[3]<-(escaped_table_BEC$[2]/(escaped_table_BEC$[2]+escaped_table_BEC$[1]))

##Create by month? Might be able to do with just the ignition data

```

