---
title: "11_fire_ignition_model_selection"
author: "Elizabeth Kleynhans"
date: '2022-07-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 11_fire_ignition_model_selection_FRT10_lightning_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection, using various initial models to inform the final model selection.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_lightning<- read.csv("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Data_Lightning.csv")

dat_lightning_t<- dat_lightning %>% filter(bclc__2=="T")
head(dat_lightning_t)

table(dat_lightning_t$vegtype)
table(dat_lightning_t$bclcs_level_5_2)

dat_lightning_t$vegtype_density<-paste(dat_lightning_t$vegtype, dat_lightning_t$bclcs_level_5_2,sep="_")

variables_all<-c("climate1","prj_h_1", "prj_g_1", "dm_h_bc", "vegtype", "bclcs_level_5_2", "vegtype_density") # ,

Cols <- variables_all
n <- length(Cols)
id <- unlist(lapply(1:n, function(i)combn(1:n,i,simplify=FALSE)) ,recursive=FALSE)
Formulas <- sapply(id,function(i) paste(Cols[i]))

zones1<-c("9") #,"7","9","10","11","12","13","14","15") 

prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 6, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "FRT", "run")

dat_lightning_t$fire_veg<-paste(dat_lightning_t$fire, dat_lightning_t$vegtype)

dat_lightning_t<- dat_lightning_t %>% filter(vegtype!="D")


########### 1. Climate and vegtype ############
for (g in 1:50){
    
    #for (i in 1: length(all.poss.mods.clim.vegtype2)){
    #  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
    
    for (i in 1: length(zones1)){
      dat2<- dat_lightning_t %>% dplyr::filter(frt ==zones1[i])
      # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
      model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
      # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
      trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                        list = FALSE,
                                        times = 1)
      
      dat1 <- model_dat[ trainIndex,]
      Valid <- model_dat[-trainIndex,]
      
      big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
        rhs <- paste(mods.in, collapse=" + ")
        form <- as.formula(paste(noquote(dep.var), " ~", rhs))
        mods.fit <- glm(form, family=binomial, data=df.train)
        mod.stuff <- summary(mods.fit)
        mod.aic <- extractAIC(mods.fit)
        mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
        roc_obj <- roc(df.test[,dep.var], mod.valid, quiet=TRUE)
        mod.auc <- auc(roc_obj)
        return(list(rhs, mod.stuff, mod.aic, mod.auc))
        
      }
      
      mods.fit <- lapply(Formulas, big.mod, df.train=dat1, df.test=Valid)
      
      #terms in each model
      x1.1 <- unlist(sapply(mods.fit, '[', 1))
      x1.1
      #Aic for models
      x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
      x3.1
      #auc from validation data
      x4.1 <- unlist(sapply(mods.fit, '[', 4))
      x4.1
      #combining all as df
      tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
      tab.sum.climate$FRT<-zones1[i]
      tab.sum.climate$run<-g
      tab.sum.climate 
      
      table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)
      
       print(paste0("run = ", g, "     FRT = ", zones1[i]))
      
    }
  }


head(table.glm.climate.simple)
table(table.glm.climate.simple$FRT, table.glm.climate.simple$run) # 100 per model

AIC_lightning_NDT1_t_ignitereed_climate<-table.glm.climate.simple

AIC_lightning_NDT1_t_ignitereed_summary_climate<- AIC_lightning_NDT1_t_ignitereed_climate %>%
  group_by(FRT, model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
  )

AIC_lightning_NDT1_t_ignitereed_summary_climate2<- AIC_lightning_NDT1_t_ignitereed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_t_ignitereed_summary_climate2)

AIC_lightning_NDT1_t_ignitereed_summary_climate2[order(-AIC_lightning_NDT1_t_ignitereed_summary_climate2$meanAUC), ]

write.csv(AIC_lightning_NDT1_t_ignitereed_summary_climate2, file="C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Ignition_lightning_treed_model_results\\FRT_all_lightning_models_treed.csv")

```

