---
title: "11_fire_ignition_model_selection"
author: "Elizabeth Kleynhans"
date: '2022-07-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 11_fire_ignition_model_selection_FRT10_lightning_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection, using various initial models to inform the final model selection.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_lightning<- read.csv("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\tmp\\dat_lightning_for_analysis.csv")
# to see which climate variables need to be included look at this table
climate_variables_lightning<-read.csv("C:/Work/caribou/clus_data/Fire/Fire_sim_data/data/climate_AIC_results_lightning_FRT_summary.csv")

## Create empty vector
dat_lightning$climate1<-"NA"
head(dat_lightning)

dat_lightning<-dat_lightning %>%
    mutate(climate1 = case_when(
                            frt == "5" ~ mean_Tave05_Tave06_Tave07_Tave08 ,
                            frt == "7" ~ Tave07,
                            frt == "9" ~ mean_Tave04_Tave05,
                            frt == "10" ~ mean_Tave07_Tave08_Tave09 ,
                            frt == "11" ~ mean_Tmax03_Tmax04_Tmax05_Tmax06_Tmax07_Tmax08,
                            frt == "12" ~ mean_Tmax07_Tmax08,
                            frt == "13" ~ Tave07,
                            frt == "14" ~ mean_Tave07_Tave08,
                            frt == "15" ~ mean_Tave06_Tave07_Tave08 ,
                            TRUE ~ NA_real_))

#Repeat for climate 2
dat_lightning$climate2<-"NA"

dat_lightning <- dat_lightning %>%
  mutate(climate2 = if_else(frt==5, mean_PPT05_PPT06_PPT07_PPT08,
                            if_else(frt==10, mean_PPT07_PPT08_PPT09,
                                    if_else(frt==13, as.numeric(PPT07),
                                            if_else(frt==15, mean_PPT06_PPT07_PPT08, NA_real_)))))
         

table(dat_lightning$FWI_veg)
table(dat_lightning$bclcs_level_5)

dat_lightning<- write.csv(dat_lightning, "C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\tmp\\dat_lightning_for_analysis.csv")


#dat5<-dat_lightning %>% filter(frt==5) %>%
#  dplyr::select(fire, climate1, climate2, elevatn, FWI_veg)

#tmp<-model.matrix(fire ~.^4, data=dat5)
## FOR FRT 5, 10, 13 and 15 as they had two climate variables
variables_all<-c("climate1", "climate2", "elevatn", "FWI_veg") # ,

#######################################


formulas <- list()
for (i in seq_along(variables_all)) {
  tmp <- combn(variables_all, i)
  tmp2 <- apply(tmp, 2, paste, collapse="+")
  #tmp <- paste0("Y~", tmp)
  formulas[[i]] <- tmp2
}

formulas <- unlist(formulas)

# for (i in 2) {
#   tmp <- combn(variables_all, i)
#   tmp3 <- paste0((apply(tmp, 2, paste, collapse="+")),"+",(apply(tmp, 2, paste, collapse=":")))
# }
# 
# formulas2<-append(formulas,tmp3)
# 
# for (i in 3) {
#   tmp3 <- combn(variables_all, i)
#   tmp4<-apply(tmp3, 2, paste, collapse="+")
# }
# # 3 variables with one two-way
# tmp <- combn(c("climate1","climate2", "elevatn"), 2)
# tmp5 <- paste0((tmp4[1]),"+",
#                  apply(tmp, 2, paste, collapse=":"))
# formulas3<-append(formulas2,tmp5)
# 
# tmp <- combn(c("climate1","climate2", "FWI_veg"), 2)
# tmp6 <- paste0((tmp4[2]),"+",
#                  apply(tmp, 2, paste, collapse=":"))
# formulas4<-append(formulas3,tmp6)
# 
# tmp <- combn(c("climate1","elevatn", "FWI_veg"), 2)
# tmp7 <- paste0((tmp4[3]),"+",
#                  apply(tmp, 2, paste, collapse=":"))
# formulas5<-append(formulas4,tmp7)
# 
# tmp <- combn(c("climate2","elevatn", "FWI_veg"), 2)
# tmp8 <- paste0((tmp4[4]),"+",
#                  apply(tmp, 2, paste, collapse=":"))
# formulas6<-append(formulas5,tmp8)
# 
# # three variables with two two-ways
# tmp_a <- combn(c("climate1","climate2", "elevatn"), 2)
# combinations_2way<-apply(tmp_a, 2, paste, collapse=":")
# 
# for (i in 1:length(combinations_2way)){
#   for (j in 1:length(combinations_2way)){
#     foo<- paste0(tmp4[1],"+",combinations_2way[i], "+", combinations_2way[j])
#     formulas6<-if (i!=j) {append(formulas6,foo )} else {append(formulas6,NA)}
#   }
# }
# 
# tmp_a <- combn(c("climate1","climate2", "FWI_veg"), 2)
# combinations_2way<-apply(tmp_a, 2, paste, collapse=":")
# 
# for (i in 1:length(combinations_2way)){
#   for (j in 1:length(combinations_2way)){
#     foo<- paste0(tmp4[2],"+",combinations_2way[i], "+", combinations_2way[j])
#     formulas6<-if (i!=j) {append(formulas6,foo )} else {append(formulas6,NA)}
#   }
# }
# 
# tmp_a <- combn(c("climate1","elevatn", "FWI_veg"), 2)
# combinations_2way<-apply(tmp_a, 2, paste, collapse=":")
# 
# for (i in 1:length(combinations_2way)){
#   for (j in 1:length(combinations_2way)){
#     foo<- paste0(tmp4[3],"+",combinations_2way[i], "+", combinations_2way[j])
#     formulas6<-if (i!=j) {append(formulas6,foo )} else {append(formulas6,NA)}
#   }
# }
# 
# tmp_a <- combn(c("climate2","elevatn", "FWI_veg"), 2)
# combinations_2way<-apply(tmp_a, 2, paste, collapse=":")
# 
# for (i in 1:length(combinations_2way)){
#   for (j in 1:length(combinations_2way)){
#     foo<- paste0(tmp4[3],"+",combinations_2way[i], "+", combinations_2way[j])
#     formulas6<-if (i!=j) {append(formulas6,foo )} else {append(formulas6,NA)}
#   }
# }
# 
# 
# # Get all two way combinations with all 4 variables and then stop!!
# # one 2-way interaction
# tmp3a <- combn(variables_all, 4)
# tmp_a <- combn(c("climate1","climate2", "elevatn", "FWI_veg"), 2)
# combinations_2way<-apply(tmp_a, 2, paste, collapse=":")
# 
# tmp9 <- paste0((apply(tmp3a, 2, paste, collapse="+")),"+",
#                  apply(tmp_a, 2, paste, collapse=":"))
# formulas7<-append(formulas6,tmp9)
# 
# # Two 2-way interactions
# for (i in 1:length(combinations_2way)){
#   for (j in 1:length(combinations_2way)){
#     foo<- paste0((apply(tmp3a, 2, paste, collapse="+")),"+",combinations_2way[i], "+", combinations_2way[j])
#     formulas7<-if (i!=j) {append(formulas7,foo )} else {append(formulas7,NA)}
#   }
# }
# 
# # Three 2-way interactions
# 
# for (i in 1:length(combinations_2way)){
#   for (j in 1:length(combinations_2way)){
#     for (k in 1:length(combinations_2way)){
#     foo<- paste0((apply(tmp3a, 2, paste, collapse="+")),"+",combinations_2way[i], "+", combinations_2way[j], "+", combinations_2way[k])
#     formulas7<-if (i!=j & i!=k & j!=k) {append(formulas7,foo )} else {append(formulas7,NA)}
#     }
#   }
# }
# 
# formulas8 <- unlist(formulas7)
# # remove NA values from list
# formulas9 <- formulas8[!is.na(formulas8)]
# duplicated(formulas9)

##########################


zones1<-c("5", "10", "13","15") #,"7","9","10","11","12","13","14","15") 

prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 6, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "FRT", "run")

dat_lightning$fire_veg<-paste(dat_lightning$fire, dat_lightning$FWI_veg)


########### 1. Climate and vegtype ############
for (g in 1:10){
    
    #for (i in 1: length(all.poss.mods.clim.vegtype2)){
    #  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
    
    for (i in 1: length(zones1)){
     # print(paste((formulas9[i]), (zones1[h]), sep=" --"))
      dat2<- dat_lightning %>% dplyr::filter(frt ==zones1[i])
      # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
      model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
      # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
      trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                        list = FALSE,
                                        times = 1)
      
      dat1 <- model_dat[ trainIndex,]
      Valid <- model_dat[-trainIndex,]
      
      big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
        rhs <- mods.in
        form <- as.formula(paste(noquote(dep.var), " ~", rhs))
        mods.fit <- glm(form, family=binomial, data=df.train)
        mod.stuff <- summary(mods.fit)
        mod.aic <- extractAIC(mods.fit)
        mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
        roc_obj <- roc(df.test[,dep.var], mod.valid, quiet=TRUE)
        mod.auc <- auc(roc_obj)
        return(list(rhs, mod.stuff, mod.aic, mod.auc))
        
      }
      
      mods.fit <- lapply(formulas, big.mod, df.train=dat1, df.test=Valid)
      
      #terms in each model
      x1.1 <- unlist(sapply(mods.fit, '[', 1))
      x1.1
      #Aic for models
      x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
      x3.1
      #auc from validation data
      x4.1 <- unlist(sapply(mods.fit, '[', 4))
      x4.1
      #combining all as df
      tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
      tab.sum.climate$FRT<-zones1[i]
      tab.sum.climate$run<-g
      tab.sum.climate 
      
      table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)
      
       print(paste0("run = ", g, "     FRT = ", zones1[i]))
      
    }
  }


head(table.glm.climate.simple)
table(table.glm.climate.simple$FRT, table.glm.climate.simple$run) # 100 per model

AIC_lightning_NDT1_t_ignitereed_climate<-table.glm.climate.simple

AIC_lightning_NDT1_t_ignitereed_summary_climate<- AIC_lightning_NDT1_t_ignitereed_climate %>%
  group_by(FRT, model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
  )

AIC_lightning_NDT1_t_ignitereed_summary_climate2<- AIC_lightning_NDT1_t_ignitereed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_t_ignitereed_summary_climate2)

AIC_lightning_NDT1_t_ignitereed_summary_climate2[order(-AIC_lightning_NDT1_t_ignitereed_summary_climate2$meanAUC), ]

write.csv(AIC_lightning_NDT1_t_ignitereed_summary_climate2, file="C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Ignition_lightning_results\\FRT_5_10_13_15_lightning_models.csv")

```

# for the other FRT's with only 1 climate variables
```{r}
variables_all<-c("climate1", "elevatn", "FWI_veg") # ,

#######################################


formulas <- list()
for (i in seq_along(variables_all)) {
  tmp <- combn(variables_all, i)
  tmp2 <- apply(tmp, 2, paste, collapse="+")
  #tmp <- paste0("Y~", tmp)
  formulas[[i]] <- tmp2
}

for (i in 2) {
  tmp <- combn(variables_all, i)
  tmp3 <- paste0((apply(tmp, 2, paste, collapse="+")),"+",(apply(tmp, 2, paste, collapse=":")))
}

formulas2<-append(formulas,tmp3)

for (i in 3) {
  tmp3 <- combn(variables_all, i)
  tmp4<-apply(tmp3, 2, paste, collapse="+")
}
# 3 variables with one two-way
tmp <- combn(c("climate1", "elevatn", "FWI_veg"), 2)
tmp5 <- paste0((tmp4[1]),"+",
                 apply(tmp, 2, paste, collapse=":"))
formulas3<-append(formulas2,tmp5)

# three variables with two two-ways
tmp_a <- combn(c("climate1","FWI_veg", "elevatn"), 2)
combinations_2way<-apply(tmp_a, 2, paste, collapse=":")

for (i in 1:length(combinations_2way)){
  for (j in 1:length(combinations_2way)){
    foo<- paste0(tmp4[1],"+",combinations_2way[i], "+", combinations_2way[j])
    formulas3<-if (i!=j) {append(formulas3,foo )} else {append(formulas3,NA)}
  }
}

formulas4 <- unlist(formulas3)
# remove NA values from list
formulas5 <- formulas4[!is.na(formulas4)]
duplicated(formulas5)
```

# Now run the model

```{r}
zones1<-c("7", "9", "11","12","14") #,"7","9","10","11","12","13","14","15") 

prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 6, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "FRT", "run")

dat_lightning$fire_veg<-paste(dat_lightning$fire, dat_lightning$FWI_veg)


########### 1. Climate and vegtype ############
for (g in 1:50){
    
    #for (i in 1: length(all.poss.mods.clim.vegtype2)){
    #  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
    
    for (i in 1: length(zones1)){
     # print(paste((formulas9[i]), (zones1[h]), sep=" --"))
      dat2<- dat_lightning %>% dplyr::filter(frt ==zones1[i])
      # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
      model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
      # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
      trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                        list = FALSE,
                                        times = 1)
      
      dat1 <- model_dat[ trainIndex,]
      Valid <- model_dat[-trainIndex,]
      
      big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
        rhs <- mods.in
        form <- as.formula(paste(noquote(dep.var), " ~", rhs))
        mods.fit <- glm(form, family=binomial, data=df.train)
        mod.stuff <- summary(mods.fit)
        mod.aic <- extractAIC(mods.fit)
        mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
        roc_obj <- roc(df.test[,dep.var], mod.valid, quiet=TRUE)
        mod.auc <- auc(roc_obj)
        return(list(rhs, mod.stuff, mod.aic, mod.auc))
        
      }
      
      mods.fit <- lapply(formulas5, big.mod, df.train=dat1, df.test=Valid)
      
      #terms in each model
      x1.1 <- unlist(sapply(mods.fit, '[', 1))
      x1.1
      #Aic for models
      x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
      x3.1
      #auc from validation data
      x4.1 <- unlist(sapply(mods.fit, '[', 4))
      x4.1
      #combining all as df
      tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
      tab.sum.climate$FRT<-zones1[i]
      tab.sum.climate$run<-g
      tab.sum.climate 
      
      table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)
      
       print(paste0("run = ", g, "     FRT = ", zones1[i]))
      
    }
  }


head(table.glm.climate.simple)
table(table.glm.climate.simple$FRT, table.glm.climate.simple$run) # 100 per model

AIC_lightning_NDT1_t_ignitereed_climate<-table.glm.climate.simple

AIC_lightning_NDT1_t_ignitereed_summary_climate<- AIC_lightning_NDT1_t_ignitereed_climate %>%
  group_by(FRT, model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
  )

AIC_lightning_NDT1_t_ignitereed_summary_climate2<- AIC_lightning_NDT1_t_ignitereed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_t_ignitereed_summary_climate2)

AIC_lightning_NDT1_t_ignitereed_summary_climate2[order(-AIC_lightning_NDT1_t_ignitereed_summary_climate2$meanAUC), ]

write.csv(AIC_lightning_NDT1_t_ignitereed_summary_climate2, file="C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Ignition_lightning_results\\FRT_7_9_11_12_14_lightning_models.csv")


```

