---
title: "11_fire_ignition_model_selection"
author: "Elizabeth Kleynhans"
date: '2022-07-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 11_fire_ignition_model_selection_FRT10_lightning_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection, using various initial models to inform the final model selection.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_lightning<- read.csv("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Data_Lightning.csv")

dat_lightning_t<- dat_lightning %>% filter(bclc__2=="T")
head(dat_lightning_t)

table(dat_lightning_t$vegtype)
table(dat_lightning_t$bclcs_level_5_2)

variables_all<-c("climate1","prj_h_1", "prj_g_1", "dm_h_bc", "vegtype", "bclcs_level_5_2") 

Cols <- variables_all
n <- length(Cols)
id <- unlist(lapply(1:n, function(i)combn(1:n,i,simplify=FALSE)) ,recursive=FALSE)
Formulas <- sapply(id,function(i) paste(Cols[i]))

zones1<-c("5","7","9","10","11","12","13","14","15") #Do one zone at a time

prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 6, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "FRT", "run")

dat_lightning_t$fire_veg<-paste(dat_lightning_t$fire, dat_lightning_t$vegtype)


########### 1. Climate and vegtype ############
for (g in 6:50){
    
    #for (i in 1: length(all.poss.mods.clim.vegtype2)){
    #  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
    
    for (i in 1: length(zones1)){
      dat2<- dat_lightning_t %>% dplyr::filter(frt ==zones1[i])
      # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
      model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
      # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
      trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                        list = FALSE,
                                        times = 1)
      
      dat1 <- model_dat[ trainIndex,]
      Valid <- model_dat[-trainIndex,]
      
      big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
        rhs <- paste(mods.in, collapse=" + ")
        form <- as.formula(paste(noquote(dep.var), " ~", rhs))
        mods.fit <- glm(form, family=binomial, data=df.train)
        mod.stuff <- summary(mods.fit)
        mod.aic <- extractAIC(mods.fit)
        mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
        roc_obj <- roc(df.test[,dep.var], mod.valid, quiet=TRUE)
        mod.auc <- auc(roc_obj)
        return(list(rhs, mod.stuff, mod.aic, mod.auc))
        
      }
      
      mods.fit <- lapply(Formulas, big.mod, df.train=dat1, df.test=Valid)
      
      #terms in each model
      x1.1 <- unlist(sapply(mods.fit, '[', 1))
      x1.1
      #Aic for models
      x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
      x3.1
      #auc from validation data
      x4.1 <- unlist(sapply(mods.fit, '[', 4))
      x4.1
      #combining all as df
      tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
      tab.sum.climate$FRT<-zones1[i]
      tab.sum.climate$run<-g
      tab.sum.climate 
      
      table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)
      
       print(paste0("run = ", g, "     FRT = ", zones1[i]))
      
    }
  }


head(table.glm.climate.simple)
table(table.glm.climate.simple$FRT, table.glm.climate.simple$run) # 100 per model

AIC_lightning_NDT1_t_ignitereed_climate<-table.glm.climate.simple

AIC_lightning_NDT1_t_ignitereed_summary_climate<- AIC_lightning_NDT1_t_ignitereed_climate %>%
  group_by(FRT, model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
  )

AIC_lightning_NDT1_t_ignitereed_summary_climate2<- AIC_lightning_NDT1_t_ignitereed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT1_t_ignitereed_summary_climate2)

write.csv(AIC_lightning_NDT1_t_ignitereed_summary_climate2, file="C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Ignition_lightning_treed_model_results\\FRT_all_lightning_models_treed.csv")

```

Now open up the table of the top models
```{r, AIC table, echo = F, message = F, eval = T}

Top_mod_set_lightning_treed<-read.csv("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Ignition_lightning_treed_model_results\\FRT_all_lightning_models_treed_top_set.csv")

head(Top_mod_set_lightning_treed) 

kable (Top_mod_set_lightning_treed,
       caption = "<b>Table 1. Top candidate variables for lightning caused fires as selected through an AIC analysis for each Fire Regime Type.<b>",
       digits = 2) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)

```

#Checking model fits for FRT 5
Climate 1 = mean PPT05 to PPT07
```{r}
dat<- dat_lightning_t %>% dplyr::select(fire_yr, ig_mnth, frt, fire, dm_h_bc, climate1, prj_h_1, prj_g_1, vegtype, bclcs_level_5_2)

dat2<- dat %>% dplyr::filter(frt == 5) %>% drop_na(prj_h_1)
dat2$logClimate1<-log(dat2$climate1)
dat2$logprj_h<-log(dat2$prj_h_1)
dat2$logelev<-log(dat2$dm_h_bc)
dat2$prj_g_1<-as.numeric(dat2$prj_g_1)

mod.frt.5<-glm(fire ~ climate1 + prj_h_1 + prj_g_1 + dm_h_bc + vegtype + bclcs_level_5_2, data=dat2, family=binomial(link="logit"))

library(caret)
varImp(mod.frt.5)
library(GmAMisc)
modelvalid(dat2, mod.frt.5)

summary(mod.frt.5)
anova(mod.frt.5)
Anova(mod.frt.5, type=3)

# model diagnostic plots
binnedplot (fitted(mod.frt.5), 
            residuals(mod.frt.5), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))


dat2$resids<-resid(mod.frt.5)

binnedplot (log(dat2$prj_h_1), 
            dat2$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (log(dat2$climate), 
            dat2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (dat2$prj_g_1, 
            dat2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (log(dat2$dm_h_bc), 
            dat2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

# Diagnostic plots look good

##Partial Residuals
visreg(mod.frt.5, scale="response") # nicer plots than the ones below!

visreg(mod.frt.5, "logClimate1")
visreg(mod.frt.5, "prj_g_1")
visreg(mod.frt.5, "logprj_h")
visreg(mod.frt.5, "logelev")
visreg(mod.frt.5, "vegtype")
visreg(mod.frt.5, "bclcs_level_5_2")


visreg(mod.frt.5, "logClimate1", by="prj_g_1")
visreg(mod.frt.5, "logClimate1", by="logprj_h")
visreg(mod.frt.5, "logClimate1", by="logelev")
visreg(mod.frt.5, "logClimate1", by="vegtype")
visreg(mod.frt.5, "logClimate1", by="bclcs_level_5_2")

visreg(mod.frt.5, "logprj_h", by="prj_g_1")
visreg(mod.frt.5, "logprj_h", by="logelev")
visreg(mod.frt.5, "logprj_h", by="vegtype")
visreg(mod.frt.5, "logprj_h", by="bclcs_level_5_2")

visreg(mod.frt.5, "prj_g_1", by="logelev")
visreg(mod.frt.5, "prj_g_1", by="vegtype")
visreg(mod.frt.5, "prj_g_1", by="bclcs_level_5_2")

visreg(mod.frt.5, "logprj_h", by="vegtype", overlay=TRUE)



#dist_mun + dist_dam + dist_nat + dist_mine + bclcs_level_5_2 + dist_mun:bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + dist_mine:bclcs_level_5_2

visreg(model.NDT1, "dist_mun", by="bclcs_level_5_2", overlay=TRUE) #look into these extreme points
visreg(model.NDT1, "dist_dam")
visreg(model.NDT1, "dist_nat", by="bclcs_level_5_2", overlay=TRUE)
visreg(model.NDT1, "dist_mine")

visreg(model.NDT1, "bclcs_level_5_2", by="dist_nat")
visreg(model.NDT1, "bclcs_level_5_2", by="dist_mun")



```


# checking assumption of linearity (http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/)

# all variables should be approximatly linear which is mostly true except for maybe prj_h_1
```{r}


# Select only numeric predictors
str(dat2)

dat2_b<-dat2 %>% dplyr::select(fire:prj_g_1 )
probabilities <- predict(mod.frt.5, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")


mydata <- dat2_b %>%
  dplyr::select_if(is.numeric) 
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")
```

Checking assumption of influential values
see: (http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/)
```{r}
plot(mod.frt.5, which = 4, id.n = 3)
```

