---
title: "FRT_13"
author: "Elizabeth Kleynhans"
date: '2022-07-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 21_fire_ignition_model_selection_FRT5_lightning_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection, using various initial models to inform the final model selection.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_lightning<- read.csv("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\tmp\\dat_lightning_for_analysis.csv")

```

```{r}
dat_lightning$climate1<-"NA"
head(dat_lightning)

# dat_lightning <- dat_lightning3 %>%
#   mutate(climate1 = if_else(frt==3, mean_MDC05_MDC06,
#                     if_else(frt==5, mean_PPT05_PPT06_PPT07, 
#                     if_else(frt==7, mean_RH05_RH06_RH07,
#                     if_else(frt==9, PPT09,
#                     if_else(frt==10, Tave07, 
#                     if_else(frt==11, Tave08,
#                     if_else(frt==12, mean_Tmax07_Tmax08,
#                     if_else(frt==13, mean_Tave07_Tave08,
#                     if_else(frt==14, Tmax08,
#                     if_else(frt==15, mean_RH07_RH08, climate1)))))))))))
# make sure value are numbers otherwise it seems to not work.
#dat_lightning$PPT09<-as.numeric(dat_lightning$PPT09)
dat_lightning<-dat_lightning %>%
    mutate(climate1 = case_when(
                            frt == "5" ~ mean_Tave05_Tave06_Tave07_Tave08 ,
                            frt == "7" ~ mean_RH05_RH06_RH07,
                            frt == "9" ~ Tmax05,
                            frt == "10" ~ mean_Tave07_Tave08_Tave09 ,
                            frt == "11" ~ mean_Tmax07_Tmax08_Tmax09,
                            frt == "12" ~ mean_Tmax07_Tmax08,
                            frt == "13" ~ Tave07,
                            frt == "14" ~ mean_Tave07_Tave08,
                            frt == "15" ~ mean_Tave06_Tave07_Tave08 ,
                            TRUE ~ NA_real_))

#Repeat for climate 2
dat_lightning$climate2<-"NA"
# # 

dat_lightning <- dat_lightning %>%
  mutate(climate2 = if_else(frt==5, mean_PPT05_PPT06_PPT07_PPT08,
                            if_else(frt==10, mean_PPT07_PPT08_PPT09,
                                    if_else(frt==11, mean_PPT07_PPT08_PPT09,
                                    if_else(frt==13, as.numeric(PPT07),
                                            if_else(frt==15, mean_PPT06_PPT07_PPT08, NA_real_))))))
   
```

#Checking model fits 
```{r}
dat<- dat_lightning %>% dplyr::select(fire_yr, ig_mnth, frt, fire, elevatn, climate1,climate2, FWI_veg)

table(dat$frt, dat$FWI_veg, dat$fire)

dat13<- dat %>% dplyr::filter(frt == 13) 
table(dat13$FWI_veg)

dat13<-dat13 %>% filter(FWI_veg!="W")
# there are only 6 observations in the C1 fuel type so since this fiel type has fire spread rates similar to C3 I will change all C1 observations to C3
# dat12$FWI_veg[dat12$FWI_veg=="C-1"]<-"C-3"
# # apparently C-4 is very similar to C-2 so Ill also change all C-4's to C'-2's. I read this in Perakkis 
dat13$FWI_veg[dat13$FWI_veg=="C-4"]<-"C-2"
## changing M-3 to M-1/2 because there are only 6 occurences of M-3 so its hard to run a model on this.
dat13$FWI_veg[dat13$FWI_veg=="M-3"]<-"O-1a/b"
table(dat13$FWI_veg)

# nice alternative figure but cant add a map or Im not sure how to.
library(popbio)
logi.hist.plot(dat13$climate1,dat13$fire,boxp=FALSE,type="hist",col="gray")
logi.hist.plot(dat13$elevatn,dat13$fire,boxp=FALSE,type="hist",col="gray")


ggplot(data=dat13, mapping=aes(x=as.factor(fire), y=climate1))+
  geom_boxplot()

ggplot(data=dat13, mapping=aes(x=as.factor(fire), y=climate2))+
  geom_boxplot()

ggplot(data=dat13, mapping=aes(x=as.factor(fire), y=elevatn))+
  geom_boxplot()

table(is.na(dat13$fire))
mod.frt.13<-glm(fire ~ climate1 +climate2 + FWI_veg + elevatn, data=dat13, family=binomial(link="logit"))

# looking at difference in link function
modclim_logit<-glm(fire ~ climate1, data=dat13, family=binomial(link="logit"))
modclim_cloglog<-glm(fire ~ climate1, data=dat13, family=binomial(link="cloglog"))

summary(dat13)
mydata<-data.frame(climate1=seq(from=7, to=25, by=0.5))
# logit and probit assume that you have even numbers of 0's and 1's
# cloglog is apparently better a good option if you have considerably more zeros than ones or vice versa.
Pred_logit<-predict(modclim_logit, newdata=mydata, type="response")
Pred_cloglog<-predict(modclim_cloglog, newdata=mydata, type="response")

plot(x=dat13$climate1, y=dat13$fire)
lines(mydata$climate1, Pred_logit, col="red")
lines(mydata$climate1, Pred_cloglog, col="blue")

dat13$FWI_veg<- as.factor(dat13$FWI_veg)


mod.frt.13<-glm(fire ~ climate1 +climate2 + FWI_veg + elevatn, data=dat13, family=binomial(link="logit"))
cor(model.matrix(mod.frt.13)[,-1])

hist(dat13$climate1)
hist(dat13$climate2)
hist(dat13$elevatn)
summary(mod.frt.13)

Anova(mod.frt.13, type=3)

mod.frt.13b<-glm(fire ~ climate1 + FWI_veg + elevatn, data=dat13, family=binomial(link="logit"))
anova(mod.frt.13, mod.frt.13b, test="Chisq")

mod.frt.13<-glm(fire ~ climate1 + FWI_veg + elevatn, data=dat13, family=binomial(link="logit"))

# model diagnostic plots
binnedplot (fitted(mod.frt.13), 
            residuals(mod.frt.13), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))


dat13$resids<-resid(mod.frt.13)

binnedplot (dat13$climate1, 
            dat13$resids, 
            nclass = NULL, 
            xlab = "climate1", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (dat13$elevatn, 
            dat13$resids, 
            nclass = NULL, 
            xlab = "elevation", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (dat13$climate2, 
            dat13$resids, 
            nclass = NULL, 
            xlab = "climate2", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

cor.test(dat13$climate1, dat13$elevatn)



##Partial Residuals
visreg(mod.frt.13, scale="response") # nicer plots than the ones below!

visreg(mod.frt.13, "climate1", by="elevatn", scale="response")
visreg(mod.frt.13, "climate1", by="climate2", scale="response")
visreg(mod.frt.13, "climate1", by="FWI_veg", scale="response")
visreg(mod.frt.13, "elevatn", by="FWI_veg", scale="response")
visreg(mod.frt.13, "elevatn", by="climate2", scale="response")
visreg(mod.frt.13, "climate2", by="FWI_veg", scale="response")
visreg(mod.frt.13, "climate1", by="FWI_veg", overlay=TRUE, scale="response")
visreg(mod.frt.13, "climate1", by="elevatn", overlay=TRUE, scale="response")

```
## checking assumptions of a logistic regression following methods outlined in  http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

First checking assumption of linearity
```{r}
#Here, we’ll check the linear relationship between continuous predictor variables and the logit of the outcome. This can be done by visually inspecting the scatter plot between each predictor and the logit values.

#Remove qualitative variables from the original data frame and bind the logit values to the data:

# Select only numeric predictors
str(dat13)


dat2_b<-dat13%>% dplyr::select(fire, elevatn, climate1, climate2)
probabilities <- predict(mod.frt.13, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

mydata <- dat2_b %>%
  dplyr::select_if(is.numeric) 
predictors <- colnames(mydata)

# Bind the logit and tidying the data for plot
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")

# all variables should be approximatly linear which is mostly true
```

Checking assumption of influential values
see: (http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/)
```{r}
#Influential values are extreme individual data points that can alter the quality of the logistic regression model.
#The most extreme values in the data can be examined by visualizing the Cook’s distance values. Here we label the top 3 largest values:

plot(mod.frt.13, which = 6, id.n = 3)

#Note that, not all outliers are influential observations. To check whether the data contains potential influential observations, the standardized residual error can be inspected. Data points with an absolute standardized residuals above 3 represent possible outliers and may deserve closer attention.

#The following R code computes the standardized residuals (.std.resid) and the Cook’s distance (.cooksd) using the R function augment() [broom package].

# Extract model results
library(broom)
model.data <- augment(mod.frt.13) %>% 
  mutate(index = 1:n()) 

#The data for the top 3 largest values, according to the Cook’s distance, can be displayed as follow:
model.data %>% 
  dplyr::select(climate1,  elevatn, FWI_veg,.std.resid, .cooksd) %>%
  top_n(5, .cooksd) 

ggplot(model.data, aes(index, .std.resid)) + 
  geom_point(aes(color = fire), alpha = .5) +
  theme_bw()

#Filter potential influential data points with abs(.std.res) > 3:

model.data %>% 
  filter(abs(.std.resid) > 3) # there are no data points with a standardized residual of greater than 3. So we are all good

```

# checking assumption of no multicollinearity

```{r}
#Multicollinearity corresponds to a situation where the data contain highly correlated predictor variables. Read more in Chapter @ref(multicollinearity).

#Multicollinearity is an important issue in regression analysis and should be fixed by removing the concerned variables. It can be assessed using the R function vif() [car package], which computes the variance inflation factors:

car::vif(mod.frt.13)

#As a rule of thumb, a VIF value that exceeds 5 or 10 indicates a problematic amount of collinearity. 
```


```{r}
summary(mod.frt.13)

#Create a new blank table and get AUC too
top_mod_table_FRT13_lightningALL <- data.frame (matrix (ncol = 18, nrow = 0))
colnames (top_mod_table_FRT13_lightningALL ) <- c ("CAUSE", "FRT",  "Model_terms", "intercept",
                                                   "coef_climate_1", 
                                                   "coef_climate2", 
                                                   "coef_FWI_veg_C-3",  
                                                   "coef_FWI_veg_C-5",  
                                                   "coef_FWI_veg_C-7", 
                                                   "coef_FWI_veg_D-1/2", 
                                                   "coef_FWI_veg_M-1/2", 
                                                   "coef_FWI_veg_N", 
                                                   "coef_FWI_veg_O-1a/b", 
                                                   "coef_FWI_veg_S-1", 
                                                   "coef_FWI_veg_S-2",  
                                                   "coef_FWI_veg_S-3",
                                                   "coef_elevatn", 
                                                   "AUC")

dat13$fire_veg<-paste(dat13$fire, dat13$FWI_veg)
```

Let's run it 100 times to get good mean values.

```{r}

for (g in 1:100){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(dat13$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- dat13[ trainIndex,]
   Valid <- dat13[-trainIndex,]
   
#Model   
mod<-glm(fire ~ climate1 + climate2 + FWI_veg + elevatn, data=dat1, family=binomial(link="logit"))

mod.valid <- predict.glm(mod, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT13_lightningL <- data.frame (matrix (ncol = 18, nrow = 0))
colnames (top_mod_table_FRT13_lightningL ) <- c ("CAUSE", "FRT",  "Model_terms", "intercept",
                                                 "coef_climate_1", 
                                                 "coef_climate2", 
                                                 "coef_FWI_veg_C-3",  
                                                 "coef_FWI_veg_C-5",  
                                                 "coef_FWI_veg_C-7", 
                                                 "coef_FWI_veg_D-1/2", 
                                                 "coef_FWI_veg_M-1/2",
                                                 "coef_FWI_veg_N",
                                                 "coef_FWI_veg_O-1a/b", 
                                                 "coef_FWI_veg_S-1", 
                                                 "coef_FWI_veg_S-2", 
                                                 "coef_FWI_veg_S-3",
                                                 "coef_elevatn", "AUC")

##Add data for NDT1
top_mod_table_FRT13_lightningL[1,1]<-"lightning"
top_mod_table_FRT13_lightningL[1,2]<-"FRT13"
top_mod_table_FRT13_lightningL[1,3]<-"fire ~ climate1 + climate2 + FWI_veg + elevatn"
top_mod_table_FRT13_lightningL[1,4]<- coef(mod)[1] #Intercept
top_mod_table_FRT13_lightningL[1,5]<- coef(mod)[2] #Climate variable 1
top_mod_table_FRT13_lightningL[1,6]<- coef(mod)[3] #Climate variable 2
top_mod_table_FRT13_lightningL[1,7]<- coef(mod)[4] #I
top_mod_table_FRT13_lightningL[1,8]<- coef(mod)[5] #co
top_mod_table_FRT13_lightningL[1,9]<- coef(mod)[6] #coe
top_mod_table_FRT13_lightningL[1,10]<- coef(mod)[7] #c
top_mod_table_FRT13_lightningL[1,11]<- coef(mod)[8] #
top_mod_table_FRT13_lightningL[1,12]<- coef(mod)[9] #
top_mod_table_FRT13_lightningL[1,13]<- coef(mod)[10] #pr
top_mod_table_FRT13_lightningL[1,14]<- coef(mod)[11] #coeffic
top_mod_table_FRT13_lightningL[1,15]<- coef(mod)[12]
top_mod_table_FRT13_lightningL[1,16]<- coef(mod)[13]
top_mod_table_FRT13_lightningL[1,17]<- coef(mod)[14]
top_mod_table_FRT13_lightningL[1,18]<- mod.auc

top_mod_table_FRT13_lightningALL<-rbind(top_mod_table_FRT13_lightningALL, top_mod_table_FRT13_lightningL)

}

```

Check.
```{r}
head(top_mod_table_FRT13_lightningALL)
top_mod_table_FRT13_lightningALL

```

#Save coefficient table

```{r}
write.csv(top_mod_table_FRT13_lightningALL, file="D:\\Fire\\fire_data\\raw_data\\Ignition Models\\Ignition_Model_Results_Lightning_Treed\\top_mod_table_FRT5_light_tree_all.csv")
```

Get mean values.

```{r}
names(top_mod_table_FRT13_lightningALL)
str(top_mod_table_FRT13_lightningALL)
stderror <- function(x) sd(x)/sqrt(length(x))

FRT13_summary_table_mean<- top_mod_table_FRT13_lightningALL %>% summarize_if(is.numeric,mean)

FRT13_summary_table_mean$Cause<-"Lightning"
FRT13_summary_table_mean$FRT<-13
FRT13_summary_table_mean$Model_terms<-"fire ~ climate1 + climate2 + FWI_veg + elevatn"


```

Save table.

```{r}
write.csv(FRT13_summary_table_mean, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT13_lightning.csv")
```

Standard deviation.

```{r}
top_mod_table_FRT12_lightningALL_sd<-top_mod_table_FRT12_lightningALL %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT1_light_t_SD

top_mod_table_NDT1_light_t_SD[1,1]<-"lightning"
top_mod_table_NDT1_light_t_SD[1,2]<-"NDT1"
top_mod_table_NDT1_light_t_SD[1,3]<-"Treed"
top_mod_table_NDT1_light_t_SD[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + proj_age_1 + climate1:climate2 + climate1:proj_height_1 + climate1:proj_age_1  + climate2:proj_age_1  + proj_height_1:proj_age_1 + dist_mun + dist_dam + dist_nat + dist_mine + bclcs_level_5_2 + dist_mun:bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + dist_mine:bclcs_level_5_2 + slope + aspect_cos + elevation" 
top_mod_table_NDT1_light_t_SD
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT1_light_t_SD, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT13_lightning.csv")
```
