---
title: "FRT_5"
author: "Elizabeth Kleynhans"
date: '2022-07-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 21_fire_ignition_model_selection_FRT5_lightning_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection, using various initial models to inform the final model selection.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_lightning<- read.csv("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\tmp\\dat_lightning_for_analysis.csv")

```


#Checking model fits 
```{r}
dat<- dat_lightning %>% dplyr::select(fire_yr, ig_mnth, frt, fire, elevatn, climate1,climate2, FWI_veg)

table(dat$frt, dat$FWI_veg)

dat12<- dat %>% dplyr::filter(frt == 12) 
table(dat12$FWI_veg)

ggplot(data=dat12, mapping=aes(x=as.factor(fire), y=climate1))+
  geom_boxplot()

ggplot(data=dat12, mapping=aes(x=as.factor(fire), y=elevatn))+
  geom_boxplot()


mod.frt.12<-glm(fire ~ climate1 + FWI_veg + elevatn, data=dat12, family=binomial(link="logit"))

# looking at difference in link function
modclim_logit<-glm(fire ~ climate1, data=dat12, family=binomial(link="logit"))
modclim_cloglog<-glm(fire ~ climate1, data=dat12, family=binomial(link="cloglog"))

mydata<-data.frame(climate1=seq(from=14, to=28, by=0.5))
# logit and probit assume that you have even numbers of 0's and 1's
# cloglog is apparently better a good option if you have considerably more zeros than ones or vice versa.
Pred_logit<-predict(modclim_logit, newdata=mydata, type="response")
Pred_cloglog<-predict(modclim_cloglog, newdata=mydata, type="response")

plot(x=dat12$climate1, y=dat12$fire)
lines(mydata$climate1, Pred_logit, col="red")
lines(mydata$climate1, Pred_cloglog, col="blue")

dat12$FWI_veg<- as.factor(dat12$FWI_veg)


mod.frt.12<-glm(fire ~ climate1 + FWI_veg + elevatn, data=dat12, family=binomial(link="logit"))


summary(mod.frt.12)

Anova(mod.frt.12, type=3)

library(caret)
varImp(mod.frt.12)
library(GmAMisc)
modelvalid(dat12, mod.frt.12)

# model diagnostic plots
binnedplot (fitted(mod.frt.12), 
            residuals(mod.frt.12), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))


dat12$resids<-resid(mod.frt.12)

binnedplot (dat12$climate1, 
            dat12$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (dat12$elevatn, 
            dat12$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))




##Partial Residuals
visreg(mod.frt.12, scale="response") # nicer plots than the ones below!

visreg(mod.frt.12, "climate1", by="elevatn", scale="response")
visreg(mod.frt.12, "climate1", by="FWI_veg", scale="response")
visreg(mod.frt.12, "elevatn", by="FWI_veg", scale="response") #I wonder if there is an interaction with elevation?

visreg(mod.frt.12, "climate1", by="FWI_veg", overlay=TRUE, scale="response")
visreg(mod.frt.12, "climate1", by="elevatn", overlay=TRUE, scale="response")

```
## checking assumptions of a logistic regression following methods outlined in  http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

First checking assumption of linearity
```{r}
#Here, we’ll check the linear relationship between continuous predictor variables and the logit of the outcome. This can be done by visually inspecting the scatter plot between each predictor and the logit values.

#Remove qualitative variables from the original data frame and bind the logit values to the data:

# Select only numeric predictors
str(dat2)

dat2_b<-dat2 %>% dplyr::select(fire:prj_g_1 )
probabilities <- predict(mod.frt.5, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

mydata <- dat2_b %>%
  dplyr::select_if(is.numeric) 
predictors <- colnames(mydata)

# Bind the logit and tidying the data for plot
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")

# all variables should be approximatly linear which is mostly true except for prj_h_1. Im going to try to log transform prj_h_1 (ok this did not work). Im going to try including height^2 and if that does not help also height^3. Note that q, I(q^2) and I(q^3) will be correlated and correlated variables can cause problems. The use of poly() lets you avoid this by producing orthogonal polynomials, therefore I’m going to use poly().
mod.frt.5_1<-glm(fire ~ climate1 + prj_h_1 + prj_g_1 + dm_h_bc + vegtype_density , data=dat2, family=binomial(link="logit"))
mod.frt.5_2<-glm(fire ~ climate1 + poly(prj_h_1,2) + prj_g_1 + dm_h_bc + vegtype_density , data=dat2, family=binomial(link="logit"))
mod.frt.5_3<-glm(fire ~ climate1 + poly(prj_h_1,3) + prj_g_1 + dm_h_bc + vegtype_density , data=dat2, family=binomial(link="logit"))
mod.frt.5_4<-glm(fire ~ climate1 + poly(prj_h_1,4) + prj_g_1 + dm_h_bc + vegtype_density , data=dat2, family=binomial(link="logit"))
anova(mod.frt.5_1, mod.frt.5_2, mod.frt.5_3, mod.frt.5_4,  test="Chisq")
print(coef(summary(mod.frt.5_4)))

summary(mod.frt.5)

dat2_b<-dat2 %>% dplyr::select(fire:prj_g_1)
probabilities <- predict(mod.frt.5_2, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")


mydata <- dat2_b %>%
  dplyr::select_if(is.numeric) 
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot
mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")

```

Checking assumption of influential values
see: (http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/)
```{r}
#Influential values are extreme individual data points that can alter the quality of the logistic regression model.
#The most extreme values in the data can be examined by visualizing the Cook’s distance values. Here we label the top 3 largest values:

plot(mod.frt.5, which = 4, id.n = 3)

#Note that, not all outliers are influential observations. To check whether the data contains potential influential observations, the standardized residual error can be inspected. Data points with an absolute standardized residuals above 3 represent possible outliers and may deserve closer attention.

#The following R code computes the standardized residuals (.std.resid) and the Cook’s distance (.cooksd) using the R function augment() [broom package].

# Extract model results
library(broom)
model.data <- augment(mod.frt.5_2) %>% 
  mutate(index = 1:n()) 

#The data for the top 3 largest values, according to the Cook’s distance, can be displayed as follow:
model.data %>% 
  dplyr::select(climate1,  prj_g_1, dm_h_bc, vegtype_density, .std.resid, .cooksd) %>%
  top_n(5, .cooksd) 

ggplot(model.data, aes(index, .std.resid)) + 
  geom_point(aes(color = fire), alpha = .5) +
  theme_bw()

#Filter potential influential data points with abs(.std.res) > 3:

model.data %>% 
  filter(abs(.std.resid) > 3) # there are no data points with a standardized residual of greater than 3. So we are all good

```

# checking assumption of no multicollinearity

```{r}
#Multicollinearity corresponds to a situation where the data contain highly correlated predictor variables. Read more in Chapter @ref(multicollinearity).

#Multicollinearity is an important issue in regression analysis and should be fixed by removing the concerned variables. It can be assessed using the R function vif() [car package], which computes the variance inflation factors:

car::vif(mod.frt.5_2)

#As a rule of thumb, a VIF value that exceeds 5 or 10 indicates a problematic amount of collinearity. 
```


#Checking model fits for FRT 5
Climate 1 = mean PPT05 to PPT07
```{r}
mod.frt.5_2<-glm(fire ~ climate1 + poly(prj_h_1,2) + prj_g_1 + dm_h_bc + vegtype_density + climate1:vegtype_density + bclcs_level_5_2, data=dat2, family=binomial(link="logit"))

mod.frt.5_3<-glm(fire ~ climate1 + poly(prj_h_1,2) + prj_g_1 + dm_h_bc + vegtype_density + bclcs_level_5_2, data=dat2, family=binomial(link="logit"))

anova(mod.frt.5_2, mod.frt.5_3, test="Chisq")
# ok remove interaction its close but not significant

mod.frt.5_4<-glm(fire ~ climate1 + poly(prj_h_1,2) + dm_h_bc + vegtype_density, data=dat2, family=binomial(link="logit"))
anova(mod.frt.5_3, mod.frt.5_4, test="Chisq") # dont remove age

mod.frt.5_5<-glm(fire ~ climate1 + poly(prj_h_1,2) + prj_g_1 + dm_h_bc + vegtype_density + vegtype_density:prj_h_1, data=dat2, family=binomial(link="logit"))
anova(mod.frt.5_5, mod.frt.5_3, test="Chisq") # dont worry about prj_h_1:vegtype_density

###################################################
#### TOP FINAL MODEL
###################################################
mod.frt.5_final<-glm(fire ~ climate1 + poly(prj_h_1,2) + prj_g_1 + dm_h_bc + vegtype_density, data=dat2, family=binomial(link="logit"))

varImp(mod.frt.5_final)
modelvalid(dat2, mod.frt.5_final)

summary(mod.frt.5_final)
Anova(mod.frt.5_final, type=3)


### Results of summary
# Call:
# glm(formula = fire ~ climate1 + poly(prj_h_1, 2) + prj_g_1 + 
#     dm_h_bc + vegtype_density, family = binomial(link = "logit"), 
#     data = dat2)
# 
# Deviance Residuals: 
#     Min       1Q   Median       3Q      Max  
# -1.2862  -0.6752  -0.5055  -0.3210   2.8179  
# 
# Coefficients:
#                        Estimate Std. Error z value         Pr(>|z|)    
# (Intercept)          -0.8831838  0.3077082  -2.870         0.004102 ** 
# climate1             -0.0175538  0.0025096  -6.995 0.00000000000266 ***
# poly(prj_h_1, 2)1    -7.6348987  3.8684872  -1.974         0.048426 *  
# poly(prj_h_1, 2)2    12.5187821  2.8487249   4.395 0.00001110171502 ***
# prj_g_1               0.0033633  0.0011804   2.849         0.004382 ** 
# dm_h_bc              -0.0017613  0.0002476  -7.112 0.00000000000114 ***
# vegtype_densityTB_OP  0.2570280  0.2926774   0.878         0.379838    
# vegtype_densityTB_SP  0.4094688  0.5745363   0.713         0.476035    
# vegtype_densityTC_DE  1.4650751  0.2678399   5.470 0.00000004501220 ***
# vegtype_densityTC_OP  1.4500942  0.2493079   5.816 0.00000000601004 ***
# vegtype_densityTC_SP  1.0757843  0.2696845   3.989 0.00006633905082 ***
# vegtype_densityTM_DE  1.1695971  0.3163575   3.697         0.000218 ***
# vegtype_densityTM_OP  0.5561967  0.2825547   1.968         0.049016 *  
# vegtype_densityTM_SP  0.9392432  0.4492893   2.091         0.036572 *  
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# (Dispersion parameter for binomial family taken to be 1)
# 
#     Null deviance: 5032.7  on 5600  degrees of freedom
# Residual deviance: 4699.0  on 5587  degrees of freedom
# AIC: 4727
# 
# Number of Fisher Scoring iterations: 5

# model diagnostic plots
binnedplot (fitted(mod.frt.5_final), 
            residuals(mod.frt.5_final), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))


dat2$resids<-resid(mod.frt.5_final)

binnedplot (dat2$prj_h_1, 
            dat2$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (log(dat2$climate1), 
            dat2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (dat2$prj_g_1, 
            dat2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))

binnedplot (log(dat2$dm_h_bc), 
            dat2$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm"))



##Partial Residuals
visreg(mod.frt.5_final, scale="response") # nicer plots than the ones below!

```

```{r}
summary(mod.frt.5_final)

#Create a new blank table and get AUC too
top_mod_table_FRT5_light_t_ALL <- data.frame (matrix (ncol = 19, nrow = 0))
colnames (top_mod_table_FRT5_light_t_ALL ) <- c ("CAUSE", "FRT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_proj_height_1", "coef_proj_height_1_sqr",  "coef_proj_age_1",  "coef_elevation", "coef_vegtype_densityTB_OP", "coef_vegtype_densityTB_SP", "coef_vegtype_densityTC_DE", "coef_vegtype_densityTC_OP", "coef_vegtype_densityTC_SP", "coef_vegtype_densityTM_DE", "coef_vegtype_densityTM_OP", "coef_vegtype_densityTM_SP", "AUC")

dat2$fire_veg<-paste(dat2$fire, dat2$vegtype)
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(dat2$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- dat2[ trainIndex,]
   Valid <- dat2[-trainIndex,]
   
#Model   
mod.frt.5_final<-glm(fire ~ climate1 + poly(prj_h_1,2) + prj_g_1 + dm_h_bc + vegtype_density, data=dat2, family=binomial(link="logit"))

mod.valid <- predict.glm(mod.frt.5_final, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT1_light_t <- data.frame (matrix (ncol = 19, nrow = 0))
colnames (top_mod_table_NDT1_light_t ) <- c ("CAUSE", "FRT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_proj_height_1", "coef_proj_height_1_sqr",  "coef_proj_age_1",  "coef_elevation", "coef_vegtype_densityTB_OP", "coef_vegtype_densityTB_SP", "coef_vegtype_densityTC_DE", "coef_vegtype_densityTC_OP", "coef_vegtype_densityTC_SP", "coef_vegtype_densityTM_DE", "coef_vegtype_densityTM_OP", "coef_vegtype_densityTM_SP", "AUC")

##Add data for NDT1
top_mod_table_NDT1_light_t[1,1]<-"lightning"
top_mod_table_NDT1_light_t[1,2]<-"FRT5"
top_mod_table_NDT1_light_t[1,3]<-"Y"
top_mod_table_NDT1_light_t[1,4]<-"fire ~ climate1 + prj_h_1 + prj_h_1_sqr + prj_g_1 + dm_h_bc + vegtype + bclcs_level_5_2"
top_mod_table_NDT1_light_t[1,5]<- coef(mod.frt.5_final)[1] #Intercept
top_mod_table_NDT1_light_t[1,6]<- coef(mod.frt.5_final)[2] #Climate variable 1
top_mod_table_NDT1_light_t[1,7]<- coef(mod.frt.5_final)[3] #Climate variable 2
top_mod_table_NDT1_light_t[1,8]<- coef(mod.frt.5_final)[4] #I
top_mod_table_NDT1_light_t[1,9]<- coef(mod.frt.5_final)[5] #co
top_mod_table_NDT1_light_t[1,10]<- coef(mod.frt.5_final)[6] #coe
top_mod_table_NDT1_light_t[1,11]<- coef(mod.frt.5_final)[7] #c
top_mod_table_NDT1_light_t[1,12]<- coef(mod.frt.5_final)[8] #
top_mod_table_NDT1_light_t[1,13]<- coef(mod.frt.5_final)[9] #
top_mod_table_NDT1_light_t[1,14]<- coef(mod.frt.5_final)[10] #pr
top_mod_table_NDT1_light_t[1,15]<- coef(mod.frt.5_final)[11] #coeffic
top_mod_table_NDT1_light_t[1,16]<- coef(mod.frt.5_final)[12] #coeffic
top_mod_table_NDT1_light_t[1,17]<- coef(mod.frt.5_final)[13] #coeffic
top_mod_table_NDT1_light_t[1,18]<- coef(mod.frt.5_final)[14] #coeffic
top_mod_table_NDT1_light_t[1,19]<- mod.auc

top_mod_table_FRT5_light_t_ALL<-rbind(top_mod_table_FRT5_light_t_ALL, top_mod_table_NDT1_light_t)

}

```

Check.
```{r}
head(top_mod_table_FRT5_light_t_ALL)

```

#Save coefficient table

```{r}
write.csv(top_mod_table_FRT5_light_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\Ignition Models\\Ignition_Model_Results_Lightning_Treed\\top_mod_table_FRT5_light_tree_all.csv")
```

Get mean values.

```{r}
names(top_mod_table_FRT5_light_t_ALL)
str(top_mod_table_FRT5_light_t_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

FRT5_summary_table_mean<- top_mod_table_FRT5_light_t_ALL %>% summarize_if(is.numeric,mean)


```

Save table.

```{r}
write.csv(top_mod_table_NDT1_light_t_Means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_light_t_Means.csv")
```

Standard deviation.

```{r}
top_mod_table_NDT1_light_t_SD<-top_mod_table_NDT1_light_t_ALL %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT1_light_t_SD

top_mod_table_NDT1_light_t_SD[1,1]<-"lightning"
top_mod_table_NDT1_light_t_SD[1,2]<-"NDT1"
top_mod_table_NDT1_light_t_SD[1,3]<-"Treed"
top_mod_table_NDT1_light_t_SD[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + live_stand_volume_125 + proj_age_1 + climate1:climate2 + climate1:proj_height_1 + climate1:proj_age_1  + climate2:proj_age_1  + proj_height_1:proj_age_1 + dist_mun + dist_dam + dist_nat + dist_mine + bclcs_level_5_2 + dist_mun:bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + dist_mine:bclcs_level_5_2 + slope + aspect_cos + elevation" 
top_mod_table_NDT1_light_t_SD
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT1_light_t_SD, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_light_t_SD.csv")
```
