---
title: "12b_fire_escape_model_selection_NDT2"
author: "Cora Skaien"
date: "28/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load relevant libraries
library(sf)
library(tidyverse)
library(ggplot2)
library (ggcorrplot)
library (RPostgreSQL)
library (rpostgis)
library (dplyr)
library (lme4)
library (arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(ggcorrplot) 
library (kableExtra)
library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(AICcmodavg)
library(caret)
library(pROC)
library(rje)
library(base)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 12b_fire_escape_model_selection_NDT2.R
#  Script Version: 1.0
#  Script Purpose: Model selection for escape by NDT.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

Load in the prepped data.

```{r}
Escape_data_lightning_t<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\escape_data_lightning_trees_NDT_Oct.csv")

head(Escape_data_lightning_t)

```

################ PART 1: Lightning Caused Fires ################

We will make a loop that does something very similar to our last loop, but with the selected climate variable plus other variables of interest. For lightning caused fires with trees, the variables of interest include:

1. Climate variable(s)
2. Projected Height (proj_height_1)
3. projected age (proj_age_1)  
4. live_stand_volume_125
5. vegtype2
6. slope
7. aspect (cos)
8. elevation
9. Various distance to infrastructure variables (dist_mun, dist_dam, dist_nat, dist_pow, dist_mine) - no interactions
10. Land use (bclcs_level_5_2)
11. windspeed (wind_atfire)
12. roads_km (road density, which may relate to ability to fight fires)
13. Tdif_atfire (temperature difference from the month prior to the month of the fire)

Interactions of interest: two-way interactions between climate (1) and vegtype (5); two-way interactions between topography measures (6-8). 

This will be done separately for trees and non-treed areas. 

##We will do each loop separately for each NDT zone given the large number of possible models for each zone.

First we will create the variable lists that contain all of our variables of interest.

```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(climate1 = "climate1", climate2 = "climate2", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2", bclcs_level_5_2 = "bclcs_level_5_2", dist_mun = "dist_mun", dist_dam ="dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", wind_atfire = "wind_atfire", roads_km="roads_km") 

variables_all_c1<-c(climate1 = "climate1", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2", bclcs_level_5_2 = "bclcs_level_5_2", dist_mun = "dist_mun", dist_dam ="dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", wind_atfire = "wind_atfire", roads_km="roads_km") 


vars.clim<-c("climate1")
vars.clim.vegtype<-c("climate1", "vegtype2")
vars.oth<-c("proj_height_1", "proj_age_1", "live_stand_volume_125") 
vars.topo<-c("slope", "aspect", "elevation", "wind_atfire")
vars.infra<-c("dist_mun", "dist_dam", "dist_nat", "dist_pow", "dist_mine", "roads_km")

#Also for later with 2 climate variables
vars.clim.vegtype2<-c("climate1", "climate2","vegtype2")
vars.clim.vegtype2b<-c("climate1", "climate2")

##Create interaction for climate and vegtype
inputs.me <- c(vars.clim.vegtype)
inputs.me2 <- c(vars.clim.vegtype2)
inputs.me2b <- c(vars.clim.vegtype2b)
```


Now, we will generate two-way interactions for each of these lists. 

```{r}

#####1a. For those with one climate variable
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints <- NULL
for (i in 1:(length(inputs.me)-1)) {
  for (j in (i+1):length(inputs.me)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me[i], inputs.me[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints)#1

#
#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}


#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype) 
#add climate vars to all of the above
mods.me.climate <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate
mods.me.climate<-mods.me.climate[-1]

#####1b. For those with two climate variables
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2 <- NULL
for (i in 1:(length(inputs.me2)-1)) {
  for (j in (i+1):length(inputs.me2)) {
     twoway.ints2 <- cbind(twoway.ints2, paste(inputs.me2[i], inputs.me2[j], sep=":"))
  }
}
twoway.ints2
length(twoway.ints2) #3

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2) 
#add climate vars to all of the above
mods.me.climate2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2
mods.me.climate2<-mods.me.climate2[-1]

#complete list of two-way interactions
mods.twoway2 <- powerSet(twoway.ints2)
length(mods.twoway2) #8
mods.twoway2
mods.twoway2<-mods.twoway2[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2 <- list()
counter <- 0
for (i in 1: length(mods.twoway2)) {
   s1 <- unique(unlist( strsplit(mods.twoway2[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2)) {
      if (all(s1 %in% mods.me.climate2[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2[[j]], mods.twoway2[[i]])
        mods.inter2[[counter]] <- both
      }
   }
}

length(mods.inter2) #10
#mods.inter2
mods.inter2


####1c. Two variables, no variation in vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2b <- NULL
for (i in 1:(length(inputs.me2b)-1)) {
  for (j in (i+1):length(inputs.me2b)) {
     twoway.ints2b <- cbind(twoway.ints2b, paste(inputs.me2b[i], inputs.me2b[j], sep=":"))
  }
}
twoway.ints2b
length(twoway.ints2b) #1

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2b) 
#add climate vars to all of the above
mods.me.climate2b <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2b[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2b
mods.me.climate2b<-mods.me.climate2b[-1]

#complete list of two-way interactions
mods.twoway2b <- powerSet(twoway.ints2b)
length(mods.twoway2b) #2
mods.twoway2b
mods.twoway2b<-mods.twoway2b[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2b <- list()
counter <- 0
for (i in 1: length(mods.twoway2b)) {
   s1 <- unique(unlist( strsplit(mods.twoway2b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2b)) {
      if (all(s1 %in% mods.me.climate2b[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2b[[j]], mods.twoway2b[[i]])
        mods.inter2b[[counter]] <- both
      }
   }
}

length(mods.inter2b)
#mods.inter2b


#########2. Now for topography data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT) #6

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT
mods.meT<-mods.meT[-1]

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #64
mods.twowayT
mods.twowayT<-mods.twowayT[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT) #97
#mods.interT


####3.For other VRI data, get without interactions

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.oth
mods.me.oth<-mods.me.oth[-1]


#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI) #15

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI
mods.meI<-mods.meI[-1]

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsI)
length(mods.twowayI) #32768 -
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI) #80136
#mods.interI


#the list of all possible model RHSs. 
#all.poss.mods <- c(1, vars.clim, twoway.ints, mods.me.oth, mods.me2, mods.inter2)
#all.poss.mods

all.poss.mods.clim.vegtype<-c(1, mods.me.climate, twoway.ints)
all.poss.mods.clim.vegtype 

all.poss.mods.clim.vegtype2<-c(1, mods.me.climate2, mods.inter2)
all.poss.mods.clim.vegtype2

all.poss.mods.clim.vegtype2b<-c(1, mods.me.climate2b, mods.inter2b)
all.poss.mods.clim.vegtype2b

all.poss.mods.VRI<-c(1, mods.me.oth)
all.poss.mods.VRI

all.poss.mods.topo<-c(1, mods.interT)
all.poss.mods.topo

all.poss.mods.infra<-c(1, mods.meI) #I don't think we want interactions here actually... we will in the next stage when we include bclcs_level_5_2 after some initial pattern exploration


#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim.vegtype) #None duplicated
duplicated(all.poss.mods.clim.vegtype2)
duplicated(all.poss.mods.clim.vegtype2b)
duplicated(all.poss.mods.VRI)
duplicated(all.poss.mods.topo)
duplicated(all.poss.mods.infra)

```

############### Part 1 of 4 Model Series: Lightning Caused Fires, Trees ##########

Because of the large number of models with all variables included, we will test the climate and vegtype first, then the VRI variables, then the topography variables. Then we will test the top models together in additional combinations, with determining best AIC model from there. Or perhaps we will just combine the top models for each together, and eliminate models if the intercept was the best predictor.

Select NDT: NDT2
#NDT2 does not have a second climate variable. Make sure to use all.poss.mods.clim.vegtype


```{r}
zones1<-c("NDT2") #Do one zone at a time

prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

########### 1. Climate and vegtype ############
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim.vegtype[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim.vegtype, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT2")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}


```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_lightning_NDT2_treed_climate<-table.glm.climate.simple

AIC_lightning_NDT2_treed_summary_climate<- AIC_lightning_NDT2_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT2_treed_summary_climate2<- AIC_lightning_NDT2_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT2_treed_summary_climate2)
```

#Now repeat for VRI data

```{r}
########### 2. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.VRI)){
#  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$NDT<-c("NDT2")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_lightning_NDT2_treed_VRI<-table.glm.VRI.simple

AIC_lightning_NDT2_treed_summary_VRI<- AIC_lightning_NDT2_treed_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT2_treed_summary_VRI2<- AIC_lightning_NDT2_treed_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT2_treed_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 3. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$NDT<-c("NDT2")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_lightning_NDT2_treed_topo<-table.glm.topo.simple

AIC_lightning_NDT2_treed_summary_topo<- AIC_lightning_NDT2_treed_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT2_treed_summary_topo2<- AIC_lightning_NDT2_treed_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT2_treed_summary_topo2)
```

#Now repeat for infrastructure

```{r}
########### 4. Distance to Infrastructure ############
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_lightning_NDT2_treed_infra<-table.glm.infra.simple

AIC_lightning_NDT2_treed_summary_infra<- AIC_lightning_NDT2_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT2_treed_summary_infra2<- AIC_lightning_NDT2_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT2_treed_summary_infra2)

```

#Now combine the datatables and save to computer

```{r}
NDT2_l_models_treed<-rbind(AIC_lightning_NDT2_treed_summary_climate2, AIC_lightning_NDT2_treed_summary_VRI2, AIC_lightning_NDT2_treed_summary_topo2, AIC_lightning_NDT2_treed_summary_infra2)
NDT2_l_models_treed
NDT2_l_models_treed$NDT<-"NDT2"

write.csv(NDT2_l_models_treed, file="D:\\Fire\\fire_data\\raw_data\\NDT2_lightning_models_treed_escape.csv")
```

################################ STAGE TWO ########################

#STAGE TWO: PUT TOGETHER MORE VARIABLES
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Models.
1. climate1
2. proj_height_1 + proj_age_1 + live_stand_volume_125
3. slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:wind_atfire + elevation:wind_atfire
4. dist_mun + dist_dam + dist_pow + dist_mine + roads_km

Additional Variables:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)
2. Tdif_atfire

##Next we will repeat the VRI to include bclcs_level_5_2
For climate and VRI, we will just start with interactions between climate and each variable

Create variable lists.

```{r}
##Create variable lists to be used in the model loop.
variables_all_NDT2<-c(climate1 = "climate1", climate2 = "climate2", vegtype2 = "vegtype2", live_stand_volume_125 = "live_stand_volume_125", proj_height_1 ="proj_height_1", proj_age_1 = "proj_age_1",  slope = "slope", elevation ="elevation", aspect = "aspect",  dist_dam = "dist_dam", dist_mun = "dist_mun", dist_nat = "dist_nat", dist_mine = "dist_mine", dist_pow = "dist_pow", roads_km = "roads_km", bclcs_level_5_2 = "bclcs_level_5_2", wind_atfire="wind_atfire")


variables_all_infra_landuse_NDT2<-c(dist_dam = "dist_dam", dist_mun = "dist_mun", dist_nat = "dist_nat", dist_mine = "dist_mine", dist_pow = "dist_pow", roads_km = "roads_km", bclcs_level_5_2 = "bclcs_level_5_2") #I don't think it makes sense to have interactions between the distance elements, but maybe with land use and each distance element?

##
inputs.me.NDT2 <- c(variables_all_NDT2)
inputs.me.infra_landuse_NDT2 <- c(variables_all_infra_landuse_NDT2)

```

```{r}
##Subset 2: Infrastructure and land use ########
#inputs.me.infra_landuse_NDT2
twoway.ints <- NULL
for (i in 1:(length(inputs.me.infra_landuse_NDT2)-1)) {
  for (j in (i+1):length(inputs.me.infra_landuse_NDT2)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me.infra_landuse_NDT2[i], inputs.me.infra_landuse_NDT2[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints) #21
#Review. If we do not want interactions between the different distance measurements, but only those between land use and distance, subset those.
twoway.ints
twoway.ints_dist<-twoway.ints[c(5,6,10,11,14,15,17,18,19,20,21)]
twoway.ints_dist


#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(variables_all_infra_landuse_NDT2) 
#add climate vars to all of the above
mods.me.infra_landuse_NDT2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.infra_landuse_NDT2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.infra_landuse_NDT2
length(mods.me.infra_landuse_NDT2) #128


#complete list of two-way interactions
#mods.twoway.NDT2b <- powerSet(twoway.ints) #
#Or use subset of interactions
mods.twoway.NDT2b <- powerSet(twoway.ints_dist) 
length(mods.twoway.NDT2b) #2048
#mods.twoway.NDT2b
mods.twoway.NDT2b[1]
mods.twoway.NDT2b<-mods.twoway.NDT2b[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter.NDT2b <- list()
counter <- 0
for (i in 1: length(mods.twoway.NDT2b)) {
   s1 <- unique(unlist( strsplit(mods.twoway.NDT2b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.infra_landuse_NDT2)) {
      if (all(s1 %in% mods.me.infra_landuse_NDT2[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.infra_landuse_NDT2[[j]], mods.twoway.NDT2b[[i]])
        mods.inter.NDT2b[[counter]] <- both
      }
   }
}

length(mods.inter.NDT2b) #6640
#mods.inter.NDT2b
```

Make final list of variables to assess.

```{r}
##### Infrastructure and land use
all.poss.mods.infra_landuse_NDT2<-c(1,mods.me.infra_landuse_NDT2, mods.inter.NDT2b)
length(all.poss.mods.infra_landuse_NDT2) #6769

##Check and rid of any duplicated models
duplicated(all.poss.mods.infra_landuse_NDT2) #Need to remove 
#all.poss.mods.infra_landuse_NDT2b<-all.poss.mods.infra_landuse_NDT2[-(34:65)]
#duplicated(all.poss.mods.infra_landuse_NDT2b) 
#all.poss.mods.infra_landuse_NDT2b[2]
#all.poss.mods.infra_landuse_NDT2b<-all.poss.mods.infra_landuse_NDT2b[-2]
```

```{r}
all.poss.mods.infra_landuse_NDT2<-all.poss.mods.infra_landuse_NDT2[-2]
```

For below, run only 10 times and run it multiple times, as it may crash R. Before running a second time, rename the table, otherwise it will be erased.

```{r}
########### Distance to Infrastructure ############

zones1<-"NDT2"

#Create empty table
table.glm.infra.lu.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.lu.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:10){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_lightning_t %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra_landuse_NDT2[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, veg_escape, variables_all_NDT2[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all_infra_landuse_NDT2)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_landuse_NDT2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra.lu <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra.lu$NDT<-c("NDT2")
tab.sum.infra.lu 

table.glm.infra.lu.simple<-rbind(table.glm.infra.lu.simple, tab.sum.infra.lu)

}
}
}
```

Rename table.
```{r}
table.glm.infra.lu.simple_ALL<-table.glm.infra.lu.simple
```

Now rerun the model code. Afterwards, combine the outputs.

```{r}
table.glm.infra.lu.simple_ALL_<-rbind(table.glm.infra.lu.simple_ALL, table.glm.infra.lu.simple)

table.glm.infra.lu.simple_ALL<-rbind(table.glm.infra.lu.simple_ALL_, table.glm.infra.lu.simple)
```


Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination. Also determine deltaAIC.

```{r}
head(table.glm.infra.lu.simple_ALL)
table(table.glm.infra.lu.simple_ALL$model) # 100 per model

AIC_lightning_NDT2_escape_treed_infra<-table.glm.infra.lu.simple_ALL

AIC_lightning_NDT2_escape_treed_summary_infra<- AIC_lightning_NDT2_escape_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT2_escape_treed_summary_infra2<- AIC_lightning_NDT2_escape_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_lightning_NDT2_escape_treed_summary_infra2)
```

Save to computer.

```{r}
write.csv(AIC_lightning_NDT2_escape_treed_summary_infra2, file="D:\\Fire\\fire_data\\raw_data\\AIC_lightning_NDT2_escape_treed_summary_infra_escape.csv")
```


################ MANUAL MODEL SELECTION ################

Top Models:
1. climate1
2. proj_height_1 + proj_age_1 + live_stand_volume_125
3. slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:wind_atfire + elevation:wind_atfire
4. dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + roads_km:bclcs_level_5_2


*Interactions to include: climate1:proj_height_1 + climate1:proj_age_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire + Tdif_atfire

#Next investigation

```{r}
escape_lightning_t_NDT2<-subset(Escape_data_lightning_t, Escape_data_lightning_t$ntrl_ds=="NDT2")

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_lightning_t_NDT2$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_lightning_t_NDT2[ trainIndex,]
   Valid <- escape_lightning_t_NDT2[-trainIndex,]

#Run model using dat1
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:wind_atfire + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + climate1:proj_height_1 + climate1:proj_age_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1510.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:wind_atfire + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1508.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1506.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1504.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1504.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1501.3

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1499.3

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + climate1:wind_atfire + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1497.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_dam:bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1495.5

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1494.1

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1491.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:bclcs_level_5_2 + dist_mine:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1490.5

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_nat + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1490.5

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.63
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#All above not fully able to converge. Remove dist_nat and experiment.
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1492.5

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.64
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)


#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1 + Tdif_atfire:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1490.6

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.64
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_mine + dist_pow + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km + dist_pow:bclcs_level_5_2 + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1, family = binomial, data = dat1)

AIC(model.NDT2.E) #1489.3

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.64
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Experiment with remving dist_pow
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + elevation:wind_atfire + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1, family = binomial, data = dat1)

AIC(model.NDT2.E) #1486.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.64
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)

#Remove east significant
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1, family = binomial, data = dat1)

AIC(model.NDT2.E) #1486.0

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.64
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE)



# Below is from a previous model selection before we had Tdif_atfire.Note, the AIC is far worse; however, the AUC is actually better.
model.NDT2.E<-glm(escape ~ climate1  + live_stand_volume_125 + slope + aspect +  wind_atfire + slope:aspect + aspect:wind_atfire  + dist_dam + dist_mun  + dist_mine + dist_pow + roads_km + bclcs_level_5_2  + dist_mun:bclcs_level_5_2  + dist_mine:roads_km  + climate1:wind_atfire, family = binomial, data = dat1)

AIC(model.NDT2.E) #1508.0

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.70
   
Anova(model.NDT2.E, type=3)
Anova(model.NDT2.E, type=3, singular.ok = TRUE) 



```


Remove NAs and tun multiple times.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT2_escape_t<-escape_lightning_t_NDT2 %>% drop_na(climate1, proj_height_1, live_stand_volume_125, slope, aspect, elevation, wind_atfire, dist_dam, dist_mun, dist_mine, roads_km, bclcs_level_5_2, Tdif_atfire)

#Run Model again with this data; but uses all data here
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1, family = binomial, data = NDT2_escape_t)

Anova(model.NDT2.E, type=3)

# model diagnostic plots
binnedplot (fitted(model.NDT2.E), 
            residuals(model.NDT2.E), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT2_escape_t$resids<-resid(model.NDT2.E)

binnedplot (NDT2_escape_t$live_stand_volume_125, 
            NDT2_escape_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT2_escape_t$climate1, 
            NDT2_escape_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good
#climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1

visreg(model.NDT2.E, "climate1", by="proj_height_1")
visreg(model.NDT2.E, "climate1", by="live_stand_volume_125")
visreg(model.NDT2.E, "climate1", by="elevation")

visreg(model.NDT2.E, "proj_height_1", by="climate1")
visreg(model.NDT2.E, "live_stand_volume_125", by="climate1")

visreg(model.NDT2.E, "slope", by="elevation")
visreg(model.NDT2.E, "aspect")
visreg(model.NDT2.E, "elevation", by="climate1")
visreg(model.NDT2.E, "elevation", by="slope")

visreg(model.NDT2.E, "Tdif_atfire", by="climate1")

#dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km
visreg(model.NDT2.E, "dist_dam", by="roads_km")
visreg(model.NDT2.E, "dist_mun", by="roads_km")
visreg(model.NDT2.E, "dist_mine", by="roads_km")
visreg(model.NDT2.E, "dist_mun", by="bclcs_level_5_2", overlay=TRUE, ylim=c(-7,7))
visreg(model.NDT2.E, "bclcs_level_5_2", by="dist_mun", ylim=c(-10,10))

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT2.E)

#Create a new blank table and get AUC too
top_mod_table_NDT2_light_t_ALL <- data.frame (matrix (ncol = 32, nrow = 0))
colnames (top_mod_table_NDT2_light_t_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_proj_height_1", "coef_live_stand_volume_125", "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_dam", "coef_dist_mun", "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_Tdif_atfire", "coef_slope:elevation", "coef_dist_dam:roads_km", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mine:roads_km", "coef_climate1:proj_height_1", "coef_climate1:live_stand_volume_125", "coef_climate1:elevation", "coef_climate1:Tdif_atfire", "AUC")
```

Let's run it 500 times to get good mean values. 

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT2_escape_t$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT2_escape_t[ trainIndex,]
   Valid <- NDT2_escape_t[-trainIndex,]
   
#Model   
model.NDT2.E<-glm(escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT2.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT2_light_t <- data.frame (matrix (ncol = 32, nrow = 0))
colnames (top_mod_table_NDT2_light_t ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_proj_height_1", "coef_live_stand_volume_125", "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_dam", "coef_dist_mun", "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_Tdif_atfire", "coef_slope:elevation", "coef_dist_dam:roads_km", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mine:roads_km", "coef_climate1:proj_height_1", "coef_climate1:live_stand_volume_125", "coef_climate1:elevation", "coef_climate1:Tdif_atfire", "AUC")

##Add data for NDT2
top_mod_table_NDT2_light_t[1,1]<-"lightning"
top_mod_table_NDT2_light_t[1,2]<-"NDT2"
top_mod_table_NDT2_light_t[1,3]<-"Y"
top_mod_table_NDT2_light_t[1,4]<-"escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1" 
top_mod_table_NDT2_light_t[1,5]<- coef(model.NDT2.E)[1] #Intercept
top_mod_table_NDT2_light_t[1,6]<- coef(model.NDT2.E)[2] #Climate variable 1
top_mod_table_NDT2_light_t[1,7]<- coef(model.NDT2.E)[3] #proj_height
top_mod_table_NDT2_light_t[1,8]<- coef(model.NDT2.E)[4] #live_stand_volume_125
top_mod_table_NDT2_light_t[1,9]<- coef(model.NDT2.E)[5] #coefficient slope
top_mod_table_NDT2_light_t[1,10]<- coef(model.NDT2.E)[6] #coefficient aspect
top_mod_table_NDT2_light_t[1,11]<- coef(model.NDT2.E)[7] #coefficient elevation
top_mod_table_NDT2_light_t[1,12]<- coef(model.NDT2.E)[8] #coefficient wind_atfire
top_mod_table_NDT2_light_t[1,13]<- coef(model.NDT2.E)[9] #coefficient dist_dam
top_mod_table_NDT2_light_t[1,14]<- coef(model.NDT2.E)[10] #coefficient dist_mun
top_mod_table_NDT2_light_t[1,15]<- coef(model.NDT2.E)[11] #coefficient dist_mine
top_mod_table_NDT2_light_t[1,16]<- coef(model.NDT2.E)[12] #coefficient roads_km
top_mod_table_NDT2_light_t[1,17]<- coef(model.NDT2.E)[13] #coefficient bclcs_level_5_2DE
top_mod_table_NDT2_light_t[1,18]<- coef(model.NDT2.E)[14] #coefficient bclcs_level_5_2OP
top_mod_table_NDT2_light_t[1,19]<- coef(model.NDT2.E)[15] #coefficient bclcs_level_5_2SP
top_mod_table_NDT2_light_t[1,20]<- coef(model.NDT2.E)[16] #coefficient Tdif_atfire
top_mod_table_NDT2_light_t[1,21]<- coef(model.NDT2.E)[17] #coefficient slope:elevation
top_mod_table_NDT2_light_t[1,22]<- coef(model.NDT2.E)[18] #coefficient dist_dam:roads_km
top_mod_table_NDT2_light_t[1,23]<- coef(model.NDT2.E)[19] #coefficient dist_mun:roads_km
top_mod_table_NDT2_light_t[1,24]<- coef(model.NDT2.E)[20] #coefficient dist_mun:bclcs_level_5_2DE 
top_mod_table_NDT2_light_t[1,25]<- coef(model.NDT2.E)[21] #coefficient dist_mun:bclcs_level_5_2OP
top_mod_table_NDT2_light_t[1,26]<- coef(model.NDT2.E)[22] #coefficient dist_mun:bclcs_level_5_2SP
top_mod_table_NDT2_light_t[1,27]<- coef(model.NDT2.E)[23] #coefficient dist_mine:roads_km  
top_mod_table_NDT2_light_t[1,28]<- coef(model.NDT2.E)[24] #coefficient climate1:proj_height_1 
top_mod_table_NDT2_light_t[1,29]<- coef(model.NDT2.E)[25] #coefficient climate1:live_stand_volume_125
top_mod_table_NDT2_light_t[1,30]<- coef(model.NDT2.E)[26] #coefficient climate1:elevation
top_mod_table_NDT2_light_t[1,31]<- coef(model.NDT2.E)[27] #coefficient climate1:Tdif_atfire 
top_mod_table_NDT2_light_t[1,32]<- mod.auc

top_mod_table_NDT2_light_t_ALL<-rbind(top_mod_table_NDT2_light_t_ALL, top_mod_table_NDT2_light_t)

}

```

Check.
```{r}
head(top_mod_table_NDT2_light_t_ALL)

```

#Save coefficient table

```{r}
write.csv(top_mod_table_NDT2_light_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT2_light_t_ALL.csv")
```

Get mean values.

```{r}
names(top_mod_table_NDT2_light_t_ALL)
mean(top_mod_table_NDT2_light_t_ALL$AUC) # 0.697

# create model table (only do this once) and add the relevant data
top_mod_table_NDT2_light_t_Means <- data.frame (matrix (ncol = 32, nrow = 0))
colnames (top_mod_table_NDT2_light_t_Means ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_proj_height_1", "coef_live_stand_volume_125", "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_dam", "coef_dist_mun", "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_Tdif_atfire", "coef_slope:elevation", "coef_dist_dam:roads_km", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mine:roads_km", "coef_climate1:proj_height_1", "coef_climate1:live_stand_volume_125", "coef_climate1:elevation", "coef_climate1:Tdif_atfire", "AUC")

head(top_mod_table_NDT2_light_t_Means)

##Add data for NDT2
top_mod_table_NDT2_light_t_Means[1,1]<-"lightning"
top_mod_table_NDT2_light_t_Means[1,2]<-"NDT2"
top_mod_table_NDT2_light_t_Means[1,3]<-"Y"
top_mod_table_NDT2_light_t_Means[1,4]<-"escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1" 
top_mod_table_NDT2_light_t_Means[1,5]<- mean(top_mod_table_NDT2_light_t_ALL$intercept) #Intercept
top_mod_table_NDT2_light_t_Means[1,6]<- mean(top_mod_table_NDT2_light_t_ALL$coef_climate_1, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,7]<- mean(top_mod_table_NDT2_light_t_ALL$coef_proj_height_1, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,8]<- mean(top_mod_table_NDT2_light_t_ALL$coef_live_stand_volume_125, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,9]<- mean(top_mod_table_NDT2_light_t_ALL$coef_slope, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,10]<- mean(top_mod_table_NDT2_light_t_ALL$coef_aspect, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,11]<- mean(top_mod_table_NDT2_light_t_ALL$coef_elevation, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,12]<- mean(top_mod_table_NDT2_light_t_ALL$coef_dist_dam, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,13]<- mean(top_mod_table_NDT2_light_t_ALL$coef_dist_mine, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,14]<- mean(top_mod_table_NDT2_light_t_ALL$coef_dist_mun, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,15]<- mean(top_mod_table_NDT2_light_t_ALL$coef_dist_mine, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,16]<- mean(top_mod_table_NDT2_light_t_ALL$coef_roads_km, na.rm=TRUE) #
top_mod_table_NDT2_light_t_Means[1,17]<- mean(top_mod_table_NDT2_light_t_ALL$coef_bclcs_level_5_2DE, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,18]<- mean(top_mod_table_NDT2_light_t_ALL$coef_bclcs_level_5_2OP, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,19]<- mean(top_mod_table_NDT2_light_t_ALL$coef_bclcs_level_5_2SP, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,20]<- mean(top_mod_table_NDT2_light_t_ALL$coef_Tdif_atfire, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,21]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_slope:elevation`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,22]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_dist_dam:roads_km`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,23]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:roads_km`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,24]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:bclcs_level_5_2DE`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,25]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:bclcs_level_5_2OP`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,26]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:bclcs_level_5_2SP`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,27]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_dist_mine:roads_km`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,28]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_climate1:proj_height_1`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,29]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_climate1:live_stand_volume_125`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,30]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_climate1:elevation`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,31]<- mean(top_mod_table_NDT2_light_t_ALL$`coef_climate1:Tdif_atfire`, na.rm=TRUE)
top_mod_table_NDT2_light_t_Means[1,32]<- mean(top_mod_table_NDT2_light_t_ALL$AUC, na.rm=TRUE)

top_mod_table_NDT2_light_t_Means

```

Save mean coefficient table.

```{r}
write.csv(top_mod_table_NDT2_light_t_Means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT2_light_t_Means.csv")
```


Get sd values.

```{r}
# create model table (only do this once) and add the relevant data
top_mod_table_NDT2_light_t_SD <- data.frame (matrix (ncol = 32, nrow = 0))
colnames (top_mod_table_NDT2_light_t_SD ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_proj_height_1", "coef_live_stand_volume_125", "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_dam", "coef_dist_mun", "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2SP", "coef_Tdif_atfire", "coef_slope:elevation", "coef_dist_dam:roads_km", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mine:roads_km", "coef_climate1:proj_height_1", "coef_climate1:live_stand_volume_125", "coef_climate1:elevation", "coef_climate1:Tdif_atfire", "AUC")

head(top_mod_table_NDT2_light_t_SD)

##Add data for NDT2
top_mod_table_NDT2_light_t_SD[1,1]<-"lightning"
top_mod_table_NDT2_light_t_SD[1,2]<-"NDT2"
top_mod_table_NDT2_light_t_SD[1,3]<-"Y"
top_mod_table_NDT2_light_t_SD[1,4]<-"escape ~ climate1 + proj_height_1 + live_stand_volume_125 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_dam + dist_mun + dist_mine + roads_km + bclcs_level_5_2 + dist_dam:roads_km + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_mine:roads_km  + climate1:proj_height_1 + climate1:live_stand_volume_125 + climate1:elevation + Tdif_atfire + Tdif_atfire:climate1" 
top_mod_table_NDT2_light_t_SD[1,5]<- sd(top_mod_table_NDT2_light_t_ALL$intercept) #Intercept
top_mod_table_NDT2_light_t_SD[1,6]<- sd(top_mod_table_NDT2_light_t_ALL$coef_climate_1, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,7]<- sd(top_mod_table_NDT2_light_t_ALL$coef_proj_height_1, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,8]<- sd(top_mod_table_NDT2_light_t_ALL$coef_live_stand_volume_125, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,9]<- sd(top_mod_table_NDT2_light_t_ALL$coef_slope, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,10]<- sd(top_mod_table_NDT2_light_t_ALL$coef_aspect, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,11]<- sd(top_mod_table_NDT2_light_t_ALL$coef_elevation, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,12]<- sd(top_mod_table_NDT2_light_t_ALL$coef_dist_dam, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,13]<- sd(top_mod_table_NDT2_light_t_ALL$coef_dist_mine, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,14]<- sd(top_mod_table_NDT2_light_t_ALL$coef_dist_mun, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,15]<- sd(top_mod_table_NDT2_light_t_ALL$coef_dist_mine, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,16]<- sd(top_mod_table_NDT2_light_t_ALL$coef_roads_km, na.rm=TRUE) #
top_mod_table_NDT2_light_t_SD[1,17]<- sd(top_mod_table_NDT2_light_t_ALL$coef_bclcs_level_5_2DE, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,18]<- sd(top_mod_table_NDT2_light_t_ALL$coef_bclcs_level_5_2OP, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,19]<- sd(top_mod_table_NDT2_light_t_ALL$coef_bclcs_level_5_2SP, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,20]<- sd(top_mod_table_NDT2_light_t_ALL$coef_Tdif_atfire, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,21]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_slope:elevation`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,22]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_dist_dam:roads_km`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,23]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:roads_km`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,24]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:bclcs_level_5_2DE`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,25]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:bclcs_level_5_2OP`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,26]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_dist_mun:bclcs_level_5_2SP`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,27]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_dist_mine:roads_km`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,28]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_climate1:proj_height_1`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,29]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_climate1:live_stand_volume_125`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,30]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_climate1:elevation`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,31]<- sd(top_mod_table_NDT2_light_t_ALL$`coef_climate1:Tdif_atfire`, na.rm=TRUE)
top_mod_table_NDT2_light_t_SD[1,32]<- sd(top_mod_table_NDT2_light_t_ALL$AUC, na.rm=TRUE)

top_mod_table_NDT2_light_t_SD

```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT2_light_t_SD, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT2_light_t_SD.csv")
```

