---
title: "12c_fire_escape_model_selection_NDT3_ALLPL_ALLTNT"
author: "Cora Skaien"
date: "20/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load relevant libraries
library(sf)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(RPostgreSQL)
library(rpostgis)
library(dplyr)
library(lme4)
library(arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(ggcorrplot) 
library(kableExtra)
library(data.table)
library(DBI)
library(here)
library(AICcmodavg)
library(rje)
library(base)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 12c_fire_escape_model_selection_NDT3_ALLPL_ALLTNT.R
#  Script Version: 1.0
#  Script Purpose: Model selection for escape by NDT.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

Load in the prepped data.

```{r}
Escape_data_ALL<-read.csv("D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\All_data_escape_Dec.csv")
head(Escape_data_ALL)

```

################ PART 1: Initial Model Selection for Subset Variables ################

We will make a loop that does something very similar to our last loop, but with the selected climate variable plus other variables of interest. For lightning caused fires with trees, the variables of interest include:

1. Climate variable(s) (Tave09 = climate1; ppt09=climate2; mdc_atfire); note, also can use temperature at time of fire and precipitation at time of fire for escape (not for ignition because areas without a fire do not have a one month value)
2. Projected Height (proj_height_1)*bclcs_level_2
3. projected age (proj_age_1)*bclcs_level_2
4. live_stand_volume_125*bclcs_level_2
5. vegtype2*bclcs_level_2
6. slope
7. aspect (cos)
8. elevation
9. dist_infra
10. windspeed (wind_atfire)
11. roads_km (road density, which may relate to ability to fight fires)
12. Tdif_atfire (temperature difference from the month prior to the month of the fire)
13. Fire cause (fire_cs)
#14. Land use (bclcs_level_5_2)

Interactions of interest: two-way interactions between climate (1) and vegtype (5); two-way interactions between topography measures (6-8). 

##We will do each loop separately for each NDT zone given the large number of possible models for each zone.

First we will create the variable lists that contain all of our variables of interest.

```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(climate1 = "climate1", climate2 = "climate2", mdc_atfire="mdc_atfire", proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect = "aspect", elevation ="elevation", vegtype2 = "vegtype2",  dist_infra = "dist_infra", wind_atfire = "wind_atfire", roads_km="roads_km", Tdif_atfire="Tdif_atfire", bclcs_level_2 ="bclcs_level_2", fire_cs ="fire_cs") 

vars.clim.vegtype2<-c("climate1", "climate2","vegtype2", "mdc_atfire")
vars.clim.vegtype2b<-c("climate1", "climate2", "mdc_atfire")
vars.oth<-c("proj_height_1", "proj_age_1", "live_stand_volume_125", "bclcs_level_2") 
vars.topo<-c("slope", "aspect", "elevation", "wind_atfire")
vars.infra<-c("dist_infra", "roads_km")
vars.oth2<-c("wind_atfire", "Tdif_atfire")


##Create interaction for climate and vegtype
inputs.me2 <- c(vars.clim.vegtype2)
inputs.me2b <- c(vars.clim.vegtype2b)
```

Now, we will generate two-way interactions for each of these lists. 

```{r}
#####1a. For those with two climate variables and vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2 <- NULL
for (i in 1:(length(inputs.me2)-1)) {
  for (j in (i+1):length(inputs.me2)) {
     twoway.ints2 <- cbind(twoway.ints2, paste(inputs.me2[i], inputs.me2[j], sep=":"))
  }
}
twoway.ints2
length(twoway.ints2) #6

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2) 
#add climate vars to all of the above
mods.me.climate2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2
mods.me.climate2<-mods.me.climate2[-1] #n = 15

#complete list of two-way interactions
mods.twoway2 <- powerSet(twoway.ints2)
length(mods.twoway2) #64
mods.twoway2[1]
mods.twoway2<-mods.twoway2[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2 <- list()
counter <- 0
for (i in 1: length(mods.twoway2)) {
   s1 <- unique(unlist( strsplit(mods.twoway2[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2)) {
      if (all(s1 %in% mods.me.climate2[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2[[j]], mods.twoway2[[i]])
        mods.inter2[[counter]] <- both
      }
   }
}

length(mods.inter2) #97
#mods.inter2
mods.inter2


####1c. Climate variables but no vegtype
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints2b <- NULL
for (i in 1:(length(inputs.me2b)-1)) {
  for (j in (i+1):length(inputs.me2b)) {
     twoway.ints2b <- cbind(twoway.ints2b, paste(inputs.me2b[i], inputs.me2b[j], sep=":"))
  }
}
twoway.ints2b
length(twoway.ints2b) #3

#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype2b) 
#add climate vars to all of the above
mods.me.climate2b <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate2b[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate2b
mods.me.climate2b<-mods.me.climate2b[-1]

#complete list of two-way interactions
mods.twoway2b <- powerSet(twoway.ints2b)
length(mods.twoway2b) #8
mods.twoway2b
mods.twoway2b<-mods.twoway2b[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added
mods.inter2b <- list()
counter <- 0
for (i in 1: length(mods.twoway2b)) {
   s1 <- unique(unlist( strsplit(mods.twoway2b[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.climate2b)) {
      if (all(s1 %in% mods.me.climate2b[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.climate2b[[j]], mods.twoway2b[[i]])
        mods.inter2b[[counter]] <- both
      }
   }
}

length(mods.inter2b) #10
mods.inter2b
```


```{r}
#########2. Now for topography data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT) #6

#No reason to believe aspect*wind_atfire would have an effect, so remove
twoway.intsT<-twoway.intsT[-5]

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT
mods.meT<-mods.meT[-1]

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #32
mods.twowayT
mods.twowayT<-mods.twowayT[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT) #56
#mods.interT
```


```{r}
####3.For other VRI data, get without interactions

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.oth
mods.me.oth<-mods.me.oth[-1]

#get the names of all possible two-way interactions
twoway.intsOTH <- NULL
for (i in 1:(length(vars.oth)-1)) {
  for (j in (i+1):length(vars.oth)) {
     twoway.intsOTH <- cbind(twoway.intsOTH, paste(vars.oth[i], vars.oth[j], sep=":"))
  }
}
twoway.intsOTH
length(twoway.intsOTH) #6

#Do not want interactions between VRI variables
twoway.intsOTH<-twoway.intsOTH[c(3,5,6)]
twoway.intsOTH

#complete list of two-way interactions
mods.twowayOTH <- powerSet(twoway.intsOTH)
length(mods.twowayOTH) #8
mods.twowayOTH
mods.twowayOTH<-mods.twowayOTH[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.inter.OTH <- list()
counter <- 0
for (i in 1: length(mods.twowayOTH)) {
   s1 <- unique(unlist( strsplit(mods.twowayOTH[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.me.oth)) {
      if (all(s1 %in% mods.me.oth[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.me.oth[[j]], mods.twowayOTH[[i]])
        mods.inter.OTH[[counter]] <- both
      }
   }
}

length(mods.inter.OTH) #19
mods.inter.OTH


```


```{r}
#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI) #1

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI
mods.meI<-mods.meI[-1]

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsI)
length(mods.twowayI) #2
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms 

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI) #4
mods.interI
```


```{r}
########5. Lastly for last list of other variables
#get the names of all possible two-way interactions
twoway.ints.O2 <- NULL
for (i in 1:(length(vars.oth2)-1)) {
  for (j in (i+1):length(vars.oth2)) {
     twoway.ints.O2 <- cbind(twoway.ints.O2, paste(vars.oth2[i], vars.oth2[j], sep=":"))
  }
}
twoway.ints.O2
length(twoway.ints.O2) #1

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.oth2) 
#add climate vars to all of the above
mods.me.O2 <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.O2[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.O2
mods.me.O2<-mods.me.O2[-1]

#complete list of two-way interactions
mods.twoway.O2 <- powerSet(twoway.ints.O2)
length(mods.twoway.O2) #2
mods.twowayI
```

Determine final models for testing.

```{r}
all.poss.mods.clim.vegtype2<-c(1, mods.me.climate2, mods.inter2)
all.poss.mods.clim.vegtype2 #113

all.poss.mods.clim.vegtype2b<-c(1, mods.me.climate2b, mods.inter2b)
all.poss.mods.clim.vegtype2b #18

all.poss.mods.VRI<-c(1, mods.inter.OTH)
all.poss.mods.VRI

all.poss.mods.topo<-c(1, mods.interT)
all.poss.mods.topo

all.poss.mods.infra<-c(1, mods.interI) 
all.poss.mods.infra

all.poss.mods.Oth2<-c(1, mods.me.O2) 
all.poss.mods.Oth2
```


```{r}
#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim.vegtype2)
duplicated(all.poss.mods.clim.vegtype2b)
duplicated(all.poss.mods.VRI)
duplicated(all.poss.mods.topo)
duplicated(all.poss.mods.infra)
duplicated(all.poss.mods.Oth2)

```

Because of the large number of models with all variables included, we will test the climate and vegtype first, then the VRI variables, then the topography variables. Then we will test the top models together in additional combinations, with determining best AIC model from there. 

Select NDT: NDT3

```{r}
zones1<-c("NDT3") #Do one zone at a time
prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

########### 1. Climate and vegtype ############
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.clim.vegtype2)){
#  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim.vegtype2[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, veg_escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim.vegtype2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$NDT<-c("NDT3")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}

```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_all_NDT3_escape_climate<-table.glm.climate.simple

AIC_all_NDT3_escape_summary_climate<- AIC_all_NDT3_escape_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_all_NDT3_escape_summary_climate2<- AIC_all_NDT3_escape_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_all_NDT3_escape_summary_climate2)
```

#Now repeat for VRI data

```{r}
########### 2. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.VRI)){
#  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$NDT<-c("NDT3")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_all_NDT3_escape_VRI<-table.glm.VRI.simple

AIC_all_NDT3_escape_summary_VRI<- AIC_all_NDT3_escape_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_all_NDT3_escape_summary_VRI2<- AIC_all_NDT3_escape_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_all_NDT3_escape_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 3. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$NDT<-c("NDT3")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_all_NDT3_escape_topo<-table.glm.topo.simple

AIC_all_NDT3_escape_summary_topo<- AIC_all_NDT3_escape_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_all_NDT3_escape_summary_topo2<- AIC_all_NDT3_escape_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_all_NDT3_escape_summary_topo2)
```

#Now repeat for infrastructure

```{r}
########### 4. Distance to Infrastructure ############
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.infra)){
#  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT3")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_all_NDT3_escape_infra<-table.glm.infra.simple

AIC_all_NDT3_escape_summary_infra<- AIC_all_NDT3_escape_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_all_NDT3_escape_summary_infra2<- AIC_all_NDT3_escape_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_all_NDT3_escape_summary_infra2)

```

#Now repeat for Tdif and windspeed

```{r}
########### 5. Tdif and windspeed ############
#Create empty table
table.glm.Tdif_wind.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.Tdif_wind.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- Escape_data_ALL %>% dplyr::filter(ntrl_ds ==zones1[h])

#for (i in 1: length(all.poss.mods.Tdif_wind)){
#  print(paste((all.poss.mods.Tdif_wind[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.Oth2[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(escape, escape, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(escape, escape, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="escape") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.Oth2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.Tdif_wind <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.Tdif_wind$NDT<-c("NDT3")
tab.sum.Tdif_wind 

table.glm.Tdif_wind.simple<-rbind(table.glm.Tdif_wind.simple, tab.sum.Tdif_wind)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.Tdif_wind.simple)
table(table.glm.Tdif_wind.simple$model) # 100 per model

AIC_all_NDT3_escape_Tdif_wind<-table.glm.Tdif_wind.simple

AIC_all_NDT3_escape_summary_Tdif_wind<- AIC_all_NDT3_escape_Tdif_wind %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_all_NDT3_escape_summary_Tdif_wind2<- AIC_all_NDT3_escape_summary_Tdif_wind %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_all_NDT3_escape_summary_Tdif_wind2)

```

#Now combine the datatables and save to computer

```{r}
NDT3_all_models<-rbind(AIC_all_NDT3_escape_summary_climate2, AIC_all_NDT3_escape_summary_VRI2, AIC_all_NDT3_escape_summary_topo2, AIC_all_NDT3_escape_summary_infra2, AIC_all_NDT3_escape_summary_Tdif_wind2)
NDT3_all_models
NDT3_all_models$NDT<-"NDT3"

write.csv(NDT3_all_models, file="D:\\Fire\\fire_data\\raw_data\\NDT3_ALL_models_escape.csv")
```

################################ STAGE TWO ########################

#STAGE TWO: PUT TOGETHER MORE VARIABLES AND MANUALLY ASSESS
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Models:
1. climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + climate2:mdc_atfire + vegtype2:mdc_atfire
2. proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2
3. slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire
4. dist_infra + roads_km + dist_infra:roads_km
5. wind_atfire + Tdif_atfire

Additional Variables:
1. fire_cs (whether fire was lightning or person caused, or unknown)

#Interactions to investigate:
1. elevation*climate1
2. elevation*climate2
3. wind_atfire*climate1
4. wind_atfire*climate2
5. wind_atfire*vegtype2
6. Tdif_atfire*climate1
7. Tdif_atfire*climate2

#Next investigation
Because there would be far too many models to investigate including all variables and their interactions, we will start with the above and make educated guesses for what may need to be enhanced. We will seek the best model from the above informed progress.

```{r}
escape_all_t_NDT3<-subset(Escape_data_ALL, Escape_data_ALL$ntrl_ds=="NDT3") #12133
table(escape_all_t_NDT3$fire_cs)
table(escape_all_t_NDT3$bclcs_level_2)

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_all_t_NDT3$escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_all_t_NDT3[ trainIndex,]
   Valid <- escape_all_t_NDT3[-trainIndex,]

#Run model using dat1
model.NDT3.E<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + climate2:mdc_atfire + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire + dist_infra + roads_km + dist_infra:roads_km + Tdif_atfire + elevation*climate1  + elevation*climate2 + wind_atfire*climate1 + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + fire_cs + fire_cs*climate1 + fire_cs*vegtype2 + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*climate1 + bclcs_level_2*vegtype2 + bclcs_level_2*mdc_atfire + bclcs_level_2*Tdif_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7299.599

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.76 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred"

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + climate2:mdc_atfire + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire + dist_infra + roads_km + dist_infra:roads_km + Tdif_atfire + elevation*climate1  + elevation*climate2 + wind_atfire*climate1 + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + fire_cs + fire_cs*climate1 + fire_cs*vegtype2 + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7290.9

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.76 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred"  

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + climate2:mdc_atfire + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire + dist_infra + roads_km + dist_infra:roads_km + Tdif_atfire  + elevation*climate2 + wind_atfire*climate1 + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate2 + fire_cs + fire_cs*vegtype2 + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7285.4

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.76 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred"  

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + climate2:mdc_atfire + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + slope:wind_atfire + aspect:elevation + elevation:wind_atfire + dist_infra + roads_km + Tdif_atfire  + elevation*climate2 + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate2 + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7277.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.76 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred" 

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + climate2:mdc_atfire + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + aspect:elevation + dist_infra + roads_km + Tdif_atfire + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate2 + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7274.2

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.76 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred" 

#Remove least significant interaction
model.NDT3.E<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + aspect:elevation + dist_infra + roads_km + Tdif_atfire + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate2 + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7272.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.76 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred" 

```

Compare full model to one with variables (Tave and ppt) for at time of fire.

```{r}
model.NDT3.E<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + aspect:elevation + dist_infra + roads_km + Tdif_atfire + wind_atfire*climate2 + wind_atfire*vegtype2 + Tdif_atfire*climate2 + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7272.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.76 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  


#Compare to temperature and precipitation at month of fire
model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + aspect:elevation + dist_infra + roads_km + Tdif_atfire + wind_atfire*ppt_atfire + wind_atfire*vegtype2 + Tdif_atfire*ppt_atfire + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*dist_infra + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7235.1

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.78 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  

#Remove least significant 
model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + aspect:elevation + dist_infra + roads_km + Tdif_atfire + wind_atfire*vegtype2 + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7229.7

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.78 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  

#Remove least significant 
model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + dist_infra + roads_km + Tdif_atfire + wind_atfire*vegtype2 + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1)

AIC(model.NDT3.E) #7229.2

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.78 --> Good!
   
#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)  


```
Ask self: how will future projections be modelled? Will they be modelled by year total, or will they be modelled by month within year and brought together? Using tave_09, will model by year; if use Tmax_atfire, then can model by month. Which is preferred? Using temperature at time of fire creates a better model.

For now, use Tmax and ppt at time of fire.

Remove NAs and run multiple times.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT3_escape_t<-escape_all_t_NDT3 %>% drop_na(Tmax_atfire, ppt_atfire, mdc_atfire, vegtype2, live_stand_volume_125, proj_height_1, proj_age_1, dist_infra, bclcs_level_2, slope, aspect, elevation, wind_atfire, Tdif_atfire, roads_km, fire_cs) #11406 observations
table(NDT3_escape_t$vegtype2)

#Run Model again with this data; but uses all data here
model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + dist_infra + roads_km + Tdif_atfire + wind_atfire*vegtype2 + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = NDT3_escape_t)

#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE) #P-values did not work; need to reduce something in model

model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*Tdif_atfire + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = NDT3_escape_t)

#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)

model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = NDT3_escape_t)

#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)

model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = NDT3_escape_t)

#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE) # Valid p-values now; reduce interactions further as deemed necessary (with p >0.20)

model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*mdc_atfire + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = NDT3_escape_t)

#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)

model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = NDT3_escape_t)

#Anova(model.NDT3.E, type=3)
Anova(model.NDT3.E, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT3.E), 
            residuals(model.NDT3.E), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT3_escape_t$resids<-resid(model.NDT3.E)

binnedplot (NDT3_escape_t$live_stand_volume_125, 
            NDT3_escape_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT3_escape_t$climate1, 
            NDT3_escape_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good

#Partial Residuals
#Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*dist_infra + bclcs_level_2*roads_km

visreg(model.NDT3.E, "Tmax_atfire")
visreg(model.NDT3.E, "ppt_atfire", by="vegtype2", overlay=TRUE)
visreg(model.NDT3.E, "ppt_atfire", by="vegtype2")
visreg(model.NDT3.E, "vegtype2", by="mdc_atfire")
visreg(model.NDT3.E, "vegtype2", by="ppt_atfire")

visreg(model.NDT3.E, "mdc_atfire", by="vegtype2", overlay=TRUE)
visreg(model.NDT3.E, "mdc_atfire", by="vegtype2")
visreg(model.NDT3.E, "mdc_atfire", by="fire_cs", overlay=TRUE)
visreg(model.NDT3.E, "Tdif_atfire")

visreg(model.NDT3.E, "live_stand_volume_125", by="bclcs_level_2", overlay=TRUE)
visreg(model.NDT3.E, "live_stand_volume_125", by="bclcs_level_2", overlay=TRUE, ylim=c(-6,3)) #L and N messed up because mostly 0s, but not all 0s for N
visreg(model.NDT3.E, "proj_height_1", by="bclcs_level_2", overlay=TRUE)
visreg(model.NDT3.E, "proj_height_1", by="bclcs_level_2", overlay=TRUE, ylim=c(-6,3)) #Missing L
visreg(model.NDT3.E, "proj_age_1")

visreg(model.NDT3.E, "slope", by="elevation")
visreg(model.NDT3.E, "aspect")
visreg(model.NDT3.E, "elevation", by="slope")

visreg(model.NDT3.E, "bclcs_level_2", by="proj_height_1")
visreg(model.NDT3.E, "bclcs_level_2", by="proj_height_1", ylim=c(-1050,50))
visreg(model.NDT3.E, "bclcs_level_2", by="proj_height_1", ylim=c(-10,10))
visreg(model.NDT3.E, "bclcs_level_2", by="live_stand_volume_125", ylim=c(-1050,50))
visreg(model.NDT3.E, "bclcs_level_2", by="live_stand_volume_125", ylim=c(-10,10))
visreg(model.NDT3.E, "bclcs_level_2", by="dist_infra", ylim=c(-1050,50))
visreg(model.NDT3.E, "bclcs_level_2", by="dist_infra", ylim=c(-10,10))
visreg(model.NDT3.E, "bclcs_level_2", by="roads_km", ylim=c(-1050,50))
visreg(model.NDT3.E, "bclcs_level_2", by="roads_km", ylim=c(-10,10))

visreg(model.NDT3.E, "fire_cs", by="mdc_atfire")
visreg(model.NDT3.E, "fire_cs", by="roads_km")

visreg(model.NDT3.E, "dist_infra", by="bclcs_level_2", overlay=TRUE)
visreg(model.NDT3.E, "dist_infra", by="bclcs_level_2", overlay=TRUE, ylim=c(-5,3)) #Missing L

visreg(model.NDT3.E, "roads_km", by="fire_cs", overlay=TRUE)
visreg(model.NDT3.E, "roads_km", by="bclcs_level_2", overlay=TRUE)
visreg(model.NDT3.E, "roads_km", by="bclcs_level_2", overlay=TRUE, ylim=c(-12,2)) #Missing L

visreg(model.NDT3.E, "wind_atfire")

```
#Need to consider what to do with category L (in bclcs_level_2) as data often wonky. Remove entirely?
#Interactions with VRI metrics (age, height, volume) with trees (bclcs_level_2) does make for weird outcomes... may wish to consider removing interaction sicne 0s are present where needed.

```{r}
table(NDT3_escape_t$bclcs_level_2)
```


We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT3.E)
names(model.NDT3.E)
model.NDT3.E[1]

#Create a new blank table and get AUC too
top_mod_table_NDT3_ALL <- data.frame (matrix (ncol = 54, nrow = 0))
colnames (top_mod_table_NDT3_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_Tmax_atfire", "coef_ppt_atfire", "coef_vegtypeOP", "coef_vegtypeRO", "coef_vegtypeS", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_vegtypeUR", "coef_mdc_atfire", "coef_proj_height_1", "coef_proj_age_1", "coef_live_stand_volume_125", "coef_bclcs_level_2N", "coef_bclcs_level_2T", "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_infra", "coef_roads_km", "coef_Tdifatfire", "coef_fire_csPerson", "coef_ppt_atfire:vegtype2OP", "coef_ppt_atfire:vegtype2RO", "coef_ppt_atfire:vegtype2S", "coef_ppt_atfire:vegtype2TB", "coef_ppt_atfire:vegtype2TC", "coef_ppt_atfire:vegtype2TM", "coef_ppt_atfire:vegtype2UR",
                                        "coef_vegtype2OP:mdc_atfire", "coef_vegtype2RO:mdc_atfire", "coef_vegtype2S:mdc_atfire", "coef_vegtype2TB:mdc_atfire", "coef_vegtype2TC:mdc_atfire", "coef_vegtype2TM:mdc_atfire", "coef_vegtype2UR:mdc_atfire", 
                                        "coef_proj_height_1:bclcs_level_2N", "coef_proj_height_1:bclcs_level_2T", "coef_live_stand_volume_125:bclcs_level_2N", "coef_live_stand_volume_125:bclcs_level_2T", "coef_slope:elevation", "coef_mdc_atfire:fire_csPerson", "coef_roads_km:fire_csPerson", "coef_bclcs_level_2N:dist_infra", "coef_bclcs_level_2T:dist_infra", "coef_bclcs_level_2N:roads_km", "coef_bclcs_level_2T:roads_km","AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT3_escape_t$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT3_escape_t[ trainIndex,]
   Valid <- NDT3_escape_t[-trainIndex,]
   
#Model   
model.NDT3.E<-glm(escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*dist_infra + bclcs_level_2*roads_km, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT3.E, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3 <- data.frame (matrix (ncol = 54, nrow = 0))
colnames (top_mod_table_NDT3 ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_Tmax_atfire", "coef_ppt_atfire", "coef_vegtypeOP", "coef_vegtypeRO", "coef_vegtypeS", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_vegtypeUR", "coef_mdc_atfire", "coef_proj_height_1", "coef_proj_age_1", "coef_live_stand_volume_125", "coef_bclcs_level_2N", "coef_bclcs_level_2T", "coef_slope", "coef_aspect", "coef_elevation", "coef_wind_atfire", "coef_dist_infra", "coef_roads_km", "coef_Tdifatfire", "coef_fire_csPerson", "coef_ppt_atfire:vegtype2OP", "coef_ppt_atfire:vegtype2RO", "coef_ppt_atfire:vegtype2S", "coef_ppt_atfire:vegtype2TB", "coef_ppt_atfire:vegtype2TC", "coef_ppt_atfire:vegtype2TM", "coef_ppt_atfire:vegtype2UR",
                                        "coef_vegtype2OP:mdc_atfire", "coef_vegtype2RO:mdc_atfire", "coef_vegtype2S:mdc_atfire", "coef_vegtype2TB:mdc_atfire", "coef_vegtype2TC:mdc_atfire", "coef_vegtype2TM:mdc_atfire", "coef_vegtype2UR:mdc_atfire", 
                                        "coef_proj_height_1:bclcs_level_2N", "coef_proj_height_1:bclcs_level_2T", "coef_live_stand_volume_125:bclcs_level_2N", "coef_live_stand_volume_125:bclcs_level_2T", "coef_slope:elevation", "coef_mdc_atfire:fire_csPerson", "coef_roads_km:fire_csPerson", "coef_bclcs_level_2N:dist_infra", "coef_bclcs_level_2T:dist_infra", "coef_bclcs_level_2N:roads_km", "coef_bclcs_level_2T:roads_km","AUC")

##Add data for NDT3
top_mod_table_NDT3[1,1]<-"lightning, person, unknown"
top_mod_table_NDT3[1,2]<-"NDT3"
top_mod_table_NDT3[1,3]<-"Y and N"
top_mod_table_NDT3[1,4]<-"escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*dist_infra + bclcs_level_2*roads_km" 
top_mod_table_NDT3[1,5]<- coef(model.NDT3.E)[1] #Intercept
top_mod_table_NDT3[1,6]<- coef(model.NDT3.E)[2] #
top_mod_table_NDT3[1,7]<- coef(model.NDT3.E)[3] #
top_mod_table_NDT3[1,8]<- coef(model.NDT3.E)[4] #coefficient 
top_mod_table_NDT3[1,9]<- coef(model.NDT3.E)[5] #coefficient 
top_mod_table_NDT3[1,10]<- coef(model.NDT3.E)[6] #coefficient
top_mod_table_NDT3[1,11]<- coef(model.NDT3.E)[7] #
top_mod_table_NDT3[1,12]<- coef(model.NDT3.E)[8] #coefficient 
top_mod_table_NDT3[1,13]<- coef(model.NDT3.E)[9] #coefficient 
top_mod_table_NDT3[1,14]<- coef(model.NDT3.E)[10] #coefficient
top_mod_table_NDT3[1,15]<- coef(model.NDT3.E)[11] #coefficient
top_mod_table_NDT3[1,16]<- coef(model.NDT3.E)[12] #coefficient
top_mod_table_NDT3[1,17]<- coef(model.NDT3.E)[13] #coefficien
top_mod_table_NDT3[1,18]<- coef(model.NDT3.E)[14] #coefficient 
top_mod_table_NDT3[1,19]<- coef(model.NDT3.E)[15] #
top_mod_table_NDT3[1,20]<- coef(model.NDT3.E)[16] #  
top_mod_table_NDT3[1,21]<- coef(model.NDT3.E)[17] # 
top_mod_table_NDT3[1,22]<- coef(model.NDT3.E)[18] #coefficient 
top_mod_table_NDT3[1,23]<- coef(model.NDT3.E)[19] #coefficient 
top_mod_table_NDT3[1,24]<- coef(model.NDT3.E)[20] #coefficient 
top_mod_table_NDT3[1,25]<- coef(model.NDT3.E)[21] #coefficient 
top_mod_table_NDT3[1,26]<- coef(model.NDT3.E)[22] #coefficient 
top_mod_table_NDT3[1,27]<- coef(model.NDT3.E)[23] #coefficient 
top_mod_table_NDT3[1,28]<- coef(model.NDT3.E)[24] #coefficient 
top_mod_table_NDT3[1,29]<- coef(model.NDT3.E)[25] #coefficient 
top_mod_table_NDT3[1,30]<- coef(model.NDT3.E)[26] #coefficient 
top_mod_table_NDT3[1,31]<- coef(model.NDT3.E)[27] #coefficient 
top_mod_table_NDT3[1,32]<- coef(model.NDT3.E)[28] #coefficient 
top_mod_table_NDT3[1,33]<- coef(model.NDT3.E)[29] #coefficient 
top_mod_table_NDT3[1,34]<- coef(model.NDT3.E)[30] #coefficient 
top_mod_table_NDT3[1,35]<- coef(model.NDT3.E)[31] #coefficient 
top_mod_table_NDT3[1,36]<- coef(model.NDT3.E)[32] #coefficient 
top_mod_table_NDT3[1,37]<- coef(model.NDT3.E)[33] #coefficient 
top_mod_table_NDT3[1,38]<- coef(model.NDT3.E)[34] #coefficient 
top_mod_table_NDT3[1,39]<- coef(model.NDT3.E)[35] #coefficient 
top_mod_table_NDT3[1,40]<- coef(model.NDT3.E)[36] #coefficient 
top_mod_table_NDT3[1,41]<- coef(model.NDT3.E)[37] #coefficient 
top_mod_table_NDT3[1,42]<- coef(model.NDT3.E)[38] #coefficient 
top_mod_table_NDT3[1,43]<- coef(model.NDT3.E)[39] #coefficient 
top_mod_table_NDT3[1,44]<- coef(model.NDT3.E)[40] #coefficient 
top_mod_table_NDT3[1,45]<- coef(model.NDT3.E)[41] #coefficient 
top_mod_table_NDT3[1,46]<- coef(model.NDT3.E)[42] #coefficient 
top_mod_table_NDT3[1,47]<- coef(model.NDT3.E)[43] #coefficient 
top_mod_table_NDT3[1,48]<- coef(model.NDT3.E)[44] #coefficient 
top_mod_table_NDT3[1,49]<- coef(model.NDT3.E)[45] #coefficient
top_mod_table_NDT3[1,50]<- coef(model.NDT3.E)[46] #coefficient 
top_mod_table_NDT3[1,51]<- coef(model.NDT3.E)[47] #coefficient 
top_mod_table_NDT3[1,52]<- coef(model.NDT3.E)[48] #coefficient 
top_mod_table_NDT3[1,53]<- coef(model.NDT3.E)[49] #coefficient 
top_mod_table_NDT3[1,54]<- mod.auc

top_mod_table_NDT3_ALL<-rbind(top_mod_table_NDT3_ALL, top_mod_table_NDT3)

}

```

Check.
```{r}
head(top_mod_table_NDT3_ALL)

```

#Save coefficient table

```{r}
write.csv(top_mod_table_NDT3_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_escape_NDT3_ALL.csv")
```

Get mean values.

```{r}
top_mod_table_NDT3_ALL_mean<-top_mod_table_NDT3_ALL %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table_NDT3_ALL_mean

top_mod_table_NDT3_ALL_mean[1,1]<-"lightning, person, unknown (ALL)"
top_mod_table_NDT3_ALL_mean[1,2]<-"NDT3"
top_mod_table_NDT3_ALL_mean[1,3]<-"ALL Treed and not treed"
top_mod_table_NDT3_ALL_mean[1,4]<-"escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*dist_infra + bclcs_level_2*roads_km" 
top_mod_table_NDT3_ALL_mean #Mean values are odd! Need to rid of outliers
```
Save mean coefficient table.

```{r}
write.csv(top_mod_table_NDT3_ALL_mean, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_ALL_mean.csv")
```

Get SD.

```{r}
top_mod_table_NDT3_ALL_SD<-top_mod_table_NDT3_ALL %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT3_ALL_SD

top_mod_table_NDT3_ALL_SD[1,1]<-"lightning, person, unknown (ALL)"
top_mod_table_NDT3_ALL_SD[1,2]<-"NDT3"
top_mod_table_NDT3_ALL_SD[1,3]<-"ALL Treed and not treed"
top_mod_table_NDT3_ALL_SD[1,4]<-"escape ~ Tmax_atfire + ppt_atfire + vegtype2 + mdc_atfire + ppt_atfire:vegtype2 + vegtype2:mdc_atfire + proj_height_1 + proj_age_1 + live_stand_volume_125 + bclcs_level_2 + proj_height_1:bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:elevation + dist_infra + roads_km + Tdif_atfire  + fire_cs + fire_cs*mdc_atfire + fire_cs*roads_km + bclcs_level_2*dist_infra + bclcs_level_2*roads_km" 
top_mod_table_NDT3_ALL_SD
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT3_ALL_SD, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT3_ALL_SD.csv")
```



############ Validation Type 2: Using recent Years as Validation Dataset ########

Create blank data table.

```{r}
#Create a new blank table and get AUC too
top_mod_table_NDT3_ALL_v2 <- data.frame (matrix (ncol = 41, nrow = 0))
colnames (top_mod_table_NDT3_ALL_v2 ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeOP", "coef_vegtypeRO", "coef_vegtypeS", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_vegtypeUR", "coef_mdc_atfire", "coef_live_stand_volume_125", "coef_bclcs_level_2N", "coef_bclcs_level_2T", "coef_slope", "coef_aspect", "coef_elevation","coef_wind_atfire", "coef_dist_infra", "coef_roads_km", "coef_Tdifatfire", "coef_fire_csPerson", "coef_climate2:mdc_atfire", "coef_live_stand_volume_125:bclcs_level_2N", "coef_live_stand_volume_125:bclcs_level_2T", "coef_slope:aspect", "coef_dist_infra:roads_km", "coef_climate2:elevation", "coef_climate1:Tdif_atfire", "coef_climate2:Tdif_atfire", "coef_dist_infra:fire_csPerson", "coef_roads_km:fire_csPerson", "coef_elevation:fire_csPerson", "coef_Tdif_atfire:fire_csPerson", "coef_climate1:bclcs_level_2N", "coef_climate1:bclcs_level_2T", "AUC")
```

```{r}
dat1 <- subset(NDT3_escape_t, NDT3_escape_t$fire_yr<2018) #10235
Valid <- subset(NDT3_escape_t, NDT3_escape_t$fire_yr>2017) #1171

table(dat1$fire_yr)
table(Valid$fire_yr) #No 2020?
```


```{r}
#Model   
model.NDT3.E.v2<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:mdc_atfire + live_stand_volume_125 + bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + dist_infra + roads_km + dist_infra:roads_km + wind_atfire + Tdif_atfire  + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + fire_cs + fire_cs*dist_infra + fire_cs*roads_km + fire_cs*elevation + fire_cs*Tdif_atfire + bclcs_level_2*climate1, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT3.E.v2, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3 <- data.frame (matrix (ncol = 41, nrow = 0))
colnames (top_mod_table_NDT3 ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeOP", "coef_vegtypeRO", "coef_vegtypeS", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_vegtypeUR", "coef_mdc_atfire", "coef_live_stand_volume_125", "coef_bclcs_level_2N", "coef_bclcs_level_2T", "coef_slope", "coef_aspect", "coef_elevation","coef_wind_atfire", "coef_dist_infra", "coef_roads_km", "coef_Tdifatfire", "coef_fire_csPerson", "coef_climate2:mdc_atfire", "coef_live_stand_volume_125:bclcs_level_2N", "coef_live_stand_volume_125:bclcs_level_2T", "coef_slope:aspect", "coef_dist_infra:roads_km", "coef_climate2:elevation", "coef_climate1:Tdif_atfire", "coef_climate2:Tdif_atfire", "coef_dist_infra:fire_csPerson", "coef_roads_km:fire_csPerson", "coef_elevation:fire_csPerson", "coef_Tdif_atfire:fire_csPerson", "coef_climate1:bclcs_level_2N", "coef_climate1:bclcs_level_2T", "AUC")

##Add data for NDT3
top_mod_table_NDT3[1,1]<-"lightning, person, unknown"
top_mod_table_NDT3[1,2]<-"NDT3"
top_mod_table_NDT3[1,3]<-"Y andN"
top_mod_table_NDT3[1,4]<-"escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:mdc_atfire + live_stand_volume_125 + bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + dist_infra + roads_km + dist_infra:roads_km + wind_atfire + Tdif_atfire  + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + fire_cs + fire_cs*dist_infra + fire_cs*roads_km + fire_cs*elevation + fire_cs*Tdif_atfire + bclcs_level_2*climate1" 
top_mod_table_NDT3[1,5]<- coef(model.NDT3.E.v2)[1] #Intercept
top_mod_table_NDT3[1,6]<- coef(model.NDT3.E.v2)[2] #
top_mod_table_NDT3[1,7]<- coef(model.NDT3.E.v2)[3] #
top_mod_table_NDT3[1,8]<- coef(model.NDT3.E.v2)[4] #coefficient 
top_mod_table_NDT3[1,9]<- coef(model.NDT3.E.v2)[5] #coefficient 
top_mod_table_NDT3[1,10]<- coef(model.NDT3.E.v2)[6] #coefficient
top_mod_table_NDT3[1,11]<- coef(model.NDT3.E.v2)[7] #
top_mod_table_NDT3[1,12]<- coef(model.NDT3.E.v2)[8] #coefficient 
top_mod_table_NDT3[1,13]<- coef(model.NDT3.E.v2)[9] #coefficient 
top_mod_table_NDT3[1,14]<- coef(model.NDT3.E.v2)[10] #coefficient
top_mod_table_NDT3[1,15]<- coef(model.NDT3.E.v2)[11] #coefficient
top_mod_table_NDT3[1,16]<- coef(model.NDT3.E.v2)[12] #coefficient
top_mod_table_NDT3[1,17]<- coef(model.NDT3.E.v2)[13] #coefficien
top_mod_table_NDT3[1,18]<- coef(model.NDT3.E.v2)[14] #coefficient 
top_mod_table_NDT3[1,19]<- coef(model.NDT3.E.v2)[15] #
top_mod_table_NDT3[1,20]<- coef(model.NDT3.E.v2)[16] #  
top_mod_table_NDT3[1,21]<- coef(model.NDT3.E.v2)[17] # 
top_mod_table_NDT3[1,22]<- coef(model.NDT3.E.v2)[18] #coefficient 
top_mod_table_NDT3[1,23]<- coef(model.NDT3.E.v2)[19] #coefficient 
top_mod_table_NDT3[1,24]<- coef(model.NDT3.E.v2)[20] #coefficient 
top_mod_table_NDT3[1,25]<- coef(model.NDT3.E.v2)[21] #coefficient 
top_mod_table_NDT3[1,26]<- coef(model.NDT3.E.v2)[22] #coefficient 
top_mod_table_NDT3[1,27]<- coef(model.NDT3.E.v2)[23] #coefficient 
top_mod_table_NDT3[1,28]<- coef(model.NDT3.E.v2)[24] #coefficient 
top_mod_table_NDT3[1,29]<- coef(model.NDT3.E.v2)[25] #coefficient 
top_mod_table_NDT3[1,30]<- coef(model.NDT3.E.v2)[26] #coefficient 
top_mod_table_NDT3[1,31]<- coef(model.NDT3.E.v2)[27] #coefficient 
top_mod_table_NDT3[1,32]<- coef(model.NDT3.E.v2)[28] #coefficient 
top_mod_table_NDT3[1,33]<- coef(model.NDT3.E.v2)[29] #coefficient 
top_mod_table_NDT3[1,34]<- coef(model.NDT3.E.v2)[30] #coefficient 
top_mod_table_NDT3[1,35]<- coef(model.NDT3.E.v2)[31] #coefficient 
top_mod_table_NDT3[1,36]<- coef(model.NDT3.E.v2)[32] #coefficient 
top_mod_table_NDT3[1,37]<- coef(model.NDT3.E.v2)[33] #coefficient 
top_mod_table_NDT3[1,38]<- coef(model.NDT3.E.v2)[34] #coefficient 
top_mod_table_NDT3[1,39]<- coef(model.NDT3.E.v2)[35] #coefficient 
top_mod_table_NDT3[1,40]<- coef(model.NDT3.E.v2)[36] #coefficient 
top_mod_table_NDT3[1,41]<- mod.auc

top_mod_table_NDT3_ALL_v2<-rbind(top_mod_table_NDT3_ALL_v2, top_mod_table_NDT3)
```

View.
```{r}
head(top_mod_table_NDT3_ALL_v2) #AUC 0.71 this way; not bad
```
Divide by one year earlier given lack of 2020


```{r}
#Create a new blank table and get AUC too
top_mod_table_NDT3_ALL_v2 <- data.frame (matrix (ncol = 41, nrow = 0))
colnames (top_mod_table_NDT3_ALL_v2 ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeOP", "coef_vegtypeRO", "coef_vegtypeS", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_vegtypeUR", "coef_mdc_atfire", "coef_live_stand_volume_125", "coef_bclcs_level_2N", "coef_bclcs_level_2T", "coef_slope", "coef_aspect", "coef_elevation","coef_wind_atfire", "coef_dist_infra", "coef_roads_km", "coef_Tdifatfire", "coef_fire_csPerson", "coef_climate2:mdc_atfire", "coef_live_stand_volume_125:bclcs_level_2N", "coef_live_stand_volume_125:bclcs_level_2T", "coef_slope:aspect", "coef_dist_infra:roads_km", "coef_climate2:elevation", "coef_climate1:Tdif_atfire", "coef_climate2:Tdif_atfire", "coef_dist_infra:fire_csPerson", "coef_roads_km:fire_csPerson", "coef_elevation:fire_csPerson", "coef_Tdif_atfire:fire_csPerson", "coef_climate1:bclcs_level_2N", "coef_climate1:bclcs_level_2T", "AUC")
```

```{r}
dat1 <- subset(NDT3_escape_t, NDT3_escape_t$fire_yr<2017) #9656
Valid <- subset(NDT3_escape_t, NDT3_escape_t$fire_yr>2016) #1750

table(dat1$fire_yr)
table(Valid$fire_yr) #No 2020?
```


```{r}
#Model   
model.NDT3.E.v2<-glm(escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:mdc_atfire + live_stand_volume_125 + bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + dist_infra + roads_km + dist_infra:roads_km + wind_atfire + Tdif_atfire  + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + fire_cs + fire_cs*dist_infra + fire_cs*roads_km + fire_cs*elevation + fire_cs*Tdif_atfire + bclcs_level_2*climate1, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT3.E.v2, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT3 <- data.frame (matrix (ncol = 41, nrow = 0))
colnames (top_mod_table_NDT3 ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtypeOP", "coef_vegtypeRO", "coef_vegtypeS", "coef_vegtypeTB", "coef_vegtypeTC", "coef_vegtypeTM", "coef_vegtypeUR", "coef_mdc_atfire", "coef_live_stand_volume_125", "coef_bclcs_level_2N", "coef_bclcs_level_2T", "coef_slope", "coef_aspect", "coef_elevation","coef_wind_atfire", "coef_dist_infra", "coef_roads_km", "coef_Tdifatfire", "coef_fire_csPerson", "coef_climate2:mdc_atfire", "coef_live_stand_volume_125:bclcs_level_2N", "coef_live_stand_volume_125:bclcs_level_2T", "coef_slope:aspect", "coef_dist_infra:roads_km", "coef_climate2:elevation", "coef_climate1:Tdif_atfire", "coef_climate2:Tdif_atfire", "coef_dist_infra:fire_csPerson", "coef_roads_km:fire_csPerson", "coef_elevation:fire_csPerson", "coef_Tdif_atfire:fire_csPerson", "coef_climate1:bclcs_level_2N", "coef_climate1:bclcs_level_2T", "AUC")

##Add data for NDT3
top_mod_table_NDT3[1,1]<-"lightning, person, unknown"
top_mod_table_NDT3[1,2]<-"NDT3"
top_mod_table_NDT3[1,3]<-"Y andN"
top_mod_table_NDT3[1,4]<-"escape ~ climate1 + climate2 + vegtype2 + mdc_atfire + climate2:mdc_atfire + live_stand_volume_125 + bclcs_level_2 + live_stand_volume_125:bclcs_level_2 + slope + aspect + elevation + wind_atfire + slope:aspect + dist_infra + roads_km + dist_infra:roads_km + wind_atfire + Tdif_atfire  + elevation*climate2 + Tdif_atfire*climate1 + Tdif_atfire*climate2 + fire_cs + fire_cs*dist_infra + fire_cs*roads_km + fire_cs*elevation + fire_cs*Tdif_atfire + bclcs_level_2*climate1" 
top_mod_table_NDT3[1,5]<- coef(model.NDT3.E.v2)[1] #Intercept
top_mod_table_NDT3[1,6]<- coef(model.NDT3.E.v2)[2] #
top_mod_table_NDT3[1,7]<- coef(model.NDT3.E.v2)[3] #
top_mod_table_NDT3[1,8]<- coef(model.NDT3.E.v2)[4] #coefficient 
top_mod_table_NDT3[1,9]<- coef(model.NDT3.E.v2)[5] #coefficient 
top_mod_table_NDT3[1,10]<- coef(model.NDT3.E.v2)[6] #coefficient
top_mod_table_NDT3[1,11]<- coef(model.NDT3.E.v2)[7] #
top_mod_table_NDT3[1,12]<- coef(model.NDT3.E.v2)[8] #coefficient 
top_mod_table_NDT3[1,13]<- coef(model.NDT3.E.v2)[9] #coefficient 
top_mod_table_NDT3[1,14]<- coef(model.NDT3.E.v2)[10] #coefficient
top_mod_table_NDT3[1,15]<- coef(model.NDT3.E.v2)[11] #coefficient
top_mod_table_NDT3[1,16]<- coef(model.NDT3.E.v2)[12] #coefficient
top_mod_table_NDT3[1,17]<- coef(model.NDT3.E.v2)[13] #coefficien
top_mod_table_NDT3[1,18]<- coef(model.NDT3.E.v2)[14] #coefficient 
top_mod_table_NDT3[1,19]<- coef(model.NDT3.E.v2)[15] #
top_mod_table_NDT3[1,20]<- coef(model.NDT3.E.v2)[16] #  
top_mod_table_NDT3[1,21]<- coef(model.NDT3.E.v2)[17] # 
top_mod_table_NDT3[1,22]<- coef(model.NDT3.E.v2)[18] #coefficient 
top_mod_table_NDT3[1,23]<- coef(model.NDT3.E.v2)[19] #coefficient 
top_mod_table_NDT3[1,24]<- coef(model.NDT3.E.v2)[20] #coefficient 
top_mod_table_NDT3[1,25]<- coef(model.NDT3.E.v2)[21] #coefficient 
top_mod_table_NDT3[1,26]<- coef(model.NDT3.E.v2)[22] #coefficient 
top_mod_table_NDT3[1,27]<- coef(model.NDT3.E.v2)[23] #coefficient 
top_mod_table_NDT3[1,28]<- coef(model.NDT3.E.v2)[24] #coefficient 
top_mod_table_NDT3[1,29]<- coef(model.NDT3.E.v2)[25] #coefficient 
top_mod_table_NDT3[1,30]<- coef(model.NDT3.E.v2)[26] #coefficient 
top_mod_table_NDT3[1,31]<- coef(model.NDT3.E.v2)[27] #coefficient 
top_mod_table_NDT3[1,32]<- coef(model.NDT3.E.v2)[28] #coefficient 
top_mod_table_NDT3[1,33]<- coef(model.NDT3.E.v2)[29] #coefficient 
top_mod_table_NDT3[1,34]<- coef(model.NDT3.E.v2)[30] #coefficient 
top_mod_table_NDT3[1,35]<- coef(model.NDT3.E.v2)[31] #coefficient 
top_mod_table_NDT3[1,36]<- coef(model.NDT3.E.v2)[32] #coefficient 
top_mod_table_NDT3[1,37]<- coef(model.NDT3.E.v2)[33] #coefficient 
top_mod_table_NDT3[1,38]<- coef(model.NDT3.E.v2)[34] #coefficient 
top_mod_table_NDT3[1,39]<- coef(model.NDT3.E.v2)[35] #coefficient 
top_mod_table_NDT3[1,40]<- coef(model.NDT3.E.v2)[36] #coefficient 
top_mod_table_NDT3[1,41]<- mod.auc

top_mod_table_NDT3_ALL_v2<-rbind(top_mod_table_NDT3_ALL_v2, top_mod_table_NDT3)
```

View.
```{r}
head(top_mod_table_NDT3_ALL_v2) #New AUC 0.69; better first way
```
