---
title: "15a_fire_escape_model_selection_NDT1_ALLPL_ALLTNT"
author: "Cora Skaien & Elizabeth Kleynhans"
date: "27/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load relevant libraries
library(sf)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(RPostgreSQL)
library(rpostgis)
library(dplyr)
library(lme4)
library(arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(ggcorrplot) 
library(kableExtra)
library(data.table)
library(DBI)
library(here)
library(AICcmodavg)
library(rje)
library(base)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 12a_fire_escape_model_selection_NDT1_ALLPL_ALLTNT.R
#  Script Version: 1.0
#  Script Purpose: Model selection for escape by NDT.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

Load in the prepped data.

```{r}
escape <- st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\escape_weather_veg.gpkg")
head(escape)
dim(escape)
escape$escape9<- NA
escape$escape9[escape$CURRENT_SIZE > 16] <- 1
escape$escape9[escape$CURRENT_SIZE <= 16] <- 0

escape<-escape %>% st_drop_geometry()



table(is.na(escape$Cluster)) # wierd there are 13 points that have no Cluster assigned to them. I looked at these points in Qgis and all but one of them are in FRT =15.
escape$Cluster[escape$idno==15511]<-13
escape$Cluster[escape$idno==31609]<-13
escape$Cluster[escape$idno==15214]<-13
escape$Cluster[escape$idno==15507]<-13
escape$Cluster[escape$idno==10828]<-13
escape$Cluster[escape$idno==119]<-14
escape$Cluster[escape$idno==20067]<-14
escape$Cluster[escape$idno==965]<-14
escape$Cluster[escape$idno==22140]<-14
escape$Cluster[escape$idno==26529]<-14
escape$Cluster[escape$idno==32226]<-14
escape$Cluster[escape$idno==27182]<-14
escape$Cluster[escape$idno==719]<-14
escape$Cluster[escape$idno==14884]<-14
escape$Cluster[escape$idno==23161]<-14
escape$Cluster[escape$idno==20054]<-14
escape$Cluster[escape$idno==21163]<-14
escape$Cluster[escape$idno==1832]<-14
escape$Cluster[escape$idno==31495]<-14

escape$Cluster[is.na(escape$Cluster)]<-15
escape$Cluster[escape$Cluster==3]<-5
escape$Cluster[escape$Cluster==9]<-11

# note Im going to combine frt9 and frt11. I re-ran the climate variable selection with both frt 9 and 11 combined results in the top climate variable being summer_Tave
#11,	summer_Tave,	mean_AIC=338.338939,	means_AUC=0.647411386,	sd_AUC=0.054643964,	delta_AIC=0

table(escape$Cluster)
table(escape$ig_mnth)
 
```

#note there are a few ignitions in the months January and December. For now Im going to filter these out but maybe I should include them in the future. Presumabily non of these fires escape
```{r}
hist(as.numeric(escape$ig_mnth))

climate_escape<-read.csv("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\climate_AIC_results_escape_summary_March2023.csv")

escape$Cluster_numeric<-as.numeric(as.character(escape$Cluster))

escape$tot_spring_PPT<-escape$PPT04+ escape$PPT05 + escape$PPT06
escape$tot_summer_PPT<-escape$PPT07+ escape$PPT08 + escape$PPT09
escape$summer_Tmax<-(escape$Tmax07+ escape$Tmax08 + escape$Tmax09)/3
escape$spring_Tave<-(escape$Tave04+ escape$Tave05 + escape$Tave06)/3
escape$summer_Tave<-(escape$Tave07+ escape$Tave08 + escape$Tave09)/3
escape$mean_PPT06_PPT07_PPT08  <-(escape$PPT06 + escape$PPT07 + escape$PPT08)/3
escape$mean_PPT05_PPT06  <-(escape$PPT05 + escape$PPT06)/2

## Create empty vector
escape$climate1<-0
head(escape)

escape<-escape %>%
    mutate(climate1 = case_when(Cluster_numeric == 5 ~ as.numeric(PPT05), 
                                Cluster_numeric == 7 ~ as.numeric(mean_PPT06_PPT07_PPT08), 
                                #Cluster_numeric == 9 ~ Tave05, 
                                Cluster_numeric == 10 ~ as.numeric(tot_spring_PPT),
                                Cluster_numeric == 11 ~ summer_Tave, 
                                Cluster_numeric == 12 ~ spring_Tave,
                                Cluster_numeric == 13 ~ summer_Tmax,
                                Cluster_numeric == 14 ~ as.numeric(mean_PPT05_PPT06),
                                Cluster_numeric == 15 ~ summer_Tave,
                                TRUE ~ NA_real_))

#Repeat for climate 2
escape$climate2<-0

#Perform mutate to get the applicable variable for each row
escape<-escape %>%
    mutate(climate2 = case_when(Cluster_numeric == 12 ~ as.numeric(tot_spring_PPT),
                                Cluster_numeric == 13 ~ as.numeric(tot_summer_PPT),
                                Cluster_numeric == 15 ~ as.numeric(tot_summer_PPT),
                                TRUE ~ NA_real_))

head(escape)

# before running any models wer are going to remove W and N because fires cannot spread on this landscape type.

escape2<-escape %>% filter(FWI_veg != "W")
escape2$veg_escape<-paste(escape2$escape9, escape2$FWI_veg)
```


################################ STAGE TWO ########################

#STAGE TWO: PUT TOGETHER MORE VARIABLES AND MANUALLY ASSESS
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Variables common to most:
1. climate1 + climate2 + vegtype2
2. Slope + elevation + wind_atfire
3. Road dist

Additional Variables:
1. fire_cs (whether fire was lightning or person caused, or unknown)


#Next investigation
Because there would be far too many models to investigate including all variables and their interactions, we will start with the above and make educated guesses for what may need to be enhanced. We will seek the best model from the above informed progress.


#### FRT 5
```{r}

escape_frt5<- escape2 %>% filter(Cluster==5)

table(is.na(escape_frt5$climate1))
table(is.na(escape_frt5$dem_ha_bc))
table(is.na(escape_frt5$FWI_veg))
table(is.na(escape_frt5$dist_roads_m))
table(is.na(escape_frt5$slope_ha_bc_3005))
table(is.na(escape_frt5$escape9))

cor.test(escape_frt5$climate1, escape_frt5$dem_ha_bc)
cor.test(escape_frt5$climate1, escape_frt5$slope_ha_bc_3005)
cor.test(escape_frt5$dem_ha_bc, escape_frt5$slope_ha_bc_3005)
cor.test(escape_frt5$dist_roads_m, escape_frt5$dist_infrastructure_m)

escape_frt5$log_road<-log(escape_frt5$dist_roads_m+1)
escape_frt5$log_infra<-log(escape_frt5$dist_infrastructure_m+1)

table(escape_frt5$FWI_veg, escape_frt5$escape9)

escape_frt5$FWI_veg[escape_frt5$FWI_veg=="C-7"]<-"D-1/2"

escape_frt5<- escape_frt5 %>% filter(FWI_veg!="N")

#Run model using dat1
model_ft5<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + win_spg + log_road +log_infra, family = binomial, data = escape_frt5)
# 1104

model_ft5<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + win_spg + dist_roads_m +log_infra, family = binomial, data = escape_frt5)
# 1101

model_ft5<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + win_spg + log_road +dist_infrastructure_m, family = binomial, data = escape_frt5)
# 1097

model_ft5<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + win_spg + dist_roads_m +dist_infrastructure_m, family = binomial, data = escape_frt5)
# 1099

model_ft5<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + win_spg + log_road +dist_infrastructure_m, family = binomial, data = escape_frt5)
AIC(model_ft5) #1097
Anova(model_ft5, type=3)

model_ft5b<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + win_spg + log_road +dist_infrastructure_m, family = binomial, data = escape_frt5)

AIC(model_ft5b) #1095
Anova(model_ft5b, type=3)

model_ft5c<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + log_road +dist_infrastructure_m, family = binomial, data = escape_frt5)
AIC(model_ft5c) #1092
Anova(model_ft5c, type=3)

#######################
### TOP MODEL
#######################
model_ft5d<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + log_road +dist_infrastructure_m, family = binomial, data = escape_frt5)

hist(escape_frt5$climate1)
hist(escape_frt5$dem_ha_bc)
hist(escape_frt5$dist_infrastructure_m)
hist(escape_frt5$log_road)

table(escape_frt5$escape9) #0 = 974 and 1 = 220 not bad actually.
table(escape_frt5$FWI_veg)
```


```{r}
# model diagnostic plots
binnedplot (fitted(model_ft5d), 
            residuals(model_ft5d), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")

escape_frt5<-escape_frt5 %>% drop_na(dem_ha_bc)
escape_frt5<-escape_frt5 %>% drop_na(escape9)
escape_frt5$resids<-resid(model_ft5d)

binnedplot (escape_frt5$climate1, 
            escape_frt5$resids, 
            nclass = NULL)

binnedplot (escape_frt5$dem_ha_bc, 
            escape_frt5$resids,  
            nclass = NULL)

binnedplot (escape_frt5$dist_infrastructure_m, 
            escape_frt5$resids,  
            nclass = NULL)

binnedplot (escape_frt5$log_road, 
            escape_frt5$resids,  
            nclass = NULL)

# Diagnostic plots look good

#Partial Residuals
library(visreg)
visreg(model_ft5d)

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft5d)

#Create a new blank table and get AUC too
top_mod_table_FRT5_ALL <- data.frame (matrix (ncol = 13, nrow = 0))
colnames (top_mod_table_FRT5_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_FWI_veg_C-2",
                                         "coef_FWI_veg_C-3",
                                         "coef_FWI_veg_D-1/2",
                                         "coef_FWI_veg_M-1/2",
                                         "coef_FWI_veg_O-1a/b",
                                         "coef_elevation",
                                         "coef_log_road",
                                         "coef_dist_infra",
                                         "AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:100){
  
  print(g)

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_frt5$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_frt5[ trainIndex,]
   Valid <- escape_frt5[-trainIndex,]
   
#Model   
model.FRT5<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + log_road +dist_infrastructure_m, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.FRT5, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT5 <- data.frame (matrix (ncol = 13, nrow = 0))
colnames (top_mod_table_FRT5 ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_FWI_veg_C-2",
                                         "coef_FWI_veg_C-3",
                                         "coef_FWI_veg_D-1/2",
                                         "coef_FWI_veg_M-1/2",
                                         "coef_FWI_veg_O-1a/b",
                                         "coef_elevation",
                                         "coef_log_road",
                                         "coef_dist_infra",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT5[1,1]<-"5"
top_mod_table_FRT5[1,2]<-"escape16 ~ climate1 + FWI_veg + dem_ha_bc + log_road +dist_infrastructure_m" 
top_mod_table_FRT5[1,3]<- coef(model.FRT5)[1] #Intercept
top_mod_table_FRT5[1,4]<- coef(model.FRT5)[2] #
top_mod_table_FRT5[1,5]<- coef(model.FRT5)[3] #
top_mod_table_FRT5[1,6]<- coef(model.FRT5)[4] #coefficient 
top_mod_table_FRT5[1,7]<- coef(model.FRT5)[5] #coefficient 
top_mod_table_FRT5[1,8]<- coef(model.FRT5)[6] #coefficient
top_mod_table_FRT5[1,9]<- coef(model.FRT5)[7] #
top_mod_table_FRT5[1,10]<- coef(model.FRT5)[8] #coefficient 
top_mod_table_FRT5[1,11]<- coef(model.FRT5)[9] #coefficient
top_mod_table_FRT5[1,12]<- coef(model.FRT5)[10] #coefficient
top_mod_table_FRT5[1,13]<- mod.auc

top_mod_table_FRT5_ALL<-rbind(top_mod_table_FRT5_ALL, top_mod_table_FRT5)

}

```

Check.
```{r}
head(top_mod_table_FRT5_ALL)

```

Get mean values.

```{r}
names(top_mod_table_FRT5_ALL)
str(top_mod_table_FRT5_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

FRT5_summary_table_mean<- top_mod_table_FRT5_ALL %>% summarize_if(is.numeric,mean)

FRT5_summary_table_mean$FRT<-5
FRT5_summary_table_mean$Model_terms<-"escape16 ~ climate1 + FWI_veg + dem_ha_bc + log_road +dist_infrastructure_m"

```

Save table.

```{r}
write.csv(FRT5_summary_table_mean, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT5_escape.csv")
```


#### FRT 7
```{r}

escape_frt7<- escape2 %>% filter(Cluster==7)
table(escape_frt7$FWI_veg, escape_frt7$escape9)
escape_frt7$FWI_veg[escape_frt7$FWI_veg=="C-1"]<-"C-3"
escape_frt7$FWI_veg[escape_frt7$FWI_veg=="N"]<-"D-1/2"
escape_frt7$FWI_veg[escape_frt7$FWI_veg=="C-7"]<-"M-1/2"
escape_frt7$FWI_veg[escape_frt7$FWI_veg=="S-1"]<-"M-1/2"
escape_frt7$veg_escape<-paste(escape_frt7$fire, escape_frt7$FWI_veg)

table(is.na(escape_frt7$climate1))
table(is.na(escape_frt7$dem_ha_bc))
table(is.na(escape_frt7$FWI_veg))
table(is.na(escape_frt7$dist_roads_m))
table(is.na(escape_frt7$slope_ha_bc_3005))
table(is.na(escape_frt7$win_spg))
table(is.na(escape_frt7$escape9))


cor.test(escape_frt7$climate1, escape_frt7$dem_ha_bc)
cor.test(escape_frt7$climate1, escape_frt7$slope_ha_bc_3005)
cor.test(escape_frt7$dem_ha_bc, escape_frt7$slope_ha_bc_3005)
cor.test(escape_frt7$dist_roads_m, escape_frt7$dist_infrastructure_m  )

escape_frt7$log_road<-log(escape_frt7$dist_roads_m+1)
escape_frt7$log_infr<-log(escape_frt7$dist_infrastructure_m  +1)

#Run model using dat1
model_ft7<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + log_road + log_infr + win_spg, family = binomial, data = escape_frt7)
#877

model_ft7<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + dist_roads_m + log_infr + win_spg, family = binomial, data = escape_frt7)
# 879

model_ft7<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + log_road + dist_infrastructure_m + win_spg, family = binomial, data = escape_frt7)
# 878

model_ft7<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + dist_roads_m + dist_infrastructure_m + win_spg, family = binomial, data = escape_frt7) # 881

model_ft7<-glm(escape9 ~ climate1 + FWI_veg + slope_ha_bc_3005 + dem_ha_bc + log_road + log_infr + win_spg, family = binomial, data = escape_frt7)

AIC(model_ft7) #877.0447
Anova(model_ft7, type=3) 

model_ft7b<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + log_road + log_infr + win_spg, family = binomial, data = escape_frt7)

AIC(model_ft7b) #875.0447
Anova(model_ft7b, type=3) 

model_ft7c<-glm(escape9 ~ climate1 + FWI_veg + log_road + log_infr + win_spg, family = binomial, data = escape_frt7)

AIC(model_ft7c) #873.0725
Anova(model_ft7c, type=3) 

model_ft7d<-glm(escape9 ~ climate1 + FWI_veg + log_road + log_infr, family = binomial, data = escape_frt7)

AIC(model_ft7d) #871
Anova(model_ft7d, type=3) 

model_ft7e<-glm(escape9 ~ climate1 + FWI_veg + log_road, family = binomial, data = escape_frt7)

AIC(model_ft7e) #872.8035
Anova(model_ft7e, type=3) 

model_ft7f<-glm(escape9 ~ climate1 + log_road, family = binomial, data = escape_frt7)

AIC(model_ft7f) #874.5528
Anova(model_ft7f, type=3) 


#######################
### TOP MODEL
#######################
model_ft7e<-glm(escape9 ~ climate1 + FWI_veg + log_road, family = binomial, data = escape_frt7)
hist(escape_frt7$climate1)
hist(escape_frt7$log_road)

table(is.na(escape_frt7$climate1))
table(is.na(escape_frt7$log_road))
table(is.na(escape_frt7$escape9))
```



```{r}
model_ft7g<-glm(escape9 ~ climate1 + FWI_veg + log_road, family = binomial, data = escape_frt7)

# model diagnostic plots
binnedplot (fitted(model_ft7g), 
            residuals(model_ft7g), 
            nclass = NULL)

escape_frt7<- escape_frt7 %>% drop_na(escape9)


escape_frt7$resids<-resid(model_ft7g)


binnedplot (escape_frt7$climate1, 
            escape_frt7$resids,  
            nclass = NULL)

binnedplot (escape_frt7$log_road, 
            escape_frt7$resids,  
            nclass = NULL)


# Diagnostic plots look good

#Partial Residuals

visreg(model_ft7g)

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft7g)

#Create a new blank table and get AUC too
top_mod_table_FRT7_ALL <- data.frame (matrix (ncol = 10, nrow = 0))
colnames (top_mod_table_FRT7_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_FWI_veg_C-3",
                                         "coef_FWI_veg_D-1/2",
                                         "coef_FWI_veg_M-1/2",
                                         "coef_FWI_veg_O-1a/b",
                                         "coef_log_roads",
                                         "AUC")
```

Let's run it 100 times to get good mean values.

```{r}

for (g in 1:100){
  
  print(g)

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_frt7$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_frt7[ trainIndex,]
   Valid <- escape_frt7[-trainIndex,]
   
#Model   
model.FRT7<-glm(escape9 ~ climate1 + FWI_veg + log_road, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.FRT7, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT5 <- data.frame (matrix (ncol = 10, nrow = 0))
colnames (top_mod_table_FRT5 ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_FWI_veg_C-3",
                                         "coef_FWI_veg_D-1/2",
                                         "coef_FWI_veg_M-1/2",
                                         "coef_FWI_veg_O-1a/b",
                                         "coef_log_roads",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT5[1,1]<-"7"
top_mod_table_FRT5[1,2]<-"escape ~ climate1 + FWI_veg + log_roads" 
top_mod_table_FRT5[1,3]<- coef(model.FRT7)[1] #Intercept
top_mod_table_FRT5[1,4]<- coef(model.FRT7)[2] #
top_mod_table_FRT5[1,5]<- coef(model.FRT7)[3] 
top_mod_table_FRT5[1,6]<- coef(model.FRT7)[4] #Intercept
top_mod_table_FRT5[1,7]<- coef(model.FRT7)[5] #
top_mod_table_FRT5[1,8]<- coef(model.FRT7)[6] 
top_mod_table_FRT5[1,9]<- coef(model.FRT7)[7] #Intercept
top_mod_table_FRT5[1,10]<- mod.auc

top_mod_table_FRT7_ALL<-rbind(top_mod_table_FRT7_ALL, top_mod_table_FRT5)

}

```

Check.
```{r}
head(top_mod_table_FRT7_ALL)

```

Get mean values.

```{r}
names(top_mod_table_FRT7_ALL)
str(top_mod_table_FRT7_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

summary_top_mod_table_FRT7_ALL<- top_mod_table_FRT7_ALL %>% summarize_if(is.numeric,mean)

summary_top_mod_table_FRT7_ALL$FRT<-7
summary_top_mod_table_FRT7_ALL$Model_terms<-"escape16 ~ climate1 + FWI_veg + log_infra" 

```

Save table.

```{r}
write.csv(summary_top_mod_table_FRT7_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT7_escape.csv")
```


<!-- #### FRT 9 -->
<!-- ```{r} -->
<!-- escape_frt9<- escape2 %>% filter(Cluster==9) -->
<!-- table(escape_frt9$FWI_veg) -->
<!-- escape_frt9$FWI_veg[escape_frt9$FWI_veg=="C-1"]<-"C-2" -->
<!-- escape_frt9$FWI_veg[escape_frt9$FWI_veg=="D-1/2"]<-"C-7" -->
<!-- escape_frt9$veg_escape<-paste(escape_frt9$fire, escape_frt9$FWI_veg) -->

<!-- table(is.na(escape_frt9$climate1)) -->
<!-- table(is.na(escape_frt9$dem_ha_bc)) -->
<!-- table(is.na(escape_frt9$FWI_veg)) -->
<!-- table(is.na(escape_frt9$dist_roads_m)) -->
<!-- table(is.na(escape_frt9$slope_ha_bc_3005)) -->

<!-- cor.test(escape_frt9$dist_roads_m, escape_frt9$dist_infrastructure_m) # these are correlated so just include 1 -->
<!-- cor.test(escape_frt9$climate1, escape_frt9$dem_ha_bc) # these are correlated! -->
<!-- cor.test(escape_frt9$dem_ha_bc, escape_frt9$slope_ha_bc_3005) -->
<!-- cor.test(escape_frt9$win_sum, escape_frt9$win_spg) # very correlated -->

<!-- escape_frt9$log_road<-log(escape_frt9$dist_roads_m+1) -->
<!-- escape_frt9$log_infr<- log(escape_frt9$dist_infrastructure_m+1) -->

<!-- #Run model using dat1 -->
<!-- model_ft9<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + log_road, family = binomial, data = escape_frt9) -->

<!-- AIC(model_ft9)  #153.3184 -->
<!-- Anova(model_ft9, type=3) -->

<!-- model_ft9b<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + log_road, family = binomial, data = escape_frt9) -->

<!-- AIC(model_ft9b) #151.3221 -->
<!-- Anova(model_ft9b, type=3) -->


<!-- model_ft9c<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + log_road, family = binomial, data = escape_frt9) -->

<!-- AIC(model_ft9c) #149.366 -->
<!-- Anova(model_ft9c, type=3) -->

<!-- model_ft9d<-glm(escape9 ~ climate1  + slope_ha_bc_3005 + log_road, family = binomial, data = escape_frt9) -->

<!-- AIC(model_ft9d) #143.891 -->
<!-- Anova(model_ft9d, type=3) -->

<!-- model_ft9e<-glm(escape9 ~ climate1 + log_road, family = binomial, data = escape_frt9) -->

<!-- AIC(model_ft9e) #143.0078 -->
<!-- Anova(model_ft9e, type=3) -->

<!-- # model diagnostic plots -->
<!-- binnedplot (fitted(model_ft9e),  -->
<!--             residuals(model_ft9e),  -->
<!--             nclass = NULL,  -->
<!--             xlab = "Expected Values",  -->
<!--             ylab = "Average residual") -->


<!-- escape_frt9$resids<-resid(model_ft9e) -->


<!-- binnedplot (escape_frt9$climate1,  -->
<!--             escape_frt9$resids,   -->
<!--             nclass = NULL) -->

<!-- binnedplot (escape_frt9$log_road,  -->
<!--             escape_frt9$resids,   -->
<!--             nclass = NULL) -->

<!-- # Diagnostic plots look good -->

<!-- #Partial Residuals -->

<!-- visreg(model_ft9e) -->

<!-- ``` -->

<!-- We should repeat the above several times and take the mean of the coefficients. -->

<!-- ```{r} -->
<!-- summary(model_ft9e) -->

<!-- #Create a new blank table and get AUC too -->
<!-- top_mod_table_FRT9_ALL <- data.frame (matrix (ncol = 6, nrow = 0)) -->
<!-- colnames (top_mod_table_FRT9_ALL ) <- c ("FRT", "Model_terms", "intercept", -->
<!--                                          "coef_climate_1", -->
<!--                                          "coef_log_rd_dst", -->
<!--                                          "AUC") -->
<!-- ``` -->

<!-- Let's run it 100 times to get good mean values. -->

<!-- ```{r} -->

<!-- for (g in 1:100){ -->

<!--   print(g) -->

<!-- prop<-0.75 -->
<!-- # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG -->
<!--   trainIndex <- createDataPartition(escape_frt9$veg_escape, p = prop, -->
<!--                                     list = FALSE, -->
<!--                                     times = 1) -->

<!--    dat1 <- escape_frt9[ trainIndex,] -->
<!--    Valid <- escape_frt9[-trainIndex,] -->

<!-- #Model    -->
<!-- model.FRT9<-glm(escape9 ~ climate1 + log_road, family = binomial, data = dat1)  -->

<!-- mod.valid <- predict.glm(model.FRT9, newdata=Valid, type="response") -->
<!--    roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE) -->
<!--    mod.auc <- auc(roc_obj) -->

<!-- # create model table (only do this once) and add the relevant data -->
<!-- top_mod_table_FRT9 <- data.frame (matrix (ncol = 6, nrow = 0)) -->
<!-- colnames (top_mod_table_FRT9 ) <- c ("FRT", "Model_terms", "intercept", -->
<!--                                          "coef_climate_1", -->
<!--                                          "coef_log_rd_dst", -->
<!--                                          "AUC") -->

<!-- ##Add data for NDT1 -->
<!-- top_mod_table_FRT9[1,1]<-"9" -->
<!-- top_mod_table_FRT9[1,2]<-"escape ~ climate1 + log_rd_dst"  -->
<!-- top_mod_table_FRT9[1,3]<- coef(model.FRT9)[1] #Intercept -->
<!-- top_mod_table_FRT9[1,4]<- coef(model.FRT9)[2] # -->
<!-- top_mod_table_FRT9[1,5]<- coef(model.FRT9)[3] # -->
<!-- top_mod_table_FRT9[1,6]<- mod.auc -->

<!-- top_mod_table_FRT9_ALL<-rbind(top_mod_table_FRT9_ALL, top_mod_table_FRT9) -->

<!-- } -->

<!-- ``` -->

<!-- Check. -->
<!-- ```{r} -->
<!-- head(top_mod_table_FRT9_ALL) -->

<!-- ``` -->

<!-- Get mean values. -->

<!-- ```{r} -->
<!-- names(top_mod_table_FRT9_ALL) -->
<!-- str(top_mod_table_FRT9_ALL) -->
<!-- stderror <- function(x) sd(x)/sqrt(length(x)) -->

<!-- summary_top_mod_table_FRT9_ALL<- top_mod_table_FRT9_ALL %>% summarize_if(is.numeric,mean) -->

<!-- summary_top_mod_table_FRT9_ALL$FRT<-9 -->
<!-- summary_top_mod_table_FRT9_ALL$Model_terms<-"escape ~ climate1 + log_rd_dst"  -->

<!-- ``` -->

<!-- Save table. -->

<!-- ```{r} -->
<!-- write.csv(summary_top_mod_table_FRT9_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT9_escape.csv") -->
<!-- ``` -->


#### FRT 10
```{r}
# top models fro FRT 9:
#climate1 + climate2 + FWI_veg
# slope_ha_bc_3005 + dem_ha_bc + slope_ha_bc_3005:dem_ha_bc
# rd_dst_
# wind_atfire

escape_frt10<- escape2 %>% filter(Cluster==10)
table(escape_frt10$FWI_veg)
escape_frt10$FWI_veg[escape_frt10$FWI_veg=="S-1"]<-"M-1/2"
escape_frt10$FWI_veg[escape_frt10$FWI_veg=="S-2"]<-"M-1/2"
escape_frt10$FWI_veg[escape_frt10$FWI_veg=="O-1a/b"]<-"M-3"
escape_frt10$veg_escape<-paste(escape_frt10$fire, escape_frt10$FWI_veg)

table(is.na(escape_frt10$climate1))
table(is.na(escape_frt10$dem_ha_bc))
table(is.na(escape_frt10$FWI_veg))
table(is.na(escape_frt10$win_sum))
table(is.na(escape_frt10$dist_roads_m))
table(is.na(escape_frt10$slope_ha_bc_3005))
#table(is.na(escape_frt10$fire_cs))
table(is.na(escape_frt10$escape9))

cor.test(escape_frt10$dist_roads_m, escape_frt10$dist_infrastructure_m)
cor.test(escape_frt10$climate1, escape_frt10$slope_ha_bc_3005)
cor.test(escape_frt10$climate1, escape_frt10$dem_ha_bc)


#Run model using dat1
model_ft10<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + dist_roads_m + dist_infrastructure_m + win_sum, family = binomial, data = escape_frt10) # 523

model_ft10<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + log(dist_roads_m+1) + dist_infrastructure_m + win_sum, family = binomial, data = escape_frt10) # 527

model_ft10<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + dist_roads_m + log(dist_infrastructure_m+1) + win_sum, family = binomial, data = escape_frt10) # 520

model_ft10<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + log(dist_roads_m+1) + log(dist_infrastructure_m+1) + win_sum, family = binomial, data = escape_frt10) # 525


model_ft10<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + dist_roads_m + log(dist_infrastructure_m+1) + win_sum, family = binomial, data = escape_frt10) # 520

AIC(model_ft10) #585.3318
Anova(model_ft10, type=3) 

#Remove least significant interaction
model_ft10b<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + dist_roads_m + log(dist_infrastructure_m+1), family = binomial, data = escape_frt10) 

AIC(model_ft10b) #518.6497
Anova(model_ft10b, type=3) 

#Remove least term ~ dem_ha_bc
model_ft10c<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dist_roads_m + log(dist_infrastructure_m+1), family = binomial, data = escape_frt10) 

AIC(model_ft10c) #517.4902
Anova(model_ft10c, type=3) 

#Remove least term ~ dem_ha_bc
model_ft10d<-glm(escape9 ~ climate1  + slope_ha_bc_3005 + dist_roads_m + log(dist_infrastructure_m+1), family = binomial, data = escape_frt10) 

AIC(model_ft10d) #509.3442
Anova(model_ft10d, type=3) 

#######################
### TOP MODEL
#######################
#Remove least term ~ slope_ha_bc_3005

escape_frt10$log_infr<-log(escape_frt10$dist_infrastructure_m+1)
model_ft10d<-glm(escape9 ~ climate1  + slope_ha_bc_3005 + dist_roads_m + log_infr, family = binomial, data = escape_frt10)

hist(escape_frt10$climate1)
hist(escape_frt10$slope_ha_bc_3005)
hist(escape_frt10$dist_roads_m)
hist(escape_frt10$log_infr)

table(escape_frt10$escape9) #0 = 948 and 1 = 267 not bad actually.

# model diagnostic plots
binnedplot (fitted(model_ft10d), 
            residuals(model_ft10d), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")

escape_frt10 <- escape_frt10 %>% drop_na(escape9)

escape_frt10$resids<-resid(model_ft10d)

binnedplot (escape_frt10$climate1, 
            escape_frt10$resids,  
            nclass = NULL)

binnedplot (escape_frt10$slope_ha_bc_3005, 
            escape_frt10$resids,  
            nclass = NULL)

binnedplot (escape_frt10$log_infr, 
            escape_frt10$resids,  
            nclass = NULL)

binnedplot (escape_frt10$dist_roads_m, 
            escape_frt10$resids,  
            nclass = NULL)

# Diagnostic plots look good

#Partial Residuals

visreg(model_ft10d)


```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft10d)

#Create a new blank table and get AUC too
top_mod_table_FRT10_ALL <- data.frame (matrix (ncol = 8, nrow = 0))
colnames (top_mod_table_FRT10_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                          "coef_climate_1",
                                         "coef_slope",
                                         "coef_road_dist",
                                         "coef_log_infr_dist",
                                         "AUC")
```

Let's run it 100 times to get good mean values.

```{r}

for (g in 1:100){
  
  print(g)

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_frt10$escape9, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_frt10[ trainIndex,]
   Valid <- escape_frt10[-trainIndex,]
   
#Model   
model.FRT10<-glm(escape9 ~ climate1  + slope_ha_bc_3005 + dist_roads_m + log_infr, family = binomial, data = dat1)

mod.valid <- predict.glm(model.FRT10, newdata=Valid, type="response")
   
roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT10 <- data.frame (matrix (ncol = 8, nrow = 0))
colnames (top_mod_table_FRT10 ) <- c ("FRT", "Model_terms", "intercept",
                                          "coef_climate_1",
                                         "coef_slope",
                                         "coef_road_dist",
                                         "coef_log_infr_dist",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT10[1,1]<-"10"
top_mod_table_FRT10[1,2]<-"escape ~ climate1 + slope  + dist_roads + log_infra_dist" 
top_mod_table_FRT10[1,3]<- coef(model.FRT10)[1] #Intercept
top_mod_table_FRT10[1,4]<- coef(model.FRT10)[2] #
top_mod_table_FRT10[1,5]<- coef(model.FRT10)[3] #
top_mod_table_FRT10[1,6]<- coef(model.FRT10)[4] #coefficient 
top_mod_table_FRT10[1,7]<- coef(model.FRT10)[5] #coefficient 

top_mod_table_FRT10[1,8]<- mod.auc

top_mod_table_FRT10_ALL<-rbind(top_mod_table_FRT10_ALL, top_mod_table_FRT10)

}

```

Check.
```{r}
head(top_mod_table_FRT10_ALL)

```

Get mean values.

```{r}
names(top_mod_table_FRT10_ALL)
str(top_mod_table_FRT10_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

summary_top_mod_table_FRT10_ALL<- top_mod_table_FRT10_ALL %>% summarize_if(is.numeric,mean)

summary_top_mod_table_FRT10_ALL$FRT<-10
summary_top_mod_table_FRT10_ALL$Model_terms<-"escape16 ~ climate1 + slope  + dist_roads + log_infra_dist" 

```

Save table.

```{r}
write.csv(summary_top_mod_table_FRT10_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT10_escape.csv")
```

#### FRT 11

```{r}
# top models fro FRT 11:
#climate1 + climate2 + FWI_veg
# slope_ha_bc_3005 + dem_ha_bc + slope_ha_bc_3005:dem_ha_bc
# rd_dst_
# wind_atfire

escape_frt11<- escape2 %>% filter(Cluster==11)
table(escape_frt11$FWI_veg)
escape_frt11$veg_escape<-paste(escape_frt11$fire, escape_frt11$FWI_veg)

table(escape_frt11$FWI_veg, escape_frt11$escape9)

table(is.na(escape_frt11$climate1))
table(is.na(escape_frt11$dem_ha_bc))
table(is.na(escape_frt11$FWI_veg))
table(is.na(escape_frt11$win_sum))
table(is.na(escape_frt11$dist_roads_m))
table(is.na(escape_frt11$slope_ha_bc_3005))

cor.test(escape_frt11$dist_roads_m, escape_frt11$dist_infrastructure_m) # correlated 0.72
cor.test(escape_frt11$log_road, escape_frt11$log_infr)
cor.test(escape_frt11$climate1, escape_frt11$dem_ha_bc) # elevation and climate are correlated -0.89
cor.test(escape_frt11$dem_ha_bc, escape_frt11$slope_ha_bc_3005)
cor.test(escape_frt11$dem_ha_bc, escape_frt11$win_sum)

escape_frt11$log_road<-log(escape_frt11$dist_roads_m+1)
escape_frt11$log_infr<- log(escape_frt11$dist_infrastructure_m+1)


#Run model using dat1 checking if climate or dem is better
model_ft11<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + log_road +log_infr + win_sum, family = binomial, data = escape_frt11)
AIC(model_ft11)

model_ft11<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc +log_infr + win_sum, family = binomial, data = escape_frt11)
AIC(model_ft11)

model_ft11<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + log_road + win_sum, family = binomial, data = escape_frt11)
AIC(model_ft11)

# log infra is a little better than roads

model_ft11<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + log_infr + win_sum, family = binomial, data = escape_frt11)
AIC(model_ft11)

model_ft11b<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + log_infr + win_sum, family = binomial, data = escape_frt11)
AIC(model_ft11b)

model_ft11c<-glm(escape9 ~ FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + log_infr + win_sum, family = binomial, data = escape_frt11)
AIC(model_ft11c)

# ok Dem and climate are correlated and the model with Dem is slightly better (<2AIC) But I want climate in my models so Ill stick with climate and throw out dem
model_ft11b<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + log_infr + win_sum, family = binomial, data = escape_frt11)

AIC(model_ft11b) #256.9731
Anova(model_ft11b, type=3) 

model_ft11c<-glm(escape9 ~ climate1 + FWI_veg  + slope_ha_bc_3005 + log_infr, family = binomial, data = escape_frt11)

AIC(model_ft11c) #255.0052
Anova(model_ft11c, type=3)

model_ft11d<-glm(escape9 ~ climate1 + FWI_veg + log_infr, family = binomial, data = escape_frt11)

AIC(model_ft11d) #253.3849
Anova(model_ft11d, type=3)

model_ft11e<-glm(escape9 ~ climate1 + log_infr, family = binomial, data = escape_frt11)

AIC(model_ft11e) #244.3102
Anova(model_ft11e, type=3) 

#######################
### TOP MODEL
#######################
#Remove least term ~ slope_ha_bc_3005

hist(escape_frt11$climate1)
hist(escape_frt11$slope_ha_bc_3005)
hist(escape_frt11$log_road)
hist(escape_frt11$log_infr)

table(escape_frt11$escape9) 

# model diagnostic plots
binnedplot (fitted(model_ft11e), 
            residuals(model_ft11e), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")

escape_frt11<- escape_frt11 %>% drop_na(escape9)
escape_frt11$resids<-resid(model_ft11e)

binnedplot (escape_frt11$climate1, 
            escape_frt11$resids,  
            nclass = NULL)

binnedplot (escape_frt11$log_infr, 
            escape_frt11$resids,  
            nclass = NULL)

# Diagnostic plots look good

#Partial Residuals

visreg(model_ft11e)

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft11e)

#Create a new blank table and get AUC too
top_mod_table_FRT11_ALL <- data.frame (matrix (ncol = 6, nrow = 0))
colnames (top_mod_table_FRT11_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                          "coef_climate_1",
                                         "coef_log_infra",
                                         "AUC")
```

Let's run it 100 times to get good mean values.

```{r}

for (g in 1:100){
  
  print(g)

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_frt11$escape9, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_frt11[ trainIndex,]
   Valid <- escape_frt11[-trainIndex,]
   
#Model   
model.FRT11<-glm(escape9 ~ climate1 + log_infr, family = binomial, data = dat1)

mod.valid <- predict.glm(model.FRT11, newdata=Valid, type="response")
   
roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT11 <- data.frame (matrix (ncol = 6, nrow = 0))
colnames (top_mod_table_FRT11 ) <- c ("FRT", "Model_terms", "intercept",
                                          "coef_climate_1",
                                         "coef_log_infra",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT11[1,1]<-"11"
top_mod_table_FRT11[1,2]<-"escape ~ climate1 + log_infra" 
top_mod_table_FRT11[1,3]<- coef(model.FRT11)[1] #Intercept
top_mod_table_FRT11[1,4]<- coef(model.FRT11)[2] #
top_mod_table_FRT11[1,5]<- coef(model.FRT11)[3] #
top_mod_table_FRT11[1,6]<- mod.auc

top_mod_table_FRT11_ALL<-rbind(top_mod_table_FRT11_ALL, top_mod_table_FRT11)

}

```

Check.
```{r}
head(top_mod_table_FRT11_ALL)

```

Get mean values.

```{r}
names(top_mod_table_FRT11_ALL)
str(top_mod_table_FRT11_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

summary_top_mod_table_FRT11_ALL<- top_mod_table_FRT11_ALL %>% summarize_if(is.numeric,mean)

summary_top_mod_table_FRT11_ALL$FRT<-11
summary_top_mod_table_FRT11_ALL$Model_terms<-"escape ~ climate1 + log_infra" 

```

Save table.

```{r}
write.csv(summary_top_mod_table_FRT11_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT11_escape.csv")
```

#### FRT 12
```{r}
escape_frt12<- escape2 %>% filter(Cluster==12)
table(escape2$Cluster)
dim(escape_frt12)
table(escape_frt12$escape9,escape_frt12$FWI_veg)
escape_frt12$FWI_veg[escape_frt12$FWI_veg=="C-4"]<-"C-2"
escape_frt12$FWI_veg[escape_frt12$FWI_veg=="S-3"]<-"S-1"
escape_frt12$FWI_veg[escape_frt12$FWI_veg=="M-3"]<-"O-1a/b"
escape_frt12$FWI_veg[escape_frt12$FWI_veg=="S-2"]<-"M-1/2"
escape_frt12$veg_escape<-paste(escape_frt12$fire, escape_frt12$FWI_veg)

table(is.na(escape_frt12$climate1))
table(is.na(escape_frt12$dem_ha_bc))
table(is.na(escape_frt12$FWI_veg))
table(is.na(escape_frt12$win_sum))
table(is.na(escape_frt12$dist_roads_m))
table(is.na(escape_frt12$slope_ha_bc_3005))
table(is.na(escape_frt12$FIRE_CAUSE))
table(is.na(escape_frt12$escape9))

cor.test(escape_frt12$dist_roads_m, escape_frt12$dist_infrastructure_m)
cor.test(escape_frt12$climate1, escape_frt12$climate2)
cor.test(escape_frt12$climate1, escape_frt12$dem_ha_bc) # these are correlated!
cor.test(escape_frt12$dem_ha_bc, escape_frt12$climate2)
cor.test(escape_frt12$win_sum, escape_frt12$win_spg) # very correlated

#Run model using dat1
escape_frt12$log_road<-log(escape_frt12$dist_roads_m+1)
escape_frt12$log_infr<-log(escape_frt12$dist_infrastructure_m+1)

model_ft12<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + log_road + log_infr, family = binomial, data = escape_frt12)
#2321

model_ft12<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + log_road + log_infr, family = binomial, data = escape_frt12)
#2320

model_ft12<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + log_road + log_infr, family = binomial, data = escape_frt12)
#2323

#keep elevation throw out climate1


model_ft12<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + log_road + log_infr, family = binomial, data = escape_frt12) # 2320

model_ft12<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + dist_roads_m + dist_infrastructure_m, family = binomial, data = escape_frt12) # 2338

model_ft12<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt12) # 2316

model_ft12<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + log_road + dist_infrastructure_m, family = binomial, data = escape_frt12) # 2332

model_ft12<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt12) # 2758
AIC(model_ft12) #2757.722
Anova(model_ft12, type=3) 

#Remove least significant interaction
model_ft12b<-glm(escape9 ~ climate2 + FWI_veg  + dem_ha_bc + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt12)

AIC(model_ft12b) #2757.568
Anova(model_ft12b, type=3) 

model_ft12c<-glm(escape9 ~ climate2 + FWI_veg + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt12)

AIC(model_ft12c) #2758.9
Anova(model_ft12c, type=3) 



#######################
### TOP MODEL
#######################
#Remove least term ~ slope_ha_bc_3005
model_ft12e<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt12)

hist(escape_frt12$climate2)
hist(escape_frt12$win_sum)
hist(escape_frt12$log_infr)
hist(escape_frt12$dist_roads_m)

table(escape_frt12$escape9) #0 = 4359 and 1 = 456 not bad actually.
table(escape_frt12$FWI_veg)

# model diagnostic plots
binnedplot (fitted(model_ft12e), 
            residuals(model_ft12e), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")

table(is.na(escape_frt12$escape9))
escape_frt12<-escape_frt12 %>% drop_na(escape9)
escape_frt12$resids<-resid(model_ft12e)


binnedplot (escape_frt12$climate2, 
            escape_frt12$resids,  
            nclass = NULL)

binnedplot (escape_frt12$dist_roads_m, 
            escape_frt12$resids,  
            nclass = NULL)

binnedplot (escape_frt12$log_infr, 
            escape_frt12$resids,  
            nclass = NULL)



# Diagnostic plots look ok ish

#Partial Residuals

visreg(model_ft12e)

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft12e)

#Create a new blank table and get AUC too
top_mod_table_FRT12_ALL <- data.frame (matrix (ncol = 19, nrow = 0))
colnames (top_mod_table_FRT12_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_2",
                                         "coef_FWI_vegC-2",
                                         "coef_FWI_vegC-3",
                                         "coef_FWI_vegC-5",
                                         "coef_FWI_vegC-7",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegO-1a/b",
                                         "coef_FWI_vegS-1",
                                         "coef_slope",
                                         "coef_elev",
                                         "coef_win_sum",
                                         "coef_dist_roads_m",
                                         "coef_log_infr_dist",
                                         "AUC")
```

Let's run it 100 times to get good mean values.

```{r}

for (g in 1:100){
  
  print(g)

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_frt12$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_frt12[ trainIndex,]
   Valid <- escape_frt12[-trainIndex,]
   
#Model   
model.FRT12<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + dist_roads_m + log_infr, family = binomial, data = dat1)

mod.valid <- predict.glm(model.FRT12, newdata=Valid, type="response")
   
roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT12 <- data.frame (matrix (ncol = 19, nrow = 0))
colnames (top_mod_table_FRT12 ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_2",
                                         "coef_FWI_vegC-2",
                                         "coef_FWI_vegC-3",
                                         "coef_FWI_vegC-5",
                                         "coef_FWI_vegC-7",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegO-1a/b",
                                         "coef_FWI_vegS-1",
                                         "coef_slope",
                                         "coef_elev",
                                         "coef_win_sum",
                                         "coef_dist_roads_m",
                                         "coef_log_infr_dist",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT12[1,1]<-"12"
top_mod_table_FRT12[1,2]<-"escape ~ climate2 + FWI_veg + win_sum + dist_roads_m + log_infr" 
top_mod_table_FRT12[1,3]<- coef(model.FRT12)[1] #Intercept
top_mod_table_FRT12[1,4]<- coef(model.FRT12)[2] #
top_mod_table_FRT12[1,5]<- coef(model.FRT12)[3] #
top_mod_table_FRT12[1,6]<- coef(model.FRT12)[4] #coefficient 
top_mod_table_FRT12[1,7]<- coef(model.FRT12)[5] #coefficient 
top_mod_table_FRT12[1,8]<- coef(model.FRT12)[6] #Intercept
top_mod_table_FRT12[1,9]<- coef(model.FRT12)[7] #
top_mod_table_FRT12[1,10]<- coef(model.FRT12)[8] #
top_mod_table_FRT12[1,11]<- coef(model.FRT12)[9] #coefficient 
top_mod_table_FRT12[1,12]<- coef(model.FRT12)[10] #coefficient 
top_mod_table_FRT12[1,13]<- coef(model.FRT12)[11] #Intercept
top_mod_table_FRT12[1,14]<- coef(model.FRT12)[12] #
top_mod_table_FRT12[1,15]<- coef(model.FRT12)[13] #
top_mod_table_FRT12[1,16]<- coef(model.FRT12)[14] #coefficient 
top_mod_table_FRT12[1,17]<- coef(model.FRT12)[15] #
top_mod_table_FRT12[1,18]<- coef(model.FRT12)[16] #coefficient 
top_mod_table_FRT12[1,19]<- mod.auc
top_mod_table_FRT12_ALL<-rbind(top_mod_table_FRT12_ALL, top_mod_table_FRT12)

}

```

Check.
```{r}
head(top_mod_table_FRT12_ALL)

```

Get mean values.

```{r}
names(top_mod_table_FRT12_ALL)
str(top_mod_table_FRT12_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

summary_top_mod_table_FRT12_ALL<- top_mod_table_FRT12_ALL %>% summarize_if(is.numeric,mean)

summary_top_mod_table_FRT12_ALL$FRT<-12
summary_top_mod_table_FRT12_ALL$Model_terms<-"escape16 ~ climate2 + FWI_veg  + slope + elev + win_sum + dist_roads_m + log_infr" 

```

Save table.

```{r}
write.csv(summary_top_mod_table_FRT12_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT12_escape.csv")
```


#### FRT 13
```{r}
escape_frt13<- escape2 %>% filter(Cluster==13)
table(escape_frt13$FWI_veg, escape_frt13$escape9)
escape_frt13$FWI_veg[escape_frt13$FWI_veg=="C-1"]<-"C-3"
escape_frt13$FWI_veg[escape_frt13$FWI_veg=="C-4"]<-"C-2"
escape_frt13$veg_escape<-paste(escape_frt13$fire, escape_frt13$FWI_veg)

table(is.na(escape_frt13$climate1))
table(is.na(escape_frt13$dem_ha_bc))
table(is.na(escape_frt13$FWI_veg))
table(is.na(escape_frt13$dist_roads_m))
table(is.na(escape_frt13$slope_ha_bc_3005))
table(is.na(escape_frt13$escape9))

# start here

cor.test(escape_frt13$dist_roads_m, escape_frt13$dist_infrastructure_m)
cor.test(escape_frt13$climate1, escape_frt13$climate2)
cor.test(escape_frt13$climate1, escape_frt13$dem_ha_bc) # these are correlated!
cor.test(escape_frt13$dem_ha_bc, escape_frt13$slope_ha_bc_3005)
cor.test(escape_frt13$win_sum, escape_frt13$win_spg) # very correlated

escape_frt13$log_road<-log(escape_frt13$dist_roads_m+1)
escape_frt13$log_infr<- log(escape_frt13$dist_infrastructure_m+1)

#Run model using dat1
model_ft13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + log_road + log_infr, family = binomial, data = escape_frt13)
#6274

model_ft13<-glm(escape9 ~ climate2 + FWI_veg  + slope_ha_bc_3005 + dem_ha_bc + win_sum + log_road + log_infr, family = binomial, data = escape_frt13)
#6298

model_ft13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + log_road + log_infr, family = binomial, data = escape_frt13)
#6279

# Best one leaves out dem

model_ft13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt13)
#6248
model_ft13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + dist_infrastructure_m, family = binomial, data = escape_frt13)
#6283
model_ft13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + log_road + dist_infrastructure_m, family = binomial, data = escape_frt13)
#6294

model_ft13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt13)
AIC(model_ft13) #7025.348
Anova(model_ft13, type=3) 

# Top model
model_ft13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt13)
Anova(model_ft13, type=3) 


#Remove least significant interaction
model_ft13b<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + dist_roads_m + log_infr, family = binomial, data = escape_frt13)
anova(model_ft13, model_ft13b, test="Chisq")


#######################
### TOP MODEL
#######################
#Remove least term ~ slope_ha_bc_3005
model_ft13e<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt13)

hist(escape_frt13$climate1)
hist(escape_frt13$climate2)
hist(escape_frt13$dist_roads_m)

table(escape_frt13$escape9) #0 = 948 and 1 = 267 not bad actually.
table(escape_frt13$FWI_veg)

# model diagnostic plots
binnedplot (fitted(model_ft13e), 
            residuals(model_ft13e), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")



#Partial Residuals

visreg(model_ft13e)


```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft13e)



#Create a new blank table and get AUC too
top_mod_table_FRT13_ALL <- data.frame (matrix (ncol = 21, nrow = 0))
colnames (top_mod_table_FRT13_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_climate_2",
                                         "coef_FWI_vegC-3",
                                         "coef_FWI_vegC-5",
                                         "coef_FWI_vegC-7",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegM-3",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegO-1a/b",
                                         "coef_FWI_vegS-1",
                                         "coef_FWI_vegS-2",
                                         "coef_FWI_vegS-3",
                                         "coef_slope",
                                         "coef_win_sum",
                                         "coef_roads_m",
                                         "coef_log_infr",
                                         "AUC")
```

Let's run it 100 times to get good mean values.

```{r}
prop<-0.75

for (g in 1:100){
  
  print(g)

# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_frt13$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_frt13[ trainIndex,]
   Valid <- escape_frt13[-trainIndex,]
   
#Model   
model.FRT13<-glm(escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = dat1)

mod.valid <- predict.glm(model.FRT13, newdata=Valid, type="response")
   
roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT13 <- data.frame (matrix (ncol = 21, nrow = 0))
colnames (top_mod_table_FRT13 ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_climate_2",
                                         "coef_FWI_vegC-3",
                                         "coef_FWI_vegC-5",
                                         "coef_FWI_vegC-7",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegM-3",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegO-1a/b",
                                         "coef_FWI_vegS-1",
                                         "coef_FWI_vegS-2",
                                         "coef_FWI_vegS-3",
                                         "coef_slope",
                                         "coef_win_sum",
                                         "coef_roads_m",
                                         "coef_log_infr",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT13[1,1]<-"13"
top_mod_table_FRT13[1,2]<-"escape9 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr" 
top_mod_table_FRT13[1,3]<- coef(model.FRT13)[1] #Intercept
top_mod_table_FRT13[1,4]<- coef(model.FRT13)[2] #
top_mod_table_FRT13[1,5]<- coef(model.FRT13)[3] #
top_mod_table_FRT13[1,6]<- coef(model.FRT13)[4] #coefficient 
top_mod_table_FRT13[1,7]<- coef(model.FRT13)[5] #coefficient 
top_mod_table_FRT13[1,8]<- coef(model.FRT13)[6] #Intercept
top_mod_table_FRT13[1,9]<- coef(model.FRT13)[7] #
top_mod_table_FRT13[1,10]<- coef(model.FRT13)[8] #
top_mod_table_FRT13[1,11]<- coef(model.FRT13)[9] #coefficient 
top_mod_table_FRT13[1,12]<- coef(model.FRT13)[10] #coefficient 
top_mod_table_FRT13[1,13]<- coef(model.FRT13)[11] #Intercept
top_mod_table_FRT13[1,14]<- coef(model.FRT13)[12] #
top_mod_table_FRT13[1,15]<- coef(model.FRT13)[13] #
top_mod_table_FRT13[1,16]<- coef(model.FRT13)[14] #coefficient 
top_mod_table_FRT13[1,17]<- coef(model.FRT13)[15] #coefficient 
top_mod_table_FRT13[1,18]<- coef(model.FRT13)[16] #Intercept
top_mod_table_FRT13[1,19]<- coef(model.FRT13)[17] #coefficient 
top_mod_table_FRT13[1,20]<- coef(model.FRT13)[18] #Intercept
top_mod_table_FRT13[1,21]<- mod.auc
top_mod_table_FRT13_ALL<-rbind(top_mod_table_FRT13_ALL, top_mod_table_FRT13)

}

```

Check.
```{r}
head(top_mod_table_FRT13_ALL)

```

Get mean values.

```{r}
names(top_mod_table_FRT13_ALL)
str(top_mod_table_FRT13_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

summary_top_mod_table_FRT13_ALL<- top_mod_table_FRT13_ALL %>% summarize_if(is.numeric,mean)

summary_top_mod_table_FRT13_ALL$FRT<-13
summary_top_mod_table_FRT13_ALL$Model_terms<-"escape16 ~ climate1 + climate2 + FWI_veg  + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr" 

```

Save table.

```{r}
write.csv(summary_top_mod_table_FRT13_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT13_escape.csv")
```


#### FRT 14
```{r}
escape_frt14<- escape2 %>% filter(Cluster==14)
table(escape_frt14$FWI_veg, escape_frt14$escape9)

escape_frt14$FWI_veg[escape_frt14$FWI_veg=="M-3"]<-"O-1a/b"
escape_frt14$FWI_veg[escape_frt14$FWI_veg=="C-5"]<-"C-7"
escape_frt14$FWI_veg[escape_frt14$FWI_veg=="S-1"]<-"M-1/2"
escape_frt14$FWI_veg[escape_frt14$FWI_veg=="C-2"]<-"C-3"

escape_frt14$veg_escape<-paste(escape_frt14$fire, escape_frt14$FWI_veg)

cor.test(escape_frt14$dist_roads_m, escape_frt14$dist_infrastructure_m)
cor.test(escape_frt14$climate1, escape_frt14$dem_ha_bc) # these are correlated!
cor.test(escape_frt14$dem_ha_bc, escape_frt14$slope_ha_bc_3005)
cor.test(escape_frt14$win_sum, escape_frt14$win_spg) # very correlated
hist(as.numeric(escape_frt14$ig_mnth))

escape_frt14$log_road<-log(escape_frt14$dist_roads_m+1)
escape_frt14$log_infr<- log(escape_frt14$dist_infrastructure_m+1)


table(is.na(escape_frt14$climate1))
table(is.na(escape_frt14$dem_ha_bc))
table(is.na(escape_frt14$FWI_veg))
table(is.na(escape_frt14$win_sum))
table(is.na(escape_frt14$dist_roads_m))
table(is.na(escape_frt14$slope_ha_bc_3005))
table(is.na(escape_frt14$escape9))

escape_frt14<-escape_frt14 %>% filter(!is.na(escape9))

#Run model using dat1
model_ft14<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + slope_ha_bc_3005 + win_sum + log_road + log_infr, family = binomial, data = escape_frt14)
#3299

model_ft14<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt14)
#3298

model_ft14<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + slope_ha_bc_3005 + win_sum + log_road + dist_infrastructure_m  , family = binomial, data = escape_frt14)
#3297

model_ft14<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + slope_ha_bc_3005 + win_sum + dist_roads_m + dist_infrastructure_m  , family = binomial, data = escape_frt14) #3303

#best model
model_ft14<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + slope_ha_bc_3005 + win_sum + log_road + dist_infrastructure_m  , family = binomial, data = escape_frt14)

AIC(model_ft14) #3737.464
Anova(model_ft14, type=3) 

#Remove least significant term
model_ft14<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + win_sum + log_road + dist_infrastructure_m  , family = binomial, data = escape_frt14)
AIC(model_ft14) #3737.464 # cant actually compare these two models because slope is missing to values and so there are different datasets
Anova(model_ft14, type=3) 


#######################
### TOP MODEL
#######################
#Remove least term ~ slope_ha_bc_3005
model_ft14e<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + win_sum + log_road + dist_infrastructure_m  , family = binomial, data = escape_frt14)

hist(escape_frt14$climate1)
hist(escape_frt14$dem_ha_bc)
hist(escape_frt14$log_road)
hist(escape_frt14$dist_infrastructure_m)

table(escape_frt14$escape9) #0 = 9123 and 1 = 556 not bad actually.
table(escape_frt14$FWI_veg)

# model diagnostic plots
binnedplot (fitted(model_ft14e), 
            residuals(model_ft14e), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")



#Partial Residuals

visreg(model_ft14e)

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft14e)


#Create a new blank table and get AUC too
top_mod_table_FRT14_ALL <- data.frame (matrix (ncol = 14, nrow = 0))
colnames (top_mod_table_FRT14_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_FWI_vegC-7",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegO-1a/b",
                                         "coef_elev",
                                         "coef_win_sum",
                                         "coef_dist_road_m",
                                         "coef_dist_infr_m",
                                         "AUC")
```

Let's run it 100 times to get good mean values.

```{r}
prop<-0.75

for (g in 1:100){
  
  print(g)

# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(escape_frt14$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- escape_frt14[ trainIndex,]
   Valid <- escape_frt14[-trainIndex,]
   
#Model   
model.FRT14<-glm(escape9 ~ climate1 + FWI_veg + dem_ha_bc + slope_ha_bc_3005 + win_sum + log_road + dist_infrastructure_m, family = binomial, data = dat1)

mod.valid <- predict.glm(model.FRT14, newdata=Valid, type="response")
   
roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT14 <- data.frame (matrix (ncol = 14, nrow = 0))
colnames (top_mod_table_FRT14 ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_1",
                                         "coef_FWI_vegC-7",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegO-1a/b",
                                         "coef_elev",
                                         "coef_win_sum",
                                         "coef_dist_road_m",
                                         "coef_dist_infr_m",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT14[1,1]<-"14"
top_mod_table_FRT14[1,2]<-"escape9 ~ climate1 + FWI_veg + elev + win_sum + log_road + dist_infrastructure_m" 
top_mod_table_FRT14[1,3]<- coef(model.FRT14)[1] #Intercept
top_mod_table_FRT14[1,4]<- coef(model.FRT14)[2] #
top_mod_table_FRT14[1,5]<- coef(model.FRT14)[3] #
top_mod_table_FRT14[1,6]<- coef(model.FRT14)[4] #coefficient 
top_mod_table_FRT14[1,7]<- coef(model.FRT14)[5] #coefficient 
top_mod_table_FRT14[1,8]<- coef(model.FRT14)[6] #Intercept
top_mod_table_FRT14[1,9]<- coef(model.FRT14)[7] #
top_mod_table_FRT14[1,10]<- coef(model.FRT14)[8] #
top_mod_table_FRT14[1,11]<- coef(model.FRT14)[9] #coefficient 
top_mod_table_FRT14[1,12]<- coef(model.FRT14)[10] #coefficient 
top_mod_table_FRT14[1,13]<- coef(model.FRT14)[11] #Intercept
top_mod_table_FRT14[1,14]<- mod.auc
top_mod_table_FRT14_ALL<-rbind(top_mod_table_FRT14_ALL, top_mod_table_FRT14)

}

```

Check.
```{r}
head(top_mod_table_FRT14_ALL)

```

Get mean values.

```{r}
names(top_mod_table_FRT14_ALL)
str(top_mod_table_FRT14_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

summary_top_mod_table_FRT14_ALL<- top_mod_table_FRT14_ALL %>% summarize_if(is.numeric,mean)

summary_top_mod_table_FRT14_ALL$FRT<-14
summary_top_mod_table_FRT14_ALL$Model_terms<-"escape9 ~ climate1 + FWI_veg + elev + win_sum + log_road + dist_infrastructure_m" 

```

Save table.

```{r}
write.csv(summary_top_mod_table_FRT14_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT14_escape.csv")
```


#### FRT 15
```{r}
escape_frt15<- escape2 %>% filter(Cluster==15)
table(escape_frt15$FWI_veg)
escape_frt15$FWI_veg[escape_frt15$FWI_veg=="S-1"]<-"S-3"
escape_frt15$FWI_veg[escape_frt15$FWI_veg=="C-7"]<-"C-5"
escape_frt15$FWI_veg[escape_frt15$FWI_veg=="O-1a/b"]<-"C-3"
escape_frt15$FWI_veg[escape_frt15$FWI_veg=="S-2"]<-"C-5"

escape_frt15$log_road<-log(escape_frt15$dist_roads_m+1)
escape_frt15$log_infr<- log(escape_frt15$dist_infrastructure_m+1)

# frt_15_0<-escape_frt15 %>% filter(escape9==0)
# frt_15_1<-escape_frt15 %>% filter(escape9==1)
# 
# frt_15_1_samp<- sample_n(frt_15_1, 313, replace = TRUE)
#    
# escape_frt15<-rbind(frt_15_0, frt_15_1_samp) # now 10% of obts are 1's


escape_frt15$veg_escape<-paste(escape_frt15$escape9, escape_frt15$FWI_veg)

cor.test(escape_frt15$dist_roads_m, escape_frt15$dist_infrastructure_m)
cor.test(escape_frt15$climate1, escape_frt15$climate2)
cor.test(escape_frt15$climate1, escape_frt15$dem_ha_bc) # these are correlated!
cor.test(escape_frt15$climate2, escape_frt15$dem_ha_bc) 
cor.test(escape_frt15$dem_ha_bc, escape_frt15$slope_ha_bc_3005)

table(is.na(escape_frt15$climate1))
table(is.na(escape_frt15$dem_ha_bc))
table(is.na(escape_frt15$FWI_veg))
table(is.na(escape_frt15$win_sum))
table(is.na(escape_frt15$log_infr))
table(is.na(escape_frt15$slope_ha_bc_3005))
table(is.na(escape_frt15$fire_cs))
table(is.na(escape_frt15$escape9))

hist(as.numeric(escape_frt15$ig_mnth))
table(as.numeric(escape_frt15$ig_mnth)) # most fires in july and aug so use win_sum

#escape_frt15<- escape_frt15 %>% filter(!is.na(dem_ha_bc))
#escape_frt15<- escape_frt15 %>% filter(!is.na(win_sum))

#Run model using dat1 and test if log road or log infra works best
model_ft15<-glm(escape9 ~ climate1 + climate2 + FWI_veg + slope_ha_bc_3005 + win_sum + log_road + log_infr, family = binomial, data = escape_frt15)

AIC(model_ft15) #898.4858
Anova(model_ft15, type=3) 

model_ft15<-glm(escape9 ~ climate1 + climate2 + FWI_veg + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt15)
#896.2
model_ft15<-glm(escape9 ~ climate1 + climate2 + FWI_veg + slope_ha_bc_3005 + win_sum + log_road + dist_infrastructure_m, family = binomial, data = escape_frt15)
#903.9
model_ft15<-glm(escape9 ~ climate1 + climate2 + FWI_veg + slope_ha_bc_3005 + win_sum + dist_roads_m + dist_infrastructure_m, family = binomial, data = escape_frt15)
#901

#Test if climate1 or dem should stay
model_ft15<-glm(escape9 ~ climate1 + climate2 + FWI_veg + dem_ha_bc + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt15)
#897.4

model_ft15<-glm(escape9 ~climate2 + FWI_veg + dem_ha_bc + slope_ha_bc_3005  + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt15)
#895.7

model_ft15<-glm(escape9 ~ climate1 + climate2 + FWI_veg + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt15)
#896.2

# Ok its the same climate1 and elevation so Ill keep climate 1

# work from here to remove least signiticant term

model_ft15<-glm(escape9 ~ climate1 + climate2 + FWI_veg + slope_ha_bc_3005 + win_sum + dist_roads_m + log_infr, family = binomial, data = escape_frt15)

AIC(model_ft15) #1128.452
Anova(model_ft15, type=3) 

model_ft15b<-glm(escape9 ~ climate1 + climate2 + FWI_veg + slope_ha_bc_3005 + dist_roads_m + log_infr, family = binomial, data = escape_frt15)

AIC(model_ft15b) #1060.653
Anova(model_ft15b, type=3) 
anova(model_ft15, model_ft15b,test="Chisq")

# choose to leave out elevation
model_ft15c<-glm(escape9 ~ climate2 + FWI_veg + slope_ha_bc_3005  + dist_roads_m + log_infr, family = binomial, data = escape_frt15)

AIC(model_ft15c) #1060.374
Anova(model_ft15c, type=3) 

#rm 
model_ft15d<-glm(escape9 ~ climate2 + FWI_veg + slope_ha_bc_3005 + log_infr, family = binomial, data = escape_frt15)

AIC(model_ft15d) #1058.55
Anova(model_ft15d, type=3) 


#######################
### TOP MODEL
#######################
#Remove least term ~ slope_ha_bc_3005
model_ft15e<-glm(escape9 ~ climate2 + FWI_veg + slope_ha_bc_3005 + log_infr, family = binomial, data = escape_frt15)

hist(escape_frt15$slope_ha_bc_3005)
hist(escape_frt15$climate2)
hist(escape_frt15$log_infr)

table(escape_frt15$escape9) #0 = 948 and 1 = 267 not bad actually.
table(escape_frt15$FWI_veg, escape_frt15$escape9)

# model diagnostic plots
binnedplot (fitted(model_ft15e), 
            residuals(model_ft15e), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual")


# Diagnostic plots look good

#Partial Residuals

visreg(model_ft15e)

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model_ft15e)


#Create a new blank table and get AUC too
top_mod_table_FRT15_ALL <- data.frame (matrix (ncol = 12, nrow = 0))
colnames (top_mod_table_FRT15_ALL ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_2",
                                         "coef_FWI_vegC-5",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegS-3",
                                         "coef_slope",
                                         "coef_log_infr",
                                         "AUC")
```

Let's run it 100 times to get good mean values.

```{r}
prop<-0.75

for (g in 1:100){
  
  print(g)
  
trainIndex <- createDataPartition(escape_frt15$escape9, p = prop,
                                    list = FALSE,
                                    times = 1)
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  dat1 <- escape_frt15[ trainIndex,] # note only 6% of obs are 1's so Im going to sample to get my sample size up to 30% 1's.
   # in total I need 1589 1's
   dat1_1<-dat1 %>% filter(escape9==1)
   dat1_0<-dat1 %>% filter(escape9==0)
   dat1_1_samp<- sample_n(dat1_1, round(length(dat1$escape9)*0.1,0), replace = TRUE)
   
   dat<-rbind(dat1_0, dat1_1_samp)
   Valid <- escape_frt15[-trainIndex,]
   
#Model   
model.FRT15<-glm(escape9 ~ climate2 + FWI_veg + slope_ha_bc_3005 + log_infr, family = binomial, data = dat)

mod.valid <- predict.glm(model.FRT15, newdata=Valid, type="response")
   
roc_obj <- roc(Valid[,"escape9"], mod.valid, quiet=TRUE)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_FRT15 <- data.frame (matrix (ncol = 12, nrow = 0))
colnames (top_mod_table_FRT15 ) <- c ("FRT", "Model_terms", "intercept",
                                         "coef_climate_2",
                                         "coef_FWI_vegC-5",
                                         "coef_FWI_vegD-1/2",
                                         "coef_FWI_vegM-1/2",
                                         "coef_FWI_vegN",
                                         "coef_FWI_vegS-3",
                                         "coef_slope",
                                         "coef_log_infr_ds",
                                         "AUC")

##Add data for NDT1
top_mod_table_FRT15[1,1]<-"15"
top_mod_table_FRT15[1,2]<-"escape ~ climate2 + FWI_veg + slope + log_infr" 

# correct intercept value following King & Zeng 2001
# B0 - ln((1-fraction of ones in pop)/fraction of ones in pop * (1-fraction of ones in sample)/fraction of ones in sample )

#frac_ones_pop<-length(escape_frt15$escape9[escape_frt15$escape9==1])/(length(escape_frt15$escape9))
#frac_ones_samp<-length(dat$escape9[dat$escape9==1])/(length(dat$escape9))


#top_mod_table_FRT15[1,3]<- coef(model.FRT15)[1] - log10((1-frac_ones_pop)/frac_ones_pop * (1-frac_ones_samp)/frac_ones_samp) #Intercept
top_mod_table_FRT15[1,3]<- coef(model.FRT15)[1] #Intercept
top_mod_table_FRT15[1,4]<- coef(model.FRT15)[2] #
top_mod_table_FRT15[1,5]<- coef(model.FRT15)[3] #
top_mod_table_FRT15[1,6]<- coef(model.FRT15)[4] #coefficient 
top_mod_table_FRT15[1,7]<- coef(model.FRT15)[5] #
top_mod_table_FRT15[1,8]<- coef(model.FRT15)[6] #
top_mod_table_FRT15[1,9]<- coef(model.FRT15)[7]
top_mod_table_FRT15[1,10]<- coef(model.FRT15)[8] #
top_mod_table_FRT15[1,11]<- coef(model.FRT15)[9] #
top_mod_table_FRT15[1,12]<- mod.auc
top_mod_table_FRT15_ALL<-rbind(top_mod_table_FRT15_ALL, top_mod_table_FRT15)

}

```

Check.
```{r}
head(top_mod_table_FRT15_ALL)



```

Get mean values.

```{r}
names(top_mod_table_FRT15_ALL)
str(top_mod_table_FRT15_ALL)
stderror <- function(x) sd(x)/sqrt(length(x))

summary_top_mod_table_FRT15_ALL<- top_mod_table_FRT15_ALL %>% summarize_if(is.numeric,mean)

summary_top_mod_table_FRT15_ALL$FRT<-15
summary_top_mod_table_FRT15_ALL$Model_terms<-"escape16 ~ climate2 + FWI_veg + slope + log_infr" 

```

Save table.

```{r}
write.csv(summary_top_mod_table_FRT15_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_FRT15_escape.csv")
```
