---
title: "15b_Fire_Spread_Polygons_Data_NDT2"
author: "Cora Skaien"
date: "29/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load relevant libraries
library(sf)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(RPostgreSQL)
library(rpostgis)
library(dplyr)
library(lme4)
library(arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(ggcorrplot) 
library(kableExtra)
library(data.table)
library(DBI)
library(here)
library(AICcmodavg)
library(rje)
library(base)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 15b_Fire_Spread_Polygons_Data_NDT2.R
#  Script Version: 1.0
#  Script Purpose: model selection for factors that dictate spread into cells (part of spread) by NDT.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

Load in the prepped data.

```{r}
fire_spread_veg_data_df<-read.csv(file="D:\\Fire\\fire_data\\raw_data\\Historical_Fire_Perimiter_polygons\\fire_spread_veg_data_.csv")

head(fire_spread_veg_data_df)

```

Check data categories.

```{r}
table(fire_spread_veg_data_df$bclcs_level_2) #T: treed; N: Not treed; W: Water; L:land, non-veg
fire_spread_veg_data_df$proj_age_1 #Lots of NAs
fire_spread_veg_data_df$proj_height_1
fire_spread_veg_data_df$live_stand_volume_125

names(fire_spread_veg_data_df)
table

str(fire_spread_veg_data_df$spread)
table(fire_spread_veg_data_df$spread)

fire_spread_veg_data_df$spread<-as.numeric(fire_spread_veg_data_df$spread)

table(fire_spread_veg_data_df$fire_cs) #must decide: do we separate into different categories? For this, I suggest not necessary.

fire_spread_veg_data_df$spread_veg<-paste(fire_spread_veg_data_df$spread, fire_spread_veg_data_df$vegtype2)
table(fire_spread_veg_data_df$spread_veg)

fire_spread_veg_data_df$spread_bclcs2<-paste(fire_spread_veg_data_df$spread, fire_spread_veg_data_df$bclcs_level_2)
table(fire_spread_veg_data_df$spread_bclcs2)

fire_spread_veg_data_df$spread_bclcs5<-paste(fire_spread_veg_data_df$spread, fire_spread_veg_data_df$bclcs_level_5_2)
table(fire_spread_veg_data_df$spread_bclcs5)

fire_spread_veg_data_df$spread_bclcs5_2<-paste(fire_spread_veg_data_df$spread, fire_spread_veg_data_df$bclcs_level_5_2, fire_spread_veg_data_df$bclcs_level_2)
table(fire_spread_veg_data_df$spread_bclcs5_2)

#Determined that we lose all water sites because not in vegtype2. So need to make all water sites from bclcs_level_2 to be water in vegtype2. No interactions possible between the two, but there will be colinearity.
fire_spread_veg_data_df$vegtype2[fire_spread_veg_data_df$bclcs_level_2=="W"] <- "W"

```

################ All fires ################

We will perform multiple loops for different subsets of variables for model selection, and then use these results to inform us on best models moving forward. The variables that will be assessed include:

1. Projected Height (proj_height_1) #Note, there may be some NAs and we may not be able to use this
2. projected age (proj_age_1) #Note, there may be some NAs and we may not be able to use this
3. live_stand_volume_125 #Note, there may be some NAs and we may not be able to use this
4. vegtype2
5. slope
6. aspect_cos (cos)
7. elev
8. Various distance to infrastructure variables (dist_mun, dist_dam, dist_nat, dist_pow, dist_mine) - no interactions
9. Land use (bclcs_level_5_2)
10. roads_km (road density, which may relate to ability to fight fires)
11. bclcs_level_2 (Treed or not treed)

First we will create the variable lists that contain all of our variables of interest.

```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(proj_height_1 = "proj_height_1", proj_age_1 = "proj_age_1", live_stand_volume_125 = "live_stand_volume_125", slope = "slope", aspect_cos = "aspect_cos", elev ="elev", vegtype2 = "vegtype2", bclcs_level_5_2 = "bclcs_level_5_2", dist_mun = "dist_mun", dist_dam ="dist_dam", dist_nat = "dist_nat", dist_pow = "dist_pow", dist_mine = "dist_mine", roads_km="roads_km", bclcs_level_2 = "bclcs_level_2") 

vars.oth<-c("proj_height_1", "proj_age_1", "live_stand_volume_125") #Note, there may be some NAs and we may not be able to use this
vars.topo<-c("slope", "aspect_cos", "elev")
vars.infra<-c("dist_mun", "dist_dam", "dist_nat", "dist_pow", "dist_mine", "roads_km", "bclcs_level_5_2")
vars.veg<-c("vegtype2", "bclcs_level_2") #Too few; will add in final model selection

```

Now, we will generate two-way interactions for each of these lists. 

```{r}

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT) #3

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT
mods.meT<-mods.meT[-1]

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #8
mods.twowayT
mods.twowayT<-mods.twowayT[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT) #10
#mods.interT


#complete list of two-way interactions
mods.twowayO <- powerSet(twoway.intsT)
length(mods.twowayO) #8
mods.twowayO
mods.twowayO<-mods.twowayO[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interO <- list()
counter <- 0
for (i in 1: length(mods.twowayO)) {
   s1 <- unique(unlist( strsplit(mods.twowayO[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayO[[i]])
        mods.interO[[counter]] <- both
      }
   }
}

length(mods.interO) #10
#mods.interO


####3.VRI data

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.oth
mods.me.oth<-mods.me.oth[-1]



#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI) #21

#Subset to get only the interactions of interest
twoway.intsIb<-twoway.intsI[c(5,6,10,11,14,15,17,18,19,20,21)]
twoway.intsIb

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI
mods.meI<-mods.meI[-1]

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsIb)
length(mods.twowayI) #2048
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI) #6767
head(mods.interI)
#mods.interI


#the list of all possible model RHSs. 
all.poss.mods.VRI<-c(1, mods.interO)
all.poss.mods.VRI

all.poss.mods.topo<-c(1, mods.interT)
all.poss.mods.topo

all.poss.mods.infra<-c(1, mods.interI) 
length(all.poss.mods.infra)
#all.poss.mods.infra
```

############### ##########

Because of the large number of models with all variables included, we will test the separate combos first. Then we will test the top models together in additional combinations, with determining best AIC model from there. 

Select NDT: NDT2

```{r}
zones1<-c("NDT2") #Do one zone at a time
prop<-0.75

########### 1. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- fire_spread_veg_data_df %>% dplyr::filter(ntrldstrbn ==zones1[h])
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(spread, spread, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(spread, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$spread, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$NDT<-c("NDT2")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_NDT2_spread_VRI<-table.glm.VRI.simple

AIC_NDT2_spread_summary_VRI<- AIC_NDT2_spread_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_NDT2_spread_summary_VRI2<- AIC_NDT2_spread_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_NDT2_spread_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 2. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- fire_spread_veg_data_df %>% dplyr::filter(ntrldstrbn ==zones1[h])

#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(spread, spread, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(spread, spread, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$spread, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$NDT<-c("NDT2")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_NDT2_spread_topo<-table.glm.topo.simple

AIC_NDT2_spread_summary_topo<- AIC_NDT2_spread_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_NDT2_spread_summary_topo2<- AIC_NDT2_spread_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_NDT2_spread_summary_topo2)
```

#Now repeat for infrastructure
Running 100 times takes up too much space, so need to run fewer times and combine.

Cannot run even one full run because too many models. Need to break up into smaller chunks if want to run all of these models. Otherwise, consider reducing models in this set. If run in chunks, need to subset the data into training and validation separately from the loop so that the entire set of variables are with the same data subset per full run for comparing AIC values.

A common problem is the result "prediction from a rank-deficient fit may be misleading Setting levels: control = 0, case = 1
Setting direction: controls < cases", which indicates (1) over-fitting, or (2) insufficient data in some categories to estimate coefficients. One issues is vegtype2 and bclcls_5_2 and bclcs_2 all have water as the same data. 


```{r}
length(all.poss.mods.infra) #6768

all.poss.mods.infra_a<-all.poss.mods.infra[c(1:1000)]
all.poss.mods.infra_b<-all.poss.mods.infra[c(1001:1400)] 
#all.poss.mods.infra_b_2<-all.poss.mods.infra[c(1101:1400)] 

all.poss.mods.infra_c<-all.poss.mods.infra[c(1401:1900)]
all.poss.mods.infra_c2<-all.poss.mods.infra[c(1901:2250)]
all.poss.mods.infra_d<-all.poss.mods.infra[c(2251:3000)]
all.poss.mods.infra_e<-all.poss.mods.infra[c(3001:3750)]
all.poss.mods.infra_f<-all.poss.mods.infra[c(3751:4500)]
all.poss.mods.infra_g<-all.poss.mods.infra[c(4501:5250)]
all.poss.mods.infra_h<-all.poss.mods.infra[c(5251:6000)]
all.poss.mods.infra_i<-all.poss.mods.infra[c(6001:6768)]

dat2<- fire_spread_veg_data_df %>% dplyr::filter(ntrldstrbn ==zones1)

 # model_dat<- dat2 %>% dplyr::select(spread, spread, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(spread, spread_bclcs5_2, ntrldstrbn, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$spread_bclcs5_2, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]
   
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

```

```{r}
all.poss.mods.infra_a_1<-all.poss.mods.infra_a[1:500]
all.poss.mods.infra_a_2<-all.poss.mods.infra_a[501:1000]
```


```{r}
########### 3. Distance to Infrastructure ############

for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_a_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_a_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}

```

```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_a_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_a_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}

```

#Need to reduce subset b
```{r}
all.poss.mods.infra_b_1<-all.poss.mods.infra_b[1:200]
all.poss.mods.infra_b_2<-all.poss.mods.infra_b[201:400]
```


Repeat for second portion (b_1)
```{r}

for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_b_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_b_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion
```{r}

for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_b_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_b_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}

for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_c[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_c, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}

for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_c2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_c2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Make section 2 smaller
```{r}
all.poss.mods.infra_d_1<-all.poss.mods.infra_d[1:400]
all.poss.mods.infra_d_2<-all.poss.mods.infra_d[401:750]
```


Repeat for next portion.
```{r}

for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_d_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_d_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}

for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_d_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_d_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

```{r}
all.poss.mods.infra_e_1<-all.poss.mods.infra_e[1:400]
all.poss.mods.infra_e_2<-all.poss.mods.infra_e[401:750]
```


Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_e_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_e_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_e_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_e_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```


```{r}
all.poss.mods.infra_f_1<-all.poss.mods.infra_f[1:400]
all.poss.mods.infra_f_2<-all.poss.mods.infra_f[401:750]
```


Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_f_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_f_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```


Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_f_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_f_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

```{r}
all.poss.mods.infra_g_1<-all.poss.mods.infra_g[1:400]
all.poss.mods.infra_g_2<-all.poss.mods.infra_g[401:750]
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_g_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_g_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_g_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_g_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

```{r}
all.poss.mods.infra_h_1<-all.poss.mods.infra_h[1:400]
all.poss.mods.infra_h_2<-all.poss.mods.infra_h[401:650]
all.poss.mods.infra_h_3<-all.poss.mods.infra_h[651:750]
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_h_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_h_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_h_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_h_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_h_3[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_h_3, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

```{r}
all.poss.mods.infra_i_1<-all.poss.mods.infra_i[1:400]
all.poss.mods.infra_i_2<-all.poss.mods.infra_i[401:600]
all.poss.mods.infra_i_3<-all.poss.mods.infra_i[601:768]

```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_i_1[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_i_1, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_i_2[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_i_2, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

Repeat for next portion.
```{r}
for (g in 1: length(zones1)){
  print(paste((all.poss.mods.infra_i_3[i]), (zones1), sep=" "))
 
big.mod <- function(mods.in, df.train, df.test, dep.var="spread") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra_i_3, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$NDT<-c("NDT2")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
```

#Save in case computer restarts
```{r}
write.csv(table.glm.infra.simple, file="D:\\Fire\\fire_data\\raw_data\\ClimateBC_Data\\table.glm.infra.spread_poly_NDT2.csv")
```


#Repeat again above steps to get repetition with a new subset of data.

```{r}
dat2<- fire_spread_veg_data_df %>% dplyr::filter(ntrldstrbn ==zones1)

 # model_dat<- dat2 %>% dplyr::select(spread, spread_bclcs5_2, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(spread, spread_bclcs5_2, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$spread_bclcs5_2, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]
```


Now that we have run the model at least 3 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_NDT2_spread_infra<-table.glm.infra.simple

AIC_NDT2_spread_summary_infra<- AIC_NDT2_spread_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_NDT2_spread_summary_infra2<- AIC_NDT2_spread_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_NDT2_spread_summary_infra2)

```

#Now combine the datatables and save to computer

```{r}
NDT2_l_spread_models_treed<-rbind(AIC_NDT2_spread_summary_VRI2, AIC_NDT2_spread_summary_topo2, AIC_NDT2_spread_summary_infra2)
NDT2_l_spread_models_treed
NDT2_l_spread_models_treed$NDT<-"NDT2"

#or if did not do infrastructure
NDT2_l_spread_models_treed<-rbind(AIC_NDT2_spread_summary_VRI2, AIC_NDT2_spread_summary_topo2)
NDT2_l_spread_models_treed
NDT2_l_spread_models_treed$NDT<-"NDT2"

write.csv(NDT2_l_spread_models_treed, file="D:\\Fire\\fire_data\\raw_data\\NDT2_spread_models_polygon.csv")

#Or if only have topography since VRI will not be used (too much lost data from non-treed locations)
AIC_NDT2_spread_summary_topo2$NDT<-"NDT2"

write.csv(AIC_NDT2_spread_summary_topo2, file="D:\\Fire\\fire_data\\raw_data\\NDT2_spread_TOPOmodels_polygon.csv")

```


################################ STAGE TWO ########################

#STAGE TWO: PUT TOGETHER MORE VARIABLES
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Models:
1. slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev
2. dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2
3. vegtype2 + bclcs_level_2 #+ vegtype2:bclcs_level_2 -->do not include interaction because not all levels there


```{r}
spread_poly_NDT2<-subset(fire_spread_veg_data_df, fire_spread_veg_data_df$ntrldstrbn=="NDT2")
head(spread_poly_NDT2) #Lots of NAs in some variables (e.g., vegtype2, bclcs_level_2, bclcs_level_5_2)

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(spread_poly_NDT2$spread_bclcs5, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- spread_poly_NDT2[ trainIndex,]
   Valid <- spread_poly_NDT2[-trainIndex,]

#Run model using dat1
model.NDT2.S<-glm(spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2 + bclcs_level_2, family = binomial, data = dat1)

AIC(model.NDT2.S) #170510.5
summary(model.NDT2.S)

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.S, newdata=Valid, type="response") #
   roc_obj <- roc(Valid[,"spread"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.66
   
Anova(model.NDT2.S, type=3)
Anova(model.NDT2.S, type=3, singular.ok = TRUE)


#All variables significant, but lots of model slowness

#Remove bclcs_2 because similar to vegtype
model.NDT2.S<-glm(spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2, family = binomial, data = dat1)

AIC(model.NDT2.S) #170519
summary(model.NDT2.S)

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.S, newdata=Valid, type="response") #
   roc_obj <- roc(Valid[,"spread"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.66
   
Anova(model.NDT2.S, type=3)
Anova(model.NDT2.S, type=3, singular.ok = TRUE)

#Try with fewer interactions
model.NDT2.S<-glm(spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_dam:roads_km + dist_nat:roads_km  + dist_pow:roads_km + dist_mine:roads_km + vegtype2, family = binomial, data = dat1)

AIC(model.NDT2.S) #172958.4
summary(model.NDT2.S)

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT2.S, newdata=Valid, type="response") #
   roc_obj <- roc(Valid[,"spread"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.64
   
Anova(model.NDT2.S, type=3)
Anova(model.NDT2.S, type=3, singular.ok = TRUE)

```

Remove NAs and run multiple times.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT2_spread<-spread_poly_NDT2 %>% drop_na(slope, aspect_cos, elev, dist_mun, dist_dam, dist_nat, dist_pow, dist_mine, roads_km, bclcs_level_5_2, vegtype2) #174741 data points

#Run Model again with this data; but uses all data here
model.NDT2.S<-glm(spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2, family = binomial, data = NDT2_spread)

#Anova(model.NDT2.S, type=3)
Anova(model.NDT2.S, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT2.S), 
            residuals(model.NDT2.S), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

NDT2_spread$resids<-resid(model.NDT2.S)

# Diagnostic plots 
#slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2

visreg(model.NDT2.S, "slope", by="aspect_cos")
visreg(model.NDT2.S, "slope", by="elev")

visreg(model.NDT2.S, "elev", by="aspect_cos")
visreg(model.NDT2.S, "elev", by="slope")

visreg(model.NDT2.S, "aspect_cos", by="slope")
visreg(model.NDT2.S, "aspect_cos", by="elev")

visreg(model.NDT2.S, "dist_mun", by="roads_km")
visreg(model.NDT2.S, "dist_mun", by="bclcs_level_5_2")
visreg(model.NDT2.S, "dist_mun", by="bclcs_level_5_2", overlay=TRUE)

visreg(model.NDT2.S, "dist_dam", by="bclcs_level_5_2", overlay=TRUE)

visreg(model.NDT2.S, "dist_nat", by="roads_km")
visreg(model.NDT2.S, "dist_nat", by="bclcs_level_5_2", overlay=TRUE)

visreg(model.NDT2.S, "dist_pow", by="roads_km")
visreg(model.NDT2.S, "dist_pow", by="bclcs_level_5_2", overlay=TRUE)

visreg(model.NDT2.S, "dist_mine", by="roads_km")
visreg(model.NDT2.S, "dist_mine", by="bclcs_level_5_2", overlay=TRUE)

visreg(model.NDT2.S, "bclcs_level_5_2", by="roads_km")
visreg(model.NDT2.S, "roads_km", by="bclcs_level_5_2", overlay=TRUE)

#vegtype2 + bclcs_level_2
visreg(model.NDT2.S, "bclcs_level_2") #Water has highest probability??
visreg(model.NDT2.S, "vegtype2") #Do we need both bclcs_level2 and vegtype? Hmmm
```
We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT2.S)

#Create a new blank table and get AUC too
top_mod_table_NDT2_spread_poly <- data.frame (matrix (ncol = 85, nrow = 0))
colnames (top_mod_table_NDT2_spread_poly ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_slope", "coef_aspect_cos", "coef_elev", "coef_dist_mun", "coef_dist_dam", "coef_dist_nat", "coef_dist_pow",  "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2BU", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2ROCK", "coef_bclcs_level_5_2SOIL", "coef_bclcs_level_5_2SP", "coef_bclcs_level_5_2UR", "coef_bclcs_level_5_2WATER", "coef_vegtype2OP", "coef_vegtype2RO", "coef_vegtype2S", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_vegtype2W", "coef_slope:aspect_cos", "coef_slope:elev", "coef_aspect_cos:elev", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2BU", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2ROCK", "coef_dist_mun:bclcs_level_5_2SOIL", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mun:bclcs_level_5_2UR", "coef_dist_mun:bclcs_level_5_2WATER", "coef_dist_dam:bclcs_level_5_2BU", "coef_dist_dam:bclcs_level_5_2DE", "coef_dist_dam:bclcs_level_5_2OP", "coef_dist_dam:bclcs_level_5_2ROCK", "coef_dist_dam:bclcs_level_5_2SOIL", "coef_dist_dam:bclcs_level_5_2SP", "coef_dist_dam:bclcs_level_5_2UR", "coef_dist_dam:bclcs_level_5_2WATER", "coef_dist_nat:roads_km", "coef_dist_nat:bclcs_level_5_2BU", "coef_dist_nat:bclcs_level_5_2DE", "coef_dist_nat:bclcs_level_5_2OP", "coef_dist_nat:bclcs_level_5_2ROCK", "coef_dist_nat:bclcs_level_5_2SOIL", "coef_dist_nat:bclcs_level_5_2SP", "coef_dist_nat:bclcs_level_5_2UR", "coef_dist_nat:bclcs_level_5_2WATER", "coef_dist_pow:roads_km", "coef_dist_pow:bclcs_level_5_2BU", "coef_dist_pow:bclcs_level_5_2DE", "coef_dist_pow:bclcs_level_5_2OP", "coef_dist_pow:bclcs_level_5_2ROCK", "coef_dist_pow:bclcs_level_5_2SOIL", "coef_dist_pow:bclcs_level_5_2SP", "coef_dist_pow:bclcs_level_5_2UR", "coef_dist_pow:bclcs_level_5_2WATER", "coef_dist_mine:roads_km", "coef_dist_mine:bclcs_level_5_2BU", "coef_dist_mine:bclcs_level_5_2DE", "coef_dist_mine:bclcs_level_5_2OP", "coef_dist_mine:bclcs_level_5_2ROCK", "coef_dist_mine:bclcs_level_5_2SOIL", "coef_dist_mine:bclcs_level_5_2SP", "coef_dist_mine:bclcs_level_5_2UR", "coef_dist_mine:bclcs_level_5_2WATER", "coef_roads_km:bclcs_level_5_2BU", "coef_roads_km:bclcs_level_5_2DE", "coef_roads_km:bclcs_level_5_2OP", "coef_roads_km:bclcs_level_5_2ROCK", "coef_roads_km:bclcs_level_5_2SOIL", "coef_roads_km:bclcs_level_5_2SP", "coef_roads_km:bclcs_level_5_2UR", "coef_roads_km:bclcs_level_5_2WATER", "AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT2_spread$spread_bclcs5, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT2_spread[ trainIndex,]
   Valid <- NDT2_spread[-trainIndex,]
   
#Model   
model.NDT2.S<-glm(spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT2.S, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"spread"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT2_spread <- data.frame (matrix (ncol = 85, nrow = 0))
colnames (top_mod_table_NDT2_spread ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_slope", "coef_aspect_cos", "coef_elev", "coef_dist_mun", "coef_dist_dam", "coef_dist_nat", "coef_dist_pow",  "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2BU", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2ROCK", "coef_bclcs_level_5_2SOIL", "coef_bclcs_level_5_2SP", "coef_bclcs_level_5_2UR", "coef_bclcs_level_5_2WATER", "coef_vegtype2OP", "coef_vegtype2RO", "coef_vegtype2S", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_vegtype2W", "coef_slope:aspect_cos", "coef_slope:elev", "coef_aspect_cos:elev", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2BU", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2ROCK", "coef_dist_mun:bclcs_level_5_2SOIL", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mun:bclcs_level_5_2UR", "coef_dist_mun:bclcs_level_5_2WATER", "coef_dist_dam:bclcs_level_5_2BU", "coef_dist_dam:bclcs_level_5_2DE", "coef_dist_dam:bclcs_level_5_2OP", "coef_dist_dam:bclcs_level_5_2ROCK", "coef_dist_dam:bclcs_level_5_2SOIL", "coef_dist_dam:bclcs_level_5_2SP", "coef_dist_dam:bclcs_level_5_2UR", "coef_dist_dam:bclcs_level_5_2WATER", "coef_dist_nat:roads_km", "coef_dist_nat:bclcs_level_5_2BU", "coef_dist_nat:bclcs_level_5_2DE", "coef_dist_nat:bclcs_level_5_2OP", "coef_dist_nat:bclcs_level_5_2ROCK", "coef_dist_nat:bclcs_level_5_2SOIL", "coef_dist_nat:bclcs_level_5_2SP", "coef_dist_nat:bclcs_level_5_2UR", "coef_dist_nat:bclcs_level_5_2WATER", "coef_dist_pow:roads_km", "coef_dist_pow:bclcs_level_5_2BU", "coef_dist_pow:bclcs_level_5_2DE", "coef_dist_pow:bclcs_level_5_2OP", "coef_dist_pow:bclcs_level_5_2ROCK", "coef_dist_pow:bclcs_level_5_2SOIL", "coef_dist_pow:bclcs_level_5_2SP", "coef_dist_pow:bclcs_level_5_2UR", "coef_dist_pow:bclcs_level_5_2WATER", "coef_dist_mine:roads_km", "coef_dist_mine:bclcs_level_5_2BU", "coef_dist_mine:bclcs_level_5_2DE", "coef_dist_mine:bclcs_level_5_2OP", "coef_dist_mine:bclcs_level_5_2ROCK", "coef_dist_mine:bclcs_level_5_2SOIL", "coef_dist_mine:bclcs_level_5_2SP", "coef_dist_mine:bclcs_level_5_2UR", "coef_dist_mine:bclcs_level_5_2WATER", "coef_roads_km:bclcs_level_5_2BU", "coef_roads_km:bclcs_level_5_2DE", "coef_roads_km:bclcs_level_5_2OP", "coef_roads_km:bclcs_level_5_2ROCK", "coef_roads_km:bclcs_level_5_2SOIL", "coef_roads_km:bclcs_level_5_2SP", "coef_roads_km:bclcs_level_5_2UR", "coef_roads_km:bclcs_level_5_2WATER", "AUC")

##Add data for NDT2
top_mod_table_NDT2_spread[1,1]<-"lightning or person (ALL)"
top_mod_table_NDT2_spread[1,2]<-"NDT2"
top_mod_table_NDT2_spread[1,3]<-"ALL Treed and not treed"
top_mod_table_NDT2_spread[1,4]<-"spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2" 
top_mod_table_NDT2_spread[1,5]<- coef(model.NDT2.S)[1] #Intercept
top_mod_table_NDT2_spread[1,6]<- coef(model.NDT2.S)[2] #
top_mod_table_NDT2_spread[1,7]<- coef(model.NDT2.S)[3] #
top_mod_table_NDT2_spread[1,8]<- coef(model.NDT2.S)[4] #
top_mod_table_NDT2_spread[1,9]<- coef(model.NDT2.S)[5] #
top_mod_table_NDT2_spread[1,10]<- coef(model.NDT2.S)[6] #
top_mod_table_NDT2_spread[1,11]<- coef(model.NDT2.S)[7] 
top_mod_table_NDT2_spread[1,12]<- coef(model.NDT2.S)[8] #
top_mod_table_NDT2_spread[1,13]<- coef(model.NDT2.S)[9] #
top_mod_table_NDT2_spread[1,14]<- coef(model.NDT2.S)[10] #
top_mod_table_NDT2_spread[1,15]<- coef(model.NDT2.S)[11] #
top_mod_table_NDT2_spread[1,16]<- coef(model.NDT2.S)[12] #
top_mod_table_NDT2_spread[1,17]<- coef(model.NDT2.S)[13] #
top_mod_table_NDT2_spread[1,18]<- coef(model.NDT2.S)[14] #
top_mod_table_NDT2_spread[1,19]<- coef(model.NDT2.S)[15] #
top_mod_table_NDT2_spread[1,20]<- coef(model.NDT2.S)[16] # 
top_mod_table_NDT2_spread[1,21]<- coef(model.NDT2.S)[17] #  
top_mod_table_NDT2_spread[1,22]<- coef(model.NDT2.S)[18] #
top_mod_table_NDT2_spread[1,23]<- coef(model.NDT2.S)[19] #
top_mod_table_NDT2_spread[1,24]<- coef(model.NDT2.S)[20] #
top_mod_table_NDT2_spread[1,25]<- coef(model.NDT2.S)[21] #
top_mod_table_NDT2_spread[1,26]<- coef(model.NDT2.S)[22] #
top_mod_table_NDT2_spread[1,27]<- coef(model.NDT2.S)[23] #
top_mod_table_NDT2_spread[1,28]<- coef(model.NDT2.S)[24] #
top_mod_table_NDT2_spread[1,29]<- coef(model.NDT2.S)[25] #
top_mod_table_NDT2_spread[1,30]<- coef(model.NDT2.S)[26] #
top_mod_table_NDT2_spread[1,31]<- coef(model.NDT2.S)[27] #
top_mod_table_NDT2_spread[1,32]<- coef(model.NDT2.S)[28] #
top_mod_table_NDT2_spread[1,33]<- coef(model.NDT2.S)[29] #
top_mod_table_NDT2_spread[1,34]<- coef(model.NDT2.S)[30] #
top_mod_table_NDT2_spread[1,35]<- coef(model.NDT2.S)[31] #
top_mod_table_NDT2_spread[1,36]<- coef(model.NDT2.S)[32] #
top_mod_table_NDT2_spread[1,37]<- coef(model.NDT2.S)[33] #
top_mod_table_NDT2_spread[1,38]<- coef(model.NDT2.S)[34] #
top_mod_table_NDT2_spread[1,39]<- coef(model.NDT2.S)[35] #
top_mod_table_NDT2_spread[1,40]<- coef(model.NDT2.S)[36] #
top_mod_table_NDT2_spread[1,41]<- coef(model.NDT2.S)[37] #
top_mod_table_NDT2_spread[1,42]<- coef(model.NDT2.S)[38] #
top_mod_table_NDT2_spread[1,43]<- coef(model.NDT2.S)[39] #
top_mod_table_NDT2_spread[1,44]<- coef(model.NDT2.S)[40] #
top_mod_table_NDT2_spread[1,45]<- coef(model.NDT2.S)[41] #
top_mod_table_NDT2_spread[1,46]<- coef(model.NDT2.S)[42] #
top_mod_table_NDT2_spread[1,47]<- coef(model.NDT2.S)[43] #
top_mod_table_NDT2_spread[1,48]<- coef(model.NDT2.S)[44] #
top_mod_table_NDT2_spread[1,49]<- coef(model.NDT2.S)[45] #
top_mod_table_NDT2_spread[1,50]<- coef(model.NDT2.S)[46] #
top_mod_table_NDT2_spread[1,51]<- coef(model.NDT2.S)[47] #
top_mod_table_NDT2_spread[1,52]<- coef(model.NDT2.S)[48] #
top_mod_table_NDT2_spread[1,53]<- coef(model.NDT2.S)[49] #
top_mod_table_NDT2_spread[1,54]<- coef(model.NDT2.S)[50] #
top_mod_table_NDT2_spread[1,55]<- coef(model.NDT2.S)[51] #
top_mod_table_NDT2_spread[1,56]<- coef(model.NDT2.S)[52] #
top_mod_table_NDT2_spread[1,57]<- coef(model.NDT2.S)[53] #
top_mod_table_NDT2_spread[1,58]<- coef(model.NDT2.S)[54] #
top_mod_table_NDT2_spread[1,59]<- coef(model.NDT2.S)[55] #
top_mod_table_NDT2_spread[1,60]<- coef(model.NDT2.S)[56] #
top_mod_table_NDT2_spread[1,61]<- coef(model.NDT2.S)[57] #
top_mod_table_NDT2_spread[1,62]<- coef(model.NDT2.S)[58] #
top_mod_table_NDT2_spread[1,63]<- coef(model.NDT2.S)[59] #
top_mod_table_NDT2_spread[1,64]<- coef(model.NDT2.S)[60] #
top_mod_table_NDT2_spread[1,65]<- coef(model.NDT2.S)[61] #
top_mod_table_NDT2_spread[1,66]<- coef(model.NDT2.S)[62] #
top_mod_table_NDT2_spread[1,67]<- coef(model.NDT2.S)[63] #
top_mod_table_NDT2_spread[1,68]<- coef(model.NDT2.S)[64] #
top_mod_table_NDT2_spread[1,69]<- coef(model.NDT2.S)[65] #
top_mod_table_NDT2_spread[1,70]<- coef(model.NDT2.S)[66] #
top_mod_table_NDT2_spread[1,71]<- coef(model.NDT2.S)[67] #
top_mod_table_NDT2_spread[1,72]<- coef(model.NDT2.S)[68] #
top_mod_table_NDT2_spread[1,73]<- coef(model.NDT2.S)[69] #
top_mod_table_NDT2_spread[1,74]<- coef(model.NDT2.S)[70] #
top_mod_table_NDT2_spread[1,75]<- coef(model.NDT2.S)[71] #
top_mod_table_NDT2_spread[1,76]<- coef(model.NDT2.S)[72] #
top_mod_table_NDT2_spread[1,77]<- coef(model.NDT2.S)[73] #
top_mod_table_NDT2_spread[1,78]<- coef(model.NDT2.S)[74] #
top_mod_table_NDT2_spread[1,79]<- coef(model.NDT2.S)[75] #
top_mod_table_NDT2_spread[1,80]<- coef(model.NDT2.S)[76] #
top_mod_table_NDT2_spread[1,81]<- coef(model.NDT2.S)[77] #
top_mod_table_NDT2_spread[1,82]<- coef(model.NDT2.S)[78] #
top_mod_table_NDT2_spread[1,83]<- coef(model.NDT2.S)[79] #
top_mod_table_NDT2_spread[1,84]<- coef(model.NDT2.S)[80] #
top_mod_table_NDT2_spread[1,85]<- mod.auc

top_mod_table_NDT2_spread_poly<-rbind(top_mod_table_NDT2_spread_poly, top_mod_table_NDT2_spread)

}

```

Check.
```{r}
head(top_mod_table_NDT2_spread_poly)
```

#Save coefficient table

```{r}
write.csv(top_mod_table_NDT2_spread_poly, file="D:\\Fire\\fire_data\\raw_data\\top_mod_NDT2_spread_poly_all_.csv")
```

```{r}
names(top_mod_table_NDT2_spread_poly)
#colMeans(top_mod_table_NDT2_spread_poly[5:30])
#sapply(top_mod_table_NDT2_spread_poly,mean, na.rm = T)
#lapply(top_mod_table_NDT2_spread_poly,mean, na.rm = T)

top_mod_table_NDT2_spread_poly_means<-top_mod_table_NDT2_spread_poly %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table_NDT2_spread_poly_means

top_mod_table_NDT2_spread_poly_means[1,1]<-"lightning or person (ALL)"
top_mod_table_NDT2_spread_poly_means[1,2]<-"NDT2"
top_mod_table_NDT2_spread_poly_means[1,3]<-"ALL Treed and not treed"
top_mod_table_NDT2_spread_poly_means[1,4]<-"spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2" 
top_mod_table_NDT2_spread_poly_means
```
Save table.

```{r}
write.csv(top_mod_table_NDT2_spread_poly_means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_NDT2_spread_poly_means.csv")
```

Standard deviation.

```{r}
top_mod_table_NDT2_spread_poly_sd<-top_mod_table_NDT2_spread_poly %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT2_spread_poly_sd

top_mod_table_NDT2_spread_poly_sd[1,1]<-"lightning or person (ALL)"
top_mod_table_NDT2_spread_poly_sd[1,2]<-"NDT2"
top_mod_table_NDT2_spread_poly_sd[1,3]<-"ALL Treed and not treed"
top_mod_table_NDT2_spread_poly_sd[1,4]<-"spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_dam:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_pow:bclcs_level_5_2 + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + roads_km:bclcs_level_5_2 + vegtype2" 
top_mod_table_NDT2_spread_poly_sd
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT2_spread_poly_sd, file="D:\\Fire\\fire_data\\raw_data\\top_mod_NDT2_spread_poly_sd.csv")
```






Compare to a second model with fewer variables
```{r}
model.NDT2.S<-glm(spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + vegtype2, family = binomial, data = NDT2_spread)

visreg(model.NDT2.S, "slope", by="aspect_cos")
visreg(model.NDT2.S, "slope", by="elev")

visreg(model.NDT2.S, "elev", by="aspect_cos")
visreg(model.NDT2.S, "elev", by="slope")

visreg(model.NDT2.S, "aspect_cos", by="slope")
visreg(model.NDT2.S, "aspect_cos", by="elev")

#dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_mine:roads_km + dist_mine:bclcs_level_5_2

##visreg issues as visreg suggests the model did not converge
visreg(model.NDT2.S, "dist_mun", by="roads_km")
visreg(model.NDT2.S, "dist_mun", by="bclcs_level_5_2")
visreg(model.NDT2.S, "dist_mun", by="bclcs_level_5_2", overlay=TRUE)

visreg(model.NDT2.S, "dist_dam")

visreg(model.NDT2.S, "dist_nat", by="roads_km")
visreg(model.NDT2.S, "dist_nat", by="bclcs_level_5_2", overlay=TRUE)

visreg(model.NDT2.S, "dist_pow", by="roads_km")

visreg(model.NDT2.S, "dist_mine", by="roads_km")

visreg(model.NDT2.S, "roads_km", by="dist_mun")
visreg(model.NDT2.S, "roads_km", by="dist_nat")
visreg(model.NDT2.S, "roads_km", by="dist_pow")
visreg(model.NDT2.S, "roads_km", by="dist_mine")

#vegtype2
visreg(model.NDT2.S, "vegtype2") 
```

```{r}
summary(model.NDT2.S)

#Create a new blank table and get AUC too
top_mod_table2_NDT2_spread_poly <- data.frame (matrix (ncol = 61, nrow = 0))
colnames (top_mod_table2_NDT2_spread_poly ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_slope", "coef_aspect_cos", "coef_elev", "coef_dist_mun", "coef_dist_dam", "coef_dist_nat", "coef_dist_pow",  "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2BU", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2ROCK", "coef_bclcs_level_5_2SOIL", "coef_bclcs_level_5_2SP", "coef_bclcs_level_5_2UR", "coef_bclcs_level_5_2WATER", "coef_vegtype2OP", "coef_vegtype2RO", "coef_vegtype2S", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_vegtype2W", "coef_slope:aspect_cos", "coef_slope:elev", "coef_aspect_cos:elev", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2BU", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2ROCK", "coef_dist_mun:bclcs_level_5_2SOIL", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mun:bclcs_level_5_2UR", "coef_dist_mun:bclcs_level_5_2WATER",  "coef_dist_nat:roads_km", "coef_dist_nat:bclcs_level_5_2BU", "coef_dist_nat:bclcs_level_5_2DE", "coef_dist_nat:bclcs_level_5_2OP", "coef_dist_nat:bclcs_level_5_2ROCK", "coef_dist_nat:bclcs_level_5_2SOIL", "coef_dist_nat:bclcs_level_5_2SP", "coef_dist_nat:bclcs_level_5_2UR", "coef_dist_nat:bclcs_level_5_2WATER", "coef_dist_pow:roads_km",  "coef_dist_mine:roads_km", "coef_dist_mine:bclcs_level_5_2BU", "coef_dist_mine:bclcs_level_5_2DE", "coef_dist_mine:bclcs_level_5_2OP", "coef_dist_mine:bclcs_level_5_2ROCK", "coef_dist_mine:bclcs_level_5_2SOIL", "coef_dist_mine:bclcs_level_5_2SP", "coef_dist_mine:bclcs_level_5_2UR", "coef_dist_mine:bclcs_level_5_2WATER", "AUC")
```

Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT2_spread$spread_bclcs5, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT2_spread[ trainIndex,]
   Valid <- NDT2_spread[-trainIndex,]
   
#Model   
model.NDT2.S<-glm (spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + vegtype2, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT2.S, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"spread"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table2_NDT2_spread <- data.frame (matrix (ncol = 61, nrow = 0))
colnames (top_mod_table2_NDT2_spread ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_slope", "coef_aspect_cos", "coef_elev", "coef_dist_mun", "coef_dist_dam", "coef_dist_nat", "coef_dist_pow",  "coef_dist_mine", "coef_roads_km", "coef_bclcs_level_5_2BU", "coef_bclcs_level_5_2DE", "coef_bclcs_level_5_2OP", "coef_bclcs_level_5_2ROCK", "coef_bclcs_level_5_2SOIL", "coef_bclcs_level_5_2SP", "coef_bclcs_level_5_2UR", "coef_bclcs_level_5_2WATER", "coef_vegtype2OP", "coef_vegtype2RO", "coef_vegtype2S", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_vegtype2W", "coef_slope:aspect_cos", "coef_slope:elev", "coef_aspect_cos:elev", "coef_dist_mun:roads_km", "coef_dist_mun:bclcs_level_5_2BU", "coef_dist_mun:bclcs_level_5_2DE", "coef_dist_mun:bclcs_level_5_2OP", "coef_dist_mun:bclcs_level_5_2ROCK", "coef_dist_mun:bclcs_level_5_2SOIL", "coef_dist_mun:bclcs_level_5_2SP", "coef_dist_mun:bclcs_level_5_2UR", "coef_dist_mun:bclcs_level_5_2WATER",  "coef_dist_nat:roads_km", "coef_dist_nat:bclcs_level_5_2BU", "coef_dist_nat:bclcs_level_5_2DE", "coef_dist_nat:bclcs_level_5_2OP", "coef_dist_nat:bclcs_level_5_2ROCK", "coef_dist_nat:bclcs_level_5_2SOIL", "coef_dist_nat:bclcs_level_5_2SP", "coef_dist_nat:bclcs_level_5_2UR", "coef_dist_nat:bclcs_level_5_2WATER", "coef_dist_pow:roads_km",  "coef_dist_mine:roads_km", "coef_dist_mine:bclcs_level_5_2BU", "coef_dist_mine:bclcs_level_5_2DE", "coef_dist_mine:bclcs_level_5_2OP", "coef_dist_mine:bclcs_level_5_2ROCK", "coef_dist_mine:bclcs_level_5_2SOIL", "coef_dist_mine:bclcs_level_5_2SP", "coef_dist_mine:bclcs_level_5_2UR", "coef_dist_mine:bclcs_level_5_2WATER", "AUC")

##Add data for NDT2
top_mod_table2_NDT2_spread[1,1]<-"lightning or person (ALL)"
top_mod_table2_NDT2_spread[1,2]<-"NDT2"
top_mod_table2_NDT2_spread[1,3]<-"ALL Treed and not treed"
top_mod_table2_NDT2_spread[1,4]<-"spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + vegtype2" 
top_mod_table2_NDT2_spread[1,5]<- coef(model.NDT2.S)[1] #Intercept
top_mod_table2_NDT2_spread[1,6]<- coef(model.NDT2.S)[2] #
top_mod_table2_NDT2_spread[1,7]<- coef(model.NDT2.S)[3] #
top_mod_table2_NDT2_spread[1,8]<- coef(model.NDT2.S)[4] #
top_mod_table2_NDT2_spread[1,9]<- coef(model.NDT2.S)[5] #
top_mod_table2_NDT2_spread[1,10]<- coef(model.NDT2.S)[6] #
top_mod_table2_NDT2_spread[1,11]<- coef(model.NDT2.S)[7] 
top_mod_table2_NDT2_spread[1,12]<- coef(model.NDT2.S)[8] #
top_mod_table2_NDT2_spread[1,13]<- coef(model.NDT2.S)[9] #
top_mod_table2_NDT2_spread[1,14]<- coef(model.NDT2.S)[10] #
top_mod_table2_NDT2_spread[1,15]<- coef(model.NDT2.S)[11] #
top_mod_table2_NDT2_spread[1,16]<- coef(model.NDT2.S)[12] #
top_mod_table2_NDT2_spread[1,17]<- coef(model.NDT2.S)[13] #
top_mod_table2_NDT2_spread[1,18]<- coef(model.NDT2.S)[14] #
top_mod_table2_NDT2_spread[1,19]<- coef(model.NDT2.S)[15] #
top_mod_table2_NDT2_spread[1,20]<- coef(model.NDT2.S)[16] # 
top_mod_table2_NDT2_spread[1,21]<- coef(model.NDT2.S)[17] #  
top_mod_table2_NDT2_spread[1,22]<- coef(model.NDT2.S)[18] #
top_mod_table2_NDT2_spread[1,23]<- coef(model.NDT2.S)[19] #
top_mod_table2_NDT2_spread[1,24]<- coef(model.NDT2.S)[20] #
top_mod_table2_NDT2_spread[1,25]<- coef(model.NDT2.S)[21] #
top_mod_table2_NDT2_spread[1,26]<- coef(model.NDT2.S)[22] #
top_mod_table2_NDT2_spread[1,27]<- coef(model.NDT2.S)[23] #
top_mod_table2_NDT2_spread[1,28]<- coef(model.NDT2.S)[24] #
top_mod_table2_NDT2_spread[1,29]<- coef(model.NDT2.S)[25] #
top_mod_table2_NDT2_spread[1,30]<- coef(model.NDT2.S)[26] #
top_mod_table2_NDT2_spread[1,31]<- coef(model.NDT2.S)[27] #
top_mod_table2_NDT2_spread[1,32]<- coef(model.NDT2.S)[28] #
top_mod_table2_NDT2_spread[1,33]<- coef(model.NDT2.S)[29] #
top_mod_table2_NDT2_spread[1,34]<- coef(model.NDT2.S)[30] #
top_mod_table2_NDT2_spread[1,35]<- coef(model.NDT2.S)[31] #
top_mod_table2_NDT2_spread[1,36]<- coef(model.NDT2.S)[32] #
top_mod_table2_NDT2_spread[1,37]<- coef(model.NDT2.S)[33] #
top_mod_table2_NDT2_spread[1,38]<- coef(model.NDT2.S)[34] #
top_mod_table2_NDT2_spread[1,39]<- coef(model.NDT2.S)[35] #
top_mod_table2_NDT2_spread[1,40]<- coef(model.NDT2.S)[36] #
top_mod_table2_NDT2_spread[1,41]<- coef(model.NDT2.S)[37] #
top_mod_table2_NDT2_spread[1,42]<- coef(model.NDT2.S)[38] #
top_mod_table2_NDT2_spread[1,43]<- coef(model.NDT2.S)[39] #
top_mod_table2_NDT2_spread[1,44]<- coef(model.NDT2.S)[40] #
top_mod_table2_NDT2_spread[1,45]<- coef(model.NDT2.S)[41] #
top_mod_table2_NDT2_spread[1,46]<- coef(model.NDT2.S)[42] #
top_mod_table2_NDT2_spread[1,47]<- coef(model.NDT2.S)[43] #
top_mod_table2_NDT2_spread[1,48]<- coef(model.NDT2.S)[44] #
top_mod_table2_NDT2_spread[1,49]<- coef(model.NDT2.S)[45] #
top_mod_table2_NDT2_spread[1,50]<- coef(model.NDT2.S)[46] #
top_mod_table2_NDT2_spread[1,51]<- coef(model.NDT2.S)[47] #
top_mod_table2_NDT2_spread[1,52]<- coef(model.NDT2.S)[48] #
top_mod_table2_NDT2_spread[1,53]<- coef(model.NDT2.S)[49] #
top_mod_table2_NDT2_spread[1,54]<- coef(model.NDT2.S)[50] #
top_mod_table2_NDT2_spread[1,55]<- coef(model.NDT2.S)[51] #
top_mod_table2_NDT2_spread[1,56]<- coef(model.NDT2.S)[52] #
top_mod_table2_NDT2_spread[1,57]<- coef(model.NDT2.S)[53] #
top_mod_table2_NDT2_spread[1,58]<- coef(model.NDT2.S)[54] #
top_mod_table2_NDT2_spread[1,59]<- coef(model.NDT2.S)[55] #
top_mod_table2_NDT2_spread[1,60]<- coef(model.NDT2.S)[56] #
top_mod_table2_NDT2_spread[1,61]<- mod.auc

top_mod_table2_NDT2_spread_poly<-rbind(top_mod_table2_NDT2_spread_poly, top_mod_table2_NDT2_spread)

}

```

Check.
```{r}
head(top_mod_table2_NDT2_spread_poly)
```

#Save coefficient table

```{r}
write.csv(top_mod_table2_NDT2_spread_poly, file="D:\\Fire\\fire_data\\raw_data\\top_mod_NDT2_spread_poly_all_2.csv")
```

```{r}
names(top_mod_table2_NDT2_spread_poly)
#colMeans(top_mod_table2_NDT2_spread_poly[5:30])
#sapply(top_mod_table2_NDT2_spread_poly,mean, na.rm = T)
#lapply(top_mod_table2_NDT2_spread_poly,mean, na.rm = T)

top_mod_table2_NDT2_spread_poly_means<-top_mod_table2_NDT2_spread_poly %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table2_NDT2_spread_poly_means

top_mod_table2_NDT2_spread_poly_means[1,1]<-"lightning or person (ALL)"
top_mod_table2_NDT2_spread_poly_means[1,2]<-"NDT2"
top_mod_table2_NDT2_spread_poly_means[1,3]<-"ALL Treed and not treed"
top_mod_table2_NDT2_spread_poly_means[1,4]<-"spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + vegtype2" 
top_mod_table2_NDT2_spread_poly_means
```
Save table.

```{r}
write.csv(top_mod_table2_NDT2_spread_poly_means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_NDT2_spread_poly_means2.csv")
```

Standard deviation.

```{r}
top_mod_table2_NDT2_spread_poly_sd<-top_mod_table2_NDT2_spread_poly %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table2_NDT2_spread_poly_sd

top_mod_table2_NDT2_spread_poly_sd[1,1]<-"lightning or person (ALL)"
top_mod_table2_NDT2_spread_poly_sd[1,2]<-"NDT2"
top_mod_table2_NDT2_spread_poly_sd[1,3]<-"ALL Treed and not treed"
top_mod_table2_NDT2_spread_poly_sd[1,4]<-"spread ~ slope + aspect_cos + elev + slope:aspect_cos + slope:elev + aspect_cos:elev + dist_mun + dist_dam + dist_nat + dist_pow + dist_mine + roads_km + bclcs_level_5_2 + dist_mun:roads_km + dist_mun:bclcs_level_5_2 + dist_nat:roads_km + dist_nat:bclcs_level_5_2 + dist_pow:roads_km + dist_mine:roads_km + dist_mine:bclcs_level_5_2 + vegtype2" 
top_mod_table2_NDT2_spread_poly_sd
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table2_NDT2_spread_poly_sd, file="D:\\Fire\\fire_data\\raw_data\\top_mod_NDT2_spread_poly_sd2.csv")
```

