---
title: "15_escape_model_fits_FRT10"
author: "Elizabeth Kleynhans"
date: '2022-10-18'
output: html_document
---

Goal with this script is to try over sampling, under sampling and doing nothing and comparing the results for FRT 14.

i.e. try to make an informed decisions as to whether I should worry about under/over/nothing sample.

# conclusion. Im not sure! the intercepts are different when I plot the individual lines but when I simulate the data to get 95% CI they overlap. Probably my simulation is bad. Although the probability line looks a bit more plausable.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Load relevant libraries
library(sf)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(RPostgreSQL)
library(rpostgis)
library(dplyr)
library(lme4)
library(arm)
library(ggpubr)
library(mgcv)
library(nlme)
library(purrr)
library(tidyr)
library(caret)
library(pROC)
library(keyring)
library(ggcorrplot) 
library(kableExtra)
library(data.table)
library(DBI)
library(here)
library(AICcmodavg)
library(rje)
library(base)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 15_escape_model_fits_FRT10
#  Script Version: 1.0
#  Script Purpose: FRT 10 looking at different methodologies for under or over sampling my data
#  Script Author: Elizabeth Kleynhans, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests.
#=================================

Load in the prepped data.

```{r}
Escape_data_ALL <- st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\Fire_escape_data_all.gpkg")
head(Escape_data_ALL)
dim(Escape_data_ALL)

# set fires > 10ha =1 (escaped) and fires<=10 = 0 (contained fires)
Escape_data_ALL$escape10<- NA
Escape_data_ALL$escape10[Escape_data_ALL$size_ha > 10] <- 1
Escape_data_ALL$escape10[Escape_data_ALL$size_ha <= 10] <- 0
```


```{r}
table(is.na(Escape_data_ALL$Cluster)) # wierd there are 13 points that have no Cluster assigned to them. I looked at these points in Qgis and all but one of them are in FRT =15.
Escape_data_ALL$Cluster[Escape_data_ALL$idno==238]<-13
Escape_data_ALL$Cluster[is.na(Escape_data_ALL$Cluster)]<-15

Escape_data_ALL$Cluster[Escape_data_ALL$Cluster==3]<-5
 table(Escape_data_ALL$Cluster)
 
Escape_data_ALL$mean_PPT04_PPT05_PPT06<-(Escape_data_ALL$PPT04 + Escape_data_ALL$PPT05 + Escape_data_ALL$PPT06)/3
Escape_data_ALL$mean_PPT05_PPT06_PPT07_PPT08  <-(Escape_data_ALL$PPT05 + Escape_data_ALL$PPT06 + Escape_data_ALL$PPT07 + Escape_data_ALL$PPT08)/4
Escape_data_ALL$mean_Tave05_Tave06_Tave07_Tave08<-(Escape_data_ALL$Tave05 + Escape_data_ALL$Tave06 + Escape_data_ALL$Tave07 + Escape_data_ALL$Tave08)/4
Escape_data_ALL$mean_Tave04_Tave05_Tave06<-(Escape_data_ALL$Tave04 + Escape_data_ALL$Tave05 + Escape_data_ALL$Tave06)/3

Escape_data_ALL$wind_atfire<-0
Escape_data_ALL$ig_mnth<-as.numeric(Escape_data_ALL$ig_mnth)
head(Escape_data_ALL)
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(wind_atfire = case_when(ig_mnth == 1 ~ win_spg, #even though not quite accurate
                                  ig_mnth == 2 ~ win_spg, #even though not quite accurate
                                  ig_mnth == 3 ~ win_spg,
                                  ig_mnth == 4 ~ win_spg,
                                  ig_mnth == 5 ~ win_spg,
                                  ig_mnth == 6 ~ win_sum,
                                  ig_mnth == 7 ~ win_sum,
                                  ig_mnth == 8 ~ win_sum,
                                  ig_mnth == 9 ~ win_sum,#even though not quite accurate
                                  ig_mnth == 10 ~ win_sum,#even though not quite accurate
                                  ig_mnth == 11 ~ win_spg,#even though not quite accurate
                                  ig_mnth == 12 ~ win_spg,#even though not quite accurate
                                  TRUE ~ win_spg))

Escape_data_ALL$wind_atfire
hist(Escape_data_ALL$wind_atfire)

```
Create variable called Tdiff_atfire, PPTdiff_atfire and MDCdiff_atfire i.e. difference between the temperature/precipitation/MDC at the month of the fire and the one before.

#note there are a few ignitions in the months January and December. For now Im going to filter these out but maybe I should include them in the future. Presumabily non of these fires escape
```{r}
Escape_data_ALL<-Escape_data_ALL %>% filter(ig_mnth > 1)
Escape_data_ALL<-Escape_data_ALL %>% filter(ig_mnth!=12)

hist(Escape_data_ALL$ig_mnth)

#############################################
# Tmax temp at fire and month before
#############################################
Escape_data_ALL$temp_atfire<-0
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(temp_atfire = case_when(
                                  ig_mnth == 2 ~ Tmax02, 
                                  ig_mnth == 3 ~ Tmax03,
                                  ig_mnth == 4 ~ Tmax04,
                                  ig_mnth == 5 ~ Tmax05,
                                  ig_mnth == 6 ~ Tmax06,
                                  ig_mnth == 7 ~ Tmax07,
                                  ig_mnth == 8 ~ Tmax08,
                                  ig_mnth == 9 ~ Tmax09,
                                  ig_mnth == 10 ~ Tmax10,#even though not quite accurate
                                  ig_mnth == 11 ~ Tmax11,                                  TRUE ~ 999))

Escape_data_ALL$temp_mnthbefore<-0
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(temp_mnthbefore = case_when(ig_mnth == 2 ~ Tmax02,
                                  ig_mnth == 3 ~ Tmax02,
                                  ig_mnth == 4 ~ Tmax03,
                                  ig_mnth == 5 ~ Tmax04,
                                  ig_mnth == 6 ~ Tmax05,
                                  ig_mnth == 7 ~ Tmax06,
                                  ig_mnth == 8 ~ Tmax07,
                                  ig_mnth == 9 ~ Tmax08,
                                  ig_mnth == 10 ~ Tmax09,
                                  ig_mnth == 11 ~ Tmax10,                                  TRUE ~ 999))

hist(Escape_data_ALL$temp_mnthbefore)
hist(Escape_data_ALL$temp_atfire)

Escape_data_ALL$tmax_2mtns<-(Escape_data_ALL$temp_mnthbefore + Escape_data_ALL$temp_atfire)/2

hist(Escape_data_ALL$tmax_2mtns)

#############################################
# average temp at fire and month before
#############################################
Escape_data_ALL$tempave_atfire<-0
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(tempave_atfire = case_when(
                                  ig_mnth == 2 ~ Tave02, 
                                  ig_mnth == 3 ~ Tave03,
                                  ig_mnth == 4 ~ Tave04,
                                  ig_mnth == 5 ~ Tave05,
                                  ig_mnth == 6 ~ Tave06,
                                  ig_mnth == 7 ~ Tave07,
                                  ig_mnth == 8 ~ Tave08,
                                  ig_mnth == 9 ~ Tave09,
                                  ig_mnth == 10 ~ Tave10,#even though not quite accurate
                                  ig_mnth == 11 ~ Tave11,                                  TRUE ~ 999))

Escape_data_ALL$tempave_mnthbefore<-0
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(tempave_mnthbefore = case_when(ig_mnth == 2 ~ Tave02,
                                  ig_mnth == 3 ~ Tave02,
                                  ig_mnth == 4 ~ Tave03,
                                  ig_mnth == 5 ~ Tave04,
                                  ig_mnth == 6 ~ Tave05,
                                  ig_mnth == 7 ~ Tave06,
                                  ig_mnth == 8 ~ Tave07,
                                  ig_mnth == 9 ~ Tave08,
                                  ig_mnth == 10 ~ Tave09,
                                  ig_mnth == 11 ~ Tave10,                                  TRUE ~ 999))

hist(Escape_data_ALL$tempave_mnthbefore)
hist(Escape_data_ALL$tempave_atfire)

Escape_data_ALL$Tave_2mtns<-(Escape_data_ALL$tempave_mnthbefore + Escape_data_ALL$tempave_atfire)/2

#############################################
# PPT at fire and month before
#############################################
Escape_data_ALL$ppt_atfire<-9999
Escape_data_ALL<-Escape_data_ALL %>% mutate_at (c ('PPT02','PPT03', 'PPT04','PPT05', 'PPT06', 'PPT07', 'PPT08', 'PPT09', 'PPT10','PPT11'), as.numeric)
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(ppt_atfire = case_when(ig_mnth == 2 ~ PPT02, 
                                  ig_mnth == 3 ~ PPT03,
                                  ig_mnth == 4 ~ PPT04,
                                  ig_mnth == 5 ~ PPT05,
                                  ig_mnth == 6 ~ PPT06,
                                  ig_mnth == 7 ~ PPT07,
                                  ig_mnth == 8 ~ PPT08,
                                  ig_mnth == 9 ~ PPT09,
                                  ig_mnth == 10 ~ PPT10,
                                  ig_mnth == 11 ~ PPT11, 
                                  TRUE ~ 9999))

Escape_data_ALL$ppt_mnthbefore<-9999
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(ppt_mnthbefore = case_when(ig_mnth == 2 ~ PPT02,
                                  ig_mnth == 3 ~ PPT02,
                                  ig_mnth == 4 ~ PPT03,
                                  ig_mnth == 5 ~ PPT04,
                                  ig_mnth == 6 ~ PPT05,
                                  ig_mnth == 7 ~ PPT06,
                                  ig_mnth == 8 ~ PPT07,
                                  ig_mnth == 9 ~ PPT08,
                                  ig_mnth == 10 ~ PPT09,
                                  ig_mnth == 11 ~ PPT10,                                  TRUE ~ 9999))

Escape_data_ALL %>% filter(ppt_atfire==9999)
Escape_data_ALL %>% filter(ppt_mnthbefore==9999)

hist(Escape_data_ALL$ppt_mnthbefore)
hist(Escape_data_ALL$ppt_atfire)

Escape_data_ALL$ppt_2mtns<-(Escape_data_ALL$ppt_mnthbefore + Escape_data_ALL$ppt_atfire)/2


## Create empty vector
Escape_data_ALL$climate1<-0
head(Escape_data_ALL)

Escape_data_ALL$Cluster_numeric<-as.numeric(as.character(Escape_data_ALL$Cluster))

Escape_data_ALL<-Escape_data_ALL %>%
    mutate(climate1 = case_when(Cluster_numeric == 5 ~ PPT05, 
                                Cluster_numeric == 7 ~ temp_mnthbefore, 
                                Cluster_numeric == 9 ~ Tave05, 
                                Cluster_numeric == 10 ~ mean_Tave05_Tave06_Tave07_Tave08,
                                Cluster_numeric == 11 ~ Tave09, 
                                Cluster_numeric == 12 ~ mean_Tave04_Tave05_Tave06,
                                Cluster_numeric == 13 ~ Tmax09,
                                Cluster_numeric == 14 ~ temp_atfire,
                                Cluster_numeric == 15 ~ Tave04,
                                TRUE ~ NA_real_))

#Repeat for climate 2
Escape_data_ALL$climate2<-0

#Perform mutate to get the applicable variable for each row
Escape_data_ALL<-Escape_data_ALL %>%
    mutate(climate2 = case_when(Cluster_numeric == 7 ~ ppt_mnthbefore,
                                Cluster_numeric == 10 ~ mean_PPT05_PPT06_PPT07_PPT08,
                                Cluster_numeric == 12 ~ mean_PPT04_PPT05_PPT06,
                                Cluster_numeric == 14 ~ ppt_atfire,
                                Cluster_numeric == 15 ~ PPT04,TRUE ~ NA_real_))

head(Escape_data_ALL)

# before running any models wer are going to remove W and N because fires cannot spread on this landscape type.

Escape_data_ALL2<-Escape_data_ALL %>% filter(!FWI_veg %in% c("W", "N"))

```

```{r}
frt14 <- Escape_data_ALL2 %>% filter(Cluster==14)

table(frt14$escape10) #(6 % are escaped)
table(frt14$FWI_veg)
#frt14$FWI_veg[frt14$FWI_veg == "C-2"] <- "C-3"
#frt14$FWI_veg[frt14$FWI_veg == "C-5"] <- "C-3"

frt14$veg_escape<-paste(frt14$escape10, frt14$FWI_veg)
table(frt14$veg_escape)
frt14 <- frt14 %>% filter(veg_escape!="0 NA")
table(frt14$veg_escape) #na value is gone, good

# remove geometry column
frt14<-st_drop_geometry(frt14)

```


### First create a model with no resampling and look at the error rate
```{r}
#Divide data into training and valid
prop<-0.75
  trainIndex <- createDataPartition(frt14$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
   dat1 <- frt14[ trainIndex,]
   Valid <- frt14[-trainIndex,]

#Run model using dat1
model_ft14<-glm(escape10 ~ climate1 + climate2 + FWI_veg + elevatn + rd_dst_ + wind_atfire + fire_cs, family = binomial, data = dat1)
summary(model_ft14)
AIC(model_ft14) #2834.331

#Determine AUC of full model
mod.valid1 <- predict.glm(model_ft14, newdata=Valid, type="response")
   roc_obj1 <- roc(Valid[,"escape10"], mod.valid1)
   mod.auc1 <- auc(roc_obj1)
   mod.auc1 #0.7038
   plot(roc_obj1)
   
Anova(model_ft14, type=3) #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred"
#Anova(model.NDT1.E, type=3, singular.ok = TRUE)

```



# now try oversampling the 1's

```{r}
prop<-0.75
  
trainIndex <- createDataPartition(frt14$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
   dat1 <- frt14[ trainIndex,] # note only 6% of obs are 1's so Im going to sample to get my sample size up to 30% 1's.
   # in total I need 1589 1's
   dat1_1<-dat1 %>% filter(escape10==1)
   dat1_0<-dat1 %>% filter(escape10==0)
   dat1_1_samp<- sample_n(dat1_1, 1590, replace = TRUE)
   
   dat<-rbind(dat1_0, dat1_1_samp)
   Valid <- frt14[-trainIndex,]

#Run model using dat1
model_ft14_over<-glm(escape10 ~ climate1 + climate2 + FWI_veg + elevatn + rd_dst_ + wind_atfire + fire_cs, family = binomial, data = dat)
summary(model_ft14_over)

# correct intercept value following King & Zeng 2001
# B0 - ln((1-fraction of ones in pop)/fraction of ones in pop * (1-fraction of ones in sample)/fraction of ones in sample )

B1<-model_ft14_over$coefficients[1] - log10(((1-509/8470)/(509/8470))* ((1-1590/6356)/(1590/6356)))
AIC(model_ft14) 

#Determine AUC of full model
mod.valid1 <- predict.glm(model_ft14, newdata=Valid, type="response")
   roc_obj1 <- roc(Valid[,"escape10"], mod.valid1)
   plot(roc_obj1)
   mod.auc <- auc(roc_obj1)
   mod.auc #0.6602
   
Anova(model_ft14, type=3) #Lots of "glm.fit: fitted probabilities numerically 0 or 1 occurred"
#Anova(model.NDT1.E, type=3, singular.ok = TRUE)
```


plot results of two models and look at outcome

```{r}
# regular model

plot(frt14$climate1, frt14$escape10)
normal_line<-invlogit(coef(model_ft14)[1] + coef(model_ft14)[2]* frt14$climate1)
lines(frt14$climate1, normal_line, col="blue")
oversamp_line<-invlogit(B1 + coef(model_ft14_over)[2]* frt14$climate1)
lines(frt14$climate1, oversamp_line, col="red")

sim1.normal<- sim(model_ft14)
for(j in 1:10){
  lines(invlogit(coef(sim1.normal)[j,1] + coef(sim1.normal)[j,2]* frt14$climate1), add=TRUE)
}

sim1.over<- sim(model_ft14_over)

for(j in 1:10){
  lines(invlogit((coef(sim1.over)[j,1] - log10(((1-509/8470)/(509/8470))* ((1-1590/6356)/(1590/6356)))) + coef(sim1.over)[j,2]* frt14$climate1))
}

coef(sim1.over)[,1] - log10(((1-509/8470)/(509/8470))* ((1-1590/6356)/(1590/6356)))

```


# TRY WITH FRT 5
```{r}
model_ft5d<-glm(escape10 ~ climate1 + as.factor(FWI_veg) + elevatn + rd_dst_ + as.factor(fire_cs), family = binomial, data = escape_frt5)
summary(model_ft5d)

# oversampling the 1's
escape_frt5$veg_escape<-paste(escape_frt5$escape10, escape_frt5$FWI_veg)

prop<-0.75
  
trainIndex <- createDataPartition(escape_frt5$veg_escape, p = prop,
                                    list = FALSE,
                                    times = 1)
   dat1 <- escape_frt5[ trainIndex,] # note only 6% of obs are 1's so Im going to sample to get my sample size up to 30% 1's.
   # in total I need 1589 1's
   dat1_1<-dat1 %>% filter(escape10==1)
   dat1_0<-dat1 %>% filter(escape10==0)
   dat1_1_samp<- sample_n(dat1_1, 467, replace = TRUE)
   
   dat<-rbind(dat1_0, dat1_1_samp)
   Valid <- escape_frt5[-trainIndex,]

#Run model using dat1
model_ft5_over<-glm(escape10 ~ climate1 + as.factor(FWI_veg) + elevatn + rd_dst_ + as.factor(fire_cs), family = binomial, data = dat)
summary(model_ft5_over)

B1<-model_ft5_over$coefficients[1] - log10(((1-243/935)/(243/935))* ((1-467/703)/(467/703)))



```

```{r}
# regular model

plot(escape_frt5$climate1, escape_frt5$escape10)
normal_line<-invlogit(coef(model_ft5d)[1] + coef(model_ft5d)[2]* escape_frt5$climate1)
lines(escape_frt5$climate1, normal_line, col="blue")
oversamp_line<-invlogit(B1 + coef(model_ft5_over)[2]* dat$climate1)
lines(dat$climate1, oversamp_line, col="red")

sim1.normal<- sim(model_ft5d)
for(j in 1:10){
  lines(invlogit(coef(sim1.normal)[j,1] + coef(sim1.normal)[j,2]* escape_frt5$climate1), add=TRUE)
}

sim1.over<- sim(model_ft5_over)

for(j in 1:10){
  lines(invlogit((coef(sim1.over)[j,1] - log10(((1-243/935)/(243/935))* ((1-467/703)/(467/703)))) + coef(sim1.over)[j,2]* frt14$climate1))
}

coef(sim1.over)[,1] - log10(((1-509/8470)/(509/8470))* ((1-1590/6356)/(1590/6356)))

```

