---
title: "Fire ignition - description of methods"
author: "Elizabeth Kleynhans"
date: "25/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Broad overview of wild fire simulation project

The goal of this project is to simulate fire into the future. To do this I am roughly following the methods outlined by Marchal et al. (2020) Turning down the heat: Vegetation feedbacks limit fire regime responses to global warming. Ecosystems 23: 204-216. (https://link.springer.com/article/10.1007/s10021-019-00398-2).
Briefly, the process of wildfires is split into three steps 1.) ignition, 2.) escape, and 3.) spread. For the ignition and escape steps the plan is to develop a statistical model using climate and vegetation parameters that best describe each process. Then I simulate the process forward by using the derived parameters and climate and vegetation data predicted for the future. More details of how the  statistical model is derived for fire ignitions is also outlined in 
Marchal.et.a.l 2017. Exploiting poisson additivity to predict fire frequency from maps of fire weather and land cover in boreal forests of Quebec, Canada. Ecography 40: 200 - 209. I roughly follow this. More details of the scripts used and exact methods I follow for ignition are described in the next section. For escape I was planning on doing what Marchal et al 2020 did. The way to model fire spread Im less clear on.


## Overview of the ignition module

This module provides the logic for simulating fire ignitions on the landscape. The main goal is to create a map of the probability of ignition for each year into the future. I develop a logistic regression model examining the presence or absence (available) of a fire ignition in relation to the climate and vegetation. Because BC is so large and bioclimatically diverse I perform a separate logistic regression model for each BEC zone. Splitting the analysis up by BEC zone hopefully helps to improve the predictive power of the model.   

## Historical data used to obtain logistic regression parameters 

Fire ignition locations for all of BC for the years 2002 to 2020 are obtained from https://catalogue.data.gov.bc.ca/dataset/fire-incident-locations-historical. The script to prepare this data can be found in C:\Work\caribou\clus\R\fire_sim\01_fire_ignition_data_prep.R.  The ignition locations include fires started by humans, lightning, and other causes such as prescribed burns. For easy I focus the analysis on lightning caused fires only, but it might be possible to calculate the probability of ignition due to human caused fires using road densities or something like the human footprint index that could be included in the statistical model in addition to vegetation and climate data. This might be something to add in the future. 

Climate data for the locations where fires were and were not observed are obtained from climateBC (http://climatebc.ca/) for all years 2002 to 2020 The script to prepare this data can be found in C:\Work\caribou\clus\R\fire_sim\02_climate_data_prep.R. 
Briefly, the script obtains the lat, long coordinates of fire ignition locations and samples locations where fires were not observed to start. It then creates a csv file with these locations that is used to manually extract monthly average climate variables from climateBC (http://climatebc.ca/) for all years 2002 to 2020. After the climate data has been extracted from climateBC this data is reimported into the script and the mean monthly drought code for the months  May - September is calculated for each year. After running this script I get the maximum temperature, minimum temperature, average temperature, total precipitation, and mean monthly drought code for the months May - September for each year 2002 - 2020 for all fire ignition locations and randomly sampled (available fire ignition locations (fire absence)) locations on the landscape. I save this climate data in postgres so that for the same locations I can query the VRI for vegetation data. 

VRI (vegetation resource inventory) data is downloaded from (https://catalogue.data.gov.bc.ca/dataset/vri-historical-vegetation-resource-inventory-2002-2019-). To query the VRI I use the script C:\Work\caribou\clus\R\fire_sim\03_vri_data_prep.R. I could only obtain VRI data for the years 2002 - 2019 and this is why the fire statistical model is fit to these years. From the VRI I obtain for each ignition location and randomly sampled location the type of vegetation e.g. coniferous forest, mixed forest, deciduous forest, shrub land, water, etc. I also obtain the projected height of the forest, the projected age of the forest, and the predicted volume of the forest. The queries are run in postgres since this is much faster than R. Detailed methods for how to do this are outlined in the script file. At the end fire, climate and vegetation data for every year is imported into R and amalgamated so the statistical analysis can be run using these variables. 

The final dataset used to fit the statistical equations can be found in postgres (KyleCLUS) under the name public.fire_ignitions_veg_climate


## Statistics

To select the best single fire weather covariate I first conducted exploratory graphical analyses of the correlations between fire frequency and various fire weather variables. Then I fit generalized linear models for each fire weather variable using a binomial error structure with logarithmic link. Candidate variables were monthly average temperature, monthly maximum temperature, monthly precipitations and the five mean drought codes (MDC’s). I also added various two, three or fourth-month means of these values (e.g. for May, June, July and August) to test for seasonal effects (e.g. spring vs. summer). These methods loosely follow those described by Marchal et al. (2017) Ecography (https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.01849) Supporting Information Appendix 1 The goal is to try to figure out which is the best climate variable or climate variables to include in my model. I run simple models of the form: logb(p/1-p) = B0 + B1x1 or logb(p/1-p) = B0 + B1x1 + B2x2 or logb(p/1-p) = B0 + B1x1 + B2x2 + B3x1x2
and extract the AIC as a means for comparison. I also calculate the AUC by splitting the data into a training and validation data set. Finally I repeat the analysis calculating the AIC and AUC using traing and validation data sets 100 times taking the average of both the AIC and AUC values. These are the values that I spit out into a csv file so that I can examine which climate variable is best for each BEC zone. The script used to run this analysis can be found here C:\Work\caribou\clus\R\fire_sim\04_ignition_climate_variable_selection.R

After determining the top candidate climate variable by using the climate variable with the lowest average AIC I fit the full model with vegetation data. The variables I consider are vegetation type (as determined by bclcs_level_4), stand height, stand age, and stand volume. The problem is that volume, age and height data are only available for treed areas and probabaly only for public land not private. As a result I decided to split the analysis in each bec zone into an analysis for treed areas and another analysis for non-treed areas.  For the full treed model I include vegetation type, projected height, projected age, stand volume and the best climate variable. This analysis is not complete but I hope that most bec zones are described by a similar vegetation type model. e.g. From a preliminary examination it seems that volume + vegetation type + climate variable might be a good combination of variables for predicting ignition. The categories I include are:
Treed coniferous, treed mixed, treed broadleaf, shrub (both tall and short shrubs are lumped together), open - this includes most other categories including Bryoid-Lichens, Bryoid-moss, bryoids, exposed land, herb, herb-forbs, herb-graminoids, rock/rubbles, and snow/ice. Lastly, I classify areas that were disturbed by a stand replacing event within the last 15 years as disturbed. 

This file can be found here: C:\Work\caribou\clus\R\fire_sim\05_Fire_ignition_model_fits_by_BEC.Rmd

I also want to do another analysis for non-treed areas this model will likely only include climate variable + vegetation type.

## Future climate and vegetation data

For projecting fire ignitions forward I need predicted data collected for the future. For vegetation data I hope to use the CLUS model which pulls volume, height and age data from tipsy curves and I should be able to access this data during a CLUS run. Need to speak to Kyle about this.

For climate data I talked to Colin Mahony. Colin suggested I down scale climate data on the fly. I've not quite done this I did down scale the climate data for one Global Climate change model and generatated rasters for each year and month from 2020 to 2100. I need to include more gcm models though. Detailed methods for what I did and the script to do this can be found in the file: C:\Work\caribou\clus\R\fire_sim\06_future_climate_data_prep.Rmd.

Lastly in script C:\Work\caribou\clus\R\fire_sim\07_compile_future_data.R I try to amalgamate the raster data so that I can easily query it. This is not complete though.










```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
