---
title: "FWI_try"
author: "Elizabeth Kleynhans"
date: "28/06/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FWI

From reading Wang et al ecological Processes (2017) it seems that you can calculate FWI and FBP from just a single value if you set batch =FALSE. So here Im going to try this and see if it works for just one FRT.



```{r cars}
library(cffdrs)
frt2002<-read.csv("C:\\Work\\BioSIM_try\\Output\\Daily_weather_2002.csv")

frt2002<-frt2002 %>% rename(year=Name)
head(frt2002)

frt2002_2<-frt2002 %>% rename(id=KeyID,
                              lat=Latitude,
                              long=Longitude,
                              yr=year,
                              mon=Month,
                              tmax=Maximum.Air.Temperature,
                              temp=Maximum.Air.Temperature,
                              rh=Relative.Humidity,
                              ws=Wind.Speed.at.10.meters,
                              prec=Total.Precipitation)
frt2002_2$tmax<-frt2002_2$temp

fs<-fireSeason(frt2002_2) # this is slow because its calculating the fire season for each of the 10000 locations

frt2002_2new<-cffdrs::fwi(input = frt2002_2,
                batch = TRUE, 
                lat.adjust = TRUE,
                out="all")

#now get means

fwi.means<-frt2002_2new %>%
    group_by(ID, MON, YR, LAT, LONG, ELEVATION) %>%
    dplyr::summarize(Temp = mean(TEMP,na.rm=TRUE),
                     PPT=mean(PREC,na.rm=TRUE),
                     rh=mean(RH,na.rm=TRUE),
                     windspeed=mean(WS,na.rm=TRUE),
                     winddirec=mean(WIND.DIRECTION,na.rm=TRUE),
                     tmax=mean(TMAX,na.rm=TRUE),
                     ffmc=mean(FFMC,na.rm=TRUE),
                     dmc=mean(DMC,na.rm=TRUE),
                     dc=mean(DC,na.rm=TRUE),
                     ISI=mean(ISI,na.rm=TRUE),
                     bui=mean(BUI,na.rm=TRUE),
                     fwi=mean(fwi,na.rm=TRUE),
                     dsr=mean(DSR,na.rm=TRUE))

plot(fwi.means$MON, fwi.means$ffmc)


```

## 

Plot lightning fires and note that FRT = 13 has many lightning fires so Ill focus this try on that FRT area
```{r pressure, echo=FALSE}
# Lightning caused fires by FRT
dat_lightning$ig_mnth<-as.numeric((dat_lightning$ig_mnth))
p<-ggplot(dat_lightning%>% filter(fire_cs=="Lightning"), aes(x=ig_mnth))+
  geom_histogram()+
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9", "10","11", "12"))+
  facet_wrap(frt~., ncol=4)

p

```

I think what I need to do is use the full dataset with lightning, human and randomly selected locations.
Then using this data I want to plot box plots of the FWI for both lightning and non lightning locations to see if there are differences between the means for these plots. 

Another important question is whether the default information is a big problem for this data does it cause a biase. I should email someone about this. 

```{r}

frt13<-dat_lightning %>% filter(frt=="13")
frt13_2<-frt13 %>% dplyr::select(idno, LATITUD, LONGITU, fire_yr, ig_mnth, Tmax04:Tmax10, RH04:RH10,win_spg, win_sum, PPT04:PPT10, MDC_04:MDC_10, fire_cs)

frt13_2_04<-frt13_2 %>% filter(ig_mnth==4) %>%
  dplyr::select(idno, LATITUD, LONGITU,fire_cs, fire_yr, ig_mnth, Tmax04, RH04, MDC_04, win_spg, PPT04) %>%
  rename(temp=Tmax04,
         rh=RH04,
         ws=win_spg,
         prec=PPT04,
         mdc=MDC_04)
frt13_2_05<-frt13_2 %>% filter(ig_mnth==5) %>%
  dplyr::select(idno, LATITUD, LONGITU,fire_cs,fire_yr, ig_mnth, Tmax05, RH05 ,MDC_05, win_spg, PPT05) %>%
  rename(temp=Tmax05,
         rh=RH05,
         ws=win_spg,
         prec=PPT05,
          mdc=MDC_05)
frt13_2_06<-frt13_2 %>% filter(ig_mnth==6) %>%
  dplyr::select(idno, LATITUD, LONGITU,fire_cs,fire_yr, ig_mnth, Tmax06, RH06, MDC_06, win_sum, PPT06) %>%
  rename(temp=Tmax06,
         rh=RH06,
         ws=win_sum,
         prec=PPT06,
          mdc=MDC_06)
frt13_2_07<-frt13_2 %>% filter(ig_mnth==7) %>%
  dplyr::select(idno, LATITUD, LONGITU,fire_cs,fire_yr, ig_mnth, Tmax07, RH07, MDC_07, win_sum, PPT07) %>%
  rename(temp=Tmax07,
         rh=RH07,
         ws=win_sum,
         prec=PPT07,
          mdc=MDC_07)
frt13_2_08<-frt13_2 %>% filter(ig_mnth==8) %>%
  dplyr::select(idno, LATITUD, LONGITU,fire_cs,fire_yr, ig_mnth, Tmax08, RH08, MDC_08, win_sum, PPT08) %>%
  rename(temp=Tmax08,
         rh=RH08,
         ws=win_sum,
         prec=PPT08,
          mdc=MDC_08)
frt13_2_09<-frt13_2 %>% filter(ig_mnth==9) %>%
  dplyr::select(idno, LATITUD, LONGITU,fire_cs,fire_yr, ig_mnth, Tmax09, RH09, MDC_09, win_sum, PPT09) %>%
  rename(temp=Tmax09,
         rh=RH09,
         ws=win_sum,
         prec=PPT09,
          mdc=MDC_09)
frt13_2_10<-frt13_2 %>% filter(ig_mnth==10) %>%
  dplyr::select(idno, LATITUD, LONGITU,fire_cs,fire_yr, ig_mnth, Tmax10, RH10,MDC_10, win_sum, PPT10) %>%
  rename(temp=Tmax10,
         rh=RH10,
         ws=win_sum,
         prec=PPT10,
          mdc=MDC_10)

frt13_new<-rbind(frt13_2_04, frt13_2_05, frt13_2_06, frt13_2_07, frt13_2_08, frt13_2_09, frt13_2_10)
names(frt13_new)

frt13_new <- frt13_new %>% rename(id=idno,
                                  lat=LATITUD,
                                  long=LONGITU,
                                  yr=fire_yr,
                                  mon=ig_mnth)
frt13_new$day<-15

frt13_new <- frt13_new %>% replace (is.na(.), 0)

frt13_new<-cffdrs::fwi(input = frt13_new,
                batch = FALSE, 
                lat.adjust = TRUE,
                out="all")

```

```{r}
p<-ggplot(data=frt13_new, aes(x=MON, y=FFMC, group= YR)) +
  geom_line(aes(colour=YR)) +
  geom_point(aes(colour=YR)) 
p

plot(frt13_new$MDC, frt13_new$DC)
plot(frt13_new$MDC, frt13_new$TEMP)

```


