---
title: "forestryCLUS"
author: ""
date: "08 April 2019"
output:
html_document: 
keep_md: yes
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

# Overview

This module provides the logic for simulating forestry decisions on the landscape. These decisions currently involve spatializing the harvest flow objectives which include: where, when and how much to harvest. These factors help determine policies related to harvest flows, opening size, seral distrubitions, road densitites, preservation areas, silvicultural systems, etc. More sophistication to these decisions would involve looking at the costs and benefits beyond the current time period; this requires optimization or improved heuristics -- which may be considered in the future. The general overview of forestryCLUS follows.

At each time step, harvest units (pixels or blocks) are ranked according to a priority (e.g., oldest first), this constructs a queue. This queue of harvest units are then subject to various constraints meant to meet objectives for the study area. Harvest units are harvested until either a constraint is binding, the queue is exhausted or the harvest flow is met. Next, the age of the forest is advanced to the next time period and the process is repeated. 

During the simulation various reports and information surrounding each pixel can be saved/recorded or used in a summary. Note these outputs are considered expected future outcomes given the inputs developed by the analyst.For a historical selection of harvesting activities see [cutblockSeqPrepCLUS](https://github.com/bcgov/clus/tree/master/R/SpaDES-modules/cutblockSeqPrepCLUS). Both  cutblockSeqPrepCLUS and forestryCLUS build a list of landing locations through simulation time. One is historical while the other is one possible future realization.

# Usage
This module could be a parent module?? It relies on: 
1. dataloadCLUS (set up the clusdb) 
2. blockingCLUS (preforms the pixel aggregation into harvest units)
3. growingStockCLUS (increments the age and volume in pixels)
4. (Optionally) rsfCLUS (track resource selection functions)
5. (Optionally) roadCLUS (preforms the access to the harvest units)
6. uploaderCLUS (uploades the outputs to a shiny app)


# Chilcotin Scenarios
business as usual (BAU); no new constraints, caribou or otherwise; establishes the current 'baseline' or benchmark to evaluate the potential impact of 'new' actions in caribou habitat


# Parameters 
## New Caribou Zone Constraints
BAU = beo, vqo, wha, uwr, fsw, parks and protected areas, community watersheds 




## 'harvestPriority' parameter 


## 'harvestFlow'



## Simulation Model

```{r module_usage}
library (SpaDES.core)
library (data.table)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/scenarios/chilcotin"))
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/forestryCLUS"))
times <- list(start = 0, end = 40) # 5 year interval; 200 years = 40 intervals
parameters <- list(
  .progress = list(type = NA, interval = NA),
  .globals = list(),
  dataLoaderCLUS = list( dbName='castor',
                         saveCastorDB = FALSE,
                         sqlite_dbname = "chilcotin_study_area",
                         useCastorDB = paste0(here::here(), "/R/scenarios/chilcotin/chilcotin_study_area_clusdb.sqlite"),
                         nameBoundaryFile = "chilcotin_area_of_interest_habitat_v3",
                         nameBoundaryColumn = "tsa_name",
                         nameBoundary = c ('Matrix', 'HEWSR', 'LESR', 'LEWR', 'out'),
                         nameBoundaryGeom = 'wkb_geometry',
                         nameCompartmentRaster = "rast.chilcotin_aoi_v3",
                         nameCompartmentTable = "vat.chilcotin_aoi_v3",
                         nameMaskHarvestLandbaseRaster='rast.thlb_2020_chilcotin',  
                         nameZoneRasters=c("rast.zone_cond_beo", 
                                           "rast.zone_cond_vqo", 
                                           "rast.zone_wha_2021", 
                                           "rast.zone_uwr_2021",  
                                           "rast.zone_cond_nharv", 
                                           "rast.zone_cond_fsw", 
                                           "rast.zone_cond_cw"
                                           ),
                           nameZoneTable = "zone.constraints",
                           nameYieldsRaster = "rast.ycid_vdyp",
                           nameYieldTable = "yc_vdyp",
                           nameYieldsTransitionRaster = "rast.tipsy2018_id",
                           nameYieldTransitionTable = "yc_tipsy",
                           nameForestInventoryRaster = "rast.vri2019_id",
                           nameForestInventoryKey = "feature_id",
                           nameForestInventoryTable = "veg_comp_lyr_r1_poly2019",
                           nameForestInventoryAge = "proj_age_1",
                           nameForestInventoryHeight = "proj_height_1",
                           nameForestInventoryCrownClosure = "crown_closure",
                           nameForestInventoryTreed = "bclcs_level_2",
                           nameForestInventorySiteIndex = "site_index"),
  blockingCLUS = list(blockMethod ='pre', 
                      patchZone = 'rast.zone_cond_beo',
                      patchVariation = 6,
                      nameCutblockRaster ="rast.cns_cut_bl",
                      useLandingsArea = FALSE, 
                      useSpreadProbRas = FALSE),
  forestryCLUS = list(harvestBlockPriority = " dist, salvage_vol DESC, age DESC ", 
                      # scenarios =  "dist, age DESC"  "dist, salvage_vol DESC, age DESC"
                      # query to prioritize blocks within 1km of disturbance, then 2.5km, then 5km, then everything >5km, then oldest first after that =  "CASE WHEN dist < 1000 THEN 3 WHEN dist < 2500 THEN 2 WHEN dist < 5000 THEN 1 ELSE 0 END DESC, age DESC"
                      #harvestZonePriority = "age DESC",
                      #harvestZonePriorityInterval = 1,
                      reportHarvestConstraints = T,
                      adjacencyConstraint = 0,
                      salvageRaster = 'rast.dead_vol_125_2020'),
  growingStockCLUS = list (periodLength = 5),
  roadCLUS = list(roadMethod = 'mst', #pre 
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.rds_cariboo_2022'),
  # rsfCLUS = list (calculateInterval = 10, # at what time interval to calculate RSF
  #                 criticalHabitatTable = "public.vat_bc_crithab_and_herd",
  #                 randomEffectsTable = "public.rsf_re_coeff",
  #                 writeRSFRasters = TRUE,
  #                 checkRasters = FALSE),
  survivalCLUS = list (caribou_herd_density = 0.05, # assign what is appropriate for the herd
                       nameRasCaribouHerd = "rast.caribou_herd", # raster of herd boundaries
                       tableCaribouHerd = "vat.caribou_herd_vat"), # look-up table of herd names
  disturbanceCASTOR = list(calculateInterval =  1, # should be 1 if using constraints on 'dist' (disturbance)
                             criticalHabitatTable = "vat.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.perm_dist_no_rds",
                             recovery = 300), # roads recover after 30 years of no use; 300 for BAU (no recovery)
  volumebyareaReportCLUS = list (calculateInterval = 1,
                                 AreaofInterestRaster = "rast.chilcotin_aoi_supply_blocks",
                                 AreaofInterestTable = "vat.chilcotin_supply_blocks_vat"),
  smcaribouAbundanceCLUS = list (nameRasSMCHerd = "rast.smc_herd_habitat", 
                                  tableSMCCoeffs = "vat.smc_coeffs"),
  survivalgrizzlyCASTOR = list (rasterGBPU = "rast.gbpu_2021", 
                              tableGBPU= "vat.gbpu", 
                              roadDensity = 10),
  uploaderCLUS = list(aoiName = 'chilcotin_caribou_plan', # name of the schema that gets uploaded to postgres
                      dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbuser", keyring="postgreSQL"), 
                                     keyring::key_get("vmdbpass", keyring="postgreSQL"),  
                                     keyring::key_get("vmdbname", keyring="postgreSQL"))
                  )
  #yieldUncertaintyCLUS = list(elevationRaster = 'rast.dem')
)

modules <- list("dataLoaderCLUS", 
                "growingStockCLUS", 
                "blockingCLUS", 
                "forestryCLUS", 
                "roadCLUS",
                "survivalgrizzlyCASTOR",
                #"yieldUncertaintyCLUS", 
                "survivalCLUS", 
                "disturbanceCASTOR", 
                "volumebyareaReportCLUS",
                # "rsfCLUS", # error line 453 - need to debug
                "smcaribouAbundanceCLUS",
                "uploaderCLUS"
                )

scenario = data.table (name = "chilcotin_bau_live_dead",
                       description = "Business as usual (BAU). Adjacency = 0m. Priority queue = Closest to disturbance first, dead volume second, oldest third (live or dead volume). Salvage dead volume in first 10 years. Minimum volume: 150 m3/year. No road recovery. Even live harvest flow: HEWSR = 9,000 m3/year; LESR = 47,250 m3/year; LEWR = 230,000m3/year; Matrix = 310,000m3/year; out = 1,200,000m3/year. Dead volume targets (in first 10 years only): HEWSR = 500 m3/year; LESR = 2,250 m3/year; LEWR = 20,000m3/year; Matrix = 50,000 m3/year; out = 105,000 m3/year.")


harvestFlow <- rbindlist(list(
                              data.table (compartment ="HEWSR",
                                          partition = ' vol > 150  ', 
                                          period = rep( seq (from = 1,
                                                           to = 2,
                                                           by = 1),
                                                     1),
                                          flow = 42500, # 8,500/yr, can't be zero
                                          partition_type = 'live'),
                              data.table (compartment ="HEWSR",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 3, #3 
                                                           to = 40, 
                                                           by = 1),
                                                     1), 
                                          flow = 45000, #9,000/yr
                                          partition_type = 'live'),
                              data.table (compartment ="HEWSR",
                                           partition = ' (salvage_vol > 150 and salvage_vol/(vol + salvage_vol) >= 0.5) ',
                                           period = rep( seq (from = 1,
                                                              to = 2,
                                                              by = 1),1),
                                           flow = 2500, # 500/yr
                                           partition_type = 'dead'),
                              data.table (compartment ="LESR",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 1,
                                                           to = 2,
                                                           by = 1),
                                                     1),
                                          flow = 225000, #45,000/yr
                                          partition_type = 'live'),
                                  data.table (compartment ="LESR",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 3, #3 
                                                           to = 40, 
                                                           by = 1),
                                                     1),
                                          flow = 236250, #47,250/yr
                                          partition_type = 'live'), 
                              data.table (compartment ="LESR",
                                          partition = ' (salvage_vol > 150 and salvage_vol/(vol + salvage_vol) >= 0.5) ',
                                          period = rep( seq (from = 1,
                                                             to = 2,
                                                             by = 1),1),
                                          flow = 11250, #2,250/yr
                                          partition_type = 'dead'),
                              data.table (compartment ="LEWR",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 1,
                                                           to = 2,
                                                           by = 1),
                                                     1),
                                          flow = 1050000, #210,000/yr
                                          partition_type = 'live'),
                               data.table (compartment ="LEWR",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 3, #3 
                                                           to = 40, 
                                                           by = 1),
                                                     1), 
                                          flow = 1150000, #230,000/yr
                                          partition_type = 'live'), 
                              data.table (compartment ="LEWR",
                                          partition = ' (salvage_vol > 150 and salvage_vol/(vol + salvage_vol) >= 0.5) ',
                                          period = rep( seq (from = 1,
                                                             to = 2,
                                                             by = 1),1),
                                          flow =  100000, #20,000/yr
                                          partition_type = 'dead'),
                              data.table (compartment ="Matrix",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 1,
                                                           to = 2,
                                                           by = 1),
                                                     1),
                                          flow = 1300000, #260,000/yr
                                          partition_type = 'live'),
                              data.table (compartment ="Matrix",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 3, #3 
                                                           to = 40, 
                                                           by = 1),
                                                     1), 
                                          flow = 1550000, #310,000/yr
                                          partition_type = 'live'),
                              data.table (compartment ="Matrix",
                                          partition = ' (salvage_vol > 150 and salvage_vol/(vol + salvage_vol) >= 0.5) ',
                                          period = rep( seq (from = 1,
                                                             to = 2,
                                                             by = 1), 1),
                                          flow = 250000, #50,000/yr
                                          partition_type = 'dead'),
                              data.table (compartment ="out",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 1,
                                                           to = 2,
                                                           by = 1),
                                                     1),
                                          flow =  5475000, #1,095,000/yr
                                          partition_type = 'live'),
                              data.table (compartment ="out",
                                          partition = ' vol > 150 ', 
                                          period = rep( seq (from = 3, #3 
                                                           to = 40, 
                                                           by = 1),
                                                     1), 
                                          flow = 6000000, #1,200,000/yr
                                          partition_type = 'live'), #,
                              data.table (compartment ="out",
                                          partition = ' (salvage_vol > 150 and salvage_vol/(vol + salvage_vol) >= 0.5) ',
                                          period = rep( seq (from = 1,
                                                             to = 2,
                                                             by = 1),1),
                                          flow = 525000, #105,000/yr
                                          partition_type = 'dead')
))


patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))


objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvivalReport",
                                             "disturbanceReport",
                                             "volumebyareaReport",
                                             "tableGrizzSurvivalReport",
                                             "tableAbundanceReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


# Events

## Flow Chart

```{r, flow_chart}
library(SpaDES.core)
eventDiagram(mysimout)
```

## Algorithm

The general algorithm (pseudo-code) follows as:

`compartment_list`= SELECT zones FROM compartments WHERE target > 0 ORDER BY priority_compartment

FOR compartment_selected in `compartment_list`
`queue`<- SELECT pixelid, blockid FROM pixels WHERE 
            compartment = compartment_selected AND thlb > 0 AND constraint = 0                 ORDER BY priority
               
IF (`queue` > 0 )
  check constraints
ELSE 
  NEXT
        

# Data dependencies

## Input data

A SQLite db is required (output from dataloaderCLUS). A harvestFlow data.table object that includes the forest management unit (i.e., compartment, aka - 'supply block'), the partition from which the harvest flow applies (e.x., All dead pine); the year at which the flow applies and the amount of volume.

## Output data

A list of landings || blocks from when they are harvested.

# Links to other modules

dataloaderCLUS is required.

