---
title: "Multiple_year_fire_spread_sim"
author: "Elizabeth Kleynhans"
date: "2023-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(mapview)
library(tmap)
library(raster)
library(SpaDES.tools)
library(quickPlot)
library(bcdata)

library(SpaDES)
library(SpaDES.core)
library(SpaDES.addins)
library(terra)
```

# Look into this: Why do I have so many locations with missing climate data? Figure out what is going on and why Im missing this information. Ok I think for some reason data for frt3 never got extracted. Ill leave this for now and myabe come back to it. Usually I lump frt3 with frt5 becauase frt3 has such a small area in the province.

## import tables with the constant and variable coefficient values
```{r}
const_coef<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_final_constant_coefficients_2021.gpkg")

var_coef_2021<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_varying_coefficient_2021.gpkg")

var_coef_2024<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_varying_coefficient_2024.gpkg")

var_coef_2029<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_varying_coefficient_2029.gpkg")

var_coef_2034<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_varying_coefficient_2034.gpkg")

var_coef_2039<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_varying_coefficient_2039.gpkg")

var_coef_2044<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_varying_coefficient_2044.gpkg")

var_coef_2049<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\estimated_coefficients\\BC_ignit_escape_spread_varying_coefficient_2049.gpkg")
```

I forgot to attach the bclcs_level_5 info to the coefficients. So Ill join it to the constant coef table here instead
```{r}
dat<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\BC_all_dat_400m_final.gpkg")

dat2<-dat %>% dplyr::select(idno, frt, bclcs_level_5)

dat2<-st_drop_geometry(dat2)
```


# not for each year calculate the probability of ignition, escape and spread by combining the coefficients.

## 2021
```{r}
const_coef<-st_drop_geometry(const_coef)
const_coef$frt<-as.numeric(as.character(const_coef$frt))
const_coef<-left_join(const_coef, dat2)

coef_2021<-left_join(var_coef_2021,const_coef)

names(coef_2021)

coef_2021$logit_P_lightning<-coef_2021$logit_P_lightning_coef_const + coef_2021$varying_coef_lightning
coef_2021$logit_P_person<-coef_2021$logit_P_person_coef_const + coef_2021$varying_coef_person
coef_2021$logit_P_escape<-coef_2021$logit_P_escape_coef_const + coef_2021$varying_coef_escape
coef_2021$logit_P_spread<-coef_2021$logit_P_spread_coef_const + coef_2021$varying_coef_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
coef_2021$prob_ignition_lightning<-exp(coef_2021$logit_P_lightning)/(1+exp(coef_2021$logit_P_lightning))
coef_2021$prob_ignition_person<-exp(coef_2021$logit_P_person)/(1+exp(coef_2021$logit_P_person))
coef_2021$prob_escape<-exp(coef_2021$logit_P_escape)/(1+exp(coef_2021$logit_P_escape))
coef_2021$prob_spread<-exp(coef_2021$logit_P_spread)/(1+exp(coef_2021$logit_P_spread))

head(coef_2021)
## make sure that water, glaciers and some frt with veg =N should have a probability of zero. Ill change these here

coef_2021<-coef_2021 %>% 
  mutate(prob_ignition_lightning=ifelse(FWI_veg == "W", 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(FWI_veg == "W", 0, prob_ignition_person),
         prob_escape=ifelse(FWI_veg == "W", 0, prob_escape),
         prob_spread=ifelse(FWI_veg == "W", 0, prob_spread))

coef_2021<-coef_2021 %>% 
  mutate(prob_ignition_lightning=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_person),
         prob_escape=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_escape),
         prob_spread=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_spread))

coef_2021$prob_ignition_lightning[coef_2021$frt==5 & coef_2021$FWI_veg=="N"]<-0
coef_2021$prob_escape[coef_2021$frt==5 & coef_2021$FWI_veg=="N"]<-0
coef_2021$prob_ignition_lightning[coef_2021$frt==7 & coef_2021$FWI_veg=="N"]<-0

hist(coef_2021$prob_escape)
hist(coef_2021$prob_ignition_lightning)
hist(coef_2021$prob_ignition_person)
hist(coef_2021$prob_spread)
```

## 2024
```{r}
coef_2024<-left_join(var_coef_2024,const_coef)

names(coef_2024)

coef_2024$logit_P_lightning<-coef_2024$logit_P_lightning_coef_const + coef_2024$varying_coef_lightning
coef_2024$logit_P_person<-coef_2024$logit_P_person_coef_const + coef_2024$varying_coef_person
coef_2024$logit_P_escape<-coef_2024$logit_P_escape_coef_const + coef_2024$varying_coef_escape
coef_2024$logit_P_spread<-coef_2024$logit_P_spread_coef_const + coef_2024$varying_coef_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
coef_2024$prob_ignition_lightning<-exp(coef_2024$logit_P_lightning)/(1+exp(coef_2024$logit_P_lightning))
coef_2024$prob_ignition_person<-exp(coef_2024$logit_P_person)/(1+exp(coef_2024$logit_P_person))
coef_2024$prob_escape<-exp(coef_2024$logit_P_escape)/(1+exp(coef_2024$logit_P_escape))
coef_2024$prob_spread<-exp(coef_2024$logit_P_spread)/(1+exp(coef_2024$logit_P_spread))

head(coef_2024)
## make sure that water, glaciers and some frt with veg =N should have a probability of zero. Ill change these here

coef_2024<-coef_2024 %>% 
  mutate(prob_ignition_lightning=ifelse(FWI_veg == "W", 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(FWI_veg == "W", 0, prob_ignition_person),
         prob_escape=ifelse(FWI_veg == "W", 0, prob_escape),
         prob_spread=ifelse(FWI_veg == "W", 0, prob_spread))

coef_2024<-coef_2024 %>% 
  mutate(prob_ignition_lightning=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_person),
         prob_escape=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_escape),
         prob_spread=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_spread))

coef_2024$prob_ignition_lightning[coef_2024$frt==5 & coef_2024$FWI_veg=="N"]<-0
coef_2024$prob_escape[coef_2024$frt==5 & coef_2024$FWI_veg=="N"]<-0
coef_2024$prob_ignition_lightning[coef_2024$frt==7 & coef_2024$FWI_veg=="N"]<-0

hist(coef_2024$prob_escape)
hist(coef_2024$prob_ignition_lightning)
hist(coef_2024$prob_ignition_person)
hist(coef_2024$prob_spread)
```

# 2029
```{r}
coef_2029<-left_join(var_coef_2029,const_coef)

names(coef_2029)

coef_2029$logit_P_lightning<-coef_2029$logit_P_lightning_coef_const + coef_2029$varying_coef_lightning
coef_2029$logit_P_person<-coef_2029$logit_P_person_coef_const + coef_2029$varying_coef_person
coef_2029$logit_P_escape<-coef_2029$logit_P_escape_coef_const + coef_2029$varying_coef_escape
coef_2029$logit_P_spread<-coef_2029$logit_P_spread_coef_const + coef_2029$varying_coef_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
coef_2029$prob_ignition_lightning<-exp(coef_2029$logit_P_lightning)/(1+exp(coef_2029$logit_P_lightning))
coef_2029$prob_ignition_person<-exp(coef_2029$logit_P_person)/(1+exp(coef_2029$logit_P_person))
coef_2029$prob_escape<-exp(coef_2029$logit_P_escape)/(1+exp(coef_2029$logit_P_escape))
coef_2029$prob_spread<-exp(coef_2029$logit_P_spread)/(1+exp(coef_2029$logit_P_spread))

head(coef_2029)
## make sure that water, glaciers and some frt with veg =N should have a probability of zero. Ill change these here

coef_2029<-coef_2029 %>% 
  mutate(prob_ignition_lightning=ifelse(FWI_veg == "W", 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(FWI_veg == "W", 0, prob_ignition_person),
         prob_escape=ifelse(FWI_veg == "W", 0, prob_escape),
         prob_spread=ifelse(FWI_veg == "W", 0, prob_spread))

coef_2029<-coef_2029 %>% 
  mutate(prob_ignition_lightning=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_person),
         prob_escape=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_escape),
         prob_spread=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_spread))

coef_2029$prob_ignition_lightning[coef_2029$frt==5 & coef_2029$FWI_veg=="N"]<-0
coef_2029$prob_escape[coef_2029$frt==5 & coef_2029$FWI_veg=="N"]<-0
coef_2029$prob_ignition_lightning[coef_2029$frt==7 & coef_2029$FWI_veg=="N"]<-0

hist(coef_2029$prob_escape)
hist(coef_2029$prob_ignition_lightning)
hist(coef_2029$prob_ignition_person)
hist(coef_2029$prob_spread)
```

## 2034
```{r}
coef_2034<-left_join(var_coef_2034,const_coef)

names(coef_2034)

coef_2034$logit_P_lightning<-coef_2034$logit_P_lightning_coef_const + coef_2034$varying_coef_lightning
coef_2034$logit_P_person<-coef_2034$logit_P_person_coef_const + coef_2034$varying_coef_person
coef_2034$logit_P_escape<-coef_2034$logit_P_escape_coef_const + coef_2034$varying_coef_escape
coef_2034$logit_P_spread<-coef_2034$logit_P_spread_coef_const + coef_2034$varying_coef_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
coef_2034$prob_ignition_lightning<-exp(coef_2034$logit_P_lightning)/(1+exp(coef_2034$logit_P_lightning))
coef_2034$prob_ignition_person<-exp(coef_2034$logit_P_person)/(1+exp(coef_2034$logit_P_person))
coef_2034$prob_escape<-exp(coef_2034$logit_P_escape)/(1+exp(coef_2034$logit_P_escape))
coef_2034$prob_spread<-exp(coef_2034$logit_P_spread)/(1+exp(coef_2034$logit_P_spread))

head(coef_2034)
## make sure that water, glaciers and some frt with veg =N should have a probability of zero. Ill change these here

coef_2034<-coef_2034 %>% 
  mutate(prob_ignition_lightning=ifelse(FWI_veg == "W", 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(FWI_veg == "W", 0, prob_ignition_person),
         prob_escape=ifelse(FWI_veg == "W", 0, prob_escape),
         prob_spread=ifelse(FWI_veg == "W", 0, prob_spread))

coef_2034<-coef_2034 %>% 
  mutate(prob_ignition_lightning=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_person),
         prob_escape=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_escape),
         prob_spread=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_spread))

coef_2034$prob_ignition_lightning[coef_2034$frt==5 & coef_2034$FWI_veg=="N"]<-0
coef_2034$prob_escape[coef_2034$frt==5 & coef_2034$FWI_veg=="N"]<-0
coef_2034$prob_ignition_lightning[coef_2034$frt==7 & coef_2034$FWI_veg=="N"]<-0

hist(coef_2034$prob_escape)
hist(coef_2034$prob_ignition_lightning)
hist(coef_2034$prob_ignition_person)
hist(coef_2034$prob_spread)
```


##2039
```{r}
coef_2039<-left_join(var_coef_2039,const_coef)

names(coef_2039)

coef_2039$logit_P_lightning<-coef_2039$logit_P_lightning_coef_const + coef_2039$varying_coef_lightning
coef_2039$logit_P_person<-coef_2039$logit_P_person_coef_const + coef_2039$varying_coef_person
coef_2039$logit_P_escape<-coef_2039$logit_P_escape_coef_const + coef_2039$varying_coef_escape
coef_2039$logit_P_spread<-coef_2039$logit_P_spread_coef_const + coef_2039$varying_coef_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
coef_2039$prob_ignition_lightning<-exp(coef_2039$logit_P_lightning)/(1+exp(coef_2039$logit_P_lightning))
coef_2039$prob_ignition_person<-exp(coef_2039$logit_P_person)/(1+exp(coef_2039$logit_P_person))
coef_2039$prob_escape<-exp(coef_2039$logit_P_escape)/(1+exp(coef_2039$logit_P_escape))
coef_2039$prob_spread<-exp(coef_2039$logit_P_spread)/(1+exp(coef_2039$logit_P_spread))

head(coef_2039)
## make sure that water, glaciers and some frt with veg =N should have a probability of zero. Ill change these here

coef_2039<-coef_2039 %>% 
  mutate(prob_ignition_lightning=ifelse(FWI_veg == "W", 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(FWI_veg == "W", 0, prob_ignition_person),
         prob_escape=ifelse(FWI_veg == "W", 0, prob_escape),
         prob_spread=ifelse(FWI_veg == "W", 0, prob_spread))

coef_2039<-coef_2039 %>% 
  mutate(prob_ignition_lightning=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_person),
         prob_escape=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_escape),
         prob_spread=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_spread))

coef_2039$prob_ignition_lightning[coef_2039$frt==5 & coef_2039$FWI_veg=="N"]<-0
coef_2039$prob_escape[coef_2039$frt==5 & coef_2039$FWI_veg=="N"]<-0
coef_2039$prob_ignition_lightning[coef_2039$frt==7 & coef_2039$FWI_veg=="N"]<-0

hist(coef_2039$prob_escape)
hist(coef_2039$prob_ignition_lightning)
hist(coef_2039$prob_ignition_person)
hist(coef_2039$prob_spread)
```

##2044
```{r}
coef_2044<-left_join(var_coef_2044,const_coef)

names(coef_2044)

coef_2044$logit_P_lightning<-coef_2044$logit_P_lightning_coef_const + coef_2044$varying_coef_lightning
coef_2044$logit_P_person<-coef_2044$logit_P_person_coef_const + coef_2044$varying_coef_person
coef_2044$logit_P_escape<-coef_2044$logit_P_escape_coef_const + coef_2044$varying_coef_escape
coef_2044$logit_P_spread<-coef_2044$logit_P_spread_coef_const + coef_2044$varying_coef_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
coef_2044$prob_ignition_lightning<-exp(coef_2044$logit_P_lightning)/(1+exp(coef_2044$logit_P_lightning))
coef_2044$prob_ignition_person<-exp(coef_2044$logit_P_person)/(1+exp(coef_2044$logit_P_person))
coef_2044$prob_escape<-exp(coef_2044$logit_P_escape)/(1+exp(coef_2044$logit_P_escape))
coef_2044$prob_spread<-exp(coef_2044$logit_P_spread)/(1+exp(coef_2044$logit_P_spread))

head(coef_2044)
## make sure that water, glaciers and some frt with veg =N should have a probability of zero. Ill change these here

coef_2044<-coef_2044 %>% 
  mutate(prob_ignition_lightning=ifelse(FWI_veg == "W", 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(FWI_veg == "W", 0, prob_ignition_person),
         prob_escape=ifelse(FWI_veg == "W", 0, prob_escape),
         prob_spread=ifelse(FWI_veg == "W", 0, prob_spread))

coef_2044<-coef_2044 %>% 
  mutate(prob_ignition_lightning=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_person),
         prob_escape=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_escape),
         prob_spread=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_spread))

coef_2044$prob_ignition_lightning[coef_2044$frt==5 & coef_2044$FWI_veg=="N"]<-0
coef_2044$prob_escape[coef_2044$frt==5 & coef_2044$FWI_veg=="N"]<-0
coef_2044$prob_ignition_lightning[coef_2044$frt==7 & coef_2044$FWI_veg=="N"]<-0

hist(coef_2044$prob_escape)
hist(coef_2044$prob_ignition_lightning)
hist(coef_2044$prob_ignition_person)
hist(coef_2044$prob_spread)
```

## 2049
```{r}
coef_2049<-left_join(var_coef_2049,const_coef)

names(coef_2049)

coef_2049$logit_P_lightning<-coef_2049$logit_P_lightning_coef_const + coef_2049$varying_coef_lightning
coef_2049$logit_P_person<-coef_2049$logit_P_person_coef_const + coef_2049$varying_coef_person
coef_2049$logit_P_escape<-coef_2049$logit_P_escape_coef_const + coef_2049$varying_coef_escape
coef_2049$logit_P_spread<-coef_2049$logit_P_spread_coef_const + coef_2049$varying_coef_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
coef_2049$prob_ignition_lightning<-exp(coef_2049$logit_P_lightning)/(1+exp(coef_2049$logit_P_lightning))
coef_2049$prob_ignition_person<-exp(coef_2049$logit_P_person)/(1+exp(coef_2049$logit_P_person))
coef_2049$prob_escape<-exp(coef_2049$logit_P_escape)/(1+exp(coef_2049$logit_P_escape))
coef_2049$prob_spread<-exp(coef_2049$logit_P_spread)/(1+exp(coef_2049$logit_P_spread))

head(coef_2049)
## make sure that water, glaciers and some frt with veg =N should have a probability of zero. Ill change these here

coef_2049<-coef_2049 %>% 
  mutate(prob_ignition_lightning=ifelse(FWI_veg == "W", 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(FWI_veg == "W", 0, prob_ignition_person),
         prob_escape=ifelse(FWI_veg == "W", 0, prob_escape),
         prob_spread=ifelse(FWI_veg == "W", 0, prob_spread))

coef_2049<-coef_2049 %>% 
  mutate(prob_ignition_lightning=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_lightning),
         prob_ignition_person=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_ignition_person),
         prob_escape=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_escape),
         prob_spread=ifelse(bclcs_level_5 %in% c("GL", "LA", "OC", "PN", "TA", "GP", "TZ", "RE"), 0, prob_spread))

coef_2049$prob_ignition_lightning[coef_2049$frt==5 & coef_2049$FWI_veg=="N"]<-0
coef_2049$prob_escape[coef_2049$frt==5 & coef_2049$FWI_veg=="N"]<-0
coef_2049$prob_ignition_lightning[coef_2049$frt==7 & coef_2049$FWI_veg=="N"]<-0

hist(coef_2049$prob_escape)
hist(coef_2049$prob_ignition_lightning)
hist(coef_2049$prob_ignition_person)
hist(coef_2049$prob_spread)
```


```{r}
coef_2021<- coef_2021 %>% 
  dplyr::select(idno, frt, prob_ignition_lightning:prob_spread) %>% 
  rename(prob_ignition_lightning_2021=prob_ignition_lightning,
         prob_ignition_person_2021=prob_ignition_person,
         prob_escape_2021=prob_escape,
         prob_spread_2021=prob_spread)
coef_2024<- coef_2024 %>% 
  dplyr::select(idno, frt, prob_ignition_lightning:prob_spread)%>% 
  rename(prob_ignition_lightning_2024=prob_ignition_lightning,
         prob_ignition_person_2024=prob_ignition_person,
         prob_escape_2024=prob_escape,
         prob_spread_2024=prob_spread)
coef_2029<- coef_2029 %>% 
  dplyr::select(idno, frt, prob_ignition_lightning:prob_spread) %>% 
  rename(prob_ignition_lightning_2029=prob_ignition_lightning,
         prob_ignition_person_2029=prob_ignition_person,
         prob_escape_2029=prob_escape,
         prob_spread_2029=prob_spread)
coef_2034<- coef_2034 %>% 
  dplyr::select(idno, frt, prob_ignition_lightning:prob_spread)%>% 
  rename(prob_ignition_lightning_2034=prob_ignition_lightning,
         prob_ignition_person_2034=prob_ignition_person,
         prob_escape_2034=prob_escape,
         prob_spread_2034=prob_spread)
coef_2039<- coef_2039 %>%
  dplyr::select(idno, frt, prob_ignition_lightning:prob_spread)%>% 
  rename(prob_ignition_lightning_2039=prob_ignition_lightning,
         prob_ignition_person_2039=prob_ignition_person,
         prob_escape_2039=prob_escape,
         prob_spread_2039=prob_spread)
coef_2044<- coef_2044 %>%
  dplyr::select(idno, frt, prob_ignition_lightning:prob_spread)%>% 
  rename(prob_ignition_lightning_2044=prob_ignition_lightning,
         prob_ignition_person_2044=prob_ignition_person,
         prob_escape_2044=prob_escape,
         prob_spread_2044=prob_spread)
coef_2049<- coef_2049 %>%
  dplyr::select(idno, frt, prob_ignition_lightning:prob_spread)%>% 
  rename(prob_ignition_lightning_2049=prob_ignition_lightning,
         prob_ignition_person_2049=prob_ignition_person,
         prob_escape_2049=prob_escape,
         prob_spread_2049=prob_spread)

```

```{r}
coef_2024<-st_drop_geometry(coef_2024)
coef_2029<-st_drop_geometry(coef_2029)
coef_2034<-st_drop_geometry(coef_2034)
coef_2039<-st_drop_geometry(coef_2039)
coef_2044<-st_drop_geometry(coef_2044)
coef_2049<-st_drop_geometry(coef_2049)

coef_all<-left_join(coef_2021, coef_2024)
coef_all<-left_join(coef_all, coef_2029)
coef_all<-left_join(coef_all, coef_2034)
coef_all<-left_join(coef_all, coef_2039)
coef_all<-left_join(coef_all, coef_2044)
coef_all<-left_join(coef_all, coef_2049)

head(coef_all)

```

```{r}
st_write(coef_all, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\Prob_ignit_escape_spread_2021-2049.gpkg", delete_layer=TRUE, driver="GPKG")
```


## create total ignition probabilities of fire by weighting lightning caused or human caused fires by their proportions

```{r}
prob_fire<-st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\Prob_ignit_escape_spread_2021-2049.gpkg")

# extract BC data
ignit<-try(
   bcdc_query_geodata("WHSE_LAND_AND_NATURAL_RESOURCE.PROT_HISTORICAL_INCIDENTS_SP") %>%
     filter(FIRE_YEAR > 1990) %>%
     filter(FIRE_TYPE == "Fire") %>%
     collect()
 )
ignit<-st_transform(ignit, 3005) #transform coordinate system to 3005 - that for BC, Canada

frt <- st_read ( dsn = "D:\\Fire\\fire_data\\Fire_Regime_Types\\FRT\\FRT_Canada.shp", stringsAsFactors = T) # Read simple features from file or database, or retrieve layer names and their geometry type(s)
st_crs(frt) #Retrieve coordinate reference system from sf or sfc object
frt<-st_transform(frt, 3005) #transform coordinate system to 3005 - that for BC, Canada
ignit_sf<-st_as_sf(ignit)
frt_sf<-st_as_sf(frt)

fire.ignt.frt <- st_join(ignit_sf, frt_sf)
```


```{r}
head(fire.ignt.frt)

x<-table(fire.ignt.frt$Cluster, fire.ignt.frt$FIRE_CAUSE)


frt5<-1503/(1503+272) # 84% lightning
frt7<- 250/(250+1294) # 16% lightning
frt9<- 143/(143+61) #70% lightning
frt10<- 1036/(1036+167) # 86% lightning
frt11<-184/(284+150) # 42% lightning
frt12<-3786/(3786+4123) # 48% lightning
frt13<-17426/(17426+3448) #83% lightning
frt14<-6200/(6200+8957) # 41% lightning
frt15<-1374/(1374+3474) # 28% lightning
```

```{r}
prob_fire<-prob_fire %>%
    mutate(tot_ignit_2021 = case_when(
                            frt == "5" ~ (prob_ignition_lightning_2021*0.84) + (prob_ignition_person_2021*0.16),
                            frt == "7" ~ (prob_ignition_lightning_2021*0.16) + (prob_ignition_person_2021*0.84),
                            frt == "9" ~ 
  (prob_ignition_lightning_2021*0.7) + (prob_ignition_person_2021*0.3),
                            frt == "10" ~ (prob_ignition_lightning_2021*0.86) + (prob_ignition_person_2021*0.14),
                            frt == "11" ~ (prob_ignition_lightning_2021*0.42) + (prob_ignition_person_2021*0.58),
                            frt == "12" ~ (prob_ignition_lightning_2021*0.48) + (prob_ignition_person_2021*0.52),
                            frt == "13" ~ (prob_ignition_lightning_2021*0.83) + (prob_ignition_person_2021*0.17),
                            frt == "14" ~ (prob_ignition_lightning_2021*0.41) + (prob_ignition_person_2021*0.59),
                            frt == "15" ~ (prob_ignition_lightning_2021*0.28) + (prob_ignition_person_2021*0.72) ,
                            TRUE ~ NA_real_))

prob_fire<-prob_fire %>%
    mutate(tot_ignit_2024 = case_when(
                            frt == "5" ~ (prob_ignition_lightning_2024*0.84) + (prob_ignition_person_2024*0.16),
                            frt == "7" ~ (prob_ignition_lightning_2024*0.16) + (prob_ignition_person_2024*0.84),
                            frt == "9" ~ 
  (prob_ignition_lightning_2024*0.7) + (prob_ignition_person_2024*0.3),
                            frt == "10" ~ (prob_ignition_lightning_2024*0.86) + (prob_ignition_person_2024*0.14),
                            frt == "11" ~ (prob_ignition_lightning_2024*0.42) + (prob_ignition_person_2024*0.58),
                            frt == "12" ~ (prob_ignition_lightning_2024*0.48) + (prob_ignition_person_2024*0.52),
                            frt == "13" ~ (prob_ignition_lightning_2024*0.83) + (prob_ignition_person_2024*0.17),
                            frt == "14" ~ (prob_ignition_lightning_2024*0.41) + (prob_ignition_person_2024*0.59),
                            frt == "15" ~ (prob_ignition_lightning_2024*0.28) + (prob_ignition_person_2024*0.72) ,
                            TRUE ~ NA_real_))

prob_fire<-prob_fire %>%
    mutate(tot_ignit_2029 = case_when(
                            frt == "5" ~ (prob_ignition_lightning_2029*0.84) + (prob_ignition_person_2029*0.16),
                            frt == "7" ~ (prob_ignition_lightning_2029*0.16) + (prob_ignition_person_2029*0.84),
                            frt == "9" ~ 
  (prob_ignition_lightning_2029*0.7) + (prob_ignition_person_2029*0.3),
                            frt == "10" ~ (prob_ignition_lightning_2029*0.86) + (prob_ignition_person_2029*0.14),
                            frt == "11" ~ (prob_ignition_lightning_2029*0.42) + (prob_ignition_person_2029*0.58),
                            frt == "12" ~ (prob_ignition_lightning_2029*0.48) + (prob_ignition_person_2029*0.52),
                            frt == "13" ~ (prob_ignition_lightning_2029*0.83) + (prob_ignition_person_2029*0.17),
                            frt == "14" ~ (prob_ignition_lightning_2029*0.41) + (prob_ignition_person_2029*0.59),
                            frt == "15" ~ (prob_ignition_lightning_2029*0.28) + (prob_ignition_person_2029*0.72) ,
                            TRUE ~ NA_real_))

prob_fire<-prob_fire %>%
    mutate(tot_ignit_2034 = case_when(
                            frt == "5" ~ (prob_ignition_lightning_2034*0.84) + (prob_ignition_person_2034*0.16),
                            frt == "7" ~ (prob_ignition_lightning_2034*0.16) + (prob_ignition_person_2034*0.84),
                            frt == "9" ~ 
  (prob_ignition_lightning_2034*0.7) + (prob_ignition_person_2034*0.3),
                            frt == "10" ~ (prob_ignition_lightning_2034*0.86) + (prob_ignition_person_2034*0.14),
                            frt == "11" ~ (prob_ignition_lightning_2034*0.42) + (prob_ignition_person_2034*0.58),
                            frt == "12" ~ (prob_ignition_lightning_2034*0.48) + (prob_ignition_person_2034*0.52),
                            frt == "13" ~ (prob_ignition_lightning_2034*0.83) + (prob_ignition_person_2034*0.17),
                            frt == "14" ~ (prob_ignition_lightning_2034*0.41) + (prob_ignition_person_2034*0.59),
                            frt == "15" ~ (prob_ignition_lightning_2034*0.28) + (prob_ignition_person_2034*0.72) ,
                            TRUE ~ NA_real_))

prob_fire<-prob_fire %>%
    mutate(tot_ignit_2039 = case_when(
                            frt == "5" ~ (prob_ignition_lightning_2039*0.84) + (prob_ignition_person_2039*0.16),
                            frt == "7" ~ (prob_ignition_lightning_2039*0.16) + (prob_ignition_person_2039*0.84),
                            frt == "9" ~ 
  (prob_ignition_lightning_2039*0.7) + (prob_ignition_person_2039*0.3),
                            frt == "10" ~ (prob_ignition_lightning_2039*0.86) + (prob_ignition_person_2039*0.14),
                            frt == "11" ~ (prob_ignition_lightning_2039*0.42) + (prob_ignition_person_2039*0.58),
                            frt == "12" ~ (prob_ignition_lightning_2039*0.48) + (prob_ignition_person_2039*0.52),
                            frt == "13" ~ (prob_ignition_lightning_2039*0.83) + (prob_ignition_person_2039*0.17),
                            frt == "14" ~ (prob_ignition_lightning_2039*0.41) + (prob_ignition_person_2039*0.59),
                            frt == "15" ~ (prob_ignition_lightning_2039*0.28) + (prob_ignition_person_2039*0.72) ,
                            TRUE ~ NA_real_))

prob_fire<-prob_fire %>%
    mutate(tot_ignit_2044 = case_when(
                            frt == "5" ~ (prob_ignition_lightning_2044*0.84) + (prob_ignition_person_2044*0.16),
                            frt == "7" ~ (prob_ignition_lightning_2044*0.16) + (prob_ignition_person_2044*0.84),
                            frt == "9" ~ 
  (prob_ignition_lightning_2044*0.7) + (prob_ignition_person_2044*0.3),
                            frt == "10" ~ (prob_ignition_lightning_2044*0.86) + (prob_ignition_person_2044*0.14),
                            frt == "11" ~ (prob_ignition_lightning_2044*0.42) + (prob_ignition_person_2044*0.58),
                            frt == "12" ~ (prob_ignition_lightning_2044*0.48) + (prob_ignition_person_2044*0.52),
                            frt == "13" ~ (prob_ignition_lightning_2044*0.83) + (prob_ignition_person_2044*0.17),
                            frt == "14" ~ (prob_ignition_lightning_2044*0.41) + (prob_ignition_person_2044*0.59),
                            frt == "15" ~ (prob_ignition_lightning_2044*0.28) + (prob_ignition_person_2044*0.72) ,
                            TRUE ~ NA_real_))

prob_fire<-prob_fire %>%
    mutate(tot_ignit_2049 = case_when(
                            frt == "5" ~ (prob_ignition_lightning_2049*0.84) + (prob_ignition_person_2049*0.16),
                            frt == "7" ~ (prob_ignition_lightning_2049*0.16) + (prob_ignition_person_2049*0.84),
                            frt == "9" ~ 
  (prob_ignition_lightning_2049*0.7) + (prob_ignition_person_2049*0.3),
                            frt == "10" ~ (prob_ignition_lightning_2049*0.86) + (prob_ignition_person_2049*0.14),
                            frt == "11" ~ (prob_ignition_lightning_2049*0.42) + (prob_ignition_person_2049*0.58),
                            frt == "12" ~ (prob_ignition_lightning_2049*0.48) + (prob_ignition_person_2049*0.52),
                            frt == "13" ~ (prob_ignition_lightning_2049*0.83) + (prob_ignition_person_2049*0.17),
                            frt == "14" ~ (prob_ignition_lightning_2049*0.41) + (prob_ignition_person_2049*0.59),
                            frt == "15" ~ (prob_ignition_lightning_2049*0.28) + (prob_ignition_person_2049*0.72) ,
                            TRUE ~ NA_real_))

hist(prob_fire$prob_ignition_lightning_2021)
hist(prob_fire$prob_ignition_lightning_2024)
hist(prob_fire$prob_ignition_lightning_2029)
hist(prob_fire$prob_ignition_lightning_2034)
hist(prob_fire$prob_ignition_lightning_2039)
hist(prob_fire$prob_ignition_lightning_2044)
hist(prob_fire$prob_ignition_lightning_2049)

hist(prob_fire$prob_spread_2021)
hist(prob_fire$prob_spread_2024)
hist(prob_fire$prob_spread_2029)
hist(prob_fire$prob_spread_2034)
hist(prob_fire$prob_spread_2039)
hist(prob_fire$prob_spread_2044)
hist(prob_fire$prob_spread_2049)

```

