---
title: "Constant_Coefficients_table"
author: "Elizabeth Kleynhans"
date: "2023-03-09"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
#library(rgeos)

```

## Purpose of Script

The purpose of this script is to take the ignition, escape and spread models and calculate the sum of the coefficients in the model that are static for each pixel. Basically, create a raster map with the static values from the model. This should save time because then I only need to extract climate and vegetation data and add those changing coefficients to my static coefficeint map.


```{r}
dat<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\BC_ignit_escape_spread_final_2022.gpkg")

dat<-st_transform(dat, 3005)
dat$frt<-as.factor(dat$frt)
dat$frt[dat$frt==3]<-5

# for escaped fires I combine frt 9 and 11 because the number of escaped fires are very small and this bolsters my sample size. I dont do it for the others though because I think the fire dynamics are a little different in the two different areas and so its better to leave them separate. 
dat$frt_escape<-dat$frt
dat$frt_escape[dat$frt_escape==9]<-11
```

#Change Aspect to N,S,E,W
```{r}
library(rvest)
library(tidyverse)

url <- 'http://snowfence.umn.edu/Components/winddirectionanddegreeswithouttable3.htm'
page <- read_html(url)
directions_raw <- page %>% html_node('td table') %>% html_table(header = TRUE)

directions <- directions_raw %>% 
    set_names(~tolower(sub(' Direction', '', .x))) %>% 
    slice(-1) %>% 
    separate(degree, c('degree_min', 'degree_max'), sep = '\\s+-\\s+', convert = TRUE)

directions

dat <- dat %>% 
    mutate(aspect_cardinal = cut(
        aspect, 
        breaks = c(0, directions$degree_max, 360), 
        labels = c(directions$cardinal, 'N')
    ))

dat$aspect_cardinal2<-0
dat$aspect_cardinal2[dat$aspect_cardinal=="N"]<-"N"
dat$aspect_cardinal2[dat$aspect_cardinal=="E"]<-"E"
dat$aspect_cardinal2[dat$aspect_cardinal=="S"]<-"S"
dat$aspect_cardinal2[dat$aspect_cardinal=="W"]<-"W"

dat$aspect_cardinal2[dat$aspect_cardinal=="NNE"]<-"N"
dat$aspect_cardinal2[dat$aspect_cardinal=="NNW"]<-"N"
dat$aspect_cardinal2[dat$aspect_cardinal=="NE" & dat$aspect<=45]<-"N"

dat$aspect_cardinal2[dat$aspect_cardinal=="NE" & dat$aspect>45]<-"E"
dat$aspect_cardinal2[dat$aspect_cardinal=="ENE"]<-"E"
dat$aspect_cardinal2[dat$aspect_cardinal=="ESE"]<-"E"
dat$aspect_cardinal2[dat$aspect_cardinal=="SE" & dat$aspect<=135]<-"E"

dat$aspect_cardinal2[dat$aspect_cardinal=="SE" & dat$aspect>135]<-"S"
dat$aspect_cardinal2[dat$aspect_cardinal=="SSE"]<-"S"
dat$aspect_cardinal2[dat$aspect_cardinal=="SSW"]<-"S"
dat$aspect_cardinal2[dat$aspect_cardinal=="SW" & dat$aspect<=225]<-"S"

dat$aspect_cardinal2[dat$aspect_cardinal=="SW" & dat$aspect>225]<-"W"
dat$aspect_cardinal2[dat$aspect_cardinal=="WSW"]<-"W"
dat$aspect_cardinal2[dat$aspect_cardinal=="WNW"]<-"W"
dat$aspect_cardinal2[dat$aspect_cardinal=="NW" & dat$aspect<=315]<-"W"
dat$aspect_cardinal2[dat$aspect_cardinal=="NW" & dat$aspect>315]<-"N"

table(dat$aspect_cardinal2)
dat[dat$aspect_cardinal2=="0",]
dat<-dat %>% drop_na(aspect_cardinal)

names(dat)
# create dummy variables for aspect
dat$aspect_N <- ifelse(dat$aspect_cardinal2 == 'N', 1, 0)
dat$aspect_E <- ifelse(dat$aspect_cardinal2 == 'E', 1, 0)
dat$aspect_S <- ifelse(dat$aspect_cardinal2 == 'S', 1, 0)
dat$aspect_W <- ifelse(dat$aspect_cardinal2 == 'W', 1, 0)
```

### FRT 5
```{r}
frt5<- dat %>% filter(frt==5)
head(frt5)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt5_lightning.csv")

model_coef_table_lightning

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_lightning_coef<- model_coef_table_lightning$intercept + 
  model_coef_table_lightning$coef_elevatn * frt5$elevation

frt5$logit_P_lightning_coef<-logit_P_lightning_coef

####################################
# PErson ignitions

model_coef_table_person<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT5_person.csv")
model_coef_table_person

logit_P_person_coef<- model_coef_table_person$intercept + 
  model_coef_table_person$coef_log_road_dist*(log(frt5$dist_roads_m+1))+
  model_coef_table_person$coef_log_infr_dist*(log(frt5$dist_infrastructure_m+1))

frt5$logit_P_person_coef<-logit_P_person_coef

##########################
# probability of escape

model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt5_escape.csv")

model_coef_table_escape

logit_P_escape_coef<- model_coef_table_escape$intercept + 
  model_coef_table_escape$coef_elevation*frt5$elevation + 
  model_coef_table_escape$coef_log_road*log(frt5$dist_roads_m+1)+
  model_coef_table_escape$coef_dist_infra*frt5$dist_infrastructure_m
  
frt5$logit_P_escape_coef<-logit_P_escape_coef

##################################
# spread probabilities

model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt5_spread.csv")

model_coef_table_spread

# there are some Na values for wind so Ill fill in those values with the average.
table(is.na(frt5$win_spr))
frt5$win_spr[is.na(frt5$win_spr)] <- mean(frt5$win_spr, na.rm = TRUE)
# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread_coef<- model_coef_table_spread$intercept + 
  model_coef_table_spread$coef_elevation*frt5$elevation +
  model_coef_table_spread$coef_aspect_N*frt5$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt5$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt5$aspect_W +
  model_coef_table_spread$coef_dist_roads*frt5$dist_roads_m +
  model_coef_table_spread$coef_dist_infr*(log(frt5$dist_infrastructure_m+1)) +
  model_coef_table_spread$coef_win_spg*frt5$win_spr
  
frt5$logit_P_spread_coef<-logit_P_spread_coef

rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread)
gc()
```

## FRT 7
```{r}
frt7<- dat %>% filter(frt==7)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt7_lightning.csv")

model_coef_table_lightning

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_lightning_coef<- model_coef_table_lightning$intercept

frt7$logit_P_lightning_coef<-logit_P_lightning_coef

#####################
# Ignition Person
model_coef_table_person<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT7_person.csv")

model_coef_table_person

logit_P_person_coef<- model_coef_table_person$intercept + 
  model_coef_table_person$coef_log_road_dist*(log(frt7$dist_roads_m+1))+
  model_coef_table_person$coef_infr_dist*(log(frt7$dist_infrastructure_m+1))

frt7$logit_P_person_coef<-logit_P_person_coef

###################
# escape
model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT7_escape.csv")

model_coef_table_escape

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_escape_coef<- model_coef_table_escape$intercept + 
  model_coef_table_escape$coef_log_roads*log(frt7$dist_roads_m +1) 

frt7$logit_P_escape_coef<-logit_P_escape_coef

######################
## spread
model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt7_spread.csv")

model_coef_table_spread

logit_P_spread_coef<- model_coef_table_spread$intercept + 
  model_coef_table_spread$coef_slope*frt7$slope +
  model_coef_table_spread$coef_aspect_N*frt7$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt7$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt7$aspect_W +
  model_coef_table_spread$coef_log_dist_roads*log(frt7$dist_roads_m+1) +
  model_coef_table_spread$coef_dist_infr*frt7$dist_infrastructure_m

frt7$logit_P_spread_coef<-logit_P_spread_coef

rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread)
gc()


```

## FRT9

```{r}
frt9<- dat %>% filter(frt==9)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt9_lightning.csv")
model_coef_table_lightning
# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_lightning_coef<- model_coef_table_lightning$intercept + 
  model_coef_table_lightning$coef_elevatn*frt9$elevation

frt9$logit_P_lightning_coef<-logit_P_lightning_coef
######################################3
# person caused ignitions

model_coef_table_person<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt9_person.csv")
model_coef_table_person

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_person_coef<- model_coef_table_person$intercept + 
  model_coef_table_person$coef_elevatn*frt9$elevation  +
  model_coef_table_person$coef_infr_dist*frt9$dist_infrastructure_m


frt9$logit_P_person_coef<-logit_P_person_coef

##################################
# escape
model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_escape.csv")

model_coef_table_escape

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_escape_coef<- model_coef_table_escape$intercept +
  model_coef_table_escape$coef_log_infra*(log(frt9$dist_infrastructure_m+1))

frt9$logit_P_escape_coef<-logit_P_escape_coef

################################
# spread
model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt9_spread.csv")

model_coef_table_spread

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table_spread$intercept +
  model_coef_table_spread$coef_elev*frt9$elevation +
  model_coef_table_spread$coef_aspect_N*frt9$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt9$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt9$aspect_W +
  model_coef_table_spread$coef_log_dist_roads*log(frt9$dist_roads_m+1)+
  model_coef_table_spread$coef_dist_infr_m*frt9$dist_infrastructure_m

logit_P_spread

frt9$logit_P_spread_coef<-logit_P_spread

rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread)
gc()

```

## FRT10
```{r}
frt10<- dat %>% filter(frt==10)

model_coef_table_lightning<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT10_lightning.csv")

model_coef_table_lightning

logit_P_lightning_coef<- model_coef_table_lightning$intercept + 
  model_coef_table_lightning$coef_elevatn*frt10$elevation

frt10$logit_P_lightning_coef<-logit_P_lightning_coef

########################################
# Person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT10_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_log_road_dist*(log(frt10$dist_roads_m+1))

frt10$logit_P_person_coef<-logit_P_person_coef

#################################
# escape
model_coef_table_escape<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt10_escape.csv")

model_coef_table_escape

logit_P_escape<- model_coef_table_escape$intercept + 
  model_coef_table_escape$coef_slope*frt10$slope +
  model_coef_table_escape$coef_road_dist*frt10$dist_roads_m +
  model_coef_table_escape$coef_log_infr_dist*log(frt10$dist_infrastructure_m +1)

frt10$logit_P_escape_coef<-logit_P_escape

###########################
# Spread

table(is.na(frt10$win_spr))
frt10$win_spr[is.na(frt10$win_spr)] <- mean(frt10$win_spr, na.rm = TRUE)


model_coef_table_spread<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt10_spread.csv")

model_coef_table_spread

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table_spread$intercept +
  model_coef_table_spread$coef_elevation*frt10$elevation +
  model_coef_table_spread$coef_slope*frt10$slope +
  model_coef_table_spread$coef_aspect_N*frt10$aspect_N +
  model_coef_table_spread$coef_aspect_S*frt10$aspect_S +
  model_coef_table_spread$coef_aspect_W*frt10$aspect_W +
  model_coef_table_spread$coef_dist_infr*frt10$dist_infrastructure_m

frt10$logit_P_spread_coef<-logit_P_spread

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread, prob_ignition_escape, prob_ignition_lightning, prob_ignition_person, prob_ignition_spread, logit_P_escape, logit_P_lightning, logit_P_person, logit_P_spread)
gc()

```


## FRT 11 

```{r}
frt11<- dat %>% filter(frt==11)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT11_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept

frt11$logit_P_lightning_coef<-logit_P_lightning_coef

##########################
#Person
model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept +
  model_coef_table$coef_log_road_dist*log(frt11$dist_roads_m+1) +
  model_coef_table$coef_log_infr_dist_m*log(frt11$dist_infrastructure_m+1) 

frt11$logit_P_person_coef<-logit_P_person_coef


################################
# Escape

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_escape.csv")

model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_log_infra*log(frt11$dist_infrastructure_m + 1)

frt11$logit_P_escape_coef<-logit_P_escape_coef

##########################
# Spread

table(is.na(frt11$win_sum))
frt11$win_sum[is.na(frt11$win_sum)] <- mean(frt11$win_sum, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt11_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt11$slope +
  model_coef_table$coef_aspect_N*frt11$aspect_N +
  model_coef_table$coef_aspect_S*frt11$aspect_S +
  model_coef_table$coef_aspect_W*frt11$aspect_W +
  model_coef_table$coef_dist_roads*frt11$dist_roads_m +
  model_coef_table$coef_dist_infr*frt11$dist_infrastructure_m +
  model_coef_table$coef_wind_summer*frt11$win_sum

frt11$logit_P_spread_coef<-logit_P_spread

```

## FRT 12

```{r}
frt12<- dat %>% filter(frt==12)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT12_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt12$elevation

frt12$logit_P_lightning_coef<-logit_P_lightning_coef

##########################
# Person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT12_person.csv")
model_coef_table

#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt12$elevation + 
  model_coef_table$coef_log_road_dist*log(frt12$dist_roads_m+1) +
  model_coef_table$coef_log_inf_dist*log(frt12$dist_infrastructure_m+1)
  
frt12$logit_P_person_coef<-logit_P_person_coef

##################################
#escape
model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt12_escape.csv")

model_coef_table

logit_P_escape_coef<- model_coef_table$intercept +
  model_coef_table$coef_slope*frt12$slope +
  model_coef_table$coef_elev*frt12$elevation +
  model_coef_table$coef_win_sum*frt12$win_sum + 
  model_coef_table$coef_dist_roads_m*frt12$dist_roads_m +
  model_coef_table$coef_log_infr_dist*log(frt12$dist_infrastructure_m+1)

frt12$logit_P_escape_coef<-logit_P_escape_coef

########################
# Spread

table(is.na(frt12$win_sum))
frt12$win_sum[is.na(frt12$win_sum)] <- mean(frt12$win_sum, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt12_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept +
  model_coef_table$coef_elevation*frt12$elevation +
  model_coef_table$coef_slope*frt12$slope +
  model_coef_table$coef_log_dist_roads*log(frt12$dist_roads_m+1) +
  model_coef_table$coef_log_dist_infra*log(frt12$dist_infrastructure_m+1) +
  model_coef_table$coef_wind_summer*frt12$win_sum

logit_P_spread
frt12$logit_P_spread_coef<-logit_P_spread


```

## FRT13
```{r}
frt13<- dat %>% filter(frt==13)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT13_lightning.csv")
model_coef_table

#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk

logit_P_lightning_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elev*frt13$elevation

frt13$logit_P_lightning_coef<-logit_P_lightning_coef

#############################
# person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT13_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt13$elevation + 
  model_coef_table$coef_log_road_dist*log(frt13$dist_roads_m+1) +
  model_coef_table$coef_log_inf_dist*log(frt13$dist_infrastructure_m+1)

frt13$logit_P_person_coef<-logit_P_person_coef

################################
#escape

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt13_escape.csv")
model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt13$slope +
  model_coef_table$coef_win_sum*frt13$win_sum +
  model_coef_table$coef_roads_m*frt13$dist_roads_m +
  model_coef_table$coef_log_infr*log(frt13$dist_infrastructure_m+1) 

frt13$logit_P_escape_coef<-logit_P_escape_coef

##########################
#spread

frt13$win_sum[is.na(frt13$win_sum)] <- mean(frt13$win_sum, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt13_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_elevation*frt13$elevation +
  model_coef_table$coef_aspect_N*frt13$aspect_N +
  model_coef_table$coef_aspect_S*frt13$aspect_S +
  model_coef_table$coef_aspect_W*frt13$aspect_W +
  model_coef_table$coef_log_dist_roads*log(frt13$dist_roads_m+1) +
  model_coef_table$coef_log_dist_infra*log(frt13$dist_infrastructure_m+1) +
  model_coef_table$coef_wind_summer*frt13$win_sum

logit_P_spread
frt13$logit_P_spread_coef<-logit_P_spread

```

#FRT 14
```{r}
frt14<- dat %>% filter(frt==14)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT14_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept
frt14$logit_P_lightning_coef<-logit_P_lightning_coef

############################
# person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT14_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept + 
  model_coef_table$coef_log_road_dist*log(frt14$dist_roads_m+1) +
  model_coef_table$coef_log_inf_dist*log(frt14$dist_infrastructure_m+1)

frt14$logit_P_person_coef<-logit_P_person_coef

##############################
#escape  

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt14_escape.csv")
model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_win_sum*frt14$win_sum +
  model_coef_table$coef_dist_road_m*log(frt14$dist_roads_m+1) +
  model_coef_table$coef_dist_infr_m*log(frt14$dist_infrastructure_m+1)
  
frt14$logit_P_escape_coef<-logit_P_escape_coef

################################
#spread

frt14$win_sum[is.na(frt14$win_sum)] <- mean(frt14$win_sum, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt14_spread.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_elevation*frt14$elevation +
  model_coef_table$coef_aspect_N*frt14$aspect_N +
  model_coef_table$coef_aspect_S*frt14$aspect_S +
  model_coef_table$coef_aspect_W*frt14$aspect_W +
  model_coef_table$coef_dist_roads*log(frt14$dist_roads_m+1) +
  model_coef_table$coef_log_dist_infra*log(frt14$dist_infrastructure_m+1) +
  model_coef_table$coef_wind_summer*frt14$win_sum

logit_P_spread
frt14$logit_P_spread_coef<-logit_P_spread

```

## FRT15
```{r}
frt15<- dat %>% filter(frt==15)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT15_lightning.csv")
model_coef_table

logit_P_lightning_coef<- model_coef_table$intercept + 
  model_coef_table$coef_elevatn*frt15$elevation

frt15$logit_P_lightning_coef<-logit_P_lightning_coef

################################
# Person

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_FRT15_person.csv")
model_coef_table

logit_P_person_coef<- model_coef_table$intercept + 
   model_coef_table$coef_log_road_dist*log(frt15$dist_roads_m+1) +
  model_coef_table$coef_infr_dist*frt15$dist_infrastructure_m 

frt15$logit_P_person_coef<-logit_P_person_coef

################################
# escape

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt15_escape.csv")
model_coef_table

logit_P_escape_coef<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt15$slope +
  model_coef_table$coef_log_infr_ds*log(frt15$dist_infrastructure_m+1)

frt15$logit_P_escape_coef<-logit_P_escape_coef

#################################
# spread
frt15$win_sum[is.na(frt15$win_sum)] <- mean(frt15$win_sum, na.rm = TRUE)

model_coef_table<-read.csv("C:\\Work\\caribou\\castor\\R\\fire_sim\\Analysis_results\\BC\\Coefficient_tables\\top_mod_table_frt15_spread.csv")
model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
logit_P_spread<- model_coef_table$intercept + 
  model_coef_table$coef_slope*frt15$slope +
  model_coef_table$coef_aspect_N*frt15$aspect_N +
  model_coef_table$coef_aspect_S*frt15$aspect_S +
  model_coef_table$coef_aspect_W*frt15$aspect_W +
  model_coef_table$coef_log_dist_infra*log(frt15$dist_infrastructure_m+1) +
  model_coef_table$coef_wind_summer*frt15$win_sum

logit_P_spread
frt15$logit_P_spread_coef<-logit_P_spread


rm(model_coef_table, model_coef_table_escape, model_coef_table_lightning, model_coef_table_person, model_coef_table_spread, prob_ignition_escape, prob_ignition_lightning, prob_ignition_person, prob_ignition_spread, logit_P_escape, logit_P_lightning, logit_P_person, logit_P_spread)
gc()

table(is.na(frt15$prob_ignition_spread))

```

# now join all the frt's back together. 
```{r}
frt_all<-rbind(rbind(rbind(rbind(rbind(rbind(rbind(rbind(frt5, frt7), frt9), frt10), frt11), frt12), frt13), frt14), frt15)

dim(frt_all)

table(is.na(frt_all$logit_P_lightning_coef ))
table(is.na(frt_all$logit_P_person_coef))
table(is.na(frt_all$logit_P_escape_coef ))
table(is.na(frt_all$logit_P_spread_coef))
```

# save it!
```{r}
st_write(frt_all, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\BC_ignit_escape_spread_final_constant_coefficients.gpkg", delete_layer=TRUE, driver="GPKG")
```

