---
title: "Extract climate data for a range of dates"
author: "Elizabeth Kleynhans"
date: "2023-02-24"
output: html_document
---

## Extract Climate Data

In this script you can extract climate data for a range of dates. I tried to get it to work with asci files but I could not get that to go properly. Annoying because I could then have deleted all the unneccessary climate variables and only have been left with the ones I wanted. I should maybe put more effort into fixing this sometime. 
```{r cars}
setwd("D:/Climatebc_v730"); # set the ClimateBC root directory as the working directory
 exe <- "ClimateBC_v7.30.exe"
 
 years<- 1964:1984

 for (i in 1:length(years)){
   
#inputFile = '/C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\rast_dem_kyle.asc'
#outputDir = '/C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\test/' 
print(years[i])
 inputFile = '/C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\bc_dem_frt_Kyle.csv'
 outputFile = paste0('/C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\Kyle\\bc_dem_',years[i] , '.csv')
 yearPeriod = paste0('/Year_', years[i], '.ann')
 system2(exe,args= c('/S', yearPeriod, inputFile, outputFile))
 
 }
 
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
