---
title: "Run models for fire escape prediction map"
author: "Elizabeth Kleynhans"
date: '2022-09-09'
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (kableExtra)
source(here::here("R/functions/R_Postgres.R"))
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(mapview)
library(tmap)

```

# open climate table to see which variables I need for climate1 and climate2
```{r eval=, message=FALSE, AIC table, echo=F}

climate_variable<-read.csv("C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/climate_AIC_results_escape_summary.csv")

kable (climate_variable,
       caption = "<b>Table 1. Top candidate climate variables for escaped fires as selected through an AIC analysis for each Fire Regime Type.<b>",
       digits = 2) %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover"),
                 fixed_thead = T,
                 full_width = F,
                 font_size = 11)
```

# Import the data

```{r}

fire_escape<-st_read( "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\BC_all_dat_400m_final.gpkg")
fire_escape <- st_transform (fire_escape, 3005)


fire_escape$mean_Tave05_Tave06_Tave07_Tave08<- (fire_escape$Tave05 + fire_escape$Tave06 + fire_escape$Tave07 + fire_escape$Tave08)/4

fire_escape$mean_PPT05_PPT06_PPT07_PPT08 <- (fire_escape$PPT05 + fire_escape$PPT06 + fire_escape$PPT07 + fire_escape$PPT08)/4

fire_escape$mean_Tave04_Tave05_Tave06<- (fire_escape$Tave04 + fire_escape$Tave05 + fire_escape$Tave06 )/3

fire_escape$mean_PPT04_PPT05_PPT06<- (fire_escape$PPT04 + fire_escape$PPT05 + fire_escape$PPT06)/3

fire_escape$mean_PPT05_PPT06<- (fire_escape$PPT05 + fire_escape$PPT06)/2

```


#Create climate1 and climate2 columns

```{r}
#View top variable
names(fire_escape)
unique(fire_escape$frt) # FRT 3 should not be in this list
fire_escape$frt[fire_escape$frt==3]<-5
table(is.na(fire_escape$frt))


fire_escape$frt<-as.numeric(fire_escape$frt)

table(fire_escape$frt)

## Create empty vector
fire_escape$climate1<-"NA"

head(fire_escape)

fire_escape<-fire_escape %>%
    mutate(climate1 = case_when(
                            frt == "5" ~ as.numeric(PPT05) ,
                            frt == "7" ~ as.numeric(PPT03),
                            frt == "9" ~ Tave05,
                            frt == "10" ~ mean_Tave05_Tave06_Tave07_Tave08 ,
                            frt == "11" ~ Tave09,
                            frt == "12" ~ mean_Tave04_Tave05_Tave06,
                            frt == "13" ~ Tave09,
                            frt == "14" ~ as.numeric(mean_PPT05_PPT06),
                            frt == "15" ~ Tave04 ,
                            TRUE ~ NA_real_))

#Repeat for climate 2
fire_escape$climate2<-"NA"

fire_escape<-fire_escape %>%
    mutate(climate2 = case_when(
                            frt == "10" ~ as.numeric(mean_PPT05_PPT06_PPT07_PPT08) ,
                            frt == "12" ~ as.numeric(mean_PPT04_PPT05_PPT06),
                            frt == "15" ~ as.numeric(PPT04),
                            TRUE ~ NA_real_))

head(fire_escape)

##Change vegtype to factor
fire_escape$FWI_veg<-as.factor(fire_escape$FWI_veg)

```

#Change Aspect to N,S,E,W 
Something to consider: I did not test aspect in the escape models so I dont know if aspect is important. I could possibly try.
```{r}
# library(rvest)
# library(tidyverse)
# 
# url <- 'http://snowfence.umn.edu/Components/winddirectionanddegreeswithouttable3.htm'
# page <- read_html(url)
# directions_raw <- page %>% html_node('td table') %>% html_table(header = TRUE)
# 
# directions <- directions_raw %>% 
#     set_names(~tolower(sub(' Direction', '', .x))) %>% 
#     slice(-1) %>% 
#     separate(degree, c('degree_min', 'degree_max'), sep = '\\s+-\\s+', convert = TRUE)
# 
# directions
# 
# fire_escape <- fire_escape %>% 
#     mutate(aspect_cardinal = cut(
#         aspect, 
#         breaks = c(0, directions$degree_max, 360), 
#         labels = c(directions$cardinal, 'N')
#     ))
# 
# fire_escape$aspect_cardinal2<-0
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="N"]<-"N"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="E"]<-"E"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="S"]<-"S"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="W"]<-"W"
# 
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="NNE"]<-"N"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="NNW"]<-"N"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="NE" & fire_escape$aspect<=45]<-"N"
# 
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="NE" & fire_escape$aspect>45]<-"E"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="ENE"]<-"E"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="ESE"]<-"E"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="SE" & fire_escape$aspect<=135]<-"E"
# 
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="SE" & fire_escape$aspect>135]<-"S"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="SSE"]<-"S"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="SSW"]<-"S"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="SW" & fire_escape$aspect<=225]<-"S"
# 
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="SW" & fire_escape$aspect>225]<-"W"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="WSW"]<-"W"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="WNW"]<-"W"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="NW" & fire_escape$aspect<=315]<-"W"
# fire_escape$aspect_cardinal2[fire_escape$aspect_cardinal=="NW" & fire_escape$aspect>315]<-"N"
# 
# fire_escape
# 
# table(fire_escape$aspect_cardinal2)
#  fire_escape[fire_escape$aspect_cardinal2=="0",]
#  fire_escape<-fire_escape %>% drop_na(aspect_cardinal)
```


```{r}
# create dummy variables for FWI_veg

fire_escape$veg_C1 <- ifelse(fire_escape$FWI_veg == 'C-1', 1, 0)
fire_escape$veg_C2 <- ifelse(fire_escape$FWI_veg == 'C-2', 1, 0)
fire_escape$veg_C3 <- ifelse(fire_escape$FWI_veg == 'C-3', 1, 0)
fire_escape$veg_C4 <- ifelse(fire_escape$FWI_veg == 'C-4', 1, 0)
fire_escape$veg_C5 <- ifelse(fire_escape$FWI_veg == 'C-5', 1, 0)
fire_escape$veg_C7 <- ifelse(fire_escape$FWI_veg == 'C-7', 1, 0)
fire_escape$veg_D12 <- ifelse(fire_escape$FWI_veg == 'D-1/2', 1, 0)
fire_escape$veg_M12 <- ifelse(fire_escape$FWI_veg == 'M-1/2', 1, 0)
fire_escape$veg_M3 <- ifelse(fire_escape$FWI_veg == 'M-3', 1, 0)
fire_escape$veg_N <- ifelse(fire_escape$FWI_veg == 'N', 1, 0)
fire_escape$veg_O1ab <- ifelse(fire_escape$FWI_veg == 'O-1a/b', 1, 0)
fire_escape$veg_S1 <- ifelse(fire_escape$FWI_veg == 'S-1', 1, 0)
fire_escape$veg_S2 <- ifelse(fire_escape$FWI_veg == 'S-2', 1, 0)
fire_escape$veg_S3 <- ifelse(fire_escape$FWI_veg == 'S-3', 1, 0)
fire_escape$veg_W <- ifelse(fire_escape$FWI_veg == 'W', 1, 0)

names(fire_escape)
table(fire_escape$frt, fire_escape$FWI_veg)
fire_escape$log_dist_roads_m<-log(fire_escape$dist_roads_m + 1)
fire_escape$log_dist_infrastructure_m<-log(fire_escape$dist_infrastructure_m + 1)

# create dummy variables for aspect
# fire_escape$aspect_N <- ifelse(fire_escape$aspect_cardinal2 == 'N', 1, 0)
# fire_escape$aspect_E <- ifelse(fire_escape$aspect_cardinal2 == 'E', 1, 0)
# fire_escape$aspect_S <- ifelse(fire_escape$aspect_cardinal2 == 'S', 1, 0)
# fire_escape$aspect_W <- ifelse(fire_escape$aspect_cardinal2 == 'W', 1, 0)

```

# remove water, glaciers, lakes stuff that cant burn from points
```{r}
no_ignition1<-fire_escape %>% 
  filter(FWI_veg =="W")

spread3<-fire_escape %>% 
  filter(FWI_veg !="W")

no_ignition2<-spread3 %>% 
  filter(bclcs_level_5 %in% c("GL", "LA"))

no_ignition<-rbind(no_ignition1, no_ignition2)

spread4<-spread3 %>% 
  filter(!bclcs_level_5 %in% c("GL", "LA"))

dim(no_ignition)
dim(fire_escape)
dim(spread4) # looks good

rm(no_ignition1, no_ignition2, spread3)
gc()


```


### FRT 5

```{r}
frt5<- spread4 %>% filter(frt==5)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt5_escape.csv")

model_coef_table

table(frt5$FWI_veg)

frt5$FWI_veg[frt5$FWI_veg=="S-1"]<-"M-1/2"
frt5$FWI_veg[frt5$FWI_veg=="S-2"]<-"M-1/2"
frt5$FWI_veg[frt5$FWI_veg=="C-4"]<-"C-2"
frt5$FWI_veg[frt5$FWI_veg=="C-5"]<-"D-1/2"
frt5$FWI_veg[frt5$FWI_veg=="C-7"]<-"D-1/2"

#remove FWI_veg type = N as there apparently were none in the model. 

frt5_n<-frt5 %>% filter(FWI_veg=="N")
frt5_2<-frt5 %>% filter(FWI_veg!="N")

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt5_2$logit_P<- model_coef_table[[2]] + 
  model_coef_table[[3]]*frt5_2$climate1 +
  model_coef_table[[4]]*frt5_2$veg_C2 +
  model_coef_table[[5]]*frt5_2$veg_C3 +
  model_coef_table[[6]]*frt5_2$veg_D12 +
  model_coef_table[[7]]*frt5_2$veg_M12 +
  model_coef_table[[8]]*frt5_2$veg_O1ab +
  model_coef_table[[9]]*frt5_2$elevation + 
  model_coef_table[[10]]*log(frt5_2$dist_infrastructure_m+1)
  

head(frt5_2)

# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt5_2$prob_ignition<-exp(frt5_2$logit_P)/(1+exp(frt5_2$logit_P))

frt5_n$logit_P<-0
frt5_n$prob_ignition<-0 # make the FWI_veg type =N have a probability of ignition =0

frt5_3<-rbind(frt5_2, frt5_n)

summary(frt5_3$prob_ignition)
hist(frt5_3$prob_ignition)

```

FRT 7 
```{r}
frt7<- spread4 %>% filter(frt==7)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt7_escape.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt7$logit_P<- model_coef_table[[2]] + 
  model_coef_table[[3]]*frt7$climate1 +
  model_coef_table[[4]]*log(frt7$dist_infrastructure_m +1) 

head(frt7)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt7$prob_ignition<-exp(frt7$logit_P)/(1+exp(frt7$logit_P))

summary(frt7$prob_ignition)
hist(frt7$prob_ignition)

```


FRT 9 
```{r}
frt9<- spread4 %>% filter(frt==9)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt9_escape.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt9$logit_P<- model_coef_table[[2]] +
  model_coef_table[[3]]*frt9$climate1 +
  model_coef_table[[4]]*frt9$log_dist_roads_m

head(frt9)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt9$prob_ignition<-exp(frt9$logit_P)/(1+exp(frt9$logit_P))

summary(frt9$prob_ignition)
hist(frt9$prob_ignition)

```

FRT 10 
```{r}
frt10<- spread4 %>% filter(frt==10)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt10_escape.csv")

model_coef_table


# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt10$logit_P<- model_coef_table[[2]] + 
  model_coef_table[[3]]*frt10$climate1 +
  model_coef_table[[4]]*frt10$climate2 +
  model_coef_table[[5]]*frt10$log_dist_roads_m +
  model_coef_table[[6]]*frt10$dist_infrastructure_m 

head(frt10)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt10$prob_ignition<-exp(frt10$logit_P)/(1+exp(frt10$logit_P))

summary(frt10$prob_ignition)
hist(frt10$prob_ignition)

```


FRT 11 
```{r}
frt11<- spread4 %>% filter(frt==11)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt11_escape.csv")

model_coef_table

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt11$logit_P<- model_coef_table[[2]] + 
  model_coef_table[[3]]*frt11$climate1 +
  model_coef_table[[4]]*frt11$log_dist_roads_m +
  model_coef_table[[5]]*frt11$log_dist_infrastructure_m

head(frt11)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt11$prob_ignition<-exp(frt11$logit_P)/(1+exp(frt11$logit_P))

summary(frt11$prob_ignition)
hist(frt11$prob_ignition)

```


FRT 12
```{r}
frt12<- spread4 %>% filter(frt==12)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt12_escape.csv")

model_coef_table

table(frt12$FWI_veg)

frt12$FWI_veg[frt12$FWI_veg=="C-4"]<-"C-2"
frt12$FWI_veg[frt12$FWI_veg=="S-1"]<-"M-1/2"
frt12$FWI_veg[frt12$FWI_veg=="S-2"]<-"C-7"
frt12$FWI_veg[frt12$FWI_veg=="S-3"]<-"M-1/2"

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt12$logit_P<- model_coef_table[[2]] +
  model_coef_table[[3]]*frt12$climate1 +
  model_coef_table[[4]]*frt12$veg_C2 +
  model_coef_table[[5]]*frt12$veg_C3 +
  model_coef_table[[6]]*frt12$veg_C5 +
  model_coef_table[[7]]*frt12$veg_C7 +
  model_coef_table[[8]]*frt12$veg_D12 +
  model_coef_table[[9]]*frt12$veg_M12 +
  model_coef_table[[10]]*frt12$veg_M3 +
  model_coef_table[[11]]*frt12$veg_N +
  model_coef_table[[12]]*frt12$veg_O1ab +
  model_coef_table[[13]]*frt12$slope +
  model_coef_table[[14]]*frt12$win_sum + 
  model_coef_table[[15]]*frt12$log_dist_roads_m +
  model_coef_table[[16]]*frt12$log_dist_infrastructure_m 

head(frt12)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt12$prob_ignition<-exp(frt12$logit_P)/(1+exp(frt12$logit_P))

summary(frt12$prob_ignition)
hist(frt12$prob_ignition)

```

FRT 13
```{r}
frt13<- spread4 %>% filter(frt==13)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt13_escape.csv")

model_coef_table

table(frt13$FWI_veg)

frt13$FWI_veg[frt13$FWI_veg=="C-1"]<-"C-7"
frt13$FWI_veg[frt13$FWI_veg=="C-4"]<-"C-2"
frt13$FWI_veg[frt13$FWI_veg=="M-3"]<-"O-1a/b"
frt13$FWI_veg[frt13$FWI_veg=="S-2"]<-"C-7"

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt13$logit_P<- model_coef_table[[2]] + 
  model_coef_table[[3]]*frt13$climate1 +
  model_coef_table[[4]]*frt13$veg_C3 +
  model_coef_table[[5]]*frt13$veg_C5 +
  model_coef_table[[6]]*frt13$veg_C7 +
  model_coef_table[[7]]*frt13$veg_D12 +
  model_coef_table[[8]]*frt13$veg_M12 +
  model_coef_table[[9]]*frt13$veg_N +
  model_coef_table[[10]]*frt13$veg_O1ab +
  model_coef_table[[11]]*frt13$veg_S1 +
  model_coef_table[[12]]*frt13$veg_S3 +
  model_coef_table[[13]]*frt13$slope +
  model_coef_table[[14]]*frt13$elevation +
  model_coef_table[[15]]*frt13$win_sum +
  model_coef_table[[16]]*frt13$log_dist_roads_m +
  model_coef_table[[17]]*frt13$log_dist_infrastructure_m 
  

head(frt13)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt13$prob_ignition<-exp(frt13$logit_P)/(1+exp(frt13$logit_P))

summary(frt13$prob_ignition)
hist(frt13$prob_ignition)

```

FRT 14
```{r}
frt14<- spread4 %>% filter(frt==14)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt14_escape.csv")

model_coef_table

table(frt14$FWI_veg)

frt14$FWI_veg[frt14$FWI_veg=="C-2"]<-"C-3"
frt14$FWI_veg[frt14$FWI_veg=="C-4"]<-"C-3"
frt14$FWI_veg[frt14$FWI_veg=="S-2"]<-"C-7"
frt14$FWI_veg[frt14$FWI_veg=="S-1"]<-"M-1/2"
frt14$FWI_veg[frt14$FWI_veg=="S-3"]<-"M-1/2"

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt14$logit_P<- model_coef_table[[2]] + 
  model_coef_table[[3]]*frt14$climate1 +
  model_coef_table[[4]]*frt14$veg_C5 +
  model_coef_table[[5]]*frt14$veg_C7 +
  model_coef_table[[6]]*frt14$veg_D12 +
  model_coef_table[[7]]*frt14$veg_M12 +
  model_coef_table[[8]]*frt14$veg_N +
  model_coef_table[[9]]*frt14$veg_O1ab +
  model_coef_table[[10]]*frt14$win_sum +
  model_coef_table[[11]]*frt14$log_dist_roads_m +
  model_coef_table[[12]]*frt14$log_dist_infrastructure_m
  

head(frt14)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt14$prob_ignition<-exp(frt14$logit_P)/(1+exp(frt14$logit_P))

summary(frt14$prob_ignition)
hist(frt14$prob_ignition)

```

FRT 15
```{r}
frt15<- spread4 %>% filter(frt==15)

model_coef_table<-read.csv("D:\\Fire\\fire_data\\raw_data\\top_mod_table_frt15_escape.csv")

model_coef_table

table(frt15$FWI_veg)

frt15$FWI_veg[frt15$FWI_veg=="C-2"]<-"C-3"
frt15$FWI_veg[frt15$FWI_veg=="C-7"]<-"C-5"
frt15$FWI_veg[frt15$FWI_veg=="O-1a/b"]<-"C-3"
frt15$FWI_veg[frt15$FWI_veg=="S-1"]<-"S-3"

# put coefficients into model formula
#logit(p) = b0+b1X1+b2X2+b3X3….+bkXk
frt15$logit_P<- model_coef_table[[2]] + 
  model_coef_table[[3]]*frt15$climate2 +
  model_coef_table[[4]]*frt15$veg_C5 +
  model_coef_table[[5]]*frt15$veg_D12 +
  model_coef_table[[6]]*frt15$veg_M12 +
  model_coef_table[[7]]*frt15$veg_N +
  model_coef_table[[8]]*frt15$veg_S3 +
  model_coef_table[[9]]*frt15$slope +
  model_coef_table[[10]]*frt15$log_dist_infrastructure_m

head(frt15)
# y = e^(b0 + b1*x) / (1 + e^(b0 + b1*x))
frt15$prob_ignition<-exp(frt15$logit_P)/(1+exp(frt15$logit_P))

summary(frt15$prob_ignition)
hist(frt15$prob_ignition)

```


### now combine all FRT's and plot it
```{r}
# reduce the number of columns before I combine the files together. 
frt5_2<-frt5_3 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt7_2<-frt7 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt9_2<-frt9 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt10_2<-frt10 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt11_2<-frt11 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt12_2<-frt12 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt13_2<-frt13 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt14_2<-frt14 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt15_2<-frt15 %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt_all<- rbind(rbind(rbind(rbind(rbind(rbind(rbind(rbind(frt5_2, frt7_2), frt9_2), frt10_2), frt11_2), frt12_2), frt13_2), frt14_2), frt15_2)

dim(frt_all)
hist(frt_all$prob_ignition)

no_ignition$prob_ignition<-0
no_ignition$logit_P<-0

no_ignition_2<-no_ignition %>% dplyr::select(idno:elevation, bclcs_level_4, bclcs_level_5, FWI_veg: dist_roads_m, dist_infrastructure_m:Tmax12, Tave01:RH12, climate1, climate2,  logit_P, prob_ignition)

frt_all2<-rbind(no_ignition_2, frt_all)

dim(frt_all2)
hist(frt_all2$prob_ignition)

# clean up a bunch of files to hopefully speed up saving
rm(frt14, frt14_2, frt5, frt5_2, frt7, frt7_2, frt9, frt9_2, frt10, frt10_2, frt11, frt11_2, frt12, frt12_2, frt13, frt13_2, frt15, frt15_2, no_ignition, no_ignition1, no_ignition2, no_ignition_2, spread3, spread4, climate_variable, directions, directions_raw, fire_escape2)

gc()
```


```{r}
st_write(frt_all2, "C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\BC_prob_escape_final.gpkg", delete_layer=TRUE, driver="GPKG")


# rasterizing the above file in QGIS:

# go to raster -> Conversion -> Rasterize (Vector to raster)

# then use the shapefile as the input layer, prob ignition as the field to use for burn-in value. 
# output raster size units -> georeferenced units
# resolution = 400m
# note: make sure you use the file rast.bc_bounds as the extent. Its found in postgres kyle clus. If you dont do this the extent will be wrong and the rasterization wont work properly.

# the full commonad should look something like this:

# gdal_rasterize -l BC_prob_escape_final -a prob_ignition -tr 400.0 400.0 -a_nodata 0.0 -te 159587.5 173787.5 1881187.5 1748187.5 -ot Float32 -of GTiff C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/BC/BC_prob_escape_final.gpkg C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/BC/rast_escape_400m.tif




```


```{r}
x<- st_read("C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\BC\\BC_prob_escape_final.gpkg")

layeraoi<-getSpatialQuery("SELECT * FROM study_area_compart limit 1")
#Create a provincial raster
prov.rast <- raster::raster(
  nrows = 3936, ncols = 4304, xmn = 159587.5, xmx = 1881187.5, ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs(layeraoi)$proj4string, resolution = c(400, 400), vals = 0)

study_area<-x %>% dplyr::select(idno, frt, prob_ignition)
st_crs(study_area)

ras.aoi2 <- crop(prov.rast, study_area2)

r<-raster(ras.aoi2)
r<-fasterize()

study_area2<-st_as_sf(study_area)
study_area3<-st_cast(study_area2, to="POLYGON")
study_area3<-st_cast(study_area3, to="MULTIPOLYGON")

x<-st_make_grid(study_area2, cellsize=c(400,400), crs=3005)
x2<-st_coordinates(st_centroid(study_area2))
# Transform the data
library(proj4)
lon_lat <- project(x2, st_crs(layeraoi)$proj4string)

# convert to a data frame
data.frame(lon = lon_lat$x, lat = lon_lat$y)


x3<-as.data.frame(x2)
colnames(x3) <- c("longitude", "latitude")
x3$idno<-1:length(x3$latitude)

ras.aoi <- fasterize::fasterize (study_area2, prov.rast, field = "prob_ignition")
```


```{r}
# create raster

layeraoi<-getSpatialQuery("SELECT * FROM study_area_compart limit 1")
#Create a provincial raster
prov.rast <- raster::raster ( # standardized provincial raster with no data in it
                              nrows = 15744, ncols = 17216, 
                              xmn = 159587.5, xmx = 1881187.5, 
                              ymn = 173787.5, ymx = 1748187.5, 
                              crs = "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", 
                              resolution = c(100, 100),                               
                              vals = 0)


study_area<-getSpatialQuery("SELECT tsa_name, tsa_number, wkb_geometry FROM study_area_compart where tsa_name in ('Quesnel TSA', 'Williams Lake TSA',  '100 Mile House TSA')")

study_area2<-study_area %>% group_by ( tsa_name, tsa_number) %>% summarise()
st_crs(study_area2)

study_area2<-st_as_sf(study_area2)
ras.aoi2 <- crop(prov.rast, study_area2)

x<-rasterize(frt_all, ras.aoi2, field="prob_ignition", update=TRUE)
#x<-fasterize::fasterize(frt_all, ras.aoi2, field="prob_ignition", update=TRUE)
plot(x)

writeRaster(x, file=" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\Probability_of_Escape_Quesnell_WilliamsL_100Mile_allFRT_800m_fasterize_try.tif", format="GTiff", overwrite=TRUE)

##########

library(sp)
library(rgdal)
library(raster)
library(gstat)
fit.p.ign <- gstat::gstat(formula = prob_ignition ~ 1, data = frt_all, nmax = 4, set = list(idp = .5))

maxint <- raster::interpolate(ras.aoi2, model=fit.p.ign) # this is pretty slow
plot(maxint, col=rev(heat.colors(255)))

# can I just do matrix maths on the rasters?



# ras.frt <- fasterize::fasterize (frt_all, prov.rast, field = "prob_ignition")
# plot(ras.frt)
# 
# plot(ras.aoi2)

writeRaster(maxint, file=" C:\\Work\\caribou\\castor_data\\Fire\\Fire_sim_data\\data\\Probability_of_Escape_Quesnell_WilliamsL_100Mile_allFRT_800m.tif", format="GTiff", overwrite=TRUE)

# run this in R:
paste0('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', 'C:/Work/caribou/castor_data/Fire/Fire_sim_data/data/Probability_of_Escape_Quesnell_WilliamsL_100Mile_allFRT_800m.tif -t 100x100 rast.prob_lightning_ignit_quesnel_williamsl_100mile | psql postgres://', keyring::key_get('dbuser', keyring = 'postgreSQL'), ':', keyring::key_get('dbpass', keyring = 'postgreSQL'), '@', keyring::key_get('dbhost', keyring = 'postgreSQL'), ':5432/castor')
# then copy the output thats between the " " from the above and paste it into the cmd and run that... should show Insert 0  1 lots of times.

```

Test whether fire map makes sense.
```{r}
library(raster)
library(fasterize)
library(sf)

head(x)
p1 <- rbind(x$Latitude, x$Longitude)

p1 <- list(p1)
pols <- st_sf(value = list(x$prob_ignition),
             geometry = st_sfc((p1), st_polygon))
r <- raster(pols, res = 1)
r <- fasterize(pols, r, field = "value", fun="sum")
plot(r)
```


