---
title: "FDW BCGW Data Extract: VRI"
output: html_document

---

## VRI data from BCGW 
## To Cloud PostgreSQl Server


Using Foreign Data Wrapper: oracle_fdw  

Processing AR2021 data.


make sure that the setup script has been run to set up the oracle connection 

## this will ignore geometry and has a reduced attribute list

Load date: `r Sys.Date()`

Start: `r format(Sys.time(),"%c")` 

Sequence:  

- load VRI from Oracle
- load tsa table from ARDATA: fids_ard_by_tsa_2021.csv
- load BEC data from CSV: bec11_vri_fid.csv
- load list of rasterized vri features: vri_rasterized_fid.csv






```{r cloud_connection, eval=TRUE,message=FALSE,warning=FALSE}

library(RPostgreSQL)
library(data.table)
library(tidyverse)

cloud <- '159.203.39.152'
database <- 'msyt'

con <- dbConnect('PostgreSQL',host=cloud,dbname=database)



```


create the msyt schema: msyt_2021  

```{sql pre_delete, eval=TRUE,connection=con,warning=FALSE}

-- create the schema for first load
create schema if not exists msyt_2021;


drop table if exists msyt_2021.veg_comp;
drop table if exists msyt_2021.veg_comp_from_fdw;


drop foreign table if exists load_2021.veg_comp_lyr_r1_poly;

select now();



```


update geometry columns

```{sql do_geom,eval=TRUE,connection=con,warning=FALSE}

select populate_geometry_columns();

select now();


```



### import the foreign schema and limit to VRI only

```{sql load_foreign_tables, eval=TRUE,connection=con}

-- FDW RESULTS data extract


import foreign schema "WHSE_FOREST_VEGETATION"
limit to (WHSE_FOREST_VEGETATION.VEG_COMP_LYR_R1_POLY)
FROM SERVER oradb_idwprod1 INTO load_2021;

-- set up pre fetch conditions
alter foreign table load_2021.veg_comp_lyr_r1_poly options (ADD prefetch '10240'); 


select count (*) from load_2021.veg_comp_lyr_r1_poly;

```


### extract VRI 

```{sql extract_vri, eval=TRUE,connection=con}


select now();

-- load the subset of attribution required
create table msyt_2021.veg_comp_from_fdw as select 
	feature_id,
	map_id,
	inventory_standard_cd,
	polygon_area,
	non_productive_descriptor_cd,
	non_productive_cd,
	input_date,
	bclcs_level_1,
	bclcs_level_2,
	bclcs_level_3,
	bclcs_level_4,
	bclcs_level_5,
	interpretation_date,
	project,
	reference_year,
	fiz_cd,
	for_mgmt_land_base_ind,
	projected_date,
	opening_id,
	adjusted_ind,
	--bec_zone_code as bec_zone,
	--bec_subzone,
	--bec_variant,
	--bec_phase,
	earliest_nonlogging_dist_type,
	earliest_nonlogging_dist_date,
	stand_percentage_dead,
	free_to_grow_ind,
	harvest_date,
	layer_id,
	for_cover_rank_cd,
	non_forest_descriptor,
	interpreted_data_src_cd,
	quad_diam_125,
	quad_diam_175,
	est_site_index_species_cd,
	est_site_index,
	est_site_index_source_cd,
	crown_closure,
	reference_date,
	site_index,
	dbh_limit,
	basal_area,
	vri_live_stems_per_ha,
	vri_dead_stems_per_ha,
	species_cd_1,
	species_pct_1,
	species_cd_2,
	species_pct_2,
	species_cd_3,
	species_pct_3,
	species_cd_4,
	species_pct_4,
	species_cd_5,
	species_pct_5,
	species_cd_6,
	species_pct_6,
	proj_age_1,
	proj_age_2,
	proj_height_1,
	proj_height_2,
	live_stand_volume_125,
	dead_stand_volume_125
from load_2021.veg_comp_lyr_r1_poly
;	



select count (*) from msyt_2021.veg_comp_from_fdw;


```

Load from Foreign Table Complete: `r format(Sys.time(),"%c")`



## Cast types after load

Oracle tends to use var char and other inefficient types.  
Cast these to text.   

```{sql update_veg_fid_types, eval=TRUE,connection=con}

-- rename loading table
alter table msyt_2021.veg_comp_from_fdw rename to veg_comp;

-- note that FDW load assigns feature as numeric
-- it should be cast to integer
alter table msyt_2021.veg_comp alter feature_id type integer;


-- change the var char to text
alter table msyt_2021.veg_comp alter map_id type text;
alter table msyt_2021.veg_comp alter inventory_standard_cd type text;
alter table msyt_2021.veg_comp alter non_productive_descriptor_cd type text;
alter table msyt_2021.veg_comp alter non_productive_cd type text;
alter table msyt_2021.veg_comp alter bclcs_level_1 type text;
alter table msyt_2021.veg_comp alter bclcs_level_2 type text;
alter table msyt_2021.veg_comp alter bclcs_level_3 type text;
alter table msyt_2021.veg_comp alter bclcs_level_4 type text;
alter table msyt_2021.veg_comp alter bclcs_level_5 type text;
alter table msyt_2021.veg_comp alter project type text;
alter table msyt_2021.veg_comp alter fiz_cd type text;
alter table msyt_2021.veg_comp alter for_mgmt_land_base_ind type text;
alter table msyt_2021.veg_comp alter adjusted_ind type text;
alter table msyt_2021.veg_comp alter earliest_nonlogging_dist_type type text;
alter table msyt_2021.veg_comp alter free_to_grow_ind type text;
alter table msyt_2021.veg_comp alter layer_id type text;
alter table msyt_2021.veg_comp alter for_cover_rank_cd type text;
alter table msyt_2021.veg_comp alter non_forest_descriptor type text;
alter table msyt_2021.veg_comp alter interpreted_data_src_cd type text;
alter table msyt_2021.veg_comp alter est_site_index_species_cd type text;
alter table msyt_2021.veg_comp alter est_site_index_source_cd type text;
alter table msyt_2021.veg_comp alter species_cd_1 type text;
alter table msyt_2021.veg_comp alter species_cd_2 type text;
alter table msyt_2021.veg_comp alter species_cd_3 type text;
alter table msyt_2021.veg_comp alter species_cd_4 type text;
alter table msyt_2021.veg_comp alter species_cd_5 type text;
alter table msyt_2021.veg_comp alter species_cd_6 type text;

-- change timestamp to text
alter table msyt_2021.veg_comp alter input_date type text;
alter table msyt_2021.veg_comp alter interpretation_date type text;
alter table msyt_2021.veg_comp alter projected_date type text;
alter table msyt_2021.veg_comp alter earliest_nonlogging_dist_date type text;
alter table msyt_2021.veg_comp alter harvest_date type text;
alter table msyt_2021.veg_comp alter reference_date type text;

update msyt_2021.veg_comp
set 
  input_date = substring(input_date,1,10),
  interpretation_date = substring(interpretation_date,1,10),
  projected_date = substring(projected_date,1,10),
  earliest_nonlogging_dist_date = substring(earliest_nonlogging_dist_date,1,10),
  harvest_date = substring(harvest_date,1,10),
  reference_date = substring(reference_date,1,10)
;
  

select count (*) from msyt_2021.veg_comp;


```


Type reset complete: `r format(Sys.time(),"%c")`



```{r eval=TRUE}

z <- dbDisconnect(con)

```


End: `r format(Sys.time(),"%c")`

