<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

---
title: "Database creation for Robson TSA BAU Analysis"
author: "Tyler Muhly"
date: "2 February 2023"
output: pdf_document
---

# Overview
-	Need timber supply impact analysis for the Central Selkirk, Groundhog, Columbia North and Wells Gray South herds
o	There are three ‘tiers’ or protection (scenarios) to model

-	Model at the timber management unit scale
o	TSA’s: Kamloops, Robson Valley, Golden, Revelstoke, TFL 55, TFL 56, Okanagan, TFL14, Arrow, Cascadia-Okanagan (TKO), TFL23, TFL14, Kootenay Lake



# Usage
Set parameters for creating the database in the code chunk below.

```{r module_usage}
library (SpaDES)
library (SpaDES.core)
library (data.table)
library (keyring)
library (terra)

source (here::here("R/functions/R_Postgres.R"))

Sys.setenv(JAVA_HOME = 'C:\\Program Files\\Java\\jdk-14.0.1') #throws an error if pointing to different version of java (i.e., 32 vs 64 bit)

moduleDir <- file.path (paste0 (here::here (), "/R/SpaDES-modules"))
inputDir <- file.path (paste0 (here::here (), "/R/scenarios/revelstoke_complex/inputs")) %>% reproducible::checkPath (create = TRUE)
outputDir <- file.path (paste0 (here::here (), "/R/scenarios/revelstoke_complex/outputs")) %>% reproducible::checkPath (create = TRUE)
cacheDir <- file.path (paste0 (here::here (), "/R/scenarios/revelstoke_complex"))

times <- list (start = 0, end = 0)

parameters <-  list (
        .progress = list (type = NA, interval = NA),
        .globals = list (),
        dataCastor = list(dbName = 'castor',
                          saveCastorDB = TRUE,
                          sqlite_dbname = "robson_bau", 
                          nameBoundaryFile = "public.tsa_aac_bounds", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = "Robson_Valley_TSA", 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "rast.tsa_aac_boundary", 
                          nameCompartmentTable = "vat.tsa_aac_bounds_vat", 
                          nameMaskHarvestLandbaseRaster = 'rast.thlb_2020', 
                          nameZoneRasters = c ("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_wha_2021", 
                                               "rast.zone_uwr_2021",  
                                               "rast.zone_cond_nharv", 
                                               "rast.zone_cond_fsw", 
                                               "rast.zone_cond_cw",
                                               "rast.zone_cond_bc_columbia_north_crithab",
                                               "rast.zone_cond_bc_groundhog_crithab",
                                               "rast.zone_cond_bc_wells_gray_south_crithab"),
                          nameZoneTable = "zone.constraints", 
                          # natural and managed stands yield curves are the same    
                          nameYieldsRaster = "rast.ycid_vdyp_2020", 
                          nameYieldTable = "yc_vdyp_2020", 
                          nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                          nameYieldTransitionTable = "tipsy_prov_2020",  
                          nameForestInventoryRaster = "rast.vri2020_id", 
                          nameForestInventoryKey = "feature_id", 
                          nameForestInventoryTable = "veg_comp_lyr_r1_poly2020",
                          nameForestInventoryAge = "proj_age_1",  
                          nameForestInventoryHeight = "proj_height_1",
                          nameForestInventoryCrownClosure = "crown_closure",                             
                          nameForestInventoryTreed = "bclcs_level_2",
                          nameForestInventoryBasalArea= "basal_area",
                          nameForestInventoryQMD = "quad_diam_125",
                          nameForestInventorySiteIndex = "site_index" 
                          ),
        growingStockCastor = list (periodLength = 5),
        blockingCastor = list(blockMethod = 'pre', 
                              patchZone = 'rast.zone_cond_beo',
                              patchVariation = 6,
                              nameCutblockRaster ="rast.cns_cut_bl",
                              useLandingsArea = FALSE),
        roadCastor = list (roadMethod = 'mst',
                           nameCostSurfaceRas = 'rast.rd_cost_surface',
                           nameRoads =  'rast.ce_road_2019'
                           ),
        survivalCastor = list (caribou_herd_density = 0.05, 
                               nameRasCaribouHerd = "rast.caribou_herd_20220725", 
                               tableCaribouHerd = "vat.caribou_herd_20220725"),
        smcpopCastor = list (nameRasSMCHerd = "rast.smc_herd_habitat", 
                             tableSMCCoeffs = "vat.smc_coeffs"),
        disturbanceCastor = list(calculateInterval =  1, 
                                 criticalHabitatTable = "vat.vat_bc_crithab_and_herd",
                                 criticalHabRaster = "rast.bc_crithab_and_herd",
                                 permDisturbanceRaster = "rast.mine_ag_wind_rail",
                                 recovery = 300), # no road recovery
        volumebyareaReportCastor = list (calculateInterval = 1,
                                         AreaofInterestRaster = "rast.bc_crithab_and_herd",
                                         AreaofInterestTable = "vat.vat_bc_crithab_and_herd"),
        uploadCastor = list(aoiName = 'revelstoke_complex_caribou',
                              dbInfo  = list(keyring::key_get("vmdbhost", keyring="postgreSQL"),
                                             keyring::key_get("vmdbuser", keyring="postgreSQL"),
                                             keyring::key_get("vmdbpass", keyring="postgreSQL"), 
                                             keyring::key_get("vmdbname", keyring="postgreSQL")))
        )

scenario = data.table (name = "load_data_robson_bau", description = "dataCastor output for Robson Valley TSA BAU")

modules <- list("dataCastor",
                "growingStockCastor",
                "blockingCastor", 
                "roadCastor",
                "survivalCastor",
                "smcpopCastor",
                "disturbanceCastor",
                "volumebyareaReportCastor",
                "uploadCastor")

objects <- list (scenario = scenario)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

inputs <- list()
outputs <- list()

mySim <- simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects,
                 paths = paths)

# outputs to keep; these are tables that get used in the uploader
outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "tableSurvival",
                                             "disturbanceReport",
                                             "volumebyareaReport",
                                             "tableAbundanceReport"))

system.time({
mysimout<-spades(mySim)
})

```

## Caclulate Some Diagnostics

```{r, Diagnostics}

db <- dbConnect(RSQLite::SQLite(), dbname = paste0(here::here(), "/R/scenarios/revelstoke_complex/robson_bau_castordb.sqlite"))

pixels <- data.table (dbGetQuery(db, "SELECT * FROM pixels;"))
thlb.area <- sum(pixels$thlb, na.rm = T) #  140,000 hectares
yields <- data.table (dbGetQuery(db, "SELECT * FROM yields;"))
yields [, mai := (tvol/age)]
max.yield <- yields [yields [, .I [which.max(mai)], by = yieldid]$V1]
yield.counts <- pixels  [, .(count = .N, count_thlb = sum (thlb, na.rm = T)), by = yieldid]
yield.counts <- merge (yield.counts, max.yield, by.x = "yieldid", by.y = "yieldid")
yield.counts [, total_vol := (mai*count_thlb)]
lrsy <- sum (yield.counts$total_vol)
yield.counts [, weight_vol := (tvol*(count_thlb/thlb.area))]
mean.vol.ha <- sum (yield.counts$weight_vol)
yield.counts [, weight_mai := (mai*(count_thlb/thlb.area))]
mean.mai <- sum (yield.counts$weight_mai)
hist (yield.counts[yield.counts$count_thlb > 0,]$mai)
```



