---
title: "fire_ignition_data_inspection"
author: "Cora Skaien"
date: "09/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#Overview
In this file, we assess the distribution of number of fires over time to create frequency distributions for number of fires that ignited and that escaped. Initially we do it all combined, but later we will also do it by BEC zone. We will bring in the data, similar to the ignition data prep, but this time we will keep more fire years than 2002 onwards. Here, we assess fire information from 1950-2020.

```{r}

library(raster)
library(data.table)
library(sf)
library(tidyverse)
library(rgeos)
library(bcmaps)
library(ggplot2)
require (RPostgreSQL)
require (rpostgis)
require (fasterize)
require (dplyr)
library(keyring)
library(stringi)

source(here::here("R/functions/R_Postgres.R"))
```

We will bring in the historic fire shape files with point data from BCGW (https://cat.data.gov.bc.ca/dataset/fire-perimeters-historical/resource/61de892c-09f4-4440-b18f-09995801558f).
Interestingly, the 2022 version of this file seems to have very few fires for which the cause is know and only fires after 2017 have any info for this. In the previous version I downloaded (2021) there was more of this data but the records for before 2010 seemed suspect because the number of fires were really low. I've emailed the curator about this and did not get a solution to these concerns, but hopefully the problems will be fixed and updated on BCGW! Will keep checking.

```{r}

# Raw fire ignition point data from BC:
# https://cat.data.gov.bc.ca/dataset/fire-perimeters-historical/resource/61de892c-09f4-4440-b18f-09995801558f


#ignition2<-st_read("C:\\Work\\caribou\\clus\\R\\fire_sim\\data\\bc_fire_ignition.shp")
ignit<-ignition2
```

Now, let's inspect some of the elements of this file.

```{r}
table(ignition2$FIRE_CAUSE3) # hmmm there are 1074 lightning caused fires, 960 human caused ones and 30043 unknown. I dont think I can filter this by the cause of fire. If I do I loose a TON of data! BAD!

ignition2$FIRE_CAUSE3<-as.factor(as.character(ignition2$FIRE_CAUSE3))
```


```{r}
##Check size of fires
min(ignition2$CURRENT_SIZE) # There are 123 zeros and 38 NA's

ignition_2<-subset(ignition2, ignit$CURRENT_SIZE!="NA")
min(ignition_2$CURRENT_SIZE)
table(ignition_2$CURRENT_SIZE)
table(ignition_2$FIRE_CAUSE) #Here, we have  20178 in lightning and 12530 in person
```

We want to extract the month for which the fire began so that we can match that specific MDC (monthly drought code) with that fire for modelling month to month.

```{r}
names(ignition2)
library(stringi)
ignition2$IGNITION_DATE
ignition2$ign_month<-stri_sub(ignition2$IGNITION_DATE,6,7)
head(ignition2)


```

Visualize by lightning and person caused fires

```{r}
counts<-table(ignition2$FIRE_YEAR, ignition2$FIRE_CAUSE)
counts

barplot(counts, beside = TRUE, legend = F)
```



#Now let's repeat for number of escaped fires

In Marchal et al. 2020, they define escape as "the probability that a fire will reach a size of at least 1 ha". We will inspect the ignition data and see the size of each fire. We will then separate them into those that are <1 ha in size, and those that are > 1 ha in size. From this, we can use logistic regression, including climate variables, topography (aspect and slope), and VRI data. Below currently only accounts for lightning caused fires. Human caused fires will be modelled down the road.

Note: Other papers use 3 ha (e.g., Wang et al. 2016, International Journal of Wildland Fire) and others use 10 ha (e.g., Parisien et al. 2013, Natural Hazards) for their definition of escape.

```{r}
#We will start with ignition_ file

ignition2$escape<- 0
ignition2$escape[ignition2$CURRENT_SIZE >= 1] <- 1

table(ignition2$escape) #We have 26541 that did not escape, and 7184 that did escape.

#Compare to a 3 ha threshold
ignition2$escape3<- 0
ignition2$escape3[ignition2$CURRENT_SIZE >= 3] <- 1

table(ignition2$escape3) #28875 that did not escape and 4850 that did.


#Compare to a 10 ha threshold
ignition2$escape10<- 0
ignition2$escape10[ignition2$CURRENT_SIZE >= 10] <- 1

table(ignition2$escape10) #30638 that did not escape and 3087 that did.

```
Create files for escaped fires at 1 ha, 3 ha and 10 ha
```{r}
escape_1ha<-subset(ignition2, ignition2$escape==1)
head(escape_1ha)

escape_3ha<-subset(ignition2, ignition2$escape3==1)
head(escape_3ha)

escape_10ha<-subset(ignition2, ignition2$escape10==1)
head(escape_10ha)

```

Visualize by lightning and person caused fires

```{r}
counts_1ha<-table(escape_1ha$FIRE_YEAR, escape_1ha$FIRE_CAUSE)
counts_1ha

barplot(counts_1ha, beside = TRUE, legend = F)
```
```{r}
counts_3ha<-table(escape_3ha$FIRE_YEAR, escape_3ha$FIRE_CAUSE3)

counts_3ha

barplot(counts_3ha, beside = TRUE, legend = TRUE)
```

```{r}
counts_10ha<-table(escape_10ha$FIRE_YEAR, escape_10ha$FIRE_CAUSE3)
counts_10ha

barplot(counts_10ha, beside = TRUE, legend = TRUE)
```


```{r}
##Make df to get dataframe
counts_1ha_df<-as.data.frame(counts_1ha)
counts_1ha_df

#Filter to get lightning and person caused separate
counts_1ha_lightning <- counts_1ha_df %>% 
  filter(Var2 == "Lightning")

hist(counts_1ha_lightning$Freq)

counts_1ha_person <- counts_1ha_df %>% 
  filter(Var2 == "Person")

hist(counts_1ha_person$Freq, xlim=c(0,600), breaks=3) #interestingly, this is more of a normal distribution than Poisson-like. 
# basically this shows that within a year there is a greater variation in the number of lightning caused fires in comparison the human caused ones.
```


```{r}
##Make df to get dataframe
counts_3ha_df<-as.data.frame(counts_3ha)
counts_3ha_df

#Filter to get lightning and person caused separate
counts_3ha_lightning <- counts_3ha_df %>% 
  filter(Var2 == "Lightning")

hist(counts_3ha_lightning$Freq, n=30)

counts_3ha_person <- counts_3ha_df %>% 
  filter(Var2 == "Person")

hist(counts_3ha_person$Freq) #interestingly, this is more of a normal distribution than Poisson-like. 
```


```{r}
##Make df to get dataframe
counts_10ha_df<-as.data.frame(counts_10ha)
counts_10ha_df

#Filter to get lightning and person caused separate
counts_10ha_lightning <- counts_10ha_df %>% 
  filter(Var2 == "Lightning")

hist(counts_10ha_lightning$Freq, n=20)

counts_10ha_person <- counts_10ha_df %>% 
  filter(Var2 == "Person")

hist(counts_10ha_person$Freq, n=10) #interestingly, this is more of a normal distribution than Poisson-like. 
```
```

