---
title: "09_2a_fire_ignition_model_selection_NDT1_person_treed"
author: "Cora Skaien"
date: "08/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (data.table)
library (DBI)
library (RPostgreSQL)
library (dplyr)
library (ggplot2)
library (here)
library(ggpubr)
library(arm)
library(tidyr)
library(AICcmodavg)
library(keyring)
library(caret)
library(pROC)
library(rje)
library(car)
library(visreg)

source(here::here("R/functions/R_Postgres.R"))
```

<!--
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

#=================================
#  Script Name: 09_2a_fire_ignition_model_selection_NDT1_person_treed.R
#  Script Version: 1.0
#  Script Purpose: Model selection, using various initial models to inform the final model selection.
#  Script Author: Cora Skaien, Ecological Modeling Specialist, Forest Analysis and Inventory Branch, B.C. Ministry of Forests, Lands, and Natural Resource Operations.
#=================================

#Load data back in if starting from here
Note: depending where your geometry column was located when saved as a csv (and turned into a dataframe), you may need to manually correct column headings on the csv file before loading back in. This has been performed for the below files.

```{r}
dat_person<-read.csv("C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\data\\Data_Person.csv")

head(dat_person)

table(dat_person$frt, dat_person$fire_cs)
```


######################### ANALYSES: TREED, PERSON #########################

Now, we will make a loop that does something very similar to our last loop, but with the selected climate variable plus other variables of interest. For person caused fires with trees, the variables of interest include:

1. Climate variable(s)
2. Projected Height (proj_height_1)
3. projected age (proj_age_1)  
4. live_stand_volume_125
5. vegtype2
6. slope
7. aspect_cos (cos)
8. elevation
9. Various distance to infrastructure variables (dist_mun, dist_dam, dist_nat, dist_pow, dist_mine, dist_any) - no interactions
10. roads_km

Variables to be added after initial model selection for next round model selection:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)

Interactions of interest: two-way interactions between climate (1) and vegtype2 (6); two-way interactions between topography measures (7-9); interactions between VRI variables.

This will be done separately for trees and non-treed areas. 

##We will do each loop separately for each NDT zone given the large number of possible models for each zone.

First we will create the variable lists that contain all of our variables of interest.


```{r}
##Create variable lists to be used in the model loop.
variables_all<-c(climate1 = "climate1", prj_h_1 = "prj_h_1", prj_g_1 = "prj_g_1", l___125 = "l___125", elevatn ="elevatn", vegtype = "vegtype", rd_dst_="rd_dst_", infr_ds="infr_ds") 

variables_all_c1<-c(climate1 = "climate1", prj_h_1 = "prj_h_1", prj_g_1 = "prj_g_1", l___125 = "l___125", elevatn ="elevatn", vegtype = "vegtype", rd_dst_="rd_dst_", infr_ds="infr_ds")  


vars.clim<-c("climate1")
vars.clim.vegtype<-c("climate1", "vegtype")
vars.veg.age<-c("prj_g_1", "vegtype")
vars.veg.height<- c("prj_h_1", "vegtype")
vars.veg.vol<- c("l___125", "vegtype")

vars.oth<-c("prj_h_1", "prj_g_1", "l___125") 
vars.topo<-c("elevatn")
vars.infra<-c("rd_dst_", "infr_ds")

##Create interaction for climate and vegtype
inputs.me <- c(vars.clim.vegtype)
inputs.me1 <- c(vars.veg.age)
inputs.me2 <- c(vars.veg.height)
inputs.me3 <- c(vars.veg.vol)


```

Now, we will generate two-way interactions for each of these lists. 

```{r}
#####1a. For those with one climate variable
#get the names of all possible two-way interactions for climate variable(s) and vegtype.
twoway.ints <- NULL
for (i in 1:(length(inputs.me)-1)) {
  for (j in (i+1):length(inputs.me)) {
     twoway.ints <- cbind(twoway.ints, paste(inputs.me[i], inputs.me[j], sep=":"))
  }
}
twoway.ints
length(twoway.ints)#1

twoway.ints1 <- NULL
for (i in 1:(length(inputs.me1)-1)) {
  for (j in (i+1):length(inputs.me1)) {
     twoway.ints1 <- cbind(twoway.ints1, paste(inputs.me1[i], inputs.me1[j], sep=":"))
  }
}
twoway.ints1
length(twoway.ints1)#1

twoway.ints2 <- NULL
for (i in 1:(length(inputs.me2)-1)) {
  for (j in (i+1):length(inputs.me2)) {
     twoway.ints2 <- cbind(twoway.ints2, paste(inputs.me2[i], inputs.me2[j], sep=":"))
  }
}
twoway.ints2
length(twoway.ints2)#1

twoway.ints3 <- NULL
for (i in 1:(length(inputs.me3)-1)) {
  for (j in (i+1):length(inputs.me3)) {
     twoway.ints3 <- cbind(twoway.ints3, paste(inputs.me3[i], inputs.me3[j], sep=":"))
  }
}
twoway.ints3
length(twoway.ints3)#1


#
#Create function to determine Powerset for any vector of variable names
## or use rje package
#powerSet <- function(x) {
#   z.list <- NULL
#   for(i in 1:length(x)) {
#      z.list <- append(z.list, combn(x, m=i, simplify=F))
#   }    
#   return(z.list)
#}


#Get variables on own
#complete list of models using non-climate vars
mods.me.tmp <- powerSet(vars.clim.vegtype) 
#add climate vars to all of the above
mods.me.climate <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.climate[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.climate
mods.me.climate<-mods.me.climate[-1]



#########2. Now for topography data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsT <- NULL
for (i in 1:(length(vars.topo)-1)) {
  for (j in (i+1):length(vars.topo)) {
     twoway.intsT <- cbind(twoway.intsT, paste(vars.topo[i], vars.topo[j], sep=":"))
  }
}
twoway.intsT
length(twoway.intsT) #3

#complete list of models using non-climate vars (topo)
mods.me.tmp <- powerSet(vars.topo) 
#add climate vars to all of the above
mods.meT <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meT[[i]] <- c(mods.me.tmp[[i]])
}

mods.meT
mods.meT<-mods.meT[-1]

#complete list of two-way interactions
mods.twowayT <- powerSet(twoway.intsT)
length(mods.twowayT) #8
mods.twowayT
mods.twowayT<-mods.twowayT[-1]

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interT <- list()
counter <- 0
for (i in 1: length(mods.twowayT)) {
   s1 <- unique(unlist( strsplit(mods.twowayT[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meT)) {
      if (all(s1 %in% mods.meT[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meT[[j]], mods.twowayT[[i]])
        mods.interT[[counter]] <- both
      }
   }
}

length(mods.interT) #10


####3.For other VRI data, get without interactions

#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.oth) 
#add climate vars to all of the above
mods.me.oth <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.me.oth[[i]] <- c(mods.me.tmp[[i]])
}

mods.me.oth
mods.me.oth<-mods.me.oth[-1]


#########4. Now for distance to infrastructure data, get all possible two-way interactions

#get the names of all possible two-way interactions
twoway.intsI <- NULL
for (i in 1:(length(vars.infra)-1)) {
  for (j in (i+1):length(vars.infra)) {
     twoway.intsI <- cbind(twoway.intsI, paste(vars.infra[i], vars.infra[j], sep=":"))
  }
}
twoway.intsI
length(twoway.intsI)

#complete list of models using non-climate vars (infra)
mods.me.tmp <- powerSet(vars.infra) 
#add climate vars to all of the above
mods.meI <- list()
for (i in 1: length(mods.me.tmp)) {
   mods.meI[[i]] <- c(mods.me.tmp[[i]])
}

mods.meI
mods.meI<-mods.meI[-1]

#complete list of two-way interactions
mods.twowayI <- powerSet(twoway.intsI)
length(mods.twowayI) #32
#mods.twowayI

#Finding models in mods.me that accommodate/allow interaction terms in each mods.twoway to be added

mods.interI <- list()
counter <- 0
for (i in 1: length(mods.twowayI)) {
   s1 <- unique(unlist( strsplit(mods.twowayI[[i]], split=':', fixed=TRUE) ) )
   for (j in 1: length(mods.meI)) {
      if (all(s1 %in% mods.meI[[j]])==TRUE) {
        counter <- counter + 1
        both <-  c(mods.meI[[j]], mods.twowayI[[i]])
        mods.interI[[counter]] <- both
      }
   }
}

length(mods.interI) #274
#mods.interI

#the list of all possible model RHSs. 
#all.poss.mods <- c(1, vars.clim, twoway.ints, mods.me.oth, mods.me2, mods.inter2)
#all.poss.mods

all.poss.mods.clim.vegtype<-c(1, mods.me.climate, twoway.ints)
all.poss.mods.clim.vegtype 

all.poss.mods.VRI<-c(1, mods.me.oth)
all.poss.mods.VRI

all.poss.mods.topo<-c(1, mods.meT, mods.interT)
all.poss.mods.topo[-3]

all.poss.mods.infra<-c(1, mods.meI, mods.interI) 
all.poss.mods.infra
```


```{r}
#If need to determine which ones are character(0), try this:
biglist <- list(list("A","B","C"), "foo", "", character(0), integer(0))
lapply(biglist, function(x) {length(x) == 0L} ) 


##Check and rid of any duplicated models
duplicated(all.poss.mods.clim.vegtype) #None duplicated
duplicated(all.poss.mods.VRI)
duplicated(all.poss.mods.topo)
duplicated(all.poss.mods.infra)

```

############### Model Series: Person Caused Fires, Trees ##########

Because of the large number of models with all variables included, we will test the climate and vegtype first, then the VRI variables, then the topography variables. Then we will test the top models together in additional combinations, with determining best AIC model from there. 

Select NDT: NDT1
- climate1 and climate2 present

```{r}
dat_person_t<- dat_person %>% filter(bclc__2=="T")
dat_person_t$fire_veg<-paste(dat_person_t$fire, dat_person_t$vegtype)



zones1<-c("7") #Do one zone at a time
prop<-0.75

#Create empty table
table.glm.climate.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.climate.simple) <- c ("model", "edf", "aic", "auc.valid", "FRT")

########### 1. Climate and vegtype ############
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_person_t %>% dplyr::filter(frt ==zones1[h])
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.clim.vegtype[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.clim.vegtype, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.climate <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.climate$FRT<-c("FRT3")
tab.sum.climate 

table.glm.climate.simple<-rbind(table.glm.climate.simple, tab.sum.climate)

}
}
}


```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.climate.simple)
table(table.glm.climate.simple$model) # 100 per model

AIC_person_NDT1_fire_pres_treed_climate<-table.glm.climate.simple

AIC_person_NDT1_fire_pres_treed_summary_climate<- AIC_person_NDT1_fire_pres_treed_climate %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT1_fire_pres_treed_summary_climate2<- AIC_person_NDT1_fire_pres_treed_summary_climate %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT1_fire_pres_treed_summary_climate2)
```

#Now repeat for VRI data

```{r}
########### 2. VRI ############
#Create empty table
table.glm.VRI.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.VRI.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

####
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_person_t %>% dplyr::filter(frt ==zones1[h])
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.VRI[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.VRI, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.VRI <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.VRI$FRT<-c("FRT3")
tab.sum.VRI 

table.glm.VRI.simple<-rbind(table.glm.VRI.simple, tab.sum.VRI)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.VRI.simple)
table(table.glm.VRI.simple$model) # 100 per model

AIC_person_NDT1_fire_pres_treed_VRI<-table.glm.VRI.simple

AIC_person_NDT1_fire_pres_treed_summary_VRI<- AIC_person_NDT1_fire_pres_treed_VRI %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT1_fire_pres_treed_summary_VRI2<- AIC_person_NDT1_fire_pres_treed_summary_VRI %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT1_fire_pres_treed_summary_VRI2)
```

#Now repeat for topography

```{r}
########### 3. topo ############
#Create empty table
table.glm.topo.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.topo.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_person_t %>% dplyr::filter(frt ==zones1[h])
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.topo, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$FRT<-c("FRT3")
tab.sum.topo 

table.glm.topo.simple<-rbind(table.glm.topo.simple, tab.sum.topo)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.topo.simple)
table(table.glm.topo.simple$model) # 100 per model

AIC_person_NDT1_fire_pres_treed_topo<-table.glm.topo.simple

AIC_person_NDT1_fire_pres_treed_summary_topo<- AIC_person_NDT1_fire_pres_treed_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT1_fire_pres_treed_summary_topo2<- AIC_person_NDT1_fire_pres_treed_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT1_fire_pres_treed_summary_topo2)
```

#Now repeat for infrastructure

```{r}
########### 4. Distance to Infrastructure ############
#Create empty table
table.glm.infra.simple <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.infra.simple) <- c ("model", "edf", "aic", "auc.valid", "NDT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_person_t %>% dplyr::filter(frt ==zones1[h])
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods.infra[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods.infra, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.infra <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.infra$FRT<-c("FRT3")
tab.sum.infra 

table.glm.infra.simple<-rbind(table.glm.infra.simple, tab.sum.infra)

}
}
}
```

Now that we have run the model 100 times, we want the average AIC and AUC for each variable combination.

```{r}
head(table.glm.infra.simple)
table(table.glm.infra.simple$model) # 100 per model

AIC_person_NDT1_fire_pres_treed_infra<-table.glm.infra.simple

AIC_person_NDT1_fire_pres_treed_summary_infra<- AIC_person_NDT1_fire_pres_treed_infra %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_person_NDT1_fire_pres_treed_summary_infra2<- AIC_person_NDT1_fire_pres_treed_summary_infra %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

head(AIC_person_NDT1_fire_pres_treed_summary_infra2)

```

#Now combine the datatables and save to computer

```{r}
NDT1_l_models_treed<-rbind(AIC_person_NDT1_fire_pres_treed_summary_climate2, AIC_person_NDT1_fire_pres_treed_summary_VRI2, AIC_person_NDT1_fire_pres_treed_summary_topo2, AIC_person_NDT1_fire_pres_treed_summary_infra2)
NDT1_l_models_treed
NDT1_l_models_treed$NDT<-"NDT1"

write.csv(NDT1_l_models_treed, file="D:\\Fire\\fire_data\\raw_data\\NDT1_person_models_treed_ignition.csv")
```


################################ STAGE TWO ########################

#STAGE TWO: PUT TOGETHER MORE VARIABLES
Now choose the top variables and create final model. The below code will need to be updated manually, depending on what the results of the above analyses are. From the top models, we will re-create two-way interactions for the variables selected from each model, plus the other variables listed as needed to be included. We will assess each set to ensure only interactions that make sense are investigated ultimately, given that sample sizes will be an issues.

Top Models:
1. climate1 + climate2 + vegtype2 + climate1:climate2 + climate1:vegtype2
2. proj_height_1 + proj_age_1 + live_stand_volume_125
3. slope + aspect_cos + elevation + aspect_cos:elevation
4. dist_mun + dist_dam + dist_nat + dist_pow + roads_km + dist_pow:roads_km

Additional Variables:
1. bclcs_level_5_2 (land use) (to be added to final investigated model)

Additional interactions:
1. elevation:climate1
2. elevation:climate2
3. bclcs_level_5_2:roads_km


```{r}

zones1 <- 15
vars.all<-c("climate1", "vegtype", "prj_h_1", "prj_g_1", "l___125", "elevatn","infr_ds", "rd_dst_")
#complete list of models using VRI - no interactions
mods.me.tmp <- powerSet(vars.all) 

# not sure this next peice of code is neccessary
all.poss.mods <- list()
for (i in 1: length(mods.me.tmp)) {
   all.poss.mods[[i]] <- c(mods.me.tmp[[i]])
}

all.poss.mods<-all.poss.mods[-1]


table.glm.all <- data.frame (matrix (ncol = 5, nrow = 0))
colnames (table.glm.all) <- c ("model", "edf", "aic", "auc.valid", "FRT")

#
for (g in 1:100){

for (h in 1:length(zones1)) {
  dat2<- dat_person_t %>% dplyr::filter(frt ==zones1[h] )#& vegtype!="D") # had to remove disturbed locations because there are too few of them
  
#for (i in 1: length(all.poss.mods.topo)){
#  print(paste((all.poss.mods.topo[i]), (zones1[h]), sep=" "))
  
for (i in 1: length(zones1)){
  print(paste((all.poss.mods[i]), (zones1[h]), sep=" "))
  
 # model_dat<- dat2 %>% dplyr::select(fire_pres, fire_veg, variables_all[i])
  model_dat<- dat2 %>% dplyr::select(fire, fire_veg, !!variables_all)
  model_dat<-drop_na(model_dat)

  # Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(model_dat$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- model_dat[ trainIndex,]
   Valid <- model_dat[-trainIndex,]

big.mod <- function(mods.in, df.train, df.test, dep.var="fire") {
   rhs <- paste(mods.in, collapse=" + ")
   form <- as.formula(paste(noquote(dep.var), " ~", rhs))
   mods.fit <- glm(form, family=binomial, data=df.train)
   mod.stuff <- summary(mods.fit)
   mod.aic <- extractAIC(mods.fit)
   mod.valid <- predict.glm(mods.fit, newdata=df.test, type="response")
   roc_obj <- roc(df.test[,dep.var], mod.valid)
   mod.auc <- auc(roc_obj)
   return(list(rhs, mod.stuff, mod.aic, mod.auc))
   
}

mods.fit <- lapply(all.poss.mods, big.mod, df.train=dat1, df.test=Valid)

#terms in each model
x1.1 <- unlist(sapply(mods.fit, '[', 1))
x1.1
#Aic for models
x3.1 <- matrix(unlist(sapply(mods.fit, '[', 3)), ncol=2, byrow=TRUE)
x3.1
#auc from validation data
x4.1 <- unlist(sapply(mods.fit, '[', 4))
x4.1
#combining all as df
tab.sum.topo <- cbind.data.frame(model=x1.1, edf=x3.1[,1], aic=x3.1[,2], auc.valid=x4.1)
tab.sum.topo$FRT<-c("FRT11")
tab.sum.topo 

table.glm.all<-rbind(table.glm.all, tab.sum.topo)

}
}
}

```

```{r}
head(table.glm.all)
table(table.glm.all$model) # 100 per model

AIC_lightning_NDT1_t_ignitereed_topo<-table.glm.all

AIC_lightning_NDT1_t_ignitereed_summary_topo<- AIC_lightning_NDT1_t_ignitereed_topo %>%
  group_by(model) %>%
  summarise(meanAIC=mean(aic),
            meanAUC=mean(auc.valid),
            sdAUC=sd(auc.valid),
            )

AIC_lightning_NDT1_t_ignitereed_summary_topo2<- AIC_lightning_NDT1_t_ignitereed_summary_topo %>%
  mutate(deltaAIC=meanAIC-min(meanAIC))

AIC_lightning_t <- AIC_lightning_NDT1_t_ignitereed_summary_topo2 %>%                 # Order table with dplyr
  as.data.frame() %>% 
  arrange((deltaAIC))
AIC_lightning_t     

```


Save.
```{r}
write.csv(AIC_lightning_t, file="C:\\Work\\caribou\\clus_data\\Fire\\Fire_sim_data\\out\\model_results_person_treed\\table.glm.FRT_15_ALL.csv")
```


```{r}
Anova(model.NDT1, type=3)
Anova(model.NDT1, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT1), 
            residuals(model.NDT1), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT1_ignition_t$resids<-resid(model.NDT1)

binnedplot (NDT1_ignition_t$live_stand_volume_125, 
            NDT1_ignition_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT1_ignition_t$climate1, 
            NDT1_ignition_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good

#Partial Residuals
library(visreg)
#climate1 + climate2 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + elevation + slope:elevation + dist_mun + dist_dam + roads_km + elevation*climate1 + elevation*climate2 + aspect_cos + aspect_cos:elevation

visreg(model.NDT1, "climate1", by="elevation")
visreg(model.NDT1, "climate2", by="elevation")

visreg(model.NDT1, "vegtype2")
visreg(model.NDT1, "vegtype2", ylim=c(-10,10))
visreg(model.NDT1, "vegtype2", ylim=c(-20,20))

visreg(model.NDT1, "proj_height_1")
visreg(model.NDT1, "proj_age_1")
visreg(model.NDT1, "live_stand_volume_125")

visreg(model.NDT1, "slope", by="elevation")
visreg(model.NDT1, "aspect_cos", by="elevation")
visreg(model.NDT1, "elevation", by="aspect_cos")
visreg(model.NDT1, "elevation", by="slope")
visreg(model.NDT1, "elevation", by="climate1")
visreg(model.NDT1, "elevation", by="climate2")

visreg(model.NDT1, "dist_mun")
visreg(model.NDT1, "dist_dam")
visreg(model.NDT1, "roads_km")

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT1)

#Create a new blank table and get AUC too
top_mod_table_NDT1_person_t_ALL <- data.frame (matrix (ncol = 25, nrow = 0))
colnames (top_mod_table_NDT1_person_t_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtype2OP", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_proj_height_1", "coef_proj_age_1", "coef_live_stand_volume_125", "coef_slope", "coef_elevation", "coef_dist_mun", "coef_dist_dam", "coef_roads_km", "coef_aspect_cos", "coef_slope:elevation", "coef_climate1:elevation", "coef_climate2:elevation", "coef_elevation:aspect_cos", "AUC")
```
Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT1_ignition_t$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT1_ignition_t[ trainIndex,]
   Valid <- NDT1_ignition_t[-trainIndex,]
   
#Model   
model.NDT1<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + elevation + slope:elevation + dist_mun + dist_dam + roads_km + elevation*climate1 + elevation*climate2 + aspect_cos + aspect_cos:elevation, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT1, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT1_person_t <- data.frame (matrix (ncol = 25, nrow = 0))
colnames (top_mod_table_NDT1_person_t ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtype2OP", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_proj_height_1", "coef_proj_age_1", "coef_live_stand_volume_125", "coef_slope", "coef_elevation", "coef_dist_mun", "coef_dist_dam", "coef_roads_km", "coef_aspect_cos", "coef_slope:elevation", "coef_climate1:elevation", "coef_climate2:elevation", "coef_elevation:aspect_cos", "AUC")

##Add data for NDT1
top_mod_table_NDT1_person_t[1,1]<-"person"
top_mod_table_NDT1_person_t[1,2]<-"NDT1"
top_mod_table_NDT1_person_t[1,3]<-"Y"
top_mod_table_NDT1_person_t[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + elevation + slope:elevation + dist_mun + dist_dam + roads_km + elevation*climate1 + elevation*climate2 + aspect_cos + aspect_cos:elevation" 
top_mod_table_NDT1_person_t[1,5]<- coef(model.NDT1)[1] #Intercept
top_mod_table_NDT1_person_t[1,6]<- coef(model.NDT1)[2] #Climate variable 1
top_mod_table_NDT1_person_t[1,7]<- coef(model.NDT1)[3] #Climate variable 2
top_mod_table_NDT1_person_t[1,8]<- coef(model.NDT1)[4] #
top_mod_table_NDT1_person_t[1,9]<- coef(model.NDT1)[5]
top_mod_table_NDT1_person_t[1,10]<- coef(model.NDT1)[6]
top_mod_table_NDT1_person_t[1,11]<- coef(model.NDT1)[7]
top_mod_table_NDT1_person_t[1,12]<- coef(model.NDT1)[8]
top_mod_table_NDT1_person_t[1,13]<- coef(model.NDT1)[9]
top_mod_table_NDT1_person_t[1,14]<- coef(model.NDT1)[10]
top_mod_table_NDT1_person_t[1,15]<- coef(model.NDT1)[11]
top_mod_table_NDT1_person_t[1,16]<- coef(model.NDT1)[12]
top_mod_table_NDT1_person_t[1,17]<- coef(model.NDT1)[13]
top_mod_table_NDT1_person_t[1,18]<- coef(model.NDT1)[14]
top_mod_table_NDT1_person_t[1,19]<- coef(model.NDT1)[15]
top_mod_table_NDT1_person_t[1,20]<- coef(model.NDT1)[16]
top_mod_table_NDT1_person_t[1,21]<- coef(model.NDT1)[17]
top_mod_table_NDT1_person_t[1,22]<- coef(model.NDT1)[18]
top_mod_table_NDT1_person_t[1,23]<- coef(model.NDT1)[19]
top_mod_table_NDT1_person_t[1,24]<- coef(model.NDT1)[20]
top_mod_table_NDT1_person_t[1,25]<- mod.auc

top_mod_table_NDT1_person_t_ALL<-rbind(top_mod_table_NDT1_person_t_ALL, top_mod_table_NDT1_person_t)

}

```

Check.
```{r}
head(top_mod_table_NDT1_person_t_ALL)
```
#Save coefficient table

```{r}
write.csv(top_mod_table_NDT1_person_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_person_t_ALL.csv")
```

#Get Mean Values

```{r}
names(top_mod_table_NDT1_person_t_ALL)

top_mod_table_NDT1_ignite_person_means<-top_mod_table_NDT1_person_t_ALL %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table_NDT1_ignite_person_means

top_mod_table_NDT1_ignite_person_means[1,1]<-"person"
top_mod_table_NDT1_ignite_person_means[1,2]<-"NDT1"
top_mod_table_NDT1_ignite_person_means[1,3]<-"Treed"
top_mod_table_NDT1_ignite_person_means[1,4]<- "fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + elevation + slope:elevation + dist_mun + dist_dam + roads_km + elevation*climate1 + elevation*climate2 + aspect_cos + aspect_cos:elevation" 
top_mod_table_NDT1_ignite_person_means
```
Save table.

```{r}
write.csv(top_mod_table_NDT1_ignite_person_means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_ignite_person_means.csv")
```

Standard deviation.

```{r}
top_mod_table_NDT1_ignite_person_sd<-top_mod_table_NDT1_person_t_ALL %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT1_ignite_person_sd

top_mod_table_NDT1_ignite_person_sd[1,1]<-"person"
top_mod_table_NDT1_ignite_person_sd[1,2]<-"NDT1"
top_mod_table_NDT1_ignite_person_sd[1,3]<-"Treed"
top_mod_table_NDT1_ignite_person_sd[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + elevation + slope:elevation + dist_mun + dist_dam + roads_km + elevation*climate1 + elevation*climate2 + aspect_cos + aspect_cos:elevation" 
top_mod_table_NDT1_ignite_person_sd
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT1_ignite_person_sd, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_ignite_person_sd.csv")
```

#Repeat above process with reduced variables

```{r}
ignition_person_t_NDT1<-subset(dat_person_t, dat_person_t$ntrl_ds=="NDT1")

#Divide data into training and valid
prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(ignition_person_t_NDT1$fire_pres, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- ignition_person_t_NDT1[ trainIndex,]
   Valid <- ignition_person_t_NDT1[-trainIndex,]

#Run model using dat1
model.NDT1<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 + climate1:vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1 + elevation*climate2, family = binomial, data = dat1)

AIC(model.NDT1) #2286.6

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.81 --> good fit!
   
Anova(model.NDT1, type=3)
Anova(model.NDT1, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT1<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 + climate1:vegtype2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1, family = binomial, data = dat1)

AIC(model.NDT1) #2285.8

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.81 --> good fit!
   
Anova(model.NDT1, type=3)
Anova(model.NDT1, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT1<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 + proj_height_1 + proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1, family = binomial, data = dat1)

AIC(model.NDT1) #2283.6

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.81 --> good fit!
   
Anova(model.NDT1, type=3)
#Anova(model.NDT1, type=3, singular.ok = TRUE)

#Remove least significant
model.NDT1<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 +  proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1, family = binomial, data = dat1)

AIC(model.NDT1) #2282.8

#Determine AUC of full model
mod.valid <- predict.glm(model.NDT1, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)
   mod.auc #0.81 --> good fit!
   
Anova(model.NDT1, type=3)
#Anova(model.NDT1, type=3, singular.ok = TRUE)


```

Remove NAs and run multiple times.

```{r}
#Remove NAs to ensure all same data used so we can compare AICs
NDT1_ignition_t<-ignition_person_t_NDT1 %>% drop_na(climate1, climate2, vegtype2, live_stand_volume_125, proj_age_1, dist_infra, roads_km, slope, elevation, aspect_cos)

#Assess vegtype
table(NDT1_ignition_t$vegtype2) #1 OP: remove
NDT1_ignition_t<-subset(NDT1_ignition_t, NDT1_ignition_t$vegtype2!="OP")

#Run Model again with this data; but uses all data here
model.NDT1<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 +  proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1, family = binomial, data = NDT1_ignition_t) 

AIC(model.NDT1) #3057.2
Anova(model.NDT1, type=3)
#Anova(model.NDT1, type=3, singular.ok = TRUE)

# model diagnostic plots
binnedplot (fitted(model.NDT1), 
            residuals(model.NDT1), 
            nclass = NULL, 
            xlab = "Expected Values", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))


NDT1_ignition_t$resids<-resid(model.NDT1)

binnedplot (NDT1_ignition_t$live_stand_volume_125, 
            NDT1_ignition_t$resids, 
            nclass = NULL, 
            xlab = "live stand volume", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

binnedplot (NDT1_ignition_t$climate1, 
            NDT1_ignition_t$resids, 
            nclass = NULL, 
            xlab = "", 
            ylab = "Average residual", 
            main = paste("Binned Residual Plot - glm", i))

# Diagnostic plots look good

#Partial Residuals
library(visreg)
#climate1 + climate2 + vegtype2 + climate1:climate2 +  proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1

visreg(model.NDT1, "climate1", by="elevation")
visreg(model.NDT1, "climate1", by="climate2")
visreg(model.NDT1, "climate2", by="climate1")

visreg(model.NDT1, "vegtype2")

visreg(model.NDT1, "proj_age_1")
visreg(model.NDT1, "live_stand_volume_125")

visreg(model.NDT1, "slope", by="elevation")
visreg(model.NDT1, "aspect_cos")
visreg(model.NDT1, "elevation", by="slope")
visreg(model.NDT1, "elevation", by="climate1")

visreg(model.NDT1, "dist_infra", by="roads_km")
visreg(model.NDT1, "roads_km", by="dist_infra")

```

We should repeat the above several times and take the mean of the coefficients.

```{r}
summary(model.NDT1)

#Create a new blank table and get AUC too
top_mod_table_NDT1_person_t_ALL <- data.frame (matrix (ncol = 22, nrow = 0))
colnames (top_mod_table_NDT1_person_t_ALL ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_proj_age_1", "coef_live_stand_volume_125", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_dist_infra", "coef_roads_km", "coef_climate1:climate2", "coef_slope:elevation", "coef_dist_infra:roads_km", "coef_climate1:elevation", "AUC")
```
Let's run it 500 times to get good mean values.

```{r}

for (g in 1:500){

prop<-0.75
# Creating training and testing datasets so that I can get a measure of how well the model actually predicts the data e.g. AUG
  trainIndex <- createDataPartition(NDT1_ignition_t$fire_veg, p = prop,
                                    list = FALSE,
                                    times = 1)
  
   dat1 <- NDT1_ignition_t[ trainIndex,]
   Valid <- NDT1_ignition_t[-trainIndex,]
   
#Model   
model.NDT1<-glm(fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 +  proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1, family = binomial, data = dat1) 

mod.valid <- predict.glm(model.NDT1, newdata=Valid, type="response")
   roc_obj <- roc(Valid[,"fire_pres"], mod.valid)
   mod.auc <- auc(roc_obj)

# create model table (only do this once) and add the relevant data
top_mod_table_NDT1_person_t <- data.frame (matrix (ncol = 22, nrow = 0))
colnames (top_mod_table_NDT1_person_t ) <- c ("CAUSE", "NDT", "TREED", "Model_terms", "intercept", "coef_climate_1", "coef_climate_2", "coef_vegtype2TB", "coef_vegtype2TC", "coef_vegtype2TM", "coef_proj_age_1", "coef_live_stand_volume_125", "coef_slope", "coef_aspect_cos", "coef_elevation", "coef_dist_infra", "coef_roads_km", "coef_climate1:climate2", "coef_slope:elevation", "coef_dist_infra:roads_km", "coef_climate1:elevation", "AUC")

##Add data for NDT1
top_mod_table_NDT1_person_t[1,1]<-"person"
top_mod_table_NDT1_person_t[1,2]<-"NDT1"
top_mod_table_NDT1_person_t[1,3]<-"Y"
top_mod_table_NDT1_person_t[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 +  proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1" 
top_mod_table_NDT1_person_t[1,5]<- coef(model.NDT1)[1] #Intercept
top_mod_table_NDT1_person_t[1,6]<- coef(model.NDT1)[2] #Climate variable 1
top_mod_table_NDT1_person_t[1,7]<- coef(model.NDT1)[3] #Climate variable 2
top_mod_table_NDT1_person_t[1,8]<- coef(model.NDT1)[4] #
top_mod_table_NDT1_person_t[1,9]<- coef(model.NDT1)[5]
top_mod_table_NDT1_person_t[1,10]<- coef(model.NDT1)[6]
top_mod_table_NDT1_person_t[1,11]<- coef(model.NDT1)[7]
top_mod_table_NDT1_person_t[1,12]<- coef(model.NDT1)[8]
top_mod_table_NDT1_person_t[1,13]<- coef(model.NDT1)[9]
top_mod_table_NDT1_person_t[1,14]<- coef(model.NDT1)[10]
top_mod_table_NDT1_person_t[1,15]<- coef(model.NDT1)[11]
top_mod_table_NDT1_person_t[1,16]<- coef(model.NDT1)[12]
top_mod_table_NDT1_person_t[1,17]<- coef(model.NDT1)[13]
top_mod_table_NDT1_person_t[1,18]<- coef(model.NDT1)[14]
top_mod_table_NDT1_person_t[1,19]<- coef(model.NDT1)[15]
top_mod_table_NDT1_person_t[1,20]<- coef(model.NDT1)[16]
top_mod_table_NDT1_person_t[1,21]<- coef(model.NDT1)[17]
top_mod_table_NDT1_person_t[1,22]<- mod.auc

top_mod_table_NDT1_person_t_ALL<-rbind(top_mod_table_NDT1_person_t_ALL, top_mod_table_NDT1_person_t)

}

```

Check.
```{r}
head(top_mod_table_NDT1_person_t_ALL)
```
#Save coefficient table

```{r}
write.csv(top_mod_table_NDT1_person_t_ALL, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_person_t_ALL_Jan.csv")
```

#Get Mean Values

```{r}
names(top_mod_table_NDT1_person_t_ALL)

top_mod_table_NDT1_ignite_person_means<-top_mod_table_NDT1_person_t_ALL %>% summarise_each(funs( mean( .,na.rm = TRUE)))
top_mod_table_NDT1_ignite_person_means

top_mod_table_NDT1_ignite_person_means[1,1]<-"person"
top_mod_table_NDT1_ignite_person_means[1,2]<-"NDT1"
top_mod_table_NDT1_ignite_person_means[1,3]<-"Treed"
top_mod_table_NDT1_ignite_person_means[1,4]<- "fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 +  proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1" 
top_mod_table_NDT1_ignite_person_means
```
Save table.

```{r}
write.csv(top_mod_table_NDT1_ignite_person_means, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_ignite_person_means_Jan.csv")
```

Standard deviation.

```{r}
top_mod_table_NDT1_ignite_person_sd<-top_mod_table_NDT1_person_t_ALL %>% summarise_each(funs( sd( .,na.rm = TRUE)))
top_mod_table_NDT1_ignite_person_sd

top_mod_table_NDT1_ignite_person_sd[1,1]<-"person"
top_mod_table_NDT1_ignite_person_sd[1,2]<-"NDT1"
top_mod_table_NDT1_ignite_person_sd[1,3]<-"Treed"
top_mod_table_NDT1_ignite_person_sd[1,4]<-"fire_pres ~ climate1 + climate2 + vegtype2 + climate1:climate2 +  proj_age_1 + live_stand_volume_125 + slope + aspect_cos + elevation + slope:elevation + dist_infra + roads_km + dist_infra:roads_km + elevation*climate1" 
top_mod_table_NDT1_ignite_person_sd
```

Save sd coefficient table.

```{r}
write.csv(top_mod_table_NDT1_ignite_person_sd, file="D:\\Fire\\fire_data\\raw_data\\top_mod_table_NDT1_ignite_person_sd_Jan.csv")
```

