---
title: "cutblockSeqPrepCLUS"
author: ""
date: "06 Dec 2022"
output: pdf_document
---
```{r, eval =FALSE}
# Copyright 2022 Province of British Columbia
# 
# Licensed under the Apache License, Version 2.0 (the "License");
# you may not use this file except in compliance with the License.
# You may obtain a copy of the License at
# 
# http://www.apache.org/licenses/LICENSE-2.0
# 
# Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
# See the License for the specific language governing permissions and limitations under the License.
#===========================================================================================
```
# Overview

The cutblockSeqPrep uses a defined area to grab the spatial locations of cutblocks that have been harvested over the past 50 years in BC.

# Usage

```{r module_usage}
library(igraph)
library(SpaDES.core)

source("C:/Users/KLOCHHEA/clus/R/functions/R_Postgres.R")

moduleDir <- file.path("C:/Users/KLOCHHEA/clus/R/SpaDES-modules")
inputDir <- file.path(moduleDir, "inputs") %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(moduleDir, "outputs")
cacheDir <- file.path(outputDir, "cache")
times <- list(start = 0, end = 10)
parameters <- list(
  cutblockSeqPrepCLUS = list(startHarvestYear = 1970,
                             nameCutblockRaster= 'rast.cns_cut_bl', 
                             nameCutblockTable= 'cns_cut_bl_polygon', 
                             queryCutblocks = 'cutseq_centroid',
                             resetAge = T # if True, converts road age and status from it's time sequence of simulation (e.g., simulated in year 1, 2, 3 etc.) to the time since the road was created or used (i.e., end time - roadyear and end time - roadstatus) which inverts the sequence (e.g., road was built 3, 2, 1 years ago)
                              )
)
modules <- list("cutblockSeqPrepCLUS")
objects <- list()
paths <- list(
  cachePath = cacheDir,
  modulePath = moduleDir,
  inputPath = inputDir,
  outputPath = outputDir
)

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects, paths = paths)

mySimOut<-spades(mySim)
eventDiagram(mySimOut)
```

# Events

The module queries the consolidated cutblocks data set that is stored within a postgres database

# Data dependencies

Boundary information - namely the file name, the column to query, the name of the boudary within the column and geometry name

## Input data

https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks-

## Output data

Produces a result set of cutblock schedules based on historic accounts

# Links to other modules

Links to dataLoaderCLUS to set up database connectivity

