---
title: "Review of Wolf Density Models and Moose Density and Habtiat Thresholds Needed to Achieve Low Predation on Caribou"
author: "Tyler Muhly"
date: "07/08/2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Federal recovery strategies for caribou have recommended wolf density thresholds for certain types of critical habitat. Specifcally, a threshold of less than 3 wolves per 1000 km ^2^ has been recommended for some southern moutnain cariobu 'matrix' habtiat types ([Environment Canada 2014](https://www.registrelep-sararegistry.gc.ca/virtual_sara/files/plans/rs_woodland_caribou_bois_s_mtn_pop_0114_e.pdf)). In addition, habtiat 'disturbance' threholds have been recommended for other types of ctritical habitat, with the implict assumption that staying below these thresholds will maintain habitats with low enough predator densities as to allow for stable or increasing cariobu popualtions. Specifically, a threshold of 35% 'disturbance' (i.e., area of cutblocks and roads buffered by 500m and burns) has been recommended for low elevation witner range and some matrix habtiat types ([Environment Canada 2014](https://www.registrelep-sararegistry.gc.ca/virtual_sara/files/plans/rs_woodland_caribou_bois_s_mtn_pop_0114_e.pdf)).

Here I attempt to estimate what moose density we likely need to acheieve to hit a target of 3 wolves per 1,000 km^2^ using exisitng pulbished wolf density models. I also review current moose density in teh CHilctoin region of British COlumbia and estimate wolf densities using these models. I then use a statiscial model that estimates mosose density as a fucntion fo variosu types of habtiat disturabnces (i.e., cutblocks, fires and roads) to estimate habitat conditions necesary to acheieve these moose densities. 

## Estimating Wolf Density from Moose Density
Seevral models have been developed to estimate wolf density from ungulate biomass or density. HEre I review some commonly cited and relevant models to British Columbia. 

### The [Fuller et al. (2003)](https://www.press.uchicago.edu/ucp/books/book/chicago/W/bo3641392.html) Model 
[Fuller et al. (2003)](https://www.press.uchicago.edu/ucp/books/book/chicago/W/bo3641392.html) developed an equation to estimate wolf density from an ungulate biomass index based on a variety of resarch studies form across North America. The equation applies an index factor to measured or estimated ungulate densities (animals/km^2^), where larger factors are applied to ungulates (i.e., moose density is multiplied by 6, elk density is multiplied by 3 and deer density is multiplied by 1). Wolf density (wolves/1,000 km ^2^) is then calculated with the equation: $W = 3.5 + (UB * 3.3)$, where W = wolf desnity and UB euqals total estimated ungulate biomass in the area of interest. The estiamted moose density to achieve estimated wolf density targets, assumign no oither ungulates are available in teh system, (or that wolves are not predating on other ungulates there) is illustrated in Figure 1. However, explicit in the [Fuller et al. (2003)](https://www.press.uchicago.edu/ucp/books/book/chicago/W/bo3641392.html) model is that there are a minimum of 3.5 wolves/1,000km^2^, regardless of ungulate biomass. This models suggests a very low, essentially near 0 ungulate density is necessary to achieve threhsolds below 3 wolves/1,000km^2^.
```{r, Fuller Wolf Density Equation, eval = T, echo = F, fig.align = "left", fig.cap = "Figure 1. Estimated Wolf Density as a Function of Moose Density Using the Fuller et al. (2003) Model"}
library (ggplot2)

data <- data.frame ("area.km2" = 1000, # 'simulated' dataset 
                    "moose.km2" = seq (0, 1.5, 0.01), "elk.km2" = 0, "white.tailed.deer.km2" = 0,
                    "mule.deer.km2" = 0,
                     stringsAsFactors = FALSE)

data$ungulate.biomass <- ((data$moose.km2 * 6) + (data$elk.km2 * 3) + # density input is animals/km2
                          (data$white.tailed.deer.km2 * 1) + (data$mule.deer.km2 * 1))

data$wolf.dens.fuller <- 3.5 + (data$ungulate.biomass * 3.3)

ggplot (data, aes (x = moose.km2, y = wolf.dens.fuller))  +
  geom_line () + 
  labs (x = expression ("Moose Density - moose per"~km^2), 
        y = expression ("Wolf Density - wolves per 1,000"~km^2)) +
  scale_x_continuous (breaks = seq (0, 1.5, 0.1)) +
  scale_y_continuous (breaks = seq (0, 35, 1)) +
  theme_classic () 
```

### The [Kuzyk and Hatter (2014)](https://wildlife.onlinelibrary.wiley.com/doi/abs/10.1002/wsb.475) Model 
[Kuzyk and Hatter (2014)](https://wildlife.onlinelibrary.wiley.com/doi/abs/10.1002/wsb.475) developed a statistical model of wolf density based on estiamted ungulate biomasss in regions of British COlumiba. Similar to [Fuller et al. (2003)](https://www.press.uchicago.edu/ucp/books/book/chicago/W/bo3641392.html), they calcualted wolf density as a fucntion of ungualte biomass, using the same ungulate biomass index. Wolf density (wolves/1,000 km ^2^) is calculated with the equation: $W = (UB * 5.4) - (UB^2^ * 3.3)$, where W = wolf desnity and UB euqals total estimated ungulate biomass in the area of interest. The estiamted moose density to achieve estimated wolf density targets, assumign no oither ungulates are available in the region, (or that wolves are not predating on other ungulates there) is illustrated in Figure 2. This model is perhaps more practical than the [Fuller et al. (2003)](https://www.press.uchicago.edu/ucp/books/book/chicago/W/bo3641392.html) model for estimatign wolf density in low ungulaet biomass regions because areas with no unglate biomass would have no wolves. This models suggests a density of approximately 0.09 moose/km^2^ is necessary to achieve thresholds below 3 wolves/1,000km^2^.
```{r, Kuzyk and Hatter Wolf Density Equation, eval = T, echo = F, fig.align = "left", fig.cap = "Figure 2. Estimated Wolf Density as a Function of Moose Density Using the Kuzyk and Hatter (2014) Model"}
library (ggplot2)

data <- data.frame ("area.km2" = 1000, # 'simulated' dataset 
                    "moose.km2" = seq (0, 1.5, 0.01), "elk.km2" = 0, "white.tailed.deer.km2" = 0,
                    "mule.deer.km2" = 0,
                     stringsAsFactors = FALSE)

data$ungulate.biomass <- ((data$moose.km2 * 6) + (data$elk.km2 * 3) + # density input is animals/km2
                          (data$white.tailed.deer.km2 * 1) + (data$mule.deer.km2 * 1))

data$wolf.dens.kuzyk <- (data$ungulate.biomass * 5.4) - (data$ungulate.biomass^2 * 0.166)

ggplot (data, aes (x = moose.km2, y = wolf.dens.kuzyk))  +
  geom_line () + 
  labs (x = expression ("Moose Density - moose per"~km^2), 
        y = expression ("Wolf Density - wolves per 1,000"~km^2)) +
  scale_x_continuous (breaks = seq (0, 1.5, 0.1)) +
  scale_y_continuous (breaks = seq (0, 35, 1)) +
  theme_classic () 
```

### The [Messier (1994)](https://www.jstor.org/stable/1939551?seq=1#page_scan_tab_contents) Model 
[Messier (1994)](https://www.jstor.org/stable/1939551?seq=1#page_scan_tab_contents) developed a statistical model of wolf density from moose desnity using data from across North America where moose were the primary prey of wolves. He calcualted wolf density as a function of moose density using a hyperbolic, Michaelis-Menten functio, using the equation: $W = (58.7 * (M - 0.03)) / (M + 0.76)$, where W = wolf density (wolves/1,000km^2^)and M = estimated moose density (moose/km^2^).The estiamted moose density to achieve estimated wolf density targets is illustrated in Figure 3.

This model allows for negative wolf densities at very low mosoe desnities, and requires a moose desnity greater than 0.03 moose/km^2^ to sustain wolves. THis model is also useful for estimatign wolf density in low ungulate biomass areas, also in areas where moose are known to be the doimannt prey of wolves. It is likely not useful in areas where otehr ungulaets are hte primary prey for wolves. This models suggests a density of less than approximately 0.08 moose/km^2^ is necessary to achieve thresholds below 3 wolves/1,000km^2^.

```{r, Messier 1994 wolf density model, val = T, echo = F, fig.align = "left", fig.cap = "Figure 3. Estimated Wolf Density as a Function of Moose Density Using the Messier (1994) Model"}

library (ggplot2)

data <- data.frame ("area.km2" = 1000, # 'simulated' dataset 
                    "moose.km2" = seq (0, 1.5, 0.01),
                     stringsAsFactors = FALSE)

data$wolf.dens.messier <- (58.7 * (data$moose.km2 - 0.03))/(0.76 + data$moose.km2)

ggplot (data, aes (x = moose.km2, y = wolf.dens.messier))  +
  geom_line () + 
  labs (x = expression ("Moose Density - moose per"~km^2), 
        y = expression ("Wolf Density - wolves per 1,000"~km^2)) +
  scale_x_continuous (breaks = seq (0, 1.5, 0.1)) +
  scale_y_continuous (breaks = seq (0, 40, 2)) +
  theme_classic ()

```

### Estimated Wolf Densities in the Chilcotin Region of British Columbia
Caribou recovery planning has begun in the Chilcotin local population unit (LPU). This LPU consists of the Itcha-Ilgachuz, Rainbows and Charlotte Alplands caribou herds, and constitutes the southernmost LPU of the Northern Mountain Caribou Designatible Unit (DU 7). These caribou are classified as *Threatened* under Canada's *Species at Risk Act*. 

The Itcha-Ilgachuz herd is considered to be of significant conservation importance provincially because it is the largest and highest density herd in west-central British Columbia (cite herd plan). However, the herd declined 17.2% annually between 2014 and 2018, and the habitat has experienced significant amounts of timber harvesting, associated road development, wildfire and mountain pine beetle infestations (cite herd plan). In addition, the 2019 population census showed a 40% popualion decline from 2018, and at that rate of decline, the herd would be functionally extirpated (i.e., less than 20 animals) in eight years (Carolyn Shores, Provincial Cariobu Biologist, pers. comm.). 

There is an  urgent need to develop an effective recovery plan for the Chilcotin LPU caribou. A critical component of this is managing wolf density directly (i.e., culling), but also indireclty by managing moose via their habitat. Addtional habtiat protections might be considered with the intent of minimizing habitat disturabnce so that moose densities adn ultimately wolf densiites are maitnained at low levels. 

Estimated moose desnities form aerial surveys done in wildlife managmen units (WMUs) of the Chilcotin region are described in Table 1. I estimated wolf densities using the three models described above and averaged them. The models suggest that wolf densities were never below 3 wolves/1,000km^2^ in any of the WMUs over the periods that they were surveyed. The lowest averaged estimates of wolf density were in WMUs 5-02-A in 1996 (4 wolves/1,000km^2^), 5-04 in 2012 (6 wolves/1,000km^2^), and 5-15-C in 2008 (5 wolves/1,000km^2^). The median wolf density estimate in the region throughout the surbvey period was 16 wolves/1,000km^2^, suggesting that wolf densities have generally been pretty high.  

```{r, Chilcotin moose desnites and estimated wolf densites Table, val = T, echo = F, warning = F}

library (data.table)
library (kableExtra)
tab_density_est <- data.table (WMU = c ("5-01", "5-01", "5-01", "5-02-A", "5-02-A", "5-02-A", "5-02-A", "5-02-B", "5-02-B", "5-02-B", "5-02-B", "5-02-B", "5-02-C", "5-02-C", "5-02-C", "5-02-C", "5-02-C", "5-02-D", "5-02-D", "5-02-D", "5-03", "5-03", "5-04", "5-04", "5-04", "5-04", "5-04", "5-04", "5-06", "5-10", "5-12-B", "5-12-B", "5-13-A", "5-13-A", "5-13-A", "5-13-A", "5-13-B", "5-13-B", "5-13-C", "5-13-C", "5-13-C", "5-14", "5-14", "5-14", "5-14", "5-15-A", "5-15-B", "5-15-C", "5-15-D"),
                                   SurveyYear = c (2015, 2000, 1996, 2014, 2001, 1998, 1996, 2018, 2006, 2000, 1996, 1994, 2019, 2011, 2001, 1997, 1994, 2014, 1999, 1994, 2019, 1997, 2017, 2012, 2005, 1998, 1995, 1994, 1995, 1995, 2012, 2002, 2017, 2003, 1998, 1995, 2018, 1999, 2019, 2008, 1997, 2019, 2013, 2001, 1994, 2008, 2008, 2008, 2004),
                                   MooseDensityKm2 = c (0.36, 0.32, 0.44, 0.33, 0.22, 0.26, 0.10, 0.46, 0.39, 0.59, 0.73, 1.42, 0.37, 0.51, 0.62, 0.30, 0.56, 0.86, 0.67, 1.19, 0.231, 0.35, 0.22, 0.14, 0.29, 0.41, 0.39, 0.71, 0.18, 0.26, 0.23, 0.58, 0.17, 0.30, 0.44, 0.32, 0.37, 0.31, 0.27, 0.49, 0.40, 0.261, 0.25, 0.46, 0.33, 0.29, 0.17, 0.11, 0.13)
                                  )
tab_density_est [, WolfDensityFuller := round (3.5 + ((MooseDensityKm2 * 6) * 3.3))] # FUller wolf density
tab_density_est [, WolfDensityKuzyk := round (((MooseDensityKm2 * 6) * 5.4) - ((MooseDensityKm2 * 6)^2 * 0.166))] # Kuzyk density
tab_density_est [, WolfDensityMessier := round ((58.7 * (MooseDensityKm2 - 0.03))/(0.76 + MooseDensityKm2))] # MEssier density
tab_density_est [, WolfDensityAverage := round ((WolfDensityFuller + WolfDensityKuzyk + WolfDensityMessier)/3)] # Averaged density

kable (tab_density_est,
       caption = "Table 1. Wolf desnity esitmates calcualted from pulbished modles and estimated moose densities form aerial surveys in teh CHilctoin region of Brtisih Columbia.") %>%
  kable_styling (position = "left",
                 bootstrap_options = c("striped", "hover", "condensed"),
                 fixed_thead = T,
                 full_width = F) 

```

### Estimated Moose Densities in Undisturbed Habitat in the Chilcotin Region
Moose density estimates in teh CHilcotin region were calculated from survey data collected between 1994 and 2019, a period during which disturabnce (i.e., forest harvest, fire and insect infestation) signfcianly inlfuenced the landscape. In apritcualr, these disturabnces likely influenced the availability and amount of forage available to moose. 

I fit a statistical model of moose density, estimated in the CHilcotin region, as a function of habitat features that may influence the density of moose in WMUs (see [here](https://github.com/bcgov/clus/blob/master/R/moose/02_moose_density_chilcotin.Rmd) for details). Habitat features were estimated in WMUs using spatial datasets, and tested in the model, including: amount of wetlands, lakes and riparian areas, climate averages (i.e., temperature and precipitation), elevation averages, area burned and forestry cutblocks, area of leading tree species, and amount of roads. 

Results of the model (Table 2) indicated that the area of disturbance (i.e., foresty cutblocks and fire), permament wet areas (i.e., rivers, wetlands and lakes), *Populus* species, Douglas fir, and length of roads in WMUs influenced moose density estimates. Increased road length in WMUs, particularly paved (road_paved_km) and rough roads (road_rough_km), negatively influenced moose density. Increased area of permanent wet areas (river_area_ha, wetland_area_ha, lake_area_ha), *Populus* species (Populus_area_ha) and Douglas fir (DougFir_area_ha) positively influenced moose density. The infleunce of burned and cut areas varied by age. The area of younger cutblocks (1 to 10 years old) positively influenced moose density, whereas the area of older cutblocks (11 to 30 years old) negatively influenced moose density. The influence of fire over time was more varied, as the area of burns 1 to 5 years old, 11 to 15 years old, and 26 to 30 years old negatively influenced moose density, whereas the area of burns 6 to 10 years old and 16 to 25 years old positively influenced moose density. 

```{r, moose desnity model results, val = T, echo = F, warning = F}
options (scipen = 999)
table.avg.coeff.est <- data.table ("Coefficient Name" = c ("Intercept", "Proportion Burnt 16 to 30 years old", "Density Paved Roads", "Density Unpaved Roads",  "Proportion Pine spp.", "Proportion Poplar spp.",  "Proportion Douglas Fir", "Proportion Spruce spp.", "Proportion Cutblocks 1 to 10 years old", "Proportion Cutblocks 11 to 30 years old"),
                                   "Coefficient Estimate" = c (0.15, 18.58, -5.94, -3.59, 0.14,
                                                               3.10, 0.02, -0.03, 0.76, -0.31),
                                   "Adjusted Std. Error" = c (0.06, 3.66, 6.35, 1.91, 0.15, 
                                                              0.83, 0.07, 0.10, 0.90, 0.46),
                                   "z-value" = c (2.39, 5.07, 0.94, 1.88, 0.91, 3.75, 
                                                  0.30, 0.27, 0.84, 0.67),
                                   "Pr(>|z|)" = c (0.02, "<0.01", 0.06, 0.01, 0.04, "<0.01", 
                                                   0.13, 0.20, 0.05, 0.06)
                                  )

kable (table.avg.coeff.est,
       caption = "Table xx. Moose density model coefficient values for the Chilcotin region of British Columbia.") %>%
  kable_styling (position = "center",
                 bootstrap_options = c("striped", "hover", "condensed"),
                 fixed_thead = T,
                 full_width = F)
```

I used this model to estimate moose densites if WMUs in the Chilcotin region were undisturbed (i.e., no roads or cutblocks) or minimally disturbed (i.e., 15% of the WMU was cutblocks aged 1 to 30 years old). This information was used to estimate potential minimum moose adn wolf densites that coudl be achieved in minimally disturbed habtaits and provide some indication of what wolf densities coudl be achieved with ahbtatio recovery. Density estiamtes are based on habiat conditosn estimated in the latest moose survey (where habitat was dynamic).  

Results are rough estiamets only, and should be used with a high degree of caution. The varaiability in factors that influence wildlfei popualtion dynmics is ginfcaint adn highyl complex. Estimaets here greatly oversimplify that complexity. However, these estimaets can be used ot provide some guidance aroudn management thresholds, which can be used in an adaptive managment appraoch where moose and wolf densites are diretcly monitroed during implemntation fo managment actions. 

Results show that estimated wolf densites are relatively low in the majority of WMUs at current levels of habitat disturbance, compared to disturbed or minimally disturbed levels of habitat (Fig. 3). These results were counterintuitive to what was expected, as current undesrtadning is that forestry activity is supporting higher wolf densites but providing forage for moose. However, our moose density model shows a strign negative efefct of roads (form forestry adn oteh types of developements) on moose densities, and an overall negative efefct of older cutblocks 11 to 30 years old 





```{r, estimated moose desnites form recovery of distrabed habtiat, val = T, echo = F, fig.align = "left", fig.cap = "Figure 3. Estimated Wolf Density in Wildlife Management Units (WMUs) as a Function of Habitat Disturbance at Current, Undisturbed (i.e, no roads or cutblocks) and Minimally Disturbed (15% of the WMU was cutblocks aged 1 to 30 years old) Conditions"}

library (ggplot2)

table.moose.density.pred <- data.frame (matrix (ncol = 21, nrow = 10))
colnames (table.moose.density.pred) <- c ("Cut_1_5_area_ha", "Cut_6_10_area_ha",  "Cut_11_20_area_ha",  "Cut_21_30_area_ha", "Fire_1_5_area_ha", "Fire_6_10_area_ha", "Fire_11_15_area_ha", "Fire_16_20_area_ha", "Fire_21_25_area_ha", "Fire_26_30_area_ha", "Populus_area_ha", "river_area_ha", "wetland_area_ha", "DougFir_area_ha", "road_loose_km", "road_paved_km", "road_rough_km", "lake_area_ha", "scenario", "wmu", "wmu_area_ha")

table.moose.density.pred [1, 1] <- 0 
table.moose.density.pred [1, 2] <- 0         
table.moose.density.pred [1, 3] <- 0        
table.moose.density.pred [1, 4] <- 0        
table.moose.density.pred [1, 5] <- 28        
table.moose.density.pred [1, 6] <- 791         
table.moose.density.pred [1, 7] <- 16         
table.moose.density.pred [1, 8] <- 0         
table.moose.density.pred [1, 9] <- 0         
table.moose.density.pred [1, 10] <- 72         
table.moose.density.pred [1, 11] <- 41909
table.moose.density.pred [1, 12] <- 78
table.moose.density.pred [1, 13] <- 7799
table.moose.density.pred [1, 14] <- 82920
table.moose.density.pred [1, 15] <- 0
table.moose.density.pred [1, 16] <- 0
table.moose.density.pred [1, 17] <- 0
table.moose.density.pred [1, 18] <- 23675
table.moose.density.pred [1, 19] <-"Undisturbed"
table.moose.density.pred [1, 20] <- "5-01"
table.moose.density.pred [1, 21] <- 232000

table.moose.density.pred [2, 1] <- 0 
table.moose.density.pred [2, 2] <- 0         
table.moose.density.pred [2, 3] <- 0        
table.moose.density.pred [2, 4] <- 0        
table.moose.density.pred [2, 5] <- 8693        
table.moose.density.pred [2, 6] <- 375         
table.moose.density.pred [2, 7] <- 12         
table.moose.density.pred [2, 8] <- 12         
table.moose.density.pred [2, 9] <- 19         
table.moose.density.pred [2, 10] <- 154         
table.moose.density.pred [2, 11] <- 13848
table.moose.density.pred [2, 12] <- 1294
table.moose.density.pred [2, 13] <- 13200
table.moose.density.pred [2, 14] <- 271868
table.moose.density.pred [2, 15] <- 0
table.moose.density.pred [2, 16] <- 0
table.moose.density.pred [2, 17] <- 0
table.moose.density.pred [2, 18] <- 14664
table.moose.density.pred [2, 19] <-"Undisturbed"
table.moose.density.pred [2, 20] <- "5-02-A"
table.moose.density.pred [2, 21] <- 342400

table.moose.density.pred [3, 1] <- 0 
table.moose.density.pred [3, 2] <- 0         
table.moose.density.pred [3, 3] <- 0        
table.moose.density.pred [3, 4] <- 0        
table.moose.density.pred [3, 5] <- 8        
table.moose.density.pred [3, 6] <- 664         
table.moose.density.pred [3, 7] <- 224         
table.moose.density.pred [3, 8] <- 24         
table.moose.density.pred [3, 9] <- 43         
table.moose.density.pred [3, 10] <- 188         
table.moose.density.pred [3, 11] <- 36027
table.moose.density.pred [3, 12] <- 315
table.moose.density.pred [3, 13] <- 8980
table.moose.density.pred [3, 14] <- 84461
table.moose.density.pred [3, 15] <- 0
table.moose.density.pred [3, 16] <- 0
table.moose.density.pred [3, 17] <- 0
table.moose.density.pred [3, 18] <- 24022
table.moose.density.pred [3, 19] <-"Undisturbed"
table.moose.density.pred [3, 20] <- "5-02-B"
table.moose.density.pred [3, 21] <- 334400

table.moose.density.pred [4, 1] <- 0 
table.moose.density.pred [4, 2] <- 0         
table.moose.density.pred [4, 3] <- 0        
table.moose.density.pred [4, 4] <- 0        
table.moose.density.pred [4, 5] <- 21559        
table.moose.density.pred [4, 6] <- 46         
table.moose.density.pred [4, 7] <- 103         
table.moose.density.pred [4, 8] <- 87         
table.moose.density.pred [4, 9] <- 92         
table.moose.density.pred [4, 10] <- 71         
table.moose.density.pred [4, 11] <- 38292
table.moose.density.pred [4, 12] <- 922
table.moose.density.pred [4, 13] <- 13860
table.moose.density.pred [4, 14] <- 137221
table.moose.density.pred [4, 15] <- 0
table.moose.density.pred [4, 16] <- 0
table.moose.density.pred [4, 17] <- 0
table.moose.density.pred [4, 18] <- 10870
table.moose.density.pred [4, 19] <-"Undisturbed"
table.moose.density.pred [4, 20] <- "5-02-C"
table.moose.density.pred [4, 21] <- 315200

table.moose.density.pred [5, 1] <- 0 
table.moose.density.pred [5, 2] <- 0         
table.moose.density.pred [5, 3] <- 0        
table.moose.density.pred [5, 4] <- 0        
table.moose.density.pred [5, 5] <- 178        
table.moose.density.pred [5, 6] <- 5         
table.moose.density.pred [5, 7] <- 0         
table.moose.density.pred [5, 8] <- 0         
table.moose.density.pred [5, 9] <- 0         
table.moose.density.pred [5, 10] <- 37         
table.moose.density.pred [5, 11] <- 47521
table.moose.density.pred [5, 12] <- 5655
table.moose.density.pred [5, 13] <- 6525
table.moose.density.pred [5, 14] <- 80398
table.moose.density.pred [5, 15] <- 0
table.moose.density.pred [5, 16] <- 0
table.moose.density.pred [5, 17] <- 0
table.moose.density.pred [5, 18] <- 3836
table.moose.density.pred [5, 19] <-"Undisturbed"
table.moose.density.pred [5, 20] <- "5-02-D"
table.moose.density.pred [5, 21] <- 329600

table.moose.density.pred [6, 1] <- 0 
table.moose.density.pred [6, 2] <- 0         
table.moose.density.pred [6, 3] <- 0        
table.moose.density.pred [6, 4] <- 0        
table.moose.density.pred [6, 5] <- 37126        
table.moose.density.pred [6, 6] <- 420         
table.moose.density.pred [6, 7] <- 139         
table.moose.density.pred [6, 8] <- 164         
table.moose.density.pred [6, 9] <- 0         
table.moose.density.pred [6, 10] <- 0         
table.moose.density.pred [6, 11] <- 4887
table.moose.density.pred [6, 12] <- 791
table.moose.density.pred [6, 13] <- 7388
table.moose.density.pred [6, 14] <- 105901
table.moose.density.pred [6, 15] <- 0
table.moose.density.pred [6, 16] <- 0
table.moose.density.pred [6, 17] <- 0
table.moose.density.pred [6, 18] <- 1476
table.moose.density.pred [6, 19] <-"Undisturbed"
table.moose.density.pred [6, 20] <- "5-03"
table.moose.density.pred [6, 21] <- 257600

table.moose.density.pred [7, 1] <- 0 
table.moose.density.pred [7, 2] <- 0         
table.moose.density.pred [7, 3] <- 0        
table.moose.density.pred [7, 4] <- 0        
table.moose.density.pred [7, 5] <- 82        
table.moose.density.pred [7, 6] <- 55761         
table.moose.density.pred [7, 7] <- 27498         
table.moose.density.pred [7, 8] <- 508         
table.moose.density.pred [7, 9] <- 192         
table.moose.density.pred [7, 10] <- 864         
table.moose.density.pred [7, 11] <- 21373
table.moose.density.pred [7, 12] <- 2019
table.moose.density.pred [7, 13] <- 23805
table.moose.density.pred [7, 14] <- 93135
table.moose.density.pred [7, 15] <- 0
table.moose.density.pred [7, 16] <- 0
table.moose.density.pred [7, 17] <- 0
table.moose.density.pred [7, 18] <- 23179
table.moose.density.pred [7, 19] <-"Undisturbed"
table.moose.density.pred [7, 20] <- "5-04"
table.moose.density.pred [7, 21] <- 515200

table.moose.density.pred [8, 1] <- 0 
table.moose.density.pred [8, 2] <- 0         
table.moose.density.pred [8, 3] <- 0        
table.moose.density.pred [8, 4] <- 0        
table.moose.density.pred [8, 5] <- 862        
table.moose.density.pred [8, 6] <- 404         
table.moose.density.pred [8, 7] <- 31         
table.moose.density.pred [8, 8] <- 48         
table.moose.density.pred [8, 9] <- 0         
table.moose.density.pred [8, 10] <- 106         
table.moose.density.pred [8, 11] <- 4825
table.moose.density.pred [8, 12] <- 1597
table.moose.density.pred [8, 13] <- 10495
table.moose.density.pred [8, 14] <- 16181
table.moose.density.pred [8, 15] <- 0
table.moose.density.pred [8, 16] <- 0
table.moose.density.pred [8, 17] <- 0
table.moose.density.pred [8, 18] <- 15724
table.moose.density.pred [8, 19] <-"Undisturbed"
table.moose.density.pred [8, 20] <- "5-06"
table.moose.density.pred [8, 21] <- 96000

table.moose.density.pred [9, 1] <- 0 
table.moose.density.pred [9, 2] <- 0         
table.moose.density.pred [9, 3] <- 0        
table.moose.density.pred [9, 4] <- 0        
table.moose.density.pred [9, 5] <- 506        
table.moose.density.pred [9, 6] <- 2489         
table.moose.density.pred [9, 7] <- 5370         
table.moose.density.pred [9, 8] <- 10         
table.moose.density.pred [9, 9] <- 0         
table.moose.density.pred [9, 10] <- 421         
table.moose.density.pred [9, 11] <- 14140
table.moose.density.pred [9, 12] <- 578
table.moose.density.pred [9, 13] <- 11351
table.moose.density.pred [9, 14] <- 920
table.moose.density.pred [9, 15] <- 0
table.moose.density.pred [9, 16] <- 0
table.moose.density.pred [9, 17] <- 0
table.moose.density.pred [9, 18] <- 10856
table.moose.density.pred [9, 19] <-"Undisturbed"
table.moose.density.pred [9, 20] <- "5-10"
table.moose.density.pred [9, 21] <- 127300

table.moose.density.pred [10, 1] <- 0 
table.moose.density.pred [10, 2] <- 0         
table.moose.density.pred [10, 3] <- 0        
table.moose.density.pred [10, 4] <- 0        
table.moose.density.pred [10, 5] <- 7331        
table.moose.density.pred [10, 6] <- 13734         
table.moose.density.pred [10, 7] <- 122         
table.moose.density.pred [10, 8] <- 0         
table.moose.density.pred [10, 9] <- 311         
table.moose.density.pred [10, 10] <- 208         
table.moose.density.pred [10, 11] <- 3563
table.moose.density.pred [10, 12] <- 594
table.moose.density.pred [10, 13] <- 22319
table.moose.density.pred [10, 14] <- 2718
table.moose.density.pred [10, 15] <- 0
table.moose.density.pred [10, 16] <- 0
table.moose.density.pred [10, 17] <- 0
table.moose.density.pred [10, 18] <- 7415
table.moose.density.pred [10, 19] <-"Undisturbed"
table.moose.density.pred [10, 20] <- "5-12-B"
table.moose.density.pred [10, 21] <- 267200

table.moose.density.pred [11, 1] <- 0 
table.moose.density.pred [11, 2] <- 0         
table.moose.density.pred [11, 3] <- 0        
table.moose.density.pred [11, 4] <- 0        
table.moose.density.pred [11, 5] <- 1508        
table.moose.density.pred [11, 6] <- 24709         
table.moose.density.pred [11, 7] <- 193         
table.moose.density.pred [11, 8] <- 0         
table.moose.density.pred [11, 9] <- 45         
table.moose.density.pred [11, 10] <- 140         
table.moose.density.pred [11, 11] <- 18453
table.moose.density.pred [11, 12] <- 207
table.moose.density.pred [11, 13] <- 27521
table.moose.density.pred [11, 14] <- 27643
table.moose.density.pred [11, 15] <- 0
table.moose.density.pred [11, 16] <- 0
table.moose.density.pred [11, 17] <- 0
table.moose.density.pred [11, 18] <- 8122
table.moose.density.pred [11, 19] <-"Undisturbed"
table.moose.density.pred [11, 20] <- "5-13-A"
table.moose.density.pred [11, 21] <- 500800

table.moose.density.pred [12, 1] <- 0 
table.moose.density.pred [12, 2] <- 0         
table.moose.density.pred [12, 3] <- 0        
table.moose.density.pred [12, 4] <- 0        
table.moose.density.pred [12, 5] <- 14665        
table.moose.density.pred [12, 6] <- 8782         
table.moose.density.pred [12, 7] <- 8080         
table.moose.density.pred [12, 8] <- 0         
table.moose.density.pred [12, 9] <- 18         
table.moose.density.pred [12, 10] <- 501         
table.moose.density.pred [12, 11] <- 32060
table.moose.density.pred [12, 12] <- 1592
table.moose.density.pred [12, 13] <- 13835
table.moose.density.pred [12, 14] <- 42625
table.moose.density.pred [12, 15] <- 0
table.moose.density.pred [12, 16] <- 0
table.moose.density.pred [12, 17] <- 0
table.moose.density.pred [12, 18] <- 3969
table.moose.density.pred [12, 19] <-"Undisturbed"
table.moose.density.pred [12, 20] <- "5-13-B"
table.moose.density.pred [12, 21] <- 456000

table.moose.density.pred [13, 1] <- 0 
table.moose.density.pred [13, 2] <- 0         
table.moose.density.pred [13, 3] <- 0        
table.moose.density.pred [13, 4] <- 0        
table.moose.density.pred [13, 5] <- 239046        
table.moose.density.pred [13, 6] <- 41271         
table.moose.density.pred [13, 7] <- 13867         
table.moose.density.pred [13, 8] <- 152         
table.moose.density.pred [13, 9] <- 2340         
table.moose.density.pred [13, 10] <- 537         
table.moose.density.pred [13, 11] <- 22991
table.moose.density.pred [13, 12] <- 712
table.moose.density.pred [13, 13] <- 28689
table.moose.density.pred [13, 14] <- 8046
table.moose.density.pred [13, 15] <- 0
table.moose.density.pred [13, 16] <- 0
table.moose.density.pred [13, 17] <- 0
table.moose.density.pred [13, 18] <- 9660
table.moose.density.pred [13, 19] <-"Undisturbed"
table.moose.density.pred [13, 20] <- "5-13-C"
table.moose.density.pred [13, 21] <- 468800

table.moose.density.pred [14, 1] <- 0 
table.moose.density.pred [14, 2] <- 0         
table.moose.density.pred [14, 3] <- 0        
table.moose.density.pred [14, 4] <- 0        
table.moose.density.pred [14, 5] <- 133342        
table.moose.density.pred [14, 6] <- 61750         
table.moose.density.pred [14, 7] <- 87         
table.moose.density.pred [14, 8] <- 106         
table.moose.density.pred [14, 9] <- 238         
table.moose.density.pred [14, 10] <- 60         
table.moose.density.pred [14, 11] <- 35202
table.moose.density.pred [14, 12] <- 2152
table.moose.density.pred [14, 13] <- 16762
table.moose.density.pred [14, 14] <- 196485
table.moose.density.pred [14, 15] <- 0
table.moose.density.pred [14, 16] <- 0
table.moose.density.pred [14, 17] <- 0
table.moose.density.pred [14, 18] <- 8856
table.moose.density.pred [14, 19] <-"Undisturbed"
table.moose.density.pred [14, 20] <- "5-14"
table.moose.density.pred [14, 21] <- 404800

table.moose.density.pred [15, 1] <- 0 
table.moose.density.pred [15, 2] <- 0         
table.moose.density.pred [15, 3] <- 0        
table.moose.density.pred [15, 4] <- 0        
table.moose.density.pred [15, 5] <- 2        
table.moose.density.pred [15, 6] <- 0         
table.moose.density.pred [15, 7] <- 24         
table.moose.density.pred [15, 8] <- 80         
table.moose.density.pred [15, 9] <- 245         
table.moose.density.pred [15, 10] <- 563         
table.moose.density.pred [15, 11] <- 2981
table.moose.density.pred [15, 12] <- 305
table.moose.density.pred [15, 13] <- 2561
table.moose.density.pred [15, 14] <- 25105
table.moose.density.pred [15, 15] <- 0
table.moose.density.pred [15, 16] <- 0
table.moose.density.pred [15, 17] <- 0
table.moose.density.pred [15, 18] <- 6750
table.moose.density.pred [15, 19] <-"Undisturbed"
table.moose.density.pred [15, 20] <- "5-15-A"
table.moose.density.pred [15, 21] <- 95800

table.moose.density.pred [16, 1] <- 0 
table.moose.density.pred [16, 2] <- 0         
table.moose.density.pred [16, 3] <- 0        
table.moose.density.pred [16, 4] <- 0        
table.moose.density.pred [16, 5] <- 931        
table.moose.density.pred [16, 6] <- 0         
table.moose.density.pred [16, 7] <- 14         
table.moose.density.pred [16, 8] <- 173         
table.moose.density.pred [16, 9] <- 207         
table.moose.density.pred [16, 10] <- 0         
table.moose.density.pred [16, 11] <- 115
table.moose.density.pred [16, 12] <- 584
table.moose.density.pred [16, 13] <- 1461
table.moose.density.pred [16, 14] <- 10746
table.moose.density.pred [16, 15] <- 0
table.moose.density.pred [16, 16] <- 0
table.moose.density.pred [16, 17] <- 0
table.moose.density.pred [16, 18] <- 13348
table.moose.density.pred [16, 19] <-"Undisturbed"
table.moose.density.pred [16, 20] <- "5-15-B"
table.moose.density.pred [16, 21] <- 84500

table.moose.density.pred [17, 1] <- 0 
table.moose.density.pred [17, 2] <- 0         
table.moose.density.pred [17, 3] <- 0        
table.moose.density.pred [17, 4] <- 0        
table.moose.density.pred [17, 5] <- 2        
table.moose.density.pred [17, 6] <- 34         
table.moose.density.pred [17, 7] <- 0         
table.moose.density.pred [17, 8] <- 0         
table.moose.density.pred [17, 9] <- 315         
table.moose.density.pred [17, 10] <- 129         
table.moose.density.pred [17, 11] <- 1167
table.moose.density.pred [17, 12] <- 78
table.moose.density.pred [17, 13] <- 831
table.moose.density.pred [17, 14] <- 14274
table.moose.density.pred [17, 15] <- 0
table.moose.density.pred [17, 16] <- 0
table.moose.density.pred [17, 17] <- 0
table.moose.density.pred [17, 18] <- 10131
table.moose.density.pred [17, 19] <-"Undisturbed"
table.moose.density.pred [17, 20] <- "5-15-C"
table.moose.density.pred [17, 21] <- 80100

table.moose.density.pred [18, 1] <- 0 
table.moose.density.pred [18, 2] <- 0         
table.moose.density.pred [18, 3] <- 0        
table.moose.density.pred [18, 4] <- 0        
table.moose.density.pred [18, 5] <- 0        
table.moose.density.pred [18, 6] <- 142         
table.moose.density.pred [18, 7] <- 198         
table.moose.density.pred [18, 8] <- 949         
table.moose.density.pred [18, 9] <- 687         
table.moose.density.pred [18, 10] <- 270         
table.moose.density.pred [18, 11] <- 7077
table.moose.density.pred [18, 12] <- 897
table.moose.density.pred [18, 13] <- 4182
table.moose.density.pred [18, 14] <- 3685
table.moose.density.pred [18, 15] <- 0
table.moose.density.pred [18, 16] <- 0
table.moose.density.pred [18, 17] <- 0
table.moose.density.pred [18, 18] <- 1530
table.moose.density.pred [18, 19] <-"Undisturbed"
table.moose.density.pred [18, 20] <- "5-15-D"
table.moose.density.pred [18, 21] <- 311500

# Current conditions
table.moose.density.pred [19, 1] <- 13029 
table.moose.density.pred [19, 2] <- 12180         
table.moose.density.pred [19, 3] <- 10631        
table.moose.density.pred [19, 4] <- 8816        
table.moose.density.pred [19, 5] <- 28        
table.moose.density.pred [19, 6] <- 791         
table.moose.density.pred [19, 7] <- 16         
table.moose.density.pred [19, 8] <- 0         
table.moose.density.pred [19, 9] <- 0         
table.moose.density.pred [19, 10] <- 72         
table.moose.density.pred [19, 11] <- 41909
table.moose.density.pred [19, 12] <- 78
table.moose.density.pred [19, 13] <- 7799
table.moose.density.pred [19, 14] <- 82920
table.moose.density.pred [19, 15] <- 123
table.moose.density.pred [19, 16] <- 66
table.moose.density.pred [19, 17] <- 0
table.moose.density.pred [19, 18] <- 23675
table.moose.density.pred [19, 19] <-"Current"
table.moose.density.pred [19, 20] <- "5-01"
table.moose.density.pred [19, 21] <- 232000

table.moose.density.pred [20, 1] <- 8893 
table.moose.density.pred [20, 2] <- 12342         
table.moose.density.pred [20, 3] <- 23143        
table.moose.density.pred [20, 4] <- 24303        
table.moose.density.pred [20, 5] <- 8693        
table.moose.density.pred [20, 6] <- 375         
table.moose.density.pred [20, 7] <- 12         
table.moose.density.pred [20, 8] <- 12         
table.moose.density.pred [20, 9] <- 19         
table.moose.density.pred [20, 10] <- 154         
table.moose.density.pred [20, 11] <- 13848
table.moose.density.pred [20, 12] <- 1294
table.moose.density.pred [20, 13] <- 13200
table.moose.density.pred [20, 14] <- 271868
table.moose.density.pred [20, 15] <- 82
table.moose.density.pred [20, 16] <- 24
table.moose.density.pred [20, 17] <- 2
table.moose.density.pred [20, 18] <- 14664
table.moose.density.pred [20, 19] <-"Current"
table.moose.density.pred [20, 20] <- "5-02-A"
table.moose.density.pred [20, 21] <- 342400

table.moose.density.pred [21, 1] <- 8412 
table.moose.density.pred [21, 2] <- 17797         
table.moose.density.pred [21, 3] <- 32888        
table.moose.density.pred [21, 4] <- 19300        
table.moose.density.pred [21, 5] <- 8        
table.moose.density.pred [21, 6] <- 664         
table.moose.density.pred [21, 7] <- 224         
table.moose.density.pred [21, 8] <- 24         
table.moose.density.pred [21, 9] <- 43         
table.moose.density.pred [21, 10] <- 188         
table.moose.density.pred [21, 11] <- 36027
table.moose.density.pred [21, 12] <- 315
table.moose.density.pred [21, 13] <- 8980
table.moose.density.pred [21, 14] <- 84461
table.moose.density.pred [21, 15] <- 68
table.moose.density.pred [21, 16] <- 6
table.moose.density.pred [21, 17] <- 3
table.moose.density.pred [21, 18] <- 24022
table.moose.density.pred [21, 19] <-"Current"
table.moose.density.pred [21, 20] <- "5-02-B"
table.moose.density.pred [21, 21] <- 334400

table.moose.density.pred [22, 1] <- 5088 
table.moose.density.pred [22, 2] <- 6964         
table.moose.density.pred [22, 3] <- 42780        
table.moose.density.pred [22, 4] <- 13163        
table.moose.density.pred [22, 5] <- 21559        
table.moose.density.pred [22, 6] <- 46         
table.moose.density.pred [22, 7] <- 103         
table.moose.density.pred [22, 8] <- 87         
table.moose.density.pred [22, 9] <- 92         
table.moose.density.pred [22, 10] <- 71         
table.moose.density.pred [22, 11] <- 38292
table.moose.density.pred [22, 12] <- 922
table.moose.density.pred [22, 13] <- 13860
table.moose.density.pred [22, 14] <- 137221
table.moose.density.pred [22, 15] <- 77
table.moose.density.pred [22, 16] <- 37
table.moose.density.pred [22, 17] <- 0
table.moose.density.pred [22, 18] <- 10870
table.moose.density.pred [22, 19] <-"Current"
table.moose.density.pred [22, 20] <- "5-02-C"
table.moose.density.pred [22, 21] <- 315200

table.moose.density.pred [23, 1] <- 7876 
table.moose.density.pred [23, 2] <- 29809         
table.moose.density.pred [23, 3] <- 31926        
table.moose.density.pred [23, 4] <- 13732        
table.moose.density.pred [23, 5] <- 178        
table.moose.density.pred [23, 6] <- 5         
table.moose.density.pred [23, 7] <- 0         
table.moose.density.pred [23, 8] <- 0         
table.moose.density.pred [23, 9] <- 0         
table.moose.density.pred [23, 10] <- 37         
table.moose.density.pred [23, 11] <- 47521
table.moose.density.pred [23, 12] <- 5655
table.moose.density.pred [23, 13] <- 6525
table.moose.density.pred [23, 14] <- 80398
table.moose.density.pred [23, 15] <- 28
table.moose.density.pred [23, 16] <- 27
table.moose.density.pred [23, 17] <- 0
table.moose.density.pred [23, 18] <- 3836
table.moose.density.pred [23, 19] <-"Current"
table.moose.density.pred [23, 20] <- "5-02-D"
table.moose.density.pred [23, 21] <- 329600

table.moose.density.pred [24, 1] <- 14032 
table.moose.density.pred [24, 2] <- 18023         
table.moose.density.pred [24, 3] <- 23639        
table.moose.density.pred [24, 4] <- 14532        
table.moose.density.pred [24, 5] <- 37126        
table.moose.density.pred [24, 6] <- 420         
table.moose.density.pred [24, 7] <- 139         
table.moose.density.pred [24, 8] <- 164         
table.moose.density.pred [24, 9] <- 0         
table.moose.density.pred [24, 10] <- 0         
table.moose.density.pred [24, 11] <- 4887
table.moose.density.pred [24, 12] <- 791
table.moose.density.pred [24, 13] <- 7388
table.moose.density.pred [24, 14] <- 105901
table.moose.density.pred [24, 15] <- 18
table.moose.density.pred [24, 16] <- 0
table.moose.density.pred [24, 17] <- 0
table.moose.density.pred [24, 18] <- 1476
table.moose.density.pred [24, 19] <-"Current"
table.moose.density.pred [24, 20] <- "5-03"
table.moose.density.pred [24, 21] <- 257600

table.moose.density.pred [25, 1] <- 22045 
table.moose.density.pred [25, 2] <- 18346         
table.moose.density.pred [25, 3] <- 15830        
table.moose.density.pred [25, 4] <- 38039        
table.moose.density.pred [25, 5] <- 82        
table.moose.density.pred [25, 6] <- 55761         
table.moose.density.pred [25, 7] <- 27498         
table.moose.density.pred [25, 8] <- 508         
table.moose.density.pred [25, 9] <- 192         
table.moose.density.pred [25, 10] <- 864         
table.moose.density.pred [25, 11] <- 21373
table.moose.density.pred [25, 12] <- 2019
table.moose.density.pred [25, 13] <- 23805
table.moose.density.pred [25, 14] <- 93135
table.moose.density.pred [25, 15] <- 134
table.moose.density.pred [25, 16] <- 0
table.moose.density.pred [25, 17] <- 61
table.moose.density.pred [25, 18] <- 23179
table.moose.density.pred [25, 19] <-"Current"
table.moose.density.pred [25, 20] <- "5-04"
table.moose.density.pred [25, 21] <- 515200

table.moose.density.pred [26, 1] <- 5869 
table.moose.density.pred [26, 2] <- 4059         
table.moose.density.pred [26, 3] <- 777        
table.moose.density.pred [26, 4] <- 136        
table.moose.density.pred [26, 5] <- 862        
table.moose.density.pred [26, 6] <- 404         
table.moose.density.pred [26, 7] <- 31         
table.moose.density.pred [26, 8] <- 48         
table.moose.density.pred [26, 9] <- 0         
table.moose.density.pred [26, 10] <- 106         
table.moose.density.pred [26, 11] <- 4825
table.moose.density.pred [26, 12] <- 1597
table.moose.density.pred [26, 13] <- 10495
table.moose.density.pred [26, 14] <- 16181
table.moose.density.pred [26, 15] <- 22
table.moose.density.pred [26, 16] <- 12
table.moose.density.pred [26, 17] <- 3
table.moose.density.pred [26, 18] <- 15724
table.moose.density.pred [26, 19] <-"Current"
table.moose.density.pred [26, 20] <- "5-06"
table.moose.density.pred [26, 21] <- 96000

table.moose.density.pred [27, 1] <- 0 
table.moose.density.pred [27, 2] <- 0         
table.moose.density.pred [27, 3] <- 0        
table.moose.density.pred [27, 4] <- 0        
table.moose.density.pred [27, 5] <- 506        
table.moose.density.pred [27, 6] <- 2489         
table.moose.density.pred [27, 7] <- 5370         
table.moose.density.pred [27, 8] <- 10         
table.moose.density.pred [27, 9] <- 0         
table.moose.density.pred [27, 10] <- 421         
table.moose.density.pred [27, 11] <- 14140
table.moose.density.pred [27, 12] <- 578
table.moose.density.pred [27, 13] <- 11351
table.moose.density.pred [27, 14] <- 920
table.moose.density.pred [27, 15] <- 0
table.moose.density.pred [27, 16] <- 0
table.moose.density.pred [27, 17] <- 0
table.moose.density.pred [27, 18] <- 10856
table.moose.density.pred [27, 19] <-"Current"
table.moose.density.pred [27, 20] <- "5-10"
table.moose.density.pred [27, 21] <- 127300

table.moose.density.pred [28, 1] <- 1177 
table.moose.density.pred [28, 2] <- 6624         
table.moose.density.pred [28, 3] <- 14901        
table.moose.density.pred [28, 4] <- 4609        
table.moose.density.pred [28, 5] <- 7331        
table.moose.density.pred [28, 6] <- 13734         
table.moose.density.pred [28, 7] <- 122         
table.moose.density.pred [28, 8] <- 0         
table.moose.density.pred [28, 9] <- 311         
table.moose.density.pred [28, 10] <- 208         
table.moose.density.pred [28, 11] <- 3563
table.moose.density.pred [28, 12] <- 594
table.moose.density.pred [28, 13] <- 22319
table.moose.density.pred [28, 14] <- 2718
table.moose.density.pred [28, 15] <- 15
table.moose.density.pred [28, 16] <- 10
table.moose.density.pred [28, 17] <- 5
table.moose.density.pred [28, 18] <- 7415
table.moose.density.pred [28, 19] <-"Current"
table.moose.density.pred [28, 20] <- "5-12-B"
table.moose.density.pred [28, 21] <- 267200

table.moose.density.pred [29, 1] <- 28562 
table.moose.density.pred [29, 2] <- 14806         
table.moose.density.pred [29, 3] <- 24076        
table.moose.density.pred [29, 4] <- 50930        
table.moose.density.pred [29, 5] <- 1508        
table.moose.density.pred [29, 6] <- 24709         
table.moose.density.pred [29, 7] <- 193         
table.moose.density.pred [29, 8] <- 0         
table.moose.density.pred [29, 9] <- 45         
table.moose.density.pred [29, 10] <- 140         
table.moose.density.pred [29, 11] <- 18453
table.moose.density.pred [29, 12] <- 207
table.moose.density.pred [29, 13] <- 27521
table.moose.density.pred [29, 14] <- 27643
table.moose.density.pred [29, 15] <- 82
table.moose.density.pred [29, 16] <- 8
table.moose.density.pred [29, 17] <- 26
table.moose.density.pred [29, 18] <- 8122
table.moose.density.pred [29, 19] <-"Current"
table.moose.density.pred [29, 20] <- "5-13-A"
table.moose.density.pred [29, 21] <- 500800

table.moose.density.pred [30, 1] <- 23001 
table.moose.density.pred [30, 2] <- 45440         
table.moose.density.pred [30, 3] <- 66667        
table.moose.density.pred [30, 4] <- 33029        
table.moose.density.pred [30, 5] <- 14665        
table.moose.density.pred [30, 6] <- 8782         
table.moose.density.pred [30, 7] <- 8080         
table.moose.density.pred [30, 8] <- 0         
table.moose.density.pred [30, 9] <- 18         
table.moose.density.pred [30, 10] <- 501         
table.moose.density.pred [30, 11] <- 32060
table.moose.density.pred [30, 12] <- 1592
table.moose.density.pred [30, 13] <- 13835
table.moose.density.pred [30, 14] <- 42625
table.moose.density.pred [30, 15] <- 57
table.moose.density.pred [30, 16] <- 29
table.moose.density.pred [30, 17] <- 0
table.moose.density.pred [30, 18] <- 3969
table.moose.density.pred [30, 19] <-"Current"
table.moose.density.pred [30, 20] <- "5-13-B"
table.moose.density.pred [30, 21] <- 456000

table.moose.density.pred [31, 1] <- 25770 
table.moose.density.pred [31, 2] <- 30890         
table.moose.density.pred [31, 3] <- 38870        
table.moose.density.pred [31, 4] <- 21097        
table.moose.density.pred [31, 5] <- 239046        
table.moose.density.pred [31, 6] <- 41271         
table.moose.density.pred [31, 7] <- 13867         
table.moose.density.pred [31, 8] <- 152         
table.moose.density.pred [31, 9] <- 2340         
table.moose.density.pred [31, 10] <- 537         
table.moose.density.pred [31, 11] <- 22991
table.moose.density.pred [31, 12] <- 712
table.moose.density.pred [31, 13] <- 28689
table.moose.density.pred [31, 14] <- 8046
table.moose.density.pred [31, 15] <- 248
table.moose.density.pred [31, 16] <- 11
table.moose.density.pred [31, 17] <- 0
table.moose.density.pred [31, 18] <- 9660
table.moose.density.pred [31, 19] <-"Current"
table.moose.density.pred [31, 20] <- "5-13-C"
table.moose.density.pred [31, 21] <- 468800

table.moose.density.pred [32, 1] <- 6896 
table.moose.density.pred [32, 2] <- 10939         
table.moose.density.pred [32, 3] <- 40059        
table.moose.density.pred [32, 4] <- 27517        
table.moose.density.pred [32, 5] <- 133342        
table.moose.density.pred [32, 6] <- 61750         
table.moose.density.pred [32, 7] <- 87         
table.moose.density.pred [32, 8] <- 106         
table.moose.density.pred [32, 9] <- 238         
table.moose.density.pred [32, 10] <- 60         
table.moose.density.pred [32, 11] <- 35202
table.moose.density.pred [32, 12] <- 2152
table.moose.density.pred [32, 13] <- 16762
table.moose.density.pred [32, 14] <- 196485
table.moose.density.pred [32, 15] <- 178
table.moose.density.pred [32, 16] <- 54
table.moose.density.pred [32, 17] <- 13
table.moose.density.pred [32, 18] <- 8856
table.moose.density.pred [32, 19] <-"Current"
table.moose.density.pred [32, 20] <- "5-14"
table.moose.density.pred [32, 21] <- 404800

table.moose.density.pred [33, 1] <- 4171 
table.moose.density.pred [33, 2] <- 2297         
table.moose.density.pred [33, 3] <- 9739        
table.moose.density.pred [33, 4] <- 6906        
table.moose.density.pred [33, 5] <- 2        
table.moose.density.pred [33, 6] <- 0         
table.moose.density.pred [33, 7] <- 24         
table.moose.density.pred [33, 8] <- 80         
table.moose.density.pred [33, 9] <- 245         
table.moose.density.pred [33, 10] <- 563         
table.moose.density.pred [33, 11] <- 2981
table.moose.density.pred [33, 12] <- 305
table.moose.density.pred [33, 13] <- 2561
table.moose.density.pred [33, 14] <- 25105
table.moose.density.pred [33, 15] <- 12
table.moose.density.pred [33, 16] <- 0
table.moose.density.pred [33, 17] <- 0
table.moose.density.pred [33, 18] <- 6750
table.moose.density.pred [33, 19] <-"Current"
table.moose.density.pred [33, 20] <- "5-15-A"
table.moose.density.pred [33, 21] <- 95800

table.moose.density.pred [34, 1] <- 688 
table.moose.density.pred [34, 2] <- 936         
table.moose.density.pred [34, 3] <- 2739        
table.moose.density.pred [34, 4] <- 3915        
table.moose.density.pred [34, 5] <- 931        
table.moose.density.pred [34, 6] <- 0         
table.moose.density.pred [34, 7] <- 14         
table.moose.density.pred [34, 8] <- 173         
table.moose.density.pred [34, 9] <- 207         
table.moose.density.pred [34, 10] <- 0         
table.moose.density.pred [34, 11] <- 115
table.moose.density.pred [34, 12] <- 584
table.moose.density.pred [34, 13] <- 1461
table.moose.density.pred [34, 14] <- 10746
table.moose.density.pred [34, 15] <- 0
table.moose.density.pred [34, 16] <- 0
table.moose.density.pred [34, 17] <- 0
table.moose.density.pred [34, 18] <- 13348
table.moose.density.pred [34, 19] <-"Current"
table.moose.density.pred [34, 20] <- "5-15-B"
table.moose.density.pred [34, 21] <- 84500

table.moose.density.pred [35, 1] <- 2331 
table.moose.density.pred [35, 2] <- 1540         
table.moose.density.pred [35, 3] <- 6267        
table.moose.density.pred [35, 4] <- 7959        
table.moose.density.pred [35, 5] <- 2        
table.moose.density.pred [35, 6] <- 34         
table.moose.density.pred [35, 7] <- 0         
table.moose.density.pred [35, 8] <- 0         
table.moose.density.pred [35, 9] <- 315         
table.moose.density.pred [35, 10] <- 129         
table.moose.density.pred [35, 11] <- 1167
table.moose.density.pred [35, 12] <- 78
table.moose.density.pred [35, 13] <- 831
table.moose.density.pred [35, 14] <- 14274
table.moose.density.pred [35, 15] <- 11
table.moose.density.pred [35, 16] <- 0
table.moose.density.pred [35, 17] <- 0
table.moose.density.pred [35, 18] <- 10131
table.moose.density.pred [35, 19] <-"Current"
table.moose.density.pred [35, 20] <- "5-15-C"
table.moose.density.pred [35, 21] <- 80100

table.moose.density.pred [36, 1] <- 5776 
table.moose.density.pred [36, 2] <- 7930         
table.moose.density.pred [36, 3] <- 21985        
table.moose.density.pred [36, 4] <- 16567        
table.moose.density.pred [36, 5] <- 0        
table.moose.density.pred [36, 6] <- 142         
table.moose.density.pred [36, 7] <- 198         
table.moose.density.pred [36, 8] <- 949         
table.moose.density.pred [36, 9] <- 687         
table.moose.density.pred [36, 10] <- 270         
table.moose.density.pred [36, 11] <- 7077
table.moose.density.pred [36, 12] <- 897
table.moose.density.pred [36, 13] <- 4182
table.moose.density.pred [36, 14] <- 3685
table.moose.density.pred [36, 15] <- 18
table.moose.density.pred [36, 16] <- 4
table.moose.density.pred [36, 17] <- 0
table.moose.density.pred [36, 18] <- 1530
table.moose.density.pred [36, 19] <-"Current"
table.moose.density.pred [36, 20] <- "5-15-D"
table.moose.density.pred [36, 21] <- 311500

# Forestry 15% area < 30 years old conditions
table.moose.density.pred [37, 1] <- 8700 # 3.75% of total area (232000*0.0375)
table.moose.density.pred [37, 2] <- 8700         
table.moose.density.pred [37, 3] <- 8700        
table.moose.density.pred [37, 4] <- 8700        
table.moose.density.pred [37, 5] <- 28        
table.moose.density.pred [37, 6] <- 791         
table.moose.density.pred [37, 7] <- 16         
table.moose.density.pred [37, 8] <- 0         
table.moose.density.pred [37, 9] <- 0         
table.moose.density.pred [37, 10] <- 72         
table.moose.density.pred [37, 11] <- 41909
table.moose.density.pred [37, 12] <- 78
table.moose.density.pred [37, 13] <- 7799
table.moose.density.pred [37, 14] <- 82920
table.moose.density.pred [37, 15] <- 123
table.moose.density.pred [37, 16] <- 66
table.moose.density.pred [37, 17] <- 0
table.moose.density.pred [37, 18] <- 23675
table.moose.density.pred [37, 19] <-"Forestry 15%"
table.moose.density.pred [37, 20] <- "5-01"
table.moose.density.pred [37, 21] <- 232000

table.moose.density.pred [38, 1] <- 12840 # 3.75% of total area (342400*0.0375)
table.moose.density.pred [38, 2] <- 12840         
table.moose.density.pred [38, 3] <- 12840        
table.moose.density.pred [38, 4] <- 12840        
table.moose.density.pred [38, 5] <- 8693        
table.moose.density.pred [38, 6] <- 375         
table.moose.density.pred [38, 7] <- 12         
table.moose.density.pred [38, 8] <- 12         
table.moose.density.pred [38, 9] <- 19         
table.moose.density.pred [38, 10] <- 154         
table.moose.density.pred [38, 11] <- 13848
table.moose.density.pred [38, 12] <- 1294
table.moose.density.pred [38, 13] <- 13200
table.moose.density.pred [38, 14] <- 271868
table.moose.density.pred [38, 15] <- 82
table.moose.density.pred [38, 16] <- 24
table.moose.density.pred [38, 17] <- 2
table.moose.density.pred [38, 18] <- 14664
table.moose.density.pred [38, 19] <-"Forestry 15%"
table.moose.density.pred [38, 20] <- "5-02-A"
table.moose.density.pred [38, 21] <- 342400

table.moose.density.pred [39, 1] <- 12540 # 3.75% of total area (334400*0.0375)
table.moose.density.pred [39, 2] <- 12540         
table.moose.density.pred [39, 3] <- 12540        
table.moose.density.pred [39, 4] <- 12540        
table.moose.density.pred [39, 5] <- 8        
table.moose.density.pred [39, 6] <- 664         
table.moose.density.pred [39, 7] <- 224         
table.moose.density.pred [39, 8] <- 24         
table.moose.density.pred [39, 9] <- 43         
table.moose.density.pred [39, 10] <- 188         
table.moose.density.pred [39, 11] <- 36027
table.moose.density.pred [39, 12] <- 315
table.moose.density.pred [39, 13] <- 8980
table.moose.density.pred [39, 14] <- 84461
table.moose.density.pred [39, 15] <- 68
table.moose.density.pred [39, 16] <- 6
table.moose.density.pred [39, 17] <- 3
table.moose.density.pred [39, 18] <- 24022
table.moose.density.pred [39, 19] <-"Forestry 15%"
table.moose.density.pred [39, 20] <- "5-02-B"
table.moose.density.pred [39, 21] <- 334400

table.moose.density.pred [40, 1] <- 11820 # 3.75% of total area (315200*0.0375)
table.moose.density.pred [40, 2] <- 11820         
table.moose.density.pred [40, 3] <- 11820        
table.moose.density.pred [40, 4] <- 11820        
table.moose.density.pred [40, 5] <- 21559        
table.moose.density.pred [40, 6] <- 46         
table.moose.density.pred [40, 7] <- 103         
table.moose.density.pred [40, 8] <- 87         
table.moose.density.pred [40, 9] <- 92         
table.moose.density.pred [40, 10] <- 71         
table.moose.density.pred [40, 11] <- 38292
table.moose.density.pred [40, 12] <- 922
table.moose.density.pred [40, 13] <- 13860
table.moose.density.pred [40, 14] <- 137221
table.moose.density.pred [40, 15] <- 77
table.moose.density.pred [40, 16] <- 37
table.moose.density.pred [40, 17] <- 0
table.moose.density.pred [40, 18] <- 10870
table.moose.density.pred [40, 19] <-"Forestry 15%"
table.moose.density.pred [40, 20] <- "5-02-C"
table.moose.density.pred [40, 21] <- 315200

table.moose.density.pred [41, 1] <- 12360 # 3.75% of total area (329600*0.0375)
table.moose.density.pred [41, 2] <- 12360         
table.moose.density.pred [41, 3] <- 12360        
table.moose.density.pred [41, 4] <- 12360        
table.moose.density.pred [41, 5] <- 178        
table.moose.density.pred [41, 6] <- 5         
table.moose.density.pred [41, 7] <- 0         
table.moose.density.pred [41, 8] <- 0         
table.moose.density.pred [41, 9] <- 0         
table.moose.density.pred [41, 10] <- 37         
table.moose.density.pred [41, 11] <- 47521
table.moose.density.pred [41, 12] <- 5655
table.moose.density.pred [41, 13] <- 6525
table.moose.density.pred [41, 14] <- 80398
table.moose.density.pred [41, 15] <- 28
table.moose.density.pred [41, 16] <- 27
table.moose.density.pred [41, 17] <- 0
table.moose.density.pred [41, 18] <- 3836
table.moose.density.pred [41, 19] <-"Forestry 15%"
table.moose.density.pred [41, 20] <- "5-02-D"
table.moose.density.pred [41, 21] <- 329600

table.moose.density.pred [42, 1] <- 9660 # 3.75% of total area (257600*0.0375)
table.moose.density.pred [42, 2] <- 9660         
table.moose.density.pred [42, 3] <- 9660        
table.moose.density.pred [42, 4] <- 9660        
table.moose.density.pred [42, 5] <- 37126        
table.moose.density.pred [42, 6] <- 420         
table.moose.density.pred [42, 7] <- 139         
table.moose.density.pred [42, 8] <- 164         
table.moose.density.pred [42, 9] <- 0         
table.moose.density.pred [42, 10] <- 0         
table.moose.density.pred [42, 11] <- 4887
table.moose.density.pred [42, 12] <- 791
table.moose.density.pred [42, 13] <- 7388
table.moose.density.pred [42, 14] <- 105901
table.moose.density.pred [42, 15] <- 18
table.moose.density.pred [42, 16] <- 0
table.moose.density.pred [42, 17] <- 0
table.moose.density.pred [42, 18] <- 1476
table.moose.density.pred [42, 19] <-"Forestry 15%"
table.moose.density.pred [42, 20] <- "5-03"
table.moose.density.pred [42, 21] <- 257600

table.moose.density.pred [43, 1] <- 19320 # 3.75% of total area (515200*0.0375)
table.moose.density.pred [43, 2] <- 19320         
table.moose.density.pred [43, 3] <- 19320        
table.moose.density.pred [43, 4] <- 19320        
table.moose.density.pred [43, 5] <- 82        
table.moose.density.pred [43, 6] <- 55761         
table.moose.density.pred [43, 7] <- 27498         
table.moose.density.pred [43, 8] <- 508         
table.moose.density.pred [43, 9] <- 192         
table.moose.density.pred [43, 10] <- 864         
table.moose.density.pred [43, 11] <- 21373
table.moose.density.pred [43, 12] <- 2019
table.moose.density.pred [43, 13] <- 23805
table.moose.density.pred [43, 14] <- 93135
table.moose.density.pred [43, 15] <- 134
table.moose.density.pred [43, 16] <- 0
table.moose.density.pred [43, 17] <- 61
table.moose.density.pred [43, 18] <- 23179
table.moose.density.pred [43, 19] <-"Forestry 15%"
table.moose.density.pred [43, 20] <- "5-04"
table.moose.density.pred [43, 21] <- 515200

table.moose.density.pred [44, 1] <- 3600 # 3.75% of total area (96000*0.0375)
table.moose.density.pred [44, 2] <- 3600         
table.moose.density.pred [44, 3] <- 3600        
table.moose.density.pred [44, 4] <- 3600        
table.moose.density.pred [44, 5] <- 862        
table.moose.density.pred [44, 6] <- 404         
table.moose.density.pred [44, 7] <- 31         
table.moose.density.pred [44, 8] <- 48         
table.moose.density.pred [44, 9] <- 0         
table.moose.density.pred [44, 10] <- 106         
table.moose.density.pred [44, 11] <- 4825
table.moose.density.pred [44, 12] <- 1597
table.moose.density.pred [44, 13] <- 10495
table.moose.density.pred [44, 14] <- 16181
table.moose.density.pred [44, 15] <- 22
table.moose.density.pred [44, 16] <- 12
table.moose.density.pred [44, 17] <- 3
table.moose.density.pred [44, 18] <- 15724
table.moose.density.pred [44, 19] <-"Forestry 15%"
table.moose.density.pred [44, 20] <- "5-06"
table.moose.density.pred [44, 21] <- 96000

table.moose.density.pred [45, 1] <- 4773 # 3.75% of total area (127300*0.0375)
table.moose.density.pred [45, 2] <- 4773         
table.moose.density.pred [45, 3] <- 4773        
table.moose.density.pred [45, 4] <- 4773        
table.moose.density.pred [45, 5] <- 506        
table.moose.density.pred [45, 6] <- 2489         
table.moose.density.pred [45, 7] <- 5370         
table.moose.density.pred [45, 8] <- 10         
table.moose.density.pred [45, 9] <- 0         
table.moose.density.pred [45, 10] <- 421         
table.moose.density.pred [45, 11] <- 14140
table.moose.density.pred [45, 12] <- 578
table.moose.density.pred [45, 13] <- 11351
table.moose.density.pred [45, 14] <- 920
table.moose.density.pred [45, 15] <- 0
table.moose.density.pred [45, 16] <- 0
table.moose.density.pred [45, 17] <- 0
table.moose.density.pred [45, 18] <- 10856
table.moose.density.pred [45, 19] <-"Forestry 15%"
table.moose.density.pred [45, 20] <- "5-10"
table.moose.density.pred [45, 21] <- 127300

table.moose.density.pred [46, 1] <- 10020 # 3.75% of total area (267200*0.0375)
table.moose.density.pred [46, 2] <- 10020         
table.moose.density.pred [46, 3] <- 10020        
table.moose.density.pred [46, 4] <- 10020        
table.moose.density.pred [46, 5] <- 7331        
table.moose.density.pred [46, 6] <- 13734         
table.moose.density.pred [46, 7] <- 122         
table.moose.density.pred [46, 8] <- 0         
table.moose.density.pred [46, 9] <- 311         
table.moose.density.pred [46, 10] <- 208         
table.moose.density.pred [46, 11] <- 3563
table.moose.density.pred [46, 12] <- 594
table.moose.density.pred [46, 13] <- 22319
table.moose.density.pred [46, 14] <- 2718
table.moose.density.pred [46, 15] <- 15
table.moose.density.pred [46, 16] <- 10
table.moose.density.pred [46, 17] <- 5
table.moose.density.pred [46, 18] <- 7415
table.moose.density.pred [46, 19] <-"Forestry 15%"
table.moose.density.pred [46, 20] <- "5-12-B"
table.moose.density.pred [46, 21] <- 267200

table.moose.density.pred [47, 1] <- 18780 # 3.75% of total area (500800*0.0375)
table.moose.density.pred [47, 2] <- 18780         
table.moose.density.pred [47, 3] <- 18780        
table.moose.density.pred [47, 4] <- 18780        
table.moose.density.pred [47, 5] <- 1508        
table.moose.density.pred [47, 6] <- 24709         
table.moose.density.pred [47, 7] <- 193         
table.moose.density.pred [47, 8] <- 0         
table.moose.density.pred [47, 9] <- 45         
table.moose.density.pred [47, 10] <- 140         
table.moose.density.pred [47, 11] <- 18453
table.moose.density.pred [47, 12] <- 207
table.moose.density.pred [47, 13] <- 27521
table.moose.density.pred [47, 14] <- 27643
table.moose.density.pred [47, 15] <- 82
table.moose.density.pred [47, 16] <- 8
table.moose.density.pred [47, 17] <- 26
table.moose.density.pred [47, 18] <- 8122
table.moose.density.pred [47, 19] <-"Forestry 15%"
table.moose.density.pred [47, 20] <- "5-13-A"
table.moose.density.pred [47, 21] <- 500800

table.moose.density.pred [48, 1] <- 17100 # 3.75% of total area (456000*0.0375)
table.moose.density.pred [48, 2] <- 17100         
table.moose.density.pred [48, 3] <- 17100        
table.moose.density.pred [48, 4] <- 17100        
table.moose.density.pred [48, 5] <- 14665        
table.moose.density.pred [48, 6] <- 8782         
table.moose.density.pred [48, 7] <- 8080         
table.moose.density.pred [48, 8] <- 0         
table.moose.density.pred [48, 9] <- 18         
table.moose.density.pred [48, 10] <- 501         
table.moose.density.pred [48, 11] <- 32060
table.moose.density.pred [48, 12] <- 1592
table.moose.density.pred [48, 13] <- 13835
table.moose.density.pred [48, 14] <- 42625
table.moose.density.pred [48, 15] <- 57
table.moose.density.pred [48, 16] <- 29
table.moose.density.pred [48, 17] <- 0
table.moose.density.pred [48, 18] <- 3969
table.moose.density.pred [48, 19] <-"Forestry 15%"
table.moose.density.pred [48, 20] <- "5-13-B"
table.moose.density.pred [48, 21] <- 456000

table.moose.density.pred [49, 1] <- 17580 # 3.75% of total area (468800*0.0375)
table.moose.density.pred [49, 2] <- 17580         
table.moose.density.pred [49, 3] <- 17580        
table.moose.density.pred [49, 4] <- 17580        
table.moose.density.pred [49, 5] <- 239046        
table.moose.density.pred [49, 6] <- 41271         
table.moose.density.pred [49, 7] <- 13867         
table.moose.density.pred [49, 8] <- 152         
table.moose.density.pred [49, 9] <- 2340         
table.moose.density.pred [49, 10] <- 537         
table.moose.density.pred [49, 11] <- 22991
table.moose.density.pred [49, 12] <- 712
table.moose.density.pred [49, 13] <- 28689
table.moose.density.pred [49, 14] <- 8046
table.moose.density.pred [49, 15] <- 248
table.moose.density.pred [49, 16] <- 11
table.moose.density.pred [49, 17] <- 0
table.moose.density.pred [49, 18] <- 9660
table.moose.density.pred [49, 19] <-"Forestry 15%"
table.moose.density.pred [49, 20] <- "5-13-C"
table.moose.density.pred [49, 21] <- 468800

table.moose.density.pred [50, 1] <- 15180 # 3.75% of total area (404800*0.0375)
table.moose.density.pred [50, 2] <- 15180         
table.moose.density.pred [50, 3] <- 15180        
table.moose.density.pred [50, 4] <- 15180        
table.moose.density.pred [50, 5] <- 133342        
table.moose.density.pred [50, 6] <- 61750         
table.moose.density.pred [50, 7] <- 87         
table.moose.density.pred [50, 8] <- 106         
table.moose.density.pred [50, 9] <- 238         
table.moose.density.pred [50, 10] <- 60         
table.moose.density.pred [50, 11] <- 35202
table.moose.density.pred [50, 12] <- 2152
table.moose.density.pred [50, 13] <- 16762
table.moose.density.pred [50, 14] <- 196485
table.moose.density.pred [50, 15] <- 178
table.moose.density.pred [50, 16] <- 54
table.moose.density.pred [50, 17] <- 13
table.moose.density.pred [50, 18] <- 8856
table.moose.density.pred [50, 19] <-"Forestry 15%"
table.moose.density.pred [50, 20] <- "5-14"
table.moose.density.pred [50, 21] <- 404800

table.moose.density.pred [51, 1] <- 3592 # 3.75% of total area (95800*0.0375)
table.moose.density.pred [51, 2] <- 3592         
table.moose.density.pred [51, 3] <- 3592        
table.moose.density.pred [51, 4] <- 3592        
table.moose.density.pred [51, 5] <- 2        
table.moose.density.pred [51, 6] <- 0         
table.moose.density.pred [51, 7] <- 24         
table.moose.density.pred [51, 8] <- 80         
table.moose.density.pred [51, 9] <- 245         
table.moose.density.pred [51, 10] <- 563         
table.moose.density.pred [51, 11] <- 2981
table.moose.density.pred [51, 12] <- 305
table.moose.density.pred [51, 13] <- 2561
table.moose.density.pred [51, 14] <- 25105
table.moose.density.pred [51, 15] <- 12
table.moose.density.pred [51, 16] <- 0
table.moose.density.pred [51, 17] <- 0
table.moose.density.pred [51, 18] <- 6750
table.moose.density.pred [51, 19] <-"Forestry 15%"
table.moose.density.pred [51, 20] <- "5-15-A"
table.moose.density.pred [51, 21] <- 95800

table.moose.density.pred [52, 1] <- 3168 # 3.75% of total area (84500*0.0375)
table.moose.density.pred [52, 2] <- 3168         
table.moose.density.pred [52, 3] <- 3168        
table.moose.density.pred [52, 4] <- 3168        
table.moose.density.pred [52, 5] <- 931        
table.moose.density.pred [52, 6] <- 0         
table.moose.density.pred [52, 7] <- 14         
table.moose.density.pred [52, 8] <- 173         
table.moose.density.pred [52, 9] <- 207         
table.moose.density.pred [52, 10] <- 0         
table.moose.density.pred [52, 11] <- 115
table.moose.density.pred [52, 12] <- 584
table.moose.density.pred [52, 13] <- 1461
table.moose.density.pred [52, 14] <- 10746
table.moose.density.pred [52, 15] <- 0
table.moose.density.pred [52, 16] <- 0
table.moose.density.pred [52, 17] <- 0
table.moose.density.pred [52, 18] <- 13348
table.moose.density.pred [52, 19] <-"Forestry 15%"
table.moose.density.pred [52, 20] <- "5-15-B"
table.moose.density.pred [52, 21] <- 84500

table.moose.density.pred [53, 1] <- 3003 # 3.75% of total area (80100*0.0375)
table.moose.density.pred [53, 2] <- 3003         
table.moose.density.pred [53, 3] <- 3003        
table.moose.density.pred [53, 4] <- 3003        
table.moose.density.pred [53, 5] <- 2        
table.moose.density.pred [53, 6] <- 34         
table.moose.density.pred [53, 7] <- 0         
table.moose.density.pred [53, 8] <- 0         
table.moose.density.pred [53, 9] <- 315         
table.moose.density.pred [53, 10] <- 129         
table.moose.density.pred [53, 11] <- 1167
table.moose.density.pred [53, 12] <- 78
table.moose.density.pred [53, 13] <- 831
table.moose.density.pred [53, 14] <- 14274
table.moose.density.pred [53, 15] <- 11
table.moose.density.pred [53, 16] <- 0
table.moose.density.pred [53, 17] <- 0
table.moose.density.pred [53, 18] <- 10131
table.moose.density.pred [53, 19] <-"Forestry 15%"
table.moose.density.pred [53, 20] <- "5-15-C"
table.moose.density.pred [53, 21] <- 80100

table.moose.density.pred [54, 1] <- 11681 # 3.75% of total area (311500*0.0375)
table.moose.density.pred [54, 2] <- 11681         
table.moose.density.pred [54, 3] <- 11681        
table.moose.density.pred [54, 4] <- 11681        
table.moose.density.pred [54, 5] <- 0        
table.moose.density.pred [54, 6] <- 142         
table.moose.density.pred [54, 7] <- 198         
table.moose.density.pred [54, 8] <- 949         
table.moose.density.pred [54, 9] <- 687         
table.moose.density.pred [54, 10] <- 270         
table.moose.density.pred [54, 11] <- 7077
table.moose.density.pred [54, 12] <- 897
table.moose.density.pred [54, 13] <- 4182
table.moose.density.pred [54, 14] <- 5485
table.moose.density.pred [54, 15] <- 18
table.moose.density.pred [54, 16] <- 4
table.moose.density.pred [54, 17] <- 0
table.moose.density.pred [54, 18] <- 1530
table.moose.density.pred [54, 19] <-"Forestry 15%"
table.moose.density.pred [54, 20] <- "5-15-D"
table.moose.density.pred [54, 21] <- 311500

table.moose.density.pred$moose.density.estimate <- 0.084 + 
                        (table.moose.density.pred$Cut_1_5_area_ha * 0.00000093) + 
                        (table.moose.density.pred$Cut_6_10_area_ha * 0.0000018) + 
                        (table.moose.density.pred$Cut_11_20_area_ha * -0.0000018) + 
                        (table.moose.density.pred$Cut_21_30_area_ha * -0.0000028) + 
                        (table.moose.density.pred$Fire_1_5_area_ha * -0.00000055) + 
                        (table.moose.density.pred$Fire_6_10_area_ha * 0.00000064) + 
                        (table.moose.density.pred$Fire_11_15_area_ha * -0.0000022) + 
                        (table.moose.density.pred$Fire_16_20_area_ha * 0.000032) + 
                        (table.moose.density.pred$Fire_21_25_area_ha * 0.000022) + 
                        (table.moose.density.pred$Fire_26_30_area_ha * -0.000012) + 
                        (table.moose.density.pred$Populus_area_ha * 0.0000081) + 
                        (table.moose.density.pred$river_area_ha * 0.000031) + 
                        (table.moose.density.pred$wetland_area_ha * 0.0000048) + 
                        (table.moose.density.pred$DougFir_area_ha * 0.00000014) + 
                        (table.moose.density.pred$road_loose_km * -0.00024) + 
                        (table.moose.density.pred$road_paved_km * -0.0028) + 
                        (table.moose.density.pred$road_rough_km * -0.0030) + 
                        (table.moose.density.pred$lake_area_ha * 0.00000060)

table.moose.density.pred <- data.table (table.moose.density.pred)

table.moose.density.pred [, WolfDensityFuller := round (3.5 + ((moose.density.estimate * 6) * 3.3))] # FUller wolf density
table.moose.density.pred [, WolfDensityKuzyk := round (((moose.density.estimate * 6) * 5.4) - ((moose.density.estimate * 6)^2 * 0.166))] # Kuzyk density
table.moose.density.pred [, WolfDensityMessier := round ((58.7 * (moose.density.estimate - 0.03))/(0.76 + moose.density.estimate))] # MEssier density
table.moose.density.pred [, WolfDensityAverage := round ((WolfDensityFuller + WolfDensityKuzyk + WolfDensityMessier)/3)] # Averaged density

table.moose.density.pred$wmu <- as.factor(table.moose.density.pred$wmu)

# ggplot (table.moose.density.pred,
#         aes (x = scenario, y = moose.density.estimate,
#              label = wmu)) +
#   geom_point (aes (x = scenario, # classify points by wmu
#                    y = moose.density.estimate,
#                    group = wmu,
#                    colour = wmu)) +
#   geom_line (aes (x = scenario, # classify lines by wmu
#                   y = moose.density.estimate,
#                   group = wmu,
#                   colour = wmu)) +
#   geom_text (aes(label = wmu), # label the points
#              hjust = 0, vjust = 1,
#              check_overlap = TRUE, # make sure the labels don't overlap
#              size = 3) +
#   theme_classic () + 
#   theme (legend.position = "none") + # turn off the legend
#   labs (x = expression ("Scenario"), 
#         y = expression ("Predicted Moose Density - moose per"~km^2)) +
#   scale_y_continuous (breaks = seq (0, 1, 0.1))

ggplot (table.moose.density.pred,
        aes (x = scenario, y = WolfDensityAverage,
             label = wmu)) +
  geom_point (aes (x = scenario, # classify points by wmu
                   y = WolfDensityAverage,
                   group = wmu,
                   colour = wmu)) +
  geom_line (aes (x = scenario, # classify lines by wmu
                  y = WolfDensityAverage,
                  group = wmu,
                  colour = wmu)) +
  geom_text (aes(label = wmu), # label the points
             hjust = 0, vjust = 1,
             check_overlap = TRUE, # make sure the labels don't overlap
             size = 3) +
  theme_classic () + 
  theme (legend.position = "none") + # turn off the legend
  labs (x = expression ("Scenario"), 
        y = expression ("Predicted Wolf Density - wolves per 1,000"~km^2)) +
  scale_y_continuous (breaks = seq (0, 22, 1))
```






