---
title: "Moose TIme Series Analysis"
author: "Tyler Muhly"
date: "16/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## Trends in Moose Density and Proportin of WMU cut

Three WMUs with increasing moose density and proportion of area cut: 5-01, 5-02-A and 5-13-B
Eight WMUs with decreasing moose density and proportion of area cut: 5-02-B, 5-02-C, 5-02-D, 5-03, 5-04, 5-13-A, 5-13-C, 5-14 


```{r, load and plot the data, echo = F, warning = F, message = F}
library (ggplot2)
library (dplyr)

data <- read.csv ("C:\\Work\\caribou\\clus_data\\moose\\analysis_moose_chilcotin_density\\data_chilcotin_moose_density_cut_trend_r.csv")

# plot of density trends by WMU
ggplot (na.omit (data), # drop the NA data
        aes (x = Time, y = density, label = wmu)) + 
  geom_line (aes (color = wmu)) +
  geom_point (aes (color = wmu)) +
  geom_text (aes (label = wmu), hjust = 0, vjust = 0, size = 3) +
  labs (x = expression ("Year"), 
        y = expression ('Estimated Moose Density')) +
  scale_x_continuous (breaks = seq (0, 25, 1)) +
  scale_y_continuous (breaks = seq (0, 1.5, 0.1)) +
  theme_classic()

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-01"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-01",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )
  
print (ggplot (na.omit (dplyr::filter (data, wmu == "5-02-A"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-02-A",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-02-B"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-02-B",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-02-C"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-02-C",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-02-D"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-02-D",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-03"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-03",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-04"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-04",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-13-A"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-13-A",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-13-B"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-13-B",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-13-C"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-13-C",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )

print (ggplot (na.omit (dplyr::filter (data, wmu == "5-14"))) + 
        geom_line (aes (x = Time, y = density),
                   colour = "red") +
        geom_point (aes (x = Time, y = density),
                   colour = "red") +
        geom_line (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_point (aes (x = Time, y = prop_cut_1_10),
                   colour = "blue") +
        geom_line (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        geom_point (aes (x = Time, y = prop_cut_11_30),
                   colour = "green") +
        theme_classic() +
        ggtitle ("WMU 5-14",
                 subtitle = "Red = Density, Blue = Prop. Cut 1 to 10, Green = Prop. Cut 11 to 30") +
        labs (x = expression ("Year"), 
              y = expression ('Density or Proportion')) +
        scale_x_continuous (breaks = seq (0, 25, 1))
        )
```


## Does cutblock proportion predict Moose Density?

- problems with data; few sampels in a WMU adn not at regular itnervals
- combiend data to fit model, i.e., use teh previos sampel, whenever it was taken to predcit currtn sample
- added efefct for 'year' (i.e., time between samples) and interacted with previosu measures to see if time to meaure was improtant
- did soem modled seciton usign AIC
- year efefct not in top models
- average top models did not show partiularly strong efefcts, but the proportin of area cut 11 to 30 years aog in teh last desnity sampel was the strignest preudictor of current density estimate (negative efefct)
- other cefficents mkae snese - last density positively realted to curent density current 'yonu'g cutblock meaure 
- model suggests there is a lag efefct, 11-30 year old (and to a lesser degree 1-10 year old) cutblocks in previosu years had a negative efefct on current moose density esitmates, but current cublocks of both ages did apepar to have a positive efefct; last density also had a positive efefct (makes sense) 

- needs more data to examine properly, but notable result here I htink


```{r, linear regression, current density as a fucntion of last density, current and last cut}
library (lme4)
library (MuMIn)


data.density.regress <- read.csv ("C:\\Work\\caribou\\clus_data\\moose\\analysis_moose_chilcotin_density\\data_chilcotin_moose_density_cut_regress.csv")

lme.density <- glmer (density_curr ~ density_last + # 'global' model withh all potential covariates
                                     prop_cut_1_10_curr + prop_cut_1_10_last +
                                     prop_cut_11_30_curr + prop_cut_11_30_last +
                                     year_last +
                                     (year_last * density_last) +
                                     (year_last * prop_cut_1_10_last) +
                                     (year_last * prop_cut_11_30_last) +
                                     (1 | wmu),
                      data = data.density.regress,
                      family = gaussian (link = 'identity'),
                      na.action = "na.fail")

summary (lme.density)

data.density.regress$lme.predicted <- predict (lme.density)   # Save the predicted values
data.density.regress$lme.residuals <- residuals (lme.density) # Save the residual values

ggplot (data.density.regress, aes (x = lme.predicted, y = density_curr)) + # predicted vs. actual
        geom_point() +
        scale_x_continuous (breaks = seq(0, 1.0, 0.2)) +
        scale_y_continuous (breaks = seq(0, 1.0, 0.2)) +
        geom_text (aes (label = paste (wmu, density_curr, sep = "_")), hjust = 0, vjust = 0, 
                   check_overlap = T,
                   size = 3)

ggplot (data.density.regress, aes (x = lme.predicted, y = lme.residuals)) + # fitted vs. residual
        geom_point () +
        geom_text (aes (label = paste (wmu, density_curr, sep = "_")), hjust = 0, vjust = 0, 
                   check_overlap = T,
                   size = 3) # these look ok; few obs at high predicted densities, but residuals are
                             # not overly large there

ggplot (data.density.regress, aes(lme.residuals)) + # normality of residuals
        geom_histogram (binwidth = 0.05) # there is some skewness here, but not terrible
plot (density (data.density.regress$lme.residuals))
shapiro.test (data.density.regress$lme.residuals) # p-value = 0.3398, so is normal statistically


qqnorm (residuals (lme.density)) # some deviation at high values
qqline (residuals (lme.density)) 


ggplot (data.density.regress, aes (x = (year_last * prop_cut_11_30_last) , y = lme.residuals)) + # covariates vs. residual
        geom_point () +
        geom_text (aes (label = paste (wmu, density_curr, sep = "_")), hjust = 0, vjust = 0, 
                   check_overlap = T,
                   size = 3) 

density_last 
prop_cut_1_10_curr
prop_cut_1_10_last 
prop_cut_11_30_curr
prop_cut_11_30_last 
year_last
(year_last * density_last)
(year_last * prop_cut_1_10_last) 
(year_last * prop_cut_11_30_last)

table.dredge <- dredge (lme.density,
                        beta = "none",
                        rank = "AICc")
table.dredge.aic.2 <- subset (table.dredge, delta < 2)

model.avg.lme.density <- model.avg (table.dredge, subset = delta < 2)
summary (model.avg.lme.density)


table.dredge.aic.10 <- subset (table.dredge, delta < 10)









model.top.lme.density <- glmer (density_curr ~ density_last + 
                                               prop_cut_1_10_curr + prop_cut_1_10_last +
                                               prop_cut_11_30_curr + prop_cut_11_30_last +
                                               (1 | wmu),
                                  data = data.density.regress,
                                  family = gaussian (link = 'identity'),
                                  na.action = "na.fail")

data.density.regress$top.lme.predicted <- predict (model.top.lme.density)   # Save the predicted values
data.density.regress$prob.model.top.lme.density <- exp(data.density.regress$top.lme.predicted)/(1+exp(data.density.regress$top.lme.predicted))

data.density.regress$top.lme.residuals <- residuals (model.top.lme.density) # Save the residual values

ggplot (data.density.regress, aes (x = top.lme.predicted, y = density_curr)) + # predicted vs. actual
        geom_point() +
        scale_x_continuous (breaks = seq(0, 1.0, 0.2)) +
        scale_y_continuous (breaks = seq(0, 1.0, 0.2)) +
        geom_text (aes (label = paste (wmu, density_curr, sep = "_")), hjust = 0, vjust = 0, 
                   check_overlap = T,
                   size = 3)

ggplot (data.density.regress, aes (x = top.lme.predicted, y = top.lme.residuals)) + # fitted vs. residual
        geom_point () +
        geom_text (aes (label = paste (wmu, density_curr, sep = "_")), hjust = 0, vjust = 0, 
                   check_overlap = T,
                   size = 3) 

ggplot (data.density.regress, aes(top.lme.residuals)) + # normality of residuals
        geom_histogram (binwidth = 0.05) 
plot (density (data.density.regress$top.lme.residuals))
shapiro.test (data.density.regress$top.lme.residuals) # p-value = 0.3119, so is normal statistically


qqnorm (residuals (model.top.lme.density)) 
qqline (residuals (model.top.lme.density)) 



ggplot (data.density.regress, aes (x = prop_cut_11_30_last, y = prob.model.top.lme.density)) + # fitted vs. residual
        geom_point () 


```





```{r, Granger test}
library (lmtest)

grangertest (data = na.omit (data), 
             density ~ prop_cut_1_10,
             order = 3,
             na.action = na.omit)

```

