---
title: "Chilcotin Cariobu Local Population Unit (LPU) critical habitat protection scenario."
author: "Tyler Muhly"
date: "July 22, 2019"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Scenario Background
This habitat protection scenario tests the influence of protecting newly designated 'critical habitat' for caribou on timber harvest flows, i.e., allowable annual cut (AAC), caribou habitat quality, moose habitat quality, moose density (?) and wolf density (?), over time, using the caribou and land use simulator (CLUS). Critical habitat for caribou was spatially defined by the government of British Columbia (source?). Provincial caribou biologists and recovery program leads defined how each type of critical habitat would be protected from forestry activity within the context of this scenario and in consideration of the functionality of the CLUS model. 

The CLUS model in general was designed to support caribou recovery planning, as a tool to explore and discuss the implications of alternative management actions to caribou and other resource values. The tool does not necessarily provide accurate or optimal solutions for caribou recovery but can help identify preferred recovery actions.  

# Scenario Study Area
This scenario was developed to support caribou recovery planning in the Chilcotin local population unit (LPU) of caribou. This LPU consists of the Itcha-Ilgachuz, Rainbows and Charlotte Alplands caribou herds, and constitutes the southernmost LPU of the Northern Mountain Caribou Designatible Unit (DU 7). These caribou are classified as *Threatened* under Canada's *Species at Risk Act*. 

The Itcha-Ilgachuz herd is considered to be of significant conservation importance provincially because it is the largest and highest density herd in west-central British Columbia (cite herd plan). However, the herd declined 17.2% annually between 2014 and 2018, and the habitat has experienced significant amounts of timber harvesting, associated road development, wildfire and mountain pine beetle infestations (cite herd plan). In addition, the 2019 population census showed a 40% popualion decline from 2018, and at that rate of decline, the herd would be functionally extirpated (i.e., less than 20 animals) in eight years (Carolyn Shores, Provincial Cariobu Biologist, pers. comm.). There is an urgent need to develop an effective recovery plan for these caribou. 

The Chilcotin LPU overlaps the following timber supply areas (TSAs) and timber supply blocks (TSBs):
* Great Bear Rainforest (GBR) North TSA
* GBR South TSA, TSB V 47C
* Prince George TSA, TSB 24D
* Quesnel TSA, TSBs 26B and 26A
* Williams Lake TSA, TSBs 29A, 29B, 29C, 29E and 29I
The overlap with the Prince George TSA is minimal (i.e., a total of 149 hectares of the timber harvest land base (THLB) in that TSA), and most of the GBR North TSA that overlaps the LPU is in Tweedsmuir Park (i.e., critical habitat overlaps only 40 hectares of the THLB in that TSA). No THLB overlaps critical habitat in the GBR South TSA. Thus, the impacts of new caribou habitat protections to timber supply in these TSAs are expected to be minimal or null. The AAC's in the GBR South and GBR North TSAs were established through legislation. Thus, they are unlikely to be quickly changed if new caribou protection orders were established in those areas. Therefore, the focus of this scenario is on impacts of critical habitat protections in the Quesnel TSA (overlaps 199,343 ha of THLB) and Williams Lake TSA (overlaps 557,414 ha of THLB).
 
Existing habitat protections for caribou (e.g., caribou-specific ungulate winter ranges) and for wildlife and ecosystems more broadly (e.g., provincial parks), are addressed in this scenario as parameters in the CLUS model. These primarily include 219,152 ha designated as 'conditional harvest' and 193,470 ha as 'no-harvest' zones within provincial parks or wildlife habtiat areas (WHAs) (cite herd plan). These existing protections are implemented in all model scenarios. 

# Scenario Habitat Protections
Critical habitat for caribou in the Chiltoin LPU consists of five types:
* high elevation winter range (HEWR)
* high elevation summer range (HESR)
* low elevation winter range (LEWR)
* low elevation summer range (LESR)
* matrix
Each of these types corresponds to a specific habitat protection definition, based on its understood importance to caribou population sustainability. This analysis uses a draft version of the spatial critical habitat data for the Chilcotin LPU as defined by British Columbia caribou biologists, dated July 31, 2019. The habitat types are consistent with the federal recovery strategy for southern mountain caribou ([Environment Canada 2014](https://www.registrelep-sararegistry.gc.ca/virtual_sara/files/plans/rs_woodland_caribou_bois_s_mtn_pop_0114_e.pdf)), although the protection definitions for some types are ambiguous within the federal strategy     

HEWR and HESR critical habitat types (often referred to as 'core' habitat) typically consist of areas heavily and regularly used by caribou. Parks, WHAs and ungulate winter ranges (UWRs) already exist over many of these areas to protect this habitat. Management plans for caribou typically recommend full protection of these types from forest harvest [Environment Canada 2014](https://www.registrelep-sararegistry.gc.ca/virtual_sara/files/plans/rs_woodland_caribou_bois_s_mtn_pop_0114_e.pdf); also cite herd plan). 

LEWR and LESR are also regularly used by caribou, but may not be as protected by existing orders and regulations. Indeed, the current priority proposed recovery actions for the Itcha-Ilgachuz herd are to protect LEWR and LESR critical habitat from further timber harvesting and development (cite herd plan). However, currently, 97% of the Itcha-Ilgachuz herd’s LEWR is available for timber harvesting (cite herd plan), and thus there is uncertainty and concern over how these proposed actions may influence forest harvest and the AAC in the Williams Lake and Quesnel TSA's. In addition, predator removal has been proposed for the Chilcotin LPU, but it's long-term effectiveness as a recovery action depends on concurrent habitat protection.  

Matrix habitat is not regularly used by caribou, and thus there are typically little or no existing protections for caribou in this habitat type. Matrix habitat areas are typically large and adjacent to HEWR, HESR, LEWR or LESR habitat types. The intent of matrix is to provide a 'buffer' against high predator density or use of HEWR, HESR, LEWR or LESR habitat types, allowing these types to function more effectively as refugia from predators. Thus, some level of reduction in forest harvest in matrix habitat is recommend in caribou plans. Specifically, the federal recovery plan for southern mountain caribou recommends maintaining matrix habitat that supports less than 3 wolves per 1,000km^2^, and the Itcha-Ilgachuz herd plan recommends maintaining habitat 'disturbance' below 35% within matrix areas.

How habitat 'disturbance' is defined is somewhat ambiguous and requires clarification here. Disturbance and the 35% threshold were originally defined in the federal boreal caribou recovery strategy [Environment Canada 2012](https://www.registrelep-sararegistry.gc.ca/virtual_sara/files/plans/rs_caribou_boreal_caribou_0912_e1.pdf). A scientific assessment was completed to support this strategy [Environment Canada 2011](https://www.registrelep-sararegistry.gc.ca/virtual_sara/files/ri_boreal_caribou_science_0811_eng.pdf), and included a regression model relating habitat disturbance in caribou population ranges to probability that boreal caribou populations are stable or growing (i.e., $\lambda$ $\geq$ 1). There, habitat disturbance was defined as anthropoegnic disturbances (i.e., 'human footprint', such as cutblocks and roads) clearly visible in 1:50,000 resolution satellite imagery, and burnt areas less than 40 years old, as defined in the national fire database [link](http://cwfis.cfs.nrcan.gc.ca/ha/nfdb?wbdisable=true). Human footprint was also buffered by 500m. The relationship between disturbance and probability of $\lambda$ $\geq$ 1 is continuous, but a 35% disturbance threshold was identified as a reasonable threshold to achieve a sustainable caribou population. This model and management threshold has since been applied to some critical habitat types for southern mountain caribou. However, the model has not been tested or validated for southern mountain caribou habtiat, and often disturbance is measured differently from how it was defined in the boreal analysis. Thus, the disturbance model and management threshold should be used with caution and under the assumption that it is highly uncertain. 

Forest harvest constraints for each critical habitat type for this scenario are summarized in Table 1.
```{r, create the protection type data.table}
library (data.table)
library (kableExtra)
tab_protection_type <- data.table (Habitat = c ('High Elevation Summer Range (HESR)', 
                                             'High Elevation Winter Range (HEWR)', 
                                             'High Elevation Winter and Summer Range (HEWSR)', 
                                             'Low Elevation Summer Range (LESR)', 
                                             'Low Elevation Winter Range (LEWR)', 
                                             'Low Elevation Winter and Summer Range (LEWSR)',
                                             'Matrix'),
                                  Constraint = c ('No Harvest', 
                                                  'No Harvest', 
                                                  'No Harvest', 
                                                  'No Harvest', 
                                                  'No Harvest',
                                                  'No Harvest',
                                                  'Less than 20% forest age less than 40 years old')
                                  #,habitat.type.id = c (1, 2, 3, 4, 5, 6, 7)
                                  )
kable (tab_protection_type,
       caption = "Table 1. Caribou critical habtiat types and constraints used in this scenario.") %>%
  kable_styling (position = "left")
```
# Scenario Outputs
Outputs from CLUS relevant to this scenario include AAC, caribou habitat quality and moose habitat quality. AAC outptus can be used to evaluate how new protections might impact forest harvest oeprations ability to achieve AAC targets in the William's Lake and Quesnel TSA's. Habitat quality outputs for wildlife are indicated by resource selection function (RSF) scores, which can be used to indicate quality of habitat available to caribou. 

Outputs should be evaluated relative to a scenario without the protections defined here (i.e., a "business-as-usual" scenario) rather than as an absolute representation of impacts to AAC and habitat.


 


## Create Scenario Habitat Data
Here we assing a unique integer identifier of each critical habitat type. We then create a raster of these unique identifiers that will be used to spatially assign forest harvest contraints. We also create an 'empty' table that represents these harvest contraints. Harvest contraints for each type are defined below.

```{r, Create Chilctoin LPU critical habitat raster and load to postgreSQL}
# Here I am loading the 'raw' spatial polygonal critical habitat and rasterzizing it to the provincal hectares BC standard
# Note that the polygonal dtat is not currently loaded into the clusdb becuase it is draft, and thus has not been released to the public or for wide distribution within government
library (here)
library (sf)
library (fasterize)
library (keyring)
library (data.table)
source (paste0 (here(),"/R/functions/R_Postgres.R")) # postgres functions

# load the data
crit.habitat <- sf::st_read (dsn = "C:\\Work\\caribou\\clus_data\\caribou\\critical_habitat\\BC\\chilcotin_lpu\\eis_19_004_bc_core_chilcotin_v20190731.gdb", 
layer = "BCHabitat_20190731")
crit.habitat$habitat_type_id <- as.character (crit.habitat$BCHab_code) # create unique field id
crit.habitat$habitat_type_id [crit.habitat$habitat_type_id == "HESR"] <- "1"
crit.habitat$habitat_type_id [crit.habitat$habitat_type_id == "HEWR"] <- "2"
crit.habitat$habitat_type_id [crit.habitat$habitat_type_id == "HEWSR"] <- "3"
crit.habitat$habitat_type_id [crit.habitat$habitat_type_id == "LESR"] <- "4"
crit.habitat$habitat_type_id [crit.habitat$habitat_type_id == "LEWR"] <- "5"
crit.habitat$habitat_type_id [crit.habitat$habitat_type_id == "LEWSR"] <- "6"
crit.habitat$habitat_type_id [crit.habitat$habitat_type_id == "Matrix"] <- "7"
crit.habitat$habitat_type_id <- as.integer (crit.habitat$habitat_type_id)

# needs to be cast to a multipolygon, because some features are 'multisurface', whatever the heck that is
crit.habitat <- sf::st_cast (crit.habitat, to = "MULTIPOLYGON")

# Create the hectares bc raster 
ProvRast <- raster(nrows = 15744, ncols = 17216, 
                   xmn = 159587.5, xmx = 1881187.5, 
                   ymn = 173787.5, ymx = 1748187.5, 
  crs = st_crs (getSpatialQuery ("SELECT * FROM public.rmp_lu_sp_polygon LIMIT 1"))$proj4string, # getting the spatial projection from existing data; should be "+proj=aea +lat_1=50 +lat_2=58.5 +lat_0=45 +lon_0=-126 +x_0=1000000 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
                  resolution = c(100, 100), vals = 0
)

# fasterize - convert the polygon to the provincal raster
crit.habitat.ras <- fasterize::fasterize (sf = crit.habitat, 
                                          raster = ProvRast, 
                                          field = "habitat_type_id")

# Create empty constraint table
zone_crit_habitat <- data.table (habitat_type_id = integer (), type = character (), 
                                 variable = character (),  threshold = numeric (), 
                                 reference_zone = character (), percentage = numeric (), 
                                 ndt = integer (), label = character ())

# get the ID from the raster
habitat_type_id <- data.table (unique (c (t (raster::as.matrix (crit.habitat.ras))))) # Note that some polygons < 1ha in size will not get an ID here
habitat_type_id <- habitat_type_id [!(is.na (V1)),] # drop NA values
```

### HESR
HESR is defined as a 'no harvest' area with the intent of protecting this habitat type because it is heavily or regularly used by caribou. This appears to be consistent with Environment Canada's recommendations for how to manage this habitat in their recovery strategy. 
```{r, HESR}
library (data.table)
# assigned 'no harvest'
tab_hesr <- data.table (habitat_type_id = 1, # HESR code
                         type = 'nh', # set as no harvest
                         variable = '', 
                         threshold = 0, 
                         reference_zone = 'rast.zone_crit_habitat_chilcotin', # raster to be loaded into pg db
                         percentage = 0, 
                         ndt = 0, 
                         label = 'hesr')
zone_crit_habitat <- rbind (zone_crit_habitat, tab_hesr)
rm (tab_hesr)
gc ()
```

### HEWR
HEWR is defined as a 'no harvest' area with the intent of protecting this habitat type because it is heavily or regularly used by caribou. This appears to be consistent with Environment Canada's recommendations for how to manage this habitat in their recovery strategy. 
```{r, HEWR}
library (data.table)
# assigned 'no harvest'
tab_hewr <- data.table (habitat_type_id = 2, # HEWR code
                         type = 'nh', # set as no harvest
                         variable = '', 
                         threshold = 0, 
                         reference_zone = 'rast.zone_crit_habitat_chilcotin',
                         percentage = 0, 
                         ndt = 0, 
                         label = 'hewr')
zone_crit_habitat <- rbind (zone_crit_habitat, tab_hewr)
rm (tab_hewr)
gc ()
```

### HEWSR
HEWSR is defined as a 'no harvest' area with the intent of protecting this habitat type because it is heavily or regularly used by caribou. This appears to be consistent with Environment Canada's recommendations for how to manage this habitat in their recovery strategy. 
```{r, HEWSR}
library (data.table)
# assigned 'no harvest'
tab_hewsr <- data.table (habitat_type_id = 3, # HEWSR code
                         type = 'nh', # set as no harvest
                         variable = '', 
                         threshold = 0, 
                         reference_zone = 'rast.zone_crit_habitat_chilcotin',
                         percentage = 0, 
                         ndt = 0, 
                         label = 'hewsr')
zone_crit_habitat <- rbind (zone_crit_habitat, tab_hewsr)
rm (tab_hewsr)
gc ()
```

### LESR
LESR is defined as a 'no harvest' area with the intent of protecting this habitat type because it is heavily or regularly used by caribou. This appears to be consistent with Environment Canada's recommendations for how to manage this habitat in their recovery strategy. 
```{r, LESR}
library (data.table)
# assigned 'no harvest'
tab_lesr <- data.table (habitat_type_id = 4, # LESR code
                         type = 'nh', # set as no harvest
                         variable = '', 
                         threshold = 0, 
                         reference_zone = 'rast.zone_crit_habitat_chilcotin',
                         percentage = 0, 
                         ndt = 0, 
                         label = 'lesr')
zone_crit_habitat <- rbind (zone_crit_habitat, tab_lesr)
rm (tab_lesr)
gc ()
```

### LEWR
LEWR is defined as a 'no harvest' area with the intent of protecting this habitat type because it is heavily or regularly used by caribou. This appears to be consistent with Environment Canada's recommendations for how to manage this habitat in their recovery strategy. 
```{r, LEWR}
library (data.table)
# assigned 'no harvest'
tab_lewr <- data.table (habitat_type_id = 5, # LEWR code
                         type = 'nh', # set as no harvest
                         variable = '', 
                         threshold = 0, 
                         reference_zone = 'rast.zone_crit_habitat_chilcotin',
                         percentage = 0, 
                         ndt = 0, 
                         label = 'lewr')
zone_crit_habitat <- rbind (zone_crit_habitat, tab_lewr)
rm (tab_lewr)
gc ()
```

### LEWSR
LEWSR is defined as a 'no harvest' area with the intent of protecting this habitat type because it is heavily or regularly used by caribou. This appears to be consistent with Environment Canada's recommendations for how to manage this habitat in their recovery strategy. 
```{r, LEWSR}
library (data.table)
# assigned 'no harvest'
tab_lewsr <- data.table (habitat_type_id = 6, # LEWSR code
                         type = 'nh', # set as no harvest
                         variable = '', 
                         threshold = 0, 
                         reference_zone = 'rast.zone_crit_habitat_chilcotin',
                         percentage = 0, 
                         ndt = 0, 
                         label = 'lewsr')
zone_crit_habitat <- rbind (zone_crit_habitat, tab_lewsr)
rm (tab_lewsr)
gc ()
```

### Matrix
Matrix areas allow for some forest harvest. Here we use a 20% area threshold of 40 year old forest definition as a means to limit the amount of early seral forest in matrix habitat. Early seral forest is thought to be a critical driver of moose popualtions, where higher amounts of early seral forest is thought to contribute to increased moose forage and moose densities (Wam et al. 2010; Bjørneraas et al. 2011; Serrouya et al. 2011). This subsequently is thought to support higher predator (ie.. wolf) densities and higher predation rates on caribou (Wittmer et al. 2007; Lesmerises et al. 2012). The 20% area threshold is based on a statistical relationship calculated between 'disturbed' habitat (defined as areas within 500 m of less than 40 year old cutblocks or roads, or within less than 40 year old burns) and the density of roads and cutblocks less than 40 years old with landscape units [Muhly 2016](https://www2.gov.bc.ca/assets/gov/farming-natural-resources-and-industry/forestry/stewardship/forest-analysis-inventory/tsr-annual-allowable-cut/wildlife-analysis/pg_tsr_caribou_20161128.pdf). The statistical model indicated that a cutblock area of 18.5% was equivalent to 35% habitat disturbance.

Alternatives:
 - use Doug LEwis model to calculate moose density and
 - develop model of raltionshp between moose dnesity and ealy seral habtiat 

```{r, Matrix}
library (data.table)
# assigned '20% area threshold of 40 year old forest
tab_matrix <- data.table (habitat_type_id = 7, # Matrix code
                          type = 'ge', # set as no harvest
                          variable = 'age', 
                          threshold = 40, 
                          reference_zone = 'rast.zone_crit_habitat_chilcotin',
                          percentage = 20, 
                          ndt = 0, 
                          label = 'matrix')
zone_crit_habitat <- rbind (zone_crit_habitat, tab_matrix)
rm (tab_matrix)
gc ()

```

## Zone Constraint Raster
Here I commit the zone constraint raster to the PostgreSQL database, for use in the CLUS model.
```{r, commit constraint raster to clus pgdb}
library (here)
source (paste0 (here(),"/R/functions/R_Postgres.R"))

# save the geotiff
writeRaster (crit.habitat.ras, file = "chilcotin_crit_habitat.tif", format = "GTiff", overwrite = TRUE)
# upload to it to the db
system ("cmd.exe", input = paste0 ('raster2pgsql -s 3005 -d -I -C -M -N 2147483648  ', here(), '/R/params/chilcotin_crit_habitat.tif -t 100x100 rast.zone_crit_habitat_chilcotin | psql -d clus'), show.output.on.console = F, invisible = TRUE)

```


## Zone Constraint Table
Here I commit the critical habtiat constraint table to the PostgreSQL database, for use in the CLUS model.
```{r, commit constraint table to clus pgdb}

df <- as.data.frame (zone_crit_habitat)
df$ndt <- as.integer (0)
df$habitat_type_id < -as.integer (df$habitat_type_id) # assign integer
df$percentage <- as.numeric (df$percentage) # assign integer

conn <- DBI::dbConnect (dbDriver("PostgreSQL"), host=keyring::key_get('dbhost', keyring = 'postgreSQL'), dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), port='5432' ,user=keyring::key_get('dbuser', keyring = 'postgreSQL'), password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

DBI::dbWriteTable (conn, c("public", "zone_crit_habitat_chilcotin"), value = df, row.names = FALSE, overwrite = TRUE) 

dbDisconnect(conn)
```


# Literature Cited
Bjørneraas, K., Solberg, E. J., Herfindal, I., Van Moorter, B., Rolandsen, C. M., Tremblay, J. P., ... & Astrup, R. (2011). Moose Alces alces habitat use at multiple temporal scales in a human-altered landscape. Wildlife Biology, 17(1), 44-54.

Lesmerises, F., Dussault, C., & St-Laurent, M. H. (2012). Wolf habitat selection is shaped by human activities in a highly managed boreal forest. Forest ecology and management, 276, 125-131.

Serrouya, R., McLellan, B. N., Boutin, S., Seip, D. R., & Nielsen, S. E. (2011). Developing a population target for an overabundant ungulate for ecosystem restoration. Journal of Applied Ecology, 48(4), 935-942.

Wam, H. K., Hjeljord, O., & Solberg, E. J. (2010). Differential forage use makes carrying capacity equivocal on ranges of Scandinavian moose (Alces alces). Canadian Journal of Zoology, 88(12), 1179-1191.

Wittmer, H. U., McLellan, B. N., Serrouya, R., & Apps, C. D. (2007). Changes in landscape composition influence the decline of a threatened woodland caribou population. Journal of animal ecology, 76(3), 568-579.