---
title: "Test of fire Castor using a small area in the central of the province"
author: "Elizabeth Kleynhans"
date: "21 July 2022"
output:
  html_document: 
    keep_md: yes
editor_options: 
  chunk_output_type: console
---

<!--
Copyright 2020 Province of British Columbia
 
Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at
 
http://www.apache.org/licenses/LICENSE-2.0
 
Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.-->

## Overview

This script acts as a test for fire Castor to test how it populates data and interacts with the other Castor modules in a small area of the province so that it runs quickly.


### Fire
FireCastor is both climate and vegetation sensitive i.e. the number of ignitions, probability of escape and spread, and final fire size are all impacted by climate and vegetation attributes. Climate data is obtained from climateCastor which is basically an interface between climR and Castor i.e. it gets the necessary climate data to run the fire simulations. Vegetation data is originally sampled from the VRI and then gets updated over time through forestryCastor, growingStockCastor and fireCastor. If an area is harvested or burned its age and volume get set back to zero, otherwise age and volume are incremented according to growth and yield calculations. 

The process of a wildfire is as follows: 1.) the number of ignitions is statistically estimated, 2.) the location of those ignitons is also statistically determined through an escape raster which details the probability of igntion, 3.) where the fire spreads is determined through a percolation model which weights the probability of spread into each pixel according to fuel type, climate, slope, distance to infrastructure/roads etc. Lastly how big the fire gets is determined through a fire size model. 

#### Usage
Set parameters for running the model simulation below and run the code chunk.


```{r module_usage}
Sys.setenv(JAVA_HOME='C:\\Program Files\\Java\\jdk-14.0.1') 
#library(climRdev)
#dbCon <- data_connect() ##connect to climate database

library (data.table)
library(dplyr)
source (paste0(here::here(), "/R/functions/R_Postgres.R"))

moduleDir <- file.path(paste0(here::here(), "/R/SpaDES-modules"))
inputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/fireCastor/inputs")) %>% reproducible::checkPath(create = TRUE)
outputDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/fireCastor/outputs")) %>% reproducible::checkPath (create = TRUE)
cacheDir <- file.path(paste0(here::here(), "/R/SpaDES-modules/tests"))
times <- list(start = 0, end = 2) # 5 year interval; 200 years = 40 intervals
parameters <-  list (
        .progress = list (type = NA, interval = NA),
        .globals = list (),
        dataCastor = list(saveCastorDB = TRUE,
                          #useCastorDB=""
                          sqlite_dbname = "fire_castor_test",
                          dbHost=keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                    dbName = keyring::key_get('dbname', keyring = 'postgreSQL'),
                    dbPort='5432' ,
                    dbUser=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                    dbPass= keyring::key_get('dbpass', keyring = 'postgreSQL'),
                          nameBoundaryFile = "castor_stsm_compare.bounds_tsa99", 
                          nameBoundaryColumn = "tsa_name", 
                          nameBoundary = "tsa99", 
                          nameBoundaryGeom = 'wkb_geometry',
                          nameCompartmentRaster = "castor_stsm_compare.rast_bounds_tsa99", 
                          nameCompartmentTable = "castor_stsm_compare.vat_bounds_tsa99", 
                          nameMaskHarvestLandbaseRaster = 'rast.bc_thlb2022',  
                          
                          nameZoneRasters = c("rast.zone_cond_beo", 
                                               "rast.zone_cond_vqo", 
                                               "rast.zone_wha_2021", 
                                               "rast.zone_uwr_2021",  
                                               "rast.zone_cond_nharv", 
                                               "rast.zone_cond_fsw", 
                                               "rast.zone_cond_cw"),
                          nameZoneTable = "zone.constraints", 
                          nameYieldsRaster = "rast.ycid_vdyp_2020_adj",
                          nameYieldTable = "yc_vdyp_2020_adj", 
                          nameYieldsCurrentRaster = "rast.ycid_tipsy_current_2020",
                          nameYieldCurrentTable = "tipsy_prov_current_2020",
                          nameYieldsTransitionRaster = "rast.ycid_tipsy_prov_2020", 
                          nameYieldTransitionTable = "tipsy_prov_2020", 
                          nameForestInventoryRaster = "rast.vri2022_id", 
                          nameForestInventoryKey = "feature_id", 
                          nameForestInventoryTable = "vri.veg_comp_lyr_r1_poly2023",
                          nameForestInventoryAge = "proj_age_1",  
                          nameForestInventoryHeight = "proj_height_1",
                          nameForestInventoryCrownClosure = "crown_closure",                                              nameForestInventoryTreed = "bclcs_level_2",
                          nameForestInventoryBasalArea= "basal_area",
                          nameForestInventoryQMD = "quad_diam_125",
                          nameForestInventorySiteIndex = "site_index" 
                          ),
  forestryCastor = list(harvestBlockPriority = " age DESC ",
                        activeZoneConstraint = c("rast.zone_cond_beo", 
                                                 "rast.zone_cond_vqo", 
                                                 "rast.zone_wha_2021", 
                                                 "rast.zone_uwr_2021",  
                                                 "rast.zone_cond_nharv", 
                                                 "rast.zone_cond_fsw", 
                                                 "rast.zone_cond_cw")
                        ),
  blockingCastor = list(blockMethod = 'pre', 
                              patchZone = 'rast.zone_cond_beo',
                              patchVariation = 6,
                              nameCutblockRaster ="rast.cns_cutblk_2023",
                              useLandingsArea = FALSE),
  growingStockCastor = list (periodLength = 1,
                             maxYieldAge = 250),
  roadCastor = list(roadMethod = 'mst', # pre mst
                  nameCostSurfaceRas = 'rast.rd_cost_surface', 
                  nameRoads =  'rast.ce_road_2022'),
  disturbanceCastor = list(calculateInterval =  1, 
                             criticalHabitatTable = "vat.vat_bc_crithab_and_herd",
                             criticalHabRaster = "rast.bc_crithab_and_herd",
                             permDisturbanceRaster = "rast.mine_ag_wind_rail",
                             recovery = 300), # no road recovery
  climateCastor = list(calculateInterval = 1,
                    climateData = "future", # if want observed data put "observed" here
                    gcm = c("MPI-ESM1-2-HR"), # for observed data put "none",
                    gcmname = c("MPI"), # for observed data put "climatena",
                    ssp = c("ssp370"), # for observed data put "none",
                    run = c("r10i1p1f1"),
                    climateYears = 2018: 2040, # note the start year needs to be 2 yrs before your year of interest to calculate CMI3yr
                    maxRun = 3, 
                    nameClimateIdnoRast = "rast.climate_prism_base_layer",
                    nameClimateTable = "vat.climate_prism_lat_lon_lookup",
                    vars_aoi=c("PPT_03","PPT_04", "PPT_05","PPT_06","PPT_07", "PPT_08", "PPT_09","Tmax_04", "Tmax_05", "Tmax_06", "Tmax_07", "Tmax_08", "Tmax_09", "Tave_03","Tave_04", "Tave_05", "Tave_06", "Tave_07", "Tave_08", "Tave_09", "Tmin_03", "Tmin_04", "Tmin_05", "Tmin_06", "Tmin_07", "Tmin_08" ,"CMD_04", "CMD_05", "CMD_06", "CMD_07", "CMD_08", "CMI_03", "CMI_04", "CMI_05", "CMI_06", "CMI_07", "CMI_08", "CMI_09"),
                    nameProvCMITable = "public.prov_cmi_ave",
                    vars_prov = c("CMI05", "CMI06", "CMI07", "CMI08")),
  fireCastor = list(calculateInterval =1,
                    ignitionMethod = 'poissonProcess', # options are poissonProcess, historicalDist, static
                    #calendarStartYear = 2020,
                    nameFrtRaster = "rast.frt",
                    nameAspectRaster = "rast.bc_ha_aspect",
                    nameSlopeRaster = "rast.bc_ha_slope",
                    nameDistInfrastructureRaster = "rast.dist_infrastructure",
                    nameRoadsRast = "rast.ce_road_2019",
                    #recovery = 300,
                    nameElevationRaster = "rast.dem",
                    #nameClimateIdnoRast="rast.climate_prism_base_layer",
                    #nameClimateTable = "vat.climate_prism_lat_lon_lookup",
                    simStartYear = 2020,
                    nameBecRast = "rast.bec_current",
                    nameBecTable = "vat.bec_zone_vat",
                    #nameForestInventoryRaster = "rast.vri2022_id",
                    #nameForestInventoryTable = "vri.veg_comp_lyr_r1_poly2022",
                    #nameForestInventoryKey = "feature_id",
                    nameForestInventorybclcs_level_1 = "bclcs_level_1",
                    nameForestInventorybec_zone_code = '99999',
                    pixelid_10kmRast = "rast.pixelId10km",
                    nameFirepixel10km = "vat.spatially_varying_10km_vat",
                    numberFireReps = 1)
)

modules <- list("dataCastor", 
                "growingStockCastor", 
                "blockingCastor",
                "roadCastor",
                "forestryCastor", 
                "disturbanceCastor",
                "climateCastor",
                "fireCastor"
                #"uploadCastor",
                #"volumebyareaReportCastor"
                )

scenario = data.table (name = "Stsm_Castor_compare",
                       description = "Business-as-usual case. Harvest flow = 950,000m3/yr. Adjacency = 3m. Oldest first.")


harvestFlow <- rbindlist(list(data.table(compartment ="tsa99",
                                     partition = ' age > 79 AND vol > 149 ', 
                                     period = rep( seq (from = 1,
                                                      to = 250, 
                                                      by = 1),
                                                1), 
                                     flow = 136000, # 136,000m3/year 
                                     partition_type = 'live') 
))


patchSizeDist<- data.table(ndt= c(1,1,1,1,1,1,
                                  2,2,2,2,2,2,
                                  3,3,3,3,3,3,
                                  4,4,4,4,4,4,
                                  5,5,5,5,5,5), 
                           sizeClass = c(40,80,120,160,200,240), 
                           freq = c(0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.3,0.3,0.1,0.1,0.1, 0.1,
                                    0.2, 0.3, 0.125, 0.125, 0.125, 0.125,
                                    0.1,0.02,0.02,0.02,0.02,0.8,
                                    0.3,0.3,0.1,0.1,0.1, 0.1))
#ds_out_summary <- data.table(RUN = "r10i1p1f1", PERIOD = 2020:2030, AveCMI = 91)

objects <- list(harvestFlow = harvestFlow, 
                patchSizeDist = patchSizeDist, 
                scenario = scenario)
                #ds_out_summary = ds_out_summary)

paths <- list(cachePath = cacheDir,
              modulePath = moduleDir,
              inputPath = inputDir,
              outputPath = outputDir)

mySim <- SpaDES.core::simInit(times = times, 
                 params = parameters, 
                 modules = modules,
                 objects = objects, 
                 paths = paths,
                 )

# outputs to keep; these are tables that get used in the uploader
SpaDES.core::outputs(mySim) <- data.frame (objectName = c("harvestReport",
                                             "growingStockReport",
                                             "disturbanceReport", 
                                             "volumebyareaReport"
                                             ))

#Run the model 1 time
system.time({mysimout<-SpaDES.core::spades(mySim)})

#Run the model with experiment
#sims3 <- experiment(mySim, replicates = 2)

#Profile the model
#profvis::profvis({system.time({mysimout<-spades(mySim)})})


```


Check that things are working as I think they should:
```{r}
library(igraph)
library(DiagrammeR)
library(SpaDES)
depsEdgeList(mySim, FALSE)
moduleDiagram(mySim, type="Plot")  
modDia <- depsGraph(mySim, plot = TRUE)


objectDiagram(mySim)
eventDiagram(mySim)

```

Make some maps
```{r}
library(RSQLite)
library(raster)

sqlite <- dbDriver("SQLite")


castordb <- dbConnect(sqlite,"C:/Work/caribou/castor/R/SpaDES-modules/fireCastor/fire_castor_test_castordb.sqlite")
ras.info<-dbGetQuery(castordb, "Select * from raster_info limit 1;")
areaBurned<-raster(extent(ras.info$xmin, ras.info$xmax, ras.info$ymin, ras.info$ymax), nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow, vals =0)
    

areaBurned[]<-probFireRasts$prob_ignition_lightning

plot(areaBurned)

# Two issues, my spread values for these locations are too high and I seem to be missing lightning info. Correct these two bugs
# the issues are in FRT 10. GO FIX

x<-mySim$probFireRasts[prob_ignition_spread>0.8,]



```

```{r}
# Plot map of fwveg for morice TSA
climdat<-merge(mySim$pts[,"pixelid"], results2, by.x="pixelid", by.y="pixelid", all.x=TRUE)

ras.info<-dbGetQuery(mySim$castordb, "Select * from raster_info limit 1;")
area<-raster(extent(ras.info$xmin, ras.info$xmax, ras.info$ymin, ras.info$ymax), nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow, vals =0)
    
area[]<-mySim$probFireRasts$prob_tot_ignit

plot(area)

par(xpd = FALSE)
plot(ras.climate,
  col = c("forestgreen", "tan", "grey"),
  xaxt = 'n',
  yaxt = 'n'
)

par(xpd = TRUE)
legend(
  "right",
  legend = c("C-2", "C-3", "C-5", "C-7", "D-1/2","M-1/2","N", "O-1a/b", "S-1","S-2", "W"),
  fill = c(
    "grey",
    "forestgreen",
    "tan",
    "lightgreen",
    "orange",
    "coral",
    "yellow",
    "pink",
    "purple",
    "violet",
    "royalblue"
  ),
  horiz = FALSE,inset = -0.42
)

# Plot climate for morice TSA


# note that there are some weird climate values when extracted from climateBC using Tongli's R code.
ras.info<-dbGetQuery(mySim$castordb, "Select * from raster_info limit 1;")
clim<-raster(extent(ras.info$xmin, ras.info$xmax, ras.info$ymin, ras.info$ymax), nrow = ras.info$nrow, ncol = ras.info$ncell/ras.info$nrow, vals =0)
    
clim[]<-climdat$PPT08
plot(clim)
plot(clim, col=rev(topo.colors(200)))


hist(climdat$PPT08)

```


```{r}

library(dplyr)
library(purrr)
fireReport <- list.files(path="C:/Work/caribou/castor/R/SpaDES-modules/fireCastor/outputs/", pattern = "fireReport", full.names = TRUE) %>% map_dfr(readRDS) 


library(ggplot2)
# Basic scatter plot
ggplot(fireReport, aes() + 
         geom_point(x=(timeperiod * 5), y=totalareaburned))+
  geom_smooth() +
  geom_point(x=(timeperiod * 5), y=thlbburned))+
  geom_smooth()

fireReport %>%
  tidyr::gather(key,value, totalareaburned, thlbburned) %>%
  ggplot(aes(x=timeperiod, y=value, colour=key)) +
  geom_point() + geom_smooth()  +xlab("Time period") + ylab("Area burned (ha)") + scale_x_discrete(limits=c("1","2","3", "4", "5", "6", "7", "8","9", "10"),
                                                                                                   labels=c("2025", "", "2035", "", "2045", "", "2055", "", "2065", "", "2075"))
# + scale_x_discrete(labels=c("2" = "2030", "4" = "2040", "6" = "2050", "8" = "2060", "10" = "2070"))


# plot raster of harvest and fire

library(sp)
library(sf)
#> Linking to GEOS 3.6.1, GDAL 2.2.3, PROJ 4.9.3
library(dplyr, warn.conflicts = F)
library(ggmap, quietly = T)
library(raster)

harvestblocks<-terra::rast("C:\\Work\\caribou\\castor\\morice_bau_Morice_TSA_harvestBlocks.tif")
harvestblocks_df<-as.data.frame(harvestblocks, xy=TRUE)

harvestblocks_df_5<-harvestblocks_df %>% filter(layer <6)

harvestblocks_df<-data.table::data.table(harvestblocks_df)
harvestblocks_df[layer==0, layer:=0]
harvestblocks_df[layer==5, layer:=2]
harvestblocks_df[layer>5, layer:=0]

fire_rast<-terra::rast("C:\\Work\\caribou\\castor\\burn_polygons_5.tif")
fire_rast_df <- as.data.frame(fire_rast, xy = TRUE) 
fire_rast_df$burn_polygons_5<-as.factor(fire_rast_df$burn_polygons_5)
fire_rast_df<- fire_rast_df %>% rename(layer = burn_polygons_5)

dat<-rbind(harvestblocks_df, fire_rast_df)
dat$layer<-as.character(dat$layer)
dat1<-dat %>% filter(layer!="0")




coordinates(dat1) <- ~x+y
proj4string(dat1) <- CRS("+init=epsg:3005")

dat1 <- st_as_sf(dat1,coords = 1:2)
unique(dat1$layer)

plot(dat1, pch=19, cex=0.4 )

```

