---
title: " Data Management Guidelines for the Caribou and Land Use Simulator"
author: "Tyler Muhly"
date: "02/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (DBI)
library (here)
library (data.table)

source (here ("R/functions/R_Postgres.R"))

```

Like any quantitative model, the caribou and land use simulator (CLUS) has a specific framework for how it uses datasets in the modeling platform. For details on this framework, see the *Getting Started with CLUS* documentation. Here we describe how to document those datasets that are developed and used within the CLUS model. 

### The Data Tracking Table
Spatial and aspatial data and parameters used in CLUS are stored in [PostgreSQL databases](https://www.postgresql.org/). We uploaded a data tracking table called 'pgdbs_data_list' to a CLUS PostgreSQL database that describes each 'table' (i.e., dataset) in each PostgreSQL database used by the CLUS model or CLUS web applications. This tracking table is intended to help CLUS users understand the origin, status and appropriate end-use of datasets in the CLUS model.  

```{r, write original spreadsheet to postgres, eval = F, echo = F, warning = F, message = F}
# Example scipt to delete row in trackign table
pgdbs_data_list <- read.csv ("C:\\Work\\pgdbs_data_list.csv",
                               header = T,
                               sep = ",") 
conn <- DBI::dbConnect(dbDriver("PostgreSQL"), 
                       host = keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                       dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                       port='5432' ,
                       user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                       password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
DBI::dbWriteTable(conn, c("public", "pgdbs_data_list"), 
                  value = pgdbs_data_list, 
                  row.names = FALSE, overwrite = TRUE)
```

The data tracking table (pgdbs_data_list) consists of 11 fields. Each row represents a unique data 'table' in a PostgreSQL database. The *computer*, *database* and *schema* fields identify the location of the PostgreSQL database that the table is stored in, and the *table_name* field identifies the name of the table in the database. The *type* field identifies whether the data table is one of three types: an aspatial 'table', spatial 'polygon', 'point' or 'line' or spatial 'raster'.  The *script* field identifies where in the CLUS script repository the data was documented and created. For example, many of the rasters and tables used to define provincial management objectives, such as visual quality objectives, are documented and created in *clus\R\Params\prov_manage_objs.Rmd*. The *source* field describes in brief what the data is and where the original data were obtained, and the *public* field describes whether the data can be shared with the public ('Yes'), or must be kept internal and confidential ('No'). The *last_updated* field documents the year the data was added to the database or last modified, and the *next_update* field documents the year the data should ideally be updated. For example, the consolidated cutblocks data should ideally be updated annually. If the data is not going to be updated and the data should be maintained long-term in the database (e.g., a 'static' landscape dataset such as a digital elevation model) the *next_update* field can be set to 'NA'. When it is not clear when an update is needed but we anticipate that a dataset will need to be updated at some point soon (e.g., the spatial boundaries of caribou population ranges) the *next_update* field can be set to 'as needed'. Finally, the *where_used* field documents where in the CLUS model the table is used, for example, in the dataLoaderCLUS module, or the CLUS scenario application. If the data are no longer used anywhere, but you don't want to delete it, the *where_used* field can be set to 'archive' (adn teh data moved to teh archive schema of the database - see below). If the data are no longer used anywhere, but you think it should be deleted the *where_used* field can be set to 'deprecated' (see below). 

### Updating the Tracking Table
The data tracking table (pgdbs_data_list) should be updated whenever a new dataset is added to or modified in the CLUS model or web applications. For example, if a new management area with a new management objective is defined and created in the database it should be documented by adding a new row to the tracking table. 

When adding new data that you anticipate will be updated on a annual basis, include the year it was uploaded to the end of the table name, e.g., 'new_table_2020'. If you anticipate the data will be updated monthly, include the year and month at the end of the table name, e.g., 'new_table_202011'. 

```{r, add new row (new data) to the table, eval = F, echo = T, warning = F, message = F}
# Example scipt to add new row to tracking table

# load the existing data tracking table
conn <- DBI::dbConnect(dbDriver("PostgreSQL"), 
                       host = keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                       dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                       port='5432' ,
                       user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                       password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
pgdbs_data_list <- getTableQuery("SELECT * from public.pgdbs_data_list;")

#Create new row for table
new_data <- data.table (computer = 'test', # e.g., 206.12.91.188 or DC052586 
                        database = 'test', # clus
                        schema = 'test', # caribou, public or rast
                        table_name = 'test', # add year adn month if relevant
                        type = 'test', # polygon, point, line, raster or table
                        script = 'test', # name and location of script to produce the data
                        source = 'test', # description of data source
                        public = 'test', # Yes, if can be shared with public, otherwise No
                        last_updated = 'test', # year when data added
                        next_update = 'test', # year when data should ideally be updated
                        where_used = 'test' # name of module of application where data used, set to 'deprecated' if no longer used, and 'archive' if moved to the archive schema
                        )
# merge tables
pgdbs_data_list_new <- merge (pgdbs_data_list, new_data, all = T)
# re-upload data to postgres
DBI::dbWriteTable(conn, c("public", "pgdbs_data_list"), 
                  value = pgdbs_data_list_new, 
                  row.names = FALSE, overwrite = TRUE)
```

If an existing dataset is updated in the database, the *last_updated* and *next_update* fields needs to be updated and documented in the tracking table (pgdbs_data_list).  

```{r, modify an existing row (table), eval = F, echo = T, warning = F, message = F}
# Example scipt to modify row in tracking table
conn <- DBI::dbConnect(dbDriver("PostgreSQL"), 
                       host = keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                       dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                       port='5432' ,
                       user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                       password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
# edit row
dbExecute (conn, 
           "UPDATE public.pgdbs_data_list set last_updated = '2020' where table_name = 'test';") # This example will edit the year of last update for the table called 'test'

```

### Deleting or Archiving Data
If data is no longer needed in the database it should be labelled as ‘deprecated’. This data should be kept in the database for one year, and re-evaluated on an annual basis. If the data is not needed after a year, it can be deleted or archived. If it is unlikely the data will be used in future analyses, delete it.  

```{r, delete an existing row (table), eval = F, echo = T, warning = F, message = F}
# Example scipt to delete row in trackign table
conn <- DBI::dbConnect(dbDriver("PostgreSQL"), 
                       host = keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                       dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                       port='5432' ,
                       user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                       password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
# label data as deprecated
dbExecute (conn, 
           "UPDATE public.pgdbs_data_list set where_used = 'deprecated' where table_name = 'test';") # This example will edit the year of last update for the table called 'test'

# delete row
dbExecute (conn, 
           "DELETE FROM public.pgdbs_data_list WHERE table_name = 'test';") # This example will delete the table called 'test'

```

If the data are no longer used, but there is some anticipated need to keep it for future analysis, it can be archived. In these cases, copy the table to the 'archive' schema in the database, and label the relevant row in the data tracking table as 'archive'. Also, change the *schema* to 'archive'.

```{r, archive a table, eval = F, echo = T, warning = F, message = F}
#Example scipt to archive data
conn <- DBI::dbConnect(dbDriver("PostgreSQL"), 
                       host = keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                       dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                       port='5432' ,
                       user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                       password= keyring::key_get('dbpass', keyring = 'postgreSQL'))
# copy table to archive schema and delete from active schema
dbExecute (conn, 
           "SELECT * INTO archive.cb_sum FROM public.cb_sum;")

# label data as 'archive'
dbExecute (conn, 
           "UPDATE public.pgdbs_data_list set where_used = 'archive' where table_name = 'test';") # This example will set the table called 'test' to the 'archive' status

# update the schema
dbExecute (conn, 
           "UPDATE public.pgdbs_data_list set schema = 'archive' where table_name = 'test';") # This example will set the schema to 'archive' for the table called 'test' 
```

### Tracking Table Change Log
Changes to the tracking table can be documented in the code chunk below. We can use this, and the orignal .csv (archived in *spatialfiles2.bcgov/archive/FOR/VIC/HTS/ANA/PROJECTS/CLUS/Data/pgdbs_data_list.csv*) to recreate the table in the event we lose the PostgreSQL database table.

```{r, change log, eval = F, echo = T, warning = F, message = F}
# Change Log
conn <- DBI::dbConnect(dbDriver("PostgreSQL"), 
                       host = keyring::key_get('dbhost', keyring = 'postgreSQL'), 
                       dbname = keyring::key_get('dbname', keyring = 'postgreSQL'), 
                       port='5432' ,
                       user=keyring::key_get('dbuser', keyring = 'postgreSQL') ,
                       password= keyring::key_get('dbpass', keyring = 'postgreSQL'))

# updates to refer to amalgamated caribou Param scripts
dbExecute (conn, 
           "UPDATE public.pgdbs_data_list SET script = 'clus\\R\\Params\\caribou_management_areas.Rmd' WHERE (table_name = 'caribou_herd') OR (table_name = 'bc_carib_poly_20090904') OR (table_name = 'bc_caribou_herd_boundary_v20200507') OR (table_name = 'du6_bounds') OR (table_name = 'du7_bounds') OR (table_name = 'du8_bounds') OR (table_name = 'du9_bounds') OR (table_name = 'caribou_herd_vat') OR (table_name = 'caribou_herd_25');")
dbExecute (conn, 
           "UPDATE public.pgdbs_data_list set script = 'clus\\R\\Params\\caribou_management_areas.Rmd' where (table_name = 'scenario_central_grp_proposed_luo') OR (table_name = 'scenario_central_grp_proposed_luo_buffer_vat') OR (table_name = 'scenario_central_grp_proposed_luo_matrix_vat') OR (table_name = 'scenario_central_grp_proposed_luo_vat') OR (table_name = 'zone_scenario_central_grp_proposed_luo') OR (table_name = 'zone_scenario_central_grp_proposed_luo_buffer') OR (table_name = 'zone_scenario_central_grp_proposed_luo_matrix') OR (table_name = 'central_grp_proposed_luo') OR (table_name = 'central_grp_proposed_luo_buffer') OR (table_name = 'central_grp_proposed_luo_matrix') OR (table_name = 'zone_cond_partnership_agreement');")
dbExecute (conn, 
           "UPDATE public.pgdbs_data_list set script = 'clus\\R\\Params\\caribou_management_areas.Rmd' where (table_name = 'mtn_caribou_pa_jan_2020') OR (table_name = 'partnership_agreement_vat') OR (table_name = 'aoi_partnership_agree');")



dbExecute (conn, 
           "UPDATE public.pgdbs_data_list set script = 'clus\\R\\Params\\caribou_management_areas.Rmd' where (table_name = 'criticalhabitat_bc_vat') OR (table_name = 'crithab') OR (table_name = 'criticalhabitat_barkerville_vat') OR (table_name = 'criticalhabitat_barkerville_vat') OR (table_name = 'criticalhabitat_burnt_pine_vat') OR (table_name = 'criticalhabitat_central_rockies_vat') OR (table_name = 'criticalhabitat_central_selkirks_vat') OR (table_name = 'criticalhabitat_charlotte_alplands_vat') OR (table_name = 'criticalhabitat_columbia_north_vat') OR (table_name = 'criticalhabitat_columbia_south_vat') OR (table_name = 'criticalhabitat_frisby_boulder_vat') OR (table_name = 'criticalhabitat_graham_vat') OR (table_name = 'criticalhabitat_groundhog_vat') OR (table_name = 'criticalhabitat_hart_ranges_vat') OR (table_name = 'criticalhabitat_itcha_ilgachuz_vat') OR (table_name = 'criticalhabitat_itchas_vat') OR (table_name = 'criticalhabitat_kennedy_siding_vat') OR (table_name = 'criticalhabitat_moberly_vat') OR (table_name = 'criticalhabitat_monashee_vat') OR (table_name = 'criticalhabitat_narraway_vat') OR (table_name = 'criticalhabitat_narrow_lake_vat') OR (table_name = 'criticalhabitat_north_cariboo_vat') OR (table_name = 'criticalhabitat_purcell_central_vat') OR (table_name = 'criticalhabitat_purcells_south_vat') OR (table_name = 'criticalhabitat_quintette_vat') OR (table_name = 'criticalhabitat_rainbows_vat') OR (table_name = 'criticalhabitat_redrock_prairie_creek_vat') OR (table_name = 'criticalhabitat_south_selkirks_vat') OR (table_name = 'criticalhabitat_telkwa_vat') OR (table_name = 'criticalhabitat_wells_gray_north_vat') OR (table_name = 'criticalhabitat_wells_gray_south_vat') OR (table_name = 'zone_cond_eccc_barkerville_crithab') OR (table_name = 'zone_cond_eccc_burnt_pine_crithab')
OR (table_name = 'zone_cond_eccc_central_rockies_crithab') OR (table_name = 'zone_cond_eccc_central_selkirks_crithab') OR (table_name = 'zone_cond_eccc_charlotte_alplands_crithab') OR (table_name = 'zone_cond_eccc_columbia_north_crithab') OR (table_name =  'zone_cond_eccc_columbia_south_crithab') OR (table_name = 'zone_cond_eccc_frisby_boulder_crithab') OR (table_name = 'zone_cond_eccc_graham_crithab')
OR (table_name = 'zone_cond_eccc_groundhog_crithab') OR (table_name = 'zone_cond_eccc_hart_ranges_crithab') OR (table_name = 'zone_cond_eccc_itcha_ilgachuz_crithab') OR (table_name = 'zone_cond_eccc_kennedy_siding_crithab') OR (table_name = 'zone_cond_eccc_moberly_crithab')
OR (table_name = 'zone_cond_eccc_monashee_crithab') OR (table_name = 'zone_cond_eccc_narraway_crithab') OR (table_name = 'zone_cond_eccc_narrow_lake_crithab')
OR (table_name = 'zone_cond_eccc_north_cariboo_crithab') OR (table_name = 'zone_cond_eccc_purcell_central_crithab') OR (table_name = 'zone_cond_eccc_purcells_south_crithab') OR (table_name = 'zone_cond_eccc_quintette_crithab') OR (table_name = 'zone_cond_eccc_rainbows_crithab') OR (table_name = 'zone_cond_eccc_redrock_prairie_creek_crithab') OR (table_name = 'zone_cond_eccc_south_selkirks_crithab') OR (table_name = 'zone_cond_eccc_telkwa_crithab') OR (table_name = 'zone_cond_eccc_wells_gray_north_crithab') OR (table_name = 'zone_cond_eccc_wells_gray_south_crithab') OR (table_name = 'zone_eccc_barkerville_crithab')
OR (table_name = 'zone_eccc_burnt_pine_crithab') OR (table_name = 'zone_eccc_central_rockies_crithab') OR (table_name = 'zone_eccc_central_selkirks_crithab')
OR (table_name = 'zone_eccc_charlotte_alplands_crithab') OR (table_name = 'zone_eccc_columbia_north_crithab') OR (table_name = 'zone_eccc_columbia_south_crithab')
OR (table_name = 'zone_eccc_frisby_boulder_crithab') OR (table_name = 'zone_eccc_graham_crithab') OR (table_name = 'zone_eccc_groundhog_crithab') OR (table_name = 'zone_eccc_hart_ranges_crithab') OR (table_name = 'zone_eccc_itcha_ilgachuz_crithab')
OR (table_name = 'zone_eccc_kennedy_siding_crithab') OR (table_name = 'zone_eccc_moberly_crithab') OR (table_name = 'zone_eccc_monashee_crithab') OR (table_name = 'zone_eccc_narraway_crithab') OR (table_name = 'zone_eccc_narrow_lake_crithab') OR (table_name = 'zone_eccc_north_cariboo_crithab') OR (table_name =  'zone_eccc_purcell_central_crithab') OR (table_name = 'zone_eccc_purcells_south_crithab') OR (table_name = 'zone_eccc_quintette_crithab') OR (table_name = 'zone_eccc_rainbows_crithab')
OR (table_name = 'zone_eccc_redrock_prairie_creek_crithab') OR (table_name = 'zone_eccc_south_selkirks_crithab') OR (table_name = 'zone_eccc_telkwa_crithab') OR (table_name = 'zone_eccc_wells_gray_north_crithab') OR (table_name = 'zone_eccc_wells_gray_south_crithab') OR (table_name = 'zone_cond_bc_barkerville_crithab')
OR (table_name = 'zone_cond_bc_burnt_pine_crithab') OR (table_name = 'zone_cond_bc_central_rockies_crithab') OR (table_name = 'zone_cond_bc_central_selkirks_crithab') OR (table_name = 'zone_cond_bc_charlotte_alplands_crithab') OR (table_name = 'zone_cond_bc_columbia_north_crithab') OR (table_name = 'zone_cond_bc_columbia_south_crithab') OR (table_name = 'zone_cond_bc_crithab') OR (table_name = 'zone_cond_bc_frisby_boulder_crithab') OR (table_name = 'zone_cond_bc_graham_crithab') OR (table_name = 'zone_cond_bc_groundhog_crithab') OR (table_name = 'zone_cond_bc_hart_ranges_crithab') OR (table_name = 'zone_cond_bc_itcha_ilgachuz_crithab') OR (table_name = 'zone_cond_bc_kennedy_siding_crithab') OR (table_name = 'zone_cond_bc_moberly_crithab') OR (table_name = 'zone_cond_bc_monashee_crithab') OR (table_name = 'zone_cond_bc_narraway_crithab') OR (table_name = 'zone_cond_bc_narrow_lake_crithab') OR (table_name = 'zone_cond_bc_north_cariboo_crithab') OR (table_name = 'zone_cond_bc_purcell_central_crithab') OR (table_name = 'zone_cond_bc_purcells_south_crithab') OR (table_name = 'zone_cond_bc_quintette_crithab') OR (table_name = 'zone_cond_bc_rainbows_crithab') OR (table_name = 'zone_cond_bc_redrock_prairie_creek_crithab') OR (table_name = 'zone_cond_bc_south_selkirks_crithab') OR (table_name = 'zone_cond_bc_telkwa_crithab') OR (table_name = 'zone_cond_bc_wells_gray_north_crithab') OR (table_name = 'zone_cond_bc_wells_gray_south_crithab') OR (table_name = 'zone_bc_barkerville_crithab')
OR (table_name = 'zone_bc_burnt_pine_crithab') OR (table_name = 'zone_bc_central_rockies_crithab') OR (table_name = 'zone_bc_charlotte_alplands_crithab')
OR (table_name = 'zone_bc_columbia_north_crithab') OR (table_name = 'zone_bc_columbia_south_crithab') OR (table_name = 'zone_bc_crithab') OR (table_name = 'zone_bc_frisby_boulder_crithab') OR (table_name = 'zone_bc_graham_crithab') OR (table_name = 'zone_bc_groundhog_crithab') OR (table_name = 'zone_bc_hart_ranges_crithab') OR (table_name = 'zone_bc_itcha_ilgachuz_crithab') OR (table_name = 'zone_bc_kennedy_siding_crithab') OR (table_name = 'zone_bc_moberly_crithab') OR (table_name = 'zone_bc_monashee_crithab') OR (table_name = 'zone_bc_narraway_crithab') OR (table_name = 'zone_bc_narrow_lake_crithab') OR (table_name = 'zone_bc_north_cariboo_crithab') OR (table_name = 'zone_bc_purcell_central_crithab') OR (table_name = 'zone_bc_purcells_south_crithab') OR (table_name = 'zone_bc_quintette_crithab') OR (table_name = 'zone_bc_rainbows_crithab') OR (table_name = 'zone_bc_redrock_prairie_creek_crithab') OR (table_name = 'zone_bc_south_selkirks_crithab')
OR (table_name = 'zone_bc_telkwa_crithab') OR (table_name = 'zone_bc_wells_gray_north_crithab') OR (table_name = 'zone_bc_wells_gray_south_crithab') OR (table_name = 'zone_bc_bounds_atlin_noharvest') OR (table_name = 'zone_bc_bounds_barkerville_noharvest') OR (table_name = 'zone_bc_bounds_burnt_pine_noharvest') OR (table_name = 'zone_bc_bounds_calendar_noharvest')
OR (table_name = 'zone_bc_bounds_carcross_noharvest') OR (table_name = 'zone_bc_bounds_central_rockies_noharvest') OR (table_name = 'zone_bc_bounds_central_selkirks_noharvest') OR (table_name = 'zone_bc_bounds_charlotte_alplands_noharvest') OR (table_name = 'zone_bc_bounds_chase_noharvest') OR (table_name = 'zone_bc_bounds_chinchaga_noharvest') OR (table_name = 'zone_bc_bounds_columbia_north_noharvest') OR (table_name = 'zone_bc_bounds_columbia_south_noharvest') OR (table_name = 'zone_bc_bounds_edziza_noharvest') OR (table_name = 'zone_bc_bounds_finlay_noharvest') OR (table_name = 'zone_bc_bounds_frisby_boulder_noharvest') OR (table_name = 'zone_bc_bounds_frog_noharvest') OR (table_name = 'zone_bc_bounds_gataga_noharvest') OR (table_name = 'zone_bc_bounds_george_mountain_noharvest') OR (table_name = 'zone_bc_bounds_graham_noharvest') OR (table_name = 'zone_bc_bounds_groundhog_noharvest') OR (table_name = 'zone_bc_bounds_hart_ranges_noharvest') OR (table_name = 'zone_bc_bounds_horseranch_noharvest') OR (table_name = 'zone_bc_bounds_itcha_ilgachuz_noharvest') OR (table_name = 'zone_bc_bounds_kennedy_siding_noharvest') OR (table_name = 'zone_bc_bounds_level_kawdy_noharvest') OR (table_name = 'zone_bc_bounds_liard_plateau_noharvest') OR (table_name = 'zone_bc_bounds_little_rancheria_noharvest') OR (table_name = 'zone_bc_bounds_maxhamish_noharvest') OR (table_name = 'zone_bc_bounds_moberly_noharvest') OR (table_name = 'zone_bc_bounds_monashee_noharvest') OR (table_name = 'zone_bc_bounds_muskwa_noharvest') OR (table_name = 'zone_bc_bounds_narraway_noharvest') OR (table_name = 'zone_bc_bounds_narrow_lake_noharvest') OR (table_name = 'zone_bc_bounds_north_cariboo_noharvest') OR (table_name = 'zone_bc_bounds_pink_mountain_noharvest') OR (table_name = 'zone_bc_bounds_purcell_central_noharvest') OR (table_name = 'zone_bc_bounds_purcells_south_noharvest') OR (table_name = 'zone_bc_bounds_quintette_noharvest') OR (table_name = 'zone_bc_bounds_rabbit_noharvest') OR (table_name = 'zone_bc_bounds_rainbows_noharvest') OR (table_name = 'zone_bc_bounds_redrock_prairie_creek_noharvest') OR (table_name = 'zone_bc_bounds_scott_noharvest') OR (table_name = 'zone_bc_bounds_snake_sahtaneh_noharvest') OR (table_name = 'zone_bc_bounds_south_selkirks_noharvest') OR (table_name = 'zone_bc_bounds_spatsizi_noharvest') OR (table_name = 'zone_bc_bounds_swan_lake_noharvest') OR (table_name = 'zone_bc_bounds_takla_noharvest') OR (table_name = 'zone_bc_bounds_telkwa_noharvest') OR (table_name = 'zone_bc_bounds_thutade_noharvest') OR (table_name = 'zone_bc_bounds_tsenaglode_noharvest') OR (table_name = 'zone_bc_bounds_tweedsmuir_noharvest') OR (table_name = 'zone_bc_bounds_wells_gray_north_noharvest') OR (table_name = 'zone_bc_bounds_wells_gray_south_noharvest') OR (table_name = 'zone_bc_bounds_westside_fort_nelson_noharvest') OR (table_name = 'zone_bc_bounds_wolverine_noharvest') OR (table_name = 'zone_bc_bounds_atlin_nh') OR (table_name = 'zone_bc_bounds_barkerville_nh') OR (table_name = 'zone_bc_bounds_burnt_pine_nh') OR (table_name = 'zone_bc_bounds_calendar_nh') OR (table_name = 'zone_bc_bounds_carcross_nh') OR (table_name = 'zone_bc_bounds_central_rockies_nh') OR (table_name = 'zone_bc_bounds_central_selkirks_nh') OR (table_name = 'zone_bc_bounds_charlotte_alplands_nh') OR (table_name = 'zone_bc_bounds_chase_nh') OR (table_name = 'zone_bc_bounds_chinchaga_nh') OR (table_name = 'zone_bc_bounds_columbia_north_nh') OR (table_name = 'zone_bc_bounds_columbia_south_nh') OR (table_name = 'zone_bc_bounds_edziza_nh') OR (table_name = 'zone_bc_bounds_finlay_nh') OR (table_name = 'zone_bc_bounds_frisby_boulder_nh') OR (table_name = 'zone_bc_bounds_frog_nh')
OR (table_name = 'zone_bc_bounds_gataga_nh') OR (table_name = 'zone_bc_bounds_george_mountain_nh') OR (table_name = 'zone_bc_bounds_graham_nh')
OR (table_name = 'zone_bc_bounds_groundhog_nh') OR (table_name = 'zone_bc_bounds_hart_ranges_nh') OR (table_name = 'zone_bc_bounds_horseranch_nh') OR (table_name = 'zone_bc_bounds_itcha_ilgachuz_nh') OR (table_name = 'zone_bc_bounds_kennedy_siding_nh') OR (table_name = 'zone_bc_bounds_level_kawdy_nh')
OR (table_name = 'zone_bc_bounds_liard_plateau_nh') OR (table_name = 'zone_bc_bounds_little_rancheria_nh') OR (table_name = 'zone_bc_bounds_maxhamish_nh') OR (table_name = 'zone_bc_bounds_moberly_nh') OR (table_name = 'zone_bc_bounds_monashee_nh')
OR (table_name = 'zone_bc_bounds_muskwa_nh') OR (table_name = 'zone_bc_bounds_narraway_nh')
OR (table_name = 'zone_bc_bounds_narrow_lake_nh') OR (table_name = 'zone_bc_bounds_north_cariboo_nh') OR (table_name = 'zone_bc_bounds_pink_mountain_nh')
OR (table_name = 'zone_bc_bounds_pinkmountain_nh') OR (table_name = 'zone_bc_bounds_purcell_central_nh') OR (table_name = 'zone_bc_bounds_purcells_south_nh')
OR (table_name = 'zone_bc_bounds_quintette_nh') OR (table_name = 'zone_bc_bounds_rabbit_nh')
OR (table_name = 'zone_bc_bounds_rainbows_nh') OR (table_name = 'zone_bc_bounds_redrock_prairie_creek_nh') OR (table_name = 'zone_bc_bounds_scott_nh')
OR (table_name = 'zone_bc_bounds_snake_sahtaneh_nh') OR (table_name = 'zone_bc_bounds_south_selkirks_nh') OR (table_name = 'zone_bc_bounds_spatsizi_nh') OR (table_name = 'zone_bc_bounds_swan_lake_nh') OR (table_name = 'zone_bc_bounds_takla_nh')
OR (table_name = 'zone_bc_bounds_telkwa_nh') OR (table_name = 'zone_bc_bounds_thutade_nh')
OR (table_name = 'zone_bc_bounds_tsenaglode_nh') OR (table_name = 'zone_bc_bounds_tweedsmuir_nh') OR (table_name = 'zone_bc_bounds_wells_gray_north_nh')
OR (table_name = 'zone_bc_bounds_wells_gray_south_nh') OR (table_name = 'zone_bc_bounds_westside_fort_nelson_nh') OR (table_name = 'zone_bc_bounds_wolverine_nh');")





OR (table_name = '')
OR (table_name = '')
OR (table_name = '')
OR (table_name = '')

zone_nh_crit_barkerville_crithab
zone_nh_crit_burnt_pine_crithab
zone_nh_crit_central_rockies_crithab
zone_nh_crit_central_selkirks_crithab
zone_nh_crit_charlotte_alplands_crithab
zone_nh_crit_columbia_north_crithab
zone_nh_crit_columbia_south_crithab
zone_nh_crit_frisby_boulder_crithab
zone_nh_crit_graham_crithab
zone_nh_crit_groundhog_crithab
zone_nh_crit_hart_ranges_crithab
zone_nh_crit_itcha_ilgachuz_crithab
zone_nh_crit_kennedy_siding_crithab
zone_nh_crit_moberly_crithab
zone_nh_crit_monashee_crithab
zone_nh_crit_narraway_crithab
zone_nh_crit_narrow_lake_crithab
zone_nh_crit_north_cariboo_crithab
zone_nh_crit_purcell_central_crithab
zone_nh_crit_purcells_south_crithab
zone_nh_crit_quintette_crithab
zone_nh_crit_rainbows_crithab
zone_nh_crit_redrock_prairie_creek_crithab
zone_nh_crit_south_selkirks_crithab
zone_nh_crit_telkwa_crithab
zone_nh_crit_wells_gray_north_crithab
zone_nh_crit_wells_gray_south_crithab
zone_cond_nh_crit_barkerville_crithab
zone_cond_nh_crit_burnt_pine_crithab
zone_cond_nh_crit_central_rockies_crithab
zone_cond_nh_crit_central_selkirks_crithab
zone_cond_nh_crit_charlotte_alplands_crithab
zone_cond_nh_crit_columbia_north_crithab
zone_cond_nh_crit_columbia_south_crithab
zone_cond_nh_crit_frisby_boulder_crithab
zone_cond_nh_crit_graham_crithab
zone_cond_nh_crit_groundhog_crithab
zone_cond_nh_crit_hart_ranges_crithab
zone_cond_nh_crit_itcha_ilgachuz_crithab
zone_cond_nh_crit_kennedy_siding_crithab
zone_cond_nh_crit_moberly_crithab
zone_cond_nh_crit_monashee_crithab
zone_cond_nh_crit_narraway_crithab
zone_cond_nh_crit_narrow_lake_crithab
zone_cond_nh_crit_north_cariboo_crithab
zone_cond_nh_crit_purcell_central_crithab
zone_cond_nh_crit_purcells_south_crithab
zone_cond_nh_crit_quintette_crithab
zone_cond_nh_crit_rainbows_crithab
zone_cond_nh_crit_redrock_prairie_creek_crithab
zone_cond_nh_crit_south_selkirks_crithab
zone_cond_nh_crit_telkwa_crithab
zone_cond_nh_crit_wells_gray_north_crithab
zone_cond_nh_crit_wells_gray_south_crithab





```

