---
title: "Forest Harvest Trends by Caribou Range"
author: "Tyler Muhly"
date: "April 6, 2018"
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F)
```

## Introduction
Here I calculate recent trends in forest harvest by caribou range for the Skeena and Omineca regions of British Columbia.  

## Methods
The spatial analyses were completed in ArcGIS 10.3. Data were downloaded from Data BC, including caribou range boundaries (downloadable 
from: <https://catalogue.data.gov.bc.ca/dataset/caribou-herd-locations-for-bc>) and cutblocks (downloadable 
from: <https://catalogue.data.gov.bc.ca/dataset/harvested-areas-of-bc-consolidated-cutblocks->). 

I only estimated historical harvest rate within the boundaries of extant caribou herds. In ArcGIS I took the cutblock data and unioned it with caribou ranges. The resulting data was exported from ArcGIS and imported into Program R for analysis. 

```{r load packages and data, include = F, results = 'hide', message = F, warning = F}
library (dplyr)
library (ggplot2)
library (ggpmisc)
library (maptools)
library (classInt)
library (RColorBrewer)
options (scipen = 999)
cut.data <- read.table ('G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\cutblock_area_in_caribou_range_by_year_and_management_unit.csv', header = T, sep = ",")
fire.data <- read.table ('G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\analysis\\timber\\data\\fire_area_in_caribou_range_by_year_and_management_unit.csv', header = T, sep = ",")
```

## Results
The following figures show the amount of area harvested annually from 1965 to 2015 within each extant caribou range in the Skeena and Omineca regions. A linear trend line has been added to illustrate the possible trend in harvest. However, these were not statistically evaluated and should not be used as a rigorous indicator of harvest trend. Caribou herd ranges with no forest harvest from 1965 to 2015 (i.e., Swan Lake, Level Kawdy, Tsenaglode, Ediza, Liard Plateau, Rabbit, Gataga, and Frog) are not illustrated. 

```{r summarize and graph total cut by year and caribou range, include = T, results = 'markup', message = F, warning = F}
cut.data.slim <- cut.data %>%
                       select (Management.Unit, Harvest.Year, Area.Harvestedha, HERD_NAME) 
cut.data.bou.rge <- cut.data.slim %>%
                    group_by (HERD_NAME, Harvest.Year) %>%                    
                    summarise (sum (Area.Harvestedha)) 
colnames (cut.data.bou.rge) [3] <- "area.harvest.ha" 
# write.csv (cut.data.bou.rge, file = "G:\\!Workgrp\\Analysts\\tmuhly\\Caribou\\sdm_alecdale\\cut_by_caribou_range.csv")
# herd.list <- data.frame (unique (cut.data.bou.rge$HERD_NAME))
# herd.list [2, 1]

plot.fxn <- function (herd.name) {
  mypath <- file.path ("G:", "!Workgrp", "Analysts", "tmuhly", "Caribou", "sdm_alecdale", "analysis", "timber", "plots", paste (herd.name, ".tiff", sep = ""))
  plot.data <- cut.data.bou.rge %>%
                 filter (HERD_NAME == herd.name)
print (ggplot (data = plot.data, aes (x = Harvest.Year, y = area.harvest.ha)) +
                    geom_point () +
                    geom_smooth (data = plot.data, method = "lm", se = F) +
                    xlab ("Harvest Year") +
                    ylab ("Area Harvested (ha)") +
                    ggtitle (herd.name) +
                    theme (axis.text = element_text (size = 12),
                           axis.title = element_text (size = 14),
                           plot.title = element_text (hjust = 0.5)) +
                    theme_classic () + # no gridlines and white background
                    scale_x_continuous (breaks = c (1965, 1970, 1975, 1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015), labels = c ("1965", "1970", "1975", "1980", "1985", "1990", "1995", "2000", "2005", "2010", "2015"), limits = c (1965, 2015)) +
                   scale_y_continuous (limits = c (0, NA)))
# ggsave (plot, filename = mypath, units="in", width = 5, height = 4, dpi = 300, compression = 'lzw') 
}

plot.fxn (herd.name = "Carcross")
plot.fxn (herd.name = "Atlin")
# plot.fxn (herd.name = "Swan Lake")
plot.fxn (herd.name = "Little Rancheria")
# plot.fxn (herd.name = "Level Kawdy")
plot.fxn (herd.name = "Horseranch")
# plot.fxn (herd.name = "Tsenaglode")
# plot.fxn (herd.name = "Ediza")
plot.fxn (herd.name = "Spatsizi")
# plot.fxn (herd.name = "Liard Plateau")
# plot.fxn (herd.name = "Rabbit")
# plot.fxn (herd.name = "Gataga")
# plot.fxn (herd.name = "Frog")
plot.fxn (herd.name = "Telkwa")
plot.fxn (herd.name = "Tweedsmuir")
plot.fxn (herd.name = "Rainbows")
plot.fxn (herd.name = "Itcha-Ilgachuz")
plot.fxn (herd.name = "Charlotte Alplands")
plot.fxn (herd.name = "Finlay")
plot.fxn (herd.name = "Pink Mountain")
plot.fxn (herd.name = "Muskwa")
plot.fxn (herd.name = "Graham")
plot.fxn (herd.name = "Chase")
plot.fxn (herd.name = "Wolverine")
plot.fxn (herd.name = "Takla")
plot.fxn (herd.name = "Scott")
plot.fxn (herd.name = "Moberly")
plot.fxn (herd.name = "Burnt Pine")
plot.fxn (herd.name = "Kennedy Siding")
plot.fxn (herd.name = "Quintette")
plot.fxn (herd.name = "Narraway")
plot.fxn (herd.name = "Hart Ranges")
```
